### 2020-08-06 main.tex
remove renv

% !TeX program = pdfLaTeX
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{textcomp}
\usepackage[hyphens]{url} % not crucial - just used below for the URL
\usepackage{hyperref}
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.3in}%
\addtolength{\topmargin}{-.8in}%

%% load any required packages here
\setlength {\marginparwidth }{2cm}

\usepackage{mathtools,amssymb,booktabs,longtable,todonotes,amsthm} \def\mod{~\text{mod}~}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\begin{document}

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\if0\blind
{
  \title{\bf Visualizing probability distributions across bivariate cyclic temporal granularities}

  \author{
        Sayani Gupta \thanks{Email: \href{mailto:Sayani.Gupta@monash.edu}{\nolinkurl{Sayani.Gupta@monash.edu}}} \\
    Department of Econometrics and Business Statistics, Monash University\\
     and \\     Rob J Hyndman \\
    Department of Econometrics and Business Statistics, Monash University\\
     and \\     Dianne Cook \\
    Department of Econometrics and Business Statistics, Monash University\\
     and \\     Antony Unwin \\
    University of Augsburg\\
      }
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Visualizing probability distributions across bivariate cyclic temporal granularities}
  \end{center}
  \medskip
} \fi

\bigskip
\begin{abstract}
Deconstructing a time index into time granularities can assist in exploration and automated analysis of large temporal data sets. This paper describes several classes of time deconstructions using linear and cyclic time granularities. Linear time granularities respect the linear progression of time such as hours, days, weeks and months with respect to a baseline. Cyclic time granularities can be circular such as hour of the day, quasi-circular such as day of the month, and aperiodic such as public holidays. The hierarchical structure of granularities creates a nested ordering. Hour of the day and second of the minute are single-order-up. Hour of the week is multiple-order-up, because it passes over day of the week. Methods are provided for creating all possible granularities for a time index. A recommendation algorithm provides an indication whether a pair of granularities can be meaningfully examined together, called a harmony or when they cannot, called a clash.

The time granularities can be used to create visualizations of the data to explore for periodicities, associations and anomalies. The granularities can be considered to be categorical variables (ordered or unordered) which induces a grouping of the observations. Assuming a numeric response variable, the resulting graphics are then displays of distributions compared across combinations of categorical variables. A recommendation of appropriate distribution display is provided.

The methods are implemented in the open source R package \texttt{gravitas}. The functions for creating granularities and exploring the associated time series are consistent with a tidy workflow (\citet{Grolemund2018-po}), and the probability distributions can be examined using the range of graphics available in \texttt{ggplot2} \citep{Wickham2009pk}.
\end{abstract}

\noindent%
{\it Keywords:} data visualization, statistical distributions, time granularities, calendar algebra, periodicties, grammar of graphics, R
\vfill

\newpage
\spacingset{1.45} % DON'T change the spacing!

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Temporal data are available at various resolutions depending on the context. Social and economic data like GDP is often collected and reported at coarse temporal scales such as monthly, quarterly or annually. With recent advancement in technology, more and more data are recorded at much finer temporal scales. Energy consumption may be collected every half an hour, energy supply may be collected every minute, and web search data might be recorded every second. As the frequency of data increases, the number of questions about the periodicity of the observed variable also increases. For example, data collected at an hourly scale can be analyzed using coarser temporal scales such as days, months or quarters. This approach requires deconstructing time in various possible ways called time granularities \citep{aigner2011visualization}.

It is important to be able to navigate through all of these time granularities to have multiple perspectives on the periodicity of the observed data. This idea aligns with the notion of EDA \citep{Tukey1977-jx} which emphasizes the use of multiple perspectives on data to help formulate hypotheses before proceeding to hypothesis testing. Visualizing probability distributions conditional on one or more granularities is an indispensable tool for exploration. Analysts are expected to comprehensively explore the many ways to view and consider temporal data. However, the plethora of choices and the lack of a systematic approach to do so quickly becomes overwhelming.

Calendar-based graphics \citep{wang2020calendar} are useful in visualizing patterns in the weekly and monthly structure, and are helpful when checking for the effects of weekends or special days. Any temporal data at sub-daily resolution can also be displayed using this type of faceting \citep{Wickham2009pk} with days of the week, month of the year, or another sub-daily deconstruction of time. But calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions. There can be many different time deconstructions, based on the calendar or on categorizations of time granularities.

Linear time granularities respect the linear progression of time and are non-repeating such as hours, days, weeks and months. One of the first attempts to characterize these granularities is due to \citet{Bettini1998-ed}. However, the definitions and rules defined are inadequate for describing cyclic or repeating granularities. Hence, there is a need to define some new cyclic time granularities, that can be useful in visualizations. Cyclic time granularities can be circular, quasi-circular or aperiodic. Examples of circular granularities are hour of the day and day of the week; an example of a quasi-circular granularity is day of the month; examples of aperiodic granularities are public holidays and school holidays.

Time deconstructions can also be based on the hierarchical structure of time. For example, hours are nested within days, days within weeks, weeks within months, and so on. Hence, it is possible to construct single-order-up granularities such as second of the minute, or multiple-order-up granularities such as second of the hour. The lubridate package \citep{Grolemund2011-vm} provides tools to access and manipulate common date-time objects. However, most of its accessor functions are limited to single-order-up granularities.

The motivation for this work stems from the desire to provide methods to better understand large quantities of measurements on energy usage reported by smart meters in households across Australia, and indeed many parts of the world. Smart meters currently provide half-hourly use in kWh for each household, from the time that they were installed, some as early as 2012. Households are distributed geographically and have different demographic properties such as the existence of solar panels, central heating or air conditioning. The behavioral patterns in households vary substantially, for example, some families use a dryer for their clothes while others hang them on a line, and some households might consist of night owls, while others are morning larks. It is common to see aggregates \citep[see][]{Goodwin_2012} of usage across households, such as half-hourly total usage by state, because energy companies need to plan for maximum loads on the network. But studying overall energy use hides the distribution of usage at finer scales, and makes it more difficult to find solutions to improve energy efficiency. We propose that the analysis of smart meter data will benefit from systematically exploring energy consumption by visualizing the probability distributions across different deconstructions of time to find regular patterns/anomalies. Although, the motivation came through the smart meter example, this is a problem that is relevant to any temporal data observed more than once per year.

This work provides tools for systematically exploring bivariate granularities within the tidy workflow. In particular, we

\begin{itemize}
\tightlist
\item
  provide a formal characterization of cyclic granularities;
\item
  facilitate manipulation of single- and multiple-order-up time granularities through cyclic calendar algebra;
\item
  develop an approach to check the feasibility of creating plots or drawing inferences for any two cyclic granularities;
\item
  recommend prospective probability distributions for exploring distributions of a univariate dependent variable across pair of granularities.
\end{itemize}

The remainder of the paper is organized as follows: Section \ref{sec:linear-time} provides some background material on linear granularities and calendar algebra for computing different linear granularities. Section \ref{sec:cyclic-gran} formally characterizes different cyclic time granularities by extending the framework of linear time granularities. Section \ref{sec:cyclic-calendar} introduces cyclic calendar algebra for computing cyclic time granularities. Section \ref{sec:data-structure} discusses the data structure for exploring the conditional distributions of the associated time series across pairs of cyclic time granularities. Section \ref{sec:visualization} discusses the role of different factors in constructing an informative and trustworthy visualization. Section \ref{sec:application} examines how systematic exploration can be carried out for a temporal and non-temporal application. Section \ref{sec:discussion} summarizes this paper and discusses possible future direction.

\hypertarget{sec:linear-time}{%
\section{Linear time granularities}\label{sec:linear-time}}

Discrete abstraction of time such as weeks, months or holidays can be thought of as ``time granularities''. Time granularities are \textbf{linear} if they respect the linear progression of time. There have been several attempts to provide a framework for formally characterizing time granularities, including \citet{Bettini1998-ed} which forms the basis of the work described here.

\hypertarget{definitions}{%
\subsection{Definitions}\label{definitions}}

\newtheorem{definition}{Definition}

\begin{definition}\label{def:definition}
A {\bf time domain} is a pair $(T; \le)$ where $T$ is a non-empty set of time instants and $\le$ is a total order on $T$.
\end{definition}

The time domain is assumed to be \emph{discrete}, and there is unique predecessor and successor for every element in the time domain except for the first and last.

\begin{definition}\label{def:index set}
There is a unique {\bf index set}, $Z=\{z: z \in \mathbb{Z}_{\geq 0}\}$, which map the time instants to a set of non-negative integers. Often, this is thought of as $t=0, \dots, T$.
\end{definition}

\begin{definition}\label{def:linear}
A {\bf linear granularity} is a mapping $G$ from the integers (the index set, $Z$) to subsets of the time domain such that:
  (1) if $i < j$ and $G(i)$ and $G(j)$ are non-empty, then each element of $G(i)$ is less
than all elements of $G(j)$; and
  (2) if $i < k < j$ and $G(i)$ and $G(j)$ are non-empty, then $G(k)$ is non-empty.
Each non-empty subset $G(i)$ is called a {\bf granule}.
\end{definition}

\noindent This implies that the granules in a linear granularity are non-overlapping, continuous and ordering is maintained. The indexing for each granule can also be associated with textual representation, called the label. A discrete time model often uses a fixed smallest linear granularity named by \citet{Bettini1998-ed} \textbf{bottom granularity}. \autoref{fig:linear-time} illustrates the linear time granularities. Here, ``hour'' is the bottom granularity and ``day'', ``week'', ``month'' and ``year'' are linear granularities which maps from index set to subsets of the hourly time domain. If we have ``hour'' running from \(\{0, 1, \dots,t\}\), we will have ``day'' running from \(\{0, 1, \dots, \lfloor t/24\rfloor\}\). These linear granularities are ordered with ordering guided by the index set which is a set of integers. Hence, they are uni-directional and non-repeating.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{Figs/linear-ex}

}

\caption{Illustration of time domain, linear granularities and index set. Hour, day, week, month and year are linear granularities and can also be considered to be time domains. These are ordered with ordering guided by integers and hence is unidirectional and non-repeating. Hours could also be considered the index set, and a bottom granularity.}\label{fig:linear-time}
\end{figure}

\hypertarget{relativities}{%
\subsection{Relativities}\label{relativities}}

Properties of pairs of granularities fall into various categories.

\begin{definition}\label{def:finerthan}
A linear granularity $G$ is {\bf finer than} a linear granularity $H$, denoted $G \preceq H$, if for each index $i$, there exists an index $j$ such that
$G(i) \subset H(j).$
\end{definition}

\begin{definition}\label{def:groupsinto}
A linear granularity $G$ {\bf groups into} a linear granularity $H$, denoted
$G \trianglelefteq H$, if for each index $j$ there exists a (possibly infinite) subset $S$ of the integers such that $H(j) = \bigcup_{i \in S}G(i).$
\end{definition}

\newtheorem*{example}{Example}

\begin{example}
{\rm Both $day \trianglelefteq week$ and $day \preceq week$ holds, since every granule of $week$ is the union of some set of granules of day and each day is a subset of a $week$. Consider another example where $day \trianglelefteq month$. This relationship however is incomplete without its association to periodicity. Each month is a grouping of the same number of days over years, hence the period of the grouping $(day, month)$ is one year, if leap years are ignored. This grouping period becomes 4 and 400 years with the inclusion of leap years and leap seconds respectively.}
\end{example}

\begin{definition}\label{def:periodical}
A granularity $G$ is {\bf periodical} with respect to a granularity $H$ if:
(1) $G \trianglelefteq H$; and
(2) there exist $R$, $P \in \mathbb{Z}_+$, where $R$ is less than the number of granules of $H$, such that for all $i \in \mathbb{Z}$, if $H(i) = \bigcup_{j \in S}G(j)$ and $H (i + R) \neq \phi$ then $H (i + R) = \bigcup_{j \in S} G(j + P)$.
\end{definition}

If \({S_0,\dots,S_{R-1}}\) are the sets of indexes of \(G\) describing
\(H(0), \dots, H(R - 1)\), respectively, then the description of an arbitrary granule \(H(j)\) is given by \(\bigcup_{i \in S_j ~\text{mod}~R}G(P*\lfloor j/R \rfloor + i)\). Also, granularities can be periodical with respect to other granularities, except for a finite number of spans of time where they behave in an anomalous way, called \textbf{quasi-periodic} relationships by \citet{Bettini2000-vy}.

\begin{example}
{\rm In a Gregorian calendar without leap years we could say $day$ groups periodically into month with the period $P = 365$ and the number of granules of $month$ in each period given by $R=12$. In a Gregorian calendar with leap years, $day$ groups quasi-periodically into $month$ with the exceptions of the time domain corresponding to $29^{\text{th}}$ February of any year.}
\end{example}

\begin{definition}\label{def:order}
The {\bf order} of a linear granularity is the level of coarseness associated with a linear granularity. A linear granularity G will have lower order than H if each granule of G is composed of lower number of granules of bottom granularity than each granule of H.
\end{definition}

\begin{example}
{\rm For two linear granularities $G$ and $H$, if $G$ {\em groups into} or {\em finer than} $H$ then $G$ is of lower order than $H$. Moreover, if we consider bottom granularity as day, linear granularity week will have lower order than month since each week consist of less number of days than each month. Here neither  week {\em groups into} month or  week {\em finer than} month, but their relative order could be determined.}
\end{example}

\hypertarget{computation}{%
\subsection{Computation}\label{computation}}

Granules in bottom granularity or any finer granularity may be aggregated in some manner to form larger granules belonging to a coarser granularity. A system of multiple granularities in lattice structures is referred to as a \textbf{calendar} by \citet{Dyreson_2000}. Linear time granularities are computed through an algebraic representation for time granularities, which is referred to as calendar algebra \citep{Ning_2002}. It is assumed that there exists a \emph{bottom granularity} and calendar algebra operations are designed to generate new granularities recursively from the bottom one. Some relevant calendar algebra operations are discussed below; these will be used in Section \ref{sec:cyclic-gran} for illustrations in circular and quasi-circular granularities.

\begin{definition}\label{def:grouping_operation}
Let $G_1$ be a full-integer labelled granularity, and $m$ a positive integer. {\bf The grouping operation} Group$_m(G)$ generates a new granularity $G_2$, by partitioning the granules of $G_1$ into $m$-granule groups and making each group a granule of the resulting granularity. More precisely, $G_2 = \text{Group}_m(G_1)$ is the full-integer labelled granularity such that for each integer $i$,
$$G_2(i) = \bigcup\limits_{j = (i-1)m+1}^{im} G_1(j).$$
The grouping operation Group$_m(G)$, provides a new granularity whose granules are the integer part of the quotient when the integer set spanned by linear granularity $G$ is divided by $m$, such that, $G_2(i) = \lfloor G_1(j)/m \rfloor$.
\end{definition}

\begin{example} 
{\rm Due to even length of $day$ and $week$, we can derive them from $hour$ using the grouping operation as follows: day = G$_{24}(\text{hour})$, week = G$_{24*7}(\text{hour})$.}
\end{example}

\noindent For more variations of calendar algebra operations, see \citet{Ning_2002}.

\hypertarget{sec:cyclic-gran}{%
\section{Cyclic time granularities}\label{sec:cyclic-gran}}

Cyclic granularities represent cyclical repetitions in time. They can be thought of as additional categorizations of time that are not linear. Cyclic granularities can be constructed by operating on two linear granularities. Cycles can be either \emph{regular}, called \textbf{circular}, or \emph{irregular}, \textbf{quasi-circular} when these two linear granularities relate periodically.

\hypertarget{sec:circular-gran-def}{%
\subsection{Circular}\label{sec:circular-gran-def}}

\begin{definition}\label{def:circular}
A {\bf circular granularity} $C_{B, G}$ relates a linear granularity $G$ to the bottom granularity B, if
\begin{equation} \label{eq:circular-gran}
\begin{split}
C_{B, G}(z) & = z~\text{mod}~P(B, G) \quad \forall z \in \mathbb{Z}_{\geq 0} \\
\end{split}
\end{equation}
where
z denotes the index set,
B denotes a full-integer labelled bottom granularity which groups periodically into linear granularity $G$ with regular mapping, and $P \equiv P(B, G)$ is the number of granules of $B$ in each granule of $G$, also called the period of the grouping $(B, G)$.
\end{definition}

\begin{example}
{\rm \autoref{fig:circular-dow} illustrates the linear and the corresponding cyclical granularities. Cyclical granularities can be considered to be cutting the linear granularity into pieces, and stacking them to match the cycles (as shown in b). $B, G, H$ (day, week, fortnight, respectively) are linear granularities. The circular granularity $C_{B , G}$ (day-of-week)is constructed from $B$ and  $G$. The circular granularity $C_{B, H}$ (day-of-fortnight) is constructed from $B$ and $H$. These overlapping cyclical granularities share elements from the linear granularity. Each of $C_{B , G}$ and $C_{B , H}$ consist of repeated patterns  $\{0, 1, 2, \dots, 6\}$ and $\{0, 1, 2, \dots, 13\}$ with $P=7$ and $P=14$ respectively. Each circular granularity can use descriptive label mappings. Suppose ${L}$ is a label mapping that defines an unique label for each index $l \in \{ 0,1,\dots, (P-1)\}$, then the label mapping $L$ for $C_{B, G}$ can be defined as
$$
  L: \{0,1,2, \dots, 6\} \longmapsto\ \{\text{Sun}, \text{Mon}, \dots, \text{Sat}\}
$$
or
$$
  L: \{0,1,2, \dots, 6\} \longmapsto\ \{\text{Sunday}, \text{Monday}, \dots, \text{Saturday}\}
$$
for example.}
\end{example}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{Figs/circular-ex}

}

\caption{Illustration of circular relative to linear granularities (a). Circular granularities can be considered to be cutting the linear granularity into pieces and stacking them (b). The circular granularity creates repeated integer sequences.}\label{fig:circular-dow}
\end{figure}

In general, any circular granularity relating two linear granularity can be expressed as \(C_{(G, H)}(z) = \lfloor z/P(B,G) \rfloor~\text{mod}~P(G,H)\), where linear granularity \(H\) is periodic with respect to linear granularity \(G\) with regular mapping and \(P(G,H)\) is the period of the grouping \((G, H)\) . Table \ref{tab:definitions} shows representation of circular granularities \(C_i\) relating two linear granularities with period \(P_i\) and minutes as the bottom granularity.

\begin{table}[ht]
\begin{center}
\begin{tabular}{lll}
\hline
circular granularity & expression & period \\
\hline
minute-of-hour                               &
  $C_1 = z ~\text{mod}~60$                     &
  $P_1 = \phantom{99}60$ \\
minute-of-day                                &
  $C_j = z ~\text{mod}~60*24$                  &
  $P_2= 1440$\\
hour-of-day                                  &
  $C_3 = \lfloor z/60\rfloor~\text{mod}~24$    &
  $P_3 = \phantom{99}24$ \\
hour-of-week                                 &
  $C_4 = \lfloor z/60\rfloor~\text{mod}~24*7$  &
  $P_4= \phantom{9}168$\\
day-of-week                                  &
  $C_5 = \lfloor z/24*60\rfloor ~\text{mod}~7$ &
  $P_5= \phantom{999}7$\\
\bottomrule
\end{tabular}
\end{center}
\caption{Examples of circular granularities with bottom granularity minutes. Circular granularity $C_i$ relates two linear granularities one of which groups periodically into the other with regular mapping and period $P_i$. Circular granularities can be expressed using modular arithmetic due to their regular mapping. }
\label{tab:definitions}
\end{table}

\hypertarget{sec:quasi-circular-gran-def}{%
\subsection{Quasi-circular}\label{sec:quasi-circular-gran-def}}

A \textbf{quasi-circular} granularity can not be defined using modular arithmetic since they are formed using two linear granularities with irregular mapping. However, they are still formed with linear granularities, one of which ``groups periodically into'' the other. \autoref{tab:quasi} shows some example of quasi-circular granularities (\(Q_i\)) with (\(P_i\)) denoting the plausible choices of period of the grouping of two linear granularities.

\begin{table}[ht]
\begin{center}
\begin{tabular}{lr@{~}lr@{~}r}
\hline
quasi-circular granularity && potential period lengths\\
\hline
$Q_1 =$ day-of-month && $P_1 = 31, 30, 29, 28$\\
$Q_2 =$ hour-of-month && $P_2 = 24*31, 24*30, 24*29, 24*28$\\
$Q_3 =$ day-of-year && $P_3 = 366, 365$\\
$Q_4 =$ week-of-month && $P_4 = 5, 4$\\
\bottomrule
\end{tabular}
\end{center}
\caption{Examples of quasi-circular granularities $Q_i$ with potential period lengths $P_i$. These quasi-circular granularities relate two linear granularities one of which groups periodically into the other with irregular mapping leading to many potential period lengths and hence can not be expressed through modular arithmetic. }
\label{tab:quasi}
\end{table}

\begin{definition}\label{def:quasicircular}
A {\bf quasi-circular granularity} $Q_{B, G'}$ relates linear granularities $G'$ and bottom granularity $B$, if
\begin{equation}\label{eq:quasi}
\begin{split}
Q_{B, G'}(z) =
z - \sum_{w=0}^{k-1}\vert T_{w ~\text{mod}~R'} \vert, & \quad \text{for}\quad z \in T_{k}
\end{split}
\end{equation}
where,
$z \in \mathbb{Z}_{\geq 0}$ denotes the index set,
$B$ denotes a full-integer labelled bottom granularity which groups periodically into linear granularity $G'$ with irregular mapping, $P'$ and $R'$ are the period of the grouping $(B, G')$ and the number of granules of $G'$ in $P'$, $T_w$ are the sets of indices of $B$ describing $G'(w)$ such that  $G'(w) = \bigcup_{z \in T_w}B(z)$ and $\vert T_w \vert$ is the cardinality of set $T_w$.
\end{definition}

\begin{example}
{\rm Consider $G'$ such that every two consecutive granules of $G'$ are made up of $7$ and $5$ granules of $B$ respectively within each period of the grouping ($B$, $G'$). Then $Q_{B, G'}$ is a repetitive categorization of time, similar to circular granularities, except that the number of granules of $B$ is not necessarily the same across different granules of $G'$. Here, $T_0 = \{0, 1, 2, 3, 4, 5, 6\}$ and $T_1 = \{7, 8, 9, 10, 11\}$. Hence using Definition \autoref{def:quasicircular} we will have:

\begin{align*}
\begin{split}
Q_{B,H'}(10) & = 10 - \sum_{w=0}^{1-1}\vert T_{w ~\text{mod}~2}\vert ,\quad since \quad 10 \in T_{1}  \\
  & = 3 \\
\end{split}
\end{align*}
}
\end{example}

If linear granularity \(G'\) is periodical with respect to \(B\) with irregular mapping, then there exist \(R'\), \(P' \in \mathbb{Z}_+\) such that if \(G'(w) = \bigcup_{z \in T_w}B(z)\) then \[G'(w) = \bigcup_{z \in T_w ~\text{mod}~R'}B(P'*\lfloor w/R' \rfloor + z)\] (from Definition \ref{def:periodical}) . Here \(w ~\text{mod}~R'\) represents the index that must be shifted to obtain \(G'(w)\). The idea here is if we know the composition of each of the granules of \(G'\) in terms of granules of \(B\) for one period, we can find the composition of any granule of \(G'\) beyond a period since the ``pattern'' repeats itself along the time domain due to the periodic property. The periodic property also ensures that \(\vert T_w \vert = \vert T_{w~\text{mod}~R'} \vert\) since every \(w^{\text{th}}\) and \((w+R')^{\text{th}}\) granule of \(G'\) will have the same number of granules of \(B\). The term \(\sum_{w=0}^{k-1}\vert T_{w}\vert\) in Definition \autoref{def:quasicircular} denotes the number of granules of \(B\) till the \((k-1)^{\text{th}}\) granule of \(G'\). Since \(\vert T_w \vert = \vert T_{w~\text{mod}~R'} \vert\), the number of granules of \(B\) till the \((k-1)^{\text{th}}\) granule of \(G'\) becomes \(\sum_{w=0}^{k-1}\vert T_{w ~\text{mod}~R'}\vert\) in Definition \autoref{def:quasicircular}.

\hypertarget{sec:aperiodic-gran-def}{%
\subsection{Aperiodic}\label{sec:aperiodic-gran-def}}

Aperiodic time granularities are the ones which can not be specified as a periodic repetition of a pattern of granules. Most public holidays repeat every year, but there is no reasonably small period within which their behavior remains constant. A classic example can be that of Easter, whose dates repeat only after 5,700,000 years. In Australia, if a standard public holiday falls on a weekend, a substitute public holiday will sometimes be observed on the first non-weekend day (usually Monday) after the weekend. Examples of aperiodic granularity may also include school holidays or a scheduled event. All of these are recurring events, but with non-periodic patterns. As such, plausible \(P_i\) from \autoref{tab:quasi} could be possibly infinite for aperiodic granularities.

\noindent Aperiodic cyclic granularities are defined using aperiodic linear granularities. Consider n aperiodic linear granularities \(M_i\) \(\forall \{i\in{1, 2, \dots, n\}}\) such that Definition \ref{def:periodical} does not hold true with respect to \(B\). However, \(B \trianglelefteq M_i\) \(\forall \{i\in{1, 2, \dots, n\}}\). Then according to Definition \ref{def:groupsinto}, for each index \(j\) there exists a (possibly infinite) subset \(T_{\{i_j\}}\) of the integers such that \(M_{i}(j) = \bigcup_{z \in T_{i_j}}B(z)\). Suppose \(M = \bigcup_{i=1}^{n}M_{i}\) is formed by collecting the granules of \(\{M_1, M_2, \dots, M_n\}\). Here, index \({\{i_j\}}\) stands for the \(j^{\text{th}}\) granule of the \(i^{\text{th}}\) linear aperiodic granularity.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{Figs/aperiodic-ex3}

}

\caption{Quasi-circular and aperiodic cyclic granularities illustrated through linear (a) and stack (b) display of time. The linear display shows linear granularities days, weeks, semester weeks, semester week type distributed linearly from past to future. Here a semester lasts for 18.3 weeks, each starting with one week of orientation followed by an in-session period of 6 weeks, a semester-break of 1 week and again an in-session period of 7 weeks and 1 week study break before final exams which continue for 1.3 weeks. This pattern remains same for all semester and hence \(Q_{H, M}\) with \(P\) = 18.3 weeks will be a quasi-circular granularity with repeating patterns. \(A_{B, M}\) will be an aperiodic cyclic granularity since the placement of the semester within an year varies across years.}\label{fig:aperiodic-example}
\end{figure}

\begin{definition}\label{def:aperiodic}
An {\bf aperiodic cyclic granularity} $A_{B, M}$ relates a linear granularity $M$ to the bottom granularity $B$, if
\begin{equation}\label{eq:aperiodic}
\begin{split}
A_{B, M}(z) & =
\begin{cases}
i, & \text{for}\quad z \in T_{i_j} \\
0  & \text{otherwise}
\end{cases}
\end{split}
\end{equation}
where,
$z \in \mathbb{Z}_{\geq 0}$ denotes the index set,
$B$ denotes a full-integer labelled bottom granularity which groups into linear granularity $M$ but not periodically, $T_{i_j}$ are the sets of indices of $B$ describing aperiodic linear granularities $M_{i}$ such that $M_{i}(j) = \bigcup_{z \in T_{i_j}}B(z)$, and $M = \bigcup_{i=1}^{n}M_{i}$.
\end{definition}

\begin{example}
{\rm Consider a school semester which always lasts for 18 weeks and 2 days, starting with one week of orientation followed by an in-session period of 6 weeks, a semester-break of 1 week and again an in-session period of 7 weeks and 1 week study break before final exams which continue for 16 days. Let the linear granularities $M_1$ and $M_2$ denote in-session semester period and semester break periods respectively. Both $M_1$, $M_2$ and $M = M_{1}\bigcup M_{2}$ denoting the semester week type are aperiodic with respect to days ($B$) or weeks ($G$). Hence $A_{B, M}$ denoting day of the semester week type would be an aperiodic cyclic granularity. This is because the placement of the semester within an year would vary across years. \autoref{fig:aperiodic-example} b shows the stack display of time with granules representing same categories (semester break/in-session) stacked on top of one another. \autoref{fig:aperiodic-example} (a) representing the linear display of time is useful in manifesting how the categories would be determined with respect to the bottom granularities using Definition \ref{def:aperiodic}. It is interesting to note here that $Q_{H, M}$ denoting semester week of the semester week type would be a quasi-circular granularity since the distribution of semester weeks within a semester is assumed to remain constant over years.}
\end{example}

\hypertarget{sec:cyclic-calendar}{%
\subsection{Relativities}\label{sec:cyclic-calendar}}

The hierarchical structure of time creates a natural nested ordering which can be used in the computation of relative pairs of granularities. This is illustrated using two examples, a Mayan calendar, which is simple, in addition to the more complex Gregorian calendar.

\begin{definition}\label{def:hierarchy} 
The nested ordering of linear granularities can be organized into a {\bf hierarchy table}, denoted as $H_n: (G, C, K)$, which arranges them from lowest to highest in order. It shows how the $n$ granularities relate through $K$, and how the cyclic granularities, $C$. can be defined relative to the linear granularities. Let $G_{l}$ and $G_{m}$ represent the linear granularity of order $l$ and $m$ respectively with $l<m$. Then $K \equiv P(l,m)$ represents the period length of the grouping $(G_{l}, G_{m})$, if $C_{G_{l}, G_{m}}$ is a circular granularity and $K \equiv k(l,m)$ represents the operation to obtain $G_{m}$ from $G_{l}$, if $C_{G_{l}, G_{m}}$ is quasi-circular.
\end{definition}

\begin{example}
{\rm  \autoref{tab:tab-mayan} shows the hierarchy table for the Mayan calendar. In the Mayan calendar, one day is referred to as a kin and the calendar was structured such that 1 kin = 1 day; 1 uinal = 20 kin; 1 tun  = 18 uinal (about a year); 1 katun = 20 tun (20 years) and 1 baktun = 20 katun. }
\end{example}

\begin{table}

\caption{\label{tab:tab-mayan}Hierarchy table for Mayan calendar with circular single-order-up granularities.}
\centering
\begin{tabular}[t]{lll}
\toprule
linear (G) & single-order-up cyclic (C) & period length/conversion operator (K)\\
\midrule
kin & kin-of-uinal & 20\\
uinal & uinal-of-tun & 18\\
tun & tun-of-katun & 20\\
katun & katun-of-baktun & 20\\
baktun & 1 & 1\\
\bottomrule
\end{tabular}
\end{table}

\noindent It is interesting to note, that in the Mayan calendar, like most calendars, that day is the basic unit of time \citep{Reingold2001-kf}. The structuring of larger units, weeks, months, years and cycle of years, though, varies substantially. An exception is the French revolutionary calendar, which divides each day into 10 ``hours'', each ``hour'' into 100 ``minutes'' and each ``minute'' into 100 ``seconds'', the duration of which is 0.864 common seconds. Nevertheless, for any calendar a hierarchy table can be defined. Note that it is not always possible to organize an aperiodic linear granularity in a hierarchy table. Hence, we assume that the hierarchy table consists of periodic linear granularities only and that the cyclic granularity \(C_{G(l),G(m)}\) is either circular or quasi-circular.

\begin{definition}\label{def:norderup} 
The hierarchy table contains {\bf multiple-order-up} granularities which are cyclic granularities that are nested within multiple levels.
A {\bf single-order-up} is a cyclic granularity which is nested within a single level. It is a special case of multiple-order-up granularity.
\end{definition}

\begin{example}
{\rm In \autoref{tab:tab-mayan}, kin-of-tun or kin-of-baktun are examples of multiple-order-up granularities and single-order-up granularities are kin-of-uinal, uinal-of-tun etc.}
\end{example}

\hypertarget{computation-1}{%
\subsection{Computation}\label{computation-1}}

In this section, we will see how to obtain cyclic granularities through an algebraic representation of other cyclic granularities. This is similar to calendar algebra in \citet{Ning_2002} for linear granularities but caters to computation of cyclic granularities. We shall refer to it as through cyclic calendar algebra operations. The cyclic calendar algebra consists of broadly two kinds of operations:
(1) \textbf{single-to-multiple} and (2) \textbf{multiple-to-single} which entails the representation of \emph{multiple-order-up} cyclic granularities from \emph{single-order-up} cyclic granularities respectively.

\hypertarget{sec:single-to-multiple}{%
\subsubsection{Single-to-multiple}\label{sec:single-to-multiple}}

\noindent Methods to obtain multiple-order-up granularity will be different based on if the hierarchy consists of all circular single-order-up granularities or a mix of circular and quasi-circular single-order-up granularities. The methods require the use of integer arithmetic, and hence it is important that the label mapping of the individual single-order-up granularity is an identity function, that is, \(L(x) = x\quad \forall x\). The label mapping of the resultant multiple-order-up granularity can be chosen depending on the context. Circular single-order-up granularities can be used recursively to obtain a multiple-order-up circular granularity using Equation \ref{eq:eq7} for \(l < m - 1\) and \(P(i, j) = 1, \quad \forall i = j \in \{0, 1, \dots, m-l-1\}\).

\begin{equation} \label{eq:eq7}
\begin{split}
C_{G_l,G_m}(z) & = C_{G_l,G_{l+1}}(z) + P(l, l+1)C_{G_{l+1},G_m}(z)\\
  & = C_{G_l,G_{l+1}}(z) + P(l, l+1)( C_{G_{l+1},G_{l+2}}(z) + P(l+1, l+2)C_{G_{l+2}, G_m}(z)) \\
  & = C_{G_l,G_{l+1}}(z) + P(l, l+1)C_{G_{l+1},G_{l+2}}(z) + P(l, l+1)P(l+1, l+2)C_{G_{l+2}, G_{m}}\\
  & = C_{G_l,G_{l+1}}(z) + P(l, l+1)C_{G_{l+1},G_{l+2}}(z) + P(l, l+2)C_{G_{l+2},G_{l+m}}(z)\\
  &\vdots\\
  & = \sum_{i=0}^{m - l - 1} P(l, l+i)C_{G_{l+i},G_{l+i+1}}(z)\\
\end{split}
\end{equation}

\noindent For example, the multiple-order-up granularity \(C_{uinal,katun}\) for Mayan calendar could be obtained using Equation \ref{eq:eq8}.

\begin{equation} \label{eq:eq8}
\begin{split}
C_{uinal, baktun}(z)  = & C_{uinal, tun}(z) + P(uinal, tun)C_{tun,katun}(z) + P(uinal, katun)C_{katun, baktun}(z) \\
               = & \lfloor z/20\rfloor ~\text{mod}~18 + 18*\lfloor z/20*18\rfloor ~\text{mod}~20  \\
               &~~~ + 18*20\lfloor z/20*18*20\rfloor ~\text{mod}~20 \\
\end{split}
\end{equation}

\noindent We consider the case of only one quasi-circular single order-up granularity in the hierarchy table while computing a multiple-order-up quasi-circular granularity. Any multiple-order-up quasi-circular granularity \(C_{l, m}(z)\) could then be obtained as a dicrete combination of circular and quasi-circular granularities.
 Depending on the order of the combination, again two different approaches need to be employed leading to the following cases:

\begin{itemize}
\item
  \(C_{l,m'}(z)\) is circular and \(C_{m',m}(z)\) is quasi-circular
  \begin{equation} \label{eq:multifromsingle-quasi1}
  \begin{split}
  C_{G_l,G_{m}}(z) & = C_{G_{l},G_{m'}}(z) + P(l, m')C_{G_{m'},G_{m}}(z) \\
  \end{split}
  \end{equation}
\item
  \(C_{l,m'}(z)\) is quasi-circular and \(C_{m',m}(z)\) is circular
  \begin{equation} \label{eq:multifromsingle-quasi2}
  \begin{split}
  C_{G_l,G_{m}}(z) & = C_{G_{l},G_{m'}}(z) + \sum_{w=0}^{C_{m',m}(z) -1}(\vert T_{w} \vert)\\
  \end{split}
  \end{equation}
\end{itemize}

\noindent where, \(T_w\) is such that \(G_{m'}(w) = \bigcup_{z \in T_w}G_{l}\) and \(\vert T_w \vert\) is the cardinality of set \(T_w\).

\noindent Consider a hierarchy using linear granularties from a Gregorian calendar in \autoref{tab:tab-gregorian}. This is an example of a hierarchy structure which has both circular and quasi-circular single-order-up granularities with day-of-month as the only single-order-up quasi-circular granularity.

\noindent Using Equations \ref{eq:multifromsingle-quasi1} and \ref{eq:multifromsingle-quasi2}, we then have:

\[C_{hour, month}(z) = C_{hour, day}(z) + P(hour, day)*C_{day, month}(z)\]
\[C_{day, year}(z) = C_{day,month}(z) + \sum_{w=0}^{C_{month, year}(z)-1}(\vert T_{w} \vert)\], where \(T_w\) is such that \(month(w) = \bigcup_{z \in T_w}day(z)\)

\begin{table}

\caption{\label{tab:tab-gregorian}Hierarchy table for the Gregorian calendar with both circular and quasi-circular single-order-up granularities.}
\centering
\begin{tabular}[t]{lll}
\toprule
linear (G) & single-order-up cyclic (C) & period length/conversion operator (K)\\
\midrule
minute & minute-of-hour & 60\\
hour & hour-of-day & 24\\
day & day-of-month & k(day, month)\\
month & month-of-year & 12\\
year & 1 & 1\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{sec:multiple-to-single}{%
\subsubsection{Multiple-to-single}\label{sec:multiple-to-single}}

\noindent Similar to single-to-multiple operations, multiple-to-single operations involve different approaches for all circular single-order-up granularities and a mix of circular and quasi-circular single-order-up granularities in the hierarchy. For a hierarchy table \(H_n: (G, C, K)\) with only circular single-order-up granularities in the hierarchy and \(l_1, l_2, m_1, m_2 \in {1, 2, \dots, n}\) and \(l_2<l_1\) and \(m_2>m_1\), multiple-order-up granularities could be obtained using \ref{eq:all-circular-multiple}.

\begin{equation} \label{eq:all-circular-multiple}
C_{G_{l_1}, G_{m_1}}(z) = \lfloor C_{G_{l_2}, G_{m_2}}(z)/P(l_2,l_1) \rfloor ~\text{mod}~P(l_1, m_1)
\end{equation}

\noindent For example, in Mayan Calendar, it is possible to compute the single-order-up granularity tun-of-katun from uinal-of-baktun, since \(C_{tun, katun}(z) = \lfloor C_{uinal, baktun}(z)/18\rfloor ~\text{mod}~20\).

\hypertarget{sec:quasi-circular-multiple}{%
\paragraph{Multiple order-up quasi-circular granularities}\label{sec:quasi-circular-multiple}}

Single-order-up quasi-circular granularity could be obtained from multiple-order-up quasi-circular granularity and single/multiple-order-up circular granularity using Equations \ref{eq:multifromsingle-quasi1} and \ref{eq:multifromsingle-quasi2}.

\hypertarget{sec:data-structure}{%
\section{Data structure}\label{sec:data-structure}}

\noindent Effective exploration and visualization benefits from well-organized data structures. \citet{wang2020tsibble} introduced a tidy data structure, tsibble, to support exploration and modeling of temporal data. This forms the basis of the structure for cyclic granularities. A tsibble consists of an index, key and measured variables. An index is a variable with inherent ordering from past to present and a key is a set of variables that define observational units over time. A linear granularity is a mapping of the index set to subsets of the time domain. For example, if the index of a tsibble is days, then a linear granularity might be weeks, months or years. A bottom granularity is represented by the index of the tsibble.

\noindent All cyclic granularities can be expressed in terms of the index set, and hence, we introduce the data structure in Figure \ref{fig:data-structure}. This basic structure of a tsibble (index, key, measurements) is augmented by columns of cyclic granularities. The total number of cyclic granularities would be based on the number of linear granularities considered in the hierarchy table and presence of any aperiodic cyclic granularities, for example, if we have \(n\) periodic linear granularities in the hierarchy table, \(n(n-1)/2\) circular or quasi-circular cyclic granularities could be constructed. Let \(N_C\) be the total number of contextual circular, quasi-circular and aperiodic cyclic granularities that could originate from \(N_L\) periodic and aperiodic linear granularities. Any attempt to encode all or many of these cyclic granularities at the same time to develop insights on periodicity might fail or otherwise become too numerous for comprehensive human consumption. Instead, this big problem is broken down by focusing on pair of cyclic granularities (\(C_i\), \(C_j\)) at a time for \(i, j \in \{1, 2, \dots, N_C\}\). Data sets of the form \textless{}\(C_i\), \(C_j\), \(v\)\textgreater{} then forms the basis for exploration and analysis of the measured variable \(v\).

\begin{figure}[htb]

{\centering \includegraphics[width=\textwidth]{Figs/data-struc-diffcol}

}

\caption{The data structure for exploring periodicities in data by including cyclic granularities in the tsibble structure with index, key and measured variables.}\label{fig:data-structure}
\end{figure}

\hypertarget{sec:synergy}{%
\subsection{Harmonies and clashes}\label{sec:synergy}}

The way cyclic granularities relate become important when we consider the data structure in Figure \ref{fig:data-structure}. Let us consider two cyclic granularities \(C_i\) and \(C_j\), such that \(C_i\) maps index set to a set \(\{A_k | k \in \mathbb{N}, k \leq K\}\) and \(C_j\) maps index set to a set \(\{B_l | l \in \mathbb{N}, l \leq L\}\). Here, \(A_k\)'s or \(B_l\)'s are the levels/categories corresponding to \(C_i\) and \(C_j\) respectively. Let \(S_{kl}\) be a subset of the index set such that for all \(s \in S_{kl}\), \(C_i(s) = A_k\) and \(C_j(s) = B_l\). Data subsets for each combination of levels (\(A_k\), \(B_l\)) like \textless{}\(A_k\), \(B_l\), \(v(s)\)\textgreater{} can be obtained for all \(k \in {1, 2, \dots, K}\) and \(l \in {1, 2, \dots, L}\) which will lead to \(KL\) data subsets. Now, some situations can lead to few or many of these sets being empty. We will discuss few cases, where one or more of these \(KL\) sets will be empty either due to the structure of the calendar, duration and location of events in a calendar or just by the construction of the cyclic granularities.

\begin{definition}\label{def:harmony}
A {\bf clash} is a pair of cyclic granularities which contains structurally, event-driven or build-based empty combinations of its categories.
\end{definition}

\begin{definition}\label{def:clash}
A {\bf harmony} is a pair of cyclic granularities that does not contain any empty combinations of its categories.
\end{definition}

\noindent Firstly, empty combinations can arise due to the structure of the calendar or hierarchy. These are called ``structurally'' empty combinations. Let us take a specific example, where \(C_i\) be day-of-month with 31 levels and \(C_j\) be week-of-month with 5 levels. There will be \(31\times 5=155\) sets \(S_{kl}\) corresponding to possible combinations of \(C_i\) and \(C_j\). Many of these like \(S_{1,5}\), \(S_{21,2}\) are empty. This is also intuitive since the first day of the month can never correspond to fifth week of the month. Hence the pair (day-of-month, week-of-month) is a clash.

\noindent Secondly, empty combinations can turn up due to differences in event location or duration in a calendar. These are called ``event-driven'' empty combinations. Let us consider \(C_i\) be day-of-week with 7 levels and \(C_j\) be WorkingDay/NonWorkingDay with 2 levels. While potentially all of these 14 sets \(S_{kl}\) can be non-empty (it is possible to have a public holiday on any day-of-week), in practice many of these will probably have very few observations. For example, there are few (if any) public holidays on Wednesdays or Thursdays in any given year in Melbourne, Australia.

\noindent Thirdly, empty combinations can be a result of how granularities are constructed. These are called ``build-based'' empty combinations. Let \(C_i\) be Business-days, which are days from Monday to Friday except holidays and \(C_j\) be day-of-month. Then the days denoting weekends in a month would not correspond to any Business days. This is different from structurally empty combinations because structure of the calendar does not lead to these missing combinations, but the construction of the granularities does.

\noindent An example when there will be no empty combinations could be where \(C_i\) and \(C_j\) maps index set to day-of-week and month-of-year respectively. Here \(C_i\) can have 7 levels while \(C_j\) can have 12 levels. So there are \(12\times7=84\) sets \(S_{kl}\). All of these are non-empty because every day-of-week can occur in every month. Hence, the pair (day-of-week, month-of-year) is a harmony.

\hypertarget{sec:summarize-measured}{%
\subsection{Summarizing the measured variable}\label{sec:summarize-measured}}

Restructuring time from linear to cyclic time granularities leads to re-organisation of the data structure, where each level of a cyclic granularity corresponds to multiple values of the measured variable. It is common to see summarization of these multiple values through aggregation or an unique summary statistic like mean or median to have each level of cyclic granularity correspond to an unique value of the measured variable. However, this approach hides the distributions of the measured variable induced by the re-organised data structure. Summarizing the distribution of the measured variable using these multiple observations could be a potential way to explore and bring forward different features of the data.

However, we need to consider the effect of number of observations on the summarization even for harmonies. Consider a data set with \((T + 1)\) observations, and two cyclic granularities \(C_i\) and \(C_j\) with \(K\) and \(L\) categories respectively. Let \(nobs\) be the number of observations for a combination of levels from \((C_i, C_j)\). Now, \(nobs\) might be equal for all combinations on an average so that \(nobs = (T + 1)/(KL)\) as \(T\rightarrow\infty\) or ideally take any value between \(\{0, 1, 2, \dots, T\}\). The statistical transformation used for summarizing the measured variable should be chosen in line with \(nobs\). For example, it might be useful to compute deciles for summarization only when \(nobs \ge 10\). Rarely occurring categories such as the 366th day of the year, or the 31st day of the month are likely to suffer from this problem.

\hypertarget{sec:visualization}{%
\section{Visualization}\label{sec:visualization}}

The grammar of graphics introduced a framework to construct statistical graphics by relating data space to the graphic space \citep{Wilkinson1999-nk}. The layered grammar of graphics proposed by \citet{Wickham2009pk}, which is an alternate and modified parametrization of the grammar suggests that graphics are made up of distinct layers of grammatical elements. Drawing from the grammar of graphics, if \textless{}\(C_i\), \(C_j\), \(v\)\textgreater{} serves as the basis of visualizing the distribution of the measured variable, the following layers can be specified:

\begin{itemize}
\tightlist
\item
  Data: \textless{}\(C_i\), \(C_j\), \(v\)\textgreater{}
\item
  Aesthetic mapping (mapping of variables to elements of the plot): \(C_i\) mapped to \(x\) position and \(v\) to \(y\) position
\item
  Statistical transformation (data summarization): any descriptive or smoothing statistics that summarizes distribution of \(v\)
\item
  Geometric objects (physical representation of the data): any geometry displaying distribution, for example, boxplot, letter value, violin, ridge or highest density region plots
\item
  Facet (split plots): \(C_j\)
\end{itemize}

\hypertarget{choice-of-statistical-transformations-and-geometric-objects}{%
\subsection{Choice of statistical transformations and geometric objects}\label{choice-of-statistical-transformations-and-geometric-objects}}

Choice of plots are dictated by the statistical transformations and geometric objects used for the visualization. The basic plot choice for our data structure is the one that can display distributions. We will discuss few conventional and recent ways to plot distributions using both Kernel density estimates and descriptive statistics. Descriptive statistics based displays include box plots \citep{Tukey1977-jx} or different variations of it like notched box plots \citep{Mcgill1978-hg}. More recent ways are the letter-value box plot \citep{Hofmann2017-sg} or quantile plots which display quantiles instead of quartiles in a traditional boxplot. Kernel density based plots for displaying a distribution include violin plots \citep{Hintze1998-zi}, summary plot \citep{Potter2010-qc}, ridge line plots, highest density regions (HDR) box \citep{Hyndman1996-ft}. Each type of density display has different parameters, that need to be estimated given the data. Each is equipped with some benefits and challenges which should be borne in mind while using them for exploration.

\hypertarget{facet-and-aesthetic-variables}{%
\subsection{Facet and aesthetic variables}\label{facet-and-aesthetic-variables}}

\hypertarget{sec:levels}{%
\subsubsection{Levels}\label{sec:levels}}

The levels of cyclic granularities has a role to play on the choice of plots since space and resolution might become a problem with too many levels. A potential approach could be to categorize the levels as very high/high/medium/low for each cyclic granularity and define some criteria based on usual cognitive power, display size available and the aesthetic mappings. Default values for these categorizations could be chosen based on levels of common temporal granularities like days of the month, days of the fortnight or days of the week.

\hypertarget{sec:vis-interaction}{%
\subsubsection{Synergy of cyclic granularities}\label{sec:vis-interaction}}

For data sets of the form (\(C_i\), \(C_j\), \(v\)) \(\forall i, j \in N_C\), if there are levels of \(C_i\) (or \(C_j\)) not spanned by levels of \(C_j\) (or \(C_i\)), empty sets are formed leading to potential ineffective graphs. The conjecture is that the synergy of these cyclic granularities are thus playing a role while deciding if the resulting plot would be a good candidate for exploratory analysis. Harmonies are pairs of granularities that do not contain empty combinations and could possibly be useful for exploring patterns. However, plotting clashes should be avoided since they might contain combinations which are empty or have too few observations. For illustration, \autoref{fig:allFig} (a) shows the distribution of half-hourly electricity consumption through letter value plot across months of the year faceted by quarters of the year. This plot does not work because every quarter does not correspond to all months of the year, for example, the first quarter of the year would never correspond to the month December of an year.

\begin{figure}

\includegraphics[width=1\linewidth]{figure/allFig-1} \hfill{}

\caption{Distribution of energy consumption displayed through letter value plots. Plot (a) displays consumption across month-of-year faceted by quarters of the year, (b) across weekday/weekend faceted by quarters of the year and (c) across quarters of the year faceted by weekday/weekend. Plots (b) and (c) both show harmonies since each quarter consists of both weekdays and weekends. Conversely, weekend and weekday can occur in every quarter. Analysts should avoid plotting such clashes. Plot (b) helps to compare weekends and weekdays for each quarter. It can be seen that for every quarter weekend and weekday consumption are fairly similar except for the second quarter where the letter values below D and E behave differently, whereas, Plot (c) helps to compare quarters within weekdays and weekends. For example, the quartile spread of consumption shrinks/lowers from first to fourth quarter for weekdays, whereas this pattern is not true for weekends. Plot (a) shows a clash since all quarters do not correspond to all months of the year.}\label{fig:allFig}
\end{figure}

\hypertarget{interchangeability-of-mappings}{%
\subsubsection{Interchangeability of mappings}\label{interchangeability-of-mappings}}

We will discuss the effect of the mapping of cyclic granularities in this section. When we consider data sets of the form \textless{}\(C_i\), \(C_j\), \(v\)\textgreater{} with \(C_i\) mapped to \(x\) position and \(C_j\) to facets, then \(A_k\)'s are placed in close proximity and each \(B_l\) represent a group/facet. Gestalt theory suggests that when items are placed in close proximity, people assume that they are in the same group because they are close to one another and apart from other groups. Hence, in this case \(A_k\)'s are compared against each other within each group. With the mapping of \(C_i\) and \(C_j\) reversed, emphasis will shift to different behavior of the variables. \autoref{fig:allFig} (b) shows the letter value plot across weekday/weekend faceted by quarters of the year and \autoref{fig:allFig} (c) shows the same two cyclic granularities with their mapping reversed. \autoref{fig:allFig} (b) helps us to compare weekday and weekend within each quarter and \autoref{fig:allFig} (c) helps to compare quarters within weekend and weekday.

\hypertarget{number-of-observations-and-statistical-transformations}{%
\subsection{Number of observations and statistical transformations}\label{number-of-observations-and-statistical-transformations}}

Visualizing distributions can be misleading if statistical transformations are performed on rarely occurring categories (Section \ref{sec:summarize-measured}). Even when there are no rarely occurring events, number of observations might vary hugely within or across each facet. This might happen due to missing observations in the data or uneven locations of events in time domain. In such cases, the statistical transformations should be used with caution as sample sizes would directly affect both the variance and consequently the confidence interval of the estimators.

\hypertarget{sec:application}{%
\section{Applications}\label{sec:application}}

\hypertarget{sec:smartmeter}{%
\subsection{Smart meter data of Australia}\label{sec:smartmeter}}

Smart meters provide large quantities of measurements on energy usage for households across Australia. One of the customer trials \citep{smart-meter} conducted as part of the Smart Grid Smart City project in Newcastle, New South Wales and some parts of Sydney provides customer wise data on energy consumption for every half hour from February 2012 to March 2014. The idea here is to show how to visualize the distribution of the energy consumption across different cyclic granularities in a systematic way to identify different behavioral patterns.

\hypertarget{cyclic-granularities-search-and-computation}{%
\subsubsection{Cyclic granularities search and computation:}\label{cyclic-granularities-search-and-computation}}

The tsibble object \texttt{smart\_meter10} from R package \texttt{gravitas} \citep{R-gravitas} consisting of \texttt{reading\_datetime}, \texttt{customer\_id} and \texttt{general\_supply\_kwh} denoting the index, key and measured variable of the tsibble is used to facilitate the systematic exploration. While trying to explore the energy behavior of these customers systematically across cyclic time granularities, the first thing to consider is which cyclic time granularities we can look at exhaustively. Let us consider conventional time deconstructions for a Gregorian calendar (second, minute, half-hour, hour, day, week, month, year). Since the interval of this tsibble is 30 minutes, the temporal granularities may range from half-hour to year. Considering \(6\) linear granularities half-hour, hour, day, week, month and year in the hierarchy table, \(N_C = (6*5/2) = 15\). If \(N_C\) seem too large, the smallest and largest linear granularities could be considered to be removed for analysis. Granularities half-year and year are removed to have \(N_C = (4*3/2) = 6\) and obtain cyclic granularities namely ``hour\_day'', ``hour\_week'', ``hour\_month'', ``day\_week'', ``day\_month'' and ``week\_month'', read as ``hour of the day'', etc. Further, we add cyclic granularity day-type( ``wknd\_wday'') to capture weekend and weekday behavior. Now that we have a list of cyclic granularities to look at, we should be able to compute them using Section \ref{sec:cyclic-calendar}.

\hypertarget{screening-and-visualizing-harmonies}{%
\subsubsection{Screening and visualizing harmonies}\label{screening-and-visualizing-harmonies}}

From the search list, \(N_C = 7\) cyclic granularities are chosen for which we would like to derive insights of energy behavior. Recalling the data structure \textless{}\(C_i\), \(C_j\), \texttt{general\_supply\_kwh}\textgreater{} for exploration \(\forall i, j \in \{1, 2, \ldots, 7\}\), each of these \(7\) cyclic granularities can either be mapped to x-axis or to facet. Choosing \(2\) of the possible \(7\) granularities, which is equivalent to having \(^{7}P_2 = 42\) candidates for visualization. Harmonies can be identified among those \(42\) possibilities to narrow the search. \autoref{tab:harmony-tab} shows \(16\) harmony pairs after removing clashes and any cyclic granularities with levels more than \(31\), as effective exploration becomes difficult with many levels (Section \ref{sec:levels}).

\noindent Few harmony pairs are displayed in \autoref{fig:bothcust} to illustrate the impact of different distribution plots and reverse mapping. For each of \autoref{fig:bothcust} (b) and (c), \(C_i\) is the circular granularity day-type (weekday/weekend) and \(C_j\) is hour of the day. The geometry used for displaying the distribution is chosen as area-quantiles and violins in \autoref{fig:bothcust} (b and c respectively). \autoref{fig:bothcust} (a) displays reverse mapping of \(C_i\) and \(C_j\) with \(C_i\) denoting hour of the day and \(C_j\) denoting day-type with distribution geometrically displayed as boxplots.
In \autoref{fig:bothcust} (b), the black line is the median, whereas the purple band covers 25th to 75th percentile, the orange band covers 10th to 90th percentile and the green band covers 1st to 99th percentile. The first facet represents the weekday behavior while the second one displays the weekend behavior and energy consumption across each hours of the day is shown inside each facet. The energy consumption is extremely (positive- or right-) skewed with the 1st, 10th and 25th percentile lying relatively close whereas 75th, 90th and 99th lying further away from each other. This is common across both weekdays and weekends. For the first few hours on weekdays, median energy consumption starts and continues to be higher for longer as compared to weekends.

\noindent Consider looking at violin plots instead of quantile plots to look at the same data in \autoref{fig:bothcust}(c) for some more insights. There is bimodality in the early hours of the day, implying both low and high energy consumption is probable in the early hours of the day both for weekdays and weekends. If we visualize the same data with reverse mapping of the cyclic granularities, then the natural tendency would be to compare weekend and weekday behavior within each hour and not across hours. For example in \autoref{fig:bothcust}(a), it can be seen that median energy consumption for the early morning hours is higher for weekdays than weekends. Also, outliers are more prominent in the latter hours of the day. All of these indicate that looking at different distribution geometry or changing the mapping might shed lights on different aspect of the energy behavior for the same sample population.

\begin{table}

\caption{\label{tab:harmony-tab}Harmonies with a pair of cyclic granularity one placed on facet and the other on x-axis. Out of 42 possible combinations of cyclic granularities, only 16 are harmony pairs.}
\centering
\begin{tabular}[t]{llrr}
\toprule
facet variable & x-axis variable & facet levels & x-axis levels\\
\midrule
day\_week & hour\_day & 7 & 24\\
day\_month & hour\_day & 31 & 24\\
week\_month & hour\_day & 5 & 24\\
wknd\_wday & hour\_day & 2 & 24\\
hour\_day & day\_week & 24 & 7\\
\addlinespace
day\_month & day\_week & 31 & 7\\
week\_month & day\_week & 5 & 7\\
hour\_day & day\_month & 24 & 31\\
day\_week & day\_month & 7 & 31\\
wknd\_wday & day\_month & 2 & 31\\
\addlinespace
hour\_day & week\_month & 24 & 5\\
day\_week & week\_month & 7 & 5\\
wknd\_wday & week\_month & 2 & 5\\
hour\_day & wknd\_wday & 24 & 2\\
day\_month & wknd\_wday & 31 & 2\\
\addlinespace
week\_month & wknd\_wday & 5 & 2\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}

{\centering \includegraphics[width=0.9\linewidth]{figure/bothcust-1}

}

\caption{Energy consumption of a single customer shown with different distribution displays, and granularity arrangements. Two granularities are used: hour of the day (I) and weekday/weekend (II). Plot (a) shows granularity I faceted by granularity II, and plots (b), (c) shows the converse mapping. Plot (a) makes a comparison of usage by workday within each hour of the day using side-by-side boxplots. Generally, on a work day there is more consumption early in the day. Plots (b) and (c) examine the temporal trend of consumption over the course of a day, separately for the type of day. Plot (b) uses an area quantile to put the emphasis on the time series, for example, the median consumption over time shows prolonged usage in the morning on weekdays. Plot (c) uses a violin plot to place emphasis on distributional differences across hours. It can be seen that the morning use on weekdays is bimodal, some work days there is low usage, which might indicate the person is working from home and also having a late start.}\label{fig:bothcust}
\end{figure}

If the data for all keys are visualized together, it might lead to Simpson's paradox, which occurs when one observation shows a particular behavior, but this behavior paradoxically becomes obscured by aggregation. For example in a particular neighborhood one household may have the least daily power consumption for a full week, yet still not be the household with the minimum weekly power consumption. This is an intuitive possibility, because heterogeneous \texttt{customer\_id}'s with very different occupation or demographics will tend to have very different energy behavior and combining them together will somehow weaken any typical or extreme behavior. A strategy for analyzing periodicities of multiple keys together could be to group the keys basis their energy behavior across different cyclic granularities. This is beyond the scope of the current work.

\hypertarget{sec:cricket}{%
\subsection{T20 cricket data of Indian Premiere League}\label{sec:cricket}}

The method is not only restricted to temporal data, and can be generalized to many hierarchical granularities (with continuous and uni-directional nature). We illustrate this with an application to the sport cricket. Although there is no conventional time component in cricket, each ball can be thought to represent an ordering from past to future with the game progressing forward with each ball. In the Twenty20 format, an over will consist of 6 balls (with some exceptions), an innings is restricted to a maximum of 20 overs, a match will consist of 2 innings and a season consists of several matches. Thus, similar to time, there is a hierarchy where ball is nested within overs, overs nested within innings and innings within matches. The idea of cyclic granularities can be likewise mapped to this hierarchy. Example granularites then include ball of the over, over of the innings and ball of the innings. Although most of these cyclic granularities are circular in design of the hierarchy, in application of the rules some granularities are aperiodic. For example, in most cases an over will consist of 6 balls with some exceptions like wide balls or when an innings finishes before the over finishes. Thus, the cyclic granularity ball-of-over will be circular in most cases and aperiodic in others.

\noindent The Indian Premier League (IPL) is a professional Twenty20 cricket league in India contested by eight teams representing eight different cities in India. The ball by ball data for IPL season 2008 to 2016 is fetched from \href{https://www.kaggle.com/josephgpinto/ipl-data-analysis/data}{Kaggle}. The \texttt{cricket} data set in the \texttt{gravitas} package summarizes the ball-by-ball data across overs and contains information for a sample of 214 matches spanning 9 seasons (2008 to 2016) such that each over has 6 balls, each innings has 20 overs and each match has 2 innings. This could be useful in a periodic world when we wish to compute any circular/quasi-circular granularity based on a hierarchy table which look like \autoref{tab:hierarchy-cric}. However, even if the situation is not periodic, it can be interesting to visualize the distribution of a measured variable to shed light on the aperiodic behavior of a non-temporal data set similar to aperiodic events like formal meetings, workshops, conferences, school semesters in a temporal set up.

\begin{table}

\caption{\label{tab:hierarchy-cric}Hierarchy table for cricket where overs are nested within an innings, innings nested within a match and matches within a season.}
\centering
\begin{tabular}[t]{lll}
\toprule
linear (G) & single-order-up cyclic (C) & period length/conversion operator (K)\\
\midrule
over & over-of-inning & 20\\
inning & inning-of-match & 2\\
match & match-of-season & k(match, season)\\
season & 1 & 1\\
\bottomrule
\end{tabular}
\end{table}

\noindent There are many interesting questions that could possibly be answered with the \texttt{cricket} data set. For example, it would be interesting to see if the distribution of total runs vary depending on if a team bats in the first or second innings. The Mumbai Indians (MI) and Chennai Super kings (CSK) appeared in final playoffs from 2010 to 2015. We take their example in order to dive deeper into this question. From Figure \ref{fig:cricex}(a), it can be observed that for the team batting in the first innings there is an upward trend of runs per over, while there is no clear upward trend in median and quartile deviation of runs for the teams batting in the second inning. This seem to indicate that players feel mounting pressure to score more runs as they approach towards the end of the first inning. Whereas teams batting in the second innings have a set target in mind and are not subjected to such mounting pressure and may adopt a more conservative strategy, to score runs. Thus winning teams like CSK and MI seem to employ different inning strategies when it comes to their batting order.

\noindent Another fascinating exploration would be to examine if runs per over decrease in the subsequent over if fielding (defending) was good in the previous over? For establishing the fielding quality, we apply an indicator function on dismissals (1 if there was at least one wicket in the previous over due to run out or catch, 0 otherwise). Runs in the current over is then the observation variable. Dismissals in the previous over can lead to a batsman adopting a more defensive play style. Figure \ref{fig:cricex}(b) shows that no dismissals in the previous over leads to a higher median and quartile spread of runs per over as compared to the case when there has been at least one dismissal in the previous over. Wickets per over are considered as an aperiodic cyclic granularity with wickets as an aperiodic linear granularity. These granularities do not appear in the hierarchy table since it is difficult to position them in a hierarchy. These are similar to holidays or special events in temporal data.

\begin{figure}

{\centering \includegraphics[width=0.9\linewidth]{figure/cricex-1} \includegraphics[width=0.9\linewidth]{figure/cricex-2}

}

\caption{Runs per over shown with different distribution displays, and granularities. Plot (a) shows letter value plot across overs faceted by innings. For the team batting in the first innings there is an upward trend of runs per over, while there is no such pattern of runs for the teams batting in the second innings. Plot (b) shows quantile plot of runs per over across an indicator of wickets in previous over faceted by current over. This indicates that at least one wicket in the previous over leads to lower median run rate and quartile spread in the subsequent over.}\label{fig:cricex}
\end{figure}

\hypertarget{sec:discussion}{%
\section{Discussion}\label{sec:discussion}}

Exploratory data analysis and data analysis in general involve many iterations of finding and summarizing patterns. With temporal data available at ever finer scales, exploring periodicity can become overwhelming with so many possible granularities to explore. This work provides a framework to systematically explore distribution of an univariate measured variable across two cyclic time granularities by creating any cyclic granularity, ranking a list of harmonies and thereby identifying possible distribution plots for effective visualization based on relationship and levels of the cyclic granularities.

A missing piece in the package \texttt{gravitas} is the computation of cyclic aperiodic granularities which would require computing aperiodic linear granularities first. A few R packages like \texttt{almanac} and \texttt{gs} provide functionality to create recurring events that are not periodic. These functions can be imported in the \texttt{gravitas} package to accommodate for aperiodic cyclic granularities. Another future direction of work could be to further refine the search of harmonies by only selecting pairs of cyclic granularities for which variation in measured variable is significant and rating these selected harmony pairs in order of importance for exploration.

\hypertarget{acknowledgements}{%
\section*{Acknowledgements}\label{acknowledgements}}
\addcontentsline{toc}{section}{Acknowledgements}

The authors would like to thank the cohort \href{https://www.monash.edu/news/articles/team-profile-monash-business-analytics-team}{NUMBATS}, Monash University for sharing their wisdom and experience of developing R packages and Dr.~Peter Toscas \href{https://data61.csiro.au/}{from Data61 CSIRO} for providing useful inputs on improving the analysis of smart meter application. The package \texttt{gravitas} was built during the \href{https://summerofcode.withgoogle.com/archive/}{Google Summer of Code, 2019}. We would also like to thank Nicholas Spyrison for many useful discussions, sketching figures and feedback on the manuscript. More details about the package can be found on the package website \href{https://sayani07.github.io/gravitas/}{sayani07.github.io/gravitas}. This article was created with \texttt{knitr} \citep[\citet{R-knitr}]{knitr2015} and \texttt{rmarkdown} \citep[\citet{R-rmarkdown}]{rmarkdown2018}. This paper's Github repository, \href{https://github.com/Sayani07/paper-gravitas}{github.com/Sayani07/paper-gravitas}, contains all materials required to reproduce this article and the code is also available online in the supplemental materials.

\hypertarget{supplemental-materials}{%
\section{Supplemental Materials}\label{supplemental-materials}}

\textbf{Data and scripts:} Data sets and R code to reproduce all figures in this article (main.Rmd).

\textbf{R-package:} The ideas presented in this article have been implemented in the open-source R \citep{R-language} package \texttt{gravitas} \citep{R-gravitas}, available from CRAN. The R-package facilitates manipulation of single and multiple-order-up time granularities through cyclic calendar algebra, check feasibility of creating plots or drawing inferences for any two cyclic granularities by providing list of harmonies and recommend prospective probability distributions through factors described in the article. Version 0.1.2 of the package was used for the results presented in the article and is available on Github (\url{https://github.com/Sayani07/gravitas}).

\textbf{R-packages:} Each of the R packages used in this article are available online with URLs provided in the bibliography.

\bibliographystyle{agsm}
\bibliography{bibliography.bib}

\end{document}

### 2020-08-06 simulations_MMPD6.Rmd
remove renv

---
title: Choosing and rating harmonies
authors:
- name: Sayani Gupta
  affiliation: Department of Econometrics and Business Statistics, Monash University
  email: Sayani.Gupta@monash.edu

bibliography: bibliography.bib
output:
  bookdown::pdf_book:
    #base_format: rticles::asa_article
    fig_height: 5
    fig_width: 8
    fig_caption: yes
    dev: "pdf"
---

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
library(tidyverse)
library(lubridate)
library(lvplot)
library(ggridges)
library(viridis)
library(tsibble)
library(gravitas)
library(ggpubr)
library(readr)

opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
read_chunk('check_gt_mnylvls.R')
```

```{r external, include = FALSE}

```

```{r load}

```

```{r rank_harmony}

```

```{r global_threshold}

```

# Idea

Even after excluding clashes, the list of harmonies left could be large and overwhelming for human consumption. Hence, there is a need to rank the harmonies basis how well they capture the variation in the measured variable and additionally reduce the number of harmonies for further exploration/visualization. Assuming a numeric response variable, our graphics are displays of distributions compared across combinations of categorical variables, one placed at x-axis and the other on the facet. Gestalt theory suggests that when items are placed in close proximity, people assume that they are in the same group because they are close to one another and apart from other groups. Hence, displays that capture more variation within different categories in the same group would be important to bring out different patterns of the data. Here, we have two main objectives:

- To choose harmonies for which distributions of categories are significantly different 
- To rank the selected harmonies from highest to lowest variation in the distribution of their categories. The idea here is to rate a harmony pair higher if this variation between different levels of the x-axis variable is higher on an average across all levels of facet variables.

# Computing distances

One of the potential ways to evaluate this variation is by computing the pairwise distances between the distributions of the measured variable. We do this through Jensen-Shannon distance which is based on Kullback-Leibler divergence.

The Jensen-Shanon distance between two probability distribution $p_1$ and $p_2$ is given by $$d = [D(p_1, r) + D(p_2, r)]/2 \quad where \quad r = (p_1 + p_2)/2$$ where,
$$D(p_1,p_2) = \int^{\infty}_{-\infty}p_1(x)log\frac{p_1(x)}{p_2(x)}\,dx$$ is the Kullback-Leibler divergence between $p_1$ and $p_2$. Probability distributions are estimated through quantiles instead of kernel density so that there is minimal dependency on selecting kernel or bandwidth.

We call this measure of variation as  Median Maximum Pairwise Distances (MMPD).

## Normalize distances

The harmony pairs could be arranged from highest to lowest average maximum pairwise distances across different levels of the harmonies. But maximum is not robust to the number of levels and is higher for harmonies with higher levels. Thus these maximum pairwise distances need to be normalized for different harmonies in a way that eliminates the effect of different levels. The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re- normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.

More formally, $d_{1},d_{2}\ldots ,d_{n}$ be a sequence of independent and identically-distributed pairwise distances and $M_{n}=\max\{d_{1},\ldots ,d_{n}\}$. Then Fisher–Tippett–Gnedenko theorem [@De_Haan2007-yx] suggests that if a sequence of pairs of real numbers $(a_{n}, b_{n})$ exists such that each $a_{n}>0$ and $\lim _{{m\to \infty }}P\left({\frac  {M_{n}-b_{n}}{a_{n}}}\leq x\right)=F(x)$, where $F$ is a non-degenerate distribution function, then the limit distribution $F$ belongs to either the Gumbel, Fréchet or Weibull family. The normalizing constants $(a_{n}, b_{n})$ vary depending on the underlying distribution of the pairwise distances. Hence to normalize appropriately, it is important to assume a distribution of these distances.

## Distribution of distances

Theoretical: JS distances are distributed as chi-squared with $m$ df where we discretize the continuous distribution with $m$ discrete values. Taking sample percentiles to approximate the integral would mean taking $m = 99$.
With large $m$, chi-squared is asymptotically normal by the CLT. Thus, by CLT, ${\chi^2}_{m} \tilde{} N(m, 2m)$, which would depend on the number of discretization used to approximate the continuous distribution. Then $b_n = 1-1/n$ quantile of the normal distribution and $a_n = 1/[n*\phi(b_n)]$ where $\phi$ is the normal density function. $n$ is the number of pairwise comparisons being made.

Empirical: Distribution of JS distances is assumed to be normal but the mean and variance are estimated from the sample, rather than deducing it from the number of discretization used to approximate the continuous distribution.

# Choose thresholds for harmonies through permutation test

**Assumption:** random permutation without considering ordering 
(global)

1. Given the data; $\{v_t: t=0, 1, 2, \dots, T-1\}$, the MMPD is computed and is represented by $MMPD_{obs}$.

2. From the original sequence a random permutation is obtained: $\{v_t^*: t=0, 1, 2, \dots, T-1\}$.

3. MMPD is computed for all random permutation of the data and is represented by $MMPD_{sample}$.

4.  Steps (2) and (3) are repeated a large number
of times M (e.g. 1000).

5. For each permutation, one $MMPD_{sample}$ value is obtained.

6. $95^{th}$ percentile of this $MMPD_{sample}$ distribution is computed and stored in $MMPD_{threshold}$.

7. If  $MMPD_{obs}> MMPD_{threshold}$, harmony pairs are accepted. Only one threshold for all harmony pairs.

Pros: Considering thresholds global for all harmony pairs would imply less computation time.

Cons: Only one threshold for all harmony pairs means we are assuming distribution of all harmonies pairs are similar, which might not be the case.But nevertheless, it is a good benchmark.

```{r, eval = FALSE, echo = FALSE}
smart_harmony <-read_rds("data/smart_harmony_nonst.rds")
smart_harmony
```

```{r smart_harmony,eval = FALSE, echo = FALSE}

sm <- smart_meter10 %>% dplyr::filter(customer_id %in% c("10017936"))

harmonies <- sm %>% 
  harmony(ugran = "month",
          filter_in = "wknd_wday",
          filter_out = c("hhour", "fortnight"))

harmony_tbl =  harmonies

smart_harmony <- sm %>% 
  rank_harmony(harmony_tbl = harmonies,
               response = "general_supply_kwh", 
               dist_ordered = TRUE)

smart_harmony %>% 
  mutate(MMPD = round(MMPD, 3), max_pd = round(max_pd, 3)) %>% 
  mutate(rankn = row_number()) %>%
  rename("rankun" = "r") %>% kable()
```

# Does normalization work? -  Minimal examples

Consider two cyclic granularities $A$ and $B$ with $2$ and $3$categories. Thus, the harmony table consisting of all possible harmony pairs (assuming all pairs are harmonies), would look like the following:

```{r harmony_min}
# harmonies <- tibble::tibble(facet_variable = c("A", "B", "A", "C", "B", "C"),
#                             x_variable  = c("B","A", "C", "A", "C", "B"),
#                             facet_levels = c(2, 3, 2, 4, 3, 4),
#                             x_levels = c(3, 2, 4, 2, 4, 3))

harmonies <- tibble::tibble(facet_variable = c("A", "B"),
                            x_variable  = c("B","A"),
                            facet_levels = c(2, 3),
                            x_levels = c(3, 2))

harmonies %>% knitr::kable()
```

The output table has the value of MMPD (normalized median maximum pairwise distances), max_pd (un-normalized maximum pairwise distances), r(Rank of max_pd), gt_MMPD(global threshold of MMPD indicator) and gt_maxpd(global threshold of max_pd indicator).

## Scenario 1: Simulated same normal distributions for all combinations of categories for all harmony pairs.

Failure to reject the null hypothesis when there is in fact no significant effect.

```{r samenull_2by4}

```

*Conclusion*: The test does not select harmony pairs when distributions of categories are same

## Scenario 2: Simulated different distributions for all combinations of categories for harmony pairs for few levels.

```{r diffnull_2by4}

```

*Conclusion*: The test select the harmony pair for which distribution of x-axis categories are significantly different

## Scenario 3: Simulated different distributions for all combinations of categories for all harmony pairs with many levels.

```{r diffnull_7by11}
```

*Conclusion*: The test with MMPD rejects the harmony pair even for which distribution of x-axis categories are significantly different. But the test with only maximum selects the pair with varying x-axis categories.

## Scenario 4: Cumulative 3 levels with 2, 7 and 11 and testing level and power

```{r samenull_3levels}

```

*Conclusion*: With 3 levels the test incorrectly chooses 1 harmony pair with similar distribution. The harmony pair which is displayed.

```{r diffnull_3levels}

```

*Conclusion*: The test with MMPD selects just one pair, as opposed to the test with maximum. This needs to be checked against what we expect from the test. The harmony pairs which are selected (either through MMPD or maximum) are displayed.

# histograms of MMPD when levels are different
When all distributions of response variables are generated from normal, how do the histogram looks

### 2020-08-06 check_gt_mnylvls.R

@@ -1,0 +1,649 @@
+##----load
+library(ggplot2)
+library(gravitas)
+library(purrr)
+library(distributional)
+library(magrittr)
+library(tidyr)
+library(dplyr)
+library(ggpubr)
+
+
+##----rank_harmony
+rank_harmony <- function(.data = NULL,
+                         harmony_tbl = NULL,
+                         response = NULL,
+                         prob = seq(0.01, 0.99, 0.01),
+                         dist_distribution = "normal",
+                         hierarchy_tbl = NULL,
+                         dist_ordered = TRUE,
+                         alpha = 0.05,
+                         create_gran_data = TRUE)
+{
+  # <- _data <- <- <- step1(.data, harmony_tbl, response)
+  
+  dist_harmony_data <- dist_harmony_tbl(.data, harmony_tbl, response, prob, dist_distribution, hierarchy_tbl, dist_ordered, create_gran_data)
+  
+  comp_dist <- dist_harmony_data %>%
+    unlist %>%
+    matrix(ncol = 2, byrow = TRUE) %>%
+    tibble::as_tibble(.name_repair = "unique")
+  
+  # all for n = 100
+  # taken from Tests for the Exponential, Weibull and Gumbel Distributions Based on the Stabilized Probability Plot
+  if(alpha == 0.05){
+    galpa <- 0.073
+  }
+  else if (alpha == 0.1){
+    galpa <- 0.066
+  }
+  else if (alpha == 0.01){
+    galpa <- 0.089
+  }
+  
+  mean_max <- comp_dist$...1
+  max_distance <- comp_dist$...2
+  
+  harmony_sort <- harmony_tbl %>%
+    dplyr::mutate(MMPD = round(mean_max,5),
+                  max_pd = round(max_distance,5)) %>%
+    dplyr::arrange(dplyr::desc(MMPD)) %>%
+    dplyr::mutate(r = rank(-max_pd)) %>%
+    #dplyr::filter(max_norm_s>=galpa) %>%
+    #dplyr::select(-max_norm_s) %>%
+    dplyr::filter(!is.na(MMPD))
+  
+  harmony_sort
+}
+
+
+# loop through all harmony pairs in the harmony table
+# uses dist_harmony_pair used for calculating max pairiwise
+# distance for one harmony pair
+
+dist_harmony_tbl <- function(.data, harmony_tbl, response, prob,
[…]

### 2020-08-06 global_threshold.R

@@ -1,0 +1,194 @@
+#' Selecting harmonies with significant difference in distributions for two cyclic granularities
+#'
+#' @param .data a tsibble.
+#' @param response response variable.
+#' @param harmony_tbl A tibble of harmonies and their levels obtained from the function().
+#' @param prob numeric vector of probabilities with values in [0,1].
+#' @param hierarchy_tbl A hierarchy table specifying the hierarchy of units
+#' @param create_gran_data if data corresponding to a pair of cyclic granularity needs to be created
+#' @param nsamp sample size of permutation test to compute threshold
+#' @param dist_ordered if levels of the time granularity is ordered.
+#' @examples
+#' \dontrun{
+#' library(tsibbledata)
+#' library(ggplot2)
+#' library(tsibble)
+#' library(lvplot)
+#' library(dplyr)
+#' library(gravitas)
+#' library(purrr)
+#' library(magrittr)
+#' sm <- smart_meter10 %>%
+#' filter(customer_id %in% c("10017936"))
+#' .data = sm
+#' harmonies <- sm %>%
+#' harmony(ugran = "month",
+#'        filter_in = "wknd_wday",
+#'        filter_out = c("hhour", "fortnight"))
+#' gran1 = "wknd_wday"
+#' gran2 = "hour_day"
+#' response  = "general_supply_kwh"
+#' global_harmony <-  sm %>%
+#' global_threshold(harmony_tbl = harmonies,
+#' response = "general_supply_kwh", nsamp = 2)
+#' }
+#' @export
+global_threshold <- function(.data = NULL,
+                             harmony_tbl = NULL,
+                             response = NULL,
+                             prob = seq(0.01,0.99, 0.01),
+                             hierarchy_tbl = NULL,
+                             create_gran_data = TRUE,
+                             dist_ordered = TRUE,
+                             nsamp = 20,...)
+{
+  MMPD_obs <-  .data %>%
+    rank_harmony(harmony_tbl = harmonies,
+                 response = response,
+                 create_gran_data = create_gran_data,
+                 dist_ordered = dist_ordered,...)
+  
+  
+  MMPD_sample_lst <- (1:nsamp) %>%
+    purrr::map(function(i){
+      
+      if(create_gran_data)
+      {
+        response_sample <-  sample(.data[[response]], size = nrow(.data))
+        
+        data_sample <- .data %>%
[…]

### 2020-08-14 simulations_MMPD6.Rmd
initial commit
cleaner code

@@
 
+# Levels and Power of the test statistic
+
 *Conclusion*: With 3 levels the test incorrectly chooses 1 harmony pair with similar distribution. The harmony pair which is displayed.
 
-```{r diffnull_3levels}
+<!-- ```{r diffnull_3levels} -->
 
-```
+<!-- ``` -->
 
@@
 When all distributions of response variables are generated from normal, how do the histogram looks
+
+# Permutation test
+
+To estimate the sampling distribution of the test statistic we
+need many samples generated under the null hypothesis.
+If the null hypothesis is true, changing the exposure would have
+no effect on the outcome. By randomly shuffling the exposures
+we can make up as many data sets as we like.
+If the null hypothesis is true the shuffled data sets should look
+like the real data, otherwise they should look different from the
+real data.
+The ranking of the real test statistic among the shuffled test
+statistics gives a p-value.
+
+```{r}
+harmonies <- tibble::tibble(facet_variable = c("A", "B"),x_variable  = c("B","A"), facet_levels = c(2, 3),x_levels = c(3, 2))
+
+har1 <- harmonies[1,]
+
+sim_dist1 = c(rep(distributional::dist_normal(mu = 10, sigma = 5),2),rep(distributional::dist_exponential(10),2), rep(distributional::dist_weibull(0.5, 2),2))
+
+data1 <- sim_distharmony1(har1, sim_dist = sim_dist1)
+data1
+
+data1 %>% unnest(sim_dist) %>%
+  ggplot(aes(x = Var2, y = sim_dist)) +
+  facet_wrap(~Var1) + geom_boxplot() + ggtitle("Same distribution 2 by 3")
+
+response = "sim_dist"
+
+MMPD_distribution <- data1 %>%
+  select(-dist) %>% 
+  unnest(sim_dist) %>% 
+  list() %>% 
+  global_threshold(harmony_tbl = har1,
+                   response = "sim_dist",
+                   dist_distribution = "normal",
+                   dist_ordered = TRUE,
+                   create_gran_data = FALSE, nsamp = 20)
+
+# as_tibble(sample_MMPD) %>% mutate(id = row_number()) %>% 
+#   ggplot() + geom_histogram(aes(x = value))
+
+```

### 2020-08-14 check_gt_mnylvls.R

@@ -8,6 +8,46 @@ library(tidyr)
 library(dplyr)
 library(ggpubr)
 
+##--sim_plot
+sim_plot <- function(.data, sim_dist, nsamp = 20)
+{
+  data1 <- sim_distharmony1(.data, sim_dist = sim_dist)
+  data2 <- data1
+  names(data2) =  c("Var2", "Var1","dist","sim_dist")
+  
+  data_l = bind_cols(pairn = 1L, data1) %>% select(-dist) %>% unnest(sim_dist)
+  data_m = bind_cols(pairn = 2L, data2) %>% select(pairn, Var1, Var2,sim_dist, -dist) %>% unnest(sim_dist)
+  data_mlist =  list(data_l, data_m)
+  
+  harmonies = .data
+  
+  global_harmony <-  map(data_mlist, ~ (.x %>% select(-1)))%>%
+    global_threshold(harmony_tbl = harmonies,
+                     response = "sim_dist",
+                     dist_distribution = "normal",
+                     dist_ordered = TRUE,
+                     create_gran_data = FALSE, nsamp = nsamp)
+  
+  g = global_harmony[[2]] %>% as_tibble()
+  h1 = global_harmony[[1]]$MMPD[1]
+  h2 = global_harmony[[1]]$MMPD[2]
+  h3 = global_harmony[[3]]
+  
+  sim_hist <- ggplot(g, aes(x = value)) + geom_histogram()  + geom_vline(xintercept =  h1, colour = "red") +
+    geom_vline(xintercept =  h2, colour = "blue") +  geom_vline(xintercept =  h3, colour = "black")
+  
+  
+  
+  plot_harmony_row1 <- data1 %>% select(-dist) %>% unnest(sim_dist) %>%
+    ggplot(aes(x = Var2, y = sim_dist)) +
+    facet_wrap(~Var1) + geom_boxplot()
+  
+  plot_harmony_row2 <- data2 %>% select(-dist) %>% unnest(sim_dist) %>%
+    ggplot(aes(x = Var2, y = sim_dist)) +
+    facet_wrap(~Var1) + geom_boxplot()
+  
+  return(list(sim_hist, plot_harmony_row1, plot_harmony_row2))
+}
 
 ##----rank_harmony
 rank_harmony <- function(.data = NULL,
[…]

### 2020-08-14 simulations_MMPD6.Rmd
README update

--- 2020-08-06 simulations_MMPD6.Rmd
@@
 
-The output table has the value of MMPD (normalized median maximum pairwise distances), max_pd (un-normalized maximum pairwise distances), r(Rank of max_pd), gt_MMPD(global threshold of MMPD indicator) and gt_maxpd(global threshold of max_pd indicator).
+The output table has the value of MMPD (normalized median maximum pairwise distances), gt_MMPD(global threshold of MMPD indicator).
 
@@
 
-```{r diffnull_3levels}
+# Levels and Power of the test statistic
 
-```
+<!-- ```{r diffnull_3levels} -->
+
+<!-- ``` -->
 
@@
 
-# histograms of MMPD when levels are different
-When all distributions of response variables are generated from normal, how do the histogram looks
+# Permutation test
+
+To estimate the sampling distribution of the test statistic we need many samples generated under the null hypothesis.
+If the null hypothesis is true, changing the exposure would have no effect on the outcome.
+By randomly shuffling the exposures we can make up as many data sets as we like.
+If the null hypothesis is true the shuffled data sets should look like the real data, otherwise they should look different from the
+real data. The ranking of the real test statistic among the shuffled test statistics gives a p-value.
+
+<!-- # ```{r} -->
+<!-- # harmonies <- tibble::tibble(facet_variable = c("A", "B"),x_variable  = c("B","A"), facet_levels = c(2, 3),x_levels = c(3, 2)) -->
+<!-- #  -->
+<!-- # har1 <- harmonies[1,] -->
+<!-- #  -->
+<!-- # sim_dist1 = c(rep(distributional::dist_normal(mu = 10, sigma = 5),2),rep(distributional::dist_exponential(10),2), rep(distributional::dist_weibull(0.5, 2),2)) -->
+<!-- #  -->
+<!-- # data1 <- sim_distharmony1(har1, sim_dist = sim_dist1) -->
+<!-- # data1 -->
+<!-- #  -->
+<!-- # data1 %>% unnest(sim_dist) %>% -->
+<!-- #   ggplot(aes(x = Var2, y = sim_dist)) + -->
+<!-- #   facet_wrap(~Var1) + geom_boxplot() + ggtitle("Same distribution 2 by 3") -->
+<!-- #  -->
+<!-- # response = "sim_dist" -->
+<!-- #  -->
+<!-- # MMPD_distribution <- data1 %>% -->
+<!-- #   select(-dist) %>%  -->
+<!-- #   unnest(sim_dist) %>%  -->
+<!-- #   list() %>%  -->
+<!-- #   global_threshold(harmony_tbl = har1, -->
+<!-- #                    response = "sim_dist", -->
+<!-- #                    dist_distribution = "normal", -->
+<!-- #                    dist_ordered = TRUE, -->
+<!-- #                    create_gran_data = FALSE, nsamp = 20) -->
+<!-- #  -->
+<!-- # # as_tibble(sample_MMPD) %>% mutate(id = row_number()) %>%  -->
+<!-- # #   ggplot() + geom_histogram(aes(x = value)) -->
+<!-- #  -->
+<!-- # ``` -->
+<!-- #  -->

### 2020-08-14 main.Rmd
paper structure

--- 2020-08-14 simulations_MMPD6.Rmd
@@
 knitr::opts_knit$set(root.dir = here::here())
-read_chunk('check_gt_mnylvls.R')
+read_chunk('main.R')
 ```
@@
 
-# Idea
+```{r}
+set.seed(321)
+```
+
+# Introduction
+
+# Background
 
@@
 
-# Computing distances
+# A new test statistic
+
+## Computing distances
 
@@
 
-Theoretical: JS distances are distributed as chi-squared with $m$ df where we discretize the continuous distribution with $m$ discrete values.
+### Theoretical evidence
+
+JS distances are distributed as chi-squared with $m$ df where we discretize the continuous distribution with $m$ discrete values.
 Taking sample percentiles to approximate the integral would mean taking $m = 99$.
@@
 
-Empirical: Distribution of JS distances is assumed to be normal but the mean and variance are estimated from the sample, rather than deducing it from the number of discretization used to approximate the continuous distribution.
+### Empirical evidence
 
-# Choose thresholds for harmonies through permutation test
+Distribution of JS distances is assumed to be normal but the mean and variance are estimated from the sample, rather than deducing it from the number of discretization used to approximate the continuous distribution.
+
+# The statistical test
+
+## Threshold definition for test through permutation test
 
@@
 
-# Does normalization work? -  Minimal examples
+## Level and power of the test
 
-Consider two cyclic granularities $A$ and $B$ with $2$ and $3$categories.
-Thus, the harmony table consisting of all possible harmony pairs (assuming all pairs are harmonies), would look like the following:
+To estimate the sampling distribution of the test statistic we need many samples generated under the null hypothesis.
+If the null hypothesis is true, changing the exposure would have no effect on the outcome.
+By randomly shuffling the exposures we can make up as many data sets as we like.
+If the null hypothesis is true the shuffled data sets should look like the real data, otherwise they should look different from the
+real data. The ranking of the real test statistic among the shuffled test statistics gives a p-value.
+
+<!-- Consider two cyclic granularities $A$ and $B$ with $2$ and $3$categories.
+Thus, the harmony table consisting of all possible harmony pairs (assuming all pairs are harmonies), would look like the following: -->
 
@@
 #                             x_levels = c(3, 2, 4, 2, 4, 3))
-
-harmonies <- tibble::tibble(facet_variable = c("A", "B"),
-                            x_variable  = c("B","A"),
-                            facet_levels = c(2, 3),
-                            x_levels = c(3, 2))
-
-harmonies %>% knitr::kable()
+# 
+# harmonies <- tibble::tibble(facet_variable = c("A", "B"),
+#                             x_variable  = c("B","A"),
+#                             facet_levels = c(2, 3),
+#                             x_levels = c(3, 2))
+#                             
+# harmonies %>% knitr::kable()
 ```
 
-The output table has the value of MMPD (normalized median maximum pairwise distances), gt_MMPD(global threshold of MMPD indicator).
+<!-- The output table has the value of MMPD (normalized median maximum pairwise distances), gt_MMPD(global threshold of MMPD indicator). -->
 
@@
 
-*Conclusion*: The test with MMPD rejects the harmony pair even for which distribution of x-axis categories are significantly different.
-But the test with only maximum selects the pair with varying x-axis categories.
+*Conclusion*: The test indicates that both harmony pairs do not have significant variation.
 
-## Scenario 4: Cumulative 3 levels with 2, 7 and 11 and testing level and power
-
-```{r samenull_3levels}
-
+```{r diffnull_7by11normal}
 ```
 
-*Conclusion*: With 3 levels the test incorrectly chooses 1 harmony pair with similar distribution. The harmony pair which is displayed.
+*Conclusion*: The test indicates that only the first harmony pair has significant variation.
 
-# Levels and Power of the test statistic
+```{r diffnull_7by11normal2}
+```
 
-<!-- ```{r diffnull_3levels} -->
+*Conclusion*: The test indicates that only the first harmony pair has significant variation.
+
+<!-- ## Scenario 4: Cumulative 3 levels with 2, 7 and 11 and testing level and power -->
+
+<!-- ```{r samenull_3levels} -->
 
@@
 
-*Conclusion*: The test with MMPD selects just one pair, as opposed to the test with maximum.
+<!-- *Conclusion*: With 3 levels the test incorrectly chooses 1 harmony pair with similar distribution. The harmony pair which is displayed. -->
+
+<!-- <!-- ```{r diffnull_3levels} --> -->
+
+<!-- <!-- ``` --> -->
+
+<!-- *Conclusion*: The test with MMPD selects just one pair, as opposed to the test with maximum.
 This needs to be checked against what we expect from the test.
 The harmony pairs which are selected (either through MMPD or maximum) are displayed.
-
-# Permutation test
-
-To estimate the sampling distribution of the test statistic we need many samples generated under the null hypothesis.
-If the null hypothesis is true, changing the exposure would have no effect on the outcome.
-By randomly shuffling the exposures we can make up as many data sets as we like.
-If the null hypothesis is true the shuffled data sets should look like the real data, otherwise they should look different from the
-real data. The ranking of the real test statistic among the shuffled test statistics gives a p-value.
+-->
 
@@
 <!-- #  -->
+
+# Application
+
+# Conclusion

### 2020-08-14 main.R

@@ -1,0 +1,609 @@
+##----load
+library(ggplot2)
+library(gravitas)
+library(purrr)
+library(distributional)
+library(magrittr)
+library(tidyr)
+library(dplyr)
+library(ggpubr)
+
+##--sim_plot
+sim_plot <- function(.data, sim_dist, nsamp = 20)
+{
+  data1 <- sim_distharmony1(.data, sim_dist = sim_dist)
+  data2 <- data1
+  names(data2) =  c("Var2", "Var1","dist","sim_dist")
+  
+  data_l = bind_cols(pairn = 1L, data1) %>% select(-dist) %>% unnest(sim_dist)
+  data_m = bind_cols(pairn = 2L, data2) %>% select(pairn, Var1, Var2,sim_dist, -dist) %>% unnest(sim_dist)
+  data_mlist =  list(data_l, data_m)
+  
+  harmonies = .data
+  
+  global_harmony <-  map(data_mlist, ~ (.x %>% select(-1)))%>%
+    global_threshold(harmony_tbl = harmonies,
+                     response = "sim_dist",
+                     dist_distribution = "normal",
+                     dist_ordered = TRUE,
+                     create_gran_data = FALSE, nsamp = nsamp)
+  
+  g = global_harmony[[2]] %>% as_tibble()
+  h1 = global_harmony[[1]]$MMPD[1]
+  h2 = global_harmony[[1]]$MMPD[2]
+  h3 = global_harmony[[3]]
+  
+  sim_hist <- ggplot(g, aes(x = value)) + geom_histogram()  + geom_vline(xintercept =  h1, colour = "red", show.legend = TRUE) +
+    geom_vline(xintercept =  h2, colour = "blue", show.legend = TRUE) +  geom_vline(xintercept =  h3, colour = "black", show.legend = TRUE) 
+  
+  
+  
+  plot_harmony_row1 <- data1 %>% select(-dist) %>% unnest(sim_dist) %>%
+    ggplot(aes(x = Var2, y = sim_dist)) +
+    facet_wrap(~Var1) + geom_boxplot()
+  
+  plot_harmony_row2 <- data2 %>% select(-dist) %>% unnest(sim_dist) %>%
+    ggplot(aes(x = Var2, y = sim_dist)) +
+    facet_wrap(~Var1) + geom_boxplot()
+  
+  return(list(sim_hist, plot_harmony_row1, plot_harmony_row2, global_harmony[[1]], data1))
+}
+
+##----rank_harmony
[…]

### 2020-08-14 main.Rmd
refining structure

@@
 
-# Background
-
 Even after excluding clashes, the list of harmonies left could be large and overwhelming for human consumption.
@@
 
-## Computing distances
+## Distance between distributions
 
@@
 
+## Algorithm
+
+\noindent The algorithm employed for computing MMPD is summarized as follows:
+<!-- Algorithm -->
+
+<!-- 1.
+Suppose $C_i$ and $C_2$ are two cyclic granularities such that $C_i$ maps index set to a set $\{A_1, A_2, A_3, \dots, A_l$\}, and $C_2$ maps index set to a set $\{B_1, B_2, B_3, \dots, B_m$\} and $v$ is the measured variable.
+Hence for each combination ($A_k$, $B_l$), we have the time series variable $v_{ij} \subseteq v$, $\forall i = {1, 2, \dots, l}$ and $\forall j = {1, 2, \dots, m}$ -->
+
+- **Input:** Data corresponding to all harmony pairs, i.e., data sets of the form $(C_i, C_j, v)$ 
+$\forall i, j \in N_C$  
+- **Output:** MMPD (Median Maximum Pairwise Distances) measuring the average variation across different levels of $C_i$ and $C_j$ $\forall i, j \in N_C$
+
+1. Fix harmony pair $(C_i, C_j)$.
+
+2. Fix $k$. Then there are $L$ groups corresponding to level $A_k$ of $C_i$.
+
+3. Compute  $m = \binom{L}{2}$ pairwise distances between distributions of $L$ unordered levels and $m = L-1$ pairwise distances for $L$ ordered categories.
+
+4. Identify maximum within the $m$ computed distances.
+
+5. Compute normalized maximum distance ($NM$) using appropriate norming constants.
+<!--so that the distribution of the normalized maximum converges to a Gumbel distribution as $m\rightarrow\infty$.-->
+
+6. Use Steps 1-5 to compute normalized maximum distance for $\forall k \in  \{1, 2, \ldots, K\}$.
+
+7. Compute MMPD = median $(NM_1, NM_2, \dots, NM_K)$/log($K$).
+
+8. Repeat Steps 1 to 7 for all harmony pairs.
+
+### Interpreting the test statistic
+
 # The statistical test
 
-## Threshold definition for test through permutation test
+## Algorithm for threshold
 
@@
 
-## Level and power of the test
+## Level and power
 
@@
 
-## Scenario 1: Simulated same normal distributions for all combinations of categories for all harmony pairs.
+### Scenario 1: Simulated same normal distributions for all combinations of categories for all harmony pairs.
 
@@
 
-## Scenario 2: Simulated different distributions for all combinations of categories for harmony pairs for few levels.
+### Scenario 2: Simulated different distributions for all combinations of categories for harmony pairs for few levels.
 
@@
 
-## Scenario 3: Simulated different distributions for all combinations of categories for all harmony pairs with many levels.
+### Scenario 3: Simulated different distributions for all combinations of categories for all harmony pairs with many levels.
 
@@
 
+### Scenario 4: Simulated different distributions for all combinations of categories for all harmony pairs with many levels - very different distribution across x-axis
+
 ```{r diffnull_7by11normal}
@@
 
+### Scenario 5: Simulated different distributions for all combinations of categories for all harmony pairs with many levels - very different distribution across facets
+
 ```{r diffnull_7by11normal2}
@@
 
-*Conclusion*: The test indicates that only the first harmony pair has significant variation.
+<!-- *Conclusion*:  -->
 

### 2020-08-15 simulations_MMPD.Rmd
rough structure

--- 2020-08-14 main.Rmd
@@
 ---
-title: Choosing and rating harmonies
-authors:
-- name: Sayani Gupta
-  affiliation: Department of Econometrics and Business Statistics, Monash University
-  email: Sayani.Gupta@monash.edu
+title: "Simulations for MMPD"
+author: "Sayani Gupta"
+date: "15/08/2020"
+output: html_document
+---
 
-bibliography: bibliography.bib
-output:
-  bookdown::pdf_book:
-    #base_format: rticles::asa_article
-    fig_height: 5
-    fig_width: 8
-    fig_caption: yes
-    dev: "pdf"
----
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+```
 
@@
 ```
-
-```{r}
-set.seed(321)
-```
-
-# Introduction
-
-# Background
-
-Even after excluding clashes, the list of harmonies left could be large and overwhelming for human consumption.
-Hence, there is a need to rank the harmonies basis how well they capture the variation in the measured variable and additionally reduce the number of harmonies for further exploration/visualization.
-Assuming a numeric response variable, our graphics are displays of distributions compared across combinations of categorical variables, one placed at x-axis and the other on the facet.
-Gestalt theory suggests that when items are placed in close proximity, people assume that they are in the same group because they are close to one another and apart from other groups.
-Hence, displays that capture more variation within different categories in the same group would be important to bring out different patterns of the data.
-Here, we have two main objectives:
-
-- To choose harmonies for which distributions of categories are significantly different 
-- To rank the selected harmonies from highest to lowest variation in the distribution of their categories.
-The idea here is to rate a harmony pair higher if this variation between different levels of the x-axis variable is higher on an average across all levels of facet variables.
-
-# A new test statistic
-
-## Computing distances
-
-One of the potential ways to evaluate this variation is by computing the pairwise distances between the distributions of the measured variable.
-We do this through Jensen-Shannon distance which is based on Kullback-Leibler divergence.
-
-The Jensen-Shanon distance between two probability distribution $p_1$ and $p_2$ is given by $$d = [D(p_1, r) + D(p_2, r)]/2 \quad where \quad r = (p_1 + p_2)/2$$ where,
-$$D(p_1,p_2) = \int^{\infty}_{-\infty}p_1(x)log\frac{p_1(x)}{p_2(x)}\,dx$$ is the Kullback-Leibler divergence between $p_1$ and $p_2$.
-Probability distributions are estimated through quantiles instead of kernel density so that there is minimal dependency on selecting kernel or bandwidth.
-
-We call this measure of variation as  Median Maximum Pairwise Distances (MMPD).
-
-## Normalize distances
-
-The harmony pairs could be arranged from highest to lowest average maximum pairwise distances across different levels of the harmonies.
-But maximum is not robust to the number of levels and is higher for harmonies with higher levels.
-Thus these maximum pairwise distances need to be normalized for different harmonies in a way that eliminates the effect of different levels.
-The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re- normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.
-
-More formally, $d_{1},d_{2}\ldots ,d_{n}$ be a sequence of independent and identically-distributed pairwise distances and $M_{n}=\max\{d_{1},\ldots ,d_{n}\}$.
-Then Fisher–Tippett–Gnedenko theorem [@De_Haan2007-yx] suggests that if a sequence of pairs of real numbers $(a_{n}, b_{n})$ exists such that each $a_{n}>0$ and $\lim _{{m\to \infty }}P\left({\frac  {M_{n}-b_{n}}{a_{n}}}\leq x\right)=F(x)$, where $F$ is a non-degenerate distribution function, then the limit distribution $F$ belongs to either the Gumbel, Fréchet or Weibull family.
-The normalizing constants $(a_{n}, b_{n})$ vary depending on the underlying distribution of the pairwise distances.
-Hence to normalize appropriately, it is important to assume a distribution of these distances.
-
-## Distribution of distances
-
-### Theoretical evidence
-
-JS distances are distributed as chi-squared with $m$ df where we discretize the continuous distribution with $m$ discrete values.
-Taking sample percentiles to approximate the integral would mean taking $m = 99$.
-With large $m$, chi-squared is asymptotically normal by the CLT.
-Thus, by CLT, ${\chi^2}_{m} \tilde{} N(m, 2m)$, which would depend on the number of discretization used to approximate the continuous distribution.
-Then $b_n = 1-1/n$ quantile of the normal distribution and $a_n = 1/[n*\phi(b_n)]$ where $\phi$ is the normal density function.
-$n$ is the number of pairwise comparisons being made.
-
-### Empirical evidence
-
-Distribution of JS distances is assumed to be normal but the mean and variance are estimated from the sample, rather than deducing it from the number of discretization used to approximate the continuous distribution.
-
-# The statistical test
-
-## Threshold definition for test through permutation test
-
-**Assumption:** random permutation without considering ordering 
-(global)
-
-1. Given the data; $\{v_t: t=0, 1, 2, \dots, T-1\}$, the MMPD is computed and is represented by $MMPD_{obs}$.
-
-2. From the original sequence a random permutation is obtained: $\{v_t^*: t=0, 1, 2, \dots, T-1\}$.
-
-3. MMPD is computed for all random permutation of the data and is represented by $MMPD_{sample}$.
-
-4.  Steps (2) and (3) are repeated a large number
-of times M (e.g. 1000).
-
-5. For each permutation, one $MMPD_{sample}$ value is obtained.
-
-6. $95^{th}$ percentile of this $MMPD_{sample}$ distribution is computed and stored in $MMPD_{threshold}$.
-
-7. If  $MMPD_{obs}> MMPD_{threshold}$, harmony pairs are accepted. Only one threshold for all harmony pairs.
-
-Pros: Considering thresholds global for all harmony pairs would imply less computation time.
-
-Cons: Only one threshold for all harmony pairs means we are assuming distribution of all harmonies pairs are similar, which might not be the case.But nevertheless, it is a good benchmark.
-
-```{r, eval = FALSE, echo = FALSE}
-smart_harmony <-read_rds("data/smart_harmony_nonst.rds")
-smart_harmony
-```
-
-```{r smart_harmony,eval = FALSE, echo = FALSE}
-
-sm <- smart_meter10 %>% dplyr::filter(customer_id %in% c("10017936"))
-
-harmonies <- sm %>% 
-  harmony(ugran = "month",
-          filter_in = "wknd_wday",
-          filter_out = c("hhour", "fortnight"))
-
-harmony_tbl =  harmonies
-
-smart_harmony <- sm %>% 
-  rank_harmony(harmony_tbl = harmonies,
-               response = "general_supply_kwh", 
-               dist_ordered = TRUE)
-
-smart_harmony %>% 
-  mutate(MMPD = round(MMPD, 3), max_pd = round(max_pd, 3)) %>% 
-  mutate(rankn = row_number()) %>%
-  rename("rankun" = "r") %>% kable()
-```
-
-## Level and power of the test
-
-To estimate the sampling distribution of the test statistic we need many samples generated under the null hypothesis.
-If the null hypothesis is true, changing the exposure would have no effect on the outcome.
-By randomly shuffling the exposures we can make up as many data sets as we like.
-If the null hypothesis is true the shuffled data sets should look like the real data, otherwise they should look different from the
-real data. The ranking of the real test statistic among the shuffled test statistics gives a p-value.
-
-<!-- Consider two cyclic granularities $A$ and $B$ with $2$ and $3$categories.
-Thus, the harmony table consisting of all possible harmony pairs (assuming all pairs are harmonies), would look like the following: -->
-
-```{r harmony_min}
-# harmonies <- tibble::tibble(facet_variable = c("A", "B", "A", "C", "B", "C"),
-#                             x_variable  = c("B","A", "C", "A", "C", "B"),
-#                             facet_levels = c(2, 3, 2, 4, 3, 4),
-#                             x_levels = c(3, 2, 4, 2, 4, 3))
-# 
-# harmonies <- tibble::tibble(facet_variable = c("A", "B"),
-#                             x_variable  = c("B","A"),
-#                             facet_levels = c(2, 3),
-#                             x_levels = c(3, 2))
-#                             
-# harmonies %>% knitr::kable()
-```
-
-<!-- The output table has the value of MMPD (normalized median maximum pairwise distances), gt_MMPD(global threshold of MMPD indicator). -->
-
-## Scenario 1: Simulated same normal distributions for all combinations of categories for all harmony pairs.
-
-Failure to reject the null hypothesis when there is in fact no significant effect.
-
-```{r samenull_2by4}
-
-```
-
-*Conclusion*: The test does not select harmony pairs when distributions of categories are same
-
-## Scenario 2: Simulated different distributions for all combinations of categories for harmony pairs for few levels.
-
-```{r diffnull_2by4}
-
-```
-
-*Conclusion*: The test select the harmony pair for which distribution of x-axis categories are significantly different
-
-## Scenario 3: Simulated different distributions for all combinations of categories for all harmony pairs with many levels.
-
-```{r diffnull_7by11}
-```
-
-*Conclusion*: The test indicates that both harmony pairs do not have significant variation.
-
-```{r diffnull_7by11normal}
-```
-
-*Conclusion*: The test indicates that only the first harmony pair has significant variation.
-
-```{r diffnull_7by11normal2}
-```
-
-*Conclusion*: The test indicates that only the first harmony pair has significant variation.
-
-<!-- ## Scenario 4: Cumulative 3 levels with 2, 7 and 11 and testing level and power -->
-
-<!-- ```{r samenull_3levels} -->
-
-<!-- ``` -->
-
-<!-- *Conclusion*: With 3 levels the test incorrectly chooses 1 harmony pair with similar distribution. The harmony pair which is displayed. -->
-
-<!-- <!-- ```{r diffnull_3levels} --> -->
-
-<!-- <!-- ``` --> -->
-
-<!-- *Conclusion*: The test with MMPD selects just one pair, as opposed to the test with maximum.
-This needs to be checked against what we expect from the test.
-The harmony pairs which are selected (either through MMPD or maximum) are displayed.
--->
-
-<!-- # ```{r} -->
-<!-- # harmonies <- tibble::tibble(facet_variable = c("A", "B"),x_variable  = c("B","A"), facet_levels = c(2, 3),x_levels = c(3, 2)) -->
-<!-- #  -->
-<!-- # har1 <- harmonies[1,] -->
-<!-- #  -->
-<!-- # sim_dist1 = c(rep(distributional::dist_normal(mu = 10, sigma = 5),2),rep(distributional::dist_exponential(10),2), rep(distributional::dist_weibull(0.5, 2),2)) -->
-<!-- #  -->
-<!-- # data1 <- sim_distharmony1(har1, sim_dist = sim_dist1) -->
-<!-- # data1 -->
-<!-- #  -->
-<!-- # data1 %>% unnest(sim_dist) %>% -->
-<!-- #   ggplot(aes(x = Var2, y = sim_dist)) + -->
-<!-- #   facet_wrap(~Var1) + geom_boxplot() + ggtitle("Same distribution 2 by 3") -->
-<!-- #  -->
-<!-- # response = "sim_dist" -->
-<!-- #  -->
-<!-- # MMPD_distribution <- data1 %>% -->
-<!-- #   select(-dist) %>%  -->
-<!-- #   unnest(sim_dist) %>%  -->
-<!-- #   list() %>%  -->
-<!-- #   global_threshold(harmony_tbl = har1, -->
-<!-- #                    response = "sim_dist", -->
-<!-- #                    dist_distribution = "normal", -->
-<!-- #                    dist_ordered = TRUE, -->
-<!-- #                    create_gran_data = FALSE, nsamp = 20) -->
-<!-- #  -->
-<!-- # # as_tibble(sample_MMPD) %>% mutate(id = row_number()) %>%  -->
-<!-- # #   ggplot() + geom_histogram(aes(x = value)) -->
-<!-- #  -->
-<!-- # ``` -->
-<!-- #  -->
-
-# Application
-
-# Conclusion

### 2020-08-19 main.Rmd
rough structure
introduction changed

@@
 ---
-title: Choosing and rating harmonies
+title: Median Maximum Pairwise Distance
 authors:
@@
 
+Take an example of a data set which are observed at fine temporal scales, like that of NYC bike usage available at https://www.citibikenyc.com/system-data.
+We use the `nyc_bikes` data set from the R package `tsibbledata` which takes a sample of 10 bikes for the year 2018.
+The `start_time` and the `stop_time` are recorded to a fineness of seconds.
+We can look at pair of cyclic granularities (hour_day, wknd_wday) or (week_month, day_week) to see how these periodicities interact.
+But there could be other pairs that are important too.
+How to understand which pairs are sufficient to explore given the data set without losing much information about the data.
+
+When we need to understand the interplay of different periodicities in a high frequency temporal datasets, we have many choices to consider.
+To be able to dice time in all possible ways in order to have multiple perspectives about peridicities in the data, there are too many things that we should look at ideally.
+Exploratory analysis is detective work and it is difficult to traverse through all possible ways without any systematic approach.
+It is immensely useful to be able to make transition from all possible ways to only ways that could potentially be important given a situation.
+The paper (gravitas) describes how we can start with all possible combinations of cyclic time granularities and narrow down our search to harmonies and remove clashes without losing any perspectives about the data.
 Even after excluding clashes, the list of harmonies left could be large and overwhelming for human consumption.
@@
 
+# Behavior of the statistic - control simulation
+
 # Application

### 2020-08-20 null_distribution.Rmd
updating text

---
title: "Simulating null distributions"
author: "Sayani Gupta"
date: "19/08/2020"
output: pdf_document
---

```{r setup, include=FALSE}

options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
library(tidyverse)
library(lubridate)
library(lvplot)
library(ggridges)
library(viridis)
library(tsibble)
library(gravitas)
library(ggpubr)
library(readr)
library(ggplot2)
library(distributional)

opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
read_chunk('check.R')
```

```{r external, include = FALSE}

```

```{r load}
```

If we suppose that MMPD is useful to normalise for the number of levels, then distribution of MMPD should be same for different levels, provided the response variable for all the levels comes from the same distribution. Following scenarios are considered to test that by breaking down the problem and checking  - 
a) Does normalising works for different x-axis levels?
b) if yes, then does further normalisation using median works for different facet categories?

## To test if normalisation works for different x-axis levels:

For x-axis, first maximum of pairwise JS distances are computed and it is normalised using Fisher–Tippett–Gnedenko theorem. Different x-axis levels viz, 10, 20, 30, 40 are considered and data is simulated 200 times for each of these cases to learn about the distribution of these normalised distances through

### All levels drawn from N(5, 10) distribution

```{r normalv11}

```

```{r normalv12}

```

```{r normalv13}

```

```{r normalv14}

```

From the above graphs, we could see that irrespective of the levels, the distribution of the normalised distances look like a normal distribution when the underlying observations are drawn from a N(5, 10) distribution. Let us check, if the same holds true if the underlying distributions are from Exp(0.5), Chi-squared(5), Gumbel(0.5, 2), Weibull(1.5, 1). Here, we fix the number of levels to 20.

### Different distributions with 20 levels

```{r exp20}

```

```{r chisq20}

```

```{r gumbel20}

```

```{r weibull20}

```

```{r alldist}

```

## To test if further normalisation using median works for different facet categories?

### All levels drawn from N(5, 10) distribution

### All levels drawn from Exp(2/3) distribution

### 2020-08-20 null_distribution.Rmd
done till if normalisation along x works?

@@
 Following scenarios are considered to test that by breaking down the problem and checking  -
-a) Does normalising works for different x-axis levels?
-b) if yes, then does further normalisation using median works for different facet categories?
+A) Does normalising works for different x-axis levels?
+B) if yes, then does further normalisation using median works for different facet categories?
 
-## To test if normalisation works for different x-axis levels:
+## A) To test if normalisation works for different x-axis levels:
 
 For x-axis, first maximum of pairwise JS distances are computed and it is normalised using Fisher–Tippett–Gnedenko theorem.
-Different x-axis levels viz, 10, 20, 30, 40 are considered and data is simulated 200 times for each of these cases to learn about the distribution of these normalised distances through
+Different x-axis levels viz, 10, 20, 30, 40 are considered and data is simulated 200 times for each of these cases to learn about the distribution of these normalised distances by plotting their histograms.
 
@@
 From the above graphs, we could see that irrespective of the levels, the distribution of the normalised distances look like a normal distribution when the underlying observations are drawn from a N(5, 10) distribution.
-Let us check, if the same holds true if the underlying distributions are from Exp(0.5), Chi-squared(5), Gumbel(0.5, 2), Weibull(1.5, 1).
+Let us check, if the same holds true if the underlying distributions are from Exp(0.5), Chi-squared(5), Gumbel(0.5, 2).
 Here, we fix the number of levels to 20.
@@
 
-```{r weibull20}
-
-```
-
 ```{r alldist}
@@
 
-## To test if further normalisation using median works for different facet categories?
+## B) To test if further normalisation using median works for different facet categories?
+
+If the normalisation along x-axis is working, we can vary the levels across facets keeping levels of x-axis constant to see if normalisation along facets work or not.
+
+For facets, first all normalised maximum distances are obtained and then their median is taken and futher divided by log(number of facet levels).
+Different facet levels viz, 10, 20, 30, 40 are considered for a fixed x-axis level and data is simulated 200 times for each of these cases to learn about the distribution of these normalised distances through a histogram.
 
@@
 
-### All levels drawn from Exp(2/3) distribution
+```{r normalv21}
+
+```
+
+```{r normalv22}
+
+```
+
+```{r normalv23}
+
+```
+
+```{r normalv24}
+
+```

### 2020-08-20 null_distribution.Rmd
update null_distribution

@@
 knitr::opts_knit$set(root.dir = here::here())
-read_chunk('check.R')
+read_chunk('null_distribution.R')
 ```
@@
 
+Null distribution of normalised maximum distances at this stage should be standardized Gumbel distribution.
+This is because we have assumed that distribution of JS distances are Normal and the maximum of such distances would follow a Gumbel distribution.
+When we normalise these maximum distances, ideally the distribution of those normalised distances should be standard Gumbel distribution (which is positively skewed).
+
 ### All levels drawn from N(5, 10) distribution
@@
 
-From the above graphs, we could see that irrespective of the levels, the distribution of the normalised distances look like a normal distribution when the underlying observations are drawn from a N(5, 10) distribution.
-Let us check, if the same holds true if the underlying distributions are from Exp(0.5), Chi-squared(5), Gumbel(0.5, 2).
+From the above graphs, we could see that irrespective of the levels, the distribution of the normalised distances look like a postively skewed distribution when the underlying observations are drawn from a N(5, 10) distribution.
+Let us check if the same holds true if the underlying distributions are from Exp(0.5), Chi-squared(5), Gumbel(0.5, 2).
 Here, we fix the number of levels to 20.
@@
 For facets, first all normalised maximum distances are obtained and then their median is taken and futher divided by log(number of facet levels).
-Different facet levels viz, 10, 20, 30, 40 are considered for a fixed x-axis level and data is simulated 200 times for each of these cases to learn about the distribution of these normalised distances through a histogram.
+Different facet levels viz, 10, 20, 30, 40 are considered for a fixed x-axis level and data is simulated 200 times for each of these cases to learn about the distributions.
 
-### All levels drawn from N(5, 10) distribution
+### All levels drawn from Exp(2/3) distribution
 
@@
 ```
+
+```{r normalallvar2}
+
+```
+
+It looks like the normalisation is also working at this stage.

### 2020-08-20 null_distribution.R

@@ -1,0 +1,253 @@
+## ----load
+library(tsibbledata)
+library(ggplot2)
+library(tsibble)
+library(lvplot)
+library(dplyr)
+library(gravitas)
+library(purrr)
+library(magrittr)
+library(distributional)
+# devtools::install_github("vigou3/actuar")
+library(actuar)
+quantile_prob <- seq(0.01, 0.99, 0.01)
+make_sim_1var <- function(sim_dist,
+                          # distribution
+                          nx = 7,
+                          # number of levels/categories,
+                          nobs_sample = 500,
+                          # number of observations in each sample
+                          nsim = 200
+                          # number of simulations to get histogram
+) {
+  gen_index <- rep(1:nx, each = nobs_sample)
+  gen_dist <- generate(sim_dist, nobs_sample) %>% unlist()
+  gen_data <- bind_cols(gen_index, gen_dist) %>% tidyr::pivot_wider(names_from = `...1`, values_from = `...2`)
+}
+
+plot_normmax_1var <- function(sim_dist,
+                              nx = 7,
+                              nobs_sample = 500,
+                              nsim = 200) {
+  suppressMessages(
+    plot_data <- (1:nsim) %>%
+      purrr::map(function(i) {
+        data <- make_sim_1var(
+          sim_dist,
+          nx,
+          nobs_sample,
+          nsim
+        )
+        gravitas::norm_jsd_maxpair(data)
+      })
+  )
+
+  MMPD_obs <- unlist(plot_data) %>% tibble(.name_repair = "universal")
+  names(MMPD_obs) <- "normalised_max"
+  MMPD_obs %>% ggplot() +
+    geom_histogram(aes(x = normalised_max))
+}
+
+nx_range <- seq(10, 60, by = 10)
+
+## ----normalv11
+set.seed(nx_range[1])
+nx <- nx_range[1]
+sim_dist <- rep(distributional::dist_normal(5, 10), nx)
+
+p1 <- plot_normmax_1var(sim_dist,
+  nx,
+  nobs_sample = 50
+) +
+  ggtitle(paste(nx, "levels"))
+
+
+## ----normalv12
+set.seed(nx_range[2])
+nx <- nx_range[2]
+sim_dist <- rep(distributional::dist_normal(5, 10), nx)
+
+p2 <- plot_normmax_1var(sim_dist,
[…]

### 2020-08-20 null_distribution.Rmd
update null_distribution

@@
 
-If we suppose that MMPD is useful to normalise for the number of levels, then distribution of MMPD should be same for different levels, provided the response variable for all the levels comes from the same distribution.
+If we suppose that MMPD is useful to normalize for the number of levels, then distribution of MMPD should be same for different levels, provided the response variable for all the levels comes from the same distribution.
 Following scenarios are considered to test that by breaking down the problem and checking  -
-A) Does normalising works for different x-axis levels?
-B) if yes, then does further normalisation using median works for different facet categories?
+A) Does normalizing works for different x-axis levels?
+B) if yes, then does further normalization using median works for different facet categories?
 
-## A) To test if normalisation works for different x-axis levels:
+## A) To test if normalization works for different x-axis levels:
 
-For x-axis, first maximum of pairwise JS distances are computed and it is normalised using Fisher–Tippett–Gnedenko theorem.
-Different x-axis levels viz, 10, 20, 30, 40 are considered and data is simulated 200 times for each of these cases to learn about the distribution of these normalised distances by plotting their histograms.
+For x-axis, first maximum of pairwise JS distances are computed and it is normalized using Fisher–Tippett–Gnedenko theorem.
+Different x-axis levels viz, 10, 20, 30, 40 are considered and data is simulated 200 times for each of these cases to learn about the distribution of these normalized distances by plotting their histograms.
 
-Null distribution of normalised maximum distances at this stage should be standardized Gumbel distribution.
+Null distribution of normalized maximum distances at this stage should be standardized Gumbel distribution.
 This is because we have assumed that distribution of JS distances are Normal and the maximum of such distances would follow a Gumbel distribution.
-When we normalise these maximum distances, ideally the distribution of those normalised distances should be standard Gumbel distribution (which is positively skewed).
+When we normalize these maximum distances, ideally the distribution of those normalized distances should be standard Gumbel distribution (which is positively skewed).
 
@@
 
-From the above graphs, we could see that irrespective of the levels, the distribution of the normalised distances look like a postively skewed distribution when the underlying observations are drawn from a N(5, 10) distribution.
+From the above graphs, we could see that irrespective of the levels, the distribution of the normalized distances look like a positively skewed distribution when the underlying observations are drawn from a N(5, 10) distribution.
 Let us check if the same holds true if the underlying distributions are from Exp(0.5), Chi-squared(5), Gumbel(0.5, 2).
@@
 
-## B) To test if further normalisation using median works for different facet categories?
+## B) To test if further normalization using median works for different facet categories?
 
-If the normalisation along x-axis is working, we can vary the levels across facets keeping levels of x-axis constant to see if normalisation along facets work or not.
+If the normalization along x-axis is working, we can vary the levels across facets keeping levels of x-axis constant to see if normalization along facets work or not.
 
-For facets, first all normalised maximum distances are obtained and then their median is taken and futher divided by log(number of facet levels).
+For facets, first all normalized maximum distances are obtained and then their median is taken and further divided by log(number of facet levels).
 Different facet levels viz, 10, 20, 30, 40 are considered for a fixed x-axis level and data is simulated 200 times for each of these cases to learn about the distributions.
@@
 
-It looks like the normalisation is also working at this stage.
+It looks like the normalization is also working at this stage.

### 2020-08-20 main.Rmd
adding text
ways of computing distances added

@@
 
-# A new test statistic
+# Computing distance measure
 
@@
 
-One of the potential ways to evaluate this variation is by computing the pairwise distances between the distributions of the measured variable.
-We do this through Jensen-Shannon distance which is based on Kullback-Leibler divergence.
+<!-- One of the most important class of divergence is the f-divergence and includes measures like Kullback-Leibler divergence, Hellinger distance etc.
+The continuous version of f -divergence is given by -->
+<!-- $$D_f(P||Q) := \int q(x)f(\frac{p(x)}{q(x)})$$, where -->
+<!-- $f : [0,\infty) \rightarrow R \cup \{\infty\}$ is a continuous convex function, and $f(1) = 0$.  -->
 
-The Jensen-Shanon distance between two probability distribution $p_1$ and $p_2$ is given by $$d = [D(p_1, r) + D(p_2, r)]/2 \quad where \quad r = (p_1 + p_2)/2$$ where,
-$$D(p_1,p_2) = \int^{\infty}_{-\infty}p_1(x)log\frac{p_1(x)}{p_2(x)}\,dx$$ is the Kullback-Leibler divergence between $p_1$ and $p_2$.
+The most common divergence measure between distributions is the Kullback-Leibler (KL) divergence introduced by Solomon Kullback and Richard Leibler in 1951.
+The KL divergence, denoted $D(p(x), q(x))$ is a non-symmetric measure of the difference between two probability distributions $p(x)$ and $q(x)$ and is interpreted as the amount of information lost when $q(x)$ is used to approximate $p(x)$.
+Although the KL divergence measures the “distance” between two distributions, it is not a distance measure since it is not symmetric.
+The Jensen-Shannon divergence based on the Kullback-Leibler divergence is symmetric and it always has a finite value.
+The square root of the Jensen-Shannon divergence is a metric, often referred to as Jensen-Shannon distance.
+Other common measures of distance are Hellinger distance, total variation distance and Fisher information metric.
+
+In the context of this paper, the pairwise distances between the distributions of the measured variable are computed through Jensen-Shannon distance which is based on Kullback-Leibler divergence and is defined by,
+
+$$JSD(P||Q) = \frac{1}{2}D(P||M) + \frac{1}{2}D(Q||M)$$
+where $M = \frac{P+Q}{2}$ and 
+$D(P||Q) := \int^\infty_{-\infty} p(x)f(\frac{p(x)}{q(x)})$ is the KL divergence between distributions $p(x)$ and $q(x)$.
 Probability distributions are estimated through quantiles instead of kernel density so that there is minimal dependency on selecting kernel or bandwidth.
+
+<!-- The Jensen-Shanon distance between two probability distribution $p_1$ and $p_2$ is given by $$d = [D(p_1, r) + D(p_2, r)]/2 \quad where \quad r = (p_1 + p_2)/2$$ where, -->
+<!-- $$D(p_1,p_2) = \int^{\infty}_{-\infty}p_1(x)log\frac{p_1(x)}{p_2(x)}\,dx$$ is the Kullback-Leibler divergence between $p_1$ and $p_2$.   -->
 
@@
 
-```{r samenull_2by4}
+```{r samenull_2by4, eval = FALSE}
 
@@
 
-```{r diffnull_2by4}
+```{r diffnull_2by4, eval = FALSE}
 
@@
 
-```{r diffnull_7by11}
+```{r diffnull_7by11, eval = FALSE}
 ```
@@
 
-```{r diffnull_7by11normal}
+```{r diffnull_7by11normal, eval = FALSE}
 ```
@@
 
-```{r diffnull_7by11normal2}
+```{r diffnull_7by11normal2, eval = FALSE}
 ```

### 2020-08-20 main.Rmd
distances of distribution added

@@
 read_chunk('main.R')
+read_chunk("null_distribution.R")
 ```
@@
 
-We call this measure of variation as  Median Maximum Pairwise Distances (MMPD).
+<!-- We call this measure of variation as  Median Maximum Pairwise Distances (MMPD). -->
 
@@
 
-The harmony pairs could be arranged from highest to lowest average maximum pairwise distances across different levels of the harmonies.
-But maximum is not robust to the number of levels and is higher for harmonies with higher levels.
+<!-- The harmony pairs could be arranged from highest to lowest average maximum pairwise distances across different levels of the harmonies. -->
+
+Maximum pairwise distances are not robust to the number of levels and is higher for harmonies with higher levels.
 Thus these maximum pairwise distances need to be normalized for different harmonies in a way that eliminates the effect of different levels.
-The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re- normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.
+The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.
 
@@
 Distribution of JS distances is assumed to be normal but the mean and variance are estimated from the sample, rather than deducing it from the number of discretization used to approximate the continuous distribution.
+We look at different scenarios, where observations are collected from Normal, Exponential, Chi-squared and Gumbel distribution and found the distribution of JS distances are similar, irrespective of which distribution they are drawn from.
+
+# Initial distribution of observed variables shown in plot title
+
+```{r distv11}
+
+```
+
+```{r distv12}
+
+```
+
+```{r distv13}
+
+```
+
+```{r distv14}
+
+```
 

### 2020-08-20 main.R

@@ -607,3 +607,6 @@ p3 <- data6 %>% unnest(sim_dist) %>%
   ggplot(aes(x = Var2, y = sim_dist)) +
   facet_wrap(~Var1) + geom_boxplot() + ggtitle("selected by max and not MMPD")
 p3
+
+
+##----

### 2020-08-20 null_distribution.R

@@ -48,6 +48,41 @@ plot_normmax_1var <- function(sim_dist,
     geom_histogram(aes(x = normalised_max))
 }
 
+hist_dist <- function(sim_dist,
+                      nx = 7,
+                      nobs_sample = 500,
+                      nsim = 50, 
+                      dist_ordered = TRUE) {
+  suppressMessages(
+    plot_data <- (1:nsim) %>%
+      purrr::map(function(i) {
+        data <- make_sim_1var(
+          sim_dist,
+          nx,
+          nobs_sample,
+          nsim
+        )
+        gravitas::dist_npair(data, quantile_prob, dist_ordered)
+      })
+  )
+  
+  MMPD_obs <- unlist(plot_data) %>% tibble(.name_repair = "universal")
+  names(MMPD_obs) <- "pairwise_jsd"
+  
+  hist_dist <- MMPD_obs %>% ggplot(aes(x = pairwise_jsd, y = ..density..)) +
+    geom_histogram() + 
+    ggplot2::geom_histogram()+
+    ggplot2::geom_density(colour = "red")
+  
+  p <- MMPD_obs %>% filter(!is.na(pairwise_jsd)) %>% ggplot(aes(sample = pairwise_jsd))
+  p
+  qq_dist <- p + stat_qq() + stat_qq_line()
+  
+  qq_dist
+  #ggarrange(hist_dist, qq_dist, ncol = 1, nrow = 2)
+}
+
+
 nx_range <- seq(10, 60, by = 10)
 
 ## ----normalv11
@@ -251,3 +286,46 @@ r4 <- plot_normmax_2var(sim_dist,
 
 ggarrange(r1, r2, r3, r4, nrow = 2, ncol = 2)
 
+## ----distv11
+set.seed(nx_range[1])
+nx <- nx_range[1]
+sim_dist <- rep(distributional::dist_normal(5, 10), nx)
+
+s1 <-hist_dist(sim_dist,
+               nx,
+               nobs_sample = 50,
+               dist_ordered = FALSE) + ggtitle("N(5, 10)")
+
+## ----distv12
+set.seed(nx_range[1])
+nx <- nx_range[1]
+sim_dist <- rep(distributional::dist_exponential(0.5), nx)
+
+s2 <-hist_dist(sim_dist,
+               nx,
+               nobs_sample = 50,
+               dist_ordered = FALSE) + ggtitle("Exp(0.5)")
+
[…]

### 2020-08-20 main.Rmd
size and power graphs added

@@
 ```{r load}
+
+```
+
+```{r load_fun_1var}
+
+```
+
+```{r load_fun_2var}
 
@@
 
-## Level and power
+## Size and power
 
@@
 
-### Scenario 1: Simulated same normal distributions for all combinations of categories for all harmony pairs.
+### Size: Simulated same distribution for all combinations of categories for all harmony pairs.
 
@@
 
-```{r samenull_2by4, eval = FALSE}
+<!-- # ```{r samenull_2by4, eval = FALSE} -->
+<!-- #  -->
+<!-- # ``` -->
+
+```{r normalv21_power}
 
@@
 
-*Conclusion*: The test does not select harmony pairs when distributions of categories are same
+```{r normalv22_power}
+
+```
+
+### Power: Simulated same distribution for all combinations of categories for all harmony pairs.
+
+```{r normalv23_power}
+
+```
+
+```{r normalv24_power}
+
+```
+
+*Conclusion*: The test does not select harmony pairs when distributions of categories are same.
 

### 2020-08-20 main.Rmd
title and subtitles changed

@@
 
-# Initial distribution of observed variables shown in plot title
+#### Initial distribution of observed variables shown in plot title
 
@@
 
-## Algorithm
+## Median Maximum Pairwise distance
+
+### Definition
+
+### Algorithm for computation for all harmony pairs
 
@@
 
-### Interpreting the test statistic
+### Bounds
+
+This is not correct becuase MMPD should be median of standardized Gumbel distribution. So no bound?
+
+By @Lin1991-fj,
+$$ 0 \leq JSD(P||Q) \leq ln(2)$$.
+
+Thus,  $$ 0 \leq MMPD \leq \frac{ln(2)}{ln(k)}$$.
+Now, by asumption $k \geq 2$ and hence,
+<!-- \begin{equation} -->
+<!-- For k = 2, $\frac{ln(2)}{ln(k)} = 1$  -->
+<!-- \end{equation} -->
+<!-- For $k > 2$, $\frac{ln(2)}{ln(k)}  <1$. -->
+
+\[\frac{ln(2)}{ln(k)} : \left\{
+  \begin{array}{lr}
+    1 & if \ k = 2\\
+    <1 & if \ k \ge 2
+  \end{array}
+\right.
+\]
+
+Thus, $$ 0 \leq MMPD \leq \ 1$$
 
@@
 
-## Algorithm for threshold
+## Definition
+
+### Algorithm for computation for all harmony pairs
 
@@
 ```
+## Simulation design
+
+Behavior of the statistic - control simulation
 
@@
 
-*Conclusion*: The test does not select harmony pairs when distributions of categories are same.
+*Conclusion*: The test rejects the null hypothesis if distributions are different.
 
@@
 
-# Behavior of the statistic - control simulation
-
 # Application
 
-# Conclusion
+# Summary and discussion

### 2020-08-20 main.Rmd
null distribution

@@
 ```
+
+## Null distribution
+
+### Normalised maximum distances follow standard Gumbel distribution
+
+### Limiting distribution of median of normalised maximum distances is normal
+
+Let a continuous population be given with cdf F(x) (cumulative distribution function) and median $\xi$ (assumed to exist uniquely).
+For a sample of size $2n + 1$, let $\tilde{x}$ denote the sample median.
+The distribution of $\tilde{x}$,under certain conditions, to be asymptotically normal with mean $\xi$ and variance $\sigma_n^2 = \frac{1}{4} [f(\xi)]^2(2n + 1)$, where $f(x) = F'(x)$ is the pdf (probability density function).
+
 ## Simulation design
@@
 Behavior of the statistic - control simulation
+
+ - To check if different distributions impact
+(simulate with different distributions but same for all levels)
+
+ - To check if x-levels are normalised
+(simulate with different distributions)
+(simulate with different x-levels)
+
+ - To check if facet-levels are normalised
+(simulate with different distributions)
+(simulate with different facet-levels for fixed x-levels)
 

### 2020-08-26 mean_null.Rmd
mean null distribution

---
title: "Mean of normal distribution"
author: "Sayani Gupta"
date: "25/08/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(ggpubr)
```

```{r functions}

# create data for each levels
set.seed(12345)
create_simdata <- function(nx = 2, nsim = 5){
  mean_dist <- (1:nsim) %>% 
  purrr::map(function(i){
    x =  rgamma(nx, 0.5, 3)
    #p = 1-(1/nx)
    #b = stats::qnorm(p, mean(x), sd(x))
    #a = 1/(nx*stats::dnorm(b, mean(x), sd(x)))
    #k = stats::quantile(x, p, type = 8, na.rm = TRUE)
    max(x)
    #mean(x)
  })
}
```

```{r tidy_data}

nlevels = seq(2, 10, 1)

data_orig <- nlevels %>% 
  purrr::map_df(function(i){
    create_datai <- create_simdata(nx = i, nsim = 500)
    tibble::tibble(ind = i, sim_data = create_datai)
  })

data_orig %>%
  unnest(sim_data) %>% 
   ggplot(aes(x = sim_data)) +
  geom_histogram() +
  facet_wrap(~ind)

```

```{r tidy_data_frame}
# nx = 20
# nsim = 500
# sim_dist <- rep(distributional::dist_gamma(0.2, 1), length(nx))
# 
# simdata_format <- function(nx, sim_dist)
# {
#   tibble(nlevel = seq_len(nx), sim_dist)
# }
# 
# create_simdata <- function(.data, nsim = 500)
# {
# nx = nrow(.data)
# sim_value <- seq_len(nx) %>%
#   purrr::map(function(i){
#     disti = .data %>% magrittr::extract(i,2)
#    distributional::generate(disti$sim_dist, nsim)
#   }) %>% enframe()
# .data %>% bind_cols(sim_value)
# #data %>% mutate(sim_value = data)
# }
# 
# data <- simdata_format(nx, sim_dist) %>%
#   create_simdata()
# 
# data %>%
#   select(-sim_dist, -name) %>%
#   unnest(value) %>%
#   unnest(value) %>%
#   ggplot(aes(x = value)) +
#   geom_histogram() +
#   facet_wrap(~nlevel)

```

### 2020-08-26 mean_null.Rmd
clean null

@@
 ```{r functions}
-
 # create data for each levels
 set.seed(12345)
-create_simdata <- function(nx = 2, nsim = 5){
+create_simdata <- function(nx = 2, nsim = 5, sim_dist = distributional::dist_gamma(0.5, 3)){
   mean_dist <- (1:nsim) %>% 
   purrr::map(function(i){
-    x =  rgamma(nx, 0.5, 3)
-    #p = 1-(1/nx)
-    #b = stats::qnorm(p, mean(x), sd(x))
-    #a = 1/(nx*stats::dnorm(b, mean(x), sd(x)))
-    #k = stats::quantile(x, p, type = 8, na.rm = TRUE)
-    max(x)
-    #mean(x)
+    #x =  rgamma(nx, 0.5, 3)
+    x =  sim_dist %>% distributional::generate(nx) %>% unlist()
+    p = 1-(1/nx)
+    b = stats::qnorm(p, mean(x), sd(x))
+    a = 1/(nx*stats::dnorm(b, mean(x), sd(x)))
+    k = stats::quantile(x, p, type = 8, na.rm = TRUE)
+    (max(x)-a)/b
+    # max(x)
   })
@@
 
-nlevels = seq(2, 10, 1)
+nlevels = seq(60, 100, 5)
 
@@
 ```
-
-```{r tidy_data_frame}
-# nx = 20
-# nsim = 500
-# sim_dist <- rep(distributional::dist_gamma(0.2, 1), length(nx))
-# 
-# simdata_format <- function(nx, sim_dist)
-# {
-#   tibble(nlevel = seq_len(nx), sim_dist)
-# }
-# 
-# create_simdata <- function(.data, nsim = 500)
-# {
-# nx = nrow(.data)
-# sim_value <- seq_len(nx) %>%
-#   purrr::map(function(i){
-#     disti = .data %>% magrittr::extract(i,2)
-#    distributional::generate(disti$sim_dist, nsim)
-#   }) %>% enframe()
-# .data %>% bind_cols(sim_value)
-# #data %>% mutate(sim_value = data)
-# }
-# 
-# data <- simdata_format(nx, sim_dist) %>%
-#   create_simdata()
-# 
-# data %>%
-#   select(-sim_dist, -name) %>%
-#   unnest(value) %>%
-#   unnest(value) %>%
-#   ggplot(aes(x = value)) +
-#   geom_histogram() +
-#   facet_wrap(~nlevel)
-
-```

### 2020-08-27 mean_null.Rmd
distribution included

@@
 ---
-title: "Mean of normal distribution"
+title: "Simulations, CLT and EVT"
 author: "Sayani Gupta"
 date: "25/08/2020"
-output: html_document
+output: pdf_document
 ---
@@
 
+Discussion: Let the sample size be $n$ and the number of iterations be $k$.
+By CLT (or EVT), when $n$ is high enough, then the limiting distribution of sample mean (or max) goes to a standard normal (or Gumbel/Freschet/Weibull) distribution, irrespective of the underlying distribution of the sample.
+This means when $n$ is high enough and we sample $n$ iid random variables multiple times (high enough $k$), by CLT, the distribution of sample mean would look like standard normal.
+What if $n$ is very small and $k$ is large?
+Would the distribution of sample mean still look like standard normal?
+It would not.
+Similarly, EVT works when $n$ is high enough.
+When we are taking the max of 2 or 3 rvs ("levels" in our terminology), $n = 2/3$, which are far too less.
+Hence, normalisation would be able to nullify the effect of $n$ only for large enough $n$.
+
+Simulation Study:
+
+Samples are taken from Gamma(0.5, 3) distribution and $k = 500$ in all the cases.
+Small values of n considered in the range  ${2, 3, \ldots, 10}$ and large values of $n$ considered within ${25, 30, 35, \ldots, 45}$.
+We study the distribution of:
+
+ 1. sample means for small $n$
+
+ 2. sample means for large $n$
+
+ 3. normalised sample means for small $n$
+
+ 4. normalised sample means for large $n$
+
+ 5. sample maximums for small $n$
+
+ 6. sample maximums for large $n$
+
+ 7. normalised sample maximums for small $n$
+
+ 8. normalised sample maximums for large $n$
+
+# CLT
+
+Suppose that $X_1$, $X_2$ , ... , $X_n$ are i.i.d. random variables with expected values $E(X_i) = \mu < \infty$ and variance $Var(X_i) = \sigma^2 < \infty$.
+Suppose the sample mean is $\bar{X} = \frac{(X_1 + X_2 + \ldots + X_n)}{n}$, then by CLT the distribution of the normalised random variable:
+$Z_n = \frac{\bar{X} - \mu}{\sqrt n\sigma}$ converges in distribution to a standard normal distribution.
+
 ```{r functions}
 # create data for each levels
-set.seed(12345)
-create_simdata <- function(nx = 2, nsim = 5, sim_dist = distributional::dist_gamma(0.5, 3)){
+create_simdata <- function(nx = 2,
+                           # number of rvs to generate
+                           nsim = 500, 
+                           # number of simulations
+                           sim_dist = distributional::dist_gamma(0.5, 3),
+                           # distribution of each rv
+                           create_fun = mean 
+                           # function used on the rvs 
+                           ){
   mean_dist <- (1:nsim) %>%
-  purrr::map(function(i){
-    #x =  rgamma(nx, 0.5, 3)
-    x =  sim_dist %>% distributional::generate(nx) %>% unlist()
-    p = 1-(1/nx)
-    b = stats::qnorm(p, mean(x), sd(x))
-    a = 1/(nx*stats::dnorm(b, mean(x), sd(x)))
-    k = stats::quantile(x, p, type = 8, na.rm = TRUE)
-    (max(x)-a)/b
-    # max(x)
+    purrr::map(function(i) {
+      x <- sim_dist %>%
+        distributional::generate(nx) %>%
+        unlist()
+      x %>% create_fun()
     })
@@
 
-nlevels = seq(60, 100, 5)
+# input vector of levels for which distributions are plotted
+nlevels <- seq(2, 10, 1)
 
+plot_simdata <- function(nlevels = seq(2, 10, 1),
+                         nsim = 500, 
+                         sim_dist = distributional::dist_gamma(0.5, 3),
+                         create_fun = mean, 
+                         distr = "norm"){
 data_orig <- nlevels %>%
-  purrr::map_df(function(i){
-    create_datai <- create_simdata(nx = i, nsim = 500)
+  purrr::map_df(function(i) {
+    create_datai <- create_simdata(nx = i, nsim, sim_dist, create_fun)
     tibble::tibble(ind = i, sim_data = create_datai)
   })
+
+# defining gumbel distribution
+dgumbel <- function(x, a, b) 1/b*exp((a-x)/b)*exp(-exp((a-x)/b))
+pgumbel <- function(q, a, b) exp(-exp((a-q)/b))
+qgumbel <- function(p, a, b) a-b*log(-log(p))
+
+response <- data_orig %>%
+  unnest(sim_data)
+
+if(distr == "gumbel")
+{
+par = fitdistrplus::fitdist(response$sim_data, distr = "gumbel", start = list(a = 0, b = 1))
+}
+
+if(distr == "norm")
+{
+par = fitdistrplus::fitdist(response$sim_data, distr = distr)
+}
+
+par1 <- round(par$estimate[1], 2)
+par2 <- round(par$estimate[2], 2)
 
@@
   geom_histogram() +
-  facet_wrap(~ind)
+  facet_wrap(~ind) + 
+  ggtitle(paste0(distr, " (",par1,", ",par2,")"))
+}
+```
 
+In facet  with label 2, two random numbers are generated and their mean is computed.
+We repeat this process 500 times and draw the histogram of the computed means.
+Similarly, for facet with label 3, 3 random numbers are generated and histogram is drawn for the computed means of 3 random numbers.
+
+# Small levels and many iterations of means
+
+```{r}
+set.seed(12345)
+plot_simdata(nlevels = seq(2, 10, 1),
+             nsim = 500, 
+             create_fun = mean,
+             distr = "norm")
 ```
+
+# Many levels and many iterations of means
+
+The histograms look like a normal distribution in this case, because number of levels are higher. For smaller number of levels, even with many repetitions the histograms do not look like normal.
+
+```{r}
+set.seed(54321)
+plot_simdata(nlevels = seq(20, 45, 5),
+             nsim = 500,
+             create_fun = mean)
+```
+
+```{r norm_mean}
+norm_mean <- function(x = NULL){
+    shape = 0.5
+    rate = 3
+    meanx = shape/rate
+    sdx = shape/(rate^2)
+    (mean(x) - meanx)/sdx
+}
+```
+
+# Small levels and many iterations of normalised means
+
+```{r normmean_small_lev}
+set.seed(12345)
+plot_simdata(nlevels = seq(2, 10, 1),
+             nsim = 500, 
+             create_fun = norm_mean)
+```
+
+# Many levels and many iterations of normalised means
+
+```{r normmean_large_lev}
+set.seed(54321)
+plot_simdata(nlevels = seq(20, 45, 5),
+             nsim = 500, 
+             create_fun = norm_mean,
+             distr = "norm")
+```
+
+# EVT
+
+## Small levels and many iterations of max
+
+```{r max_small_lev}
+set.seed(12345)
+plot_simdata(nlevels = seq(2, 10, 1),
+             nsim = 500, 
+             create_fun = max)
+```
+
+## Many levels and many iterations of max
+
+```{r max_large_lev}
+set.seed(54321)
+plot_simdata(nlevels = seq(20, 45, 5),
+             nsim = 500, 
+             create_fun = max)
+```
+
+```{r norm_max}
+# normalised maximum of a vector
+norm_max <- function(x = NULL){
+      nx <- length(x)
+      p = 1-(1/nx)
+      shape = 0.5
+      rate = 3
+      meanx = shape/rate
+      sdx = shape/(rate^2)
+      b = stats::qnorm(p, meanx, sdx)
+      a = 1/(nx*stats::dnorm(b, meanx, sdx))
+      #k = stats::quantile(x, p, type = 8, na.rm = TRUE)
+      (max(x) - a)/b
+      #max(x)/k
+      }
+```
+
+## Small levels and many iterations of norm max
+
+```{r normmax_small_lev}
+set.seed(12345)
+plot_simdata(nlevels = seq(2, 10, 1),
+             nsim = 500, 
+             create_fun = norm_max,
+             distr = "gumbel")
+```
+
+## Many levels and many iterations of norm max
+
+```{r normmax_large_lev}
+set.seed(54321)
+plot_simdata(nlevels = seq(20, 45, 5),
+             nsim = 500, 
+             create_fun = norm_max, 
+             distr = "gumbel")
+```

### 2020-08-27 mean_null.Rmd
delete dsitribution

@@
              nsim = 500, 
-             create_fun = max)
+             create_fun = max,
+               sim_dist = distributional::dist_normal(5, 10),
+             distr = "gumbel")
 ```
@@
       rate = 3
-      meanx = shape/rate
-      sdx = shape/(rate^2)
+      # meanx = shape/rate
+      # sdx = shape/(rate^2)
+      meanx = 5
+      sdx = 10
       b = stats::qnorm(p, meanx, sdx)
@@
              nsim = 500, 
+             sim_dist = distributional::dist_normal(5, 10),
              create_fun = norm_max,
@@
              create_fun = norm_max, 
+             sim_dist = distributional::dist_normal(5, 10),
              distr = "gumbel")

### 2020-08-27 mean_null.Rmd
adding CLT, EVT and simulations

--- 2020-08-27 mean_null.Rmd
@@
 
-Samples are taken from Gamma(0.5, 3) distribution and $k = 500$ in all the cases.
+Samples are taken from Gamma(3, 0.5) distribution and $k = 500$ in all the cases.
 Small values of n considered in the range  ${2, 3, \ldots, 10}$ and large values of $n$ considered within ${25, 30, 35, \ldots, 45}$.
@@
  1. sample means for small $n$ 
+(Obs: distribution doesn't look similar or normal)
 
  2. sample means for large $n$
+(Obs: distribution looks similar and normal like with different scales)
 
  3. normalised sample means for small $n$
+(Obs: distribution doesn't look similar)
 
  4. normalised sample means for large $n$ 
+(Obs: distribution looks similar in both shape and scale with mean 0)
 
  5. sample maximums for small $n$ 
+(Obs: distribution doesn't look too different except for tails, high scale)
 
  6. sample maximums for large $n$ 
+(Obs: distribution looks similar and positively skewed with very high scales)
 
  7. normalised sample maximums for small $n$ 
+(Obs: distribution doesn't look similar, scaled down, maybe similar after facet label 5)
 
  8. normalised sample maximums for large $n$ 
+(Obs: distribution looks similar and it has been scaled down much more than maximum without normalisation. Can we use this fact to explore maximums more?)
+
+Q: So when we are talking about normalising for the levels when number of levels are low? - Not by using limit theorems. Transformation?
 
@@
 
+```{r shape_rate}
+shape1 = 3
+rate1 = 0.5
+```
+
 ```{r functions}
 # create data for each levels
+
 create_simdata <- function(nx = 2,
@@
                            # number of simulations
-                           sim_dist = distributional::dist_gamma(0.5, 3),
+                           sim_dist = distributional::dist_gamma(shape = shape1, 
+                                                                 rate = rate1),
                            # distribution of each rv
@@
                            # function used on the rvs
-                           ){
+) {
   mean_dist <- (1:nsim) %>%
@@
                          nsim = 500,
-                         sim_dist = distributional::dist_gamma(0.5, 3),
-                         create_fun = mean, 
-                         distr = "norm"){
+                         sim_dist = distributional::dist_gamma(shape = shape1,
+                      rate = rate1),
+                         # distr = "norm",
+                         create_fun = mean) {
   data_orig <- nlevels %>%
@@
 
-# defining gumbel distribution
-dgumbel <- function(x, a, b) 1/b*exp((a-x)/b)*exp(-exp((a-x)/b))
-pgumbel <- function(q, a, b) exp(-exp((a-q)/b))
-qgumbel <- function(p, a, b) a-b*log(-log(p))
-
-response <- data_orig %>%
-  unnest(sim_data)
-
-if(distr == "gumbel")
-{
-par = fitdistrplus::fitdist(response$sim_data, distr = "gumbel", start = list(a = 0, b = 1))
-}
-
-if(distr == "norm")
-{
-par = fitdistrplus::fitdist(response$sim_data, distr = distr)
-}
-
-par1 <- round(par$estimate[1], 2)
-par2 <- round(par$estimate[2], 2)
-
   data_orig %>%
@@
     geom_histogram() +
-  facet_wrap(~ind) + 
-  ggtitle(paste0(distr, " (",par1,", ",par2,")"))
+    facet_wrap(~ind)
+  # + ggtitle(paste0(distr, " (",par1,", ",par2,")"))
 }
@@
 set.seed(12345)
-plot_simdata(nlevels = seq(2, 10, 1),
+plot_simdata(
+  nlevels = seq(2, 10, 1),
   nsim = 500,
-             create_fun = mean,
-             distr = "norm")
+  create_fun = mean
+)
 ```
@@
 set.seed(54321)
-plot_simdata(nlevels = seq(20, 45, 5),
+plot_simdata(
+  nlevels = seq(20, 45, 5),
   nsim = 500,
-             create_fun = mean)
+  create_fun = mean
+)
 ```
@@
 ```{r norm_mean}
-norm_mean <- function(x = NULL){
-    shape = 0.5
-    rate = 3
-    meanx = shape/rate
-    sdx = shape/(rate^2)
-    (mean(x) - meanx)/sdx
+norm_mean <- function(x = NULL,
+                      shape = shape1,
+                      rate = rate1) {
+  meanx <- shape / rate
+  sdx <- shape / (rate^2)
+  (mean(x) - meanx) / sdx
 }
@@
 set.seed(12345)
-plot_simdata(nlevels = seq(2, 10, 1),
+plot_simdata(
+  nlevels = seq(2, 10, 1),
   nsim = 500,
-             create_fun = norm_mean)
+  create_fun = norm_mean
+)
 ```
@@
 set.seed(54321)
-plot_simdata(nlevels = seq(20, 45, 5),
+plot_simdata(
+  nlevels = seq(20, 45, 5),
   nsim = 500,
-             create_fun = norm_mean,
-             distr = "norm")
+  create_fun = norm_mean
+)
 ```
@@
 set.seed(12345)
-plot_simdata(nlevels = seq(2, 10, 1),
+plot_simdata(
+  nlevels = seq(2, 10, 1),
   nsim = 500,
-             create_fun = max)
+  create_fun = max
+)
+# sim_dist = distributional::dist_normal(5, 10))
+# distr = "gumbel")
 ```
@@
 set.seed(54321)
-plot_simdata(nlevels = seq(20, 45, 5),
+plot_simdata(
+  nlevels = seq(20, 45, 5),
   nsim = 500,
-             create_fun = max)
+  create_fun = max
+)
+# distr = "gumbel",
+# sim_dist = distributional::dist_normal(5, 10))
 ```
@@
 # normalised maximum of a vector
-norm_max <- function(x = NULL){
+norm_max <- function(x = NULL,
+                     shape = shape1,
+                      rate = rate1) {
   nx <- length(x)
-      p = 1-(1/nx)
-      shape = 0.5
-      rate = 3
-      meanx = shape/rate
-      sdx = shape/(rate^2)
-      b = stats::qnorm(p, meanx, sdx)
-      a = 1/(nx*stats::dnorm(b, meanx, sdx))
-      #k = stats::quantile(x, p, type = 8, na.rm = TRUE)
-      (max(x) - a)/b
-      #max(x)/k
+  p <- 1 - (1 / nx)
+  meanx <- shape / rate
+  sdx <- shape / (rate^2)
+  # meanx = 5
+  # sdx = 10
+  b <- stats::qnorm(p, meanx, sdx)
+  a <- 1 / (nx * stats::dnorm(b, meanx, sdx))
+  # k = stats::quantile(x, p, type = 8, na.rm = TRUE)
+  (max(x) - a) / b
+  # max(x)/k
 }
@@
 set.seed(12345)
-plot_simdata(nlevels = seq(2, 10, 1),
+plot_simdata(
+  nlevels = seq(2, 10, 1),
   nsim = 500,
-             create_fun = norm_max,
-             distr = "gumbel")
+  # distr = "gumbel",
+  # sim_dist = distributional::dist_normal(5, 10),
+  create_fun = norm_max
+)
 ```
@@
 set.seed(54321)
-plot_simdata(nlevels = seq(20, 45, 5),
+plot_simdata(
+  nlevels = seq(20, 45, 5),
   nsim = 500,
-             create_fun = norm_max, 
-             distr = "gumbel")
+  create_fun = norm_max
+  # distr = "gumbel",
+  # sim_dist = distributional::dist_normal(5, 10))
+)
 ```

### 2020-08-27 null_distribution.R

@@ -604,3 +604,111 @@ manynull.r1 %>%
   plot_nsim_2var() + 
   geom_vline(xintercept =  nullvalue, colour = "purple", show.legend = TRUE, labels = pvalue) + 
   ggtitle(paste("p-value: ", pvalue, ", x: ", nx, "levels", ", facet: ", nfacet, "levels")) 
+
+## ----normalv11_low
+set.seed(nx_range[1])
+nx <- 2
+sim_dist <- rep(distributional::dist_normal(5, 10), nx)
+
+p1 <- plot_normmax_1var(sim_dist,
+                        nx,
+                        nobs_sample = 5000
+) +
+  ggtitle(paste(nx, "levels"))
+
+## ----normalv12_low
+set.seed(3000)
+nx <- 3
+sim_dist <- rep(distributional::dist_normal(5, 10), nx)
+
+p2 <- plot_normmax_1var(sim_dist,
+                        nx,
+                        nobs_sample = 5000
+) +
+  ggtitle(paste(nx, "levels"))
+
+## ----normalv13_low
+set.seed(4000)
+nx <- 4
+sim_dist <- rep(distributional::dist_normal(5, 10), nx)
+
+p3 <- plot_normmax_1var(sim_dist,
+                        nx,
+                        nobs_sample = 5000
+) +
+  ggtitle(paste(nx, "levels"))
+
+
+## ----normalv14_low
+set.seed(5000)
+nx <- 5
+sim_dist <- rep(distributional::dist_normal(5, 10), nx)
+
+p4 <- plot_normmax_1var(sim_dist,
+                        nx,
+                        nobs_sample = 5000
+) +
+  ggtitle(paste(nx, "levels"))
+
+## ----normalv15_low
+set.seed(6000)
+nx <- 6
+sim_dist <- rep(distributional::dist_normal(5, 10), nx)
+
+p5 <- plot_normmax_1var(sim_dist,
+                        nx,
+                        nobs_sample = 5000
+) +
+  ggtitle(paste(nx, "levels"))
+
+## ----normalv16_low
+set.seed(7000)
+nx <- 7
+sim_dist <- rep(distributional::dist_normal(5, 10), nx)
+
+p6 <- plot_normmax_1var(sim_dist,
+                        nx,
+                        nobs_sample = 5000
+) +
+  ggtitle(paste(nx, "levels"))
+
+
+## ----normalv17_low
+set.seed(8000)
+nx <- 8
[…]

### 2020-08-27 mean_null.Rmd
minor change

@@
 
-Samples are taken from Gamma(3, 0.5) distribution and $k = 500$ in all the cases.
+Samples are taken from Gamma(shape = 3, rate = 0.5) distribution and $k = 500$ in all the cases.
 Small values of n considered in the range  ${2, 3, \ldots, 10}$ and large values of $n$ considered within ${25, 30, 35, \ldots, 45}$.
@@
 
-Q: So when we are talking about normalising for the levels when number of levels are low? - Not by using limit theorems. Transformation?
+Question: So we cannot normalise for the number of levels using limit theorems when we are talking about normalising for few levels?
+By normalisation, if we mean adjusting values measured on different scales to a common scale, then that could be done through limit theorems.
+If the intention is to align distributions to a normal like distribution, then we have to resort to something else like distribution transformation?
 
@@
 ```{r shape_rate}
-shape1 = 3
-rate1 = 0.5
+shape1 <- 3
+rate1 <- 0.5
 ```
@@
                            # number of simulations
-                           sim_dist = distributional::dist_gamma(shape = shape1, 
-                                                                 rate = rate1),
+                           sim_dist = distributional::dist_gamma(
+                             shape = shape1,
+                             rate = rate1
+                           ),
                            # distribution of each rv
@@
                          nsim = 500,
-                         sim_dist = distributional::dist_gamma(shape = shape1,
-                      rate = rate1),
+                         sim_dist = distributional::dist_gamma(
+                           shape = shape1,
+                           rate = rate1
+                         ),
                          # distr = "norm",

### 2020-08-27 mean_null.Rmd
tidy data structure

@@
 
-```{r functions}
+```{r create_simdata}
 # create data for each levels
@@
 
-```{r tidy_data}
-
-# input vector of levels for which distributions are plotted
-nlevels <- seq(2, 10, 1)
-
-plot_simdata <- function(nlevels = seq(2, 10, 1),
+```{r create_nlevels}
+create_nlevels <- function(nlevels = seq(2, 10, 2),
                            nsim = 500,
@@
     })
-
-  data_orig %>%
-    unnest(sim_data) %>%
-    ggplot(aes(x = sim_data)) +
-    geom_histogram() +
-    facet_wrap(~ind)
-  # + ggtitle(paste0(distr, " (",par1,", ",par2,")"))
+  data_orig %>% unnest(sim_data)
 }
-```
-
-In facet  with label 2, two random numbers are generated and their mean is computed.
-We repeat this process 500 times and draw the histogram of the computed means.
-Similarly, for facet with label 3, 3 random numbers are generated and histogram is drawn for the computed means of 3 random numbers.
-
-# Small levels and many iterations of means
-
-```{r}
-set.seed(12345)
-plot_simdata(
-  nlevels = seq(2, 10, 1),
-  nsim = 500,
-  create_fun = mean
-)
-```
-
-# Many levels and many iterations of means
-
-The histograms look like a normal distribution in this case, because number of levels are higher. For smaller number of levels, even with many repetitions the histograms do not look like normal.
-
-```{r}
-set.seed(54321)
-plot_simdata(
-  nlevels = seq(20, 45, 5),
-  nsim = 500,
-  create_fun = mean
-)
 ```
@@
 }
-```
-
-# Small levels and many iterations of normalised means
-
-```{r normmean_small_lev}
-set.seed(12345)
-plot_simdata(
-  nlevels = seq(2, 10, 1),
-  nsim = 500,
-  create_fun = norm_mean
-)
-```
-
-# Many levels and many iterations of normalised means
-
-```{r normmean_large_lev}
-set.seed(54321)
-plot_simdata(
-  nlevels = seq(20, 45, 5),
-  nsim = 500,
-  create_fun = norm_mean
-)
-```
-
-# EVT
-
-## Small levels and many iterations of max
-
-```{r max_small_lev}
-set.seed(12345)
-plot_simdata(
-  nlevels = seq(2, 10, 1),
-  nsim = 500,
-  create_fun = max
-)
-# sim_dist = distributional::dist_normal(5, 10))
-# distr = "gumbel")
-```
-
-## Many levels and many iterations of max
-
-```{r max_large_lev}
-set.seed(54321)
-plot_simdata(
-  nlevels = seq(20, 45, 5),
-  nsim = 500,
-  create_fun = max
-)
-# distr = "gumbel",
-# sim_dist = distributional::dist_normal(5, 10))
 ```
@@
 
+```{r create_scenarios}
+set.seed(12345)
+data_all_mean <- create_nlevels(nlevels = seq(2, 50, 1), create_fun = mean)
+
+set.seed(12345)
+data_all_max <- create_nlevels(nlevels = seq(2, 50, 1),
+                               create_fun = max)
+
+set.seed(12345)
+data_all_norm_mean <- create_nlevels(nlevels = seq(2, 50, 1),
+                               create_fun = norm_mean)
+
+set.seed(12345)
+data_all_norm_max <- create_nlevels(nlevels = seq(2, 50, 1),
+                               create_fun = norm_max)
+```
+
+# Small levels and many iterations of means
+
+```{r mean_small}
+data_all_mean %>%
+  filter(ind %in% seq(2, 10, 1)) %>%
+  ggplot(aes(x = sim_data)) +
+  geom_histogram() +
+  facet_wrap(~ind)
+```
+
+In facet  with label 2, two random numbers are generated and their mean is computed.
+We repeat this process 500 times and draw the histogram of the computed means.
+Similarly, for facet with label 3, 3 random numbers are generated and histogram is drawn for the computed means of 3 random numbers.
+
+# Many levels and many iterations of means
+
+```{r mean_large}
+data_all_mean %>%
+  filter(ind %in% seq(20, 45, 5)) %>%
+  ggplot(aes(x = sim_data)) +
+  geom_histogram() +
+  facet_wrap(~ind)
+```
+
+The histograms look like a normal distribution in this case, because number of levels are higher. For smaller number of levels, even with many repetitions the histograms do not look like normal.
+
+# Small levels and many iterations of normalised means
+
+```{r norm_mean_small}
+data_all_norm_mean %>%
+  filter(ind %in% seq(2, 10, 1)) %>%
+  ggplot(aes(x = sim_data)) +
+  geom_histogram() +
+  facet_wrap(~ind)
+```
+
+# Many levels and many iterations of normalised means
+
+```{r norm_mean_large}
+data_all_norm_mean %>%
+  filter(ind %in% seq(20, 45, 5)) %>%
+  ggplot(aes(x = sim_data)) +
+  geom_histogram() +
+  facet_wrap(~ind)
+```
+
+# EVT
+
+## Small levels and many iterations of max
+
+```{r max_small}
+data_all_max %>%
+  filter(ind %in% seq(2, 10, 1)) %>%
+  ggplot(aes(x = sim_data)) +
+  geom_histogram() +
+  facet_wrap(~ind)
+```
+
+## Many levels and many iterations of max
+
+```{r max_large}
+data_all_max %>%
+  filter(ind %in% seq(20, 45, 5)) %>%
+  ggplot(aes(x = sim_data)) +
+  geom_histogram() +
+  facet_wrap(~ind)
+```
+
 ## Small levels and many iterations of norm max
 
-```{r normmax_small_lev}
-set.seed(12345)
-plot_simdata(
-  nlevels = seq(2, 10, 1),
-  nsim = 500,
-  # distr = "gumbel",
-  # sim_dist = distributional::dist_normal(5, 10),
-  create_fun = norm_max
-)
+```{r norm_max_small}
+data_all_norm_max %>%
+  filter(ind %in% seq(2, 10, 1)) %>%
+  ggplot(aes(x = sim_data)) +
+  geom_histogram() +
+  facet_wrap(~ind)
 ```
@@
 
-```{r normmax_large_lev}
-set.seed(54321)
-plot_simdata(
-  nlevels = seq(20, 45, 5),
-  nsim = 500,
-  create_fun = norm_max
-  # distr = "gumbel",
-  # sim_dist = distributional::dist_normal(5, 10))
-)
+```{r norm_max_large}
+data_all_norm_max %>%
+  filter(ind %in% seq(20, 45, 5)) %>%
+  ggplot(aes(x = sim_data)) +
+  geom_histogram() +
+  facet_wrap(~ind)
 ```

### 2020-08-27 mean_null.Rmd
tidy data structure

@@
 When we are taking the max of 2 or 3 rvs ("levels" in our terminology), $n = 2/3$, which are far too less.
-Hence, normalisation would be able to nullify the effect of $n$ only for large enough $n$.
+Hence, normalization would be able to nullify the effect of $n$ only for large enough $n$.
 
@@
 
- 3. normalised sample means for small $n$
+ 3. normalized sample means for small $n$
 (Obs: distribution doesn't look similar)
 
- 4. normalised sample means for large $n$ 
+ 4. normalized sample means for large $n$ 
 (Obs: distribution looks similar in both shape and scale with mean 0)
@@
 
- 7. normalised sample maximums for small $n$ 
+ 7. normalized sample maximums for small $n$ 
 (Obs: distribution doesn't look similar, scaled down, maybe similar after facet label 5)
 
- 8. normalised sample maximums for large $n$ 
-(Obs: distribution looks similar and it has been scaled down much more than maximum without normalisation. Can we use this fact to explore maximums more?)
+ 8. normalized sample maximums for large $n$ 
+(Obs: distribution looks similar and it has been scaled down much more than maximum without normalization. Can we use this fact to explore maximums more?)
 
-Question: So we cannot normalise for the number of levels using limit theorems when we are talking about normalising for few levels?
-By normalisation, if we mean adjusting values measured on different scales to a common scale, then that could be done through limit theorems.
+Question: So we cannot normalize for the number of levels using limit theorems when we are talking about normalizing for few levels?
+By normalization, if we mean adjusting values measured on different scales to a common scale, then that could be done through limit theorems.
 If the intention is to align distributions to a normal like distribution, then we have to resort to something else like distribution transformation?
@@
 Suppose that $X_1$, $X_2$ , ... , $X_n$ are i.i.d. random variables with expected values $E(X_i) = \mu < \infty$ and variance $Var(X_i) = \sigma^2 < \infty$.
-Suppose the sample mean is $\bar{X} = \frac{(X_1 + X_2 + \ldots + X_n)}{n}$, then by CLT the distribution of the normalised random variable:
+Suppose the sample mean is $\bar{X} = \frac{(X_1 + X_2 + \ldots + X_n)}{n}$, then by CLT the distribution of the normalized random variable:
 $Z_n = \frac{\bar{X} - \mu}{\sqrt n\sigma}$ converges in distribution to a standard normal distribution.
@@
 set.seed(12345)
-data_all_max <- create_nlevels(nlevels = seq(2, 50, 1),
-                               create_fun = max)
+data_all_max <- create_nlevels(
+  nlevels = seq(2, 50, 1),
+  create_fun = max
+)
 
 set.seed(12345)
-data_all_norm_mean <- create_nlevels(nlevels = seq(2, 50, 1),
-                               create_fun = norm_mean)
+data_all_norm_mean <- create_nlevels(
+  nlevels = seq(2, 50, 1),
+  create_fun = norm_mean
+)
 
 set.seed(12345)
-data_all_norm_max <- create_nlevels(nlevels = seq(2, 50, 1),
-                               create_fun = norm_max)
+data_all_norm_max <- create_nlevels(
+  nlevels = seq(2, 50, 1),
+  create_fun = norm_max
+)
 ```
@@
 
-# Small levels and many iterations of normalised means
+# Small levels and many iterations of normalized means
 
@@
 
-# Many levels and many iterations of normalised means
+# Many levels and many iterations of normalized means
 

### 2020-09-02 manual_distribution_max.Rmd
mean null updated with scripts all in mean_null.R

---
title: "Untitled"
author: "Sayani Gupta"
date: "28/08/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Why normalise?

Suppose that $X_1$, $X_2$ , ... , $X_n$ are i.i.d. random variables with expected values $E(X_i) = \mu < \infty$ and variance $Var(X_i) = \sigma^2 < \infty$. Let 
$Y = max(X_1, X_2, \dots, X_n)$.

Let $F_X(x)$ be the common distribution of the variables $X_i$ and let $F_Y(y)$ be the
corresponding distribution of $Y$. $F_Y(y)$ could be obtained from $F_X(x)$ simply by using:
$F_Y(y) = P[(X_1 ≤ y)∩(X_2 ≤ y) ∩...∩ (X_n ≤ y)] = {F_X(y)}^n$. For large $n$, the distribution of $Y$ approaches a standard shape, which does not depend on $F_X$.But what about the case when $n$ is not large enough. Then the distribution of maximum will indeed depend on maximum is taken for random variables from which distributions. If $F_X(x)$ is the CDF of $X$, then $F_Y(y) = {F_x(y)}^n$. If $\Phi$ nd $\phi$ are the cdf and pdf of a standard normal distribution, then
$f_Y(y) = n{\Phi(y)}^{n-1}\phi(y)$, which depends on $n$. Hence, we are trying to normalise for $n$, since the distribution of maximum depends on $n$.As $n$ grows, we  can see the right tail growing, which implies that the probability that we will get a higher maximum is more. Now, for large $n$, we used EVT to normalise for $n$, that is, we brought them to the same scale without distorting the range of the distribution. But in our case, we will mostly have small $n$. It is important to ensure that they have the same mean and variation, for being able to compare the maximum value across $n$.

## Mean and standard deviation of the distribution of maximum for small n

Analytically,
sample mean: $ \frac{\sum(Y_i)}{n}$
throeretical mean: $ \frac{\int_i(y_if_Y(y_i))}{n}$

### 2020-09-02 mean_null.Rmd
mean null updated with scripts all in mean_null.R

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-library(tidyverse)
-library(ggplot2)
-library(ggpubr)
+library(knitr)
+opts_chunk$set(
+  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
+  fig.path = "figure/", fig.align = "center", fig.show = "hold",
+  cache = TRUE, cache.path = "cache/",
+  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
+)
+knitr::opts_knit$set(root.dir = here::here())
+read_chunk('mean_null.R')
 ```
@@
 ```{r shape_rate}
-shape1 <- 3
-rate1 <- 0.5
 ```
@@
 ```{r create_simdata}
-# create data for each levels
 
-create_simdata <- function(nx = 2,
-                           # number of rvs to generate
-                           nsim = 500,
-                           # number of simulations
-                           sim_dist = distributional::dist_gamma(
-                             shape = shape1,
-                             rate = rate1
-                           ),
-                           # distribution of each rv
-                           create_fun = mean
-                           # function used on the rvs
-) {
-  mean_dist <- (1:nsim) %>%
-    purrr::map(function(i) {
-      x <- sim_dist %>%
-        distributional::generate(nx) %>%
-        unlist()
-      x %>% create_fun()
-    })
-}
 ```
@@
 ```{r create_nlevels}
-create_nlevels <- function(nlevels = seq(2, 10, 2),
-                           nsim = 500,
-                           sim_dist = distributional::dist_gamma(
-                             shape = shape1,
-                             rate = rate1
-                           ),
-                           # distr = "norm",
-                           create_fun = mean) {
-  data_orig <- nlevels %>%
-    purrr::map_df(function(i) {
-      create_datai <- create_simdata(nx = i, nsim, sim_dist, create_fun)
-      tibble::tibble(ind = i, sim_data = create_datai)
-    })
-  data_orig %>% unnest(sim_data)
-}
 ```
@@
 ```{r norm_mean}
-norm_mean <- function(x = NULL,
-                      shape = shape1,
-                      rate = rate1) {
-  meanx <- shape / rate
-  sdx <- shape / (rate^2)
-  (mean(x) - meanx) / sdx
-}
 ```
@@
 ```{r norm_max}
-# normalised maximum of a vector
-norm_max <- function(x = NULL,
-                     shape = shape1,
-                     rate = rate1) {
-  nx <- length(x)
-  p <- 1 - (1 / nx)
-  meanx <- shape / rate
-  sdx <- shape / (rate^2)
-  # meanx = 5
-  # sdx = 10
-  b <- stats::qnorm(p, meanx, sdx)
-  a <- 1 / (nx * stats::dnorm(b, meanx, sdx))
-  # k = stats::quantile(x, p, type = 8, na.rm = TRUE)
-  (max(x) - a) / b
-  # max(x)/k
-}
+
 ```
@@
 ```{r create_scenarios}
-set.seed(12345)
-data_all_mean <- create_nlevels(nlevels = seq(2, 50, 1), create_fun = mean)
 
-set.seed(12345)
-data_all_max <- create_nlevels(
-  nlevels = seq(2, 50, 1),
-  create_fun = max
-)
-
-set.seed(12345)
-data_all_norm_mean <- create_nlevels(
-  nlevels = seq(2, 50, 1),
-  create_fun = norm_mean
-)
-
-set.seed(12345)
-data_all_norm_max <- create_nlevels(
-  nlevels = seq(2, 50, 1),
-  create_fun = norm_max
-)
 ```
@@
 ```{r mean_small}
-data_all_mean %>%
-  filter(ind %in% seq(2, 10, 1)) %>%
-  ggplot(aes(x = sim_data)) +
-  geom_histogram() +
-  facet_wrap(~ind)
+
 ```
@@
 ```{r mean_large}
-data_all_mean %>%
-  filter(ind %in% seq(20, 45, 5)) %>%
-  ggplot(aes(x = sim_data)) +
-  geom_histogram() +
-  facet_wrap(~ind)
+
 ```
@@
 ```{r norm_mean_small}
-data_all_norm_mean %>%
-  filter(ind %in% seq(2, 10, 1)) %>%
-  ggplot(aes(x = sim_data)) +
-  geom_histogram() +
-  facet_wrap(~ind)
+
 ```
@@
 ```{r norm_mean_large}
-data_all_norm_mean %>%
-  filter(ind %in% seq(20, 45, 5)) %>%
-  ggplot(aes(x = sim_data)) +
-  geom_histogram() +
-  facet_wrap(~ind)
+
 ```
@@
 ```{r max_small}
-data_all_max %>%
-  filter(ind %in% seq(2, 10, 1)) %>%
-  ggplot(aes(x = sim_data)) +
-  geom_histogram() +
-  facet_wrap(~ind)
 ```
@@
 ```{r max_large}
-data_all_max %>%
-  filter(ind %in% seq(20, 45, 5)) %>%
-  ggplot(aes(x = sim_data)) +
-  geom_histogram() +
-  facet_wrap(~ind)
 ```
@@
 ```{r norm_max_small}
-data_all_norm_max %>%
-  filter(ind %in% seq(2, 10, 1)) %>%
-  ggplot(aes(x = sim_data)) +
-  geom_histogram() +
-  facet_wrap(~ind)
 ```
@@
 ```{r norm_max_large}
-data_all_norm_max %>%
-  filter(ind %in% seq(20, 45, 5)) %>%
-  ggplot(aes(x = sim_data)) +
-  geom_histogram() +
-  facet_wrap(~ind)
 ```

### 2020-09-02 manual_distribution_max.Rmd
mean and sd of the distribution of max - delete html

@@
 ---
-title: "Untitled"
+title: "Mean and sd of null distribution"
 author: "Sayani Gupta"
-date: "28/08/2020"
-output: html_document
+output: pdf_document
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+library(knitr)
+opts_chunk$set(
+  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
+  fig.path = "figure/", fig.align = "center", fig.show = "hold",
+  cache = TRUE, cache.path = "cache/",
+  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
+)
+knitr::opts_knit$set(root.dir = here::here())
+read_chunk("mean_null.R")
 ```
-
-## Why normalise?
 
@@
 corresponding distribution of $Y$. $F_Y(y)$ could be obtained from $F_X(x)$ simply by using:
-$F_Y(y) = P[(X_1 ≤ y)∩(X_2 ≤ y) ∩...∩ (X_n ≤ y)] = {F_X(y)}^n$.
-For large $n$, the distribution of $Y$ approaches a standard shape, which does not depend on $F_X$.But what about the case when $n$ is not large enough.
-Then the distribution of maximum will indeed depend on maximum is taken for random variables from which distributions.
+$F_Y(y) = P[(X_1 \leq y)\cap(X_2 \leq y) \cap...\cap (X_n \leq y)] = {F_X(y)}^n$.
+For large $n$, the distribution of $Y$ approaches a standard shape, which does not depend on $F_X$.
+But what about the case when $n$ is not large enough?
+The distribution of maximum in that case will indeed depend on $n$ and the underlying distribution of $X$.
 If $F_X(x)$ is the CDF of $X$, then $F_Y(y) = {F_x(y)}^n$.
-If $\Phi$ nd $\phi$ are the cdf and pdf of a standard normal distribution, then
+Suppose $\Phi$ nd $\phi$ are the cdf and pdf of a standard normal distribution, then
 $f_Y(y) = n{\Phi(y)}^{n-1}\phi(y)$, which depends on $n$.
-Hence, we are trying to normalise for $n$, since the distribution of maximum depends on $n$.As $n$ grows, we  can see the right tail growing, which implies that the probability that we will get a higher maximum is more.
+Hence, we are trying to normalise for $n$.
+Also, it depends on the underlying distribution of $X$, which we have assumed as normal in our case.
+As $n$ grows, we  can see the right tail growing, which implies that the probability that we will get a higher maximum is more.
 Now, for large $n$, we used EVT to normalise for $n$, that is, we brought them to the same scale without distorting the range of the distribution.
@@
 It is important to ensure that they have the same mean and variation, for being able to compare the maximum value across $n$.
+We observe from the following graphs that our normalisation works after $n=6$, after which the difference in mean and standard deviation flattens out a lot.
 
-## Mean and standard deviation of the distribution of maximum for small n
+```{r create_simdata}
 
-Analytically,
-sample mean: $ \frac{\sum(Y_i)}{n}$
-throeretical mean: $ \frac{\int_i(y_if_Y(y_i))}{n}$
+```
+
+```{r create_nlevels}
+
+```
+
+```{r shape_rate}
+
+```
+
+```{r norm_max}
+
+```
+
+## Mean and standard deviation of the distribution of maximum
+
+```{r max_large_mean_sd}
+
+```
+
+## Mean and standard deviation of the distribution of normalised maximum
+
+```{r max_large_mean_sd_norm}
+
+```
+
+Looking at the smaller values of $n$, what we already saw last week.
+
+## Distribution of max for smaller n
+```{r small_max_normal}
+
+```
+
+## Distribution of normalised max for smaller n
+
+```{r small_normmax_normal}
+
+```

### 2020-09-03 manual_distribution_max.Rmd
bootstrap code added

@@
 ```
+
+# Question:1
+
+I'm definite that the theeretical distribution of Jensen Shannon statistic follows a Chi-squared distribution with $m$ degrees of freedom.
+If $m$ is sufficiently large, Chi square distribution will tend to a Normal distribution with mean $m$ and variance $2m$.
+
+Empirical test: In my case, do we mean that no matter what is the underlying distribution of the dataset, if you compute Jensen Shannon distances they will be normal like?
+
+Let's find out!
+
+Simulation study:
+
+ 1. Fix $n$.
+ 2. Take a particular distribution and generate $N$ random samples of size $n$ each.
+ 3. Compute pairwise distances for each random sample.
+ 4. Construct a histogram to see of the pairwise distances follow Normal?
+
+# Question:2
+
+Let's suppose they are normal!
+How would the max of these normal distances behave?
+Would the distribution of the maximum differ if you are taking max between 2 random variables or maximum between 10 random variables?
+
+Yes they would! So what do you do about it?
+
+We want to make the distribution of the max same for any $n$.
+By making the distribution same, we just mean that at least the mean and sd of the distribution of the maximum should be same for varied n.
+This means we should be able to compare values across different $n$.
+What is a consistent estimator of max?
+
+## Simulation Study
+
+Aim:  To see if norm_max is working after a certain $n$ for all cases.
+ 1. Generate N(1:10,10) distribution and compute distribution of max and norm_max.  
+ 2. Generate N(10,1:10) distribution and compute distribution of max and norm_max.
+
+## Behavior of mean and sd of the distribution of maximum
 
@@
 
-```{r shape_rate}
-
-```
-
-```{r norm_max}
+```{r norm_max_new}
 
@@
 ```
+
+Aim:  To compute mean and sd by bootstrap method for small samples and compute norm_max to see if it is working for $n$ cases.
+
+## Non-parametric bootstrap
+
+Assuming a data set $x = (x_1, ..., x_n)$ is available.  
+1. Fix the number of bootstrap re-samples $N$. Often $N \in [1000, 2000]$.  
+2. Sample a new data set $x^{*}$ set of size $n$ from $x$ with replacement (this is equivalent to sampling from the empirical cdf $\hat{F}$).  
+3. Estimate $\theta$ from $x^*$. Call the estimate $\hat{\theta}$ $\forall i \in {1,\ldots, N}$. Store.  
+4. Repeat step 2 and 3 $N$ times.  
+5. Consider the empirical distribution of ($\hat{\theta}^*_1, \hat{\theta}^*_2, \ldots, \hat{\theta}^*_N$) as an approximation of the true
+distribution of $\hat{\theta}$.
+
+We assume that distances are normal, but we do not assume anything about the distribution of max distances. So using the non-paramteric bootstrap approach to estimate the $\theta = (\mu, \sigma)$.
+
+I construct the data structure for $n = 2$ here to ensure that the methodology is correct.
+
+| N 	| $x_1$    	| $x_2$    	| max 	|
+|---	|-------	|-------	|------	|----	|
+| 1 	| $x_{1,1}$  	| $x_{1,2}$  	| $m_1$   	|
+| 2 	| .     	| .     	| $m_2$   	|
+| . 	| .     	| .     	| .    	|
+| . 	| .     	| .     	| .    	|
+| N 	| $x_{1, N}$ 	| $x_{2, N}$ 	| $m_N$   	|
+
+Question:3
+
+This is just for one level! What do you do for the other level?
+
+Do you take median or max. Given that you take median how do you normalise for the value of $n$ there? What is a consistent estimator of median?

### 2020-09-03 bootstrap.R

@@ -8,27 +8,45 @@ sim_dist <- dist_normal(5, 10)
 
 # generate samples of size 1, 2, 3,... upto 50
 # generate bootstrap (sample with replacement) from one drawn sample
-set.seed(150)
 data_n <- n %>% map_df(function(i) {
-  sim_data <- generate(sim_dist, i)
-  data_orig <- bind_cols(n = i, sim_data)
-  boot_data <- bootstraps(data_orig, times = 2000, apparent = TRUE)
+  set.seed(1000 + i)
+  sim_data <- distributional::generate(sim_dist, i)
+  data_orig <- bind_cols(n = i, unlist(sim_data))
+  boot_data <- bootstraps(data_orig, times = 20000, apparent = TRUE)
   data_bootstrap <- bind_cols(n = i, boot_data)
   data_bootstrap
 })
 
-# compute mean and sd of the bootstrap samples
+# mean and sd of extracted data from bootstrap data
 
 mean_bootstrap <- function(split) {
-  mean(analysis(split), na.rm = TRUE)
+  data = analysis(split)
+  mean(data$`...2`, na.rm = TRUE)
 }
 
+sd_bootstrap <- function(split) {
+  data = analysis(split)
+  sd(data$`...2`, na.rm = TRUE)
+}
 
+max_bootstrap <- function(split) {
+  data = analysis(split)
+  max(data$`...2`, na.rm = TRUE)
+}
 
-boot_models <-
+# compute mean and sd of the bootstrap samples
+boot_max <-
   data_n %>%
-  filter(n==2) %>% 
+  group_by(n) %>% 
   mutate(
-    mean = map(splits, mean_bootstrap)
-    #sd = map(splits, sd)
-  )
+    sim_max = map(splits, max_bootstrap)
+  ) %>% unnest(cols = sim_max)
+
+
+
+boot_max %>%
+  filter(n %in% 2:10) %>% 
+  group_by(sim_max) %>% 
+  ggplot() +
+  geom_histogram(aes(x = sim_max)) +
+  facet_wrap(~n)

### 2020-09-03 mean_null.R

@@ -1,16 +1,16 @@
-##----load_lib
+## ----load_lib
 library(tidyverse)
 library(ggplot2)
 library(ggpubr)
 library(distributional)
 
-##----shape_rate
+## ----shape_rate
 shape1 <- 3
 rate1 <- 0.5
 
 
 
-##----create_simdata
+## ----create_simdata
 # create data for each levels
 
 create_simdata <- function(nx = 2,
@@ -34,7 +34,7 @@ create_simdata <- function(nx = 2,
     })
 }
 
-##----create_nlevels
+## ----create_nlevels
 create_nlevels <- function(nlevels = seq(2, 10, 2),
                            nsim = 500,
                            sim_dist = distributional::dist_gamma(
@@ -51,7 +51,7 @@ create_nlevels <- function(nlevels = seq(2, 10, 2),
   data_orig %>% unnest(sim_data)
 }
 
-##----norm_mean
+## ----norm_mean
 norm_mean <- function(x = NULL,
                       shape = shape1,
                       rate = rate1) {
@@ -62,7 +62,7 @@ norm_mean <- function(x = NULL,
 
 
 
-##----norm_max
+## ----norm_max
 # normalised maximum of a vector
 norm_max <- function(x = NULL,
                      shape = shape1,
@@ -75,13 +75,13 @@ norm_max <- function(x = NULL,
   # sdx = 10
   b <- stats::qnorm(p, meanx, sdx)
   a <- 1 / (nx * stats::dnorm(b, meanx, sdx))
-  #k = stats::quantile(x, p, type = 8, na.rm = TRUE)
+  # k = stats::quantile(x, p, type = 8, na.rm = TRUE)
   (max(x) - a) / b
-  #max(x)/k
+  # max(x)/k
 }
 
 
-##----create_scenarios
+## ----create_scenarios
 set.seed(12345)
 data_all_mean <- create_nlevels(nlevels = seq(2, 50, 1), create_fun = mean)
 
@@ -104,7 +104,7 @@ data_all_norm_max <- create_nlevels(
 )
 
 
-##----mean_small
+## ----mean_small
 data_all_mean %>%
   filter(ind %in% seq(2, 10, 1)) %>%
   ggplot(aes(x = sim_data)) +
@@ -112,21 +112,21 @@ data_all_mean %>%
[…]

### 2020-09-30 main.Rmd
adding CLT, EVT and simulations
distribution of median and sd added

@@
 read_chunk("null_distribution.R")
+read_chunk("mean_null.R")
 ```
@@
 When we need to understand the interplay of different periodicities in a high frequency temporal datasets, we have many choices to consider.
-To be able to dice time in all possible ways in order to have multiple perspectives about peridicities in the data, there are too many things that we should look at ideally.
-Exploratory analysis is detective work and it is difficult to traverse through all possible ways without any systematic approach.
-It is immensely useful to be able to make transition from all possible ways to only ways that could potentially be important given a situation.
+In [@wang2019tsibble] and [@wang2020calendar], periodicities are explored across hour of the day and day of the week or months.
+But calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions.
 The paper (gravitas) describes how we can start with all possible combinations of cyclic time granularities and narrow down our search to harmonies and remove clashes without losing any perspectives about the data.
@@
 The idea here is to rate a harmony pair higher if this variation between different levels of the x-axis variable is higher on an average across all levels of facet variables.
+
+To be able to dice time in all possible ways in order to have multiple perspectives about peridicities in the data, there are too many things that we should look at ideally.
+Exploratory analysis is detective work and it is difficult to traverse through all possible ways without any systematic approach.
+It is immensely useful to be able to make transition from all possible ways to only ways that could potentially be important given a situation.
+
+Talk about Scagnostics: Tukey
 
@@
 The normalizing constants $(a_{n}, b_{n})$ vary depending on the underlying distribution of the pairwise distances.
-Hence to normalize appropriately, it is important to assume a distribution of these distances.
+Hence to normalize appropriately, it is
+important to assume a distribution of these distances.
+
+### why normalize
+
+Suppose that $X_1$, $X_2$ , ... , $X_n$ are i.i.d. random variables with expected values $E(X_i) = \mu < \infty$ and variance $Var(X_i) = \sigma^2 < \infty$. Let 
+$Y = max(X_1, X_2, \dots, X_n)$.
+
+Let $F_X(x)$ be the common distribution of the variables $X_i$ and let $F_Y(y)$ be the corresponding distribution of $Y$. $F_Y(y)$ could be obtained from $F_X(x)$ simply by using:
+$F_Y(y) = P[(X_1 \leq y)\cap(X_2 \leq y) \cap...\cap (X_n \leq y)] = {F_X(y)}^n$.
+For large $n$, the distribution of $Y$ approaches a standard shape, which does not depend on $F_X$.
+But what about the case when $n$ is not large enough?
+The distribution of maximum in that case will indeed depend on $n$ and the underlying distribution of $X$.
+If $F_X(x)$ is the CDF of $X$, then $F_Y(y) = {F_x(y)}^n$.
+Suppose $\Phi$ nd $\phi$ are the cdf and pdf of a standard normal distribution, then
+$f_Y(y) = n{\Phi(y)}^{n-1}\phi(y)$, which depends on $n$.
+Hence, we are trying to normalise for $n$.
+Also, it depends on the underlying distribution of $X$, which we have assumed as normal in our case.
+As $n$ grows, we  can see the right tail growing, which implies that the probability that we will get a higher maximum is more.
+Now, for large $n$, we used EVT to normalise for $n$, that is, we brought them to the same scale without distorting the range of the distribution.
+But in our case, we will mostly have small $n$.
+It is important to ensure that they have the same mean and variation, for being able to compare the maximum value across $n$.
+We observe from the following graphs that our normalisation works after $n=6$, after which the difference in mean and standard deviation flattens out a lot.
+
+```{r create_simdata}
+
+```
+
+```{r create_nlevels}
+
+```
+
+```{r norm_max_new}
+
+```
+
+## Mean and standard deviation of the distribution of maximum
+
+```{r}
+library(ggridges)
+library(viridis)
+max_all_data <- create_nlevels(nlevels = seq(2, 30, 2),
+                           nsim = 500,
+                           sim_dist = distributional::dist_normal(5, 10), create_fun = max)
+
+g1 <- max_all_data %>% ggplot() + geom_density_ridges(aes(x=sim_data, y = as.factor(ind))) + ylab("n") + xlab("max")
+
+median_all_data <- create_nlevels(nlevels = seq(2, 30, 2),
+                           nsim = 500,
+                           sim_dist = distributional::dist_normal(5, 10), create_fun = median)
+
+g2 <- max_all_data %>% ggplot() + geom_boxplot(aes(x=sim_data, y = as.factor(ind)))  + ylab("n") + xlab("median")
+
+ggpubr::ggarrange(g1, g2, ncol = 2)
+
+```
 
@@
 
+### Confidence interval of test statistic
+
 ## Simulation design

### 2020-10-01 main.Rmd
commit for new branch
introduction and drake workflow

@@
 
-Take an example of a data set which are observed at fine temporal scales, like that of NYC bike usage available at https://www.citibikenyc.com/system-data.
+Take the example of the calendar display of electricity smart meter data used in @wang2020calendar for four households in Melbourne, Australia.
+The authors show how hour-of-the-day interact with weekday and weekends and then move on to use calendar display to display the daily schedules.
+The calendar display has several components in it which helps us to look at energy consumption across hour-of-the-day, day-of-the-week, week-of-the-month and month-of-the-year all at once.
+Some interaction of these cyclic granularities[@our-paper] could also be interpreted from this display.
+However, there are two things that might be of concern.
+Due to the combination of linear and cyclic representation of time, it is difficult to comprehend the interaction of periodicities at once from this display.
+For example, this display might not be the best to understand how hour-of-the-day or month-of-year varies across week-of-the-month.
+Further, it is not clear what all interactions of cyclic granularities should be read from this display as there could be many combinations that one can look at.
+Moreover, calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions (@our-paper) and could include other cyclic granularities like hour-of-week or day-of-fortnight which could potentially become useful depending on context.
+Lastly, there might be certain interactions which are interesting and others which are not.
+It could be potentially useful to know which all cyclic granularities could be useful.
+
+<!-- Take an example of a data set which are observed at fine temporal scales, like that of NYC bike usage available at https://www.citibikenyc.com/system-data.
 We use the `nyc_bikes` data set from the R package `tsibbledata` which takes a sample of 10 bikes for the year 2018.
@@
 How to understand which pairs are sufficient to explore given the data set without losing much information about the data.
+-->
 
-When we need to understand the interplay of different periodicities in a high frequency temporal datasets, we have many choices to consider.
+<!-- When we need to understand the interplay of different periodicities in a high frequency temporal datasets, we have many choices to consider.
 In [@wang2019tsibble] and [@wang2020calendar], periodicities are explored across hour of the day and day of the week or months.
 But calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions.
+-->
+
 The paper (gravitas) describes how we can start with all possible combinations of cyclic time granularities and narrow down our search to harmonies and remove clashes without losing any perspectives about the data.
@@
 Assuming a numeric response variable, our graphics are displays of distributions compared across combinations of categorical variables, one placed at x-axis and the other on the facet.
-Gestalt theory suggests that when items are placed in close proximity, people assume that they are in the same group because they are close to one another and apart from other groups.
-Hence, displays that capture more variation within different categories in the same group would be important to bring out different patterns of the data.
+Displays that capture more variation within different categories in the same group would be important to bring out different patterns of the data.
 Here, we have two main objectives:
@@
 
-```{r distv11}
+<!-- ```{r distv11} -->
 
-```
+<!-- ``` -->
 
-```{r distv12}
+<!-- ```{r distv12} -->
 
-```
+<!-- ``` -->
 
-```{r distv13}
+<!-- ```{r distv13} -->
 
-```
+<!-- ``` -->
 
-```{r distv14}
+<!-- ```{r distv14} -->
 
-```
+<!-- ``` -->
 

### 2020-10-01 R/plan.R

@@ -3,4 +3,27 @@ the_plan <-
 
    ## Plan targets in here.
 
+    # use gravitas to show motivation
+    plots_motivation = check_if_gravitas(),
+    # mean and sd of distribution of maximum and median
+    plot_why_normalise = why_normalise(),
+    
+    # null distribution
+  null_dist_sim1 <- null_sim1(),
+  null_dist_sim2 <- null_sim2(),
+  null_dist_sim3 <- null_sim3(),
+   
+  # alternate distribution
+   
+  alt_dist_sim1 <- alt_sim1(),
+  alt_dist_sim2 <- alt_sim2(),
+  alt_dist_sim3 <- alt_sim3(),
+  
+  # application1
+  # 
+  # application2
+  # 
+  # 
+  
+    
 )

### 2020-10-01 main.Rmd
introduction structure decided

@@
 
+<!-- background of the problem -->
 Take the example of the calendar display of electricity smart meter data used in @wang2020calendar for four households in Melbourne, Australia.
@@
 Lastly, there might be certain interactions which are interesting and others which are not.
-It could be potentially useful to know which all cyclic granularities could be useful.
+It is immensely useful to be able to make transition from all possible ways to only ways that could potentially be important given a situation.
 
@@
 
-The paper (gravitas) describes how we can start with all possible combinations of cyclic time granularities and narrow down our search to harmonies and remove clashes without losing any perspectives about the data.
-Even after excluding clashes, the list of harmonies left could be large and overwhelming for human consumption.
-Hence, there is a need to rank the harmonies basis how well they capture the variation in the measured variable and additionally reduce the number of harmonies for further exploration/visualization.
-Assuming a numeric response variable, our graphics are displays of distributions compared across combinations of categorical variables, one placed at x-axis and the other on the facet.
-Displays that capture more variation within different categories in the same group would be important to bring out different patterns of the data.
+<!-- what is the dimension of the problem -->
+The paper (gravitas) describes how we can compute all possible combinations of cyclic time granularities.
+If we have $n$ periodic linear granularities in the hierarchy table, then $n(n-1)/2$ circular or quasi-circular cyclic granularities could be constructed.
+Let $N_C$ be the total number of contextual circular, quasi-circular and aperiodic cyclic granularities that can originate from the underlying periodic and aperiodic linear granularities.
+Assuming a numeric response variable, the graphics are displays of distributions compared across combinations of these cyclic granularities, one placed at x-axis and the other on the facet.
+With this design, potentially there are $^{N_C}P_2$ possible pairwise plots, where each plot would display pair of cyclic granularities.
+Now this is large and overwhelming for human consumption.
+
+<!-- Scagnostics literature -->
+This is similar to Scagnostics (Scatterplot Diagnostics)[@mention-paper] which is used to discern meaningful patterns in large collections of scatterplots.
+Given a set of $v$ variables, there are $v(v-1)/2$ pairs of variables, and thus the same number of possible pairwise scatterplots.
+Therefore
+for even small $v$, the number of scatterplots can be
+large and scatterplot matrices (SPLOMs) could easily run out of pixels when presenting high-dimensional data.
+[@ScagExplorer], [@otherref] provides solution to this, where few characterizations helps us to locate anomalies for further analysis or search for
+similar distributions in a “large” SPLOM with more than a hundred dimensions.
+
+<!-- harmonies and why it is not enough -->
+The paper (gravitas) narrows down our search to harmonies and remove clashes without losing any perspectives about the data.
+But even after excluding clashes, the list of harmonies left could be large and overwhelming for human consumption.
+Hence, there is a need to rank the harmonies basis how well they capture the variation in the measured variable and additionally reduce the number of harmonies to include only those for which variation within different categories are significant.
+
+<!-- in the same group would be important to bring out different patterns of the data. -->
+
 Here, we have two main objectives:
@@
 
-To be able to dice time in all possible ways in order to have multiple perspectives about peridicities in the data, there are too many things that we should look at ideally.
-Exploratory analysis is detective work and it is difficult to traverse through all possible ways without any systematic approach.
-It is immensely useful to be able to make transition from all possible ways to only ways that could potentially be important given a situation.
-
-Talk about Scagnostics: Tukey
+<!-- Talk about Scagnostics: Tukey -->
 

### 2020-10-01 main.Rmd
introduction revise

@@
 The authors show how hour-of-the-day interact with weekday and weekends and then move on to use calendar display to display the daily schedules.
-The calendar display has several components in it which helps us to look at energy consumption across hour-of-the-day, day-of-the-week, week-of-the-month and month-of-the-year all at once.
+The calendar display has several components in it, which helps us look at energy consumption across hour-of-the-day, day-of-the-week, week-of-the-month, and month-of-the-year at once.
 Some interaction of these cyclic granularities[@our-paper] could also be interpreted from this display.
-However, there are two things that might be of concern.
-Due to the combination of linear and cyclic representation of time, it is difficult to comprehend the interaction of periodicities at once from this display.
+However, certain things might be of concern.
+Due to the combination of linear and cyclic representation of time, it is not easy to comprehend the interaction of some periodicities' interaction from this display.
 For example, this display might not be the best to understand how hour-of-the-day or month-of-year varies across week-of-the-month.
 Further, it is not clear what all interactions of cyclic granularities should be read from this display as there could be many combinations that one can look at.
-Moreover, calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions (@our-paper) and could include other cyclic granularities like hour-of-week or day-of-fortnight which could potentially become useful depending on context.
-Lastly, there might be certain interactions which are interesting and others which are not.
-It is immensely useful to be able to make transition from all possible ways to only ways that could potentially be important given a situation.
+Moreover, calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions (@our-paper) and could include other cyclic granularities like hour-of-week or day-of-fortnight, which could potentially become useful depending on the context.
+Lastly, there might be specific interactions that are interesting and others that are not.
+It is immensely useful to make the transition from all possible ways to only ways that could potentially be important given a situation.
 
@@
 Let $N_C$ be the total number of contextual circular, quasi-circular and aperiodic cyclic granularities that can originate from the underlying periodic and aperiodic linear granularities.
-Assuming a numeric response variable, the graphics are displays of distributions compared across combinations of these cyclic granularities, one placed at x-axis and the other on the facet.
-With this design, potentially there are $^{N_C}P_2$ possible pairwise plots, where each plot would display pair of cyclic granularities.
-Now this is large and overwhelming for human consumption.
+Assuming a numeric response variable, the graphics display distributions compared across combinations of these cyclic granularities, one placed at x-axis and the other on the facet.
+With this design, potentially, there are $^{N_C}P_2$ possible pairwise plots, where each plot would display a pair of cyclic granularities.
+Now, this is large and overwhelming for human consumption.
 
 <!-- Scagnostics literature -->
-This is similar to Scagnostics (Scatterplot Diagnostics)[@mention-paper] which is used to discern meaningful patterns in large collections of scatterplots.
+This is similar to Scagnostics (Scatterplot Diagnostics)[@mention-paper], which is used to discern meaningful patterns in large collections of scatterplots.
 Given a set of $v$ variables, there are $v(v-1)/2$ pairs of variables, and thus the same number of possible pairwise scatterplots.
@@
 for even small $v$, the number of scatterplots can be
-large and scatterplot matrices (SPLOMs) could easily run out of pixels when presenting high-dimensional data.
-[@ScagExplorer], [@otherref] provides solution to this, where few characterizations helps us to locate anomalies for further analysis or search for
-similar distributions in a “large” SPLOM with more than a hundred dimensions.
+large, and scatterplot matrices (SPLOMs) could easily run out of pixels when presenting high-dimensional data.
+[@ScagExplorer], [@otherref] provides a solution to this, where few characterizations help us to locate anomalies for further analysis or search for
+similar distributions in a "large" SPLOM with more than a hundred dimensions.
 
 <!-- harmonies and why it is not enough -->
-The paper (gravitas) narrows down our search to harmonies and remove clashes without losing any perspectives about the data.
-But even after excluding clashes, the list of harmonies left could be large and overwhelming for human consumption.
-Hence, there is a need to rank the harmonies basis how well they capture the variation in the measured variable and additionally reduce the number of harmonies to include only those for which variation within different categories are significant.
+The paper (gravitas) narrows down our search to harmonies and removes clashes without losing any data perspectives.
+However, even after excluding clashes, the list of harmonies left could be extensive and overwhelming for human consumption.
+Hence, there is a need to rank the harmonies based on how well they capture the variation in the measured variable and reduce the number of harmonies to include only those for which variation within different categories is significant.
 
@@
 - To rank the selected harmonies from highest to lowest variation in the distribution of their categories.
-The idea here is to rate a harmony pair higher if this variation between different levels of the x-axis variable is higher on an average across all levels of facet variables.
+The idea here is to rate a harmony pair higher if this variation between different x-axis variable levels is higher on an average across all levels of facet variables.
 

### 2020-10-02 main.Rmd
introduction drafted without example

@@
 Take the example of the calendar display of electricity smart meter data used in @wang2020calendar for four households in Melbourne, Australia.
-The authors show how hour-of-the-day interact with weekday and weekends and then move on to use calendar display to display the daily schedules.
+The authors show how hour-of-the-day interact with weekday and weekends and then move on to use calendar display to show daily schedules.
 The calendar display has several components in it, which helps us look at energy consumption across hour-of-the-day, day-of-the-week, week-of-the-month, and month-of-the-year at once.
 Some interaction of these cyclic granularities[@our-paper] could also be interpreted from this display.
-However, certain things might be of concern.
-Due to the combination of linear and cyclic representation of time, it is not easy to comprehend the interaction of some periodicities' interaction from this display.
+This is a great start to have an overview of the energy consumption.
+However, if one wants to understand the periodicities in energy behavior and how the periodicities interact in greater details, it is not easy to comprehend the interactions of some periodicities' from this display, due to the combination of linear and cyclic representation of time.
 For example, this display might not be the best to understand how hour-of-the-day or month-of-year varies across week-of-the-month.
@@
 Let $N_C$ be the total number of contextual circular, quasi-circular and aperiodic cyclic granularities that can originate from the underlying periodic and aperiodic linear granularities.
-Assuming a numeric response variable, the graphics display distributions compared across combinations of these cyclic granularities, one placed at x-axis and the other on the facet.
-With this design, potentially, there are $^{N_C}P_2$ possible pairwise plots, where each plot would display a pair of cyclic granularities.
-Now, this is large and overwhelming for human consumption.
+The mapping of the graphical elements chosen in the paper implies that, for a numeric response variable, the graphics display distributions across combinations of cyclic granularities, one placed at x-axis and the other on the facet.
+That essentially implies there are $^{N_C}P_2$ possible pairwise plots exhaustively, where each plot would display a pair of cyclic granularities.
+This is large and overwhelming for human consumption.
 
@@
 large, and scatterplot matrices (SPLOMs) could easily run out of pixels when presenting high-dimensional data.
-[@ScagExplorer], [@otherref] provides a solution to this, where few characterizations help us to locate anomalies for further analysis or search for
-similar distributions in a "large" SPLOM with more than a hundred dimensions.
+[@ScagExplorer], [@otherref] provides a solution to this, where few characterizations help us to locate anomalies for further analysis or search for similar distributions in a "large" SPLOM with more than a hundred dimensions.
 
 <!-- harmonies and why it is not enough -->
-The paper (gravitas) narrows down our search to harmonies and removes clashes without losing any data perspectives.
-However, even after excluding clashes, the list of harmonies left could be extensive and overwhelming for human consumption.
-Hence, there is a need to rank the harmonies based on how well they capture the variation in the measured variable and reduce the number of harmonies to include only those for which variation within different categories is significant.
+The paper (gravitas) narrows down the search from $^{N_C}P_2$ plots by identifying pairs of granularities that can be meaningfully examined together (a "harmony"), or when they cannot (a "clash").
+However, even after excluding clashes, the list of harmonies left could be enormous for exhaustive exploration.
+Hence, there is a need to reduce the search even further by including only those harmonies for which variation within different categories is significant.
+Also, ranking the remaining harmonies based on how well they capture the variation in the measured variable could be potentially useful.
 
@@
 - To rank the selected harmonies from highest to lowest variation in the distribution of their categories.
-The idea here is to rate a harmony pair higher if this variation between different x-axis variable levels is higher on an average across all levels of facet variables.
+
+<!-- The idea here is to rate a harmony pair higher if this variation between different x-axis variable levels is higher on an average across all levels of facet variables. -->
 
@@
 
-Maximum pairwise distances are not robust to the number of levels and is higher for harmonies with higher levels.
-Thus these maximum pairwise distances need to be normalized for different harmonies in a way that eliminates the effect of different levels.
-The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.
+<!-- With increasing n, mean and sd of distribution of max increases. -->
 
-More formally, $d_{1},d_{2}\ldots ,d_{n}$ be a sequence of independent and identically-distributed pairwise distances and $M_{n}=\max\{d_{1},\ldots ,d_{n}\}$.
-Then Fisher–Tippett–Gnedenko theorem [@De_Haan2007-yx] suggests that if a sequence of pairs of real numbers $(a_{n}, b_{n})$ exists such that each $a_{n}>0$ and $\lim _{{m\to \infty }}P\left({\frac  {M_{n}-b_{n}}{a_{n}}}\leq x\right)=F(x)$, where $F$ is a non-degenerate distribution function, then the limit distribution $F$ belongs to either the Gumbel, Fréchet or Weibull family.
-The normalizing constants $(a_{n}, b_{n})$ vary depending on the underlying distribution of the pairwise distances.
-Hence to normalize appropriately, it is
-important to assume a distribution of these distances.
+<!-- FTP theorem works for large n -->
 
-### why normalize
+<!-- For small n resort to bootstrapping -->
 
@@
 We observe from the following graphs that our normalisation works after $n=6$, after which the difference in mean and standard deviation flattens out a lot.
+
+Maximum pairwise distances are not robust to the number of levels and is higher for harmonies with higher levels.
+Thus these maximum pairwise distances need to be normalized for different harmonies in a way that eliminates the effect of different levels.
+The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.
+
+More formally, $d_{1},d_{2}\ldots ,d_{n}$ be a sequence of independent and identically-distributed pairwise distances and $M_{n}=\max\{d_{1},\ldots ,d_{n}\}$.
+Then Fisher–Tippett–Gnedenko theorem [@De_Haan2007-yx] suggests that if a sequence of pairs of real numbers $(a_{n}, b_{n})$ exists such that each $a_{n}>0$ and $\lim _{{m\to \infty }}P\left({\frac  {M_{n}-b_{n}}{a_{n}}}\leq x\right)=F(x)$, where $F$ is a non-degenerate distribution function, then the limit distribution $F$ belongs to either the Gumbel, Fréchet or Weibull family.
+The normalizing constants $(a_{n}, b_{n})$ vary depending on the underlying distribution of the pairwise distances.
+Hence to normalize appropriately, it is
+important to assume a distribution of these distances.
+
+### why normalize
 

### 2020-10-07 hakear.Rmd
principle updated

---
title: Median Maximum Pairwise Distance
authors:
- name: Sayani Gupta
  affiliation: Department of Econometrics and Business Statistics, Monash University
  email: Sayani.Gupta@monash.edu

bibliography: bibliography.bib
output:
  bookdown::pdf_book:
    #base_format: rticles::asa_article
    fig_height: 5
    fig_width: 8
    fig_caption: yes
    dev: "pdf"
---

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
library(tidyverse)
library(lubridate)
library(lvplot)
library(ggridges)
library(viridis)
library(tsibble)
library(gravitas)
library(ggpubr)
library(readr)

opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
read_chunk('main.R')
read_chunk("null_distribution.R")
read_chunk("mean_null.R")
```

```{r external, include = FALSE}

```

```{r load}

```

```{r load_fun_1var}

```

```{r load_fun_2var}

```

```{r rank_harmony}

```

```{r global_threshold}

```

```{r}
set.seed(321)
```

# Introduction

<!-- background of the problem -->
Take the example of the calendar display of electricity smart meter data used in @wang2020calendar for four households in Melbourne, Australia. The authors show how hour-of-the-day interact with weekday and weekends and then move on to use calendar display to show daily schedules. The calendar display has several components in it, which helps us look at energy consumption across hour-of-the-day, day-of-the-week, week-of-the-month, and month-of-the-year at once.
Some interaction of these cyclic granularities[@our-paper] could also be interpreted from this display. This is a great start to have an overview of the energy consumption. However, if one wants to understand the periodicities in energy behavior and how the periodicities interact in greater details, it is not easy to comprehend the interactions of some periodicities' from this display, due to the combination of linear and cyclic representation of time. For example, this display might not be the best to understand how hour-of-the-day or month-of-year varies across week-of-the-month. Further, it is not clear what all interactions of cyclic granularities should be read from this display as there could be many combinations that one can look at. Moreover, calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions (@our-paper) and could include other cyclic granularities like hour-of-week or day-of-fortnight, which could potentially become useful depending on the context. Lastly, there might be specific interactions that are interesting and others that are not. It is immensely useful to make the transition from all possible ways to only ways that could potentially be important given a situation.

<!-- Take an example of a data set which are observed at fine temporal scales, like that of NYC bike usage available at https://www.citibikenyc.com/system-data. We use the `nyc_bikes` data set from the R package `tsibbledata` which takes a sample of 10 bikes for the year 2018. The `start_time` and the `stop_time` are recorded to a fineness of seconds. We can look at pair of cyclic granularities (hour_day, wknd_wday) or (week_month, day_week) to see how these periodicities interact. But there could be other pairs that are important too. How to understand which pairs are sufficient to explore given the data set without losing much information about the data. -->

<!-- When we need to understand the interplay of different periodicities in a high frequency temporal datasets, we have many choices to consider. In [@wang2019tsibble] and [@wang2020calendar], periodicities are explored across hour of the day and day of the week or months. But calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions. -->

<!-- what is the dimension of the problem -->
The paper (gravitas) describes how we can compute all possible combinations of cyclic time granularities. If we have $n$ periodic linear granularities in the hierarchy table, then $n(n-1)/2$ circular or quasi-circular cyclic granularities could be constructed. Let $N_C$ be the total number of contextual circular, quasi-circular and aperiodic cyclic granularities that can originate from the underlying periodic and aperiodic linear granularities. The mapping of the graphical elements chosen in the paper implies that, for a numeric response variable, the graphics display distributions across combinations of cyclic granularities, one placed at x-axis and the other on the facet. That essentially implies there are $^{N_C}P_2$ possible pairwise plots exhaustively, where each plot would display a pair of cyclic granularities. This is large and overwhelming for human consumption.

<!-- Scagnostics literature -->
This is similar to Scagnostics (Scatterplot Diagnostics)[@mention-paper], which is used to discern meaningful patterns in large collections of scatterplots. Given a set of $v$ variables, there are $v(v-1)/2$ pairs of variables, and thus the same number of possible pairwise scatterplots. Therefore
for even small $v$, the number of scatterplots can be
large, and scatterplot matrices (SPLOMs) could easily run out of pixels when presenting high-dimensional data. [@ScagExplorer], [@otherref] provides a solution to this, where few characterizations help us to locate anomalies for further analysis or search for similar distributions in a "large" SPLOM with more than a hundred dimensions.

<!-- harmonies and why it is not enough -->
The paper (gravitas) narrows down the search from $^{N_C}P_2$ plots by identifying pairs of granularities that can be meaningfully examined together (a "harmony"), or when they cannot (a "clash"). However, even after excluding clashes, the list of harmonies left could be enormous for exhaustive exploration. Hence, there is a need to reduce the search even further by including only those harmonies for which variation within different categories is significant. Also, ranking the remaining harmonies based on how well they capture the variation in the measured variable could be potentially useful.

Here, we have two main objectives:

- To choose harmonies for which distributions of categories are significantly different 
- To rank the selected harmonies from highest to lowest variation in the distribution of their categories.

<!-- Talk about Scagnostics: Tukey -->

# Building a new metric

## Rationale

Take the example of Gestalt theory suggests that when items are placed in close proximity, people assume that they are in the same group because they are close to one another and apart from other groups. Hence, displays that capture more variation within different categories in the same group would be important to bring out different patterns of the data. Thus the idea here is to rate a harmony pair higher if this variation between different levels of the x-axis variable is higher on an average across all levels of facet variables.

<!-- in the same group would be important to bring out different patterns of the data. -->
## Distance between distributions

<!-- One of the most important class of divergence is the f-divergence and includes measures like Kullback-Leibler divergence, Hellinger distance etc. The continuous version of f -divergence is given by -->
<!-- $$D_f(P||Q) := \int q(x)f(\frac{p(x)}{q(x)})$$, where -->
<!-- $f : [0,\infty) \rightarrow R \cup \{\infty\}$ is a continuous convex function, and $f(1) = 0$.  -->

The most common divergence measure between distributions is the Kullback-Leibler (KL) divergence[@Kullback1951-jy] introduced by Solomon Kullback and Richard Leibler in 1951. The KL divergence, denoted $D(p(x), q(x))$ is a non-symmetric measure of the difference between two probability distributions $p(x)$ and $q(x)$ and is interpreted as the amount of information lost when $q(x)$ is used to approximate $p(x)$. Although the KL divergence measures the “distance” between two distributions, it is not a distance measure since it is not symmetric and does not satisdy the triangle inequality. The Jensen-Shannon divergence [@Menendez1997-in] based on the Kullback-Leibler divergence is symmetric and it always has a finite value. The square root of the Jensen-Shannon divergence is a metric, often referred to as Jensen-Shannon distance. Other common measures of distance are Hellinger distance, total variation distance and Fisher information metric.

In the context of this paper, the pairwise distances between the distributions of the measured variable are computed through Jensen-Shannon distance (JSD) which is based on Kullback-Leibler divergence and is defined by,

$$JSD(P||Q) = \frac{1}{2}D(P||M) + \frac{1}{2}D(Q||M)$$
where $M = \frac{P+Q}{2}$ and 
$D(P||Q) := \int^\infty_{-\infty} p(x)f(\frac{p(x)}{q(x)})$ is the KL divergence between distributions $p(x)$ and $q(x)$. Probability distributions are estimated through quantiles instead of kernel density so that there is minimal dependency on selecting kernel or bandwidth.

<!-- The Jensen-Shanon distance between two probability distribution $p_1$ and $p_2$ is given by $$d = [D(p_1, r) + D(p_2, r)]/2 \quad where \quad r = (p_1 + p_2)/2$$ where, -->
<!-- $$D(p_1,p_2) = \int^{\infty}_{-\infty}p_1(x)log\frac{p_1(x)}{p_2(x)}\,dx$$ is the Kullback-Leibler divergence between $p_1$ and $p_2$.   -->

<!-- We call this measure of variation as  Median Maximum Pairwise Distances (MMPD). -->

# Distribution of Jensen-Shannon distances

Jensen-Shannon distances (JSD) are distributed as chi-squared with $m$ df where we discretize the continuous distribution with $m$ discrete values. Taking sample percentiles to approximate the integral would mean taking $m = 99$.
With large $m$, chi-squared is asymptotically normal by the CLT. Thus, by CLT, ${\chi^2}_{m} \tilde{} N(m, 2m)$, which would depend on the number of discretization used to approximate the continuous distribution. Then $b_n = 1-1/n$ quantile of the normal distribution and $a_n = 1/[n*\phi(b_n)]$ where $\phi$ is the normal density function. $n$ is the number of pairwise comparisons being made.

## Normalize distances

<!-- The harmony pairs could be arranged from highest to lowest average maximum pairwise distances across different levels of the harmonies. -->

<!-- With increasing n, mean and sd of distribution of max increases. -->

<!-- FTP theorem works for large n -->

<!-- For small n resort to bootstrapping -->

Suppose that $X_1$, $X_2$ , ... , $X_n$ are i.i.d. random variables with expected values $E(X_i) = \mu < \infty$ and variance $Var(X_i) = \sigma^2 < \infty$. Let 
$Y = max(X_1, X_2, \dots, X_n)$.

Let $F_X(x)$ be the common distribution of the variables $X_i$ and let $F_Y(y)$ be the corresponding distribution of $Y$. $F_Y(y)$ could be obtained from $F_X(x)$ simply by using:
$F_Y(y) = P[(X_1 \leq y)\cap(X_2 \leq y) \cap...\cap (X_n \leq y)] = {F_X(y)}^n$. For large $n$, the distribution of $Y$ approaches a standard shape, which does not depend on $F_X$. But what about the case when $n$ is not large enough? The distribution of maximum in that case will indeed depend on $n$ and the underlying distribution of $X$. If $F_X(x)$ is the CDF of $X$, then $F_Y(y) = {F_x(y)}^n$. Suppose $\Phi$ nd $\phi$ are the cdf and pdf of a standard normal distribution, then
$f_Y(y) = n{\Phi(y)}^{n-1}\phi(y)$, which depends on $n$. Hence, we are trying to normalise for $n$. Also, it depends on the underlying distribution of $X$, which we have assumed as normal in our case. As $n$ grows, we  can see the right tail growing, which implies that the probability that we will get a higher maximum is more. Now, for large $n$, we used EVT to normalise for $n$, that is, we brought them to the same scale without distorting the range of the distribution. But in our case, we will mostly have small $n$. It is important to ensure that they have the same mean and variation, for being able to compare the maximum value across $n$. We observe from the following graphs that our normalisation works after $n=6$, after which the difference in mean and standard deviation flattens out a lot.

Maximum pairwise distances are not robust to the number of levels and is higher for harmonies with higher levels. Thus these maximum pairwise distances need to be normalized for different harmonies in a way that eliminates the effect of different levels. The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.

More formally, $d_{1},d_{2}\ldots ,d_{n}$ be a sequence of independent and identically-distributed pairwise distances and $M_{n}=\max\{d_{1},\ldots ,d_{n}\}$. Then Fisher–Tippett–Gnedenko theorem [@De_Haan2007-yx] suggests that if a sequence of pairs of real numbers $(a_{n}, b_{n})$ exists such that each $a_{n}>0$ and $\lim _{{m\to \infty }}P\left({\frac  {M_{n}-b_{n}}{a_{n}}}\leq x\right)=F(x)$, where $F$ is a non-degenerate distribution function, then the limit distribution $F$ belongs to either the Gumbel, Fréchet or Weibull family. The normalizing constants $(a_{n}, b_{n})$ vary depending on the underlying distribution of the pairwise distances. Hence to normalize appropriately, it is 
important to assume a distribution of these distances.

### why normalize

```{r create_simdata}

```

```{r create_nlevels}

```

```{r norm_max_new}

```

## Mean and standard deviation of the distribution of maximum

```{r}
library(ggridges)
library(viridis)
max_all_data <- create_nlevels(nlevels = seq(2, 30, 2),
                           nsim = 500,
                           sim_dist = distributional::dist_normal(5, 10), create_fun = max)

g1 <- max_all_data %>% ggplot() + geom_density_ridges(aes(x=sim_data, y = as.factor(ind))) + ylab("n") + xlab("max")

median_all_data <- create_nlevels(nlevels = seq(2, 30, 2),
                           nsim = 500,
                           sim_dist = distributional::dist_normal(5, 10), create_fun = median)

g2 <- max_all_data %>% ggplot() + geom_boxplot(aes(x=sim_data, y = as.factor(ind)))  + ylab("n") + xlab("median")

ggpubr::ggarrange(g1, g2, ncol = 2)

```

## Distribution of distances

### Theoretical evidence

JS distances are distributed as chi-squared with $m$ df where we discretize the continuous distribution with $m$ discrete values. Taking sample percentiles to approximate the integral would mean taking $m = 99$.
With large $m$, chi-squared is asymptotically normal by the CLT. Thus, by CLT, ${\chi^2}_{m} \tilde{} N(m, 2m)$, which would depend on the number of discretization used to approximate the continuous distribution. Then $b_n = 1-1/n$ quantile of the normal distribution and $a_n = 1/[n*\phi(b_n)]$ where $\phi$ is the normal density function. $n$ is the number of pairwise comparisons being made.

### Empirical evidence

Distribution of JS distances is assumed to be normal but the mean and variance are estimated from the sample, rather than deducing it from the number of discretization used to approximate the continuous distribution. We look at different scenarios, where observations are collected from Normal, Exponential, Chi-squared and Gumbel distribution and found the distribution of JS distances are similar, irrespective of which distribution they are drawn from.

#### Initial distribution of observed variables shown in plot title

<!-- ```{r distv11} -->

<!-- ``` -->

<!-- ```{r distv12} -->

<!-- ``` -->

<!-- ```{r distv13} -->

<!-- ``` -->

<!-- ```{r distv14} -->

<!-- ``` -->

## Median Maximum Pairwise distance

### Definition

### Algorithm for computation for all harmony pairs

\noindent The algorithm employed for computing MMPD is summarized as follows:
<!-- Algorithm -->

<!-- 1. Suppose $C_i$ and $C_2$ are two cyclic granularities such that $C_i$ maps index set to a set $\{A_1, A_2, A_3, \dots, A_l$\}, and $C_2$ maps index set to a set $\{B_1, B_2, B_3, \dots, B_m$\} and $v$ is the measured variable. Hence for each combination ($A_k$, $B_l$), we have the time series variable $v_{ij} \subseteq v$, $\forall i = {1, 2, \dots, l}$ and $\forall j = {1, 2, \dots, m}$ -->

- **Input:** Data corresponding to all harmony pairs, i.e., data sets of the form $(C_i, C_j, v)$ 
$\forall i, j \in N_C$  
- **Output:** MMPD (Median Maximum Pairwise Distances) measuring the average variation across different levels of $C_i$ and $C_j$ $\forall i, j \in N_C$

1. Fix harmony pair $(C_i, C_j)$.

2. Fix $k$. Then there are $L$ groups corresponding to level $A_k$ of $C_i$.

3. Compute  $m = \binom{L}{2}$ pairwise distances between distributions of $L$ unordered levels and $m = L-1$ pairwise distances for $L$ ordered categories.

4. Identify maximum within the $m$ computed distances.

5. Compute normalized maximum distance ($NM$) using appropriate norming constants.
<!--so that the distribution of the normalized maximum converges to a Gumbel distribution as $m\rightarrow\infty$.-->

6. Use Steps 1-5 to compute normalized maximum distance for $\forall k \in  \{1, 2, \ldots, K\}$.

7. Compute MMPD = median $(NM_1, NM_2, \dots, NM_K)$/log($K$).

8. Repeat Steps 1 to 7 for all harmony pairs.

### Bounds

This is not correct becuase MMPD should be median of standardized Gumbel distribution. So no bound?

By @Lin1991-fj,
$$ 0 \leq JSD(P||Q) \leq ln(2)$$.

Thus,  $$ 0 \leq MMPD \leq \frac{ln(2)}{ln(k)}$$.
Now, by asumption $k \geq 2$ and hence,
<!-- \begin{equation} -->
<!-- For k = 2, $\frac{ln(2)}{ln(k)} = 1$  -->
<!-- \end{equation} -->
<!-- For $k > 2$, $\frac{ln(2)}{ln(k)}  <1$. -->

\[\frac{ln(2)}{ln(k)} : \left\{
  \begin{array}{lr}
    1 & if \ k = 2\\
    <1 & if \ k \ge 2
  \end{array}
\right.
\]

Thus, $$ 0 \leq MMPD \leq \ 1$$

# The statistical test

## Definition

### Algorithm for computation for all harmony pairs

**Assumption:** random permutation without considering ordering 
(global)

1. Given the data; $\{v_t: t=0, 1, 2, \dots, T-1\}$, the MMPD is computed and is represented by $MMPD_{obs}$.

2. From the original sequence a random permutation is obtained: $\{v_t^*: t=0, 1, 2, \dots, T-1\}$.

3. MMPD is computed for all random permutation of the data and is represented by $MMPD_{sample}$.

4.  Steps (2) and (3) are repeated a large number
of times M (e.g. 1000).

5. For each permutation, one $MMPD_{sample}$ value is obtained.

6. $95^{th}$ percentile of this $MMPD_{sample}$ distribution is computed and stored in $MMPD_{threshold}$.

7. If  $MMPD_{obs}> MMPD_{threshold}$, harmony pairs are accepted. Only one threshold for all harmony pairs.

Pros: Considering thresholds global for all harmony pairs would imply less computation time.

Cons: Only one threshold for all harmony pairs means we are assuming distribution of all harmonies pairs are similar, which might not be the case.But nevertheless, it is a good benchmark.

```{r, eval = FALSE, echo = FALSE}
smart_harmony <-read_rds("data/smart_harmony_nonst.rds")
smart_harmony
```

```{r smart_harmony,eval = FALSE, echo = FALSE}

sm <- smart_meter10 %>% dplyr::filter(customer_id %in% c("10017936"))

harmonies <- sm %>% 
  harmony(ugran = "month",
          filter_in = "wknd_wday",
          filter_out = c("hhour", "fortnight"))

harmony_tbl =  harmonies

smart_harmony <- sm %>% 
  rank_harmony(harmony_tbl = harmonies,
               response = "general_supply_kwh", 
               dist_ordered = TRUE)

smart_harmony %>% 
  mutate(MMPD = round(MMPD, 3), max_pd = round(max_pd, 3)) %>% 
  mutate(rankn = row_number()) %>%
  rename("rankun" = "r") %>% kable()
```

## Null distribution

### Normalised maximum distances follow standard Gumbel distribution

### Limiting distribution of median of normalised maximum distances is normal

Let a continuous population be given with cdf F(x) (cumulative distribution function) and median $\xi$ (assumed to exist uniquely). For a sample of size $2n + 1$, let $\tilde{x}$ denote the sample median. The distribution of $\tilde{x}$,under certain conditions, to be asymptotically normal with mean $\xi$ and variance $\sigma_n^2 = \frac{1}{4} [f(\xi)]^2(2n + 1)$, where $f(x) = F'(x)$ is the pdf (probability density function).

### Confidence interval of test statistic

## Simulation design

Behavior of the statistic - control simulation

 - To check if different distributions impact
(simulate with different distributions but same for all levels)

 - To check if x-levels and facets are normalised
(simulate with different distributions)
(simulate with different x and facet levels)

## Size and power

To estimate the sampling distribution of the test statistic we need many samples generated under the null hypothesis. If the null hypothesis is true, changing the exposure would have no effect on the outcome. By randomly shuffling the exposures we can make up as many data sets as we like. If the null hypothesis is true the shuffled data sets should look like the real data, otherwise they should look different from the
real data. The ranking of the real test statistic among the shuffled test statistics gives a p-value.

<!-- Consider two cyclic granularities $A$ and $B$ with $2$ and $3$categories. Thus, the harmony table consisting of all possible harmony pairs (assuming all pairs are harmonies), would look like the following: -->

```{r harmony_min}
# harmonies <- tibble::tibble(facet_variable = c("A", "B", "A", "C", "B", "C"),
#                             x_variable  = c("B","A", "C", "A", "C", "B"),
#                             facet_levels = c(2, 3, 2, 4, 3, 4),
#                             x_levels = c(3, 2, 4, 2, 4, 3))
# 
# harmonies <- tibble::tibble(facet_variable = c("A", "B"),
#                             x_variable  = c("B","A"),
#                             facet_levels = c(2, 3),
#                             x_levels = c(3, 2))
#                             
# harmonies %>% knitr::kable()
```

<!-- The output table has the value of MMPD (normalized median maximum pairwise distances), gt_MMPD(global threshold of MMPD indicator). -->

### Size: Simulated same distribution for all combinations of categories for all harmony pairs.

Failure to reject the null hypothesis when there is in fact no significant effect.

<!-- # ```{r samenull_2by4, eval = FALSE} -->
<!-- #  -->
<!-- # ``` -->

```{r normalv21_power}

```

```{r normalv22_power}

```

### Power: Simulated same distribution for all combinations of categories for all harmony pairs.

```{r normalv23_power}

```

```{r normalv24_power}

```

*Conclusion*: The test rejects the null hypothesis if distributions are different.

### Scenario 2: Simulated different distributions for all combinations of categories for harmony pairs for few levels.

```{r diffnull_2by4, eval = FALSE}

```

*Conclusion*: The test select the harmony pair for which distribution of x-axis categories are significantly different

### Scenario 3: Simulated different distributions for all combinations of categories for all harmony pairs with many levels.

```{r diffnull_7by11, eval = FALSE}
```

*Conclusion*: The test indicates that both harmony pairs do not have significant variation.

### Scenario 4: Simulated different distributions for all combinations of categories for all harmony pairs with many levels - very different distribution across x-axis

```{r diffnull_7by11normal, eval = FALSE}
```

*Conclusion*: The test indicates that only the first harmony pair has significant variation.

### Scenario 5: Simulated different distributions for all combinations of categories for all harmony pairs with many levels - very different distribution across facets

```{r diffnull_7by11normal2, eval = FALSE}
```

<!-- *Conclusion*:  -->

<!-- ## Scenario 4: Cumulative 3 levels with 2, 7 and 11 and testing level and power -->

<!-- ```{r samenull_3levels} -->

<!-- ``` -->

<!-- *Conclusion*: With 3 levels the test incorrectly chooses 1 harmony pair with similar distribution. The harmony pair which is displayed. -->

<!-- <!-- ```{r diffnull_3levels} --> -->

<!-- <!-- ``` --> -->

<!-- *Conclusion*: The test with MMPD selects just one pair, as opposed to the test with maximum. This needs to be checked against what we expect from the test. The harmony pairs which are selected (either through MMPD or maximum) are displayed. -->

<!-- # ```{r} -->
<!-- # harmonies <- tibble::tibble(facet_variable = c("A", "B"),x_variable  = c("B","A"), facet_levels = c(2, 3),x_levels = c(3, 2)) -->
<!-- #  -->
<!-- # har1 <- harmonies[1,] -->
<!-- #  -->
<!-- # sim_dist1 = c(rep(distributional::dist_normal(mu = 10, sigma = 5),2),rep(distributional::dist_exponential(10),2), rep(distributional::dist_weibull(0.5, 2),2)) -->
<!-- #  -->
<!-- # data1 <- sim_distharmony1(har1, sim_dist = sim_dist1) -->
<!-- # data1 -->
<!-- #  -->
<!-- # data1 %>% unnest(sim_dist) %>% -->
<!-- #   ggplot(aes(x = Var2, y = sim_dist)) + -->
<!-- #   facet_wrap(~Var1) + geom_boxplot() + ggtitle("Same distribution 2 by 3") -->
<!-- #  -->
<!-- # response = "sim_dist" -->
<!-- #  -->
<!-- # MMPD_distribution <- data1 %>% -->
<!-- #   select(-dist) %>%  -->
<!-- #   unnest(sim_dist) %>%  -->
<!-- #   list() %>%  -->
<!-- #   global_threshold(harmony_tbl = har1, -->
<!-- #                    response = "sim_dist", -->
<!-- #                    dist_distribution = "normal", -->
<!-- #                    dist_ordered = TRUE, -->
<!-- #                    create_gran_data = FALSE, nsamp = 20) -->
<!-- #  -->
<!-- # # as_tibble(sample_MMPD) %>% mutate(id = row_number()) %>%  -->
<!-- # #   ggplot() + geom_histogram(aes(x = value)) -->
<!-- #  -->
<!-- # ``` -->
<!-- #  -->

# Application

# Applications {#sec:application}

## Smart meter data of Australia {#sec:smartmeter}

<!-- # how data looks -->
Smart meters provide large quantities of measurements on energy usage for households across Australia. One of the customer trials [@smart-meter] conducted as part of the Smart Grid Smart City project in Newcastle, New South Wales and some parts of Sydney provides customer wise data on energy consumption for every half hour from February 2012 to March 2014. <!--It would be interesting to explore the energy consumption distribution for these customers and gain insights on their energy behavior which are lost either due to aggregation or looking only at coarser temporal units.-->The idea here is to show how to visualize the distribution of the energy consumption across different cyclic granularities in a systematic way to identify different behavioral patterns.

<!-- and identify the extreme and regular households. -->

<!-- ### Data structure for visualization: -->

<!-- The data structure for a sample of 50 households from that trial is depicted in \autoref{tab:smart-data} where the variable `reading_datetime`, `customer_id` and `general_supply_kwh` denote the index, key and measured variable of the tsibble. -->
<!-- <!-- We take a random sample of 50 households to see how we can achieve that.  -->

```{r smart-data}
# load("data/sm_cust50.Rdata")
#
# smart_data <- smart_meter <- sm_cust50 %>%
#   as_tsibble() %>%
#   dplyr::select(
#     customer_id,
#     reading_datetime,
#     general_supply_kwh
#   ) %>% head(n = 5)
#
#   knitr::kable(smart_data,
#                format = "latex",
#                booktabs = TRUE,
#                caption = "Smart meter data structure with electricity demand for 50 households from SGSC project for every 30 minutes from 2012 to 2014.")
```

<!--of the tsibble and represents the time variable. The variable denoting different households represent the key of the tsibble and is the time series variable which needs to be analyzed.Data sets of the form <$C1$, $C2$, `general_supply_kwh`> will form the basis of exploration for each key in the data set, where the cyclic granularity $C1$ would be mapped to $x$ axis and `general_supply_kwh` to $y$ axis with the cyclic granularity $C2$ mapped to facet. Any geometry displaying the probability distribution of `general_supply_kwh` like boxplot, letter value, violin,
ridge or highest density region plots can then be used to explore the data set.-->

### Cyclic granularities search and computation:

The tsibble object `smart_meter10` from R package `gravitas` [@R-gravitas] consisting of `reading_datetime`, `customer_id` and `general_supply_kwh` denoting the index, key and measured variable of the tsibble is used to facilitate the systematic exploration. While trying to explore the energy behavior of these customers systematically across cyclic time granularities, the first thing to consider is which cyclic time granularities we can look at exhaustively. Let us consider conventional time deconstructions for a Gregorian calendar (second, minute, half-hour, hour, day, week, month, year). Since the interval of this tsibble is 30 minutes, the temporal granularities may range from half-hour to year. Considering $6$ linear granularities half-hour, hour, day, week, month and year in the hierarchy table, $N_C = (6*5/2) = 15$. <!--(via Section \ref{sec:data-structure}) circular or quasi-circular granularities that could be formed relating two linear granularities at a time.--> If $N_C$ seem too large, the smallest and largest linear granularities could be considered to be removed from the hierarchy table. We remove half-year and year to have $N_C = (4*3/2) = 6$ and obtain cyclic granularities namely "hour_day", "hour_week", "hour_month", "day_week", "day_month" and "week_month", read as "hour of the day", etc. Further, we add cyclic granularity day-type( "wknd_wday") to capture weekend and weekday behavior. Now that we have a list of cyclic granularities to look at, we should be able to compute the multiple-order-up granularities using Section \ref{sec:cyclic-calendar}. <!-- The lubridate package [@Grolemund2011-vm] provides tools to compute single-order-up granularities, \ref{sec:circular-gran-def} (for hour_day, hour_week and day_week) and \ref{sec:quasi-circular-gran-def} (for hour_month, day_month, week_month).  
with the index set mapping half-hourly time periods to a set of positive integers.-->

<!-- R package **gravitas** [@R-gravitas] is used to facilitate the systematic exploration here. While trying to explore the energy behavior of these customers systematically across cyclic time granularities, the first thing we should have at our disposal is to know which all cyclic time granularities we can look at exhaustively. Let us consider conventional time deconstructions for a Gregorian calendar (second, minute, half-hour, hour, day, week, month, year). Since the interval of this tsibble is 30 minutes, the temporal granularities may range from half-hour to year. Considering $6$ linear granularities half-hour, hour, day, week, month, year, there could be $(6*5/2) = 15$ circular or quasi-circular granularities that could be formed. If these options are considered too many, the most coarse temporal unit can be set to a “month” and some intermediate temporal units which might not be pertinent to the analysis like hhour could be dropped. Then we will be left with six cyclic granularites namely "hour_day", "hour_week", "hour_month", "day_week", "day_month" and "week_month". Now that we have a list of cyclic granularities to look at, we should be able to compute the multiple-order-up granularities using Sections \ref{sec:cyclic-calendar}. <!-- The lubridate package [@Grolemund2011-vm] provides tools to compute single-order-up granularities, \ref{sec:circular-gran-def} (for hour_day, hour_week and day_week) and \ref{sec:quasi-circular-gran-def} (for hour_month, day_month, week_month).  -->
<!-- Here, the index set $Z=\{z: z \in \mathbb{Z}_{\geq 0}\}$ maps the half-hourly time instants to a set of positive integers. Then, multiple-order-up circular granularity $hour\_week$ and quasi-circular granularity $hour\_month$ could be computed from single-order-up granularities as follows: -->
<!-- <!-- $$ hour\_day(z) = \lfloor z/2 \rfloor \mod 7$$ (Definition \autoref{def:circular}) -->
<!-- \begin{align} -->
<!--   hour\_week(z) =  day\_week(z) + 24*hour\_day(z) -->
<!-- \end{align} -->

<!-- <!-- $$ day\_month(z) =   \lfloor z/2*24 \rfloor  - \sum_{w=0}^{k-1}\vert T_{w \mod 12*4} \vert$$ (\autoref{def:quasi-circular}) -->
<!-- \begin{align} -->
<!-- hour\_month(z) =  hour\_day(z) + 24*day\_month(z) -->
<!-- \end{align} -->

<!-- These cyclic granularities are a function of the index variable and are computed based on if they are circular <!--(Section \ref{sec:circular-gran-def}), quasi-circular. <!--(Section \ref{sec:quasi- circular-gran-def}) or aperiodic (Section \ref{sec:aperiodic-gran-def})-->

```{r search, echo=FALSE, eval = FALSE}
library(gravitas)
smart_meter %>%
  search_gran(filter_out = c("semester", 
                             "quarter",
                             "fortnight"))
```

<!-- #smart_smart_search <- smart_meter %>% search_gran() -->
<!-- #knitr::kable(smart_smart_search, format = "markdown") -->

<!-- CONTENT CUT -->
<!-- # ```{r search_limit1, echo=TRUE} -->
<!-- # smart_meter10 %>% -->
<!-- #   search_gran(highest_unit = "month") -->
<!-- # ``` -->

<!-- # smart_meter_limit1 <- smart_meter10 %>%  -->
<!-- #   search_gran(highest_unit = "month") -->
<!-- # knitr::kable(smart_meter_limit1, format = "markdown") -->

```{r search_gran_limit2, echo = FALSE, eval = FALSE}
smart_meter10 %>% search_gran(
  highest_unit = "month",
  filter_out = c("hhour", "fortnight"))%>%
  knitr::kable(format = "latex",
      booktabs = TRUE) %>%
  #row_spec(0, bold = TRUE)%>%
  kable_styling()
```

<!-- # smart_meter_limit2 <- smart_meter10 %>% search_gran(highest_unit = "month", -->
<!-- #                               filter_out = c("hhour", "fortnight") -->
<!-- # ) -->
<!-- # knitr::kable(smart_meter_limit2, format = "markdown") -->

<!-- Now that we have a list of cyclic granularities to look at, we should be able to compute them from the data using Sections \ref{sec:circular-gran-def}, \ref{sec:quasi-circular-gran-def} and \ref{sec:aperiodic-gran-def}. -->

### Screening and visualizing harmonies

From the search list, $N_C = 7$ cyclic granularities are chosen for which we would like to derive insights of energy behavior. Recalling the data structure <$C_i$, $C_j$, `general_supply_kwh`> for exploration $\forall i, j \in \{1, 2, \ldots, 7\}$, each of these $7$ cyclic granularities can either be mapped to x-axis or to facet. Choosing $2$ of the possible $7$ granularities, which is equivalent to having $^{7}P_2 = 42$ candidates for visualization. Fortunately, harmonies can be identified among those $42$ possibilities to narrow the search. \autoref{tab:harmony-tab} shows $16$ harmony pairs after removing clashes and any cyclic granularities with levels more than $31$, as effective  exploration becomes difficult with many levels (Section \ref{sec:levels}). The MMPD is also shown along with indicator (*) only when variation of measured variable across the harmony pair significant. Starting from $42$ possible pairs of cyclic granularities to visualize, we are finally left with only $6$, which is a very sizable number of displays for exploration.

Few harmony pairs are displayed in \autoref{fig:bothcust} to illustrate the siginificance of MMPD, threshold and the impact of different distribution plots and reverse mapping.
\noindent For each of \autoref{fig:bothcust} (b) and (c), $C_i$ is the circular granularity day-type (weekday/weekend) and $C_j$ is hour of the day. The geometry used for displaying the distribution is chosen as area-quantiles and violins in \autoref{fig:bothcust} (b and c respectively). \autoref{fig:bothcust} (a) displays reverse mapping of $C_i$ and $C_j$ with $C_i$ denoting hour of the day and $C_j$ denoting day-type with distribution geometrically displayed as boxplots.

<!-- From the search list, we found six cyclic granularities for which we would like to derive insights of energy behavior. Given the data structure <$C1$, $C2$, `general_supply_kwh`>, each of those six cyclic granularities can either be mapped to x-axis or to facet. Thus the problem is equivalent to taking 2 granularities at a time from six, which essentially is equivalent to having 30 data subsets for visualization. However, harmony/clash pairs can be identified among those 30 possibilities to determine feasibility of plotting any pairs together. \autoref{tab:harmony-tab} shows 13 harmonies pairs, each of which can be plotted together to look at the energy behavior from different perspectives. -->

<!-- We will look at few harmony pairs and see how the proposed workflow can be utilized.  -->

<!-- From the Gestalt theory with the same data  <$C1$ $C2$, `general_supply_kwh`>, mapping $C1$ on the x-axis vs facet might lead to different insights. -->

```{r harmony-tab, echo=FALSE, cache=TRUE}
# if(!dir.exists("cache/"))
# {
#   dir.create("cache")
# }
# if (!file.exists("cache/smart_harmony.rds")) {
  sm <- smart_meter10 %>%
  filter(customer_id %in% c(10017936))

  harmonies <- sm %>%
  harmony(ugran = "month",
          filter_in = "wknd_wday", 
          filter_out = c("hhour", "fortnight"))
set.seed(12345)

global_harmony <- sm %>%
  global_threshold(harmony_tbl = harmonies,
                   response = "general_supply_kwh", nsamp = 5) %>%
  rename(`facet variable` = facet_variable,
         `x-axis variable` = x_variable,
         `facet levels` = facet_levels,
         `x-axis levels` = x_levels) %>% 
  mutate(MMPD = if_else(gt_MMPD == TRUE,
                        paste0(MMPD, "*"), paste0(MMPD))) %>%
  select(`facet variable`,`x-axis variable`,
         `facet levels`,`x-axis levels` ,MMPD)

#   write_rds(smart_harmony,"cache/smart_harmony_ak.rds")
# }
#smart_harmony <- read_rds("cache/smart_harmony.rds")

  knitr::kable(global_harmony,
               format = "latex",
               booktabs = TRUE,
                caption = "Harmonies with a pair of cyclic granularity one placed on facet and the other on x-axis. Out of 42 possible combinations of cyclic granularities, only 16 are harmony pairs. The harmony pairs are ranked basis highest to lowest MMPD and only the first 6 show significant variation in the measured variable.") %>%
    #row_spec(0, bold = TRUE) %>%
    kable_styling()
```

<!-- # smart_meter10 %>% gran_advice("wknd_wday", "hour_day") -->

<!-- The median consumption or width of other bands doesn't vary much across seasons, implying extreme behavior or extreme customers does not vary across seasons much.  -->

<!-- No need to share the same for 50 customers - cut down text and anyway nothing much interesting is coming -->

<!-- ```{r wknd-wday50, fig.cap = "Quantile plot of energy consumption of 50 households across different hours of the day faceted by weekday and weekend. The quantiles are not different for weekdays and weekends implying either the behavior balances out among these customers or most of them do not behave differently for weekdays and weekends."} -->

<!-- smart_meter <-  -->
<!--   read_rds("data/sm_cust50.rds") -->

<!-- smart_meter %>%  -->
<!--   prob_plot("wknd_wday", -->
<!--                             "hour_day", -->
<!--                             response = "general_supply_kwh", -->
<!--                             plot_type = "quantile", -->
<!--             symmetric = FALSE,  -->
<!--             quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)) + -->
<!--   scale_y_sqrt() -->
<!-- ``` -->

<!-- # ```{r wknd-wday50_df} -->
<!-- # smart_meter10 %>%  -->
<!-- #   prob_plot("month_year", -->
<!-- #                             "day_fortnight", -->
<!-- #                             response = "general_supply_kwh", -->
<!-- #                             plot_type = "quantile", -->
<!-- #             symmetric = TRUE,  -->
<!-- #             quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)) + -->
<!-- #   scale_y_sqrt(breaks = c(0.1, 0.25, 0.5, 1:3)) -->
<!-- # ``` -->

<!-- ```{r my-hd, fig.cap="Area quantile plots of energy consumption across hours of the day faceted by months of the year. The black line is the median, whereas the pink band covers 25th to 75th percentile, the orange band covers 10th to 90th percentile and the green band covers 1st to 99th percentile. The median and quartile consumption increase in winter months, but extreme behavior represented by higher bands mostly stay the same across seasons. "} -->

<!-- library(gravitas) -->
<!-- library(tsibble) -->

<!-- library(ggplot2) -->
<!-- smart_meter %>% -->
<!--   prob_plot("month_year", "hour_day", -->
<!--     response = "general_supply_kwh", -->
<!--     plot_type = "quantile", -->
<!--     quantile_prob = c(0.01, 0.05, 0.1, 0.25, 0.5, 0.75, 0.9, 0.95, 0.99), -->
<!--     symmetric = TRUE) + -->
<!--   ggtitle("") + scale_y_sqrt(breaks = c(0.01, 0.1, 0.5, 1:3)) -->
<!-- ``` -->

<!-- Figure \ref{fig:dw-hd} shows that on morning peaks for Saturday and Sunday are higher and occurs in a later hour of the day compared to weekdays. This is true for both top 50% and 75% of the customers. Hence, this is indicative of the fact that at least 50% of the households in this subset has traditional work days (Mon-Fri) and weekends(Sat-Sun). All the percentiles peaks up in the morning hours and then drops in the afternoon, before again peaking up in the evening.  -->

<!-- ```{r dw-hd} -->

<!-- # Hourly usage across days of the week -->
<!-- sm_cust50 %>% -->
<!--   prob_plot("day_week",  -->
<!--            "hour_day", -->
<!--            "general_supply_kwh",  -->
<!--            plot_type = "quantile",  -->
<!--           quantile_prob = c(0.25, 0.5, 0.75), -->
<!--            response = "general_supply_kwh", overlay = FALSE) + -->
<!--   ggtitle("") -->

<!-- ``` -->

<!-- on half-hourly energy usage and detailed information on appliance use, climate, retail and distributor product offers, and other related factors.  -->

<!-- typical and extreme behaviors of 50 households from that trial.  -->

<!-- , and indeed many parts of the world. Households are distributed geographically and have different demographic properties such as the existence of solar panels, central heating or air conditioning. The behavioral patterns in households vary substantially, for example, some families use a dryer for their clothes while others hang them on a line, and some households might consist of night owls, while others are morning larks.  -->

<!-- <!-- Existing approaches, why we need to drill down, or why we want to -- probability distributions -->
<!-- It is common to see aggregates of usage across households, total kwh used each half-hour by state, for example, because energy companies need to understand maximum loads that they will have to plan ahead to accommodate. But studying overall energy use hides the distributions of usage at finer scales, and making it more difficult to find solutions to improve energy efficiency.  -->

<!-- We want to look at the distribution of energy across coarser temporal granularities and then deep dive into finer temporal granularities. -->

<!-- In Figure \ref{fig:day-fortnight} and \ref{fig:day-fortnight-agg} , the smart meter data is filtered for two customers to illustrate what kinds of insights can be drawn for the energy behavior of these two customers. -->

<!-- can be added later -->

<!-- In Figure \ref{fig:day-fortnight},to illustrate what kinds of insights can be drawn for the energy behavior of these two customers. it can be seen that for most days of the fortnight, the second household has much less consumption than the first one. However, there is additional information that we can derive looking at the distribution. If we consider letter value F as a regular behavior and letter values beyond F as not-so-regular behavior, we can conclude that the regular behavior of the first household is more stable than the second household. However, the distribution of tail of the first household is more variable, observed through distinct letter values, implying that their not-so-regular behavior is quite extreme. This shows, how looking at the distribution of the dependent variable can throw more light on the energy behavior of the customers, which are lost using aggregate or summary statistics.  -->

<!-- # ```{r day-fortnight_agg, echo = FALSE} -->
<!-- # library(lvplot) -->
<!-- # library(ggplot2) -->
<!-- # library(dplyr) -->
<!-- # library(tibble) -->
<!-- # library(gravitas) -->
<!-- # library(tidyr) -->
<!-- # smart_meter10 %>%  -->
<!-- #   filter(customer_id %in% c(10006704, 10017936)) %>%  -->
<!-- #   create_gran("day_fortnight") %>% -->
<!-- #   as_tibble() %>%  -->
<!-- #   group_by(customer_id, day_fortnight) %>%  -->
<!-- #   summarize(median= log(median(general_supply_kwh)), -->
<!-- #             total = log(sum(general_supply_kwh))) %>%  -->
<!-- #   gather("daily_consumption", "value", - c(customer_id, day_fortnight)) %>%  -->
<!-- #   ggplot2::ggplot(aes( -->
<!-- #     x = as.factor(day_fortnight), -->
<!-- #     y = value,  -->
<!-- #     color = daily_consumption, -->
<!-- #     group = daily_consumption)) + -->
<!-- #   geom_line() + -->
<!-- #   xlab("day_fortnight") + -->
<!-- #   ylab("general_supply_kwh") +  -->
<!-- #   facet_wrap(~customer_id) +  -->
<!-- #   theme_bw()  -->

<!-- # smart_meter10 %>%  -->
<!-- #   filter(customer_id %in% c(10006704, 10017936)) %>%  -->
<!-- #   create_gran("day_fortnight") %>% -->
<!-- #   as_tibble() %>%  -->
<!-- #   group_by(customer_id, day_fortnight) %>%  -->
<!-- #   summarize(median_consumption= median(general_supply_kwh)) %>% -->
<!-- #   ggplot2::ggplot(aes( -->
<!-- #     x = as.factor(day_fortnight), -->
<!-- #     y = median_consumption, -->
<!-- #     color =  customer_id, -->
<!-- #     group = customer_id)) + -->
<!-- #   geom_line() + -->
<!-- #   xlab("day_fortnight") + -->
<!-- #   ylab("general_supply_kwh") +  -->
<!-- #   theme_bw()  -->
<!-- ``` -->

<!-- ```{r day-fortnight, fig.cap="Letter value plot of two households across days of the fortnight. M, F, E, D and C represents the letter values of energy consumption. Regular behavior (within letter value F) is more variable for the 2nd household, whereas extreme behavior (beyond letter value F) is varying more for the first household."} -->
<!-- library(lvplot) -->
<!-- library(ggplot2) -->
<!-- library(dplyr) -->
<!-- library(tibble) -->
<!-- library(gravitas) -->
<!-- smart_meter10 %>% -->
<!--   filter(customer_id %in% c(10006704, 10017936)) %>%  -->
<!--   create_gran("day_fortnight") %>% -->
<!--   ggplot2::ggplot(aes( -->
<!--     x = as.factor(day_fortnight), -->
<!--     y = general_supply_kwh)) + -->
<!--   xlab("day_fortnight") + -->
<!--   geom_lv( -->
<!--     outlier.colour = "red", -->
<!--     aes(fill = ..LV..), -->
<!--     k = 5) + -->
<!--   facet_wrap(~customer_id) +  -->
<!--   scale_fill_lv() + -->
<!--   theme_bw() + -->
<!--   scale_y_sqrt()  -->
<!-- ``` -->

<!-- Figure \autoref{fig:my-hd} shows the overlay quantile plot of energy consumption of 50 households. The black line is the median, whereas the pink band covers 25th to 75th percentile, the orange band covers 10th to 90th percentile and the green band covers 1st to 99th percentile. Each facet represents a month and energy consumption across each hours of the day is shown inside each facet. It can be observed that the median is very close (and hence not distinctly visible) to the lower boundaries of all the other bands implying energy consumption for these households are extremely left skewed.75% of the households has distinct higher evening peaks compared to morning peaks, especially in the winter months. The top 5% households behave very differently than even the top 10% households in terms of total energy consumption across hours of the day.  -->

<!-- # ```{r is_harmony, echo= TRUE} -->
<!-- # smart_meter10 %>%  -->
<!-- #   is_harmony(gran1 = "hour_day",  -->
<!-- #              gran2 = "day_week") -->
<!-- #  -->
<!-- # smart_meter10 %>% -->
<!-- #   is_harmony(gran1 = "hour_day",  -->
<!-- #              gran2 = "day_week",  -->
<!-- #              facet_h = 14) -->
<!-- #  -->
<!-- # smart_meter10 %>%  -->
<!-- #   is_harmony(gran1 = "day_month", -->
<!-- #              gran2 = "week_month") -->
<!-- # ``` -->

<!-- Boxplot of energy consumption is shown across `wknd_wday` (facet) and `hour_day` (x-axis) for the same two households. For the first household, the shape of the distribution does not change significantly for weekdays and weekends. The distribution is roughly smooth with a morning and an evening peak. -->

In \autoref{fig:bothcust} (b), <!--the distribution of energy consumption is plotted across the harmony pair (weekday/weekend, hour of the day) through an area quantile plot-->the black line is the median, whereas the purple band covers 25th to 75th percentile, the orange band covers 10th to 90th percentile and the green band covers 1st to 99th percentile. The first facet represents the weekday behavior while the second one displays the weekend behavior and energy consumption across each hours of the day is shown inside each facet. The energy consumption is extremely (positive- or right-) skewed with the 1st, 10th and 25th percentile lying relatively close whereas 75th, 90th and 99th lying further away from each other. This is common across both weekdays and weekends. For the first few hours on weekdays, median energy consumption starts and continues to be higher for longer as compared to weekends.

Consider looking at violin plots instead of quantile plots to look at the same data in \autoref{fig:bothcust}(c). There is additional information that we can derive looking at the distribution. There is bimodality in the early hours of the day, implying both low and high energy consumption is probable in the early hours of the day both for weekdays and weekends. <!--Also the hours from 7 to 13 look most volatile.--> If we visualize the same data with reverse mapping of the cyclic granularities, then the natural tendency would be to compare weekend and weekday behavior within each hour and not across hours. For example in \autoref{fig:bothcust}(a), it can be seen that median energy consumption for the early morning hours is extremely high for weekdays compared to weekends. Also, outliers are more prominent in the latter part of the day. All of these indicate that looking at different distribution geometry or changing the mapping might shed lights on different aspect of the energy behavior for the same sample population.

<!-- If we consider letter value F as a regular behavior and letter values beyond F as not-so-regular behavior, we can conclude that the regular behavior of the first household is more stable than the second household. However, the distribution of tail of the first household is more variable, observed through distinct letter values, implying that their not-so-regular behavior is quite extreme. This shows, how looking at the distribution of the dependent variable can throw more light on the energy behavior of the customers, which are lost using aggregate or summary statistics. -->

```{r bothcust, fig.cap = "Energy consumption of a single customer shown with different distribution displays, and granularity arrangements. Two granularities are used: hour of the day (I) and weekday/weekend (II). Plot (a) shows granularity I facetted by granularity II, and plots (b), (c) shows the converse mapping. Plot (a) makes a comparison of usage by workday within each hour of the day using side-by-side boxplots. Generally, on a work day there is more consumption early in the day.  Plots (b) and (c) examine the temporal trend of consumption over the course of a day, separately for the type of day. Plot (b) uses an area quantile to put the emphasis on the time series, for example, the median consumption over time shows prolonged usage in the morning on weekdays. Plot (c) uses a violin plot to place emphasis on distributional differences across hours. It can be seen that the morning use on weekdays is bimodal, some work days there is low usage, which might indicate the person is working from home and also having a late start.", out.width="90%"}

# plot for only customer is shown
# cust1 <- smart_meter10 %>%
# filter(customer_id %in% c(10006704)) %>%
#   prob_plot("wknd_wday",
#                             "hour_day",
#                             response = "general_supply_kwh",
#                             plot_type = "quantile",
#             symmetric = FALSE,
#             quantile_prob = c(0.25, 0.5, 0.75, 0.9))
#   scale_y_sqrt() +
#   ggtitle("Energy consumption distribution for customer id: 10006704")
cust2_quantile <- smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("wknd_wday",
    "hour_day",
    response = "general_supply_kwh",
    plot_type = "quantile",
    symmetric = TRUE,
    quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)
  ) +
  scale_y_sqrt() +
  #ggtitle(" (b) Area quantile plot faceted by weekend-weekday") +
  ylab("electricity demand [KWh]") + xlab("hours of the day") + ggtitle("") + ylab("")+ 
  theme_minimal()
#
# smart_meter10 %>%
#   filter(customer_id %in% c(10006704)) %>%
#   prob_plot("wknd_wday",
#                             "hour_day",
#                             response = "general_supply_kwh",
#                             plot_type = "violin") +
#   scale_y_sqrt() +
#   ggtitle("Energy consumption distribution for customer id: 10006704")

cust2_violin <- smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("wknd_wday",
    "hour_day",
    response = "general_supply_kwh",
    plot_type = "violin"
  ) +
  scale_y_sqrt()+
  #ggtitle(" (c) Violin plot faceted by weekend-weekday") +
  ylab("") + xlab("hours of the day") + ggtitle("") +
  scale_x_discrete( breaks = seq(0, 23, 5))+ 
  theme_minimal()

cust2_box <- smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("hour_day",
    "wknd_wday",
    response = "general_supply_kwh",
    plot_type = "boxplot"
  ) +
  scale_y_sqrt() +
  #ggtitle(" (a) Box plot faceted by hour-of-day") +
  xlab("") +
  ggtitle("") + ylab("") +
  scale_x_discrete(labels = c('wday','wend')) +
  ggplot2::theme(axis.text.x = element_text(size = 7))+ 
  theme_minimal()

#ggarrange(cust2_quantile, cust2_violin, nrow = 2)

gg_fig <- ggarrange(cust2_box,
          ggarrange(cust2_quantile, cust2_violin, nrow = 2, labels = c("b", "c")),
          ncol = 2, labels = "a")
          #label.y = "electricity demand [KWh]"\

ggpubr::annotate_figure(gg_fig,
                left = text_grob("electricity demand [KWh]",  rot = 90))
```

<!-- # ```{r cust-ridge, fig.cap ="Boxplot of energy consumption across hours of the day faceted by weekday/weekend for customer id: 10017936. The change in mapping of the cyclic granularities leads to easier comparison within weekdays and weekends for each hour. Median consumption till 6am is higher for weekends compared to weekdays although the quartiles look similar. Outliers appear more during the end of the day implying more uncertain behavior in latter hours of the day compared to early morning hours."} -->
<!-- #  -->
<!-- # smart_meter10 %>% -->
<!-- #   filter(customer_id %in% c(10017936)) %>% -->
<!-- #   prob_plot("hour_day", -->
<!-- #     "wknd_wday", -->
<!-- #     response = "general_supply_kwh", -->
<!-- #     plot_type = "boxplot" -->
<!-- #   ) + -->
<!-- #   scale_y_sqrt() -->
<!-- # ``` -->

<!-- Now, we would like to see how these customers' behavior relate to the rest of the 50 households across these two measures -   -->

<!-- - if energy distribution is skewed towards extreme? -->

<!-- - if the weekend and weekday behavior are different for most of these households? -->

If the data for all keys are visualized together, it might lead to Simpson's paradox, which occurs when one observation shows a particular behavior, but this behavior paradoxically becomes obscured by aggregation. For example in a particular neighborhood one household may have the least daily power consumption for a full week, yet still not be the household with the minimum weekly power consumption. This is an intuitive possibility, because heterogeneous `customer_id`'s with very different occupation or demographics will tend to have very different energy behavior and combining them together will somehow weaken any typical or extreme behavior. A strategy for analyzing multiple keys together could be to first group them basis time series or demographic features and then look at their energy behavior. This is beyond the scope of the current work.

<!-- For the purpose of this paper, the smart meter data is filtered for two customers to illustrate kinds of insights that can be drawn after proceeding with the systematic exploration. -->

<!-- For example, Figure \ref{fig:wknd-wday50} shows the quantile plot of energy consumption of a sample of 50 households. Quantiles for weekends and weekdays for these customers look exactly the same. It is not clear if the behaviors of most of these customers do not alter between weekdays and weekends or looking at all customers together balances out the behaviors. Consider another example in Figure \ref{fig:my-hd} showing the area quantile plots of 50 customers. The median is very close to the lower boundaries of all the other bands implying energy consumption for these households are left skewed. The pink band changes significantly in winter months (May - August) implying that much of the behavioral changes occur in the quartiles, that too in peak hours of the day. It is to be noted here that the the level of all quantiles increased too in winter months (increased energy usage in weather conditions), the interesting part is to notice that the relationship between bands other than quartile stayed same across seasons. -->

This case study shows systematic exploration of energy behavior for a household to gain exhaustive insights on periodic behavior of the households. 
<!--First, it helps us to find the list of cyclic granularities to look at, then shrinks the number of possible visualizations by identifying harmonies, visualize a harmony pair and shows the effect of different distribution plots or reverse mapping.-->

## T20 cricket data of Indian Premiere League {#sec:cricket}

The method is not only restricted to temporal data, and can be generalized to many hierarchical granularities (with  continuous and uni-directional nature). We illustrate this with an application to the sport cricket. Although there is no conventional time component in cricket, each ball can be thought to represent an ordering from past to future with the game progressing forward with each ball. In the Twenty20 format, an over will consist of 6 balls (with some exceptions), an inning is restricted to a maximum of 20 overs, a match will consist of 2 innings and a season consists of several matches. Thus, similar to time, there is a hierarchy where ball is nested within overs, overs nested within innings and innings within matches. The idea of cyclic granularities can be likewise mapped to this hierarchy. Example granularites then include ball of the over, over of the inning and ball of the inning. Although most of these cyclic granularities are circular in design of the hierarchy, in application of the rules some granularities are aperiodic. For example, in most cases an over will consist of 6 balls with some exceptions like wide balls or when an inning finishes before the over finishes. Thus, the cyclic granularity ball-of-over will be circular in most cases and aperiodic in others.

<!-- However, irrespective of the type of cyclic granularities, it can be interesting to visualize the distribution of a measured variable across these cyclic granularities to throw light on the periodic behavior of a non-temporal data set similar to any temporal data set. -->

The Indian Premier League (IPL) is a professional Twenty20 cricket league in India contested by eight teams representing eight different cities in India. The ball by ball data for IPL season 2008 to 2016 is fetched from [Kaggle](https://www.kaggle.com/josephgpinto/ipl-data-analysis/data). The `cricket` data set in the `gravitas` package summarizes the ball-by-ball data across overs and contains information for a sample of 214 matches spanning 9 seasons (2008 to 2016) such that each over has 6 balls, each inning has 20 overs and each match has 2 innings. This could be useful in a periodic world when we wish to compute any circular/quasi-circular granularity based on a hierarchy table which look like \autoref{tab:hierarchy-cric}.

```{r hierarchy-cric}
library(gravitas)
library(tibble)
hierarchy_model <- tibble::tibble(
  `linear (G)` = c("over", "inning", "match", "season"),
  `single-order-up cyclic (C)` = c("over-of-inning", "inning-of-match", "match-of-season", 1),
  `period length/conversion operator (K)` = c(20, 2, "k(match, season)", 1)
)
knitr::kable(hierarchy_model,
             format = "latex",
             booktabs = TRUE,
             caption = "Hierarchy table for cricket where overs are nested within an inning, innings nested within a match and matches within a season.") %>%
  #row_spec(0, bold = TRUE)%>%
  kable_styling()
```

However, even if the situation is not periodic and a similar hierarchy can not be formed, it can be interesting to visualize the distribution of a measured variable across relevant cyclic granularities to shed light on the aperiodic behavior of a non-temporal data set similar to aperiodic events like formal meetings, workshops, conferences, school semesters in a temporal set up. There are many interesting questions that could possibly be answered with such a data set irrespective of the type of cyclic granularities. <!--We will explore a few interesting questions and understand how the proposed approach in the paper can help answer some of the questions.-->

<!-- the two teams have a single innings each, which is restricted to a maximum of 20 overs. Hence, in this format of cricket, a match will consist of 2 innings, an innings will consist of 20 overs, an over will consist of 6 balls with some exceptions. -->

<!-- ```{r hierarchy, echo=FALSE} -->
<!-- hierarchy_model <- tibble::tibble(linear gran = c("ball", "over", "inning", "match"),  -->
<!--                                   convert_fct = c(6, 20, 2, 1)) -->
<!-- knitr::kable(hierarchy_model, caption = " A hierarchy table for T20 cricket") -->
<!-- ``` -->

<!-- Each team is given a two-and-a-half-minute "strategic timeout" during each innings; one must be taken by the bowling team between the ends of the 6th and 9th overs, and one by the batting team between the ends of the 13th and 16th overs. -->

<!-- Suppose, we are interested to see how the distribution of scores vary from the start to the end of the game. Let us brainstorm some of the questions that might help us comprehend that. -->

<!-- a) What is the most common pattern for batting and bowling teams across balls, overs, innings and matches? Which are the teams which are typical and which are exceptions? -->

<!-- How the scores per over vary across granularities/categorizations like innings of a match or matches of a season? Are these different for the winning teams in that season and the teams that couldn't qualify for the playoffs? -->

<!-- Is the outcome of the game dependent on who bats first? Do some teams have more chance to win if they are batting in the first innings? -->

<!-- We will look at the ball by ball data for all batting teams. Since we want a periodic world, where each over consists of 6 balls and each match consists of two innings, we shall filter out the matches or overs for which that is not true. Also, we look at runs per over as that would have more variability compared to runs per ball and it be easier to observe the strategies of the winning team through that.  -->

<!-- Making it short -->

<!-- First, we look at the distribution of runs (measured variable) across over-of-inning (circular granularity) and match-of-season (aperiodic cyclic granularity) in \autoref{fig:seas-over-inning}. The distribution of runs per over has not significantly changed from 2008 to 2016. There is no clear pattern/trend that runs per over is increasing or decreasing across seasons. Hence, we work with subsets of seasons to answer some of the questions: -->

First, it would be interesting to see if the distribution of total runs vary depending on if a team bats in the first or second innings. The Mumbai Indians (MI) and Chennai Super kings (CSK) <!--are considered one of the best teams in IPL with multiple winning titles and --> appeared in final playoffs from 2010 to 2015. We take their example in order to dive deeper into this question. <!--Circular granularities "over-of-inning" and "inning-of-match" can be computed using \ref{sec:circular-gran-def} with over as index of the tsibble.--> From Figure \ref{fig:cricex}(a), it can be observed that for the team batting in the first inning there is an upward trend of runs per over, while there is no clear upward trend in median and quartile deviation of runs for the teams batting in the second inning. This seem to indicate that players feel mounting pressure to score more runs as they approach towards the end of the first inning. Whereas teams batting in the second inning have a set target in mind and are not subjected to such mounting pressure and may adopt a more conservative strategy, to score runs. Thus winning teams like CSK and MI seem to employ different inning strategies when it comes to their batting order.

<!-- Also longer and more distinct letter values in the second innings suggests that the variability is more in the second innings. -->
<!-- - Q1: How their run rates vary depending on if they bat first or 2nd? Is there a chance that they are more likely to win if they bat first? -->

<!-- - Q2: Which team is more consistent in their approach in terms of run rate across different overs of the innings? -->

<!-- # ```{r seas-over-inning, fig.cap = "Quantile plot of runs per over across overs of different seasons. There is no pattern on increase or decrease of runs across overs for seasons."} -->
<!-- #   cricket_tsibble_all %>%  -->
<!-- #   prob_plot("over",  -->
<!-- #             "season", -->
<!-- #             hierarchy_model, -->
<!-- #             response = "runs_per_over", -->
<!-- #             plot_type = "quantile", -->
<!-- #             quantile_prob = c(0.25, 0.5, 0.75),  -->
<!-- #             symmetric = FALSE)  + -->
<!-- #      theme( # remove the vertical grid lines -->
<!-- #             panel.grid.major.x = element_blank() , -->
<!-- #             # explicitly set the horizontal lines (or they will disappear too) -->
<!-- #             panel.grid.major.y = element_blank()) + scale_x_discrete(breaks = seq(2008, 2016, 3)) -->
<!-- # ``` -->

Another interesting question could be: do runs per over decrease in the subsequent over if fielding (defending) was good in the previous over? For establishing the fielding quality, we apply an indicator function on dismissals (1 if there was at least one wicket in the previous over due to run out or catch, 0 otherwise). Runs in the current over is then the observation variable.  <!--If a batsman is bowled out, it does not necessarily signify good fielding. So we only include number of catches and run out in an over as a measure of good fielding.
Difference in runs across overs are likely to be negative if good fielding has an impact on the runs scored in the subsequent overs. --> Dismissals in the previous over can lead to a batsman adopting a more defensive play style. Figure \ref{fig:cricex}(b) shows that no dismissals in the previous over leads to a higher median and quartile spread of runs per over as compared to the case when there has been at least one dismissal in the previous over.

<!-- Difference in runs across over should be negative if good fielding has an impact on the runs scored in the subsequent overs.  -->

<!-- fetching raw data since dot and fielding information not available in dismissal type not available in cricket data gravitas. Also `cricket` is aggregated across overs -->

```{r cricex, fig.cap= "Runs per over shown with different distribution displays, and granularities. Plot (a) shows letter value plot across overs faceted by innings. For the team batting in the first innings there is an upward trend of runs per over, while there is no such pattern of runs for the teams batting in the second innings. Plot (b) shows quantile plot of runs per over across an indicator of wickets in previous over faceted by current over. This indicates that at least one wicket in the previous over leads to lower median run rate and quartile spread in the subsequent over.", warning = FALSE, message = FALSE, out.width = "90%"}

library(tsibble)
cricket_tsibble <- cricket %>%
  mutate(data_index = row_number()) %>%
  as_tsibble(index = data_index)

hierarchy_model <- tibble::tibble(
  units = c("index", "over", "inning", "match"),
  convert_fct = c(1, 20, 2, 1)
)

cricket_tsibble %>%
  filter(batting_team %in% c(
    "Mumbai Indians",
    "Chennai Super Kings"
  )) %>%
  mutate(inning = paste0("innings: ", inning)) %>%
  prob_plot("inning",
    "over",
    response = "runs_per_over",
    hierarchy_model,
    plot_type = "lv"
  ) +
  scale_fill_brewer(palette = "Dark2") +
  #ggtitle("(a) Runs per over across over faceted by inning") +
  theme(legend.position = "right") +
  ggtitle("a") +
  ylab("runs per over") +
  xlab("overs of the innings") +
  theme(plot.title = element_text(face = "bold")) +
  ggplot2::theme(
       strip.text = ggplot2::element_text(
        size = 10,
         margin = ggplot2::margin(b=0, t=0)
      )
     ) +  theme_minimal() 
#geom_smooth(aes( x = over,
#                               y=runs_per_over), method = lm, #formula = y ~ splines::bs(x, 3), se = FALSE)

library(tsibble)

cricket_all <- read_csv("data-raw/deliveries_all.csv")
matches_all <- read_csv("data-raw/matches_all.csv")

cricket_season <- cricket_all %>% left_join(matches_all, by = c("match_id" = "id"))

# cricket_per_over <- cricket_season %>%
#   group_by(season,
#            match_id,
#            batting_team,
#            bowling_team,
#            inning,
#            over) %>%
#   summarise(runs_per_over = sum(total_runs),
#             run_rate = sum(total_runs)/length(total_runs))
#
# cricket_tsibble_all <- cricket_per_over %>%
#   ungroup() %>%
#   mutate(data_index = row_number()) %>%
#   as_tsibble(index = data_index)

cricket_dot_field <- cricket_season %>%
  mutate(
    fielding_proxy = if_else(dismissal_kind %in%
      c("caught", "caught and bowled"), 1, 0),
    dot_ball_proxy = if_else(total_runs == 0, 1, 0),
    wicket_proxy = if_else(is.na(dismissal_kind), 0, 1)
  ) %>%
  group_by(
    season,
    match_id,
    batting_team,
    bowling_team,
    inning,
    over
  ) %>%
  summarise(
    runs_per_over = sum(total_runs),
    run_rate = sum(total_runs)*6 / length(total_runs),
    fielding_wckts = sum(fielding_proxy),
    dot_balls = sum(dot_ball_proxy)
  ) %>%
  mutate(diff_run_rate = c(0, diff(run_rate)))

cricket_tsibble <- cricket_dot_field %>%
  ungroup() %>%
  mutate(data_index = row_number()) %>%
  as_tsibble(index = data_index)

cricket_data <- cricket_tsibble %>%
  mutate(
    field = if_else(fielding_wckts == 0, "0", "1+"),
    dot = if_else(dot_balls == 0, "no dot balls", ">0 dot balls"),
    lag_field = lag(field),
    lag_dot = lag(dot)
  ) %>%
  filter(lag_field != 0, lag_dot != 0)

cricket_data$lag_field <- factor(cricket_data$field, levels = c("0", "1+"))

# filter(fielding_wckts %in% c(0,1)) %>%
#
 cricket_data %>%
  filter(over!=1) %>%
  prob_plot("over", "lag_field",
  hierarchy_model,
  response = "run_rate",
  plot_type = "quantile",
  symmetric = FALSE,
 quantile_prob = c(0.25, 0.5, 0.75)) +
   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") +
  ylab("runs per over")  +
  xlab("number of wickets in previous over") +
  ggtitle("b") +
   theme(plot.title = element_text(face = "bold")) +
        theme(axis.ticks = element_blank(), legend.background = element_blank(),
            legend.key = element_blank(), panel.background = element_blank(), strip.background = element_blank(),
            plot.background = element_blank(), complete = TRUE, panel.grid.major = element_line(colour = "#E0E0E0"),
            panel.border = element_rect(colour = "#E0E0E0", fill = NA))
```

<!-- Q2: Among good fielding and bowling - which affect the runs of the subsequent overs more? -->

<!-- Q3: Are runs set to reduce in the next over for dot balls in the previous over? -->

<!-- A dot ball is a delivery bowled without any runs scored off it. The number of dot balls is reflective of the quality of bowling in the game. Run rate of an over should ideally decrease if the number of dot balls increase. However, what is the effect of dot balls on runs scored in the subsequent over. Will players batsman likely to go for big shots because they couldn't score good runs in the previous over? Or they should play consistently and avoid scoring high? Figure \ref{fig:exdot} shows the quantile plot of runs across overs for at least one dot ball per over (facet 1) or no dot balls per over (facet 2). -->
<!-- With at least one dot balls per over, the distribution of run rates in facet 1 increase slower compared to that in facet 2. This implies that run rates are likely to decrease in the subsequent over as a result of dot balls in the previous over. -->

<!-- ```{r exdot, fig.cap="25th, 50th, 75th quantiles of runs per over are drawn across overs of the innings with no (facet 2), more than zero (facet 1) dot balls per over. For all quantiles, run rates mostly increase at a higher rate in facet 2 compared to facet 1 implying run rates decrease with at least one dot ball in the previous over.", fig.pos="ht"} -->

<!-- cricket_data %>% -->
<!--   # filter(dot_balls %in% c(0, 1, 2)) %>% -->
<!--   prob_plot("lag_dot", -->
<!--     "over", -->
<!--     hierarchy_model, -->
<!--     response = "run_rate", -->
<!--     plot_type = "quantile", -->
<!--     quantile_prob = c(0.25, 0.5, 0.75), -->
<!--     symmetric = FALSE -->
<!--   ) + ggtitle("") -->
<!-- ``` -->

Wickets per over are considered as an aperiodic cyclic granularity with wickets as an aperiodic linear granularity. These granularities do not appear in the hierarchy table since it is difficult to position them in a hierarchy. These are similar to holidays or special events in temporal data.
<!-- CONTENT CUT -->
<!--While any special event that corresponds to a time domain can be treated as an aperiodic linear granularity in a temporal case, dot balls or wickets that corresponds to certain balls (index) could be treated as aperiodic events in cricket.-->

# Summary and discussion

### 2020-10-07 main.Rmd
principle updated

@@
 library(readr)
+library(kableExtra)
 
@@
 read_chunk("mean_null.R")
+source("R/sim_panel.R")
+
 ```
@@
 
-<!-- in the same group would be important to bring out different patterns of the data. -->
-
 Here, we have two main objectives:
@@
 
-<!-- The idea here is to rate a harmony pair higher if this variation between different x-axis variable levels is higher on an average across all levels of facet variables. -->
-
 <!-- Talk about Scagnostics: Tukey -->
 
-# Computing distance measure
+# Building a new metric
 
+## Principle
+
+The principle employed for building a new metric is explained through a simple example explained in Figure \ref{fig:null4by2}.
+Each of these figures have the same panel design with 2 x-axis categories and 4 facet levels.
+Figure \ref{fig:null4by2}a has all x categories drawn from N(5, 10) distribution for each facet.
+It is not an interesting display particularly, as distributions do not vary across x-axis or facet categories.
+Figure \ref{fig:null4by2}b has x categories drawn from the same distribution within a facet and different for different facet categories.
+Figure \ref{fig:null4by2}b exhibits an exact opposite situation where distribution between the x-axis categories within each facet is different but they are same across facets.
+Figure \ref{fig:null4by2}d takes a step further by varying the distribution across both facet and x-axis categories.
+If we are asked to rank the displays in order of importance from minimum to maximum, we might order it as a, b, c and then d.
+It might be argued that it is not clear if b should precede or succeed c.
+Gestalt theory suggests that when items are placed in close proximity, people assume that they are in the same group because they are close to one another and apart from other groups.
+Hence, displays that capture more variation within different categories in the same group would be important to bring out different patterns of the data.
+With this principle, display b could be considered less informative as compared to display c.
+
+With reference to the graphical design in \ref{@paper-gravitas}, therefore the idea would be to rate a harmony pair higher if the variation between different levels of the x-axis variable is higher on an average across all levels of facet variables.
+
+<!-- To elaborate further, look at the examples in Figure \ref{}, where Figure \ref{}a represents the panel design with distribution of each x categories drawn from N(5, 10) distribution.
+It could be observed that the graph is not particularly interesting, as there is no significant change in distribution between x-axis levels or facets.
+Figure \ref{}b represents the same panel design with no difference in distribution of x-axis categories within a facet, but different distribution of x-axis categories for different facets.
+For example, if there are 4 facet levels and 2 x-axis levels, data is generated in the way as described in Table \ref{}.
+Figure \ref{}b exhibits an exact opposite situation where the x-axis within facets are different but not across facets.
+-->
+<!-- Figure \ref{}d takes it futher by varying the distribution across both facet and x-axis categories. -->
+
+```{r null4by2,fig.cap=" A graphical display with two categories mapped to x-axis and 4 categories mapped to facets with the distribution of a continuous random variable plotted on the y-axis.
+Display a is not interesting as the distribution of the continuous rv does not depend across x-axis or facet categories.
+Display b and c are more interesting than a since there is a change in distribution either across facets(b) or x-axis(a).
+Display d is most interesting as distribution of the rv changes across both facet and x-axis variable."}
+
+p1 <- sim_panel(nx = 2, nfacet = 3, ntimes = 500) %>%
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
+
+simulated_data <- sim_panel(nx = 2,
+          nfacet = 3,
+          ntimes = 500,
+          sim_dist = rep(dist_normal(seq(5, 15, 5), 5), each = 2))
+
+p2 <- simulated_data %>% ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
+
+p3 <- simulated_data %>% ggplot(aes(x = as.factor(id_facet), y = sim_data)) + facet_wrap(~id_x) + geom_boxplot()
+
+p4 <- sim_panel(nx = 2,
+          nfacet = 3,
+          ntimes = 500,
+          sim_dist = dist_normal(seq(5,30, 5), 5)) %>% 
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
+
+ggpubr::ggarrange(p1, p2, p3, p4, nrow = 2, ncol = 2,
+                  common.legend = TRUE,
+                  labels = c("a", "b", "c", "d"))
+
+```
+
+<!-- in the same group would be important to bring out different patterns of the data. -->
 ## Distance between distributions
@@
 
-The most common divergence measure between distributions is the Kullback-Leibler (KL) divergence introduced by Solomon Kullback and Richard Leibler in 1951.
+The most common divergence measure between distributions is the Kullback-Leibler (KL) divergence[@Kullback1951-jy] introduced by Solomon Kullback and Richard Leibler in 1951.
 The KL divergence, denoted $D(p(x), q(x))$ is a non-symmetric measure of the difference between two probability distributions $p(x)$ and $q(x)$ and is interpreted as the amount of information lost when $q(x)$ is used to approximate $p(x)$.
-Although the KL divergence measures the “distance” between two distributions, it is not a distance measure since it is not symmetric.
-The Jensen-Shannon divergence based on the Kullback-Leibler divergence is symmetric and it always has a finite value.
+Although the KL divergence measures the “distance” between two distributions, it is not a distance measure since it is not symmetric and does not satisfy the triangle inequality.
+The Jensen-Shannon divergence [@Menendez1997-in] based on the Kullback-Leibler divergence is symmetric and it always has a finite value.
 The square root of the Jensen-Shannon divergence is a metric, often referred to as Jensen-Shannon distance.
@@
 
-In the context of this paper, the pairwise distances between the distributions of the measured variable are computed through Jensen-Shannon distance which is based on Kullback-Leibler divergence and is defined by,
+In the context of this paper, the pairwise distances between the distributions of the measured variable are computed through Jensen-Shannon distance (JSD) which is based on Kullback-Leibler divergence and is defined by,
 
@@
 <!-- We call this measure of variation as  Median Maximum Pairwise Distances (MMPD). -->
+
+# Distribution of Jensen-Shannon distances
+
+Jensen-Shannon distances (JSD) are distributed as chi-squared with $m$ df where we discretize the continuous distribution with $m$ discrete values.
+Taking sample percentiles to approximate the integral would mean taking $m = 99$.
+With large $m$, chi-squared is asymptotically normal by the CLT.
+Thus, by CLT, ${\chi^2}_{m} \tilde{} N(m, 2m)$, which would depend on the number of discretization used to approximate the continuous distribution.
+Then $b_n = 1-1/n$ quantile of the normal distribution and $a_n = 1/[n*\phi(b_n)]$ where $\phi$ is the normal density function.
+$n$ is the number of pairwise comparisons being made.
 
@@
 
-This is not correct becuase MMPD should be median of standardized Gumbel distribution. So no bound?
+This is not correct because MMPD should be median of standardized Gumbel distribution. So no bound?
 
@@
 Thus,  $$ 0 \leq MMPD \leq \frac{ln(2)}{ln(k)}$$.
-Now, by asumption $k \geq 2$ and hence,
+Now, by assumption $k \geq 2$ and hence,
 <!-- \begin{equation} -->
@@
 
- - To check if x-levels are normalised
+ - To check if x-levels and facets are normalized
 (simulate with different distributions)
-(simulate with different x-levels)
-
- - To check if facet-levels are normalised
-(simulate with different distributions)
-(simulate with different facet-levels for fixed x-levels)
+(simulate with different x and facet levels)
 
@@
 
-# Application
+# Applications {#sec:application}
+
+## Smart meter data of Australia {#sec:smartmeter}
+
+<!-- # how data looks -->
+Smart meters provide large quantities of measurements on energy usage for households across Australia.
+One of the customer trials [@smart-meter] conducted as part of the Smart Grid Smart City project in Newcastle, New South Wales and some parts of Sydney provides customer wise data on energy consumption for every half hour from February 2012 to March 2014.
+<!--It would be interesting to explore the energy consumption distribution for these customers and gain insights on their energy behavior which are lost either due to aggregation or looking only at coarser temporal units.-->The idea here is to show how to visualize the distribution of the energy consumption across different cyclic granularities in a systematic way to identify different behavioral patterns.
+
+<!-- and identify the extreme and regular households. -->
+
+<!-- ### Data structure for visualization: -->
+
+<!-- The data structure for a sample of 50 households from that trial is depicted in \autoref{tab:smart-data} where the variable `reading_datetime`, `customer_id` and `general_supply_kwh` denote the index, key and measured variable of the tsibble.
+-->
+<!-- <!-- We take a random sample of 50 households to see how we can achieve that.  -->
+
+```{r smart-data}
+# load("data/sm_cust50.Rdata")
+#
+# smart_data <- smart_meter <- sm_cust50 %>%
+#   as_tsibble() %>%
+#   dplyr::select(
+#     customer_id,
+#     reading_datetime,
+#     general_supply_kwh
+#   ) %>% head(n = 5)
+#
+#   knitr::kable(smart_data,
+#                format = "latex",
+#                booktabs = TRUE,
+#                caption = "Smart meter data structure with electricity demand for 50 households from SGSC project for every 30 minutes from 2012 to 2014.")
+```
+
+<!--of the tsibble and represents the time variable.
+The variable denoting different households represent the key of the tsibble and is the time series variable which needs to be analyzed.Data sets of the form <$C1$, $C2$, `general_supply_kwh`> will form the basis of exploration for each key in the data set, where the cyclic granularity $C1$ would be mapped to $x$ axis and `general_supply_kwh` to $y$ axis with the cyclic granularity $C2$ mapped to facet.
+Any geometry displaying the probability distribution of `general_supply_kwh` like boxplot, letter value, violin,
+ridge or highest density region plots can then be used to explore the data set.-->
+
+### Cyclic granularities search and computation:
+
+The tsibble object `smart_meter10` from R package `gravitas` [@R-gravitas] consisting of `reading_datetime`, `customer_id` and `general_supply_kwh` denoting the index, key and measured variable of the tsibble is used to facilitate the systematic exploration.
+While trying to explore the energy behavior of these customers systematically across cyclic time granularities, the first thing to consider is which cyclic time granularities we can look at exhaustively.
+Let us consider conventional time deconstructions for a Gregorian calendar (second, minute, half-hour, hour, day, week, month, year).
+Since the interval of this tsibble is 30 minutes, the temporal granularities may range from half-hour to year.
+Considering $6$ linear granularities half-hour, hour, day, week, month and year in the hierarchy table, $N_C = (6*5/2) = 15$.
+<!--(via Section \ref{sec:data-structure}) circular or quasi-circular granularities that could be formed relating two linear granularities at a time.--> If $N_C$ seem too large, the smallest and largest linear granularities could be considered to be removed from the hierarchy table.
+We remove half-year and year to have $N_C = (4*3/2) = 6$ and obtain cyclic granularities namely "hour_day", "hour_week", "hour_month", "day_week", "day_month" and "week_month", read as "hour of the day", etc.
+Further, we add cyclic granularity day-type( "wknd_wday") to capture weekend and weekday behavior.
+Now that we have a list of cyclic granularities to look at, we should be able to compute the multiple-order-up granularities using Section \ref{sec:cyclic-calendar}.
+<!-- The lubridate package [@Grolemund2011-vm] provides tools to compute single-order-up granularities, \ref{sec:circular-gran-def} (for hour_day, hour_week and day_week) and \ref{sec:quasi-circular-gran-def} (for hour_month, day_month, week_month).
+with the index set mapping half-hourly time periods to a set of positive integers.-->
+
+<!-- R package **gravitas** [@R-gravitas] is used to facilitate the systematic exploration here.
+While trying to explore the energy behavior of these customers systematically across cyclic time granularities, the first thing we should have at our disposal is to know which all cyclic time granularities we can look at exhaustively.
+Let us consider conventional time deconstructions for a Gregorian calendar (second, minute, half-hour, hour, day, week, month, year).
+Since the interval of this tsibble is 30 minutes, the temporal granularities may range from half-hour to year.
+Considering $6$ linear granularities half-hour, hour, day, week, month, year, there could be $(6*5/2) = 15$ circular or quasi-circular granularities that could be formed.
+If these options are considered too many, the most coarse temporal unit can be set to a “month” and some intermediate temporal units which might not be pertinent to the analysis like hhour could be dropped.
+Then we will be left with six cyclic granularites namely "hour_day", "hour_week", "hour_month", "day_week", "day_month" and "week_month".
+Now that we have a list of cyclic granularities to look at, we should be able to compute the multiple-order-up granularities using Sections \ref{sec:cyclic-calendar}.
+<!-- The lubridate package [@Grolemund2011-vm] provides tools to compute single-order-up granularities, \ref{sec:circular-gran-def} (for hour_day, hour_week and day_week) and \ref{sec:quasi-circular-gran-def} (for hour_month, day_month, week_month).
+-->
+<!-- Here, the index set $Z=\{z: z \in \mathbb{Z}_{\geq 0}\}$ maps the half-hourly time instants to a set of positive integers.
+Then, multiple-order-up circular granularity $hour\_week$ and quasi-circular granularity $hour\_month$ could be computed from single-order-up granularities as follows: -->
+<!-- <!-- $$ hour\_day(z) = \lfloor z/2 \rfloor \mod 7$$ (Definition \autoref{def:circular}) -->
+<!-- \begin{align} -->
+<!--   hour\_week(z) =  day\_week(z) + 24*hour\_day(z) -->
+<!-- \end{align} -->
+
+<!-- <!-- $$ day\_month(z) =   \lfloor z/2*24 \rfloor  - \sum_{w=0}^{k-1}\vert T_{w \mod 12*4} \vert$$ (\autoref{def:quasi-circular}) -->
+<!-- \begin{align} -->
+<!-- hour\_month(z) =  hour\_day(z) + 24*day\_month(z) -->
+<!-- \end{align} -->
+
+<!-- These cyclic granularities are a function of the index variable and are computed based on if they are circular <!--(Section \ref{sec:circular-gran-def}), quasi-circular.
+<!--(Section \ref{sec:quasi- circular-gran-def}) or aperiodic (Section \ref{sec:aperiodic-gran-def})-->
+
+```{r search, echo=FALSE, eval = FALSE}
+library(gravitas)
+smart_meter %>%
+  search_gran(filter_out = c("semester", 
+                             "quarter",
+                             "fortnight"))
+```
+
+<!-- #smart_smart_search <- smart_meter %>% search_gran() -->
+<!-- #knitr::kable(smart_smart_search, format = "markdown") -->
+
+<!-- CONTENT CUT -->
+<!-- # ```{r search_limit1, echo=TRUE} -->
+<!-- # smart_meter10 %>% -->
+<!-- #   search_gran(highest_unit = "month") -->
+<!-- # ``` -->
+
+<!-- # smart_meter_limit1 <- smart_meter10 %>%  -->
+<!-- #   search_gran(highest_unit = "month") -->
+<!-- # knitr::kable(smart_meter_limit1, format = "markdown") -->
+
+```{r search_gran_limit2, echo = FALSE, eval = FALSE}
+smart_meter10 %>% search_gran(
+  highest_unit = "month",
+  filter_out = c("hhour", "fortnight"))%>%
+  knitr::kable(format = "latex",
+      booktabs = TRUE) %>%
+  #row_spec(0, bold = TRUE)%>%
+  kable_styling()
+```
+
+<!-- # smart_meter_limit2 <- smart_meter10 %>% search_gran(highest_unit = "month", -->
+<!-- #                               filter_out = c("hhour", "fortnight") -->
+<!-- # ) -->
+<!-- # knitr::kable(smart_meter_limit2, format = "markdown") -->
+
+<!-- Now that we have a list of cyclic granularities to look at, we should be able to compute them from the data using Sections \ref{sec:circular-gran-def}, \ref{sec:quasi-circular-gran-def} and \ref{sec:aperiodic-gran-def}.
+-->
+
+### Screening and visualizing harmonies
+
+From the search list, $N_C = 7$ cyclic granularities are chosen for which we would like to derive insights of energy behavior.
+Recalling the data structure <$C_i$, $C_j$, `general_supply_kwh`> for exploration $\forall i, j \in \{1, 2, \ldots, 7\}$, each of these $7$ cyclic granularities can either be mapped to x-axis or to facet.
+Choosing $2$ of the possible $7$ granularities, which is equivalent to having $^{7}P_2 = 42$ candidates for visualization.
+Fortunately, harmonies can be identified among those $42$ possibilities to narrow the search.
+\autoref{tab:harmony-tab} shows $16$ harmony pairs after removing clashes and any cyclic granularities with levels more than $31$, as effective  exploration becomes difficult with many levels (Section \ref{sec:levels}).
+The MMPD is also shown along with indicator (*) only when variation of measured variable across the harmony pair significant.
+Starting from $42$ possible pairs of cyclic granularities to visualize, we are finally left with only $6$, which is a very sizable number of displays for exploration.
+
+Few harmony pairs are displayed in \autoref{fig:bothcust} to illustrate the siginificance of MMPD, threshold and the impact of different distribution plots and reverse mapping.
+\noindent For each of \autoref{fig:bothcust} (b) and (c), $C_i$ is the circular granularity day-type (weekday/weekend) and $C_j$ is hour of the day.
+The geometry used for displaying the distribution is chosen as area-quantiles and violins in \autoref{fig:bothcust} (b and c respectively).
+\autoref{fig:bothcust} (a) displays reverse mapping of $C_i$ and $C_j$ with $C_i$ denoting hour of the day and $C_j$ denoting day-type with distribution geometrically displayed as boxplots.
+
+<!-- From the search list, we found six cyclic granularities for which we would like to derive insights of energy behavior.
+Given the data structure <$C1$, $C2$, `general_supply_kwh`>, each of those six cyclic granularities can either be mapped to x-axis or to facet.
+Thus the problem is equivalent to taking 2 granularities at a time from six, which essentially is equivalent to having 30 data subsets for visualization.
+However, harmony/clash pairs can be identified among those 30 possibilities to determine feasibility of plotting any pairs together.
+\autoref{tab:harmony-tab} shows 13 harmonies pairs, each of which can be plotted together to look at the energy behavior from different perspectives.
+-->
+
+<!-- We will look at few harmony pairs and see how the proposed workflow can be utilized.  -->
+
+<!-- From the Gestalt theory with the same data  <$C1$ $C2$, `general_supply_kwh`>, mapping $C1$ on the x-axis vs facet might lead to different insights. -->
+
+```{r harmony-tab, echo=FALSE, eval = FALSE, cache=TRUE}
+# if(!dir.exists("cache/"))
+# {
+#   dir.create("cache")
+# }
+# 
+# if (!file.exists("cache/smart_harmony.rds")) {
+  sm <- smart_meter10 %>%
+  filter(customer_id %in% c(10017936))
+
+  harmonies <- sm %>%
+  harmony(ugran = "month",
+          filter_in = "wknd_wday", 
+          filter_out = c("hhour", "fortnight"))
+set.seed(12345)
+
+global_harmony <- sm %>%
+  global_threshold(harmony_tbl = harmonies,
+                   response = "general_supply_kwh", nsamp = 5) %>%
+  rename(`facet variable` = facet_variable,
+         `x-axis variable` = x_variable,
+         `facet levels` = facet_levels,
+         `x-axis levels` = x_levels) %>% 
+  mutate(MMPD = if_else(gt_MMPD == TRUE,
+                        paste0(MMPD, "*"), paste0(MMPD))) %>%
+  select(`facet variable`,`x-axis variable`,
+         `facet levels`,`x-axis levels` ,MMPD)
+
+#   write_rds(smart_harmony,"cache/smart_harmony_ak.rds")
+# }
+#smart_harmony <- read_rds("cache/smart_harmony.rds")
+
+  knitr::kable(global_harmony,
+               format = "latex",
+               booktabs = TRUE,
+                caption = "Harmonies with a pair of cyclic granularity one placed on facet and the other on x-axis.
+Out of 42 possible combinations of cyclic granularities, only 16 are harmony pairs.
+The harmony pairs are ranked basis highest to lowest MMPD and only the first 6 show significant variation in the measured variable.") %>%
+    #row_spec(0, bold = TRUE) %>%
+    kable_styling()
+```
+
+<!-- # smart_meter10 %>% gran_advice("wknd_wday", "hour_day") -->
+
+<!-- The median consumption or width of other bands doesn't vary much across seasons, implying extreme behavior or extreme customers does not vary across seasons much.  -->
+
+<!-- No need to share the same for 50 customers - cut down text and anyway nothing much interesting is coming -->
+
+<!-- ```{r wknd-wday50, fig.cap = "Quantile plot of energy consumption of 50 households across different hours of the day faceted by weekday and weekend.
+The quantiles are not different for weekdays and weekends implying either the behavior balances out among these customers or most of them do not behave differently for weekdays and weekends."} -->
+
+<!-- smart_meter <-  -->
+<!--   read_rds("data/sm_cust50.rds") -->
+
+<!-- smart_meter %>%  -->
+<!--   prob_plot("wknd_wday", -->
+<!--                             "hour_day", -->
+<!--                             response = "general_supply_kwh", -->
+<!--                             plot_type = "quantile", -->
+<!--             symmetric = FALSE,  -->
+<!--             quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)) + -->
+<!--   scale_y_sqrt() -->
+<!-- ``` -->
+
+<!-- # ```{r wknd-wday50_df} -->
+<!-- # smart_meter10 %>%  -->
+<!-- #   prob_plot("month_year", -->
+<!-- #                             "day_fortnight", -->
+<!-- #                             response = "general_supply_kwh", -->
+<!-- #                             plot_type = "quantile", -->
+<!-- #             symmetric = TRUE,  -->
+<!-- #             quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)) + -->
+<!-- #   scale_y_sqrt(breaks = c(0.1, 0.25, 0.5, 1:3)) -->
+<!-- # ``` -->
+
+<!-- ```{r my-hd, fig.cap="Area quantile plots of energy consumption across hours of the day faceted by months of the year.
+The black line is the median, whereas the pink band covers 25th to 75th percentile, the orange band covers 10th to 90th percentile and the green band covers 1st to 99th percentile.
+The median and quartile consumption increase in winter months, but extreme behavior represented by higher bands mostly stay the same across seasons.
+"} -->
+
+<!-- library(gravitas) -->
+<!-- library(tsibble) -->
+
+<!-- library(ggplot2) -->
+<!-- smart_meter %>% -->
+<!--   prob_plot("month_year", "hour_day", -->
+<!--     response = "general_supply_kwh", -->
+<!--     plot_type = "quantile", -->
+<!--     quantile_prob = c(0.01, 0.05, 0.1, 0.25, 0.5, 0.75, 0.9, 0.95, 0.99), -->
+<!--     symmetric = TRUE) + -->
+<!--   ggtitle("") + scale_y_sqrt(breaks = c(0.01, 0.1, 0.5, 1:3)) -->
+<!-- ``` -->
+
+<!-- Figure \ref{fig:dw-hd} shows that on morning peaks for Saturday and Sunday are higher and occurs in a later hour of the day compared to weekdays.
+This is true for both top 50% and 75% of the customers.
+Hence, this is indicative of the fact that at least 50% of the households in this subset has traditional work days (Mon-Fri) and weekends(Sat-Sun).
+All the percentiles peaks up in the morning hours and then drops in the afternoon, before again peaking up in the evening.
+-->
+
+<!-- ```{r dw-hd} -->
+
+<!-- # Hourly usage across days of the week -->
+<!-- sm_cust50 %>% -->
+<!--   prob_plot("day_week",  -->
+<!--            "hour_day", -->
+<!--            "general_supply_kwh",  -->
+<!--            plot_type = "quantile",  -->
+<!--           quantile_prob = c(0.25, 0.5, 0.75), -->
+<!--            response = "general_supply_kwh", overlay = FALSE) + -->
+<!--   ggtitle("") -->
+
+<!-- ``` -->
+
+<!-- on half-hourly energy usage and detailed information on appliance use, climate, retail and distributor product offers, and other related factors.  -->
+
+<!-- typical and extreme behaviors of 50 households from that trial.  -->
+
+<!-- , and indeed many parts of the world.
+Households are distributed geographically and have different demographic properties such as the existence of solar panels, central heating or air conditioning.
+The behavioral patterns in households vary substantially, for example, some families use a dryer for their clothes while others hang them on a line, and some households might consist of night owls, while others are morning larks.
+-->
+
+<!-- <!-- Existing approaches, why we need to drill down, or why we want to -- probability distributions -->
+<!-- It is common to see aggregates of usage across households, total kwh used each half-hour by state, for example, because energy companies need to understand maximum loads that they will have to plan ahead to accommodate.
+But studying overall energy use hides the distributions of usage at finer scales, and making it more difficult to find solutions to improve energy efficiency.
+-->
+
+<!-- We want to look at the distribution of energy across coarser temporal granularities and then deep dive into finer temporal granularities. -->
+
+<!-- In Figure \ref{fig:day-fortnight} and \ref{fig:day-fortnight-agg} , the smart meter data is filtered for two customers to illustrate what kinds of insights can be drawn for the energy behavior of these two customers.
+-->
+
+<!-- can be added later -->
+
+<!-- In Figure \ref{fig:day-fortnight},to illustrate what kinds of insights can be drawn for the energy behavior of these two customers.
+it can be seen that for most days of the fortnight, the second household has much less consumption than the first one.
+However, there is additional information that we can derive looking at the distribution.
+If we consider letter value F as a regular behavior and letter values beyond F as not-so-regular behavior, we can conclude that the regular behavior of the first household is more stable than the second household.
+However, the distribution of tail of the first household is more variable, observed through distinct letter values, implying that their not-so-regular behavior is quite extreme.
+This shows, how looking at the distribution of the dependent variable can throw more light on the energy behavior of the customers, which are lost using aggregate or summary statistics.
+-->
+
+<!-- # ```{r day-fortnight_agg, echo = FALSE} -->
+<!-- # library(lvplot) -->
+<!-- # library(ggplot2) -->
+<!-- # library(dplyr) -->
+<!-- # library(tibble) -->
+<!-- # library(gravitas) -->
+<!-- # library(tidyr) -->
+<!-- # smart_meter10 %>%  -->
+<!-- #   filter(customer_id %in% c(10006704, 10017936)) %>%  -->
+<!-- #   create_gran("day_fortnight") %>% -->
+<!-- #   as_tibble() %>%  -->
+<!-- #   group_by(customer_id, day_fortnight) %>%  -->
+<!-- #   summarize(median= log(median(general_supply_kwh)), -->
+<!-- #             total = log(sum(general_supply_kwh))) %>%  -->
+<!-- #   gather("daily_consumption", "value", - c(customer_id, day_fortnight)) %>%  -->
+<!-- #   ggplot2::ggplot(aes( -->
+<!-- #     x = as.factor(day_fortnight), -->
+<!-- #     y = value,  -->
+<!-- #     color = daily_consumption, -->
+<!-- #     group = daily_consumption)) + -->
+<!-- #   geom_line() + -->
+<!-- #   xlab("day_fortnight") + -->
+<!-- #   ylab("general_supply_kwh") +  -->
+<!-- #   facet_wrap(~customer_id) +  -->
+<!-- #   theme_bw()  -->
+
+<!-- # smart_meter10 %>%  -->
+<!-- #   filter(customer_id %in% c(10006704, 10017936)) %>%  -->
+<!-- #   create_gran("day_fortnight") %>% -->
+<!-- #   as_tibble() %>%  -->
+<!-- #   group_by(customer_id, day_fortnight) %>%  -->
+<!-- #   summarize(median_consumption= median(general_supply_kwh)) %>% -->
+<!-- #   ggplot2::ggplot(aes( -->
+<!-- #     x = as.factor(day_fortnight), -->
+<!-- #     y = median_consumption, -->
+<!-- #     color =  customer_id, -->
+<!-- #     group = customer_id)) + -->
+<!-- #   geom_line() + -->
+<!-- #   xlab("day_fortnight") + -->
+<!-- #   ylab("general_supply_kwh") +  -->
+<!-- #   theme_bw()  -->
+<!-- ``` -->
+
+<!-- ```{r day-fortnight, fig.cap="Letter value plot of two households across days of the fortnight.
+M, F, E, D and C represents the letter values of energy consumption.
+Regular behavior (within letter value F) is more variable for the 2nd household, whereas extreme behavior (beyond letter value F) is varying more for the first household."} -->
+<!-- library(lvplot) -->
+<!-- library(ggplot2) -->
+<!-- library(dplyr) -->
+<!-- library(tibble) -->
+<!-- library(gravitas) -->
+<!-- smart_meter10 %>% -->
+<!--   filter(customer_id %in% c(10006704, 10017936)) %>%  -->
+<!--   create_gran("day_fortnight") %>% -->
+<!--   ggplot2::ggplot(aes( -->
+<!--     x = as.factor(day_fortnight), -->
+<!--     y = general_supply_kwh)) + -->
+<!--   xlab("day_fortnight") + -->
+<!--   geom_lv( -->
+<!--     outlier.colour = "red", -->
+<!--     aes(fill = ..LV..), -->
+<!--     k = 5) + -->
+<!--   facet_wrap(~customer_id) +  -->
+<!--   scale_fill_lv() + -->
+<!--   theme_bw() + -->
+<!--   scale_y_sqrt()  -->
+<!-- ``` -->
+
+<!-- Figure \autoref{fig:my-hd} shows the overlay quantile plot of energy consumption of 50 households.
+The black line is the median, whereas the pink band covers 25th to 75th percentile, the orange band covers 10th to 90th percentile and the green band covers 1st to 99th percentile.
+Each facet represents a month and energy consumption across each hours of the day is shown inside each facet.
+It can be observed that the median is very close (and hence not distinctly visible) to the lower boundaries of all the other bands implying energy consumption for these households are extremely left skewed.75% of the households has distinct higher evening peaks compared to morning peaks, especially in the winter months.
+The top 5% households behave very differently than even the top 10% households in terms of total energy consumption across hours of the day.
+-->
+
+<!-- # ```{r is_harmony, echo= TRUE} -->
+<!-- # smart_meter10 %>%  -->
+<!-- #   is_harmony(gran1 = "hour_day",  -->
+<!-- #              gran2 = "day_week") -->
+<!-- #  -->
+<!-- # smart_meter10 %>% -->
+<!-- #   is_harmony(gran1 = "hour_day",  -->
+<!-- #              gran2 = "day_week",  -->
+<!-- #              facet_h = 14) -->
+<!-- #  -->
+<!-- # smart_meter10 %>%  -->
+<!-- #   is_harmony(gran1 = "day_month", -->
+<!-- #              gran2 = "week_month") -->
+<!-- # ``` -->
+
+<!-- Boxplot of energy consumption is shown across `wknd_wday` (facet) and `hour_day` (x-axis) for the same two households.
+For the first household, the shape of the distribution does not change significantly for weekdays and weekends.
+The distribution is roughly smooth with a morning and an evening peak.
+-->
+
+In \autoref{fig:bothcust} (b), <!--the distribution of energy consumption is plotted across the harmony pair (weekday/weekend, hour of the day) through an area quantile plot-->the black line is the median, whereas the purple band covers 25th to 75th percentile, the orange band covers 10th to 90th percentile and the green band covers 1st to 99th percentile.
+The first facet represents the weekday behavior while the second one displays the weekend behavior and energy consumption across each hours of the day is shown inside each facet.
+The energy consumption is extremely (positive- or right-) skewed with the 1st, 10th and 25th percentile lying relatively close whereas 75th, 90th and 99th lying further away from each other.
+This is common across both weekdays and weekends.
+For the first few hours on weekdays, median energy consumption starts and continues to be higher for longer as compared to weekends.
+
+Consider looking at violin plots instead of quantile plots to look at the same data in \autoref{fig:bothcust}(c).
+There is additional information that we can derive looking at the distribution.
+There is bimodality in the early hours of the day, implying both low and high energy consumption is probable in the early hours of the day both for weekdays and weekends.
+<!--Also the hours from 7 to 13 look most volatile.--> If we visualize the same data with reverse mapping of the cyclic granularities, then the natural tendency would be to compare weekend and weekday behavior within each hour and not across hours.
+For example in \autoref{fig:bothcust}(a), it can be seen that median energy consumption for the early morning hours is extremely high for weekdays compared to weekends.
+Also, outliers are more prominent in the latter part of the day.
+All of these indicate that looking at different distribution geometry or changing the mapping might shed lights on different aspect of the energy behavior for the same sample population.
+
+<!-- If we consider letter value F as a regular behavior and letter values beyond F as not-so-regular behavior, we can conclude that the regular behavior of the first household is more stable than the second household.
+However, the distribution of tail of the first household is more variable, observed through distinct letter values, implying that their not-so-regular behavior is quite extreme.
+This shows, how looking at the distribution of the dependent variable can throw more light on the energy behavior of the customers, which are lost using aggregate or summary statistics.
+-->
+
+```{r bothcust, fig.cap = "Energy consumption of a single customer shown with different distribution displays, and granularity arrangements.
+Two granularities are used: hour of the day (I) and weekday/weekend (II).
+Plot (a) shows granularity I facetted by granularity II, and plots (b), (c) shows the converse mapping.
+Plot (a) makes a comparison of usage by workday within each hour of the day using side-by-side boxplots.
+Generally, on a work day there is more consumption early in the day.
+Plots (b) and (c) examine the temporal trend of consumption over the course of a day, separately for the type of day.
+Plot (b) uses an area quantile to put the emphasis on the time series, for example, the median consumption over time shows prolonged usage in the morning on weekdays.
+Plot (c) uses a violin plot to place emphasis on distributional differences across hours.
+It can be seen that the morning use on weekdays is bimodal, some work days there is low usage, which might indicate the person is working from home and also having a late start.", out.width="90%"}
+
+# plot for only customer is shown
+# cust1 <- smart_meter10 %>%
+# filter(customer_id %in% c(10006704)) %>%
+#   prob_plot("wknd_wday",
+#                             "hour_day",
+#                             response = "general_supply_kwh",
+#                             plot_type = "quantile",
+#             symmetric = FALSE,
+#             quantile_prob = c(0.25, 0.5, 0.75, 0.9))
+#   scale_y_sqrt() +
+#   ggtitle("Energy consumption distribution for customer id: 10006704")
+cust2_quantile <- smart_meter10 %>%
+  filter(customer_id %in% c(10017936)) %>%
+  prob_plot("wknd_wday",
+    "hour_day",
+    response = "general_supply_kwh",
+    plot_type = "quantile",
+    symmetric = TRUE,
+    quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)
+  ) +
+  scale_y_sqrt() +
+  #ggtitle(" (b) Area quantile plot faceted by weekend-weekday") +
+  ylab("electricity demand [KWh]") + xlab("hours of the day") + ggtitle("") + ylab("")+ 
+  theme_minimal()
+#
+# smart_meter10 %>%
+#   filter(customer_id %in% c(10006704)) %>%
+#   prob_plot("wknd_wday",
+#                             "hour_day",
+#                             response = "general_supply_kwh",
+#                             plot_type = "violin") +
+#   scale_y_sqrt() +
+#   ggtitle("Energy consumption distribution for customer id: 10006704")
+
+cust2_violin <- smart_meter10 %>%
+  filter(customer_id %in% c(10017936)) %>%
+  prob_plot("wknd_wday",
+    "hour_day",
+    response = "general_supply_kwh",
+    plot_type = "violin"
+  ) +
+  scale_y_sqrt()+
+  #ggtitle(" (c) Violin plot faceted by weekend-weekday") +
+  ylab("") + xlab("hours of the day") + ggtitle("") +
+  scale_x_discrete( breaks = seq(0, 23, 5))+ 
+  theme_minimal()
+
+cust2_box <- smart_meter10 %>%
+  filter(customer_id %in% c(10017936)) %>%
+  prob_plot("hour_day",
+    "wknd_wday",
+    response = "general_supply_kwh",
+    plot_type = "boxplot"
+  ) +
+  scale_y_sqrt() +
+  #ggtitle(" (a) Box plot faceted by hour-of-day") +
+  xlab("") +
+  ggtitle("") + ylab("") +
+  scale_x_discrete(labels = c('wday','wend')) +
+  ggplot2::theme(axis.text.x = element_text(size = 7))+ 
+  theme_minimal()
+
+#ggarrange(cust2_quantile, cust2_violin, nrow = 2)
+
+gg_fig <- ggarrange(cust2_box,
+          ggarrange(cust2_quantile, cust2_violin, nrow = 2, labels = c("b", "c")),
+          ncol = 2, labels = "a")
+          #label.y = "electricity demand [KWh]"\
+
+ggpubr::annotate_figure(gg_fig,
+                left = text_grob("electricity demand [KWh]",  rot = 90))
+```
+
+<!-- # ```{r cust-ridge, fig.cap ="Boxplot of energy consumption across hours of the day faceted by weekday/weekend for customer id: 10017936.
+The change in mapping of the cyclic granularities leads to easier comparison within weekdays and weekends for each hour.
+Median consumption till 6am is higher for weekends compared to weekdays although the quartiles look similar.
+Outliers appear more during the end of the day implying more uncertain behavior in latter hours of the day compared to early morning hours."} -->
+<!-- #  -->
+<!-- # smart_meter10 %>% -->
+<!-- #   filter(customer_id %in% c(10017936)) %>% -->
+<!-- #   prob_plot("hour_day", -->
+<!-- #     "wknd_wday", -->
+<!-- #     response = "general_supply_kwh", -->
+<!-- #     plot_type = "boxplot" -->
+<!-- #   ) + -->
+<!-- #   scale_y_sqrt() -->
+<!-- # ``` -->
+
+<!-- Now, we would like to see how these customers' behavior relate to the rest of the 50 households across these two measures -   -->
+
+<!-- - if energy distribution is skewed towards extreme? -->
+
+<!-- - if the weekend and weekday behavior are different for most of these households? -->
+
+If the data for all keys are visualized together, it might lead to Simpson's paradox, which occurs when one observation shows a particular behavior, but this behavior paradoxically becomes obscured by aggregation.
+For example in a particular neighborhood one household may have the least daily power consumption for a full week, yet still not be the household with the minimum weekly power consumption.
+This is an intuitive possibility, because heterogeneous `customer_id`'s with very different occupation or demographics will tend to have very different energy behavior and combining them together will somehow weaken any typical or extreme behavior.
+A strategy for analyzing multiple keys together could be to first group them basis time series or demographic features and then look at their energy behavior.
+This is beyond the scope of the current work.
+
+<!-- For the purpose of this paper, the smart meter data is filtered for two customers to illustrate kinds of insights that can be drawn after proceeding with the systematic exploration. -->
+
+<!-- For example, Figure \ref{fig:wknd-wday50} shows the quantile plot of energy consumption of a sample of 50 households.
+Quantiles for weekends and weekdays for these customers look exactly the same.
+It is not clear if the behaviors of most of these customers do not alter between weekdays and weekends or looking at all customers together balances out the behaviors.
+Consider another example in Figure \ref{fig:my-hd} showing the area quantile plots of 50 customers.
+The median is very close to the lower boundaries of all the other bands implying energy consumption for these households are left skewed.
+The pink band changes significantly in winter months (May - August) implying that much of the behavioral changes occur in the quartiles, that too in peak hours of the day.
+It is to be noted here that the the level of all quantiles increased too in winter months (increased energy usage in weather conditions), the interesting part is to notice that the relationship between bands other than quartile stayed same across seasons.
+-->
+
+This case study shows systematic exploration of energy behavior for a household to gain exhaustive insights on periodic behavior of the households. 
+<!--First, it helps us to find the list of cyclic granularities to look at, then shrinks the number of possible visualizations by identifying harmonies, visualize a harmony pair and shows the effect of different distribution plots or reverse mapping.-->
+
+## T20 cricket data of Indian Premiere League {#sec:cricket}
+
+The method is not only restricted to temporal data, and can be generalized to many hierarchical granularities (with  continuous and uni-directional nature).
+We illustrate this with an application to the sport cricket.
+Although there is no conventional time component in cricket, each ball can be thought to represent an ordering from past to future with the game progressing forward with each ball.
+In the Twenty20 format, an over will consist of 6 balls (with some exceptions), an inning is restricted to a maximum of 20 overs, a match will consist of 2 innings and a season consists of several matches.
+Thus, similar to time, there is a hierarchy where ball is nested within overs, overs nested within innings and innings within matches.
+The idea of cyclic granularities can be likewise mapped to this hierarchy.
+Example granularites then include ball of the over, over of the inning and ball of the inning.
+Although most of these cyclic granularities are circular in design of the hierarchy, in application of the rules some granularities are aperiodic.
+For example, in most cases an over will consist of 6 balls with some exceptions like wide balls or when an inning finishes before the over finishes.
+Thus, the cyclic granularity ball-of-over will be circular in most cases and aperiodic in others.
+
+<!-- However, irrespective of the type of cyclic granularities, it can be interesting to visualize the distribution of a measured variable across these cyclic granularities to throw light on the periodic behavior of a non-temporal data set similar to any temporal data set.
+-->
+
+The Indian Premier League (IPL) is a professional Twenty20 cricket league in India contested by eight teams representing eight different cities in India.
+The ball by ball data for IPL season 2008 to 2016 is fetched from [Kaggle](https://www.kaggle.com/josephgpinto/ipl-data-analysis/data).
+The `cricket` data set in the `gravitas` package summarizes the ball-by-ball data across overs and contains information for a sample of 214 matches spanning 9 seasons (2008 to 2016) such that each over has 6 balls, each inning has 20 overs and each match has 2 innings.
+This could be useful in a periodic world when we wish to compute any circular/quasi-circular granularity based on a hierarchy table which look like \autoref{tab:hierarchy-cric}.
+
+```{r hierarchy-cric}
+library(gravitas)
+library(tibble)
+hierarchy_model <- tibble::tibble(
+  `linear (G)` = c("over", "inning", "match", "season"),
+  `single-order-up cyclic (C)` = c("over-of-inning", "inning-of-match", "match-of-season", 1),
+  `period length/conversion operator (K)` = c(20, 2, "k(match, season)", 1)
+)
+knitr::kable(hierarchy_model,
+             format = "latex",
+             booktabs = TRUE,
+             caption = "Hierarchy table for cricket where overs are nested within an inning, innings nested within a match and matches within a season.") %>%
+  #row_spec(0, bold = TRUE)%>%
+  kable_styling()
+```
+
+However, even if the situation is not periodic and a similar hierarchy can not be formed, it can be interesting to visualize the distribution of a measured variable across relevant cyclic granularities to shed light on the aperiodic behavior of a non-temporal data set similar to aperiodic events like formal meetings, workshops, conferences, school semesters in a temporal set up.
+There are many interesting questions that could possibly be answered with such a data set irrespective of the type of cyclic granularities.
+<!--We will explore a few interesting questions and understand how the proposed approach in the paper can help answer some of the questions.-->
+
+<!-- the two teams have a single innings each, which is restricted to a maximum of 20 overs.
+Hence, in this format of cricket, a match will consist of 2 innings, an innings will consist of 20 overs, an over will consist of 6 balls with some exceptions.
+-->
+
+<!-- ```{r hierarchy, echo=FALSE} -->
+<!-- hierarchy_model <- tibble::tibble(linear gran = c("ball", "over", "inning", "match"),  -->
+<!--                                   convert_fct = c(6, 20, 2, 1)) -->
+<!-- knitr::kable(hierarchy_model, caption = " A hierarchy table for T20 cricket") -->
+<!-- ``` -->
+
+<!-- Each team is given a two-and-a-half-minute "strategic timeout" during each innings; one must be taken by the bowling team between the ends of the 6th and 9th overs, and one by the batting team between the ends of the 13th and 16th overs.
+-->
+
+<!-- Suppose, we are interested to see how the distribution of scores vary from the start to the end of the game. Let us brainstorm some of the questions that might help us comprehend that. -->
+
+<!-- a) What is the most common pattern for batting and bowling teams across balls, overs, innings and matches? Which are the teams which are typical and which are exceptions? -->
+
+<!-- How the scores per over vary across granularities/categorizations like innings of a match or matches of a season?
+Are these different for the winning teams in that season and the teams that couldn't qualify for the playoffs?
+-->
+
+<!-- Is the outcome of the game dependent on who bats first? Do some teams have more chance to win if they are batting in the first innings? -->
+
+<!-- We will look at the ball by ball data for all batting teams.
+Since we want a periodic world, where each over consists of 6 balls and each match consists of two innings, we shall filter out the matches or overs for which that is not true.
+Also, we look at runs per over as that would have more variability compared to runs per ball and it be easier to observe the strategies of the winning team through that.
+-->
+
+<!-- Making it short -->
+
+<!-- First, we look at the distribution of runs (measured variable) across over-of-inning (circular granularity) and match-of-season (aperiodic cyclic granularity) in \autoref{fig:seas-over-inning}.
+The distribution of runs per over has not significantly changed from 2008 to 2016.
+There is no clear pattern/trend that runs per over is increasing or decreasing across seasons.
+Hence, we work with subsets of seasons to answer some of the questions: -->
+
+First, it would be interesting to see if the distribution of total runs vary depending on if a team bats in the first or second innings.
+The Mumbai Indians (MI) and Chennai Super kings (CSK) <!--are considered one of the best teams in IPL with multiple winning titles and --> appeared in final playoffs from 2010 to 2015.
+We take their example in order to dive deeper into this question.
+<!--Circular granularities "over-of-inning" and "inning-of-match" can be computed using \ref{sec:circular-gran-def} with over as index of the tsibble.--> From Figure \ref{fig:cricex}(a), it can be observed that for the team batting in the first inning there is an upward trend of runs per over, while there is no clear upward trend in median and quartile deviation of runs for the teams batting in the second inning.
+This seem to indicate that players feel mounting pressure to score more runs as they approach towards the end of the first inning.
+Whereas teams batting in the second inning have a set target in mind and are not subjected to such mounting pressure and may adopt a more conservative strategy, to score runs.
+Thus winning teams like CSK and MI seem to employ different inning strategies when it comes to their batting order.
+
+<!-- Also longer and more distinct letter values in the second innings suggests that the variability is more in the second innings. -->
+<!-- - Q1: How their run rates vary depending on if they bat first or 2nd? Is there a chance that they are more likely to win if they bat first? -->
+
+<!-- - Q2: Which team is more consistent in their approach in terms of run rate across different overs of the innings? -->
+
+<!-- # ```{r seas-over-inning, fig.cap = "Quantile plot of runs per over across overs of different seasons. There is no pattern on increase or decrease of runs across overs for seasons."} -->
+<!-- #   cricket_tsibble_all %>%  -->
+<!-- #   prob_plot("over",  -->
+<!-- #             "season", -->
+<!-- #             hierarchy_model, -->
+<!-- #             response = "runs_per_over", -->
+<!-- #             plot_type = "quantile", -->
+<!-- #             quantile_prob = c(0.25, 0.5, 0.75),  -->
+<!-- #             symmetric = FALSE)  + -->
+<!-- #      theme( # remove the vertical grid lines -->
+<!-- #             panel.grid.major.x = element_blank() , -->
+<!-- #             # explicitly set the horizontal lines (or they will disappear too) -->
+<!-- #             panel.grid.major.y = element_blank()) + scale_x_discrete(breaks = seq(2008, 2016, 3)) -->
+<!-- # ``` -->
+
+Another interesting question could be: do runs per over decrease in the subsequent over if fielding (defending) was good in the previous over?
+For establishing the fielding quality, we apply an indicator function on dismissals (1 if there was at least one wicket in the previous over due to run out or catch, 0 otherwise).
+Runs in the current over is then the observation variable.
+<!--If a batsman is bowled out, it does not necessarily signify good fielding.
+So we only include number of catches and run out in an over as a measure of good fielding.
+Difference in runs across overs are likely to be negative if good fielding has an impact on the runs scored in the subsequent overs.
+--> Dismissals in the previous over can lead to a batsman adopting a more defensive play style.
+Figure \ref{fig:cricex}(b) shows that no dismissals in the previous over leads to a higher median and quartile spread of runs per over as compared to the case when there has been at least one dismissal in the previous over.
+
+<!-- Difference in runs across over should be negative if good fielding has an impact on the runs scored in the subsequent overs.  -->
+
+<!-- fetching raw data since dot and fielding information not available in dismissal type not available in cricket data gravitas. Also `cricket` is aggregated across overs -->
+
+```{r cricex, fig.cap= "Runs per over shown with different distribution displays, and granularities.
+Plot (a) shows letter value plot across overs faceted by innings.
+For the team batting in the first innings there is an upward trend of runs per over, while there is no such pattern of runs for the teams batting in the second innings.
+Plot (b) shows quantile plot of runs per over across an indicator of wickets in previous over faceted by current over.
+This indicates that at least one wicket in the previous over leads to lower median run rate and quartile spread in the subsequent over.", warning = FALSE, message = FALSE, out.width = "90%"}
+
+library(tsibble)
+cricket_tsibble <- cricket %>%
+  mutate(data_index = row_number()) %>%
+  as_tsibble(index = data_index)
+
+hierarchy_model <- tibble::tibble(
+  units = c("index", "over", "inning", "match"),
+  convert_fct = c(1, 20, 2, 1)
+)
+
+cricket_tsibble %>%
+  filter(batting_team %in% c(
+    "Mumbai Indians",
+    "Chennai Super Kings"
+  )) %>%
+  mutate(inning = paste0("innings: ", inning)) %>%
+  prob_plot("inning",
+    "over",
+    response = "runs_per_over",
+    hierarchy_model,
+    plot_type = "lv"
+  ) +
+  scale_fill_brewer(palette = "Dark2") +
+  #ggtitle("(a) Runs per over across over faceted by inning") +
+  theme(legend.position = "right") +
+  ggtitle("a") +
+  ylab("runs per over") +
+  xlab("overs of the innings") +
+  theme(plot.title = element_text(face = "bold")) +
+  ggplot2::theme(
+       strip.text = ggplot2::element_text(
+        size = 10,
+         margin = ggplot2::margin(b=0, t=0)
+      )
+     ) +  theme_minimal() 
+#geom_smooth(aes( x = over,
+#                               y=runs_per_over), method = lm, #formula = y ~ splines::bs(x, 3), se = FALSE)
+
+library(tsibble)
+
+cricket_all <- read_csv("data-raw/deliveries_all.csv")
+matches_all <- read_csv("data-raw/matches_all.csv")
+
+cricket_season <- cricket_all %>% left_join(matches_all, by = c("match_id" = "id"))
+
+# cricket_per_over <- cricket_season %>%
+#   group_by(season,
+#            match_id,
+#            batting_team,
+#            bowling_team,
+#            inning,
+#            over) %>%
+#   summarise(runs_per_over = sum(total_runs),
+#             run_rate = sum(total_runs)/length(total_runs))
+#
+# cricket_tsibble_all <- cricket_per_over %>%
+#   ungroup() %>%
+#   mutate(data_index = row_number()) %>%
+#   as_tsibble(index = data_index)
+
+cricket_dot_field <- cricket_season %>%
+  mutate(
+    fielding_proxy = if_else(dismissal_kind %in%
+      c("caught", "caught and bowled"), 1, 0),
+    dot_ball_proxy = if_else(total_runs == 0, 1, 0),
+    wicket_proxy = if_else(is.na(dismissal_kind), 0, 1)
+  ) %>%
+  group_by(
+    season,
+    match_id,
+    batting_team,
+    bowling_team,
+    inning,
+    over
+  ) %>%
+  summarise(
+    runs_per_over = sum(total_runs),
+    run_rate = sum(total_runs)*6 / length(total_runs),
+    fielding_wckts = sum(fielding_proxy),
+    dot_balls = sum(dot_ball_proxy)
+  ) %>%
+  mutate(diff_run_rate = c(0, diff(run_rate)))
+
+cricket_tsibble <- cricket_dot_field %>%
+  ungroup() %>%
+  mutate(data_index = row_number()) %>%
+  as_tsibble(index = data_index)
+
+cricket_data <- cricket_tsibble %>%
+  mutate(
+    field = if_else(fielding_wckts == 0, "0", "1+"),
+    dot = if_else(dot_balls == 0, "no dot balls", ">0 dot balls"),
+    lag_field = lag(field),
+    lag_dot = lag(dot)
+  ) %>%
+  filter(lag_field != 0, lag_dot != 0)
+
+cricket_data$lag_field <- factor(cricket_data$field, levels = c("0", "1+"))
+
+# filter(fielding_wckts %in% c(0,1)) %>%
+#
+ cricket_data %>%
+  filter(over!=1) %>%
+  prob_plot("over", "lag_field",
+  hierarchy_model,
+  response = "run_rate",
+  plot_type = "quantile",
+  symmetric = FALSE,
+ quantile_prob = c(0.25, 0.5, 0.75)) +
+   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") +
+  ylab("runs per over")  +
+  xlab("number of wickets in previous over") +
+  ggtitle("b") +
+   theme(plot.title = element_text(face = "bold")) +
+        theme(axis.ticks = element_blank(), legend.background = element_blank(),
+            legend.key = element_blank(), panel.background = element_blank(), strip.background = element_blank(),
+            plot.background = element_blank(), complete = TRUE, panel.grid.major = element_line(colour = "#E0E0E0"),
+            panel.border = element_rect(colour = "#E0E0E0", fill = NA))
+```
+
+<!-- Q2: Among good fielding and bowling - which affect the runs of the subsequent overs more? -->
+
+<!-- Q3: Are runs set to reduce in the next over for dot balls in the previous over? -->
+
+<!-- A dot ball is a delivery bowled without any runs scored off it.
+The number of dot balls is reflective of the quality of bowling in the game.
+Run rate of an over should ideally decrease if the number of dot balls increase.
+However, what is the effect of dot balls on runs scored in the subsequent over.
+Will players batsman likely to go for big shots because they couldn't score good runs in the previous over?
+Or they should play consistently and avoid scoring high?
+Figure \ref{fig:exdot} shows the quantile plot of runs across overs for at least one dot ball per over (facet 1) or no dot balls per over (facet 2).
+-->
+<!-- With at least one dot balls per over, the distribution of run rates in facet 1 increase slower compared to that in facet 2.
+This implies that run rates are likely to decrease in the subsequent over as a result of dot balls in the previous over.
+-->
+
+<!-- ```{r exdot, fig.cap="25th, 50th, 75th quantiles of runs per over are drawn across overs of the innings with no (facet 2), more than zero (facet 1) dot balls per over.
+For all quantiles, run rates mostly increase at a higher rate in facet 2 compared to facet 1 implying run rates decrease with at least one dot ball in the previous over.", fig.pos="ht"} -->
+
+<!-- cricket_data %>% -->
+<!--   # filter(dot_balls %in% c(0, 1, 2)) %>% -->
+<!--   prob_plot("lag_dot", -->
+<!--     "over", -->
+<!--     hierarchy_model, -->
+<!--     response = "run_rate", -->
+<!--     plot_type = "quantile", -->
+<!--     quantile_prob = c(0.25, 0.5, 0.75), -->
+<!--     symmetric = FALSE -->
+<!--   ) + ggtitle("") -->
+<!-- ``` -->
+
+Wickets per over are considered as an aperiodic cyclic granularity with wickets as an aperiodic linear granularity.
+These granularities do not appear in the hierarchy table since it is difficult to position them in a hierarchy.
+These are similar to holidays or special events in temporal data.
+<!-- CONTENT CUT -->
+<!--While any special event that corresponds to a time domain can be treated as an aperiodic linear granularity in a temporal case, dot balls or wickets that corresponds to certain balls (index) could be treated as aperiodic events in cricket.-->
 

### 2020-10-07 R/compute_mmpd_panel.R

@@ -1,0 +1,23 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param slct_lvl_orig
+##' @param quantile_prob
+##' @param dist_ordered
+##' @param nperm
+##' @return
+##' @author Sayani07
+##' @export
+compute_mmpd_panel <- function(.data, quantile_prob = seq(0.01,
+                               0.99, 0.01), dist_ordered = TRUE, nperm = 20) {
+
+  dist_data_panel <- .data %>% 
+    compute_quantiles(quantile_prob = quantile_prob) %>% 
+    distance_panel(dist_ordered = dist_ordered)
+  
+  
+    mpd_data <- mpd(.data, dist_data_panel, nperm)
+    mmpd(.data, mpd_data, nperm)
+}

### 2020-10-07 R/create_sim_n.R

@@ -1,0 +1,19 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param norm_data1
+##' @param nsim
+##' @return
+##' @author Sayani07
+##' @export
+create_sim_n <- function(nlevel = 2, nsim = 500, nperm = 2000, sim_dist = dist_normal(5, 10) ) {
+  (1:nsim) %>%
+    map_df(function(i) {
+      sim_data <- create_data_sim1(nlevel, sim_dist) %>% 
+        create_data_sim1_nperm(nperm) %>% 
+        create_norm_max1()
+      bind_cols(sim_id = i, sim_data = sim_data)
+})
+}

### 2020-10-07 R/mmpd.R

@@ -1,0 +1,34 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param normx_data
+##' @param nperm
+##' @return
+##' @author Sayani07
+##' @export
+mmpd <- function(sim_panel_data, normx_data, nperm = 20) {
+
+  panel_facet <- normx_data %>% select(id_facet, norm_x) 
+  
+  nperm_data_1 <- bind_cols(perm_id = 1, perm_data = panel_facet) %>% 
+    rename("perm_data" ="norm_x") %>% 
+    select(-id_facet)
+  
+nperm_data_n <- (2:nperm) %>%
+    map_df(function(i) {
+      perm_data <- sample(panel_facet$norm_x, size = nrow(panel_facet), replace = TRUE)
+      bind_cols(perm_id = i,perm_data = perm_data)
+    })
+
+perm_facet_data <- bind_rows(nperm_data_1, nperm_data_n)
+
+perm_facet_data %>% 
+  summarise(mean_perm = mean(perm_data),
+            sd_perm = sd(perm_data)) %>% 
+  mutate(mmpd = if_else(sd_perm !=0,
+                        (median(nperm_data_1$perm_data, na.rm = TRUE) - mean_perm)/sd_perm,
+median(nperm_data_1$perm_data, na.rm = TRUE))) %>% pull(mmpd) %>% round(3)
+
+}

### 2020-10-07 R/mpd.R

@@ -1,0 +1,56 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param distance_panel_data
+##' @param nperm
+##' @return
+##' @author Sayani07
+##' @export
+
+source("R/shuffle_x_for_each_facet.R")
+mpd <- function(sim_panel_data, distance_panel_data, nperm = 2000) {
+  nfacet <- nrow(distance_panel_data)
+
+  # nperm_data_facet <- lapply(seq_len(nfacet),
+  #                           function(k) {
+  #     
+      panel_row <- distance_panel_data %>%
+        tidyr::pivot_longer(cols = -1, names_to = "j") %>% select(id_facet, value)
+      
+      nperm_data_1 <- bind_cols(perm_data = panel_row) %>%
+        rename("perm_data" = "value")
+      
+      nperm_data <- data.frame(2:nperm)
+      #nperm_data_n <- (2:nperm) %>%
+      nperm_data_n <- lapply(2:nperm, 
+                            function(i) {
+          z = NULL
+          
+          perm_data <- sim_panel_data %>% 
+            #dplyr::group_by(id_facet) %>% 
+            shuffle_x_for_each_facet() %>% 
+            compute_quantiles() %>% 
+            distance_panel() %>% 
+            pivot_longer(-1, names_to = "dist", 
+                         values_to = "perm_data") %>% select(-dist)
+            #rename("perm_data" = "...2")
+          
+          #z = bind_cols(perm_id = i, id_facet = k, perm_data = perm_data$perm_data)
+           #z = bind_cols(perm_data = perm_data$perm_data,
+        })
+      
+      nperm_data_facet <- bind_rows(nperm_data_n, nperm_data_n, .id = "perm_id")
+
+  nperm_data_facet %>%
+    group_by(id_facet) %>%
+    summarise(
+      max = max(perm_data, na.rm = TRUE),
+      mean_perm = mean(perm_data, na.rm = TRUE),
+      sd_perm = sd(perm_data, na.rm = TRUE)
+    ) %>%
+    mutate(norm_x = if_else(sd_perm !=0, 
+                            (max - mean_perm) / sd_perm,max))
+}
+

### 2020-10-07 R/plot_mmpd_null_grid.R

@@ -1,0 +1,28 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param mmpd_dist_null_grid
+##' @param mmpd_null_orig
+##' @return
+##' @author Sayani Gupta
+##' @export
+plot_mmpd_null_grid <- function(mmpd_dist_null_grid, mmpd_null_orig) {
+  
+  compute_p_value <- left_join(mmpd_dist_null_grid, mmpd_null_orig,
+                               by = c("nx", "nfacet")) %>% 
+    group_by(nx, nfacet) %>% 
+    summarise(p_value = sum(if_else(abs(mmpd.x)>abs(mmpd.y),1,0))/n(), .groups = 'drop')
+
+  ggplot() + 
+    geom_histogram(data = mmpd_dist_null_grid, aes(x = mmpd))  + 
+    geom_vline(data = mmpd_null_orig, aes(xintercept = mmpd),colour = "red") +
+    geom_text(data = compute_p_value, size = 3,  
+              aes(x = -Inf,
+                  y =  Inf,
+                  label = paste("p-value:",p_value),
+                  hjust   = 0,
+                  vjust   = 1)) + 
+    facet_grid(nx ~ nfacet)
+}

### 2020-10-07 main.R

@@ -609,4 +609,56 @@ p3 <- data6 %>% unnest(sim_dist) %>%
 p3
 
 
-##----
+##----introduction
+sm <- smart_meter10 %>%
+  filter(customer_id %in% c(10017936))
+
+library(lubridate)
+ptry <- sm %>%
+  create_gran("wknd_wday") %>% 
+  create_gran("week_month") %>% 
+  create_gran("hhour_day") %>% 
+  create_gran("month_year") %>% 
+  create_gran("day_month") %>%
+  filter(year(reading_datetime)==2013)%>% 
+  ggplot(aes(x = as.numeric(week_month), 
+             y = general_supply_kwh)) +
+  geom_line(aes(group = hhour_day,
+                color = as.numeric(month_year)))
+
+
+
+
++ geom_smooth(aes(x = as.numeric(week_month), y = general_supply_kwh), method = "loess", formula = y~x, color = "red", se = TRUE)  + facet_wrap(~wknd_wday)
+  
+
+ptry2 <- sm %>%
+  filter(year(reading_datetime)==2013) %>% 
+  create_gran("wknd_wday") %>% 
+  create_gran("hour_day") %>% 
+  ggplot(aes(x = as.numeric(hour_day), 
+             y = general_supply_kwh)) +
+  geom_point()+ geom_smooth(aes(x = as.numeric(week_month), y = general_supply_kwh), method = "loess", formula = y~x, color = "red", se = TRUE)  + facet_wrap(~wknd_wday)
+ 
+  #facet_wrap(~wknd_wday)
+  
+
+
+ p1 <- prob_plot("wknd_wday", 
+                       "week_month",
+                       plot_type = "boxplot",
+                       alpha = 0.5) + ggtitle("") +
+  ylab("") + 
+  xlab("") +
+  geom_smooth(aes(x = as.numeric(week_month), y = general_supply_kwh), method = "loess", formula = y~x, color = "red", se = TRUE) 
+
+
+p4 <- sm %>% prob_plot("wknd_wday", 
+                       "hour_day",
+                       plot_type = "boxplot") + ggtitle("") +
+  ylab("") + 
+  xlab("") + scale_x_discrete(breaks = c(0,seq(3, 23, 3))) +
+  geom_violin(alpha = 0.3, color = "red") + 
[…]

### 2020-10-07 main.Rmd
introduction, principle and structure

@@
 
-Here, we have two main objectives:
+Here, we aim to build a new measure to follow through these two main objectives:
 
@@
 
-# Building a new metric
+# Median Maximum Pairwise Distances (MMPD)
 
@@
 
-With reference to the graphical design in \ref{@paper-gravitas}, therefore the idea would be to rate a harmony pair higher if the variation between different levels of the x-axis variable is higher on an average across all levels of facet variables.
+With reference to the graphical design in \ref{@paper-gravitas}, therefore the idea would be to rate a harmony pair higher if the variation between different levels of the x-axis variable is higher on an average across all levels of the facet variables.
+Thus the metric could be obtained by computing maximum pairwise distances between distributions of the continuous random variable across x-axis categories for all facets and then taking the median of those maximum pairwise distances across facets.
+This would help capture the average maximum difference in distribution of the measurement variable explained by the two cyclic granularities together.
+We call this metric MMPD which stands for Median Maximum Pairwise Distances.
+In the next section we shall see how we go about computing this measure.
 

### 2020-10-08 main.Rmd
change the subsections name
added plots in intro as motivation

@@
 
+```{r intro_all}
+elec <- read_rds("data/elec.rds")
+
+id2_tsibble <- elec %>% 
+   filter(id == 2) %>% 
+   as_tsibble(index = date_time)
+
+id4_tsibble <- elec %>% 
+   filter(id == 4) %>% 
+   as_tsibble(index = date_time)
+
+# hour-of-day and month-of-year (important pair) id2's behavior across different hours of the day very different across months, but for id4 behavior across different hours of the day is not likely a function of month.
+p1 <- id2_tsibble %>%
+   prob_plot("month_year",
+             "hour_day",
+             response = "kwh",
+             plot_type = "quantile",
+             symmetric = TRUE,
+             quantile_prob = c(0.1, 0.25,0.5,0.75, 0.9)) +
+  ggtitle("")
+
+p2 <- id4_tsibble %>%
+   prob_plot("month_year",
+             "hour_day",
+             response = "kwh",
+             plot_type = "quantile",
+             symmetric = TRUE,
+             quantile_prob = c(0.1, 0.25,0.5,0.75, 0.9)) + 
+  ggtitle("")
+
+# wknd_wday and week_month (important pair) id2's behavior across different hours of the day very different across months, but for id4 beahvior across different hours of the day is not likely a function of month.
+
+p3 <- id2_tsibble %>%
+   prob_plot("wknd_wday",
+             "week_month",
+             response = "kwh",
+             plot_type = "quantile",
+             symmetric = FALSE,
+             quantile_prob = c(0.25,0.5,0.75)) +
+  ggtitle("") #+ scale_x_discrete(breaks = seq(0, 23, 4))
+
+p4 <- id4_tsibble %>%
+   prob_plot("wknd_wday",
+             "week_month",
+             response = "kwh",
+             plot_type = "quantile",
+             symmetric = FALSE,
+             quantile_prob = c(0.25,0.5,0.75)) +
+  ggtitle("") #+ scale_x_discrete(breaks = seq(0, 23, 4))
+
+```
+
+```{r p1_p2}
+ggpubr::ggarrange(p1, p2, ncol = 2)
+```
+
+```{r p4_p3}
+ggpubr::ggarrange(p3, p4, ncol = 2)
+```
+
 Here, we aim to build a new measure to follow through these two main objectives:
@@
 <!-- in the same group would be important to bring out different patterns of the data. -->
-## Distance between distributions
+
+## Computation
+
+### Distance between distributions
 
@@
 
-# Distribution of Jensen-Shannon distances
+### Distribution of Jensen-Shannon distances
 
@@
 
-## Normalize distances
+### Normalize distances
 
@@
 
-## Mean and standard deviation of the distribution of maximum
+### Mean and standard deviation of the distribution of maximum
 
@@
 
-## Distribution of distances
+### Distribution of distances
 
@@
 
-## Median Maximum Pairwise distance
-
-### Definition
-
-### Algorithm for computation for all harmony pairs
+## Algorithm
 
@@
 
-## Null distribution
+## Null distribution of MMPD
 
@@
 <!-- # how data looks -->
+
 Smart meters provide large quantities of measurements on energy usage for households across Australia.
@@
 <!--It would be interesting to explore the energy consumption distribution for these customers and gain insights on their energy behavior which are lost either due to aggregation or looking only at coarser temporal units.-->The idea here is to show how to visualize the distribution of the energy consumption across different cyclic granularities in a systematic way to identify different behavioral patterns.
-
-<!-- and identify the extreme and regular households. -->
-
-<!-- ### Data structure for visualization: -->
-
-<!-- The data structure for a sample of 50 households from that trial is depicted in \autoref{tab:smart-data} where the variable `reading_datetime`, `customer_id` and `general_supply_kwh` denote the index, key and measured variable of the tsibble.
--->
-<!-- <!-- We take a random sample of 50 households to see how we can achieve that.  -->
-
-```{r smart-data}
-# load("data/sm_cust50.Rdata")
-#
-# smart_data <- smart_meter <- sm_cust50 %>%
-#   as_tsibble() %>%
-#   dplyr::select(
-#     customer_id,
-#     reading_datetime,
-#     general_supply_kwh
-#   ) %>% head(n = 5)
-#
-#   knitr::kable(smart_data,
-#                format = "latex",
-#                booktabs = TRUE,
-#                caption = "Smart meter data structure with electricity demand for 50 households from SGSC project for every 30 minutes from 2012 to 2014.")
-```
-
-<!--of the tsibble and represents the time variable.
-The variable denoting different households represent the key of the tsibble and is the time series variable which needs to be analyzed.Data sets of the form <$C1$, $C2$, `general_supply_kwh`> will form the basis of exploration for each key in the data set, where the cyclic granularity $C1$ would be mapped to $x$ axis and `general_supply_kwh` to $y$ axis with the cyclic granularity $C2$ mapped to facet.
-Any geometry displaying the probability distribution of `general_supply_kwh` like boxplot, letter value, violin,
-ridge or highest density region plots can then be used to explore the data set.-->
 
@@
 Now that we have a list of cyclic granularities to look at, we should be able to compute the multiple-order-up granularities using Section \ref{sec:cyclic-calendar}.
-<!-- The lubridate package [@Grolemund2011-vm] provides tools to compute single-order-up granularities, \ref{sec:circular-gran-def} (for hour_day, hour_week and day_week) and \ref{sec:quasi-circular-gran-def} (for hour_month, day_month, week_month).
-with the index set mapping half-hourly time periods to a set of positive integers.-->
-
-<!-- R package **gravitas** [@R-gravitas] is used to facilitate the systematic exploration here.
-While trying to explore the energy behavior of these customers systematically across cyclic time granularities, the first thing we should have at our disposal is to know which all cyclic time granularities we can look at exhaustively.
-Let us consider conventional time deconstructions for a Gregorian calendar (second, minute, half-hour, hour, day, week, month, year).
-Since the interval of this tsibble is 30 minutes, the temporal granularities may range from half-hour to year.
-Considering $6$ linear granularities half-hour, hour, day, week, month, year, there could be $(6*5/2) = 15$ circular or quasi-circular granularities that could be formed.
-If these options are considered too many, the most coarse temporal unit can be set to a “month” and some intermediate temporal units which might not be pertinent to the analysis like hhour could be dropped.
-Then we will be left with six cyclic granularites namely "hour_day", "hour_week", "hour_month", "day_week", "day_month" and "week_month".
-Now that we have a list of cyclic granularities to look at, we should be able to compute the multiple-order-up granularities using Sections \ref{sec:cyclic-calendar}.
-<!-- The lubridate package [@Grolemund2011-vm] provides tools to compute single-order-up granularities, \ref{sec:circular-gran-def} (for hour_day, hour_week and day_week) and \ref{sec:quasi-circular-gran-def} (for hour_month, day_month, week_month).
--->
-<!-- Here, the index set $Z=\{z: z \in \mathbb{Z}_{\geq 0}\}$ maps the half-hourly time instants to a set of positive integers.
-Then, multiple-order-up circular granularity $hour\_week$ and quasi-circular granularity $hour\_month$ could be computed from single-order-up granularities as follows: -->
-<!-- <!-- $$ hour\_day(z) = \lfloor z/2 \rfloor \mod 7$$ (Definition \autoref{def:circular}) -->
-<!-- \begin{align} -->
-<!--   hour\_week(z) =  day\_week(z) + 24*hour\_day(z) -->
-<!-- \end{align} -->
-
-<!-- <!-- $$ day\_month(z) =   \lfloor z/2*24 \rfloor  - \sum_{w=0}^{k-1}\vert T_{w \mod 12*4} \vert$$ (\autoref{def:quasi-circular}) -->
-<!-- \begin{align} -->
-<!-- hour\_month(z) =  hour\_day(z) + 24*day\_month(z) -->
-<!-- \end{align} -->
-
-<!-- These cyclic granularities are a function of the index variable and are computed based on if they are circular <!--(Section \ref{sec:circular-gran-def}), quasi-circular.
-<!--(Section \ref{sec:quasi- circular-gran-def}) or aperiodic (Section \ref{sec:aperiodic-gran-def})-->
 
@@
 ```
-
-<!-- #smart_smart_search <- smart_meter %>% search_gran() -->
-<!-- #knitr::kable(smart_smart_search, format = "markdown") -->
-
-<!-- CONTENT CUT -->
-<!-- # ```{r search_limit1, echo=TRUE} -->
-<!-- # smart_meter10 %>% -->
-<!-- #   search_gran(highest_unit = "month") -->
-<!-- # ``` -->
-
-<!-- # smart_meter_limit1 <- smart_meter10 %>%  -->
-<!-- #   search_gran(highest_unit = "month") -->
-<!-- # knitr::kable(smart_meter_limit1, format = "markdown") -->
 
@@
 
-<!-- # smart_meter10 %>% gran_advice("wknd_wday", "hour_day") -->
-
-<!-- The median consumption or width of other bands doesn't vary much across seasons, implying extreme behavior or extreme customers does not vary across seasons much.  -->
-
-<!-- No need to share the same for 50 customers - cut down text and anyway nothing much interesting is coming -->
-
-<!-- ```{r wknd-wday50, fig.cap = "Quantile plot of energy consumption of 50 households across different hours of the day faceted by weekday and weekend.
-The quantiles are not different for weekdays and weekends implying either the behavior balances out among these customers or most of them do not behave differently for weekdays and weekends."} -->
-
-<!-- smart_meter <-  -->
-<!--   read_rds("data/sm_cust50.rds") -->
-
-<!-- smart_meter %>%  -->
-<!--   prob_plot("wknd_wday", -->
-<!--                             "hour_day", -->
-<!--                             response = "general_supply_kwh", -->
-<!--                             plot_type = "quantile", -->
-<!--             symmetric = FALSE,  -->
-<!--             quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)) + -->
-<!--   scale_y_sqrt() -->
-<!-- ``` -->
-
-<!-- # ```{r wknd-wday50_df} -->
-<!-- # smart_meter10 %>%  -->
-<!-- #   prob_plot("month_year", -->
-<!-- #                             "day_fortnight", -->
-<!-- #                             response = "general_supply_kwh", -->
-<!-- #                             plot_type = "quantile", -->
-<!-- #             symmetric = TRUE,  -->
-<!-- #             quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)) + -->
-<!-- #   scale_y_sqrt(breaks = c(0.1, 0.25, 0.5, 1:3)) -->
-<!-- # ``` -->
-
-<!-- ```{r my-hd, fig.cap="Area quantile plots of energy consumption across hours of the day faceted by months of the year.
-The black line is the median, whereas the pink band covers 25th to 75th percentile, the orange band covers 10th to 90th percentile and the green band covers 1st to 99th percentile.
-The median and quartile consumption increase in winter months, but extreme behavior represented by higher bands mostly stay the same across seasons.
-"} -->
-
-<!-- library(gravitas) -->
-<!-- library(tsibble) -->
-
-<!-- library(ggplot2) -->
-<!-- smart_meter %>% -->
-<!--   prob_plot("month_year", "hour_day", -->
-<!--     response = "general_supply_kwh", -->
-<!--     plot_type = "quantile", -->
-<!--     quantile_prob = c(0.01, 0.05, 0.1, 0.25, 0.5, 0.75, 0.9, 0.95, 0.99), -->
-<!--     symmetric = TRUE) + -->
-<!--   ggtitle("") + scale_y_sqrt(breaks = c(0.01, 0.1, 0.5, 1:3)) -->
-<!-- ``` -->
-
-<!-- Figure \ref{fig:dw-hd} shows that on morning peaks for Saturday and Sunday are higher and occurs in a later hour of the day compared to weekdays.
-This is true for both top 50% and 75% of the customers.
-Hence, this is indicative of the fact that at least 50% of the households in this subset has traditional work days (Mon-Fri) and weekends(Sat-Sun).
-All the percentiles peaks up in the morning hours and then drops in the afternoon, before again peaking up in the evening.
--->
-
-<!-- ```{r dw-hd} -->
-
-<!-- # Hourly usage across days of the week -->
-<!-- sm_cust50 %>% -->
-<!--   prob_plot("day_week",  -->
-<!--            "hour_day", -->
-<!--            "general_supply_kwh",  -->
-<!--            plot_type = "quantile",  -->
-<!--           quantile_prob = c(0.25, 0.5, 0.75), -->
-<!--            response = "general_supply_kwh", overlay = FALSE) + -->
-<!--   ggtitle("") -->
-
-<!-- ``` -->
-
-<!-- on half-hourly energy usage and detailed information on appliance use, climate, retail and distributor product offers, and other related factors.  -->
-
-<!-- typical and extreme behaviors of 50 households from that trial.  -->
-
-<!-- , and indeed many parts of the world.
-Households are distributed geographically and have different demographic properties such as the existence of solar panels, central heating or air conditioning.
-The behavioral patterns in households vary substantially, for example, some families use a dryer for their clothes while others hang them on a line, and some households might consist of night owls, while others are morning larks.
--->
-
-<!-- <!-- Existing approaches, why we need to drill down, or why we want to -- probability distributions -->
-<!-- It is common to see aggregates of usage across households, total kwh used each half-hour by state, for example, because energy companies need to understand maximum loads that they will have to plan ahead to accommodate.
-But studying overall energy use hides the distributions of usage at finer scales, and making it more difficult to find solutions to improve energy efficiency.
--->
-
-<!-- We want to look at the distribution of energy across coarser temporal granularities and then deep dive into finer temporal granularities. -->
-
-<!-- In Figure \ref{fig:day-fortnight} and \ref{fig:day-fortnight-agg} , the smart meter data is filtered for two customers to illustrate what kinds of insights can be drawn for the energy behavior of these two customers.
--->
-
-<!-- can be added later -->
-
-<!-- In Figure \ref{fig:day-fortnight},to illustrate what kinds of insights can be drawn for the energy behavior of these two customers.
-it can be seen that for most days of the fortnight, the second household has much less consumption than the first one.
-However, there is additional information that we can derive looking at the distribution.
-If we consider letter value F as a regular behavior and letter values beyond F as not-so-regular behavior, we can conclude that the regular behavior of the first household is more stable than the second household.
-However, the distribution of tail of the first household is more variable, observed through distinct letter values, implying that their not-so-regular behavior is quite extreme.
-This shows, how looking at the distribution of the dependent variable can throw more light on the energy behavior of the customers, which are lost using aggregate or summary statistics.
--->
-
-<!-- # ```{r day-fortnight_agg, echo = FALSE} -->
-<!-- # library(lvplot) -->
-<!-- # library(ggplot2) -->
-<!-- # library(dplyr) -->
-<!-- # library(tibble) -->
-<!-- # library(gravitas) -->
-<!-- # library(tidyr) -->
-<!-- # smart_meter10 %>%  -->
-<!-- #   filter(customer_id %in% c(10006704, 10017936)) %>%  -->
-<!-- #   create_gran("day_fortnight") %>% -->
-<!-- #   as_tibble() %>%  -->
-<!-- #   group_by(customer_id, day_fortnight) %>%  -->
-<!-- #   summarize(median= log(median(general_supply_kwh)), -->
-<!-- #             total = log(sum(general_supply_kwh))) %>%  -->
-<!-- #   gather("daily_consumption", "value", - c(customer_id, day_fortnight)) %>%  -->
-<!-- #   ggplot2::ggplot(aes( -->
-<!-- #     x = as.factor(day_fortnight), -->
-<!-- #     y = value,  -->
-<!-- #     color = daily_consumption, -->
-<!-- #     group = daily_consumption)) + -->
-<!-- #   geom_line() + -->
-<!-- #   xlab("day_fortnight") + -->
-<!-- #   ylab("general_supply_kwh") +  -->
-<!-- #   facet_wrap(~customer_id) +  -->
-<!-- #   theme_bw()  -->
-
-<!-- # smart_meter10 %>%  -->
-<!-- #   filter(customer_id %in% c(10006704, 10017936)) %>%  -->
-<!-- #   create_gran("day_fortnight") %>% -->
-<!-- #   as_tibble() %>%  -->
-<!-- #   group_by(customer_id, day_fortnight) %>%  -->
-<!-- #   summarize(median_consumption= median(general_supply_kwh)) %>% -->
-<!-- #   ggplot2::ggplot(aes( -->
-<!-- #     x = as.factor(day_fortnight), -->
-<!-- #     y = median_consumption, -->
-<!-- #     color =  customer_id, -->
-<!-- #     group = customer_id)) + -->
-<!-- #   geom_line() + -->
-<!-- #   xlab("day_fortnight") + -->
-<!-- #   ylab("general_supply_kwh") +  -->
-<!-- #   theme_bw()  -->
-<!-- ``` -->
-
-<!-- ```{r day-fortnight, fig.cap="Letter value plot of two households across days of the fortnight.
-M, F, E, D and C represents the letter values of energy consumption.
-Regular behavior (within letter value F) is more variable for the 2nd household, whereas extreme behavior (beyond letter value F) is varying more for the first household."} -->
-<!-- library(lvplot) -->
-<!-- library(ggplot2) -->
-<!-- library(dplyr) -->
-<!-- library(tibble) -->
-<!-- library(gravitas) -->
-<!-- smart_meter10 %>% -->
-<!--   filter(customer_id %in% c(10006704, 10017936)) %>%  -->
-<!--   create_gran("day_fortnight") %>% -->
-<!--   ggplot2::ggplot(aes( -->
-<!--     x = as.factor(day_fortnight), -->
-<!--     y = general_supply_kwh)) + -->
-<!--   xlab("day_fortnight") + -->
-<!--   geom_lv( -->
-<!--     outlier.colour = "red", -->
-<!--     aes(fill = ..LV..), -->
-<!--     k = 5) + -->
-<!--   facet_wrap(~customer_id) +  -->
-<!--   scale_fill_lv() + -->
-<!--   theme_bw() + -->
-<!--   scale_y_sqrt()  -->
-<!-- ``` -->
-
-<!-- Figure \autoref{fig:my-hd} shows the overlay quantile plot of energy consumption of 50 households.
-The black line is the median, whereas the pink band covers 25th to 75th percentile, the orange band covers 10th to 90th percentile and the green band covers 1st to 99th percentile.
-Each facet represents a month and energy consumption across each hours of the day is shown inside each facet.
-It can be observed that the median is very close (and hence not distinctly visible) to the lower boundaries of all the other bands implying energy consumption for these households are extremely left skewed.75% of the households has distinct higher evening peaks compared to morning peaks, especially in the winter months.
-The top 5% households behave very differently than even the top 10% households in terms of total energy consumption across hours of the day.
--->
-
-<!-- # ```{r is_harmony, echo= TRUE} -->
-<!-- # smart_meter10 %>%  -->
-<!-- #   is_harmony(gran1 = "hour_day",  -->
-<!-- #              gran2 = "day_week") -->
-<!-- #  -->
-<!-- # smart_meter10 %>% -->
-<!-- #   is_harmony(gran1 = "hour_day",  -->
-<!-- #              gran2 = "day_week",  -->
-<!-- #              facet_h = 14) -->
-<!-- #  -->
-<!-- # smart_meter10 %>%  -->
-<!-- #   is_harmony(gran1 = "day_month", -->
-<!-- #              gran2 = "week_month") -->
-<!-- # ``` -->
-
-<!-- Boxplot of energy consumption is shown across `wknd_wday` (facet) and `hour_day` (x-axis) for the same two households.
-For the first household, the shape of the distribution does not change significantly for weekdays and weekends.
-The distribution is roughly smooth with a morning and an evening peak.
--->
-
 In \autoref{fig:bothcust} (b), <!--the distribution of energy consumption is plotted across the harmony pair (weekday/weekend, hour of the day) through an area quantile plot-->the black line is the median, whereas the purple band covers 25th to 75th percentile, the orange band covers 10th to 90th percentile and the green band covers 1st to 99th percentile.
@@
 All of these indicate that looking at different distribution geometry or changing the mapping might shed lights on different aspect of the energy behavior for the same sample population.
-
-<!-- If we consider letter value F as a regular behavior and letter values beyond F as not-so-regular behavior, we can conclude that the regular behavior of the first household is more stable than the second household.
-However, the distribution of tail of the first household is more variable, observed through distinct letter values, implying that their not-so-regular behavior is quite extreme.
-This shows, how looking at the distribution of the dependent variable can throw more light on the energy behavior of the customers, which are lost using aggregate or summary statistics.
--->
 
@@
 
-# plot for only customer is shown
-# cust1 <- smart_meter10 %>%
-# filter(customer_id %in% c(10006704)) %>%
-#   prob_plot("wknd_wday",
-#                             "hour_day",
-#                             response = "general_supply_kwh",
-#                             plot_type = "quantile",
-#             symmetric = FALSE,
-#             quantile_prob = c(0.25, 0.5, 0.75, 0.9))
-#   scale_y_sqrt() +
-#   ggtitle("Energy consumption distribution for customer id: 10006704")
 cust2_quantile <- smart_meter10 %>%
@@
   theme_minimal()
-#
-# smart_meter10 %>%
-#   filter(customer_id %in% c(10006704)) %>%
-#   prob_plot("wknd_wday",
-#                             "hour_day",
-#                             response = "general_supply_kwh",
-#                             plot_type = "violin") +
-#   scale_y_sqrt() +
-#   ggtitle("Energy consumption distribution for customer id: 10006704")
 

### 2020-10-08 main.Rmd
introduction and motivation updated with examples

@@
 
-# Introduction
+# Introduction and background
 
@@
 However, if one wants to understand the periodicities in energy behavior and how the periodicities interact in greater details, it is not easy to comprehend the interactions of some periodicities' from this display, due to the combination of linear and cyclic representation of time.
-For example, this display might not be the best to understand how hour-of-the-day or month-of-year varies across week-of-the-month.
+For example, this display might not be the best to understand how hour-of-the-day varies across month-of-year varies across week-of-the-month.
 Further, it is not clear what all interactions of cyclic granularities should be read from this display as there could be many combinations that one can look at.
 Moreover, calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions (@our-paper) and could include other cyclic granularities like hour-of-week or day-of-fortnight, which could potentially become useful depending on the context.
-Lastly, there might be specific interactions that are interesting and others that are not.
-It is immensely useful to make the transition from all possible ways to only ways that could potentially be important given a situation.
+Lastly, there might be specific interactions that are interesting and others that are not and that too will vary with different households.
+For example, area distribution quantiles are plotted for household 2 and 4 in Figure ref{fig:}a and b respectively.
+For the first household, the 75th and 90th percentile for Jan, Feb and July are very close, implying that energy usage for these months are generally on a much higher side due to the usage of air conditioners (in Jan and Feb) and heaters (in July).
+The energy consumption for household 2 is also higher relative to its own consumption for Jan, Feb and March but the 75th and 90th percentile are apart implying that contrary to the first household, the second household resorts to air conditioners and heaters much less regularly than the first one.
+Moreover, the 75th percentile distribution is not bimodal across hours of the day for the first household in those months, but the distribution looks similar for all months for the second household.
+Difference in the energy consumption seem to be varying both across month-of-year (facets) and hour-of-day (x-axis).
+And thus, both the cyclic granularities would deem important while studying the periodicities in the first household.
+However, it seems like energy consumption across hours of the day are not that different across different months for the second household.
+Differences seem to be more prominent across month-of-year (facets) than hour-of-day (x-axis).
+Again, look at \ref{fig:} c and d, where energy consumption for these two households are plotted against (weekend/weekday, week-of-month).
+Here, for both households, the pattern of energy consumption vary  across different weeks of the month irrespective of the fact it is a weekday or weekend.
+In that respect, the harmony pair (month-of-year, hour-of-day) seems to be more informative than (weekend/weekday, week-of-month) for the first household.
+It could be immensely useful to make the transition from all possible ways to only ways that could potentially be informative given a household.
 
@@
 However, even after excluding clashes, the list of harmonies left could be enormous for exhaustive exploration.
-Hence, there is a need to reduce the search even further by including only those harmonies for which variation within different categories is significant.
-Also, ranking the remaining harmonies based on how well they capture the variation in the measured variable could be potentially useful.
+Hence, there is a need to reduce the search even further by including only those harmonies which are informative enough.
+Also, ranking the remaining harmony pairs based on how well they capture the variation in the measured variable could be potentially useful.
 

### 2020-10-08 main.Rmd
updated structure to discuss

@@
 However, if one wants to understand the periodicities in energy behavior and how the periodicities interact in greater details, it is not easy to comprehend the interactions of some periodicities' from this display, due to the combination of linear and cyclic representation of time.
-For example, this display might not be the best to understand how hour-of-the-day varies across month-of-year varies across week-of-the-month.
+For example, this display might not be the best to understand how hour-of-the-day varies and month-of-year varies across week-of-the-month.
 Further, it is not clear what all interactions of cyclic granularities should be read from this display as there could be many combinations that one can look at.
@@
 
-# wknd_wday and week_month (important pair) id2's behavior across different hours of the day very different across months, but for id4 beahvior across different hours of the day is not likely a function of month.
+# wknd_wday and week_month (important pair) id2's behavior across different hours of the day very different across months, but for id4 behavior across different hours of the day is not likely a function of month.
 
@@
 
-Here, we aim to build a new measure to follow through these two main objectives:
+In this paper, we aim to build a new measure to follow through these two main objectives:
 
@@
 -->
-<!-- Figure \ref{}d takes it futher by varying the distribution across both facet and x-axis categories. -->
+<!-- Figure \ref{}d takes it further by varying the distribution across both facet and x-axis categories. -->
 
@@
 
-Suppose that $X_1$, $X_2$ , ... , $X_n$ are i.i.d. random variables with expected values $E(X_i) = \mu < \infty$ and variance $Var(X_i) = \sigma^2 < \infty$. Let 
-$Y = max(X_1, X_2, \dots, X_n)$.
-
-Let $F_X(x)$ be the common distribution of the variables $X_i$ and let $F_Y(y)$ be the corresponding distribution of $Y$. $F_Y(y)$ could be obtained from $F_X(x)$ simply by using:
-$F_Y(y) = P[(X_1 \leq y)\cap(X_2 \leq y) \cap...\cap (X_n \leq y)] = {F_X(y)}^n$.
+<!-- bullet points end here -->
+
+<!-- Suppose that $X_1$, $X_2$ , ... , $X_n$ are i.i.d. random variables with expected values $E(X_i) = \mu < \infty$ and variance $Var(X_i) = \sigma^2 < \infty$. Let  -->
+<!-- $Y = max(X_1, X_2, \dots, X_n)$. -->
+
+<!-- Let $F_X(x)$ be the common distribution of the variables $X_i$ and let $F_Y(y)$ be the corresponding distribution of $Y$. $F_Y(y)$ could be obtained from $F_X(x)$ simply by using: -->
+<!-- $F_Y(y) = P[(X_1 \leq y)\cap(X_2 \leq y) \cap...\cap (X_n \leq y)] = {F_X(y)}^n$.
 For large $n$, the distribution of $Y$ approaches a standard shape, which does not depend on $F_X$.
@@
 If $F_X(x)$ is the CDF of $X$, then $F_Y(y) = {F_x(y)}^n$.
-Suppose $\Phi$ nd $\phi$ are the cdf and pdf of a standard normal distribution, then
-$f_Y(y) = n{\Phi(y)}^{n-1}\phi(y)$, which depends on $n$.
+Suppose $\Phi$ nd $\phi$ are the cdf and pdf of a standard normal distribution, then -->
+<!-- $f_Y(y) = n{\Phi(y)}^{n-1}\phi(y)$, which depends on $n$.
 Hence, we are trying to normalise for $n$.
@@
 We observe from the following graphs that our normalisation works after $n=6$, after which the difference in mean and standard deviation flattens out a lot.
-
-Maximum pairwise distances are not robust to the number of levels and is higher for harmonies with higher levels.
-Thus these maximum pairwise distances need to be normalized for different harmonies in a way that eliminates the effect of different levels.
+-->
+
+<!-- ### why normalize -->
+
+Median and maximum distances are not robust to the number of levels and the metric would have higher values for harmonies with higher levels.
+Figure \ref{fig:mean-sd-max} shows how both mean and standard deviation of the distribution of maximum and median varies for different sample sizes ($n$).
+There is a rightward shift in the location and decrease in scale with increasing $n$.
+Thus these median maximum pairwise distances need to be normalized for different harmonies in a way that eliminates the effect of different levels, consequently enabling comparison across different harmonies.
 The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.
@@
 
-### why normalize
+For large $n$, the distribution of $M$ approaches a standard shape.
+But what about the case when $n$ is not large enough?
+The distribution of maximum in that case will indeed depend on $n$ and the underlying distribution of $D$.
+For large $n$, we could use EVT and CLT to normalise for $n$, however, most of the cyclic granularities encountered in practice have low $n$.
+Hence, normalisation could be done by bootstrapping procedure to ensure that the distribution of maximum/median have the same mean and variation for varying $n$.
 
@@
 
-### Mean and standard deviation of the distribution of maximum
-
-```{r}
+```{r mean-sd-max, fig.cap = "Display shows mean and standard deviation of the distribution of maximum for sample sizes ranging from 2 to 30.
+There is a right shift in the distribution of maximum and median with increasing sample sizes."}
+
 library(ggridges)
@@
 
-## Null distribution of MMPD
+## Design and analysis of simulation experiments
+
+Simulation experiments with different designs could help monitor and understand the behavior of the test statistic.
+
+### Impact of different levels from the same distribution of the measured variable (for understanding size)
+
+A 2 way contingency table with number of facet levels, x-axis levels should be constructed with values as the p-values.
+
+Table
+Conclusions
+(in Null distribution)
+
+### Impact of different distribution of the measured variable keeping the same distribution for each
+panel (for understanding size)
+
+To check if different distributions impact, simulate data from different distributions.
+A 3 way contingency table with number of facet levels, x-axis levels and distribution type should be constructed with each cell value as the p-value.
+
+Table
+Conclusions
+(in Null distribution)
+
+### Impact of simulating different distributions across categories for understanding power
+
+#### Varying distribution across facet
+#### Varying distribution across x-axis
+#### Varying distribution across both facets and x-axis
+#### Repeat all with varying facet and x-axis levels
+
+Table
+Conclusions
+(in power)
+
+## Null distribution
+
+### Size: Simulated same distribution for all combinations of categories for all harmony pairs.
+
+Failure to reject the null hypothesis when there is in fact no significant effect.
 
@@
 
-### Confidence interval of test statistic
-
-## Simulation design
-
-Behavior of the statistic - control simulation
-
- - To check if different distributions impact
-(simulate with different distributions but same for all levels)
-
- - To check if x-levels and facets are normalized
-(simulate with different distributions)
-(simulate with different x and facet levels)
-
-## Size and power
+<!-- ### Confidence interval of test statistic -->
+
+## Power and confidence interval
+
+Failure to reject the null hypothesis when there is in fact a significant effect.
 
@@
 
-### Size: Simulated same distribution for all combinations of categories for all harmony pairs.
-
-Failure to reject the null hypothesis when there is in fact no significant effect.
-
 <!-- # ```{r samenull_2by4, eval = FALSE} -->
@@
 
-```{r normalv21_power}
-
-```
-
-```{r normalv22_power}
-
-```
-
-### Power: Simulated same distribution for all combinations of categories for all harmony pairs.
-
-```{r normalv23_power}
-
-```
-
-```{r normalv24_power}
-
-```
-
-*Conclusion*: The test rejects the null hypothesis if distributions are different.
-
-### Scenario 2: Simulated different distributions for all combinations of categories for harmony pairs for few levels.
-
-```{r diffnull_2by4, eval = FALSE}
-
-```
-
-*Conclusion*: The test select the harmony pair for which distribution of x-axis categories are significantly different
-
-### Scenario 3: Simulated different distributions for all combinations of categories for all harmony pairs with many levels.
-
-```{r diffnull_7by11, eval = FALSE}
-```
-
-*Conclusion*: The test indicates that both harmony pairs do not have significant variation.
-
-### Scenario 4: Simulated different distributions for all combinations of categories for all harmony pairs with many levels - very different distribution across x-axis
-
-```{r diffnull_7by11normal, eval = FALSE}
-```
-
-*Conclusion*: The test indicates that only the first harmony pair has significant variation.
-
-### Scenario 5: Simulated different distributions for all combinations of categories for all harmony pairs with many levels - very different distribution across facets
-
-```{r diffnull_7by11normal2, eval = FALSE}
-```
+<!-- # ```{r normalv21_power} -->
+<!-- #  -->
+<!-- # ``` -->
+<!-- #  -->
+<!-- #  -->
+<!-- # ```{r normalv22_power} -->
+<!-- #  -->
+<!-- # ``` -->
+
+### Varying distribution across facet
+### Varying distribution across x-axis
+### Varying distribution across both facets and x-axis
+### Repeat all with varying facet and x-axis levels
+
+<!-- ### Power: Simulated same distribution for all combinations of categories for all harmony pairs. -->
+
+<!-- # ```{r normalv23_power} -->
+<!-- #  -->
+<!-- # ``` -->
+<!-- #  -->
+<!-- #  -->
+<!-- # ```{r normalv24_power} -->
+<!-- #  -->
+<!-- # ``` -->
+
+*Conclusion*: The test should reject the null hypothesis if distributions are different.
+
+<!-- ### Scenario 2: Simulated different distributions for all combinations of categories for harmony pairs for few levels. -->
+
+<!-- ```{r diffnull_2by4, eval = FALSE} -->
+
+<!-- ``` -->
+
+<!-- *Conclusion*: The test select the harmony pair for which distribution of x-axis categories are significantly different -->
+
+<!-- ### Scenario 3: Simulated different distributions for all combinations of categories for all harmony pairs with many levels. -->
+
+<!-- ```{r diffnull_7by11, eval = FALSE} -->
+<!-- ``` -->
+
+<!-- *Conclusion*: The test indicates that both harmony pairs do not have significant variation. -->
+
+<!-- ### Scenario 4: Simulated different distributions for all combinations of categories for all harmony pairs with many levels - very different distribution across x-axis -->
+
+<!-- ```{r diffnull_7by11normal, eval = FALSE} -->
+<!-- ``` -->
+
+<!-- *Conclusion*: The test indicates that only the first harmony pair has significant variation. -->
+
+<!-- ### Scenario 5: Simulated different distributions for all combinations of categories for all harmony pairs with many levels - very different distribution across facets -->
+
+<!-- ```{r diffnull_7by11normal2, eval = FALSE} -->
+<!-- ``` -->
 
@@
 
-<!-- <!-- ```{r diffnull_3levels} --> -->
-
-<!-- <!-- ``` --> -->
+<!-- <!-- ```{r diffnull_3levels} -->
+
+<!-- <!-- ``` -->
 
@@
 
-Few harmony pairs are displayed in \autoref{fig:bothcust} to illustrate the siginificance of MMPD, threshold and the impact of different distribution plots and reverse mapping.
+Few harmony pairs are displayed in \autoref{fig:bothcust} to illustrate the significance of MMPD, threshold and the impact of different distribution plots and reverse mapping.
 \noindent For each of \autoref{fig:bothcust} (b) and (c), $C_i$ is the circular granularity day-type (weekday/weekend) and $C_j$ is hour of the day.

### 2020-10-08 R/check_if_gravitas.R

@@ -23,7 +23,7 @@ id3 <- elec %>%
 
 id3_tsibble <- id3 %>% 
   as_tsibble(index = date_time)
-
+   
 
 harmonies <- id3_tsibble %>%
   harmony(

### 2020-10-15 hakear.Rmd
update all files

@@
 # }
+# 
 # if (!file.exists("cache/smart_harmony.rds")) {

### 2020-10-15 main.Rmd
update all files

@@
   fig.path = "figure/", fig.align = "center", fig.show = "hold",
-  cache = TRUE, cache.path = "cache/",
+  cache = FALSE, cache.path = "cache/",
   out.width = ifelse(is_html_output(), "100%", "\\textwidth")
@@
 
+# Set up plan
+source("_drake.R")
+# Run all code required
+drake::r_make()
+# load each object as required
+# loadd()
 ```
@@
 The calendar display has several components in it, which helps us look at energy consumption across hour-of-the-day, day-of-the-week, week-of-the-month, and month-of-the-year at once.
-Some interaction of these cyclic granularities[@our-paper] could also be interpreted from this display.
+Some interaction of these cyclic granularities[@Gupta2020-vo] could also be interpreted from this display.
 This is a great start to have an overview of the energy consumption.
@@
 Further, it is not clear what all interactions of cyclic granularities should be read from this display as there could be many combinations that one can look at.
-Moreover, calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions (@our-paper) and could include other cyclic granularities like hour-of-week or day-of-fortnight, which could potentially become useful depending on the context.
+Moreover, calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions (@Gupta2020-vo) and could include other cyclic granularities like hour-of-week or day-of-fortnight, which could potentially become useful depending on the context.
 Lastly, there might be specific interactions that are interesting and others that are not and that too will vary with different households.
@@
 <!-- what is the dimension of the problem -->
-The paper (gravitas) describes how we can compute all possible combinations of cyclic time granularities.
+The paper (@Gupta2020-vo) describes how we can compute all possible combinations of cyclic time granularities.
 If we have $n$ periodic linear granularities in the hierarchy table, then $n(n-1)/2$ circular or quasi-circular cyclic granularities could be constructed.
@@
              quantile_prob = c(0.1, 0.25,0.5,0.75, 0.9)) +
-  ggtitle("")
+  ggtitle("") + theme(
+        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
 
@@
              quantile_prob = c(0.1, 0.25,0.5,0.75, 0.9)) + 
-  ggtitle("")
+  ggtitle("") + theme(
+        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
 
@@
 p3 <- id2_tsibble %>%
+  create_gran("week_month") %>% 
+  filter(week_month != 5) %>% 
    prob_plot("wknd_wday",
@@
              quantile_prob = c(0.25,0.5,0.75)) +
-  ggtitle("") #+ scale_x_discrete(breaks = seq(0, 23, 4))
+   ggtitle("") +
+#scale_x_discrete(breaks = seq(0, 23, 4))  + theme(
+        theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
 
 p4 <- id4_tsibble %>%
+    create_gran("week_month") %>% 
+  filter(week_month != 5) %>% 
    prob_plot("wknd_wday",
@@
              quantile_prob = c(0.25,0.5,0.75)) +
-  ggtitle("") #+ scale_x_discrete(breaks = seq(0, 23, 4))
+  ggtitle("") +  #+ scale_x_discrete(breaks = seq(0, 23, 4)) + 
+theme(
+        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
 
@@
 
-With reference to the graphical design in \ref{@paper-gravitas}, therefore the idea would be to rate a harmony pair higher if the variation between different levels of the x-axis variable is higher on an average across all levels of the facet variables.
+With reference to the graphical design in \ref{@Gupta2020-vo}, therefore the idea would be to rate a harmony pair higher if the variation between different levels of the x-axis variable is higher on an average across all levels of the facet variables.
 Thus the metric could be obtained by computing maximum pairwise distances between distributions of the continuous random variable across x-axis categories for all facets and then taking the median of those maximum pairwise distances across facets.
@@
 
-Simulation experiments with different designs could help monitor and understand the behavior of the test statistic.
-
-### Impact of different levels from the same distribution of the measured variable (for understanding size)
-
-A 2 way contingency table with number of facet levels, x-axis levels should be constructed with values as the p-values.
-
-Table
-Conclusions
-(in Null distribution)
-
-### Impact of different distribution of the measured variable keeping the same distribution for each
-panel (for understanding size)
-
-To check if different distributions impact, simulate data from different distributions.
+The behavior of the test statistic is monitored and understood through simulation experiments.
+A single simulation consisting of computational operations on a panel generating MMPD the value of which represents to what extent a pair of cyclic granularities would be interesting when displayed in the design.
+In comparing different simulation runs, we distinguish between different distributions and simulation scenarios (also iterations may be).
+
+### Simulated scenarios:
+
+ 1. Same distribution of the measured variable across all x-axis and facet categories
+ 2. Different distribution across x-axis categories but same across facet categories
+ 3. Different distribution across facet categories but same across x-axis categories
+ 4. Different across both x-axis and facet categories 
+ 5. Each of these case scenarios tried against following distribution to check if underlying distribution has a role to play.
+ a) Normal 
+ b) Exponential
+ c) Gamma
+ d) Weibull
+
+### Environment
+
+R version 4.0.1 (2020-06-06) is used with platform: x86_64-apple-darwin17.0 (64-bit) running under: macOS Mojave 10.14.6
+
+### Experimental set up
+
+This section desctibes the design of simulation runs, in terms of the scenarios simulated, the number of permutations used to compute estimates and to display the distribution of MMPD.
+
+ - seed while generating random observations `seed1 = set.seed(9999)`  
+ - grid with how many x levels `range_nx_vec = seq(2:4)`  
+ - grid with how many facet levels `range_nfacet_vec = seq(2:4)`  
+ - number of observations to be generated `ntimes_val = 500`  
+ - number of permutation of data done to compute estimates `nperm_val = 2`  
+ - number of permutations of data done to display histogram for each panel `nsim_val = 10`   
+ - ordered or un-ordered categories of x levels while computing distances `dist_ordered_val = TRUE`  
+ - distance between which quantiles are computed `quantile_prob_vec = seq(0.01, 0.99, 0.01)`  
+- from which distribution observations are drawn for each combination of categories:  
+`sim_norm_null =   distributional::dist_normal(5, 10)`  
+`sim_exp_null  =   distributional::dist_expoential(5)`  
+`sim_gamma_null  =   distributional::dist_gamma(0.5, 2)`  
+`sim_weibull_null  =   distributional::dist_weibull(1.5, 3)`
+
+<!-- To check if different distributions impact, simulate data from different distributions.
 A 3 way contingency table with number of facet levels, x-axis levels and distribution type should be constructed with each cell value as the p-value.
-
-Table
-Conclusions
-(in Null distribution)
-
-### Impact of simulating different distributions across categories for understanding power
-
-#### Varying distribution across facet
-#### Varying distribution across x-axis
-#### Varying distribution across both facets and x-axis
-#### Repeat all with varying facet and x-axis levels
-
-Table
-Conclusions
-(in power)
+-->
+
+<!-- Table -->
+<!-- Conclusions -->
+<!-- (in Null distribution) -->
+
+<!-- #### Varying distribution across facet -->
+<!-- #### Varying distribution across x-axis -->
+<!-- #### Varying distribution across both facets and x-axis -->
+<!-- #### Repeat all with varying facet and x-axis levels -->
+
+<!-- Table -->
+<!-- Conclusions -->
+<!-- (in power) -->
+
+### Interpretation and reporting
+
+A set of simulation runs that are conducted and some outputs of which are reported.
 
@@
 <!-- #  -->
+
+# Visualisation
+
+Leader plots like in Scagnostics paper
 

### 2020-10-15 packages.R

@@ -8,3 +8,8 @@ library(gravitas)
 library(tsibble)
 library(sugrrants)
 library(distributional)
+library(patchwork)
+library(rmarkdown)
+library(tsibble)
+library(ggplot2)
+library(tidyverse)

### 2020-10-15 main.Rmd
deleting old plan

@@
 
+<!-- <introducing the problem> -->
 <!-- background of the problem -->
+Exploratory data analysis involve many iterations of finding and summarizing patterns.
+With temporal data available at ever finer scales, exploring periodicity can become overwhelming with so many possible granularities to explore.
 Take the example of the calendar display of electricity smart meter data used in @wang2020calendar for four households in Melbourne, Australia.
@@
 
-# Summary and discussion
+# Discussion points and future work
+
+Exploratory data analysis involve many iterations of finding and summarizing patterns.
+With temporal data available at ever finer scales, exploring periodicity has become overwhelming with so many possible granularities to explore.
+This work refines the selection of appropriate pairs of granularities by identifying those for which the differences between the displayed distributions is greatest, and rating these selected harmony pairs in order of importance for exploration.
+
+A future direction of work could be to look at more individuals/subjects and group them according to similar periodic behavior.
+Behaviors across different cyclic granularities would be different for different subjects and one way to find groups would be to actually locate clusters who have similar periodic behavior.
+
+<!-- patterns are interesting and others are not.
+The subjects for which behaviors across a group of cyclic granularities are similar, could be grouped together as their periodic behavior is similar.
+to group subjects  -->

### 2020-10-15 main.R

@@ -653,12 +653,12 @@ ptry2 <- sm %>%
   geom_smooth(aes(x = as.numeric(week_month), y = general_supply_kwh), method = "loess", formula = y~x, color = "red", se = TRUE) 
 
 
-p4 <- sm %>% prob_plot("wknd_wday", 
-                       "hour_day",
-                       plot_type = "boxplot") + ggtitle("") +
-  ylab("") + 
-  xlab("") + scale_x_discrete(breaks = c(0,seq(3, 23, 3))) +
-  geom_violin(alpha = 0.3, color = "red") + 
-  geom_smooth(aes(x = as.numeric(hour_day), y = general_supply_kwh), method = "loess", formula = y~x, color = "red", se = TRUE) 
+# p4 <- sm %>% prob_plot("wknd_wday", 
+#                        "hour_day",
+#                        plot_type = "boxplot") + ggtitle("") +
+#   ylab("") + 
+#   xlab("") + scale_x_discrete(breaks = c(0,seq(3, 23, 3))) +
+#   geom_violin(alpha = 0.3, color = "red") + 
+#   geom_smooth(aes(x = as.numeric(hour_day), y = general_supply_kwh), method = "loess", formula = y~x, color = "red", se = TRUE) 
 
 ggarrange(p1, p4, nrow = 2, labels = c("a", "b"))

### 2020-11-05 main.Rmd
fixed some intro

@@
 ---
-title: Median Maximum Pairwise Distance
+title: Selecting and ranking interesting pairs of cyclic temporal granularities
 authors:
@@
 library(kableExtra)
+library(distributional)
+library(ggplot2)
+library(sugrrants)
 
@@
   fig.path = "figure/", fig.align = "center", fig.show = "hold",
-  cache = FALSE, cache.path = "cache/",
+  cache = TRUE, cache.path = "cache/",
   out.width = ifelse(is_html_output(), "100%", "\\textwidth")
@@
 knitr::opts_knit$set(root.dir = here::here())
-read_chunk('main.R')
+#                                                                read_chunk('main.R')
 read_chunk("null_distribution.R")
@@
 source("R/sim_panel.R")
-
 # Set up plan
-source("_drake.R")
+#source("_drake.R")
 # Run all code required
-drake::r_make()
+#drake::r_make()
 # load each object as required
@@
 
-```{r external, include = FALSE}
-
-```
-
-```{r load}
-
-```
-
-```{r load_fun_1var}
-
-```
-
-```{r load_fun_2var}
-
-```
-
-```{r rank_harmony}
-
-```
-
-```{r global_threshold}
-
-```
-
 ```{r}
@@
 
-# Introduction and background
+# Introduction
 
@@
 <!-- background of the problem -->
-Exploratory data analysis involve many iterations of finding and summarizing patterns.
-With temporal data available at ever finer scales, exploring periodicity can become overwhelming with so many possible granularities to explore.
-Take the example of the calendar display of electricity smart meter data used in @wang2020calendar for four households in Melbourne, Australia.
+
+Exploratory data analysis, as coined by John W.
+Tukey (Tukey 1965) involves many iterations of finding structures and patterns that allows the data to be informative.
+With temporal data available at finer scales, exploring periodicity and their relationships can become overwhelming with so many possible cyclic temporal granularities [@Gupta2020-vo] to explore.
+
+```{r calendar-elec, fig.height = 10.5, fig.cap="Calendar display."}
+elec <- read_rds("data/elec.rds") %>% 
+  filter(date >= ymd("20180101"), date < ymd("20180701"))
+rdbl <- c("Weekday" = "#d7191c", "Weekend" = "#2c7bb6")
+
+elec <- elec %>% 
+  mutate(
+    wday = wday(date, label = TRUE, week_start = 1),
+    weekday = if_else(wday %in% c("Sat", "Sun"), "Weekend", "Weekday")
+  )
+p_cal_elec <- elec %>% 
+  frame_calendar(x = time, y = kwh, date = date, nrow = 1) %>% 
+    ggplot(aes(x = .time, y = .kwh, group = date)) +
+    geom_line(aes(colour = as.factor(id)), size = 0.5) +
+    scale_colour_brewer(name = "", palette = "PiYG") +
+    facet_grid(id ~ ., labeller = label_both) +
+    theme(legend.position = "bottom")
+prettify(p_cal_elec, size = 2.5, label.padding = unit(0.1, "lines"))
+```
+
+\noindent Take the example of the calendar display of electricity smart meter data (\ref{fig:calendar-elec}) used in @wang2020calendar for four households in Melbourne, Australia.
 The authors show how hour-of-the-day interact with weekday and weekends and then move on to use calendar display to show daily schedules.
 The calendar display has several components in it, which helps us look at energy consumption across hour-of-the-day, day-of-the-week, week-of-the-month, and month-of-the-year at once.
-Some interaction of these cyclic granularities[@Gupta2020-vo] could also be interpreted from this display.
+Some interaction of these cyclic granularities could also be interpreted from this display.
 This is a great start to have an overview of the energy consumption.
@@
 Moreover, calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions (@Gupta2020-vo) and could include other cyclic granularities like hour-of-week or day-of-fortnight, which could potentially become useful depending on the context.
-Lastly, there might be specific interactions that are interesting and others that are not and that too will vary with different households.
-For example, area distribution quantiles are plotted for household 2 and 4 in Figure ref{fig:}a and b respectively.
-For the first household, the 75th and 90th percentile for Jan, Feb and July are very close, implying that energy usage for these months are generally on a much higher side due to the usage of air conditioners (in Jan and Feb) and heaters (in July).
-The energy consumption for household 2 is also higher relative to its own consumption for Jan, Feb and March but the 75th and 90th percentile are apart implying that contrary to the first household, the second household resorts to air conditioners and heaters much less regularly than the first one.
-Moreover, the 75th percentile distribution is not bimodal across hours of the day for the first household in those months, but the distribution looks similar for all months for the second household.
-Difference in the energy consumption seem to be varying both across month-of-year (facets) and hour-of-day (x-axis).
-And thus, both the cyclic granularities would deem important while studying the periodicities in the first household.
-However, it seems like energy consumption across hours of the day are not that different across different months for the second household.
-Differences seem to be more prominent across month-of-year (facets) than hour-of-day (x-axis).
-Again, look at \ref{fig:} c and d, where energy consumption for these two households are plotted against (weekend/weekday, week-of-month).
-Here, for both households, the pattern of energy consumption vary  across different weeks of the month irrespective of the fact it is a weekday or weekend.
-In that respect, the harmony pair (month-of-year, hour-of-day) seems to be more informative than (weekend/weekday, week-of-month) for the first household.
-It could be immensely useful to make the transition from all possible ways to only ways that could potentially be informative given a household.
-
-<!-- Take an example of a data set which are observed at fine temporal scales, like that of NYC bike usage available at https://www.citibikenyc.com/system-data.
-We use the `nyc_bikes` data set from the R package `tsibbledata` which takes a sample of 10 bikes for the year 2018.
-The `start_time` and the `stop_time` are recorded to a fineness of seconds.
-We can look at pair of cyclic granularities (hour_day, wknd_wday) or (week_month, day_week) to see how these periodicities interact.
-But there could be other pairs that are important too.
-How to understand which pairs are sufficient to explore given the data set without losing much information about the data.
--->
-
-<!-- When we need to understand the interplay of different periodicities in a high frequency temporal datasets, we have many choices to consider.
-In [@wang2019tsibble] and [@wang2020calendar], periodicities are explored across hour of the day and day of the week or months.
-But calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions.
--->
-
-<!-- what is the dimension of the problem -->
-The paper (@Gupta2020-vo) describes how we can compute all possible combinations of cyclic time granularities.
-If we have $n$ periodic linear granularities in the hierarchy table, then $n(n-1)/2$ circular or quasi-circular cyclic granularities could be constructed.
-Let $N_C$ be the total number of contextual circular, quasi-circular and aperiodic cyclic granularities that can originate from the underlying periodic and aperiodic linear granularities.
-The mapping of the graphical elements chosen in the paper implies that, for a numeric response variable, the graphics display distributions across combinations of cyclic granularities, one placed at x-axis and the other on the facet.
-That essentially implies there are $^{N_C}P_2$ possible pairwise plots exhaustively, where each plot would display a pair of cyclic granularities.
-This is large and overwhelming for human consumption.
-
-<!-- Scagnostics literature -->
-This is similar to Scagnostics (Scatterplot Diagnostics)[@mention-paper], which is used to discern meaningful patterns in large collections of scatterplots.
-Given a set of $v$ variables, there are $v(v-1)/2$ pairs of variables, and thus the same number of possible pairwise scatterplots.
-Therefore
-for even small $v$, the number of scatterplots can be
-large, and scatterplot matrices (SPLOMs) could easily run out of pixels when presenting high-dimensional data.
-[@ScagExplorer], [@otherref] provides a solution to this, where few characterizations help us to locate anomalies for further analysis or search for similar distributions in a "large" SPLOM with more than a hundred dimensions.
-
-<!-- harmonies and why it is not enough -->
-The paper (gravitas) narrows down the search from $^{N_C}P_2$ plots by identifying pairs of granularities that can be meaningfully examined together (a "harmony"), or when they cannot (a "clash").
-However, even after excluding clashes, the list of harmonies left could be enormous for exhaustive exploration.
-Hence, there is a need to reduce the search even further by including only those harmonies which are informative enough.
-Also, ranking the remaining harmony pairs based on how well they capture the variation in the measured variable could be potentially useful.
 
 ```{r intro_all}
-elec <- read_rds("data/elec.rds")
 
@@
   ggtitle("") + theme(
-        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
+        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + 
+  scale_colour_brewer(name = "", palette = "PiYG")
 
@@
 
-```{r p1_p2}
+```{r id2, fig.cap = "something"}
 ggpubr::ggarrange(p1, p2, ncol = 2)
@@
 
-```{r p4_p3}
+```{r id4, fig.cap = "something2"}
 ggpubr::ggarrange(p3, p4, ncol = 2)
 ```
+
+Moreover, there might be specific interactions that are interesting and others that are not and that too will vary with different households.
+For example, area distribution quantiles are plotted for household 2 and 4 in Figure \ref{fig:id2}a and b respectively.
+For the first household, the 75th and 90th percentile for Jan, Feb and July are very close, implying that energy usage for these months are generally on a much higher side due to the usage of air conditioners (in Jan and Feb) and heaters (in July).
+The energy consumption for household 2 is also higher relative to its own consumption for Jan, Feb and March but the 75th and 90th percentile are apart implying that contrary to the first household, the second household resorts to air conditioners and heaters much less regularly than the first one.
+Moreover, the 75th percentile distribution is not bimodal across hours of the day for the first household in those months, but the distribution looks similar for all months for the second household.
+Difference in the energy consumption seem to be varying both across month-of-year (facets) and hour-of-day (x-axis).
+And thus, both the cyclic granularities would deem important while studying the periodicities in the first household.
+However, it seems like energy consumption across hours of the day are not that different across different months for the second household.
+Differences seem to be more prominent across month-of-year (facets) than hour-of-day (x-axis).
+Again, look at \ref{fig:} c and d, where energy consumption for these two households are plotted against (weekend/weekday, week-of-month).
+Here, for both households, the pattern of energy consumption vary  across different weeks of the month irrespective of the fact it is a weekday or weekend.
+In that respect, the harmony pair (month-of-year, hour-of-day) seems to be more informative than (weekend/weekday, week-of-month) for the first household.
+It could be immensely useful to make the transition from all possible ways to only ways that could potentially be informative given a household.
+
+<!-- Take an example of a data set which are observed at fine temporal scales, like that of NYC bike usage available at https://www.citibikenyc.com/system-data.
+We use the `nyc_bikes` data set from the R package `tsibbledata` which takes a sample of 10 bikes for the year 2018.
+The `start_time` and the `stop_time` are recorded to a fineness of seconds.
+We can look at pair of cyclic granularities (hour_day, wknd_wday) or (week_month, day_week) to see how these periodicities interact.
+But there could be other pairs that are important too.
+How to understand which pairs are sufficient to explore given the data set without losing much information about the data.
+-->
+
+<!-- When we need to understand the interplay of different periodicities in a high frequency temporal datasets, we have many choices to consider.
+In [@wang2019tsibble] and [@wang2020calendar], periodicities are explored across hour of the day and day of the week or months.
+But calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions.
+-->
+
+<!-- what is the dimension of the problem -->
+The paper @Gupta2020-vo describes how we can compute all possible combinations of cyclic time granularities.
+If we have $n$ periodic linear granularities in the hierarchy table, then $n(n-1)/2$ circular or quasi-circular cyclic granularities could be constructed.
+Let $N_C$ be the total number of contextual circular, quasi-circular and aperiodic cyclic granularities that can originate from the underlying periodic and aperiodic linear granularities.
+The mapping of the graphical elements chosen in the paper implies that, for a numeric response variable, the graphics display distributions across combinations of cyclic granularities, one placed at x-axis and the other on the facet.
+That essentially implies there are $^{N_C}P_2$ possible pairwise plots exhaustively, where each plot would display a pair of cyclic granularities.
+This is large and overwhelming for human consumption.
+
+<!-- Scagnostics literature -->
+This is similar to Scagnostics (Scatterplot Diagnostics) by @tukey1988computer, which is used to discern meaningful patterns in large collections of scatterplots.
+Given a set of $v$ variables, there are $v(v-1)/2$ pairs of variables, and thus the same number of possible pairwise scatterplots.
+Therefore
+for even small $v$, the number of scatterplots can be
+large, and scatterplot matrices (SPLOMs) could easily run out of pixels when presenting high-dimensional data.
+@Dang2014-tw and @wilkinson2005graph provides potential solutions to this, where few characterizations help us to locate anomalies for further analysis or search for similar distributions in a "large" SPLOM with more than a hundred dimensions.
+
+<!-- harmonies and why it is not enough -->
+The paper (@Gupta2020-vo) narrows down the search from $^{N_C}P_2$ plots by identifying pairs of granularities that can be meaningfully examined together (a "harmony"), or when they cannot (a "clash").
+However, even after excluding clashes, the list of harmonies left could be enormous for exhaustive exploration.
+Hence, there is a need to reduce the search even further by including only those harmonies which are informative enough.
+Also, ranking the remaining harmony pairs based on how well they capture the variation in the measured variable could be potentially useful.
 
@@
 
-### Simulated scenarios:
-
- 1. Same distribution of the measured variable across all x-axis and facet categories
- 2. Different distribution across x-axis categories but same across facet categories
- 3. Different distribution across facet categories but same across x-axis categories
- 4. Different across both x-axis and facet categories 
- 5. Each of these case scenarios tried against following distribution to check if underlying distribution has a role to play.
+### Simulated designs:
+
+ D1. Same distribution of the measured variable across all x-axis and facet categories
+ D2. Different distribution across facet categories but same across x-axis categories
+ D3. Different distribution across x-axis categories but same across facet categories
+ D4. Different across both x-axis and facet categories
+
+Each of these case scenarios tried against following distribution to check if underlying distribution has a role to play.
+
  a) Normal 
@@
 
- - seed while generating random observations `seed1 = set.seed(9999)`  
- - grid with how many x levels `range_nx_vec = seq(2:4)`  
- - grid with how many facet levels `range_nfacet_vec = seq(2:4)`  
- - number of observations to be generated `ntimes_val = 500`  
- - number of permutation of data done to compute estimates `nperm_val = 2`  
- - number of permutations of data done to display histogram for each panel `nsim_val = 10`   
- - ordered or un-ordered categories of x levels while computing distances `dist_ordered_val = TRUE`  
- - distance between which quantiles are computed `quantile_prob_vec = seq(0.01, 0.99, 0.01)`  
-- from which distribution observations are drawn for each combination of categories:  
+ <!-- - seed while generating random observations `seed1 = set.seed(9999)`   -->
+ <!-- - grid with how many x levels `range_nx_vec = seq(2:4)`   -->
+ <!-- - grid with how many facet levels `range_nfacet_vec = seq(2:4)`   -->
+ <!-- - number of observations to be generated `ntimes_val = 500`   -->
+ <!-- - number of permutation of data done to compute estimates `nperm_val = 2`   -->
+ <!-- - number of permutations of data done to display histogram for each panel `nsim_val = 10`    -->
+ <!-- - ordered or un-ordered categories of x levels while computing distances `dist_ordered_val = TRUE`   -->
+ <!-- - distance between which quantiles are computed `quantile_prob_vec = seq(0.01, 0.99, 0.01)`   -->
+
+```{r}
+knitr::include_graphics("Figs/simulation.png")
+```
+
+Observations from the null distribution are chosen as:  
 `sim_norm_null =   distributional::dist_normal(5, 10)`  
@@
 
+The various designs are selected by increasing the mean/rate/shape of these distributions proportionally with that parameter.
+
 <!-- To check if different distributions impact, simulate data from different distributions.
@@
 
-### Interpretation and reporting
+### Simulation results
+
+#### Null distribution
+
+Under the null hypothesis, all the combinations of x-axis and facets are obtained from the same distribution.
+We need to study the distribution of the mmpd values under the null hypothesis to see if comparison of their values across different x-axis and facet levels are at all possible.
+
+```{r}
+# all_files = list.files(path = "../hakear-drake/data", pattern = ".rds")
+# all_files
+# 
+# read_files = lapply(all_files, function(x){
+#   read_rds(paste0("../hakear-drake/data/", x))
+# })
+# 
+# names(read_files) = str_remove(all_files, pattern = ".rds")
+# 
+# null_all = bind_rows(normal = read_files$null_normal,
+#                      exponential = read_files$null_exp,
+#                      gamma = read_files$null_gamma,
+#                      weibull = read_files$null_weibull,
+#                      .id = "distribution")
+design_all = readr::read_rds("../hakear-drake/data/design_all.rds")
+
+design_all$design = 
+  factor(design_all$design,
+         levels = c("null","vary_f", "vary_x", "vary_all"), labels = c("D1", "D2", "D3", "D4"))
+
+design_all$distribution = 
+  factor(design_all$distribution,
+         levels = c("normal","exponential", "gamma", "weibull"), labels = c("norm", "exp", "gam", "wei"))
+
+library(dplyr)
+library(ggplot2)
+ggplot2::ggplot(design_all %>% 
+                      filter(design == "D1")) +
+  ggridges::geom_density_ridges(aes(y = distribution, x = mmpd.x, fill = distribution)) + 
+  facet_grid(nx~nfacet) +
+  scale_fill_viridis_d() +
+  xlab("MMPD")
+```
+
+#### Characteristics under different simulation designs
 
 A set of simulation runs that are conducted and some outputs of which are reported.
+
+```{r sim_all, echo = FALSE}
+bind_files = readr::read_rds("../hakear-drake/data/compute_p_value.rds")
+
+bind_files$design = 
+  factor(bind_files$design,
+         levels = c("null","vary_f", "vary_x", "vary_all"), labels = c("D1", "D2", "D3", "D4"))
+
+ggplot(bind_files %>% 
+         filter(distribution == "normal")) +
+  geom_point(aes(x=design, y = p_value),
+                 alpha = 0.5)+
+  facet_grid(nx~nfacet) +
+  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
+
+ggplot(bind_files %>% 
+         filter(distribution == "exponential")) +
+  geom_point(aes(x=design, y = p_value),
+                 alpha = 0.5)+
+  facet_grid(nx~nfacet) +
+  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
+
+ggplot(bind_files %>% 
+         filter(distribution == "gamma")) +
+  geom_point(aes(x=design, y = p_value),
+                 alpha = 0.5)+
+  facet_grid(nx~nfacet) +
+  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
+
+ggplot(bind_files %>% 
+         filter(distribution == "weibull")) +
+  geom_point(aes(x=design, y = p_value),
+                 alpha = 0.5)+
+  facet_grid(nx~nfacet) +
+  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
+```
+
+# confidence interval
+
+```{r sim_conf, echo = FALSE}
+library(dplyr)
+library(ggplot2)
+ggplot2::ggplot(design_all %>% 
+                      filter(design == "D1", distribution == "norm")) +
+  geom_boxplot(aes(x = as.factor(nx), 
+                   y = mmpd.x), width = 0.1) + 
+  facet_wrap(~nfacet) +
+  scale_fill_viridis_d() +
+  xlab("number of x levels") +
+  coord_flip()
+
+```
 

### 2020-11-05 structure.Rmd
fixed some intro

---
title: "Untitled"
author: "Sayani Gupta"
date: "02/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Paper structure

## Title (should be more informative than MMPD): Exploring the most interesting pairs of cyclic temporal granularities

# Introduction

<!-- Data structure for analysis -->
The data structure laid out in paper gravitas for visualizing probability distributions across pairs of cyclic granularities. Why it is important and how it leads to large number of potentially useful displays.

<!-- Motivation -->
With limited human attention span, it could be useful to select displays that are especially informative.

Give an example which you would come back to later to show your metric works

<!-- Earlier work -->
Inspired from John Tukey’s “cognostics” which are diagnostics intended for computer rather than human consumption.

TimeSeer: Scagnostics for High-Dimensional Time Series
presents characterisation which can help locate anomalous or interesting sub-series for further analysis in doubly-multivariate time series.

<!-- Objective:  -->
- Assign a numeric importance “index” to each cognostic and rank the "significant" ones.

# Proposition of the new metric

# Computation and normalisation
Simulation study comes here to show normalization works

# Show the statistics do what you wanted it to do through an example

# Selecting significantly important pairs
Test statistic, size and power

# Application
How it would help in real time data examples

### 2020-11-05 main.Rmd
bounds deleted

@@
 large, and scatterplot matrices (SPLOMs) could easily run out of pixels when presenting high-dimensional data.
-@Dang2014-tw and @wilkinson2005graph provides potential solutions to this, where few characterizations help us to locate anomalies for further analysis or search for similar distributions in a "large" SPLOM with more than a hundred dimensions.
+@Dang2014-tw and @wilkinson2005graph provides potential solutions to this, where few characterizations help us to locate anomalies for defining several measures aimed to detect anomalies in density, shape, trend, and
+other features in the 2D point scatters.
 
@@
 
-# Median Maximum Pairwise Distances (MMPD)
-
-## Principle
+# Proposed measure: Median Maximum Pairwise Distances (MMPD)
+
+We are interested in assessing structure in probability distributions of the measured variable across bivariate cyclic granularities.
+We propose a measure called Median Maximum Pairwise Distances (MMPD) to evaluate structure in such a design.
+
+## Idea
 
@@
 
-## Computation
-
-### Distance between distributions
+# Computation
+
+## Distance between distributions
 
@@
 
-### Normalize distances
+## Normalize distances
 
@@
 
-### Distribution of distances
-
-### Theoretical evidence
-
-JS distances are distributed as chi-squared with $m$ df where we discretize the continuous distribution with $m$ discrete values.
+# Simulation study
+
+<!-- ### Distribution of distances -->
+
+<!-- ### Theoretical evidence -->
+
+<!-- JS distances are distributed as chi-squared with $m$ df where we discretize the continuous distribution with $m$ discrete values.
 Taking sample percentiles to approximate the integral would mean taking $m = 99$.
-With large $m$, chi-squared is asymptotically normal by the CLT.
+-->
+<!-- With large $m$, chi-squared is asymptotically normal by the CLT.
 Thus, by CLT, ${\chi^2}_{m} \tilde{} N(m, 2m)$, which would depend on the number of discretization used to approximate the continuous distribution.
@@
 $n$ is the number of pairwise comparisons being made.
-
-### Empirical evidence
-
-Distribution of JS distances is assumed to be normal but the mean and variance are estimated from the sample, rather than deducing it from the number of discretization used to approximate the continuous distribution.
+-->
+
+<!-- ### Empirical evidence -->
+
+<!-- Distribution of JS distances is assumed to be normal but the mean and variance are estimated from the sample, rather than deducing it from the number of discretization used to approximate the continuous distribution.
 We look at different scenarios, where observations are collected from Normal, Exponential, Chi-squared and Gumbel distribution and found the distribution of JS distances are similar, irrespective of which distribution they are drawn from.
-
-#### Initial distribution of observed variables shown in plot title
+-->
+
+<!-- #### Initial distribution of observed variables shown in plot title -->
 
@@
 
-## Algorithm
+# Algorithm
 
@@
 8. Repeat Steps 1 to 7 for all harmony pairs.
-
-### Bounds
-
-This is not correct because MMPD should be median of standardized Gumbel distribution. So no bound?
-
-By @Lin1991-fj,
-$$ 0 \leq JSD(P||Q) \leq ln(2)$$.
-
-Thus,  $$ 0 \leq MMPD \leq \frac{ln(2)}{ln(k)}$$.
-Now, by assumption $k \geq 2$ and hence,
-<!-- \begin{equation} -->
-<!-- For k = 2, $\frac{ln(2)}{ln(k)} = 1$  -->
-<!-- \end{equation} -->
-<!-- For $k > 2$, $\frac{ln(2)}{ln(k)}  <1$. -->
-
-\[\frac{ln(2)}{ln(k)} : \left\{
-  \begin{array}{lr}
-    1 & if \ k = 2\\
-    <1 & if \ k \ge 2
-  \end{array}
-\right.
-\]
-
-Thus, $$ 0 \leq MMPD \leq \ 1$$
 
@@
   rename("rankun" = "r") %>% kable()
-```
-
-## Design and analysis of simulation experiments
-
-The behavior of the test statistic is monitored and understood through simulation experiments.
-A single simulation consisting of computational operations on a panel generating MMPD the value of which represents to what extent a pair of cyclic granularities would be interesting when displayed in the design.
-In comparing different simulation runs, we distinguish between different distributions and simulation scenarios (also iterations may be).
-
-### Simulated designs:
-
- D1. Same distribution of the measured variable across all x-axis and facet categories
- D2. Different distribution across facet categories but same across x-axis categories
- D3. Different distribution across x-axis categories but same across facet categories
- D4. Different across both x-axis and facet categories
-
-Each of these case scenarios tried against following distribution to check if underlying distribution has a role to play.
-
- a) Normal 
- b) Exponential
- c) Gamma
- d) Weibull
-
-### Environment
-
-R version 4.0.1 (2020-06-06) is used with platform: x86_64-apple-darwin17.0 (64-bit) running under: macOS Mojave 10.14.6
-
-### Experimental set up
-
-This section desctibes the design of simulation runs, in terms of the scenarios simulated, the number of permutations used to compute estimates and to display the distribution of MMPD.
-
- <!-- - seed while generating random observations `seed1 = set.seed(9999)`   -->
- <!-- - grid with how many x levels `range_nx_vec = seq(2:4)`   -->
- <!-- - grid with how many facet levels `range_nfacet_vec = seq(2:4)`   -->
- <!-- - number of observations to be generated `ntimes_val = 500`   -->
- <!-- - number of permutation of data done to compute estimates `nperm_val = 2`   -->
- <!-- - number of permutations of data done to display histogram for each panel `nsim_val = 10`    -->
- <!-- - ordered or un-ordered categories of x levels while computing distances `dist_ordered_val = TRUE`   -->
- <!-- - distance between which quantiles are computed `quantile_prob_vec = seq(0.01, 0.99, 0.01)`   -->
-
-```{r}
-knitr::include_graphics("Figs/simulation.png")
-```
-
-Observations from the null distribution are chosen as:  
-`sim_norm_null =   distributional::dist_normal(5, 10)`  
-`sim_exp_null  =   distributional::dist_expoential(5)`  
-`sim_gamma_null  =   distributional::dist_gamma(0.5, 2)`  
-`sim_weibull_null  =   distributional::dist_weibull(1.5, 3)`
-
-The various designs are selected by increasing the mean/rate/shape of these distributions proportionally with that parameter.
-
-<!-- To check if different distributions impact, simulate data from different distributions.
-A 3 way contingency table with number of facet levels, x-axis levels and distribution type should be constructed with each cell value as the p-value.
--->
-
-<!-- Table -->
-<!-- Conclusions -->
-<!-- (in Null distribution) -->
-
-<!-- #### Varying distribution across facet -->
-<!-- #### Varying distribution across x-axis -->
-<!-- #### Varying distribution across both facets and x-axis -->
-<!-- #### Repeat all with varying facet and x-axis levels -->
-
-<!-- Table -->
-<!-- Conclusions -->
-<!-- (in power) -->
-
-### Simulation results
-
-#### Null distribution
-
-Under the null hypothesis, all the combinations of x-axis and facets are obtained from the same distribution.
-We need to study the distribution of the mmpd values under the null hypothesis to see if comparison of their values across different x-axis and facet levels are at all possible.
-
-```{r}
-# all_files = list.files(path = "../hakear-drake/data", pattern = ".rds")
-# all_files
-# 
-# read_files = lapply(all_files, function(x){
-#   read_rds(paste0("../hakear-drake/data/", x))
-# })
-# 
-# names(read_files) = str_remove(all_files, pattern = ".rds")
-# 
-# null_all = bind_rows(normal = read_files$null_normal,
-#                      exponential = read_files$null_exp,
-#                      gamma = read_files$null_gamma,
-#                      weibull = read_files$null_weibull,
-#                      .id = "distribution")
-design_all = readr::read_rds("../hakear-drake/data/design_all.rds")
-
-design_all$design = 
-  factor(design_all$design,
-         levels = c("null","vary_f", "vary_x", "vary_all"), labels = c("D1", "D2", "D3", "D4"))
-
-design_all$distribution = 
-  factor(design_all$distribution,
-         levels = c("normal","exponential", "gamma", "weibull"), labels = c("norm", "exp", "gam", "wei"))
-
-library(dplyr)
-library(ggplot2)
-ggplot2::ggplot(design_all %>% 
-                      filter(design == "D1")) +
-  ggridges::geom_density_ridges(aes(y = distribution, x = mmpd.x, fill = distribution)) + 
-  facet_grid(nx~nfacet) +
-  scale_fill_viridis_d() +
-  xlab("MMPD")
 ```

### 2020-11-05 main.Rmd
update structure

@@
 p_cal_elec <- elec %>% 
+  filter(id %in% c(2, 4)) %>% 
   frame_calendar(x = time, y = kwh, date = date, nrow = 1) %>% 
@@
     geom_line(aes(colour = as.factor(id)), size = 0.5) +
-    scale_colour_brewer(name = "", palette = "PiYG") +
+    scale_colour_brewer(name = "", palette = "PiYG", direction = -1) +
     facet_grid(id ~ ., labeller = label_both) +
@@
 We propose a measure called Median Maximum Pairwise Distances (MMPD) to evaluate structure in such a design.
-
-## Idea
 
@@
 
-# Simulation study
+## Simulation study
 
@@
 
-# Algorithm
-
-\noindent The algorithm employed for computing MMPD is summarized as follows:
-<!-- Algorithm -->
-
-<!-- 1.
-Suppose $C_i$ and $C_2$ are two cyclic granularities such that $C_i$ maps index set to a set $\{A_1, A_2, A_3, \dots, A_l$\}, and $C_2$ maps index set to a set $\{B_1, B_2, B_3, \dots, B_m$\} and $v$ is the measured variable.
-Hence for each combination ($A_k$, $B_l$), we have the time series variable $v_{ij} \subseteq v$, $\forall i = {1, 2, \dots, l}$ and $\forall j = {1, 2, \dots, m}$ -->
-
-- **Input:** Data corresponding to all harmony pairs, i.e., data sets of the form $(C_i, C_j, v)$ 
-$\forall i, j \in N_C$  
-- **Output:** MMPD (Median Maximum Pairwise Distances) measuring the average variation across different levels of $C_i$ and $C_j$ $\forall i, j \in N_C$
-
-1. Fix harmony pair $(C_i, C_j)$.
-
-2. Fix $k$. Then there are $L$ groups corresponding to level $A_k$ of $C_i$.
-
-3. Compute  $m = \binom{L}{2}$ pairwise distances between distributions of $L$ unordered levels and $m = L-1$ pairwise distances for $L$ ordered categories.
-
-4. Identify maximum within the $m$ computed distances.
-
-5. Compute normalized maximum distance ($NM$) using appropriate norming constants.
-<!--so that the distribution of the normalized maximum converges to a Gumbel distribution as $m\rightarrow\infty$.-->
-
-6. Use Steps 1-5 to compute normalized maximum distance for $\forall k \in  \{1, 2, \ldots, K\}$.
-
-7. Compute MMPD = median $(NM_1, NM_2, \dots, NM_K)$/log($K$).
-
-8. Repeat Steps 1 to 7 for all harmony pairs.
+### Design and analysis of simulation experiments
+
+The behavior of the test statistic is monitored and understood through simulation experiments.
+A single simulation consisting of computational operations on a panel generating MMPD the value of which represents to what extent a pair of cyclic granularities would be interesting when displayed in the design.
+In comparing different simulation runs, we distinguish between different distributions and simulation scenarios (also iterations may be).
+
+#### Simulated designs:
+
+ D1. Same distribution of the measured variable across all x-axis and facet categories
+ D2. Different distribution across facet categories but same across x-axis categories
+ D3. Different distribution across x-axis categories but same across facet categories
+ D4. Different across both x-axis and facet categories
+
+Each of these case scenarios tried against following distribution to check if underlying distribution has a role to play.
+
+ a) Normal 
+ b) Exponential
+ c) Gamma
+ d) Weibull
+
+#### Environment
+
+R version 4.0.1 (2020-06-06) is used with platform: x86_64-apple-darwin17.0 (64-bit) running under: macOS Mojave 10.14.6
+
+#### Experimental set up
+
+This section desctibes the design of simulation runs, in terms of the scenarios simulated, the number of permutations used to compute estimates and to display the distribution of MMPD.
+
+ <!-- - seed while generating random observations `seed1 = set.seed(9999)`   -->
+ <!-- - grid with how many x levels `range_nx_vec = seq(2:4)`   -->
+ <!-- - grid with how many facet levels `range_nfacet_vec = seq(2:4)`   -->
+ <!-- - number of observations to be generated `ntimes_val = 500`   -->
+ <!-- - number of permutation of data done to compute estimates `nperm_val = 2`   -->
+ <!-- - number of permutations of data done to display histogram for each panel `nsim_val = 10`    -->
+ <!-- - ordered or un-ordered categories of x levels while computing distances `dist_ordered_val = TRUE`   -->
+ <!-- - distance between which quantiles are computed `quantile_prob_vec = seq(0.01, 0.99, 0.01)`   -->
+
+```{r}
+knitr::include_graphics("Figs/simulation.png")
+```
+
+Observations from the null distribution are chosen as:  
+`sim_norm_null =   distributional::dist_normal(5, 10)`  
+`sim_exp_null  =   distributional::dist_expoential(5)`  
+`sim_gamma_null  =   distributional::dist_gamma(0.5, 2)`  
+`sim_weibull_null  =   distributional::dist_weibull(1.5, 3)`
+
+The various designs are selected by increasing the mean/rate/shape of these distributions proportionally with that parameter.
+
+<!-- To check if different distributions impact, simulate data from different distributions.
+A 3 way contingency table with number of facet levels, x-axis levels and distribution type should be constructed with each cell value as the p-value.
+-->
+
+<!-- Table -->
+<!-- Conclusions -->
+<!-- (in Null distribution) -->
+
+<!-- #### Varying distribution across facet -->
+<!-- #### Varying distribution across x-axis -->
+<!-- #### Varying distribution across both facets and x-axis -->
+<!-- #### Repeat all with varying facet and x-axis levels -->
+
+<!-- Table -->
+<!-- Conclusions -->
+<!-- (in power) -->
+
+#### Simulation results
+
+##### Null distribution
+
+Under the null hypothesis, all the combinations of x-axis and facets are obtained from the same distribution.
+We need to study the distribution of the mmpd values under the null hypothesis to see if comparison of their values across different x-axis and facet levels are at all possible.
+
+```{r}
+# all_files = list.files(path = "../hakear-drake/data", pattern = ".rds")
+# all_files
+# 
+# read_files = lapply(all_files, function(x){
+#   read_rds(paste0("../hakear-drake/data/", x))
+# })
+# 
+# names(read_files) = str_remove(all_files, pattern = ".rds")
+# 
+# null_all = bind_rows(normal = read_files$null_normal,
+#                      exponential = read_files$null_exp,
+#                      gamma = read_files$null_gamma,
+#                      weibull = read_files$null_weibull,
+#                      .id = "distribution")
+design_all = readr::read_rds("../hakear-drake/data/design_all.rds")
+design_all$design = 
+  factor(design_all$design,
+         levels = c("null","vary_f", "vary_x", "vary_all"), labels = c("D1", "D2", "D3", "D4"))
+design_all$distribution = 
+  factor(design_all$distribution,
+         levels = c("normal","exponential", "gamma", "weibull"), labels = c("norm", "exp", "gam", "wei"))
+library(dplyr)
+library(ggplot2)
+ggplot2::ggplot(design_all %>% 
+                      filter(design == "D1")) +
+  ggridges::geom_density_ridges(aes(y = distribution, x = mmpd.x, fill = distribution)) + 
+  facet_grid(nx~nfacet) +
+  scale_fill_viridis_d() +
+  xlab("MMPD")
+```
 
@@
 
-## Definition
-
-### Algorithm for computation for all harmony pairs
+Algorithm for computation for all harmony pairs
 
@@
 #### Characteristics under different simulation designs   
-
 A set of simulation runs that are conducted and some outputs of which are reported.
@@
 
-# confidence interval
-
-```{r sim_conf, echo = FALSE}
+```{r sim_conf, echo = FALSE, eval = FALSE}
 library(dplyr)
@@
 
-## Power and confidence interval
+## Power
+
+## Confidence interval
 
@@
 <!-- #  -->
+
+# Algorithm
+
+\noindent The algorithm employed for computing MMPD is summarized as follows:
+<!-- Algorithm -->
+
+<!-- 1.
+Suppose $C_i$ and $C_2$ are two cyclic granularities such that $C_i$ maps index set to a set $\{A_1, A_2, A_3, \dots, A_l$\}, and $C_2$ maps index set to a set $\{B_1, B_2, B_3, \dots, B_m$\} and $v$ is the measured variable.
+Hence for each combination ($A_k$, $B_l$), we have the time series variable $v_{ij} \subseteq v$, $\forall i = {1, 2, \dots, l}$ and $\forall j = {1, 2, \dots, m}$ -->
+
+- **Input:** Data corresponding to all harmony pairs, i.e., data sets of the form $(C_i, C_j, v)$ 
+$\forall i, j \in N_C$  
+- **Output:** MMPD (Median Maximum Pairwise Distances) measuring the average variation across different levels of $C_i$ and $C_j$ $\forall i, j \in N_C$
+
+1. Fix harmony pair $(C_i, C_j)$.
+
+2. Fix $k$. Then there are $L$ groups corresponding to level $A_k$ of $C_i$.
+
+3. Compute  $m = \binom{L}{2}$ pairwise distances between distributions of $L$ unordered levels and $m = L-1$ pairwise distances for $L$ ordered categories.
+
+4. Identify maximum within the $m$ computed distances.
+
+5. Compute normalized maximum distance ($NM$) using appropriate norming constants.
+<!--so that the distribution of the normalized maximum converges to a Gumbel distribution as $m\rightarrow\infty$.-->
+
+6. Use Steps 1-5 to compute normalized maximum distance for $\forall k \in  \{1, 2, \ldots, K\}$.
+
+7. Compute MMPD = median $(NM_1, NM_2, \dots, NM_K)$/log($K$).
+
+8. Repeat Steps 1 to 7 for all harmony pairs.
 

### 2020-11-12 main.Rmd
structure cleaned

@@
 
-# Proposed measure: Median Maximum Pairwise Distances (MMPD)
+# Median Maximum Pairwise Distances (MMPD)
 
@@
 We propose a measure called Median Maximum Pairwise Distances (MMPD) to evaluate structure in such a design.
+
+## Idea
 
@@
 
-# Computation
-
-## Distance between distributions
+## Computation
+
+### Distance between distributions
 
@@
 
-### Distribution of Jensen-Shannon distances
+#### Distribution of Jensen-Shannon distances
 
@@
 
-## Simulation study
+## Performance
+
+# Simulation study
 
@@
 
-### Design and analysis of simulation experiments
-
-The behavior of the test statistic is monitored and understood through simulation experiments.
+<!-- ### Design and analysis of simulation experiments -->
+
+The behavior of the measure is monitored and understood through simulation experiments.
 A single simulation consisting of computational operations on a panel generating MMPD the value of which represents to what extent a pair of cyclic granularities would be interesting when displayed in the design.
@@
 
-#### Simulated designs:
+## Simulated designs
 
@@
 
-#### Environment
+## Environment
 
@@
 
-#### Experimental set up
+## Experimental set up
 
@@
 
-#### Simulation results
-
-##### Null distribution
+## Results
+
+### Null distribution
+
+Objective: distribution equal and hence values could be compared and normalisation works
 
@@
 
-Algorithm for computation for all harmony pairs
+## Algorithm
+
+for computation for all harmony pairs
 
@@
 ```
+
+## Size, power and confidence interval
 
@@
 
-## Null distribution
-
-### Size: Simulated same distribution for all combinations of categories for all harmony pairs.
-
-Failure to reject the null hypothesis when there is in fact no significant effect.
-
-### Normalised maximum distances follow standard Gumbel distribution
-
-### Limiting distribution of median of normalised maximum distances is normal
-
-Let a continuous population be given with cdf F(x) (cumulative distribution function) and median $\xi$ (assumed to exist uniquely).
-For a sample of size $2n + 1$, let $\tilde{x}$ denote the sample median.
-The distribution of $\tilde{x}$,under certain conditions, to be asymptotically normal with mean $\xi$ and variance $\sigma_n^2 = \frac{1}{4} [f(\xi)]^2(2n + 1)$, where $f(x) = F'(x)$ is the pdf (probability density function).
-
-<!-- ### Confidence interval of test statistic -->
-
-## Power
-
-## Confidence interval
-
-Failure to reject the null hypothesis when there is in fact a significant effect.
-
-To estimate the sampling distribution of the test statistic we need many samples generated under the null hypothesis.
-If the null hypothesis is true, changing the exposure would have no effect on the outcome.
-By randomly shuffling the exposures we can make up as many data sets as we like.
-If the null hypothesis is true the shuffled data sets should look like the real data, otherwise they should look different from the
-real data. The ranking of the real test statistic among the shuffled test statistics gives a p-value.
-
-<!-- Consider two cyclic granularities $A$ and $B$ with $2$ and $3$categories.
-Thus, the harmony table consisting of all possible harmony pairs (assuming all pairs are harmonies), would look like the following: -->
-
-```{r harmony_min}
-# harmonies <- tibble::tibble(facet_variable = c("A", "B", "A", "C", "B", "C"),
-#                             x_variable  = c("B","A", "C", "A", "C", "B"),
-#                             facet_levels = c(2, 3, 2, 4, 3, 4),
-#                             x_levels = c(3, 2, 4, 2, 4, 3))
-# 
-# harmonies <- tibble::tibble(facet_variable = c("A", "B"),
-#                             x_variable  = c("B","A"),
-#                             facet_levels = c(2, 3),
-#                             x_levels = c(3, 2))
-#                             
-# harmonies %>% knitr::kable()
-```
-
-<!-- The output table has the value of MMPD (normalized median maximum pairwise distances), gt_MMPD(global threshold of MMPD indicator). -->
-
-<!-- # ```{r samenull_2by4, eval = FALSE} -->
-<!-- #  -->
-<!-- # ``` -->
-
-<!-- # ```{r normalv21_power} -->
-<!-- #  -->
-<!-- # ``` -->
-<!-- #  -->
-<!-- #  -->
-<!-- # ```{r normalv22_power} -->
-<!-- #  -->
-<!-- # ``` -->
-
-### Varying distribution across facet
-### Varying distribution across x-axis
-### Varying distribution across both facets and x-axis
-### Repeat all with varying facet and x-axis levels
-
-<!-- ### Power: Simulated same distribution for all combinations of categories for all harmony pairs. -->
-
-<!-- # ```{r normalv23_power} -->
-<!-- #  -->
-<!-- # ``` -->
-<!-- #  -->
-<!-- #  -->
-<!-- # ```{r normalv24_power} -->
-<!-- #  -->
-<!-- # ``` -->
-
-*Conclusion*: The test should reject the null hypothesis if distributions are different.
-
-<!-- ### Scenario 2: Simulated different distributions for all combinations of categories for harmony pairs for few levels. -->
-
-<!-- ```{r diffnull_2by4, eval = FALSE} -->
-
-<!-- ``` -->
-
-<!-- *Conclusion*: The test select the harmony pair for which distribution of x-axis categories are significantly different -->
-
-<!-- ### Scenario 3: Simulated different distributions for all combinations of categories for all harmony pairs with many levels. -->
-
-<!-- ```{r diffnull_7by11, eval = FALSE} -->
-<!-- ``` -->
-
-<!-- *Conclusion*: The test indicates that both harmony pairs do not have significant variation. -->
-
-<!-- ### Scenario 4: Simulated different distributions for all combinations of categories for all harmony pairs with many levels - very different distribution across x-axis -->
-
-<!-- ```{r diffnull_7by11normal, eval = FALSE} -->
-<!-- ``` -->
-
-<!-- *Conclusion*: The test indicates that only the first harmony pair has significant variation. -->
-
-<!-- ### Scenario 5: Simulated different distributions for all combinations of categories for all harmony pairs with many levels - very different distribution across facets -->
-
-<!-- ```{r diffnull_7by11normal2, eval = FALSE} -->
-<!-- ``` -->
-
-<!-- *Conclusion*:  -->
-
-<!-- ## Scenario 4: Cumulative 3 levels with 2, 7 and 11 and testing level and power -->
-
-<!-- ```{r samenull_3levels} -->
-
-<!-- ``` -->
-
-<!-- *Conclusion*: With 3 levels the test incorrectly chooses 1 harmony pair with similar distribution. The harmony pair which is displayed. -->
-
-<!-- <!-- ```{r diffnull_3levels} -->
-
-<!-- <!-- ``` -->
-
-<!-- *Conclusion*: The test with MMPD selects just one pair, as opposed to the test with maximum.
-This needs to be checked against what we expect from the test.
-The harmony pairs which are selected (either through MMPD or maximum) are displayed.
--->
-
-<!-- # ```{r} -->
-<!-- # harmonies <- tibble::tibble(facet_variable = c("A", "B"),x_variable  = c("B","A"), facet_levels = c(2, 3),x_levels = c(3, 2)) -->
-<!-- #  -->
-<!-- # har1 <- harmonies[1,] -->
-<!-- #  -->
-<!-- # sim_dist1 = c(rep(distributional::dist_normal(mu = 10, sigma = 5),2),rep(distributional::dist_exponential(10),2), rep(distributional::dist_weibull(0.5, 2),2)) -->
-<!-- #  -->
-<!-- # data1 <- sim_distharmony1(har1, sim_dist = sim_dist1) -->
-<!-- # data1 -->
-<!-- #  -->
-<!-- # data1 %>% unnest(sim_dist) %>% -->
-<!-- #   ggplot(aes(x = Var2, y = sim_dist)) + -->
-<!-- #   facet_wrap(~Var1) + geom_boxplot() + ggtitle("Same distribution 2 by 3") -->
-<!-- #  -->
-<!-- # response = "sim_dist" -->
-<!-- #  -->
-<!-- # MMPD_distribution <- data1 %>% -->
-<!-- #   select(-dist) %>%  -->
-<!-- #   unnest(sim_dist) %>%  -->
-<!-- #   list() %>%  -->
-<!-- #   global_threshold(harmony_tbl = har1, -->
-<!-- #                    response = "sim_dist", -->
-<!-- #                    dist_distribution = "normal", -->
-<!-- #                    dist_ordered = TRUE, -->
-<!-- #                    create_gran_data = FALSE, nsamp = 20) -->
-<!-- #  -->
-<!-- # # as_tibble(sample_MMPD) %>% mutate(id = row_number()) %>%  -->
-<!-- # #   ggplot() + geom_histogram(aes(x = value)) -->
-<!-- #  -->
-<!-- # ``` -->
-<!-- #  -->
-
 # Algorithm
@@
 8. Repeat Steps 1 to 7 for all harmony pairs.
-
-# Visualisation
-
-Leader plots like in Scagnostics paper
 
@@
 to group subjects  -->
+
+# Appendix
+
+## Null distribution
+
+### Size: Simulated same distribution for all combinations of categories for all harmony pairs.
+
+Failure to reject the null hypothesis when there is in fact no significant effect.
+
+### Normalised maximum distances follow standard Gumbel distribution
+
+### Limiting distribution of median of normalised maximum distances is normal
+
+Let a continuous population be given with cdf F(x) (cumulative distribution function) and median $\xi$ (assumed to exist uniquely).
+For a sample of size $2n + 1$, let $\tilde{x}$ denote the sample median.
+The distribution of $\tilde{x}$,under certain conditions, to be asymptotically normal with mean $\xi$ and variance $\sigma_n^2 = \frac{1}{4} [f(\xi)]^2(2n + 1)$, where $f(x) = F'(x)$ is the pdf (probability density function).
+
+<!-- ### Confidence interval of test statistic -->
+
+## Power
+
+## Confidence interval
+
+Failure to reject the null hypothesis when there is in fact a significant effect.
+
+To estimate the sampling distribution of the test statistic we need many samples generated under the null hypothesis.
+If the null hypothesis is true, changing the exposure would have no effect on the outcome.
+By randomly shuffling the exposures we can make up as many data sets as we like.
+If the null hypothesis is true the shuffled data sets should look like the real data, otherwise they should look different from the
+real data. The ranking of the real test statistic among the shuffled test statistics gives a p-value.
+
+<!-- Consider two cyclic granularities $A$ and $B$ with $2$ and $3$categories.
+Thus, the harmony table consisting of all possible harmony pairs (assuming all pairs are harmonies), would look like the following: -->
+
+```{r harmony_min}
+# harmonies <- tibble::tibble(facet_variable = c("A", "B", "A", "C", "B", "C"),
+#                             x_variable  = c("B","A", "C", "A", "C", "B"),
+#                             facet_levels = c(2, 3, 2, 4, 3, 4),
+#                             x_levels = c(3, 2, 4, 2, 4, 3))
+# 
+# harmonies <- tibble::tibble(facet_variable = c("A", "B"),
+#                             x_variable  = c("B","A"),
+#                             facet_levels = c(2, 3),
+#                             x_levels = c(3, 2))
+#                             
+# harmonies %>% knitr::kable()
+```
+
+<!-- The output table has the value of MMPD (normalized median maximum pairwise distances), gt_MMPD(global threshold of MMPD indicator). -->
+
+<!-- # ```{r samenull_2by4, eval = FALSE} -->
+<!-- #  -->
+<!-- # ``` -->
+
+<!-- # ```{r normalv21_power} -->
+<!-- #  -->
+<!-- # ``` -->
+<!-- #  -->
+<!-- #  -->
+<!-- # ```{r normalv22_power} -->
+<!-- #  -->
+<!-- # ``` -->
+
+### Varying distribution across facet
+### Varying distribution across x-axis
+### Varying distribution across both facets and x-axis
+### Repeat all with varying facet and x-axis levels
+
+<!-- ### Power: Simulated same distribution for all combinations of categories for all harmony pairs. -->
+
+<!-- # ```{r normalv23_power} -->
+<!-- #  -->
+<!-- # ``` -->
+<!-- #  -->
+<!-- #  -->
+<!-- # ```{r normalv24_power} -->
+<!-- #  -->
+<!-- # ``` -->
+
+*Conclusion*: The test should reject the null hypothesis if distributions are different.
+
+<!-- ### Scenario 2: Simulated different distributions for all combinations of categories for harmony pairs for few levels. -->
+
+<!-- ```{r diffnull_2by4, eval = FALSE} -->
+
+<!-- ``` -->
+
+<!-- *Conclusion*: The test select the harmony pair for which distribution of x-axis categories are significantly different -->
+
+<!-- ### Scenario 3: Simulated different distributions for all combinations of categories for all harmony pairs with many levels. -->
+
+<!-- ```{r diffnull_7by11, eval = FALSE} -->
+<!-- ``` -->
+
+<!-- *Conclusion*: The test indicates that both harmony pairs do not have significant variation. -->
+
+<!-- ### Scenario 4: Simulated different distributions for all combinations of categories for all harmony pairs with many levels - very different distribution across x-axis -->
+
+<!-- ```{r diffnull_7by11normal, eval = FALSE} -->
+<!-- ``` -->
+
+<!-- *Conclusion*: The test indicates that only the first harmony pair has significant variation. -->
+
+<!-- ### Scenario 5: Simulated different distributions for all combinations of categories for all harmony pairs with many levels - very different distribution across facets -->
+
+<!-- ```{r diffnull_7by11normal2, eval = FALSE} -->
+<!-- ``` -->
+
+<!-- *Conclusion*:  -->
+
+<!-- ## Scenario 4: Cumulative 3 levels with 2, 7 and 11 and testing level and power -->
+
+<!-- ```{r samenull_3levels} -->
+
+<!-- ``` -->
+
+<!-- *Conclusion*: With 3 levels the test incorrectly chooses 1 harmony pair with similar distribution. The harmony pair which is displayed. -->
+
+<!-- <!-- ```{r diffnull_3levels} -->
+
+<!-- <!-- ``` -->
+
+<!-- *Conclusion*: The test with MMPD selects just one pair, as opposed to the test with maximum.
+This needs to be checked against what we expect from the test.
+The harmony pairs which are selected (either through MMPD or maximum) are displayed.
+-->
+
+<!-- # ```{r} -->
+<!-- # harmonies <- tibble::tibble(facet_variable = c("A", "B"),x_variable  = c("B","A"), facet_levels = c(2, 3),x_levels = c(3, 2)) -->
+<!-- #  -->
+<!-- # har1 <- harmonies[1,] -->
+<!-- #  -->
+<!-- # sim_dist1 = c(rep(distributional::dist_normal(mu = 10, sigma = 5),2),rep(distributional::dist_exponential(10),2), rep(distributional::dist_weibull(0.5, 2),2)) -->
+<!-- #  -->
+<!-- # data1 <- sim_distharmony1(har1, sim_dist = sim_dist1) -->
+<!-- # data1 -->
+<!-- #  -->
+<!-- # data1 %>% unnest(sim_dist) %>% -->
+<!-- #   ggplot(aes(x = Var2, y = sim_dist)) + -->
+<!-- #   facet_wrap(~Var1) + geom_boxplot() + ggtitle("Same distribution 2 by 3") -->
+<!-- #  -->
+<!-- # response = "sim_dist" -->
+<!-- #  -->
+<!-- # MMPD_distribution <- data1 %>% -->
+<!-- #   select(-dist) %>%  -->
+<!-- #   unnest(sim_dist) %>%  -->
+<!-- #   list() %>%  -->
+<!-- #   global_threshold(harmony_tbl = har1, -->
+<!-- #                    response = "sim_dist", -->
+<!-- #                    dist_distribution = "normal", -->
+<!-- #                    dist_ordered = TRUE, -->
+<!-- #                    create_gran_data = FALSE, nsamp = 20) -->
+<!-- #  -->
+<!-- # # as_tibble(sample_MMPD) %>% mutate(id = row_number()) %>%  -->
+<!-- # #   ggplot() + geom_histogram(aes(x = value)) -->
+<!-- #  -->
+<!-- # ``` -->
+<!-- #  -->
+
+<!-- # Visualisation -->
+
+<!-- Leader plots like in Scagnostics paper -->

### 2020-11-12 main.Rmd
add normal and gamma

@@
 
-This section desctibes the design of simulation runs, in terms of the scenarios simulated, the number of permutations used to compute estimates and to display the distribution of MMPD.
+This section describes the design of simulation runs, in terms of the scenarios simulated, the number of permutations used to compute estimates and to display the distribution of MMPD.
 
@@
 `sim_norm_null =   distributional::dist_normal(5, 10)`  
-`sim_exp_null  =   distributional::dist_expoential(5)`  
-`sim_gamma_null  =   distributional::dist_gamma(0.5, 2)`  
-`sim_weibull_null  =   distributional::dist_weibull(1.5, 3)`
+<!--`sim_exp_null  =   distributional::dist_expoential(5)`  -->
+`sim_gamma_null  =   distributional::dist_gamma(0.5, 0.2)`  
+<!--`sim_weibull_null  =   distributional::dist_weibull(1.5, 3)`-->
 
@@
 We need to study the distribution of the mmpd values under the null hypothesis to see if comparison of their values across different x-axis and facet levels are at all possible.
+
+Currently, we see that the normalisation works fine for each facet since the distributions for each column are equal irrespective of the distribution type. But it does not work along the x-axis.
 
@@
 #                      .id = "distribution")
-design_all = readr::read_rds("../hakear-drake/data/design_all.rds")
+# design_all = readr::read_rds("../hakear-drake/data/design_all.rds")
+design_all = readr::read_rds("data/design_all.rds")
+
 design_all$design = 
@@
   factor(design_all$distribution,
-         levels = c("normal","exponential", "gamma", "weibull"), labels = c("norm", "exp", "gam", "wei"))
+         levels = c("normal","gamma"), labels = c("norm","gam"))
 library(dplyr)

### 2020-11-12 main.Rmd
fig update

@@
 
-Objective: distribution equal and hence values could be compared and normalisation works
-
+<!-- Objective: distribution equal and hence values could be compared and normalisation works -->
 Under the null hypothesis, all the combinations of x-axis and facets are obtained from the same distribution.
 We need to study the distribution of the mmpd values under the null hypothesis to see if comparison of their values across different x-axis and facet levels are at all possible.
-
-Currently, we see that the normalisation works fine for each facet since the distributions for each column are equal irrespective of the distribution type. But it does not work along the x-axis.
-
-```{r}
+So, in turn it needs to be checked that if normalisation worked.
+
+Currently, we see in Figure \ref{fig:null-dist} that the normalisation works fine for each facet since the distributions for each column are equal irrespective of the distribution type.
+But it does not work along the x-axis.
+
+```{r null-dist, fig.cap="Distribution of mmpd across different facet levels (columns) and x-axis levels (rows) for null ditribution normal(5,10) and gamma(0.5, 0.2).
+The distribution of MMPD is unaffected by the null distribution considered.
+It is also the same across all facet levels but not across the x-axis, which means normalisation is failing across x-axis."}
 # all_files = list.files(path = "../hakear-drake/data", pattern = ".rds")

### 2020-11-12 main.Rmd
minor update

@@
     geom_line(aes(colour = as.factor(id)), size = 0.5) +
-    scale_colour_brewer(name = "", palette = "PiYG", direction = -1) +
+    scale_colour_brewer(name = "", palette = "Dark2", direction = 1) +
     facet_grid(id ~ ., labeller = label_both) +
@@
 <!-- (in power) -->
+
+## Data Shuffling method
+
+<!-- ```{r} -->
+<!-- raw_data = rnorm(12, 5, 10) %>%  -->
+<!--   as_tibble() %>%  -->
+<!--   mutate(nfacet = rep(1:4, each = 3), -->
+<!--          nx = rep(1:3, 4)) -->
+
+<!-- raw_data %>% group_by(nfacet, nx) %>% nest() -->
+
+<!-- raw_data2 = raw_data %>% pivot_wider(id_cols = 2, names_from = "nx", values_from = "value") -->
+
+<!-- ``` -->
+
+<!--  ### Original -->
+<!-- | facets/x-axis     	| A_1  	| A_2  	| A_3  	| .. 	| .. 	| A_m  	| -->
+<!-- |-----	|------	|------	|------	|----	|----	|------	| -->
+<!-- | B_1 	| x_1 	| x_2 	| x_3 	| .. 	| .. 	| x_n 	| -->
+<!-- | B_2 	| y_1 	| y_2 	| y_3 	| .. 	| .. 	| y_n 	| -->
+<!-- | B_3 	|      	|      	|      	|    	|    	|      	| -->
+<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
+<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
+<!-- | B_L 	| z_1 	| z_2 	| z_3 	| .. 	| .. 	| z_m 	| -->
+
+<!-- ### Step1 -->
+
+<!-- | facets/x-axis     	| A_1  	| A_2  	| A_3  	| .. 	| .. 	| A_m  	| -->
+<!-- |-----	|------	|------	|------	|----	|----	|------	| -->
+<!-- | B_1 	| x_1 	| x_2 	| x_3 	| .. 	| .. 	| x_n 	| -->
+<!-- | B_2 	| y_1 	| y_2 	| y_3 	| .. 	| .. 	| y_n 	| -->
+<!-- | B_3 	|      	|      	|      	|    	|    	|      	| -->
+<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
+<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
+<!-- | B_L 	| z_1 	| z_2 	| z_3 	| .. 	| .. 	| z_m 	| -->
+
+The mean and sd needs to be computed by permuting the data repeatedly. These permutations could be done in several ways given the design.
+
+### Method 1:
+
+All data is repeatedly shuffled $nperm$ times in random manner to obtain the measure $m = median_{facets}(max_{x}dist)$.
+Then the normalised $m$ is obtained by scaling the observed value by the mean and sd of all $m$ obtained from the permutated data.
+
+### Method 2:
+
+$m' = max_{x}dist$ is obtained for each facet.
+All $x$ levels are shuffled for each facet to obtain several $m'$s.
+Hence $m'$ is normalized for each facet level and the facets are aggregated using $m''= median(m')$, which is basically median(norm(max)).
+We need to normalise this median across facets as well.
+So we shuffle all facets for each $x$ level and obtain several $m''$s.
+In this approach, data is shuffled $2*nperm$ times and hence distances are computed $2*nperm$ times.
+It is computationally very intensive.
+
+Hence, it was decided that the first approach will be employed to implement normalisation.
+One of the advantages of the second method could be to have normalisation separately for max and median measure.
+There is nothing that is stopping the users to implement this with more efficient computing power.
+
+```{r}
+# design_time <- readr::read_rds("../hakear-drake/data/design_time.rds")
+# write_rds(design_time, "data/design_time.rds")
+time_data <-readr::read_rds("data/design_time.rds")
+time_data$design = 
+  factor(time_data$design,
+         levels = c("null","vary_f", "vary_x", "vary_all"))
+
+time_data %>% 
+  pivot_longer(cols = c(time_obs, time_dist),
+               names_to = "type",
+               values_to = "time") %>% 
+  dplyr::filter(distribution == "normal") %>% 
+  ggplot(aes(x= design, 
+             y = log(time, exp(1)), 
+             colour = type, group = nfacet)) + geom_point() + geom_line(aes(group = type)) +
+  facet_grid(nx~nfacet) + ylab("ln(time)")
+
+```
 

### 2020-11-17 main.Rmd
computing quantiles

@@
 ## Computation
+
+### Notations
+
+Consider two cyclic granularities $C_i$ and $C_j$, such that $C_i$ maps index set to a set $\{A_k \mid k=1,\dots,K\}$ and $C_j$ maps index set to a set $\{B_\ell \mid \ell =1,\dots,L\}$.
+Here, $A_k$ and $B_\ell$ are the levels/categories corresponding to $C_i$ and $C_j$ respectively.
+Let $S_{k\ell}$ be a subset of the index set such that for all $s \in S_{k\ell}$, $C_i(s) = A_k$ and $C_j(s) = B_\ell$.
+There are $KL$ such data subsets, one for each combination of levels ($A_k$, $B_\ell$).
+Moreover, consider that in the graphical space, $C_i$ is mapped to facets and $C_j$ is mapped to x-axis.
+
+### Estimating distributions
+
+Each of the $KL$ data subsets in the data structure have multiple observations and may vary widely across different subsets due to the structure of the calendar, missing observations or uneven locations of events in the time domain.
+The set of observations corresponding to each combination is assumed to be a sample from an unknown probability density function.
+While the whole population of observations has certain characteristics, we can typically never measure all of them.
+Often shape, central tendency, and variability are the common characteristics used to describe the distribution.
+Another way to describe the probability distribution is through quantiles.
+(Define quantiles here) <!--There are two broad approaches to quantile estimation, viz, parameteric and non-parameteric.
+The benefit of using a non-parametric estimator is that there are less rigid assumptions made about the nature of the underlying distribution of the data.--> Sample quantiles could be thought to estimate the population quantiles.
+But there are a large number of different definitions used for sample quantiles.
+The median-unbiased estimator is recommended (Rob's paper) because of its desirable properties of a quantile estimator and can be defined independently of the underlying distribution.
 

### 2020-11-18 main.Rmd
normalise new results

@@
 
-### Estimating distributions
+### Characterising distribution
 
@@
 
-#### Distribution of Jensen-Shannon distances
-
-Jensen-Shannon distances (JSD) are distributed as chi-squared with $m$ df where we discretize the continuous distribution with $m$ discrete values.
+<!-- #### Distribution of Jensen-Shannon distances -->
+
+<!-- Jensen-Shannon distances (JSD) are distributed as chi-squared with $m$ df where we discretize the continuous distribution with $m$ discrete values.
 Taking sample percentiles to approximate the integral would mean taking $m = 99$.
-With large $m$, chi-squared is asymptotically normal by the CLT.
+-->
+<!-- With large $m$, chi-squared is asymptotically normal by the CLT.
 Thus, by CLT, ${\chi^2}_{m} \tilde{} N(m, 2m)$, which would depend on the number of discretization used to approximate the continuous distribution.
@@
 $n$ is the number of pairwise comparisons being made.
+-->
+
+### Distance measure
+
+The algorithm employed for computing the distance measure is summarized as follows:
+
+1. Fix harmony pair $(C_i, C_j)$.
+
+2. Fix $k$. Then there are $L$ groups corresponding to level $A_k$ of $C_i$.
+
+3. Compute  $m = \binom{L}{2}$ pairwise distances between distributions of $L$ unordered levels and $m = L-1$ pairwise distances for $L$ ordered categories.
+
+4. Identify maximum within the $m$ computed distances.
+
+5. Compute maximum distance ($M$) using appropriate norming constants.
+
+6. Use Steps 1-5 to compute maximum distance for $\forall k \in  \{1, 2, \ldots, K\}$.
+
+7. Compute the distance measure MMPD_raw = median $(M_1, M_2, \dots, M_K)$.
+
+However, median and maximum distances are not robust to the number of levels and the distance measure MMPD_raw would have higher values if $C_i$ or $C_j$ has higher levels.
+Figure \ref{fig:mean-sd-max} shows how distribution of MMPD_raw varies for different levels of $C_i$ and $C_j$.
+In this example, both the cyclic granularities $C_i$ and $C_j$ are considered such that their levels vary in the range $(2, 3, 4, 5,7 ,9, 14, 21, 30, 45)$.
+Each of these combinations is considered a panel for each of which MMPD_raw has been constructed 100 times to compute the distribution.
+This shows that with the increase in the number of levels of $C_i$, the distributions shift rightward and upward.
+With increasing number of levels of x-axis, such a direction is not clear.
+This implies we need to atleast normalise for the levels of the facets so that we could correctly compare MMPD_raw across different combinations.
+
+both mean and standard deviation of the distribution of maximum and median varies for different sample sizes ($n$).
+There is a rightward shift in the location and decrease in scale with increasing $n$.
+
+Thus these median maximum pairwise distances need to be normalized for different harmonies in a way that eliminates the effect of different levels, consequently enabling comparison across different harmonies.
+The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.
 

### 2020-11-18 main.Rmd
update with non-normalised displays

@@
 
-However, median and maximum distances are not robust to the number of levels and the distance measure MMPD_raw would have higher values if $C_i$ or $C_j$ has higher levels.
+However, median and maximum distances are not unaffected by the number of levels and hence the distance measure MMPD_raw, which is a combination of median and maximum would also be influenced by the number of levels.
+It would have higher values if $C_i$ or $C_j$ has higher levels.
+We would ideally want a higher value of the measure if there is significant difference between distributions across facet or x-axis categories, and not because the number of categories are higher.
+From the histogram we could see that th both the shape and scale of the distribution are different when we move across different levels.
+
 Figure \ref{fig:mean-sd-max} shows how distribution of MMPD_raw varies for different levels of $C_i$ and $C_j$.
@@
 The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.
+
+```{r}
+mmpd_raw = read_rds("../hakear-drake/data/data_all23457914n.rds")
+data_long = mmpd_raw %>% pivot_longer(c(1:2), names_to = "category", values_to = "levels")
+
+g1 <- data_long %>%
+filter(category == "nfacet") %>% 
+ggplot() +
+ggridges::geom_density_ridges(aes(x = raw_mmpd, y = as.factor(levels)))  + ylab("facet levels") + xlab("Raw MMPD")
+
+g2 <- data_long %>%
+filter(category == "nx") %>% 
+ggplot() +
+geom_boxplot(aes(x = as.factor(levels) , y = raw_mmpd)) +
+  xlab("x-axis levels") + ylab("Raw MMPD") +  coord_flip()
+
+library(patchwork)
+g1|g2 
+```
+
+```{r hist_plot}
+ hist_plot = mmpd_raw %>% 
+      ggplot() +
+      geom_density(aes(x = raw_mmpd), fill = "blue") +
+      facet_grid(nx~nfacet)
+hist_plot
+```
 

### 2020-11-19 main.Rmd
get mmpd_raw line back

--- 2020-11-18 main.Rmd
@@
 
-However, median and maximum distances are not robust to the number of levels and the distance measure MMPD_raw would have higher values if $C_i$ or $C_j$ has higher levels.
-Figure \ref{fig:mean-sd-max} shows how distribution of MMPD_raw varies for different levels of $C_i$ and $C_j$.
+A stronger measure "max" is chosen for aggregating x-axis categories compared to "median" for aggregating facet categories as the measure is intended to put more importance in pointing towards distributional differences between x-axis categories than for facet categories.
+
+### Need for normalisation
+
+Median and maximum distances are affected by the number of categories considered and hence the distance measure $MMPD_{raw}$, which is a combination of median and maximum would also be influenced by the number of levels.
+It would have higher values if $C_i$ or $C_j$ has higher levels.
+We would ideally want a higher value of the measure if there is significant difference between distributions across facet or x-axis categories, and not because the number of categories are higher.
 In this example, both the cyclic granularities $C_i$ and $C_j$ are considered such that their levels vary in the range $(2, 3, 4, 5,7 ,9, 14, 21, 30, 45)$.
 Each of these combinations is considered a panel for each of which MMPD_raw has been constructed 100 times to compute the distribution.
-This shows that with the increase in the number of levels of $C_i$, the distributions shift rightward and upward.
-With increasing number of levels of x-axis, such a direction is not clear.
-This implies we need to atleast normalise for the levels of the facets so that we could correctly compare MMPD_raw across different combinations.
-
-both mean and standard deviation of the distribution of maximum and median varies for different sample sizes ($n$).
+From the histogram we could see that both the shape and scale of the distribution are different when we move across different levels.
+More specifically, Figure \ref{fig:mean-sd-max} shows the marginal contribution of increasing levels of $C_i$ and $C_j$ on distribution of $MMPD_raw$.
+This shows that with the increase in the number of levels of $C_i$, the location of the distribution shift rightward, whereas for increasing x-axis levels, the scale of the distribution decreases.
+
+This implies we need to eliminate the impact of different levels of the facets and x-axis first and get a normalized measure, so that we could correctly compare $MMPD_{raw}$ across different combinations of facet and x-axis levels.
+
+<!-- both mean and standard deviation of the distribution of maximum and median varies for different sample sizes ($n$).
 There is a rightward shift in the location and decrease in scale with increasing $n$.
+-->
+
+# Normalisation
+
+In an attempt to make the densities \ref{fig:hist_plot} same across different levels, we want to start by making their scale and location same.
+In that regard, we shuffle the data multiple times and compute the sampling distribution of $mmpd_{raw}$ for each combination of facet and x-axis levels.
+
+mmpd_raw = read_rds("../hakear-drake/data/data_all23457914n.rds")
+data_long = mmpd_raw %>% pivot_longer(c(1:2), names_to = "category", values_to = "levels")
+The null hypothesis is that the two cyclic granularities do not differ on the outcome (i.e., that the outcome is observed independently of treatment assignment).
+When we permute the outcome values during the test, we therefore see all of the possible alternative treatment assignments we could have had and where the mean-difference in our observed data falls relative to all of the differences we could have seen if the outcome was independent of treatment assignment.
+While a permutation test requires that we see all possible permutations of the data (which can become quite large), we can easily conduct “approximate permutation tests” by simply conducting a vary large number of resamples.
+That process should, in expectation, approximate the permutation distribution.
+
+Finally, we run some simulation experiments to see if normalisation works. If normalisation has worked, it should work for both x levle and facet-levels.
 
@@
 The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.
+
+```{r hist_plot, fig.cap="density mmpd raw"}
+ hist_plot = mmpd_raw %>% 
+      ggplot() +
+      geom_density(aes(x = raw_mmpd), fill = "blue") +
+      facet_grid(nx~nfacet)
+hist_plot
+```
 

### 2020-11-19 main.Rmd
before structure change where noralisation is one section

@@
 
-mmpd_raw = read_rds("../hakear-drake/data/data_all23457914n.rds")
-data_long = mmpd_raw %>% pivot_longer(c(1:2), names_to = "category", values_to = "levels")
 The null hypothesis is that the two cyclic granularities do not differ on the outcome (i.e., that the outcome is observed independently of treatment assignment).
@@
 
-```{r hist_plot, fig.cap="density mmpd raw"}
- hist_plot = mmpd_raw %>% 
+```{r hist-plot, fig.cap = "density mmpd raw"}
+mmpd_raw = read_rds("../hakear-drake/data/data_all23457914n.rds") 
+mmpd_xmore = read_rds("../hakear-drake/data/data_all213045x.rds") 
+mmpd_fmore = read_rds("../hakear-drake/data/data_all_213045f_allx.rds")
+
+data_all = bind_rows(mmpd_raw, mmpd_xmore, mmpd_fmore)
+
+data_long = data_all %>% pivot_longer(c(1:2), names_to = "category", values_to = "levels")
+
+g1 <- data_all %>% 
+  filter(!(nx %in% c(3, 4))) %>% 
   ggplot() +
-      geom_density(aes(x = raw_mmpd), fill = "blue") +
-      facet_grid(nx~nfacet)
-hist_plot
+  ggridges::geom_density_ridges(aes(x = raw_mmpd, 
+                                    y = as.factor(nfacet))) +
+  facet_wrap(~nx, nrow = 2)
+
+g2 <- data_all %>% 
+  filter(nfacet<=14, nfacet!=3) %>% 
+  ggplot() +
+  geom_boxplot(aes(y = raw_mmpd, 
+                                    x = as.factor(nx))) +
+  facet_wrap(~nfacet) + coord_flip()
+
+#  hist_plot = data_all %>% 
+#       ggplot() +
+#       geom_density(aes(x = raw_mmpd), fill = "blue") +
+#       facet_grid(nx~nfacet)
+# hist_plot
+library(patchwork)
+g1/g2
 ```

### 2020-11-19 main.Rmd
prelude to normalisation built

--- 2020-11-19 main.Rmd
@@
 
-### Need for normalisation
+### Distribution of $MMPD_{raw}$
+<!-- ### Need for normalisation -->
+
+From Figure \ref{fig:dist-across-facets} and \ref{fig:dist-across-x} shows the MMPD distribution is different for different levels of facets and x-axis levels.
+With increasing number of facets, the location of the distribution shift rightwards and with increasing x-axis levels, the scale of the distribution reduces.
 
@@
 We would ideally want a higher value of the measure if there is significant difference between distributions across facet or x-axis categories, and not because the number of categories are higher.
-In this example, both the cyclic granularities $C_i$ and $C_j$ are considered such that their levels vary in the range $(2, 3, 4, 5,7 ,9, 14, 21, 30, 45)$.
-Each of these combinations is considered a panel for each of which MMPD_raw has been constructed 100 times to compute the distribution.
-From the histogram we could see that both the shape and scale of the distribution are different when we move across different levels.
-More specifically, Figure \ref{fig:mean-sd-max} shows the marginal contribution of increasing levels of $C_i$ and $C_j$ on distribution of $MMPD_raw$.
-This shows that with the increase in the number of levels of $C_i$, the location of the distribution shift rightward, whereas for increasing x-axis levels, the scale of the distribution decreases.
-
-This implies we need to eliminate the impact of different levels of the facets and x-axis first and get a normalized measure, so that we could correctly compare $MMPD_{raw}$ across different combinations of facet and x-axis levels.
+In Figures \ref{fig:dist-across-facets} and \ref{fig:dist-across-x}, both the cyclic granularities $C_i$ and $C_j$ are considered such that their levels vary in the range $(2, 5,7 ,9, 14, 21, 30, 45)$.
+Each of these combinations is considered a panel for each of which $MMPD_{raw}$ has been constructed $100$ times to compute the distribution.
+<!--More specifically, Figure \ref{fig:mean-sd-max} shows the marginal contribution of increasing levels of $C_i$ and $C_j$ on distribution of $MMPD_raw$.
+This shows that with the increase in the number of levels of $C_i$, the location of the distribution shift rightward, whereas for increasing x-axis levels, the scale of the distribution decreases.-->
+
+Therefore, in order to compare $MMPD_{raw}$ across different combinations of facet and x-axis levels, we need to eliminate the impact of different levels of the facets and x-axis first and get a normalized measure.
+
+```{r dist-across-facets, fig.cap = "Distribution of $MMPD_{raw}$ for different facet levels are shown.
+The location of the distribution shifts rightwards implying that as the number of facets increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained.
+"}
+mmpd_raw = read_rds("../hakear-drake/data/data_all23457914n.rds") 
+mmpd_xmore = read_rds("../hakear-drake/data/data_all213045x.rds") 
+mmpd_fmore = read_rds("../hakear-drake/data/data_all_213045f_allx.rds")
+
+data_all = bind_rows(mmpd_raw, mmpd_xmore)
+
+data_long = data_all %>% pivot_longer(c(1:2), names_to = "category", values_to = "levels")
+
+g1 <- data_all %>% 
+  filter(!(nx %in% c(3, 4))) %>% 
+  ggplot() +
+  ggridges::geom_density_ridges(aes(x = raw_mmpd, 
+                                    y = as.factor(nfacet))) +
+  facet_wrap(~nx, nrow = 2)
+g1
+```
+
+```{r dist-across-x, fig.cap = "Distribution of $MMPD_{raw}$ for different x levels are shown.
+The scale of the distribution becomes less and less implying that as the number of x levels increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained as the spread of the distribution decreases.
+"}
+g2 <- data_all %>% 
+  filter(nfacet<=14, nfacet!=3) %>% 
+  ggplot() +
+  geom_boxplot(aes(y = raw_mmpd, 
+                                    x = as.factor(nx))) +
+  facet_wrap(~nfacet) + coord_flip()
+
+#  hist_plot = data_all %>% 
+#       ggplot() +
+#       geom_density(aes(x = raw_mmpd), fill = "blue") +
+#       facet_grid(nx~nfacet)
+# hist_plot
+g2
+```
 
@@
 The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.
-
-```{r hist_plot, fig.cap="density mmpd raw"}
- hist_plot = mmpd_raw %>% 
-      ggplot() +
-      geom_density(aes(x = raw_mmpd), fill = "blue") +
-      facet_grid(nx~nfacet)
-hist_plot
-```
 

### 2020-11-19 main.Rmd
normalisation structure

@@
 
-### Distance measure
+### Algorithm
 
@@
 
-### Distribution of $MMPD_{raw}$
+### Distribution
 <!-- ### Need for normalisation -->
@@
 
-### Normalize distances
+## Methodology
 
@@
 
-Median and maximum distances are not robust to the number of levels and the metric would have higher values for harmonies with higher levels.
+<!-- Median and maximum distances are not robust to the number of levels and the metric would have higher values for harmonies with higher levels.
 Figure \ref{fig:mean-sd-max} shows how both mean and standard deviation of the distribution of maximum and median varies for different sample sizes ($n$).
@@
 The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.
-
-More formally, $d_{1},d_{2}\ldots ,d_{n}$ be a sequence of independent and identically-distributed pairwise distances and $M_{n}=\max\{d_{1},\ldots ,d_{n}\}$.
+-->
+
+<!-- More formally, $d_{1},d_{2}\ldots ,d_{n}$ be a sequence of independent and identically-distributed pairwise distances and $M_{n}=\max\{d_{1},\ldots ,d_{n}\}$.
 Then Fisher–Tippett–Gnedenko theorem [@De_Haan2007-yx] suggests that if a sequence of pairs of real numbers $(a_{n}, b_{n})$ exists such that each $a_{n}>0$ and $\lim _{{m\to \infty }}P\left({\frac  {M_{n}-b_{n}}{a_{n}}}\leq x\right)=F(x)$, where $F$ is a non-degenerate distribution function, then the limit distribution $F$ belongs to either the Gumbel, Fréchet or Weibull family.
 The normalizing constants $(a_{n}, b_{n})$ vary depending on the underlying distribution of the pairwise distances.
-Hence to normalize appropriately, it is
-important to assume a distribution of these distances.
-
-For large $n$, the distribution of $M$ approaches a standard shape.
+Hence to normalize appropriately, it is  -->
+<!-- important to assume a distribution of these distances.  -->
+
+<!-- For large $n$, the distribution of $M$ approaches a standard shape.
 But what about the case when $n$ is not large enough?
@@
 Hence, normalisation could be done by bootstrapping procedure to ensure that the distribution of maximum/median have the same mean and variation for varying $n$.
-
-```{r create_simdata}
-
-```
-
-```{r create_nlevels}
-
-```
-
-```{r norm_max_new}
-
-```
-
-```{r mean-sd-max, fig.cap = "Display shows mean and standard deviation of the distribution of maximum for sample sizes ranging from 2 to 30.
-There is a right shift in the distribution of maximum and median with increasing sample sizes."}
-
-library(ggridges)
-library(viridis)
-max_all_data <- create_nlevels(nlevels = seq(2, 30, 2),
-                           nsim = 500,
-                           sim_dist = distributional::dist_normal(5, 10), create_fun = max)
-
-g1 <- max_all_data %>% ggplot() + geom_density_ridges(aes(x=sim_data, y = as.factor(ind))) + ylab("n") + xlab("max")
-
-median_all_data <- create_nlevels(nlevels = seq(2, 30, 2),
-                           nsim = 500,
-                           sim_dist = distributional::dist_normal(5, 10), create_fun = median)
-
-g2 <- max_all_data %>% ggplot() + geom_boxplot(aes(x=sim_data, y = as.factor(ind)))  + ylab("n") + xlab("median")
-
-ggpubr::ggarrange(g1, g2, ncol = 2)
-
-```
-
-## Performance
-
-# Simulation study
+-->
+
+<!-- ```{r create_simdata} -->
+
+<!-- ``` -->
+
+<!-- ```{r create_nlevels} -->
+
+<!-- ``` -->
+
+<!-- ```{r norm_max_new} -->
+
+<!-- ``` -->
+
+<!-- ```{r mean-sd-max, fig.cap = "Display shows mean and standard deviation of the distribution of maximum for sample sizes ranging from 2 to 30.
+There is a right shift in the distribution of maximum and median with increasing sample sizes."} -->
+
+<!-- library(ggridges) -->
+<!-- library(viridis) -->
+<!-- max_all_data <- create_nlevels(nlevels = seq(2, 30, 2), -->
+<!--                            nsim = 500, -->
+<!--                            sim_dist = distributional::dist_normal(5, 10), create_fun = max) -->
+
+<!-- g1 <- max_all_data %>% ggplot() + geom_density_ridges(aes(x=sim_data, y = as.factor(ind))) + ylab("n") + xlab("max") -->
+
+<!-- median_all_data <- create_nlevels(nlevels = seq(2, 30, 2), -->
+<!--                            nsim = 500, -->
+<!--                            sim_dist = distributional::dist_normal(5, 10), create_fun = median) -->
+
+<!-- g2 <- max_all_data %>% ggplot() + geom_boxplot(aes(x=sim_data, y = as.factor(ind)))  + ylab("n") + xlab("median") -->
+
+<!-- ggpubr::ggarrange(g1, g2, ncol = 2) -->
+
+<!-- ``` -->
+
+## Simulation study
 
@@
 
-## Simulated designs
+### Simulated designs
 
@@
 
-## Environment
+### Environment
 
@@
 
-## Experimental set up
+### Experimental set up
 
@@
 
-## Data Shuffling method
+### Data Shuffling method
 
@@
 
-### Method 1:
+#### Method 1:
 
@@
 
-### Method 2:
+#### Method 2:
 
@@
   xlab("MMPD")
+```
+
+### Performance of normalised MMPD
+
+```{r}
+
 ```

### 2020-11-19 main.Rmd
normalisation result update

@@
 
+The mean and sd for each combination of facet and x levels could be computed by shuffling the data repeatedly and obtaining the distribution of $MMPD_{raw}$ for different combinations.
+If $MMPD_{raw}$ is then adjusted by the location and scale of this distribution, we could assume that the distribution of the resultant $MMPD_{norm}$ will have same distribution across different combinations of x and facet levels.
+All data is repeatedly shuffled $nperm$ times in random manner to obtain the measure $MMPD_{raw}$.
+Then the $MMPD_{norm}$ is obtained by scaling the observed value by the mean and sd of the distribution of $MMPD_{raw}$ obtained from the permuted data.
+
+\noindent Step 7 in the Algorithm defined in Section \ref{sec:} need to be revised in order to compute $MMPD_{norm}$ instead of $MMPD_{raw}$.
+Step 1-6 stays the same.
+The entire algorithm will have to repeated for all harmony pairs considered in the context.
+
+A simulation study is conducted to see if this methodology is working.
+
+<!-- #### Method 2: -->
+
+<!-- $m' = max_{x}dist$ is obtained for each facet. -->
+<!-- All $x$ levels are shuffled for each facet to obtain several $m'$s.
+Hence $m'$ is normalized for each facet level and the facets are aggregated using $m''= median(m')$, which is basically median(norm(max)).
+We need to normalise this median across facets as well.
+So we shuffle all facets for each $x$ level and obtain several $m''$s.
+In this approach, data is shuffled $2*nperm$ times and hence distances are computed $2*nperm$ times.
+It is computationally very intensive.
+-->
+
+<!-- Hence, it was decided that the first approach will be employed to implement normalisation.
+One of the advantages of the second method could be to have normalisation separately for max and median measure.
+There is nothing that is stopping the users to implement this with more efficient computing power.
+-->
+
 <!-- The harmony pairs could be arranged from highest to lowest average maximum pairwise distances across different levels of the harmonies. -->
@@
 
-Each of these case scenarios tried against following distribution to check if underlying distribution has a role to play.
-
- a) Normal 
- b) Exponential
- c) Gamma
- d) Weibull
+Each of these case scenarios tried against Normal and a non-normal (Gamma) distribution to check if underlying distribution has a role to play.
 
@@
 
-Observations from the null distribution are chosen as:  
-`sim_norm_null =   distributional::dist_normal(5, 10)`  
-<!--`sim_exp_null  =   distributional::dist_expoential(5)`  -->
-`sim_gamma_null  =   distributional::dist_gamma(0.5, 0.2)`  
-<!--`sim_weibull_null  =   distributional::dist_weibull(1.5, 3)`-->
-
-The various designs are selected by increasing the mean/rate/shape of these distributions proportionally with that parameter.
+Observations from Normal(5, 10) and Gamma(0.5, 0.2) are3 chosen in all the designs.
+
+<!-- . the null distribution are chosen as:   -->
+<!-- `sim_norm_null =   distributional::dist_normal(5, 10)`   -->
+<!-- <!--`sim_exp_null  =   distributional::dist_expoential(5)`  --> -->
+<!-- `sim_gamma_null  =   distributional::dist_gamma(0.5, 0.2)`   -->
+<!-- <!--`sim_weibull_null  =   distributional::dist_weibull(1.5, 3)`-->   -->
+
+<!-- The various designs are selected by increasing the mean/rate/shape of these distributions proportionally with that parameter. -->
 
@@
 <!-- (in power) -->
-
-### Data Shuffling method
 
@@
 
-The mean and sd needs to be computed by permuting the data repeatedly. These permutations could be done in several ways given the design.
-
-#### Method 1:
-
-All data is repeatedly shuffled $nperm$ times in random manner to obtain the measure $m = median_{facets}(max_{x}dist)$.
-Then the normalised $m$ is obtained by scaling the observed value by the mean and sd of all $m$ obtained from the permutated data.
-
-#### Method 2:
-
-$m' = max_{x}dist$ is obtained for each facet.
-All $x$ levels are shuffled for each facet to obtain several $m'$s.
-Hence $m'$ is normalized for each facet level and the facets are aggregated using $m''= median(m')$, which is basically median(norm(max)).
-We need to normalise this median across facets as well.
-So we shuffle all facets for each $x$ level and obtain several $m''$s.
-In this approach, data is shuffled $2*nperm$ times and hence distances are computed $2*nperm$ times.
-It is computationally very intensive.
-
-Hence, it was decided that the first approach will be employed to implement normalisation.
-One of the advantages of the second method could be to have normalisation separately for max and median measure.
-There is nothing that is stopping the users to implement this with more efficient computing power.
-
-```{r}
+```{r, eval = FALSE}
 # design_time <- readr::read_rds("../hakear-drake/data/design_time.rds")
@@
 
-```{r null-dist, fig.cap="Distribution of mmpd across different facet levels (columns) and x-axis levels (rows) for null ditribution normal(5,10) and gamma(0.5, 0.2).
+```{r norm-data, "Distribution of $MMPD_{norm}$ across different levels of facet and x-axis. These distributions should look the same if normalisation worked." }
+mmpd_norm = read_rds("../hakear-drake/data/data_norm_213045f.rds") 
+hist_plot = mmpd_norm %>% 
+      ggplot() +
+      geom_histogram(aes(x = raw_mmpd)) +
+      facet_grid(nx~nfacet)
+hist_plot
+```
+
+```{r null-dist, echo = FALSE, fig.cap="Distribution of mmpd across different facet levels (columns) and x-axis levels (rows) for null ditribution normal(5,10) and gamma(0.5, 0.2).
 The distribution of MMPD is unaffected by the null distribution considered.

### 2020-11-19 main.tex
normalisation result update

@@
-% !TeX program = pdfLaTeX
-\documentclass[12pt]{article}
-\usepackage{amsmath}
-\usepackage{graphicx,psfrag,epsf}
-\usepackage{enumerate}
-\usepackage{natbib}
-\usepackage{textcomp}
-\usepackage[hyphens]{url} % not crucial - just used below for the URL
-\usepackage{hyperref}
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+]{article}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Selecting and ranking interesting pairs of cyclic temporal granularities},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
+\usepackage[margin=1in]{geometry}
+\usepackage{longtable,booktabs}
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\setlength{\emergencystretch}{3em} % prevent overfull lines
 \providecommand{\tightlist}{%
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-%\pdfminorversion=4
-% NOTE: To produce blinded version, replace "0" with "1" below.
-\newcommand{\blind}{0}
-
-% DON'T change margins - should be 1 inch all around.
-\addtolength{\oddsidemargin}{-.5in}%
-\addtolength{\evensidemargin}{-.5in}%
-\addtolength{\textwidth}{1in}%
-\addtolength{\textheight}{1.3in}%
-\addtolength{\topmargin}{-.8in}%
-
-%% load any required packages here
-\setlength {\marginparwidth }{2cm}
-
-\usepackage{mathtools,amssymb,booktabs,longtable,todonotes,amsthm} \def\mod{~\text{mod}~}
-
+\setcounter{secnumdepth}{5}
 \usepackage{booktabs}
@@
 \usepackage{makecell}
-\usepackage{xcolor}
+
+\title{Selecting and ranking interesting pairs of cyclic temporal granularities}
+\author{}
+\date{\vspace{-2.5em}}
 
 \begin{document}
+\maketitle
 
-\def\spacingset#1{\renewcommand{\baselinestretch}%
-{#1}\small\normalsize} \spacingset{1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\if0\blind
 {
-  \title{\bf Visualizing probability distributions across bivariate cyclic temporal granularities}
-
-  \author{
-        Sayani Gupta \thanks{Email: \href{mailto:Sayani.Gupta@monash.edu}{\nolinkurl{Sayani.Gupta@monash.edu}}} \\
-    Department of Econometrics and Business Statistics, Monash University\\
-     and \\     Rob J Hyndman \\
-    Department of Econometrics and Business Statistics, Monash University\\
-     and \\     Dianne Cook \\
-    Department of Econometrics and Business Statistics, Monash University\\
-     and \\     Antony Unwin \\
-    University of Augsburg\\
+\setcounter{tocdepth}{2}
+\tableofcontents
 }
-  \maketitle
-} \fi
-
-\if1\blind
-{
-  \bigskip
-  \bigskip
-  \bigskip
-  \begin{center}
-    {\LARGE\bf Visualizing probability distributions across bivariate cyclic temporal granularities}
-  \end{center}
-  \medskip
-} \fi
-
-\bigskip
-\begin{abstract}
-Deconstructing a time index into time granularities can assist in exploration and automated analysis of large temporal data sets.
-This paper describes several classes of time deconstructions using linear and cyclic time granularities.
-Linear time granularities respect the linear progression of time such as hours, days, weeks and months with respect to a baseline.
-Cyclic time granularities can be circular such as hour of the day, quasi-circular such as day of the month, and aperiodic such as public holidays.
-The hierarchical structure of granularities creates a nested ordering.
-Hour of the day and second of the minute are single-order-up.
-Hour of the week is multiple-order-up, because it passes over day of the week.
-Methods are provided for creating all possible granularities for a time index.
-A recommendation algorithm provides an indication whether a pair of granularities can be meaningfully examined together, called a harmony or when they cannot, called a clash.
-
-The time granularities can be used to create visualizations of the data to explore for periodicities, associations and anomalies.
-The granularities can be considered to be categorical variables (ordered or unordered) which induces a grouping of the observations.
-Assuming a numeric response variable, the resulting graphics are then displays of distributions compared across combinations of categorical variables.
-A recommendation of appropriate distribution display is provided.
-
-The methods are implemented in the open source R package \texttt{gravitas}.
-The functions for creating granularities and exploring the associated time series are consistent with a tidy workflow (\citet{Grolemund2018-po}), and the probability distributions can be examined using the range of graphics available in \texttt{ggplot2} \citep{Wickham2009pk}.
-\end{abstract}
-
-\noindent%
-{\it Keywords:} data visualization, statistical distributions, time granularities, calendar algebra, periodicties, grammar of graphics, R
-\vfill
-
-\newpage
-\spacingset{1.45} % DON'T change the spacing!
-
 \hypertarget{introduction}{%
@@
 
-Temporal data are available at various resolutions depending on the context.
-Social and economic data like GDP is often collected and reported at coarse temporal scales such as monthly, quarterly or annually.
-With recent advancement in technology, more and more data are recorded at much finer temporal scales.
-Energy consumption may be collected every half an hour, energy supply may be collected every minute, and web search data might be recorded every second.
-As the frequency of data increases, the number of questions about the periodicity of the observed variable also increases.
-For example, data collected at an hourly scale can be analyzed using coarser temporal scales such as days, months or quarters.
-This approach requires deconstructing time in various possible ways called time granularities \citep{aigner2011visualization}.
+Exploratory data analysis, as coined by John W.
+Tukey (Tukey 1965) involves many iterations of finding structures and patterns that allows the data to be informative.
+With temporal data available at finer scales, exploring periodicity and their relationships can become overwhelming with so many possible cyclic temporal granularities (Gupta et al.
+2020) to explore.
 
-It is important to be able to navigate through all of these time granularities to have multiple perspectives on the periodicity of the observed data.
-This idea aligns with the notion of EDA \citep{Tukey1977-jx} which emphasizes the use of multiple perspectives on data to help formulate hypotheses before proceeding to hypothesis testing.
-Visualizing probability distributions conditional on one or more granularities is an indispensable tool for exploration.
-Analysts are expected to comprehensively explore the many ways to view and consider temporal data.
-However, the plethora of choices and the lack of a systematic approach to do so quickly becomes overwhelming.
+\begin{figure}
 
-Calendar-based graphics \citep{wang2020calendar} are useful in visualizing patterns in the weekly and monthly structure, and are helpful when checking for the effects of weekends or special days.
-Any temporal data at sub-daily resolution can also be displayed using this type of faceting \citep{Wickham2009pk} with days of the week, month of the year, or another sub-daily deconstruction of time.
-But calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions.
-There can be many different time deconstructions, based on the calendar or on categorizations of time granularities.
+{\centering \includegraphics[width=\textwidth]{figure/calendar-elec-1}
 
-Linear time granularities respect the linear progression of time and are non-repeating such as hours, days, weeks and months.
-One of the first attempts to characterize these granularities is due to \citet{Bettini1998-ed}.
-However, the definitions and rules defined are inadequate for describing cyclic or repeating granularities.
-Hence, there is a need to define some new cyclic time granularities, that can be useful in visualizations.
-Cyclic time granularities can be circular, quasi-circular or aperiodic.
-Examples of circular granularities are hour of the day and day of the week; an example of a quasi-circular granularity is day of the month; examples of aperiodic granularities are public holidays and school holidays.
+}
 
-Time deconstructions can also be based on the hierarchical structure of time.
-For example, hours are nested within days, days within weeks, weeks within months, and so on.
-Hence, it is possible to construct single-order-up granularities such as second of the minute, or multiple-order-up granularities such as second of the hour.
-The lubridate package \citep{Grolemund2011-vm} provides tools to access and manipulate common date-time objects.
-However, most of its accessor functions are limited to single-order-up granularities.
+\caption{Calendar display.}\label{fig:calendar-elec}
+\end{figure}
 
-The motivation for this work stems from the desire to provide methods to better understand large quantities of measurements on energy usage reported by smart meters in households across Australia, and indeed many parts of the world.
-Smart meters currently provide half-hourly use in kWh for each household, from the time that they were installed, some as early as 2012.
-Households are distributed geographically and have different demographic properties such as the existence of solar panels, central heating or air conditioning.
-The behavioral patterns in households vary substantially, for example, some families use a dryer for their clothes while others hang them on a line, and some households might consist of night owls, while others are morning larks.
-It is common to see aggregates \citep[see][]{Goodwin_2012} of usage across households, such as half-hourly total usage by state, because energy companies need to plan for maximum loads on the network.
-But studying overall energy use hides the distribution of usage at finer scales, and makes it more difficult to find solutions to improve energy efficiency.
-We propose that the analysis of smart meter data will benefit from systematically exploring energy consumption by visualizing the probability distributions across different deconstructions of time to find regular patterns/anomalies.
-Although, the motivation came through the smart meter example, this is a problem that is relevant to any temporal data observed more than once per year.
+\noindent Take the example of the calendar display of electricity smart meter data (\ref{fig:calendar-elec}) used in Wang, Cook, and Hyndman (2020) for four households in Melbourne, Australia.
+The authors show how hour-of-the-day interact with weekday and weekends and then move on to use calendar display to show daily schedules.
+The calendar display has several components in it, which helps us look at energy consumption across hour-of-the-day, day-of-the-week, week-of-the-month, and month-of-the-year at once.
+Some interaction of these cyclic granularities could also be interpreted from this display.
+This is a great start to have an overview of the energy consumption.
+However, if one wants to understand the periodicities in energy behavior and how the periodicities interact in greater details, it is not easy to comprehend the interactions of some periodicities' from this display, due to the combination of linear and cyclic representation of time.
+For example, this display might not be the best to understand how hour-of-the-day varies and month-of-year varies across week-of-the-month.
+Further, it is not clear what all interactions of cyclic granularities should be read from this display as there could be many combinations that one can look at.
+Moreover, calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions (Gupta et al.
+(2020)) and could include other cyclic granularities like hour-of-week or day-of-fortnight, which could potentially become useful depending on the context.
 
-This work provides tools for systematically exploring bivariate granularities within the tidy workflow. In particular, we
+\begin{figure}
+
+{\centering \includegraphics[width=\textwidth]{figure/id2-1}
+
+}
+
+\caption{something}\label{fig:id2}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=\textwidth]{figure/id4-1}
+
+}
+
+\caption{something2}\label{fig:id4}
+\end{figure}
+
+Moreover, there might be specific interactions that are interesting and others that are not and that too will vary with different households.
+For example, area distribution quantiles are plotted for household 2 and 4 in Figure \ref{fig:id2}a and b respectively.
+For the first household, the 75th and 90th percentile for Jan, Feb and July are very close, implying that energy usage for these months are generally on a much higher side due to the usage of air conditioners (in Jan and Feb) and heaters (in July).
+The energy consumption for household 2 is also higher relative to its own consumption for Jan, Feb and March but the 75th and 90th percentile are apart implying that contrary to the first household, the second household resorts to air conditioners and heaters much less regularly than the first one.
+Moreover, the 75th percentile distribution is not bimodal across hours of the day for the first household in those months, but the distribution looks similar for all months for the second household.
+Difference in the energy consumption seem to be varying both across month-of-year (facets) and hour-of-day (x-axis).
+And thus, both the cyclic granularities would deem important while studying the periodicities in the first household.
+However, it seems like energy consumption across hours of the day are not that different across different months for the second household.
+Differences seem to be more prominent across month-of-year (facets) than hour-of-day (x-axis).
+Again, look at \ref{fig:} c and d, where energy consumption for these two households are plotted against (weekend/weekday, week-of-month).
+Here, for both households, the pattern of energy consumption vary across different weeks of the month irrespective of the fact it is a weekday or weekend.
+In that respect, the harmony pair (month-of-year, hour-of-day) seems to be more informative than (weekend/weekday, week-of-month) for the first household.
+It could be immensely useful to make the transition from all possible ways to only ways that could potentially be informative given a household.
+
+The paper Gupta et al.
+(2020) describes how we can compute all possible combinations of cyclic time granularities.
+If we have \(n\) periodic linear granularities in the hierarchy table, then \(n(n-1)/2\) circular or quasi-circular cyclic granularities could be constructed.
+Let \(N_C\) be the total number of contextual circular, quasi-circular and aperiodic cyclic granularities that can originate from the underlying periodic and aperiodic linear granularities.
+The mapping of the graphical elements chosen in the paper implies that, for a numeric response variable, the graphics display distributions across combinations of cyclic granularities, one placed at x-axis and the other on the facet.
+That essentially implies there are \(^{N_C}P_2\) possible pairwise plots exhaustively, where each plot would display a pair of cyclic granularities.
+This is large and overwhelming for human consumption.
+
+This is similar to Scagnostics (Scatterplot Diagnostics) by Tukey and Tukey (1988), which is used to discern meaningful patterns in large collections of scatterplots.
+Given a set of \(v\) variables, there are \(v(v-1)/2\) pairs of variables, and thus the same number of possible pairwise scatterplots.
+Therefore
+for even small \(v\), the number of scatterplots can be
+large, and scatterplot matrices (SPLOMs) could easily run out of pixels when presenting high-dimensional data.
+Dang and Wilkinson (2014) and Wilkinson, Anand, and Grossman (2005) provides potential solutions to this, where few characterizations help us to locate anomalies for defining several measures aimed to detect anomalies in density, shape, trend, and
+other features in the 2D point scatters.
+
+The paper (Gupta et al.
+(2020)) narrows down the search from \(^{N_C}P_2\) plots by identifying pairs of granularities that can be meaningfully examined together (a ``harmony''), or when they cannot (a ``clash'').
+However, even after excluding clashes, the list of harmonies left could be enormous for exhaustive exploration.
+Hence, there is a need to reduce the search even further by including only those harmonies which are informative enough.
+Also, ranking the remaining harmony pairs based on how well they capture the variation in the measured variable could be potentially useful.
+
+In this paper, we aim to build a new measure to follow through these two main objectives:
 
@@
 \item
-  provide a formal characterization of cyclic granularities;
+  To choose harmonies for which distributions of categories are significantly different
 \item
-  facilitate manipulation of single- and multiple-order-up time granularities through cyclic calendar algebra;
-\item
-  develop an approach to check the feasibility of creating plots or drawing inferences for any two cyclic granularities;
-\item
-  recommend prospective probability distributions for exploring distributions of a univariate dependent variable across pair of granularities.
+  To rank the selected harmonies from highest to lowest variation in the distribution of their categories.
 \end{itemize}
 
-The remainder of the paper is organized as follows: Section \ref{sec:linear-time} provides some background material on linear granularities and calendar algebra for computing different linear granularities.
-Section \ref{sec:cyclic-gran} formally characterizes different cyclic time granularities by extending the framework of linear time granularities.
-Section \ref{sec:cyclic-calendar} introduces cyclic calendar algebra for computing cyclic time granularities.
-Section \ref{sec:data-structure} discusses the data structure for exploring the conditional distributions of the associated time series across pairs of cyclic time granularities.
-Section \ref{sec:visualization} discusses the role of different factors in constructing an informative and trustworthy visualization.
-Section \ref{sec:application} examines how systematic exploration can be carried out for a temporal and non-temporal application.
-Section \ref{sec:discussion} summarizes this paper and discusses possible future direction.
+\hypertarget{median-maximum-pairwise-distances-mmpd}{%
+\section{Median Maximum Pairwise Distances (MMPD)}\label{median-maximum-pairwise-distances-mmpd}}
 
-\hypertarget{sec:linear-time}{%
-\section{Linear time granularities}\label{sec:linear-time}}
+We are interested in assessing structure in probability distributions of the measured variable across bivariate cyclic granularities.
+We propose a measure called Median Maximum Pairwise Distances (MMPD) to evaluate structure in such a design.
 
-Discrete abstraction of time such as weeks, months or holidays can be thought of as ``time granularities''.
-Time granularities are \textbf{linear} if they respect the linear progression of time.
-There have been several attempts to provide a framework for formally characterizing time granularities, including \citet{Bettini1998-ed} which forms the basis of the work described here.
+\hypertarget{idea}{%
+\subsection{Idea}\label{idea}}
 
-\hypertarget{definitions}{%
-\subsection{Definitions}\label{definitions}}
+The principle employed for building a new metric is explained through a simple example explained in Figure \ref{fig:null4by2}.
+Each of these figures have the same panel design with 2 x-axis categories and 4 facet levels.
+Figure \ref{fig:null4by2}a has all x categories drawn from N(5, 10) distribution for each facet.
+It is not an interesting display particularly, as distributions do not vary across x-axis or facet categories.
+Figure \ref{fig:null4by2}b has x categories drawn from the same distribution within a facet and different for different facet categories.
+Figure \ref{fig:null4by2}b exhibits an exact opposite situation where distribution between the x-axis categories within each facet is different but they are same across facets.
+Figure \ref{fig:null4by2}d takes a step further by varying the distribution across both facet and x-axis categories.
+If we are asked to rank the displays in order of importance from minimum to maximum, we might order it as a, b, c and then d.~It might be argued that it is not clear if b should precede or succeed c.~Gestalt theory suggests that when items are placed in close proximity, people assume that they are in the same group because they are close to one another and apart from other groups.
+Hence, displays that capture more variation within different categories in the same group would be important to bring out different patterns of the data.
+With this principle, display b could be considered less informative as compared to display c.
 
-\newtheorem{definition}{Definition}
-
-\begin{definition}\label{def:definition}
-A {\bf time domain} is a pair $(T; \le)$ where $T$ is a non-empty set of time instants and $\le$ is a total order on $T$.
-\end{definition}
-
-The time domain is assumed to be \emph{discrete}, and there is unique predecessor and successor for every element in the time domain except for the first and last.
-
-\begin{definition}\label{def:index set}
-There is a unique {\bf index set}, $Z=\{z: z \in \mathbb{Z}_{\geq 0}\}$, which map the time instants to a set of non-negative integers. Often, this is thought of as $t=0, \dots, T$.
-\end{definition}
-
-\begin{definition}\label{def:linear}
-A {\bf linear granularity} is a mapping $G$ from the integers (the index set, $Z$) to subsets of the time domain such that:
-  (1) if $i < j$ and $G(i)$ and $G(j)$ are non-empty, then each element of $G(i)$ is less
-than all elements of $G(j)$; and
-  (2) if $i < k < j$ and $G(i)$ and $G(j)$ are non-empty, then $G(k)$ is non-empty.
-Each non-empty subset $G(i)$ is called a {\bf granule}.
-\end{definition}
-
-\noindent This implies that the granules in a linear granularity are non-overlapping, continuous and ordering is maintained.
-The indexing for each granule can also be associated with textual representation, called the label.
-A discrete time model often uses a fixed smallest linear granularity named by \citet{Bettini1998-ed} \textbf{bottom granularity}.
-\autoref{fig:linear-time} illustrates the linear time granularities.
-Here, ``hour'' is the bottom granularity and ``day'', ``week'', ``month'' and ``year'' are linear granularities which maps from index set to subsets of the hourly time domain.
-If we have ``hour'' running from \(\{0, 1, \dots,t\}\), we will have ``day'' running from \(\{0, 1, \dots, \lfloor t/24\rfloor\}\).
-These linear granularities are ordered with ordering guided by the index set which is a set of integers.
-Hence, they are uni-directional and non-repeating.
+With reference to the graphical design in \ref{@Gupta2020-vo}, therefore the idea would be to rate a harmony pair higher if the variation between different levels of the x-axis variable is higher on an average across all levels of the facet variables.
+Thus the metric could be obtained by computing maximum pairwise distances between distributions of the continuous random variable across x-axis categories for all facets and then taking the median of those maximum pairwise distances across facets.
+This would help capture the average maximum difference in distribution of the measurement variable explained by the two cyclic granularities together.
+We call this metric MMPD which stands for Median Maximum Pairwise Distances.
+In the next section we shall see how we go about computing this measure.
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{Figs/linear-ex}
+{\centering \includegraphics[width=\textwidth]{figure/null4by2-1}
 
@@
 
-\caption{Illustration of time domain, linear granularities and index set.
-Hour, day, week, month and year are linear granularities and can also be considered to be time domains.
-These are ordered with ordering guided by integers and hence is unidirectional and non-repeating.
-Hours could also be considered the index set, and a bottom granularity.}\label{fig:linear-time}
+\caption{ A graphical display with two categories mapped to x-axis and 4 categories mapped to facets with the distribution of a continuous random variable plotted on the y-axis.
+Display a is not interesting as the distribution of the continuous rv does not depend across x-axis or facet categories.
+Display b and c are more interesting than a since there is a change in distribution either across facets(b) or x-axis(a).
+Display d is most interesting as distribution of the rv changes across both facet and x-axis variable.}\label{fig:null4by2}
 \end{figure}
-
-\hypertarget{relativities}{%
-\subsection{Relativities}\label{relativities}}
-
-Properties of pairs of granularities fall into various categories.
-
-\begin{definition}\label{def:finerthan}
-A linear granularity $G$ is {\bf finer than} a linear granularity $H$, denoted $G \preceq H$, if for each index $i$, there exists an index $j$ such that
-$G(i) \subset H(j).$
-\end{definition}
-
-\begin{definition}\label{def:groupsinto}
-A linear granularity $G$ {\bf groups into} a linear granularity $H$, denoted
-$G \trianglelefteq H$, if for each index $j$ there exists a (possibly infinite) subset $S$ of the integers such that $H(j) = \bigcup_{i \in S}G(i).$
-\end{definition}
-
-\newtheorem*{example}{Example}
-
-\begin{example}
-{\rm Both $day \trianglelefteq week$ and $day \preceq week$ holds, since every granule of $week$ is the union of some set of granules of day and each day is a subset of a $week$.
-Consider another example where $day \trianglelefteq month$.
-This relationship however is incomplete without its association to periodicity.
-Each month is a grouping of the same number of days over years, hence the period of the grouping $(day, month)$ is one year, if leap years are ignored.
-This grouping period becomes 4 and 400 years with the inclusion of leap years and leap seconds respectively.}
-\end{example}
-
-\begin{definition}\label{def:periodical}
-A granularity $G$ is {\bf periodical} with respect to a granularity $H$ if:
-(1) $G \trianglelefteq H$; and
-(2) there exist $R$, $P \in \mathbb{Z}_+$, where $R$ is less than the number of granules of $H$, such that for all $i \in \mathbb{Z}$, if $H(i) = \bigcup_{j \in S}G(j)$ and $H (i + R) \neq \phi$ then $H (i + R) = \bigcup_{j \in S} G(j + P)$.
-\end{definition}
-
-If \({S_0,\dots,S_{R-1}}\) are the sets of indexes of \(G\) describing
-\(H(0), \dots, H(R - 1)\), respectively, then the description of an arbitrary granule \(H(j)\) is given by \(\bigcup_{i \in S_j ~\text{mod}~R}G(P*\lfloor j/R \rfloor + i)\).
-Also, granularities can be periodical with respect to other granularities, except for a finite number of spans of time where they behave in an anomalous way, called \textbf{quasi-periodic} relationships by \citet{Bettini2000-vy}.
-
-\begin{example}
-{\rm In a Gregorian calendar without leap years we could say $day$ groups periodically into month with the period $P = 365$ and the number of granules of $month$ in each period given by $R=12$.
-In a Gregorian calendar with leap years, $day$ groups quasi-periodically into $month$ with the exceptions of the time domain corresponding to $29^{\text{th}}$ February of any year.}
-\end{example}
-
-\begin{definition}\label{def:order}
-The {\bf order} of a linear granularity is the level of coarseness associated with a linear granularity.
-A linear granularity G will have lower order than H if each granule of G is composed of lower number of granules of bottom granularity than each granule of H.
-\end{definition}
-
-\begin{example}
-{\rm For two linear granularities $G$ and $H$, if $G$ {\em groups into} or {\em finer than} $H$ then $G$ is of lower order than $H$.
-Moreover, if we consider bottom granularity as day, linear granularity week will have lower order than month since each week consist of less number of days than each month.
-Here neither  week {\em groups into} month or  week {\em finer than} month, but their relative order could be determined.}
-\end{example}
 
@@
 
-Granules in bottom granularity or any finer granularity may be aggregated in some manner to form larger granules belonging to a coarser granularity.
-A system of multiple granularities in lattice structures is referred to as a \textbf{calendar} by \citet{Dyreson_2000}.
-Linear time granularities are computed through an algebraic representation for time granularities, which is referred to as calendar algebra \citep{Ning_2002}.
-It is assumed that there exists a \emph{bottom granularity} and calendar algebra operations are designed to generate new granularities recursively from the bottom one.
-Some relevant calendar algebra operations are discussed below; these will be used in Section \ref{sec:cyclic-gran} for illustrations in circular and quasi-circular granularities.
+\hypertarget{notations}{%
+\subsubsection{Notations}\label{notations}}
 
-\begin{definition}\label{def:grouping_operation}
-Let $G_1$ be a full-integer labelled granularity, and $m$ a positive integer.
-{\bf The grouping operation} Group$_m(G)$ generates a new granularity $G_2$, by partitioning the granules of $G_1$ into $m$-granule groups and making each group a granule of the resulting granularity.
-More precisely, $G_2 = \text{Group}_m(G_1)$ is the full-integer labelled granularity such that for each integer $i$,
-$$G_2(i) = \bigcup\limits_{j = (i-1)m+1}^{im} G_1(j).$$
-The grouping operation Group$_m(G)$, provides a new granularity whose granules are the integer part of the quotient when the integer set spanned by linear granularity $G$ is divided by $m$, such that, $G_2(i) = \lfloor G_1(j)/m \rfloor$.
-\end{definition}
+Consider two cyclic granularities \(C_i\) and \(C_j\), such that \(C_i\) maps index set to a set \(\{A_k \mid k=1,\dots,K\}\) and \(C_j\) maps index set to a set \(\{B_\ell \mid \ell =1,\dots,L\}\).
+Here, \(A_k\) and \(B_\ell\) are the levels/categories corresponding to \(C_i\) and \(C_j\) respectively.
+Let \(S_{k\ell}\) be a subset of the index set such that for all \(s \in S_{k\ell}\), \(C_i(s) = A_k\) and \(C_j(s) = B_\ell\).
+There are \(KL\) such data subsets, one for each combination of levels (\(A_k\), \(B_\ell\)).
+Moreover, consider that in the graphical space, \(C_i\) is mapped to facets and \(C_j\) is mapped to x-axis.
 
-\begin{example} 
-{\rm Due to even length of $day$ and $week$, we can derive them from $hour$ using the grouping operation as follows: day = G$_{24}(\text{hour})$, week = G$_{24*7}(\text{hour})$.}
-\end{example}
+\hypertarget{characterising-distribution}{%
+\subsubsection{Characterising distribution}\label{characterising-distribution}}
 
-\noindent For more variations of calendar algebra operations, see \citet{Ning_2002}.
+Each of the \(KL\) data subsets in the data structure have multiple observations and may vary widely across different subsets due to the structure of the calendar, missing observations or uneven locations of events in the time domain.
+The set of observations corresponding to each combination is assumed to be a sample from an unknown probability density function.
+While the whole population of observations has certain characteristics, we can typically never measure all of them.
+Often shape, central tendency, and variability are the common characteristics used to describe the distribution.
+Another way to describe the probability distribution is through quantiles.
+(Define quantiles here) Sample quantiles could be thought to estimate the population quantiles.
+But there are a large number of different definitions used for sample quantiles.
+The median-unbiased estimator is recommended (Rob's paper) because of its desirable properties of a quantile estimator and can be defined independently of the underlying distribution.
 
-\hypertarget{sec:cyclic-gran}{%
-\section{Cyclic time granularities}\label{sec:cyclic-gran}}
+\hypertarget{distance-between-distributions}{%
+\subsubsection{Distance between distributions}\label{distance-between-distributions}}
 
-Cyclic granularities represent cyclical repetitions in time.
-They can be thought of as additional categorizations of time that are not linear.
-Cyclic granularities can be constructed by operating on two linear granularities.
-Cycles can be either \emph{regular}, called \textbf{circular}, or \emph{irregular}, \textbf{quasi-circular} when these two linear granularities relate periodically.
+The most common divergence measure between distributions is the Kullback-Leibler (KL) divergence(Kullback and Leibler 1951) introduced by Solomon Kullback and Richard Leibler in 1951.
+The KL divergence, denoted \(D(p(x), q(x))\) is a non-symmetric measure of the difference between two probability distributions \(p(x)\) and \(q(x)\) and is interpreted as the amount of information lost when \(q(x)\) is used to approximate \(p(x)\).
+Although the KL divergence measures the ``distance'' between two distributions, it is not a distance measure since it is not symmetric and does not satisfy the triangle inequality.
+The Jensen-Shannon divergence (Menéndez et al.
+1997) based on the Kullback-Leibler divergence is symmetric and it always has a finite value.
+The square root of the Jensen-Shannon divergence is a metric, often referred to as Jensen-Shannon distance.
+Other common measures of distance are Hellinger distance, total variation distance and Fisher information metric.
 
-\hypertarget{sec:circular-gran-def}{%
-\subsection{Circular}\label{sec:circular-gran-def}}
+In the context of this paper, the pairwise distances between the distributions of the measured variable are computed through Jensen-Shannon distance (JSD) which is based on Kullback-Leibler divergence and is defined by,
 
-\begin{definition}\label{def:circular}
-A {\bf circular granularity} $C_{B, G}$ relates a linear granularity $G$ to the bottom granularity B, if
-\begin{equation} \label{eq:circular-gran}
-\begin{split}
-C_{B, G}(z) & = z~\text{mod}~P(B, G) \quad \forall z \in \mathbb{Z}_{\geq 0} \\
-\end{split}
-\end{equation}
-where
-z denotes the index set,
-B denotes a full-integer labelled bottom granularity which groups periodically into linear granularity $G$ with regular mapping, and $P \equiv P(B, G)$ is the number of granules of $B$ in each granule of $G$, also called the period of the grouping $(B, G)$.
-\end{definition}
+\[JSD(P||Q) = \frac{1}{2}D(P||M) + \frac{1}{2}D(Q||M)\]
+where \(M = \frac{P+Q}{2}\) and
+\(D(P||Q) := \int^\infty_{-\infty} p(x)f(\frac{p(x)}{q(x)})\) is the KL divergence between distributions \(p(x)\) and \(q(x)\).
+Probability distributions are estimated through quantiles instead of kernel density so that there is minimal dependency on selecting kernel or bandwidth.
 
-\begin{example}
-{\rm \autoref{fig:circular-dow} illustrates the linear and the corresponding cyclical granularities.
-Cyclical granularities can be considered to be cutting the linear granularity into pieces, and stacking them to match the cycles (as shown in b).
-$B, G, H$ (day, week, fortnight, respectively) are linear granularities.
-The circular granularity $C_{B , G}$ (day-of-week)is constructed from $B$ and  $G$.
-The circular granularity $C_{B, H}$ (day-of-fortnight) is constructed from $B$ and $H$.
-These overlapping cyclical granularities share elements from the linear granularity.
-Each of $C_{B , G}$ and $C_{B , H}$ consist of repeated patterns  $\{0, 1, 2, \dots, 6\}$ and $\{0, 1, 2, \dots, 13\}$ with $P=7$ and $P=14$ respectively.
-Each circular granularity can use descriptive label mappings.
-Suppose ${L}$ is a label mapping that defines an unique label for each index $l \in \{ 0,1,\dots, (P-1)\}$, then the label mapping $L$ for $C_{B, G}$ can be defined as
-$$
-  L: \{0,1,2, \dots, 6\} \longmapsto\ \{\text{Sun}, \text{Mon}, \dots, \text{Sat}\}
-$$
-or
-$$
-  L: \{0,1,2, \dots, 6\} \longmapsto\ \{\text{Sunday}, \text{Monday}, \dots, \text{Saturday}\}
-$$
-for example.}
-\end{example}
+\hypertarget{algorithm}{%
+\subsubsection{Algorithm}\label{algorithm}}
+
+The algorithm employed for computing the distance measure is summarized as follows:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  Fix harmony pair \((C_i, C_j)\).
+\item
+  Fix \(k\). Then there are \(L\) groups corresponding to level \(A_k\) of \(C_i\).
+\item
+  Compute \(m = \binom{L}{2}\) pairwise distances between distributions of \(L\) unordered levels and \(m = L-1\) pairwise distances for \(L\) ordered categories.
+\item
+  Identify maximum within the \(m\) computed distances.
+\item
+  Compute maximum distance (\(M\)) using appropriate norming constants.
+\item
+  Use Steps 1-5 to compute maximum distance for \(\forall k \in \{1, 2, \ldots, K\}\).
+\item
+  Compute the distance measure MMPD\_raw = median \((M_1, M_2, \dots, M_K)\).
+\end{enumerate}
+
+A stronger measure ``max'' is chosen for aggregating x-axis categories compared to ``median'' for aggregating facet categories as the measure is intended to put more importance in pointing towards distributional differences between x-axis categories than for facet categories.
+
+\hypertarget{distribution}{%
+\subsubsection{Distribution}\label{distribution}}
+
+From Figure \ref{fig:dist-across-facets} and \ref{fig:dist-across-x} shows the MMPD distribution is different for different levels of facets and x-axis levels.
+With increasing number of facets, the location of the distribution shift rightwards and with increasing x-axis levels, the scale of the distribution reduces.
+
+Median and maximum distances are affected by the number of categories considered and hence the distance measure \(MMPD_{raw}\), which is a combination of median and maximum would also be influenced by the number of levels.
+It would have higher values if \(C_i\) or \(C_j\) has higher levels.
+We would ideally want a higher value of the measure if there is significant difference between distributions across facet or x-axis categories, and not because the number of categories are higher.
+In Figures \ref{fig:dist-across-facets} and \ref{fig:dist-across-x}, both the cyclic granularities \(C_i\) and \(C_j\) are considered such that their levels vary in the range \((2, 5,7 ,9, 14, 21, 30, 45)\).
+Each of these combinations is considered a panel for each of which \(MMPD_{raw}\) has been constructed \(100\) times to compute the distribution.
+
+Therefore, in order to compare \(MMPD_{raw}\) across different combinations of facet and x-axis levels, we need to eliminate the impact of different levels of the facets and x-axis first and get a normalized measure.
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{Figs/circular-ex}
+{\centering \includegraphics[width=\textwidth]{figure/dist-across-facets-1}
 
@@
 
-\caption{Illustration of circular relative to linear granularities (a).
-Circular granularities can be considered to be cutting the linear granularity into pieces and stacking them (b).
-The circular granularity creates repeated integer sequences.}\label{fig:circular-dow}
+\caption{Distribution of $MMPD_{raw}$ for different facet levels are shown.
+The location of the distribution shifts rightwards implying that as the number of facets increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained.
+}\label{fig:dist-across-facets}
 \end{figure}
-
-In general, any circular granularity relating two linear granularity can be expressed as \(C_{(G, H)}(z) = \lfloor z/P(B,G) \rfloor~\text{mod}~P(G,H)\), where linear granularity \(H\) is periodic with respect to linear granularity \(G\) with regular mapping and \(P(G,H)\) is the period of the grouping \((G, H)\) .
-Table \ref{tab:definitions} shows representation of circular granularities \(C_i\) relating two linear granularities with period \(P_i\) and minutes as the bottom granularity.
-
-\begin{table}[ht]
-\begin{center}
-\begin{tabular}{lll}
-\hline
-circular granularity & expression & period \\
-\hline
-minute-of-hour                               &
-  $C_1 = z ~\text{mod}~60$                     &
-  $P_1 = \phantom{99}60$ \\
-minute-of-day                                &
-  $C_j = z ~\text{mod}~60*24$                  &
-  $P_2= 1440$\\
-hour-of-day                                  &
-  $C_3 = \lfloor z/60\rfloor~\text{mod}~24$    &
-  $P_3 = \phantom{99}24$ \\
-hour-of-week                                 &
-  $C_4 = \lfloor z/60\rfloor~\text{mod}~24*7$  &
-  $P_4= \phantom{9}168$\\
-day-of-week                                  &
-  $C_5 = \lfloor z/24*60\rfloor ~\text{mod}~7$ &
-  $P_5= \phantom{999}7$\\
-\bottomrule
-\end{tabular}
-\end{center}
-\caption{Examples of circular granularities with bottom granularity minutes.
-Circular granularity $C_i$ relates two linear granularities one of which groups periodically into the other with regular mapping and period $P_i$.
-Circular granularities can be expressed using modular arithmetic due to their regular mapping.
-}
-\label{tab:definitions}
-\end{table}
-
-\hypertarget{sec:quasi-circular-gran-def}{%
-\subsection{Quasi-circular}\label{sec:quasi-circular-gran-def}}
-
-A \textbf{quasi-circular} granularity can not be defined using modular arithmetic since they are formed using two linear granularities with irregular mapping.
-However, they are still formed with linear granularities, one of which ``groups periodically into'' the other.
-\autoref{tab:quasi} shows some example of quasi-circular granularities (\(Q_i\)) with (\(P_i\)) denoting the plausible choices of period of the grouping of two linear granularities.
-
-\begin{table}[ht]
-\begin{center}
-\begin{tabular}{lr@{~}lr@{~}r}
-\hline
-quasi-circular granularity && potential period lengths\\
-\hline
-$Q_1 =$ day-of-month && $P_1 = 31, 30, 29, 28$\\
-$Q_2 =$ hour-of-month && $P_2 = 24*31, 24*30, 24*29, 24*28$\\
-$Q_3 =$ day-of-year && $P_3 = 366, 365$\\
-$Q_4 =$ week-of-month && $P_4 = 5, 4$\\
-\bottomrule
-\end{tabular}
-\end{center}
-\caption{Examples of quasi-circular granularities $Q_i$ with potential period lengths $P_i$.
-These quasi-circular granularities relate two linear granularities one of which groups periodically into the other with irregular mapping leading to many potential period lengths and hence can not be expressed through modular arithmetic.
-}
-\label{tab:quasi}
-\end{table}
-
-\begin{definition}\label{def:quasicircular}
-A {\bf quasi-circular granularity} $Q_{B, G'}$ relates linear granularities $G'$ and bottom granularity $B$, if
-\begin{equation}\label{eq:quasi}
-\begin{split}
-Q_{B, G'}(z) =
-z - \sum_{w=0}^{k-1}\vert T_{w ~\text{mod}~R'} \vert, & \quad \text{for}\quad z \in T_{k}
-\end{split}
-\end{equation}
-where,
-$z \in \mathbb{Z}_{\geq 0}$ denotes the index set,
-$B$ denotes a full-integer labelled bottom granularity which groups periodically into linear granularity $G'$ with irregular mapping, $P'$ and $R'$ are the period of the grouping $(B, G')$ and the number of granules of $G'$ in $P'$, $T_w$ are the sets of indices of $B$ describing $G'(w)$ such that  $G'(w) = \bigcup_{z \in T_w}B(z)$ and $\vert T_w \vert$ is the cardinality of set $T_w$.
-\end{definition}
-
-\begin{example}
-{\rm Consider $G'$ such that every two consecutive granules of $G'$ are made up of $7$ and $5$ granules of $B$ respectively within each period of the grouping ($B$, $G'$).
-Then $Q_{B, G'}$ is a repetitive categorization of time, similar to circular granularities, except that the number of granules of $B$ is not necessarily the same across different granules of $G'$.
-Here, $T_0 = \{0, 1, 2, 3, 4, 5, 6\}$ and $T_1 = \{7, 8, 9, 10, 11\}$.
-Hence using Definition \autoref{def:quasicircular} we will have:
-
-\begin{align*}
-\begin{split}
-Q_{B,H'}(10) & = 10 - \sum_{w=0}^{1-1}\vert T_{w ~\text{mod}~2}\vert ,\quad since \quad 10 \in T_{1}  \\
-  & = 3 \\
-\end{split}
-\end{align*}
-}
-\end{example}
-
-If linear granularity \(G'\) is periodical with respect to \(B\) with irregular mapping, then there exist \(R'\), \(P' \in \mathbb{Z}_+\) such that if \(G'(w) = \bigcup_{z \in T_w}B(z)\) then \[G'(w) = \bigcup_{z \in T_w ~\text{mod}~R'}B(P'*\lfloor w/R' \rfloor + z)\] (from Definition \ref{def:periodical}) .
-Here \(w ~\text{mod}~R'\) represents the index that must be shifted to obtain \(G'(w)\).
-The idea here is if we know the composition of each of the granules of \(G'\) in terms of granules of \(B\) for one period, we can find the composition of any granule of \(G'\) beyond a period since the ``pattern'' repeats itself along the time domain due to the periodic property.
-The periodic property also ensures that \(\vert T_w \vert = \vert T_{w~\text{mod}~R'} \vert\) since every \(w^{\text{th}}\) and \((w+R')^{\text{th}}\) granule of \(G'\) will have the same number of granules of \(B\).
-The term \(\sum_{w=0}^{k-1}\vert T_{w}\vert\) in Definition \autoref{def:quasicircular} denotes the number of granules of \(B\) till the \((k-1)^{\text{th}}\) granule of \(G'\).
-Since \(\vert T_w \vert = \vert T_{w~\text{mod}~R'} \vert\), the number of granules of \(B\) till the \((k-1)^{\text{th}}\) granule of \(G'\) becomes \(\sum_{w=0}^{k-1}\vert T_{w ~\text{mod}~R'}\vert\) in Definition \autoref{def:quasicircular}.
-
-\hypertarget{sec:aperiodic-gran-def}{%
-\subsection{Aperiodic}\label{sec:aperiodic-gran-def}}
-
-Aperiodic time granularities are the ones which can not be specified as a periodic repetition of a pattern of granules.
-Most public holidays repeat every year, but there is no reasonably small period within which their behavior remains constant.
-A classic example can be that of Easter, whose dates repeat only after 5,700,000 years.
-In Australia, if a standard public holiday falls on a weekend, a substitute public holiday will sometimes be observed on the first non-weekend day (usually Monday) after the weekend.
-Examples of aperiodic granularity may also include school holidays or a scheduled event.
-All of these are recurring events, but with non-periodic patterns.
-As such, plausible \(P_i\) from \autoref{tab:quasi} could be possibly infinite for aperiodic granularities.
-
-\noindent Aperiodic cyclic granularities are defined using aperiodic linear granularities.
-Consider n aperiodic linear granularities \(M_i\) \(\forall \{i\in{1, 2, \dots, n\}}\) such that Definition \ref{def:periodical} does not hold true with respect to \(B\).
-However, \(B \trianglelefteq M_i\) \(\forall \{i\in{1, 2, \dots, n\}}\).
-Then according to Definition \ref{def:groupsinto}, for each index \(j\) there exists a (possibly infinite) subset \(T_{\{i_j\}}\) of the integers such that \(M_{i}(j) = \bigcup_{z \in T_{i_j}}B(z)\).
-Suppose \(M = \bigcup_{i=1}^{n}M_{i}\) is formed by collecting the granules of \(\{M_1, M_2, \dots, M_n\}\).
-Here, index \({\{i_j\}}\) stands for the \(j^{\text{th}}\) granule of the \(i^{\text{th}}\) linear aperiodic granularity.
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{Figs/aperiodic-ex3}
+{\centering \includegraphics[width=\textwidth]{figure/dist-across-x-1}
 
@@
 
-\caption{Quasi-circular and aperiodic cyclic granularities illustrated through linear (a) and stack (b) display of time.
-The linear display shows linear granularities days, weeks, semester weeks, semester week type distributed linearly from past to future.
-Here a semester lasts for 18.3 weeks, each starting with one week of orientation followed by an in-session period of 6 weeks, a semester-break of 1 week and again an in-session period of 7 weeks and 1 week study break before final exams which continue for 1.3 weeks.
-This pattern remains same for all semester and hence \(Q_{H, M}\) with \(P\) = 18.3 weeks will be a quasi-circular granularity with repeating patterns.
-\(A_{B, M}\) will be an aperiodic cyclic granularity since the placement of the semester within an year varies across years.}\label{fig:aperiodic-example}
+\caption{Distribution of $MMPD_{raw}$ for different x levels are shown.
+The scale of the distribution becomes less and less implying that as the number of x levels increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained as the spread of the distribution decreases.
+}\label{fig:dist-across-x}
 \end{figure}
 
-\begin{definition}\label{def:aperiodic}
-An {\bf aperiodic cyclic granularity} $A_{B, M}$ relates a linear granularity $M$ to the bottom granularity $B$, if
-\begin{equation}\label{eq:aperiodic}
-\begin{split}
-A_{B, M}(z) & =
-\begin{cases}
-i, & \text{for}\quad z \in T_{i_j} \\
-0  & \text{otherwise}
-\end{cases}
-\end{split}
-\end{equation}
-where,
-$z \in \mathbb{Z}_{\geq 0}$ denotes the index set,
-$B$ denotes a full-integer labelled bottom granularity which groups into linear granularity $M$ but not periodically, $T_{i_j}$ are the sets of indices of $B$ describing aperiodic linear granularities $M_{i}$ such that $M_{i}(j) = \bigcup_{z \in T_{i_j}}B(z)$, and $M = \bigcup_{i=1}^{n}M_{i}$.
-\end{definition}
+\hypertarget{normalisation}{%
+\section{Normalisation}\label{normalisation}}
 
-\begin{example}
-{\rm Consider a school semester which always lasts for 18 weeks and 2 days, starting with one week of orientation followed by an in-session period of 6 weeks, a semester-break of 1 week and again an in-session period of 7 weeks and 1 week study break before final exams which continue for 16 days.
-Let the linear granularities $M_1$ and $M_2$ denote in-session semester period and semester break periods respectively.
-Both $M_1$, $M_2$ and $M = M_{1}\bigcup M_{2}$ denoting the semester week type are aperiodic with respect to days ($B$) or weeks ($G$).
-Hence $A_{B, M}$ denoting day of the semester week type would be an aperiodic cyclic granularity.
-This is because the placement of the semester within an year would vary across years.
-\autoref{fig:aperiodic-example} b shows the stack display of time with granules representing same categories (semester break/in-session) stacked on top of one another.
-\autoref{fig:aperiodic-example} (a) representing the linear display of time is useful in manifesting how the categories would be determined with respect to the bottom granularities using Definition \ref{def:aperiodic}.
-It is interesting to note here that $Q_{H, M}$ denoting semester week of the semester week type would be a quasi-circular granularity since the distribution of semester weeks within a semester is assumed to remain constant over years.}
-\end{example}
+In an attempt to make the densities \ref{fig:hist_plot} same across different levels, we want to start by making their scale and location same.
+In that regard, we shuffle the data multiple times and compute the sampling distribution of \(mmpd_{raw}\) for each combination of facet and x-axis levels.
 
-\hypertarget{sec:cyclic-calendar}{%
-\subsection{Relativities}\label{sec:cyclic-calendar}}
+The null hypothesis is that the two cyclic granularities do not differ on the outcome (i.e., that the outcome is observed independently of treatment assignment).
+When we permute the outcome values during the test, we therefore see all of the possible alternative treatment assignments we could have had and where the mean-difference in our observed data falls relative to all of the differences we could have seen if the outcome was independent of treatment assignment.
+While a permutation test requires that we see all possible permutations of the data (which can become quite large), we can easily conduct ``approximate permutation tests'' by simply conducting a vary large number of resamples.
+That process should, in expectation, approximate the permutation distribution.
 
-The hierarchical structure of time creates a natural nested ordering which can be used in the computation of relative pairs of granularities.
-This is illustrated using two examples, a Mayan calendar, which is simple, in addition to the more complex Gregorian calendar.
+Finally, we run some simulation experiments to see if normalisation works. If normalisation has worked, it should work for both x levle and facet-levels.
 
-\begin{definition}\label{def:hierarchy} 
-The nested ordering of linear granularities can be organized into a {\bf hierarchy table}, denoted as $H_n: (G, C, K)$, which arranges them from lowest to highest in order.
-It shows how the $n$ granularities relate through $K$, and how the cyclic granularities, $C$.
-can be defined relative to the linear granularities.
-Let $G_{l}$ and $G_{m}$ represent the linear granularity of order $l$ and $m$ respectively with $l<m$.
-Then $K \equiv P(l,m)$ represents the period length of the grouping $(G_{l}, G_{m})$, if $C_{G_{l}, G_{m}}$ is a circular granularity and $K \equiv k(l,m)$ represents the operation to obtain $G_{m}$ from $G_{l}$, if $C_{G_{l}, G_{m}}$ is quasi-circular.
-\end{definition}
+Thus these median maximum pairwise distances need to be normalized for different harmonies in a way that eliminates the effect of different levels, consequently enabling comparison across different harmonies.
+The Fisher--Tippett--Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.
 
-\begin{example}
-{\rm  \autoref{tab:tab-mayan} shows the hierarchy table for the Mayan calendar.
-In the Mayan calendar, one day is referred to as a kin and the calendar was structured such that 1 kin = 1 day; 1 uinal = 20 kin; 1 tun  = 18 uinal (about a year); 1 katun = 20 tun (20 years) and 1 baktun = 20 katun.
-}
-\end{example}
+\hypertarget{methodology}{%
+\subsection{Methodology}\label{methodology}}
 
-\begin{table}
+The mean and sd for each combination of facet and x levels could be computed by shuffling the data repeatedly and obtaining the distribution of \(MMPD_{raw}\) for different combinations.
+If \(MMPD_{raw}\) is then adjusted by the location and scale of this distribution, we could assume that the distribution of the resultant \(MMPD_{norm}\) will have same distribution across different combinations of x and facet levels.
+All data is repeatedly shuffled \(nperm\) times in random manner to obtain the measure \(MMPD_{raw}\).
+Then the \(MMPD_{norm}\) is obtained by scaling the observed value by the mean and sd of the distribution of \(MMPD_{raw}\) obtained from the permuted data.
 
-\caption{\label{tab:tab-mayan}Hierarchy table for Mayan calendar with circular single-order-up granularities.}
-\centering
-\begin{tabular}[t]{lll}
-\toprule
-linear (G) & single-order-up cyclic (C) & period length/conversion operator (K)\\
-\midrule
-kin & kin-of-uinal & 20\\
-uinal & uinal-of-tun & 18\\
-tun & tun-of-katun & 20\\
-katun & katun-of-baktun & 20\\
-baktun & 1 & 1\\
-\bottomrule
-\end{tabular}
-\end{table}
+\noindent Step 7 in the Algorithm defined in Section \ref{sec:} need to be revised in order to compute \(MMPD_{norm}\) instead of \(MMPD_{raw}\).
+Step 1-6 stays the same.
+The entire algorithm will have to repeated for all harmony pairs considered in the context.
 
-\noindent It is interesting to note, that in the Mayan calendar, like most calendars, that day is the basic unit of time \citep{Reingold2001-kf}.
-The structuring of larger units, weeks, months, years and cycle of years, though, varies substantially.
-An exception is the French revolutionary calendar, which divides each day into 10 ``hours'', each ``hour'' into 100 ``minutes'' and each ``minute'' into 100 ``seconds'', the duration of which is 0.864 common seconds.
-Nevertheless, for any calendar a hierarchy table can be defined.
-Note that it is not always possible to organize an aperiodic linear granularity in a hierarchy table.
-Hence, we assume that the hierarchy table consists of periodic linear granularities only and that the cyclic granularity \(C_{G(l),G(m)}\) is either circular or quasi-circular.
+A simulation study is conducted to see if this methodology is working.
 
-\begin{definition}\label{def:norderup} 
-The hierarchy table contains {\bf multiple-order-up} granularities which are cyclic granularities that are nested within multiple levels.
-A {\bf single-order-up} is a cyclic granularity which is nested within a single level. It is a special case of multiple-order-up granularity.
-\end{definition}
+\hypertarget{simulation-study}{%
+\subsection{Simulation study}\label{simulation-study}}
 
-\begin{example}
-{\rm In \autoref{tab:tab-mayan}, kin-of-tun or kin-of-baktun are examples of multiple-order-up granularities and single-order-up granularities are kin-of-uinal, uinal-of-tun etc.}
-\end{example}
+The behavior of the measure is monitored and understood through simulation experiments.
+A single simulation consisting of computational operations on a panel generating MMPD the value of which represents to what extent a pair of cyclic granularities would be interesting when displayed in the design.
+In comparing different simulation runs, we distinguish between different distributions and simulation scenarios (also iterations may be).
 
-\hypertarget{computation-1}{%
-\subsection{Computation}\label{computation-1}}
+\hypertarget{simulated-designs}{%
+\subsubsection{Simulated designs}\label{simulated-designs}}
 
-In this section, we will see how to obtain cyclic granularities through an algebraic representation of other cyclic granularities.
-This is similar to calendar algebra in \citet{Ning_2002} for linear granularities but caters to computation of cyclic granularities.
-We shall refer to it as through cyclic calendar algebra operations.
-The cyclic calendar algebra consists of broadly two kinds of operations:
-(1) \textbf{single-to-multiple} and (2) \textbf{multiple-to-single} which entails the representation of \emph{multiple-order-up} cyclic granularities from \emph{single-order-up} cyclic granularities respectively.
+D1. Same distribution of the measured variable across all x-axis and facet categories
+D2. Different distribution across facet categories but same across x-axis categories
+D3. Different distribution across x-axis categories but same across facet categories
+D4. Different across both x-axis and facet categories
 
-\hypertarget{sec:single-to-multiple}{%
-\subsubsection{Single-to-multiple}\label{sec:single-to-multiple}}
+Each of these case scenarios tried against Normal and a non-normal (Gamma) distribution to check if underlying distribution has a role to play.
 
-\noindent Methods to obtain multiple-order-up granularity will be different based on if the hierarchy consists of all circular single-order-up granularities or a mix of circular and quasi-circular single-order-up granularities.
-The methods require the use of integer arithmetic, and hence it is important that the label mapping of the individual single-order-up granularity is an identity function, that is, \(L(x) = x\quad \forall x\).
-The label mapping of the resultant multiple-order-up granularity can be chosen depending on the context.
-Circular single-order-up granularities can be used recursively to obtain a multiple-order-up circular granularity using Equation \ref{eq:eq7} for \(l < m - 1\) and \(P(i, j) = 1, \quad \forall i = j \in \{0, 1, \dots, m-l-1\}\).
+\hypertarget{environment}{%
+\subsubsection{Environment}\label{environment}}
 
-\begin{equation} \label{eq:eq7}
-\begin{split}
-C_{G_l,G_m}(z) & = C_{G_l,G_{l+1}}(z) + P(l, l+1)C_{G_{l+1},G_m}(z)\\
-  & = C_{G_l,G_{l+1}}(z) + P(l, l+1)( C_{G_{l+1},G_{l+2}}(z) + P(l+1, l+2)C_{G_{l+2}, G_m}(z)) \\
-  & = C_{G_l,G_{l+1}}(z) + P(l, l+1)C_{G_{l+1},G_{l+2}}(z) + P(l, l+1)P(l+1, l+2)C_{G_{l+2}, G_{m}}\\
-  & = C_{G_l,G_{l+1}}(z) + P(l, l+1)C_{G_{l+1},G_{l+2}}(z) + P(l, l+2)C_{G_{l+2},G_{l+m}}(z)\\
-  &\vdots\\
-  & = \sum_{i=0}^{m - l - 1} P(l, l+i)C_{G_{l+i},G_{l+i+1}}(z)\\
-\end{split}
-\end{equation}
+R version 4.0.1 (2020-06-06) is used with platform: x86\_64-apple-darwin17.0 (64-bit) running under: macOS Mojave 10.14.6
 
-\noindent For example, the multiple-order-up granularity \(C_{uinal,katun}\) for Mayan calendar could be obtained using Equation \ref{eq:eq8}.
+\hypertarget{experimental-set-up}{%
+\subsubsection{Experimental set up}\label{experimental-set-up}}
 
-\begin{equation} \label{eq:eq8}
-\begin{split}
-C_{uinal, baktun}(z)  = & C_{uinal, tun}(z) + P(uinal, tun)C_{tun,katun}(z) + P(uinal, katun)C_{katun, baktun}(z) \\
-               = & \lfloor z/20\rfloor ~\text{mod}~18 + 18*\lfloor z/20*18\rfloor ~\text{mod}~20  \\
-               &~~~ + 18*20\lfloor z/20*18*20\rfloor ~\text{mod}~20 \\
-\end{split}
-\end{equation}
+This section describes the design of simulation runs, in terms of the scenarios simulated, the number of permutations used to compute estimates and to display the distribution of MMPD.
 
-\noindent We consider the case of only one quasi-circular single order-up granularity in the hierarchy table while computing a multiple-order-up quasi-circular granularity.
-Any multiple-order-up quasi-circular granularity \(C_{l, m}(z)\) could then be obtained as a dicrete combination of circular and quasi-circular granularities.
- Depending on the order of the combination, again two different approaches need to be employed leading to the following cases:
+\begin{center}\includegraphics[width=\textwidth]{Figs/simulation} \end{center}
 
-\begin{itemize}
-\item
-  \(C_{l,m'}(z)\) is circular and \(C_{m',m}(z)\) is quasi-circular
-  \begin{equation} \label{eq:multifromsingle-quasi1}
-  \begin{split}
-  C_{G_l,G_{m}}(z) & = C_{G_{l},G_{m'}}(z) + P(l, m')C_{G_{m'},G_{m}}(z) \\
-  \end{split}
-  \end{equation}
-\item
-  \(C_{l,m'}(z)\) is quasi-circular and \(C_{m',m}(z)\) is circular
-  \begin{equation} \label{eq:multifromsingle-quasi2}
-  \begin{split}
-  C_{G_l,G_{m}}(z) & = C_{G_{l},G_{m'}}(z) + \sum_{w=0}^{C_{m',m}(z) -1}(\vert T_{w} \vert)\\
-  \end{split}
-  \end{equation}
-\end{itemize}
+Observations from the null distribution are chosen as:\\
+\texttt{sim\_norm\_null\ =\ \ \ distributional::dist\_normal(5,\ 10)}~\\
+\texttt{sim\_gamma\_null\ \ =\ \ \ distributional::dist\_gamma(0.5,\ 0.2)}~\\
 
-\noindent where, \(T_w\) is such that \(G_{m'}(w) = \bigcup_{z \in T_w}G_{l}\) and \(\vert T_w \vert\) is the cardinality of set \(T_w\).
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
 
-\noindent Consider a hierarchy using linear granularties from a Gregorian calendar in \autoref{tab:tab-gregorian}.
-This is an example of a hierarchy structure which has both circular and quasi-circular single-order-up granularities with day-of-month as the only single-order-up quasi-circular granularity.
+\hypertarget{null-distribution}{%
+\subsubsection{Null distribution}\label{null-distribution}}
 
-\noindent Using Equations \ref{eq:multifromsingle-quasi1} and \ref{eq:multifromsingle-quasi2}, we then have:
+Under the null hypothesis, all the combinations of x-axis and facets are obtained from the same distribution.
+We need to study the distribution of the mmpd values under the null hypothesis to see if comparison of their values across different x-axis and facet levels are at all possible.
+So, in turn it needs to be checked that if normalisation worked.
 
-\[C_{hour, month}(z) = C_{hour, day}(z) + P(hour, day)*C_{day, month}(z)\]
-\[C_{day, year}(z) = C_{day,month}(z) + \sum_{w=0}^{C_{month, year}(z)-1}(\vert T_{w} \vert)\], where \(T_w\) is such that \(month(w) = \bigcup_{z \in T_w}day(z)\)
+Currently, we see in Figure \ref{fig:null-dist} that the normalisation works fine for each facet since the distributions for each column are equal irrespective of the distribution type.
+But it does not work along the x-axis.
 
-\begin{table}
+\begin{center}\includegraphics[width=\textwidth]{figure/norm-data, "Distribution of $MMPD_{norm}$ across different levels of facet and x-axis.
+These distributions should look the same if normalisation worked."-1} \end{center}
 
-\caption{\label{tab:tab-gregorian}Hierarchy table for the Gregorian calendar with both circular and quasi-circular single-order-up granularities.}
-\centering
-\begin{tabular}[t]{lll}
-\toprule
-linear (G) & single-order-up cyclic (C) & period length/conversion operator (K)\\
-\midrule
-minute & minute-of-hour & 60\\
-hour & hour-of-day & 24\\
-day & day-of-month & k(day, month)\\
-month & month-of-year & 12\\
-year & 1 & 1\\
-\bottomrule
-\end{tabular}
-\end{table}
+\begin{figure}
 
-\hypertarget{sec:multiple-to-single}{%
-\subsubsection{Multiple-to-single}\label{sec:multiple-to-single}}
-
-\noindent Similar to single-to-multiple operations, multiple-to-single operations involve different approaches for all circular single-order-up granularities and a mix of circular and quasi-circular single-order-up granularities in the hierarchy.
-For a hierarchy table \(H_n: (G, C, K)\) with only circular single-order-up granularities in the hierarchy and \(l_1, l_2, m_1, m_2 \in {1, 2, \dots, n}\) and \(l_2<l_1\) and \(m_2>m_1\), multiple-order-up granularities could be obtained using \ref{eq:all-circular-multiple}.
-
-\begin{equation} \label{eq:all-circular-multiple}
-C_{G_{l_1}, G_{m_1}}(z) = \lfloor C_{G_{l_2}, G_{m_2}}(z)/P(l_2,l_1) \rfloor ~\text{mod}~P(l_1, m_1)
-\end{equation}
-
-\noindent For example, in Mayan Calendar, it is possible to compute the single-order-up granularity tun-of-katun from uinal-of-baktun, since \(C_{tun, katun}(z) = \lfloor C_{uinal, baktun}(z)/18\rfloor ~\text{mod}~20\).
-
-\hypertarget{sec:quasi-circular-multiple}{%
-\paragraph{Multiple order-up quasi-circular granularities}\label{sec:quasi-circular-multiple}}
-
-Single-order-up quasi-circular granularity could be obtained from multiple-order-up quasi-circular granularity and single/multiple-order-up circular granularity using Equations \ref{eq:multifromsingle-quasi1} and \ref{eq:multifromsingle-quasi2}.
-
-\hypertarget{sec:data-structure}{%
-\section{Data structure}\label{sec:data-structure}}
-
-\noindent Effective exploration and visualization benefits from well-organized data structures.
-\citet{wang2020tsibble} introduced a tidy data structure, tsibble, to support exploration and modeling of temporal data.
-This forms the basis of the structure for cyclic granularities.
-A tsibble consists of an index, key and measured variables.
-An index is a variable with inherent ordering from past to present and a key is a set of variables that define observational units over time.
-A linear granularity is a mapping of the index set to subsets of the time domain.
-For example, if the index of a tsibble is days, then a linear granularity might be weeks, months or years.
-A bottom granularity is represented by the index of the tsibble.
-
-\noindent All cyclic granularities can be expressed in terms of the index set, and hence, we introduce the data structure in Figure \ref{fig:data-structure}.
-This basic structure of a tsibble (index, key, measurements) is augmented by columns of cyclic granularities.
-The total number of cyclic granularities would be based on the number of linear granularities considered in the hierarchy table and presence of any aperiodic cyclic granularities, for example, if we have \(n\) periodic linear granularities in the hierarchy table, \(n(n-1)/2\) circular or quasi-circular cyclic granularities could be constructed.
-Let \(N_C\) be the total number of contextual circular, quasi-circular and aperiodic cyclic granularities that could originate from \(N_L\) periodic and aperiodic linear granularities.
-Any attempt to encode all or many of these cyclic granularities at the same time to develop insights on periodicity might fail or otherwise become too numerous for comprehensive human consumption.
-Instead, this big problem is broken down by focusing on pair of cyclic granularities (\(C_i\), \(C_j\)) at a time for \(i, j \in \{1, 2, \dots, N_C\}\).
-Data sets of the form \textless{}\(C_i\), \(C_j\), \(v\)\textgreater{} then forms the basis for exploration and analysis of the measured variable \(v\).
-
-\begin{figure}[htb]
-
-{\centering \includegraphics[width=\textwidth]{Figs/data-struc-diffcol}
+{\centering \includegraphics[width=\textwidth]{figure/null-dist-1}
 
@@
 
-\caption{The data structure for exploring periodicities in data by including cyclic granularities in the tsibble structure with index, key and measured variables.}\label{fig:data-structure}
+\caption{Distribution of mmpd across different facet levels (columns) and x-axis levels (rows) for null ditribution normal(5,10) and gamma(0.5, 0.2).
+The distribution of MMPD is unaffected by the null distribution considered.
+It is also the same across all facet levels but not across the x-axis, which means normalisation is failing across x-axis.}\label{fig:null-dist}
 \end{figure}
 
-\hypertarget{sec:synergy}{%
-\subsection{Harmonies and clashes}\label{sec:synergy}}
+\hypertarget{performance-of-normalised-mmpd}{%
+\subsubsection{Performance of normalised MMPD}\label{performance-of-normalised-mmpd}}
 
-The way cyclic granularities relate become important when we consider the data structure in Figure \ref{fig:data-structure}.
-Let us consider two cyclic granularities \(C_i\) and \(C_j\), such that \(C_i\) maps index set to a set \(\{A_k | k \in \mathbb{N}, k \leq K\}\) and \(C_j\) maps index set to a set \(\{B_l | l \in \mathbb{N}, l \leq L\}\).
-Here, \(A_k\)'s or \(B_l\)'s are the levels/categories corresponding to \(C_i\) and \(C_j\) respectively.
-Let \(S_{kl}\) be a subset of the index set such that for all \(s \in S_{kl}\), \(C_i(s) = A_k\) and \(C_j(s) = B_l\).
-Data subsets for each combination of levels (\(A_k\), \(B_l\)) like \textless{}\(A_k\), \(B_l\), \(v(s)\)\textgreater{} can be obtained for all \(k \in {1, 2, \dots, K}\) and \(l \in {1, 2, \dots, L}\) which will lead to \(KL\) data subsets.
-Now, some situations can lead to few or many of these sets being empty.
-We will discuss few cases, where one or more of these \(KL\) sets will be empty either due to the structure of the calendar, duration and location of events in a calendar or just by the construction of the cyclic granularities.
+\hypertarget{the-statistical-test}{%
+\section{The statistical test}\label{the-statistical-test}}
 
-\begin{definition}\label{def:harmony}
-A {\bf clash} is a pair of cyclic granularities which contains structurally, event-driven or build-based empty combinations of its categories.
-\end{definition}
+\hypertarget{algorithm-1}{%
+\subsection{Algorithm}\label{algorithm-1}}
 
-\begin{definition}\label{def:clash}
-A {\bf harmony} is a pair of cyclic granularities that does not contain any empty combinations of its categories.
-\end{definition}
+for computation for all harmony pairs
 
-\noindent Firstly, empty combinations can arise due to the structure of the calendar or hierarchy.
-These are called ``structurally'' empty combinations.
-Let us take a specific example, where \(C_i\) be day-of-month with 31 levels and \(C_j\) be week-of-month with 5 levels.
-There will be \(31\times 5=155\) sets \(S_{kl}\) corresponding to possible combinations of \(C_i\) and \(C_j\).
-Many of these like \(S_{1,5}\), \(S_{21,2}\) are empty.
-This is also intuitive since the first day of the month can never correspond to fifth week of the month.
-Hence the pair (day-of-month, week-of-month) is a clash.
+\textbf{Assumption:} random permutation without considering ordering
+(global)
 
-\noindent Secondly, empty combinations can turn up due to differences in event location or duration in a calendar.
-These are called ``event-driven'' empty combinations.
-Let us consider \(C_i\) be day-of-week with 7 levels and \(C_j\) be WorkingDay/NonWorkingDay with 2 levels.
-While potentially all of these 14 sets \(S_{kl}\) can be non-empty (it is possible to have a public holiday on any day-of-week), in practice many of these will probably have very few observations.
-For example, there are few (if any) public holidays on Wednesdays or Thursdays in any given year in Melbourne, Australia.
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  Given the data; \(\{v_t: t=0, 1, 2, \dots, T-1\}\), the MMPD is computed and is represented by \(MMPD_{obs}\).
+\item
+  From the original sequence a random permutation is obtained: \(\{v_t^*: t=0, 1, 2, \dots, T-1\}\).
+\item
+  MMPD is computed for all random permutation of the data and is represented by \(MMPD_{sample}\).
+\item
+  Steps (2) and (3) are repeated a large number
+  of times M (e.g.~1000).
+\item
+  For each permutation, one \(MMPD_{sample}\) value is obtained.
+\item
+  \(95^{th}\) percentile of this \(MMPD_{sample}\) distribution is computed and stored in \(MMPD_{threshold}\).
+\item
+  If \(MMPD_{obs}> MMPD_{threshold}\), harmony pairs are accepted. Only one threshold for all harmony pairs.
+\end{enumerate}
 
-\noindent Thirdly, empty combinations can be a result of how granularities are constructed.
-These are called ``build-based'' empty combinations.
-Let \(C_i\) be Business-days, which are days from Monday to Friday except holidays and \(C_j\) be day-of-month.
-Then the days denoting weekends in a month would not correspond to any Business days.
-This is different from structurally empty combinations because structure of the calendar does not lead to these missing combinations, but the construction of the granularities does.
+Pros: Considering thresholds global for all harmony pairs would imply less computation time.
 
-\noindent An example when there will be no empty combinations could be where \(C_i\) and \(C_j\) maps index set to day-of-week and month-of-year respectively.
-Here \(C_i\) can have 7 levels while \(C_j\) can have 12 levels.
-So there are \(12\times7=84\) sets \(S_{kl}\).
-All of these are non-empty because every day-of-week can occur in every month.
-Hence, the pair (day-of-week, month-of-year) is a harmony.
+Cons: Only one threshold for all harmony pairs means we are assuming distribution of all harmonies pairs are similar, which might not be the case.But nevertheless, it is a good benchmark.
 
-\hypertarget{sec:summarize-measured}{%
-\subsection{Summarizing the measured variable}\label{sec:summarize-measured}}
+\hypertarget{size-power-and-confidence-interval}{%
+\subsection{Size, power and confidence interval}\label{size-power-and-confidence-interval}}
 
-Restructuring time from linear to cyclic time granularities leads to re-organisation of the data structure, where each level of a cyclic granularity corresponds to multiple values of the measured variable.
-It is common to see summarization of these multiple values through aggregation or an unique summary statistic like mean or median to have each level of cyclic granularity correspond to an unique value of the measured variable.
-However, this approach hides the distributions of the measured variable induced by the re-organised data structure.
-Summarizing the distribution of the measured variable using these multiple observations could be a potential way to explore and bring forward different features of the data.
+\hypertarget{characteristics-under-different-simulation-designs}{%
+\paragraph{Characteristics under different simulation designs}\label{characteristics-under-different-simulation-designs}}
 
-However, we need to consider the effect of number of observations on the summarization even for harmonies.
-Consider a data set with \((T + 1)\) observations, and two cyclic granularities \(C_i\) and \(C_j\) with \(K\) and \(L\) categories respectively.
-Let \(nobs\) be the number of observations for a combination of levels from \((C_i, C_j)\).
-Now, \(nobs\) might be equal for all combinations on an average so that \(nobs = (T + 1)/(KL)\) as \(T\rightarrow\infty\) or ideally take any value between \(\{0, 1, 2, \dots, T\}\).
-The statistical transformation used for summarizing the measured variable should be chosen in line with \(nobs\).
-For example, it might be useful to compute deciles for summarization only when \(nobs \ge 10\).
-Rarely occurring categories such as the 366th day of the year, or the 31st day of the month are likely to suffer from this problem.
+A set of simulation runs that are conducted and some outputs of which are reported.
 
-\hypertarget{sec:visualization}{%
-\section{Visualization}\label{sec:visualization}}
+\begin{center}\includegraphics[width=\textwidth]{figure/sim_all-1} \includegraphics[width=\textwidth]{figure/sim_all-2} \includegraphics[width=\textwidth]{figure/sim_all-3} \includegraphics[width=\textwidth]{figure/sim_all-4} \end{center}
 
-The grammar of graphics introduced a framework to construct statistical graphics by relating data space to the graphic space \citep{Wilkinson1999-nk}.
-The layered grammar of graphics proposed by \citet{Wickham2009pk}, which is an alternate and modified parametrization of the grammar suggests that graphics are made up of distinct layers of grammatical elements.
-Drawing from the grammar of graphics, if \textless{}\(C_i\), \(C_j\), \(v\)\textgreater{} serves as the basis of visualizing the distribution of the measured variable, the following layers can be specified:
+\hypertarget{algorithm-2}{%
+\section{Algorithm}\label{algorithm-2}}
+
+\noindent The algorithm employed for computing MMPD is summarized as follows:
 
@@
 \item
-  Data: \textless{}\(C_i\), \(C_j\), \(v\)\textgreater{}
+  \textbf{Input:} Data corresponding to all harmony pairs, i.e., data sets of the form \((C_i, C_j, v)\)
+  \(\forall i, j \in N_C\)\\
 \item
-  Aesthetic mapping (mapping of variables to elements of the plot): \(C_i\) mapped to \(x\) position and \(v\) to \(y\) position
-\item
-  Statistical transformation (data summarization): any descriptive or smoothing statistics that summarizes distribution of \(v\)
-\item
-  Geometric objects (physical representation of the data): any geometry displaying distribution, for example, boxplot, letter value, violin, ridge or highest density region plots
-\item
-  Facet (split plots): \(C_j\)
+  \textbf{Output:} MMPD (Median Maximum Pairwise Distances) measuring the average variation across different levels of \(C_i\) and \(C_j\) \(\forall i, j \in N_C\)
 \end{itemize}
 
-\hypertarget{choice-of-statistical-transformations-and-geometric-objects}{%
-\subsection{Choice of statistical transformations and geometric objects}\label{choice-of-statistical-transformations-and-geometric-objects}}
-
-Choice of plots are dictated by the statistical transformations and geometric objects used for the visualization.
-The basic plot choice for our data structure is the one that can display distributions.
-We will discuss few conventional and recent ways to plot distributions using both Kernel density estimates and descriptive statistics.
-Descriptive statistics based displays include box plots \citep{Tukey1977-jx} or different variations of it like notched box plots \citep{Mcgill1978-hg}.
-More recent ways are the letter-value box plot \citep{Hofmann2017-sg} or quantile plots which display quantiles instead of quartiles in a traditional boxplot.
-Kernel density based plots for displaying a distribution include violin plots \citep{Hintze1998-zi}, summary plot \citep{Potter2010-qc}, ridge line plots, highest density regions (HDR) box \citep{Hyndman1996-ft}.
-Each type of density display has different parameters, that need to be estimated given the data.
-Each is equipped with some benefits and challenges which should be borne in mind while using them for exploration.
-
-\hypertarget{facet-and-aesthetic-variables}{%
-\subsection{Facet and aesthetic variables}\label{facet-and-aesthetic-variables}}
-
-\hypertarget{sec:levels}{%
-\subsubsection{Levels}\label{sec:levels}}
-
-The levels of cyclic granularities has a role to play on the choice of plots since space and resolution might become a problem with too many levels.
-A potential approach could be to categorize the levels as very high/high/medium/low for each cyclic granularity and define some criteria based on usual cognitive power, display size available and the aesthetic mappings.
-Default values for these categorizations could be chosen based on levels of common temporal granularities like days of the month, days of the fortnight or days of the week.
-
-\hypertarget{sec:vis-interaction}{%
-\subsubsection{Synergy of cyclic granularities}\label{sec:vis-interaction}}
-
-For data sets of the form (\(C_i\), \(C_j\), \(v\)) \(\forall i, j \in N_C\), if there are levels of \(C_i\) (or \(C_j\)) not spanned by levels of \(C_j\) (or \(C_i\)), empty sets are formed leading to potential ineffective graphs.
-The conjecture is that the synergy of these cyclic granularities are thus playing a role while deciding if the resulting plot would be a good candidate for exploratory analysis.
-Harmonies are pairs of granularities that do not contain empty combinations and could possibly be useful for exploring patterns.
-However, plotting clashes should be avoided since they might contain combinations which are empty or have too few observations.
-For illustration, \autoref{fig:allFig} (a) shows the distribution of half-hourly electricity consumption through letter value plot across months of the year faceted by quarters of the year.
-This plot does not work because every quarter does not correspond to all months of the year, for example, the first quarter of the year would never correspond to the month December of an year.
-
-\begin{figure}
-
-\includegraphics[width=1\linewidth]{figure/allFig-1} \hfill{}
-
-\caption{Distribution of energy consumption displayed through letter value plots.
-Plot (a) displays consumption across month-of-year faceted by quarters of the year, (b) across weekday/weekend faceted by quarters of the year and (c) across quarters of the year faceted by weekday/weekend.
-Plots (b) and (c) both show harmonies since each quarter consists of both weekdays and weekends.
-Conversely, weekend and weekday can occur in every quarter.
-Analysts should avoid plotting such clashes.
-Plot (b) helps to compare weekends and weekdays for each quarter.
-It can be seen that for every quarter weekend and weekday consumption are fairly similar except for the second quarter where the letter values below D and E behave differently, whereas, Plot (c) helps to compare quarters within weekdays and weekends.
-For example, the quartile spread of consumption shrinks/lowers from first to fourth quarter for weekdays, whereas this pattern is not true for weekends.
-Plot (a) shows a clash since all quarters do not correspond to all months of the year.}\label{fig:allFig}
-\end{figure}
-
-\hypertarget{interchangeability-of-mappings}{%
-\subsubsection{Interchangeability of mappings}\label{interchangeability-of-mappings}}
-
-We will discuss the effect of the mapping of cyclic granularities in this section.
-When we consider data sets of the form \textless{}\(C_i\), \(C_j\), \(v\)\textgreater{} with \(C_i\) mapped to \(x\) position and \(C_j\) to facets, then \(A_k\)'s are placed in close proximity and each \(B_l\) represent a group/facet.
-Gestalt theory suggests that when items are placed in close proximity, people assume that they are in the same group because they are close to one another and apart from other groups.
-Hence, in this case \(A_k\)'s are compared against each other within each group.
-With the mapping of \(C_i\) and \(C_j\) reversed, emphasis will shift to different behavior of the variables.
-\autoref{fig:allFig} (b) shows the letter value plot across weekday/weekend faceted by quarters of the year and \autoref{fig:allFig} (c) shows the same two cyclic granularities with their mapping reversed.
-\autoref{fig:allFig} (b) helps us to compare weekday and weekend within each quarter and \autoref{fig:allFig} (c) helps to compare quarters within weekend and weekday.
-
-\hypertarget{number-of-observations-and-statistical-transformations}{%
-\subsection{Number of observations and statistical transformations}\label{number-of-observations-and-statistical-transformations}}
-
-Visualizing distributions can be misleading if statistical transformations are performed on rarely occurring categories (Section \ref{sec:summarize-measured}).
-Even when there are no rarely occurring events, number of observations might vary hugely within or across each facet.
-This might happen due to missing observations in the data or uneven locations of events in time domain.
-In such cases, the statistical transformations should be used with caution as sample sizes would directly affect both the variance and consequently the confidence interval of the estimators.
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  Fix harmony pair \((C_i, C_j)\).
+\item
+  Fix \(k\). Then there are \(L\) groups corresponding to level \(A_k\) of \(C_i\).
+\item
+  Compute \(m = \binom{L}{2}\) pairwise distances between distributions of \(L\) unordered levels and \(m = L-1\) pairwise distances for \(L\) ordered categories.
+\item
+  Identify maximum within the \(m\) computed distances.
+\item
+  Compute normalized maximum distance (\(NM\)) using appropriate norming constants.
+\item
+  Use Steps 1-5 to compute normalized maximum distance for \(\forall k \in \{1, 2, \ldots, K\}\).
+\item
+  Compute MMPD = median \((NM_1, NM_2, \dots, NM_K)\)/log(\(K\)).
+\item
+  Repeat Steps 1 to 7 for all harmony pairs.
+\end{enumerate}
 
@@
 Smart meters provide large quantities of measurements on energy usage for households across Australia.
-One of the customer trials \citep{smart-meter} conducted as part of the Smart Grid Smart City project in Newcastle, New South Wales and some parts of Sydney provides customer wise data on energy consumption for every half hour from February 2012 to March 2014.
+One of the customer trials (Department of the Environment and Energy 2018) conducted as part of the Smart Grid Smart City project in Newcastle, New South Wales and some parts of Sydney provides customer wise data on energy consumption for every half hour from February 2012 to March 2014.
 The idea here is to show how to visualize the distribution of the energy consumption across different cyclic granularities in a systematic way to identify different behavioral patterns.
@@
 
-The tsibble object \texttt{smart\_meter10} from R package \texttt{gravitas} \citep{R-gravitas} consisting of \texttt{reading\_datetime}, \texttt{customer\_id} and \texttt{general\_supply\_kwh} denoting the index, key and measured variable of the tsibble is used to facilitate the systematic exploration.
+The tsibble object \texttt{smart\_meter10} from R package \texttt{gravitas} (Gupta et al.
+2019) consisting of \texttt{reading\_datetime}, \texttt{customer\_id} and \texttt{general\_supply\_kwh} denoting the index, key and measured variable of the tsibble is used to facilitate the systematic exploration.
 While trying to explore the energy behavior of these customers systematically across cyclic time granularities, the first thing to consider is which cyclic time granularities we can look at exhaustively.
@@
 Considering \(6\) linear granularities half-hour, hour, day, week, month and year in the hierarchy table, \(N_C = (6*5/2) = 15\).
-If \(N_C\) seem too large, the smallest and largest linear granularities could be considered to be removed for analysis.
-Granularities half-year and year are removed to have \(N_C = (4*3/2) = 6\) and obtain cyclic granularities namely ``hour\_day'', ``hour\_week'', ``hour\_month'', ``day\_week'', ``day\_month'' and ``week\_month'', read as ``hour of the day'', etc.
+If \(N_C\) seem too large, the smallest and largest linear granularities could be considered to be removed from the hierarchy table.
+We remove half-year and year to have \(N_C = (4*3/2) = 6\) and obtain cyclic granularities namely ``hour\_day'', ``hour\_week'', ``hour\_month'', ``day\_week'', ``day\_month'' and ``week\_month'', read as ``hour of the day'', etc.
 Further, we add cyclic granularity day-type( ``wknd\_wday'') to capture weekend and weekday behavior.
-Now that we have a list of cyclic granularities to look at, we should be able to compute them using Section \ref{sec:cyclic-calendar}.
+Now that we have a list of cyclic granularities to look at, we should be able to compute the multiple-order-up granularities using Section \ref{sec:cyclic-calendar}.
 
@@
 Choosing \(2\) of the possible \(7\) granularities, which is equivalent to having \(^{7}P_2 = 42\) candidates for visualization.
-Harmonies can be identified among those \(42\) possibilities to narrow the search.
+Fortunately, harmonies can be identified among those \(42\) possibilities to narrow the search.
 \autoref{tab:harmony-tab} shows \(16\) harmony pairs after removing clashes and any cyclic granularities with levels more than \(31\), as effective exploration becomes difficult with many levels (Section \ref{sec:levels}).
+The MMPD is also shown along with indicator (*) only when variation of measured variable across the harmony pair significant.
+Starting from \(42\) possible pairs of cyclic granularities to visualize, we are finally left with only \(6\), which is a very sizable number of displays for exploration.
 
-\noindent Few harmony pairs are displayed in \autoref{fig:bothcust} to illustrate the impact of different distribution plots and reverse mapping.
-For each of \autoref{fig:bothcust} (b) and (c), \(C_i\) is the circular granularity day-type (weekday/weekend) and \(C_j\) is hour of the day.
+Few harmony pairs are displayed in \autoref{fig:bothcust} to illustrate the significance of MMPD, threshold and the impact of different distribution plots and reverse mapping.
+\noindent For each of \autoref{fig:bothcust} (b) and (c), \(C_i\) is the circular granularity day-type (weekday/weekend) and \(C_j\) is hour of the day.
 The geometry used for displaying the distribution is chosen as area-quantiles and violins in \autoref{fig:bothcust} (b and c respectively).
 \autoref{fig:bothcust} (a) displays reverse mapping of \(C_i\) and \(C_j\) with \(C_i\) denoting hour of the day and \(C_j\) denoting day-type with distribution geometrically displayed as boxplots.
+
 In \autoref{fig:bothcust} (b), the black line is the median, whereas the purple band covers 25th to 75th percentile, the orange band covers 10th to 90th percentile and the green band covers 1st to 99th percentile.
@@
 
-\noindent Consider looking at violin plots instead of quantile plots to look at the same data in \autoref{fig:bothcust}(c) for some more insights.
+Consider looking at violin plots instead of quantile plots to look at the same data in \autoref{fig:bothcust}(c).
+There is additional information that we can derive looking at the distribution.
 There is bimodality in the early hours of the day, implying both low and high energy consumption is probable in the early hours of the day both for weekdays and weekends.
 If we visualize the same data with reverse mapping of the cyclic granularities, then the natural tendency would be to compare weekend and weekday behavior within each hour and not across hours.
-For example in \autoref{fig:bothcust}(a), it can be seen that median energy consumption for the early morning hours is higher for weekdays than weekends.
-Also, outliers are more prominent in the latter hours of the day.
+For example in \autoref{fig:bothcust}(a), it can be seen that median energy consumption for the early morning hours is extremely high for weekdays compared to weekends.
+Also, outliers are more prominent in the latter part of the day.
 All of these indicate that looking at different distribution geometry or changing the mapping might shed lights on different aspect of the energy behavior for the same sample population.
-
-\begin{table}
-
-\caption{\label{tab:harmony-tab}Harmonies with a pair of cyclic granularity one placed on facet and the other on x-axis.
-Out of 42 possible combinations of cyclic granularities, only 16 are harmony pairs.}
-\centering
-\begin{tabular}[t]{llrr}
-\toprule
-facet variable & x-axis variable & facet levels & x-axis levels\\
-\midrule
-day\_week & hour\_day & 7 & 24\\
-day\_month & hour\_day & 31 & 24\\
-week\_month & hour\_day & 5 & 24\\
-wknd\_wday & hour\_day & 2 & 24\\
-hour\_day & day\_week & 24 & 7\\
-\addlinespace
-day\_month & day\_week & 31 & 7\\
-week\_month & day\_week & 5 & 7\\
-hour\_day & day\_month & 24 & 31\\
-day\_week & day\_month & 7 & 31\\
-wknd\_wday & day\_month & 2 & 31\\
-\addlinespace
-hour\_day & week\_month & 24 & 5\\
-day\_week & week\_month & 7 & 5\\
-wknd\_wday & week\_month & 2 & 5\\
-hour\_day & wknd\_wday & 24 & 2\\
-day\_month & wknd\_wday & 31 & 2\\
-\addlinespace
-week\_month & wknd\_wday & 5 & 2\\
-\bottomrule
-\end{tabular}
-\end{table}
 
@@
 Two granularities are used: hour of the day (I) and weekday/weekend (II).
-Plot (a) shows granularity I faceted by granularity II, and plots (b), (c) shows the converse mapping.
+Plot (a) shows granularity I facetted by granularity II, and plots (b), (c) shows the converse mapping.
 Plot (a) makes a comparison of usage by workday within each hour of the day using side-by-side boxplots.
@@
 This is an intuitive possibility, because heterogeneous \texttt{customer\_id}'s with very different occupation or demographics will tend to have very different energy behavior and combining them together will somehow weaken any typical or extreme behavior.
-A strategy for analyzing periodicities of multiple keys together could be to group the keys basis their energy behavior across different cyclic granularities.
+A strategy for analyzing multiple keys together could be to first group them basis time series or demographic features and then look at their energy behavior.
 This is beyond the scope of the current work.
+
+This case study shows systematic exploration of energy behavior for a household to gain exhaustive insights on periodic behavior of the households.
 
@@
 Although there is no conventional time component in cricket, each ball can be thought to represent an ordering from past to future with the game progressing forward with each ball.
-In the Twenty20 format, an over will consist of 6 balls (with some exceptions), an innings is restricted to a maximum of 20 overs, a match will consist of 2 innings and a season consists of several matches.
+In the Twenty20 format, an over will consist of 6 balls (with some exceptions), an inning is restricted to a maximum of 20 overs, a match will consist of 2 innings and a season consists of several matches.
 Thus, similar to time, there is a hierarchy where ball is nested within overs, overs nested within innings and innings within matches.
 The idea of cyclic granularities can be likewise mapped to this hierarchy.
-Example granularites then include ball of the over, over of the innings and ball of the innings.
+Example granularites then include ball of the over, over of the inning and ball of the inning.
 Although most of these cyclic granularities are circular in design of the hierarchy, in application of the rules some granularities are aperiodic.
-For example, in most cases an over will consist of 6 balls with some exceptions like wide balls or when an innings finishes before the over finishes.
+For example, in most cases an over will consist of 6 balls with some exceptions like wide balls or when an inning finishes before the over finishes.
 Thus, the cyclic granularity ball-of-over will be circular in most cases and aperiodic in others.
 
-\noindent The Indian Premier League (IPL) is a professional Twenty20 cricket league in India contested by eight teams representing eight different cities in India.
+The Indian Premier League (IPL) is a professional Twenty20 cricket league in India contested by eight teams representing eight different cities in India.
 The ball by ball data for IPL season 2008 to 2016 is fetched from \href{https://www.kaggle.com/josephgpinto/ipl-data-analysis/data}{Kaggle}.
-The \texttt{cricket} data set in the \texttt{gravitas} package summarizes the ball-by-ball data across overs and contains information for a sample of 214 matches spanning 9 seasons (2008 to 2016) such that each over has 6 balls, each innings has 20 overs and each match has 2 innings.
+The \texttt{cricket} data set in the \texttt{gravitas} package summarizes the ball-by-ball data across overs and contains information for a sample of 214 matches spanning 9 seasons (2008 to 2016) such that each over has 6 balls, each inning has 20 overs and each match has 2 innings.
 This could be useful in a periodic world when we wish to compute any circular/quasi-circular granularity based on a hierarchy table which look like \autoref{tab:hierarchy-cric}.
-However, even if the situation is not periodic, it can be interesting to visualize the distribution of a measured variable to shed light on the aperiodic behavior of a non-temporal data set similar to aperiodic events like formal meetings, workshops, conferences, school semesters in a temporal set up.
 
@@
 
-\caption{\label{tab:hierarchy-cric}Hierarchy table for cricket where overs are nested within an innings, innings nested within a match and matches within a season.}
+\caption{\label{tab:hierarchy-cric}Hierarchy table for cricket where overs are nested within an inning, innings nested within a match and matches within a season.}
 \centering
@@
 
-\noindent There are many interesting questions that could possibly be answered with the \texttt{cricket} data set.
-For example, it would be interesting to see if the distribution of total runs vary depending on if a team bats in the first or second innings.
+However, even if the situation is not periodic and a similar hierarchy can not be formed, it can be interesting to visualize the distribution of a measured variable across relevant cyclic granularities to shed light on the aperiodic behavior of a non-temporal data set similar to aperiodic events like formal meetings, workshops, conferences, school semesters in a temporal set up.
+There are many interesting questions that could possibly be answered with such a data set irrespective of the type of cyclic granularities.
+
+First, it would be interesting to see if the distribution of total runs vary depending on if a team bats in the first or second innings.
 The Mumbai Indians (MI) and Chennai Super kings (CSK) appeared in final playoffs from 2010 to 2015.
 We take their example in order to dive deeper into this question.
-From Figure \ref{fig:cricex}(a), it can be observed that for the team batting in the first innings there is an upward trend of runs per over, while there is no clear upward trend in median and quartile deviation of runs for the teams batting in the second inning.
+From Figure \ref{fig:cricex}(a), it can be observed that for the team batting in the first inning there is an upward trend of runs per over, while there is no clear upward trend in median and quartile deviation of runs for the teams batting in the second inning.
 This seem to indicate that players feel mounting pressure to score more runs as they approach towards the end of the first inning.
-Whereas teams batting in the second innings have a set target in mind and are not subjected to such mounting pressure and may adopt a more conservative strategy, to score runs.
+Whereas teams batting in the second inning have a set target in mind and are not subjected to such mounting pressure and may adopt a more conservative strategy, to score runs.
 Thus winning teams like CSK and MI seem to employ different inning strategies when it comes to their batting order.
 
-\noindent Another fascinating exploration would be to examine if runs per over decrease in the subsequent over if fielding (defending) was good in the previous over?
+Another interesting question could be: do runs per over decrease in the subsequent over if fielding (defending) was good in the previous over?
 For establishing the fielding quality, we apply an indicator function on dismissals (1 if there was at least one wicket in the previous over due to run out or catch, 0 otherwise).
@@
 Figure \ref{fig:cricex}(b) shows that no dismissals in the previous over leads to a higher median and quartile spread of runs per over as compared to the case when there has been at least one dismissal in the previous over.
-Wickets per over are considered as an aperiodic cyclic granularity with wickets as an aperiodic linear granularity.
-These granularities do not appear in the hierarchy table since it is difficult to position them in a hierarchy.
-These are similar to holidays or special events in temporal data.
 
@@
 
-\hypertarget{sec:discussion}{%
-\section{Discussion}\label{sec:discussion}}
+Wickets per over are considered as an aperiodic cyclic granularity with wickets as an aperiodic linear granularity.
+These granularities do not appear in the hierarchy table since it is difficult to position them in a hierarchy.
+These are similar to holidays or special events in temporal data.
 
-Exploratory data analysis and data analysis in general involve many iterations of finding and summarizing patterns.
-With temporal data available at ever finer scales, exploring periodicity can become overwhelming with so many possible granularities to explore.
-This work provides a framework to systematically explore distribution of an univariate measured variable across two cyclic time granularities by creating any cyclic granularity, ranking a list of harmonies and thereby identifying possible distribution plots for effective visualization based on relationship and levels of the cyclic granularities.
+\hypertarget{discussion-points-and-future-work}{%
+\section{Discussion points and future work}\label{discussion-points-and-future-work}}
 
-A missing piece in the package \texttt{gravitas} is the computation of cyclic aperiodic granularities which would require computing aperiodic linear granularities first.
-A few R packages like \texttt{almanac} and \texttt{gs} provide functionality to create recurring events that are not periodic.
-These functions can be imported in the \texttt{gravitas} package to accommodate for aperiodic cyclic granularities.
-Another future direction of work could be to further refine the search of harmonies by only selecting pairs of cyclic granularities for which variation in measured variable is significant and rating these selected harmony pairs in order of importance for exploration.
+Exploratory data analysis involve many iterations of finding and summarizing patterns.
+With temporal data available at ever finer scales, exploring periodicity has become overwhelming with so many possible granularities to explore.
+This work refines the selection of appropriate pairs of granularities by identifying those for which the differences between the displayed distributions is greatest, and rating these selected harmony pairs in order of importance for exploration.
 
-\hypertarget{acknowledgements}{%
-\section*{Acknowledgements}\label{acknowledgements}}
-\addcontentsline{toc}{section}{Acknowledgements}
+A future direction of work could be to look at more individuals/subjects and group them according to similar periodic behavior.
+Behaviors across different cyclic granularities would be different for different subjects and one way to find groups would be to actually locate clusters who have similar periodic behavior.
 
-The authors would like to thank the cohort \href{https://www.monash.edu/news/articles/team-profile-monash-business-analytics-team}{NUMBATS}, Monash University for sharing their wisdom and experience of developing R packages and Dr.~Peter Toscas \href{https://data61.csiro.au/}{from Data61 CSIRO} for providing useful inputs on improving the analysis of smart meter application.
-The package \texttt{gravitas} was built during the \href{https://summerofcode.withgoogle.com/archive/}{Google Summer of Code, 2019}.
-We would also like to thank Nicholas Spyrison for many useful discussions, sketching figures and feedback on the manuscript.
-More details about the package can be found on the package website \href{https://sayani07.github.io/gravitas/}{sayani07.github.io/gravitas}.
-This article was created with \texttt{knitr} \citep[\citet{R-knitr}]{knitr2015} and \texttt{rmarkdown} \citep[\citet{R-rmarkdown}]{rmarkdown2018}.
-This paper's Github repository, \href{https://github.com/Sayani07/paper-gravitas}{github.com/Sayani07/paper-gravitas}, contains all materials required to reproduce this article and the code is also available online in the supplemental materials.
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
 
-\hypertarget{supplemental-materials}{%
-\section{Supplemental Materials}\label{supplemental-materials}}
+\hypertarget{null-distribution-1}{%
+\subsection{Null distribution}\label{null-distribution-1}}
 
-\textbf{Data and scripts:} Data sets and R code to reproduce all figures in this article (main.Rmd).
+\hypertarget{size-simulated-same-distribution-for-all-combinations-of-categories-for-all-harmony-pairs.}{%
+\subsubsection{Size: Simulated same distribution for all combinations of categories for all harmony pairs.}\label{size-simulated-same-distribution-for-all-combinations-of-categories-for-all-harmony-pairs.}}
 
-\textbf{R-package:} The ideas presented in this article have been implemented in the open-source R \citep{R-language} package \texttt{gravitas} \citep{R-gravitas}, available from CRAN.
-The R-package facilitates manipulation of single and multiple-order-up time granularities through cyclic calendar algebra, check feasibility of creating plots or drawing inferences for any two cyclic granularities by providing list of harmonies and recommend prospective probability distributions through factors described in the article.
-Version 0.1.2 of the package was used for the results presented in the article and is available on Github (\url{https://github.com/Sayani07/gravitas}).
+Failure to reject the null hypothesis when there is in fact no significant effect.
 
-\textbf{R-packages:} Each of the R packages used in this article are available online with URLs provided in the bibliography.
+\hypertarget{normalised-maximum-distances-follow-standard-gumbel-distribution}{%
+\subsubsection{Normalised maximum distances follow standard Gumbel distribution}\label{normalised-maximum-distances-follow-standard-gumbel-distribution}}
 
-\bibliographystyle{agsm}
-\bibliography{bibliography.bib}
+\hypertarget{limiting-distribution-of-median-of-normalised-maximum-distances-is-normal}{%
+\subsubsection{Limiting distribution of median of normalised maximum distances is normal}\label{limiting-distribution-of-median-of-normalised-maximum-distances-is-normal}}
+
+Let a continuous population be given with cdf F(x) (cumulative distribution function) and median \(\xi\) (assumed to exist uniquely).
+For a sample of size \(2n + 1\), let \(\tilde{x}\) denote the sample median.
+The distribution of \(\tilde{x}\),under certain conditions, to be asymptotically normal with mean \(\xi\) and variance \(\sigma_n^2 = \frac{1}{4} [f(\xi)]^2(2n + 1)\), where \(f(x) = F'(x)\) is the pdf (probability density function).
+
+\hypertarget{power}{%
+\subsection{Power}\label{power}}
+
+\hypertarget{confidence-interval}{%
+\subsection{Confidence interval}\label{confidence-interval}}
+
+Failure to reject the null hypothesis when there is in fact a significant effect.
+
+To estimate the sampling distribution of the test statistic we need many samples generated under the null hypothesis.
+If the null hypothesis is true, changing the exposure would have no effect on the outcome.
+By randomly shuffling the exposures we can make up as many data sets as we like.
+If the null hypothesis is true the shuffled data sets should look like the real data, otherwise they should look different from the
+real data. The ranking of the real test statistic among the shuffled test statistics gives a p-value.
+
+\hypertarget{varying-distribution-across-facet}{%
+\subsubsection{Varying distribution across facet}\label{varying-distribution-across-facet}}
+
+\hypertarget{varying-distribution-across-x-axis}{%
+\subsubsection{Varying distribution across x-axis}\label{varying-distribution-across-x-axis}}
+
+\hypertarget{varying-distribution-across-both-facets-and-x-axis}{%
+\subsubsection{Varying distribution across both facets and x-axis}\label{varying-distribution-across-both-facets-and-x-axis}}
+
+\hypertarget{repeat-all-with-varying-facet-and-x-axis-levels}{%
+\subsubsection{Repeat all with varying facet and x-axis levels}\label{repeat-all-with-varying-facet-and-x-axis-levels}}
+
+\emph{Conclusion}: The test should reject the null hypothesis if distributions are different.
+
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-Dang2014-tw}{}%
+Dang, T N, and L Wilkinson. 2014. ``ScagExplorer: Exploring Scatterplots by Their Scagnostics.'' In \emph{2014 IEEE Pacific Visualization Symposium}, 73--80.
+
+\leavevmode\hypertarget{ref-smart-meter}{}%
+Department of the Environment and Energy.
+2018.
+\emph{Smart-Grid Smart-City Customer Trial Data}.
+Australian Government, Department of the Environment; Energy: Department of the Environment; Energy, Australia.
+\url{https://data.gov.au/dataset/4e21dea3-9b87-4610-94c7-15a8a77907ef}.
+
+\leavevmode\hypertarget{ref-R-gravitas}{}%
+Gupta, Sayani, Rob Hyndman, Di Cook, and Antony Unwin. 2019. \emph{gravitas: Explore Probability Distributions for Bivariate Temporal Granularities}. \url{https://CRAN.R-project.org/package=gravitas}.
+
+\leavevmode\hypertarget{ref-Gupta2020-vo}{}%
+Gupta, Sayani, Rob J Hyndman, Dianne Cook, and Antony Unwin.
+2020.
+``Visualizing Probability Distributions Across Bivariate Cyclic Temporal Granularities,'' October.
+\url{http://arxiv.org/abs/2010.00794}.
+
+\leavevmode\hypertarget{ref-Kullback1951-jy}{}%
+Kullback, S, and R A Leibler. 1951. ``On Information and Sufficiency.'' \emph{Ann. Math. Stat.} 22 (1): 79--86.
+
+\leavevmode\hypertarget{ref-Menendez1997-in}{}%
+Menéndez, M L, J A Pardo, L Pardo, and M C Pardo. 1997. ``The Jensen-Shannon Divergence.'' \emph{J. Franklin Inst.} 334 (2): 307--18.
+
+\leavevmode\hypertarget{ref-tukey1988computer}{}%
+Tukey, John W, and Paul A Tukey. 1988. ``Computer Graphics and Exploratory Data Analysis: An Introduction.'' \emph{The Collected Works of John W. Tukey: Graphics: 1965-1985} 5: 419.
+
+\leavevmode\hypertarget{ref-wang2020calendar}{}%
+Wang, Earo, Dianne Cook, and Rob J Hyndman.
+2020.
+``Calendar-Based Graphics for Visualizing People's Daily Schedules.'' \emph{Journal of Computational and Graphical Statistics}.
+\url{https://doi.org/10.1080/10618600.2020.1715226}.
+
+\leavevmode\hypertarget{ref-wilkinson2005graph}{}%
+Wilkinson, Leland, Anushka Anand, and Robert Grossman. 2005. ``Graph-Theoretic Scagnostics.'' In \emph{IEEE Symposium on Information Visualization, 2005. INFOVIS 2005.}, 157--64. IEEE.
 

### 2020-11-19 main.Rmd
normalisation results look like it is not normalised

@@
 
-```{r norm-data, "Distribution of $MMPD_{norm}$ across different levels of facet and x-axis. These distributions should look the same if normalisation worked." }
+```{r norm-data, fig.cap = "Distribution of $MMPD_{norm}$ across different levels of facet and x-axis. These distributions should look the same if normalisation worked." }
 mmpd_norm = read_rds("../hakear-drake/data/data_norm_213045f.rds") 
@@
 
-```{r null-dist, echo = FALSE, fig.cap="Distribution of mmpd across different facet levels (columns) and x-axis levels (rows) for null ditribution normal(5,10) and gamma(0.5, 0.2).
+```{r null-dist, eval =  FALSE, echo = FALSE, fig.cap="Distribution of mmpd across different facet levels (columns) and x-axis levels (rows) for null ditribution normal(5,10) and gamma(0.5, 0.2).
 The distribution of MMPD is unaffected by the null distribution considered.

### 2020-11-19 main.Rmd
added MMPD_norm values

@@
 ```{r}
+data1  = sim_panel(nx = 2, nfacet = 3, ntimes = 500)
+simulated_data <- sim_panel(nx = 2,
+nfacet = 3,
+ntimes = 500,
+sim_dist = rep(dist_normal(seq(5, 15, 5), 5), each = 2))
+data2 = simulated_data
+data4 = sim_panel(nx = 2,
+nfacet = 3,
+ntimes = 500,
+sim_dist = dist_normal(seq(5,30, 5), 5))
+data3 = data2 %>% rename("temp" = "id_facet") %>% rename("id_facet" = "id_x") %>% rename("id_x" = "temp")
+
+library(parallel)
+library(gravitas)
+library(hakear)
+
+set.seed(1000)
+r1 <- compute_mmpd_norm(data1, "id_x", "id_facet", response = sim_data, nperm = 200)
+
+r2 <- compute_mmpd_norm(data2, "id_x", "id_facet", response = sim_data, nperm = 200)
+
+r3 <- compute_mmpd_norm(data3, "id_x", "id_facet", response = sim_data, nperm = 200)
+
+r4 <- compute_mmpd_norm(data4, "id_x", "id_facet", response = sim_data, nperm = 200)
+
+p1 <- data1 %>%
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +xlab("")
+
+p2 <- data2 %>% ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +xlab("")
+
+p3 <- data3 %>% ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +xlab("")
+
+p4 <- data4 %>% 
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +xlab("")
+
+gridExtra::grid.arrange(gridExtra::arrangeGrob(p1, top = paste("MMPD_norm:", round(r1, 3))),
+                        gridExtra::arrangeGrob(p2, top = paste("MMPD_norm:", round(r2, 3))),
+                        gridExtra::arrangeGrob(p3, top = paste("MMPD_norm:", round(r3, 3))),
+                        gridExtra::arrangeGrob(p4, top = paste("MMPD_norm:", round(r4, 3))),
+                        ncol = 2, nrow=2)
 

### 2020-11-19 main.Rmd
algorithm section delete

@@
 ```
-
-# Algorithm
-
-\noindent The algorithm employed for computing MMPD is summarized as follows:
-<!-- Algorithm -->
-
-<!-- 1.
-Suppose $C_i$ and $C_2$ are two cyclic granularities such that $C_i$ maps index set to a set $\{A_1, A_2, A_3, \dots, A_l$\}, and $C_2$ maps index set to a set $\{B_1, B_2, B_3, \dots, B_m$\} and $v$ is the measured variable.
-Hence for each combination ($A_k$, $B_l$), we have the time series variable $v_{ij} \subseteq v$, $\forall i = {1, 2, \dots, l}$ and $\forall j = {1, 2, \dots, m}$ -->
-
-- **Input:** Data corresponding to all harmony pairs, i.e., data sets of the form $(C_i, C_j, v)$ 
-$\forall i, j \in N_C$  
-- **Output:** MMPD (Median Maximum Pairwise Distances) measuring the average variation across different levels of $C_i$ and $C_j$ $\forall i, j \in N_C$
-
-1. Fix harmony pair $(C_i, C_j)$.
-
-2. Fix $k$. Then there are $L$ groups corresponding to level $A_k$ of $C_i$.
-
-3. Compute  $m = \binom{L}{2}$ pairwise distances between distributions of $L$ unordered levels and $m = L-1$ pairwise distances for $L$ ordered categories.
-
-4. Identify maximum within the $m$ computed distances.
-
-5. Compute normalized maximum distance ($NM$) using appropriate norming constants.
-<!--so that the distribution of the normalized maximum converges to a Gumbel distribution as $m\rightarrow\infty$.-->
-
-6. Use Steps 1-5 to compute normalized maximum distance for $\forall k \in  \{1, 2, \ldots, K\}$.
-
-7. Compute MMPD = median $(NM_1, NM_2, \dots, NM_K)$/log($K$).
-
-8. Repeat Steps 1 to 7 for all harmony pairs.
 

### 2020-11-24 main.Rmd
minor changes

@@
 bibliography: bibliography.bib
+preamble: >
+  \usepackage{mathtools,amssymb,booktabs,amsthm,todonotes,colortbl}
+  \def\mod{~\text{mod}~}
+  \newtheorem{definition}{Definition}
+  \usepackage{mathptmx}
+  \usepackage{caption}
+  \usepackage{algorithm, algorithmicx, algpseudocode}
+  \DeclareCaptionStyle{italic}{labelfont={bf},textfont={it},labelsep=colon}
+  \captionsetup[figure]{style=italic,format=hang,singlelinecheck=true}
+  \captionsetup[table]{style=italic,format=hang,singlelinecheck=true}
+  \def\novspacing{\setlength{\aboverulesep}{0pt}\setlength{\belowrulesep}{0pt}}
+  \def\vspacing{\setlength{\aboverulesep}{0.4ex}\setlength{\belowrulesep}{0.65ex}}
 output:
@@
 ```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
-options("knitr.graphics.auto_pdf" = TRUE)
+options("knitr.graphics.auto_pdf" = TRUE,
+        tinytex.verbose = TRUE)
 library(knitr)
@@
 ```{r norm-data, fig.cap = "Distribution of $MMPD_{norm}$ across different levels of facet and x-axis. These distributions should look the same if normalisation worked." }
-mmpd_norm = read_rds("../hakear-drake/data/data_norm_213045f.rds") 
+mmpd_norm = read_rds("../hakear-drake/data/data_norm_low_new.rds") 
 hist_plot = mmpd_norm %>% 

### 2020-11-25 paper/main.Rmd
new structure for maintaining simulations

--- 2020-11-24 main.Rmd
@@
 #                                                                read_chunk('main.R')
-read_chunk("null_distribution.R")
-read_chunk("mean_null.R")
+read_chunk("R/null_distribution.R")
+read_chunk("R/mean_null.R")
 source("R/sim_panel.R")

### 2020-11-26 paper/main.Rmd
structure change with runs pairwise and mmpd raw included

--- 2020-11-24 main.Rmd
@@
 library(sugrrants)
+library(here)
 
@@
 #                                                                read_chunk('main.R')
-read_chunk("null_distribution.R")
-read_chunk("mean_null.R")
-source("R/sim_panel.R")
+here::here()
+read_chunk(here::here("paper/R/", "null_distribution.R"))
+read_chunk(here::here("paper/R/", "mean_null.R"))
+source(here::here("paper/R/sim_panel.R"))
 # Set up plan
@@
 ```{r calendar-elec, fig.height = 10.5, fig.cap="Calendar display."}
-elec <- read_rds("data/elec.rds") %>% 
+elec <- read_rds(here("paper/data/elec.rds")) %>% 
   filter(date >= ymd("20180101"), date < ymd("20180701"))
@@
 
+sim_varf_dist1 = function(nx, nfacet){
+  rep(dist_normal(seq(mean,mean*nfacet, by = mean), sd), each = nx)}
+
 p1 <- sim_panel(nx = 2, nfacet = 3, ntimes = 500) %>%
@@
 
-### Distribution
+# Behavior of raw distance measure
+
+## Distribution
 <!-- ### Need for normalisation -->
@@
 
+```{r hist-nx-nfacet}
+knitr::include_graphics(here::here("simulations/result_report/hist_nxbyfacet.png"))
+```
+
 ```{r dist-across-facets, fig.cap = "Distribution of $MMPD_{raw}$ for different facet levels are shown.
+The location of the distribution shifts rightwards implying that as the number of facets increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained."}
+here::here()
+knitr::include_graphics(here::here("simulations/result_report","nx_by_facet_raw.png"))
+```
+
+<!-- # ```{r dist-across-facets, fig.cap = "Distribution of $MMPD_{raw}$ for different facet levels are shown.
 The location of the distribution shifts rightwards implying that as the number of facets increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained.
-"}
-mmpd_raw = read_rds("../hakear-drake/data/data_all23457914n.rds") 
-mmpd_xmore = read_rds("../hakear-drake/data/data_all213045x.rds") 
-mmpd_fmore = read_rds("../hakear-drake/data/data_all_213045f_allx.rds")
-
-data_all = bind_rows(mmpd_raw, mmpd_xmore)
-
-data_long = data_all %>% pivot_longer(c(1:2), names_to = "category", values_to = "levels")
-
-g1 <- data_all %>% 
-  filter(!(nx %in% c(3, 4))) %>% 
-  ggplot() +
-  ggridges::geom_density_ridges(aes(x = raw_mmpd, 
-                                    y = as.factor(nfacet))) +
-  facet_wrap(~nx, nrow = 2)
-g1
-```
+"} -->
+<!-- # mmpd_raw = read_rds("../hakear-drake/data/data_all23457914n.rds")  -->
+<!-- # mmpd_xmore = read_rds("../hakear-drake/data/data_all213045x.rds")  -->
+<!-- # mmpd_fmore = read_rds("../hakear-drake/data/data_all_213045f_allx.rds") -->
+<!-- #  -->
+<!-- # data_all = bind_rows(mmpd_raw, mmpd_xmore) -->
+<!-- #  -->
+<!-- # data_long = data_all %>% pivot_longer(c(1:2), names_to = "category", values_to = "levels") -->
+<!-- #  -->
+<!-- # g1 <- data_all %>%  -->
+<!-- #   filter(!(nx %in% c(3, 4))) %>%  -->
+<!-- #   ggplot() + -->
+<!-- #   ggridges::geom_density_ridges(aes(x = raw_mmpd,  -->
+<!-- #                                     y = as.factor(nfacet))) + -->
+<!-- #   facet_wrap(~nx, nrow = 2) -->
+<!-- # g1 -->
+<!-- # ``` -->
 
@@
 "}
-g2 <- data_all %>% 
-  filter(nfacet<=14, nfacet!=3) %>% 
-  ggplot() +
-  geom_boxplot(aes(y = raw_mmpd, 
-                                    x = as.factor(nx))) +
-  facet_wrap(~nfacet) + coord_flip()
-
-#  hist_plot = data_all %>% 
-#       ggplot() +
-#       geom_density(aes(x = raw_mmpd), fill = "blue") +
-#       facet_grid(nx~nfacet)
-# hist_plot
-g2
-```
+knitr::include_graphics(here::here("simulations/result_report/","nfacet_by_nx_raw.png"))
+```
+
+<!-- # ```{r dist-across-x, fig.cap = "Distribution of $MMPD_{raw}$ for different x levels are shown.
+The scale of the distribution becomes less and less implying that as the number of x levels increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained as the spread of the distribution decreases.
+"} -->
+<!-- # g2 <- data_all %>%  -->
+<!-- #   filter(nfacet<=14, nfacet!=3) %>%  -->
+<!-- #   ggplot() + -->
+<!-- #   geom_boxplot(aes(y = raw_mmpd,  -->
+<!-- #                                     x = as.factor(nx))) + -->
+<!-- #   facet_wrap(~nfacet) + coord_flip() -->
+<!-- #  -->
+<!-- # #  hist_plot = data_all %>%  -->
+<!-- # #       ggplot() + -->
+<!-- # #       geom_density(aes(x = raw_mmpd), fill = "blue") + -->
+<!-- # #       facet_grid(nx~nfacet) -->
+<!-- # # hist_plot -->
+<!-- # g2 -->
+<!-- # ``` -->
 
@@
 ```{r}
-knitr::include_graphics("Figs/simulation.png")
+knitr::include_graphics(here::here("paper/Figs/simulation.png"))
 ```
@@
 
-cricket_all <- read_csv("data-raw/deliveries_all.csv")
-matches_all <- read_csv("data-raw/matches_all.csv")
+cricket_all <- read_csv("paper/data-raw/deliveries_all.csv")
+matches_all <- read_csv("paper/data-raw/matches_all.csv")
 

### 2020-11-26 simulations/null/job-pairwise_max.sh

@@ -1,0 +1,12 @@
+#! /bin/bash
+#SBATCH --job-name=null_normal_norm
+#SBATCH --output=trace_%a.out
+#SBATCH --error=error_%a.err
+#SBATCH --mem-per-cpu=4096
+#SBATCH --time=168:00:00
+#SBATCH --array=1-64
+#SBATCH --ntasks=1
+#SBATCH --cpus-per-task=1
+#SBATCH --export=NONE
+module load R/4.0.0-openblas
+Rscript raw_pairwise_max.R $SLURM_ARRAY_TASK_ID 

### 2020-11-26 simulations/null/raw_mmpd.R

@@ -1,9 +1,8 @@
 #This script calculates raw mmpd for each simulation scenario
 ##Read Simulation Table
-
+.libPaths(c("~/R/libs", .libPaths()))
 library(distributional)
 library(readr)
-library(drake)
 library(tidyverse)
 
 
@@ -21,9 +20,9 @@ nxj<-simj$nx #Which nx level
 
 #create data for each row for null normal
 set.seed(9999)
-sim_null_normal = function(nxj, nfacetj){
+sim_null_normal = function(nx, nfacet){
   rep(distributional::dist_normal(5, 10), 
-      times = nxj*nfacetj)
+      times = nx*nfacet)
 }
 
 sim_panel_data = 

### 2020-11-26 simulations/null/raw_pairwise_data.R

@@ -1,0 +1,61 @@
+#This script calculates raw distance measure based on transforming pairwise distances for each simulation scenario
+##Read Simulation Table
+
+.libPaths(c("~/R/libs", .libPaths()))
+library(distributional)
+library(readr)
+library(drake)
+library(tidyverse)
+library(hakear)
+
+nsim = 2
+simtable<-read_csv('sim_table.csv')
+
+### Extract flags from simulation scenario
+
+scen<- 3 #If running within R uncomment this.  This will only run first scenario
+#scen<-as.numeric(commandArgs()[[6]]) # If running batch job uncomment this
+
+simj<-simtable[scen,] #Extract row of table
+nfacetj<-simj$nfacet # Which nfacet level
+nxj<-simj$nx #Which nx level
+
+#create data for each row for null normal
+set.seed(9999)
+sim_null_normal = function(nxj, nfacetj){
+  rep(distributional::dist_normal(5, 10), 
+      times = nxj*nfacetj)
+}
+
+sim_panel_data = 
+  hakear::sim_panel(nx = nxj,
+                    nfacet = nfacetj, 
+                    ntimes = 500, 
+                    sim_dist = sim_null_normal) %>% 
+  unnest(c(data)) %>% ungroup()
+
+#shuffling this data
+set.seed(1111)
+
+raw_dist <- map(seq_len(nsim), function(i)
+{
+  new_sim_data = sample(sim_panel_data$sim_data, 
+                        size = nrow(sim_panel_data))
+  new_data = sim_panel_data %>% 
+    select(-sim_data) %>% 
+    mutate(sim_data = new_sim_data)
+  
+  # for creating one raw mmpd
+  raw_mmpd = hakear::compute_pairwise_dist(new_data, 
+                                  gran_x = "id_x",
+                                  gran_facet = "id_facet",
+                                  response = sim_data) %>% 
+    as_tibble() %>% mutate(perm_id = i)
+  
+}) %>% bind_rows()
+
+saveRDS(raw_dist, paste0('../results/raw/data/',
+                         nxj,'_',
+                         nfacetj,'_pairwise_max_data.rds'))
+
+

### 2020-11-26 paper/main.Rmd
algo update separate pdf

@@
 
-### Notations
-
-Consider two cyclic granularities $C_i$ and $C_j$, such that $C_i$ maps index set to a set $\{A_k \mid k=1,\dots,K\}$ and $C_j$ maps index set to a set $\{B_\ell \mid \ell =1,\dots,L\}$.
-Here, $A_k$ and $B_\ell$ are the levels/categories corresponding to $C_i$ and $C_j$ respectively.
-Let $S_{k\ell}$ be a subset of the index set such that for all $s \in S_{k\ell}$, $C_i(s) = A_k$ and $C_j(s) = B_\ell$.
-There are $KL$ such data subsets, one for each combination of levels ($A_k$, $B_\ell$).
-Moreover, consider that in the graphical space, $C_i$ is mapped to facets and $C_j$ is mapped to x-axis.
-
 ### Characterising distribution
 
-Each of the $KL$ data subsets in the data structure have multiple observations and may vary widely across different subsets due to the structure of the calendar, missing observations or uneven locations of events in the time domain.
+Each of the data subsets in the data structure have multiple observations and may vary widely across different subsets due to the structure of the calendar, missing observations or uneven locations of events in the time domain.
 The set of observations corresponding to each combination is assumed to be a sample from an unknown probability density function.
@@
 
+Consider two cyclic granularities $C_i$ and $C_j$, such that $C_i$ maps index set to a set $\{A_k \mid k=1,\dots,K\}$ and $C_j$ maps index set to a set $\{B_\ell \mid \ell =1,\dots,L\}$.
+Here, $A_k$ and $B_\ell$ are the levels/categories corresponding to $C_i$ and $C_j$ respectively.
+Let $S_{k\ell}$ be a subset of the index set such that for all $s \in S_{k\ell}$, $C_i(s) = A_k$ and $C_j(s) = B_\ell$.
+There are $KL$ such data subsets, one for each combination of levels ($A_k$, $B_\ell$).
+Moreover, consider that in the graphical space, $C_i$ is mapped to facets and $C_j$ is mapped to x-axis.
+
 The algorithm employed for computing the distance measure is summarized as follows:
@@
 
-5. Compute maximum distance ($M$) using appropriate norming constants.
-
-6. Use Steps 1-5 to compute maximum distance for $\forall k \in  \{1, 2, \ldots, K\}$.
-
-7. Compute the distance measure MMPD_raw = median $(M_1, M_2, \dots, M_K)$.
+<!-- 5. Compute distribution of maximum distance ($M$) by shuffling the data $200$ times and finishing Steps1-4 in each case. Scale $M$ using the mean and sd of the distribution.  -->
+
+5. Use Steps 1-4 to compute maximum distance for $\forall k \in  \{1, 2, \ldots, K\}$.
+
+6. Compute the distance measure MMPD_raw = median $(M_1, M_2, \dots, M_K)$.
+
+<!-- \begin{algorithm}[!thb] -->
+<!-- 	\caption{Calculation for a raw distance measure between two cyclic granularities $A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.}\label{alg:scoreopt}.
+-->
+<!-- 	\begin{algorithmic}[1] -->
+<!-- 		\Procedure{RawMMPD}{$A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$, $v = \{ v_t: t = 1, 2, \dots, T\}$}. -->
+<!-- 		\For{$k=1:K$, $j=1:J$} -->
+<!-- 		\State Find distances between pairs of all possible combinations of categories $(a_jb_k,a_j'b_k')$ by computing JSD between quantiles of the measured variable $q(v)$ across these combinations.
+-->
+<!-- 		\State $d \gets JSD(\tilde{q(v)_{a_{j}b_{k}}},\tilde{q(v)_{a_{j}'b_{k}'}})$ -->
+<!-- 		\If {$b_k = b_k'$}  -->
+<!-- 		\State $d* \gets \lambda d$  \Comment{upweight within-facet distances} -->
+<!-- 		\Else  -->
+<!-- 		\State $d* \gets 1/\lambda d $ \Comment{downweight across-facet distances} -->
+<!-- 		\EndFor -->
+<!-- 		\State Set the raw distance measure as $max(d*)$ where max is taken over all $j, j', k, k'$. -->
+
+<!-- 		\EndProcedure -->
+<!-- 	\end{algorithmic} -->
+<!-- \end{algorithm} -->
 
@@
 
-## Distribution
+## Simulation study
+
+To understand the behavior of raw MMPD for different parameters $nperm$ <number of permutations>, $n$ <sample size> ($n_x$, $n_f$ and combination), $D$ <different data set>, $l_x$<levels of x-axis>, $l_f$ <levels of facets>.
+
+## Distribution across facet and x categories
 <!-- ### Need for normalisation -->
@@
 -->
+
+## Distribution across different sample size
+## Distribution across different permutation size
+## Distribution across normal and non-normal underlying distribution
 

### 2020-11-26 paper/main.Rmd
cleaning images

@@
 
+r1prime <- compute_norm_pairwise_max(data1, "id_x", "id_facet", response = sim_data, nperm = 200)
+
+r2prime <- compute_norm_pairwise_max(data2, "id_x", "id_facet", response = sim_data, nperm = 200)
+
+r3prime <- compute_norm_pairwise_max(data3, "id_x", "id_facet", response = sim_data, nperm = 200)
+
+r4prime <- compute_norm_pairwise_max(data4, "id_x", "id_facet", response = sim_data, nperm = 200)
+
 p1 <- data1 %>%
@@
 
-gridExtra::grid.arrange(gridExtra::arrangeGrob(p1, top = paste("MMPD_norm:", round(r1, 3))),
-                        gridExtra::arrangeGrob(p2, top = paste("MMPD_norm:", round(r2, 3))),
-                        gridExtra::arrangeGrob(p3, top = paste("MMPD_norm:", round(r3, 3))),
-                        gridExtra::arrangeGrob(p4, top = paste("MMPD_norm:", round(r4, 3))),
+gridExtra::grid.arrange(gridExtra::arrangeGrob(p1, top = paste("MMPD", round(r1, 3), "pairwise", round(r1prime, 3))),
+                        gridExtra::arrangeGrob(p2, top = paste("MMPD", round(r2, 3), "pairwise", round(r2prime, 3))),
+                        gridExtra::arrangeGrob(p3, top = paste("MMPD", round(r3, 3), "pairwise", round(r3prime, 3))),
+                        gridExtra::arrangeGrob(p4, top = paste("MMPD", round(r4, 3), "pairwise", round(r4prime, 3))),
                         ncol = 2, nrow=2)

### 2020-12-01 paper/main.Rmd
adding description of files and objectives

@@
   \usepackage{caption}
-  \usepackage{algorithm, algorithmicx, algpseudocode}
+  \usepackage{algorithm}
+  \usepackage{algorithmicx}
+  \usepackage{algpseudocode}
   \DeclareCaptionStyle{italic}{labelfont={bf},textfont={it},labelsep=colon}
@@
 
-<!-- \begin{algorithm}[!thb] -->
-<!-- 	\caption{Calculation for a raw distance measure between two cyclic granularities $A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.}\label{alg:scoreopt}.
--->
-<!-- 	\begin{algorithmic}[1] -->
-<!-- 		\Procedure{RawMMPD}{$A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$, $v = \{ v_t: t = 1, 2, \dots, T\}$}. -->
-<!-- 		\For{$k=1:K$, $j=1:J$} -->
-<!-- 		\State Find distances between pairs of all possible combinations of categories $(a_jb_k,a_j'b_k')$ by computing JSD between quantiles of the measured variable $q(v)$ across these combinations.
--->
-<!-- 		\State $d \gets JSD(\tilde{q(v)_{a_{j}b_{k}}},\tilde{q(v)_{a_{j}'b_{k}'}})$ -->
-<!-- 		\If {$b_k = b_k'$}  -->
-<!-- 		\State $d* \gets \lambda d$  \Comment{upweight within-facet distances} -->
-<!-- 		\Else  -->
-<!-- 		\State $d* \gets 1/\lambda d $ \Comment{downweight across-facet distances} -->
-<!-- 		\EndFor -->
-<!-- 		\State Set the raw distance measure as $max(d*)$ where max is taken over all $j, j', k, k'$. -->
-
-<!-- 		\EndProcedure -->
-<!-- 	\end{algorithmic} -->
-<!-- \end{algorithm} -->
+\begin{algorithm}[!thb]
+	\caption{Calculation for a raw distance measure between two cyclic granularities $A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.}\label{alg:scoreopt}.
+	\begin{algorithmic}[1]
+		\Procedure{RawMMPD}{$A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$, $v = \{ v_t: t = 1, 2, \dots, T\}$}.
+		\For{$k=1:K$, $j=1:J$}
+		\State Find distances between pairs of all possible combinations of categories $(a_jb_k,a_j'b_k')$ by computing JSD between quantiles of the measured variable $q(v)$ across these combinations.
+		\State $d \gets JSD(\tilde{q(v)_{a_{j}b_{k}}},\tilde{q(v)_{a_{j}'b_{k}'}})$
+		\If {$b_k = b_k'$}
+		\State $d* \gets \lambda d$  \Comment{upweight within-facet distances}
+		\Else
+		\State $d* \gets 1/\lambda d $ \Comment{downweight across-facet distances}
+		\EndFor
+		\State Set the raw distance measure as $max(d*)$ where max is taken over all $j, j', k, k'$.
+
+		\EndProcedure
+	\end{algorithmic}
+\end{algorithm}
 

### 2020-12-01 paper/main.tex
adding description of files and objectives

--- 2020-11-19 main.tex
@@
 \usepackage{makecell}
+\usepackage{xcolor}
 
@@
 
-\hypertarget{notations}{%
-\subsubsection{Notations}\label{notations}}
-
-Consider two cyclic granularities \(C_i\) and \(C_j\), such that \(C_i\) maps index set to a set \(\{A_k \mid k=1,\dots,K\}\) and \(C_j\) maps index set to a set \(\{B_\ell \mid \ell =1,\dots,L\}\).
-Here, \(A_k\) and \(B_\ell\) are the levels/categories corresponding to \(C_i\) and \(C_j\) respectively.
-Let \(S_{k\ell}\) be a subset of the index set such that for all \(s \in S_{k\ell}\), \(C_i(s) = A_k\) and \(C_j(s) = B_\ell\).
-There are \(KL\) such data subsets, one for each combination of levels (\(A_k\), \(B_\ell\)).
-Moreover, consider that in the graphical space, \(C_i\) is mapped to facets and \(C_j\) is mapped to x-axis.
-
 \hypertarget{characterising-distribution}{%
@@
 
-Each of the \(KL\) data subsets in the data structure have multiple observations and may vary widely across different subsets due to the structure of the calendar, missing observations or uneven locations of events in the time domain.
+Each of the data subsets in the data structure have multiple observations and may vary widely across different subsets due to the structure of the calendar, missing observations or uneven locations of events in the time domain.
 The set of observations corresponding to each combination is assumed to be a sample from an unknown probability density function.
@@
 
+Consider two cyclic granularities \(C_i\) and \(C_j\), such that \(C_i\) maps index set to a set \(\{A_k \mid k=1,\dots,K\}\) and \(C_j\) maps index set to a set \(\{B_\ell \mid \ell =1,\dots,L\}\).
+Here, \(A_k\) and \(B_\ell\) are the levels/categories corresponding to \(C_i\) and \(C_j\) respectively.
+Let \(S_{k\ell}\) be a subset of the index set such that for all \(s \in S_{k\ell}\), \(C_i(s) = A_k\) and \(C_j(s) = B_\ell\).
+There are \(KL\) such data subsets, one for each combination of levels (\(A_k\), \(B_\ell\)).
+Moreover, consider that in the graphical space, \(C_i\) is mapped to facets and \(C_j\) is mapped to x-axis.
+
 The algorithm employed for computing the distance measure is summarized as follows:
@@
   Identify maximum within the \(m\) computed distances.
+\end{enumerate}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{4}
 \item
-  Compute maximum distance (\(M\)) using appropriate norming constants.
-\item
-  Use Steps 1-5 to compute maximum distance for \(\forall k \in \{1, 2, \ldots, K\}\).
+  Use Steps 1-4 to compute maximum distance for \(\forall k \in \{1, 2, \ldots, K\}\).
 \item
@@
 
+\begin{algorithm}[!thb]
+    \caption{Calculation for a raw distance measure between two cyclic granularities $A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.}\label{alg:scoreopt}.
+    \begin{algorithmic}[1]
+        \Procedure{RawMMPD}{$A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$, $v = \{ v_t: t = 1, 2, \dots, T\}$}.
+        \For{$k=1:K$, $j=1:J$}
+        \State Find distances between pairs of all possible combinations of categories $(a_jb_k,a_j'b_k')$ by computing JSD between quantiles of the measured variable $q(v)$ across these combinations.
+        \State $d \gets JSD(\tilde{q(v)_{a_{j}b_{k}}},\tilde{q(v)_{a_{j}'b_{k}'}})$
+        \If {$b_k = b_k'$}
+        \State $d* \gets \lambda d$  \Comment{upweight within-facet distances}
+        \Else
+        \State $d* \gets 1/\lambda d $ \Comment{downweight across-facet distances}
+        \EndFor
+        \State Set the raw distance measure as $max(d*)$ where max is taken over all $j, j', k, k'$.
+
+        \EndProcedure
+    \end{algorithmic}
+\end{algorithm}
+
 A stronger measure ``max'' is chosen for aggregating x-axis categories compared to ``median'' for aggregating facet categories as the measure is intended to put more importance in pointing towards distributional differences between x-axis categories than for facet categories.
 
-\hypertarget{distribution}{%
-\subsubsection{Distribution}\label{distribution}}
+\hypertarget{behavior-of-raw-distance-measure}{%
+\section{Behavior of raw distance measure}\label{behavior-of-raw-distance-measure}}
+
+\hypertarget{simulation-study}{%
+\subsection{Simulation study}\label{simulation-study}}
+
+To understand the behavior of raw MMPD for different parameters \(nperm\) , \(n\) (\(n_x\), \(n_f\) and combination), \(D\) , \(l_x\), \(l_f\) .
+
+\hypertarget{distribution-across-facet-and-x-categories}{%
+\subsection{Distribution across facet and x categories}\label{distribution-across-facet-and-x-categories}}
 
@@
 
+\begin{center}\includegraphics[width=\textwidth]{/Users/sgup0008/Documents/paper-hakear/simulations/result_report/hist_nxbyfacet} \end{center}
+
+\begin{verbatim}
+#> [1] "/Users/sgup0008/Documents/paper-hakear"
+\end{verbatim}
+
 \begin{figure}
 
-{\centering \includegraphics[width=\textwidth]{figure/dist-across-facets-1}
+{\centering \includegraphics[width=\textwidth]{/Users/sgup0008/Documents/paper-hakear/simulations/result_report/nx_by_facet_raw}
 
@@
 \caption{Distribution of $MMPD_{raw}$ for different facet levels are shown.
-The location of the distribution shifts rightwards implying that as the number of facets increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained.
-}\label{fig:dist-across-facets}
+The location of the distribution shifts rightwards implying that as the number of facets increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained.}\label{fig:dist-across-facets}
 \end{figure}
@@
 
-{\centering \includegraphics[width=\textwidth]{figure/dist-across-x-1}
+{\centering \includegraphics[width=\textwidth]{/Users/sgup0008/Documents/paper-hakear/simulations/result_report//nfacet_by_nx_raw}
 
@@
 \end{figure}
+
+\hypertarget{distribution-across-different-sample-size}{%
+\subsection{Distribution across different sample size}\label{distribution-across-different-sample-size}}
+
+\hypertarget{distribution-across-different-permutation-size}{%
+\subsection{Distribution across different permutation size}\label{distribution-across-different-permutation-size}}
+
+\hypertarget{distribution-across-normal-and-non-normal-underlying-distribution}{%
+\subsection{Distribution across normal and non-normal underlying distribution}\label{distribution-across-normal-and-non-normal-underlying-distribution}}
 
@@
 
-\hypertarget{simulation-study}{%
-\subsection{Simulation study}\label{simulation-study}}
+\hypertarget{simulation-study-1}{%
+\subsection{Simulation study}\label{simulation-study-1}}
 
@@
 
-\begin{center}\includegraphics[width=\textwidth]{Figs/simulation} \end{center}
+\begin{center}\includegraphics[width=\textwidth]{/Users/sgup0008/Documents/paper-hakear/paper/Figs/simulation} \end{center}
 
-Observations from the null distribution are chosen as:\\
-\texttt{sim\_norm\_null\ =\ \ \ distributional::dist\_normal(5,\ 10)}~\\
-\texttt{sim\_gamma\_null\ \ =\ \ \ distributional::dist\_gamma(0.5,\ 0.2)}~\\
+Observations from Normal(5, 10) and Gamma(0.5, 0.2) are3 chosen in all the designs.
+
+--\textgreater{}
+--\textgreater{}
 
@@
 
-\begin{center}\includegraphics[width=\textwidth]{figure/norm-data, "Distribution of $MMPD_{norm}$ across different levels of facet and x-axis.
-These distributions should look the same if normalisation worked."-1} \end{center}
-
 \begin{figure}
 
-{\centering \includegraphics[width=\textwidth]{figure/null-dist-1}
+{\centering \includegraphics[width=\textwidth]{figure/norm-data-1}
 
@@
 
-\caption{Distribution of mmpd across different facet levels (columns) and x-axis levels (rows) for null ditribution normal(5,10) and gamma(0.5, 0.2).
-The distribution of MMPD is unaffected by the null distribution considered.
-It is also the same across all facet levels but not across the x-axis, which means normalisation is failing across x-axis.}\label{fig:null-dist}
+\caption{Distribution of $MMPD_{norm}$ across different levels of facet and x-axis. These distributions should look the same if normalisation worked.}\label{fig:norm-data}
 \end{figure}
@@
 \subsubsection{Performance of normalised MMPD}\label{performance-of-normalised-mmpd}}
+
+\begin{center}\includegraphics[width=\textwidth]{figure/unnamed-chunk-4-1} \end{center}
 
@@
 \begin{center}\includegraphics[width=\textwidth]{figure/sim_all-1} \includegraphics[width=\textwidth]{figure/sim_all-2} \includegraphics[width=\textwidth]{figure/sim_all-3} \includegraphics[width=\textwidth]{figure/sim_all-4} \end{center}
-
-\hypertarget{algorithm-2}{%
-\section{Algorithm}\label{algorithm-2}}
-
-\noindent The algorithm employed for computing MMPD is summarized as follows:
-
-\begin{itemize}
-\tightlist
-\item
-  \textbf{Input:} Data corresponding to all harmony pairs, i.e., data sets of the form \((C_i, C_j, v)\)
-  \(\forall i, j \in N_C\)\\
-\item
-  \textbf{Output:} MMPD (Median Maximum Pairwise Distances) measuring the average variation across different levels of \(C_i\) and \(C_j\) \(\forall i, j \in N_C\)
-\end{itemize}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  Fix harmony pair \((C_i, C_j)\).
-\item
-  Fix \(k\). Then there are \(L\) groups corresponding to level \(A_k\) of \(C_i\).
-\item
-  Compute \(m = \binom{L}{2}\) pairwise distances between distributions of \(L\) unordered levels and \(m = L-1\) pairwise distances for \(L\) ordered categories.
-\item
-  Identify maximum within the \(m\) computed distances.
-\item
-  Compute normalized maximum distance (\(NM\)) using appropriate norming constants.
-\item
-  Use Steps 1-5 to compute normalized maximum distance for \(\forall k \in \{1, 2, \ldots, K\}\).
-\item
-  Compute MMPD = median \((NM_1, NM_2, \dots, NM_K)\)/log(\(K\)).
-\item
-  Repeat Steps 1 to 7 for all harmony pairs.
-\end{enumerate}
 

### 2020-12-01 simulations/objectives.Rmd
adding description of files and objectives

---
title: "Simulation objectives"
author: "Sayani Gupta"
date: "01/12/2020"
output: pdf_document
---

This file contains objectives of the simulations and description of parameters and files or folders in simulations/Results/ with corresponding objective in parenthesis.

## Objectives:

(A) to understand how the measure (raw or normalised) changes across different levels of facets and x-axis for fixed $nsim$, $nperm$ and $\lambda$ in null case. Original values are not scaled., sim_table has just nx and nfacet. Description of parameters: 
 - $nfacet = nx = c(2, 3, 5, 7, 14, 20, 31, 50)$
 - $nsim = 200$
 - $nperm = 100$
 - $lambda = 0.67$
 - $sim_dist = normal(5, 10)$
 - $weights (dist_{within-facet}, dist_{across-facet}) = (\lambda, 1/\lambda)$

(B) 
(C)
(D)

## Description of files

Folder raw/

- Files ending with _dist.rds : ran from null/job-raw.sh (A)
- Files ending with _pairwise_max_dist.rds: ran from null/job-pairwise_max.sh (A)
- Folder data:  ran from null/job-pairwise_data.sh (A)

Folder norm/

- Files ending with _dist.rds: run from null/job-norm.sh (A)

### 2020-12-01 simulations/result_report/makegraph-02.R

@@ -5,6 +5,10 @@ all_data <- read_rds("simulations/result_report/all_data_raw_pairwise_max.rds")
 # 
 # add_pairwise_max while writing if plots are for max pairwise distances
 
+# normalised mmpd
+# all_data <- read_rds("simulations/result_report/all_data_norm_mmpd.rds")
+
+
 hist_nxbyfacet <- all_data %>% 
   ggplot(aes(x = value)) +
   geom_histogram() +

### 2020-12-07 paper/main.Rmd
added picture and caption

--- 2020-11-26 paper/main.Rmd
@@
 
-Consider two cyclic granularities $C_i$ and $C_j$, such that $C_i$ maps index set to a set $\{A_k \mid k=1,\dots,K\}$ and $C_j$ maps index set to a set $\{B_\ell \mid \ell =1,\dots,L\}$.
+Consider two cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.
+Let the pairwise distances between combinations be denoted as $d_{(j,k), (j', k')} = JSD(a_{j}b_{k}, a_{j'}b_{k'})$.
+If $b_{k} = b_{k'}$, distances considered are within-facet.
+Otherwise they are between-facet.
+
+```{r distance-explain, fig.cap = "Mapping to data space to graphic space shown.
+Cyclic granularity A is mapped to x-axis and B is mapped to facets and the dotted lines represent the distances between different categories.
+Panel 1) and 2) show the between-facet distances.
+Panel 3) and 4) are used to illustrate within-facet distances when categories are un-ordered or ordered respectively.
+When categories are ordered, distances should only be considered for consecutive x-axis categories.
+Between-facet distances are distances between different facet levels for the same x-axis category, for example, distances between {($a_1$,$b_1$) and ($a_1$, $b_2$)} or {($a_1$,$b_1$) and ($a_1$, $b_3$)}."}
+knitr::include_graphics(here::here("paper/Figs/dist_explain.png"))
+```
+
+The maximum weighted pairwise distances are defined as:
+$$MEPD = max_{j, j', k, k'}(d*_{(j,k), (j', k')})
+\forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}$$
+where,
+
+\begin{equation}
+d*_{(j,k), (j', k')} =
+\begin{cases}
+\lambda * d_{(j,k), (j', k')},& \text{if } b_{k} = b_{k'}\\
+(1-\lambda) * d_{(j,k), (j', k')},              & \text{otherwise}
+\end{cases}
+\end{equation}
+
+<!-- _j$ maps index set to a set $\{B_\ell \mid \ell =1,\dots,L\}$.
 Here, $A_k$ and $B_\ell$ are the levels/categories corresponding to $C_i$ and $C_j$ respectively.
@@
 Moreover, consider that in the graphical space, $C_i$ is mapped to facets and $C_j$ is mapped to x-axis.
-
-The algorithm employed for computing the distance measure is summarized as follows:
-
-1. Fix harmony pair $(C_i, C_j)$.
-
-2. Fix $k$. Then there are $L$ groups corresponding to level $A_k$ of $C_i$.
-
-3. Compute  $m = \binom{L}{2}$ pairwise distances between distributions of $L$ unordered levels and $m = L-1$ pairwise distances for $L$ ordered categories.
-
-4. Identify maximum within the $m$ computed distances.
-
-<!-- 5. Compute distribution of maximum distance ($M$) by shuffling the data $200$ times and finishing Steps1-4 in each case. Scale $M$ using the mean and sd of the distribution.  -->
-
-5. Use Steps 1-4 to compute maximum distance for $\forall k \in  \{1, 2, \ldots, K\}$.
-
-6. Compute the distance measure MMPD_raw = median $(M_1, M_2, \dots, M_K)$.
+-->
+
+ <!-- old -->
+<!-- Consider two cyclic granularities $C_i$ and $C_j$, such that $C_i$ maps index set to a set $\{A_k \mid k=1,\dots,K\}$ and $C_j$ maps index set to a set $\{B_\ell \mid \ell =1,\dots,L\}$.
+Here, $A_k$ and $B_\ell$ are the levels/categories corresponding to $C_i$ and $C_j$ respectively.
+Let $S_{k\ell}$ be a subset of the index set such that for all $s \in S_{k\ell}$, $C_i(s) = A_k$ and $C_j(s) = B_\ell$.
+There are $KL$ such data subsets, one for each combination of levels ($A_k$, $B_\ell$).
+Moreover, consider that in the graphical space, $C_i$ is mapped to facets and $C_j$ is mapped to x-axis.
+-->
+
+<!-- The algorithm employed for computing the distance measure is summarized as follows: -->
+
+<!-- 1. Fix harmony pair $(C_i, C_j)$. -->
+
+<!-- 2. Fix $k$. Then there are $L$ groups corresponding to level $A_k$ of $C_i$. -->
+
+<!-- 3. Compute  $m = \binom{L}{2}$ pairwise distances between distributions of $L$ unordered levels and $m = L-1$ pairwise distances for $L$ ordered categories. -->
+
+<!-- 4. Identify maximum within the $m$ computed distances. -->
+
+<!-- <!-- 5. Compute distribution of maximum distance ($M$) by shuffling the data $200$ times and finishing Steps1-4 in each case. Scale $M$ using the mean and sd of the distribution.  --> -->
+
+<!-- 5. Use Steps 1-4 to compute maximum distance for $\forall k \in  \{1, 2, \ldots, K\}$. -->
+
+<!-- 6. Compute the distance measure MMPD_raw = median $(M_1, M_2, \dots, M_K)$. -->
 
@@
 
-A stronger measure "max" is chosen for aggregating x-axis categories compared to "median" for aggregating facet categories as the measure is intended to put more importance in pointing towards distributional differences between x-axis categories than for facet categories.
+<!-- A stronger measure "max" is chosen for aggregating x-axis categories compared to "median" for aggregating facet categories as the measure is intended to put more importance in pointing towards distributional differences between x-axis categories than for facet categories.
+-->
 

### 2020-12-07 simulations/objectives.Rmd
renv update

@@
 
-(A) to understand how the measure (raw or normalised) changes across different levels of facets and x-axis for fixed $nsim$, $nperm$ and $\lambda$ in null case.
-Original values are not scaled., sim_table has just nx and nfacet.
+ (1A) to understand how the measure (raw or normalised) changes across different levels of facets and x-axis for fixed $nsim$, $nperm$ and $\lambda$ in null case.
+Original values are **not scaled**, sim_table has just nx and nfacet.
 Description of parameters:
@@
 
-(B) 
-(C)
-(D)
+(1B)  Original values are **scaled** and other parameters look exactly like (A)
+
+(2)  Original values are **scaled** and $weights (dist_{within-facet}, dist_{across-facet}) = (\lambda, 1 - \lambda)$, other parameters like (A), for $lambda = seq(0.1, 0.9, 0.05)$
 

### 2020-12-07 lambda_grid.R

@@ -18,7 +18,7 @@ library(rlang)
 
 # objective 2
 all_files = list.files(path = "simulations/results/demo_all_design/", 
-                        pattern = "_dist.rds")
+                       pattern = "_dist.rds")
 
 
 names_levels <- map_dfr(all_files, 
@@ -30,15 +30,22 @@ names_levels <- map_dfr(all_files,
                         })
 
 # nsim = 200 types repeated
-names_rep <- names_levels %>% slice(rep(1:n(), each = 200))
+names_rep <- names_levels %>% slice(rep(1:n(), each = 17*4))
 
 
-all_data <- paste0("simulations/results/raw/", 
+all_data <- paste0("simulations/results/demo_all_design/", 
                    all_files)%>%
   map(readRDS) %>% 
   bind_rows() %>%
   bind_cols(names_rep) %>%
   arrange(nfacet, nx)
+
+
+all_data %>% 
+  mutate(design = factor(design, levels = c("D1", "D2", "D3", "D4"))) %>% 
+  ggplot(aes(x=lambda, y = raw_mpd, colour = design)) +
+  geom_line() + scale_x_continuous(breaks = seq(0.1, 0.9, 0.1)) +
+  facet_grid(nx~nfacet, )
 
 
 # run for raw MMPD files aggregation

### 2020-12-07 simulations/demo_all_design/job-raw_objective2.sh

@@ -1,0 +1,12 @@
+#! /bin/bash
+#SBATCH --job-name=null_normal_raw
+#SBATCH --output=trace_%a.out
+#SBATCH --error=error_%a.err
+#SBATCH --mem-per-cpu=4096
+#SBATCH --time=168:00:00
+#SBATCH --array=1-64
+#SBATCH --ntasks=1
+#SBATCH --cpus-per-task=1
+#SBATCH --export=NONE
+module load R/4.0.0-openblas
+Rscript raw_objective2.R $SLURM_ARRAY_TASK_ID 

### 2020-12-07 simulations/result_report/null/simtable.R

@@ -1,0 +1,19 @@
+### This code creates a table of data for different simulations scenarios ###
+library(tidyverse)
+# nperm and nsim can run parallelly
+sim_table <- expand.grid(#data = c(99, 9999), # different data with same specifications
+  #nperm = c(20, 100), # different permutations to compute mean and sd
+  #nobs_each_comb  = c(10, 40, 500), # different number of observations for each combinations for each panel
+  #nobs_diff_comb  = c("comb1", "comb2"), # different number of observations for different combinations for each panel
+  #nsim = c(100, 500), # number of simulations of the entire exercise to compute distribution and CI of MMPD 
+  #dist = c("norm", "non-norm"), # distributions from where data is generated
+  # nfacet = c(2, 3, 5, 7, 14, 20, 31, 50), # range of facet levels 
+   nfacet = c(2, 3),
+   nx = c(2, 3)
+   #nx = c(2, 3, 5, 7, 14, 20, 31, 50) # range of x levels
+) %>% tibble()
+
+
+#Export as .csv
+
+write_csv(sim_table,'sim_table.csv')

### 2020-12-07 simulations/vary_x/omega_lambda.R

@@ -1,0 +1,164 @@
+
+
+# starting with standard normal
+# mu = 0, sd = 1, nx = 4, nfacet = 7
+
+library(hakear)
+library(tidyverse)
+library(parallel)
+library(distributional)
+
+mean = 0
+range_mean = c(0, 1, 3,  5, 7, 15, 20)
+sd = 1
+range_sd = c(0, 1, 3,  5, 7, 15, 20)
+range_w =  c(1, 2, 3, 4, 5)
+range_lambda = seq(0.1, 0.9, 0.05)
+
+# functions to generate distribution vector across combinations so that they are same across facet and different across x
+
+sim_varx_normal = function(nx, nfacet, mean, sd, w)
+{
+  rep(dist_normal((mean + seq(0, nx-1, by  = 1)*w), sd), nfacet)
+}
+
+# functions to generate distribution vector across combinations so that they are same across x and different across facet
+
+sim_varf_normal = function(nx, nfacet, mean, sd, w)
+{
+  rep(dist_normal((mean + seq(0, nfacet-1, by  = 1)*w), sd), each = nx)
+}
+
+### changing mean with constant sd
+
+set.seed(9999)
+data_varx <- mclapply(range_lambda, function(x){
+  data_w <- mclapply(range_w, function(w){
+    data_y <- mclapply(range_mean, function(y){   
+      # generate the data
+      data <- sim_panel(nx = 3,
+                        nfacet = 2,
+                        ntimes = 500,
+                        sim_dist = sim_varx_normal(nx = 3, nfacet = 2, mean = y, sd = 2, w = w)) %>%
+        unnest(c(data))
+      
+      # compute wpd
+      wpd <- compute_pairwise_max(data, 
+                                  gran_x = "id_x",
+                                  gran_facet = "id_facet",
+                                  response = sim_data, lambda = x)
+      tibble(mean = y, wpd)
+    }) %>% bind_rows() 
+    bind_cols(omega = w, data_y)
+  })  %>% bind_rows() 
+  
+  bind_cols(lambda = x, data_w)
+}) %>% bind_rows() 
+# 
+# data_all_varx <- data_varx %>% rename("wpd" = "value",
+#                                       "omega" = "name")
+
+
+set.seed(9999)
+data_varf <- mclapply(range_lambda, function(x){
+  data_w <- mclapply(range_w, function(w){
+    data_y <- mclapply(range_mean, function(y){   
+      # generate the data
+      data <- sim_panel(nx = 3,
+                        nfacet = 2,
[…]

### 2020-12-07 paper/main.Rmd
definitions added

@@
 
-## Idea
+## Idea {#sec:idea}
 
@@
 
-### Algorithm
+### Methodology
 
 Consider two cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.
-Let the pairwise distances between combinations be denoted as $d_{(j,k), (j', k')} = JSD(a_{j}b_{k}, a_{j'}b_{k'})$.
-If $b_{k} = b_{k'}$, distances considered are within-facet.
-Otherwise they are between-facet.
-
-```{r distance-explain, fig.cap = "Mapping to data space to graphic space shown.
-Cyclic granularity A is mapped to x-axis and B is mapped to facets and the dotted lines represent the distances between different categories.
+Let the pairwise distances between pairs $(a_{j} b_{k}, a_{j'}, b_{k})$ be denoted as $d_{(jk, j', k')} = JSD(a_{j}b_{k}, a_{j'}b_{k'})$.
+Pairwise distances could be within-facets or between-facets.
+Figure \ref{fig:distance-explain} illustrates how the within-facet or between-facet distances are defined.
+Pairwise distances are within-facets ($d_{w}$) when $b_{k} = b_{k'}$, that is, between pairs of the form $(a_{j}b_{k}, a_{j'}b_{k})$ as shown in panel (3) of Figure \ref{fig:distance-explain}.
+If categories are ordered (like all temporal cyclic granularities), then only distances between pairs where $a_{j'} = (a_{j+1})$ are considered (panel (4)).
+Pairwise distances are between-facets ($d_{b}$) when they are considered between pairs of the form $(a_{j}b_{k}, a_{j}b_{k'})$.
+
+```{r distance-explain, fig.pos="p", fig.cap = "Within and between-facet distances shown for two cyclic granularities A and B, where A is mapped to x-axis and B is mapped to facets.
+The dotted lines represent the distances between different categories.
 Panel 1) and 2) show the between-facet distances.
@@
 
-The maximum weighted pairwise distances are defined as:
-$$MEPD = max_{j, j', k, k'}(d*_{(j,k), (j', k')})
-\forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}$$
-where,
+From Section \ref{sec:idea}, the idea is to put more weightage on within-facet distances than between-facet distances.
+Hence, for a suitable tuning parameter $\lambda > 1$, the pairwise distances $d_{(jk, j'k')}$ are transformed based on the distance type as follows:
 
 \begin{equation}
-d*_{(j,k), (j', k')} =
+d*_{(j,k), (j'k')} =
 \begin{cases}
-\lambda * d_{(j,k), (j', k')},& \text{if } b_{k} = b_{k'}\\
-(1-\lambda) * d_{(j,k), (j', k')},              & \text{otherwise}
+\lambda d_{(j,k), (j'k')},& \text{if } d = d_w\\
+(1-\lambda)  d_{(j,k), (j', k')},              & \text{if } d = d_b\\
 \end{cases}
 \end{equation}
+
+<!-- The maximum weighted pairwise distances are defined as: -->
+<!-- $$MEPD = max_{j, j', k, k'}(d*_{(j,k), (j', k')}) -->
+<!-- \forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}$$ -->
+<!-- where,  -->
 

### 2020-12-10 paper/main.Rmd
tuning paramter section update

@@
 preamble: >
-  \usepackage{mathtools,amssymb,booktabs,amsthm,todonotes,colortbl}
+  \usepackage{mathtools,booktabs,amsthm,todonotes,colortbl}
   \def\mod{~\text{mod}~}
@@
 options("knitr.graphics.auto_pdf" = TRUE,
-        tinytex.verbose = TRUE)
+        tinytex.verbose = FALSE)
 library(knitr)
@@
 
-# Median Maximum Pairwise Distances (MMPD)
+# Distance measure
 
@@
 
-## Computation
+## Methodology
 
@@
 
-### Methodology
+### Definitions
 
@@
 
-```{r distance-explain, fig.pos="p", fig.cap = "Within and between-facet distances shown for two cyclic granularities A and B, where A is mapped to x-axis and B is mapped to facets.
+```{r distance-explain, fig.cap = "Within and between-facet distances shown for two cyclic granularities A and B, where A is mapped to x-axis and B is mapped to facets.
 The dotted lines represent the distances between different categories.
@@
 
-From Section \ref{sec:idea}, the idea is to put more weightage on within-facet distances than between-facet distances.
+From Section \ref{sec:idea}, the idea is to put more weights on within-facet distances than between-facet distances.
 Hence, for a suitable tuning parameter $\lambda > 1$, the pairwise distances $d_{(jk, j'k')}$ are transformed based on the distance type as follows:
@@
 
-<!-- The maximum weighted pairwise distances are defined as: -->
-<!-- $$MEPD = max_{j, j', k, k'}(d*_{(j,k), (j', k')}) -->
-<!-- \forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}$$ -->
-<!-- where,  -->
+The maximum weighted pairwise distances are defined as:
+$$WPD = max_{j, j', k, k'}(d*_{(j,k), (j', k')})
+\forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}$$.
 
@@
 To understand the behavior of raw MMPD for different parameters $nperm$ <number of permutations>, $n$ <sample size> ($n_x$, $n_f$ and combination), $D$ <different data set>, $l_x$<levels of x-axis>, $l_f$ <levels of facets>.
+
+D1 - Design null: 
+D2 - Design vary_f:
+D3 - Design var_x:
+B4 - Design vary_all:
+
+## Choice of parameters of the distribution
+
+Under null distribution
+
+Null design only where all combinations are equal for fixed values of $\mu$ and $\sigma$
+Dist 1: $N(0,1)$ individual graph
+Dist 2: $N(\mu, 1)$ (faceted with different values of $\mu$: not yet just for one value now)
+Dist 3: $N(0, \sigma)$ (faceted with different values of $\sigma$: not yet just for one value now)
+Dist 4: $N(\mu, \sigma)$ faceted with different values of mu and sigma, for all levels of x and facet to see how value of wpd changes with that of change in parameters.
+
+### Choice of alternate designs
+
+A normal distribution is taken for this purpose. We would calibrate the values of $WPD$ for different designs illustrated in Section \ref{sec:idea}.
+
+$$\mu_{j.} = \mu + j\omega$$
+or, $$\mu_{.k} = \mu + k\omega$$ where,   
+$j$ and $k$ are the index of the x and facet category respectively 
+$\mu$ is the mean of the first category and $\omega$ is the increment from the starting value.
+
+mean = 0
+range_mean = c(0, 1, 3,  5, 7, 15, 20)
+sd = 1
+range_sd = c(1, 3,  5, 7, 15, 20)
+range_w =  c(1, 2, 3, 4, 5)
+range_lambda = seq(0.1, 0.9, 0.05)
+
+## Parameters of the distribution
+
+## Choice of tuning parameters
+
+Objective: Choice of optimal tuning parameter $lambda$ with the help of two alternate designs (vary_x and vary_f)  for different nx and nfacets.
+The lambda for which the two designs intersect have to be chosen to put appropriate weights for within-facet and between-facet distances.
+
+Assumptions: The initial combination has a $N(\mu,\sigma)$ distribution and then every combination increases as follows:
+- $$\mu_{j.} = \mu + j\omega$$ (for design vary_x)
+- $$\mu_{.k} = \mu + k\omega$$ (for design vary_f)
+Value of the parameters chosen for this simulation are $\mu = 0$, $\sigma = 1$ and $\omega = {1, 2, \dots, 10}$
+
+Fixing omega, where the design interacts
+
+```{r tuning-one-omega}
+knitr::include_graphics(here::here("simulations/tuning_param/figs/intersection_plot.png"))
+```
+
+How value of lambda changes with increasing omega
+
+```{r tuning-parameter-intersection}
+knitr::include_graphics(here::here("simulations/tuning_param/figs/intersection_plot.png"))
+```
+
+How value of lambda changes with increasing omega and mean for fixed nx, nfacet and standard deviation?
+
+```{r lambda-omega-mean}
+knitr::include_graphics(here::here("simulations/result_report/lambda_omega_mean_3_2.png"))
+```
+
+How value of lambda changes with increasing omega and sd for fixed nx, nfacet and mean?
+
+```{r lambda-omega-sd}
+knitr::include_graphics(here::here("simulations/result_report/lambda_omega_sd_3_2.png"))
+```
 

### 2020-12-10 paper/main.tex
tuning paramter section update

@@
 
-\hypertarget{median-maximum-pairwise-distances-mmpd}{%
-\section{Median Maximum Pairwise Distances (MMPD)}\label{median-maximum-pairwise-distances-mmpd}}
+\hypertarget{distance-measure}{%
+\section{Distance measure}\label{distance-measure}}
 
@@
 
-\hypertarget{idea}{%
-\subsection{Idea}\label{idea}}
+\hypertarget{sec:idea}{%
+\subsection{Idea}\label{sec:idea}}
 
@@
 
-\hypertarget{computation}{%
-\subsection{Computation}\label{computation}}
+\hypertarget{methodology}{%
+\subsection{Methodology}\label{methodology}}
 
@@
 
-\hypertarget{algorithm}{%
-\subsubsection{Algorithm}\label{algorithm}}
+\hypertarget{definitions}{%
+\subsubsection{Definitions}\label{definitions}}
 
-Consider two cyclic granularities \(C_i\) and \(C_j\), such that \(C_i\) maps index set to a set \(\{A_k \mid k=1,\dots,K\}\) and \(C_j\) maps index set to a set \(\{B_\ell \mid \ell =1,\dots,L\}\).
-Here, \(A_k\) and \(B_\ell\) are the levels/categories corresponding to \(C_i\) and \(C_j\) respectively.
-Let \(S_{k\ell}\) be a subset of the index set such that for all \(s \in S_{k\ell}\), \(C_i(s) = A_k\) and \(C_j(s) = B_\ell\).
-There are \(KL\) such data subsets, one for each combination of levels (\(A_k\), \(B_\ell\)).
-Moreover, consider that in the graphical space, \(C_i\) is mapped to facets and \(C_j\) is mapped to x-axis.
+Consider two cyclic granularities \(A\) and \(B\), such that \(A = \{ a_j: j = 1, 2, \dots, J\}\) and \(B = \{ b_k: k = 1, 2, \dots, K\}\) with \(A\) placed across x-axis and \(B\) across facets.
+Let the pairwise distances between pairs \((a_{j} b_{k}, a_{j'}, b_{k})\) be denoted as \(d_{(jk, j', k')} = JSD(a_{j}b_{k}, a_{j'}b_{k'})\).
+Pairwise distances could be within-facets or between-facets.
+Figure \ref{fig:distance-explain} illustrates how the within-facet or between-facet distances are defined.
+Pairwise distances are within-facets (\(d_{w}\)) when \(b_{k} = b_{k'}\), that is, between pairs of the form \((a_{j}b_{k}, a_{j'}b_{k})\) as shown in panel (3) of Figure \ref{fig:distance-explain}.
+If categories are ordered (like all temporal cyclic granularities), then only distances between pairs where \(a_{j'} = (a_{j+1})\) are considered (panel (4)).
+Pairwise distances are between-facets (\(d_{b}\)) when they are considered between pairs of the form \((a_{j}b_{k}, a_{j}b_{k'})\).
 
-The algorithm employed for computing the distance measure is summarized as follows:
+\begin{figure}
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  Fix harmony pair \((C_i, C_j)\).
-\item
-  Fix \(k\). Then there are \(L\) groups corresponding to level \(A_k\) of \(C_i\).
-\item
-  Compute \(m = \binom{L}{2}\) pairwise distances between distributions of \(L\) unordered levels and \(m = L-1\) pairwise distances for \(L\) ordered categories.
-\item
-  Identify maximum within the \(m\) computed distances.
-\end{enumerate}
+{\centering \includegraphics[width=\textwidth]{/Users/sgup0008/Documents/paper-hakear/paper/Figs/dist_explain}
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{4}
-\item
-  Use Steps 1-4 to compute maximum distance for \(\forall k \in \{1, 2, \ldots, K\}\).
-\item
-  Compute the distance measure MMPD\_raw = median \((M_1, M_2, \dots, M_K)\).
-\end{enumerate}
+}
 
-\begin{algorithm}[!thb]
-    \caption{Calculation for a raw distance measure between two cyclic granularities $A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.}\label{alg:scoreopt}.
-    \begin{algorithmic}[1]
-        \Procedure{RawMMPD}{$A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$, $v = \{ v_t: t = 1, 2, \dots, T\}$}.
-        \For{$k=1:K$, $j=1:J$}
-        \State Find distances between pairs of all possible combinations of categories $(a_jb_k,a_j'b_k')$ by computing JSD between quantiles of the measured variable $q(v)$ across these combinations.
-        \State $d \gets JSD(\tilde{q(v)_{a_{j}b_{k}}},\tilde{q(v)_{a_{j}'b_{k}'}})$
-        \If {$b_k = b_k'$}
-        \State $d* \gets \lambda d$  \Comment{upweight within-facet distances}
-        \Else
-        \State $d* \gets 1/\lambda d $ \Comment{downweight across-facet distances}
-        \EndFor
-        \State Set the raw distance measure as $max(d*)$ where max is taken over all $j, j', k, k'$.
+\caption{Within and between-facet distances shown for two cyclic granularities A and B, where A is mapped to x-axis and B is mapped to facets.
+The dotted lines represent the distances between different categories.
+Panel 1) and 2) show the between-facet distances.
+Panel 3) and 4) are used to illustrate within-facet distances when categories are un-ordered or ordered respectively.
+When categories are ordered, distances should only be considered for consecutive x-axis categories.
+Between-facet distances are distances between different facet levels for the same x-axis category, for example, distances between {($a_1$,$b_1$) and ($a_1$, $b_2$)} or {($a_1$,$b_1$) and ($a_1$, $b_3$)}.}\label{fig:distance-explain}
+\end{figure}
 
-        \EndProcedure
-    \end{algorithmic}
-\end{algorithm}
+From Section \ref{sec:idea}, the idea is to put more weights on within-facet distances than between-facet distances.
+Hence, for a suitable tuning parameter \(\lambda > 1\), the pairwise distances \(d_{(jk, j'k')}\) are transformed based on the distance type as follows:
 
-A stronger measure ``max'' is chosen for aggregating x-axis categories compared to ``median'' for aggregating facet categories as the measure is intended to put more importance in pointing towards distributional differences between x-axis categories than for facet categories.
+\begin{equation}
+d*_{(j,k), (j'k')} =
+\begin{cases}
+\lambda d_{(j,k), (j'k')},& \text{if } d = d_w\\
+(1-\lambda)  d_{(j,k), (j', k')},              & \text{if } d = d_b\\
+\end{cases}
+\end{equation}
+
+The maximum weighted pairwise distances are defined as:
+\[WPD = max_{j, j', k, k'}(d*_{(j,k), (j', k')})
+\forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}\].
+
+--\textgreater{}
 
@@
 To understand the behavior of raw MMPD for different parameters \(nperm\) , \(n\) (\(n_x\), \(n_f\) and combination), \(D\) , \(l_x\), \(l_f\) .
+
+D1 - Design null:
+D2 - Design vary\_f:
+D3 - Design var\_x:
+B4 - Design vary\_all:
+
+\hypertarget{choice-of-parameters-of-the-distribution}{%
+\subsection{Choice of parameters of the distribution}\label{choice-of-parameters-of-the-distribution}}
+
+Under null distribution
+
+Null design only where all combinations are equal for fixed values of \(\mu\) and \(\sigma\)
+Dist 1: \(N(0,1)\) individual graph
+Dist 2: \(N(\mu, 1)\) (faceted with different values of \(\mu\): not yet just for one value now)
+Dist 3: \(N(0, \sigma)\) (faceted with different values of \(\sigma\): not yet just for one value now)
+Dist 4: \(N(\mu, \sigma)\) faceted with different values of mu and sigma, for all levels of x and facet to see how value of wpd changes with that of change in parameters.
+
+\hypertarget{choice-of-alternate-designs}{%
+\subsubsection{Choice of alternate designs}\label{choice-of-alternate-designs}}
+
+A normal distribution is taken for this purpose. We would calibrate the values of \(WPD\) for different designs illustrated in Section \ref{sec:idea}.
+
+\[\mu_{j.} = \mu + j\omega\]
+or, \[\mu_{.k} = \mu + k\omega\] where,\\
+\(j\) and \(k\) are the index of the x and facet category respectively
+\(\mu\) is the mean of the first category and \(\omega\) is the increment from the starting value.
+
+mean = 0
+range\_mean = c(0, 1, 3, 5, 7, 15, 20)
+sd = 1
+range\_sd = c(1, 3, 5, 7, 15, 20)
+range\_w = c(1, 2, 3, 4, 5)
+range\_lambda = seq(0.1, 0.9, 0.05)
+
+\hypertarget{parameters-of-the-distribution}{%
+\subsection{Parameters of the distribution}\label{parameters-of-the-distribution}}
+
+\hypertarget{choice-of-tuning-parameters}{%
+\subsection{Choice of tuning parameters}\label{choice-of-tuning-parameters}}
+
+Objective: Choice of optimal tuning parameter \(lambda\) with the help of two alternate designs (vary\_x and vary\_f) for different nx and nfacets.
+The lambda for which the two designs intersect have to be chosen to put appropriate weights for within-facet and between-facet distances.
+
+Assumptions: The initial combination has a \(N(\mu,\sigma)\) distribution and then every combination increases as follows:
+- \[\mu_{j.} = \mu + j\omega\] (for design vary\_x)
+- \[\mu_{.k} = \mu + k\omega\] (for design vary\_f)
+Value of the parameters chosen for this simulation are \(\mu = 0\), \(\sigma = 1\) and \(\omega = {1, 2, \dots, 10}\)
+
+Fixing omega, where the design interacts
+
+\begin{center}\includegraphics[width=\textwidth]{/Users/sgup0008/Documents/paper-hakear/simulations/tuning_param/figs/intersection_plot} \end{center}
+
+How value of lambda changes with increasing omega
+
+\begin{center}\includegraphics[width=\textwidth]{/Users/sgup0008/Documents/paper-hakear/simulations/tuning_param/figs/intersection_plot} \end{center}
+
+How value of lambda changes with increasing omega and mean for fixed nx, nfacet and standard deviation?
+
+\begin{center}\includegraphics[width=\textwidth]{/Users/sgup0008/Documents/paper-hakear/simulations/result_report/lambda_omega_mean_3_2} \end{center}
+
+How value of lambda changes with increasing omega and sd for fixed nx, nfacet and mean?
+
+\begin{center}\includegraphics[width=\textwidth]{/Users/sgup0008/Documents/paper-hakear/simulations/result_report/lambda_omega_sd_3_2} \end{center}
 
@@
 
-\hypertarget{methodology}{%
-\subsection{Methodology}\label{methodology}}
+\hypertarget{methodology-1}{%
+\subsection{Methodology}\label{methodology-1}}
 
@@
 
-\hypertarget{algorithm-1}{%
-\subsection{Algorithm}\label{algorithm-1}}
+\hypertarget{algorithm}{%
+\subsection{Algorithm}\label{algorithm}}
 

### 2020-12-10 paper/main.Rmd
main update

@@
 
-## Choice of parameters of the distribution
-
-Under null distribution
+## Effect of parameters of the distribution under null distribution
 
@@
 Dist 4: $N(\mu, \sigma)$ faceted with different values of mu and sigma, for all levels of x and facet to see how value of wpd changes with that of change in parameters.
+
+**Objective:** 1.
+Behavior of wpd under different null designs N(0,1), N(5, 1), N(0,5) and N(5,5), Gamma(0,1), Gamma(0, 0.2) for different nx and nfacets.
+Here, we have to fix a value of lambda = 0.67.
+
+**Assumptions:** There is no difference in distribution between any facet or x-category
+nsim = 200
+lambda = 0.67
+
+**Questions:** 
+- How raw value of wpd changes with different nx and nfacet for different location and scale of a Normal and non-normal distribution
+
+```{r}
+
+```
+
+```{r}
+
+```
 
@@
 range_lambda = seq(0.1, 0.9, 0.05)
-
-## Parameters of the distribution
 

### 2020-12-10 paper/main.Rmd
pdf update

@@
 Consider two cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.
-Let the pairwise distances between pairs $(a_{j} b_{k}, a_{j'}, b_{k})$ be denoted as $d_{(jk, j', k')} = JSD(a_{j}b_{k}, a_{j'}b_{k'})$.
+Let the pairwise distances between pairs $(a_{j} b_{k}, a_{j'}, b_{k})$ be denoted as $d_{(jk, j'k')} = JSD(a_{j}b_{k}, a_{j'}b_{k'})$.
 Pairwise distances could be within-facets or between-facets.
@@
 \begin{cases}
-\lambda d_{(j,k), (j'k')},& \text{if } d = d_w\\
-(1-\lambda)  d_{(j,k), (j', k')},              & \text{if } d = d_b\\
+\lambda d_{(jk), (j'k')},& \text{if } d = d_w\\
+(1-\lambda)  d_{(jk), (j'k')},              & \text{if } d = d_b\\
 \end{cases}
@@
 The maximum weighted pairwise distances are defined as:
-$$WPD = max_{j, j', k, k'}(d*_{(j,k), (j', k')})
+$$WPD = max_{j, j', k, k'}(d*_{(jk), (j'k')})
 \forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}$$.
@@
 
-**Objective:** 1.
-Behavior of wpd under different null designs N(0,1), N(5, 1), N(0,5) and N(5,5), Gamma(0,1), Gamma(0, 0.2) for different nx and nfacets.
-Here, we have to fix a value of lambda = 0.67.
+**Objective:** 1. Behavior of wpd under different null designs N(0,1), N(5, 1), Gamma(0.5,1), Gamma(2,1) for different nx and nfacets. Here, we have to fix a value of lambda = 0.67.
 
@@
 
-```{r}
-
-```
-
-```{r}
-
-```
-
-### Choice of alternate designs
-
-A normal distribution is taken for this purpose. We would calibrate the values of $WPD$ for different designs illustrated in Section \ref{sec:idea}.
-
-$$\mu_{j.} = \mu + j\omega$$
-or, $$\mu_{.k} = \mu + k\omega$$ where,   
-$j$ and $k$ are the index of the x and facet category respectively 
-$\mu$ is the mean of the first category and $\omega$ is the increment from the starting value.
-
-mean = 0
-range_mean = c(0, 1, 3,  5, 7, 15, 20)
-sd = 1
-range_sd = c(1, 3,  5, 7, 15, 20)
-range_w =  c(1, 2, 3, 4, 5)
-range_lambda = seq(0.1, 0.9, 0.05)
+```{r normal-diff, fig.cap="Ridge plots of raw wpd is shown for N(0,1) and N(5,1) distribution.
+The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change is mean value of the normal distribution"}
+knitr::include_graphics(here::here("simulations/null_design/figs/normal_ridge_nxbynfacet_wpd_N01.png"))
+```
+
+```{r gamma-diff, fig.cap="Ridge plots of raw wpd is shown for G(0.5,1) and G(2,1) distribution.
+The densities change across different facet and x levels and also for the two distributions, which implies wpd value is affected by the change in location value when distributions are not normal."}
+knitr::include_graphics(here::here("simulations/null_design/figs/gamma_ridge_nxbynfacet.png"))
+```
+
+<!-- ### Choice of alternate designs -->
+
+<!-- A normal distribution is taken for this purpose. We would calibrate the values of $WPD$ for different designs illustrated in Section \ref{sec:idea}. -->
+
+<!-- $$\mu_{j.} = \mu + j\omega$$ -->
+<!-- or, $$\mu_{.k} = \mu + k\omega$$ where,    -->
+<!-- $j$ and $k$ are the index of the x and facet category respectively  -->
+<!-- $\mu$ is the mean of the first category and $\omega$ is the increment from the starting value. -->
+
+<!-- mean = 0 -->
+<!-- range_mean = c(0, 1, 3,  5, 7, 15, 20) -->
+<!-- sd = 1 -->
+<!-- range_sd = c(1, 3,  5, 7, 15, 20) -->
+<!-- range_w =  c(1, 2, 3, 4, 5) -->
+<!-- range_lambda = seq(0.1, 0.9, 0.05) -->
 
@@
 
-```{r tuning-one-omega}
-knitr::include_graphics(here::here("simulations/tuning_param/figs/intersection_plot.png"))
+```{r tuning-one-omega, fig.caption = "WPD from two designs are plotted for different values of lambda for different x and facet categories.
+For omega = 1, the designs intersect for 0.6<lamba<=0.75, whereas for higher omega, design intersects at lambda = 0.5"}
+knitr::include_graphics(here::here("simulations/tuning_param/figs/fixed_omega.png"))
 ```

### 2020-12-16 paper/main.Rmd
paper folder update

@@
 
-# Behavior of raw distance measure
+# Behavior of raw wpd (weighted pairwise distances)
 
@@
 
-To understand the behavior of raw MMPD for different parameters $nperm$ <number of permutations>, $n$ <sample size> ($n_x$, $n_f$ and combination), $D$ <different data set>, $l_x$<levels of x-axis>, $l_f$ <levels of facets>.
-
-D1 - Design null: 
-D2 - Design vary_f:
-D3 - Design var_x:
-B4 - Design vary_all:
-
-## Effect of parameters of the distribution under null distribution
+We conduct simulations to understand the behavior of raw WPD for different parameters
+$l_x$ (levels of x-axis), $l_f$ (levels of facets), $\lambda$ (tuning parameter), $\omega$ (increment in each panel design) $data$ (data sets), $sample-size$ (tuning parameter), $nsim$ (number of simulations), $nperm$ (number of permutations (might not need depending on if norm works) and designs
+$D_{null}$  (No difference in distribution)  
+$D_{var_f}$ (Difference in distribution only across facets)  
+$D_{var_x}$ (Difference in distribution only across x-axis)  
+$D_{var_{all}}$ (Difference in distribution in both facets and x-axis)
+
+## Location and scale of the distribution under null design
 
@@
 
+### Normal Distribution
+
 ```{r normal-diff, fig.cap="Ridge plots of raw wpd is shown for N(0,1) and N(5,1) distribution.
@@
 ```
+
+### Gamma Distribution
 
@@
 
-## Choice of tuning parameters
+## Choice of tuning parameters and effect of different increments
 
@@
 
-## Distribution across facet and x categories
+## Alternate designs
+
+```{r lamba-omega-alternate-design}
+knitr::include_graphics((here::here("simulations/result_report/wpd_alterate_designs.png")))
+```
+
+ Distribution across facet and x categories
 <!-- ### Need for normalisation -->
@@
 
-```{r hist-nx-nfacet}
+```{r hist-nx-nfacet, eval = FALSE}
 knitr::include_graphics(here::here("simulations/result_report/hist_nxbyfacet.png"))
@@
 ```{r dist-across-facets, fig.cap = "Distribution of $MMPD_{raw}$ for different facet levels are shown.
-The location of the distribution shifts rightwards implying that as the number of facets increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained."}
+The location of the distribution shifts rightwards implying that as the number of facets increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained.", eval = FALSE}
 here::here()
@@
 The scale of the distribution becomes less and less implying that as the number of x levels increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained as the spread of the distribution decreases.
-"}
+", eval = FALSE}
 knitr::include_graphics(here::here("simulations/result_report/","nfacet_by_nx_raw.png"))
@@
 
-## Distribution across different sample size
-## Distribution across different permutation size
-## Distribution across normal and non-normal underlying distribution
+## Sample size
+## Number of permutations
 
@@
 The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.
+
+```{r}
+knitr::include_graphics(here::here("simulations/null_design/figs/normalised","gamma_ridge_nxbynfacet.png"))
+```
 

### 2020-12-18 vary_distribution.Rmd
all raw results after transformation added

--- 2020-12-16 paper/main.Rmd
@@
 ---
-title: Selecting and ranking interesting pairs of cyclic temporal granularities
-authors:
-- name: Sayani Gupta
-  affiliation: Department of Econometrics and Business Statistics, Monash University
-  email: Sayani.Gupta@monash.edu
-
-bibliography: bibliography.bib
-preamble: >
-  \usepackage{mathtools,booktabs,amsthm,todonotes,colortbl}
-  \def\mod{~\text{mod}~}
-  \newtheorem{definition}{Definition}
-  \usepackage{mathptmx}
-  \usepackage{caption}
-  \usepackage{algorithm}
-  \usepackage{algorithmicx}
-  \usepackage{algpseudocode}
-  \DeclareCaptionStyle{italic}{labelfont={bf},textfont={it},labelsep=colon}
-  \captionsetup[figure]{style=italic,format=hang,singlelinecheck=true}
-  \captionsetup[table]{style=italic,format=hang,singlelinecheck=true}
-  \def\novspacing{\setlength{\aboverulesep}{0pt}\setlength{\belowrulesep}{0pt}}
-  \def\vspacing{\setlength{\aboverulesep}{0.4ex}\setlength{\belowrulesep}{0.65ex}}
-output:
-  bookdown::pdf_book:
-    #base_format: rticles::asa_article
-    fig_height: 5
-    fig_width: 8
-    fig_caption: yes
-    dev: "pdf"
+title: "vary_distribution"
+author: "Sayani Gupta"
+date: "18/12/2020"
+output: pdf_document
 ---
 
-```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
-options("knitr.graphics.auto_pdf" = TRUE,
-        tinytex.verbose = FALSE)
-library(knitr)
-library(tidyverse)
-library(lubridate)
-library(lvplot)
-library(ggridges)
-library(viridis)
-library(tsibble)
-library(gravitas)
-library(ggpubr)
-library(readr)
-library(kableExtra)
-library(distributional)
-library(ggplot2)
-library(sugrrants)
-library(here)
-
-opts_chunk$set(
-  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
-  fig.path = "figure/", fig.align = "center", fig.show = "hold",
-  cache = TRUE, cache.path = "cache/",
-  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
-)
-knitr::opts_knit$set(root.dir = here::here())
-#                                                                read_chunk('main.R')
-here::here()
-read_chunk(here::here("paper/R/", "null_distribution.R"))
-read_chunk(here::here("paper/R/", "mean_null.R"))
-source(here::here("paper/R/sim_panel.R"))
-# Set up plan
-#source("_drake.R")
-# Run all code required
-#drake::r_make()
-# load each object as required
-# loadd()
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE)
 ```
-
-```{r}
-set.seed(321)
-```
-
-# Introduction
-
-<!-- <introducing the problem> -->
-<!-- background of the problem -->
-
-Exploratory data analysis, as coined by John W.
-Tukey (Tukey 1965) involves many iterations of finding structures and patterns that allows the data to be informative.
-With temporal data available at finer scales, exploring periodicity and their relationships can become overwhelming with so many possible cyclic temporal granularities [@Gupta2020-vo] to explore.
-
-```{r calendar-elec, fig.height = 10.5, fig.cap="Calendar display."}
-elec <- read_rds(here("paper/data/elec.rds")) %>% 
-  filter(date >= ymd("20180101"), date < ymd("20180701"))
-rdbl <- c("Weekday" = "#d7191c", "Weekend" = "#2c7bb6")
-
-elec <- elec %>% 
-  mutate(
-    wday = wday(date, label = TRUE, week_start = 1),
-    weekday = if_else(wday %in% c("Sat", "Sun"), "Weekend", "Weekday")
-  )
-p_cal_elec <- elec %>% 
-  filter(id %in% c(2, 4)) %>% 
-  frame_calendar(x = time, y = kwh, date = date, nrow = 1) %>% 
-    ggplot(aes(x = .time, y = .kwh, group = date)) +
-    geom_line(aes(colour = as.factor(id)), size = 0.5) +
-    scale_colour_brewer(name = "", palette = "Dark2", direction = 1) +
-    facet_grid(id ~ ., labeller = label_both) +
-    theme(legend.position = "bottom")
-prettify(p_cal_elec, size = 2.5, label.padding = unit(0.1, "lines"))
-```
-
-\noindent Take the example of the calendar display of electricity smart meter data (\ref{fig:calendar-elec}) used in @wang2020calendar for four households in Melbourne, Australia.
-The authors show how hour-of-the-day interact with weekday and weekends and then move on to use calendar display to show daily schedules.
-The calendar display has several components in it, which helps us look at energy consumption across hour-of-the-day, day-of-the-week, week-of-the-month, and month-of-the-year at once.
-Some interaction of these cyclic granularities could also be interpreted from this display.
-This is a great start to have an overview of the energy consumption.
-However, if one wants to understand the periodicities in energy behavior and how the periodicities interact in greater details, it is not easy to comprehend the interactions of some periodicities' from this display, due to the combination of linear and cyclic representation of time.
-For example, this display might not be the best to understand how hour-of-the-day varies and month-of-year varies across week-of-the-month.
-Further, it is not clear what all interactions of cyclic granularities should be read from this display as there could be many combinations that one can look at.
-Moreover, calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions (@Gupta2020-vo) and could include other cyclic granularities like hour-of-week or day-of-fortnight, which could potentially become useful depending on the context.
-
-```{r intro_all}
-
-id2_tsibble <- elec %>% 
-   filter(id == 2) %>% 
-   as_tsibble(index = date_time)
-
-id4_tsibble <- elec %>% 
-   filter(id == 4) %>% 
-   as_tsibble(index = date_time)
-
-# hour-of-day and month-of-year (important pair) id2's behavior across different hours of the day very different across months, but for id4 behavior across different hours of the day is not likely a function of month.
-p1 <- id2_tsibble %>%
-   prob_plot("month_year",
-             "hour_day",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = TRUE,
-             quantile_prob = c(0.1, 0.25,0.5,0.75, 0.9)) +
-  ggtitle("") + theme(
-        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + 
-  scale_colour_brewer(name = "", palette = "PiYG")
-
-p2 <- id4_tsibble %>%
-   prob_plot("month_year",
-             "hour_day",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = TRUE,
-             quantile_prob = c(0.1, 0.25,0.5,0.75, 0.9)) + 
-  ggtitle("") + theme(
-        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
-
-# wknd_wday and week_month (important pair) id2's behavior across different hours of the day very different across months, but for id4 behavior across different hours of the day is not likely a function of month.
-
-p3 <- id2_tsibble %>%
-  create_gran("week_month") %>% 
-  filter(week_month != 5) %>% 
-   prob_plot("wknd_wday",
-             "week_month",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = FALSE,
-             quantile_prob = c(0.25,0.5,0.75)) +
-   ggtitle("") +
-#scale_x_discrete(breaks = seq(0, 23, 4))  + theme(
-        theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
-
-p4 <- id4_tsibble %>%
-    create_gran("week_month") %>% 
-  filter(week_month != 5) %>% 
-   prob_plot("wknd_wday",
-             "week_month",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = FALSE,
-             quantile_prob = c(0.25,0.5,0.75)) +
-  ggtitle("") +  #+ scale_x_discrete(breaks = seq(0, 23, 4)) + 
-theme(
-        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
-
-```
-
-```{r id2, fig.cap = "something"}
-ggpubr::ggarrange(p1, p2, ncol = 2)
-```
-
-```{r id4, fig.cap = "something2"}
-ggpubr::ggarrange(p3, p4, ncol = 2)
-```
-
-Moreover, there might be specific interactions that are interesting and others that are not and that too will vary with different households.
-For example, area distribution quantiles are plotted for household 2 and 4 in Figure \ref{fig:id2}a and b respectively.
-For the first household, the 75th and 90th percentile for Jan, Feb and July are very close, implying that energy usage for these months are generally on a much higher side due to the usage of air conditioners (in Jan and Feb) and heaters (in July).
-The energy consumption for household 2 is also higher relative to its own consumption for Jan, Feb and March but the 75th and 90th percentile are apart implying that contrary to the first household, the second household resorts to air conditioners and heaters much less regularly than the first one.
-Moreover, the 75th percentile distribution is not bimodal across hours of the day for the first household in those months, but the distribution looks similar for all months for the second household.
-Difference in the energy consumption seem to be varying both across month-of-year (facets) and hour-of-day (x-axis).
-And thus, both the cyclic granularities would deem important while studying the periodicities in the first household.
-However, it seems like energy consumption across hours of the day are not that different across different months for the second household.
-Differences seem to be more prominent across month-of-year (facets) than hour-of-day (x-axis).
-Again, look at \ref{fig:} c and d, where energy consumption for these two households are plotted against (weekend/weekday, week-of-month).
-Here, for both households, the pattern of energy consumption vary  across different weeks of the month irrespective of the fact it is a weekday or weekend.
-In that respect, the harmony pair (month-of-year, hour-of-day) seems to be more informative than (weekend/weekday, week-of-month) for the first household.
-It could be immensely useful to make the transition from all possible ways to only ways that could potentially be informative given a household.
-
-<!-- Take an example of a data set which are observed at fine temporal scales, like that of NYC bike usage available at https://www.citibikenyc.com/system-data.
-We use the `nyc_bikes` data set from the R package `tsibbledata` which takes a sample of 10 bikes for the year 2018.
-The `start_time` and the `stop_time` are recorded to a fineness of seconds.
-We can look at pair of cyclic granularities (hour_day, wknd_wday) or (week_month, day_week) to see how these periodicities interact.
-But there could be other pairs that are important too.
-How to understand which pairs are sufficient to explore given the data set without losing much information about the data.
--->
-
-<!-- When we need to understand the interplay of different periodicities in a high frequency temporal datasets, we have many choices to consider.
-In [@wang2019tsibble] and [@wang2020calendar], periodicities are explored across hour of the day and day of the week or months.
-But calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions.
--->
-
-<!-- what is the dimension of the problem -->
-The paper @Gupta2020-vo describes how we can compute all possible combinations of cyclic time granularities.
-If we have $n$ periodic linear granularities in the hierarchy table, then $n(n-1)/2$ circular or quasi-circular cyclic granularities could be constructed.
-Let $N_C$ be the total number of contextual circular, quasi-circular and aperiodic cyclic granularities that can originate from the underlying periodic and aperiodic linear granularities.
-The mapping of the graphical elements chosen in the paper implies that, for a numeric response variable, the graphics display distributions across combinations of cyclic granularities, one placed at x-axis and the other on the facet.
-That essentially implies there are $^{N_C}P_2$ possible pairwise plots exhaustively, where each plot would display a pair of cyclic granularities.
-This is large and overwhelming for human consumption.
-
-<!-- Scagnostics literature -->
-This is similar to Scagnostics (Scatterplot Diagnostics) by @tukey1988computer, which is used to discern meaningful patterns in large collections of scatterplots.
-Given a set of $v$ variables, there are $v(v-1)/2$ pairs of variables, and thus the same number of possible pairwise scatterplots.
-Therefore
-for even small $v$, the number of scatterplots can be
-large, and scatterplot matrices (SPLOMs) could easily run out of pixels when presenting high-dimensional data.
-@Dang2014-tw and @wilkinson2005graph provides potential solutions to this, where few characterizations help us to locate anomalies for defining several measures aimed to detect anomalies in density, shape, trend, and
-other features in the 2D point scatters.
-
-<!-- harmonies and why it is not enough -->
-The paper (@Gupta2020-vo) narrows down the search from $^{N_C}P_2$ plots by identifying pairs of granularities that can be meaningfully examined together (a "harmony"), or when they cannot (a "clash").
-However, even after excluding clashes, the list of harmonies left could be enormous for exhaustive exploration.
-Hence, there is a need to reduce the search even further by including only those harmonies which are informative enough.
-Also, ranking the remaining harmony pairs based on how well they capture the variation in the measured variable could be potentially useful.
-
-In this paper, we aim to build a new measure to follow through these two main objectives:
-
-- To choose harmonies for which distributions of categories are significantly different 
-- To rank the selected harmonies from highest to lowest variation in the distribution of their categories.
-
-<!-- Talk about Scagnostics: Tukey -->
-
-# Distance measure
-
-We are interested in assessing structure in probability distributions of the measured variable across bivariate cyclic granularities.
-We propose a measure called Median Maximum Pairwise Distances (MMPD) to evaluate structure in such a design.
-
-## Idea {#sec:idea}
-
-The principle employed for building a new metric is explained through a simple example explained in Figure \ref{fig:null4by2}.
-Each of these figures have the same panel design with 2 x-axis categories and 4 facet levels.
-Figure \ref{fig:null4by2}a has all x categories drawn from N(5, 10) distribution for each facet.
-It is not an interesting display particularly, as distributions do not vary across x-axis or facet categories.
-Figure \ref{fig:null4by2}b has x categories drawn from the same distribution within a facet and different for different facet categories.
-Figure \ref{fig:null4by2}b exhibits an exact opposite situation where distribution between the x-axis categories within each facet is different but they are same across facets.
-Figure \ref{fig:null4by2}d takes a step further by varying the distribution across both facet and x-axis categories.
-If we are asked to rank the displays in order of importance from minimum to maximum, we might order it as a, b, c and then d.
-It might be argued that it is not clear if b should precede or succeed c.
-Gestalt theory suggests that when items are placed in close proximity, people assume that they are in the same group because they are close to one another and apart from other groups.
-Hence, displays that capture more variation within different categories in the same group would be important to bring out different patterns of the data.
-With this principle, display b could be considered less informative as compared to display c.
-
-With reference to the graphical design in \ref{@Gupta2020-vo}, therefore the idea would be to rate a harmony pair higher if the variation between different levels of the x-axis variable is higher on an average across all levels of the facet variables.
-Thus the metric could be obtained by computing maximum pairwise distances between distributions of the continuous random variable across x-axis categories for all facets and then taking the median of those maximum pairwise distances across facets.
-This would help capture the average maximum difference in distribution of the measurement variable explained by the two cyclic granularities together.
-We call this metric MMPD which stands for Median Maximum Pairwise Distances.
-In the next section we shall see how we go about computing this measure.
-
-<!-- To elaborate further, look at the examples in Figure \ref{}, where Figure \ref{}a represents the panel design with distribution of each x categories drawn from N(5, 10) distribution.
-It could be observed that the graph is not particularly interesting, as there is no significant change in distribution between x-axis levels or facets.
-Figure \ref{}b represents the same panel design with no difference in distribution of x-axis categories within a facet, but different distribution of x-axis categories for different facets.
-For example, if there are 4 facet levels and 2 x-axis levels, data is generated in the way as described in Table \ref{}.
-Figure \ref{}b exhibits an exact opposite situation where the x-axis within facets are different but not across facets.
--->
-<!-- Figure \ref{}d takes it further by varying the distribution across both facet and x-axis categories. -->
-
-```{r null4by2,fig.cap=" A graphical display with two categories mapped to x-axis and 4 categories mapped to facets with the distribution of a continuous random variable plotted on the y-axis.
-Display a is not interesting as the distribution of the continuous rv does not depend across x-axis or facet categories.
-Display b and c are more interesting than a since there is a change in distribution either across facets(b) or x-axis(a).
-Display d is most interesting as distribution of the rv changes across both facet and x-axis variable."}
-
-sim_varf_dist1 = function(nx, nfacet){
-  rep(dist_normal(seq(mean,mean*nfacet, by = mean), sd), each = nx)}
-
-p1 <- sim_panel(nx = 2, nfacet = 3, ntimes = 500) %>%
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
-
-simulated_data <- sim_panel(nx = 2,
-          nfacet = 3,
-          ntimes = 500,
-          sim_dist = rep(dist_normal(seq(5, 15, 5), 5), each = 2))
-
-p2 <- simulated_data %>% ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
-
-p3 <- simulated_data %>% ggplot(aes(x = as.factor(id_facet), y = sim_data)) + facet_wrap(~id_x) + geom_boxplot()
-
-p4 <- sim_panel(nx = 2,
-          nfacet = 3,
-          ntimes = 500,
-          sim_dist = dist_normal(seq(5,30, 5), 5)) %>% 
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
-
-ggpubr::ggarrange(p1, p2, p3, p4, nrow = 2, ncol = 2,
-                  common.legend = TRUE,
-                  labels = c("a", "b", "c", "d"))
-
-```
-
-<!-- in the same group would be important to bring out different patterns of the data. -->
-
-## Methodology
-
-### Characterising distribution
-
-Each of the data subsets in the data structure have multiple observations and may vary widely across different subsets due to the structure of the calendar, missing observations or uneven locations of events in the time domain.
-The set of observations corresponding to each combination is assumed to be a sample from an unknown probability density function.
-While the whole population of observations has certain characteristics, we can typically never measure all of them.
-Often shape, central tendency, and variability are the common characteristics used to describe the distribution.
-Another way to describe the probability distribution is through quantiles.
-(Define quantiles here) <!--There are two broad approaches to quantile estimation, viz, parameteric and non-parameteric.
-The benefit of using a non-parametric estimator is that there are less rigid assumptions made about the nature of the underlying distribution of the data.--> Sample quantiles could be thought to estimate the population quantiles.
-But there are a large number of different definitions used for sample quantiles.
-The median-unbiased estimator is recommended (Rob's paper) because of its desirable properties of a quantile estimator and can be defined independently of the underlying distribution.
-
-### Distance between distributions
-
-<!-- One of the most important class of divergence is the f-divergence and includes measures like Kullback-Leibler divergence, Hellinger distance etc.
-The continuous version of f -divergence is given by -->
-<!-- $$D_f(P||Q) := \int q(x)f(\frac{p(x)}{q(x)})$$, where -->
-<!-- $f : [0,\infty) \rightarrow R \cup \{\infty\}$ is a continuous convex function, and $f(1) = 0$.  -->
-
-The most common divergence measure between distributions is the Kullback-Leibler (KL) divergence[@Kullback1951-jy] introduced by Solomon Kullback and Richard Leibler in 1951.
-The KL divergence, denoted $D(p(x), q(x))$ is a non-symmetric measure of the difference between two probability distributions $p(x)$ and $q(x)$ and is interpreted as the amount of information lost when $q(x)$ is used to approximate $p(x)$.
-Although the KL divergence measures the “distance” between two distributions, it is not a distance measure since it is not symmetric and does not satisfy the triangle inequality.
-The Jensen-Shannon divergence [@Menendez1997-in] based on the Kullback-Leibler divergence is symmetric and it always has a finite value.
-The square root of the Jensen-Shannon divergence is a metric, often referred to as Jensen-Shannon distance.
-Other common measures of distance are Hellinger distance, total variation distance and Fisher information metric.
-
-In the context of this paper, the pairwise distances between the distributions of the measured variable are computed through Jensen-Shannon distance (JSD) which is based on Kullback-Leibler divergence and is defined by,
-
-$$JSD(P||Q) = \frac{1}{2}D(P||M) + \frac{1}{2}D(Q||M)$$
-where $M = \frac{P+Q}{2}$ and 
-$D(P||Q) := \int^\infty_{-\infty} p(x)f(\frac{p(x)}{q(x)})$ is the KL divergence between distributions $p(x)$ and $q(x)$.
-Probability distributions are estimated through quantiles instead of kernel density so that there is minimal dependency on selecting kernel or bandwidth.
-
-<!-- The Jensen-Shanon distance between two probability distribution $p_1$ and $p_2$ is given by $$d = [D(p_1, r) + D(p_2, r)]/2 \quad where \quad r = (p_1 + p_2)/2$$ where, -->
-<!-- $$D(p_1,p_2) = \int^{\infty}_{-\infty}p_1(x)log\frac{p_1(x)}{p_2(x)}\,dx$$ is the Kullback-Leibler divergence between $p_1$ and $p_2$.   -->
-
-<!-- We call this measure of variation as  Median Maximum Pairwise Distances (MMPD). -->
-
-<!-- #### Distribution of Jensen-Shannon distances -->
-
-<!-- Jensen-Shannon distances (JSD) are distributed as chi-squared with $m$ df where we discretize the continuous distribution with $m$ discrete values.
-Taking sample percentiles to approximate the integral would mean taking $m = 99$.
--->
-<!-- With large $m$, chi-squared is asymptotically normal by the CLT.
-Thus, by CLT, ${\chi^2}_{m} \tilde{} N(m, 2m)$, which would depend on the number of discretization used to approximate the continuous distribution.
-Then $b_n = 1-1/n$ quantile of the normal distribution and $a_n = 1/[n*\phi(b_n)]$ where $\phi$ is the normal density function.
-$n$ is the number of pairwise comparisons being made.
--->
-
-### Definitions
-
-Consider two cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.
-Let the pairwise distances between pairs $(a_{j} b_{k}, a_{j'}, b_{k})$ be denoted as $d_{(jk, j'k')} = JSD(a_{j}b_{k}, a_{j'}b_{k'})$.
-Pairwise distances could be within-facets or between-facets.
-Figure \ref{fig:distance-explain} illustrates how the within-facet or between-facet distances are defined.
-Pairwise distances are within-facets ($d_{w}$) when $b_{k} = b_{k'}$, that is, between pairs of the form $(a_{j}b_{k}, a_{j'}b_{k})$ as shown in panel (3) of Figure \ref{fig:distance-explain}.
-If categories are ordered (like all temporal cyclic granularities), then only distances between pairs where $a_{j'} = (a_{j+1})$ are considered (panel (4)).
-Pairwise distances are between-facets ($d_{b}$) when they are considered between pairs of the form $(a_{j}b_{k}, a_{j}b_{k'})$.
-
-```{r distance-explain, fig.cap = "Within and between-facet distances shown for two cyclic granularities A and B, where A is mapped to x-axis and B is mapped to facets.
-The dotted lines represent the distances between different categories.
-Panel 1) and 2) show the between-facet distances.
-Panel 3) and 4) are used to illustrate within-facet distances when categories are un-ordered or ordered respectively.
-When categories are ordered, distances should only be considered for consecutive x-axis categories.
-Between-facet distances are distances between different facet levels for the same x-axis category, for example, distances between {($a_1$,$b_1$) and ($a_1$, $b_2$)} or {($a_1$,$b_1$) and ($a_1$, $b_3$)}."}
-knitr::include_graphics(here::here("paper/Figs/dist_explain.png"))
-```
-
-From Section \ref{sec:idea}, the idea is to put more weights on within-facet distances than between-facet distances.
-Hence, for a suitable tuning parameter $\lambda > 1$, the pairwise distances $d_{(jk, j'k')}$ are transformed based on the distance type as follows:
-
-\begin{equation}
-d*_{(j,k), (j'k')} =
-\begin{cases}
-\lambda d_{(jk), (j'k')},& \text{if } d = d_w\\
-(1-\lambda)  d_{(jk), (j'k')},              & \text{if } d = d_b\\
-\end{cases}
-\end{equation}
-
-The maximum weighted pairwise distances are defined as:
-$$WPD = max_{j, j', k, k'}(d*_{(jk), (j'k')})
-\forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}$$.
-
-<!-- _j$ maps index set to a set $\{B_\ell \mid \ell =1,\dots,L\}$.
-Here, $A_k$ and $B_\ell$ are the levels/categories corresponding to $C_i$ and $C_j$ respectively.
-Let $S_{k\ell}$ be a subset of the index set such that for all $s \in S_{k\ell}$, $C_i(s) = A_k$ and $C_j(s) = B_\ell$.
-There are $KL$ such data subsets, one for each combination of levels ($A_k$, $B_\ell$).
-Moreover, consider that in the graphical space, $C_i$ is mapped to facets and $C_j$ is mapped to x-axis.
--->
-
- <!-- old -->
-<!-- Consider two cyclic granularities $C_i$ and $C_j$, such that $C_i$ maps index set to a set $\{A_k \mid k=1,\dots,K\}$ and $C_j$ maps index set to a set $\{B_\ell \mid \ell =1,\dots,L\}$.
-Here, $A_k$ and $B_\ell$ are the levels/categories corresponding to $C_i$ and $C_j$ respectively.
-Let $S_{k\ell}$ be a subset of the index set such that for all $s \in S_{k\ell}$, $C_i(s) = A_k$ and $C_j(s) = B_\ell$.
-There are $KL$ such data subsets, one for each combination of levels ($A_k$, $B_\ell$).
-Moreover, consider that in the graphical space, $C_i$ is mapped to facets and $C_j$ is mapped to x-axis.
--->
-
-<!-- The algorithm employed for computing the distance measure is summarized as follows: -->
-
-<!-- 1. Fix harmony pair $(C_i, C_j)$. -->
-
-<!-- 2. Fix $k$. Then there are $L$ groups corresponding to level $A_k$ of $C_i$. -->
-
-<!-- 3. Compute  $m = \binom{L}{2}$ pairwise distances between distributions of $L$ unordered levels and $m = L-1$ pairwise distances for $L$ ordered categories. -->
-
-<!-- 4. Identify maximum within the $m$ computed distances. -->
-
-<!-- <!-- 5. Compute distribution of maximum distance ($M$) by shuffling the data $200$ times and finishing Steps1-4 in each case. Scale $M$ using the mean and sd of the distribution.  --> -->
-
-<!-- 5. Use Steps 1-4 to compute maximum distance for $\forall k \in  \{1, 2, \ldots, K\}$. -->
-
-<!-- 6. Compute the distance measure MMPD_raw = median $(M_1, M_2, \dots, M_K)$. -->
-
-<!-- \begin{algorithm}[!thb] -->
-<!-- 	\caption{Calculation for a raw distance measure between two cyclic granularities $A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.}\label{alg:scoreopt}.
--->
-<!-- 	\begin{algorithmic}[1] -->
-<!-- 		\Procedure{RawMMPD}{$A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$, $v = \{ v_t: t = 1, 2, \dots, T\}$}. -->
-<!-- 		\For{$k=1:K$, $j=1:J$} -->
-<!-- 		\State Find distances between pairs of all possible combinations of categories $(a_jb_k,a_j'b_k')$ by computing JSD between quantiles of the measured variable $q(v)$ across these combinations.
--->
-<!-- 		\State $d \gets JSD(\tilde{q(v)_{a_{j}b_{k}}},\tilde{q(v)_{a_{j}'b_{k}'}})$ -->
-<!-- 		\If {$b_k = b_k'$} -->
-<!-- 		\State $d* \gets \lambda d$  \Comment{upweight within-facet distances} -->
-<!-- 		\Else -->
-<!-- 		\State $d* \gets 1/\lambda d $ \Comment{downweight across-facet distances} -->
-<!-- 		\EndFor -->
-<!-- 		\State Set the raw distance measure as $max(d*)$ where max is taken over all $j, j', k, k'$. -->
-
-<!-- 		\EndProcedure -->
-<!-- 	\end{algorithmic} -->
-<!-- \end{algorithm} -->
-
-<!-- A stronger measure "max" is chosen for aggregating x-axis categories compared to "median" for aggregating facet categories as the measure is intended to put more importance in pointing towards distributional differences between x-axis categories than for facet categories.
--->
 
@@
 
-### Normal Distribution
+### Standard normal distribution
+
+```{r normal, fig.cap="Density plots of raw wpd is shown for N(0,1) distribution.
+The densities change across different facet and x levels, which implies wpd value changes with increasing and facet levels"}
+
+knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/nxbyfacet_density_wpd_N01.png"))
+```
+
+### Comparing normal distributions with different means
 
 ```{r normal-diff, fig.cap="Ridge plots of raw wpd is shown for N(0,1) and N(5,1) distribution.
-The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change is mean value of the normal distribution"}
-knitr::include_graphics(here::here("simulations/null_design/figs/normal_ridge_nxbynfacet_wpd_N01.png"))
+The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change in mean value of the normal distribution"}
+knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_normal.png"))
 ```
 
-### Gamma Distribution
+### Gamma Distribution with different locations
 
@@
 The densities change across different facet and x levels and also for the two distributions, which implies wpd value is affected by the change in location value when distributions are not normal."}
-knitr::include_graphics(here::here("simulations/null_design/figs/gamma_ridge_nxbynfacet.png"))
+knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/extra/gamma_ridge_nxbynfacet.png"))
 ```
 
-<!-- ### Choice of alternate designs -->
+### Gamma Distribution with different locations after quantile transformation
 
-<!-- A normal distribution is taken for this purpose. We would calibrate the values of $WPD$ for different designs illustrated in Section \ref{sec:idea}. -->
-
-<!-- $$\mu_{j.} = \mu + j\omega$$ -->
-<!-- or, $$\mu_{.k} = \mu + k\omega$$ where,    -->
-<!-- $j$ and $k$ are the index of the x and facet category respectively  -->
-<!-- $\mu$ is the mean of the first category and $\omega$ is the increment from the starting value. -->
-
-<!-- mean = 0 -->
-<!-- range_mean = c(0, 1, 3,  5, 7, 15, 20) -->
-<!-- sd = 1 -->
-<!-- range_sd = c(1, 3,  5, 7, 15, 20) -->
-<!-- range_w =  c(1, 2, 3, 4, 5) -->
-<!-- range_lambda = seq(0.1, 0.9, 0.05) -->
-
-## Choice of tuning parameters and effect of different increments
-
-Objective: Choice of optimal tuning parameter $lambda$ with the help of two alternate designs (vary_x and vary_f)  for different nx and nfacets.
-The lambda for which the two designs intersect have to be chosen to put appropriate weights for within-facet and between-facet distances.
-
-Assumptions: The initial combination has a $N(\mu,\sigma)$ distribution and then every combination increases as follows:
-- $$\mu_{j.} = \mu + j\omega$$ (for design vary_x)
-- $$\mu_{.k} = \mu + k\omega$$ (for design vary_f)
-Value of the parameters chosen for this simulation are $\mu = 0$, $\sigma = 1$ and $\omega = {1, 2, \dots, 10}$
-
-Fixing omega, where the design interacts
-
-```{r tuning-one-omega, fig.caption = "WPD from two designs are plotted for different values of lambda for different x and facet categories.
-For omega = 1, the designs intersect for 0.6<lamba<=0.75, whereas for higher omega, design intersects at lambda = 0.5"}
-knitr::include_graphics(here::here("simulations/tuning_param/figs/fixed_omega.png"))
+```{r gamma-diff-trans, fig.cap="Ridge plots of raw wpd is shown for G(0.5,1) and G(2,1) distribution after quantile transformation looks similar and hence is unaffected by change in location"}
+knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_gamma.png"))
 ```
-
-How value of lambda changes with increasing omega
-
-```{r tuning-parameter-intersection}
-knitr::include_graphics(here::here("simulations/tuning_param/figs/intersection_plot.png"))
-```
-
-How value of lambda changes with increasing omega and mean for fixed nx, nfacet and standard deviation?
-
-```{r lambda-omega-mean}
-knitr::include_graphics(here::here("simulations/result_report/lambda_omega_mean_3_2.png"))
-```
-
-How value of lambda changes with increasing omega and sd for fixed nx, nfacet and mean?
-
-```{r lambda-omega-sd}
-knitr::include_graphics(here::here("simulations/result_report/lambda_omega_sd_3_2.png"))
-```
-
-## Alternate designs
-
-```{r lamba-omega-alternate-design}
-knitr::include_graphics((here::here("simulations/result_report/wpd_alterate_designs.png")))
-```
-
- Distribution across facet and x categories
-<!-- ### Need for normalisation -->
-
-From Figure \ref{fig:dist-across-facets} and \ref{fig:dist-across-x} shows the MMPD distribution is different for different levels of facets and x-axis levels.
-With increasing number of facets, the location of the distribution shift rightwards and with increasing x-axis levels, the scale of the distribution reduces.
-
-Median and maximum distances are affected by the number of categories considered and hence the distance measure $MMPD_{raw}$, which is a combination of median and maximum would also be influenced by the number of levels.
-It would have higher values if $C_i$ or $C_j$ has higher levels.
-We would ideally want a higher value of the measure if there is significant difference between distributions across facet or x-axis categories, and not because the number of categories are higher.
-In Figures \ref{fig:dist-across-facets} and \ref{fig:dist-across-x}, both the cyclic granularities $C_i$ and $C_j$ are considered such that their levels vary in the range $(2, 5,7 ,9, 14, 21, 30, 45)$.
-Each of these combinations is considered a panel for each of which $MMPD_{raw}$ has been constructed $100$ times to compute the distribution.
-<!--More specifically, Figure \ref{fig:mean-sd-max} shows the marginal contribution of increasing levels of $C_i$ and $C_j$ on distribution of $MMPD_raw$.
-This shows that with the increase in the number of levels of $C_i$, the location of the distribution shift rightward, whereas for increasing x-axis levels, the scale of the distribution decreases.-->
-
-Therefore, in order to compare $MMPD_{raw}$ across different combinations of facet and x-axis levels, we need to eliminate the impact of different levels of the facets and x-axis first and get a normalized measure.
-
-```{r hist-nx-nfacet, eval = FALSE}
-knitr::include_graphics(here::here("simulations/result_report/hist_nxbyfacet.png"))
-```
-
-```{r dist-across-facets, fig.cap = "Distribution of $MMPD_{raw}$ for different facet levels are shown.
-The location of the distribution shifts rightwards implying that as the number of facets increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained.", eval = FALSE}
-here::here()
-knitr::include_graphics(here::here("simulations/result_report","nx_by_facet_raw.png"))
-```
-
-<!-- # ```{r dist-across-facets, fig.cap = "Distribution of $MMPD_{raw}$ for different facet levels are shown.
-The location of the distribution shifts rightwards implying that as the number of facets increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained.
-"} -->
-<!-- # mmpd_raw = read_rds("../hakear-drake/data/data_all23457914n.rds")  -->
-<!-- # mmpd_xmore = read_rds("../hakear-drake/data/data_all213045x.rds")  -->
-<!-- # mmpd_fmore = read_rds("../hakear-drake/data/data_all_213045f_allx.rds") -->
-<!-- #  -->
-<!-- # data_all = bind_rows(mmpd_raw, mmpd_xmore) -->
-<!-- #  -->
-<!-- # data_long = data_all %>% pivot_longer(c(1:2), names_to = "category", values_to = "levels") -->
-<!-- #  -->
-<!-- # g1 <- data_all %>%  -->
-<!-- #   filter(!(nx %in% c(3, 4))) %>%  -->
-<!-- #   ggplot() + -->
-<!-- #   ggridges::geom_density_ridges(aes(x = raw_mmpd,  -->
-<!-- #                                     y = as.factor(nfacet))) + -->
-<!-- #   facet_wrap(~nx, nrow = 2) -->
-<!-- # g1 -->
-<!-- # ``` -->
-
-```{r dist-across-x, fig.cap = "Distribution of $MMPD_{raw}$ for different x levels are shown.
-The scale of the distribution becomes less and less implying that as the number of x levels increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained as the spread of the distribution decreases.
-", eval = FALSE}
-knitr::include_graphics(here::here("simulations/result_report/","nfacet_by_nx_raw.png"))
-```
-
-<!-- # ```{r dist-across-x, fig.cap = "Distribution of $MMPD_{raw}$ for different x levels are shown.
-The scale of the distribution becomes less and less implying that as the number of x levels increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained as the spread of the distribution decreases.
-"} -->
-<!-- # g2 <- data_all %>%  -->
-<!-- #   filter(nfacet<=14, nfacet!=3) %>%  -->
-<!-- #   ggplot() + -->
-<!-- #   geom_boxplot(aes(y = raw_mmpd,  -->
-<!-- #                                     x = as.factor(nx))) + -->
-<!-- #   facet_wrap(~nfacet) + coord_flip() -->
-<!-- #  -->
-<!-- # #  hist_plot = data_all %>%  -->
-<!-- # #       ggplot() + -->
-<!-- # #       geom_density(aes(x = raw_mmpd), fill = "blue") + -->
-<!-- # #       facet_grid(nx~nfacet) -->
-<!-- # # hist_plot -->
-<!-- # g2 -->
-<!-- # ``` -->
-
-<!-- both mean and standard deviation of the distribution of maximum and median varies for different sample sizes ($n$).
-There is a rightward shift in the location and decrease in scale with increasing $n$.
--->
-
-## Sample size
-## Number of permutations
-
-# Normalisation
-
-In an attempt to make the densities \ref{fig:hist_plot} same across different levels, we want to start by making their scale and location same.
-In that regard, we shuffle the data multiple times and compute the sampling distribution of $mmpd_{raw}$ for each combination of facet and x-axis levels.
-
-The null hypothesis is that the two cyclic granularities do not differ on the outcome (i.e., that the outcome is observed independently of treatment assignment).
-When we permute the outcome values during the test, we therefore see all of the possible alternative treatment assignments we could have had and where the mean-difference in our observed data falls relative to all of the differences we could have seen if the outcome was independent of treatment assignment.
-While a permutation test requires that we see all possible permutations of the data (which can become quite large), we can easily conduct “approximate permutation tests” by simply conducting a vary large number of resamples.
-That process should, in expectation, approximate the permutation distribution.
-
-Finally, we run some simulation experiments to see if normalisation works. If normalisation has worked, it should work for both x levle and facet-levels.
-
-Thus these median maximum pairwise distances need to be normalized for different harmonies in a way that eliminates the effect of different levels, consequently enabling comparison across different harmonies.
-The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.
-
-```{r}
-knitr::include_graphics(here::here("simulations/null_design/figs/normalised","gamma_ridge_nxbynfacet.png"))
-```
-
-## Methodology
-
-The mean and sd for each combination of facet and x levels could be computed by shuffling the data repeatedly and obtaining the distribution of $MMPD_{raw}$ for different combinations.
-If $MMPD_{raw}$ is then adjusted by the location and scale of this distribution, we could assume that the distribution of the resultant $MMPD_{norm}$ will have same distribution across different combinations of x and facet levels.
-All data is repeatedly shuffled $nperm$ times in random manner to obtain the measure $MMPD_{raw}$.
-Then the $MMPD_{norm}$ is obtained by scaling the observed value by the mean and sd of the distribution of $MMPD_{raw}$ obtained from the permuted data.
-
-\noindent Step 7 in the Algorithm defined in Section \ref{sec:} need to be revised in order to compute $MMPD_{norm}$ instead of $MMPD_{raw}$.
-Step 1-6 stays the same.
-The entire algorithm will have to repeated for all harmony pairs considered in the context.
-
-A simulation study is conducted to see if this methodology is working.
-
-<!-- #### Method 2: -->
-
-<!-- $m' = max_{x}dist$ is obtained for each facet. -->
-<!-- All $x$ levels are shuffled for each facet to obtain several $m'$s.
-Hence $m'$ is normalized for each facet level and the facets are aggregated using $m''= median(m')$, which is basically median(norm(max)).
-We need to normalise this median across facets as well.
-So we shuffle all facets for each $x$ level and obtain several $m''$s.
-In this approach, data is shuffled $2*nperm$ times and hence distances are computed $2*nperm$ times.
-It is computationally very intensive.
--->
-
-<!-- Hence, it was decided that the first approach will be employed to implement normalisation.
-One of the advantages of the second method could be to have normalisation separately for max and median measure.
-There is nothing that is stopping the users to implement this with more efficient computing power.
--->
-
-<!-- The harmony pairs could be arranged from highest to lowest average maximum pairwise distances across different levels of the harmonies. -->
-
-<!-- With increasing n, mean and sd of distribution of max increases. -->
-
-<!-- FTP theorem works for large n -->
-
-<!-- For small n resort to bootstrapping -->
-
-<!-- bullet points end here -->
-
-<!-- Suppose that $X_1$, $X_2$ , ... , $X_n$ are i.i.d. random variables with expected values $E(X_i) = \mu < \infty$ and variance $Var(X_i) = \sigma^2 < \infty$. Let  -->
-<!-- $Y = max(X_1, X_2, \dots, X_n)$. -->
-
-<!-- Let $F_X(x)$ be the common distribution of the variables $X_i$ and let $F_Y(y)$ be the corresponding distribution of $Y$. $F_Y(y)$ could be obtained from $F_X(x)$ simply by using: -->
-<!-- $F_Y(y) = P[(X_1 \leq y)\cap(X_2 \leq y) \cap...\cap (X_n \leq y)] = {F_X(y)}^n$.
-For large $n$, the distribution of $Y$ approaches a standard shape, which does not depend on $F_X$.
-But what about the case when $n$ is not large enough?
-The distribution of maximum in that case will indeed depend on $n$ and the underlying distribution of $X$.
-If $F_X(x)$ is the CDF of $X$, then $F_Y(y) = {F_x(y)}^n$.
-Suppose $\Phi$ nd $\phi$ are the cdf and pdf of a standard normal distribution, then -->
-<!-- $f_Y(y) = n{\Phi(y)}^{n-1}\phi(y)$, which depends on $n$.
-Hence, we are trying to normalise for $n$.
-Also, it depends on the underlying distribution of $X$, which we have assumed as normal in our case.
-As $n$ grows, we  can see the right tail growing, which implies that the probability that we will get a higher maximum is more.
-Now, for large $n$, we used EVT to normalise for $n$, that is, we brought them to the same scale without distorting the range of the distribution.
-But in our case, we will mostly have small $n$.
-It is important to ensure that they have the same mean and variation, for being able to compare the maximum value across $n$.
-We observe from the following graphs that our normalisation works after $n=6$, after which the difference in mean and standard deviation flattens out a lot.
--->
-
-<!-- ### why normalize -->
-
-<!-- Median and maximum distances are not robust to the number of levels and the metric would have higher values for harmonies with higher levels.
-Figure \ref{fig:mean-sd-max} shows how both mean and standard deviation of the distribution of maximum and median varies for different sample sizes ($n$).
-There is a rightward shift in the location and decrease in scale with increasing $n$.
-Thus these median maximum pairwise distances need to be normalized for different harmonies in a way that eliminates the effect of different levels, consequently enabling comparison across different harmonies.
-The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.
--->
-
-<!-- More formally, $d_{1},d_{2}\ldots ,d_{n}$ be a sequence of independent and identically-distributed pairwise distances and $M_{n}=\max\{d_{1},\ldots ,d_{n}\}$.
-Then Fisher–Tippett–Gnedenko theorem [@De_Haan2007-yx] suggests that if a sequence of pairs of real numbers $(a_{n}, b_{n})$ exists such that each $a_{n}>0$ and $\lim _{{m\to \infty }}P\left({\frac  {M_{n}-b_{n}}{a_{n}}}\leq x\right)=F(x)$, where $F$ is a non-degenerate distribution function, then the limit distribution $F$ belongs to either the Gumbel, Fréchet or Weibull family.
-The normalizing constants $(a_{n}, b_{n})$ vary depending on the underlying distribution of the pairwise distances.
-Hence to normalize appropriately, it is  -->
-<!-- important to assume a distribution of these distances.  -->
-
-<!-- For large $n$, the distribution of $M$ approaches a standard shape.
-But what about the case when $n$ is not large enough?
-The distribution of maximum in that case will indeed depend on $n$ and the underlying distribution of $D$.
-For large $n$, we could use EVT and CLT to normalise for $n$, however, most of the cyclic granularities encountered in practice have low $n$.
-Hence, normalisation could be done by bootstrapping procedure to ensure that the distribution of maximum/median have the same mean and variation for varying $n$.
--->
-
-<!-- ```{r create_simdata} -->
-
-<!-- ``` -->
-
-<!-- ```{r create_nlevels} -->
-
-<!-- ``` -->
-
-<!-- ```{r norm_max_new} -->
-
-<!-- ``` -->
-
-<!-- ```{r mean-sd-max, fig.cap = "Display shows mean and standard deviation of the distribution of maximum for sample sizes ranging from 2 to 30.
-There is a right shift in the distribution of maximum and median with increasing sample sizes."} -->
-
-<!-- library(ggridges) -->
-<!-- library(viridis) -->
-<!-- max_all_data <- create_nlevels(nlevels = seq(2, 30, 2), -->
-<!--                            nsim = 500, -->
-<!--                            sim_dist = distributional::dist_normal(5, 10), create_fun = max) -->
-
-<!-- g1 <- max_all_data %>% ggplot() + geom_density_ridges(aes(x=sim_data, y = as.factor(ind))) + ylab("n") + xlab("max") -->
-
-<!-- median_all_data <- create_nlevels(nlevels = seq(2, 30, 2), -->
-<!--                            nsim = 500, -->
-<!--                            sim_dist = distributional::dist_normal(5, 10), create_fun = median) -->
-
-<!-- g2 <- max_all_data %>% ggplot() + geom_boxplot(aes(x=sim_data, y = as.factor(ind)))  + ylab("n") + xlab("median") -->
-
-<!-- ggpubr::ggarrange(g1, g2, ncol = 2) -->
-
-<!-- ``` -->
-
-## Simulation study
-
-<!-- ### Distribution of distances -->
-
-<!-- ### Theoretical evidence -->
-
-<!-- JS distances are distributed as chi-squared with $m$ df where we discretize the continuous distribution with $m$ discrete values.
-Taking sample percentiles to approximate the integral would mean taking $m = 99$.
--->
-<!-- With large $m$, chi-squared is asymptotically normal by the CLT.
-Thus, by CLT, ${\chi^2}_{m} \tilde{} N(m, 2m)$, which would depend on the number of discretization used to approximate the continuous distribution.
-Then $b_n = 1-1/n$ quantile of the normal distribution and $a_n = 1/[n*\phi(b_n)]$ where $\phi$ is the normal density function.
-$n$ is the number of pairwise comparisons being made.
--->
-
-<!-- ### Empirical evidence -->
-
-<!-- Distribution of JS distances is assumed to be normal but the mean and variance are estimated from the sample, rather than deducing it from the number of discretization used to approximate the continuous distribution.
-We look at different scenarios, where observations are collected from Normal, Exponential, Chi-squared and Gumbel distribution and found the distribution of JS distances are similar, irrespective of which distribution they are drawn from.
--->
-
-<!-- #### Initial distribution of observed variables shown in plot title -->
-
-<!-- ```{r distv11} -->
-
-<!-- ``` -->
-
-<!-- ```{r distv12} -->
-
-<!-- ``` -->
-
-<!-- ```{r distv13} -->
-
-<!-- ``` -->
-
-<!-- ```{r distv14} -->
-
-<!-- ``` -->
-
-<!-- ### Design and analysis of simulation experiments -->
-
-The behavior of the measure is monitored and understood through simulation experiments.
-A single simulation consisting of computational operations on a panel generating MMPD the value of which represents to what extent a pair of cyclic granularities would be interesting when displayed in the design.
-In comparing different simulation runs, we distinguish between different distributions and simulation scenarios (also iterations may be).
-
-### Simulated designs
-
- D1. Same distribution of the measured variable across all x-axis and facet categories
- D2. Different distribution across facet categories but same across x-axis categories
- D3. Different distribution across x-axis categories but same across facet categories
- D4. Different across both x-axis and facet categories
-
-Each of these case scenarios tried against Normal and a non-normal (Gamma) distribution to check if underlying distribution has a role to play.
-
-### Environment
-
-R version 4.0.1 (2020-06-06) is used with platform: x86_64-apple-darwin17.0 (64-bit) running under: macOS Mojave 10.14.6
-
-### Experimental set up
-
-This section describes the design of simulation runs, in terms of the scenarios simulated, the number of permutations used to compute estimates and to display the distribution of MMPD.
-
- <!-- - seed while generating random observations `seed1 = set.seed(9999)`   -->
- <!-- - grid with how many x levels `range_nx_vec = seq(2:4)`   -->
- <!-- - grid with how many facet levels `range_nfacet_vec = seq(2:4)`   -->
- <!-- - number of observations to be generated `ntimes_val = 500`   -->
- <!-- - number of permutation of data done to compute estimates `nperm_val = 2`   -->
- <!-- - number of permutations of data done to display histogram for each panel `nsim_val = 10`    -->
- <!-- - ordered or un-ordered categories of x levels while computing distances `dist_ordered_val = TRUE`   -->
- <!-- - distance between which quantiles are computed `quantile_prob_vec = seq(0.01, 0.99, 0.01)`   -->
-
-```{r}
-knitr::include_graphics(here::here("paper/Figs/simulation.png"))
-```
-
-Observations from Normal(5, 10) and Gamma(0.5, 0.2) are3 chosen in all the designs.
-
-<!-- . the null distribution are chosen as:   -->
-<!-- `sim_norm_null =   distributional::dist_normal(5, 10)`   -->
-<!-- <!--`sim_exp_null  =   distributional::dist_expoential(5)`  --> -->
-<!-- `sim_gamma_null  =   distributional::dist_gamma(0.5, 0.2)`   -->
-<!-- <!--`sim_weibull_null  =   distributional::dist_weibull(1.5, 3)`-->   -->
-
-<!-- The various designs are selected by increasing the mean/rate/shape of these distributions proportionally with that parameter. -->
-
-<!-- To check if different distributions impact, simulate data from different distributions.
-A 3 way contingency table with number of facet levels, x-axis levels and distribution type should be constructed with each cell value as the p-value.
--->
-
-<!-- Table -->
-<!-- Conclusions -->
-<!-- (in Null distribution) -->
-
-<!-- #### Varying distribution across facet -->
-<!-- #### Varying distribution across x-axis -->
-<!-- #### Varying distribution across both facets and x-axis -->
-<!-- #### Repeat all with varying facet and x-axis levels -->
-
-<!-- Table -->
-<!-- Conclusions -->
-<!-- (in power) -->
-
-<!-- ```{r} -->
-<!-- raw_data = rnorm(12, 5, 10) %>%  -->
-<!--   as_tibble() %>%  -->
-<!--   mutate(nfacet = rep(1:4, each = 3), -->
-<!--          nx = rep(1:3, 4)) -->
-
-<!-- raw_data %>% group_by(nfacet, nx) %>% nest() -->
-
-<!-- raw_data2 = raw_data %>% pivot_wider(id_cols = 2, names_from = "nx", values_from = "value") -->
-
-<!-- ``` -->
-
-<!--  ### Original -->
-<!-- | facets/x-axis     	| A_1  	| A_2  	| A_3  	| .. 	| .. 	| A_m  	| -->
-<!-- |-----	|------	|------	|------	|----	|----	|------	| -->
-<!-- | B_1 	| x_1 	| x_2 	| x_3 	| .. 	| .. 	| x_n 	| -->
-<!-- | B_2 	| y_1 	| y_2 	| y_3 	| .. 	| .. 	| y_n 	| -->
-<!-- | B_3 	|      	|      	|      	|    	|    	|      	| -->
-<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
-<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
-<!-- | B_L 	| z_1 	| z_2 	| z_3 	| .. 	| .. 	| z_m 	| -->
-
-<!-- ### Step1 -->
-
-<!-- | facets/x-axis     	| A_1  	| A_2  	| A_3  	| .. 	| .. 	| A_m  	| -->
-<!-- |-----	|------	|------	|------	|----	|----	|------	| -->
-<!-- | B_1 	| x_1 	| x_2 	| x_3 	| .. 	| .. 	| x_n 	| -->
-<!-- | B_2 	| y_1 	| y_2 	| y_3 	| .. 	| .. 	| y_n 	| -->
-<!-- | B_3 	|      	|      	|      	|    	|    	|      	| -->
-<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
-<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
-<!-- | B_L 	| z_1 	| z_2 	| z_3 	| .. 	| .. 	| z_m 	| -->
-
-```{r, eval = FALSE}
-# design_time <- readr::read_rds("../hakear-drake/data/design_time.rds")
-# write_rds(design_time, "data/design_time.rds")
-time_data <-readr::read_rds("data/design_time.rds")
-time_data$design = 
-  factor(time_data$design,
-         levels = c("null","vary_f", "vary_x", "vary_all"))
-
-time_data %>% 
-  pivot_longer(cols = c(time_obs, time_dist),
-               names_to = "type",
-               values_to = "time") %>% 
-  dplyr::filter(distribution == "normal") %>% 
-  ggplot(aes(x= design, 
-             y = log(time, exp(1)), 
-             colour = type, group = nfacet)) + geom_point() + geom_line(aes(group = type)) +
-  facet_grid(nx~nfacet) + ylab("ln(time)")
-
-```
-
-## Results
-
-### Null distribution
-
-<!-- Objective: distribution equal and hence values could be compared and normalisation works -->
-Under the null hypothesis, all the combinations of x-axis and facets are obtained from the same distribution.
-We need to study the distribution of the mmpd values under the null hypothesis to see if comparison of their values across different x-axis and facet levels are at all possible.
-So, in turn it needs to be checked that if normalisation worked.
-
-Currently, we see in Figure \ref{fig:null-dist} that the normalisation works fine for each facet since the distributions for each column are equal irrespective of the distribution type.
-But it does not work along the x-axis.
-
-```{r norm-data, fig.cap = "Distribution of $MMPD_{norm}$ across different levels of facet and x-axis. These distributions should look the same if normalisation worked." }
-mmpd_norm = read_rds("../hakear-drake/data/data_norm_low_new.rds") 
-hist_plot = mmpd_norm %>% 
-      ggplot() +
-      geom_histogram(aes(x = raw_mmpd)) +
-      facet_grid(nx~nfacet)
-hist_plot
-```
-
-```{r null-dist, eval =  FALSE, echo = FALSE, fig.cap="Distribution of mmpd across different facet levels (columns) and x-axis levels (rows) for null ditribution normal(5,10) and gamma(0.5, 0.2).
-The distribution of MMPD is unaffected by the null distribution considered.
-It is also the same across all facet levels but not across the x-axis, which means normalisation is failing across x-axis."}
-# all_files = list.files(path = "../hakear-drake/data", pattern = ".rds")
-# all_files
-# 
-# read_files = lapply(all_files, function(x){
-#   read_rds(paste0("../hakear-drake/data/", x))
-# })
-# 
-# names(read_files) = str_remove(all_files, pattern = ".rds")
-# 
-# null_all = bind_rows(normal = read_files$null_normal,
-#                      exponential = read_files$null_exp,
-#                      gamma = read_files$null_gamma,
-#                      weibull = read_files$null_weibull,
-#                      .id = "distribution")
-# design_all = readr::read_rds("../hakear-drake/data/design_all.rds")
-design_all = readr::read_rds("data/design_all.rds")
-
-design_all$design = 
-  factor(design_all$design,
-         levels = c("null","vary_f", "vary_x", "vary_all"), labels = c("D1", "D2", "D3", "D4"))
-design_all$distribution = 
-  factor(design_all$distribution,
-         levels = c("normal","gamma"), labels = c("norm","gam"))
-library(dplyr)
-library(ggplot2)
-ggplot2::ggplot(design_all %>% 
-                      filter(design == "D1")) +
-  ggridges::geom_density_ridges(aes(y = distribution, x = mmpd.x, fill = distribution)) + 
-  facet_grid(nx~nfacet) +
-  scale_fill_viridis_d() +
-  xlab("MMPD")
-```
-
-### Performance of normalised MMPD
-
-```{r}
-data1  = sim_panel(nx = 2, nfacet = 3, ntimes = 500)
-simulated_data <- sim_panel(nx = 2,
-nfacet = 3,
-ntimes = 500,
-sim_dist = rep(dist_normal(seq(5, 15, 5), 5), each = 2))
-data2 = simulated_data
-data4 = sim_panel(nx = 2,
-nfacet = 3,
-ntimes = 500,
-sim_dist = dist_normal(seq(5,30, 5), 5))
-data3 = data2 %>% rename("temp" = "id_facet") %>% rename("id_facet" = "id_x") %>% rename("id_x" = "temp")
-
-library(parallel)
-library(gravitas)
-library(hakear)
-
-set.seed(1000)
-r1 <- compute_mmpd_norm(data1, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-r2 <- compute_mmpd_norm(data2, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-r3 <- compute_mmpd_norm(data3, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-r4 <- compute_mmpd_norm(data4, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-r1prime <- compute_norm_pairwise_max(data1, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-r2prime <- compute_norm_pairwise_max(data2, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-r3prime <- compute_norm_pairwise_max(data3, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-r4prime <- compute_norm_pairwise_max(data4, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-p1 <- data1 %>%
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +xlab("")
-
-p2 <- data2 %>% ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +xlab("")
-
-p3 <- data3 %>% ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +xlab("")
-
-p4 <- data4 %>% 
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +xlab("")
-
-gridExtra::grid.arrange(gridExtra::arrangeGrob(p1, top = paste("MMPD", round(r1, 3), "pairwise", round(r1prime, 3))),
-                        gridExtra::arrangeGrob(p2, top = paste("MMPD", round(r2, 3), "pairwise", round(r2prime, 3))),
-                        gridExtra::arrangeGrob(p3, top = paste("MMPD", round(r3, 3), "pairwise", round(r3prime, 3))),
-                        gridExtra::arrangeGrob(p4, top = paste("MMPD", round(r4, 3), "pairwise", round(r4prime, 3))),
-                        ncol = 2, nrow=2)
-
-```
-
-# The statistical test
-
-## Algorithm
-
-for computation for all harmony pairs
-
-**Assumption:** random permutation without considering ordering 
-(global)
-
-1. Given the data; $\{v_t: t=0, 1, 2, \dots, T-1\}$, the MMPD is computed and is represented by $MMPD_{obs}$.
-
-2. From the original sequence a random permutation is obtained: $\{v_t^*: t=0, 1, 2, \dots, T-1\}$.
-
-3. MMPD is computed for all random permutation of the data and is represented by $MMPD_{sample}$.
-
-4.  Steps (2) and (3) are repeated a large number
-of times M (e.g. 1000).
-
-5. For each permutation, one $MMPD_{sample}$ value is obtained.
-
-6. $95^{th}$ percentile of this $MMPD_{sample}$ distribution is computed and stored in $MMPD_{threshold}$.
-
-7. If  $MMPD_{obs}> MMPD_{threshold}$, harmony pairs are accepted. Only one threshold for all harmony pairs.
-
-Pros: Considering thresholds global for all harmony pairs would imply less computation time.
-
-Cons: Only one threshold for all harmony pairs means we are assuming distribution of all harmonies pairs are similar, which might not be the case.But nevertheless, it is a good benchmark.
-
-```{r, eval = FALSE, echo = FALSE}
-smart_harmony <-read_rds("data/smart_harmony_nonst.rds")
-smart_harmony
-```
-
-```{r smart_harmony,eval = FALSE, echo = FALSE}
-
-sm <- smart_meter10 %>% dplyr::filter(customer_id %in% c("10017936"))
-
-harmonies <- sm %>% 
-  harmony(ugran = "month",
-          filter_in = "wknd_wday",
-          filter_out = c("hhour", "fortnight"))
-
-harmony_tbl =  harmonies
-
-smart_harmony <- sm %>% 
-  rank_harmony(harmony_tbl = harmonies,
-               response = "general_supply_kwh", 
-               dist_ordered = TRUE)
-
-smart_harmony %>% 
-  mutate(MMPD = round(MMPD, 3), max_pd = round(max_pd, 3)) %>% 
-  mutate(rankn = row_number()) %>%
-  rename("rankun" = "r") %>% kable()
-```
-
-## Size, power and confidence interval
-
-#### Characteristics under different simulation designs   
-A set of simulation runs that are conducted and some outputs of which are reported.
-
-```{r sim_all, echo = FALSE}
-bind_files = readr::read_rds("../hakear-drake/data/compute_p_value.rds")
-
-bind_files$design = 
-  factor(bind_files$design,
-         levels = c("null","vary_f", "vary_x", "vary_all"), labels = c("D1", "D2", "D3", "D4"))
-
-ggplot(bind_files %>% 
-         filter(distribution == "normal")) +
-  geom_point(aes(x=design, y = p_value),
-                 alpha = 0.5)+
-  facet_grid(nx~nfacet) +
-  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
-
-ggplot(bind_files %>% 
-         filter(distribution == "exponential")) +
-  geom_point(aes(x=design, y = p_value),
-                 alpha = 0.5)+
-  facet_grid(nx~nfacet) +
-  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
-
-ggplot(bind_files %>% 
-         filter(distribution == "gamma")) +
-  geom_point(aes(x=design, y = p_value),
-                 alpha = 0.5)+
-  facet_grid(nx~nfacet) +
-  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
-
-ggplot(bind_files %>% 
-         filter(distribution == "weibull")) +
-  geom_point(aes(x=design, y = p_value),
-                 alpha = 0.5)+
-  facet_grid(nx~nfacet) +
-  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
-```
-
-```{r sim_conf, echo = FALSE, eval = FALSE}
-library(dplyr)
-library(ggplot2)
-ggplot2::ggplot(design_all %>% 
-                      filter(design == "D1", distribution == "norm")) +
-  geom_boxplot(aes(x = as.factor(nx), 
-                   y = mmpd.x), width = 0.1) + 
-  facet_wrap(~nfacet) +
-  scale_fill_viridis_d() +
-  xlab("number of x levels") +
-  coord_flip()
-
-```
-
-# Applications {#sec:application}
-
-## Smart meter data of Australia {#sec:smartmeter}
-
-<!-- # how data looks -->
-
-Smart meters provide large quantities of measurements on energy usage for households across Australia.
-One of the customer trials [@smart-meter] conducted as part of the Smart Grid Smart City project in Newcastle, New South Wales and some parts of Sydney provides customer wise data on energy consumption for every half hour from February 2012 to March 2014.
-<!--It would be interesting to explore the energy consumption distribution for these customers and gain insights on their energy behavior which are lost either due to aggregation or looking only at coarser temporal units.-->The idea here is to show how to visualize the distribution of the energy consumption across different cyclic granularities in a systematic way to identify different behavioral patterns.
-
-### Cyclic granularities search and computation:
-
-The tsibble object `smart_meter10` from R package `gravitas` [@R-gravitas] consisting of `reading_datetime`, `customer_id` and `general_supply_kwh` denoting the index, key and measured variable of the tsibble is used to facilitate the systematic exploration.
-While trying to explore the energy behavior of these customers systematically across cyclic time granularities, the first thing to consider is which cyclic time granularities we can look at exhaustively.
-Let us consider conventional time deconstructions for a Gregorian calendar (second, minute, half-hour, hour, day, week, month, year).
-Since the interval of this tsibble is 30 minutes, the temporal granularities may range from half-hour to year.
-Considering $6$ linear granularities half-hour, hour, day, week, month and year in the hierarchy table, $N_C = (6*5/2) = 15$.
-<!--(via Section \ref{sec:data-structure}) circular or quasi-circular granularities that could be formed relating two linear granularities at a time.--> If $N_C$ seem too large, the smallest and largest linear granularities could be considered to be removed from the hierarchy table.
-We remove half-year and year to have $N_C = (4*3/2) = 6$ and obtain cyclic granularities namely "hour_day", "hour_week", "hour_month", "day_week", "day_month" and "week_month", read as "hour of the day", etc.
-Further, we add cyclic granularity day-type( "wknd_wday") to capture weekend and weekday behavior.
-Now that we have a list of cyclic granularities to look at, we should be able to compute the multiple-order-up granularities using Section \ref{sec:cyclic-calendar}.
-
-```{r search, echo=FALSE, eval = FALSE}
-library(gravitas)
-smart_meter %>%
-  search_gran(filter_out = c("semester", 
-                             "quarter",
-                             "fortnight"))
-```
-
-```{r search_gran_limit2, echo = FALSE, eval = FALSE}
-smart_meter10 %>% search_gran(
-  highest_unit = "month",
-  filter_out = c("hhour", "fortnight"))%>%
-  knitr::kable(format = "latex",
-      booktabs = TRUE) %>%
-  #row_spec(0, bold = TRUE)%>%
-  kable_styling()
-```
-
-<!-- # smart_meter_limit2 <- smart_meter10 %>% search_gran(highest_unit = "month", -->
-<!-- #                               filter_out = c("hhour", "fortnight") -->
-<!-- # ) -->
-<!-- # knitr::kable(smart_meter_limit2, format = "markdown") -->
-
-<!-- Now that we have a list of cyclic granularities to look at, we should be able to compute them from the data using Sections \ref{sec:circular-gran-def}, \ref{sec:quasi-circular-gran-def} and \ref{sec:aperiodic-gran-def}.
--->
-
-### Screening and visualizing harmonies
-
-From the search list, $N_C = 7$ cyclic granularities are chosen for which we would like to derive insights of energy behavior.
-Recalling the data structure <$C_i$, $C_j$, `general_supply_kwh`> for exploration $\forall i, j \in \{1, 2, \ldots, 7\}$, each of these $7$ cyclic granularities can either be mapped to x-axis or to facet.
-Choosing $2$ of the possible $7$ granularities, which is equivalent to having $^{7}P_2 = 42$ candidates for visualization.
-Fortunately, harmonies can be identified among those $42$ possibilities to narrow the search.
-\autoref{tab:harmony-tab} shows $16$ harmony pairs after removing clashes and any cyclic granularities with levels more than $31$, as effective  exploration becomes difficult with many levels (Section \ref{sec:levels}).
-The MMPD is also shown along with indicator (*) only when variation of measured variable across the harmony pair significant.
-Starting from $42$ possible pairs of cyclic granularities to visualize, we are finally left with only $6$, which is a very sizable number of displays for exploration.
-
-Few harmony pairs are displayed in \autoref{fig:bothcust} to illustrate the significance of MMPD, threshold and the impact of different distribution plots and reverse mapping.
-\noindent For each of \autoref{fig:bothcust} (b) and (c), $C_i$ is the circular granularity day-type (weekday/weekend) and $C_j$ is hour of the day.
-The geometry used for displaying the distribution is chosen as area-quantiles and violins in \autoref{fig:bothcust} (b and c respectively).
-\autoref{fig:bothcust} (a) displays reverse mapping of $C_i$ and $C_j$ with $C_i$ denoting hour of the day and $C_j$ denoting day-type with distribution geometrically displayed as boxplots.
-
-<!-- From the search list, we found six cyclic granularities for which we would like to derive insights of energy behavior.
-Given the data structure <$C1$, $C2$, `general_supply_kwh`>, each of those six cyclic granularities can either be mapped to x-axis or to facet.
-Thus the problem is equivalent to taking 2 granularities at a time from six, which essentially is equivalent to having 30 data subsets for visualization.
-However, harmony/clash pairs can be identified among those 30 possibilities to determine feasibility of plotting any pairs together.
-\autoref{tab:harmony-tab} shows 13 harmonies pairs, each of which can be plotted together to look at the energy behavior from different perspectives.
--->
-
-<!-- We will look at few harmony pairs and see how the proposed workflow can be utilized.  -->
-
-<!-- From the Gestalt theory with the same data  <$C1$ $C2$, `general_supply_kwh`>, mapping $C1$ on the x-axis vs facet might lead to different insights. -->
-
-```{r harmony-tab, echo=FALSE, eval = FALSE, cache=TRUE}
-# if(!dir.exists("cache/"))
-# {
-#   dir.create("cache")
-# }
-# 
-# if (!file.exists("cache/smart_harmony.rds")) {
-  sm <- smart_meter10 %>%
-  filter(customer_id %in% c(10017936))
-
-  harmonies <- sm %>%
-  harmony(ugran = "month",
-          filter_in = "wknd_wday", 
-          filter_out = c("hhour", "fortnight"))
-set.seed(12345)
-
-global_harmony <- sm %>%
-  global_threshold(harmony_tbl = harmonies,
-                   response = "general_supply_kwh", nsamp = 5) %>%
-  rename(`facet variable` = facet_variable,
-         `x-axis variable` = x_variable,
-         `facet levels` = facet_levels,
-         `x-axis levels` = x_levels) %>% 
-  mutate(MMPD = if_else(gt_MMPD == TRUE,
-                        paste0(MMPD, "*"), paste0(MMPD))) %>%
-  select(`facet variable`,`x-axis variable`,
-         `facet levels`,`x-axis levels` ,MMPD)
-
-#   write_rds(smart_harmony,"cache/smart_harmony_ak.rds")
-# }
-#smart_harmony <- read_rds("cache/smart_harmony.rds")
-
-  knitr::kable(global_harmony,
-               format = "latex",
-               booktabs = TRUE,
-                caption = "Harmonies with a pair of cyclic granularity one placed on facet and the other on x-axis.
-Out of 42 possible combinations of cyclic granularities, only 16 are harmony pairs.
-The harmony pairs are ranked basis highest to lowest MMPD and only the first 6 show significant variation in the measured variable.") %>%
-    #row_spec(0, bold = TRUE) %>%
-    kable_styling()
-```
-
-In \autoref{fig:bothcust} (b), <!--the distribution of energy consumption is plotted across the harmony pair (weekday/weekend, hour of the day) through an area quantile plot-->the black line is the median, whereas the purple band covers 25th to 75th percentile, the orange band covers 10th to 90th percentile and the green band covers 1st to 99th percentile.
-The first facet represents the weekday behavior while the second one displays the weekend behavior and energy consumption across each hours of the day is shown inside each facet.
-The energy consumption is extremely (positive- or right-) skewed with the 1st, 10th and 25th percentile lying relatively close whereas 75th, 90th and 99th lying further away from each other.
-This is common across both weekdays and weekends.
-For the first few hours on weekdays, median energy consumption starts and continues to be higher for longer as compared to weekends.
-
-Consider looking at violin plots instead of quantile plots to look at the same data in \autoref{fig:bothcust}(c).
-There is additional information that we can derive looking at the distribution.
-There is bimodality in the early hours of the day, implying both low and high energy consumption is probable in the early hours of the day both for weekdays and weekends.
-<!--Also the hours from 7 to 13 look most volatile.--> If we visualize the same data with reverse mapping of the cyclic granularities, then the natural tendency would be to compare weekend and weekday behavior within each hour and not across hours.
-For example in \autoref{fig:bothcust}(a), it can be seen that median energy consumption for the early morning hours is extremely high for weekdays compared to weekends.
-Also, outliers are more prominent in the latter part of the day.
-All of these indicate that looking at different distribution geometry or changing the mapping might shed lights on different aspect of the energy behavior for the same sample population.
-
-```{r bothcust, fig.cap = "Energy consumption of a single customer shown with different distribution displays, and granularity arrangements.
-Two granularities are used: hour of the day (I) and weekday/weekend (II).
-Plot (a) shows granularity I facetted by granularity II, and plots (b), (c) shows the converse mapping.
-Plot (a) makes a comparison of usage by workday within each hour of the day using side-by-side boxplots.
-Generally, on a work day there is more consumption early in the day.
-Plots (b) and (c) examine the temporal trend of consumption over the course of a day, separately for the type of day.
-Plot (b) uses an area quantile to put the emphasis on the time series, for example, the median consumption over time shows prolonged usage in the morning on weekdays.
-Plot (c) uses a violin plot to place emphasis on distributional differences across hours.
-It can be seen that the morning use on weekdays is bimodal, some work days there is low usage, which might indicate the person is working from home and also having a late start.", out.width="90%"}
-
-cust2_quantile <- smart_meter10 %>%
-  filter(customer_id %in% c(10017936)) %>%
-  prob_plot("wknd_wday",
-    "hour_day",
-    response = "general_supply_kwh",
-    plot_type = "quantile",
-    symmetric = TRUE,
-    quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)
-  ) +
-  scale_y_sqrt() +
-  #ggtitle(" (b) Area quantile plot faceted by weekend-weekday") +
-  ylab("electricity demand [KWh]") + xlab("hours of the day") + ggtitle("") + ylab("")+ 
-  theme_minimal()
-
-cust2_violin <- smart_meter10 %>%
-  filter(customer_id %in% c(10017936)) %>%
-  prob_plot("wknd_wday",
-    "hour_day",
-    response = "general_supply_kwh",
-    plot_type = "violin"
-  ) +
-  scale_y_sqrt()+
-  #ggtitle(" (c) Violin plot faceted by weekend-weekday") +
-  ylab("") + xlab("hours of the day") + ggtitle("") +
-  scale_x_discrete( breaks = seq(0, 23, 5))+ 
-  theme_minimal()
-
-cust2_box <- smart_meter10 %>%
-  filter(customer_id %in% c(10017936)) %>%
-  prob_plot("hour_day",
-    "wknd_wday",
-    response = "general_supply_kwh",
-    plot_type = "boxplot"
-  ) +
-  scale_y_sqrt() +
-  #ggtitle(" (a) Box plot faceted by hour-of-day") +
-  xlab("") +
-  ggtitle("") + ylab("") +
-  scale_x_discrete(labels = c('wday','wend')) +
-  ggplot2::theme(axis.text.x = element_text(size = 7))+ 
-  theme_minimal()
-
-#ggarrange(cust2_quantile, cust2_violin, nrow = 2)
-
-gg_fig <- ggarrange(cust2_box,
-          ggarrange(cust2_quantile, cust2_violin, nrow = 2, labels = c("b", "c")),
-          ncol = 2, labels = "a")
-          #label.y = "electricity demand [KWh]"\
-
-ggpubr::annotate_figure(gg_fig,
-                left = text_grob("electricity demand [KWh]",  rot = 90))
-```
-
-<!-- # ```{r cust-ridge, fig.cap ="Boxplot of energy consumption across hours of the day faceted by weekday/weekend for customer id: 10017936.
-The change in mapping of the cyclic granularities leads to easier comparison within weekdays and weekends for each hour.
-Median consumption till 6am is higher for weekends compared to weekdays although the quartiles look similar.
-Outliers appear more during the end of the day implying more uncertain behavior in latter hours of the day compared to early morning hours."} -->
-<!-- #  -->
-<!-- # smart_meter10 %>% -->
-<!-- #   filter(customer_id %in% c(10017936)) %>% -->
-<!-- #   prob_plot("hour_day", -->
-<!-- #     "wknd_wday", -->
-<!-- #     response = "general_supply_kwh", -->
-<!-- #     plot_type = "boxplot" -->
-<!-- #   ) + -->
-<!-- #   scale_y_sqrt() -->
-<!-- # ``` -->
-
-<!-- Now, we would like to see how these customers' behavior relate to the rest of the 50 households across these two measures -   -->
-
-<!-- - if energy distribution is skewed towards extreme? -->
-
-<!-- - if the weekend and weekday behavior are different for most of these households? -->
-
-If the data for all keys are visualized together, it might lead to Simpson's paradox, which occurs when one observation shows a particular behavior, but this behavior paradoxically becomes obscured by aggregation.
-For example in a particular neighborhood one household may have the least daily power consumption for a full week, yet still not be the household with the minimum weekly power consumption.
-This is an intuitive possibility, because heterogeneous `customer_id`'s with very different occupation or demographics will tend to have very different energy behavior and combining them together will somehow weaken any typical or extreme behavior.
-A strategy for analyzing multiple keys together could be to first group them basis time series or demographic features and then look at their energy behavior.
-This is beyond the scope of the current work.
-
-<!-- For the purpose of this paper, the smart meter data is filtered for two customers to illustrate kinds of insights that can be drawn after proceeding with the systematic exploration. -->
-
-<!-- For example, Figure \ref{fig:wknd-wday50} shows the quantile plot of energy consumption of a sample of 50 households.
-Quantiles for weekends and weekdays for these customers look exactly the same.
-It is not clear if the behaviors of most of these customers do not alter between weekdays and weekends or looking at all customers together balances out the behaviors.
-Consider another example in Figure \ref{fig:my-hd} showing the area quantile plots of 50 customers.
-The median is very close to the lower boundaries of all the other bands implying energy consumption for these households are left skewed.
-The pink band changes significantly in winter months (May - August) implying that much of the behavioral changes occur in the quartiles, that too in peak hours of the day.
-It is to be noted here that the the level of all quantiles increased too in winter months (increased energy usage in weather conditions), the interesting part is to notice that the relationship between bands other than quartile stayed same across seasons.
--->
-
-This case study shows systematic exploration of energy behavior for a household to gain exhaustive insights on periodic behavior of the households. 
-<!--First, it helps us to find the list of cyclic granularities to look at, then shrinks the number of possible visualizations by identifying harmonies, visualize a harmony pair and shows the effect of different distribution plots or reverse mapping.-->
-
-## T20 cricket data of Indian Premiere League {#sec:cricket}
-
-The method is not only restricted to temporal data, and can be generalized to many hierarchical granularities (with  continuous and uni-directional nature).
-We illustrate this with an application to the sport cricket.
-Although there is no conventional time component in cricket, each ball can be thought to represent an ordering from past to future with the game progressing forward with each ball.
-In the Twenty20 format, an over will consist of 6 balls (with some exceptions), an inning is restricted to a maximum of 20 overs, a match will consist of 2 innings and a season consists of several matches.
-Thus, similar to time, there is a hierarchy where ball is nested within overs, overs nested within innings and innings within matches.
-The idea of cyclic granularities can be likewise mapped to this hierarchy.
-Example granularites then include ball of the over, over of the inning and ball of the inning.
-Although most of these cyclic granularities are circular in design of the hierarchy, in application of the rules some granularities are aperiodic.
-For example, in most cases an over will consist of 6 balls with some exceptions like wide balls or when an inning finishes before the over finishes.
-Thus, the cyclic granularity ball-of-over will be circular in most cases and aperiodic in others.
-
-<!-- However, irrespective of the type of cyclic granularities, it can be interesting to visualize the distribution of a measured variable across these cyclic granularities to throw light on the periodic behavior of a non-temporal data set similar to any temporal data set.
--->
-
-The Indian Premier League (IPL) is a professional Twenty20 cricket league in India contested by eight teams representing eight different cities in India.
-The ball by ball data for IPL season 2008 to 2016 is fetched from [Kaggle](https://www.kaggle.com/josephgpinto/ipl-data-analysis/data).
-The `cricket` data set in the `gravitas` package summarizes the ball-by-ball data across overs and contains information for a sample of 214 matches spanning 9 seasons (2008 to 2016) such that each over has 6 balls, each inning has 20 overs and each match has 2 innings.
-This could be useful in a periodic world when we wish to compute any circular/quasi-circular granularity based on a hierarchy table which look like \autoref{tab:hierarchy-cric}.
-
-```{r hierarchy-cric}
-library(gravitas)
-library(tibble)
-hierarchy_model <- tibble::tibble(
-  `linear (G)` = c("over", "inning", "match", "season"),
-  `single-order-up cyclic (C)` = c("over-of-inning", "inning-of-match", "match-of-season", 1),
-  `period length/conversion operator (K)` = c(20, 2, "k(match, season)", 1)
-)
-knitr::kable(hierarchy_model,
-             format = "latex",
-             booktabs = TRUE,
-             caption = "Hierarchy table for cricket where overs are nested within an inning, innings nested within a match and matches within a season.") %>%
-  #row_spec(0, bold = TRUE)%>%
-  kable_styling()
-```
-
-However, even if the situation is not periodic and a similar hierarchy can not be formed, it can be interesting to visualize the distribution of a measured variable across relevant cyclic granularities to shed light on the aperiodic behavior of a non-temporal data set similar to aperiodic events like formal meetings, workshops, conferences, school semesters in a temporal set up.
-There are many interesting questions that could possibly be answered with such a data set irrespective of the type of cyclic granularities.
-<!--We will explore a few interesting questions and understand how the proposed approach in the paper can help answer some of the questions.-->
-
-<!-- the two teams have a single innings each, which is restricted to a maximum of 20 overs.
-Hence, in this format of cricket, a match will consist of 2 innings, an innings will consist of 20 overs, an over will consist of 6 balls with some exceptions.
--->
-
-<!-- ```{r hierarchy, echo=FALSE} -->
-<!-- hierarchy_model <- tibble::tibble(linear gran = c("ball", "over", "inning", "match"),  -->
-<!--                                   convert_fct = c(6, 20, 2, 1)) -->
-<!-- knitr::kable(hierarchy_model, caption = " A hierarchy table for T20 cricket") -->
-<!-- ``` -->
-
-<!-- Each team is given a two-and-a-half-minute "strategic timeout" during each innings; one must be taken by the bowling team between the ends of the 6th and 9th overs, and one by the batting team between the ends of the 13th and 16th overs.
--->
-
-<!-- Suppose, we are interested to see how the distribution of scores vary from the start to the end of the game. Let us brainstorm some of the questions that might help us comprehend that. -->
-
-<!-- a) What is the most common pattern for batting and bowling teams across balls, overs, innings and matches? Which are the teams which are typical and which are exceptions? -->
-
-<!-- How the scores per over vary across granularities/categorizations like innings of a match or matches of a season?
-Are these different for the winning teams in that season and the teams that couldn't qualify for the playoffs?
--->
-
-<!-- Is the outcome of the game dependent on who bats first? Do some teams have more chance to win if they are batting in the first innings? -->
-
-<!-- We will look at the ball by ball data for all batting teams.
-Since we want a periodic world, where each over consists of 6 balls and each match consists of two innings, we shall filter out the matches or overs for which that is not true.
-Also, we look at runs per over as that would have more variability compared to runs per ball and it be easier to observe the strategies of the winning team through that.
--->
-
-<!-- Making it short -->
-
-<!-- First, we look at the distribution of runs (measured variable) across over-of-inning (circular granularity) and match-of-season (aperiodic cyclic granularity) in \autoref{fig:seas-over-inning}.
-The distribution of runs per over has not significantly changed from 2008 to 2016.
-There is no clear pattern/trend that runs per over is increasing or decreasing across seasons.
-Hence, we work with subsets of seasons to answer some of the questions: -->
-
-First, it would be interesting to see if the distribution of total runs vary depending on if a team bats in the first or second innings.
-The Mumbai Indians (MI) and Chennai Super kings (CSK) <!--are considered one of the best teams in IPL with multiple winning titles and --> appeared in final playoffs from 2010 to 2015.
-We take their example in order to dive deeper into this question.
-<!--Circular granularities "over-of-inning" and "inning-of-match" can be computed using \ref{sec:circular-gran-def} with over as index of the tsibble.--> From Figure \ref{fig:cricex}(a), it can be observed that for the team batting in the first inning there is an upward trend of runs per over, while there is no clear upward trend in median and quartile deviation of runs for the teams batting in the second inning.
-This seem to indicate that players feel mounting pressure to score more runs as they approach towards the end of the first inning.
-Whereas teams batting in the second inning have a set target in mind and are not subjected to such mounting pressure and may adopt a more conservative strategy, to score runs.
-Thus winning teams like CSK and MI seem to employ different inning strategies when it comes to their batting order.
-
-<!-- Also longer and more distinct letter values in the second innings suggests that the variability is more in the second innings. -->
-<!-- - Q1: How their run rates vary depending on if they bat first or 2nd? Is there a chance that they are more likely to win if they bat first? -->
-
-<!-- - Q2: Which team is more consistent in their approach in terms of run rate across different overs of the innings? -->
-
-<!-- # ```{r seas-over-inning, fig.cap = "Quantile plot of runs per over across overs of different seasons. There is no pattern on increase or decrease of runs across overs for seasons."} -->
-<!-- #   cricket_tsibble_all %>%  -->
-<!-- #   prob_plot("over",  -->
-<!-- #             "season", -->
-<!-- #             hierarchy_model, -->
-<!-- #             response = "runs_per_over", -->
-<!-- #             plot_type = "quantile", -->
-<!-- #             quantile_prob = c(0.25, 0.5, 0.75),  -->
-<!-- #             symmetric = FALSE)  + -->
-<!-- #      theme( # remove the vertical grid lines -->
-<!-- #             panel.grid.major.x = element_blank() , -->
-<!-- #             # explicitly set the horizontal lines (or they will disappear too) -->
-<!-- #             panel.grid.major.y = element_blank()) + scale_x_discrete(breaks = seq(2008, 2016, 3)) -->
-<!-- # ``` -->
-
-Another interesting question could be: do runs per over decrease in the subsequent over if fielding (defending) was good in the previous over?
-For establishing the fielding quality, we apply an indicator function on dismissals (1 if there was at least one wicket in the previous over due to run out or catch, 0 otherwise).
-Runs in the current over is then the observation variable.
-<!--If a batsman is bowled out, it does not necessarily signify good fielding.
-So we only include number of catches and run out in an over as a measure of good fielding.
-Difference in runs across overs are likely to be negative if good fielding has an impact on the runs scored in the subsequent overs.
---> Dismissals in the previous over can lead to a batsman adopting a more defensive play style.
-Figure \ref{fig:cricex}(b) shows that no dismissals in the previous over leads to a higher median and quartile spread of runs per over as compared to the case when there has been at least one dismissal in the previous over.
-
-<!-- Difference in runs across over should be negative if good fielding has an impact on the runs scored in the subsequent overs.  -->
-
-<!-- fetching raw data since dot and fielding information not available in dismissal type not available in cricket data gravitas. Also `cricket` is aggregated across overs -->
-
-```{r cricex, fig.cap= "Runs per over shown with different distribution displays, and granularities.
-Plot (a) shows letter value plot across overs faceted by innings.
-For the team batting in the first innings there is an upward trend of runs per over, while there is no such pattern of runs for the teams batting in the second innings.
-Plot (b) shows quantile plot of runs per over across an indicator of wickets in previous over faceted by current over.
-This indicates that at least one wicket in the previous over leads to lower median run rate and quartile spread in the subsequent over.", warning = FALSE, message = FALSE, out.width = "90%"}
-
-library(tsibble)
-cricket_tsibble <- cricket %>%
-  mutate(data_index = row_number()) %>%
-  as_tsibble(index = data_index)
-
-hierarchy_model <- tibble::tibble(
-  units = c("index", "over", "inning", "match"),
-  convert_fct = c(1, 20, 2, 1)
-)
-
-cricket_tsibble %>%
-  filter(batting_team %in% c(
-    "Mumbai Indians",
-    "Chennai Super Kings"
-  )) %>%
-  mutate(inning = paste0("innings: ", inning)) %>%
-  prob_plot("inning",
-    "over",
-    response = "runs_per_over",
-    hierarchy_model,
-    plot_type = "lv"
-  ) +
-  scale_fill_brewer(palette = "Dark2") +
-  #ggtitle("(a) Runs per over across over faceted by inning") +
-  theme(legend.position = "right") +
-  ggtitle("a") +
-  ylab("runs per over") +
-  xlab("overs of the innings") +
-  theme(plot.title = element_text(face = "bold")) +
-  ggplot2::theme(
-       strip.text = ggplot2::element_text(
-        size = 10,
-         margin = ggplot2::margin(b=0, t=0)
-      )
-     ) +  theme_minimal() 
-#geom_smooth(aes( x = over,
-#                               y=runs_per_over), method = lm, #formula = y ~ splines::bs(x, 3), se = FALSE)
-
-library(tsibble)
-
-cricket_all <- read_csv("paper/data-raw/deliveries_all.csv")
-matches_all <- read_csv("paper/data-raw/matches_all.csv")
-
-cricket_season <- cricket_all %>% left_join(matches_all, by = c("match_id" = "id"))
-
-# cricket_per_over <- cricket_season %>%
-#   group_by(season,
-#            match_id,
-#            batting_team,
-#            bowling_team,
-#            inning,
-#            over) %>%
-#   summarise(runs_per_over = sum(total_runs),
-#             run_rate = sum(total_runs)/length(total_runs))
-#
-# cricket_tsibble_all <- cricket_per_over %>%
-#   ungroup() %>%
-#   mutate(data_index = row_number()) %>%
-#   as_tsibble(index = data_index)
-
-cricket_dot_field <- cricket_season %>%
-  mutate(
-    fielding_proxy = if_else(dismissal_kind %in%
-      c("caught", "caught and bowled"), 1, 0),
-    dot_ball_proxy = if_else(total_runs == 0, 1, 0),
-    wicket_proxy = if_else(is.na(dismissal_kind), 0, 1)
-  ) %>%
-  group_by(
-    season,
-    match_id,
-    batting_team,
-    bowling_team,
-    inning,
-    over
-  ) %>%
-  summarise(
-    runs_per_over = sum(total_runs),
-    run_rate = sum(total_runs)*6 / length(total_runs),
-    fielding_wckts = sum(fielding_proxy),
-    dot_balls = sum(dot_ball_proxy)
-  ) %>%
-  mutate(diff_run_rate = c(0, diff(run_rate)))
-
-cricket_tsibble <- cricket_dot_field %>%
-  ungroup() %>%
-  mutate(data_index = row_number()) %>%
-  as_tsibble(index = data_index)
-
-cricket_data <- cricket_tsibble %>%
-  mutate(
-    field = if_else(fielding_wckts == 0, "0", "1+"),
-    dot = if_else(dot_balls == 0, "no dot balls", ">0 dot balls"),
-    lag_field = lag(field),
-    lag_dot = lag(dot)
-  ) %>%
-  filter(lag_field != 0, lag_dot != 0)
-
-cricket_data$lag_field <- factor(cricket_data$field, levels = c("0", "1+"))
-
-# filter(fielding_wckts %in% c(0,1)) %>%
-#
- cricket_data %>%
-  filter(over!=1) %>%
-  prob_plot("over", "lag_field",
-  hierarchy_model,
-  response = "run_rate",
-  plot_type = "quantile",
-  symmetric = FALSE,
- quantile_prob = c(0.25, 0.5, 0.75)) +
-   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") +
-  ylab("runs per over")  +
-  xlab("number of wickets in previous over") +
-  ggtitle("b") +
-   theme(plot.title = element_text(face = "bold")) +
-        theme(axis.ticks = element_blank(), legend.background = element_blank(),
-            legend.key = element_blank(), panel.background = element_blank(), strip.background = element_blank(),
-            plot.background = element_blank(), complete = TRUE, panel.grid.major = element_line(colour = "#E0E0E0"),
-            panel.border = element_rect(colour = "#E0E0E0", fill = NA))
-```
-
-<!-- Q2: Among good fielding and bowling - which affect the runs of the subsequent overs more? -->
-
-<!-- Q3: Are runs set to reduce in the next over for dot balls in the previous over? -->
-
-<!-- A dot ball is a delivery bowled without any runs scored off it.
-The number of dot balls is reflective of the quality of bowling in the game.
-Run rate of an over should ideally decrease if the number of dot balls increase.
-However, what is the effect of dot balls on runs scored in the subsequent over.
-Will players batsman likely to go for big shots because they couldn't score good runs in the previous over?
-Or they should play consistently and avoid scoring high?
-Figure \ref{fig:exdot} shows the quantile plot of runs across overs for at least one dot ball per over (facet 1) or no dot balls per over (facet 2).
--->
-<!-- With at least one dot balls per over, the distribution of run rates in facet 1 increase slower compared to that in facet 2.
-This implies that run rates are likely to decrease in the subsequent over as a result of dot balls in the previous over.
--->
-
-<!-- ```{r exdot, fig.cap="25th, 50th, 75th quantiles of runs per over are drawn across overs of the innings with no (facet 2), more than zero (facet 1) dot balls per over.
-For all quantiles, run rates mostly increase at a higher rate in facet 2 compared to facet 1 implying run rates decrease with at least one dot ball in the previous over.", fig.pos="ht"} -->
-
-<!-- cricket_data %>% -->
-<!--   # filter(dot_balls %in% c(0, 1, 2)) %>% -->
-<!--   prob_plot("lag_dot", -->
-<!--     "over", -->
-<!--     hierarchy_model, -->
-<!--     response = "run_rate", -->
-<!--     plot_type = "quantile", -->
-<!--     quantile_prob = c(0.25, 0.5, 0.75), -->
-<!--     symmetric = FALSE -->
-<!--   ) + ggtitle("") -->
-<!-- ``` -->
-
-Wickets per over are considered as an aperiodic cyclic granularity with wickets as an aperiodic linear granularity.
-These granularities do not appear in the hierarchy table since it is difficult to position them in a hierarchy.
-These are similar to holidays or special events in temporal data.
-<!-- CONTENT CUT -->
-<!--While any special event that corresponds to a time domain can be treated as an aperiodic linear granularity in a temporal case, dot balls or wickets that corresponds to certain balls (index) could be treated as aperiodic events in cricket.-->
-
-# Discussion points and future work
-
-Exploratory data analysis involve many iterations of finding and summarizing patterns.
-With temporal data available at ever finer scales, exploring periodicity has become overwhelming with so many possible granularities to explore.
-This work refines the selection of appropriate pairs of granularities by identifying those for which the differences between the displayed distributions is greatest, and rating these selected harmony pairs in order of importance for exploration.
-
-A future direction of work could be to look at more individuals/subjects and group them according to similar periodic behavior.
-Behaviors across different cyclic granularities would be different for different subjects and one way to find groups would be to actually locate clusters who have similar periodic behavior.
-
-<!-- patterns are interesting and others are not.
-The subjects for which behaviors across a group of cyclic granularities are similar, could be grouped together as their periodic behavior is similar.
-to group subjects  -->
-
-# Appendix
-
-## Null distribution
-
-### Size: Simulated same distribution for all combinations of categories for all harmony pairs.
-
-Failure to reject the null hypothesis when there is in fact no significant effect.
-
-### Normalised maximum distances follow standard Gumbel distribution
-
-### Limiting distribution of median of normalised maximum distances is normal
-
-Let a continuous population be given with cdf F(x) (cumulative distribution function) and median $\xi$ (assumed to exist uniquely).
-For a sample of size $2n + 1$, let $\tilde{x}$ denote the sample median.
-The distribution of $\tilde{x}$,under certain conditions, to be asymptotically normal with mean $\xi$ and variance $\sigma_n^2 = \frac{1}{4} [f(\xi)]^2(2n + 1)$, where $f(x) = F'(x)$ is the pdf (probability density function).
-
-<!-- ### Confidence interval of test statistic -->
-
-## Power
-
-## Confidence interval
-
-Failure to reject the null hypothesis when there is in fact a significant effect.
-
-To estimate the sampling distribution of the test statistic we need many samples generated under the null hypothesis.
-If the null hypothesis is true, changing the exposure would have no effect on the outcome.
-By randomly shuffling the exposures we can make up as many data sets as we like.
-If the null hypothesis is true the shuffled data sets should look like the real data, otherwise they should look different from the
-real data. The ranking of the real test statistic among the shuffled test statistics gives a p-value.
-
-<!-- Consider two cyclic granularities $A$ and $B$ with $2$ and $3$categories.
-Thus, the harmony table consisting of all possible harmony pairs (assuming all pairs are harmonies), would look like the following: -->
-
-```{r harmony_min}
-# harmonies <- tibble::tibble(facet_variable = c("A", "B", "A", "C", "B", "C"),
-#                             x_variable  = c("B","A", "C", "A", "C", "B"),
-#                             facet_levels = c(2, 3, 2, 4, 3, 4),
-#                             x_levels = c(3, 2, 4, 2, 4, 3))
-# 
-# harmonies <- tibble::tibble(facet_variable = c("A", "B"),
-#                             x_variable  = c("B","A"),
-#                             facet_levels = c(2, 3),
-#                             x_levels = c(3, 2))
-#                             
-# harmonies %>% knitr::kable()
-```
-
-<!-- The output table has the value of MMPD (normalized median maximum pairwise distances), gt_MMPD(global threshold of MMPD indicator). -->
-
-<!-- # ```{r samenull_2by4, eval = FALSE} -->
-<!-- #  -->
-<!-- # ``` -->
-
-<!-- # ```{r normalv21_power} -->
-<!-- #  -->
-<!-- # ``` -->
-<!-- #  -->
-<!-- #  -->
-<!-- # ```{r normalv22_power} -->
-<!-- #  -->
-<!-- # ``` -->
-
-### Varying distribution across facet
-### Varying distribution across x-axis
-### Varying distribution across both facets and x-axis
-### Repeat all with varying facet and x-axis levels
-
-<!-- ### Power: Simulated same distribution for all combinations of categories for all harmony pairs. -->
-
-<!-- # ```{r normalv23_power} -->
-<!-- #  -->
-<!-- # ``` -->
-<!-- #  -->
-<!-- #  -->
-<!-- # ```{r normalv24_power} -->
-<!-- #  -->
-<!-- # ``` -->
-
-*Conclusion*: The test should reject the null hypothesis if distributions are different.
-
-<!-- ### Scenario 2: Simulated different distributions for all combinations of categories for harmony pairs for few levels. -->
-
-<!-- ```{r diffnull_2by4, eval = FALSE} -->
-
-<!-- ``` -->
-
-<!-- *Conclusion*: The test select the harmony pair for which distribution of x-axis categories are significantly different -->
-
-<!-- ### Scenario 3: Simulated different distributions for all combinations of categories for all harmony pairs with many levels. -->
-
-<!-- ```{r diffnull_7by11, eval = FALSE} -->
-<!-- ``` -->
-
-<!-- *Conclusion*: The test indicates that both harmony pairs do not have significant variation. -->
-
-<!-- ### Scenario 4: Simulated different distributions for all combinations of categories for all harmony pairs with many levels - very different distribution across x-axis -->
-
-<!-- ```{r diffnull_7by11normal, eval = FALSE} -->
-<!-- ``` -->
-
-<!-- *Conclusion*: The test indicates that only the first harmony pair has significant variation. -->
-
-<!-- ### Scenario 5: Simulated different distributions for all combinations of categories for all harmony pairs with many levels - very different distribution across facets -->
-
-<!-- ```{r diffnull_7by11normal2, eval = FALSE} -->
-<!-- ``` -->
-
-<!-- *Conclusion*:  -->
-
-<!-- ## Scenario 4: Cumulative 3 levels with 2, 7 and 11 and testing level and power -->
-
-<!-- ```{r samenull_3levels} -->
-
-<!-- ``` -->
-
-<!-- *Conclusion*: With 3 levels the test incorrectly chooses 1 harmony pair with similar distribution. The harmony pair which is displayed. -->
-
-<!-- <!-- ```{r diffnull_3levels} -->
-
-<!-- <!-- ``` -->
-
-<!-- *Conclusion*: The test with MMPD selects just one pair, as opposed to the test with maximum.
-This needs to be checked against what we expect from the test.
-The harmony pairs which are selected (either through MMPD or maximum) are displayed.
--->
-
-<!-- # ```{r} -->
-<!-- # harmonies <- tibble::tibble(facet_variable = c("A", "B"),x_variable  = c("B","A"), facet_levels = c(2, 3),x_levels = c(3, 2)) -->
-<!-- #  -->
-<!-- # har1 <- harmonies[1,] -->
-<!-- #  -->
-<!-- # sim_dist1 = c(rep(distributional::dist_normal(mu = 10, sigma = 5),2),rep(distributional::dist_exponential(10),2), rep(distributional::dist_weibull(0.5, 2),2)) -->
-<!-- #  -->
-<!-- # data1 <- sim_distharmony1(har1, sim_dist = sim_dist1) -->
-<!-- # data1 -->
-<!-- #  -->
-<!-- # data1 %>% unnest(sim_dist) %>% -->
-<!-- #   ggplot(aes(x = Var2, y = sim_dist)) + -->
-<!-- #   facet_wrap(~Var1) + geom_boxplot() + ggtitle("Same distribution 2 by 3") -->
-<!-- #  -->
-<!-- # response = "sim_dist" -->
-<!-- #  -->
-<!-- # MMPD_distribution <- data1 %>% -->
-<!-- #   select(-dist) %>%  -->
-<!-- #   unnest(sim_dist) %>%  -->
-<!-- #   list() %>%  -->
-<!-- #   global_threshold(harmony_tbl = har1, -->
-<!-- #                    response = "sim_dist", -->
-<!-- #                    dist_distribution = "normal", -->
-<!-- #                    dist_ordered = TRUE, -->
-<!-- #                    create_gran_data = FALSE, nsamp = 20) -->
-<!-- #  -->
-<!-- # # as_tibble(sample_MMPD) %>% mutate(id = row_number()) %>%  -->
-<!-- # #   ggplot() + geom_histogram(aes(x = value)) -->
-<!-- #  -->
-<!-- # ``` -->
-<!-- #  -->
-
-<!-- # Visualisation -->
-
-<!-- Leader plots like in Scagnostics paper -->

### 2020-12-18 simulations/norm/null_design_quantrans/R-agg/makegraph02.R

@@ -7,46 +7,43 @@ library(tidyverse)
 
 
 makegraph02 <- function(folder_name){
-  
-all_data <- read_rds(paste0("simulations/raw/null_design_quantrans/data-agg/all_data_", folder_name, ".rds"))
+all_data <- read_rds(paste0("simulations/null_design/data/all_data_", folder_name, ".rds"))
   
 
-nxbyfacet_density <- all_data %>% 
+nxbyfacet <- all_data %>% 
   ggplot(aes(x = value)) + 
   geom_density(fill = "blue") +
   facet_grid(nx~nfacet,
              labeller = "label_both") + 
-  xlab("wpd")
+  xlab(" norm wpd")
 
-ggsave(nxbyfacet_density, filename = paste0("simulations/raw/null_design_quantrans/figs/", "nxbyfacet_density_", folder_name,".png"))
+ggsave(nxbyfacet, filename = paste0("simulations/null_design/figs/normalised/", "density_nx_by_nfacet_", folder_name,".png"))
 
 
-nxbyfacet_ridge <- all_data %>% 
+ norm_nxbyfacet <- all_data %>% 
   ggplot(aes(x = value, y = as.factor(nx))) +
   ggridges::geom_density_ridges() +
   facet_wrap(~nfacet, labeller = "label_both", nrow = 2) + 
-  xlab("mmpd") +
+  xlab(" norm mmpd") +
   ylab("nx")
 
-ggsave(nxbyfacet_ridge, filename = paste0("simulations/raw/null_design_quantrans/figs/", "nxbyfacet_ridge_", folder_name,".png"))
+ggsave( norm_nxbyfacet, filename = paste0("simulations/null_design/figs/normalised/", "ridge_by_nfacet_", folder_name,".png"))
 
 
-nfacetbynx_ridge <- all_data %>% 
+ norm_nfacetbynx <- all_data %>% 
   ggplot(aes(x = value, y = as.factor(nfacet))) +
   ggridges::geom_density_ridges() +
   facet_wrap(~nx, labeller = "label_both", nrow = 2) + 
-  xlab("mmpd") +
+  xlab(" norm mmpd") +
   ylab("nfacet")
 
-ggsave(nfacetbynx_ridge, filename = paste0("simulations/raw/null_design_quantrans/figs/", "nfacetbynx_ridge_", folder_name,".png"))
[…]

### 2020-12-20 vary_distribution.Rmd
update norm folder

@@
 ```
+# How mean and sd changes with increasing x-axis and facet levels?
+
+```{r mean-sd-ns-nfacet, fig.cap="Movement of mean and sd for raw wpd is shown for different number of levels (nlevel) of x-axis and facets through line plots.
+Mean increases and sd decreases more sharply for increasing x-axis levels as compared to facet levels.
+It seems like both mean and standard deviation are affected more by change in the x-axis levels than the facet levels."}
+knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/mean_sd_nx_nfacet.png"))
+```
 
@@
 ```
+
+# Normalise by dividing log(number of distances)
+
+```{r normalise-n01, fig.cap="Density plots of raw wpd is shown for N(0,1) distribution after dividing max by log(number of distances).
+The densities are reduced to zero and varies.
+So this normalisation approach is not efficient.
+The raw wpd values are already very low and then dividing them by logarithm of a large number brings it back to zero."}
+
+knitr::include_graphics(here::here("simulations/norm/null_design_quantrans/figs/nxbyfacet_density_wpd_N01.png"))
+```
+
+# How to design the alternate designs when distributions are actually different?

### 2020-12-22 results_simulation.Rmd
sim results update

---
title: "Update on simulation results and queries"
author: "Sayani Gupta"
preamble: >
  \usepackage{mathtools,booktabs,amsthm,todonotes,colortbl}
  \usepackage{float}
  \def\mod{~\text{mod}~}
  \newtheorem{definition}{Definition}
  \usepackage{mathptmx}
  \usepackage{caption}
  \usepackage{algorithm}
  \usepackage{algorithmicx}
  \usepackage{algpseudocode}
  \DeclareCaptionStyle{italic}{labelfont={bf},textfont={it},labelsep=colon}
  \captionsetup[figure]{style=italic,format=hang,singlelinecheck=true}
  \captionsetup[table]{style=italic,format=hang,singlelinecheck=true}
  \def\novspacing{\setlength{\aboverulesep}{0pt}\setlength{\belowrulesep}{0pt}}
  \def\vspacing{\setlength{\aboverulesep}{0.4ex}\setlength{\belowrulesep}{0.65ex}}
output:
  bookdown::pdf_book:
    #base_format: rticles::asa_article
    fig_height: 5
    fig_width: 8
    fig_caption: yes
    dev: "pdf"
---

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Designs

$D_{null}$  (No difference in distribution)  
$D_{var_f}$ (Difference in distribution only across facets)  
$D_{var_x}$ (Difference in distribution only across x-axis)  
$D_{var_{all}}$ (Difference in distribution in both facets and x-axis)

# Recap of last week

## What worked?

We saw the effect on raw wpd for different choices of tuning parameter ($\lambda$) and effect of different increments ($\omega$). We saw that raw wpd has least values for null design $D_{null}$  and gradually increase with more deviation from the null case with maximum for $D_{var_{all}}$  (which was great). Values of $\lambda$ for which $D_{var_x}$ and $D_{var_f}$
interact is $0.5$ (nice as that's what we were expecting). Moreover, the raw wpd values increase with increasing  $\lambda$ for $D_{var_x}$ and decrease with increasing  $\lambda$ for $D_{var_f}$ (as expected since the measure is linearly related to $\lambda$.)

## What  didn't work?

Though the distribution of wpd remains the same with normal distribution with different means just by scaling the data as a preprossing step. The same doesn't happen for a Gamma distribution where the location of the distribution changes with different locations of the Gamma distribution. Box-cox transformations on the raw data did not work. It was suggested that we try out quantile transformation to bring back the quantiles of the raw data to standard normal.

# Results from this week

## What worked?

- Preprocess data: quantile  transformation of the data to standard normal.

[Sort the sample $x_{(1)}, x_{(2)}, \dots, x_{(n)}$. Estimate the cumulative probabilities for each point
$p_{(1)}, p_{(2)}, \dots, p_{(n)}$ such that $p_{(i)} = P(X< x_{(i)})$. Transform each observation $x_{(i)}$ into observation $y_{(i)} = \Phi^{-1}(p_{(i)})$, where $\Phi^{-1}$ is the inverse of the cumulative distribution of a standard normal distribution.]

(** All of this is being done by the R function `qqnorm`. I checked that data from different distribution ($z$) could be transformed to normal using `qqnorm(z)$x`. Please let me know if you think I am missing anything here**)

- check if the distribution of the raw wpd starting from a Gamma (0,5, 1) and Gamma(2, 1) distribution looks similar to the distribution of the raw wpd starting from a N(0,1) distribution.
(More or less it does, yippee. (**Please let me know if you think I am missing anything here
\autoref{fig:gamma-diff},
\autoref{fig:gamma-diff-trans}**)

- how mean and sd of the distribution of raw wpd changes with increasing x-axis and facet categories - more understanding of which normalisation process to choose. (\autoref{fig:mean-sd-ns-nfacet})

- Now that quantile transformation has worked, we wanted to check which process of normalization works. Suppose $\{d_1, d_2, \dots, d_D\}$ are the JS distances from a panel

a) $wpd_{norm1} = wpd/log(D)$

b) $wpd_{norm2} = wpd - mean(wpd^*)/sd(wpd^*)$, where $wpd^*$ 's are obtained by shuffling the data. The distribution of $wpd_{norm2}$ is expected to have similar mean and sd for different x-axis and facet categories.

Appoach a) did not work. But Approach b) is working. (**Please let me know if you think I am missing something in my conclusions by looking at 
\autoref{fig:normal01-norm},
\autoref{fig:gamma01-norm},
\autoref{fig:gamma21-norm}
**)

## To do now?

### Alternate designs
Behavior of $wpd_{norm2}$ under different designs need to be monitored. Designs need to be constructed such that there is no **confounding factors** while deciding how distribution of $wpd_{norm2}$ changes with different x-axis and facet categories.

- $$\mu_{j.} = \mu + j\omega$$
(for design vary_x)
- $$\mu_{.k} = \mu + k\omega$$
(for design vary_f)

If the designs are like the above, it would mean that mean and sd of the panels would also increase when x-axis and facet categories increase.

One way to keep mean comparable across situations would be to do the following (as discussed last with Di)
Suppose we will allow a highest mean difference of $M$ unit for each panels, which means panels with different x-axis and facet categories would also have a highest mean difference of $M$ units.

For example, if $M=5$ and design = $D_{var_x}$ then $$\mu_{j.} = \mu + j\omega$$

- $\omega$ = 5, for $nx = 2$
- $\omega$ = 5/2, for $nx = 3$
- $\omega$ = 5/3, for $nx = 4$ and so on.

**Should we be bothered about it or not since we are pre-processing the data to start with?**

### Structuring the simulation section of the paper

Follow the story line like this one?
**Or you suggest some other ways?**

# Detail results:

**Assumptions:** There is no difference in distribution between any facet or x-category since it is the null design.
Process is run $nsim$ times to plot the distribution.
$nsim = 200$ 
$\lambda = 0.67$

**Questions:** 
- How raw value of wpd changes with different nx and nfacet for different location and scale of a Normal and non-normal distribution

## Standard normal distribution

```{r normal, fig.cap="Density plots of raw wpd is shown for N(0,1) distribution. The densities change across different facet and x levels, which implies wpd value changes with increasing x and facet levels."}

knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/nxbyfacet_density_wpd_N01.png"))
```

<!-- ## Location and scale of the distribution under null design -->

<!-- **Objective:** 1. Behavior of wpd under different null designs N(0,1), N(5, 1), Gamma(0.5,1), Gamma(2,1) for different nx and nfacets.  -->

## How mean and sd changes with increasing x-axis and facet levels?

```{r mean-sd-ns-nfacet, fig.cap="Movement of mean and sd for raw wpd is shown for different number of levels (nlevel) of x-axis and facets through line plots. Mean increases and sd decreases more sharply for increasing x-axis levels as compared to facet levels. It seems like both mean and standard deviation are affected more by change in the x-axis levels than the facet levels.", fig.pos="h"}
knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/mean_sd_nx_nfacet.png"))

```

## Normal distributions with different means

```{r normal-diff, fig.cap="Ridge plots of raw wpd is shown for N(0,1), N(0,5)  and N(5,1) distribution. The densities change across different facet and x levels but look same for the three normal distributions, which implies wpd value is unaffected by the change in mean value of the normal distribution.", fig.pos="h"}
knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_normal.png"))
```

## Gamma Distribution with different locations before quantile transformation

```{r gamma-diff, fig.cap="Ridge plots of raw wpd is shown for G(0.5,1) and G(2,1) distribution (before quantile transformation). The densities change across different facet and x levels and also for the two distributions, which implies wpd value is affected by the change in location value when distributions are not normal.", fig.pos="h"}
knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/extra/gamma_ridge_nxbynfacet.png"))
```

## Gamma Distribution with different locations after quantile transformation

```{r gamma-diff-trans, fig.cap="Ridge plots of raw wpd is shown for G(0.5,1) and G(2,1) distribution after quantile transformation looks similar and hence is unaffected by change in location.", fig.pos="h"}
knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_gamma.png"))
```

<!-- ## Normalise by dividing log(number of distances) -->

<!-- ```{r normalise-n01, fig.cap="Density plots of raw wpd is shown for N(0,1) distribution after dividing max by log(number of distances). The densities are reduced to zero and varies. So this normalisation approach is not efficient. The raw wpd values are already very low and then dividing them by logarithm of a large number brings it back to zero."} -->

<!-- knitr::include_graphics(here::here("simulations/norm/null_design_quantrans/figs/nxbyfacet_density_wpd_N01.png")) -->
<!-- ``` -->

<!--  The densities are reduced to zero and varies. So this normalisation approach is not efficient. The raw wpd values are already very low and then dividing them by logarithm of a large number brings it back to zero -->

## Normalise by permuting data

```{r gamma21-norm, fig.cap="Density plots of normalised wpd is shown for Gamma(2,1) distribution. The mean and sd of the distribution looks almost similar for different facet and x-axis categories", fig.pos="h"}

knitr::include_graphics("simulations/norm/null_design_quantrans_nperm/figs/nxbyfacet_density_wpd_Gamma21.png")
```

```{r gamma01-norm, fig.cap="Density plots of normalised wpd is shown for Gamma(0.5,1) distribution, which is more skewed. The mean and sd of the distribution looks almost similar for different facet and x-axis categories", fig.pos="h"}

knitr::include_graphics("simulations/norm/null_design_quantrans_nperm/figs/nxbyfacet_density_wpd_Gamma01.png")
```

```{r normal01-norm, fig.cap="Density plots of normalised wpd is shown for Normal(0,1) distribution. The mean and sd of the distribution looks almost similar for different facet and x-axis categories.", fig.pos="h"}

knitr::include_graphics("simulations/norm/null_design_quantrans_nperm/figs/nxbyfacet_density_wpd_N01.png")

# How to design the alternate designs when distributions are actually different?

### 2020-12-23 results_simulation.Rmd
minor change

@@
 knitr::include_graphics("simulations/norm/null_design_quantrans_nperm/figs/nxbyfacet_density_wpd_N01.png")
-
+```
 # How to design the alternate designs when distributions are actually different?

### 2021-01-04 results_simulation.Rmd
adding norm  wpd for other non-standard normal distribution

--- 2020-12-22 results_simulation.Rmd
@@
 knitr::include_graphics("simulations/norm/null_design_quantrans_nperm/figs/nxbyfacet_density_wpd_N01.png")
+```
+
+```{r normal05-norm, fig.cap="Density plots of normalised wpd is shown for Normal(0,5) distribution.
+The mean and sd of the distribution looks almost similar for different facet and x-axis categories.", fig.pos="h"}
+
+knitr::include_graphics("simulations/norm/null_design_quantrans_nperm/figs/nxbyfacet_density_wpd_N05.png")
+```
+
+```{r normal51-norm, fig.cap="Density plots of normalised wpd is shown for Normal(5,1) distribution.
+The mean and sd of the distribution looks almost similar for different facet and x-axis categories.", fig.pos="h"}
+
+knitr::include_graphics("simulations/norm/null_design_quantrans_nperm/figs/nxbyfacet_density_wpd_N51.png")
+```
+
+```{r normal55-norm, fig.cap="Density plots of normalised wpd is shown for Normal(5,5) distribution.
+The mean and sd of the distribution looks almost similar for different facet and x-axis categories.", fig.pos="h"}
+
+knitr::include_graphics("simulations/norm/null_design_quantrans_nperm/figs/nxbyfacet_density_wpd_N55.png")
+```
 

### 2021-01-04 extra/for_norm_G21.R

@@ -10,7 +10,7 @@ library(hakear)
 library(parallel)
 
 
-nsim = 200
+nsim = 2
 # change path while running it on HPC
 simtable<-read_csv(here::here('simulations/null/sim_table.csv'))
 #simtable<-read_csv('sim_table.csv')

### 2021-01-10 paper/main.Rmd
null distribution update

@@
 Consider two cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.
-Let the pairwise distances between pairs $(a_{j} b_{k}, a_{j'}, b_{k})$ be denoted as $d_{(jk, j'k')} = JSD(a_{j}b_{k}, a_{j'}b_{k'})$.
+Let the pairwise distances between pairs $(a_{j} b_{k}, a_{j'}b_{k'})$ b   e denoted as $d_{(jk, j'k')} = JSD(a_{j}b_{k}, a_{j'}b_{k'})$.
 Pairwise distances could be within-facets or between-facets.
@@
 
-We conduct simulations to understand the behavior of raw WPD for different parameters
-$l_x$ (levels of x-axis), $l_f$ (levels of facets), $\lambda$ (tuning parameter), $\omega$ (increment in each panel design) $data$ (data sets), $sample-size$ (tuning parameter), $nsim$ (number of simulations), $nperm$ (number of permutations (might not need depending on if norm works) and designs
+Most of the behavior was studied via simulation.
+The simulations explore how wpd performs under various simulations and its limitations.
+Numerous simulations were carried out in a wide range of scenarios.
+Same scenarios were used, when possible with normalized wpd, keeping all other simulation variables constant.
+
+The factors that are thought to potentially have some impact on wpd are as follows:
+
+- $nx$ (number of levels of x-axis)
+- $nfacet$ (number of levels of facets)
+- $\lambda$ (tuning parameter)
+- $\omega$ (increment in each panel design)
+- $dist$ (normal/non-normal distributions with different location and scale)
+- $n$ (sample size for each combination of categories)
+- $nsim$ (number of simulations)
+- $nperm$ (number of permutations of data)  
+- $designs$  
 $D_{null}$  (No difference in distribution)  
@@
 
-## Location and scale of the distribution under null design
-
-Null design only where all combinations are equal for fixed values of $\mu$ and $\sigma$
-Dist 1: $N(0,1)$ individual graph
-Dist 2: $N(\mu, 1)$ (faceted with different values of $\mu$: not yet just for one value now)
-Dist 3: $N(0, \sigma)$ (faceted with different values of $\sigma$: not yet just for one value now)
-Dist 4: $N(\mu, \sigma)$ faceted with different values of mu and sigma, for all levels of x and facet to see how value of wpd changes with that of change in parameters.
-
-**Objective:** 1. Behavior of wpd under different null designs N(0,1), N(5, 1), Gamma(0.5,1), Gamma(2,1) for different nx and nfacets. Here, we have to fix a value of lambda = 0.67.
-
-**Assumptions:** There is no difference in distribution between any facet or x-category
-nsim = 200
-lambda = 0.67
-
-**Questions:** 
-- How raw value of wpd changes with different nx and nfacet for different location and scale of a Normal and non-normal distribution
-
-### Normal Distribution
+```{r simtable, eval = FALSE}
+variable = c("nx", "nfacet", "lambda", "omega", "dist", "n", "nsim", "nperm", "design")
+
+description = c("number of levels of x-axis", "number of levels of facets",
+                "tuning parameter","increment in each panel design", "normal/non-normal distributions with different location and scale", "sample size", "number of simulations", "number of permutations of data",
+                "$D_{null}$ (No difference in distribution), $D_{var_f}$ (Difference in distribution only across facets), $D_{var_x}$ (Difference in distribution only across x-axis), $D_{var_all}$ (Difference in distribution in both facets and x-axis)")
+table = tibble::tibble(variable, description)
+
+table %>% 
+knitr::kable(format = "latex",
+             escape = TRUE) %>% 
+  kableExtra::kable_styling(
+    bootstrap_options = "striped", 
+    full_width = T, 
+    font_size = 7)
+
+```
+
+## Distribution of wpd under $D_{null}$
+
+In this section, the effect of all the factors are evaluated under the null design $D_{null}$, that is, there is no difference in distribution between any facet or x-category.
+It is further assumed that the values of the following factors are fixed to $nsim = 200$, $n = 500$, $\lambda = 0.67$ and $\omega = 0$, since there is no significant differences between distributions in the null case.
+
+### dist
+
+wpd is computed for different normal and non-normal distributions to see how the underlying distribution has a role to play in the value of wpd.
+Since we are concerned with detecting the differences in distributions, it would be ideal if wpd has minimal dependency on the type, location and scale of the  underlying distribution.
+To that end, some pre-processing of the data is preferred to bring it to the same scale, location and type.
+The Normal Score Transform or NQT has been applied in various fields of geo-statistics in order to make the mostly asymmetrical distributed real world measured variables more
+treatable and normal-like.
+
+Following the work of Krzysztofowicz (1997) the empirical NQT involves the following steps:
+1. Sort the sample of measured variable $X$ from the smallest to the largest observation $x_{(1)},\dots, x_{(i)}, .., x_{(n)}$.
+2. Estimate the cumulative probabilities $p_{(1)},\dots, p_{(i)}, .., p_{(n)}$.
+using a plotting position like $i/(n + 1)$ such that $p_{(i)} = P(X \leq x_{(i)})$.
+3. Transforming each observation $x_(i)$ of $X$ into observation $y(i) = Q^{-1}(p(i))$ of the standard normal variate $Y$ , with $Q$ denoting the standard normal distribution and
+$Q^{-1}$ its inverse, applying discrete mapping.
+
+wpd is computed with the initial distribution set as N(0,1), N(5, 1), N(0,5), G(0.5, 1) and G(2, 1).
+
+<!-- Null design only where all combinations are equal for fixed values of $\mu$ and $\sigma$ -->
+<!-- Dist 1: $N(0,1)$ individual graph -->
+<!-- Dist 2: $N(\mu, 1)$ (faceted with different values of $\mu$: not yet just for one value now) -->
+<!-- Dist 3: $N(0, \sigma)$ (faceted with different values of $\sigma$: not yet just for one value now) -->
+<!-- Dist 4: $N(\mu, \sigma)$ faceted with different values of mu and sigma, for all levels of x and facet to see how value of wpd changes with that of change in parameters. -->
+
+**Objective:** 1. Study the behavior of wpd under different initial distributions for different $nx$ and $nfacet$.
+<!-- **Assumptions:** There is no difference in distribution between any facet or x-category -->
+<!-- nsim = 200 -->
+<!-- lambda = 0.67 -->
+
+<!-- **Questions:**  -->
+<!-- - How raw value of wpd changes with different nx and nfacet for different location and scale of a Normal and non-normal distribution -->
+
+Figure \ref{fig:normal-3diff} shows distribution of wpd for N(0,1), N(5,1) and N(0,5) distribution to see the effect of changing location and scale on the distribution of wpd.
+It seems like the  distribution changes across different facet and x levels but look same for different  normal distributions, which implies wpd value is unaffected by the change is location and scale of the the normal distribution.
 
 ```{r normal-diff, fig.cap="Ridge plots of raw wpd is shown for N(0,1) and N(5,1) distribution.
-The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change is mean value of the normal distribution"}
+The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change is mean value of the normal distribution", eval = FALSE}
 knitr::include_graphics(here::here("simulations/null_design/figs/normal_ridge_nxbynfacet_wpd_N01.png"))
@@
 
+```{r normal-3diff, fig.cap="Ridge plots of raw wpd is shown for N(0,1), N(5,1) and N(0,5) distribution.
+The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change is mean value of the normal distribution", eval = FALSE}
+knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_normal.png"))
+```
+
+```{r mean-sd-ns-nfacet, fig.cap="Movement of mean and sd for raw wpd is shown for different number of levels (nlevel) of x-axis and facets through line plots.
+Mean increases and sd decreases more sharply for increasing x-axis levels as compared to facet levels.
+It seems like both mean and standard deviation are affected more by change in the x-axis levels than the facet levels.", fig.pos="h"}
+knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/mean_sd_nx_nfacet.png"))
+
+```
+
 ### Gamma Distribution
@@
 ```{r gamma-diff, fig.cap="Ridge plots of raw wpd is shown for G(0.5,1) and G(2,1) distribution.
-The densities change across different facet and x levels and also for the two distributions, which implies wpd value is affected by the change in location value when distributions are not normal."}
+The densities change across different facet and x levels and also for the two distributions, which implies wpd value is affected by the change in location value when distributions are not normal.", eval = FALSE}
 knitr::include_graphics(here::here("simulations/null_design/figs/gamma_ridge_nxbynfacet.png"))
@@
 ```{r tuning-one-omega, fig.caption = "WPD from two designs are plotted for different values of lambda for different x and facet categories.
-For omega = 1, the designs intersect for 0.6<lamba<=0.75, whereas for higher omega, design intersects at lambda = 0.5"}
+For omega = 1, the designs intersect for 0.6<lamba<=0.75, whereas for higher omega, design intersects at lambda = 0.5", eval = FALSE}
 knitr::include_graphics(here::here("simulations/tuning_param/figs/fixed_omega.png"))
@@
 
-```{r tuning-parameter-intersection}
+```{r tuning-parameter-intersection, eval = FALSE}
 knitr::include_graphics(here::here("simulations/tuning_param/figs/intersection_plot.png"))
@@
 
-```{r lambda-omega-mean}
+```{r lambda-omega-mean, eval = FALSE}
 knitr::include_graphics(here::here("simulations/result_report/lambda_omega_mean_3_2.png"))
@@
 
-```{r lambda-omega-sd}
+```{r lambda-omega-sd, eval = FALSE}
 knitr::include_graphics(here::here("simulations/result_report/lambda_omega_sd_3_2.png"))
@@
 
-```{r}
+```{r, eval = FALSE}
 knitr::include_graphics(here::here("simulations/null_design/figs/normalised","gamma_ridge_nxbynfacet.png"))

### 2021-01-12 paper/main.Rmd
adding vary_x raw results

@@
 
-## Distribution of wpd under $D_{null}$
+## Distribution of wpd
+
+### $D_{null}$
+
+**Objective:**  Study the behavior of wpd under different initial distributions for different $nx$ and $nfacet$
 
@@
 It is further assumed that the values of the following factors are fixed to $nsim = 200$, $n = 500$, $\lambda = 0.67$ and $\omega = 0$, since there is no significant differences between distributions in the null case.
-
-### dist
 
@@
 To that end, some pre-processing of the data is preferred to bring it to the same scale, location and type.
-The Normal Score Transform or NQT has been applied in various fields of geo-statistics in order to make the mostly asymmetrical distributed real world measured variables more
+The Normal Score Transform or NQT has been applied in various fields of geo-statistics in order to make most asymmetrical distributed real world measured variables more
 treatable and normal-like.
@@
 
-**Objective:** 1. Study the behavior of wpd under different initial distributions for different $nx$ and $nfacet$.
 <!-- **Assumptions:** There is no difference in distribution between any facet or x-category -->
@@
 Figure \ref{fig:normal-3diff} shows distribution of wpd for N(0,1), N(5,1) and N(0,5) distribution to see the effect of changing location and scale on the distribution of wpd.
-It seems like the  distribution changes across different facet and x levels but look same for different  normal distributions, which implies wpd value is unaffected by the change is location and scale of the the normal distribution.
+It seems like the  distribution changes across different facet and x levels but look same for different  normal distributions, which implies wpd value is unaffected by the change in location and scale of the the normal distribution.
+
+Figure \ref{fig:mean-sd-ns-nfacet} shows how mean and sd of the distribution of wpd changes with the increasing x and facet levels.
+It seems like both mean and standard deviation are affected more by change in the x-axis levels than the facet levels.
 
@@
 
-### Gamma Distribution
-
 ```{r gamma-diff, fig.cap="Ridge plots of raw wpd is shown for G(0.5,1) and G(2,1) distribution.
@@
 knitr::include_graphics(here::here("simulations/null_design/figs/gamma_ridge_nxbynfacet.png"))
+```
+
+```{r gamma-diff-trans, fig.cap="Ridge plots of raw wpd is shown for G(0.5,1) and G(2,1) distribution after quantile transformation looks similar and hence is unaffected by change in location.", fig.pos="h"}
+knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_gamma.png"))
 ```
@@
 
-## Choice of tuning parameters and effect of different increments
-
-Objective: Choice of optimal tuning parameter $lambda$ with the help of two alternate designs (vary_x and vary_f)  for different nx and nfacets.
-The lambda for which the two designs intersect have to be chosen to put appropriate weights for within-facet and between-facet distances.
+### Alternate designs
+
+Objective: Study the effect of different tuning parameters $\lambda$ and $\omega$     with the help of two alternate designs ($vary_x$ and $vary_f$) for different $nx$ and $nfacet$.
+The $\lambda$ for which the two designs intersect will then be chosen as the optimal $\lambda$ that could then be weighed appropriately to up-weigh the within-facet distances and down-weigh the between-facet distances.
+Figure \ref{fig:tuning-one-omega} are plotted for different values of $\lambda$ for a relatively small and higher $\omega$.
+Designs mostly intersect at $\lambda = 0.5$ for the higher value of $\lambda$.
+Figure \ref{fig:tuning-parameter-intersection} shows how the value of lambda changes with increasing omega.
 
@@
 ```{r tuning-one-omega, fig.caption = "WPD from two designs are plotted for different values of lambda for different x and facet categories.
-For omega = 1, the designs intersect for 0.6<lamba<=0.75, whereas for higher omega, design intersects at lambda = 0.5", eval = FALSE}
+For omega = 1, the designs intersect for 0.6<lamba<=0.75, whereas for higher omega, design intersects at lambda = 0.5"}
 knitr::include_graphics(here::here("simulations/tuning_param/figs/fixed_omega.png"))
@@
 
-How value of lambda changes with increasing omega
-
-```{r tuning-parameter-intersection, eval = FALSE}
+```{r tuning-parameter-intersection, fig.cap="For most panels it is observed that the most common values for which the "}
 knitr::include_graphics(here::here("simulations/tuning_param/figs/intersection_plot.png"))
@@
 ```
-
-## Alternate designs
 

### 2021-01-12 simulations/vary_all/norm/R-agg/makegraph02.R

@@ -1,0 +1,159 @@
+library(here)
+library(readr)
+library(tidyverse)
+# run for  norm MMPD files aggregation
+#all_data <- read_rds("simulations/result_report/all_data_ norm.rds")
+# run for  norm max pairwise distances files aggregation
+
+
+makegraph02 <- function(folder_name){
+  
+all_data <- read_rds(paste0("simulations/raw/null_design_quantrans/data-agg/all_data_", folder_name, ".rds"))
+  
+
+nxbyfacet_density <- all_data %>% 
+  ggplot(aes(x = value)) + 
+  geom_density(fill = "blue") +
+  facet_grid(nx~nfacet,
+             labeller = "label_both") + 
+  xlab("wpd") +
+  scale_x_continuous(breaks = scales::breaks_extended(3))
+
+ggsave(nxbyfacet_density, filename = paste0("simulations/raw/null_design_quantrans/figs/", "nxbyfacet_density_", folder_name,".png"))
+
+
+nxbyfacet_ridge <- all_data %>% 
+  ggplot(aes(x = value, y = as.factor(nx))) +
+  ggridges::geom_density_ridges() +
+  facet_wrap(~nfacet, labeller = "label_both", nrow = 2) + 
+  xlab("mmpd") +
+  ylab("nx") +
+  scale_x_continuous(breaks = scales::breaks_extended(4))
+
+ggsave(nxbyfacet_ridge, filename = paste0("simulations/raw/null_design_quantrans/figs/", "nxbyfacet_ridge_", folder_name,".png"))
+
+
+nfacetbynx_ridge <- all_data %>% 
+  ggplot(aes(x = value, y = as.factor(nfacet))) +
+  ggridges::geom_density_ridges() +
+  facet_wrap(~nx, labeller = "label_both", nrow = 2) + 
+  xlab("mmpd") +
+  ylab("nfacet") +
+  scale_x_continuous(breaks = scales::breaks_extended(4))
+
+ggsave(nfacetbynx_ridge, filename = paste0("simulations/raw/null_design_quantrans/figs/", "nfacetbynx_ridge_", folder_name,".png"))
+}
+
+makegraph02(folder_name = "wpd_N01")
+makegraph02(folder_name = "wpd_N05")
+makegraph02(folder_name = "wpd_N51")
+makegraph02(folder_name = "wpd_N55")
+
+
+
+
+# N(0,1) and N(5,1) together as they will go in the paper
+
+normal_0_1 <- aggregate01(folder_name = "wpd_N01")
[…]

### 2021-01-12 simulations/vary_all/norm/R-ind/raw_pairwise_Gamma01.R

@@ -1,0 +1,76 @@
+#This script calculates raw mmpd for each simulation scenario
+##Read Simulation Table
+
+.libPaths(c("~/R/libs", .libPaths()))
+library(distributional)
+library(readr)
+library(drake)
+library(tidyverse)
+library(hakear)
+
+set.seed(9999)
+
+nsim = 200
+# change path while running it on HPC
+# simtable<-read_csv(here::here('simulations/null/sim_table.csv'))
+
+simtable<-read_csv('../sim_table.csv')
+
+### Extract flags from simulation scenario
+
+#scen<- 2 #If running within R uncomment this.  This will only run first scenario
+scen<-as.numeric(commandArgs()[[6]]) # If running batch job uncomment this
+
+simj<-simtable[scen,] #Extract row of table
+nfacetj<-simj$nfacet # Which nfacet level
+nxj<-simj$nx #Which nx level
+wj <- simj$w
+
+#create data for each row for null normal
+
+sim_varx_normal = function(nx, 
+                           nfacet, 
+                           shape = 0.5, 
+                           rate = 1,
+                           w)
+{
+  rep(dist_normal((shape + seq(0, nx-1, by  = 1)*w), rate), nfacet)
+}
+
+sim_panel_data = 
+  hakear::sim_panel(nx = nxj,
+                    nfacet = nfacetj, 
+                    ntimes = 500, 
+                    sim_dist = sim_varx_normal(nx = nxj, nfacet = nfacetj, w = wj)) %>% 
+  unnest(c(data)) %>% ungroup() %>% 
+  bind_cols(w = wj)
+
+set.seed(1111)
+
+raw_dist <- map(seq_len(nsim), function(i)
+{
+  new_sim_data = sample(sim_panel_data$sim_data, 
+                        size = nrow(sim_panel_data))
+  new_data = sim_panel_data %>% 
+    select(-sim_data) %>% 
+    mutate(sim_data = new_sim_data)
+  
+  # for creating one raw mmpd
+  raw_mmpd = compute_pairwise_max(new_data, 
+                                  gran_x = "id_x",
+                                  gran_facet = "id_facet",
+                                  response = sim_data) %>% 
+    as_tibble() %>% mutate(perm_id = i)
+  
+}) %>% bind_rows()
+
+
+if(!dir.exists("simulations/vary_x/null_design_quantrans/data-ind/wpd_Gamma01"))
+{
[…]

### 2021-01-12 simulations/vary_all/raw/R-ind/raw_pairwise_Gamma21.R

@@ -1,0 +1,76 @@
+#This script calculates raw mmpd for each simulation scenario
+##Read Simulation Table
+
+.libPaths(c("~/R/libs", .libPaths()))
+library(distributional)
+library(readr)
+library(drake)
+library(tidyverse)
+library(hakear)
+
+set.seed(9999)
+
+nsim = 200
+# change path while running it on HPC
+# simtable<-read_csv(here::here('simulations/null/sim_table.csv'))
+
+simtable<-read_csv('../sim_table.csv')
+
+### Extract flags from simulation scenario
+
+#scen<- 2 #If running within R uncomment this.  This will only run first scenario
+scen<-as.numeric(commandArgs()[[6]]) # If running batch job uncomment this
+
+simj<-simtable[scen,] #Extract row of table
+nfacetj<-simj$nfacet # Which nfacet level
+nxj<-simj$nx #Which nx level
+wj <- simj$w
+
+#create data for each row for null normal
+
+sim_varf = function(nx, 
+                    nfacet,
+                    mean = 0, 
+                    sd = 1,
+                    w)
+{
+  rep(dist_gamma((mean + seq(0, nfacet-1, by  = 1)*w), sd), each = nx)
+}
+
+sim_panel_data = 
+  hakear::sim_panel(nx = nxj,
+                    nfacet = nfacetj, 
+                    ntimes = 500, 
+                    sim_dist = sim_varf(nx = nxj, nfacet = nfacetj, w = wj)) %>% 
+  unnest(c(data)) %>% ungroup() %>% 
+  bind_cols(w = wj)
+
+set.seed(1111)
+
+raw_dist <- map(seq_len(nsim), function(i)
+{
+  new_sim_data = sample(sim_panel_data$sim_data, 
+                        size = nrow(sim_panel_data))
+  new_data = sim_panel_data %>% 
+    select(-sim_data) %>% 
+    mutate(sim_data = new_sim_data)
+  
+  # for creating one raw mmpd
+  raw_mmpd = compute_pairwise_max(new_data, 
+                                  gran_x = "id_x",
+                                  gran_facet = "id_facet",
+                                  response = sim_data) %>% 
+    as_tibble() %>% mutate(perm_id = i)
+  
+}) %>% bind_rows()
+
+
+if(!dir.exists("simulations/vary_facet/raw/data-ind/wpd_Gamma21"))
+{
[…]

### 2021-01-12 simulations/vary_facet/norm/R-ind/raw_pairwise_Gamma21.R

@@ -1,0 +1,76 @@
+#This script calculates raw mmpd for each simulation scenario
+##Read Simulation Table
+
+.libPaths(c("~/R/libs", .libPaths()))
+library(distributional)
+library(readr)
+library(drake)
+library(tidyverse)
+library(hakear)
+
+set.seed(9999)
+
+nsim = 200
+# change path while running it on HPC
+# simtable<-read_csv(here::here('simulations/null/sim_table.csv'))
+
+simtable<-read_csv('../sim_table.csv')
+
+### Extract flags from simulation scenario
+
+#scen<- 2 #If running within R uncomment this.  This will only run first scenario
+scen<-as.numeric(commandArgs()[[6]]) # If running batch job uncomment this
+
+simj<-simtable[scen,] #Extract row of table
+nfacetj<-simj$nfacet # Which nfacet level
+nxj<-simj$nx #Which nx level
+wj <- simj$w
+
+#create data for each row for null normal
+
+sim_varx_normal = function(nx, 
+                           nfacet, 
+                           shape = 2, 
+                           rate = 1,
+                           w)
+{
+  rep(dist_normal((shape + seq(0, nx-1, by  = 1)*w), rate), nfacet)
+}
+
+sim_panel_data = 
+  hakear::sim_panel(nx = nxj,
+                    nfacet = nfacetj, 
+                    ntimes = 500, 
+                    sim_dist = sim_varx_normal(nx = nxj, nfacet = nfacetj, w = wj)) %>% 
+  unnest(c(data)) %>% ungroup() %>% 
+  bind_cols(w = wj)
+
+set.seed(1111)
+
+raw_dist <- map(seq_len(nsim), function(i)
+{
+  new_sim_data = sample(sim_panel_data$sim_data, 
+                        size = nrow(sim_panel_data))
+  new_data = sim_panel_data %>% 
+    select(-sim_data) %>% 
+    mutate(sim_data = new_sim_data)
+  
+  # for creating one raw mmpd
+  raw_mmpd = compute_pairwise_max(new_data, 
+                                  gran_x = "id_x",
+                                  gran_facet = "id_facet",
+                                  response = sim_data) %>% 
+    as_tibble() %>% mutate(perm_id = i)
+  
+}) %>% bind_rows()
+
+
+if(!dir.exists("simulations/vary_x/null_design_quantrans/data-ind/wpd_Gamma01"))
+{
[…]

### 2021-01-12 simulations/vary_facet/norm/R-ind/raw_pairwise_N51.R

@@ -1,0 +1,76 @@
+#This script calculates raw mmpd for each simulation scenario
+##Read Simulation Table
+
+.libPaths(c("~/R/libs", .libPaths()))
+library(distributional)
+library(readr)
+library(drake)
+library(tidyverse)
+library(hakear)
+
+set.seed(9999)
+
+nsim = 200
+# change path while running it on HPC
+# simtable<-read_csv(here::here('simulations/null/sim_table.csv'))
+
+simtable<-read_csv('../sim_table.csv')
+
+### Extract flags from simulation scenario
+
+#scen<- 2 #If running within R uncomment this.  This will only run first scenario
+scen<-as.numeric(commandArgs()[[6]]) # If running batch job uncomment this
+
+simj<-simtable[scen,] #Extract row of table
+nfacetj<-simj$nfacet # Which nfacet level
+nxj<-simj$nx #Which nx level
+wj <- simj$w
+
+#create data for each row for null normal
+
+sim_varx_normal = function(nx, 
+                           nfacet, 
+                           mean = 5, 
+                           sd = 1,
+                           w)
+{
+  rep(dist_normal((mean + seq(0, nx-1, by  = 1)*w), sd), nfacet)
+}
+
+sim_panel_data = 
+  hakear::sim_panel(nx = nxj,
+                    nfacet = nfacetj, 
+                    ntimes = 500, 
+                    sim_dist = sim_varx_normal(nx = nxj, nfacet = nfacetj, w = wj)) %>% 
+  unnest(c(data)) %>% ungroup() %>% 
+  bind_cols(w = wj)
+
+set.seed(1111)
+
+raw_dist <- map(seq_len(nsim), function(i)
+{
+  new_sim_data = sample(sim_panel_data$sim_data, 
+                        size = nrow(sim_panel_data))
+  new_data = sim_panel_data %>% 
+    select(-sim_data) %>% 
+    mutate(sim_data = new_sim_data)
+  
+  # for creating one raw mmpd
+  raw_mmpd = compute_pairwise_max(new_data, 
+                                  gran_x = "id_x",
+                                  gran_facet = "id_facet",
+                                  response = sim_data) %>% 
+    as_tibble() %>% mutate(perm_id = i)
+  
+}) %>% bind_rows()
+
+
+if(!dir.exists("simulations/vary_x/null_design_quantrans/data-ind/wpd_N51"))
+{
[…]

### 2021-01-12 simulations/vary_facet/raw/R-ind/raw_pairwise_N51.R

@@ -1,0 +1,76 @@
+#This script calculates raw mmpd for each simulation scenario
+##Read Simulation Table
+
+.libPaths(c("~/R/libs", .libPaths()))
+library(distributional)
+library(readr)
+library(drake)
+library(tidyverse)
+library(hakear)
+
+set.seed(9999)
+
+nsim = 200
+# change path while running it on HPC
+# simtable<-read_csv(here::here('simulations/null/sim_table.csv'))
+
+simtable<-read_csv('../sim_table.csv')
+
+### Extract flags from simulation scenario
+
+#scen<- 2 #If running within R uncomment this.  This will only run first scenario
+scen<-as.numeric(commandArgs()[[6]]) # If running batch job uncomment this
+
+simj<-simtable[scen,] #Extract row of table
+nfacetj<-simj$nfacet # Which nfacet level
+nxj<-simj$nx #Which nx level
+wj <- simj$w
+
+#create data for each row for null normal
+
+sim_varf = function(nx, 
+                    nfacet,
+                    mean = 5, 
+                    sd = 1,
+                    w)
+{
+  rep(dist_normal((mean + seq(0, nfacet-1, by  = 1)*w), sd), each = nx)
+}
+
+sim_panel_data = 
+  hakear::sim_panel(nx = nxj,
+                    nfacet = nfacetj, 
+                    ntimes = 500, 
+                    sim_dist = sim_varf(nx = nxj, nfacet = nfacetj, w = wj)) %>% 
+  unnest(c(data)) %>% ungroup() %>% 
+  bind_cols(w = wj)
+
+set.seed(1111)
+
+raw_dist <- map(seq_len(nsim), function(i)
+{
+  new_sim_data = sample(sim_panel_data$sim_data, 
+                        size = nrow(sim_panel_data))
+  new_data = sim_panel_data %>% 
+    select(-sim_data) %>% 
+    mutate(sim_data = new_sim_data)
+  
+  # for creating one raw mmpd
+  raw_mmpd = compute_pairwise_max(new_data, 
+                                  gran_x = "id_x",
+                                  gran_facet = "id_facet",
+                                  response = sim_data) %>% 
+    as_tibble() %>% mutate(perm_id = i)
+  
+}) %>% bind_rows()
+
+
+if(!dir.exists("simulations/vary_facet/raw/data-ind/wpd_N51"))
+{
[…]

### 2021-01-12 simulations/vary_x/null_design_quantrans/R-agg/aggregate01.R

@@ -1,0 +1,56 @@
+# contains function to aggregate data each for from N(0,1), N(0,5), N(5,1), N(5,5), Gamma(0.5, 1), Gamma(2, 1)
+#  aggregated data from the file simulations/results/norm/folder_name and tidy them up
+library(tidyverse)
+library(here)
+library(readr)
+library(rlang)
+
+aggregate01 <-  function(folder_name){
+  
+all_files = list.files(path = paste0("simulations/vary_x/null_design_quantrans/data-ind/", folder_name), 
+                       pattern = ".rds")
+
+names_levels <- map_dfr(all_files, 
+                        function(x){
+                          z = str_split(str_remove(x, "_dist.rds"), "_") %>% 
+                            unlist()
+                          bind_cols(nx = as.numeric(z[1]),
+                                    nfacet = as.numeric(z[2]))
+                        })
+
+# len_file = read_rds(("simulations/results/norm/tuning_param/2_2_tuning_param.rds"))
+# 
+# names_rep <- names_levels %>% slice(rep(1:n(), each = nrow(len_file)))
+
+  
+all_files_path <- paste0("simulations/vary_x/null_design_quantrans/data-ind/",folder_name,"/",
+         all_files)  
+  
+
+all_data <- lapply(1:length(all_files_path), function(x){
+    
+  data = all_files_path %>% magrittr::extract2(x) %>% 
+    readRDS()
+  
+  names = names_levels %>% magrittr::extract(x,)
+  names_rep =   names %>% slice(rep(1:n(), each = nrow(data)))
+  bind_cols(names_rep, data)
+  }) %>% bind_rows() %>% 
+    arrange(nfacet, nx)
+    
+write_rds(all_data, paste0("simulations/vary_x/null_design_quantrans/data-agg/all_data_", folder_name, ".rds"))
+}
+
+
+# use functions for all folders
+
+aggregate01(folder_name = "wpd_N01")
+aggregate01(folder_name = "wpd_N05")
+aggregate01(folder_name = "wpd_N51")
+aggregate01(folder_name = "wpd_N55")
+
+
+aggregate01(folder_name = "wpd_Gamma01")
+aggregate01(folder_name = "wpd_Gamma21")
+
+

### 2021-01-12 simulations/vary_x/null_design_quantrans/R-ind/raw_pairwise_Gamma01.R

@@ -1,0 +1,76 @@
+#This script calculates raw mmpd for each simulation scenario
+##Read Simulation Table
+
+.libPaths(c("~/R/libs", .libPaths()))
+library(distributional)
+library(readr)
+library(drake)
+library(tidyverse)
+library(hakear)
+
+set.seed(9999)
+
+nsim = 200
+# change path while running it on HPC
+# simtable<-read_csv(here::here('simulations/null/sim_table.csv'))
+
+simtable<-read_csv('../sim_table.csv')
+
+### Extract flags from simulation scenario
+
+#scen<- 2 #If running within R uncomment this.  This will only run first scenario
+scen<-as.numeric(commandArgs()[[6]]) # If running batch job uncomment this
+
+simj<-simtable[scen,] #Extract row of table
+nfacetj<-simj$nfacet # Which nfacet level
+nxj<-simj$nx #Which nx level
+wj <- simj$w
+
+#create data for each row for null normal
+
+sim_varf = function(nx, 
+                    nfacet,
+                    shape = 0.5, 
+                    rate = 1,
+                    w)
+{
+  rep(dist_gamma((shape + seq(0, nfacet-1, by  = 1)*w), rate), each = nx)
+}
+
+sim_panel_data = 
+  hakear::sim_panel(nx = nxj,
+                    nfacet = nfacetj, 
+                    ntimes = 500, 
+                    sim_dist = sim_varf(nx = nxj, nfacet = nfacetj, w = wj)) %>% 
+  unnest(c(data)) %>% ungroup() %>% 
+  bind_cols(w = wj)
+
+set.seed(1111)
+
+raw_dist <- map(seq_len(nsim), function(i)
+{
+  new_sim_data = sample(sim_panel_data$sim_data, 
+                        size = nrow(sim_panel_data))
+  new_data = sim_panel_data %>% 
+    select(-sim_data) %>% 
+    mutate(sim_data = new_sim_data)
+  
+  # for creating one raw mmpd
+  raw_mmpd = compute_pairwise_max(new_data, 
+                                  gran_x = "id_x",
+                                  gran_facet = "id_facet",
+                                  response = sim_data) %>% 
+    as_tibble() %>% mutate(perm_id = i)
+  
+}) %>% bind_rows()
+
+
+if(!dir.exists("simulations/vary_facet/raw/data-ind/wpd_Gamma01"))
+{
[…]

### 2021-01-12 simulations/vary_x/null_design_quantrans/R-ind/raw_pairwise_N01.R

@@ -1,0 +1,81 @@
+#This script calculates raw mmpd for each simulation scenario
+##Read Simulation Table
+
+.libPaths(c("~/R/libs", .libPaths()))
+library(distributional)
+library(readr)
+library(drake)
+library(tidyverse)
+library(hakear)
+
+set.seed(9999)
+
+nsim = 200
+# change path while running it on HPC
+# simtable<-read_csv(here::here('simulations/null/sim_table.csv'))
+
+simtable<-read_csv('../sim_table.csv')
+
+### Extract flags from simulation scenario
+
+#scen<- 2 #If running within R uncomment this.  This will only run first scenario
+scen<-as.numeric(commandArgs()[[6]]) # If running batch job uncomment this
+
+simj<-simtable[scen,] #Extract row of table
+nfacetj<-simj$nfacet # Which nfacet level
+nxj<-simj$nx #Which nx level
+wj <- simj$w
+
+#create data for each row for null normal
+
+sim_null_normal = function(nxj, nfacetj){
+  rep(distributional::dist_normal(0, 1), 
+      times = nxj*nfacetj)
+}
+
+sim_varx_normal = function(nx, 
+                           nfacet, 
+                           mean = 0, 
+                           sd = 1,
+                           w)
+{
+  rep(dist_normal((mean + seq(0, nx-1, by  = 1)*w), sd), nfacet)
+}
+
+sim_panel_data = 
+  hakear::sim_panel(nx = nxj,
+                    nfacet = nfacetj, 
+                    ntimes = 500, 
+                    sim_dist = sim_varx_normal(nx = nxj, nfacet = nfacetj, w = wj)) %>% 
+  unnest(c(data)) %>% ungroup() %>% 
+  bind_cols(w = wj)
+
+set.seed(1111)
+
+  raw_dist <- map(seq_len(nsim), function(i)
+{
+  new_sim_data = sample(sim_panel_data$sim_data, 
+                        size = nrow(sim_panel_data))
+  new_data = sim_panel_data %>% 
+    select(-sim_data) %>% 
+    mutate(sim_data = new_sim_data)
+  
+  # for creating one raw mmpd
+  raw_mmpd = compute_pairwise_max(new_data, 
+                                 gran_x = "id_x",
+                                 gran_facet = "id_facet",
+                                 response = sim_data) %>% 
+    as_tibble() %>% mutate(perm_id = i)
+  
[…]

### 2021-01-12 paper/main.Rmd
improvise simulations writeup

@@
 
-## Simulation study
-
-Most of the behavior was studied via simulation.
-The simulations explore how wpd performs under various simulations and its limitations.
-Numerous simulations were carried out in a wide range of scenarios.
-Same scenarios were used, when possible with normalized wpd, keeping all other simulation variables constant.
-
-The factors that are thought to potentially have some impact on wpd are as follows:
+Most of the behavior of the measure wpd was studied via simulation.
+The simulations explore how wpd performs under various designs and parameters and its limitations.
+To study the behavior of wpd, simulations were carried out for four different designs and the following factors that could potentially have an impact on the values of wpd:
+
+<!-- Numerous simulations were carried out in a wide range of scenarios. -->
+
+<!-- Same scenarios were used, when possible with normalized wpd, keeping all other simulation variables constant. -->
 
@@
     bootstrap_options = "striped", 
-    full_width = T, 
+    full_width = F, 
     font_size = 7)
@@
 
-## Distribution of wpd
-
-### $D_{null}$
-
-**Objective:**  Study the behavior of wpd under different initial distributions for different $nx$ and $nfacet$
-
-In this section, the effect of all the factors are evaluated under the null design $D_{null}$, that is, there is no difference in distribution between any facet or x-category.
-It is further assumed that the values of the following factors are fixed to $nsim = 200$, $n = 500$, $\lambda = 0.67$ and $\omega = 0$, since there is no significant differences between distributions in the null case.
-
-wpd is computed for different normal and non-normal distributions to see how the underlying distribution has a role to play in the value of wpd.
-Since we are concerned with detecting the differences in distributions, it would be ideal if wpd has minimal dependency on the type, location and scale of the  underlying distribution.
+## Null design $D_{null}$
+
+This section explores the behavior of wpd in designs where there is no difference in distribution between x and facet categories.
+We have considered different initial distributions to study the impact of initial distribution under the null setup.
+Since the measure wpd is essentially set up to detect differences in distributions irrespective of underlying distribution, it would be ideal if it has minimal dependency on the type, location and scale of the initial distribution.
 To that end, some pre-processing of the data is preferred to bring it to the same scale, location and type.
@@
 
-wpd is computed with the initial distribution set as N(0,1), N(5, 1), N(0,5), G(0.5, 1) and G(2, 1).
+Further, we want to study the distribution of wpd for different $nx$ and $nfacet$.
+
+### Simulation set up
+
+<!-- Study the behavior of wpd under different initial distributions for different $nx$ and $nfacet$ -->
+
+Using two types of distributions, viz.
+normal and gamma (non-normal), we generated observations for each combination of $nx$ and $nfacet$ from the following sets: $nx = \{2, 3, 5, 7, 14, 20, 31, 50\}$ and $nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
+Each combination is being referred to as a _panel_.
+That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$.
+For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
+That is, if we consider the panel  $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
+The values of $\lambda$ is set to $0.67$, since we want to up-weigh the within-facet distances and that of $\omega$ is set to $0$, since there is no significant differences between distributions in the null case.
+Observations were generated for each type of distribution changing the shape and scale to study the effect of shape, scale and type of distribution on wpd.
+The set of distributions considered for this purpose is ${N(0,1), N(5, 1), N(0,5), \Gamma(0.5, 1), \Gamma(2, 1)}$.
+Each of the scenario is run $nsim = 200$ times to see the distribution of wpd values for each scenario.
+
+<!-- wpd is computed for different normal and non-normal distributions to see how the underlying distribution has a role to play in the value of wpd.
+Since we are concerned with detecting the differences in distributions, it would be ideal if wpd has minimal dependency on the type, location and scale of the  underlying distribution.
+To that end, some pre-processing of the data is preferred to bring it to the same scale, location and type.
+-->
 
@@
 
-Figure \ref{fig:normal-3diff} shows distribution of wpd for N(0,1), N(5,1) and N(0,5) distribution to see the effect of changing location and scale on the distribution of wpd.
-It seems like the  distribution changes across different facet and x levels but look same for different  normal distributions, which implies wpd value is unaffected by the change in location and scale of the the normal distribution.
-
+Figure \ref{fig:normal-diff-quantrans} and \ref{fig:gamma-diff-quantrans} show distribution of wpd for different initial normal and gamma distribution to study the effect of changing location and scale on the distribution of wpd.
+It seems like the  distribution changes across different facet and x levels but look the same for each panel, which implies wpd value is unaffected by the change in location and scale of the the normal distribution.
 Figure \ref{fig:mean-sd-ns-nfacet} shows how mean and sd of the distribution of wpd changes with the increasing x and facet levels.
 It seems like both mean and standard deviation are affected more by change in the x-axis levels than the facet levels.
-
-```{r normal-diff, fig.cap="Ridge plots of raw wpd is shown for N(0,1) and N(5,1) distribution.
-The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change is mean value of the normal distribution", eval = FALSE}
-knitr::include_graphics(here::here("simulations/null_design/figs/normal_ridge_nxbynfacet_wpd_N01.png"))
-```
-
-```{r normal-3diff, fig.cap="Ridge plots of raw wpd is shown for N(0,1), N(5,1) and N(0,5) distribution.
-The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change is mean value of the normal distribution", eval = FALSE}
+Figure \ref{fig:nxbyfacet-ridge-N05} gives another way to look at the effect of changing facet and x levels on the distribution of wpd for an initial distribution $N(0,5)$.
+Clearly, the location of the distribution shifts to the right for increasing x levels and scale is different for low and high values of facet levels with a longer left tail for lower facet levels.
+We have considered alternate distribution, location and scale for this simulation setting, but do not present the results as they are behaviorally similar.
+
+<!-- # ```{r normal-diff, fig.cap="Ridge plots of raw wpd is shown for N(0,1) and N(5,1) distribution.
+The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change in mean and standard deviation of the normal distribution", eval = FALSE} -->
+<!-- # knitr::include_graphics(here::here("simulations/null_design/figs/normal_ridge_nxbynfacet_wpd_N01.png")) -->
+<!-- # ``` -->
+
+```{r normal-diff-quantrans, fig.cap = "Ridge plots of raw wpd is shown for N(0,1), N(5,1) and N(0,5) distribution.
+The densities change across different facet and x levels but look same for each panel, which implies wpd value is unaffected by the change in mean and standard deviation of the normal distribution"}
 knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_normal.png"))
+```
+
+```{r gamma-diff-quantrans, fig.cap="Ridge plots of raw wpd is shown for Gamma(0.5,1), Gamma(2,1) distribution.
+The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change in the shape paramter of the gamma distribution"}
+knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_gamma.png"))
 ```
@@
 
+```
+
+```{r nxbyfacet-ridge-N05, fig.cap="Ridge plots of raw wpd is shown for N(0,5) distribution.
+For each panel, it could be seen that the location shifts to the right for increasing x levels.
+Across each panel, the scale of the distribution seems to change for low/moderately lower values and higher values of nfacets and left tails are longer for lower facet levels."}
+knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/nxbyfacet_ridge_wpd_N05.png"))
 ```

### 2021-01-12 paper/main.Rmd
improvise simulations writeup

@@
 
-Figure \ref{fig:normal-diff-quantrans} and \ref{fig:gamma-diff-quantrans} show distribution of wpd for different initial normal and gamma distribution to study the effect of changing location and scale on the distribution of wpd.
+Figure \ref{fig:normal-diff-quantrans} shows distribution of wpd for initial distribution N(0,1), N(5,1) and N(0,5) to study the effect of changing location and scale on the distribution of wpd.
 It seems like the  distribution changes across different facet and x levels but look the same for each panel, which implies wpd value is unaffected by the change in location and scale of the the normal distribution.
+
 Figure \ref{fig:mean-sd-ns-nfacet} shows how mean and sd of the distribution of wpd changes with the increasing x and facet levels.
 It seems like both mean and standard deviation are affected more by change in the x-axis levels than the facet levels.
-Figure \ref{fig:nxbyfacet-ridge-N05} gives another way to look at the effect of changing facet and x levels on the distribution of wpd for an initial distribution $N(0,5)$.
-Clearly, the location of the distribution shifts to the right for increasing x levels and scale is different for low and high values of facet levels with a longer left tail for lower facet levels.
-We have considered alternate distribution, location and scale for this simulation setting, but do not present the results as they are behaviorally similar.
-
-<!-- # ```{r normal-diff, fig.cap="Ridge plots of raw wpd is shown for N(0,1) and N(5,1) distribution.
-The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change in mean and standard deviation of the normal distribution", eval = FALSE} -->
-<!-- # knitr::include_graphics(here::here("simulations/null_design/figs/normal_ridge_nxbynfacet_wpd_N01.png")) -->
-<!-- # ``` -->
-
-```{r normal-diff-quantrans, fig.cap = "Ridge plots of raw wpd is shown for N(0,1), N(5,1) and N(0,5) distribution.
-The densities change across different facet and x levels but look same for each panel, which implies wpd value is unaffected by the change in mean and standard deviation of the normal distribution"}
+
+```{r normal-diff, fig.cap="Ridge plots of raw wpd is shown for N(0,1) and N(5,1) distribution.
+The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change is mean value of the normal distribution", eval = FALSE}
+knitr::include_graphics(here::here("simulations/null_design/figs/normal_ridge_nxbynfacet_wpd_N01.png"))
+```
+
+```{r normal-diff-quantrans, fig.cap="Ridge plots of raw wpd is shown for N(0,1), N(5,1) and N(0,5) distribution.
+The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change is mean value of the normal distribution"}
 knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_normal.png"))
-```
-
-```{r gamma-diff-quantrans, fig.cap="Ridge plots of raw wpd is shown for Gamma(0.5,1), Gamma(2,1) distribution.
-The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change in the shape paramter of the gamma distribution"}
-knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_gamma.png"))
 ```
@@
 
-```
-
-```{r nxbyfacet-ridge-N05, fig.cap="Ridge plots of raw wpd is shown for N(0,5) distribution.
-For each panel, it could be seen that the location shifts to the right for increasing x levels.
-Across each panel, the scale of the distribution seems to change for low/moderately lower values and higher values of nfacets and left tails are longer for lower facet levels."}
-knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/nxbyfacet_ridge_wpd_N05.png"))
 ```

### 2021-01-13 paper/main.Rmd
alternate design write up improvisation

--- 2021-01-12 paper/main.Rmd
@@
 
-### Definitions
+### Notations Definitions
 
@@
 
-## Null design $D_{null}$
+## Null design
 
@@
 
-### Simulation set up
+### Simulation setup
 
@@
 
-### Alternate designs
-
-Objective: Study the effect of different tuning parameters $\lambda$ and $\omega$     with the help of two alternate designs ($vary_x$ and $vary_f$) for different $nx$ and $nfacet$.
+## Alternate designs
+
+This section explores the behavior of wpd in designs where there is infact difference in distribution between facet categories ($D_{var_f}$) or across x-categories ($D_{var_x}$) or both ($D_{var_{all}}$).
+Since it is established in the last section that after preprocessing the data through NQT, the initial distribution does not have a role to play in the values of wpd, we proceed with a N(0,1) distribution only.
+Supposably, the tuning parameter ($\lambda$) and increment parameter ($\omega$) should impact the values of wpd.
+
+### Simulation setup
+
+Using $\omega =  \{1, 2, \dots, 10\}$ and $\lambda = seq(from  = 0.1, to = 0.9, by = 0.05)$, observations are drawn from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet =  \{2, 3, 5, 7, 14, 20, 31, 50\}$.
+$ntimes = 500$ is assumed for this setup as well.
+Furthermore, to generate different distributions across different combination of facet and x levels, the following method is deployed - suppose the distribution of the combination of first levels of x and facet category is $N(\mu,\sigma)$ and $\mu_{jk}$ denotes the mean of the combination $(a_jb_k)$, then $\mu_{j.} = \mu + j\omega$ (for design $D_{var_x}$) and $\mu_{.k} = \mu + k\omega$ (for design $D_{var_f}$).
+Table \ref{tab:explain-design} shows an example of how initial distributions are assigned in a panel with $nfacet = 3$ and $nx = 2$ for different designs using $\omega = 1$.
+
+```{r explain-design}
+sim_varx_normal = function(nx, nfacet, mean, sd, w)
+{
+  rep(dist_normal((mean + seq(0, nx-1, by  = 1)*w), sd), nfacet)
+}
+
+sim_varf_normal = function(nx, nfacet, mean, sd, w)
+{
+  rep(dist_normal((mean + seq(0, nfacet-1, by  = 1)*w), sd), each = nx)
+}
+  sim_varall_normal = function(nx, nfacet, mean, sd, w)
+  {
+    dist_normal((mean + seq(0, (nx*nfacet - 1), by  = 1)*w), sd)
+  }
+
+mean = 0
+sd = 1
+w = 1
+nx = 2
+nfacet = 3
+
+raw_levels = expand.grid(facet = c("$b_1$", "$b_2$", "$b_3$"),
+                         x = c("$a_1$", "$a_2$"))
+
+facet = rep(c("$b_1$", "$b_2$", "$b_3$"), each = nx)
+x =  rep(c("$a_1$", "$a_2$"), nfacet)
+
+vary_f <-  sim_varf_normal(nx, nfacet, mean, sd, w) %>% tibble()
+vary_x <-  sim_varx_normal(nx, nfacet, mean, sd, w) %>% tibble()
+vary_all <-  sim_varall_normal(nx, nfacet, mean, sd, w) %>% tibble()
+
+raw_table <- bind_cols(x = x, 
+                       facet = facet, 
+                       vary_f = vary_f, 
+                       vary_x = vary_x, 
+                       vary_all = vary_all) %>% 
+  tibble() 
+names(raw_table) = c("x", "facet", "$D_{var_f}$", "$D_{var_x}$", "$D_{var_{all}}$" )
+raw_table %>% 
+  kable(format = "latex",
+    booktabs = TRUE, 
+    escape = FALSE,
+    caption = "Simulation setup for a panel with 3 facet levels and 2 x-axis levels for different designs starting from an initial distribution N(0, 1) for the combination $(a_1, b_1)$.") %>% kable_styling()
+```
+
+<!--  - Exploring the effect of tuning parameter $\lambda$: -->
+
+We now discuss the effect of different tuning parameters $\lambda$ and $\omega$ with the help of two alternate designs ($D_{var_x}$ and $D_{var_f}$).
+Figure \ref{fig:tuning-one-omega} displays different values of $\lambda$ for a relatively small and higher $\omega$ for $nx = nfacet =  \{2, 3, 5, 7, 9\}$.
 The $\lambda$ for which the two designs intersect will then be chosen as the optimal $\lambda$ that could then be weighed appropriately to up-weigh the within-facet distances and down-weigh the between-facet distances.
-Figure \ref{fig:tuning-one-omega} are plotted for different values of $\lambda$ for a relatively small and higher $\omega$.
-Designs mostly intersect at $\lambda = 0.5$ for the higher value of $\lambda$.
-Figure \ref{fig:tuning-parameter-intersection} shows how the value of lambda changes with increasing omega.
-
-Assumptions: The initial combination has a $N(\mu,\sigma)$ distribution and then every combination increases as follows:
-- $$\mu_{j.} = \mu + j\omega$$ (for design vary_x)
-- $$\mu_{.k} = \mu + k\omega$$ (for design vary_f)
-Value of the parameters chosen for this simulation are $\mu = 0$, $\sigma = 1$ and $\omega = {1, 2, \dots, 10}$
-
-Fixing omega, where the design interacts
+The design $D_{var_x}$ increases linearly with increasing $\lambda$, whereas $D_{var_f}$ decreases linearly with increasing $\lambda$.
+This is expected as wpd has a linear relationship with $\lambda$ by construction.
+The two designs mostly intersect at $\lambda = 0.5$ for a higher value of $\omega$.
+\autoref{fig:tuning-parameter-intersection} shows how the value of $\lambda$ changes with increasing $\omega$ for $\omega =  \{1, 2, \dots, 10\}$ and $\lambda = seq(from  = 0.1, to = 0.9, by = 0.05)$.
+
+<!-- Assumptions: The initial combination has a $N(\mu,\sigma)$ distribution and then every combination increases as follows: -->
+<!-- - $$\mu_{j.} = \mu + j\omega$$ (for design vary_x) -->
+<!-- - $$\mu_{.k} = \mu + k\omega$$ (for design vary_f) -->
+<!-- Value of the parameters chosen for this simulation are $\mu = 0$, $\sigma = 1$ and $\omega = {1, 2, \dots, 10}$ -->
 
@@
 
-```{r tuning-parameter-intersection, fig.cap="For most panels it is observed that the most common values for which the "}
+```{r tuning-parameter-intersection, fig.cap="For most panels it is observed that the most common value of the tuning paramter for which the designs interact is 0.5, which implies any value greater than 0.5 could be chosen to up-weigh the within-facet distances and down-weigh the between-facet distances for most sitatuions."}
 knitr::include_graphics(here::here("simulations/tuning_param/figs/intersection_plot.png"))
@@
 <!-- CONTENT CUT -->
-<!--While any special event that corresponds to a time domain can be treated as an aperiodic linear granularity in a temporal case, dot balls or wickets that corresponds to certain balls (index) could be treated as aperiodic events in cricket.-->
+<!--While any special event that corresponds to a time domain can be treated as an aperiodic linear granularity in a temporal xacase, dot balls or wickets that corresponds to certain balls (index) could be treated as aperiodic events in cricket.-->
 

### 2021-01-13 paper/main.Rmd
update all files to run raw N(0,1) for different designs

@@
 
-### Notations Definitions
+### Notations and Definitions
 
@@
 
-# Behavior of raw wpd (weighted pairwise distances)
+# Behavior of raw wpd
 
@@
 
-We now discuss the effect of different tuning parameters $\lambda$ and $\omega$ with the help of two alternate designs ($D_{var_x}$ and $D_{var_f}$).
-Figure \ref{fig:tuning-one-omega} displays different values of $\lambda$ for a relatively small and higher $\omega$ for $nx = nfacet =  \{2, 3, 5, 7, 9\}$.
+We now discuss the effect of different tuning parameters $\lambda$  with the help of two alternate designs ($D_{var_x}$ and $D_{var_f}$) and $\omega$.
+\autoref{fig:tuning-oneomega} displays different values of $\lambda$ for a relatively small and higher $\omega$ for $nx = nfacet =  \{2, 3, 5, 7, 9\}$.
 The $\lambda$ for which the two designs intersect will then be chosen as the optimal $\lambda$ that could then be weighed appropriately to up-weigh the within-facet distances and down-weigh the between-facet distances.
@@
 The two designs mostly intersect at $\lambda = 0.5$ for a higher value of $\omega$.
-\autoref{fig:tuning-parameter-intersection} shows how the value of $\lambda$ changes with increasing $\omega$ for $\omega =  \{1, 2, \dots, 10\}$ and $\lambda = seq(from  = 0.1, to = 0.9, by = 0.05)$.
+\autoref{fig:tuning-parameter-inter} shows how the value of $\lambda$ changes with increasing $\omega$ for $\omega =  \{1, 2, \dots, 10\}$ and $\lambda = seq(from  = 0.1, to = 0.9, by = 0.05)$.
 
@@
 
-```{r tuning-one-omega, fig.caption = "WPD from two designs are plotted for different values of lambda for different x and facet categories.
+```{r tuning-oneomega, fig.caption = "WPD from two designs are plotted for different values of lambda for different x and facet categories.
 For omega = 1, the designs intersect for 0.6<lamba<=0.75, whereas for higher omega, design intersects at lambda = 0.5"}
@@
 
-```{r tuning-parameter-intersection, fig.cap="For most panels it is observed that the most common value of the tuning paramter for which the designs interact is 0.5, which implies any value greater than 0.5 could be chosen to up-weigh the within-facet distances and down-weigh the between-facet distances for most sitatuions."}
+```{r tuning-parameter-inter, fig.cap ="For most panels it is observed that the most common value of the tuning paramter for which the designs interact is 0.5, which implies any value greater than 0.5 could be chosen to up-weigh the within-facet distances and down-weigh the between-facet distances for most sitatuions."}
 knitr::include_graphics(here::here("simulations/tuning_param/figs/intersection_plot.png"))
@@
 
-How value of lambda changes with increasing omega and mean for fixed nx, nfacet and standard deviation?
-
-```{r lambda-omega-mean, eval = FALSE}
-knitr::include_graphics(here::here("simulations/result_report/lambda_omega_mean_3_2.png"))
-```
-
-How value of lambda changes with increasing omega and sd for fixed nx, nfacet and mean?
-
-```{r lambda-omega-sd, eval = FALSE}
-knitr::include_graphics(here::here("simulations/result_report/lambda_omega_sd_3_2.png"))
-```
-
-```{r lamba-omega-alternate-design}
-knitr::include_graphics((here::here("simulations/result_report/wpd_alterate_designs.png")))
-```
-
- Distribution across facet and x categories
+We now discuss the values wpd takes for different designs.
+Ideally the wpd should have the higherst values for $D_{var_{all}}$, followed by $D_{var_x}$ and $D_{var_y}$ for $\lambda \geq 0.5$.
+We test this for lower and higher values of $\omega = c(1, 8, 15, 50)$
+
+<!-- How value of lambda changes with increasing omega and mean for fixed nx, nfacet and standard deviation? -->
+
+<!-- # ```{r lambda-omega-mean, eval = FALSE} -->
+<!-- # knitr::include_graphics(here::here("simulations/result_report/lambda_omega_mean_3_2.png")) -->
+<!-- # ``` -->
+<!-- #  -->
+<!-- # How value of lambda changes with increasing omega and sd for fixed nx, nfacet and mean? -->
+<!-- #  -->
+<!-- # ```{r lambda-omega-sd, eval = FALSE} -->
+<!-- # knitr::include_graphics(here::here("simulations/result_report/lambda_omega_sd_3_2.png")) -->
+<!-- # ``` -->
+<!-- #  -->
+<!-- # ```{r lamba-omega-alternate-design} -->
+<!-- # knitr::include_graphics((here::here("simulations/result_report/wpd_alterate_designs.png"))) -->
+<!-- # ``` -->
+
+ <!-- Distribution across facet and x categories -->
 <!-- ### Need for normalisation -->
 
-From Figure \ref{fig:dist-across-facets} and \ref{fig:dist-across-x} shows the MMPD distribution is different for different levels of facets and x-axis levels.
-With increasing number of facets, the location of the distribution shift rightwards and with increasing x-axis levels, the scale of the distribution reduces.
-
-Median and maximum distances are affected by the number of categories considered and hence the distance measure $MMPD_{raw}$, which is a combination of median and maximum would also be influenced by the number of levels.
-It would have higher values if $C_i$ or $C_j$ has higher levels.
-We would ideally want a higher value of the measure if there is significant difference between distributions across facet or x-axis categories, and not because the number of categories are higher.
-In Figures \ref{fig:dist-across-facets} and \ref{fig:dist-across-x}, both the cyclic granularities $C_i$ and $C_j$ are considered such that their levels vary in the range $(2, 5,7 ,9, 14, 21, 30, 45)$.
+### Discussion
+
+The distribution of wpd is different for different levels of facets and x-axis levels.
+This is because the statistic maximum which is used to define wpd is affected by the number of categories.
+The measure would have higher values if $C_i$ or $C_j$ has higher levels.
+However, we would ideally want a higher value of the measure only if there is significant difference between distributions across facet or x-axis categories, and not because the number of categories are higher.
+Therefore, in order to compare wpd across different combinations of facet and x-axis levels, we need to eliminate the impact of different levels of the facets and x-axis first and get a normalized measure.
+Henceforth we call the measure discussed as $wpd_{raw}$ and the normalised measure as $wpd_{norm}$.
+The measure $wpd_{norm}$ could potentially lead to comparison of the measure across different panels and also identifying only the interesting panels from a dataset.
+
+<!-- In Figures \ref{fig:dist-across-facets} and \ref{fig:dist-across-x}, both the cyclic granularities $C_i$ and $C_j$ are considered such that their levels vary in the range $(2, 5,7 ,9, 14, 21, 30, 45)$.
 Each of these combinations is considered a panel for each of which $MMPD_{raw}$ has been constructed $100$ times to compute the distribution.
@@
 This shows that with the increase in the number of levels of $C_i$, the location of the distribution shift rightward, whereas for increasing x-axis levels, the scale of the distribution decreases.-->
-
-Therefore, in order to compare $MMPD_{raw}$ across different combinations of facet and x-axis levels, we need to eliminate the impact of different levels of the facets and x-axis first and get a normalized measure.
 
@@
 
-## Sample size
-## Number of permutations
-
 # Normalisation
@@
 In an attempt to make the densities \ref{fig:hist_plot} same across different levels, we want to start by making their scale and location same.
-In that regard, we shuffle the data multiple times and compute the sampling distribution of $mmpd_{raw}$ for each combination of facet and x-axis levels.
+In that regard, we shuffle the data multiple times and compute the sampling distribution of  for each combination of facet and x-axis levels.
 
@@
 
-## Simulation study
+## Null design
+
+## Alternate designs
 
@@
 
-```{r}
+```{r, eval = FALSE}
 knitr::include_graphics(here::here("paper/Figs/simulation.png"))
@@
 
-## Results
+## Sample size
+
+How smaller or different sample size play a role in the distribution of the measure.
+
+## Number of permutations
+
+Find the number of permutations which are sufficient for consistent estimation of mean and standard deviation
+
+## Discussion
+
+Did normalisation work?
 
@@
 
-```{r norm-data, fig.cap = "Distribution of $MMPD_{norm}$ across different levels of facet and x-axis. These distributions should look the same if normalisation worked." }
+```{r norm-data, fig.cap = "Distribution of $MMPD_{norm}$ across different levels of facet and x-axis. These distributions should look the same if normalisation worked." , eval = F}
 mmpd_norm = read_rds("../hakear-drake/data/data_norm_low_new.rds") 
@@
 The distribution of MMPD is unaffected by the null distribution considered.
-It is also the same across all facet levels but not across the x-axis, which means normalisation is failing across x-axis."}
+It is also the same across all facet levels but not across the x-axis, which means normalisation is failing across x-axis.", eval = F}
 # all_files = list.files(path = "../hakear-drake/data", pattern = ".rds")
@@
 
-### Performance of normalised MMPD
-
-```{r}
+<!-- ### Performance of normalised MMPD -->
+
+```{r, eval = FALSE}
 data1  = sim_panel(nx = 2, nfacet = 3, ntimes = 500)

### 2021-01-13 simulations/vary_all/norm/R-ind/raw_pairwise_N01.R

@@ -1,81 +1,0 @@
-#This script calculates raw mmpd for each simulation scenario
-##Read Simulation Table
-
-.libPaths(c("~/R/libs", .libPaths()))
-library(distributional)
-library(readr)
-library(drake)
-library(tidyverse)
-library(hakear)
-
-set.seed(9999)
-
-nsim = 200
-# change path while running it on HPC
-# simtable<-read_csv(here::here('simulations/null/sim_table.csv'))
-
-simtable<-read_csv('../sim_table.csv')
-
-### Extract flags from simulation scenario
-
-#scen<- 2 #If running within R uncomment this.  This will only run first scenario
-scen<-as.numeric(commandArgs()[[6]]) # If running batch job uncomment this
-
-simj<-simtable[scen,] #Extract row of table
-nfacetj<-simj$nfacet # Which nfacet level
-nxj<-simj$nx #Which nx level
-wj <- simj$w
-
-#create data for each row for null normal
-
-sim_null_normal = function(nxj, nfacetj){
-  rep(distributional::dist_normal(0, 1), 
-      times = nxj*nfacetj)
-}
-
-sim_varx_normal = function(nx, 
-                           nfacet, 
-                           mean = 0, 
-                           sd = 1,
-                           w)
-{
-  rep(dist_normal((mean + seq(0, nx-1, by  = 1)*w), sd), nfacet)
-}
-
-sim_panel_data = 
-  hakear::sim_panel(nx = nxj,
-                    nfacet = nfacetj, 
-                    ntimes = 500, 
-                    sim_dist = sim_varx_normal(nx = nxj, nfacet = nfacetj, w = wj)) %>% 
-  unnest(c(data)) %>% ungroup() %>% 
-  bind_cols(w = wj)
-
-set.seed(1111)
-
-  raw_dist <- map(seq_len(nsim), function(i)
-{
-  new_sim_data = sample(sim_panel_data$sim_data, 
-                        size = nrow(sim_panel_data))
-  new_data = sim_panel_data %>% 
-    select(-sim_data) %>% 
-    mutate(sim_data = new_sim_data)
-  
-  # for creating one raw mmpd
-  raw_mmpd = compute_pairwise_max(new_data, 
-                                 gran_x = "id_x",
-                                 gran_facet = "id_facet",
-                                 response = sim_data) %>% 
-    as_tibble() %>% mutate(perm_id = i)
-  
[…]

### 2021-01-13 simulations/vary_all/norm/R-ind/raw_pairwise_N55.R

@@ -1,76 +1,0 @@
-#This script calculates raw mmpd for each simulation scenario
-##Read Simulation Table
-
-.libPaths(c("~/R/libs", .libPaths()))
-library(distributional)
-library(readr)
-library(drake)
-library(tidyverse)
-library(hakear)
-
-set.seed(9999)
-
-nsim = 200
-# change path while running it on HPC
-# simtable<-read_csv(here::here('simulations/null/sim_table.csv'))
-
-simtable<-read_csv('../sim_table.csv')
-
-### Extract flags from simulation scenario
-
-#scen<- 2 #If running within R uncomment this.  This will only run first scenario
-scen<-as.numeric(commandArgs()[[6]]) # If running batch job uncomment this
-
-simj<-simtable[scen,] #Extract row of table
-nfacetj<-simj$nfacet # Which nfacet level
-nxj<-simj$nx #Which nx level
-wj <- simj$w
-
-#create data for each row for null normal
-
-sim_varx_normal = function(nx, 
-                           nfacet, 
-                           mean = 5, 
-                           sd = 5,
-                           w)
-{
-  rep(dist_normal((mean + seq(0, nx-1, by  = 1)*w), sd), nfacet)
-}
-
-sim_panel_data = 
-  hakear::sim_panel(nx = nxj,
-                    nfacet = nfacetj, 
-                    ntimes = 500, 
-                    sim_dist = sim_varx_normal(nx = nxj, nfacet = nfacetj, w = wj)) %>% 
-  unnest(c(data)) %>% ungroup() %>% 
-  bind_cols(w = wj)
-
-set.seed(1111)
-
-raw_dist <- map(seq_len(nsim), function(i)
-{
-  new_sim_data = sample(sim_panel_data$sim_data, 
-                        size = nrow(sim_panel_data))
-  new_data = sim_panel_data %>% 
-    select(-sim_data) %>% 
-    mutate(sim_data = new_sim_data)
-  
-  # for creating one raw mmpd
-  raw_mmpd = compute_pairwise_max(new_data, 
-                                  gran_x = "id_x",
-                                  gran_facet = "id_facet",
-                                  response = sim_data) %>% 
-    as_tibble() %>% mutate(perm_id = i)
-  
-}) %>% bind_rows()
-
-
-if(!dir.exists("simulations/vary_x/null_design_quantrans/data-ind/wpd_N55"))
-{
[…]

### 2021-01-13 simulations/vary_all/raw/R-ind/raw_pairwise_Gamma01.R

@@ -28,20 +28,21 @@ wj <- simj$w
 
 #create data for each row for null normal
 
-sim_varf = function(nx, 
-                    nfacet,
-                    mean = 0, 
-                    sd = 1,
-                    w)
+
+sim_varall = function(nx,
+                      nfacet,
+                      shape = 0.5,
+                      rate = 1,
+                      w)
 {
-  rep(dist_normal((mean + seq(0, nfacet-1, by  = 1)*w), sd), each = nx)
+  dist_gamma((shape + seq(0, (nx*nfacet - 1), by  = 1)*w), rate)
 }
 
 sim_panel_data = 
   hakear::sim_panel(nx = nxj,
                     nfacet = nfacetj, 
                     ntimes = 500, 
-                    sim_dist = sim_varf(nx = nxj, nfacet = nfacetj, w = wj)) %>% 
+                    sim_dist = sim_varall(nx = nxj, nfacet = nfacetj, w = wj)) %>% 
   unnest(c(data)) %>% ungroup() %>% 
   bind_cols(w = wj)
 
@@ -65,12 +66,12 @@ raw_dist <- map(seq_len(nsim), function(i)
 }) %>% bind_rows()
 
 
-if(!dir.exists("simulations/vary_facet/raw/data-ind/wpd_N01"))
+if(!dir.exists("simulations/vary_all/raw/data-ind/wpd_Gamma01"))
 {
-  dir.create("simulations/vary_facet/raw/data-ind/wpd_N01")
+  dir.create("simulations/vary_all/raw/data-ind/wpd_Gamma01")
 }
 saveRDS(raw_dist,
-        paste0('../data-ind/wpd_N01/',
+        paste0('../data-ind/wpd_Gamma01/',
                nxj,'_',
                nfacetj,"_",
                wj, '_wpd.rds'))

### 2021-01-13 simulations/vary_all/raw/R-ind/raw_pairwise_Gamma21.R

@@ -28,20 +28,21 @@ wj <- simj$w
 
 #create data for each row for null normal
 
-sim_varf = function(nx, 
-                    nfacet,
-                    mean = 0, 
-                    sd = 1,
-                    w)
+
+sim_varall = function(nx,
+                      nfacet,
+                      shape = 2 ,
+                      rate = 1,
+                      w)
 {
-  rep(dist_gamma((mean + seq(0, nfacet-1, by  = 1)*w), sd), each = nx)
+  dist_gamma((shape + seq(0, (nx*nfacet - 1), by  = 1)*w), rate)
 }
 
 sim_panel_data = 
   hakear::sim_panel(nx = nxj,
                     nfacet = nfacetj, 
                     ntimes = 500, 
-                    sim_dist = sim_varf(nx = nxj, nfacet = nfacetj, w = wj)) %>% 
+                    sim_dist = sim_varall(nx = nxj, nfacet = nfacetj, w = wj)) %>% 
   unnest(c(data)) %>% ungroup() %>% 
   bind_cols(w = wj)
 
@@ -65,9 +66,9 @@ raw_dist <- map(seq_len(nsim), function(i)
 }) %>% bind_rows()
 
 
-if(!dir.exists("simulations/vary_facet/raw/data-ind/wpd_Gamma21"))
+if(!dir.exists("simulations/vary_all/raw/data-ind/wpd_Gamma21"))
 {
-  dir.create("simulations/vary_facet/raw/data-ind/wpd_Gamma21")
+  dir.create("simulations/vary_all/raw/data-ind/wpd_Gamma21")
 }
 saveRDS(raw_dist,
         paste0('../data-ind/wpd_Gamma21/',

### 2021-01-13 simulations/vary_all/raw/R-ind/raw_pairwise_N51.R

@@ -28,20 +28,21 @@ wj <- simj$w
 
 #create data for each row for null normal
 
-sim_varf = function(nx, 
-                    nfacet,
-                    mean = 5, 
-                    sd = 1,
-                    w)
+
+sim_varall = function(nx,
+                      nfacet,
+                      mean = 5,
+                      sd = 1,
+                      w)
 {
-  rep(dist_normal((mean + seq(0, nfacet-1, by  = 1)*w), sd), each = nx)
+  dist_normal((mean + seq(0, (nx*nfacet - 1), by  = 1)*w), sd)
 }
 
 sim_panel_data = 
   hakear::sim_panel(nx = nxj,
                     nfacet = nfacetj, 
                     ntimes = 500, 
-                    sim_dist = sim_varf(nx = nxj, nfacet = nfacetj, w = wj)) %>% 
+                    sim_dist = sim_varall(nx = nxj, nfacet = nfacetj, w = wj)) %>% 
   unnest(c(data)) %>% ungroup() %>% 
   bind_cols(w = wj)
 
@@ -65,9 +66,9 @@ raw_dist <- map(seq_len(nsim), function(i)
 }) %>% bind_rows()
 
 
-if(!dir.exists("simulations/vary_facet/raw/data-ind/wpd_N51"))
+if(!dir.exists("simulations/vary_all/raw/data-ind/wpd_N51"))
 {
-  dir.create("simulations/vary_facet/raw/data-ind/wpd_N51")
+  dir.create("simulations/vary_all/raw/data-ind/wpd_N51")
 }
 saveRDS(raw_dist,
         paste0('../data-ind/wpd_N51/',

### 2021-01-13 simulations/vary_facet/norm/R-agg/aggregate01.R

@@ -7,7 +7,7 @@ library(rlang)
 
 aggregate01 <-  function(folder_name){
   
-all_files = list.files(path = paste0("simulations/vary_x/null_design_quantrans/data-ind/", folder_name), 
+all_files = list.files(path = paste0("simulations/norm/null_design_quantrans_nperm/data-ind/", folder_name), 
                        pattern = ".rds")
 
 names_levels <- map_dfr(all_files, 
@@ -23,7 +23,7 @@ names_levels <- map_dfr(all_files,
 # names_rep <- names_levels %>% slice(rep(1:n(), each = nrow(len_file)))
 
   
-all_files_path <- paste0("simulations/vary_x/null_design_quantrans/data-ind/",folder_name,"/",
+all_files_path <- paste0("simulations/norm/null_design_quantrans_nperm/data-ind/",folder_name,"/",
          all_files)  
   
 
@@ -38,7 +38,7 @@ all_data <- lapply(1:length(all_files_path), function(x){
   }) %>% bind_rows() %>% 
     arrange(nfacet, nx)
     
-write_rds(all_data, paste0("simulations/vary_x/null_design_quantrans/data-agg/all_data_", folder_name, ".rds"))
+write_rds(all_data, paste0("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_", folder_name, ".rds"))
 }
 
 

### 2021-01-13 simulations/vary_x/null_design_quantrans/R-ind/raw_pairwise_N01.R

@@ -12,7 +12,7 @@ set.seed(9999)
 
 nsim = 200
 # change path while running it on HPC
-# simtable<-read_csv(here::here('simulations/null/sim_table.csv'))
+# simtable<-read_csv(here::here('simulations/vary_x/null_design_quantrans/sim_table.csv'))
 
 simtable<-read_csv('../sim_table.csv')
 

### 2021-01-13 simulations/vary_x/null_design_quantrans/job/job-raw-Gamma01.sh

@@ -4,7 +4,7 @@
 #SBATCH --error=error_%a.err
 #SBATCH --mem-per-cpu=4096
 #SBATCH --time=168:00:00
-#SBATCH --array=1-64
+#SBATCH --array=65-256
 #SBATCH --ntasks=1
 #SBATCH --cpus-per-task=1
 #SBATCH --export=NONE

### 2021-01-13 paper/main.Rmd
including some figures

@@
 We are interested in assessing structure in probability distributions of the measured variable across bivariate cyclic granularities.
-We propose a measure called Median Maximum Pairwise Distances (MMPD) to evaluate structure in such a design.
+We propose a measure called Median Maximum Pairwise Distances (wpd) to evaluate structure in such a design.
 
@@
 This would help capture the average maximum difference in distribution of the measurement variable explained by the two cyclic granularities together.
-We call this metric MMPD which stands for Median Maximum Pairwise Distances.
+We call this metric wpd which stands for Median Maximum Pairwise Distances.
 In the next section we shall see how we go about computing this measure.
@@
 
+```{r all-design-relative, fig.cap = "Distribution of wpd under different designs are overlapped to see how they measure relative to each other.
+We would have expected values of wpd to be such that vary_facet is less than vary_x is less than vary_all but distribution of vary_x to lie above vary_facet."}
+
+library(readr)
+library(tidyverse)
+
+vary_x <- read_rds("simulations/vary_x/null_design_quantrans/data-agg/all_data_wpd_N01.rds")
+
+vary_all <- read_rds("simulations/vary_all/raw/data-agg/all_data_wpd_N01.rds")
+
+vary_facet <- read_rds("simulations/vary_facet/raw/data-agg/all_data_wpd_N01.rds")
+
+all_design <- bind_rows(vary_facet, vary_x, vary_all, .id = "design") %>% 
+  mutate(design = case_when(
+    design=="1" ~ "vary_facet",
+    design=="2" ~ "vary_x",
+    design=="3" ~ "vary_all",
+    TRUE ~ as.character(design)                                                                 ))
+
+all_design %>% 
+  ggplot() +
+  geom_histogram(aes(x=value, fill = design), 
+                 alpha = 0.7) +
+  scale_fill_brewer(palette = "Dark2")  +
+  facet_wrap(~w, labeller = "label_both")
+```
+
 <!-- How value of lambda changes with increasing omega and mean for fixed nx, nfacet and standard deviation? -->
@@
 
-```{r, eval = FALSE}
-knitr::include_graphics(here::here("simulations/null_design/figs/normalised","gamma_ridge_nxbynfacet.png"))
+```{r normal01-norm, fig.cap="Density plots of normalised wpd is shown for Normal(0,1) distribution.
+The mean and sd of the distribution looks almost similar for different facet and x-axis categories.", fig.pos="h"}
+
+knitr::include_graphics(here::here("simulations/norm/null_design_quantrans_nperm/figs/nxbyfacet_density_wpd_N01.png"))
 ```

### 2021-01-13 assimiate_design.R

@@ -1,0 +1,29 @@
+library(readr)
+library(tidyverse)
+
+vary_x <- read_rds("simulations/vary_x/null_design_quantrans/data-agg/all_data_wpd_N01.rds")
+
+vary_all <- read_rds("simulations/vary_all/raw/data-agg/all_data_wpd_N01.rds")
+
+vary_facet <- read_rds("simulations/vary_facet/raw/data-agg/all_data_wpd_N01.rds")
+
+all_design <- bind_rows(vary_facet, vary_x, vary_all, .id = "design") %>% 
+  mutate(design = case_when(
+    design=="1" ~ "vary_facet",
+    design=="2" ~ "vary_x",
+    design=="3" ~ "vary_all",
+    TRUE ~ as.character(design)                                                                 ))
+
+all_design %>% 
+  ggplot() +
+  geom_density(aes(x=value), 
+                 alpha = 0.7) +
+  scale_fill_brewer(palette = "Dark2")  +
+  facet_wrap(~w, labeller = "label_both")
+#+ facet_grid(nx~nfacet)
+  
+
+
+
+
+  

### 2021-01-13 simulations/vary_all/norm/R-ind/norm_pairwise_N01.R

@@ -14,7 +14,8 @@ set.seed(9999)
 nsim = 200
 # change path while running it on HPC
 # simtable<-read_csv(here::here('simulations/null/sim_table.csv'))
-simtable<-read_csv('../../../sim_table/sim_table.csv')
+simtable<-read_csv('../sim_table.csv')
+
 
 ### Extract flags from simulation scenario
 
@@ -24,20 +25,28 @@ scen<-as.numeric(commandArgs()[[6]]) # If running batch job uncomment this
 simj<-simtable[scen,] #Extract row of table
 nfacetj<-simj$nfacet # Which nfacet level
 nxj<-simj$nx #Which nx level
+wj <- simj$w
 
 #create data for each row for null normal
 
-sim_null_normal = function(nxj, nfacetj){
-  rep(distributional::dist_normal(0, 1), 
-      times = nxj*nfacetj)
+sim_varall = function(nx,
+                      nfacet,
+                      mean = 0,
+                      sd = 1,
+                      w)
+{
+  dist_normal((mean + seq(0, (nx*nfacet - 1), by  = 1)*w), sd)
 }
+
 
 sim_panel_data = 
   hakear::sim_panel(nx = nxj,
                     nfacet = nfacetj, 
                     ntimes = 500, 
-                    sim_dist = sim_null_normal) %>% 
-  unnest(c(data)) %>% ungroup()
+                    sim_dist = sim_varall(nx = nxj, nfacet = nfacetj, w = wj)) %>% 
+  unnest(c(data)) %>%
+  ungroup()%>% 
+  bind_cols(w = wj)
 
 set.seed(1111)
 
@@ -58,7 +67,13 @@ set.seed(1111)
   
 }) %>% bind_rows()
 
-saveRDS(raw_dist,
+if(!dir.exists("simulations/vary_all/norm/data-ind/wpd_N01"))
+  {
+    dir.create("simulations/vary_all/norm/data-ind/wpd_N01")
+  }  
+  
+  saveRDS(raw_dist,
           paste0('../data-ind/wpd_N01/',
                  nxj,'_',
-                 nfacetj,'_wpd.rds'))
+                 nfacetj,"_",
+                 wj, '_wpd.rds'))

### 2021-01-20 paper/supplementary.Rmd
adding simulations for all parameters together

--- 2021-01-13 paper/main.Rmd
@@
 ---
-title: Selecting and ranking interesting pairs of cyclic temporal granularities
+title: Supplementary materials 
 authors:
@@
 
-```{r}
-set.seed(321)
-```
-
-# Introduction
-
-<!-- <introducing the problem> -->
-<!-- background of the problem -->
-
-Exploratory data analysis, as coined by John W.
-Tukey (Tukey 1965) involves many iterations of finding structures and patterns that allows the data to be informative.
-With temporal data available at finer scales, exploring periodicity and their relationships can become overwhelming with so many possible cyclic temporal granularities [@Gupta2020-vo] to explore.
-
-```{r calendar-elec, fig.height = 10.5, fig.cap="Calendar display."}
-elec <- read_rds(here("paper/data/elec.rds")) %>% 
-  filter(date >= ymd("20180101"), date < ymd("20180701"))
-rdbl <- c("Weekday" = "#d7191c", "Weekend" = "#2c7bb6")
-
-elec <- elec %>% 
-  mutate(
-    wday = wday(date, label = TRUE, week_start = 1),
-    weekday = if_else(wday %in% c("Sat", "Sun"), "Weekend", "Weekday")
-  )
-p_cal_elec <- elec %>% 
-  filter(id %in% c(2, 4)) %>% 
-  frame_calendar(x = time, y = kwh, date = date, nrow = 1) %>% 
-    ggplot(aes(x = .time, y = .kwh, group = date)) +
-    geom_line(aes(colour = as.factor(id)), size = 0.5) +
-    scale_colour_brewer(name = "", palette = "Dark2", direction = 1) +
-    facet_grid(id ~ ., labeller = label_both) +
-    theme(legend.position = "bottom")
-prettify(p_cal_elec, size = 2.5, label.padding = unit(0.1, "lines"))
-```
-
-\noindent Take the example of the calendar display of electricity smart meter data (\ref{fig:calendar-elec}) used in @wang2020calendar for four households in Melbourne, Australia.
-The authors show how hour-of-the-day interact with weekday and weekends and then move on to use calendar display to show daily schedules.
-The calendar display has several components in it, which helps us look at energy consumption across hour-of-the-day, day-of-the-week, week-of-the-month, and month-of-the-year at once.
-Some interaction of these cyclic granularities could also be interpreted from this display.
-This is a great start to have an overview of the energy consumption.
-However, if one wants to understand the periodicities in energy behavior and how the periodicities interact in greater details, it is not easy to comprehend the interactions of some periodicities' from this display, due to the combination of linear and cyclic representation of time.
-For example, this display might not be the best to understand how hour-of-the-day varies and month-of-year varies across week-of-the-month.
-Further, it is not clear what all interactions of cyclic granularities should be read from this display as there could be many combinations that one can look at.
-Moreover, calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions (@Gupta2020-vo) and could include other cyclic granularities like hour-of-week or day-of-fortnight, which could potentially become useful depending on the context.
-
-```{r intro_all}
-
-id2_tsibble <- elec %>% 
-   filter(id == 2) %>% 
-   as_tsibble(index = date_time)
-
-id4_tsibble <- elec %>% 
-   filter(id == 4) %>% 
-   as_tsibble(index = date_time)
-
-# hour-of-day and month-of-year (important pair) id2's behavior across different hours of the day very different across months, but for id4 behavior across different hours of the day is not likely a function of month.
-p1 <- id2_tsibble %>%
-   prob_plot("month_year",
-             "hour_day",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = TRUE,
-             quantile_prob = c(0.1, 0.25,0.5,0.75, 0.9)) +
-  ggtitle("") + theme(
-        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + 
-  scale_colour_brewer(name = "", palette = "PiYG")
-
-p2 <- id4_tsibble %>%
-   prob_plot("month_year",
-             "hour_day",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = TRUE,
-             quantile_prob = c(0.1, 0.25,0.5,0.75, 0.9)) + 
-  ggtitle("") + theme(
-        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
-
-# wknd_wday and week_month (important pair) id2's behavior across different hours of the day very different across months, but for id4 behavior across different hours of the day is not likely a function of month.
-
-p3 <- id2_tsibble %>%
-  create_gran("week_month") %>% 
-  filter(week_month != 5) %>% 
-   prob_plot("wknd_wday",
-             "week_month",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = FALSE,
-             quantile_prob = c(0.25,0.5,0.75)) +
-   ggtitle("") +
-#scale_x_discrete(breaks = seq(0, 23, 4))  + theme(
-        theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
-
-p4 <- id4_tsibble %>%
-    create_gran("week_month") %>% 
-  filter(week_month != 5) %>% 
-   prob_plot("wknd_wday",
-             "week_month",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = FALSE,
-             quantile_prob = c(0.25,0.5,0.75)) +
-  ggtitle("") +  #+ scale_x_discrete(breaks = seq(0, 23, 4)) + 
-theme(
-        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
-
-```
-
-```{r id2, fig.cap = "something"}
-ggpubr::ggarrange(p1, p2, ncol = 2)
-```
-
-```{r id4, fig.cap = "something2"}
-ggpubr::ggarrange(p3, p4, ncol = 2)
-```
-
-Moreover, there might be specific interactions that are interesting and others that are not and that too will vary with different households.
-For example, area distribution quantiles are plotted for household 2 and 4 in Figure \ref{fig:id2}a and b respectively.
-For the first household, the 75th and 90th percentile for Jan, Feb and July are very close, implying that energy usage for these months are generally on a much higher side due to the usage of air conditioners (in Jan and Feb) and heaters (in July).
-The energy consumption for household 2 is also higher relative to its own consumption for Jan, Feb and March but the 75th and 90th percentile are apart implying that contrary to the first household, the second household resorts to air conditioners and heaters much less regularly than the first one.
-Moreover, the 75th percentile distribution is not bimodal across hours of the day for the first household in those months, but the distribution looks similar for all months for the second household.
-Difference in the energy consumption seem to be varying both across month-of-year (facets) and hour-of-day (x-axis).
-And thus, both the cyclic granularities would deem important while studying the periodicities in the first household.
-However, it seems like energy consumption across hours of the day are not that different across different months for the second household.
-Differences seem to be more prominent across month-of-year (facets) than hour-of-day (x-axis).
-Again, look at \ref{fig:} c and d, where energy consumption for these two households are plotted against (weekend/weekday, week-of-month).
-Here, for both households, the pattern of energy consumption vary  across different weeks of the month irrespective of the fact it is a weekday or weekend.
-In that respect, the harmony pair (month-of-year, hour-of-day) seems to be more informative than (weekend/weekday, week-of-month) for the first household.
-It could be immensely useful to make the transition from all possible ways to only ways that could potentially be informative given a household.
-
-<!-- Take an example of a data set which are observed at fine temporal scales, like that of NYC bike usage available at https://www.citibikenyc.com/system-data.
-We use the `nyc_bikes` data set from the R package `tsibbledata` which takes a sample of 10 bikes for the year 2018.
-The `start_time` and the `stop_time` are recorded to a fineness of seconds.
-We can look at pair of cyclic granularities (hour_day, wknd_wday) or (week_month, day_week) to see how these periodicities interact.
-But there could be other pairs that are important too.
-How to understand which pairs are sufficient to explore given the data set without losing much information about the data.
--->
-
-<!-- When we need to understand the interplay of different periodicities in a high frequency temporal datasets, we have many choices to consider.
-In [@wang2019tsibble] and [@wang2020calendar], periodicities are explored across hour of the day and day of the week or months.
-But calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions.
--->
-
-<!-- what is the dimension of the problem -->
-The paper @Gupta2020-vo describes how we can compute all possible combinations of cyclic time granularities.
-If we have $n$ periodic linear granularities in the hierarchy table, then $n(n-1)/2$ circular or quasi-circular cyclic granularities could be constructed.
-Let $N_C$ be the total number of contextual circular, quasi-circular and aperiodic cyclic granularities that can originate from the underlying periodic and aperiodic linear granularities.
-The mapping of the graphical elements chosen in the paper implies that, for a numeric response variable, the graphics display distributions across combinations of cyclic granularities, one placed at x-axis and the other on the facet.
-That essentially implies there are $^{N_C}P_2$ possible pairwise plots exhaustively, where each plot would display a pair of cyclic granularities.
-This is large and overwhelming for human consumption.
-
-<!-- Scagnostics literature -->
-This is similar to Scagnostics (Scatterplot Diagnostics) by @tukey1988computer, which is used to discern meaningful patterns in large collections of scatterplots.
-Given a set of $v$ variables, there are $v(v-1)/2$ pairs of variables, and thus the same number of possible pairwise scatterplots.
-Therefore
-for even small $v$, the number of scatterplots can be
-large, and scatterplot matrices (SPLOMs) could easily run out of pixels when presenting high-dimensional data.
-@Dang2014-tw and @wilkinson2005graph provides potential solutions to this, where few characterizations help us to locate anomalies for defining several measures aimed to detect anomalies in density, shape, trend, and
-other features in the 2D point scatters.
-
-<!-- harmonies and why it is not enough -->
-The paper (@Gupta2020-vo) narrows down the search from $^{N_C}P_2$ plots by identifying pairs of granularities that can be meaningfully examined together (a "harmony"), or when they cannot (a "clash").
-However, even after excluding clashes, the list of harmonies left could be enormous for exhaustive exploration.
-Hence, there is a need to reduce the search even further by including only those harmonies which are informative enough.
-Also, ranking the remaining harmony pairs based on how well they capture the variation in the measured variable could be potentially useful.
-
-In this paper, we aim to build a new measure to follow through these two main objectives:
-
-- To choose harmonies for which distributions of categories are significantly different 
-- To rank the selected harmonies from highest to lowest variation in the distribution of their categories.
-
-<!-- Talk about Scagnostics: Tukey -->
-
-# Distance measure
-
-We are interested in assessing structure in probability distributions of the measured variable across bivariate cyclic granularities.
-We propose a measure called Median Maximum Pairwise Distances (wpd) to evaluate structure in such a design.
-
-## Idea {#sec:idea}
-
-The principle employed for building a new metric is explained through a simple example explained in Figure \ref{fig:null4by2}.
-Each of these figures have the same panel design with 2 x-axis categories and 4 facet levels.
-Figure \ref{fig:null4by2}a has all x categories drawn from N(5, 10) distribution for each facet.
-It is not an interesting display particularly, as distributions do not vary across x-axis or facet categories.
-Figure \ref{fig:null4by2}b has x categories drawn from the same distribution within a facet and different for different facet categories.
-Figure \ref{fig:null4by2}b exhibits an exact opposite situation where distribution between the x-axis categories within each facet is different but they are same across facets.
-Figure \ref{fig:null4by2}d takes a step further by varying the distribution across both facet and x-axis categories.
-If we are asked to rank the displays in order of importance from minimum to maximum, we might order it as a, b, c and then d.
-It might be argued that it is not clear if b should precede or succeed c.
-Gestalt theory suggests that when items are placed in close proximity, people assume that they are in the same group because they are close to one another and apart from other groups.
-Hence, displays that capture more variation within different categories in the same group would be important to bring out different patterns of the data.
-With this principle, display b could be considered less informative as compared to display c.
-
-With reference to the graphical design in \ref{@Gupta2020-vo}, therefore the idea would be to rate a harmony pair higher if the variation between different levels of the x-axis variable is higher on an average across all levels of the facet variables.
-Thus the metric could be obtained by computing maximum pairwise distances between distributions of the continuous random variable across x-axis categories for all facets and then taking the median of those maximum pairwise distances across facets.
-This would help capture the average maximum difference in distribution of the measurement variable explained by the two cyclic granularities together.
-We call this metric wpd which stands for Median Maximum Pairwise Distances.
-In the next section we shall see how we go about computing this measure.
-
-<!-- To elaborate further, look at the examples in Figure \ref{}, where Figure \ref{}a represents the panel design with distribution of each x categories drawn from N(5, 10) distribution.
-It could be observed that the graph is not particularly interesting, as there is no significant change in distribution between x-axis levels or facets.
-Figure \ref{}b represents the same panel design with no difference in distribution of x-axis categories within a facet, but different distribution of x-axis categories for different facets.
-For example, if there are 4 facet levels and 2 x-axis levels, data is generated in the way as described in Table \ref{}.
-Figure \ref{}b exhibits an exact opposite situation where the x-axis within facets are different but not across facets.
--->
-<!-- Figure \ref{}d takes it further by varying the distribution across both facet and x-axis categories. -->
-
-```{r null4by2,fig.cap=" A graphical display with two categories mapped to x-axis and 4 categories mapped to facets with the distribution of a continuous random variable plotted on the y-axis.
-Display a is not interesting as the distribution of the continuous rv does not depend across x-axis or facet categories.
-Display b and c are more interesting than a since there is a change in distribution either across facets(b) or x-axis(a).
-Display d is most interesting as distribution of the rv changes across both facet and x-axis variable."}
-
-sim_varf_dist1 = function(nx, nfacet){
-  rep(dist_normal(seq(mean,mean*nfacet, by = mean), sd), each = nx)}
-
-p1 <- sim_panel(nx = 2, nfacet = 3, ntimes = 500) %>%
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
-
-simulated_data <- sim_panel(nx = 2,
-          nfacet = 3,
-          ntimes = 500,
-          sim_dist = rep(dist_normal(seq(5, 15, 5), 5), each = 2))
-
-p2 <- simulated_data %>% ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
-
-p3 <- simulated_data %>% ggplot(aes(x = as.factor(id_facet), y = sim_data)) + facet_wrap(~id_x) + geom_boxplot()
-
-p4 <- sim_panel(nx = 2,
-          nfacet = 3,
-          ntimes = 500,
-          sim_dist = dist_normal(seq(5,30, 5), 5)) %>% 
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
-
-ggpubr::ggarrange(p1, p2, p3, p4, nrow = 2, ncol = 2,
-                  common.legend = TRUE,
-                  labels = c("a", "b", "c", "d"))
-
-```
-
-<!-- in the same group would be important to bring out different patterns of the data. -->
-
-## Methodology
-
-### Characterising distribution
-
-Each of the data subsets in the data structure have multiple observations and may vary widely across different subsets due to the structure of the calendar, missing observations or uneven locations of events in the time domain.
-The set of observations corresponding to each combination is assumed to be a sample from an unknown probability density function.
-While the whole population of observations has certain characteristics, we can typically never measure all of them.
-Often shape, central tendency, and variability are the common characteristics used to describe the distribution.
-Another way to describe the probability distribution is through quantiles.
-(Define quantiles here) <!--There are two broad approaches to quantile estimation, viz, parameteric and non-parameteric.
-The benefit of using a non-parametric estimator is that there are less rigid assumptions made about the nature of the underlying distribution of the data.--> Sample quantiles could be thought to estimate the population quantiles.
-But there are a large number of different definitions used for sample quantiles.
-The median-unbiased estimator is recommended (Rob's paper) because of its desirable properties of a quantile estimator and can be defined independently of the underlying distribution.
-
-### Distance between distributions
-
-<!-- One of the most important class of divergence is the f-divergence and includes measures like Kullback-Leibler divergence, Hellinger distance etc.
-The continuous version of f -divergence is given by -->
-<!-- $$D_f(P||Q) := \int q(x)f(\frac{p(x)}{q(x)})$$, where -->
-<!-- $f : [0,\infty) \rightarrow R \cup \{\infty\}$ is a continuous convex function, and $f(1) = 0$.  -->
-
-The most common divergence measure between distributions is the Kullback-Leibler (KL) divergence[@Kullback1951-jy] introduced by Solomon Kullback and Richard Leibler in 1951.
-The KL divergence, denoted $D(p(x), q(x))$ is a non-symmetric measure of the difference between two probability distributions $p(x)$ and $q(x)$ and is interpreted as the amount of information lost when $q(x)$ is used to approximate $p(x)$.
-Although the KL divergence measures the “distance” between two distributions, it is not a distance measure since it is not symmetric and does not satisfy the triangle inequality.
-The Jensen-Shannon divergence [@Menendez1997-in] based on the Kullback-Leibler divergence is symmetric and it always has a finite value.
-The square root of the Jensen-Shannon divergence is a metric, often referred to as Jensen-Shannon distance.
-Other common measures of distance are Hellinger distance, total variation distance and Fisher information metric.
-
-In the context of this paper, the pairwise distances between the distributions of the measured variable are computed through Jensen-Shannon distance (JSD) which is based on Kullback-Leibler divergence and is defined by,
-
-$$JSD(P||Q) = \frac{1}{2}D(P||M) + \frac{1}{2}D(Q||M)$$
-where $M = \frac{P+Q}{2}$ and 
-$D(P||Q) := \int^\infty_{-\infty} p(x)f(\frac{p(x)}{q(x)})$ is the KL divergence between distributions $p(x)$ and $q(x)$.
-Probability distributions are estimated through quantiles instead of kernel density so that there is minimal dependency on selecting kernel or bandwidth.
-
-<!-- The Jensen-Shanon distance between two probability distribution $p_1$ and $p_2$ is given by $$d = [D(p_1, r) + D(p_2, r)]/2 \quad where \quad r = (p_1 + p_2)/2$$ where, -->
-<!-- $$D(p_1,p_2) = \int^{\infty}_{-\infty}p_1(x)log\frac{p_1(x)}{p_2(x)}\,dx$$ is the Kullback-Leibler divergence between $p_1$ and $p_2$.   -->
-
-<!-- We call this measure of variation as  Median Maximum Pairwise Distances (MMPD). -->
-
-<!-- #### Distribution of Jensen-Shannon distances -->
-
-<!-- Jensen-Shannon distances (JSD) are distributed as chi-squared with $m$ df where we discretize the continuous distribution with $m$ discrete values.
-Taking sample percentiles to approximate the integral would mean taking $m = 99$.
--->
-<!-- With large $m$, chi-squared is asymptotically normal by the CLT.
-Thus, by CLT, ${\chi^2}_{m} \tilde{} N(m, 2m)$, which would depend on the number of discretization used to approximate the continuous distribution.
-Then $b_n = 1-1/n$ quantile of the normal distribution and $a_n = 1/[n*\phi(b_n)]$ where $\phi$ is the normal density function.
-$n$ is the number of pairwise comparisons being made.
--->
-
-### Notations and Definitions
+# Notations and Definitions
 
@@
 ```
-
-From Section \ref{sec:idea}, the idea is to put more weights on within-facet distances than between-facet distances.
-Hence, for a suitable tuning parameter $\lambda > 1$, the pairwise distances $d_{(jk, j'k')}$ are transformed based on the distance type as follows:
-
-\begin{equation}
-d*_{(j,k), (j'k')} =
-\begin{cases}
-\lambda d_{(jk), (j'k')},& \text{if } d = d_w\\
-(1-\lambda)  d_{(jk), (j'k')},              & \text{if } d = d_b\\
-\end{cases}
-\end{equation}
-
-The maximum weighted pairwise distances are defined as:
-$$WPD = max_{j, j', k, k'}(d*_{(jk), (j'k')})
-\forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}$$.
-
-<!-- _j$ maps index set to a set $\{B_\ell \mid \ell =1,\dots,L\}$.
-Here, $A_k$ and $B_\ell$ are the levels/categories corresponding to $C_i$ and $C_j$ respectively.
-Let $S_{k\ell}$ be a subset of the index set such that for all $s \in S_{k\ell}$, $C_i(s) = A_k$ and $C_j(s) = B_\ell$.
-There are $KL$ such data subsets, one for each combination of levels ($A_k$, $B_\ell$).
-Moreover, consider that in the graphical space, $C_i$ is mapped to facets and $C_j$ is mapped to x-axis.
--->
-
- <!-- old -->
-<!-- Consider two cyclic granularities $C_i$ and $C_j$, such that $C_i$ maps index set to a set $\{A_k \mid k=1,\dots,K\}$ and $C_j$ maps index set to a set $\{B_\ell \mid \ell =1,\dots,L\}$.
-Here, $A_k$ and $B_\ell$ are the levels/categories corresponding to $C_i$ and $C_j$ respectively.
-Let $S_{k\ell}$ be a subset of the index set such that for all $s \in S_{k\ell}$, $C_i(s) = A_k$ and $C_j(s) = B_\ell$.
-There are $KL$ such data subsets, one for each combination of levels ($A_k$, $B_\ell$).
-Moreover, consider that in the graphical space, $C_i$ is mapped to facets and $C_j$ is mapped to x-axis.
--->
-
-<!-- The algorithm employed for computing the distance measure is summarized as follows: -->
-
-<!-- 1. Fix harmony pair $(C_i, C_j)$. -->
-
-<!-- 2. Fix $k$. Then there are $L$ groups corresponding to level $A_k$ of $C_i$. -->
-
-<!-- 3. Compute  $m = \binom{L}{2}$ pairwise distances between distributions of $L$ unordered levels and $m = L-1$ pairwise distances for $L$ ordered categories. -->
-
-<!-- 4. Identify maximum within the $m$ computed distances. -->
-
-<!-- <!-- 5. Compute distribution of maximum distance ($M$) by shuffling the data $200$ times and finishing Steps1-4 in each case. Scale $M$ using the mean and sd of the distribution.  --> -->
-
-<!-- 5. Use Steps 1-4 to compute maximum distance for $\forall k \in  \{1, 2, \ldots, K\}$. -->
-
-<!-- 6. Compute the distance measure MMPD_raw = median $(M_1, M_2, \dots, M_K)$. -->
-
-<!-- \begin{algorithm}[!thb] -->
-<!-- 	\caption{Calculation for a raw distance measure between two cyclic granularities $A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.}\label{alg:scoreopt}.
--->
-<!-- 	\begin{algorithmic}[1] -->
-<!-- 		\Procedure{RawMMPD}{$A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$, $v = \{ v_t: t = 1, 2, \dots, T\}$}. -->
-<!-- 		\For{$k=1:K$, $j=1:J$} -->
-<!-- 		\State Find distances between pairs of all possible combinations of categories $(a_jb_k,a_j'b_k')$ by computing JSD between quantiles of the measured variable $q(v)$ across these combinations.
--->
-<!-- 		\State $d \gets JSD(\tilde{q(v)_{a_{j}b_{k}}},\tilde{q(v)_{a_{j}'b_{k}'}})$ -->
-<!-- 		\If {$b_k = b_k'$} -->
-<!-- 		\State $d* \gets \lambda d$  \Comment{upweight within-facet distances} -->
-<!-- 		\Else -->
-<!-- 		\State $d* \gets 1/\lambda d $ \Comment{downweight across-facet distances} -->
-<!-- 		\EndFor -->
-<!-- 		\State Set the raw distance measure as $max(d*)$ where max is taken over all $j, j', k, k'$. -->
-
-<!-- 		\EndProcedure -->
-<!-- 	\end{algorithmic} -->
-<!-- \end{algorithm} -->
-
-<!-- A stronger measure "max" is chosen for aggregating x-axis categories compared to "median" for aggregating facet categories as the measure is intended to put more importance in pointing towards distributional differences between x-axis categories than for facet categories.
--->
 
@@
 
-<!-- #### Method 2: -->
-
-<!-- $m' = max_{x}dist$ is obtained for each facet. -->
-<!-- All $x$ levels are shuffled for each facet to obtain several $m'$s.
-Hence $m'$ is normalized for each facet level and the facets are aggregated using $m''= median(m')$, which is basically median(norm(max)).
-We need to normalise this median across facets as well.
-So we shuffle all facets for each $x$ level and obtain several $m''$s.
-In this approach, data is shuffled $2*nperm$ times and hence distances are computed $2*nperm$ times.
-It is computationally very intensive.
--->
-
-<!-- Hence, it was decided that the first approach will be employed to implement normalisation.
-One of the advantages of the second method could be to have normalisation separately for max and median measure.
-There is nothing that is stopping the users to implement this with more efficient computing power.
--->
-
-<!-- The harmony pairs could be arranged from highest to lowest average maximum pairwise distances across different levels of the harmonies. -->
-
-<!-- With increasing n, mean and sd of distribution of max increases. -->
-
-<!-- FTP theorem works for large n -->
-
-<!-- For small n resort to bootstrapping -->
-
-<!-- bullet points end here -->
-
-<!-- Suppose that $X_1$, $X_2$ , ... , $X_n$ are i.i.d. random variables with expected values $E(X_i) = \mu < \infty$ and variance $Var(X_i) = \sigma^2 < \infty$. Let  -->
-<!-- $Y = max(X_1, X_2, \dots, X_n)$. -->
-
-<!-- Let $F_X(x)$ be the common distribution of the variables $X_i$ and let $F_Y(y)$ be the corresponding distribution of $Y$. $F_Y(y)$ could be obtained from $F_X(x)$ simply by using: -->
-<!-- $F_Y(y) = P[(X_1 \leq y)\cap(X_2 \leq y) \cap...\cap (X_n \leq y)] = {F_X(y)}^n$.
-For large $n$, the distribution of $Y$ approaches a standard shape, which does not depend on $F_X$.
-But what about the case when $n$ is not large enough?
-The distribution of maximum in that case will indeed depend on $n$ and the underlying distribution of $X$.
-If $F_X(x)$ is the CDF of $X$, then $F_Y(y) = {F_x(y)}^n$.
-Suppose $\Phi$ nd $\phi$ are the cdf and pdf of a standard normal distribution, then -->
-<!-- $f_Y(y) = n{\Phi(y)}^{n-1}\phi(y)$, which depends on $n$.
-Hence, we are trying to normalise for $n$.
-Also, it depends on the underlying distribution of $X$, which we have assumed as normal in our case.
-As $n$ grows, we  can see the right tail growing, which implies that the probability that we will get a higher maximum is more.
-Now, for large $n$, we used EVT to normalise for $n$, that is, we brought them to the same scale without distorting the range of the distribution.
-But in our case, we will mostly have small $n$.
-It is important to ensure that they have the same mean and variation, for being able to compare the maximum value across $n$.
-We observe from the following graphs that our normalisation works after $n=6$, after which the difference in mean and standard deviation flattens out a lot.
--->
-
-<!-- ### why normalize -->
-
-<!-- Median and maximum distances are not robust to the number of levels and the metric would have higher values for harmonies with higher levels.
-Figure \ref{fig:mean-sd-max} shows how both mean and standard deviation of the distribution of maximum and median varies for different sample sizes ($n$).
-There is a rightward shift in the location and decrease in scale with increasing $n$.
-Thus these median maximum pairwise distances need to be normalized for different harmonies in a way that eliminates the effect of different levels, consequently enabling comparison across different harmonies.
-The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.
--->
-
-<!-- More formally, $d_{1},d_{2}\ldots ,d_{n}$ be a sequence of independent and identically-distributed pairwise distances and $M_{n}=\max\{d_{1},\ldots ,d_{n}\}$.
-Then Fisher–Tippett–Gnedenko theorem [@De_Haan2007-yx] suggests that if a sequence of pairs of real numbers $(a_{n}, b_{n})$ exists such that each $a_{n}>0$ and $\lim _{{m\to \infty }}P\left({\frac  {M_{n}-b_{n}}{a_{n}}}\leq x\right)=F(x)$, where $F$ is a non-degenerate distribution function, then the limit distribution $F$ belongs to either the Gumbel, Fréchet or Weibull family.
-The normalizing constants $(a_{n}, b_{n})$ vary depending on the underlying distribution of the pairwise distances.
-Hence to normalize appropriately, it is  -->
-<!-- important to assume a distribution of these distances.  -->
-
-<!-- For large $n$, the distribution of $M$ approaches a standard shape.
-But what about the case when $n$ is not large enough?
-The distribution of maximum in that case will indeed depend on $n$ and the underlying distribution of $D$.
-For large $n$, we could use EVT and CLT to normalise for $n$, however, most of the cyclic granularities encountered in practice have low $n$.
-Hence, normalisation could be done by bootstrapping procedure to ensure that the distribution of maximum/median have the same mean and variation for varying $n$.
--->
-
-<!-- ```{r create_simdata} -->
-
-<!-- ``` -->
-
-<!-- ```{r create_nlevels} -->
-
-<!-- ``` -->
-
-<!-- ```{r norm_max_new} -->
-
-<!-- ``` -->
-
-<!-- ```{r mean-sd-max, fig.cap = "Display shows mean and standard deviation of the distribution of maximum for sample sizes ranging from 2 to 30.
-There is a right shift in the distribution of maximum and median with increasing sample sizes."} -->
-
-<!-- library(ggridges) -->
-<!-- library(viridis) -->
-<!-- max_all_data <- create_nlevels(nlevels = seq(2, 30, 2), -->
-<!--                            nsim = 500, -->
-<!--                            sim_dist = distributional::dist_normal(5, 10), create_fun = max) -->
-
-<!-- g1 <- max_all_data %>% ggplot() + geom_density_ridges(aes(x=sim_data, y = as.factor(ind))) + ylab("n") + xlab("max") -->
-
-<!-- median_all_data <- create_nlevels(nlevels = seq(2, 30, 2), -->
-<!--                            nsim = 500, -->
-<!--                            sim_dist = distributional::dist_normal(5, 10), create_fun = median) -->
-
-<!-- g2 <- max_all_data %>% ggplot() + geom_boxplot(aes(x=sim_data, y = as.factor(ind)))  + ylab("n") + xlab("median") -->
-
-<!-- ggpubr::ggarrange(g1, g2, ncol = 2) -->
-
-<!-- ``` -->
-
 ## Null design
@@
 ## Alternate designs
-
-<!-- ### Distribution of distances -->
-
-<!-- ### Theoretical evidence -->
-
-<!-- JS distances are distributed as chi-squared with $m$ df where we discretize the continuous distribution with $m$ discrete values.
-Taking sample percentiles to approximate the integral would mean taking $m = 99$.
--->
-<!-- With large $m$, chi-squared is asymptotically normal by the CLT.
-Thus, by CLT, ${\chi^2}_{m} \tilde{} N(m, 2m)$, which would depend on the number of discretization used to approximate the continuous distribution.
-Then $b_n = 1-1/n$ quantile of the normal distribution and $a_n = 1/[n*\phi(b_n)]$ where $\phi$ is the normal density function.
-$n$ is the number of pairwise comparisons being made.
--->
-
-<!-- ### Empirical evidence -->
-
-<!-- Distribution of JS distances is assumed to be normal but the mean and variance are estimated from the sample, rather than deducing it from the number of discretization used to approximate the continuous distribution.
-We look at different scenarios, where observations are collected from Normal, Exponential, Chi-squared and Gumbel distribution and found the distribution of JS distances are similar, irrespective of which distribution they are drawn from.
--->
-
-<!-- #### Initial distribution of observed variables shown in plot title -->
-
-<!-- ```{r distv11} -->
-
-<!-- ``` -->
-
-<!-- ```{r distv12} -->
-
-<!-- ``` -->
-
-<!-- ```{r distv13} -->
-
-<!-- ``` -->
-
-<!-- ```{r distv14} -->
-
-<!-- ``` -->
-
-<!-- ### Design and analysis of simulation experiments -->
 
@@
 
-### Experimental set up
-
-This section describes the design of simulation runs, in terms of the scenarios simulated, the number of permutations used to compute estimates and to display the distribution of MMPD.
-
- <!-- - seed while generating random observations `seed1 = set.seed(9999)`   -->
- <!-- - grid with how many x levels `range_nx_vec = seq(2:4)`   -->
- <!-- - grid with how many facet levels `range_nfacet_vec = seq(2:4)`   -->
- <!-- - number of observations to be generated `ntimes_val = 500`   -->
- <!-- - number of permutation of data done to compute estimates `nperm_val = 2`   -->
- <!-- - number of permutations of data done to display histogram for each panel `nsim_val = 10`    -->
- <!-- - ordered or un-ordered categories of x levels while computing distances `dist_ordered_val = TRUE`   -->
- <!-- - distance between which quantiles are computed `quantile_prob_vec = seq(0.01, 0.99, 0.01)`   -->
-
-```{r, eval = FALSE}
-knitr::include_graphics(here::here("paper/Figs/simulation.png"))
-```
-
-Observations from Normal(5, 10) and Gamma(0.5, 0.2) are3 chosen in all the designs.
-
-<!-- . the null distribution are chosen as:   -->
-<!-- `sim_norm_null =   distributional::dist_normal(5, 10)`   -->
-<!-- <!--`sim_exp_null  =   distributional::dist_expoential(5)`  --> -->
-<!-- `sim_gamma_null  =   distributional::dist_gamma(0.5, 0.2)`   -->
-<!-- <!--`sim_weibull_null  =   distributional::dist_weibull(1.5, 3)`-->   -->
-
-<!-- The various designs are selected by increasing the mean/rate/shape of these distributions proportionally with that parameter. -->
-
-<!-- To check if different distributions impact, simulate data from different distributions.
-A 3 way contingency table with number of facet levels, x-axis levels and distribution type should be constructed with each cell value as the p-value.
--->
-
-<!-- Table -->
-<!-- Conclusions -->
-<!-- (in Null distribution) -->
-
-<!-- #### Varying distribution across facet -->
-<!-- #### Varying distribution across x-axis -->
-<!-- #### Varying distribution across both facets and x-axis -->
-<!-- #### Repeat all with varying facet and x-axis levels -->
-
-<!-- Table -->
-<!-- Conclusions -->
-<!-- (in power) -->
-
-<!-- ```{r} -->
-<!-- raw_data = rnorm(12, 5, 10) %>%  -->
-<!--   as_tibble() %>%  -->
-<!--   mutate(nfacet = rep(1:4, each = 3), -->
-<!--          nx = rep(1:3, 4)) -->
-
-<!-- raw_data %>% group_by(nfacet, nx) %>% nest() -->
-
-<!-- raw_data2 = raw_data %>% pivot_wider(id_cols = 2, names_from = "nx", values_from = "value") -->
-
-<!-- ``` -->
-
-<!--  ### Original -->
-<!-- | facets/x-axis     	| A_1  	| A_2  	| A_3  	| .. 	| .. 	| A_m  	| -->
-<!-- |-----	|------	|------	|------	|----	|----	|------	| -->
-<!-- | B_1 	| x_1 	| x_2 	| x_3 	| .. 	| .. 	| x_n 	| -->
-<!-- | B_2 	| y_1 	| y_2 	| y_3 	| .. 	| .. 	| y_n 	| -->
-<!-- | B_3 	|      	|      	|      	|    	|    	|      	| -->
-<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
-<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
-<!-- | B_L 	| z_1 	| z_2 	| z_3 	| .. 	| .. 	| z_m 	| -->
-
-<!-- ### Step1 -->
-
-<!-- | facets/x-axis     	| A_1  	| A_2  	| A_3  	| .. 	| .. 	| A_m  	| -->
-<!-- |-----	|------	|------	|------	|----	|----	|------	| -->
-<!-- | B_1 	| x_1 	| x_2 	| x_3 	| .. 	| .. 	| x_n 	| -->
-<!-- | B_2 	| y_1 	| y_2 	| y_3 	| .. 	| .. 	| y_n 	| -->
-<!-- | B_3 	|      	|      	|      	|    	|    	|      	| -->
-<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
-<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
-<!-- | B_L 	| z_1 	| z_2 	| z_3 	| .. 	| .. 	| z_m 	| -->
-
-```{r, eval = FALSE}
-# design_time <- readr::read_rds("../hakear-drake/data/design_time.rds")
-# write_rds(design_time, "data/design_time.rds")
-time_data <-readr::read_rds("data/design_time.rds")
-time_data$design = 
-  factor(time_data$design,
-         levels = c("null","vary_f", "vary_x", "vary_all"))
-
-time_data %>% 
-  pivot_longer(cols = c(time_obs, time_dist),
-               names_to = "type",
-               values_to = "time") %>% 
-  dplyr::filter(distribution == "normal") %>% 
-  ggplot(aes(x= design, 
-             y = log(time, exp(1)), 
-             colour = type, group = nfacet)) + geom_point() + geom_line(aes(group = type)) +
-  facet_grid(nx~nfacet) + ylab("ln(time)")
-
-```
-
 ## Sample size
@@
 Find the number of permutations which are sufficient for consistent estimation of mean and standard deviation
-
-## Discussion
-
-Did normalisation work?
-
-### Null distribution
-
-<!-- Objective: distribution equal and hence values could be compared and normalisation works -->
-Under the null hypothesis, all the combinations of x-axis and facets are obtained from the same distribution.
-We need to study the distribution of the mmpd values under the null hypothesis to see if comparison of their values across different x-axis and facet levels are at all possible.
-So, in turn it needs to be checked that if normalisation worked.
-
-Currently, we see in Figure \ref{fig:null-dist} that the normalisation works fine for each facet since the distributions for each column are equal irrespective of the distribution type.
-But it does not work along the x-axis.
-
-```{r norm-data, fig.cap = "Distribution of $MMPD_{norm}$ across different levels of facet and x-axis. These distributions should look the same if normalisation worked." , eval = F}
-mmpd_norm = read_rds("../hakear-drake/data/data_norm_low_new.rds") 
-hist_plot = mmpd_norm %>% 
-      ggplot() +
-      geom_histogram(aes(x = raw_mmpd)) +
-      facet_grid(nx~nfacet)
-hist_plot
-```
-
-```{r null-dist, eval =  FALSE, echo = FALSE, fig.cap="Distribution of mmpd across different facet levels (columns) and x-axis levels (rows) for null ditribution normal(5,10) and gamma(0.5, 0.2).
-The distribution of MMPD is unaffected by the null distribution considered.
-It is also the same across all facet levels but not across the x-axis, which means normalisation is failing across x-axis.", eval = F}
-# all_files = list.files(path = "../hakear-drake/data", pattern = ".rds")
-# all_files
-# 
-# read_files = lapply(all_files, function(x){
-#   read_rds(paste0("../hakear-drake/data/", x))
-# })
-# 
-# names(read_files) = str_remove(all_files, pattern = ".rds")
-# 
-# null_all = bind_rows(normal = read_files$null_normal,
-#                      exponential = read_files$null_exp,
-#                      gamma = read_files$null_gamma,
-#                      weibull = read_files$null_weibull,
-#                      .id = "distribution")
-# design_all = readr::read_rds("../hakear-drake/data/design_all.rds")
-design_all = readr::read_rds("data/design_all.rds")
-
-design_all$design = 
-  factor(design_all$design,
-         levels = c("null","vary_f", "vary_x", "vary_all"), labels = c("D1", "D2", "D3", "D4"))
-design_all$distribution = 
-  factor(design_all$distribution,
-         levels = c("normal","gamma"), labels = c("norm","gam"))
-library(dplyr)
-library(ggplot2)
-ggplot2::ggplot(design_all %>% 
-                      filter(design == "D1")) +
-  ggridges::geom_density_ridges(aes(y = distribution, x = mmpd.x, fill = distribution)) + 
-  facet_grid(nx~nfacet) +
-  scale_fill_viridis_d() +
-  xlab("MMPD")
-```
-
-<!-- ### Performance of normalised MMPD -->
-
-```{r, eval = FALSE}
-data1  = sim_panel(nx = 2, nfacet = 3, ntimes = 500)
-simulated_data <- sim_panel(nx = 2,
-nfacet = 3,
-ntimes = 500,
-sim_dist = rep(dist_normal(seq(5, 15, 5), 5), each = 2))
-data2 = simulated_data
-data4 = sim_panel(nx = 2,
-nfacet = 3,
-ntimes = 500,
-sim_dist = dist_normal(seq(5,30, 5), 5))
-data3 = data2 %>% rename("temp" = "id_facet") %>% rename("id_facet" = "id_x") %>% rename("id_x" = "temp")
-
-library(parallel)
-library(gravitas)
-library(hakear)
-
-set.seed(1000)
-r1 <- compute_mmpd_norm(data1, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-r2 <- compute_mmpd_norm(data2, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-r3 <- compute_mmpd_norm(data3, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-r4 <- compute_mmpd_norm(data4, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-r1prime <- compute_norm_pairwise_max(data1, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-r2prime <- compute_norm_pairwise_max(data2, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-r3prime <- compute_norm_pairwise_max(data3, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-r4prime <- compute_norm_pairwise_max(data4, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-p1 <- data1 %>%
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +xlab("")
-
-p2 <- data2 %>% ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +xlab("")
-
-p3 <- data3 %>% ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +xlab("")
-
-p4 <- data4 %>% 
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +xlab("")
-
-gridExtra::grid.arrange(gridExtra::arrangeGrob(p1, top = paste("MMPD", round(r1, 3), "pairwise", round(r1prime, 3))),
-                        gridExtra::arrangeGrob(p2, top = paste("MMPD", round(r2, 3), "pairwise", round(r2prime, 3))),
-                        gridExtra::arrangeGrob(p3, top = paste("MMPD", round(r3, 3), "pairwise", round(r3prime, 3))),
-                        gridExtra::arrangeGrob(p4, top = paste("MMPD", round(r4, 3), "pairwise", round(r4prime, 3))),
-                        ncol = 2, nrow=2)
-
-```
-
-# The statistical test
-
-## Algorithm
-
-for computation for all harmony pairs
-
-**Assumption:** random permutation without considering ordering 
-(global)
-
-1. Given the data; $\{v_t: t=0, 1, 2, \dots, T-1\}$, the MMPD is computed and is represented by $MMPD_{obs}$.
-
-2. From the original sequence a random permutation is obtained: $\{v_t^*: t=0, 1, 2, \dots, T-1\}$.
-
-3. MMPD is computed for all random permutation of the data and is represented by $MMPD_{sample}$.
-
-4.  Steps (2) and (3) are repeated a large number
-of times M (e.g. 1000).
-
-5. For each permutation, one $MMPD_{sample}$ value is obtained.
-
-6. $95^{th}$ percentile of this $MMPD_{sample}$ distribution is computed and stored in $MMPD_{threshold}$.
-
-7. If  $MMPD_{obs}> MMPD_{threshold}$, harmony pairs are accepted. Only one threshold for all harmony pairs.
-
-Pros: Considering thresholds global for all harmony pairs would imply less computation time.
-
-Cons: Only one threshold for all harmony pairs means we are assuming distribution of all harmonies pairs are similar, which might not be the case.But nevertheless, it is a good benchmark.
-
-```{r, eval = FALSE, echo = FALSE}
-smart_harmony <-read_rds("data/smart_harmony_nonst.rds")
-smart_harmony
-```
-
-```{r smart_harmony,eval = FALSE, echo = FALSE}
-
-sm <- smart_meter10 %>% dplyr::filter(customer_id %in% c("10017936"))
-
-harmonies <- sm %>% 
-  harmony(ugran = "month",
-          filter_in = "wknd_wday",
-          filter_out = c("hhour", "fortnight"))
-
-harmony_tbl =  harmonies
-
-smart_harmony <- sm %>% 
-  rank_harmony(harmony_tbl = harmonies,
-               response = "general_supply_kwh", 
-               dist_ordered = TRUE)
-
-smart_harmony %>% 
-  mutate(MMPD = round(MMPD, 3), max_pd = round(max_pd, 3)) %>% 
-  mutate(rankn = row_number()) %>%
-  rename("rankun" = "r") %>% kable()
-```
-
-## Size, power and confidence interval
-
-#### Characteristics under different simulation designs   
-A set of simulation runs that are conducted and some outputs of which are reported.
-
-```{r sim_all, echo = FALSE}
-bind_files = readr::read_rds("../hakear-drake/data/compute_p_value.rds")
-
-bind_files$design = 
-  factor(bind_files$design,
-         levels = c("null","vary_f", "vary_x", "vary_all"), labels = c("D1", "D2", "D3", "D4"))
-
-ggplot(bind_files %>% 
-         filter(distribution == "normal")) +
-  geom_point(aes(x=design, y = p_value),
-                 alpha = 0.5)+
-  facet_grid(nx~nfacet) +
-  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
-
-ggplot(bind_files %>% 
-         filter(distribution == "exponential")) +
-  geom_point(aes(x=design, y = p_value),
-                 alpha = 0.5)+
-  facet_grid(nx~nfacet) +
-  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
-
-ggplot(bind_files %>% 
-         filter(distribution == "gamma")) +
-  geom_point(aes(x=design, y = p_value),
-                 alpha = 0.5)+
-  facet_grid(nx~nfacet) +
-  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
-
-ggplot(bind_files %>% 
-         filter(distribution == "weibull")) +
-  geom_point(aes(x=design, y = p_value),
-                 alpha = 0.5)+
-  facet_grid(nx~nfacet) +
-  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
-```
-
-```{r sim_conf, echo = FALSE, eval = FALSE}
-library(dplyr)
-library(ggplot2)
-ggplot2::ggplot(design_all %>% 
-                      filter(design == "D1", distribution == "norm")) +
-  geom_boxplot(aes(x = as.factor(nx), 
-                   y = mmpd.x), width = 0.1) + 
-  facet_wrap(~nfacet) +
-  scale_fill_viridis_d() +
-  xlab("number of x levels") +
-  coord_flip()
-
-```
-
-# Applications {#sec:application}
-
-## Smart meter data of Australia {#sec:smartmeter}
-
-<!-- # how data looks -->
-
-Smart meters provide large quantities of measurements on energy usage for households across Australia.
-One of the customer trials [@smart-meter] conducted as part of the Smart Grid Smart City project in Newcastle, New South Wales and some parts of Sydney provides customer wise data on energy consumption for every half hour from February 2012 to March 2014.
-<!--It would be interesting to explore the energy consumption distribution for these customers and gain insights on their energy behavior which are lost either due to aggregation or looking only at coarser temporal units.-->The idea here is to show how to visualize the distribution of the energy consumption across different cyclic granularities in a systematic way to identify different behavioral patterns.
-
-### Cyclic granularities search and computation:
-
-The tsibble object `smart_meter10` from R package `gravitas` [@R-gravitas] consisting of `reading_datetime`, `customer_id` and `general_supply_kwh` denoting the index, key and measured variable of the tsibble is used to facilitate the systematic exploration.
-While trying to explore the energy behavior of these customers systematically across cyclic time granularities, the first thing to consider is which cyclic time granularities we can look at exhaustively.
-Let us consider conventional time deconstructions for a Gregorian calendar (second, minute, half-hour, hour, day, week, month, year).
-Since the interval of this tsibble is 30 minutes, the temporal granularities may range from half-hour to year.
-Considering $6$ linear granularities half-hour, hour, day, week, month and year in the hierarchy table, $N_C = (6*5/2) = 15$.
-<!--(via Section \ref{sec:data-structure}) circular or quasi-circular granularities that could be formed relating two linear granularities at a time.--> If $N_C$ seem too large, the smallest and largest linear granularities could be considered to be removed from the hierarchy table.
-We remove half-year and year to have $N_C = (4*3/2) = 6$ and obtain cyclic granularities namely "hour_day", "hour_week", "hour_month", "day_week", "day_month" and "week_month", read as "hour of the day", etc.
-Further, we add cyclic granularity day-type( "wknd_wday") to capture weekend and weekday behavior.
-Now that we have a list of cyclic granularities to look at, we should be able to compute the multiple-order-up granularities using Section \ref{sec:cyclic-calendar}.
-
-```{r search, echo=FALSE, eval = FALSE}
-library(gravitas)
-smart_meter %>%
-  search_gran(filter_out = c("semester", 
-                             "quarter",
-                             "fortnight"))
-```
-
-```{r search_gran_limit2, echo = FALSE, eval = FALSE}
-smart_meter10 %>% search_gran(
-  highest_unit = "month",
-  filter_out = c("hhour", "fortnight"))%>%
-  knitr::kable(format = "latex",
-      booktabs = TRUE) %>%
-  #row_spec(0, bold = TRUE)%>%
-  kable_styling()
-```
-
-<!-- # smart_meter_limit2 <- smart_meter10 %>% search_gran(highest_unit = "month", -->
-<!-- #                               filter_out = c("hhour", "fortnight") -->
-<!-- # ) -->
-<!-- # knitr::kable(smart_meter_limit2, format = "markdown") -->
-
-<!-- Now that we have a list of cyclic granularities to look at, we should be able to compute them from the data using Sections \ref{sec:circular-gran-def}, \ref{sec:quasi-circular-gran-def} and \ref{sec:aperiodic-gran-def}.
--->
-
-### Screening and visualizing harmonies
-
-From the search list, $N_C = 7$ cyclic granularities are chosen for which we would like to derive insights of energy behavior.
-Recalling the data structure <$C_i$, $C_j$, `general_supply_kwh`> for exploration $\forall i, j \in \{1, 2, \ldots, 7\}$, each of these $7$ cyclic granularities can either be mapped to x-axis or to facet.
-Choosing $2$ of the possible $7$ granularities, which is equivalent to having $^{7}P_2 = 42$ candidates for visualization.
-Fortunately, harmonies can be identified among those $42$ possibilities to narrow the search.
-\autoref{tab:harmony-tab} shows $16$ harmony pairs after removing clashes and any cyclic granularities with levels more than $31$, as effective  exploration becomes difficult with many levels (Section \ref{sec:levels}).
-The MMPD is also shown along with indicator (*) only when variation of measured variable across the harmony pair significant.
-Starting from $42$ possible pairs of cyclic granularities to visualize, we are finally left with only $6$, which is a very sizable number of displays for exploration.
-
-Few harmony pairs are displayed in \autoref{fig:bothcust} to illustrate the significance of MMPD, threshold and the impact of different distribution plots and reverse mapping.
-\noindent For each of \autoref{fig:bothcust} (b) and (c), $C_i$ is the circular granularity day-type (weekday/weekend) and $C_j$ is hour of the day.
-The geometry used for displaying the distribution is chosen as area-quantiles and violins in \autoref{fig:bothcust} (b and c respectively).
-\autoref{fig:bothcust} (a) displays reverse mapping of $C_i$ and $C_j$ with $C_i$ denoting hour of the day and $C_j$ denoting day-type with distribution geometrically displayed as boxplots.
-
-<!-- From the search list, we found six cyclic granularities for which we would like to derive insights of energy behavior.
-Given the data structure <$C1$, $C2$, `general_supply_kwh`>, each of those six cyclic granularities can either be mapped to x-axis or to facet.
-Thus the problem is equivalent to taking 2 granularities at a time from six, which essentially is equivalent to having 30 data subsets for visualization.
-However, harmony/clash pairs can be identified among those 30 possibilities to determine feasibility of plotting any pairs together.
-\autoref{tab:harmony-tab} shows 13 harmonies pairs, each of which can be plotted together to look at the energy behavior from different perspectives.
--->
-
-<!-- We will look at few harmony pairs and see how the proposed workflow can be utilized.  -->
-
-<!-- From the Gestalt theory with the same data  <$C1$ $C2$, `general_supply_kwh`>, mapping $C1$ on the x-axis vs facet might lead to different insights. -->
-
-```{r harmony-tab, echo=FALSE, eval = FALSE, cache=TRUE}
-# if(!dir.exists("cache/"))
-# {
-#   dir.create("cache")
-# }
-# 
-# if (!file.exists("cache/smart_harmony.rds")) {
-  sm <- smart_meter10 %>%
-  filter(customer_id %in% c(10017936))
-
-  harmonies <- sm %>%
-  harmony(ugran = "month",
-          filter_in = "wknd_wday", 
-          filter_out = c("hhour", "fortnight"))
-set.seed(12345)
-
-global_harmony <- sm %>%
-  global_threshold(harmony_tbl = harmonies,
-                   response = "general_supply_kwh", nsamp = 5) %>%
-  rename(`facet variable` = facet_variable,
-         `x-axis variable` = x_variable,
-         `facet levels` = facet_levels,
-         `x-axis levels` = x_levels) %>% 
-  mutate(MMPD = if_else(gt_MMPD == TRUE,
-                        paste0(MMPD, "*"), paste0(MMPD))) %>%
-  select(`facet variable`,`x-axis variable`,
-         `facet levels`,`x-axis levels` ,MMPD)
-
-#   write_rds(smart_harmony,"cache/smart_harmony_ak.rds")
-# }
-#smart_harmony <- read_rds("cache/smart_harmony.rds")
-
-  knitr::kable(global_harmony,
-               format = "latex",
-               booktabs = TRUE,
-                caption = "Harmonies with a pair of cyclic granularity one placed on facet and the other on x-axis.
-Out of 42 possible combinations of cyclic granularities, only 16 are harmony pairs.
-The harmony pairs are ranked basis highest to lowest MMPD and only the first 6 show significant variation in the measured variable.") %>%
-    #row_spec(0, bold = TRUE) %>%
-    kable_styling()
-```
-
-In \autoref{fig:bothcust} (b), <!--the distribution of energy consumption is plotted across the harmony pair (weekday/weekend, hour of the day) through an area quantile plot-->the black line is the median, whereas the purple band covers 25th to 75th percentile, the orange band covers 10th to 90th percentile and the green band covers 1st to 99th percentile.
-The first facet represents the weekday behavior while the second one displays the weekend behavior and energy consumption across each hours of the day is shown inside each facet.
-The energy consumption is extremely (positive- or right-) skewed with the 1st, 10th and 25th percentile lying relatively close whereas 75th, 90th and 99th lying further away from each other.
-This is common across both weekdays and weekends.
-For the first few hours on weekdays, median energy consumption starts and continues to be higher for longer as compared to weekends.
-
-Consider looking at violin plots instead of quantile plots to look at the same data in \autoref{fig:bothcust}(c).
-There is additional information that we can derive looking at the distribution.
-There is bimodality in the early hours of the day, implying both low and high energy consumption is probable in the early hours of the day both for weekdays and weekends.
-<!--Also the hours from 7 to 13 look most volatile.--> If we visualize the same data with reverse mapping of the cyclic granularities, then the natural tendency would be to compare weekend and weekday behavior within each hour and not across hours.
-For example in \autoref{fig:bothcust}(a), it can be seen that median energy consumption for the early morning hours is extremely high for weekdays compared to weekends.
-Also, outliers are more prominent in the latter part of the day.
-All of these indicate that looking at different distribution geometry or changing the mapping might shed lights on different aspect of the energy behavior for the same sample population.
-
-```{r bothcust, fig.cap = "Energy consumption of a single customer shown with different distribution displays, and granularity arrangements.
-Two granularities are used: hour of the day (I) and weekday/weekend (II).
-Plot (a) shows granularity I facetted by granularity II, and plots (b), (c) shows the converse mapping.
-Plot (a) makes a comparison of usage by workday within each hour of the day using side-by-side boxplots.
-Generally, on a work day there is more consumption early in the day.
-Plots (b) and (c) examine the temporal trend of consumption over the course of a day, separately for the type of day.
-Plot (b) uses an area quantile to put the emphasis on the time series, for example, the median consumption over time shows prolonged usage in the morning on weekdays.
-Plot (c) uses a violin plot to place emphasis on distributional differences across hours.
-It can be seen that the morning use on weekdays is bimodal, some work days there is low usage, which might indicate the person is working from home and also having a late start.", out.width="90%"}
-
-cust2_quantile <- smart_meter10 %>%
-  filter(customer_id %in% c(10017936)) %>%
-  prob_plot("wknd_wday",
-    "hour_day",
-    response = "general_supply_kwh",
-    plot_type = "quantile",
-    symmetric = TRUE,
-    quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)
-  ) +
-  scale_y_sqrt() +
-  #ggtitle(" (b) Area quantile plot faceted by weekend-weekday") +
-  ylab("electricity demand [KWh]") + xlab("hours of the day") + ggtitle("") + ylab("")+ 
-  theme_minimal()
-
-cust2_violin <- smart_meter10 %>%
-  filter(customer_id %in% c(10017936)) %>%
-  prob_plot("wknd_wday",
-    "hour_day",
-    response = "general_supply_kwh",
-    plot_type = "violin"
-  ) +
-  scale_y_sqrt()+
-  #ggtitle(" (c) Violin plot faceted by weekend-weekday") +
-  ylab("") + xlab("hours of the day") + ggtitle("") +
-  scale_x_discrete( breaks = seq(0, 23, 5))+ 
-  theme_minimal()
-
-cust2_box <- smart_meter10 %>%
-  filter(customer_id %in% c(10017936)) %>%
-  prob_plot("hour_day",
-    "wknd_wday",
-    response = "general_supply_kwh",
-    plot_type = "boxplot"
-  ) +
-  scale_y_sqrt() +
-  #ggtitle(" (a) Box plot faceted by hour-of-day") +
-  xlab("") +
-  ggtitle("") + ylab("") +
-  scale_x_discrete(labels = c('wday','wend')) +
-  ggplot2::theme(axis.text.x = element_text(size = 7))+ 
-  theme_minimal()
-
-#ggarrange(cust2_quantile, cust2_violin, nrow = 2)
-
-gg_fig <- ggarrange(cust2_box,
-          ggarrange(cust2_quantile, cust2_violin, nrow = 2, labels = c("b", "c")),
-          ncol = 2, labels = "a")
-          #label.y = "electricity demand [KWh]"\
-
-ggpubr::annotate_figure(gg_fig,
-                left = text_grob("electricity demand [KWh]",  rot = 90))
-```
-
-<!-- # ```{r cust-ridge, fig.cap ="Boxplot of energy consumption across hours of the day faceted by weekday/weekend for customer id: 10017936.
-The change in mapping of the cyclic granularities leads to easier comparison within weekdays and weekends for each hour.
-Median consumption till 6am is higher for weekends compared to weekdays although the quartiles look similar.
-Outliers appear more during the end of the day implying more uncertain behavior in latter hours of the day compared to early morning hours."} -->
-<!-- #  -->
-<!-- # smart_meter10 %>% -->
-<!-- #   filter(customer_id %in% c(10017936)) %>% -->
-<!-- #   prob_plot("hour_day", -->
-<!-- #     "wknd_wday", -->
-<!-- #     response = "general_supply_kwh", -->
-<!-- #     plot_type = "boxplot" -->
-<!-- #   ) + -->
-<!-- #   scale_y_sqrt() -->
-<!-- # ``` -->
-
-<!-- Now, we would like to see how these customers' behavior relate to the rest of the 50 households across these two measures -   -->
-
-<!-- - if energy distribution is skewed towards extreme? -->
-
-<!-- - if the weekend and weekday behavior are different for most of these households? -->
-
-If the data for all keys are visualized together, it might lead to Simpson's paradox, which occurs when one observation shows a particular behavior, but this behavior paradoxically becomes obscured by aggregation.
-For example in a particular neighborhood one household may have the least daily power consumption for a full week, yet still not be the household with the minimum weekly power consumption.
-This is an intuitive possibility, because heterogeneous `customer_id`'s with very different occupation or demographics will tend to have very different energy behavior and combining them together will somehow weaken any typical or extreme behavior.
-A strategy for analyzing multiple keys together could be to first group them basis time series or demographic features and then look at their energy behavior.
-This is beyond the scope of the current work.
-
-<!-- For the purpose of this paper, the smart meter data is filtered for two customers to illustrate kinds of insights that can be drawn after proceeding with the systematic exploration. -->
-
-<!-- For example, Figure \ref{fig:wknd-wday50} shows the quantile plot of energy consumption of a sample of 50 households.
-Quantiles for weekends and weekdays for these customers look exactly the same.
-It is not clear if the behaviors of most of these customers do not alter between weekdays and weekends or looking at all customers together balances out the behaviors.
-Consider another example in Figure \ref{fig:my-hd} showing the area quantile plots of 50 customers.
-The median is very close to the lower boundaries of all the other bands implying energy consumption for these households are left skewed.
-The pink band changes significantly in winter months (May - August) implying that much of the behavioral changes occur in the quartiles, that too in peak hours of the day.
-It is to be noted here that the the level of all quantiles increased too in winter months (increased energy usage in weather conditions), the interesting part is to notice that the relationship between bands other than quartile stayed same across seasons.
--->
-
-This case study shows systematic exploration of energy behavior for a household to gain exhaustive insights on periodic behavior of the households. 
-<!--First, it helps us to find the list of cyclic granularities to look at, then shrinks the number of possible visualizations by identifying harmonies, visualize a harmony pair and shows the effect of different distribution plots or reverse mapping.-->
-
-## T20 cricket data of Indian Premiere League {#sec:cricket}
-
-The method is not only restricted to temporal data, and can be generalized to many hierarchical granularities (with  continuous and uni-directional nature).
-We illustrate this with an application to the sport cricket.
-Although there is no conventional time component in cricket, each ball can be thought to represent an ordering from past to future with the game progressing forward with each ball.
-In the Twenty20 format, an over will consist of 6 balls (with some exceptions), an inning is restricted to a maximum of 20 overs, a match will consist of 2 innings and a season consists of several matches.
-Thus, similar to time, there is a hierarchy where ball is nested within overs, overs nested within innings and innings within matches.
-The idea of cyclic granularities can be likewise mapped to this hierarchy.
-Example granularites then include ball of the over, over of the inning and ball of the inning.
-Although most of these cyclic granularities are circular in design of the hierarchy, in application of the rules some granularities are aperiodic.
-For example, in most cases an over will consist of 6 balls with some exceptions like wide balls or when an inning finishes before the over finishes.
-Thus, the cyclic granularity ball-of-over will be circular in most cases and aperiodic in others.
-
-<!-- However, irrespective of the type of cyclic granularities, it can be interesting to visualize the distribution of a measured variable across these cyclic granularities to throw light on the periodic behavior of a non-temporal data set similar to any temporal data set.
--->
-
-The Indian Premier League (IPL) is a professional Twenty20 cricket league in India contested by eight teams representing eight different cities in India.
-The ball by ball data for IPL season 2008 to 2016 is fetched from [Kaggle](https://www.kaggle.com/josephgpinto/ipl-data-analysis/data).
-The `cricket` data set in the `gravitas` package summarizes the ball-by-ball data across overs and contains information for a sample of 214 matches spanning 9 seasons (2008 to 2016) such that each over has 6 balls, each inning has 20 overs and each match has 2 innings.
-This could be useful in a periodic world when we wish to compute any circular/quasi-circular granularity based on a hierarchy table which look like \autoref{tab:hierarchy-cric}.
-
-```{r hierarchy-cric}
-library(gravitas)
-library(tibble)
-hierarchy_model <- tibble::tibble(
-  `linear (G)` = c("over", "inning", "match", "season"),
-  `single-order-up cyclic (C)` = c("over-of-inning", "inning-of-match", "match-of-season", 1),
-  `period length/conversion operator (K)` = c(20, 2, "k(match, season)", 1)
-)
-knitr::kable(hierarchy_model,
-             format = "latex",
-             booktabs = TRUE,
-             caption = "Hierarchy table for cricket where overs are nested within an inning, innings nested within a match and matches within a season.") %>%
-  #row_spec(0, bold = TRUE)%>%
-  kable_styling()
-```
-
-However, even if the situation is not periodic and a similar hierarchy can not be formed, it can be interesting to visualize the distribution of a measured variable across relevant cyclic granularities to shed light on the aperiodic behavior of a non-temporal data set similar to aperiodic events like formal meetings, workshops, conferences, school semesters in a temporal set up.
-There are many interesting questions that could possibly be answered with such a data set irrespective of the type of cyclic granularities.
-<!--We will explore a few interesting questions and understand how the proposed approach in the paper can help answer some of the questions.-->
-
-<!-- the two teams have a single innings each, which is restricted to a maximum of 20 overs.
-Hence, in this format of cricket, a match will consist of 2 innings, an innings will consist of 20 overs, an over will consist of 6 balls with some exceptions.
--->
-
-<!-- ```{r hierarchy, echo=FALSE} -->
-<!-- hierarchy_model <- tibble::tibble(linear gran = c("ball", "over", "inning", "match"),  -->
-<!--                                   convert_fct = c(6, 20, 2, 1)) -->
-<!-- knitr::kable(hierarchy_model, caption = " A hierarchy table for T20 cricket") -->
-<!-- ``` -->
-
-<!-- Each team is given a two-and-a-half-minute "strategic timeout" during each innings; one must be taken by the bowling team between the ends of the 6th and 9th overs, and one by the batting team between the ends of the 13th and 16th overs.
--->
-
-<!-- Suppose, we are interested to see how the distribution of scores vary from the start to the end of the game. Let us brainstorm some of the questions that might help us comprehend that. -->
-
-<!-- a) What is the most common pattern for batting and bowling teams across balls, overs, innings and matches? Which are the teams which are typical and which are exceptions? -->
-
-<!-- How the scores per over vary across granularities/categorizations like innings of a match or matches of a season?
-Are these different for the winning teams in that season and the teams that couldn't qualify for the playoffs?
--->
-
-<!-- Is the outcome of the game dependent on who bats first? Do some teams have more chance to win if they are batting in the first innings? -->
-
-<!-- We will look at the ball by ball data for all batting teams.
-Since we want a periodic world, where each over consists of 6 balls and each match consists of two innings, we shall filter out the matches or overs for which that is not true.
-Also, we look at runs per over as that would have more variability compared to runs per ball and it be easier to observe the strategies of the winning team through that.
--->
-
-<!-- Making it short -->
-
-<!-- First, we look at the distribution of runs (measured variable) across over-of-inning (circular granularity) and match-of-season (aperiodic cyclic granularity) in \autoref{fig:seas-over-inning}.
-The distribution of runs per over has not significantly changed from 2008 to 2016.
-There is no clear pattern/trend that runs per over is increasing or decreasing across seasons.
-Hence, we work with subsets of seasons to answer some of the questions: -->
-
-First, it would be interesting to see if the distribution of total runs vary depending on if a team bats in the first or second innings.
-The Mumbai Indians (MI) and Chennai Super kings (CSK) <!--are considered one of the best teams in IPL with multiple winning titles and --> appeared in final playoffs from 2010 to 2015.
-We take their example in order to dive deeper into this question.
-<!--Circular granularities "over-of-inning" and "inning-of-match" can be computed using \ref{sec:circular-gran-def} with over as index of the tsibble.--> From Figure \ref{fig:cricex}(a), it can be observed that for the team batting in the first inning there is an upward trend of runs per over, while there is no clear upward trend in median and quartile deviation of runs for the teams batting in the second inning.
-This seem to indicate that players feel mounting pressure to score more runs as they approach towards the end of the first inning.
-Whereas teams batting in the second inning have a set target in mind and are not subjected to such mounting pressure and may adopt a more conservative strategy, to score runs.
-Thus winning teams like CSK and MI seem to employ different inning strategies when it comes to their batting order.
-
-<!-- Also longer and more distinct letter values in the second innings suggests that the variability is more in the second innings. -->
-<!-- - Q1: How their run rates vary depending on if they bat first or 2nd? Is there a chance that they are more likely to win if they bat first? -->
-
-<!-- - Q2: Which team is more consistent in their approach in terms of run rate across different overs of the innings? -->
-
-<!-- # ```{r seas-over-inning, fig.cap = "Quantile plot of runs per over across overs of different seasons. There is no pattern on increase or decrease of runs across overs for seasons."} -->
-<!-- #   cricket_tsibble_all %>%  -->
-<!-- #   prob_plot("over",  -->
-<!-- #             "season", -->
-<!-- #             hierarchy_model, -->
-<!-- #             response = "runs_per_over", -->
-<!-- #             plot_type = "quantile", -->
-<!-- #             quantile_prob = c(0.25, 0.5, 0.75),  -->
-<!-- #             symmetric = FALSE)  + -->
-<!-- #      theme( # remove the vertical grid lines -->
-<!-- #             panel.grid.major.x = element_blank() , -->
-<!-- #             # explicitly set the horizontal lines (or they will disappear too) -->
-<!-- #             panel.grid.major.y = element_blank()) + scale_x_discrete(breaks = seq(2008, 2016, 3)) -->
-<!-- # ``` -->
-
-Another interesting question could be: do runs per over decrease in the subsequent over if fielding (defending) was good in the previous over?
-For establishing the fielding quality, we apply an indicator function on dismissals (1 if there was at least one wicket in the previous over due to run out or catch, 0 otherwise).
-Runs in the current over is then the observation variable.
-<!--If a batsman is bowled out, it does not necessarily signify good fielding.
-So we only include number of catches and run out in an over as a measure of good fielding.
-Difference in runs across overs are likely to be negative if good fielding has an impact on the runs scored in the subsequent overs.
---> Dismissals in the previous over can lead to a batsman adopting a more defensive play style.
-Figure \ref{fig:cricex}(b) shows that no dismissals in the previous over leads to a higher median and quartile spread of runs per over as compared to the case when there has been at least one dismissal in the previous over.
-
-<!-- Difference in runs across over should be negative if good fielding has an impact on the runs scored in the subsequent overs.  -->
-
-<!-- fetching raw data since dot and fielding information not available in dismissal type not available in cricket data gravitas. Also `cricket` is aggregated across overs -->
-
-```{r cricex, fig.cap= "Runs per over shown with different distribution displays, and granularities.
-Plot (a) shows letter value plot across overs faceted by innings.
-For the team batting in the first innings there is an upward trend of runs per over, while there is no such pattern of runs for the teams batting in the second innings.
-Plot (b) shows quantile plot of runs per over across an indicator of wickets in previous over faceted by current over.
-This indicates that at least one wicket in the previous over leads to lower median run rate and quartile spread in the subsequent over.", warning = FALSE, message = FALSE, out.width = "90%"}
-
-library(tsibble)
-cricket_tsibble <- cricket %>%
-  mutate(data_index = row_number()) %>%
-  as_tsibble(index = data_index)
-
-hierarchy_model <- tibble::tibble(
-  units = c("index", "over", "inning", "match"),
-  convert_fct = c(1, 20, 2, 1)
-)
-
-cricket_tsibble %>%
-  filter(batting_team %in% c(
-    "Mumbai Indians",
-    "Chennai Super Kings"
-  )) %>%
-  mutate(inning = paste0("innings: ", inning)) %>%
-  prob_plot("inning",
-    "over",
-    response = "runs_per_over",
-    hierarchy_model,
-    plot_type = "lv"
-  ) +
-  scale_fill_brewer(palette = "Dark2") +
-  #ggtitle("(a) Runs per over across over faceted by inning") +
-  theme(legend.position = "right") +
-  ggtitle("a") +
-  ylab("runs per over") +
-  xlab("overs of the innings") +
-  theme(plot.title = element_text(face = "bold")) +
-  ggplot2::theme(
-       strip.text = ggplot2::element_text(
-        size = 10,
-         margin = ggplot2::margin(b=0, t=0)
-      )
-     ) +  theme_minimal() 
-#geom_smooth(aes( x = over,
-#                               y=runs_per_over), method = lm, #formula = y ~ splines::bs(x, 3), se = FALSE)
-
-library(tsibble)
-
-cricket_all <- read_csv("paper/data-raw/deliveries_all.csv")
-matches_all <- read_csv("paper/data-raw/matches_all.csv")
-
-cricket_season <- cricket_all %>% left_join(matches_all, by = c("match_id" = "id"))
-
-# cricket_per_over <- cricket_season %>%
-#   group_by(season,
-#            match_id,
-#            batting_team,
-#            bowling_team,
-#            inning,
-#            over) %>%
-#   summarise(runs_per_over = sum(total_runs),
-#             run_rate = sum(total_runs)/length(total_runs))
-#
-# cricket_tsibble_all <- cricket_per_over %>%
-#   ungroup() %>%
-#   mutate(data_index = row_number()) %>%
-#   as_tsibble(index = data_index)
-
-cricket_dot_field <- cricket_season %>%
-  mutate(
-    fielding_proxy = if_else(dismissal_kind %in%
-      c("caught", "caught and bowled"), 1, 0),
-    dot_ball_proxy = if_else(total_runs == 0, 1, 0),
-    wicket_proxy = if_else(is.na(dismissal_kind), 0, 1)
-  ) %>%
-  group_by(
-    season,
-    match_id,
-    batting_team,
-    bowling_team,
-    inning,
-    over
-  ) %>%
-  summarise(
-    runs_per_over = sum(total_runs),
-    run_rate = sum(total_runs)*6 / length(total_runs),
-    fielding_wckts = sum(fielding_proxy),
-    dot_balls = sum(dot_ball_proxy)
-  ) %>%
-  mutate(diff_run_rate = c(0, diff(run_rate)))
-
-cricket_tsibble <- cricket_dot_field %>%
-  ungroup() %>%
-  mutate(data_index = row_number()) %>%
-  as_tsibble(index = data_index)
-
-cricket_data <- cricket_tsibble %>%
-  mutate(
-    field = if_else(fielding_wckts == 0, "0", "1+"),
-    dot = if_else(dot_balls == 0, "no dot balls", ">0 dot balls"),
-    lag_field = lag(field),
-    lag_dot = lag(dot)
-  ) %>%
-  filter(lag_field != 0, lag_dot != 0)
-
-cricket_data$lag_field <- factor(cricket_data$field, levels = c("0", "1+"))
-
-# filter(fielding_wckts %in% c(0,1)) %>%
-#
- cricket_data %>%
-  filter(over!=1) %>%
-  prob_plot("over", "lag_field",
-  hierarchy_model,
-  response = "run_rate",
-  plot_type = "quantile",
-  symmetric = FALSE,
- quantile_prob = c(0.25, 0.5, 0.75)) +
-   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") +
-  ylab("runs per over")  +
-  xlab("number of wickets in previous over") +
-  ggtitle("b") +
-   theme(plot.title = element_text(face = "bold")) +
-        theme(axis.ticks = element_blank(), legend.background = element_blank(),
-            legend.key = element_blank(), panel.background = element_blank(), strip.background = element_blank(),
-            plot.background = element_blank(), complete = TRUE, panel.grid.major = element_line(colour = "#E0E0E0"),
-            panel.border = element_rect(colour = "#E0E0E0", fill = NA))
-```
-
-<!-- Q2: Among good fielding and bowling - which affect the runs of the subsequent overs more? -->
-
-<!-- Q3: Are runs set to reduce in the next over for dot balls in the previous over? -->
-
-<!-- A dot ball is a delivery bowled without any runs scored off it.
-The number of dot balls is reflective of the quality of bowling in the game.
-Run rate of an over should ideally decrease if the number of dot balls increase.
-However, what is the effect of dot balls on runs scored in the subsequent over.
-Will players batsman likely to go for big shots because they couldn't score good runs in the previous over?
-Or they should play consistently and avoid scoring high?
-Figure \ref{fig:exdot} shows the quantile plot of runs across overs for at least one dot ball per over (facet 1) or no dot balls per over (facet 2).
--->
-<!-- With at least one dot balls per over, the distribution of run rates in facet 1 increase slower compared to that in facet 2.
-This implies that run rates are likely to decrease in the subsequent over as a result of dot balls in the previous over.
--->
-
-<!-- ```{r exdot, fig.cap="25th, 50th, 75th quantiles of runs per over are drawn across overs of the innings with no (facet 2), more than zero (facet 1) dot balls per over.
-For all quantiles, run rates mostly increase at a higher rate in facet 2 compared to facet 1 implying run rates decrease with at least one dot ball in the previous over.", fig.pos="ht"} -->
-
-<!-- cricket_data %>% -->
-<!--   # filter(dot_balls %in% c(0, 1, 2)) %>% -->
-<!--   prob_plot("lag_dot", -->
-<!--     "over", -->
-<!--     hierarchy_model, -->
-<!--     response = "run_rate", -->
-<!--     plot_type = "quantile", -->
-<!--     quantile_prob = c(0.25, 0.5, 0.75), -->
-<!--     symmetric = FALSE -->
-<!--   ) + ggtitle("") -->
-<!-- ``` -->
-
-Wickets per over are considered as an aperiodic cyclic granularity with wickets as an aperiodic linear granularity.
-These granularities do not appear in the hierarchy table since it is difficult to position them in a hierarchy.
-These are similar to holidays or special events in temporal data.
-<!-- CONTENT CUT -->
-<!--While any special event that corresponds to a time domain can be treated as an aperiodic linear granularity in a temporal xacase, dot balls or wickets that corresponds to certain balls (index) could be treated as aperiodic events in cricket.-->
-
-# Discussion points and future work
-
-Exploratory data analysis involve many iterations of finding and summarizing patterns.
-With temporal data available at ever finer scales, exploring periodicity has become overwhelming with so many possible granularities to explore.
-This work refines the selection of appropriate pairs of granularities by identifying those for which the differences between the displayed distributions is greatest, and rating these selected harmony pairs in order of importance for exploration.
-
-A future direction of work could be to look at more individuals/subjects and group them according to similar periodic behavior.
-Behaviors across different cyclic granularities would be different for different subjects and one way to find groups would be to actually locate clusters who have similar periodic behavior.
-
-<!-- patterns are interesting and others are not.
-The subjects for which behaviors across a group of cyclic granularities are similar, could be grouped together as their periodic behavior is similar.
-to group subjects  -->
-
-# Appendix
-
-## Null distribution
-
-### Size: Simulated same distribution for all combinations of categories for all harmony pairs.
-
-Failure to reject the null hypothesis when there is in fact no significant effect.
-
-### Normalised maximum distances follow standard Gumbel distribution
-
-### Limiting distribution of median of normalised maximum distances is normal
-
-Let a continuous population be given with cdf F(x) (cumulative distribution function) and median $\xi$ (assumed to exist uniquely).
-For a sample of size $2n + 1$, let $\tilde{x}$ denote the sample median.
-The distribution of $\tilde{x}$,under certain conditions, to be asymptotically normal with mean $\xi$ and variance $\sigma_n^2 = \frac{1}{4} [f(\xi)]^2(2n + 1)$, where $f(x) = F'(x)$ is the pdf (probability density function).
-
-<!-- ### Confidence interval of test statistic -->
-
-## Power
-
-## Confidence interval
-
-Failure to reject the null hypothesis when there is in fact a significant effect.
-
-To estimate the sampling distribution of the test statistic we need many samples generated under the null hypothesis.
-If the null hypothesis is true, changing the exposure would have no effect on the outcome.
-By randomly shuffling the exposures we can make up as many data sets as we like.
-If the null hypothesis is true the shuffled data sets should look like the real data, otherwise they should look different from the
-real data. The ranking of the real test statistic among the shuffled test statistics gives a p-value.
-
-<!-- Consider two cyclic granularities $A$ and $B$ with $2$ and $3$categories.
-Thus, the harmony table consisting of all possible harmony pairs (assuming all pairs are harmonies), would look like the following: -->
-
-```{r harmony_min}
-# harmonies <- tibble::tibble(facet_variable = c("A", "B", "A", "C", "B", "C"),
-#                             x_variable  = c("B","A", "C", "A", "C", "B"),
-#                             facet_levels = c(2, 3, 2, 4, 3, 4),
-#                             x_levels = c(3, 2, 4, 2, 4, 3))
-# 
-# harmonies <- tibble::tibble(facet_variable = c("A", "B"),
-#                             x_variable  = c("B","A"),
-#                             facet_levels = c(2, 3),
-#                             x_levels = c(3, 2))
-#                             
-# harmonies %>% knitr::kable()
-```
-
-<!-- The output table has the value of MMPD (normalized median maximum pairwise distances), gt_MMPD(global threshold of MMPD indicator). -->
-
-<!-- # ```{r samenull_2by4, eval = FALSE} -->
-<!-- #  -->
-<!-- # ``` -->
-
-<!-- # ```{r normalv21_power} -->
-<!-- #  -->
-<!-- # ``` -->
-<!-- #  -->
-<!-- #  -->
-<!-- # ```{r normalv22_power} -->
-<!-- #  -->
-<!-- # ``` -->
-
-### Varying distribution across facet
-### Varying distribution across x-axis
-### Varying distribution across both facets and x-axis
-### Repeat all with varying facet and x-axis levels
-
-<!-- ### Power: Simulated same distribution for all combinations of categories for all harmony pairs. -->
-
-<!-- # ```{r normalv23_power} -->
-<!-- #  -->
-<!-- # ``` -->
-<!-- #  -->
-<!-- #  -->
-<!-- # ```{r normalv24_power} -->
-<!-- #  -->
-<!-- # ``` -->
-
-*Conclusion*: The test should reject the null hypothesis if distributions are different.
-
-<!-- ### Scenario 2: Simulated different distributions for all combinations of categories for harmony pairs for few levels. -->
-
-<!-- ```{r diffnull_2by4, eval = FALSE} -->
-
-<!-- ``` -->
-
-<!-- *Conclusion*: The test select the harmony pair for which distribution of x-axis categories are significantly different -->
-
-<!-- ### Scenario 3: Simulated different distributions for all combinations of categories for all harmony pairs with many levels. -->
-
-<!-- ```{r diffnull_7by11, eval = FALSE} -->
-<!-- ``` -->
-
-<!-- *Conclusion*: The test indicates that both harmony pairs do not have significant variation. -->
-
-<!-- ### Scenario 4: Simulated different distributions for all combinations of categories for all harmony pairs with many levels - very different distribution across x-axis -->
-
-<!-- ```{r diffnull_7by11normal, eval = FALSE} -->
-<!-- ``` -->
-
-<!-- *Conclusion*: The test indicates that only the first harmony pair has significant variation. -->
-
-<!-- ### Scenario 5: Simulated different distributions for all combinations of categories for all harmony pairs with many levels - very different distribution across facets -->
-
-<!-- ```{r diffnull_7by11normal2, eval = FALSE} -->
-<!-- ``` -->
-
-<!-- *Conclusion*:  -->
-
-<!-- ## Scenario 4: Cumulative 3 levels with 2, 7 and 11 and testing level and power -->
-
-<!-- ```{r samenull_3levels} -->
-
-<!-- ``` -->
-
-<!-- *Conclusion*: With 3 levels the test incorrectly chooses 1 harmony pair with similar distribution. The harmony pair which is displayed. -->
-
-<!-- <!-- ```{r diffnull_3levels} -->
-
-<!-- <!-- ``` -->
-
-<!-- *Conclusion*: The test with MMPD selects just one pair, as opposed to the test with maximum.
-This needs to be checked against what we expect from the test.
-The harmony pairs which are selected (either through MMPD or maximum) are displayed.
--->
-
-<!-- # ```{r} -->
-<!-- # harmonies <- tibble::tibble(facet_variable = c("A", "B"),x_variable  = c("B","A"), facet_levels = c(2, 3),x_levels = c(3, 2)) -->
-<!-- #  -->
-<!-- # har1 <- harmonies[1,] -->
-<!-- #  -->
-<!-- # sim_dist1 = c(rep(distributional::dist_normal(mu = 10, sigma = 5),2),rep(distributional::dist_exponential(10),2), rep(distributional::dist_weibull(0.5, 2),2)) -->
-<!-- #  -->
-<!-- # data1 <- sim_distharmony1(har1, sim_dist = sim_dist1) -->
-<!-- # data1 -->
-<!-- #  -->
-<!-- # data1 %>% unnest(sim_dist) %>% -->
-<!-- #   ggplot(aes(x = Var2, y = sim_dist)) + -->
-<!-- #   facet_wrap(~Var1) + geom_boxplot() + ggtitle("Same distribution 2 by 3") -->
-<!-- #  -->
-<!-- # response = "sim_dist" -->
-<!-- #  -->
-<!-- # MMPD_distribution <- data1 %>% -->
-<!-- #   select(-dist) %>%  -->
-<!-- #   unnest(sim_dist) %>%  -->
-<!-- #   list() %>%  -->
-<!-- #   global_threshold(harmony_tbl = har1, -->
-<!-- #                    response = "sim_dist", -->
-<!-- #                    dist_distribution = "normal", -->
-<!-- #                    dist_ordered = TRUE, -->
-<!-- #                    create_gran_data = FALSE, nsamp = 20) -->
-<!-- #  -->
-<!-- # # as_tibble(sample_MMPD) %>% mutate(id = row_number()) %>%  -->
-<!-- # #   ggplot() + geom_histogram(aes(x = value)) -->
-<!-- #  -->
-<!-- # ``` -->
-<!-- #  -->
-
-<!-- # Visualisation -->
-
-<!-- Leader plots like in Scagnostics paper -->

### 2021-01-20 simulations/supplementary/sim_table/simtable.R

@@ -1,0 +1,31 @@
+### This code creates a table of data for different simulations scenarios ###
+library(tidyverse)
+# nperm and nsim can run parallelly
+sim_table <- expand.grid(#data = c(99, 9999), # different data with same specifications
+  #nperm = c(10, 30, 50, 100, 300, 500),
+  nperm = c(10, 30, 500),
+  #ntimes = c(2, 5, 10, 30, 100, 500),
+  ntimes = c(5, 500),
+  # different permutations to compute mean and sd
+  #nobs_each_comb  = c(10, 40, 500), # different number of observations for each combinations for each panel
+  #nobs_diff_comb  = c("comb1", "comb2"), # different number of observations for different combinations for each panel
+  #nsim = c(100, 500), # number of simulations of the entire exercise to compute distribution and CI of MMPD 
+  #dist = c("N01", "N05", "N51", "N55", "G01", "G21"), #
+  dist = c("N01"), #distributions from where data is generated
+   nfacet = c(5, 7, 14, 20, 31), # range of facet levels 
+  # 50 removed for now
+   #nfacet = c(2, 3),
+   #nx = c(2, 3)
+   nx = c(5, 7, 14, 20, 31), # range of x levels
+  design = c("null", "vary_x", "vary_f", "vary_all"),
+  #seed = seq(1500, 7500, 1000),
+  seed = c(1500),
+  w = c(seq(1, 20, 7), 50),
+  type = c("raw", "norm-nperm")
+             
+) %>% tibble()
+
+
+#Export as .csv
+
+write_csv(sim_table, here::here('simulations/supplementary/sim_table/sim_table.csv'))

### 2021-01-20 paper/main.Rmd
removed behavior of raw wpd

--- 2021-01-13 paper/main.Rmd
@@
 
-# Distance measure
+# The distance measure
 
 We are interested in assessing structure in probability distributions of the measured variable across bivariate cyclic granularities.
-We propose a measure called Median Maximum Pairwise Distances (MMPD) to evaluate structure in such a design.
+We propose a measure called Median Maximum Pairwise Distances (wpd) to evaluate structure in such a design.
 
@@
 
-# Behavior of raw wpd (weighted pairwise distances)
-
-Most of the behavior of the measure wpd was studied via simulation.
-The simulations explore how wpd performs under various designs and parameters and its limitations.
-To study the behavior of wpd, simulations were carried out for four different designs and the following factors that could potentially have an impact on the values of wpd:
-
-<!-- Numerous simulations were carried out in a wide range of scenarios. -->
-
-<!-- Same scenarios were used, when possible with normalized wpd, keeping all other simulation variables constant. -->
-
-- $nx$ (number of levels of x-axis)
-- $nfacet$ (number of levels of facets)
-- $\lambda$ (tuning parameter)
-- $\omega$ (increment in each panel design)
-- $dist$ (normal/non-normal distributions with different location and scale)
-- $n$ (sample size for each combination of categories)
-- $nsim$ (number of simulations)
-- $nperm$ (number of permutations of data)  
-- $designs$  
-$D_{null}$  (No difference in distribution)  
-$D_{var_f}$ (Difference in distribution only across facets)  
-$D_{var_x}$ (Difference in distribution only across x-axis)  
-$D_{var_{all}}$ (Difference in distribution in both facets and x-axis)
-
-```{r simtable, eval = FALSE}
-variable = c("nx", "nfacet", "lambda", "omega", "dist", "n", "nsim", "nperm", "design")
-
-description = c("number of levels of x-axis", "number of levels of facets",
-                "tuning parameter","increment in each panel design", "normal/non-normal distributions with different location and scale", "sample size", "number of simulations", "number of permutations of data",
-                "$D_{null}$ (No difference in distribution), $D_{var_f}$ (Difference in distribution only across facets), $D_{var_x}$ (Difference in distribution only across x-axis), $D_{var_all}$ (Difference in distribution in both facets and x-axis)")
-table = tibble::tibble(variable, description)
-
-table %>% 
-knitr::kable(format = "latex",
-             escape = TRUE) %>% 
-  kableExtra::kable_styling(
-    bootstrap_options = "striped", 
-    full_width = F, 
-    font_size = 7)
-
-```
-
-## Null design
-
-This section explores the behavior of wpd in designs where there is no difference in distribution between x and facet categories.
-We have considered different initial distributions to study the impact of initial distribution under the null setup.
-Since the measure wpd is essentially set up to detect differences in distributions irrespective of underlying distribution, it would be ideal if it has minimal dependency on the type, location and scale of the initial distribution.
-To that end, some pre-processing of the data is preferred to bring it to the same scale, location and type.
-The Normal Score Transform or NQT has been applied in various fields of geo-statistics in order to make most asymmetrical distributed real world measured variables more
-treatable and normal-like.
-
-Following the work of Krzysztofowicz (1997) the empirical NQT involves the following steps:
-1. Sort the sample of measured variable $X$ from the smallest to the largest observation $x_{(1)},\dots, x_{(i)}, .., x_{(n)}$.
-2. Estimate the cumulative probabilities $p_{(1)},\dots, p_{(i)}, .., p_{(n)}$.
-using a plotting position like $i/(n + 1)$ such that $p_{(i)} = P(X \leq x_{(i)})$.
-3. Transforming each observation $x_(i)$ of $X$ into observation $y(i) = Q^{-1}(p(i))$ of the standard normal variate $Y$ , with $Q$ denoting the standard normal distribution and
-$Q^{-1}$ its inverse, applying discrete mapping.
-
-Further, we want to study the distribution of wpd for different $nx$ and $nfacet$.
-
-### Simulation setup
-
-<!-- Study the behavior of wpd under different initial distributions for different $nx$ and $nfacet$ -->
-
-Using two types of distributions, viz.
-normal and gamma (non-normal), we generated observations for each combination of $nx$ and $nfacet$ from the following sets: $nx = \{2, 3, 5, 7, 14, 20, 31, 50\}$ and $nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
-Each combination is being referred to as a _panel_.
-That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$.
-For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
-That is, if we consider the panel  $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
-The values of $\lambda$ is set to $0.67$, since we want to up-weigh the within-facet distances and that of $\omega$ is set to $0$, since there is no significant differences between distributions in the null case.
-Observations were generated for each type of distribution changing the shape and scale to study the effect of shape, scale and type of distribution on wpd.
-The set of distributions considered for this purpose is ${N(0,1), N(5, 1), N(0,5), \Gamma(0.5, 1), \Gamma(2, 1)}$.
-Each of the scenario is run $nsim = 200$ times to see the distribution of wpd values for each scenario.
-
-<!-- wpd is computed for different normal and non-normal distributions to see how the underlying distribution has a role to play in the value of wpd.
-Since we are concerned with detecting the differences in distributions, it would be ideal if wpd has minimal dependency on the type, location and scale of the  underlying distribution.
-To that end, some pre-processing of the data is preferred to bring it to the same scale, location and type.
--->
-
-<!-- Null design only where all combinations are equal for fixed values of $\mu$ and $\sigma$ -->
-<!-- Dist 1: $N(0,1)$ individual graph -->
-<!-- Dist 2: $N(\mu, 1)$ (faceted with different values of $\mu$: not yet just for one value now) -->
-<!-- Dist 3: $N(0, \sigma)$ (faceted with different values of $\sigma$: not yet just for one value now) -->
-<!-- Dist 4: $N(\mu, \sigma)$ faceted with different values of mu and sigma, for all levels of x and facet to see how value of wpd changes with that of change in parameters. -->
-
-<!-- **Assumptions:** There is no difference in distribution between any facet or x-category -->
-<!-- nsim = 200 -->
-<!-- lambda = 0.67 -->
-
-<!-- **Questions:**  -->
-<!-- - How raw value of wpd changes with different nx and nfacet for different location and scale of a Normal and non-normal distribution -->
-
-Figure \ref{fig:normal-diff-quantrans} and \ref{fig:gamma-diff-quantrans} show distribution of wpd for different initial normal and gamma distribution to study the effect of changing location and scale on the distribution of wpd.
-It seems like the  distribution changes across different facet and x levels but look the same for each panel, which implies wpd value is unaffected by the change in location and scale of the the normal distribution.
-Figure \ref{fig:mean-sd-ns-nfacet} shows how mean and sd of the distribution of wpd changes with the increasing x and facet levels.
-It seems like both mean and standard deviation are affected more by change in the x-axis levels than the facet levels.
-Figure \ref{fig:nxbyfacet-ridge-N05} gives another way to look at the effect of changing facet and x levels on the distribution of wpd for an initial distribution $N(0,5)$.
-Clearly, the location of the distribution shifts to the right for increasing x levels and scale is different for low and high values of facet levels with a longer left tail for lower facet levels.
-We have considered alternate distribution, location and scale for this simulation setting, but do not present the results as they are behaviorally similar.
-
-<!-- # ```{r normal-diff, fig.cap="Ridge plots of raw wpd is shown for N(0,1) and N(5,1) distribution.
-The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change in mean and standard deviation of the normal distribution", eval = FALSE} -->
-<!-- # knitr::include_graphics(here::here("simulations/null_design/figs/normal_ridge_nxbynfacet_wpd_N01.png")) -->
-<!-- # ``` -->
-
-```{r normal-diff-quantrans, fig.cap = "Ridge plots of raw wpd is shown for N(0,1), N(5,1) and N(0,5) distribution.
-The densities change across different facet and x levels but look same for each panel, which implies wpd value is unaffected by the change in mean and standard deviation of the normal distribution"}
-knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_normal.png"))
-```
-
-```{r gamma-diff-quantrans, fig.cap="Ridge plots of raw wpd is shown for Gamma(0.5,1), Gamma(2,1) distribution.
-The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change in the shape paramter of the gamma distribution"}
-knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_gamma.png"))
-```
-
-```{r mean-sd-ns-nfacet, fig.cap="Movement of mean and sd for raw wpd is shown for different number of levels (nlevel) of x-axis and facets through line plots.
-Mean increases and sd decreases more sharply for increasing x-axis levels as compared to facet levels.
-It seems like both mean and standard deviation are affected more by change in the x-axis levels than the facet levels.", fig.pos="h"}
-knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/mean_sd_nx_nfacet.png"))
-
-```
-
-```{r nxbyfacet-ridge-N05, fig.cap="Ridge plots of raw wpd is shown for N(0,5) distribution.
-For each panel, it could be seen that the location shifts to the right for increasing x levels.
-Across each panel, the scale of the distribution seems to change for low/moderately lower values and higher values of nfacets and left tails are longer for lower facet levels."}
-knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/nxbyfacet_ridge_wpd_N05.png"))
-```
-
-```{r gamma-diff, fig.cap="Ridge plots of raw wpd is shown for G(0.5,1) and G(2,1) distribution.
-The densities change across different facet and x levels and also for the two distributions, which implies wpd value is affected by the change in location value when distributions are not normal.", eval = FALSE}
-knitr::include_graphics(here::here("simulations/null_design/figs/gamma_ridge_nxbynfacet.png"))
-```
-
-```{r gamma-diff-trans, fig.cap="Ridge plots of raw wpd is shown for G(0.5,1) and G(2,1) distribution after quantile transformation looks similar and hence is unaffected by change in location.", fig.pos="h"}
-knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_gamma.png"))
-```
-
-<!-- ### Choice of alternate designs -->
-
-<!-- A normal distribution is taken for this purpose. We would calibrate the values of $WPD$ for different designs illustrated in Section \ref{sec:idea}. -->
-
-<!-- $$\mu_{j.} = \mu + j\omega$$ -->
-<!-- or, $$\mu_{.k} = \mu + k\omega$$ where,    -->
-<!-- $j$ and $k$ are the index of the x and facet category respectively  -->
-<!-- $\mu$ is the mean of the first category and $\omega$ is the increment from the starting value. -->
-
-<!-- mean = 0 -->
-<!-- range_mean = c(0, 1, 3,  5, 7, 15, 20) -->
-<!-- sd = 1 -->
-<!-- range_sd = c(1, 3,  5, 7, 15, 20) -->
-<!-- range_w =  c(1, 2, 3, 4, 5) -->
-<!-- range_lambda = seq(0.1, 0.9, 0.05) -->
-
-## Alternate designs
-
-This section explores the behavior of wpd in designs where there is infact difference in distribution between facet categories ($D_{var_f}$) or across x-categories ($D_{var_x}$) or both ($D_{var_{all}}$).
-Since it is established in the last section that after preprocessing the data through NQT, the initial distribution does not have a role to play in the values of wpd, we proceed with a N(0,1) distribution only.
-Supposably, the tuning parameter ($\lambda$) and increment parameter ($\omega$) should impact the values of wpd.
-
-### Simulation setup
-
-Using $\omega =  \{1, 2, \dots, 10\}$ and $\lambda = seq(from  = 0.1, to = 0.9, by = 0.05)$, observations are drawn from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet =  \{2, 3, 5, 7, 14, 20, 31, 50\}$.
-$ntimes = 500$ is assumed for this setup as well.
-Furthermore, to generate different distributions across different combination of facet and x levels, the following method is deployed - suppose the distribution of the combination of first levels of x and facet category is $N(\mu,\sigma)$ and $\mu_{jk}$ denotes the mean of the combination $(a_jb_k)$, then $\mu_{j.} = \mu + j\omega$ (for design $D_{var_x}$) and $\mu_{.k} = \mu + k\omega$ (for design $D_{var_f}$).
-Table \ref{tab:explain-design} shows an example of how initial distributions are assigned in a panel with $nfacet = 3$ and $nx = 2$ for different designs using $\omega = 1$.
-
-```{r explain-design}
-sim_varx_normal = function(nx, nfacet, mean, sd, w)
-{
-  rep(dist_normal((mean + seq(0, nx-1, by  = 1)*w), sd), nfacet)
-}
-
-sim_varf_normal = function(nx, nfacet, mean, sd, w)
-{
-  rep(dist_normal((mean + seq(0, nfacet-1, by  = 1)*w), sd), each = nx)
-}
-  sim_varall_normal = function(nx, nfacet, mean, sd, w)
-  {
-    dist_normal((mean + seq(0, (nx*nfacet - 1), by  = 1)*w), sd)
-  }
-
-mean = 0
-sd = 1
-w = 1
-nx = 2
-nfacet = 3
-
-raw_levels = expand.grid(facet = c("$b_1$", "$b_2$", "$b_3$"),
-                         x = c("$a_1$", "$a_2$"))
-
-facet = rep(c("$b_1$", "$b_2$", "$b_3$"), each = nx)
-x =  rep(c("$a_1$", "$a_2$"), nfacet)
-
-vary_f <-  sim_varf_normal(nx, nfacet, mean, sd, w) %>% tibble()
-vary_x <-  sim_varx_normal(nx, nfacet, mean, sd, w) %>% tibble()
-vary_all <-  sim_varall_normal(nx, nfacet, mean, sd, w) %>% tibble()
-
-raw_table <- bind_cols(x = x, 
-                       facet = facet, 
-                       vary_f = vary_f, 
-                       vary_x = vary_x, 
-                       vary_all = vary_all) %>% 
-  tibble() 
-names(raw_table) = c("x", "facet", "$D_{var_f}$", "$D_{var_x}$", "$D_{var_{all}}$" )
-raw_table %>% 
-  kable(format = "latex",
-    booktabs = TRUE, 
-    escape = FALSE,
-    caption = "Simulation setup for a panel with 3 facet levels and 2 x-axis levels for different designs starting from an initial distribution N(0, 1) for the combination $(a_1, b_1)$.") %>% kable_styling()
-```
-
-<!--  - Exploring the effect of tuning parameter $\lambda$: -->
-
-We now discuss the effect of different tuning parameters $\lambda$ and $\omega$ with the help of two alternate designs ($D_{var_x}$ and $D_{var_f}$).
-Figure \ref{fig:tuning-one-omega} displays different values of $\lambda$ for a relatively small and higher $\omega$ for $nx = nfacet =  \{2, 3, 5, 7, 9\}$.
-The $\lambda$ for which the two designs intersect will then be chosen as the optimal $\lambda$ that could then be weighed appropriately to up-weigh the within-facet distances and down-weigh the between-facet distances.
-The design $D_{var_x}$ increases linearly with increasing $\lambda$, whereas $D_{var_f}$ decreases linearly with increasing $\lambda$.
-This is expected as wpd has a linear relationship with $\lambda$ by construction.
-The two designs mostly intersect at $\lambda = 0.5$ for a higher value of $\omega$.
-\autoref{fig:tuning-parameter-intersection} shows how the value of $\lambda$ changes with increasing $\omega$ for $\omega =  \{1, 2, \dots, 10\}$ and $\lambda = seq(from  = 0.1, to = 0.9, by = 0.05)$.
-
-<!-- Assumptions: The initial combination has a $N(\mu,\sigma)$ distribution and then every combination increases as follows: -->
-<!-- - $$\mu_{j.} = \mu + j\omega$$ (for design vary_x) -->
-<!-- - $$\mu_{.k} = \mu + k\omega$$ (for design vary_f) -->
-<!-- Value of the parameters chosen for this simulation are $\mu = 0$, $\sigma = 1$ and $\omega = {1, 2, \dots, 10}$ -->
-
-```{r tuning-one-omega, fig.caption = "WPD from two designs are plotted for different values of lambda for different x and facet categories.
-For omega = 1, the designs intersect for 0.6<lamba<=0.75, whereas for higher omega, design intersects at lambda = 0.5"}
-knitr::include_graphics(here::here("simulations/tuning_param/figs/fixed_omega.png"))
-```
-
-```{r tuning-parameter-intersection, fig.cap="For most panels it is observed that the most common value of the tuning paramter for which the designs interact is 0.5, which implies any value greater than 0.5 could be chosen to up-weigh the within-facet distances and down-weigh the between-facet distances for most sitatuions."}
-knitr::include_graphics(here::here("simulations/tuning_param/figs/intersection_plot.png"))
-```
-
-How value of lambda changes with increasing omega and mean for fixed nx, nfacet and standard deviation?
-
-```{r lambda-omega-mean, eval = FALSE}
-knitr::include_graphics(here::here("simulations/result_report/lambda_omega_mean_3_2.png"))
-```
-
-How value of lambda changes with increasing omega and sd for fixed nx, nfacet and mean?
-
-```{r lambda-omega-sd, eval = FALSE}
-knitr::include_graphics(here::here("simulations/result_report/lambda_omega_sd_3_2.png"))
-```
-
-```{r lamba-omega-alternate-design}
-knitr::include_graphics((here::here("simulations/result_report/wpd_alterate_designs.png")))
-```
-
- Distribution across facet and x categories
-<!-- ### Need for normalisation -->
-
-From Figure \ref{fig:dist-across-facets} and \ref{fig:dist-across-x} shows the MMPD distribution is different for different levels of facets and x-axis levels.
-With increasing number of facets, the location of the distribution shift rightwards and with increasing x-axis levels, the scale of the distribution reduces.
-
-Median and maximum distances are affected by the number of categories considered and hence the distance measure $MMPD_{raw}$, which is a combination of median and maximum would also be influenced by the number of levels.
-It would have higher values if $C_i$ or $C_j$ has higher levels.
-We would ideally want a higher value of the measure if there is significant difference between distributions across facet or x-axis categories, and not because the number of categories are higher.
-In Figures \ref{fig:dist-across-facets} and \ref{fig:dist-across-x}, both the cyclic granularities $C_i$ and $C_j$ are considered such that their levels vary in the range $(2, 5,7 ,9, 14, 21, 30, 45)$.
-Each of these combinations is considered a panel for each of which $MMPD_{raw}$ has been constructed $100$ times to compute the distribution.
-<!--More specifically, Figure \ref{fig:mean-sd-max} shows the marginal contribution of increasing levels of $C_i$ and $C_j$ on distribution of $MMPD_raw$.
-This shows that with the increase in the number of levels of $C_i$, the location of the distribution shift rightward, whereas for increasing x-axis levels, the scale of the distribution decreases.-->
-
-Therefore, in order to compare $MMPD_{raw}$ across different combinations of facet and x-axis levels, we need to eliminate the impact of different levels of the facets and x-axis first and get a normalized measure.
-
-```{r hist-nx-nfacet, eval = FALSE}
-knitr::include_graphics(here::here("simulations/result_report/hist_nxbyfacet.png"))
-```
-
-```{r dist-across-facets, fig.cap = "Distribution of $MMPD_{raw}$ for different facet levels are shown.
-The location of the distribution shifts rightwards implying that as the number of facets increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained.", eval = FALSE}
-here::here()
-knitr::include_graphics(here::here("simulations/result_report","nx_by_facet_raw.png"))
-```
-
-<!-- # ```{r dist-across-facets, fig.cap = "Distribution of $MMPD_{raw}$ for different facet levels are shown.
-The location of the distribution shifts rightwards implying that as the number of facets increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained.
-"} -->
-<!-- # mmpd_raw = read_rds("../hakear-drake/data/data_all23457914n.rds")  -->
-<!-- # mmpd_xmore = read_rds("../hakear-drake/data/data_all213045x.rds")  -->
-<!-- # mmpd_fmore = read_rds("../hakear-drake/data/data_all_213045f_allx.rds") -->
-<!-- #  -->
-<!-- # data_all = bind_rows(mmpd_raw, mmpd_xmore) -->
-<!-- #  -->
-<!-- # data_long = data_all %>% pivot_longer(c(1:2), names_to = "category", values_to = "levels") -->
-<!-- #  -->
-<!-- # g1 <- data_all %>%  -->
-<!-- #   filter(!(nx %in% c(3, 4))) %>%  -->
-<!-- #   ggplot() + -->
-<!-- #   ggridges::geom_density_ridges(aes(x = raw_mmpd,  -->
-<!-- #                                     y = as.factor(nfacet))) + -->
-<!-- #   facet_wrap(~nx, nrow = 2) -->
-<!-- # g1 -->
-<!-- # ``` -->
-
-```{r dist-across-x, fig.cap = "Distribution of $MMPD_{raw}$ for different x levels are shown.
-The scale of the distribution becomes less and less implying that as the number of x levels increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained as the spread of the distribution decreases.
-", eval = FALSE}
-knitr::include_graphics(here::here("simulations/result_report/","nfacet_by_nx_raw.png"))
-```
-
-<!-- # ```{r dist-across-x, fig.cap = "Distribution of $MMPD_{raw}$ for different x levels are shown.
-The scale of the distribution becomes less and less implying that as the number of x levels increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained as the spread of the distribution decreases.
-"} -->
-<!-- # g2 <- data_all %>%  -->
-<!-- #   filter(nfacet<=14, nfacet!=3) %>%  -->
-<!-- #   ggplot() + -->
-<!-- #   geom_boxplot(aes(y = raw_mmpd,  -->
-<!-- #                                     x = as.factor(nx))) + -->
-<!-- #   facet_wrap(~nfacet) + coord_flip() -->
-<!-- #  -->
-<!-- # #  hist_plot = data_all %>%  -->
-<!-- # #       ggplot() + -->
-<!-- # #       geom_density(aes(x = raw_mmpd), fill = "blue") + -->
-<!-- # #       facet_grid(nx~nfacet) -->
-<!-- # # hist_plot -->
-<!-- # g2 -->
-<!-- # ``` -->
-
-<!-- both mean and standard deviation of the distribution of maximum and median varies for different sample sizes ($n$).
-There is a rightward shift in the location and decrease in scale with increasing $n$.
--->
-
-## Sample size
-## Number of permutations
-
-# Normalisation
-
-In an attempt to make the densities \ref{fig:hist_plot} same across different levels, we want to start by making their scale and location same.
-In that regard, we shuffle the data multiple times and compute the sampling distribution of $mmpd_{raw}$ for each combination of facet and x-axis levels.
-
-The null hypothesis is that the two cyclic granularities do not differ on the outcome (i.e., that the outcome is observed independently of treatment assignment).
-When we permute the outcome values during the test, we therefore see all of the possible alternative treatment assignments we could have had and where the mean-difference in our observed data falls relative to all of the differences we could have seen if the outcome was independent of treatment assignment.
-While a permutation test requires that we see all possible permutations of the data (which can become quite large), we can easily conduct “approximate permutation tests” by simply conducting a vary large number of resamples.
-That process should, in expectation, approximate the permutation distribution.
-
-Finally, we run some simulation experiments to see if normalisation works. If normalisation has worked, it should work for both x levle and facet-levels.
-
-Thus these median maximum pairwise distances need to be normalized for different harmonies in a way that eliminates the effect of different levels, consequently enabling comparison across different harmonies.
-The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.
-
-```{r, eval = FALSE}
-knitr::include_graphics(here::here("simulations/null_design/figs/normalised","gamma_ridge_nxbynfacet.png"))
-```
-
-## Methodology
-
-The mean and sd for each combination of facet and x levels could be computed by shuffling the data repeatedly and obtaining the distribution of $MMPD_{raw}$ for different combinations.
-If $MMPD_{raw}$ is then adjusted by the location and scale of this distribution, we could assume that the distribution of the resultant $MMPD_{norm}$ will have same distribution across different combinations of x and facet levels.
-All data is repeatedly shuffled $nperm$ times in random manner to obtain the measure $MMPD_{raw}$.
-Then the $MMPD_{norm}$ is obtained by scaling the observed value by the mean and sd of the distribution of $MMPD_{raw}$ obtained from the permuted data.
-
-\noindent Step 7 in the Algorithm defined in Section \ref{sec:} need to be revised in order to compute $MMPD_{norm}$ instead of $MMPD_{raw}$.
-Step 1-6 stays the same.
-The entire algorithm will have to repeated for all harmony pairs considered in the context.
-
-A simulation study is conducted to see if this methodology is working.
-
-<!-- #### Method 2: -->
-
-<!-- $m' = max_{x}dist$ is obtained for each facet. -->
-<!-- All $x$ levels are shuffled for each facet to obtain several $m'$s.
-Hence $m'$ is normalized for each facet level and the facets are aggregated using $m''= median(m')$, which is basically median(norm(max)).
-We need to normalise this median across facets as well.
-So we shuffle all facets for each $x$ level and obtain several $m''$s.
-In this approach, data is shuffled $2*nperm$ times and hence distances are computed $2*nperm$ times.
-It is computationally very intensive.
--->
-
-<!-- Hence, it was decided that the first approach will be employed to implement normalisation.
-One of the advantages of the second method could be to have normalisation separately for max and median measure.
-There is nothing that is stopping the users to implement this with more efficient computing power.
--->
-
-<!-- The harmony pairs could be arranged from highest to lowest average maximum pairwise distances across different levels of the harmonies. -->
-
-<!-- With increasing n, mean and sd of distribution of max increases. -->
-
-<!-- FTP theorem works for large n -->
-
-<!-- For small n resort to bootstrapping -->
-
-<!-- bullet points end here -->
-
-<!-- Suppose that $X_1$, $X_2$ , ... , $X_n$ are i.i.d. random variables with expected values $E(X_i) = \mu < \infty$ and variance $Var(X_i) = \sigma^2 < \infty$. Let  -->
-<!-- $Y = max(X_1, X_2, \dots, X_n)$. -->
-
-<!-- Let $F_X(x)$ be the common distribution of the variables $X_i$ and let $F_Y(y)$ be the corresponding distribution of $Y$. $F_Y(y)$ could be obtained from $F_X(x)$ simply by using: -->
-<!-- $F_Y(y) = P[(X_1 \leq y)\cap(X_2 \leq y) \cap...\cap (X_n \leq y)] = {F_X(y)}^n$.
-For large $n$, the distribution of $Y$ approaches a standard shape, which does not depend on $F_X$.
-But what about the case when $n$ is not large enough?
-The distribution of maximum in that case will indeed depend on $n$ and the underlying distribution of $X$.
-If $F_X(x)$ is the CDF of $X$, then $F_Y(y) = {F_x(y)}^n$.
-Suppose $\Phi$ nd $\phi$ are the cdf and pdf of a standard normal distribution, then -->
-<!-- $f_Y(y) = n{\Phi(y)}^{n-1}\phi(y)$, which depends on $n$.
-Hence, we are trying to normalise for $n$.
-Also, it depends on the underlying distribution of $X$, which we have assumed as normal in our case.
-As $n$ grows, we  can see the right tail growing, which implies that the probability that we will get a higher maximum is more.
-Now, for large $n$, we used EVT to normalise for $n$, that is, we brought them to the same scale without distorting the range of the distribution.
-But in our case, we will mostly have small $n$.
-It is important to ensure that they have the same mean and variation, for being able to compare the maximum value across $n$.
-We observe from the following graphs that our normalisation works after $n=6$, after which the difference in mean and standard deviation flattens out a lot.
--->
-
-<!-- ### why normalize -->
-
-<!-- Median and maximum distances are not robust to the number of levels and the metric would have higher values for harmonies with higher levels.
-Figure \ref{fig:mean-sd-max} shows how both mean and standard deviation of the distribution of maximum and median varies for different sample sizes ($n$).
-There is a rightward shift in the location and decrease in scale with increasing $n$.
-Thus these median maximum pairwise distances need to be normalized for different harmonies in a way that eliminates the effect of different levels, consequently enabling comparison across different harmonies.
-The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.
--->
-
-<!-- More formally, $d_{1},d_{2}\ldots ,d_{n}$ be a sequence of independent and identically-distributed pairwise distances and $M_{n}=\max\{d_{1},\ldots ,d_{n}\}$.
-Then Fisher–Tippett–Gnedenko theorem [@De_Haan2007-yx] suggests that if a sequence of pairs of real numbers $(a_{n}, b_{n})$ exists such that each $a_{n}>0$ and $\lim _{{m\to \infty }}P\left({\frac  {M_{n}-b_{n}}{a_{n}}}\leq x\right)=F(x)$, where $F$ is a non-degenerate distribution function, then the limit distribution $F$ belongs to either the Gumbel, Fréchet or Weibull family.
-The normalizing constants $(a_{n}, b_{n})$ vary depending on the underlying distribution of the pairwise distances.
-Hence to normalize appropriately, it is  -->
-<!-- important to assume a distribution of these distances.  -->
-
-<!-- For large $n$, the distribution of $M$ approaches a standard shape.
-But what about the case when $n$ is not large enough?
-The distribution of maximum in that case will indeed depend on $n$ and the underlying distribution of $D$.
-For large $n$, we could use EVT and CLT to normalise for $n$, however, most of the cyclic granularities encountered in practice have low $n$.
-Hence, normalisation could be done by bootstrapping procedure to ensure that the distribution of maximum/median have the same mean and variation for varying $n$.
--->
-
-<!-- ```{r create_simdata} -->
-
-<!-- ``` -->
-
-<!-- ```{r create_nlevels} -->
-
-<!-- ``` -->
-
-<!-- ```{r norm_max_new} -->
-
-<!-- ``` -->
-
-<!-- ```{r mean-sd-max, fig.cap = "Display shows mean and standard deviation of the distribution of maximum for sample sizes ranging from 2 to 30.
-There is a right shift in the distribution of maximum and median with increasing sample sizes."} -->
-
-<!-- library(ggridges) -->
-<!-- library(viridis) -->
-<!-- max_all_data <- create_nlevels(nlevels = seq(2, 30, 2), -->
-<!--                            nsim = 500, -->
-<!--                            sim_dist = distributional::dist_normal(5, 10), create_fun = max) -->
-
-<!-- g1 <- max_all_data %>% ggplot() + geom_density_ridges(aes(x=sim_data, y = as.factor(ind))) + ylab("n") + xlab("max") -->
-
-<!-- median_all_data <- create_nlevels(nlevels = seq(2, 30, 2), -->
-<!--                            nsim = 500, -->
-<!--                            sim_dist = distributional::dist_normal(5, 10), create_fun = median) -->
-
-<!-- g2 <- max_all_data %>% ggplot() + geom_boxplot(aes(x=sim_data, y = as.factor(ind)))  + ylab("n") + xlab("median") -->
-
-<!-- ggpubr::ggarrange(g1, g2, ncol = 2) -->
-
-<!-- ``` -->
+## Normalisation
 
@@
 
-<!-- ### Distribution of distances -->
-
-<!-- ### Theoretical evidence -->
-
-<!-- JS distances are distributed as chi-squared with $m$ df where we discretize the continuous distribution with $m$ discrete values.
-Taking sample percentiles to approximate the integral would mean taking $m = 99$.
--->
-<!-- With large $m$, chi-squared is asymptotically normal by the CLT.
-Thus, by CLT, ${\chi^2}_{m} \tilde{} N(m, 2m)$, which would depend on the number of discretization used to approximate the continuous distribution.
-Then $b_n = 1-1/n$ quantile of the normal distribution and $a_n = 1/[n*\phi(b_n)]$ where $\phi$ is the normal density function.
-$n$ is the number of pairwise comparisons being made.
--->
-
-<!-- ### Empirical evidence -->
-
-<!-- Distribution of JS distances is assumed to be normal but the mean and variance are estimated from the sample, rather than deducing it from the number of discretization used to approximate the continuous distribution.
-We look at different scenarios, where observations are collected from Normal, Exponential, Chi-squared and Gumbel distribution and found the distribution of JS distances are similar, irrespective of which distribution they are drawn from.
--->
-
-<!-- #### Initial distribution of observed variables shown in plot title -->
-
-<!-- ```{r distv11} -->
-
-<!-- ``` -->
-
-<!-- ```{r distv12} -->
-
-<!-- ``` -->
-
-<!-- ```{r distv13} -->
-
-<!-- ``` -->
-
-<!-- ```{r distv14} -->
-
-<!-- ``` -->
-
-<!-- ### Design and analysis of simulation experiments -->
-
-The behavior of the measure is monitored and understood through simulation experiments.
-A single simulation consisting of computational operations on a panel generating MMPD the value of which represents to what extent a pair of cyclic granularities would be interesting when displayed in the design.
-In comparing different simulation runs, we distinguish between different distributions and simulation scenarios (also iterations may be).
-
-### Simulated designs
-
- D1. Same distribution of the measured variable across all x-axis and facet categories
- D2. Different distribution across facet categories but same across x-axis categories
- D3. Different distribution across x-axis categories but same across facet categories
- D4. Different across both x-axis and facet categories
-
-Each of these case scenarios tried against Normal and a non-normal (Gamma) distribution to check if underlying distribution has a role to play.
-
-### Environment
-
-R version 4.0.1 (2020-06-06) is used with platform: x86_64-apple-darwin17.0 (64-bit) running under: macOS Mojave 10.14.6
-
-### Experimental set up
-
-This section describes the design of simulation runs, in terms of the scenarios simulated, the number of permutations used to compute estimates and to display the distribution of MMPD.
-
- <!-- - seed while generating random observations `seed1 = set.seed(9999)`   -->
- <!-- - grid with how many x levels `range_nx_vec = seq(2:4)`   -->
- <!-- - grid with how many facet levels `range_nfacet_vec = seq(2:4)`   -->
- <!-- - number of observations to be generated `ntimes_val = 500`   -->
- <!-- - number of permutation of data done to compute estimates `nperm_val = 2`   -->
- <!-- - number of permutations of data done to display histogram for each panel `nsim_val = 10`    -->
- <!-- - ordered or un-ordered categories of x levels while computing distances `dist_ordered_val = TRUE`   -->
- <!-- - distance between which quantiles are computed `quantile_prob_vec = seq(0.01, 0.99, 0.01)`   -->
-
-```{r}
-knitr::include_graphics(here::here("paper/Figs/simulation.png"))
-```
-
-Observations from Normal(5, 10) and Gamma(0.5, 0.2) are3 chosen in all the designs.
-
-<!-- . the null distribution are chosen as:   -->
-<!-- `sim_norm_null =   distributional::dist_normal(5, 10)`   -->
-<!-- <!--`sim_exp_null  =   distributional::dist_expoential(5)`  --> -->
-<!-- `sim_gamma_null  =   distributional::dist_gamma(0.5, 0.2)`   -->
-<!-- <!--`sim_weibull_null  =   distributional::dist_weibull(1.5, 3)`-->   -->
-
-<!-- The various designs are selected by increasing the mean/rate/shape of these distributions proportionally with that parameter. -->
-
-<!-- To check if different distributions impact, simulate data from different distributions.
-A 3 way contingency table with number of facet levels, x-axis levels and distribution type should be constructed with each cell value as the p-value.
--->
-
-<!-- Table -->
-<!-- Conclusions -->
-<!-- (in Null distribution) -->
-
-<!-- #### Varying distribution across facet -->
-<!-- #### Varying distribution across x-axis -->
-<!-- #### Varying distribution across both facets and x-axis -->
-<!-- #### Repeat all with varying facet and x-axis levels -->
-
-<!-- Table -->
-<!-- Conclusions -->
-<!-- (in power) -->
-
-<!-- ```{r} -->
-<!-- raw_data = rnorm(12, 5, 10) %>%  -->
-<!--   as_tibble() %>%  -->
-<!--   mutate(nfacet = rep(1:4, each = 3), -->
-<!--          nx = rep(1:3, 4)) -->
-
-<!-- raw_data %>% group_by(nfacet, nx) %>% nest() -->
-
-<!-- raw_data2 = raw_data %>% pivot_wider(id_cols = 2, names_from = "nx", values_from = "value") -->
-
-<!-- ``` -->
-
-<!--  ### Original -->
-<!-- | facets/x-axis     	| A_1  	| A_2  	| A_3  	| .. 	| .. 	| A_m  	| -->
-<!-- |-----	|------	|------	|------	|----	|----	|------	| -->
-<!-- | B_1 	| x_1 	| x_2 	| x_3 	| .. 	| .. 	| x_n 	| -->
-<!-- | B_2 	| y_1 	| y_2 	| y_3 	| .. 	| .. 	| y_n 	| -->
-<!-- | B_3 	|      	|      	|      	|    	|    	|      	| -->
-<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
-<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
-<!-- | B_L 	| z_1 	| z_2 	| z_3 	| .. 	| .. 	| z_m 	| -->
-
-<!-- ### Step1 -->
-
-<!-- | facets/x-axis     	| A_1  	| A_2  	| A_3  	| .. 	| .. 	| A_m  	| -->
-<!-- |-----	|------	|------	|------	|----	|----	|------	| -->
-<!-- | B_1 	| x_1 	| x_2 	| x_3 	| .. 	| .. 	| x_n 	| -->
-<!-- | B_2 	| y_1 	| y_2 	| y_3 	| .. 	| .. 	| y_n 	| -->
-<!-- | B_3 	|      	|      	|      	|    	|    	|      	| -->
-<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
-<!-- | ..  	|      	|      	|      	|    	|    	|      	| -->
-<!-- | B_L 	| z_1 	| z_2 	| z_3 	| .. 	| .. 	| z_m 	| -->
-
-```{r, eval = FALSE}
-# design_time <- readr::read_rds("../hakear-drake/data/design_time.rds")
-# write_rds(design_time, "data/design_time.rds")
-time_data <-readr::read_rds("data/design_time.rds")
-time_data$design = 
-  factor(time_data$design,
-         levels = c("null","vary_f", "vary_x", "vary_all"))
-
-time_data %>% 
-  pivot_longer(cols = c(time_obs, time_dist),
-               names_to = "type",
-               values_to = "time") %>% 
-  dplyr::filter(distribution == "normal") %>% 
-  ggplot(aes(x= design, 
-             y = log(time, exp(1)), 
-             colour = type, group = nfacet)) + geom_point() + geom_line(aes(group = type)) +
-  facet_grid(nx~nfacet) + ylab("ln(time)")
-
-```
-
-## Results
-
-### Null distribution
-
-<!-- Objective: distribution equal and hence values could be compared and normalisation works -->
-Under the null hypothesis, all the combinations of x-axis and facets are obtained from the same distribution.
-We need to study the distribution of the mmpd values under the null hypothesis to see if comparison of their values across different x-axis and facet levels are at all possible.
-So, in turn it needs to be checked that if normalisation worked.
-
-Currently, we see in Figure \ref{fig:null-dist} that the normalisation works fine for each facet since the distributions for each column are equal irrespective of the distribution type.
-But it does not work along the x-axis.
-
-```{r norm-data, fig.cap = "Distribution of $MMPD_{norm}$ across different levels of facet and x-axis. These distributions should look the same if normalisation worked." }
-mmpd_norm = read_rds("../hakear-drake/data/data_norm_low_new.rds") 
-hist_plot = mmpd_norm %>% 
-      ggplot() +
-      geom_histogram(aes(x = raw_mmpd)) +
-      facet_grid(nx~nfacet)
-hist_plot
-```
-
-```{r null-dist, eval =  FALSE, echo = FALSE, fig.cap="Distribution of mmpd across different facet levels (columns) and x-axis levels (rows) for null ditribution normal(5,10) and gamma(0.5, 0.2).
-The distribution of MMPD is unaffected by the null distribution considered.
-It is also the same across all facet levels but not across the x-axis, which means normalisation is failing across x-axis."}
-# all_files = list.files(path = "../hakear-drake/data", pattern = ".rds")
-# all_files
-# 
-# read_files = lapply(all_files, function(x){
-#   read_rds(paste0("../hakear-drake/data/", x))
-# })
-# 
-# names(read_files) = str_remove(all_files, pattern = ".rds")
-# 
-# null_all = bind_rows(normal = read_files$null_normal,
-#                      exponential = read_files$null_exp,
-#                      gamma = read_files$null_gamma,
-#                      weibull = read_files$null_weibull,
-#                      .id = "distribution")
-# design_all = readr::read_rds("../hakear-drake/data/design_all.rds")
-design_all = readr::read_rds("data/design_all.rds")
-
-design_all$design = 
-  factor(design_all$design,
-         levels = c("null","vary_f", "vary_x", "vary_all"), labels = c("D1", "D2", "D3", "D4"))
-design_all$distribution = 
-  factor(design_all$distribution,
-         levels = c("normal","gamma"), labels = c("norm","gam"))
-library(dplyr)
-library(ggplot2)
-ggplot2::ggplot(design_all %>% 
-                      filter(design == "D1")) +
-  ggridges::geom_density_ridges(aes(y = distribution, x = mmpd.x, fill = distribution)) + 
-  facet_grid(nx~nfacet) +
-  scale_fill_viridis_d() +
-  xlab("MMPD")
-```
-
-### Performance of normalised MMPD
-
-```{r}
-data1  = sim_panel(nx = 2, nfacet = 3, ntimes = 500)
-simulated_data <- sim_panel(nx = 2,
-nfacet = 3,
-ntimes = 500,
-sim_dist = rep(dist_normal(seq(5, 15, 5), 5), each = 2))
-data2 = simulated_data
-data4 = sim_panel(nx = 2,
-nfacet = 3,
-ntimes = 500,
-sim_dist = dist_normal(seq(5,30, 5), 5))
-data3 = data2 %>% rename("temp" = "id_facet") %>% rename("id_facet" = "id_x") %>% rename("id_x" = "temp")
-
-library(parallel)
-library(gravitas)
-library(hakear)
-
-set.seed(1000)
-r1 <- compute_mmpd_norm(data1, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-r2 <- compute_mmpd_norm(data2, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-r3 <- compute_mmpd_norm(data3, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-r4 <- compute_mmpd_norm(data4, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-r1prime <- compute_norm_pairwise_max(data1, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-r2prime <- compute_norm_pairwise_max(data2, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-r3prime <- compute_norm_pairwise_max(data3, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-r4prime <- compute_norm_pairwise_max(data4, "id_x", "id_facet", response = sim_data, nperm = 200)
-
-p1 <- data1 %>%
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +xlab("")
-
-p2 <- data2 %>% ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +xlab("")
-
-p3 <- data3 %>% ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +xlab("")
-
-p4 <- data4 %>% 
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +xlab("")
-
-gridExtra::grid.arrange(gridExtra::arrangeGrob(p1, top = paste("MMPD", round(r1, 3), "pairwise", round(r1prime, 3))),
-                        gridExtra::arrangeGrob(p2, top = paste("MMPD", round(r2, 3), "pairwise", round(r2prime, 3))),
-                        gridExtra::arrangeGrob(p3, top = paste("MMPD", round(r3, 3), "pairwise", round(r3prime, 3))),
-                        gridExtra::arrangeGrob(p4, top = paste("MMPD", round(r4, 3), "pairwise", round(r4prime, 3))),
-                        ncol = 2, nrow=2)
-
-```
-
-# The statistical test
-
-## Algorithm
-
-for computation for all harmony pairs
-
-**Assumption:** random permutation without considering ordering 
-(global)
-
-1. Given the data; $\{v_t: t=0, 1, 2, \dots, T-1\}$, the MMPD is computed and is represented by $MMPD_{obs}$.
-
-2. From the original sequence a random permutation is obtained: $\{v_t^*: t=0, 1, 2, \dots, T-1\}$.
-
-3. MMPD is computed for all random permutation of the data and is represented by $MMPD_{sample}$.
-
-4.  Steps (2) and (3) are repeated a large number
-of times M (e.g. 1000).
-
-5. For each permutation, one $MMPD_{sample}$ value is obtained.
-
-6. $95^{th}$ percentile of this $MMPD_{sample}$ distribution is computed and stored in $MMPD_{threshold}$.
-
-7. If  $MMPD_{obs}> MMPD_{threshold}$, harmony pairs are accepted. Only one threshold for all harmony pairs.
-
-Pros: Considering thresholds global for all harmony pairs would imply less computation time.
-
-Cons: Only one threshold for all harmony pairs means we are assuming distribution of all harmonies pairs are similar, which might not be the case.But nevertheless, it is a good benchmark.
-
-```{r, eval = FALSE, echo = FALSE}
-smart_harmony <-read_rds("data/smart_harmony_nonst.rds")
-smart_harmony
-```
-
-```{r smart_harmony,eval = FALSE, echo = FALSE}
-
-sm <- smart_meter10 %>% dplyr::filter(customer_id %in% c("10017936"))
-
-harmonies <- sm %>% 
-  harmony(ugran = "month",
-          filter_in = "wknd_wday",
-          filter_out = c("hhour", "fortnight"))
-
-harmony_tbl =  harmonies
-
-smart_harmony <- sm %>% 
-  rank_harmony(harmony_tbl = harmonies,
-               response = "general_supply_kwh", 
-               dist_ordered = TRUE)
-
-smart_harmony %>% 
-  mutate(MMPD = round(MMPD, 3), max_pd = round(max_pd, 3)) %>% 
-  mutate(rankn = row_number()) %>%
-  rename("rankun" = "r") %>% kable()
-```
-
-## Size, power and confidence interval
-
-#### Characteristics under different simulation designs   
-A set of simulation runs that are conducted and some outputs of which are reported.
-
-```{r sim_all, echo = FALSE}
-bind_files = readr::read_rds("../hakear-drake/data/compute_p_value.rds")
-
-bind_files$design = 
-  factor(bind_files$design,
-         levels = c("null","vary_f", "vary_x", "vary_all"), labels = c("D1", "D2", "D3", "D4"))
-
-ggplot(bind_files %>% 
-         filter(distribution == "normal")) +
-  geom_point(aes(x=design, y = p_value),
-                 alpha = 0.5)+
-  facet_grid(nx~nfacet) +
-  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
-
-ggplot(bind_files %>% 
-         filter(distribution == "exponential")) +
-  geom_point(aes(x=design, y = p_value),
-                 alpha = 0.5)+
-  facet_grid(nx~nfacet) +
-  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
-
-ggplot(bind_files %>% 
-         filter(distribution == "gamma")) +
-  geom_point(aes(x=design, y = p_value),
-                 alpha = 0.5)+
-  facet_grid(nx~nfacet) +
-  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
-
-ggplot(bind_files %>% 
-         filter(distribution == "weibull")) +
-  geom_point(aes(x=design, y = p_value),
-                 alpha = 0.5)+
-  facet_grid(nx~nfacet) +
-  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
-```
-
-```{r sim_conf, echo = FALSE, eval = FALSE}
-library(dplyr)
-library(ggplot2)
-ggplot2::ggplot(design_all %>% 
-                      filter(design == "D1", distribution == "norm")) +
-  geom_boxplot(aes(x = as.factor(nx), 
-                   y = mmpd.x), width = 0.1) + 
-  facet_wrap(~nfacet) +
-  scale_fill_viridis_d() +
-  xlab("number of x levels") +
-  coord_flip()
-
-```
+# Choosing harmonies with significant wpd
 

### 2021-01-20 paper/main.Rmd
changing paper structure

@@
 
-# The distance measure
+# The proposed distance measure
 
 We are interested in assessing structure in probability distributions of the measured variable across bivariate cyclic granularities.
-We propose a measure called Median Maximum Pairwise Distances (wpd) to evaluate structure in such a design.
+We propose a measure called Weighted Maximum Pairwise Distances (wpd) to evaluate structure in such a design.
 
@@
 
-## Methodology
-
-### Characterising distribution
+## Characterising distributions
 
@@
 
-### Distance between distributions
+## Distance between distributions
 
@@
 
-### Notations and Definitions
+## Definition of the proposed distance measure
 
 Consider two cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.
-Let the pairwise distances between pairs $(a_{j} b_{k}, a_{j'}b_{k'})$ b   e denoted as $d_{(jk, j'k')} = JSD(a_{j}b_{k}, a_{j'}b_{k'})$.
+Let the pairwise distances between pairs $(a_{j} b_{k}, a_{j'}b_{k'})$ be denoted as $d_{(jk, j'k')} = JSD(a_{j}b_{k}, a_{j'}b_{k'})$.
 Pairwise distances could be within-facets or between-facets.
@@
 
-<!-- <!-- 5. Compute distribution of maximum distance ($M$) by shuffling the data $200$ times and finishing Steps1-4 in each case. Scale $M$ using the mean and sd of the distribution.  --> -->
+<!-- <!-- 5. Compute distribution of maximum distance ($M$) by shuffling the data $200$ times and finishing Steps1-4 in each case. Scale $M$ using the mean and sd of the distribution.  -->
 
@@
 
+The distribution of wpd is different for different levels of facets and x-axis levels.
+This is because the statistic maximum which is used to define wpd is affected by the number of categories.
+The measure would have higher values if $C_i$ or $C_j$ has higher levels.
+However, we would ideally want a higher value of the measure only if there is significant difference between distributions across facet or x-axis categories, and not because the number of categories are higher.
+Therefore, in order to compare wpd across different combinations of facet and x-axis levels, we need to eliminate the impact of different levels of the facets and x-axis first and get a normalized measure.
+Henceforth we call the measure discussed as $wpd_{raw}$ and the normalised measure as $wpd_{norm}$.
+The measure $wpd_{norm}$ could potentially lead to comparison of the measure across different panels and also identifying only the interesting panels from a dataset.
+
 ## Simulation study
+
+Most of the behavior of the measure wpd was studied via simulation.
+The simulations explore how wpd performs under various designs and parameters and its limitations.
+To study the behavior of wpd, simulations were carried out for four different designs and the following factors that could potentially have an impact on the values of wpd:
+
+<!-- Numerous simulations were carried out in a wide range of scenarios. -->
+
+<!-- Same scenarios were used, when possible with normalized wpd, keeping all other simulation variables constant. -->
+
+- $nx$ (number of levels of x-axis)
+- $nfacet$ (number of levels of facets)
+- $\lambda$ (tuning parameter)
+- $\omega$ (increment in each panel design)
+- $dist$ (normal/non-normal distributions with different location and scale)
+- $n$ (sample size for each combination of categories)
+- $nsim$ (number of simulations)
+- $nperm$ (number of permutations of data)  
+- $designs$  
+$D_{null}$  (No difference in distribution)  
+$D_{var_f}$ (Difference in distribution only across facets)  
+$D_{var_x}$ (Difference in distribution only across x-axis)  
+$D_{var_{all}}$ (Difference in distribution in both facets and x-axis)
+
+### Environment
+
+R version 4.0.1 (2020-06-06) is used with platform: x86_64-apple-darwin17.0 (64-bit) running under: macOS Mojave 10.14.6 and MonaRCH, which is a next-generation HPC/HTC Cluster, designed from the ground up to address the computing needs of the Monash HPC community.
+The nodes and the storage used are as follows:
+
+### Results
+
+This section reports the results of a simulation study that was carried out to evaluate the
+behavior of our distance measure across all potential factors.
+The results are reported in two parts: for the a) raw measure and then b) normalised one to show how the loopholes for the raw measures were removed using the normalized ones.
+
+First, the behavior of $wpd_{raw}$ and $wpd_{norm}$ is explored in designs where there is no difference in distribution between x and facet categories.
+We have considered different initial distributions to study the impact of initial distribution under the null setup.
+Using two types of distributions, viz.
+normal and gamma (non-normal), we generated observations for each combination of $nx$ and $nfacet$ from the following sets: $nx = \{2, 3, 5, 7, 14, 20, 31, 50\}$ and $nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
+Each combination is being referred to as a _panel_.
+That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$.
+For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
+That is, if we consider the panel  $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
+The values of $\lambda$ is set to $0.67$, since we want to up-weigh the within-facet distances and that of $\omega$ is set to $0$, since there is no significant differences between distributions in the null case.
+Observations were generated for each type of distribution changing the shape and scale to study the effect of shape, scale and type of distribution on wpd.
+The set of distributions considered for this purpose is ${N(0,1), N(5, 1), N(0,5), \Gamma(0.5, 1), \Gamma(2, 1)}$.
+Each of the scenario is run $nsim = 200$ times to see the distribution of wpd values for each scenario.
+
+Secondly, the behavior of raw and normalized wpd is explored in designs where there is in fact difference in distribution between facet categories ($D_{var_f}$) or across x-categories ($D_{var_x}$) or both ($D_{var_{all}}$).
+Using $\omega =  \{1, 2, \dots, 10\}$ and $\lambda = seq(from  = 0.1, to = 0.9, by = 0.05)$, observations are drawn from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet =  \{2, 3, 5, 7, 14, 20, 31, 50\}$.
+$ntimes = 500$ is assumed for this setup as well.
+Furthermore, to generate different distributions across different combination of facet and x levels, the following method is deployed - suppose the distribution of the combination of first levels of x and facet category is $N(\mu,\sigma)$ and $\mu_{jk}$ denotes the mean of the combination $(a_jb_k)$, then $\mu_{j.} = \mu + j\omega$ (for design $D_{var_x}$) and $\mu_{.k} = \mu + k\omega$ (for design $D_{var_f}$).
+
+The tabulated values and graphical representations of the simulation results are provided in Appendix. The learning from the simulations are as follows:
+
+## Properties
 

### 2021-01-20 paper/main.Rmd
cleaning trash in R folder

@@
 - $n$ (sample size for each combination of categories)
-- $nsim$ (number of simulations)
+- $nsim$ (number of simulations)a
 - $nperm$ (number of permutations of data)  
@@
 
-### Cyclic granularities search and computation:
-
-The tsibble object `smart_meter10` from R package `gravitas` [@R-gravitas] consisting of `reading_datetime`, `customer_id` and `general_supply_kwh` denoting the index, key and measured variable of the tsibble is used to facilitate the systematic exploration.
-While trying to explore the energy behavior of these customers systematically across cyclic time granularities, the first thing to consider is which cyclic time granularities we can look at exhaustively.
-Let us consider conventional time deconstructions for a Gregorian calendar (second, minute, half-hour, hour, day, week, month, year).
-Since the interval of this tsibble is 30 minutes, the temporal granularities may range from half-hour to year.
-Considering $6$ linear granularities half-hour, hour, day, week, month and year in the hierarchy table, $N_C = (6*5/2) = 15$.
-<!--(via Section \ref{sec:data-structure}) circular or quasi-circular granularities that could be formed relating two linear granularities at a time.--> If $N_C$ seem too large, the smallest and largest linear granularities could be considered to be removed from the hierarchy table.
-We remove half-year and year to have $N_C = (4*3/2) = 6$ and obtain cyclic granularities namely "hour_day", "hour_week", "hour_month", "day_week", "day_month" and "week_month", read as "hour of the day", etc.
-Further, we add cyclic granularity day-type( "wknd_wday") to capture weekend and weekday behavior.
-Now that we have a list of cyclic granularities to look at, we should be able to compute the multiple-order-up granularities using Section \ref{sec:cyclic-calendar}.
-
-```{r search, echo=FALSE, eval = FALSE}
-library(gravitas)
-smart_meter %>%
-  search_gran(filter_out = c("semester", 
-                             "quarter",
-                             "fortnight"))
-```
-
-```{r search_gran_limit2, echo = FALSE, eval = FALSE}
-smart_meter10 %>% search_gran(
-  highest_unit = "month",
-  filter_out = c("hhour", "fortnight"))%>%
-  knitr::kable(format = "latex",
-      booktabs = TRUE) %>%
-  #row_spec(0, bold = TRUE)%>%
-  kable_styling()
-```
-
-<!-- # smart_meter_limit2 <- smart_meter10 %>% search_gran(highest_unit = "month", -->
-<!-- #                               filter_out = c("hhour", "fortnight") -->
-<!-- # ) -->
-<!-- # knitr::kable(smart_meter_limit2, format = "markdown") -->
-
-<!-- Now that we have a list of cyclic granularities to look at, we should be able to compute them from the data using Sections \ref{sec:circular-gran-def}, \ref{sec:quasi-circular-gran-def} and \ref{sec:aperiodic-gran-def}.
--->
-
-### Screening and visualizing harmonies
-
-From the search list, $N_C = 7$ cyclic granularities are chosen for which we would like to derive insights of energy behavior.
-Recalling the data structure <$C_i$, $C_j$, `general_supply_kwh`> for exploration $\forall i, j \in \{1, 2, \ldots, 7\}$, each of these $7$ cyclic granularities can either be mapped to x-axis or to facet.
-Choosing $2$ of the possible $7$ granularities, which is equivalent to having $^{7}P_2 = 42$ candidates for visualization.
-Fortunately, harmonies can be identified among those $42$ possibilities to narrow the search.
-\autoref{tab:harmony-tab} shows $16$ harmony pairs after removing clashes and any cyclic granularities with levels more than $31$, as effective  exploration becomes difficult with many levels (Section \ref{sec:levels}).
-The MMPD is also shown along with indicator (*) only when variation of measured variable across the harmony pair significant.
-Starting from $42$ possible pairs of cyclic granularities to visualize, we are finally left with only $6$, which is a very sizable number of displays for exploration.
-
-Few harmony pairs are displayed in \autoref{fig:bothcust} to illustrate the significance of MMPD, threshold and the impact of different distribution plots and reverse mapping.
-\noindent For each of \autoref{fig:bothcust} (b) and (c), $C_i$ is the circular granularity day-type (weekday/weekend) and $C_j$ is hour of the day.
-The geometry used for displaying the distribution is chosen as area-quantiles and violins in \autoref{fig:bothcust} (b and c respectively).
-\autoref{fig:bothcust} (a) displays reverse mapping of $C_i$ and $C_j$ with $C_i$ denoting hour of the day and $C_j$ denoting day-type with distribution geometrically displayed as boxplots.
-
-<!-- From the search list, we found six cyclic granularities for which we would like to derive insights of energy behavior.
-Given the data structure <$C1$, $C2$, `general_supply_kwh`>, each of those six cyclic granularities can either be mapped to x-axis or to facet.
-Thus the problem is equivalent to taking 2 granularities at a time from six, which essentially is equivalent to having 30 data subsets for visualization.
-However, harmony/clash pairs can be identified among those 30 possibilities to determine feasibility of plotting any pairs together.
-\autoref{tab:harmony-tab} shows 13 harmonies pairs, each of which can be plotted together to look at the energy behavior from different perspectives.
--->
-
-<!-- We will look at few harmony pairs and see how the proposed workflow can be utilized.  -->
-
-<!-- From the Gestalt theory with the same data  <$C1$ $C2$, `general_supply_kwh`>, mapping $C1$ on the x-axis vs facet might lead to different insights. -->
-
-```{r harmony-tab, echo=FALSE, eval = FALSE, cache=TRUE}
-# if(!dir.exists("cache/"))
-# {
-#   dir.create("cache")
-# }
-# 
-# if (!file.exists("cache/smart_harmony.rds")) {
-  sm <- smart_meter10 %>%
-  filter(customer_id %in% c(10017936))
-
-  harmonies <- sm %>%
-  harmony(ugran = "month",
-          filter_in = "wknd_wday", 
-          filter_out = c("hhour", "fortnight"))
-set.seed(12345)
-
-global_harmony <- sm %>%
-  global_threshold(harmony_tbl = harmonies,
-                   response = "general_supply_kwh", nsamp = 5) %>%
-  rename(`facet variable` = facet_variable,
-         `x-axis variable` = x_variable,
-         `facet levels` = facet_levels,
-         `x-axis levels` = x_levels) %>% 
-  mutate(MMPD = if_else(gt_MMPD == TRUE,
-                        paste0(MMPD, "*"), paste0(MMPD))) %>%
-  select(`facet variable`,`x-axis variable`,
-         `facet levels`,`x-axis levels` ,MMPD)
-
-#   write_rds(smart_harmony,"cache/smart_harmony_ak.rds")
-# }
-#smart_harmony <- read_rds("cache/smart_harmony.rds")
-
-  knitr::kable(global_harmony,
-               format = "latex",
-               booktabs = TRUE,
-                caption = "Harmonies with a pair of cyclic granularity one placed on facet and the other on x-axis.
-Out of 42 possible combinations of cyclic granularities, only 16 are harmony pairs.
-The harmony pairs are ranked basis highest to lowest MMPD and only the first 6 show significant variation in the measured variable.") %>%
-    #row_spec(0, bold = TRUE) %>%
-    kable_styling()
-```
-
-In \autoref{fig:bothcust} (b), <!--the distribution of energy consumption is plotted across the harmony pair (weekday/weekend, hour of the day) through an area quantile plot-->the black line is the median, whereas the purple band covers 25th to 75th percentile, the orange band covers 10th to 90th percentile and the green band covers 1st to 99th percentile.
-The first facet represents the weekday behavior while the second one displays the weekend behavior and energy consumption across each hours of the day is shown inside each facet.
-The energy consumption is extremely (positive- or right-) skewed with the 1st, 10th and 25th percentile lying relatively close whereas 75th, 90th and 99th lying further away from each other.
-This is common across both weekdays and weekends.
-For the first few hours on weekdays, median energy consumption starts and continues to be higher for longer as compared to weekends.
-
-Consider looking at violin plots instead of quantile plots to look at the same data in \autoref{fig:bothcust}(c).
-There is additional information that we can derive looking at the distribution.
-There is bimodality in the early hours of the day, implying both low and high energy consumption is probable in the early hours of the day both for weekdays and weekends.
-<!--Also the hours from 7 to 13 look most volatile.--> If we visualize the same data with reverse mapping of the cyclic granularities, then the natural tendency would be to compare weekend and weekday behavior within each hour and not across hours.
-For example in \autoref{fig:bothcust}(a), it can be seen that median energy consumption for the early morning hours is extremely high for weekdays compared to weekends.
-Also, outliers are more prominent in the latter part of the day.
-All of these indicate that looking at different distribution geometry or changing the mapping might shed lights on different aspect of the energy behavior for the same sample population.
-
-```{r bothcust, fig.cap = "Energy consumption of a single customer shown with different distribution displays, and granularity arrangements.
-Two granularities are used: hour of the day (I) and weekday/weekend (II).
-Plot (a) shows granularity I facetted by granularity II, and plots (b), (c) shows the converse mapping.
-Plot (a) makes a comparison of usage by workday within each hour of the day using side-by-side boxplots.
-Generally, on a work day there is more consumption early in the day.
-Plots (b) and (c) examine the temporal trend of consumption over the course of a day, separately for the type of day.
-Plot (b) uses an area quantile to put the emphasis on the time series, for example, the median consumption over time shows prolonged usage in the morning on weekdays.
-Plot (c) uses a violin plot to place emphasis on distributional differences across hours.
-It can be seen that the morning use on weekdays is bimodal, some work days there is low usage, which might indicate the person is working from home and also having a late start.", out.width="90%"}
-
-cust2_quantile <- smart_meter10 %>%
-  filter(customer_id %in% c(10017936)) %>%
-  prob_plot("wknd_wday",
-    "hour_day",
-    response = "general_supply_kwh",
-    plot_type = "quantile",
-    symmetric = TRUE,
-    quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)
-  ) +
-  scale_y_sqrt() +
-  #ggtitle(" (b) Area quantile plot faceted by weekend-weekday") +
-  ylab("electricity demand [KWh]") + xlab("hours of the day") + ggtitle("") + ylab("")+ 
-  theme_minimal()
-
-cust2_violin <- smart_meter10 %>%
-  filter(customer_id %in% c(10017936)) %>%
-  prob_plot("wknd_wday",
-    "hour_day",
-    response = "general_supply_kwh",
-    plot_type = "violin"
-  ) +
-  scale_y_sqrt()+
-  #ggtitle(" (c) Violin plot faceted by weekend-weekday") +
-  ylab("") + xlab("hours of the day") + ggtitle("") +
-  scale_x_discrete( breaks = seq(0, 23, 5))+ 
-  theme_minimal()
-
-cust2_box <- smart_meter10 %>%
-  filter(customer_id %in% c(10017936)) %>%
-  prob_plot("hour_day",
-    "wknd_wday",
-    response = "general_supply_kwh",
-    plot_type = "boxplot"
-  ) +
-  scale_y_sqrt() +
-  #ggtitle(" (a) Box plot faceted by hour-of-day") +
-  xlab("") +
-  ggtitle("") + ylab("") +
-  scale_x_discrete(labels = c('wday','wend')) +
-  ggplot2::theme(axis.text.x = element_text(size = 7))+ 
-  theme_minimal()
-
-#ggarrange(cust2_quantile, cust2_violin, nrow = 2)
-
-gg_fig <- ggarrange(cust2_box,
-          ggarrange(cust2_quantile, cust2_violin, nrow = 2, labels = c("b", "c")),
-          ncol = 2, labels = "a")
-          #label.y = "electricity demand [KWh]"\
-
-ggpubr::annotate_figure(gg_fig,
-                left = text_grob("electricity demand [KWh]",  rot = 90))
-```
-
-<!-- # ```{r cust-ridge, fig.cap ="Boxplot of energy consumption across hours of the day faceted by weekday/weekend for customer id: 10017936.
-The change in mapping of the cyclic granularities leads to easier comparison within weekdays and weekends for each hour.
-Median consumption till 6am is higher for weekends compared to weekdays although the quartiles look similar.
-Outliers appear more during the end of the day implying more uncertain behavior in latter hours of the day compared to early morning hours."} -->
-<!-- #  -->
-<!-- # smart_meter10 %>% -->
-<!-- #   filter(customer_id %in% c(10017936)) %>% -->
-<!-- #   prob_plot("hour_day", -->
-<!-- #     "wknd_wday", -->
-<!-- #     response = "general_supply_kwh", -->
-<!-- #     plot_type = "boxplot" -->
-<!-- #   ) + -->
-<!-- #   scale_y_sqrt() -->
-<!-- # ``` -->
-
-<!-- Now, we would like to see how these customers' behavior relate to the rest of the 50 households across these two measures -   -->
-
-<!-- - if energy distribution is skewed towards extreme? -->
-
-<!-- - if the weekend and weekday behavior are different for most of these households? -->
-
-If the data for all keys are visualized together, it might lead to Simpson's paradox, which occurs when one observation shows a particular behavior, but this behavior paradoxically becomes obscured by aggregation.
-For example in a particular neighborhood one household may have the least daily power consumption for a full week, yet still not be the household with the minimum weekly power consumption.
-This is an intuitive possibility, because heterogeneous `customer_id`'s with very different occupation or demographics will tend to have very different energy behavior and combining them together will somehow weaken any typical or extreme behavior.
-A strategy for analyzing multiple keys together could be to first group them basis time series or demographic features and then look at their energy behavior.
-This is beyond the scope of the current work.
-
-<!-- For the purpose of this paper, the smart meter data is filtered for two customers to illustrate kinds of insights that can be drawn after proceeding with the systematic exploration. -->
-
-<!-- For example, Figure \ref{fig:wknd-wday50} shows the quantile plot of energy consumption of a sample of 50 households.
-Quantiles for weekends and weekdays for these customers look exactly the same.
-It is not clear if the behaviors of most of these customers do not alter between weekdays and weekends or looking at all customers together balances out the behaviors.
-Consider another example in Figure \ref{fig:my-hd} showing the area quantile plots of 50 customers.
-The median is very close to the lower boundaries of all the other bands implying energy consumption for these households are left skewed.
-The pink band changes significantly in winter months (May - August) implying that much of the behavioral changes occur in the quartiles, that too in peak hours of the day.
-It is to be noted here that the the level of all quantiles increased too in winter months (increased energy usage in weather conditions), the interesting part is to notice that the relationship between bands other than quartile stayed same across seasons.
--->
-
-This case study shows systematic exploration of energy behavior for a household to gain exhaustive insights on periodic behavior of the households. 
-<!--First, it helps us to find the list of cyclic granularities to look at, then shrinks the number of possible visualizations by identifying harmonies, visualize a harmony pair and shows the effect of different distribution plots or reverse mapping.-->
+### 50 households together
+
+### Multidimensional scaling
+
+### Putting similar households on linear scale
 

### 2021-01-20 paper/R/compute_mmpd_panel_grid.R

@@ -1,35 +1,0 @@
-##' .. content for \description{} (no empty lines) ..
-##'
-##' .. content for \details{} ..
-##'
-##' @title
-##' @param sim_null_orig
-##' @param quantile_prob
-##' @param dist_ordered
-##' @param nperm
-##' @return
-##' @author Sayani Gupta
-##' @export
-compute_mmpd_panel_grid <- function(sim_null_orig, quantile_prob = seq(0.01,
-                                    0.99, 0.01), dist_ordered = TRUE, nperm = 20) {
-
-  nx <- sim_null_orig %>% distinct(nx) %>% .$nx
-  nfacet <- sim_null_orig %>% distinct(nfacet) %>% .$nfacet
-  
-  (nx) %>% 
-    map_df(function(i){
-      (nfacet) %>% 
-        map_df(function(j){
-          
-  mmpd <- sim_null_orig %>% 
-  dplyr::filter(nx == i, nfacet == j) %>%  
-  compute_mmpd_panel(quantile_prob, 
-                     dist_ordered, 
-                     nperm = nperm)
-  
-  bind_cols(nx = i, nfacet = j, mmpd = mmpd)
-        
-  })
-    })
-
-}

### 2021-01-20 paper/R/compute_norm.R

@@ -1,25 +1,0 @@
-##' .. content for \description{} (no empty lines) ..
-##'
-##' .. content for \details{} ..
-##'
-##' @title
-##' @param data_boot
-##' @param method
-##' @return
-##' @author Sayani07
-##' @export
-compute_norm <- function(data_boot, method = "std") {
-
-  nrow_data <- nrow(data_boot)
-  nlevel <- data_boot %>% group_by(perm_id) %>% tally() %>% slice(1) %>% .$n
-  data_orig <- data_boot %>% slice(seq_len(nlevel))
-  
-  stat_data <- data_boot %>% 
-    summarise(mean = mean(value), 
-              sd = sd(value))
-  
-  data_orig %>% 
-    group_by(panel_id) %>% 
-    summarise((norm_max = (max(value) - stat_data$mean)/stat_data$sd), .groups = 'drop') %>% summarize(MMPD = median(norm_max)/n())
-
-}

### 2021-01-20 paper/R/create_sim_nlev.R

@@ -1,19 +1,0 @@
-##' .. content for \description{} (no empty lines) ..
-##'
-##' .. content for \details{} ..
-##'
-##' @title
-##' @param nlevel
-##' @param nsim
-##' @param nperm
-##' @return
-##' @author Sayani07
-##' @export
-create_sim_nlev <- function(nlevel = 2:20, nsim = 50, nperm = 200) {
-
-  (nlevel) %>% purrr::map_df(function(i){
-    sim_data <- create_sim_n(nlevel = i, nsim, nperm)
-    bind_cols(nlevel = i, norm_max = sim_data)
-  })
-  
-}

### 2021-01-20 paper/R/create_simulate_norm.R

@@ -1,30 +1,0 @@
-##' .. content for \description{} (no empty lines) ..
-##'
-##' .. content for \details{} ..
-##'
-##' @title
-##' @param nlevel
-##' @param ncol
-##' @param sim_dist
-##' @param nsim
-##' @return
-##' @author Sayani07
-##' @export
-create_simulate_norm <- function(nlevel = 6,
-                                 ncol = 3, 
-                                 nrow = 2, 
-                                 sim_dist = dist_normal(5, 10),
-                                 nperm = 500,
-                                 nsim = 200) {
-
-  (1:nsim) %>%
-    map_df(function(i) {
-      sim_data <- create_data_sim1(nlevel, sim_dist) %>% 
-        create_panel(ncol,nrow) %>% 
-        boot_panel(nperm) %>% 
-        compute_norm()
-      
-      bind_cols(sim_id = i, sim_data = sim_data)
-    })
-
-}

### 2021-01-20 paper/R/distance_panel.R

@@ -1,70 +1,0 @@
-##' .. content for \description{} (no empty lines) ..
-##'
-##' .. content for \details{} ..
-##'
-##' @title
-##' @param sim_panel_data
-##' @param quantile_prob
-##' @param method
-##' @return
-##' @author Sayani07
-##' @export
-distance_panel <- function(sim_panel_quantiles,
-                           quantile_prob = seq(0.01, 0.99, 0.01),
-                           dist_ordered = TRUE) {
-  ncoly <- sim_panel_quantiles %>% distinct(id_facet) %>% nrow()
-  nrowy <- sim_panel_quantiles %>% distinct(id_x) %>% nrow()
-  
-  #(seq_len(nrowy)) %>% 
-  (seq_len(ncoly)) %>% 
-    purrr::map_dfr(function(k) {
-      dist_facet <- (1:(nrowy-1)) %>%
-        purrr::map_dfc(function(i) {
-          dist <- ((i + 1):nrowy) %>%
-            purrr::map_dfc(function(j) {
-              m1 <- sim_panel_quantiles %>% 
-                dplyr::filter(id_facet == k, id_x == i)  %>%
-                select(sim_data_quantile) %>% 
-                unlist()
-              
-              m2 <- sim_panel_quantiles %>% 
-                dplyr::filter(id_facet ==k, id_x == j)%>%
-                select(sim_data_quantile) %>% 
-                unlist()
-              
-              z <- JS(prob = quantile_prob, m1, m2)
-              if (dist_ordered) {
-                if (j != i + 1) {
-                  z <- NA
-                }
-              }
-              return(z)
-            })
-          dist %>% 
-            select_if(not_is_na) 
-        })
-      
-      bind_cols(id_facet = k, dist_facet = dist_facet)
-      
-    })
-}
-not_is_na <- function(x) any(!is.na(x))
-
-JS <- function(prob, q, p) {
-  # Compute approximate densities
-  x <- seq(min(q, p), max(q, p), l = 201)
-  qpmf <- pmf(x, prob, q)
-  ppmf <- pmf(x, prob, p)
-  m <- 0.5 * (ppmf + qpmf)
-  JS <- suppressWarnings(0.5 * (sum(stats::na.omit(ppmf * log(ppmf / m, base = 2))) +
-                                  sum(stats::na.omit(qpmf * log(qpmf / m, base = 2)))))
-  return(JS)
-}
-
[…]

### 2021-01-20 paper/R/main.R

@@ -1,664 +1,0 @@
-##----load
-library(ggplot2)
-library(gravitas)
-library(purrr)
-library(distributional)
-library(magrittr)
-library(tidyr)
-library(dplyr)
-library(ggpubr)
-
-##--sim_plot
-sim_plot <- function(.data, sim_dist, nsamp = 20)
-{
-  data1 <- sim_distharmony1(.data, sim_dist = sim_dist)
-  #data2 <- data1
-  #names(data2) =  c("Var2", "Var1","dist","sim_dist")
-  
-  data_l = bind_cols(pairn = 1L, data1) %>% select(-dist) %>% unnest(sim_dist)
-  #data_m = bind_cols(pairn = 2L, data2) %>% select(pairn, Var1, Var2,sim_dist, -dist) %>% unnest(sim_dist)
-  #data_mlist =  list(data_l, data_m)
-  data_mlist = list(data_l)
-  harmonies = .data
-  
-  global_harmony <-  map(data_mlist, ~ (.x %>% select(-1)))%>%
-    global_threshold(harmony_tbl = harmonies,
-                     response = "sim_dist",
-                     dist_distribution = "normal",
-                     dist_ordered = TRUE,
-                     create_gran_data = FALSE, nsamp = nsamp)
-  
-  g = global_harmony[[2]] %>% as_tibble()
-  h1 = global_harmony[[1]]$MMPD[1]
-  h2 = global_harmony[[1]]$MMPD[2]
-  h3 = global_harmony[[3]]
-  
-  sim_hist <- ggplot(g, aes(x = value)) + geom_histogram()  + geom_vline(xintercept =  h1, colour = "red", show.legend = TRUE) +
-    geom_vline(xintercept =  h2, colour = "blue", show.legend = TRUE) +  geom_vline(xintercept =  h3, colour = "black", show.legend = TRUE) 
-  
-  
-  
-  plot_harmony_row1 <- data1 %>% select(-dist) %>% unnest(sim_dist) %>%
-    ggplot(aes(x = Var2, y = sim_dist)) +
-    facet_wrap(~Var1) + geom_boxplot()
-  
-  plot_harmony_row2 <- data2 %>% select(-dist) %>% unnest(sim_dist) %>%
-    ggplot(aes(x = Var2, y = sim_dist)) +
-    facet_wrap(~Var1) + geom_boxplot()
-  
[…]

### 2021-01-20 paper/R/mpd.R

@@ -1,56 +1,0 @@
-##' .. content for \description{} (no empty lines) ..
-##'
-##' .. content for \details{} ..
-##'
-##' @title
-##' @param distance_panel_data
-##' @param nperm
-##' @return
-##' @author Sayani07
-##' @export
-
-source("R/shuffle_x_for_each_facet.R")
-mpd <- function(sim_panel_data, distance_panel_data, nperm = 2000) {
-  nfacet <- nrow(distance_panel_data)
-
-  # nperm_data_facet <- lapply(seq_len(nfacet),
-  #                           function(k) {
-  #     
-      panel_row <- distance_panel_data %>%
-        tidyr::pivot_longer(cols = -1, names_to = "j") %>% select(id_facet, value)
-      
-      nperm_data_1 <- bind_cols(perm_data = panel_row) %>%
-        rename("perm_data" = "value")
-      
-      nperm_data <- data.frame(2:nperm)
-      #nperm_data_n <- (2:nperm) %>%
-      nperm_data_n <- lapply(2:nperm, 
-                            function(i) {
-          z = NULL
-          
-          perm_data <- sim_panel_data %>% 
-            #dplyr::group_by(id_facet) %>% 
-            shuffle_x_for_each_facet() %>% 
-            compute_quantiles() %>% 
-            distance_panel() %>% 
-            pivot_longer(-1, names_to = "dist", 
-                         values_to = "perm_data") %>% select(-dist)
-            #rename("perm_data" = "...2")
-          
-          #z = bind_cols(perm_id = i, id_facet = k, perm_data = perm_data$perm_data)
-           #z = bind_cols(perm_data = perm_data$perm_data,
-        })
-      
-      nperm_data_facet <- bind_rows(nperm_data_n, nperm_data_n, .id = "perm_id")
-
-  nperm_data_facet %>%
-    group_by(id_facet) %>%
-    summarise(
-      max = max(perm_data, na.rm = TRUE),
-      mean_perm = mean(perm_data, na.rm = TRUE),
-      sd_perm = sd(perm_data, na.rm = TRUE)
-    ) %>%
-    mutate(norm_x = if_else(sd_perm !=0, 
-                            (max - mean_perm) / sd_perm,max))
-}
-

### 2021-01-20 paper/R/perm_mmpd.R

@@ -1,26 +1,0 @@
-##' .. content for \description{} (no empty lines) ..
-##'
-##' .. content for \details{} ..
-##'
-##' @title
-##' @param sim_panel_data
-##' @param nperm
-##' @return
-##' @author Sayani07
-##' @export
-perm_mmpd <- function(sim_panel_data, nperm = 5) {
-
-  (seq_len(nperm)) %>% 
-    map(function(i)
-      {
-      set.seed(i)
-    perm_data = sample(sim_panel_data$sim_data, size = nrow(sim_panel_data))
-    sample_data <- bind_cols(sim_panel_data, perm_data = perm_data) %>% 
-      select(-sim_data) %>% 
-      rename("sim_data" = "perm_data") 
-    
-    perm_mmpd_data <- sample_data %>% compute_mmpd_panel(nperm = 2)
-    
-    })
-  perm_mmpd_data %>% unlist() %>% as_tibble()
-}

### 2021-01-20 paper/R/plot_mmpd_null_grid.R

@@ -1,28 +1,0 @@
-##' .. content for \description{} (no empty lines) ..
-##'
-##' .. content for \details{} ..
-##'
-##' @title
-##' @param mmpd_dist_null_grid
-##' @param mmpd_null_orig
-##' @return
-##' @author Sayani Gupta
-##' @export
-plot_mmpd_null_grid <- function(mmpd_dist_null_grid, mmpd_null_orig) {
-  
-  compute_p_value <- left_join(mmpd_dist_null_grid, mmpd_null_orig,
-                               by = c("nx", "nfacet")) %>% 
-    group_by(nx, nfacet) %>% 
-    summarise(p_value = sum(if_else(abs(mmpd.x)>abs(mmpd.y),1,0))/n(), .groups = 'drop')
-
-  ggplot() + 
-    geom_histogram(data = mmpd_dist_null_grid, aes(x = mmpd))  + 
-    geom_vline(data = mmpd_null_orig, aes(xintercept = mmpd),colour = "red") +
-    geom_text(data = compute_p_value, size = 3,  
-              aes(x = -Inf,
-                  y =  Inf,
-                  label = paste("p-value:",p_value),
-                  hjust   = 0,
-                  vjust   = 1)) + 
-    facet_grid(nx ~ nfacet)
-}

### 2021-01-20 paper/R/rank_harmony.R

@@ -1,306 +1,0 @@
-#' Plotting probability distributions across granularities
-#'
-#' Plot probability distribution of univariate series across bivariate temporal granularities.
-#'
-#' @param .data a tsibble, if cyclic granularity needs to be constructed or a list consisting of tibbles for each pair of cyclic granularity in the harmony table
-#' @param harmony_tbl A tibble of harmonies and their levels obtained from the function().
-#' @param response response variable.
-#' @param prob numeric vector of probabilities with values in [0,1].
-#' @param hierarchy_tbl A hierarchy table specifying the hierarchy of units
-#' @param dist_distribution Underlying distribution of distances. Look at hist_distance()
-#' @param dist_ordered if levels of the time granularity is ordered.
-#' @param alpha significance level
-#' @param create_gran_data if data corresponding to a pair of cyclic granularity needs to be created
-#' @return  A tibble of harmonies and their levels ranked in descending order of average maximum pairwise distance of the harmony pairs.
-#
-#' @examples
-#' library(tsibbledata)
-#' library(ggplot2)
-#' library(tsibble)
-#' library(lvplot)
-#' library(dplyr)
-#' library(gravitas)
-#' library(purrr)
-#' library(magrittr)
-#' sm <- smart_meter10 %>%
-#' filter(customer_id %in% c("10017936"))
-#' harmonies <- sm %>%
-#' harmony(ugran = "month",
-#'        filter_in = "wknd_wday",
-#'        filter_out = c("hhour", "fortnight"))
-#' .data = sm
-#' response  = "general_supply_kwh"
-#' harmony_tbl =  harmonies
-#' smart_harmony <- .data %>% rank_harmony(harmony_tbl = harmonies,
-#' response = "general_supply_kwh", dist_ordered = TRUE)
-#' harmony_tbl <- PBS %>% harmony(ugran = "year")
-#' rank_harmony(PBS, harmony_tbl = harmony_tbl, response = "Cost")
-#' @export rank_harmony
-#' @export create_harmony_data
-
-rank_harmony <- function(.data = NULL,
-                         harmony_tbl = NULL,
-                         response = NULL,
[…]

### 2021-01-20 paper/R/shuffle_x_for_each_facet.R

@@ -1,52 +1,0 @@
-##' .. content for \description{} (no empty lines) ..
-##'
-##' .. content for \details{} ..
-##'
-##' @title
-##' @param sim_panel_data
-##' @return
-##' @author Sayani Gupta
-##' @export
-##' @example 
-#'sim_panel_ex  = sim_panel(nx = 3,     
-#'                          nfacet = 2, 
-#'                          ntimes = 2,                   
-#'                          sim_dist = distributional::dist_normal(5, 10))
-#' shuffle_x_for_each_facet(sim_panel_ex)
-
-shuffle_x_for_each_facet <- function(sim_panel_data) {
-
-  nx <- sim_panel_data %>% distinct(nx) %>% .$nx
-  nfacet <- sim_panel_data %>% distinct(nfacet) %>% .$nfacet
-  
-  
-  shuffled_data <- (seq_len(nfacet)) %>% 
-    map_df(function(i){
-      #(nx)%>%
-        #map_df(function(j){
-          filter_data = sim_panel_data %>% dplyr::filter(id_facet==i)
-          new_sim_data = sample(filter_data$sim_data, nrow(filter_data))
-          bind_cols(filter_data, new_sim_data = new_sim_data)
-        }) %>% select(-sim_data) %>% 
-        rename("sim_data" = "new_sim_data")
-  
-  
-  # nsample <- sim_panel_data %>% 
-  #   group_by(nfacet, nx) %>% 
-  #   summarise(count = n()) %>% 
-  #   ungroup() %>% 
-  #   .$count
-  # 
-  # nested_data <- sim_panel_data %>%
-  #   group_by(nfacet, nx)  %>% 
-  #   nest(sim_data) %>% 
-  #   ungroup() %>% 
-  #   mutate(n = nsample)
-  # 
-  #     shuffled_data <- nested_data %>%
-  #       mutate(samp = map2(data, n, sample_n, replace = TRUE)) %>%
-  #       select(-data, -n) %>% 
-  #       unnest(samp)
-  #     
-      shuffled_data 
-}

### 2021-01-21 loop_local_all_households.R
updating materials

@@ -1,0 +1,68 @@
+#This script calculates raw mmpd for each simulation scenario
+##Read Simulation Table
+
+.libPaths(c("~/R/libs", .libPaths()))
+library(distributional)
+library(readr)
+library(drake)
+library(tidyverse)
+library(hakear)
+library(gravitas)
+library(parallel)
+
+
+set.seed(9999)
+
+# change path while running it on HPC
+simtable<-read_csv('paper/sim_table/sim_table.csv')
+harmonies<-read_csv('paper/sim_table/harmonies.csv')
+sm_cust_data <- read_rds("paper/data/sm_cust_data.rds")
+
+### Extract flags from simulation scenario
+
+# scen<- 170 #If running within R uncomment this.  This will only run first scenario
+#scen<-as.numeric(commandArgs()[[6]]) # If running batch job uncomment this
+
+mclapply(seq_len(nrow(simtable)),
+                   function(scen){
+
+simj<-simtable[scen,] #Extract row of table
+customer_idj <- simj$customer_id
+facetj <- simj$facet_variable
+xj <- simj$x_variable
+harmony_tbl_rowj <- simj[-c(1:2)]
+dataj <- sm_cust_data %>% filter(customer_id %in% customer_idj)
+
+# all_data <- create_harmony_tbl_data(dataj,
+#                     harmonies,
+#                     general_supply_kwh)  
+#   
+
+all_data <- create_harmony_data(dataj,
+                                harmony_tbl_rowj,
+                                general_supply_kwh)  
+
+
+# wpd_norm <- mclapply(all_data, function(x){
+
+
+wpd_norm <- compute_pairwise_norm(all_data, 
+                                  gran_x = "id_x",
+                                  gran_facet = "id_facet",
+                                  response = sim_data,
+                                  quantile_prob =
+                                    seq(0.01, 0.99, 0.01), 
+                                  nperm = 200)
+
+
+wpd_harmonies <- bind_cols(customer_id = customer_idj, 
+                           harmony_tbl_rowj,
+                           wpd_norm = wpd_norm %>% unlist() %>% round(digits = 3))
+
+
+saveRDS(wpd_harmonies,
+        paste0('paper/sim_table/results/',
+               customer_idj,"-",
+               facetj, "-", 
+               xj, '.rds')) # seed and dist not included yet
+})

### 2021-01-21 paper/sim_table/aggregate01.R

@@ -1,0 +1,44 @@
+# contains function to aggregate data each for from N(0,1), N(0,5), N(5,1), N(5,5), Gamma(0.5, 1), Gamma(2, 1)
+#  aggregated data from the file simulations/results/norm/folder_name and tidy them up
+library(tidyverse)
+library(here)
+library(readr)
+library(rlang)
+
+  
+  all_files = list.files(path = paste0("paper/sim_table/results/"), 
+                         pattern = ".rds")
+  
+  names_levels <- map_dfr(all_files, 
+                          function(x){
+                            z = str_split(str_remove(x, 
+                                                     ".rds"), 
+                                          "-") %>% unlist()
+  
+                            bind_cols(customer_id = as.numeric(z[1]),
+                                      facet_variable = z[2],
+                                      x_variable = z[3])
+                          })
+  
+  # len_file = read_rds(("simulations/results/norm/tuning_param/2_2_tuning_param.rds"))
+  # 
+  # names_rep <- names_levels %>% slice(rep(1:n(), each = nrow(len_file)))
+  
+  
+  all_files_path <- paste0("paper/sim_table/results/",
+                           all_files)  
+  
+  
+  all_data <- lapply(1:length(all_files_path), function(x){
+    
+    data = all_files_path %>% magrittr::extract2(x) %>% 
+      readRDS()
+    # 
+    # names = names_levels %>% magrittr::extract(x,)
+    # names_rep =   names %>% slice(rep(1:n(), each = nrow(data)))
+    # bind_cols(names_rep, data)
+  }) %>% 
+    bind_rows() %>%
+    arrange(customer_id)
+  
+  write_rds(all_data, "paper/sim_table/all_data.rds")

### 2021-01-21 paper/sim_table/makegraph02.R

@@ -1,0 +1,32 @@
+library(here)
+library(readr)
+library(tidyverse)
+# run for  norm MMPD files aggregation
+#all_data <- read_rds("simulations/result_report/all_data_ norm.rds")
+# run for  norm max pairwise distances files aggregation
+
+
+
+
+all_data <- write_rds(all_data, "paper/sim_table/all_data.rds")
+
+facet_variable = "day_week"
+x_variable = "hour_day"
+
+one_harmony_data <- all_data %>% filter(facet_variable == "day_week",
+                    x_variable == "hour_day")
+
+mds<- one_harmony_data %>%
+  select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
+  dist() %>%          
+  cmdscale() %>%
+  as_tibble()
+
+colnames(mds) <- c("Dim.1", "Dim.2")
+rownames(mds) <- unique(one_harmony_data$customer_id)
+# Plot MDS
+ggpubr::ggscatter(mds, x = "Dim.1", y = "Dim.2", 
+          label = rownames(mds),
+          size = 1,
+          repel = TRUE)
+

### 2021-01-21 simulations/supplementary/sim_table/simtable.R

@@ -2,10 +2,10 @@
 library(tidyverse)
 # nperm and nsim can run parallelly
 sim_table <- expand.grid(#data = c(99, 9999), # different data with same specifications
-  #nperm = c(10, 30, 50, 100, 300, 500),
-  nperm = c(10, 30, 500),
-  #ntimes = c(2, 5, 10, 30, 100, 500),
-  ntimes = c(5, 500),
+  nperm = c(10, 30, 50, 100, 300, 500),
+  #nperm = c(10, 30, 500),
+  ntimes = c(2, 5, 10, 30, 100, 500),
+  #ntimes = c(5, 500),
   # different permutations to compute mean and sd
   #nobs_each_comb  = c(10, 40, 500), # different number of observations for each combinations for each panel
   #nobs_diff_comb  = c("comb1", "comb2"), # different number of observations for different combinations for each panel

### 2021-01-27 scalar_transformation.Rmd
scalar transformation document update

---
title: "Choosing an appropriate scalar transformation to normalise wpd"
author: "Sayani Gupta"
date: "28/01/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      eval = TRUE,
                      warning = FALSE,
                      message = FALSE)
knitr::read_chunk("example_transformations.R")
library(tidyverse)
library(readr)
library(ggplot2)
```

 - Data presented

Observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high. Each combination is being referred to as a _panel_. That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$. For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories. That is, if we consider the panel  $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$. The values of $\lambda$ is set to $0.67$ and values of raw wpd is obtained.

 - How the distribution of the raw wpd looks across nfacets and nx?

 Both shape and scale of the distribution changes for different nx and nfacet categories.

```{r read}
N01 <- read_rds("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds")
```

```{r raw}
N01 %>% 
  ggplot(aes(x = value)) + 
  geom_density(fill = "blue") +
  facet_grid(nx~nfacet,
             labeller = "label_both") + 
  scale_x_continuous(breaks = scales::breaks_extended(3)) + 
  xlab("raw wpd")
```

 - Plot the values of wpd against nx*nfacet to see the rough relationship

```{r}
N01 %>% 
  ggplot(aes(x=as.factor(nx*nfacet), y = value)) +
  geom_boxplot() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + xlab("nx*nfacet") + ylab("raw wpd")

```
 - Plot the values of wpd against nx*nfacet to see if the same relationship holds for different nx and nfacet relationships

Looks like for all the variations, there is a quadratic relationship between wpd values and nx*nfacet

```{r}
every_nth = function(n) {
  return(function(x) {x[c(TRUE, rep(FALSE, n - 1))]})
}
```

```{r}
N01 %>% 
  mutate(comp_lev = if_else(nx<nfacet, "nx<nfacet",
                            if_else(nx>nfacet,
                               "nx>nfacet", "nx=nfacet"))) %>% 
  ggplot(aes(x=as.factor(nx*nfacet), y = value)) +
  geom_boxplot() + facet_wrap(~comp_lev) + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + xlab("nx*nfacet") + ylab("raw wpd") + scale_x_discrete(breaks = every_nth(n = 5))
```

 - Attempt to linearize it with sqrt, sqrt(sqrt) and log (sqrt(sqrt))

 The transformation log (sqrt(sqrt())) on nx*nfacet finally makes it approximately linear.

```{r}
N01 %>% 
  mutate(comp_lev = if_else(nx<nfacet, "nx<nfacet",
                            if_else(nx>nfacet,
                                    "nx>nfacet", "nx=nfacet"))) %>% 
  ggplot(aes(x=sqrt(nx*nfacet), y = value)) +
  geom_point() + facet_wrap(~comp_lev) + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + ylab("raw wpd")

N01 %>% 
  mutate(comp_lev = if_else(nx<nfacet, "nx<nfacet",
                            if_else(nx>nfacet,
                                    "nx>nfacet", "nx=nfacet"))) %>% 
  ggplot(aes(x=sqrt(sqrt(nx*nfacet)), y = value)) +
  geom_point() + facet_wrap(~comp_lev) + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + ylab("raw wpd")

N01 %>% 
  mutate(comp_lev = if_else(nx<nfacet, "nx<nfacet",
                            if_else(nx>nfacet,
                                    "nx>nfacet", "nx=nfacet"))) %>% 
  ggplot(aes(x=log(sqrt(sqrt(nx*nfacet))), y = value)) +
  geom_point() + facet_wrap(~comp_lev) + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + ylab("raw wpd")

```

 - Distribution after linearizing it

The distribution of $wpd_{norm} = log(sqrt(sqrt(nx*nfacet)))/wpd$ is plotted. The shape and spread look similar but location is shifting to the right.

(If we define $wpd_{norm}$ as the inverse of it, the values become too small and the distribution too skewed. Hence the inverse of it is considered.)

<!-- even after doing Box-cox transformation to up-weight the lower values of nx*nfacet and down-weigh higher values -->

```{r}
 N01 %>% 
  ggplot(aes(x = forecast::BoxCox(log(sqrt(sqrt(nx*nfacet)))/value,
             lambda = "auto"))) + 
  geom_density(fill = "blue") +
  facet_grid(nx~nfacet,
             labeller = "label_both") + 
  xlab("wpd norm")

```

What we want is a transformation which will be constant and not linear to obtain similar locations for all panels.

### 2021-01-31 paper/main.Rmd
updating materials
added what I learnt from simulation

@@
 here::here()
-read_chunk(here::here("paper/R/", "null_distribution.R"))
-read_chunk(here::here("paper/R/", "mean_null.R"))
-source(here::here("paper/R/sim_panel.R"))
+#knitr::read_chunk(here::here("paper/R/", "null_distribution.R"))
+#knitr::read_chunk(here::here("paper/R/", "mean_null.R"))
+#source(here::here("paper/R/sim_panel.R"))
 # Set up plan
@@
 The tabulated values and graphical representations of the simulation results are provided in Appendix. The learning from the simulations are as follows:
-
-## Properties
+The values of the measure $wpd_{raw}$ is least for $D_{null}$, followed by 
+$D_{var_f}$, $D_{var_x}$) and $D_{var_{all}}$). This is a desirable result since the measure $wpd_{raw}$ was designed such that this relationship holds.
+Furthermore, the distribution of the measure $wpd_{raw}$ changes for different facet and x categories.
+The location of the distribution shifts to the right and it also becomes more skewed for more higher facet and x-axis categories.
+Now this is not desirable, as it would mean that we can't compare the $wpd_{raw}$ values across different panels.
+The distribution of $wpd_{norm}$ looks more similar with at least the mean and standard of the distributions being uniform across panels.
+This means,  $wpd_{norm}$ could be used to measure differences in distribution across panels.
+Also, note that since the data is processed using normal-quantile-transform, this measure is independepent of the intial distribution of the underlying data and hence is also comparable across different datasets.
+This is valid for the case when sample size $ntimes$ for each combination of categories is at least 30 and  $nperm$ used for computing $wpd_{norm}$ is at least 100.
+More detailed results about the properties of $wpd_{raw}$ and $wpd_{norm}$ could be found in Appendix.
 

### 2021-02-03 paper/main.Rmd
renv lib and minor edits in application of main.Rmd

@@
 
+Complete randomness in the measured variable indicates that the process follows a homogeneous underlying distribution over the whole time series, irrespective of the different cyclic granularities; which essentially implies there is no interesting distinct across any particular time deconstruction.
+We can remove the harmonies for which no interesting patterns are observed through a randomisation permutation method.
+Essentially, this method is
+based on the generation of randomly chosen reassignments
+(permutations) of the data across different cyclic granularities and the the computation for each permutated data of the theoretical distribution of $wpd_{norm}$ expected under the null hypothesis.
+The percentages of the theoretical distribution greater than or equal to the respective observed $wpd_{norm}$ values are calculated and used to obtain the P value.
+The procedure for the permutation test is:
+
+**Assumption:** random permutation without considering ordering 
+(global)
+
+1. Given the data; $\{v_t: t=0, 1, 2, \dots, T-1\}$, the $wpd_norm$ is computed and is represented by $wpd_{obs}$.
+
+2. From the original sequence a random permutation is obtained: $\{v_t^*: t=0, 1, 2, \dots, T-1\}$.
+
+3. $wpd_norm$ is computed for all random permutation of the data and is represented by $wpd_{sample}$.
+
+4.  Steps (2) and (3) are repeated a large number
+of times M (e.g. 200).
+
+5. For each permutation, one $wpd_{sample}$ value is obtained.
+
+6. $95^{th}$ percentile of this $wpd_{sample}$ distribution is computed and stored in $wpd_{threshold}$.
+
+7. If $wpd_{obs}> wpd_{threshold}$, harmony pairs are accepted. Only one threshold for all harmony pairs.
+
+Pros: Considering thresholds global for all harmony pairs would imply less computation time.
+
+```{r, eval = FALSE, echo = FALSE}
+smart_harmony <-read_rds("data/smart_harmony_nonst.rds")
+smart_harmony
+```
+
+```{r smart_harmony,eval = FALSE, echo = FALSE}
+
+sm <- smart_meter10 %>% dplyr::filter(customer_id %in% c("10017936"))
+
+harmonies <- sm %>% 
+  harmony(ugran = "month",
+          filter_in = "wknd_wday",
+          filter_out = c("hhour", "fortnight"))
+
+harmony_tbl =  harmonies
+
+smart_harmony <- sm %>% 
+  rank_harmony(harmony_tbl = harmonies,
+               response = "general_supply_kwh", 
+               dist_ordered = TRUE)
+
+smart_harmony %>% 
+  mutate(MMPD = round(MMPD, 3), max_pd = round(max_pd, 3)) %>% 
+  mutate(rankn = row_number()) %>%
+  rename("rankun" = "r") %>% kable()
+```
+
+## Size, power and confidence interval
+
+#### Characteristics under different simulation designs   
+A set of simulation runs that are conducted and some outputs of which are reported.
+
+```{r sim_all, echo = FALSE}
+bind_files = readr::read_rds("../hakear-drake/data/compute_p_value.rds")
+
+bind_files$design = 
+  factor(bind_files$design,
+         levels = c("null","vary_f", "vary_x", "vary_all"), labels = c("D1", "D2", "D3", "D4"))
+
+ggplot(bind_files %>% 
+         filter(distribution == "normal")) +
+  geom_point(aes(x=design, y = p_value),
+                 alpha = 0.5)+
+  facet_grid(nx~nfacet) +
+  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
+
+ggplot(bind_files %>% 
+         filter(distribution == "exponential")) +
+  geom_point(aes(x=design, y = p_value),
+                 alpha = 0.5)+
+  facet_grid(nx~nfacet) +
+  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
+
+ggplot(bind_files %>% 
+         filter(distribution == "gamma")) +
+  geom_point(aes(x=design, y = p_value),
+                 alpha = 0.5)+
+  facet_grid(nx~nfacet) +
+  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
+
+ggplot(bind_files %>% 
+         filter(distribution == "weibull")) +
+  geom_point(aes(x=design, y = p_value),
+                 alpha = 0.5)+
+  facet_grid(nx~nfacet) +
+  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
+```
+
+```{r sim_conf, echo = FALSE, eval = FALSE}
+library(dplyr)
+library(ggplot2)
+ggplot2::ggplot(design_all %>% 
+                      filter(design == "D1", distribution == "norm")) +
+  geom_boxplot(aes(x = as.factor(nx), 
+                   y = mmpd.x), width = 0.1) + 
+  facet_wrap(~nfacet) +
+  scale_fill_viridis_d() +
+  xlab("number of x levels") +
+  coord_flip()
+
+```
+
 # Applications {#sec:application}
@@
 ### 50 households together
+
+Cluster analysis and multidimensional scaling (MDS) methods are used to explore the temporal structure of various households, their interrelations and determine similar behaving clusters of households in this study.
+
+$wpd_norm$ is considered as the measure of similarity or dissimilarity while using MDS and clustering techniques.
+$wpd_norm$ could be constructed for each pair of harmony for each household and then similarity could be measured across individual or all harmonies together.
+MDS methods are used to produce a lower dimensional display space where each household is represented by a point and the distance between these points give the measure of similarity between these households.
+On the other hand, clustering techniques are used to provide information about the clustering structure of the households.
+Households that are in the same cluster can be considered to be more similar, while households are more dissimilar in their energy behavior across one or few temporal deconstructions.
 

### 2021-02-03 shinu.R

@@ -1,27 +1,0 @@
-library(shiny)
-library(plotly)
-library(ggplot2)
-
-ui <- fluidPage(
-  plotlyOutput("mainplot"),
-  plotlyOutput("hover")
-)
-
-server <- function(input, output) {
-  output$mainplot <- renderPlotly({
-    # https://plot.ly/r/
-    d <- diamonds[sample(nrow(diamonds), 1000), ]
-    plot_ly(d, x = carat, y = price, text = paste("Clarity: ", clarity), mode = "markers", color = carat, size = carat, source="main")
-  })
-  
-  output$hover <- renderPlotly({
-    eventdat <- event_data('plotly_hover', source="main") # get event data from source main
-    if(is.null(eventdat) == T) return(NULL)        # If NULL dont do anything
-    point <- as.numeric(eventdat[['pointNumber']]) # Index of the data point being charted
-    
-    # draw plot according to the point number on hover
-    plot_ly(  x = c(1,2,3), y = c(point, point*2, point*3), mode = "scatter")
-  })
-}
-shinyApp(ui, server)
-

### 2021-02-03 simulations/supplementary/sim_table/simtable.R

@@ -2,9 +2,9 @@
 library(tidyverse)
 # nperm and nsim can run parallelly
 sim_table <- expand.grid(#data = c(99, 9999), # different data with same specifications
-  nperm = c(10, 30, 50, 100, 300, 500),
+  nperm = c(10, 30, 50, 100, 300),
   #nperm = c(10, 30, 500),
-  ntimes = c(2, 5, 10, 30, 100, 500),
+  ntimes = c(5, 30, 100, 500),
   #ntimes = c(5, 500),
   # different permutations to compute mean and sd
   #nobs_each_comb  = c(10, 40, 500), # different number of observations for each combinations for each panel
@@ -20,8 +20,9 @@ sim_table <- expand.grid(#data = c(99, 9999), # different data with same specifi
   design = c("null", "vary_x", "vary_f", "vary_all"),
   #seed = seq(1500, 7500, 1000),
   seed = c(1500),
-  w = c(seq(1, 20, 7), 50),
-  type = c("raw", "norm-nperm")
+  #w = c(seq(1, 20, 7), 50),
+  w = c(1, 10, 50),
+  type = c("norm-nperm")
              
 ) %>% tibble()
 

### 2021-02-04 scalar_transformation.Rmd
added transformation script

@@
 
- - How the distribution of the raw wpd looks across nfacets and nx?
-
+ - How the distribution of the raw wpd (without any transformation for normalization) looks across nfacets and nx?
 Both shape and scale of the distribution changes for different nx and nfacet categories.
@@
 ```{r read}
-N01 <- read_rds("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds")
+N01 <- read_csv("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.csv")
 ```
@@
 
- - Plot the values of wpd against nx*nfacet to see the rough relationship
+ - Plot the values of raw wpd against nx*nfacet to see the rough relationship
 
@@
 N01 %>% 
-  ggplot(aes(x=as.factor(nx*nfacet), y = value)) +
-  geom_boxplot() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + xlab("nx*nfacet") + ylab("raw wpd")
+  ggplot(aes(x=nx*nfacet, y = value)) +
+  geom_point() + stat_summary(fun=median, geom="line", aes(group=1), color = "blue") + xlab("nx*nfacet") + ylab("raw wpd")
 
 ```
- - Plot the values of wpd against nx*nfacet to see if the same relationship holds for different nx and nfacet relationships
 
-Looks like for all the variations, there is a quadratic relationship between wpd values and nx*nfacet
+**Current attempt**
+
+- Fit a log-linear relationship of median(values) to log(nx*nfacet) as discussed today. The fit is pretty good.
+
+```{r, echo = TRUE}
+N01_median <- N01 %>% 
+  group_by(nx*nfacet) %>% 
+  summarise(actual = median(value))
+
+fit_lm2 <- lm(actual ~ poly(log(`nx * nfacet`) ,1, raw=TRUE), data = N01_median)
+summary(fit_lm2)
+```
+
+- Make it a horizontal line so that the values are not affected by 
+nx\*nfacet by plotting (value - intercept)/log(nx\*nfacet) against log(nx*nfacet). The line actually becomes horizontal after this transformation.
 
 ```{r}
-every_nth = function(n) {
-  return(function(x) {x[c(TRUE, rep(FALSE, n - 1))]})
-}
+intercept <- fit_lm2$coefficients[1]
+slope <- fit_lm2$coefficients[2]
+
+N01 %>% 
+  ggplot(aes(x=log(nx*nfacet), y = (value - intercept)/log(nx*nfacet))) +
+  geom_point() + stat_summary(fun=median, geom="line", aes(group=1), color = "blue")
+
 ```
+- See distribution of the transformed variable across nx and nfacets. For higher values of nx and nfacet, the distribution is similar, but not for lower values.
 
@@
 N01 %>% 
-  mutate(comp_lev = if_else(nx<nfacet, "nx<nfacet",
-                            if_else(nx>nfacet,
-                               "nx>nfacet", "nx=nfacet"))) %>% 
-  ggplot(aes(x=as.factor(nx*nfacet), y = value)) +
-  geom_boxplot() + facet_wrap(~comp_lev) + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + xlab("nx*nfacet") + ylab("raw wpd") + scale_x_discrete(breaks = every_nth(n = 5))
-```
-
- - Attempt to linearize it with sqrt, sqrt(sqrt) and log (sqrt(sqrt))
-
- The transformation log (sqrt(sqrt())) on nx*nfacet finally makes it approximately linear.
-
-```{r}
-N01 %>% 
-  mutate(comp_lev = if_else(nx<nfacet, "nx<nfacet",
-                            if_else(nx>nfacet,
-                                    "nx>nfacet", "nx=nfacet"))) %>% 
-  ggplot(aes(x=sqrt(nx*nfacet), y = value)) +
-  geom_point() + facet_wrap(~comp_lev) + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + ylab("raw wpd")
-
-N01 %>% 
-  mutate(comp_lev = if_else(nx<nfacet, "nx<nfacet",
-                            if_else(nx>nfacet,
-                                    "nx>nfacet", "nx=nfacet"))) %>% 
-  ggplot(aes(x=sqrt(sqrt(nx*nfacet)), y = value)) +
-  geom_point() + facet_wrap(~comp_lev) + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + ylab("raw wpd")
-
-N01 %>% 
-  mutate(comp_lev = if_else(nx<nfacet, "nx<nfacet",
-                            if_else(nx>nfacet,
-                                    "nx>nfacet", "nx=nfacet"))) %>% 
-  ggplot(aes(x=log(sqrt(sqrt(nx*nfacet))), y = value)) +
-  geom_point() + facet_wrap(~comp_lev) + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + ylab("raw wpd")
+  ggplot(aes(x = (value - intercept)/(log(nx*nfacet)))) + 
+  geom_density(fill = "blue") +
+  facet_grid(nx~nfacet,
+             labeller = "label_both") + 
+  xlab("wpd") +
+  scale_x_continuous(breaks = scales::breaks_extended(3))
 
@@
 
- - Distribution after linearizing it
-
-The distribution of $wpd_{norm} = log(sqrt(sqrt(nx*nfacet)))/wpd$ is plotted. The shape and spread look similar but location is shifting to the right.
-
-(If we define $wpd_{norm}$ as the inverse of it, the values become too small and the distribution too skewed. Hence the inverse of it is considered.)
+**Earlier attempt**
+ - The distribution of $wpd_{norm} = log(sqrt(sqrt(nx*nfacet)))/wpd$ is plotted since the plot of log(sqrt(sqrt(nx * nfacet))) against wpd looked linear.
+The shape and spread look similar but location is shifting to the right.
+(If we define $wpd_{norm}$ as the inverse of it, the values become too small and the distribution too skewed.
+Hence the inverse of it is considered.)
 
@@
 ```{r}
+
 N01 %>% 
-  ggplot(aes(x = forecast::BoxCox(log(sqrt(sqrt(nx*nfacet)))/value,
-             lambda = "auto"))) + 
+  ggplot(aes(x=log(nx*nfacet),
+             y = log(sqrt(nx*nfacet))/value)) +
+  geom_point() + stat_summary(fun=median, geom="line", aes(group=1), color = "blue")
+
+ N01 %>% 
+  ggplot(aes(x = log(sqrt(nx*nfacet))/value)) + 
+  geom_density(fill = "blue") +
+  facet_grid(nx~nfacet,
+             labeller = "label_both") + 
+  xlab("wpd norm")
+```
+
+What we want is a transformation which will be constant and not linear to obtain similar locations for all panels.
+
+```{r}
+fit2 <- lm(log(sqrt(nx*nfacet))/value ~ log(nx*nfacet), N01)
+intercept <- fit2$coefficients[1]
+slope <- fit2$coefficients[2]
+
+N01 %>% 
+ggplot(aes(x = 
+             (log(sqrt(nx*nfacet)) - intercept)/log(nx*nfacet))) +
 geom_density(fill = "blue") +
@@
 ```
-
-What we want is a transformation which will be constant and not linear to obtain similar locations for all panels.

### 2021-02-04 example_transformations.R

@@ -2,11 +2,15 @@ library(readr)
 library(tidyverse)
 
 ## --- read
-N01 <- read_rds("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds")
+# N01 <- read_rds("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds")
+
+N01 <- read_csv("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.csv")
+
 
 write_csv(N01, "simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.csv")
 
 ## ---raw
+
 N01 %>% 
   ggplot(aes(x = value)) + 
   geom_density(fill = "blue") +
@@ -14,6 +18,7 @@ N01 %>%
              labeller = "label_both") + 
   xlab("wpd") +
   scale_x_continuous(breaks = scales::breaks_extended(3))
+
 
 ## ----log
 log <- N01 %>% 
@@ -62,14 +67,17 @@ boxcox <- N01 %>%
              labeller = "label_both") + 
   xlab("wpd") +
   scale_x_continuous(breaks = scales::breaks_extended(3))
-
+x
 
 ##----raw-nx_nfacet_product
 # raw: Di asked you to see this relationship
 
 N01 %>% 
-  ggplot(aes(x=as.factor(nx*nfacet), y = value)) +
-  geom_boxplot() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") 
+  ggplot(aes(x=log(nx*nfacet), y = (value - mean(value))/log(nx*nfacet))) +
+  geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") 
+
+
+
 
 ##----raw-nx_nfacet_product_cat
 # seeing if the relationship differs for nx<nfacet or nx>nfacet
@@ -140,28 +148,62 @@ N01_median <- N01 %>%
 # fit4 <- lm(median_value~poly(`nx * nfacet` ,4, raw=TRUE), data = N01_median)
 # 
 
-N01_median %>% 
+fit <- N01_median %>% 
   mutate(lm  = predict(lm(actual ~`nx * nfacet` , data = N01_median)),
          lm_order2 = predict(lm(actual ~ poly(`nx * nfacet` ,2, raw=TRUE), data = N01_median)),
          fit3 = predict(lm(actual ~ poly(`nx * nfacet` ,3, raw=TRUE), data = N01_median)),
[…]

### 2021-02-04 scalar_transformation.Rmd
transformation with my earlier attempt included

@@
  - How the distribution of the raw wpd (without any transformation for normalization) looks across nfacets and nx?
-Both shape and scale of the distribution changes for different nx and nfacet categories.
+Both shape and scale of the distribution changes for different nx and nfacet categories as could be seen in Figure \ref{fig:raw}.
 
@@
 
-```{r raw}
+```{r raw, fig.cap="Distribution of raw wpd is plotted across different nx and nfacet categories. Both shape and scale of the distribution changes for different nx and nfacet categories."}
 N01 %>% 
@@
 
- - Plot the values of raw wpd against nx*nfacet to see the rough relationship
+ - Plot the values of raw wpd against nx*nfacet to see the rough relationship (\ref{fig:quadratic}).
 
-```{r}
+```{r quadratic, fig.cap = "The raw wpd is plotted against nx*nfacet and the blue line represents the median of the multiple values for each nx*nfacet levels."}
 N01 %>% 
@@
 
-- Fit a log-linear relationship of median(values) to log(nx*nfacet) as discussed today. The fit is pretty good.
+- Fit a log-linear model of median(values) to log(nx*nfacet) as discussed today. The fit is pretty good and the summary of the fit is shown below.
 
@@
 - Make it a horizontal line so that the values are not affected by 
-nx\*nfacet by plotting (value - intercept)/log(nx\*nfacet) against log(nx*nfacet). The line actually becomes horizontal after this transformation.
+nx\*nfacet by plotting $wpd_{norm} = (value - intercept)/log(nx*nfacet)$ against log(nx*nfacet).
+The line actually becomes horizontal after this transformation as could be seen in Figure \ref{fig:horizontal}.
 
-```{r}
+```{r horizontal, fig.cap = "wpd_{norm} is plotted against log(nx*nfacet).
+The relationship changed from being non-linear to almost horizontal.
+The horizontal line would imply that median values of wpd are unaffected by the value of nx* nfacet."}
+
 intercept <- fit_lm2$coefficients[1]
@@
   ggplot(aes(x=log(nx*nfacet), y = (value - intercept)/log(nx*nfacet))) +
-  geom_point() + stat_summary(fun=median, geom="line", aes(group=1), color = "blue")
+  geom_point() + stat_summary(fun=median, geom="line", aes(group=1), color = "blue")  +
+  ylab("wpd_norm = (wpd - intercept)/log(nx*nfacet)")
 
 ```
-- See distribution of the transformed variable across nx and nfacets. For higher values of nx and nfacet, the distribution is similar, but not for lower values.
+- See distribution of the transformed variable $wpd_{norm}$ across nx and nfacets. For higher values of nx and nfacet, the distribution is similar, but not for lower values.
 
-```{r}
+```{r, fig.cap = "The distribution of the transformed wpd is plotted.
+The shape and the scale of the distribution still changes across different nx and nfacet levels, but seems uniform for higher levels." }
 N01 %>% 
@@
 
-```{r}
+```{r, fig.cap = "Earlier attempt: A different transformation was used for making the relationship linear and then horizontal.
+The linear relationship looks promising but when the same method was applied to make it horizonal and eventually look at the distribution, it was again found that the distributions across different nx and nfacets are not similar."}
 
@@
              labeller = "label_both") + 
-  xlab("wpd norm")
+  xlab("log(sqrt(nx*nfacet))/value")
 ```
@@
 
-```{r}
+```{r, fig.cap="Same approach was employed to make it" }
 fit2 <- lm(log(sqrt(nx*nfacet))/value ~ log(nx*nfacet), N01)
@@
 N01 %>% 
+  ggplot(aes(x=log(nx*nfacet), 
+             y = ((log(sqrt(nx*nfacet))/value - intercept)/log(nx*nfacet)))) +
+  geom_point() + stat_summary(fun=median, geom="line", aes(group=1), color = "blue")
+
+N01 %>% 
 ggplot(aes(x = 
-             (log(sqrt(nx*nfacet)) - intercept)/log(nx*nfacet))) +
+             (log(sqrt(nx*nfacet))/value - intercept)/log(nx*nfacet))) +
 geom_density(fill = "blue") +

### 2021-02-04 scalar_transformation.Rmd
trnsformation with earlier attempts removed

@@
   xlab("wpd") +
-  scale_x_continuous(breaks = scales::breaks_extended(3))
+  scale_x_continuous(breaks = scales::breaks_extended(3)) +
+  xlab("wpd_norm = (wpd - intercept)/(log(nx*nfacet)")
 
@@
 
-**Earlier attempt**
- - The distribution of $wpd_{norm} = log(sqrt(sqrt(nx*nfacet)))/wpd$ is plotted since the plot of log(sqrt(sqrt(nx * nfacet))) against wpd looked linear.
-The shape and spread look similar but location is shifting to the right.
-(If we define $wpd_{norm}$ as the inverse of it, the values become too small and the distribution too skewed.
-Hence the inverse of it is considered.)
+It was suggested that we can do permutation normalization for smaller levels and this scalar transformation for higher levels as this transformation is working well when both nx and nfacet are high enough.
+There are potentially two problems if we follow that approach:
 
-<!-- even after doing Box-cox transformation to up-weight the lower values of nx*nfacet and down-weigh higher values -->
+- Since the normalized wpd's for different harmonies will be on different scales, harmonies could not be ranked even for the same objects (households) to select the most important household for that object - which was essentially the idea.
+Hence, the normalized wpd's would have to be brought on the same scale irrespective of the approach (whether permutation approach or scalar transformation).
 
-```{r, fig.cap = "Earlier attempt: A different transformation was used for making the relationship linear and then horizontal.
-The linear relationship looks promising but when the same method was applied to make it horizonal and eventually look at the distribution, it was again found that the distributions across different nx and nfacets are not similar."}
-
-N01 %>% 
-  ggplot(aes(x=log(nx*nfacet),
-             y = log(sqrt(nx*nfacet))/value)) +
-  geom_point() + stat_summary(fun=median, geom="line", aes(group=1), color = "blue")
-
- N01 %>% 
-  ggplot(aes(x = log(sqrt(nx*nfacet))/value)) + 
-  geom_density(fill = "blue") +
-  facet_grid(nx~nfacet,
-             labeller = "label_both") + 
-  xlab("log(sqrt(nx*nfacet))/value")
-```
-
-What we want is a transformation which will be constant and not linear to obtain similar locations for all panels.
-
-```{r, fig.cap="Same approach was employed to make it" }
-fit2 <- lm(log(sqrt(nx*nfacet))/value ~ log(nx*nfacet), N01)
-intercept <- fit2$coefficients[1]
-slope <- fit2$coefficients[2]
-
-N01 %>% 
-  ggplot(aes(x=log(nx*nfacet), 
-             y = ((log(sqrt(nx*nfacet))/value - intercept)/log(nx*nfacet)))) +
-  geom_point() + stat_summary(fun=median, geom="line", aes(group=1), color = "blue")
-
-N01 %>% 
-ggplot(aes(x = 
-             (log(sqrt(nx*nfacet))/value - intercept)/log(nx*nfacet))) +
-geom_density(fill = "blue") +
-facet_grid(nx~nfacet,
-labeller = "label_both") +
-xlab("wpd norm")
-
-```
+- We have to think about the cut-offs, that is, for which level of nx and nfacets, we want to move to scalar transformation like this.

### 2021-02-04 scalar_transformation.Rmd
figure caption update
date removed

@@
 author: "Sayani Gupta"
-date: "28/01/2021"
 output: pdf_document
@@
 
-```{r raw, fig.cap="Distribution of raw wpd is plotted across different nx and nfacet categories. Both shape and scale of the distribution changes for different nx and nfacet categories."}
+```{r raw, fig.cap = "Distribution of raw wpd is plotted across different nx and nfacet categories. Both shape and scale of the distribution changes for different nx and nfacet categories."}
 N01 %>% 

### 2021-02-07 scalar_transformation.Rmd
document updated

@@
 author: "Sayani Gupta"
-output: pdf_document
+output:
+  bookdown::pdf_book:
+    #base_format: rticles::asa_article
+    fig_height: 5
+    fig_width: 8
+    fig_caption: yes
+    dev: "pdf"
+    toc: FALSE
 ---
@@
   geom_point() + stat_summary(fun=median, geom="line", aes(group=1), color = "blue")  +
-  ylab("wpd_norm = (wpd - intercept)/log(nx*nfacet)")
+  ylab("wpd_norm1 = (wpd - intercept)/log(nx*nfacet)")
 
@@
   scale_x_continuous(breaks = scales::breaks_extended(3)) +
-  xlab("wpd_norm = (wpd - intercept)/(log(nx*nfacet)")
+  xlab("wpd_norm1")
 
@@
 - We have to think about the cut-offs, that is, for which level of nx and nfacets, we want to move to scalar transformation like this.
+
+# Reduce the heteroskedasticity by the transformation y - a - b*log(n)
+
+In Figure \ref{fig:new-transform}, we see that the transformed wpd value $wpd_{norm2} = wpd - intercept - slope*log(nx*nfacet)$ has lower heteroscedasticity as compared to $wpd_{norm1}$ when plotted across $log(nx*nfacet)$.
+
+```{r new-transform, echo = TRUE, fig.cap = "$wpd_{norm2}$ is plotted against log(nx*nfacet). The relationship is horizontal with reduced heteroscedasticity."}
+N01 %>% 
+  ggplot(aes(x=log(nx*nfacet), y = (value - intercept - slope*log(nx*nfacet)))) +
+  geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
+  xlab("wpd_norm2 =  value - intercept - slope*log(nx*nfacet)")
+```
+
+In Figure \ref{fig:dist-new-transform}, we see that the distribution of $wpd_{norm2}$ is more similar across nx and nfacets than $wpd_{norm1}$.
+
+```{r dist-new-transform, echo = TRUE, fig.cap = " The distribution of $wpd_{norm2}$ is plotted. The distributions are more similar across different nx and nfacets as compared to $wpd_{norm1}$."}
+N01 %>% 
+  ggplot(aes(x = ((value - intercept - slope*log(nx*nfacet))))) + 
+  geom_density(fill = "blue") +
+  facet_grid(nx~nfacet,
+             labeller = "label_both") + 
+  xlab("wpd_norm2 =  value - intercept - slope*log(nx*nfacet)") +
+  scale_x_continuous(breaks = scales::breaks_extended(3))
+```
+
+In Figure \ref{fig:dist-new-approx}, we see that the distribution of $wpd_{norm2}$ is similar when normalised with true or approximate estimates of a and b.
+
+```{r dist-new-approx, echo = TRUE, fig.cap = " The distribution of $wpd_{norm2}$ is plotted for approximate estimate of a and b.
+The distributions are similar when plotted against true estimate of and b."}
+N01_compare <- N01 %>% 
+  mutate(with_true_est = (value - intercept - slope*log(nx*nfacet)),
+
+                          with_approx_est = (value - 0.04 - 0.003*log(nx*nfacet))) %>% 
+  pivot_longer(cols = 5:6,
+               names_to = "type_estimate",
+               values_to = "value_estimate")
+
+N01_compare %>% 
+  ggplot() +
+  geom_density(aes(x = value_estimate, fill = type_estimate), alpha = 0.5) +
+  facet_grid(nx~nfacet,
+             labeller = "label_both") + 
+  xlab("value - intercept - slope*log(nx*nfacet)") +
+  scale_x_continuous(breaks = scales::breaks_extended(3)) +
+  theme(legend.position = "bottom") +
+  scale_fill_manual(values = c("#0072B2", "#D55E00")) +
+  xlab("wpd_norm2")
+```

### 2021-02-08 comparison_perm_scalar.Rmd
comparison of scalar and permutation transformation

---
title: "Compare permutation and scalar transformation approaches on simulated and real data"
author: "Sayani Gupta"
date: "08/02/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      eval = TRUE,
                      warning = FALSE,
                      message = FALSE)
knitr::read_chunk("example_transformations.R")
library(tidyverse)
library(readr)
library(ggplot2)
```

**Simulated data generation:** Observations are generated from a Gamma(2,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high. Each combination is being referred to as a _panel_. That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$. For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories. That is, if we consider the panel  $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$. The values of $\lambda$ is set to $0.67$ and values of raw wpd $wpd_{raw}$ is obtained.

## Scalar transformation approach to normalisation

A log-linear model is fitted to see how the values of $wpd_{raw}$ changes with the values of $nx$ and $nfacet$. The model is of the form $$y = a+b*log(x) +e$$, where $y = median(wpd_{raw})$ and $x = nx*nfacet$. $wpd_norm$ is a transformation on $wpd_{raw}$ which should be designed to remove the effect of $nx*nfacet$ on $wpd_{raw}$ and thus is defined as follows:
$wpd_{norm} = wpd_{raw} - b*log(nx*nfacet)$

## Permutation approach to normalisation

The simulated data for each of the panels is permuted/shuffled $nperm = 100$ times and for each of those permutations $wpd_{norm}$ is computed as follows: $wpd_{norm} =  (wpd_{raw} - mean(wpd_{raw}))/sd(wpd_{raw})$
. This is done so that the distribution of the normalised measure $wpd_{norm}$ has the same mean and standard deviation across different nx and nfacet.

## Comparing the two approaches for simulated data

In Figure \ref{fig:dist-new-transform}, we see that the distribution of $wpd_{norm2}$ is more similar across nx and nfacets than $wpd_{norm1}$.

In Figure \ref{fig:dist-new-approx}, we see that the distribution of $wpd_{norm2}$ is similar when normalised with true or approximate estimates of a and b.

```{r dist-new-approx, echo = TRUE, fig.cap = " The distribution of $wpd_{norm2}$ is plotted for approximate estimate of a and b. The distributions are similar when plotted against true estimate of and b."}

G21 <- read_rds("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds")

G21_median <- G21 %>% 
  group_by(nx*nfacet) %>% 
  summarise(actual = median(value))

# fit model median to log(nx*nfacet)
fit_lm2 <- lm(actual ~ poly(log(`nx * nfacet`) ,1, raw=TRUE), data = G21_median)

summary(fit_lm2)

intercept <- fit_lm2$coefficients[1]
slope <- fit_lm2$coefficients[2]

G21_compare <- G21 %>% 
  mutate(with_true_est = (value - slope*log(nx*nfacet)),

                          with_approx_est = (value - 0.0027*log(nx*nfacet))) %>% 
  pivot_longer(cols = 5:6,
               names_to = "type_estimate",
               values_to = "value_estimate")

G21_compare %>% 
  ggplot() +
  geom_density(aes(x = value_estimate, fill = type_estimate), alpha = 0.5) +
  facet_grid(nx~nfacet,
             labeller = "label_both") + 
  scale_x_continuous(breaks = scales::breaks_extended(3)) +
  theme(legend.position = "bottom") +
  scale_fill_manual(values = c("#0072B2", "#D55E00")) +
  xlab("wpd_norm2")
```

## Comparing the two approaches from real data

### 2021-02-10 comparison_perm_scalar.Rmd
application write up and renv update

@@
 author: "Sayani Gupta"
-date: "08/02/2021"
-output: pdf_document
+output:
+  bookdown::pdf_book:
+    #base_format: rticles::asa_article
+    fig_height: 5
+    fig_width: 8
+    fig_caption: yes
+    dev: "pdf"
+    toc: FALSE
 ---
@@
 
-**Simulated data generation:** Observations are generated from a Gamma(2,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
+# Simulated data
+
+## Data generation
+
+Observations are generated from a Gamma(2,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
 Each combination is being referred to as a _panel_.
@@
 
-The simulated data for each of the panels is permuted/shuffled $nperm = 100$ times and for each of those permutations $wpd_{norm}$ is computed as follows: $wpd_{norm} =  (wpd_{raw} - mean(wpd_{raw}))/sd(wpd_{raw})$
+The simulated data for each of the panels is permuted/shuffled $nperm = 200$ times and for each of those permutations $wpd_{norm}$ is computed as follows: $wpd_{norm} =  (wpd_{raw} - mean(wpd_{raw}))/sd(wpd_{raw})$
 . This is done so that the distribution of the normalised measure $wpd_{norm}$ has the same mean and standard deviation across different nx and nfacet.
 
-## Comparing the two approaches for simulated data
+## Comparing the two approaches
 
-In Figure \ref{fig:dist-new-transform}, we see that the distribution of $wpd_{norm2}$ is more similar across nx and nfacets than $wpd_{norm1}$.
+In Figure \ref{fig:dist-new-approx}, we see that the distribution of $wpd_{norm2} = wpd_{raw} - b*log(nx*nfacet)$ is similar when normalised with true or approximate estimate of b.
+Morever, the distributions are pretty similar across different nx and nfacet.
 
-In Figure \ref{fig:dist-new-approx}, we see that the distribution of $wpd_{norm2}$ is similar when normalised with true or approximate estimates of a and b.
-
-```{r dist-new-approx, echo = TRUE, fig.cap = " The distribution of $wpd_{norm2}$ is plotted for approximate estimate of a and b.
-The distributions are similar when plotted against true estimate of and b."}
+```{r dist-new-approx, echo = FALSE, fig.cap = " The distribution of $wpd_{norm2}$ is plotted for approximate estimate of b.
+The distributions are similar when plotted against true and approxiomate estimate and b."}
 
@@
 
-G21_compare <- G21 %>% 
-  mutate(with_true_est = (value - slope*log(nx*nfacet)),
+G21_permutation <- read_rds("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_Gamma21.rds") %>% 
+  rename("wpd_permutation" = "value")
 
-                          with_approx_est = (value - 0.0027*log(nx*nfacet))) %>% 
+G21_all_data <- G21 %>% 
+  mutate(wpd_exact_est = (value - slope*log(nx*nfacet)),
+
+                          wpd_approx_est = (value - 0.0027*log(nx*nfacet))) %>% 
   pivot_longer(cols = 5:6,
@@
 
-G21_compare %>% 
+G21_all_data %>% 
   ggplot() +
-  geom_density(aes(x = value_estimate, fill = type_estimate), alpha = 0.5) +
+  geom_density(aes(x = value_estimate, 
+                   fill = type_estimate), 
+               alpha = 0.5) +
   facet_grid(nx~nfacet,
              labeller = "label_both") +
-  scale_x_continuous(breaks = scales::breaks_extended(3)) +
   theme(legend.position = "bottom") +
-  scale_fill_manual(values = c("#0072B2", "#D55E00")) +
+  scale_fill_manual(values = c("#0072B2", "#D55E00", "#CC79A7")) +
   xlab("wpd_norm2")
@@
 
-## Comparing the two approaches from real data
+```{r wpd-permutation, fig.cap = " The distribution of $wpd_{permutation}$ is plotted.
+The distributions are more similar across different nx and nfacet (specially for small nx and nfacet) but this approach has the downside of more computational time."}
+
+G21_permutation %>% 
+    ggplot() +
+  geom_density(aes(x = wpd_permutation), 
+                   fill = "blue") +
+  facet_grid(nx~nfacet,
+             labeller = "label_both") +
+  theme(legend.position = "bottom") 
+```
+
+<!-- # left_join(G21_permutation, -->
+<!-- #                                   by = c("nx", "nfacet", "perm_id")) %>%  -->
+<!-- #   rename("wpd_raw" = "value.x", -->
+<!-- #          "wpd_permutation" = "value.y") -->
+<!-- ``` -->
+
+## Ranking different designs
+
+```{r}
+data <- read_rds("simulations/supplementary/data-agg/wpd_N01/all_data.rds")
+
+# data_validate <-  data %>% 
+#   filter(
+#     nperm == 10, ntimes == 100, w == 1
+#   ) %>% 
+#   pivot_wider(id_cols = -2,
+#               names_from = design,
+#               values_from = value) %>% 
+#   mutate(right_order = ((null<=vary_f<=vary_x)))
+
+data_filter <- data %>% 
+    filter(
+        nperm == 10, ntimes == 100, w == 1
+    )
+
+data_filter %>% 
+    pivot_wider(id_cols = -2,
+                names_from = design,
+                values_from = value) %>% 
+    mutate(right_order = (null <= min(null, vary_f, vary_x)))
+
+  #            
+  #            ((null<=vary_f) & (vary_f<=vary_x))) %>% 
+  # mutate(right_order_proxy = if_else(right_order==TRUE, 1, 0)) %>% 
+  # group_by(nx, nfacet) %>% 
+  # summarise(n_order =  sum(right_order_proxy)/200) %>% View()
+
+data_filter %>% 
+  mutate(value = value - 0.0027*log(nx*nfacet)) %>% 
+    pivot_wider(id_cols = -2,
+                names_from = design,
+                values_from = value) %>% 
+    mutate(right_order = ((null<=vary_f) & (vary_f<=vary_x))) %>% 
+  mutate(right_order_proxy = if_else(right_order==TRUE, 1, 0)) %>% 
+  group_by(nx, nfacet) %>% 
+  summarise(n_order =  sum(right_order_proxy)/200) %>% View
+
+```
+
+# Real Data
+
+- Check if the ranking of the harmonies from the two approaches (wpd_norm_perm and  wpd_norm_scalar) are similar or not?
+
+- Check if the threshold is visually too different
+
+```{r}
+all_data_perm <- read_rds("paper/sim_table/all_data.rds")
+
+all_data_scalar <- 
+```

### 2021-02-10 paper/main.Rmd
application write up and renv update

@@
 Therefore, in order to compare wpd across different combinations of facet and x-axis levels, we need to eliminate the impact of different levels of the facets and x-axis first and get a normalized measure.
-Henceforth we call the measure discussed as $wpd_{raw}$ and the normalised measure as $wpd_{norm}$.
-The measure $wpd_{norm}$ could potentially lead to comparison of the measure across different panels and also identifying only the interesting panels from a dataset.
+Henceforth we call the measure already discussed as $wpd_{raw}$ and the normalised measure as $wpd_{norm}$.
+The measure $wpd_{norm}$ could potentially lead to comparison of the measure across different panels and also identifying only the interesting panels from a data set.
+In the coming section, we have discussed two approaches to normalisation both through simulations.
 
@@
 
-# Applications {#sec:application}
-
-## Smart meter data of Australia {#sec:smartmeter}
+# Application {#sec:application}
+
+<!-- ## Smart meter data of Australia {#sec:smartmeter} -->
 
@@
 
-Smart meters provide large quantities of measurements on energy usage for households across Australia.
-One of the customer trials [@smart-meter] conducted as part of the Smart Grid Smart City project in Newcastle, New South Wales and some parts of Sydney provides customer wise data on energy consumption for every half hour from February 2012 to March 2014.
-<!--It would be interesting to explore the energy consumption distribution for these customers and gain insights on their energy behavior which are lost either due to aggregation or looking only at coarser temporal units.-->The idea here is to show how to visualize the distribution of the energy consumption across different cyclic granularities in a systematic way to identify different behavioral patterns.
-
-### 50 households together
+Clustering of electricity customers based on their consumption behavior facilitate effective market segmentation and hence better management and pricing.
+Electricity demand time series are the primary source of information of customers' consumption behavior.
+Due to technological developments, smart meters could provide large quantities of measurements on energy usage at more and more finer time intervals.
+Due to this extreme dimensionality along time of the demand data, it is a challenge to have clustering methods which could reduce the dimensionality to produce distinct clusters.
+One of the potential solutions is time series feature extraction.
+However, it is limited by the type of noisy, patchy and unequal time series that is very common in data sets of any residential customers.
+The idea is to choose similarity measures, which do not lose the core characteristic information of demand across different time deconstructions in aggregation processes and is robust against asynchronous or incomplete time series.
+
+We use the data from one of the customer trials [@smart-meter] conducted as part of the Smart Grid Smart City project in Newcastle, New South Wales and some parts of Sydney.
+The data has customer wise data on energy consumption for every half hour from February 2012 to March 2014.
+<!--It would be interesting to explore the energy consumption distribution for these customers and gain insights on their energy behavior which are lost either due to aggregation or looking only at coarser temporal units.--> The idea here is to
+use our similarity measure and show improved cluster distinction as compared to baseline feature based approaches.
+A data set of 100 homes is used to evaluate both approaches.
+This is different to deterministic segmentation which attempts to characterise load as a function of a fixed number of parameters, such as occupancy or types of appliances, and use those parameters for classification.
+We only use their load patterns across time deconstructions to define the similarity measure.
+
+<!-- Write about common load clustering methods -->
+
+### Multidimensional scaling and cluster analysis
 
 Cluster analysis and multidimensional scaling (MDS) methods are used to explore the temporal structure of various households, their interrelations and determine similar behaving clusters of households in this study.
-
-$wpd_norm$ is considered as the measure of similarity or dissimilarity while using MDS and clustering techniques.
-$wpd_norm$ could be constructed for each pair of harmony for each household and then similarity could be measured across individual or all harmonies together.
 MDS methods are used to produce a lower dimensional display space where each household is represented by a point and the distance between these points give the measure of similarity between these households.
@@
 
-### Multidimensional scaling
+$wpd_norm$ is considered as the measure of similarity or dissimilarity while using MDS and clustering techniques.
+$wpd_norm$ could be constructed for each pair of harmony for each household and then similarity could be measured across single or all harmonies together.
+
+```{r mds}
+set.seed(7777)
+library(gravitas)
+library(tsibble)
+library(lubridate)
+library(readr)
+
+all_data <- read_rds("sim_table/all_data.rds")
+sm_cust_data <- read_rds("data/sm_cust_data.rds") %>% 
+  as_tsibble(index = reading_datetime,
+             key = customer_id)
+
+sm_unique_cust <- sm_cust_data %>% distinct(customer_id)
+
+#sm_30 <- sample(sm_unique_cust$customer_id, 30)
+sm_cust_samp <- sm_cust_data %>% 
+  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
+  filter(year(reading_datetime) == 2012)  %>% 
+  create_gran("day_week") %>% 
+  create_gran("hour_day")
+
+#all_data <- write_rds(all_data, "paper/sim_table/all_data.rds")
+
+facet_variable = "day_week"
+x_variable = "hour_day"
+
+one_harmony_data <- all_data %>%
+  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
+  filter(facet_variable == "day_week",
+                    x_variable == "hour_day") %>% 
+  mutate(customer_id = as.character(customer_id))
+
+mds<- one_harmony_data %>%
+  select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
+  dist() %>%          
+  cmdscale() %>%
+  as_tibble()
+
+colnames(mds) <- c("Dim.1", "Dim.2")
+rownames(mds) <- unique(one_harmony_data$customer_id)
+mds <- mds %>%
+  mutate(customer_id = as.character(unique(one_harmony_data$customer_id))) %>%
+  select((customer_id)
+         , Dim.1, Dim.2)
+
+# ggpubr::ggscatter(mds,
+#                   x = "Dim.1",
+#                   y = "Dim.2", 
+#                   label = rownames(mds),
+#                   size = 1,
+#                   repel = TRUE) 
+```
+
+```{r clustering}
+# K-means clustering
+clust <- kmeans(mds, 3)$cluster %>%
+  as.factor()
+mds <- mds %>%
+  mutate(groups = clust)
+
+# Plot and color by groups
+ggpubr::ggscatter(mds, x = "Dim.1", y = "Dim.2", 
+          label = rownames(mds),
+          color = "groups",
+          palette = "jco",
+          size = 1, 
+          ellipse = TRUE,
+          ellipse.type = "convex",
+          repel = TRUE)
+
+#   d = one_harmony_data %>%
+#     select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
+#     dist()
+#   
+#   hc = stats::hclust(d,method="complete")
+#   plot(hc)
+#   groups<-cutree(hc, k=4)
+#   
+#   all_data_cluster <- cbind(one_harmony_data, groups) %>% 
+#     left_join(mds, by = "customer_id") %>% 
+#     mutate(groups = as.factor(groups))
+# 
+# 
+# 
+# ggpubr::ggscatter(all_data_cluster,
+#                   x = "Dim.1",
+#                   y = "Dim.2", 
+#                   label = rownames(mds),
+#                   color = "groups",
+#                   size = 1,
+#                   repel = TRUE)
+
+```
+
+10018272 is a customer from cluster 3, for which hour_day/wknd-wday comes after wknd-wday/day-month as opposed to 10006414 (cluster 1) for whom the direction is reversed.
+
+```{r}
+
+10006414
+
+all_data %>% 
+  filter(customer_id ==  10006414) %>% 
+  arrange(-wpd_norm)
+
+sm_cust_data %>% 
+  filter(customer_id ==  10006414) %>% 
+  prob_plot("hour_day",
+            "wknd_wday",
+            plot_type = "quantile",
+            quantile_prob = c(0.5),
+            symmetric = FALSE,
+            response = "general_supply_kwh")
+
+sm_cust_data %>% 
+  filter(customer_id ==  10006414) %>% 
+  prob_plot("hour_day",
+            "day_week",
+            plot_type = "quantile",
+            quantile_prob = c(0.5),
+            symmetric = FALSE,
+            response = "general_supply_kwh")
+
+all_data %>% 
+  filter(customer_id ==  10007340) %>% 
+  arrange(-wpd_norm)
+
+sm_cust_data %>% 
+  filter(customer_id ==  10007340) %>% 
+  prob_plot("day_month",
+            "day_week",
+            plot_type = "quantile",
+            quantile_prob = c(0.5),
+            symmetric = FALSE,
+            response = "general_supply_kwh")
+
+sm_cust_data %>% 
+  filter(customer_id ==  10007340) %>% 
+  prob_plot("hour_day",
+            "day_month",
+            plot_type = "quantile",
+            quantile_prob = c(0.5),
+            symmetric = FALSE,
+            response = "general_supply_kwh")
+
+all_data %>% 
+  filter(customer_id ==  10018272) %>% 
+  arrange(-wpd_norm)
+
+```
+
+```{r}
+raw_data <- sm_cust_data %>% 
+  left_join(mds, by = "customer_id")
+
+p1 <- raw_data %>% 
+  filter(groups==1) %>% 
+  ggplot() + 
+  geom_line(aes(x = reading_datetime,
+            y = general_supply_kwh)
+  )
+
+p2 <- raw_data %>% 
+  filter(groups==2) %>% 
+  ggplot() + 
+  geom_line(aes(x = reading_datetime,
+            y = general_supply_kwh)
+  )
+
+p3 <- raw_data %>% 
+  filter(groups==3) %>% 
+  ggplot() + 
+  geom_line(aes(x = reading_datetime,
+            y = general_supply_kwh)
+  )
+library(patchwork)
+p1/p2/p3
+
+```
+
+```{r}
+raw_data <- sm_cust_data %>% 
+  left_join(mds, by = "customer_id")
+
+p1 <- raw_data %>% 
+  filter(groups==1) %>% 
+  prob_plot("day_week",
+            "hour_day",
+            response = "general_supply_kwh",
+            plot_type = "quantile",
+            symmetric = FALSE
+)
+
+p2 <- raw_data %>% 
+  filter(groups==2) %>% 
+  prob_plot("day_week",
+            "hour_day",
+            response = "general_supply_kwh",
+            plot_type = "quantile",
+            symmetric = FALSE
+)
+
+p3 <- raw_data %>% 
+  filter(groups==3) %>% 
+  prob_plot("day_week",
+            "hour_day",
+            response = "general_supply_kwh",
+            plot_type = "quantile",
+            symmetric = FALSE
+)
+library(patchwork)
+p1/p2/p3
+
+```
+
+```{r hour-day-day-month, eval = FALSE}
+
+set.seed(7777)
+library(gravitas)
+library(tsibble)
+library(lubridate)
+library(readr)
+
+all_data <- read_rds("sim_table/all_data.rds")
+sm_cust_data <- read_rds("data/sm_cust_data.rds")
+sm_unique_cust <- sm_cust_data %>% distinct(customer_id)
+
+#sm_30 <- sample(sm_unique_cust$customer_id, 30)
+sm_cust_samp <- sm_cust_data %>% 
+  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
+  filter(year(reading_datetime) == 2012) %>% #for demo just show one column
+  as_tsibble(index = reading_datetime,
+             key = customer_id) %>% 
+  create_gran("wknd_wday") %>% 
+  create_gran("week_month")
+
+#all_data <- write_rds(all_data, "paper/sim_table/all_data.rds")
+
+facet_variable = "wknd_wday"
+x_variable = "week_month"
+
+one_harmony_data <- all_data %>%
+  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
+  filter(facet_variable == "wknd_wday",
+                    x_variable == "week_month") %>% 
+  mutate(customer_id = as.character(customer_id))
+
+mds<- one_harmony_data %>%
+  select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
+  dist() %>%          
+  cmdscale() %>%
+  as_tibble()
+
+colnames(mds) <- c("Dim.1", "Dim.2")
+rownames(mds) <- unique(one_harmony_data$customer_id)
+mds <- mds %>%
+  mutate(customer_id = as.character(unique(one_harmony_data$customer_id))) %>%
+  select((customer_id)
+         , Dim.1, Dim.2)
+
+clust <- kmeans(mds, 3)$cluster %>%
+  as.factor()
+mds <- mds %>%
+  mutate(groups = clust)
+
+# Plot and color by groups
+ggpubr::ggscatter(mds, x = "Dim.1", y = "Dim.2", 
+          label = rownames(mds),
+          color = "groups",
+          palette = "jco",
+          size = 1, 
+          ellipse = TRUE,
+          ellipse.type = "convex",
+          repel = TRUE)
+
+```
+
+### Advantage over taditional feature based methods
+
+Since probability distribution of the load is considered across different cyclic granularity, there is no discarding of valuable data that might result from bringing all customers to the same time horizon.
+Moreover, since our metric is based on probability distribution, it will not be sensitive to outlier days and hence the clustering process will not be biased.
+Moreover, feature extraction applies to all days for all customers at once and therefore does not support parallel computing.
+Our metric is computed for each household separately and can even run for each each harmonies separately and thus fits well into the parallel computing framework.
+
+### Write the method in notations
+
+-  notation of time series for each customer
+-  wpd
+-  harmonies
+-  cluster
+
+### Distinction, repeatability, and robustness metrics
 

### 2021-02-10 loop_local_scalar_all_households.R

@@ -1,0 +1,66 @@
+#This script calculates raw wpd for each simulation scenario
+##Read Simulation Table
+
+.libPaths(c("~/R/libs", .libPaths()))
+library(distributional)
+library(readr)
+library(drake)
+library(tidyverse)
+library(hakear)
+library(gravitas)
+library(parallel)
+
+
+set.seed(9999)
+
+# change path while running it on HPC
+simtable<-read_csv('paper/sim_table/sim_table.csv')
+harmonies<-read_csv('paper/sim_table/harmonies.csv')
+sm_cust_data <- read_rds("paper/data/sm_cust_data.rds")
+
+### Extract flags from simulation scenario
+
+# scen<- 170 #If running within R uncomment this.  This will only run first scenario
+#scen<-as.numeric(commandArgs()[[6]]) # If running batch job uncomment this
+
+mclapply(seq_len(nrow(simtable)),
+         function(scen){
+           
+           simj<-simtable[scen,] #Extract row of table
+           customer_idj <- simj$customer_id
+           facetj <- simj$facet_variable
+           xj <- simj$x_variable
+           harmony_tbl_rowj <- simj[-c(1:2)]
+           dataj <- sm_cust_data %>% filter(customer_id %in% customer_idj)
+           
+           # all_data <- create_harmony_tbl_data(dataj,
+           #                     harmonies,
+           #                     general_supply_kwh)  
+           #   
+           
+           all_data <- create_harmony_data(dataj,
+                                           harmony_tbl_rowj,
+                                           general_supply_kwh)  
+           
+           
+           # wpd_norm <- mclapply(all_data, function(x){
+           
+           
+           wpd_norm <- compute_pairwise_norm_scalar(all_data, 
+                                             gran_x = "id_x",
+                                             gran_facet = "id_facet",
+                                             response = sim_data,
+                                             quantile_prob =
+                                               seq(0.01, 0.99, 0.01))
+           
+           wpd_harmonies <- bind_cols(customer_id = customer_idj, 
+                                      harmony_tbl_rowj,
+                                      wpd_norm = wpd_norm %>% unlist() %>% round(digits = 3))
+           
+           
+           saveRDS(wpd_harmonies,
+                   paste0('paper/sim_table/results_norm_scalar/',
+                          customer_idj,"-",
+                          facetj, "-", 
+                          xj, '.rds')) # seed and dist not included yet
+         })

### 2021-02-10 paper/sim_table/aggregate01.R

@@ -1,12 +1,12 @@
 # contains function to aggregate data each for from N(0,1), N(0,5), N(5,1), N(5,5), Gamma(0.5, 1), Gamma(2, 1)
-#  aggregated data from the file simulations/results/norm/folder_name and tidy them up
+#  aggregated data from the file simulations/results_norm_scalar/norm/folder_name and tidy them up
 library(tidyverse)
 library(here)
 library(readr)
 library(rlang)
 
   
-  all_files = list.files(path = paste0("paper/sim_table/results/"), 
+  all_files = list.files(path = paste0("paper/sim_table/results_norm_scalar/"), 
                          pattern = ".rds")
   
   names_levels <- map_dfr(all_files, 
@@ -20,12 +20,12 @@ library(rlang)
                                       x_variable = z[3])
                           })
   
-  # len_file = read_rds(("simulations/results/norm/tuning_param/2_2_tuning_param.rds"))
+  # len_file = read_rds(("simulations/results_norm_scalar/norm/tuning_param/2_2_tuning_param.rds"))
   # 
   # names_rep <- names_levels %>% slice(rep(1:n(), each = nrow(len_file)))
   
   
-  all_files_path <- paste0("paper/sim_table/results/",
+  all_files_path <- paste0("paper/sim_table/results_norm_scalar/",
                            all_files)  
   
   
@@ -41,4 +41,4 @@ library(rlang)
     bind_rows() %>%
     arrange(customer_id)
   
-  write_rds(all_data, "paper/sim_table/all_data.rds")
+  write_rds(all_data, "paper/sim_table/all_data_scalar.rds")

### 2021-02-10 paper/sim_table/makegraph02.R

@@ -15,7 +15,7 @@ set.seed(7777)
 sm_unique_cust <- sm_cust_data %>% distinct(customer_id)
 sm_30 <- sample(sm_unique_cust$customer_id, 30)
 sm_cust_samp <- sm_cust_data %>% 
-  filter(customer_id %in% sm_30) %>% # for demo show 30 customers
+  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
   filter(year(reading_datetime) == 2012) %>% #for demo just show one column
   as_tsibble(index = reading_datetime,
              key = customer_id) %>% 
@@ -28,7 +28,7 @@ facet_variable = "day_week"
 x_variable = "hour_day"
 
 one_harmony_data <- all_data %>%
-  filter(customer_id %in% sm_30) %>% # for demo show 30 customers
+  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
   filter(facet_variable == "day_week",
                     x_variable == "hour_day") %>% 
   mutate(customer_id = as.character(customer_id))
@@ -252,6 +252,5 @@ base %>%
   filter_select("id",
                 "select a customer_id", 
                 sm,
-                ~customer_id),
-                ) %>%
+                customer_id) %>%
   add_lines(x = ~reading_datetime, y = ~general_supply_kwh)

### 2021-02-10 simulations/supplementary/R-agg/aggregate01.R

@@ -11,7 +11,7 @@ library(rlang)
 
   names_levels <- map_dfr(all_files, 
                           function(x){
-                            z = str_split(str_remove(x, "_dist.rds"), "-") %>% 
+                            z = str_split(str_remove(x, "-wpd.rds"), "-") %>% 
                               unlist()
                             bind_cols(type = z[1],
                                       design = z[2],

### 2021-02-10 paper/main.Rmd
methodology updated

@@
 
-## Normalisation
+# Normalisation
 
@@
 
-### Environment
+## Simulation environment
 
@@
 
-### Results
+## Methodology
+
+### Notations
+
+Let $\{nx_{i}, i = 1, 2, \dots, nx\}$, $\{nfacet_{j}, j = 1, 2, \dots, nfacet\}$ be the set of x-axis and facet categories respectively.
+Each combination of $nx_{i}$ and $nfacet_{j}$is being referred to as a _panel_.
+Then the total number of panel is $nx*nfacet$.
+Let the total number of pairwise distances that could result in each panel be $\{z_k, k = 1, 2 , \dots, nx*nfacet\}$.
+Here, $\{z_1 = nx_1*nfacet_1\}$, $\{z_2 = nx_2*nfacet_2\}$ and $\{z_k = nx*nfacet\}$.
+Now, let $\{x_{k,l}, k = 1, 2, \dots, nx*nfacet, l = 1, 2, \dots, nsim\}$ denote the values of $wpd_{raw}$ obtained from the simulation study for $k^{th}$ panel in the $i^{th}$ simulation.
+Hence, for each of those $k$ panel, we have $nsim$ values of $wpd_{raw}$.
+
+### Data generation
+
+Observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
+That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$.
+For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
+That is, if we consider the panel  $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
+The value of $\lambda$ is set to $0.67$.
+$nsim = 200$, which means each of these scenarios are run $200$ times by permuting the data in each of the panels.
+And hence $200$ values of $wpd_{raw}$ are obtained for each of those 64 panels.
+
+### Permutation approach
+
+The permutation approach ensures that the distribution of the normalised weighted pairwise distance measure has the same mean and standard deviation across all combinations of $nx_i$ and $nfacet_j$.
+Thus, the normalised distances is computed as follows: $x^{norm}_{k} =  (x_{k} - mean_l(x_{k,l}))/sd_l(x_{k, l})$,  $x^{norm}_{k}$ is the value of the $wpd_{norm}$ for the $k^{th}$ panel.
+
+While this works successfully to make the mean and standard deviation across different nx and nfacet (as seen in Figure \ref{fig:}), it is computationally heavy and time consuming, and hence less user friendly when being actually used in practice.
+Hence, we propose another approach to normalisation which is more approximate than exact but still has the same accuracy when compared to the permutation approach.
+
+### Modelling approach
+
+A log-linear model is fitted to see how the values of $wpd_{raw}$ changes with the values of $nx$ and $nfacet$.
+The model is of the form $$y_k = a+b*log(z_k) + e_k$$, where, $y_k = median_l(x_{k, l})$ and $e_k$ are idiosyncratic errors.
+We have gone with the approach of fitting a linear regression model to estimate the parameters $a$ and $b$.
+The estimates and other model summary is given in \ref{tab:linear-model}.
+
+```{r linear-model}
+G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds"))
+
+G21_median <- G21 %>% 
+  group_by(nx*nfacet) %>% 
+  summarise(actual = median(value))
+
+# fit model median to log(nx*nfacet)
+fit_lm2 <- lm(actual ~ poly(log(`nx * nfacet`) ,1, raw=TRUE), data = G21_median)
+
+summary(fit_lm2)
+```
+
+The final idea is to find a transformation on $wpd_{raw}$ which would remove the effect of $nx*nfacet$ on $wpd_{raw}$ and thus is defined as follows:
+$y^* =  y - \hat b*log(z)$, where 
+$y^*$ is the $median(wpd_{norm})$, 
+$y$ is the $median(wpd_{raw})$,
+$\hat b$ is the estimated value of the parameter $b$, 
+and $z = nx*nfacet$.
+
+The above takes care of the mean and the heterogeneity of the median transformed measure.
+But, the original distribution will still have some dissimilarities in shape and location specially for small values of $nx$ and $nfacet$ as could be seen in \ref{fig:}
+
+```{r}
+
+intercept <- fit_lm2$coefficients[1]
+slope <- fit_lm2$coefficients[2]
+
+G21 %>% 
+  ggplot(aes(x=log(nx*nfacet), y = (value - slope*log(nx*nfacet)))) +
+  geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
+  ylab("wpd_norm =  wpd_raw - slope*log(nx*nfacet)")
+
+```
+
+<!-- Let ${x_p, p = 1, 2, \dots, npanel}$ denote the total number of distances $nx*nfacet$ obtained in each panel. So for each $nx*nfacet$, we have $nsim = 200$ values of ${y_i}$. -->
+
+<!-- from $nx_{i}$ x-categories and $nfacet_{j}$ facet-categories is $nx_{i}*nfacet_{j}$ and  -->
+
+## Results
 
@@
 
-all_data <- read_rds("sim_table/all_data.rds")
-sm_cust_data <- read_rds("data/sm_cust_data.rds") %>% 
+all_data <- read_rds(here("paper/sim_table/all_data.rds"))
+sm_cust_data <- read_rds(here("paper/data/sm_cust_data.rds")) %>% 
   as_tsibble(index = reading_datetime,
@@
 
-## T20 cricket data of Indian Premiere League {#sec:cricket}
-
-The method is not only restricted to temporal data, and can be generalized to many hierarchical granularities (with  continuous and uni-directional nature).
-We illustrate this with an application to the sport cricket.
-Although there is no conventional time component in cricket, each ball can be thought to represent an ordering from past to future with the game progressing forward with each ball.
-In the Twenty20 format, an over will consist of 6 balls (with some exceptions), an inning is restricted to a maximum of 20 overs, a match will consist of 2 innings and a season consists of several matches.
-Thus, similar to time, there is a hierarchy where ball is nested within overs, overs nested within innings and innings within matches.
-The idea of cyclic granularities can be likewise mapped to this hierarchy.
-Example granularites then include ball of the over, over of the inning and ball of the inning.
-Although most of these cyclic granularities are circular in design of the hierarchy, in application of the rules some granularities are aperiodic.
-For example, in most cases an over will consist of 6 balls with some exceptions like wide balls or when an inning finishes before the over finishes.
-Thus, the cyclic granularity ball-of-over will be circular in most cases and aperiodic in others.
-
-<!-- However, irrespective of the type of cyclic granularities, it can be interesting to visualize the distribution of a measured variable across these cyclic granularities to throw light on the periodic behavior of a non-temporal data set similar to any temporal data set.
--->
-
-The Indian Premier League (IPL) is a professional Twenty20 cricket league in India contested by eight teams representing eight different cities in India.
-The ball by ball data for IPL season 2008 to 2016 is fetched from [Kaggle](https://www.kaggle.com/josephgpinto/ipl-data-analysis/data).
-The `cricket` data set in the `gravitas` package summarizes the ball-by-ball data across overs and contains information for a sample of 214 matches spanning 9 seasons (2008 to 2016) such that each over has 6 balls, each inning has 20 overs and each match has 2 innings.
-This could be useful in a periodic world when we wish to compute any circular/quasi-circular granularity based on a hierarchy table which look like \autoref{tab:hierarchy-cric}.
-
-```{r hierarchy-cric}
-library(gravitas)
-library(tibble)
-hierarchy_model <- tibble::tibble(
-  `linear (G)` = c("over", "inning", "match", "season"),
-  `single-order-up cyclic (C)` = c("over-of-inning", "inning-of-match", "match-of-season", 1),
-  `period length/conversion operator (K)` = c(20, 2, "k(match, season)", 1)
-)
-knitr::kable(hierarchy_model,
-             format = "latex",
-             booktabs = TRUE,
-             caption = "Hierarchy table for cricket where overs are nested within an inning, innings nested within a match and matches within a season.") %>%
-  #row_spec(0, bold = TRUE)%>%
-  kable_styling()
-```
-
-However, even if the situation is not periodic and a similar hierarchy can not be formed, it can be interesting to visualize the distribution of a measured variable across relevant cyclic granularities to shed light on the aperiodic behavior of a non-temporal data set similar to aperiodic events like formal meetings, workshops, conferences, school semesters in a temporal set up.
-There are many interesting questions that could possibly be answered with such a data set irrespective of the type of cyclic granularities.
-<!--We will explore a few interesting questions and understand how the proposed approach in the paper can help answer some of the questions.-->
-
-<!-- the two teams have a single innings each, which is restricted to a maximum of 20 overs.
-Hence, in this format of cricket, a match will consist of 2 innings, an innings will consist of 20 overs, an over will consist of 6 balls with some exceptions.
--->
-
-<!-- ```{r hierarchy, echo=FALSE} -->
-<!-- hierarchy_model <- tibble::tibble(linear gran = c("ball", "over", "inning", "match"),  -->
-<!--                                   convert_fct = c(6, 20, 2, 1)) -->
-<!-- knitr::kable(hierarchy_model, caption = " A hierarchy table for T20 cricket") -->
-<!-- ``` -->
-
-<!-- Each team is given a two-and-a-half-minute "strategic timeout" during each innings; one must be taken by the bowling team between the ends of the 6th and 9th overs, and one by the batting team between the ends of the 13th and 16th overs.
--->
-
-<!-- Suppose, we are interested to see how the distribution of scores vary from the start to the end of the game. Let us brainstorm some of the questions that might help us comprehend that. -->
-
-<!-- a) What is the most common pattern for batting and bowling teams across balls, overs, innings and matches? Which are the teams which are typical and which are exceptions? -->
-
-<!-- How the scores per over vary across granularities/categorizations like innings of a match or matches of a season?
-Are these different for the winning teams in that season and the teams that couldn't qualify for the playoffs?
--->
-
-<!-- Is the outcome of the game dependent on who bats first? Do some teams have more chance to win if they are batting in the first innings? -->
-
-<!-- We will look at the ball by ball data for all batting teams.
-Since we want a periodic world, where each over consists of 6 balls and each match consists of two innings, we shall filter out the matches or overs for which that is not true.
-Also, we look at runs per over as that would have more variability compared to runs per ball and it be easier to observe the strategies of the winning team through that.
--->
-
-<!-- Making it short -->
-
-<!-- First, we look at the distribution of runs (measured variable) across over-of-inning (circular granularity) and match-of-season (aperiodic cyclic granularity) in \autoref{fig:seas-over-inning}.
-The distribution of runs per over has not significantly changed from 2008 to 2016.
-There is no clear pattern/trend that runs per over is increasing or decreasing across seasons.
-Hence, we work with subsets of seasons to answer some of the questions: -->
-
-First, it would be interesting to see if the distribution of total runs vary depending on if a team bats in the first or second innings.
-The Mumbai Indians (MI) and Chennai Super kings (CSK) <!--are considered one of the best teams in IPL with multiple winning titles and --> appeared in final playoffs from 2010 to 2015.
-We take their example in order to dive deeper into this question.
-<!--Circular granularities "over-of-inning" and "inning-of-match" can be computed using \ref{sec:circular-gran-def} with over as index of the tsibble.--> From Figure \ref{fig:cricex}(a), it can be observed that for the team batting in the first inning there is an upward trend of runs per over, while there is no clear upward trend in median and quartile deviation of runs for the teams batting in the second inning.
-This seem to indicate that players feel mounting pressure to score more runs as they approach towards the end of the first inning.
-Whereas teams batting in the second inning have a set target in mind and are not subjected to such mounting pressure and may adopt a more conservative strategy, to score runs.
-Thus winning teams like CSK and MI seem to employ different inning strategies when it comes to their batting order.
-
-<!-- Also longer and more distinct letter values in the second innings suggests that the variability is more in the second innings. -->
-<!-- - Q1: How their run rates vary depending on if they bat first or 2nd? Is there a chance that they are more likely to win if they bat first? -->
-
-<!-- - Q2: Which team is more consistent in their approach in terms of run rate across different overs of the innings? -->
-
-<!-- # ```{r seas-over-inning, fig.cap = "Quantile plot of runs per over across overs of different seasons. There is no pattern on increase or decrease of runs across overs for seasons."} -->
-<!-- #   cricket_tsibble_all %>%  -->
-<!-- #   prob_plot("over",  -->
-<!-- #             "season", -->
-<!-- #             hierarchy_model, -->
-<!-- #             response = "runs_per_over", -->
-<!-- #             plot_type = "quantile", -->
-<!-- #             quantile_prob = c(0.25, 0.5, 0.75),  -->
-<!-- #             symmetric = FALSE)  + -->
-<!-- #      theme( # remove the vertical grid lines -->
-<!-- #             panel.grid.major.x = element_blank() , -->
-<!-- #             # explicitly set the horizontal lines (or they will disappear too) -->
-<!-- #             panel.grid.major.y = element_blank()) + scale_x_discrete(breaks = seq(2008, 2016, 3)) -->
-<!-- # ``` -->
-
-Another interesting question could be: do runs per over decrease in the subsequent over if fielding (defending) was good in the previous over?
-For establishing the fielding quality, we apply an indicator function on dismissals (1 if there was at least one wicket in the previous over due to run out or catch, 0 otherwise).
-Runs in the current over is then the observation variable.
-<!--If a batsman is bowled out, it does not necessarily signify good fielding.
-So we only include number of catches and run out in an over as a measure of good fielding.
-Difference in runs across overs are likely to be negative if good fielding has an impact on the runs scored in the subsequent overs.
---> Dismissals in the previous over can lead to a batsman adopting a more defensive play style.
-Figure \ref{fig:cricex}(b) shows that no dismissals in the previous over leads to a higher median and quartile spread of runs per over as compared to the case when there has been at least one dismissal in the previous over.
-
-<!-- Difference in runs across over should be negative if good fielding has an impact on the runs scored in the subsequent overs.  -->
-
-<!-- fetching raw data since dot and fielding information not available in dismissal type not available in cricket data gravitas. Also `cricket` is aggregated across overs -->
-
-```{r cricex, fig.cap= "Runs per over shown with different distribution displays, and granularities.
-Plot (a) shows letter value plot across overs faceted by innings.
-For the team batting in the first innings there is an upward trend of runs per over, while there is no such pattern of runs for the teams batting in the second innings.
-Plot (b) shows quantile plot of runs per over across an indicator of wickets in previous over faceted by current over.
-This indicates that at least one wicket in the previous over leads to lower median run rate and quartile spread in the subsequent over.", warning = FALSE, message = FALSE, out.width = "90%"}
-
-library(tsibble)
-cricket_tsibble <- cricket %>%
-  mutate(data_index = row_number()) %>%
-  as_tsibble(index = data_index)
-
-hierarchy_model <- tibble::tibble(
-  units = c("index", "over", "inning", "match"),
-  convert_fct = c(1, 20, 2, 1)
-)
-
-cricket_tsibble %>%
-  filter(batting_team %in% c(
-    "Mumbai Indians",
-    "Chennai Super Kings"
-  )) %>%
-  mutate(inning = paste0("innings: ", inning)) %>%
-  prob_plot("inning",
-    "over",
-    response = "runs_per_over",
-    hierarchy_model,
-    plot_type = "lv"
-  ) +
-  scale_fill_brewer(palette = "Dark2") +
-  #ggtitle("(a) Runs per over across over faceted by inning") +
-  theme(legend.position = "right") +
-  ggtitle("a") +
-  ylab("runs per over") +
-  xlab("overs of the innings") +
-  theme(plot.title = element_text(face = "bold")) +
-  ggplot2::theme(
-       strip.text = ggplot2::element_text(
-        size = 10,
-         margin = ggplot2::margin(b=0, t=0)
-      )
-     ) +  theme_minimal() 
-#geom_smooth(aes( x = over,
-#                               y=runs_per_over), method = lm, #formula = y ~ splines::bs(x, 3), se = FALSE)
-
-library(tsibble)
-
-cricket_all <- read_csv("paper/data-raw/deliveries_all.csv")
-matches_all <- read_csv("paper/data-raw/matches_all.csv")
-
-cricket_season <- cricket_all %>% left_join(matches_all, by = c("match_id" = "id"))
-
-# cricket_per_over <- cricket_season %>%
-#   group_by(season,
-#            match_id,
-#            batting_team,
-#            bowling_team,
-#            inning,
-#            over) %>%
-#   summarise(runs_per_over = sum(total_runs),
-#             run_rate = sum(total_runs)/length(total_runs))
-#
-# cricket_tsibble_all <- cricket_per_over %>%
-#   ungroup() %>%
-#   mutate(data_index = row_number()) %>%
-#   as_tsibble(index = data_index)
-
-cricket_dot_field <- cricket_season %>%
-  mutate(
-    fielding_proxy = if_else(dismissal_kind %in%
-      c("caught", "caught and bowled"), 1, 0),
-    dot_ball_proxy = if_else(total_runs == 0, 1, 0),
-    wicket_proxy = if_else(is.na(dismissal_kind), 0, 1)
-  ) %>%
-  group_by(
-    season,
-    match_id,
-    batting_team,
-    bowling_team,
-    inning,
-    over
-  ) %>%
-  summarise(
-    runs_per_over = sum(total_runs),
-    run_rate = sum(total_runs)*6 / length(total_runs),
-    fielding_wckts = sum(fielding_proxy),
-    dot_balls = sum(dot_ball_proxy)
-  ) %>%
-  mutate(diff_run_rate = c(0, diff(run_rate)))
-
-cricket_tsibble <- cricket_dot_field %>%
-  ungroup() %>%
-  mutate(data_index = row_number()) %>%
-  as_tsibble(index = data_index)
-
-cricket_data <- cricket_tsibble %>%
-  mutate(
-    field = if_else(fielding_wckts == 0, "0", "1+"),
-    dot = if_else(dot_balls == 0, "no dot balls", ">0 dot balls"),
-    lag_field = lag(field),
-    lag_dot = lag(dot)
-  ) %>%
-  filter(lag_field != 0, lag_dot != 0)
-
-cricket_data$lag_field <- factor(cricket_data$field, levels = c("0", "1+"))
-
-# filter(fielding_wckts %in% c(0,1)) %>%
-#
- cricket_data %>%
-  filter(over!=1) %>%
-  prob_plot("over", "lag_field",
-  hierarchy_model,
-  response = "run_rate",
-  plot_type = "quantile",
-  symmetric = FALSE,
- quantile_prob = c(0.25, 0.5, 0.75)) +
-   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") +
-  ylab("runs per over")  +
-  xlab("number of wickets in previous over") +
-  ggtitle("b") +
-   theme(plot.title = element_text(face = "bold")) +
-        theme(axis.ticks = element_blank(), legend.background = element_blank(),
-            legend.key = element_blank(), panel.background = element_blank(), strip.background = element_blank(),
-            plot.background = element_blank(), complete = TRUE, panel.grid.major = element_line(colour = "#E0E0E0"),
-            panel.border = element_rect(colour = "#E0E0E0", fill = NA))
-```
-
-<!-- Q2: Among good fielding and bowling - which affect the runs of the subsequent overs more? -->
-
-<!-- Q3: Are runs set to reduce in the next over for dot balls in the previous over? -->
-
-<!-- A dot ball is a delivery bowled without any runs scored off it.
-The number of dot balls is reflective of the quality of bowling in the game.
-Run rate of an over should ideally decrease if the number of dot balls increase.
-However, what is the effect of dot balls on runs scored in the subsequent over.
-Will players batsman likely to go for big shots because they couldn't score good runs in the previous over?
-Or they should play consistently and avoid scoring high?
-Figure \ref{fig:exdot} shows the quantile plot of runs across overs for at least one dot ball per over (facet 1) or no dot balls per over (facet 2).
--->
-<!-- With at least one dot balls per over, the distribution of run rates in facet 1 increase slower compared to that in facet 2.
-This implies that run rates are likely to decrease in the subsequent over as a result of dot balls in the previous over.
--->
-
-<!-- ```{r exdot, fig.cap="25th, 50th, 75th quantiles of runs per over are drawn across overs of the innings with no (facet 2), more than zero (facet 1) dot balls per over.
-For all quantiles, run rates mostly increase at a higher rate in facet 2 compared to facet 1 implying run rates decrease with at least one dot ball in the previous over.", fig.pos="ht"} -->
-
-<!-- cricket_data %>% -->
-<!--   # filter(dot_balls %in% c(0, 1, 2)) %>% -->
-<!--   prob_plot("lag_dot", -->
-<!--     "over", -->
-<!--     hierarchy_model, -->
-<!--     response = "run_rate", -->
-<!--     plot_type = "quantile", -->
-<!--     quantile_prob = c(0.25, 0.5, 0.75), -->
-<!--     symmetric = FALSE -->
-<!--   ) + ggtitle("") -->
-<!-- ``` -->
-
-Wickets per over are considered as an aperiodic cyclic granularity with wickets as an aperiodic linear granularity.
-These granularities do not appear in the hierarchy table since it is difficult to position them in a hierarchy.
-These are similar to holidays or special events in temporal data.
-<!-- CONTENT CUT -->
-<!--While any special event that corresponds to a time domain can be treated as an aperiodic linear granularity in a temporal xacase, dot balls or wickets that corresponds to certain balls (index) could be treated as aperiodic events in cricket.-->
-
 # Discussion points and future work

### 2021-02-10 paper/R/scalar_trans_wpd_all_households.R

@@ -20,7 +20,7 @@ sm_cust_data <- read_rds("paper/data/sm_cust_data.rds")
 
 ### Extract flags from simulation scenario
 
-# scen<- 170 #If running within R uncomment this.  This will only run first scenario
+# scen<- 200 #If running within R uncomment this.  This will only run first scenario
 #scen<-as.numeric(commandArgs()[[6]]) # If running batch job uncomment this
 
 simj<-simtable[scen,] #Extract row of table
@@ -48,17 +48,16 @@ wpd_norm <- compute_pairwise_norm_scalar(all_data,
                         gran_facet = "id_facet",
                         response = sim_data,
                         quantile_prob =
-                          seq(0.01, 0.99, 0.01), 
-                        nperm = 200)
+                          seq(0.01, 0.99, 0.01))
 
   
-wpd_harmonies <- bind_cols(customer_id = customer_idj, 
+swpd_harmonies <- bind_cols(customer_id = customer_idj, 
                            harmony_tbl_rowj,
           wpd_norm = wpd_norm %>% unlist() %>% round(digits = 3))
 
 
 saveRDS(wpd_harmonies,
-        paste0('paper/sim_table/results/',
+        paste0('paper/sim_table/results_norm_scalar/',
                customer_idj,"-",
                facetj, "-", 
                xj, '.rds')) # seed and dist not included yet

### 2021-02-10 paper/main.Rmd
updating threshold section

@@
 This means,  $wpd_{norm}$ could be used to measure differences in distribution across panels.
-Also, note that since the data is processed using normal-quantile-transform, this measure is independepent of the intial distribution of the underlying data and hence is also comparable across different datasets.
+Also, note that since the data is processed using normal-quantile-transform, this measure is independent of the intial distribution of the underlying data and hence is also comparable across different data sets.
 This is valid for the case when sample size $ntimes$ for each combination of categories is at least 30 and  $nperm$ used for computing $wpd_{norm}$ is at least 100.
@@
 
-Complete randomness in the measured variable indicates that the process follows a homogeneous underlying distribution over the whole time series, irrespective of the different cyclic granularities; which essentially implies there is no interesting distinct across any particular time deconstruction.
-We can remove the harmonies for which no interesting patterns are observed through a randomisation permutation method.
-Essentially, this method is
-based on the generation of randomly chosen reassignments
-(permutations) of the data across different cyclic granularities and the the computation for each permutated data of the theoretical distribution of $wpd_{norm}$ expected under the null hypothesis.
-The percentages of the theoretical distribution greater than or equal to the respective observed $wpd_{norm}$ values are calculated and used to obtain the P value.
+Complete randomness in the measured variable indicates that the process follows a homogeneous underlying distribution over the whole time series, which essentially implies there is no interesting distinction across any different categories of the cyclic granularities.
+We can remove the harmonies for which no interesting patterns are observed through a randomization permutation method.
+Essentially, the assumption is that under the null hypothesis, there is no difference in categories between the pair of cyclic granularities in the chosen harmony.
+This method is based on the generation of randomly chosen reassignments (permutations) of the data across different cyclic granularities and the computation of
+$wpd_{norm}$ for each of these reassignments.
+The percentages of times the theoretical distribution greater than or equal to the respective observed $wpd_{norm}$ values are calculated and are used to obtain the P value.
 The procedure for the permutation test is:
 
-**Assumption:** random permutation without considering ordering 
-(global)
+<!-- **Assumption:** random permutation of the data keeping the categories of the cyclic granularities constant. -->
 
@@
 
-3. $wpd_norm$ is computed for all random permutation of the data and is represented by $wpd_{sample}$.
+3. $wpd_norm$ is computed for the permuted sequence of the data and is represented by $wpd_{perm_1}$.
 
 4.  Steps (2) and (3) are repeated a large number
-of times M (e.g. 200).
-
-5. For each permutation, one $wpd_{sample}$ value is obtained.
+of times M (M = 200).
+
+5. For each permutation, one $wpd_{perm_i}$ is obtained. Define $wpd_{sample} = \{wpd_{perm_1}, wpd_{perm_2}, \dots, wpd_{perm_M}\}$.
 
@@
 7. If $wpd_{obs}> wpd_{threshold}$, harmony pairs are accepted. Only one threshold for all harmony pairs.
-
-Pros: Considering thresholds global for all harmony pairs would imply less computation time.
 

### 2021-02-10 paper/main.Rmd
size section rough writing

@@
 
-1. Given the data; $\{v_t: t=0, 1, 2, \dots, T-1\}$, the $wpd_norm$ is computed and is represented by $wpd_{obs}$.
+1. Given the data; $\{v_t: t=0, 1, 2, \dots, T-1\}$, the $wpd_{norm}$ is computed and is represented by $wpd_{obs}$.
 
@@
 
-3. $wpd_norm$ is computed for the permuted sequence of the data and is represented by $wpd_{perm_1}$.
+3. $wpd_{norm}$ is computed for the permuted sequence of the data and is represented by $wpd_{perm_1}$.
 
@@
 7. If $wpd_{obs}> wpd_{threshold}$, harmony pairs are accepted. Only one threshold for all harmony pairs.
+
+The p-value of the design $D_{null}$ is size.
+The p-value of other designs is power.
+Confidence interval of the
 
@@
 
-## Size, power and confidence interval
+## Size
+
+The p-value is almost always greater than 0.05, which means there is no significant differences between the different categories, which is true from the simulation design.
+
+```{r size}
+library(readr)
+library(tidyverse)
+data_N01 <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds"))
+
+data_N01_obs <- data_N01 %>% filter(perm_id==1)
+data_N01_samp <- data_N01 %>% filter(perm_id!=1)
+
+plot_mmpd_null_grid(data_N01_samp, data_N01_obs)
+
+mmpd_dist_null_grid  = data_N01_samp
+
+mmpd_null_orig = data_N01_obs
+compute_p_value <- left_join(mmpd_dist_null_grid, mmpd_null_orig,
+                               by = c("nx", "nfacet")) %>% 
+    group_by(nx, nfacet) %>% 
+    summarise(p_value = sum(if_else(abs(value.x)>abs(value.y),1,0))/n(), .groups = 'drop')
+
+  ggplot() + 
+    geom_histogram(data = mmpd_dist_null_grid, aes(x = value))  + 
+    geom_vline(data = mmpd_null_orig, aes(xintercept = value),colour = "red") +
+    geom_text(data = round(compute_p_value, 3), size = 3,  
+              aes(x = -Inf,
+                  y =  Inf,
+                  label = paste("p-value:",p_value),
+                  hjust   = 0,
+                  vjust   = 1)) + 
+    facet_grid(nx ~ nfacet)
+```
+
+```{r power}
+library(readr)
+library(tidyverse)
+data_N01 <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds"))
+
+data_N01_obs <- data_N01 %>% filter(perm_id==1)
+data_N01_samp <- data_N01 %>% filter(perm_id!=1)
+
+plot_mmpd_null_grid(data_N01_samp, data_N01_obs)
+
+mmpd_dist_null_grid  = data_N01_samp
+
+mmpd_null_orig = data_N01_obs
+compute_p_value <- left_join(mmpd_dist_null_grid, mmpd_null_orig,
+                               by = c("nx", "nfacet")) %>% 
+    group_by(nx, nfacet) %>% 
+    summarise(p_value = sum(if_else(abs(value.x)>abs(value.y),1,0))/n(), .groups = 'drop')
+
+  ggplot() + 
+    geom_histogram(data = mmpd_dist_null_grid, aes(x = value))  + 
+    geom_vline(data = mmpd_null_orig, aes(xintercept = value),colour = "red") +
+    geom_text(data = round(compute_p_value, 3), size = 3,  
+              aes(x = -Inf,
+                  y =  Inf,
+                  label = paste("p-value:",p_value),
+                  hjust   = 0,
+                  vjust   = 1)) + 
+    facet_grid(nx ~ nfacet)
+```
 

### 2021-02-10 paper/main.Rmd
updating figures

@@
          , Dim.1, Dim.2)
-
-# ggpubr::ggscatter(mds,
-#                   x = "Dim.1",
-#                   y = "Dim.2", 
-#                   label = rownames(mds),
-#                   size = 1,
-#                   repel = TRUE) 
 ```
@@
 
-#   d = one_harmony_data %>%
-#     select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
-#     dist()
-#   
-#   hc = stats::hclust(d,method="complete")
-#   plot(hc)
-#   groups<-cutree(hc, k=4)
-#   
-#   all_data_cluster <- cbind(one_harmony_data, groups) %>% 
-#     left_join(mds, by = "customer_id") %>% 
-#     mutate(groups = as.factor(groups))
-# 
-# 
-# 
-# ggpubr::ggscatter(all_data_cluster,
-#                   x = "Dim.1",
-#                   y = "Dim.2", 
-#                   label = rownames(mds),
-#                   color = "groups",
-#                   size = 1,
-#                   repel = TRUE)
+```
+
+# check transformation and scalar approaches are same
+
+```{r scalar-approach}
+set.seed(7777)
+all_data <- read_rds("paper/sim_table/all_data_scalar.rds")
+sm_cust_data <- read_rds("paper/data/sm_cust_data.rds")
+set.seed(7777)
+sm_unique_cust <- sm_cust_data %>% distinct(customer_id)
+sm_cust_samp <- sm_cust_data %>% 
+  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
+  #filter(year(reading_datetime) == 2012) %>% #for demo just show one column
+  as_tsibble(index = reading_datetime,
+             key = customer_id) %>% 
+  create_gran("day_week") %>% 
+  create_gran("hour_day")
+
+#all_data <- write_rds(all_data, "paper/sim_table/all_data.rds")
+
+facet_variable = "day_week"
+x_variable = "hour_day"
+
+one_harmony_data <- all_data %>%
+  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
+  filter(facet_variable == "day_week",
+         x_variable == "hour_day") %>% 
+  mutate(customer_id = as.character(customer_id))
+
+mds<- one_harmony_data %>%
+  select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
+  dist() %>%          
+  cmdscale() %>%
+  as_tibble()
+
+colnames(mds) <- c("Dim.1", "Dim.2")
+rownames(mds) <- unique(one_harmony_data$customer_id)
+mds <- mds %>%
+  mutate(customer_id = as.character(unique(one_harmony_data$customer_id))) %>%
+  select((customer_id)
+         , Dim.1, Dim.2)
+
+ggpubr::ggscatter(mds,
+                  x = "Dim.1",
+                  y = "Dim.2", 
+                  label = rownames(mds),
+                  size = 1,
+                  repel = TRUE)
+
+# clustering as well
+
+d = one_harmony_data %>%
+  select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
+  dist()
+
+hc = stats::hclust(d,method="complete")
+plot(hc)
+groups<-cutree(hc, k=4)
+
+all_data_cluster <- cbind(one_harmony_data, groups) %>% 
+  left_join(mds, by = "customer_id") %>% 
+  mutate(groups = as.factor(groups))
+
+ggpubr::ggscatter(all_data_cluster,
+                  x = "Dim.1",
+                  y = "Dim.2", 
+                  label = rownames(mds),
+                  color = "groups",
+                  size = 1,
+                  repel = TRUE)
 
@@
 library(patchwork)
-p1/p2/p3
+p1
+p2
+p3
 

### 2021-02-11 comparison_perm_scalar.Rmd
methodology updated
some figures update

@@
 
-G21 <- read_rds("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds")
+G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds"))
 
@@
 slope <- fit_lm2$coefficients[2]
+
+G21 %>% 
+  ggplot(aes(x=log(nx*nfacet), y = (value - slope*log(nx*nfacet)))) +
+  geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
+  xlab("$wpd_norm =  wpd_raw - slope*log(nx*nfacet)$")
 
@@
 
-all_data_scalar <- 
+#all_data_scalar <- 
 ```

### 2021-02-11 paper/main.Rmd
some figures update

@@
 
-## Size
-
 The p-value is almost always greater than 0.05, which means there is no significant differences between the different categories, which is true from the simulation design.
@@
 
-plot_mmpd_null_grid(data_N01_samp, data_N01_obs)
+#plot_mmpd_null_grid(data_N01_samp, data_N01_obs)
 
@@
 # Plot and color by groups
-ggpubr::ggscatter(mds, x = "Dim.1", y = "Dim.2", 
+q1 <- ggpubr::ggscatter(mds, x = "Dim.1", y = "Dim.2", 
           label = rownames(mds),
@@
 
-# check transformation and scalar approaches are same
+- check transformation and scalar approaches are same
 
@@
 set.seed(7777)
-all_data <- read_rds("paper/sim_table/all_data_scalar.rds")
-sm_cust_data <- read_rds("paper/data/sm_cust_data.rds")
+all_data <- read_rds(here("paper/sim_table/all_data_scalar.rds"))
+sm_cust_data <- read_rds(here("paper/data/sm_cust_data.rds"))
 set.seed(7777)
@@
 hc = stats::hclust(d,method="complete")
-plot(hc)
-groups<-cutree(hc, k=4)
+#plot(hc)
+groups<-cutree(hc, k=3)
 
@@
 
-ggpubr::ggscatter(all_data_cluster,
+q2 <- ggpubr::ggscatter(all_data_cluster,
                   x = "Dim.1",
@@
 
+q1 + q2
 ```
@@
 
-```{r}
+```{r, echo = FALSE}
 
@@
 
-```{r}
+```{r linear}
 raw_data <- sm_cust_data %>% 
-  left_join(mds, by = "customer_id")
+  left_join(all_data_cluster, by = "customer_id")
 
@@
             y = general_supply_kwh)
-  )
+  ) + ggtitle("Group 1")
 
@@
             y = general_supply_kwh)
-  )
+  ) + ggtitle("Group 2")
 
@@
             y = general_supply_kwh)
-  )
+  ) + ggtitle("Group 3")
 library(patchwork)
@@
 
-```{r}
+```{r gravitas}
 raw_data <- sm_cust_data %>% 
-  left_join(mds, by = "customer_id")
+  left_join(all_data_cluster, by = "customer_id")
 
@@
             symmetric = FALSE
-)
+)  + ggtitle("Group 1")
 
@@
             symmetric = FALSE
-)
+)  + ggtitle("Group 2")
 
@@
             symmetric = FALSE
-)
+)  + ggtitle("Group 3")
+
 library(patchwork)
@@
 
-### Advantage over taditional feature based methods
+### Advantage over taditional feature based clustering methods
 

### 2021-02-15 comparison_perm_scalar.Rmd
transformations episode

@@
 library(ggplot2)
+library(here)
 ```
@@
 
-```{r wpd-permutation, fig.cap = " The distribution of $wpd_{permutation}$ is plotted.
+```{r wpd-permutation-d, fig.cap = " The distribution of $wpd_{permutation}$ is plotted.
 The distributions are more similar across different nx and nfacet (specially for small nx and nfacet) but this approach has the downside of more computational time."}
@@
 ```
+
+- the two approaches permutation and modelling could be brought to the same scale so that for smaller categories, permutation could be done and for larger categories, stick to modelling approach
+
+## bringing both to the same scale also helps means you have a lower and upper bound for the normalised wpd
+
+```{r dist-new-same-scale}
+
+G21 <- read_csv("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.csv")
+
+G21_median <- G21 %>% 
+  group_by(nx*nfacet) %>% 
+  summarise(actual = median(value))
+
+# fit model median to log(nx*nfacet)
+fit_lm2 <- lm(actual ~ poly(log(`nx * nfacet`) ,1, raw=TRUE), data = G21_median)
+
+summary(fit_lm2)
+
+beta_lm2 <- lm(actual ~ log(`nx * nfacet`), data = G21_median)
+
+summary(fit_lm2)
+
+beta_lm2 <- lm(actual ~ log(`nx * nfacet`), data = G21_median)
+
+summary(fit_lm2)
+
+intercept <- fit_lm2$coefficients[1]
+slope <- fit_lm2$coefficients[2]
+
+G21 %>% 
+  ggplot(aes(x=log(nx*nfacet), y = (value - intercept -slope*log(nx*nfacet)))) +
+  geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
+  xlab("$wpd_norm =  wpd_raw - slope*log(nx*nfacet)$")
+
+G21_permutation <- read_rds("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_Gamma21.rds") %>% 
+  rename("wpd_permutation" = "value")
+
+G21_model_data <- G21 %>% 
+  mutate(model =
+           (value - intercept - 0.0027*log(nx*nfacet))/0.0027
+         ) %>% 
+  mutate(model_trans = 
+           (model - min(model))/(max(model) - min(model)))
+
+G21_model_data$model %>% summary()
+G21_model_data$model_trans %>% summary()
+
+G21_perm_data <- G21_permutation %>% 
+  mutate(perm_trans =
+           (
+             (wpd_permutation - min(wpd_permutation))/
+                (
+                  max(wpd_permutation) - min(wpd_permutation)
+                )
+             )
+           )
+
+G21_all_data <- G21_model_data %>% 
+  left_join(G21_perm_data, by = c("nx", "nfacet", "perm_id")) %>% 
+  pivot_longer(cols = c(6,8),
+               names_to = "type_estimate",
+               values_to = "value_estimate")
+
+G21_all_data %>% 
+  ggplot() +
+  geom_density(aes(x = value_estimate, 
+                   fill = type_estimate), 
+               alpha = 0.7) +
+  facet_grid(nx~nfacet,
+             labeller = "label_both") +
+  theme(legend.position = "bottom") +
+  scale_fill_manual(values = c("#0072B2", "#CC79A7")) +
+  xlab("wpd_norm2")
+```
+
+```{r wpd-permutation, fig.cap = " The distribution of $wpd_{permutation}$ is plotted.
+The distributions are more similar across different nx and nfacet (specially for small nx and nfacet) but this approach has the downside of more computational time."}
+
+G21_perm_data %>% 
+    ggplot() +
+  geom_density(aes(x = perm_trans), 
+                   fill = "blue") +
+  facet_grid(nx~nfacet,
+             labeller = "label_both") +
+  theme(legend.position = "bottom") 
+```
+
+# bringing both to same scale
+
+```{r}
+data <- read_rds("simulations/supplementary/data-agg/wpd_N01/all_data.rds")
+
+# data_validate <-  data %>% 
+#   filter(
+#     nperm == 10, ntimes == 100, w == 1
+#   ) %>% 
+#   pivot_wider(id_cols = -2,
+#               names_from = design,
+#               values_from = value) %>% 
+#   mutate(right_order = ((null<=vary_f<=vary_x)))
+
+data_filter <- data %>% 
+    filter(
+        nperm == 10, ntimes == 100, w == 1
+    )
+
+data_filter %>% 
+    pivot_wider(id_cols = -2,
+                names_from = design,
+                values_from = value) %>% 
+    mutate(right_order = (null <= min(null, vary_f, vary_x)))
+
+  #            
+  #            ((null<=vary_f) & (vary_f<=vary_x))) %>% 
+  # mutate(right_order_proxy = if_else(right_order==TRUE, 1, 0)) %>% 
+  # group_by(nx, nfacet) %>% 
+  # summarise(n_order =  sum(right_order_proxy)/200) %>% View()
+
+data_filter %>% 
+  mutate(value = value - 0.0027*log(nx*nfacet)) %>% 
+    pivot_wider(id_cols = -2,
+                names_from = design,
+                values_from = value) %>% 
+    mutate(right_order = ((null<=vary_f) & (vary_f<=vary_x))) %>% 
+  mutate(right_order_proxy = if_else(right_order==TRUE, 1, 0)) %>% 
+  group_by(nx, nfacet) %>% 
+  summarise(n_order =  sum(right_order_proxy)/200) %>% View
+
+```
+
+# Real Data
+
+- Check if the ranking of the harmonies from the two approaches (wpd_norm_perm and  wpd_norm_scalar) are similar or not?
+
+- Check if the threshold is visually too different
+
+```{r}
+all_data_perm <- read_rds("paper/sim_table/all_data.rds")
+
+#all_data_scalar <- 
+```
+
+- the two approaches permutation and modelling could be brought to the same scale so that for smaller categories, permutation could be done and for larger categories, stick to modelling approach
+
+## bringing both to the same scale also helps means you have a lower and upper bound for the normalised wpd
+
+# the following looks right where the $wpd_{norm}$ are just plotted like that and the model is GLM with distribution Gamma and link-function inverse
+
+```{r dist-new-same-scale-link}
+
+G21 <- read_csv("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.csv")
+
+G21_median <- G21 %>% 
+  group_by(nx*nfacet) %>% 
+  summarise(actual = median(value))
+
+# fit model median to log(nx*nfacet)
+# fit_lm2 <- lm(actual ~ poly(log(`nx * nfacet`) ,1, raw=TRUE), data = G21_median)
+# 
+# summary(fit_lm2)
+
+glm_fit <- glm(actual ~ log(`nx * nfacet`),
+              family = Gamma(link = "inverse"),
+              data = G21_median)
+
+summary(glm_fit)
+
+intercept <- glm_fit$coefficients[1]
+slope <- glm_fit$coefficients[2]
+
+G21 %>% 
+  ggplot(aes(x=log(nx*nfacet),
+             y = ((1/value)
+                  - intercept - 
+                    slope*log(nx*nfacet))/slope)) +
+  geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue")
+
+G21_permutation <- read_rds("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_Gamma21.rds") %>% 
+  rename("wpd_permutation" = "value")
+
+G21_model_data <- G21 %>% 
+  mutate(model =
+           ((1/value)
+                  - intercept - 
+                    slope*log(nx*nfacet))/slope) %>% 
+  mutate(model_trans = 
+           (model - mean(model))/sd(model))
+
+G21_model_data$model %>% summary()
+
+G21_perm_data <- G21_permutation %>% 
+  mutate(perm_trans =
+           (
+             (wpd_permutation - min(wpd_permutation))/
+                (
+                  max(wpd_permutation) - min(wpd_permutation)
+                )
+             )
+           )
+
+G21_all_data <- G21_model_data %>% 
+  left_join(G21_perm_data, by = c("nx", "nfacet", "perm_id")) %>% 
+  pivot_longer(cols = c(6,7),
+               names_to = "type_estimate",
+               values_to = "value_estimate")
+
+G21_all_data %>% 
+  ggplot() +
+  geom_density(aes(x = value_estimate, 
+                   fill = type_estimate), 
+               alpha = 0.7) +
+  facet_grid(nx~nfacet,
+             labeller = "label_both") +
+  theme(legend.position = "bottom") +
+  scale_fill_manual(values = c("#CC79A7", "#0072B2")) +
+  xlab("wpd_norm2")
+
+# are scales same
+
+G21_model_data %>%
+  group_by(nx, nfacet) %>% 
+  summarise(sd_model = sd(model))
+
+```

### 2021-02-15 paper/main.Rmd
transformations episode

@@
 
+```{r}
+all_data_scalar <- read_rds(here("paper/sim_table/all_data_scalar.rds"))
+all_data <- read_rds(here("paper/sim_table/all_data.rds"))
+
+merged_data <- left_join(all_data_scalar,all_data, by = c("customer_id",
+                                                          "facet_variable",
+                                                          "x_variable")) %>% 
+  rename("wpd_scalar"  = "wpd_norm.x",
+         "wpd_perm" = "wpd_norm.y")
+
+merged_data %>% 
+  mutate(pair = paste(facet_variable, x_variable, sep = "-")) %>% 
+  ggplot() +
+  geom_point(aes(x = wpd_scalar, y = wpd_perm, color = pair, group = pair))
+  #geom_point(aes(x = wpd_scalar, y = wpd_perm, alpha = 0.05))
+
+```
+
 ```{r linear}

### 2021-02-15 example_transformations.R

@@ -131,8 +131,6 @@ N01 %>%
 
 
 
-
-
 N01_median <- N01 %>% 
   group_by(nx*nfacet) %>% 
   summarise(actual = median(value))

### 2021-02-16 combining_perm-model.Rmd
working on combining permutation and modeling approach

---
title: "Permutation and scalar transformation approaches to normalisation and combining them"
author: "Sayani Gupta"
output:
  bookdown::pdf_book:
    #base_format: rticles::asa_article
    fig_height: 5
    fig_width: 8
    fig_caption: yes
    dev: "pdf"
    toc: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      eval = TRUE,
                      warning = FALSE,
                      message = FALSE)
knitr::read_chunk("example_transformations.R")
library(tidyverse)
library(readr)
library(ggplot2)
library(here)
library(patchwork)
```

# Data generation

Observations are generated from a Gamma(2,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high. Each combination is being referred to as a _panel_. That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$. For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories. That is, if we consider the panel  $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$. The values of $\lambda$ is set to $0.67$ and values of raw wpd $wpd_{raw}$ is obtained.

```{r raw, fig.cap = "Distribution of raw wpd is plotted across different nx and nfacet categories. Both shape and scale of the distribution changes for different nx and nfacet categories."}
G21 <- read_rds("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds")

G21 %>% 
  ggplot(aes(x = value)) + 
  geom_density(fill = "blue") +
  facet_grid(nx~nfacet,
             labeller = "label_both") + 
  scale_x_continuous(breaks = scales::breaks_extended(3)) + 
  xlab("raw wpd")
```

Figure \ref{Fig:raw} shows the distribution of $wpd_{raw}$ is plotted across different nx and nfacet categories. Both shape and scale of the distribution changes for different $nx$ and $nfacet$ categories. This is not desirable as it would mean we would not be able to compare $wpd_{raw}$ across different $nx$ and $nfacet$ as each of them are drawn from distributions of different locations and scale. In Figure \ref{fig:quadratic} we see how the median of $wpd_{raw}$ varies with the total number of distances $nx_i*nfacet_j$ for a panel with $nx = nx_i$ categories and $nfacet = nfacet_j$ categories. The median increases abruptly for lower values of $nx_i*nfacet_j$ and the increase becomes more gradual for higher $nx_i*nfacet_j$.

```{r quadratic, fig.cap = "The raw wpd is plotted against nx*nfacet and the blue line represents the median of the multiple values for each nx*nfacet levels."}
G21 %>% 
  ggplot(aes(x=nx*nfacet, y = value)) +
  geom_point() + stat_summary(fun=median, geom="line", aes(group=1), color = "blue") + xlab("nx*nfacet") + ylab("raw wpd")

```

We need a transformation on $raw_{wpd}$ which will make it independent of the values of $nx*nfacet$. Two approaches have been employed for that purpose, the first one involves fitting a model and the latter involves a permutation method to make the distribution of the transformed $wpd$ similar across different $nx$ and $nfacet$.

## Scalar transformation approach to normalisation

### Linear model

A log-linear model is fitted to see how the values of $wpd_{raw}$ changes with the values of $nx$ and $nfacet$. The model is of the form $$y = a+b*log(x) +e$$, where $y = median(wpd_{raw})$ and $x = nx*nfacet$. $wpd_{lm}$ is a transformation on $wpd_{raw}$ which should be designed to remove the effect of $nx*nfacet$ on $wpd_{raw}$ and thus is defined as follows:
$wpd_{lm} = wpd_{raw} - a - b*log(nx*nfacet)$

```{r wpd-lm-horizontal,echo=FALSE, fig.caption = "$wpd_{lm}$ is platted again log(nx*nfacet) and this transformation leads to median($wpd_{lm}$) to having almost no relationship with log(nx*nfacet)"}

G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds"))

G21_median <- G21 %>% 
  group_by(nx*nfacet) %>% 
  summarise(actual = median(value))

# fit model median to log(nx*nfacet)
fit_lm2 <- lm(actual ~ poly(log(`nx * nfacet`) ,1, raw=TRUE), data = G21_median)

#summary(fit_lm2)

intercept <- fit_lm2$coefficients[1]
slope <- fit_lm2$coefficients[2]

G21 %>% 
  ggplot(aes(x=log(nx*nfacet), y = (value - intercept - slope*log(nx*nfacet)))) +
  geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") +
  ylab("wpd_lm = wpd_raw - a - b*log(nx*nfacet)")
```

```{r wpd-lm-dist, fig.cap = " The distribution of $wpd_{lm}$ is plotted. The distributions are more similar across higher  nx and nfacet and are different for smaller nx and nfacet."}

G21_lm <- G21 %>% 
  mutate(wpd_lm =  (value - intercept - slope*log(nx*nfacet)))

G21_lm %>% 
  ggplot() +
  geom_density(aes(x = wpd_lm), 
                   fill = "blue") +
  facet_grid(nx~nfacet,
             labeller = "label_both") +
  theme(legend.position = "bottom") 
```

### Generalised linear model

In the earlier approach, $wpd_{raw} \in R$, whereas,  $0 \leq wpd_{raw}\leq 1$ since it is a JS distance. Also, JSD follows a Chi-square distribution, which could be considered as a Gamma distribution. Hence, to restrict the range of the measure between 0 and 1, and deviate from the normality assumption of the response variable in a OLS approach, we fit a generalized linear model (GLM) with the error distributed as a gamma distribution and link function as "inverse". Hence, the model is of the form  $$1/y = a+b*log(x) +e$$, where $y = median(wpd_{raw})$ and $x = nx*nfacet$. Again, $wpd_{glm}$ is a transformation on $wpd_{raw}$ which should be designed to remove the effect of $nx*nfacet$ on $wpd_{raw}$ and thus is defined as follows:
$wpd_{glm} = 1/wpd_{raw} - a - b*log(nx*nfacet)$.

Please note:

- subtracting the intercept brings the location of the transformed variable to 0 for either case
- heterogeneity is higher for this case after normalization as compared to the earlier one.

```{r wpd-glm-horizontal, echo = FALSE, fig.caption = "$wpd_{glm}$ is plotted against log(nx*nfacet) and this transformation leads to the median of $wpd_{glm}$ to have no relationship with log(nx*nfacet)"}

G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds"))

G21_median <- G21 %>% 
  group_by(nx*nfacet) %>% 
  summarise(actual = median(value))

glm_fit <- glm(actual ~ log(`nx * nfacet`),
              family = Gamma(link = "inverse"),
              data = G21_median)

intercept <- glm_fit$coefficients[1]
slope <- glm_fit$coefficients[2]

# checking the fit of the residuals from glm fit

# fitted_glm <- fitted(glm_fit, type = "response")
# residuals <- residuals.glm(glm_fit, type = "response")
# hist(residuals)

#h = augment(glm_fit)
# ggplot(h) +
#   geom_histogram(aes(x = .resid))

# residual <- G21_median$actual  - fitted_glm
# 
# hist(residual)

G21 %>% 
  ggplot(aes(x=log(nx*nfacet),
             y = (value - (1/(intercept + slope*log(nx*nfacet)
                    )
                    )
             )
  )
  ) +
  geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
  ylab("wpd_glm = 1/wpd_raw - a - b*log(nx*nfacet)")
```

```{r wpd-glm-dist, fig.cap = " The distribution of $wpd_{glm}$ is plotted. The distributions are more similar across higher nx and nfacet and dissimilar for fewer nc and nfacets."}

G21_glm <- G21 %>% 
  mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
                    )
                    )
             ),
         wpd_glm_trans = ((wpd_glm*300)))

G21_glm %>% 
  ggplot() +
  geom_density(aes(x = wpd_glm), 
                   fill = "blue") +
  facet_grid(nx~nfacet,
             labeller = "label_both") +
  theme(legend.position = "bottom") 
```

## Permutation approach to normalisation

The simulated data for each of the panels is permuted/shuffled $nperm = 200$ times and for each of those permutations $wpd_{norm}$ is computed as follows: $wpd_{perm} =  (wpd_{raw} - mean(wpd_{raw}))/sd(wpd_{raw})$
. This is done so that the distribution of the normalised measure $wpd_{norm}$ has the same mean and standard deviation across different nx and nfacet.

Please note that standardizing the variable $wpd_{perm}$ in this approach leads to $location = 0$ and $scale = 1$ for this variable.

```{r wpd-permutation-dist, fig.cap = " The distribution of $wpd_{permutation}$ is plotted. The distributions are more similar across different nx and nfacet (specially for small nx and nfacet) but this approach has the downside of more computational time."}

G21_permutation <- read_rds("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_Gamma21.rds") %>%
  rename("wpd_permutation" = "value") %>% 
  mutate(perm_trans =
           (
             (wpd_permutation - min(wpd_permutation))/
                (
                  max(wpd_permutation) - min(wpd_permutation)
                )
             )
           )

G21_permutation %>% 
    ggplot() +
  geom_density(aes(x = wpd_permutation), 
                   fill = "blue") +
  facet_grid(nx~nfacet,
             labeller = "label_both") +
  theme(legend.position = "bottom") 
```

## Bringing them both to the same scale

We see that the transformation through the modeling approach leads to very similar distribution across high $nx$ and $nfacet$ (higher than 7) and not so much for lower $nx$ and $nfacet$. Hence, the computational load of permutation approach could be alleviated by using the modeling approach for the higher $nx$ and $nfacet$, however, it is important that we use the permutation approach for lower $nx$ and $nfacet$. However, it is  difficult to compare the transformed $wpd$ from both of these approaches, since each of the variables is measured on a different scale (each of them have location 0). The transformed variables from the two approaches could be brought to the same scale so that for smaller categories, permutation approach is used and for larger categories, we can stick to modeling approach. These could be done through the following:

 - Making the range of both the variables same by using min-max scaling method. In practice, however, we would only have one value of $wpd_{raw}$ which we need to transform using the modeling appraoch. Hence, min-max scaling approach could not be used here.

 - Standardizing the variables and expressing scores at standard deviation units. Again in practice, however, we would only have one value of $wpd_{raw}$ which we need to transform using the modeling appraoch. Hence, standardizing scores could not be used here as we do not have the mean and standard deviation of a series while using transfomation using modeling.

- Make the location and scale of both the approaches similar so that they could be compared. Please note that the range of values could be different in this case, however location and scale are brought to same levels.)

The measure $wpd_{glm}$ seems to roughly follow a normal distribution except in the tails as could be seen in Figure \ref{fig:hist-qq} and the very method of permuation approach ensures that $wpd_permutation$ is also normally distributed. Further, they are brought to the similar scale and location and hence could be compared.

```{r hist-qq, fig.cap = "In panel a, the histogram of $wpd_glm_trans$ is plotted. In parl b, the QQ plot is shown with the theoretical quantiles on the x-axis and $wpd_glm_trans$ quantiles on the y-axis. The distribution looks symmetric and looks like normal except in the tails."}
hist <- ggplot(G21_glm) +
  geom_histogram(aes(x = wpd_glm_trans)) +
  ggtitle("a")

p <- ggplot(G21_glm, aes(sample = wpd_glm_trans))
qqplot <-  p + geom_qq() + geom_qq_line() + coord_fixed(ratio = 4/5) +
  ggtitle("b")

# G21_glm <- G21 %>% 
#     mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
#     )
#     )
#     ),
#     wpd_glm_trans = 300*(wpd_glm))

 # G21_glm$wpd_glm_trans %>% 
 #   range()
hist + qqplot
```

```{r dist-new-same-scale-link, fig.cap="wpd_permutation and wpd_lm are in very different scale and could not be plotted together without transforming further. Whereas wpd_permutation and wpd_glm could be plotted together as they at least have the same location. Are they on the same scale though? Can they be compared?"}

# 
# G21_permutation <- read_rds("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_Gamma21.rds") %>%
#   rename("wpd_permutation" = "value")
# 
# 
# G21_model_data <- G21 %>%
#   mutate(model =
#            ((1/value)
#                   - intercept -
#                     slope*log(nx*nfacet))/slope) %>%
#   mutate(model_trans =
#            (model - mean(model))/sd(model))

# G21_model_data$model %>% summary()

G21_all_data <- G21_permutation %>% 
  left_join(G21_lm, by = c("nx", "nfacet", "perm_id")) %>% 
  left_join(G21_glm, by = c("nx", "nfacet", "perm_id")) %>% 
  pivot_longer(cols = c(3, 10),
               names_to = "type_estimate",
               values_to = "value_estimate")
G21_all_data$type_estimate = factor(G21_all_data$type_estimate , levels = c( "wpd_permutation", "wpd_glm_trans"))

G21_all_data %>% 
  filter(type_estimate %in% c("wpd_glm_trans", "wpd_permutation")) %>% 
  ggplot() +
  geom_density(aes(x = value_estimate, 
                   fill = type_estimate)) +
  facet_grid(nx~nfacet,
             labeller = "label_both") +
  theme(legend.position = "bottom") +
  scale_fill_manual(values = c("#999999",  "#D55E00")) +
  xlab("wpd_norm2")

# G21_all_data %>% 
#   filter(type_estimate %in% c("wpd_permutation", "wpd_glm")) %>% 
#   ggplot() +
#   geom_density(aes(x = value_estimate, 
#                    fill = type_estimate), 
#                alpha = 0.7) +
#   facet_grid(nx~nfacet,
#              labeller = "label_both") +
#   theme(legend.position = "bottom") +
#   scale_fill_manual(values = c("#CC79A7", "#0072B2")) +
#   xlab("wpd_norm2")

# are scales same
# 
# G21_model_data %>%
#   group_by(nx, nfacet) %>% 
#   summarize(sd_model = sd(model))
#   
# G21_all_data %>%
#   filter(type_estimate == c("perm_trans")) %>% 
#   select(value_estimate) %>% 
#   range()
# 
# G21_all_data %>%
#   filter(type_estimate == c("wpd_glm_trans")) %>% 
#   select(value_estimate) %>% 
#   range()
```

Questions:

 1. Does the approach of $wpd_{glm}$ looks correct?

 2. Are $wpd_{glm}$ and $wpd_{permuation}$ be compared from this plot or both should be brought to the scale 1 for comparison?

 3. Forcing same range (0,1) to both $wpd_{glm}$ and $wpd_{permutation}$ could be obtained by using the transformation
$(z- z_{min})/ (z_{max} - z_{min})$. This could be used for the permutation approach. But the modeling approach would only have one value of $wpd_{raw}$ for a panel in practice, how to scale the values in the modeling approach so that they are within 0 and 1?

```{r variance}
#glm-wpd-sd
glm_wpd_sd <- G21_glm$wpd_glm %>% sd
#permutation-wpd_sd
glm_wpd_sd <- G21_permutation$wpd_permutation %>% sd
#lm-wpd_sd
G21_lm$wpd_lm %>% sd
```
<!-- In Figure \ref{fig:dist-new-approx}, we see that the distribution of $wpd_{norm2} = wpd_{raw} - b*log(nx*nfacet)$ is similar when normalised with true or approximate estimate of b. Moreover, the distributions are pretty similar across different nx and nfacet. -->

<!-- ```{r dist-new-approx, echo = FALSE, fig.cap = " The distribution of $wpd_{norm2}$ is plotted for approximate estimate of b. The distributions are similar when plotted against true and approximate estimate and b."} -->

<!-- G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds")) -->

<!-- G21_median <- G21 %>%  -->
<!--   group_by(nx*nfacet) %>%  -->
<!--   summarize(actual = median(value)) -->

<!-- # fit model median to log(nx*nfacet) -->
<!-- fit_lm2 <- lm(actual ~ poly(log(`nx * nfacet`) ,1, raw=TRUE), data = G21_median) -->

<!-- summary(fit_lm2) -->

<!-- intercept <- fit_lm2$coefficients[1] -->
<!-- slope <- fit_lm2$coefficients[2] -->

<!-- G21 %>%  -->
<!--   ggplot(aes(x=log(nx*nfacet), y = (value - slope*log(nx*nfacet)))) + -->
<!--   geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue")  -->

<!-- G21_permutation <- read_rds("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_Gamma21.rds") %>%  -->
<!--   rename("wpd_permutation" = "value") -->

<!-- G21_all_data <- G21 %>%  -->
<!--   mutate(wpd_exact_est = (value - slope*log(nx*nfacet)), -->

<!--                           wpd_approx_est = (value - 0.0027*log(nx*nfacet))) %>%  -->
<!--   pivot_longer(cols = 5:6, -->
<!--                names_to = "type_estimate", -->
<!--                values_to = "value_estimate") -->

<!-- G21_all_data %>%  -->
<!--   ggplot() + -->
<!--   geom_density(aes(x = value_estimate,  -->
<!--                    fill = type_estimate),  -->
<!--                alpha = 0.5) + -->
<!--   facet_grid(nx~nfacet, -->
<!--              labeller = "label_both") + -->
<!--   theme(legend.position = "bottom") + -->
<!--   scale_fill_manual(values = c("#0072B2", "#D55E00", "#CC79A7")) + -->
<!--   xlab("wpd_norm2") -->
<!-- ``` -->

### 2021-02-16 combining_perm-model.Rmd
spell check

@@
 
+Figure \ref{Fig:raw} shows the distribution of $wpd_{raw}$ is plotted across different nx and nfacet categories.
+Both shape and scale of the distribution changes for different $nx$ and $nfacet$ categories.
+This is not desirable as it would mean we would not be able to compare $wpd_{raw}$ across different $nx$ and $nfacet$ as each of them are drawn from distributions of different locations and scale.
+In Figure \ref{fig:quadratic} we see how the median of $wpd_{raw}$ varies with the total number of distances $nx_i*nfacet_j$ for a panel with $nx = nx_i$ categories and $nfacet = nfacet_j$ categories.
+The median increases abruptly for lower values of $nx_i*nfacet_j$ and the increase becomes more gradual for higher $nx_i*nfacet_j$.
+
 ```{r raw, fig.cap = "Distribution of raw wpd is plotted across different nx and nfacet categories. Both shape and scale of the distribution changes for different nx and nfacet categories."}
@@
 
-Figure \ref{Fig:raw} shows the distribution of $wpd_{raw}$ is plotted across different nx and nfacet categories.
-Both shape and scale of the distribution changes for different $nx$ and $nfacet$ categories.
-This is not desirable as it would mean we would not be able to compare $wpd_{raw}$ across different $nx$ and $nfacet$ as each of them are drawn from distributions of different locations and scale.
-In Figure \ref{fig:quadratic} we see how the median of $wpd_{raw}$ varies with the total number of distances $nx_i*nfacet_j$ for a panel with $nx = nx_i$ categories and $nfacet = nfacet_j$ categories.
-The median increases abruptly for lower values of $nx_i*nfacet_j$ and the increase becomes more gradual for higher $nx_i*nfacet_j$.
-
-```{r quadratic, fig.cap = "The raw wpd is plotted against nx*nfacet and the blue line represents the median of the multiple values for each nx*nfacet levels."}
+```{r quadratic, fig.cap = "$wpd_{raw}$ is plotted against nx*nfacet and the blue line represents the median of the multiple values for each nx*nfacet levels."}
 G21 %>% 
@@
 $wpd_{lm}$ is a transformation on $wpd_{raw}$ which should be designed to remove the effect of $nx*nfacet$ on $wpd_{raw}$ and thus is defined as follows:
-$wpd_{lm} = wpd_{raw} - a - b*log(nx*nfacet)$
+$wpd_{lm} = wpd_{raw} - \hat a - \hat b*log(nx*nfacet)$
 
-```{r wpd-lm-horizontal,echo=FALSE, fig.caption = "$wpd_{lm}$ is platted again log(nx*nfacet) and this transformation leads to median($wpd_{lm}$) to having almost no relationship with log(nx*nfacet)"}
+```{r wpd-lm-horizontal,echo=FALSE, fig.caption = "$wpd_{lm}$ is plotted again log(nx*nfacet) and this transformation leads to median($wpd_{lm}$) to having almost no relationship with log(nx*nfacet)"}
 
@@
 
-In the earlier approach, $wpd_{raw} \in R$, whereas,  $0 \leq wpd_{raw}\leq 1$ since it is a JS distance.
-Also, JSD follows a Chi-square distribution, which could be considered as a Gamma distribution.
-Hence, to restrict the range of the measure between 0 and 1, and deviate from the normality assumption of the response variable in a OLS approach, we fit a generalized linear model (GLM) with the error distributed as a gamma distribution and link function as "inverse".
-Hence, the model is of the form  $$1/y = a+b*log(x) +e$$, where $y = median(wpd_{raw})$ and $x = nx*nfacet$.
-Again, $wpd_{glm}$ is a transformation on $wpd_{raw}$ which should be designed to remove the effect of $nx*nfacet$ on $wpd_{raw}$ and thus is defined as follows:
-$wpd_{glm} = 1/wpd_{raw} - a - b*log(nx*nfacet)$.
+In the earlier approach, $wpd_{raw} \in R$ was assumed, whereas,  $0 \leq wpd_{raw}\leq 1$ since it is a Jensen-Shannon Distance (JSD).
+Further, we know JSD follows a Chi-square distribution, which is a special case of Gamma distribution and hence belongs to exponential family of distributions.
+Therefore, we can fit a generalized linear model instead of a linear model to allow the response variable to follow a Gamma distribution.
+The inverse link is used when we know that the mean response to be bounded, which is applicable in our case since JSD will lie between between 0 and 1.
 
-Please note:
+We fit the Gamma generalized linear model with inverse link which is of the form:  
+$$y = 1/(a+b*log(x)) + e$$, where $y = median(wpd_{raw})$, $x = nx*nfacet$.
+Again, $wpd_{glm}$ which is a transformation on $wpd_{raw}$ and is designed to remove the effect of $nx*nfacet$ on $wpd_{raw}$ are chosen as the residuals and defined as
+$wpd_{glm} = wpd_{raw} - 1/(\hat a + \hat b*log(nx*nfacet))$.
 
-- subtracting the intercept brings the location of the transformed variable to 0 for either case
-- heterogeneity is higher for this case after normalization as compared to the earlier one.
+<!-- Please note: -->
+
+<!-- - subtracting the intercept brings the location of the transformed variable to 0 for either case -->
+<!-- - heterogeneity is higher for this case after normalization as compared to the earlier one. -->
 
@@
  - Making the range of both the variables same by using min-max scaling method.
-In practice, however, we would only have one value of $wpd_{raw}$ which we need to transform using the modeling appraoch.
+In practice, however, we would only have one value of $wpd_{raw}$ which we need to transform using the modeling approach.
 Hence, min-max scaling approach could not be used here.
@@
  - Standardizing the variables and expressing scores at standard deviation units.
-Again in practice, however, we would only have one value of $wpd_{raw}$ which we need to transform using the modeling appraoch.
-Hence, standardizing scores could not be used here as we do not have the mean and standard deviation of a series while using transfomation using modeling.
+Again in practice, however, we would only have one value of $wpd_{raw}$ which we need to transform using the modeling approach.
+Hence, standardizing scores could not be used here as we do not have the mean and standard deviation of a series while using transformation using modeling.
 
@@
 
-The measure $wpd_{glm}$ seems to roughly follow a normal distribution except in the tails as could be seen in Figure \ref{fig:hist-qq} and the very method of permuation approach ensures that $wpd_permutation$ is also normally distributed.
+The measure $wpd_{glm}$ seems to roughly follow a normal distribution except in the tails as could be seen in Figure \ref{fig:hist-qq} and the very method of permutation approach ensures that $wpd_permutation$ is also normally distributed.
 Further, they are brought to the similar scale and location and hence could be compared.

### 2021-02-16 combining_normalisation_method.Rmd
done combining normalisation approaches

--- 2021-02-16 combining_perm-model.Rmd
@@
 ---
-title: "Permutation and scalar transformation approaches to normalisation and combining them"
-author: "Sayani Gupta"
+title: "Combining the permutation and modeling approaches for normalisation"
 output:
@@
 
-Figure \ref{Fig:raw} shows the distribution of $wpd_{raw}$ is plotted across different nx and nfacet categories.
-Both shape and scale of the distribution changes for different $nx$ and $nfacet$ categories.
-This is not desirable as it would mean we would not be able to compare $wpd_{raw}$ across different $nx$ and $nfacet$ as each of them are drawn from distributions of different locations and scale.
-In Figure \ref{fig:quadratic} we see how the median of $wpd_{raw}$ varies with the total number of distances $nx_i*nfacet_j$ for a panel with $nx = nx_i$ categories and $nfacet = nfacet_j$ categories.
-The median increases abruptly for lower values of $nx_i*nfacet_j$ and the increase becomes more gradual for higher $nx_i*nfacet_j$.
+Figure \ref{fig:raw} shows the distribution of $wpd_{raw}$ plotted across different nx and nfacet categories.
+Both shape and scale of the distributions change across panels.
+This is not desirable as it would mean we would not be able to compare $wpd_{raw}$ across different $nx$ and $nfacet$ as each of them are drawn from distributions with different locations and scale.
+In Figure \ref{fig:quadratic}, we see how the median of $wpd_{raw}$ varies with the total number of distances $nx*nfacet$ for each panel.
+The median increases abruptly for lower values of $nx*nfacet$ and slowly for higher $nx*nfacet$.
 
@@
 We need a transformation on $raw_{wpd}$ which will make it independent of the values of $nx*nfacet$.
-Two approaches have been employed for that purpose, the first one involves fitting a model and the latter involves a permutation method to make the distribution of the transformed $wpd$ similar across different $nx$ and $nfacet$.
+Two approaches have been employed for that purpose, the first one involves fitting a model and the latter involves a permutation method to make the distribution of the transformed $wpd_raw$ similar across different $nx$ and $nfacet$.
 
-## Scalar transformation approach to normalisation
+## Modeling approach to normalisation
 
@@
 
-A log-linear model is fitted to see how the values of $wpd_{raw}$ changes with the values of $nx$ and $nfacet$.
+A linear model is fitted to see how the values of $wpd_{raw}$ changes with the values of $nx$ and $nfacet$.
 The model is of the form $$y = a+b*log(x) +e$$, where $y = median(wpd_{raw})$ and $x = nx*nfacet$.
-$wpd_{lm}$ is a transformation on $wpd_{raw}$ which should be designed to remove the effect of $nx*nfacet$ on $wpd_{raw}$ and thus is defined as follows:
+$wpd_{lm}$ is a transformation on $wpd_{raw}$ which is designed to remove the impact of $nx*nfacet$ on $wpd_{raw}$ and thus is defined as follows:
 $wpd_{lm} = wpd_{raw} - \hat a - \hat b*log(nx*nfacet)$
+$wpd-lm-horizontal$ seems to have no relationship with $nx*nfacet$ as could be seen in Figure \ref{fig:wpd-lm-horizontal}.
 
-```{r wpd-lm-horizontal,echo=FALSE, fig.caption = "$wpd_{lm}$ is plotted again log(nx*nfacet) and this transformation leads to median($wpd_{lm}$) to having almost no relationship with log(nx*nfacet)"}
+```{r wpd-lm-horizontal, echo=FALSE, fig.cap = "$wpd_{lm}$ is plotted against log(nx*nfacet) and this transformation leads to median($wpd_{lm}$) to having almost no relationship with log(nx*nfacet)"}
 
@@
 
-In the earlier approach, $wpd_{raw} \in R$ was assumed, whereas,  $0 \leq wpd_{raw}\leq 1$ since it is a Jensen-Shannon Distance (JSD).
-Further, we know JSD follows a Chi-square distribution, which is a special case of Gamma distribution and hence belongs to exponential family of distributions.
-Therefore, we can fit a generalized linear model instead of a linear model to allow the response variable to follow a Gamma distribution.
-The inverse link is used when we know that the mean response to be bounded, which is applicable in our case since JSD will lie between between 0 and 1.
+In the linear model approach, $wpd_{raw} \in R$ was assumed, whereas, $wpd_{raw}$, Jensen-Shannon Distance (JSD) lies between 0 and 1.
+Furthermore, JSD follows a Chi-square distribution, which is a special case of Gamma distribution and hence belongs to exponential family of distributions.
+Therefore, we can fit a generalized linear model instead of a linear model to allow for the response variable to follow a Gamma distribution.
+The inverse link is used when we know that the mean response is bounded, which is applicable in our case since $0 \leq wpd_{raw}\leq 1$.
 
-We fit the Gamma generalized linear model with inverse link which is of the form:  
-$$y = 1/(a+b*log(x)) + e$$, where $y = median(wpd_{raw})$, $x = nx*nfacet$.
-Again, $wpd_{glm}$ which is a transformation on $wpd_{raw}$ and is designed to remove the effect of $nx*nfacet$ on $wpd_{raw}$ are chosen as the residuals and defined as
+We fit a Gamma generalized linear model with the inverse link which is of the form:  
+$$y = a+b*log(x) + e$$, where $y = median(wpd_{raw})$, $x = nx*nfacet$.
+Let $E(y) = \mu$ and $a + b*log(x) = g(\mu)$ where $g$ is the link function.
+Then $g(\mu)=  1/mu$ and $\hat \mu  = 1/(\hat a + \hat b log(x))$.
+The residuals from this model $(y-\hat y) = (y-1/(\hat a + \hat b log(x)))$ would be expected to have no dependency on $x$.
+Thus,  $wpd_{glm}$ is chosen as the residuals from this model and is defined as:
 $wpd_{glm} = wpd_{raw} - 1/(\hat a + \hat b*log(nx*nfacet))$.
@@
   geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
-  ylab("wpd_glm = 1/wpd_raw - a - b*log(nx*nfacet)")
+  ylab("wpd_glm = wpd_raw - 1/(a  + b*log(nx*nfacet))")
 ```
@@
              ),
-         wpd_glm_trans = ((wpd_glm*300)))
+         wpd_glm_scaled = ((wpd_glm*300)))
 
@@
 
-The measure $wpd_{glm}$ seems to roughly follow a normal distribution except in the tails as could be seen in Figure \ref{fig:hist-qq} and the very method of permutation approach ensures that $wpd_permutation$ is also normally distributed.
+The measure $wpd_{glm}$ has location 0 and standard deviation ~ 0.003, whereas the measure $wpd_{permutation}$ which is a z-score, has a normal distribution with location 0 and standard deviation 1.
+To bring them to the same scale, we have defined $wpd_{glm-scaled} = wpd_{glm}*300$, which brings the standard deviation of $wpd_{glm-scaled}$ to almost 1, without changing the location.
+
+The measure $wpd_{glm-scaled}$ seems to roughly follow a normal distribution except in the tails as could be seen in Figure \ref{fig:hist-qq} and the very method of permutation approach ensures that $wpd_permutation$ is also normally distributed.
 Further, they are brought to the similar scale and location and hence could be compared.
 
-```{r hist-qq, fig.cap = "In panel a, the histogram of $wpd_glm_trans$ is plotted.
-In parl b, the QQ plot is shown with the theoretical quantiles on the x-axis and $wpd_glm_trans$ quantiles on the y-axis.
+```{r hist-qq, fig.cap = "In panel a, the histogram of $wpd_{glm-scaled}$ is plotted.
+In parl b, the QQ plot is shown with the theoretical quantiles on the x-axis and $wpd_{glm-scaled}$ quantiles on the y-axis.
 The distribution looks symmetric and looks like normal except in the tails."}
 hist <- ggplot(G21_glm) +
-  geom_histogram(aes(x = wpd_glm_trans)) +
+  geom_histogram(aes(x = wpd_glm_scaled)) +
   ggtitle("a")
 
-p <- ggplot(G21_glm, aes(sample = wpd_glm_trans))
+p <- ggplot(G21_glm, aes(sample = wpd_glm_scaled))
 qqplot <-  p + geom_qq() + geom_qq_line() + coord_fixed(ratio = 4/5) +
@@
 #     ),
-#     wpd_glm_trans = 300*(wpd_glm))
+#     wpd_glm_scaled = 300*(wpd_glm))
 
- # G21_glm$wpd_glm_trans %>% 
+ # G21_glm$wpd_glm_scaled %>% 
  #   range()
@@
 
-```{r dist-new-same-scale-link, fig.cap="wpd_permutation and wpd_lm are in very different scale and could not be plotted together without transforming further.
-Whereas wpd_permutation and wpd_glm could be plotted together as they at least have the same location.
-Are they on the same scale though?
-Can they be compared?"}
-
+```{r dist-new-same-scale-link, fig.cap="w$pd_permutation$ and $wpd_{glm-scaled}$ are plotted together on the same scale.
+They also have the same location and hence the values from these two approaches could be compared across panels.
+$wpd_{glm-scaled}$ would be used to normalise $wpd_{raw}$ for higher $nx$ and $nfacet$ and $wpd_{glm-scaled}$ would be used for smaller levels to alleviate the problem of computational time."}
 # 
@@
                values_to = "value_estimate")
-G21_all_data$type_estimate = factor(G21_all_data$type_estimate , levels = c( "wpd_permutation", "wpd_glm_trans"))
+G21_all_data$type_estimate = factor(G21_all_data$type_estimate , levels = c( "wpd_permutation", "wpd_glm_scaled"))
 
 G21_all_data %>% 
-  filter(type_estimate %in% c("wpd_glm_trans", "wpd_permutation")) %>% 
+  filter(type_estimate %in% c("wpd_glm_scaled", "wpd_permutation")) %>% 
   ggplot() +
   geom_density(aes(x = value_estimate, 
-                   fill = type_estimate)) +
+                   fill = type_estimate), alpha = 0.5) +
   facet_grid(nx~nfacet,
@@
   theme(legend.position = "bottom") +
-  scale_fill_manual(values = c("#999999",  "#D55E00")) +
-  xlab("wpd_norm2")
+  scale_fill_manual(values = c( "#D55E00", "#0072B2")) +
+  xlab("wpd_norm2") +
+  scale_x_continuous(breaks = c(-5, -3, 0, 3, 5))
 
@@
 # G21_all_data %>%
-#   filter(type_estimate == c("wpd_glm_trans")) %>% 
+#   filter(type_estimate == c("wpd_glm_scaled")) %>% 
 #   select(value_estimate) %>% 
@@
 But the modeling approach would only have one value of $wpd_{raw}$ for a panel in practice, how to scale the values in the modeling approach so that they are within 0 and 1?
+Getting them to 0 and 1 is changing the location making the comparison difficult.
 
-```{r variance}
+```{r variance, eval = FALSE}
 #glm-wpd-sd

### 2021-02-21 choosing_significant_harmonies.Rmd
computing threshold

---
title: "choosing_best"
author: "Sayani Gupta"
date: "17/02/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(here)
```

# Choosing harmonies with significant wpd

In this section, we provide a method to select important harmonies by eliminating all harmonies for which patterns are not significant across x or facet categories through randomization test. Randomization tests (permutation tests)
generates a random distribution by re-ordering our observed data and allow to test if the observed data is significantly different from any random distribution. Complete randomness in the measured variable indicates that the process follows a homogeneous underlying distribution over the whole time series, which essentially implies there is no interesting distinction across any different categories of the cyclic granularities.

Typically, a randomization test involves calculating a test statistic, randomly shuffling the data and calculating the test statistic several times to obtain a distribution of the test statistic. We will use this procedure to test if there is any interesting pattern captured by the harmonies, which essentially implies if $wpd_{norm}$ is significantly different from zero. The percentages of times the $wpd_{norm}$ obtained from the permuted data is greater than or equal to the observed $wpd_{norm}$ is the p-value. The randomization test is described as follows:

<!-- <!-- We can remove the harmonies for which no interesting patterns are observed through a randomization permutation method. --> 
<!-- Essentially, the assumption is that under the null hypothesis, there is no difference in categories between the pair of cyclic granularities in the chosen harmony. This method is based on the generation of randomly chosen reassignments (permutations) of the data across different cyclic granularities and the computation of  -->
<!-- $wpd_{norm}$ for each of these reassignments. -->

<!-- **Assumption:** random permutation of the data keeping the categories of the cyclic granularities constant. -->

- **Input:** All harmonies of the form $\{(A, B), A = \{ a_j: j = 1, 2, \dots, J\}, B = \{ b_k: k = 1, 2, \dots, K\}\}$  with $A$ placed across x-axis and $B$ across facets $\forall (A, B) \in N_C$.

- **Output:** Harmony pairs $(A, B)$ for which $wpd_{norm}$ is significant.

1. Fix harmony pair $(A, B)$.

2. Given the data; $\{v_t: t=0, 1, 2, \dots, T-1\}$, the $wpd_{norm}$ is computed and is represented by $wpd_{obs}$.

3. From the original sequence a random permutation is obtained: $\{v_t^*: t=0, 1, 2, \dots, T-1\}$.

4. $wpd_{norm}$ is computed for the permuted sequence of the data and is represented by $wpd_{perm_1}$.

5.  Steps (3) and (4) are repeated a large number
of times M (M = 200).

6. For each permutation, one $wpd_{perm_i}$ is obtained. Define $wpd_{sample} = \{wpd_{perm_1}, wpd_{perm_2}, \dots, wpd_{perm_M}\}$.

7. Repeat Steps (1-6) for all harmony pairs.

8. $95^{th}$ percentile of $wpd_{sample}$ obtained for all harmony pairs is computed and stored in $wpd_{threshold}$.

7. If $wpd_{obs_{A, B}}> wpd_{threshold}$, harmony pair $(A, B)$ is selected, otherwise rejected.

Data generation:

We generate a data set from a N(0,1) distribution and simulate the cyclic granularity labels for levels  $\{2, 3, 5, 7, 14, 20, 31, 50\}$. We fix two categories at a time with levels $(i, j) \in  \{2, 3, 5, 7, 14, 20, 31, 50\}$ and compute $wpd_{sample}$ and repeat this for all categories to obtain $wpd_{threshold}$.

Size computation:

Perform the test described in the algorithm a large number
of times M (M = 200) and detect the number of times, in total, when harmonies are chosen to be significant, when in fact they are not. Here, we test the null hypotheses:

$H_0: wpd_{C_i, C_j} = 0 \forall (C_i, C_j) \in N_C$.

Since, multiple tests are done, the probability of type-1 error needs to be adjusted to incorporate this multiple testing problem.

```{r, eval = FALSE, echo = FALSE}
set.seed(12345)

# simulate one big data which will have all categories generated on the #fly

library(distributional)
sim_dist <- distributional::dist_normal(0,1)
sim_orig <-  distributional::generate(sim_dist, 50000)
sim_orig <- sim_orig[[1]]
lensim <- length(sim_orig)

simtable<-read_csv(here::here('simulations/sim_table/sim_table.csv'))

lapply(1:2, 
                           function(scen){

simj<-simtable[scen,] 
nfacetj<-simj$nfacet
nxj<-simj$nx
nperm = 20

id_x <- rep_len(seq_len(nxj), length.out = lensim) 
id_facet <- rep_len(seq_len(nfacetj), length.out = lensim)

sim_panel_orig <- bind_cols(id_x = id_x, id_facet = id_facet, sim_data = sim_orig)

wpd_orig = compute_pairwise_max(sim_panel_data, 
                                gran_x = "id_x",
                                gran_facet = "id_facet",
                                response = sim_data)

wpd_sample <- lapply(seq_len(nperm), function(x){

  sample_data <- sample(sim_orig, size =  lensim)

  sim_panel_sample <- bind_cols(id_x = id_x, 
                                id_facet = id_facet, 
                                sim_data = sample_data)

  wpd =  compute_pairwise_max(sim_panel_sample, 
                              gran_x = "id_x",
                              gran_facet = "id_facet",
                              response = sim_data) %>% 
    as_tibble() %>% mutate(perm_id = x)

}) %>% bind_rows()

wpd_all <- wpd_orig %>% as_tibble() %>% 
  mutate(perm_id = 0) %>% 
  bind_rows(wpd_sample)

saveRDS(wpd_all,
        paste0('simulations/supplementary/test/wpd_N01/data-ind/',
               nxj,'-',
               #"nfacetj-",
               nfacetj,"-",
               '-wpd-test.rds'))
})
```

The p-value of the design $D_{null}$ is size.
The p-value of other designs is power.
Confidence interval of the

The p-value is almost always greater than 0.05, which means there is no significant differences between the different categories, which is true from the simulation design.

```{r size}
library(readr)
library(tidyverse)
data_N01 <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds"))

data_N01_obs <- data_N01 %>% filter(perm_id==1)
data_N01_samp <- data_N01 %>% filter(perm_id!=1)

#plot_mmpd_null_grid(data_N01_samp, data_N01_obs)

mmpd_dist_null_grid  = data_N01_samp

mmpd_null_orig = data_N01_obs
compute_p_value <- left_join(mmpd_dist_null_grid, mmpd_null_orig,
                               by = c("nx", "nfacet")) %>% 
    group_by(nx, nfacet) %>% 
    summarise(p_value = sum(if_else(abs(value.x)>abs(value.y),1,0))/n(), .groups = 'drop')

  ggplot() + 
    geom_histogram(data = mmpd_dist_null_grid, aes(x = value))  + 
    geom_vline(data = mmpd_null_orig, aes(xintercept = value),colour = "red") +
    geom_text(data = round(compute_p_value, 3), size = 3,  
              aes(x = -Inf,
                  y =  Inf,
                  label = paste("p-value:",p_value),
                  hjust   = 0,
                  vjust   = 1)) + 
    facet_grid(nx ~ nfacet)
```

```{r power}
library(readr)
library(tidyverse)
data_N01 <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds"))

data_N01_obs <- data_N01 %>% filter(perm_id==1)
data_N01_samp <- data_N01 %>% filter(perm_id!=1)

#plot_mmpd_null_grid(data_N01_samp, data_N01_obs)

mmpd_dist_null_grid  = data_N01_samp

mmpd_null_orig = data_N01_obs
compute_p_value <- left_join(mmpd_dist_null_grid, mmpd_null_orig,
                               by = c("nx", "nfacet")) %>% 
    group_by(nx, nfacet) %>% 
    summarise(p_value = sum(if_else(abs(value.x)>abs(value.y),1,0))/n(), .groups = 'drop')

  ggplot() + 
    geom_histogram(data = mmpd_dist_null_grid, aes(x = value))  + 
    geom_vline(data = mmpd_null_orig, aes(xintercept = value),colour = "red") +
    geom_text(data = round(compute_p_value, 3), size = 3,  
              aes(x = -Inf,
                  y =  Inf,
                  label = paste("p-value:",p_value),
                  hjust   = 0,
                  vjust   = 1)) + 
    facet_grid(nx ~ nfacet)
```

### 2021-02-21 paper/main.Rmd
computing threshold
changing normalisation section

--- 2021-02-10 paper/main.Rmd
@@
 ---
-title: Selecting and ranking interesting pairs of cyclic temporal granularities
+title: An automatic approach to find all possible calendar effects (periodic patterns) for an univariate time series
 authors:
@@
 
-# The proposed distance measure
+# The distance measure for quantifying patterns in harmonies
 
@@
 Display b and c are more interesting than a since there is a change in distribution either across facets(b) or x-axis(a).
-Display d is most interesting as distribution of the rv changes across both facet and x-axis variable."}
-
-sim_varf_dist1 = function(nx, nfacet){
-  rep(dist_normal(seq(mean,mean*nfacet, by = mean), sd), each = nx)}
+Display d is most interesting as distribution of the rv changes across both facet and x-axis variable.", eval = FALSE}
+
+# sim_varf_dist1 = function(nx, nfacet){
+#   rep(dist_normal(seq(mean,mean*nfacet, by = mean), sd), each = nx)}
 
@@
 
-## Definition of the proposed distance measure
+## Definition of the distance measure
 
@@
 From Section \ref{sec:idea}, the idea is to put more weights on within-facet distances than between-facet distances.
-Hence, for a suitable tuning parameter $\lambda > 1$, the pairwise distances $d_{(jk, j'k')}$ are transformed based on the distance type as follows:
+Hence, for a suitable tuning parameter $0<\lambda<1$, the pairwise distances $d_{(jk, j'k')}$ are transformed based on the distance type as follows:
 
@@
 The maximum weighted pairwise distances are defined as:
-$$WPD = max_{j, j', k, k'}(d*_{(jk), (j'k')})
+$$wpd = max_{j, j', k, k'}(d*_{(jk), (j'k')})
 \forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}$$.
@@
 
-# Normalisation
-
-The distribution of wpd is different for different levels of facets and x-axis levels.
-This is because the statistic maximum which is used to define wpd is affected by the number of categories.
-The measure would have higher values if $C_i$ or $C_j$ has higher levels.
-However, we would ideally want a higher value of the measure only if there is significant difference between distributions across facet or x-axis categories, and not because the number of categories are higher.
-Therefore, in order to compare wpd across different combinations of facet and x-axis levels, we need to eliminate the impact of different levels of the facets and x-axis first and get a normalized measure.
-Henceforth we call the measure already discussed as $wpd_{raw}$ and the normalised measure as $wpd_{norm}$.
-The measure $wpd_{norm}$ could potentially lead to comparison of the measure across different panels and also identifying only the interesting panels from a data set.
-In the coming section, we have discussed two approaches to normalisation both through simulations.
-
-## Simulation study
-
-Most of the behavior of the measure wpd was studied via simulation.
-The simulations explore how wpd performs under various designs and parameters and its limitations.
-To study the behavior of wpd, simulations were carried out for four different designs and the following factors that could potentially have an impact on the values of wpd:
-
-<!-- Numerous simulations were carried out in a wide range of scenarios. -->
-
-<!-- Same scenarios were used, when possible with normalized wpd, keeping all other simulation variables constant. -->
+## Properties of the distance measure
+
+A simulation study is carried out to explore how $wpd$ performs under various designs, its parameters and limitations.
+To this end, simulations were carried out for four different designs and the following factors that could potentially have an impact on the values of $wpd$:
 
@@
 - $n$ (sample size for each combination of categories)
-- $nsim$ (number of simulations)a
+- $nsim$ (number of simulations)
 - $nperm$ (number of permutations of data)  
@@
 
-## Simulation environment
-
-R version 4.0.1 (2020-06-06) is used with platform: x86_64-apple-darwin17.0 (64-bit) running under: macOS Mojave 10.14.6 and MonaRCH, which is a next-generation HPC/HTC Cluster, designed from the ground up to address the computing needs of the Monash HPC community.
-The nodes and the storage used are as follows:
+Results are presented in two parts.
+The dependence of $wpd$ on $nx$ and $nfacet$ under $D_{null}$ is presented here, which lays the foundation for the next section.
+The rest of the results that discusses the relationship of the $wpd$ with other factors is presented in the Supplementary section of the paper.
+
+### Design of the simulation study
+
+Observations are generated from a Gamma(2,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
+Each combination is being referred to as a _panel_.
+That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$.
+For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
+That is, if we consider the panel  $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
+The values of $\lambda$ is set to $0.67$ and values of raw wpd $wpd$ is obtained.
+This entire design applies to the null cases and hence there is no difference in distribution between any categories in the panel.
+
+### Results
+
+Figure \ref{fig:raw} shows the distribution of $wpd$ plotted across different nx and nfacet categories.
+Both shape and scale of the distributions change across panels.
+This is not desirable as it would mean we would not be able to compare $wpd$ across different $nx$ and $nfacet$ as each of them are drawn from distributions with different locations and scale.
+In Figure \ref{fig:quadratic}, we see how the median of $wpd_{raw}$ varies with the total number of distances $nx*nfacet$ for each panel.
+The median increases abruptly for lower values of $nx*nfacet$ and slowly for higher $nx*nfacet$.
+
+```{r raw, fig.cap = "Distribution of raw wpd is plotted across different nx and nfacet categories. Both shape and scale of the distribution changes for different nx and nfacet categories."}
+G21 <- read_rds("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds")
+
+G21 %>% 
+  ggplot(aes(x = value)) + 
+  geom_density(fill = "blue") +
+  facet_grid(nx~nfacet,
+             labeller = "label_both") + 
+  scale_x_continuous(breaks = scales::breaks_extended(3)) + 
+  xlab("raw wpd")
+```
+
+```{r quadratic, fig.cap = "$wpd_{raw}$ is plotted against nx*nfacet and the blue line represents the median of the multiple values for each nx*nfacet levels."}
+G21 %>% 
+  ggplot(aes(x=nx*nfacet, y = value)) +
+  geom_point() + stat_summary(fun=median, geom="line", aes(group=1), color = "blue") + xlab("nx*nfacet") + ylab("raw wpd")
+
+```
+
+# Normalisation of the distance measure
+
+The distribution of wpd is different for different levels of facets and x-axis levels.
+This is because the statistic maximum which is used to define $wpd$ is affected by the number of categories.
+The measure would have higher values if $A$ or $B$ has higher levels.
+However, we would ideally want a higher value of the measure only if there is significant difference between distributions across facet or x-axis categories, and not because the number of categories $J$ or $K$ is high.
+Therefore, in order to compare $wpd$ across different combinations of facet and x-axis levels, we need to eliminate the impact of different levels of the facets and x-axis first and get a normalized measure.
+Henceforth we call the measure already discussed as $wpd_{raw}$ and the normalized measure as $wpd_{norm}$.
+The measure $wpd_{norm}$ could potentially lead to comparison of the measure across different panels and also identifying only the interesting panels from a data set.
+We discuss two approaches for normalization, both of which are based on the simulation results conducted in the earlier section.
+
+<!-- The nodes and the storage used are as follows: -->
 
@@
 
-### Notations
-
-Let $\{nx_{i}, i = 1, 2, \dots, nx\}$, $\{nfacet_{j}, j = 1, 2, \dots, nfacet\}$ be the set of x-axis and facet categories respectively.
+We need a transformation on ${wpd}$ which will make it independent of the values of $nx*nfacet$.
+Two approaches have been employed for that purpose, the first one involves fitting a model and the latter involves a permutation method to make the distribution of the transformed $wpd$ similar across different $nx$ and $nfacet$.
+
+<!-- ### Notations -->
+
+<!-- Let $\{nx_{i}, i = 1, 2, \dots, nx\}$, $\{nfacet_{j}, j = 1, 2, \dots, nfacet\}$ be the set of x-axis and facet categories respectively.
 Each combination of $nx_{i}$ and $nfacet_{j}$is being referred to as a _panel_.
@@
 Hence, for each of those $k$ panel, we have $nsim$ values of $wpd_{raw}$.
-
-### Data generation
-
-Observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
-That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$.
-For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
-That is, if we consider the panel  $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
-The value of $\lambda$ is set to $0.67$.
-$nsim = 200$, which means each of these scenarios are run $200$ times by permuting the data in each of the panels.
-And hence $200$ values of $wpd_{raw}$ are obtained for each of those 64 panels.
+-->
 
@@
 
-The permutation approach ensures that the distribution of the normalised weighted pairwise distance measure has the same mean and standard deviation across all combinations of $nx_i$ and $nfacet_j$.
-Thus, the normalised distances is computed as follows: $x^{norm}_{k} =  (x_{k} - mean_l(x_{k,l}))/sd_l(x_{k, l})$,  $x^{norm}_{k}$ is the value of the $wpd_{norm}$ for the $k^{th}$ panel.
-
-While this works successfully to make the mean and standard deviation across different nx and nfacet (as seen in Figure \ref{fig:}), it is computationally heavy and time consuming, and hence less user friendly when being actually used in practice.
-Hence, we propose another approach to normalisation which is more approximate than exact but still has the same accuracy when compared to the permutation approach.
+The permutation approach ensures that the distribution of the normalized distance measure has the same mean and standard deviation across all combinations of $nx_i$ and $nfacet_j$.
+The normalized distances through permutation is computed as follows: $x^{perm}_{k} =  (x_{k} - mean_l(x_{k,l}))/sd_l(x_{k, l})$,  $x^{perm}_{k}$ is the value of the $wpd_{perm$ for the $k^{th}$ panel.
+Standardizing the variable $wpd_{perm}$ in this approach leads to $location = 0$ and $scale = 1$ for this variable.
+
+While this works successfully to make the mean and standard deviation across different $nx$ and $nfacet$ (as seen in Figure \ref{fig:}), it is computationally heavy and time consuming, and hence less user friendly when being actually used in practice.
+Hence, we propose another approach to normalization which is more approximate than exact but still has the same accuracy when compared to the permutation approach.
+
+*incorporate from the document combining_normalisation_method.Rmd*
 
@@
 
-This section reports the results of a simulation study that was carried out to evaluate the
-behavior of our distance measure across all potential factors.
+This section reports the results of a simulation study that was carried out to evaluate the behavior of our distance measure across all potential factors.
 The results are reported in two parts: for the a) raw measure and then b) normalised one to show how the loopholes for the raw measures were removed using the normalized ones.
@@
 
-# Choosing harmonies with significant wpd
+## Simulation environment
+
+Simulation studies were carried out to study the behavior of $wpd$, build the normalization method as well as compare and evaluate different normalization approaches.
+R version 4.0.1 (2020-06-06) is used with the platform: x86_64-apple-darwin17.0 (64-bit) running under: macOS Mojave 10.14.6 and MonaRCH, which is a next-generation HPC/HTC Cluster, designed from the ground up to address the computing needs of the Monash HPC community.
+
+# Ranking and selecting significant harmonies
 
@@
 
-# Application {#sec:application}
-
-<!-- ## Smart meter data of Australia {#sec:smartmeter} -->
-
-<!-- # how data looks -->
-
-Clustering of electricity customers based on their consumption behavior facilitate effective market segmentation and hence better management and pricing.
-Electricity demand time series are the primary source of information of customers' consumption behavior.
-Due to technological developments, smart meters could provide large quantities of measurements on energy usage at more and more finer time intervals.
-Due to this extreme dimensionality along time of the demand data, it is a challenge to have clustering methods which could reduce the dimensionality to produce distinct clusters.
-One of the potential solutions is time series feature extraction.
-However, it is limited by the type of noisy, patchy and unequal time series that is very common in data sets of any residential customers.
-The idea is to choose similarity measures, which do not lose the core characteristic information of demand across different time deconstructions in aggregation processes and is robust against asynchronous or incomplete time series.
-
-We use the data from one of the customer trials [@smart-meter] conducted as part of the Smart Grid Smart City project in Newcastle, New South Wales and some parts of Sydney.
-The data has customer wise data on energy consumption for every half hour from February 2012 to March 2014.
-<!--It would be interesting to explore the energy consumption distribution for these customers and gain insights on their energy behavior which are lost either due to aggregation or looking only at coarser temporal units.--> The idea here is to
-use our similarity measure and show improved cluster distinction as compared to baseline feature based approaches.
-A data set of 100 homes is used to evaluate both approaches.
-This is different to deterministic segmentation which attempts to characterise load as a function of a fixed number of parameters, such as occupancy or types of appliances, and use those parameters for classification.
-We only use their load patterns across time deconstructions to define the similarity measure.
-
-<!-- Write about common load clustering methods -->
-
-### Multidimensional scaling and cluster analysis
-
-Cluster analysis and multidimensional scaling (MDS) methods are used to explore the temporal structure of various households, their interrelations and determine similar behaving clusters of households in this study.
-MDS methods are used to produce a lower dimensional display space where each household is represented by a point and the distance between these points give the measure of similarity between these households.
-On the other hand, clustering techniques are used to provide information about the clustering structure of the households.
-Households that are in the same cluster can be considered to be more similar, while households are more dissimilar in their energy behavior across one or few temporal deconstructions.
-
-$wpd_norm$ is considered as the measure of similarity or dissimilarity while using MDS and clustering techniques.
-$wpd_norm$ could be constructed for each pair of harmony for each household and then similarity could be measured across single or all harmonies together.
-
-```{r mds}
-set.seed(7777)
-library(gravitas)
-library(tsibble)
-library(lubridate)
-library(readr)
-
-all_data <- read_rds(here("paper/sim_table/all_data.rds"))
-sm_cust_data <- read_rds(here("paper/data/sm_cust_data.rds")) %>% 
-  as_tsibble(index = reading_datetime,
-             key = customer_id)
-
-sm_unique_cust <- sm_cust_data %>% distinct(customer_id)
-
-#sm_30 <- sample(sm_unique_cust$customer_id, 30)
-sm_cust_samp <- sm_cust_data %>% 
-  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
-  filter(year(reading_datetime) == 2012)  %>% 
-  create_gran("day_week") %>% 
-  create_gran("hour_day")
-
-#all_data <- write_rds(all_data, "paper/sim_table/all_data.rds")
-
-facet_variable = "day_week"
-x_variable = "hour_day"
-
-one_harmony_data <- all_data %>%
-  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
-  filter(facet_variable == "day_week",
-                    x_variable == "hour_day") %>% 
-  mutate(customer_id = as.character(customer_id))
-
-mds<- one_harmony_data %>%
-  select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
-  dist() %>%          
-  cmdscale() %>%
-  as_tibble()
-
-colnames(mds) <- c("Dim.1", "Dim.2")
-rownames(mds) <- unique(one_harmony_data$customer_id)
-mds <- mds %>%
-  mutate(customer_id = as.character(unique(one_harmony_data$customer_id))) %>%
-  select((customer_id)
-         , Dim.1, Dim.2)
-```
-
-```{r clustering}
-# K-means clustering
-clust <- kmeans(mds, 3)$cluster %>%
-  as.factor()
-mds <- mds %>%
-  mutate(groups = clust)
-
-# Plot and color by groups
-ggpubr::ggscatter(mds, x = "Dim.1", y = "Dim.2", 
-          label = rownames(mds),
-          color = "groups",
-          palette = "jco",
-          size = 1, 
-          ellipse = TRUE,
-          ellipse.type = "convex",
-          repel = TRUE)
-
-```
-
-# check transformation and scalar approaches are same
-
-```{r scalar-approach}
-set.seed(7777)
-all_data <- read_rds("paper/sim_table/all_data_scalar.rds")
-sm_cust_data <- read_rds("paper/data/sm_cust_data.rds")
-set.seed(7777)
-sm_unique_cust <- sm_cust_data %>% distinct(customer_id)
-sm_cust_samp <- sm_cust_data %>% 
-  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
-  #filter(year(reading_datetime) == 2012) %>% #for demo just show one column
-  as_tsibble(index = reading_datetime,
-             key = customer_id) %>% 
-  create_gran("day_week") %>% 
-  create_gran("hour_day")
-
-#all_data <- write_rds(all_data, "paper/sim_table/all_data.rds")
-
-facet_variable = "day_week"
-x_variable = "hour_day"
-
-one_harmony_data <- all_data %>%
-  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
-  filter(facet_variable == "day_week",
-         x_variable == "hour_day") %>% 
-  mutate(customer_id = as.character(customer_id))
-
-mds<- one_harmony_data %>%
-  select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
-  dist() %>%          
-  cmdscale() %>%
-  as_tibble()
-
-colnames(mds) <- c("Dim.1", "Dim.2")
-rownames(mds) <- unique(one_harmony_data$customer_id)
-mds <- mds %>%
-  mutate(customer_id = as.character(unique(one_harmony_data$customer_id))) %>%
-  select((customer_id)
-         , Dim.1, Dim.2)
-
-ggpubr::ggscatter(mds,
-                  x = "Dim.1",
-                  y = "Dim.2", 
-                  label = rownames(mds),
-                  size = 1,
-                  repel = TRUE)
-
-# clustering as well
-
-d = one_harmony_data %>%
-  select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
-  dist()
-
-hc = stats::hclust(d,method="complete")
-plot(hc)
-groups<-cutree(hc, k=4)
-
-all_data_cluster <- cbind(one_harmony_data, groups) %>% 
-  left_join(mds, by = "customer_id") %>% 
-  mutate(groups = as.factor(groups))
-
-ggpubr::ggscatter(all_data_cluster,
-                  x = "Dim.1",
-                  y = "Dim.2", 
-                  label = rownames(mds),
-                  color = "groups",
-                  size = 1,
-                  repel = TRUE)
-
-```
-
-10018272 is a customer from cluster 3, for which hour_day/wknd-wday comes after wknd-wday/day-month as opposed to 10006414 (cluster 1) for whom the direction is reversed.
-
-```{r}
-
-10006414
-
-all_data %>% 
-  filter(customer_id ==  10006414) %>% 
-  arrange(-wpd_norm)
-
-sm_cust_data %>% 
-  filter(customer_id ==  10006414) %>% 
-  prob_plot("hour_day",
-            "wknd_wday",
-            plot_type = "quantile",
-            quantile_prob = c(0.5),
-            symmetric = FALSE,
-            response = "general_supply_kwh")
-
-sm_cust_data %>% 
-  filter(customer_id ==  10006414) %>% 
-  prob_plot("hour_day",
-            "day_week",
-            plot_type = "quantile",
-            quantile_prob = c(0.5),
-            symmetric = FALSE,
-            response = "general_supply_kwh")
-
-all_data %>% 
-  filter(customer_id ==  10007340) %>% 
-  arrange(-wpd_norm)
-
-sm_cust_data %>% 
-  filter(customer_id ==  10007340) %>% 
-  prob_plot("day_month",
-            "day_week",
-            plot_type = "quantile",
-            quantile_prob = c(0.5),
-            symmetric = FALSE,
-            response = "general_supply_kwh")
-
-sm_cust_data %>% 
-  filter(customer_id ==  10007340) %>% 
-  prob_plot("hour_day",
-            "day_month",
-            plot_type = "quantile",
-            quantile_prob = c(0.5),
-            symmetric = FALSE,
-            response = "general_supply_kwh")
-
-all_data %>% 
-  filter(customer_id ==  10018272) %>% 
-  arrange(-wpd_norm)
-
-```
-
-```{r}
-raw_data <- sm_cust_data %>% 
-  left_join(mds, by = "customer_id")
-
-p1 <- raw_data %>% 
-  filter(groups==1) %>% 
-  ggplot() + 
-  geom_line(aes(x = reading_datetime,
-            y = general_supply_kwh)
+# Application in residential smart meter data {#sec:application}
+
+```{r household2and4}
+id2_tsibble <- elec %>% 
+   filter(id == 2) %>% 
+   as_tsibble(index = date_time)
+
+id4_tsibble <- elec %>% 
+   filter(id == 4) %>% 
+   as_tsibble(index = date_time)
+
+harmonies2 <- id2_tsibble %>%
+  harmony(
+    ugran = "month",
+    filter_in = "wknd_wday",
+    filter_out = c("hhour", "fortnight")
   )
 
-p2 <- raw_data %>% 
-  filter(groups==2) %>% 
-  ggplot() + 
-  geom_line(aes(x = reading_datetime,
-            y = general_supply_kwh)
+harmonies4 <- id4_tsibble %>%
+  harmony(
+    ugran = "month",
+    filter_in = "wknd_wday",
+    filter_out = c("hhour", "fortnight")
   )
 
-p3 <- raw_data %>% 
-  filter(groups==3) %>% 
-  ggplot() + 
-  geom_line(aes(x = reading_datetime,
-            y = general_supply_kwh)
+library(tictoc)
+tic()
+
+all_harmony2 <- hakear::select_harmonies(id2_tsibble,
+   harmony_tbl = harmonies2,
+   response = kwh,
+   nperm = 200,
+   nsamp = 200
  )
-library(patchwork)
-p1/p2/p3
-
-```
-
-```{r}
-raw_data <- sm_cust_data %>% 
-  left_join(mds, by = "customer_id")
-
-p1 <- raw_data %>% 
-  filter(groups==1) %>% 
-  prob_plot("day_week",
-            "hour_day",
-            response = "general_supply_kwh",
-            plot_type = "quantile",
-            symmetric = FALSE
+
+toc()
+
+library(tictoc)
+tic()
+all_harmony4 <- hakear::select_harmonies(id2_tsibble,
+   harmony_tbl = harmonies2,
+   response = kwh,
+   nperm = 200,
+   nsamp = 20
  )
-
-p2 <- raw_data %>% 
-  filter(groups==2) %>% 
-  prob_plot("day_week",
-            "hour_day",
-            response = "general_supply_kwh",
-            plot_type = "quantile",
-            symmetric = FALSE
-)
-
-p3 <- raw_data %>% 
-  filter(groups==3) %>% 
-  prob_plot("day_week",
-            "hour_day",
-            response = "general_supply_kwh",
-            plot_type = "quantile",
-            symmetric = FALSE
-)
-library(patchwork)
-p1
-p2
-p3
-
-```
-
-```{r hour-day-day-month, eval = FALSE}
-
-set.seed(7777)
-library(gravitas)
-library(tsibble)
-library(lubridate)
-library(readr)
-
-all_data <- read_rds("sim_table/all_data.rds")
-sm_cust_data <- read_rds("data/sm_cust_data.rds")
-sm_unique_cust <- sm_cust_data %>% distinct(customer_id)
-
-#sm_30 <- sample(sm_unique_cust$customer_id, 30)
-sm_cust_samp <- sm_cust_data %>% 
-  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
-  filter(year(reading_datetime) == 2012) %>% #for demo just show one column
-  as_tsibble(index = reading_datetime,
-             key = customer_id) %>% 
-  create_gran("wknd_wday") %>% 
-  create_gran("week_month")
-
-#all_data <- write_rds(all_data, "paper/sim_table/all_data.rds")
-
-facet_variable = "wknd_wday"
-x_variable = "week_month"
-
-one_harmony_data <- all_data %>%
-  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
-  filter(facet_variable == "wknd_wday",
-                    x_variable == "week_month") %>% 
-  mutate(customer_id = as.character(customer_id))
-
-mds<- one_harmony_data %>%
-  select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
-  dist() %>%          
-  cmdscale() %>%
-  as_tibble()
-
-colnames(mds) <- c("Dim.1", "Dim.2")
-rownames(mds) <- unique(one_harmony_data$customer_id)
-mds <- mds %>%
-  mutate(customer_id = as.character(unique(one_harmony_data$customer_id))) %>%
-  select((customer_id)
-         , Dim.1, Dim.2)
-
-clust <- kmeans(mds, 3)$cluster %>%
-  as.factor()
-mds <- mds %>%
-  mutate(groups = clust)
-
-# Plot and color by groups
-ggpubr::ggscatter(mds, x = "Dim.1", y = "Dim.2", 
-          label = rownames(mds),
-          color = "groups",
-          palette = "jco",
-          size = 1, 
-          ellipse = TRUE,
-          ellipse.type = "convex",
-          repel = TRUE)
-
-```
-
-### Advantage over taditional feature based methods
-
-Since probability distribution of the load is considered across different cyclic granularity, there is no discarding of valuable data that might result from bringing all customers to the same time horizon.
-Moreover, since our metric is based on probability distribution, it will not be sensitive to outlier days and hence the clustering process will not be biased.
-Moreover, feature extraction applies to all days for all customers at once and therefore does not support parallel computing.
-Our metric is computed for each household separately and can even run for each each harmonies separately and thus fits well into the parallel computing framework.
-
-### Write the method in notations
-
--  notation of time series for each customer
--  wpd
--  harmonies
--  cluster
-
-### Distinction, repeatability, and robustness metrics
-
-### Putting similar households on linear scale
+toc()
+
+```
 

### 2021-02-21 choosing_significant_harmonies.Rmd
restructure section on normalisation

@@
 library(here)
+library(hakear)
+library(tidyr)
+library(distributional)
+library(dplyr)
+library(ggplot2)
 ```
@@
 In this section, we provide a method to select important harmonies by eliminating all harmonies for which patterns are not significant across x or facet categories through randomization test.
-Randomization tests (permutation tests)
-generates a random distribution by re-ordering our observed data and allow to test if the observed data is significantly different from any random distribution.
+Randomization tests (permutation tests) generates a random distribution by re-ordering our observed data and allow to test if the observed data is significantly different from any random distribution.
 Complete randomness in the measured variable indicates that the process follows a homogeneous underlying distribution over the whole time series, which essentially implies there is no interesting distinction across any different categories of the cyclic granularities.
@@
 ```
+
+```{r varall}
+
+sim_varall_normal <- function(nx, nfacet, mean, sd, w) {
+  dist_normal((mean + seq(0,
+    (nx *
+      nfacet - 1),
+    by = 1
+  ) * w), sd)
+}
+sim_panel_varall <- sim_panel(
+  nx = 2, nfacet = 3,
+  ntimes = 500,
+  sim_dist = sim_varall_normal(2, 3, 0, 1, 10)
+) %>% unnest(data)
+
+set.seed(9999)
+varall <- compute_pairwise_norm(sim_panel_varall, 
+                           gran_x = "id_x",
+                           gran_facet = "id_facet",
+                           response = sim_data, 
+                           nperm = 200
+)
+
+# plot
+p_varall <- sim_panel_varall %>%
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
+```
+
+```{r varx}
+sim_varx_normal <- function(nx, nfacet, mean, sd, w) {
+   rep(dist_normal((mean + seq(0, nx - 1, by = 1) * w), sd), nfacet)
+ }
+
+sim_panel_varx <- sim_panel(
+   nx = 2, nfacet = 3,
+   ntimes = 5,
+   sim_dist = sim_varx_normal(2, 3, 0, 1, 10)
+ ) %>% unnest(data)
+
+set.seed(9999)
+varx <- compute_pairwise_norm(sim_panel_varx, 
+                           gran_x = "id_x",
+                           gran_facet = "id_facet",
+                           response = sim_data, 
+                           nperm = 200
+)
+
+# plot
+p_varx <- sim_panel_varx %>%
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
+```
+
+```{r varf}
+sim_varf_normal <- function(nx, nfacet, mean, sd, w) {
+  rep(dist_normal((mean + seq(0, nfacet - 1, by = 1) * w), sd), each = nx)
+}
+sim_panel_varf <- sim_panel(
+  nx = 2, nfacet = 3,
+  ntimes = 5,
+  sim_dist = sim_varf_normal(2, 3, 0, 1, 10)
+) %>% unnest(data)
+
+set.seed(9999)
+varf <- compute_pairwise_norm(sim_panel_varf, 
+                           gran_x = "id_x",
+                           gran_facet = "id_facet",
+                           response = sim_data, 
+                           nperm = 200
+)
+
+p_varf <- sim_panel_varf %>%
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
+```
+
+```{r null}
+sim_panel_null <- sim_panel(
+   nx = 2,
+   nfacet = 3,
+   ntimes = 500,
+   sim_dist = distributional
+   ::dist_normal(0, 1)
+) %>% unnest(c(data))
+
+set.seed(9999)
+
+null <- compute_pairwise_norm(sim_panel_null, 
+                           gran_x = "id_x",
+                           gran_facet = "id_facet",
+                           response = sim_data, 
+                           nperm = 200
+)
+
+p_null <- sim_panel_null %>%
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
+```

### 2021-02-21 paper/main.Rmd
Added lm and glm results

@@
 
-## Definition of the distance measure
+## Definition
 
@@
 
-## Properties of the distance measure
+## Properties
 
@@
 The measure $wpd_{norm}$ could potentially lead to comparison of the measure across different panels and also identifying only the interesting panels from a data set.
-We discuss two approaches for normalization, both of which are based on the simulation results conducted in the earlier section.
+We discuss two approaches for normalization, both of which are based on the simulation results.
 
 <!-- The nodes and the storage used are as follows: -->
+
+## Simulation environment
+
+Simulation studies were carried out to study the behavior of $wpd$, build the normalization method as well as compare and evaluate different normalization approaches.
+R version 4.0.1 (2020-06-06) is used with the platform: x86_64-apple-darwin17.0 (64-bit) running under: macOS Mojave 10.14.6 and MonaRCH, which is a next-generation HPC/HTC Cluster, designed from the ground up to address the computing needs of the Monash HPC community.
 
@@
 The permutation approach ensures that the distribution of the normalized distance measure has the same mean and standard deviation across all combinations of $nx_i$ and $nfacet_j$.
-The normalized distances through permutation is computed as follows: $x^{perm}_{k} =  (x_{k} - mean_l(x_{k,l}))/sd_l(x_{k, l})$,  $x^{perm}_{k}$ is the value of the $wpd_{perm$ for the $k^{th}$ panel.
+The normalized distances through permutation is computed as follows: $x^{perm}_{k} =  (x_{k} - mean_l(x_{k,l}))/sd_l(x_{k, l})$,  $x^{perm}_{k}$ is the value of the $wpd_{perm}$ for the $k^{th}$ panel.
 Standardizing the variable $wpd_{perm}$ in this approach leads to $location = 0$ and $scale = 1$ for this variable.
@@
 ### Modelling approach
+
+_Linear model_
 
@@
 
-```{r linear-model}
+```{r linear-model,message=FALSE}
 G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds"))
@@
 <!-- from $nx_{i}$ x-categories and $nfacet_{j}$ facet-categories is $nx_{i}*nfacet_{j}$ and  -->
+
+_Generalised linear model_
+
+In the linear model approach, $wpd_{raw} \in R$ was assumed, whereas, $wpd_{raw}$, Jensen-Shannon Distance (JSD) lies between 0 and 1.
+Furthermore, JSD follows a Chi-square distribution, which is a special case of Gamma distribution and hence belongs to exponential family of distributions.
+Therefore, we can fit a generalized linear model instead of a linear model to allow for the response variable to follow a Gamma distribution.
+The inverse link is used when we know that the mean response is bounded, which is applicable in our case since $0 \leq wpd_{raw}\leq 1$.
+
+We fit a Gamma generalized linear model with the inverse link which is of the form:  
+$$y = a+b*log(x) + e$$, where $y = median(wpd_{raw})$, $x = nx*nfacet$.
+Let $E(y) = \mu$ and $a + b*log(x) = g(\mu)$ where $g$ is the link function.
+Then $g(\mu)=  1/mu$ and $\hat \mu  = 1/(\hat a + \hat b log(x))$.
+The residuals from this model $(y-\hat y) = (y-1/(\hat a + \hat b log(x)))$ would be expected to have no dependency on $x$.
+Thus,  $wpd_{glm}$ is chosen as the residuals from this model and is defined as:
+$wpd_{glm} = wpd_{raw} - 1/(\hat a + \hat b*log(nx*nfacet))$.
+
+<!-- Please note: -->
+
+<!-- - subtracting the intercept brings the location of the transformed variable to 0 for either case -->
+<!-- - heterogeneity is higher for this case after normalization as compared to the earlier one. -->
+
+```{r wpd-glm-horizontal, echo = FALSE, message=FALSE, fig.caption = "$wpd_{glm}$ is plotted against log(nx*nfacet) and this transformation leads to the median of $wpd_{glm}$ to have no relationship with log(nx*nfacet)"}
+
+G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds"))
+
+G21_median <- G21 %>% 
+  group_by(nx*nfacet) %>% 
+  summarise(actual = median(value))
+
+glm_fit <- glm(actual ~ log(`nx * nfacet`),
+              family = Gamma(link = "inverse"),
+              data = G21_median)
+
+intercept <- glm_fit$coefficients[1]
+slope <- glm_fit$coefficients[2]
+
+G21_sd  = G21 %>% 
+    mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
+    )
+    )
+    ))
+
+scale_fac <- 1/G21_sd$wpd_glm %>% sd()
+
+# checking the fit of the residuals from glm fit
+
+# fitted_glm <- fitted(glm_fit, type = "response")
+# residuals <- residuals.glm(glm_fit, type = "response")
+# hist(residuals)
+
+#h = augment(glm_fit)
+# ggplot(h) +
+#   geom_histogram(aes(x = .resid))
+
+# residual <- G21_median$actual  - fitted_glm
+# 
+# hist(residual)
+
+G21 %>% 
+  ggplot(aes(x=log(nx*nfacet),
+             y = (value - (1/(intercept + slope*log(nx*nfacet)
+                    )
+                    )
+             )
+  )
+  ) +
+  geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
+  ylab("wpd_glm = wpd_raw - 1/(a  + b*log(nx*nfacet))")
+```
+
+```{r wpd-glm-dist, fig.cap = " The distribution of $wpd_{glm}$ is plotted. The distributions are more similar across higher nx and nfacet and dissimilar for fewer nc and nfacets."}
+
+G21_glm <- G21 %>% 
+  mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
+                    )
+                    )
+             ),
+         wpd_glm_scaled = ((wpd_glm*320)))
+
+G21_glm$wpd_glm_scaled %>% sd()
+
+G21_glm %>% 
+  ggplot() +
+  geom_density(aes(x = wpd_glm), 
+                   fill = "blue") +
+  facet_grid(nx~nfacet,
+             labeller = "label_both") +
+  theme(legend.position = "bottom") 
+```
 
@@
 This means,  $wpd_{norm}$ could be used to measure differences in distribution across panels.
-Also, note that since the data is processed using normal-quantile-transform, this measure is independent of the intial distribution of the underlying data and hence is also comparable across different data sets.
+Also, note that since the data is processed using normal-quantile-transform, this measure is independent of the initial distribution of the underlying data and hence is also comparable across different data sets.
 This is valid for the case when sample size $ntimes$ for each combination of categories is at least 30 and  $nperm$ used for computing $wpd_{norm}$ is at least 100.
 More detailed results about the properties of $wpd_{raw}$ and $wpd_{norm}$ could be found in Appendix.
-
-## Simulation environment
-
-Simulation studies were carried out to study the behavior of $wpd$, build the normalization method as well as compare and evaluate different normalization approaches.
-R version 4.0.1 (2020-06-06) is used with the platform: x86_64-apple-darwin17.0 (64-bit) running under: macOS Mojave 10.14.6 and MonaRCH, which is a next-generation HPC/HTC Cluster, designed from the ground up to address the computing needs of the Monash HPC community.
 

### 2021-02-21 choosing_significant_harmonies.Rmd
restructure section on normalisation

@@
 p_varall <- sim_panel_varall %>%
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
+  ggtitle(paste("Design $D_{var_{all}}$:", varall))
 ```
@@
 p_varx <- sim_panel_varx %>%
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
+    ggtitle(paste("Design $D_{var_x}$:", varx))
 ```
@@
 p_varf <- sim_panel_varf %>%
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
+    ggtitle(paste("Design $D_{var_f}$:", varf))
 ```
@@
 p_null <- sim_panel_null %>%
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
+    ggtitle(paste("Design $D_{null}$:", null))
 ```
+
+```{r}
+library(patchwork)
+(p_null + p_varf)/(p_varx + p_varall)
+```

### 2021-02-21 paper/main.Rmd
restructure section on normalisation

@@
 
-# Normalisation of the distance measure
+# Normalized distance measure
 
@@
 
-```{r linear-model,message=FALSE}
+```{r linear-model, message=FALSE}
 G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds"))
@@
 
-## Results
-
-This section reports the results of a simulation study that was carried out to evaluate the behavior of our distance measure across all potential factors.
-The results are reported in two parts: for the a) raw measure and then b) normalised one to show how the loopholes for the raw measures were removed using the normalized ones.
-
-First, the behavior of $wpd_{raw}$ and $wpd_{norm}$ is explored in designs where there is no difference in distribution between x and facet categories.
-We have considered different initial distributions to study the impact of initial distribution under the null setup.
-Using two types of distributions, viz.
-normal and gamma (non-normal), we generated observations for each combination of $nx$ and $nfacet$ from the following sets: $nx = \{2, 3, 5, 7, 14, 20, 31, 50\}$ and $nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
-Each combination is being referred to as a _panel_.
-That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$.
-For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
-That is, if we consider the panel  $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
-The values of $\lambda$ is set to $0.67$, since we want to up-weigh the within-facet distances and that of $\omega$ is set to $0$, since there is no significant differences between distributions in the null case.
-Observations were generated for each type of distribution changing the shape and scale to study the effect of shape, scale and type of distribution on wpd.
-The set of distributions considered for this purpose is ${N(0,1), N(5, 1), N(0,5), \Gamma(0.5, 1), \Gamma(2, 1)}$.
-Each of the scenario is run $nsim = 200$ times to see the distribution of wpd values for each scenario.
-
-Secondly, the behavior of raw and normalized wpd is explored in designs where there is in fact difference in distribution between facet categories ($D_{var_f}$) or across x-categories ($D_{var_x}$) or both ($D_{var_{all}}$).
+## Combining normalizing approaches
+
+We see that the transformation through the modeling approach leads to very similar distribution across high $nx$ and $nfacet$ (higher than 7) and not so much for lower $nx$ and $nfacet$.
+Hence, the computational load of permutation approach could be alleviated by using the modeling approach for the higher $nx$ and $nfacet$, however, it is important that we use the permutation approach for lower $nx$ and $nfacet$.
+However, it is  difficult to compare the transformed $wpd$ from both of these approaches, since each of the variables is measured on a different scale (each of them have location 0).
+The transformed variables from the two approaches could be brought to the same scale so that for smaller categories, permutation approach is used and for larger categories, we can stick to modeling approach.
+These could be done through the following:
+
+ - Making the range of both the variables same by using min-max scaling method.
+In practice, however, we would only have one value of $wpd_{raw}$ which we need to transform using the modeling approach.
+Hence, min-max scaling approach could not be used here.
+
+ - Standardizing the variables and expressing scores at standard deviation units.
+Again in practice, however, we would only have one value of $wpd_{raw}$ which we need to transform using the modeling approach.
+Hence, standardizing scores could not be used here as we do not have the mean and standard deviation of a series while using transformation using modeling.
+
+- Make the location and scale of both the approaches similar so that they could be compared.
+Please note that the range of values could be different in this case, however location and scale are brought to same levels.)
+
+The measure $wpd_{glm}$ has location 0 and standard deviation ~ 0.003, whereas the measure $wpd_{permutation}$ which is a z-score, has a normal distribution with location 0 and standard deviation 1.
+To bring them to the same scale, we have defined $wpd_{glm-scaled} = wpd_{glm}*300$, which brings the standard deviation of $wpd_{glm-scaled}$ to almost 1, without changing the location.
+
+The measure $wpd_{glm-scaled}$ seems to roughly follow a normal distribution except in the tails as could be seen in Figure \ref{fig:hist-qq} and the very method of permutation approach ensures that $wpd_permutation$ is also normally distributed.
+Further, they are brought to the similar scale and location and hence could be compared.
+
+```{r hist-qq, fig.cap = "In panel a, the histogram of $wpd_{glm-scaled}$ is plotted.
+In parl b, the QQ plot is shown with the theoretical quantiles on the x-axis and $wpd_{glm-scaled}$ quantiles on the y-axis.
+The distribution looks symmetric and looks like normal except in the tails."}
+hist <- ggplot(G21_glm) +
+  geom_histogram(aes(x = wpd_glm_scaled)) +
+  ggtitle("a")
+
+p <- ggplot(G21_glm, aes(sample = wpd_glm_scaled))
+qqplot <-  p + geom_qq() + geom_qq_line() + coord_fixed(ratio = 4/5) +
+  ggtitle("b")
+
+# G21_glm <- G21 %>% 
+#     mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
+#     )
+#     )
+#     ),
+#     wpd_glm_scaled = 300*(wpd_glm))
+
+ # G21_glm$wpd_glm_scaled %>% 
+ #   range()
+hist + qqplot
+```
+
+```{r dist-new-same-scale-link, fig.cap="w$pd_permutation$ and $wpd_{glm-scaled}$ are plotted together on the same scale.
+They also have the same location and hence the values from these two approaches could be compared across panels.
+$wpd_{glm-scaled}$ would be used to normalise $wpd_{raw}$ for higher $nx$ and $nfacet$ and $wpd_{glm-scaled}$ would be used for smaller levels to alleviate the problem of computational time."}
+# 
+# G21_permutation <- read_rds("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_Gamma21.rds") %>%
+#   rename("wpd_permutation" = "value")
+# 
+# 
+# G21_model_data <- G21 %>%
+#   mutate(model =
+#            ((1/value)
+#                   - intercept -
+#                     slope*log(nx*nfacet))/slope) %>%
+#   mutate(model_trans =
+#            (model - mean(model))/sd(model))
+
+# G21_model_data$model %>% summary()
+
+G21_all_data <- G21_permutation %>% 
+  left_join(G21_lm, by = c("nx", "nfacet", "perm_id")) %>% 
+  left_join(G21_glm, by = c("nx", "nfacet", "perm_id")) %>% 
+  pivot_longer(cols = c(3, 10),
+               names_to = "type_estimate",
+               values_to = "value_estimate")
+G21_all_data$type_estimate = factor(G21_all_data$type_estimate , levels = c( "wpd_permutation", "wpd_glm_scaled"))
+
+G21_all_data %>% 
+  filter(type_estimate %in% c("wpd_glm_scaled", "wpd_permutation")) %>% 
+  ggplot() +
+  geom_density(aes(x = value_estimate, 
+                   fill = type_estimate), alpha = 0.5) +
+  facet_grid(nx~nfacet,
+             labeller = "label_both") +
+  theme(legend.position = "bottom") +
+  scale_fill_manual(values = c( "#D55E00", "#0072B2")) +
+  xlab("wpd_norm2") +
+  scale_x_continuous(breaks = c(-5, -3, 0, 3, 5))
+
+# G21_all_data %>% 
+#   filter(type_estimate %in% c("wpd_permutation", "wpd_glm")) %>% 
+#   ggplot() +
+#   geom_density(aes(x = value_estimate, 
+#                    fill = type_estimate), 
+#                alpha = 0.7) +
+#   facet_grid(nx~nfacet,
+#              labeller = "label_both") +
+#   theme(legend.position = "bottom") +
+#   scale_fill_manual(values = c("#CC79A7", "#0072B2")) +
+#   xlab("wpd_norm2")
+
+# are scales same
+# 
+# G21_model_data %>%
+#   group_by(nx, nfacet) %>% 
+#   summarize(sd_model = sd(model))
+#   
+# G21_all_data %>%
+#   filter(type_estimate == c("perm_trans")) %>% 
+#   select(value_estimate) %>% 
+#   range()
+# 
+# G21_all_data %>%
+#   filter(type_estimate == c("wpd_glm_scaled")) %>% 
+#   select(value_estimate) %>% 
+#   range()
+```
+
+## Properties
+
+This section reports the results of a simulation study that was carried out to evaluate the behavior of $wpd_{norm}$.
+The behavior of $wpd_{norm}$ is explored in designs where there is in fact difference in distribution between facet categories ($D_{var_f}$) or across x-categories ($D_{var_x}$) or both ($D_{var_{all}}$).
 Using $\omega =  \{1, 2, \dots, 10\}$ and $\lambda = seq(from  = 0.1, to = 0.9, by = 0.05)$, observations are drawn from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet =  \{2, 3, 5, 7, 14, 20, 31, 50\}$.
 $ntimes = 500$ is assumed for this setup as well.
-Furthermore, to generate different distributions across different combination of facet and x levels, the following method is deployed - suppose the distribution of the combination of first levels of x and facet category is $N(\mu,\sigma)$ and $\mu_{jk}$ denotes the mean of the combination $(a_jb_k)$, then $\mu_{j.} = \mu + j\omega$ (for design $D_{var_x}$) and $\mu_{.k} = \mu + k\omega$ (for design $D_{var_f}$).
-
-The tabulated values and graphical representations of the simulation results are provided in Appendix. The learning from the simulations are as follows:
-The values of the measure $wpd_{raw}$ is least for $D_{null}$, followed by 
-$D_{var_f}$, $D_{var_x}$) and $D_{var_{all}}$). This is a desirable result since the measure $wpd_{raw}$ was designed such that this relationship holds.
-Furthermore, the distribution of the measure $wpd_{raw}$ changes for different facet and x categories.
-The location of the distribution shifts to the right and it also becomes more skewed for more higher facet and x-axis categories.
-Now this is not desirable, as it would mean that we can't compare the $wpd_{raw}$ values across different panels.
-The distribution of $wpd_{norm}$ looks more similar with at least the mean and standard of the distributions being uniform across panels.
+Furthermore, to generate different distributions across different combination of facet and x levels, the following method is deployed - suppose the distribution of the combination of first levels of $x$ and $facet$ category is $N(\mu,\sigma)$ and $\mu_{jk}$ denotes the mean of the combination $(a_jb_k)$, then $\mu_{j.} = \mu + j\omega$ (for design $D_{var_x}$) and $\mu_{.k} = \mu + k\omega$ (for design $D_{var_f}$).
+
+The tabulated values and graphical representations of the simulation results are provided in Appendix.
+The learning from the simulations are as follows: The values of $wpd_{norm}$ is least for $D_{null}$, followed by
+$D_{var_f}$, $D_{var_x}$) and $D_{var_{all}}$). This is a desirable result since the measure $wpd_{norm}$ was designed such that this relationship holds.
+Furthermore, the distribution of the measure $wpd_{norm}$ does not change for different facet and x categories.
+The distribution of $wpd_{norm}$ looks similar with at least the mean and standard of the distributions being uniform across panels.
 This means,  $wpd_{norm}$ could be used to measure differences in distribution across panels.
@@
 7. If $wpd_{obs}> wpd_{threshold}$, harmony pairs are accepted. Only one threshold for all harmony pairs.
+
+```{r varall}
+
+sim_varall_normal <- function(nx, nfacet, mean, sd, w) {
+  dist_normal((mean + seq(0,
+    (nx *
+      nfacet - 1),
+    by = 1
+  ) * w), sd)
+}
+sim_panel_varall <- sim_panel(
+  nx = 2, nfacet = 3,
+  ntimes = 500,
+  sim_dist = sim_varall_normal(2, 3, 0, 1, 10)
+) %>% unnest(data)
+
+set.seed(9999)
+varall <- compute_pairwise_norm(sim_panel_varall, 
+                           gran_x = "id_x",
+                           gran_facet = "id_facet",
+                           response = sim_data, 
+                           nperm = 200
+)
+
+# plot
+p_varall <- sim_panel_varall %>%
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
+  ggtitle(paste("Design $D_{var_{all}}$:", varall))
+```
+
+```{r varx}
+sim_varx_normal <- function(nx, nfacet, mean, sd, w) {
+   rep(dist_normal((mean + seq(0, nx - 1, by = 1) * w), sd), nfacet)
+ }
+
+sim_panel_varx <- sim_panel(
+   nx = 2, nfacet = 3,
+   ntimes = 5,
+   sim_dist = sim_varx_normal(2, 3, 0, 1, 10)
+ ) %>% unnest(data)
+
+set.seed(9999)
+varx <- compute_pairwise_norm(sim_panel_varx, 
+                           gran_x = "id_x",
+                           gran_facet = "id_facet",
+                           response = sim_data, 
+                           nperm = 200
+)
+
+# plot
+p_varx <- sim_panel_varx %>%
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
+    ggtitle(paste("Design $D_{var_x}$:", varx))
+```
+
+```{r varf}
+sim_varf_normal <- function(nx, nfacet, mean, sd, w) {
+  rep(dist_normal((mean + seq(0, nfacet - 1, by = 1) * w), sd), each = nx)
+}
+sim_panel_varf <- sim_panel(
+  nx = 2, nfacet = 3,
+  ntimes = 5,
+  sim_dist = sim_varf_normal(2, 3, 0, 1, 10)
+) %>% unnest(data)
+
+set.seed(9999)
+varf <- compute_pairwise_norm(sim_panel_varf, 
+                           gran_x = "id_x",
+                           gran_facet = "id_facet",
+                           response = sim_data, 
+                           nperm = 200
+)
+
+p_varf <- sim_panel_varf %>%
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
+    ggtitle(paste("Design $D_{var_f}$:", varf))
+```
+
+```{r null}
+sim_panel_null <- sim_panel(
+   nx = 2,
+   nfacet = 3,
+   ntimes = 500,
+   sim_dist = distributional
+   ::dist_normal(0, 1)
+) %>% unnest(c(data))
+
+set.seed(9999)
+
+null <- compute_pairwise_norm(sim_panel_null, 
+                           gran_x = "id_x",
+                           gran_facet = "id_facet",
+                           response = sim_data, 
+                           nperm = 200
+)
+
+p_null <- sim_panel_null %>%
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
+    ggtitle(paste("Design $D_{null}$:", null))
+```
+
+```{r plot-all}
+library(patchwork)
+(p_null + p_varf)/(p_varx + p_varall)
+```
 

### 2021-02-21 paper/supplementary.Rmd
restructure section on normalisation

@@
 Find the number of permutations which are sufficient for consistent estimation of mean and standard deviation
+
+## Results
+
+This section reports the results of a simulation study that was carried out to evaluate the behavior of our distance measure across all potential factors.
+The results are reported in two parts: for the a) raw measure and then b) normalised one to show how the loopholes for the raw measures were removed using the normalized ones.
+
+First, the behavior of $wpd_{raw}$ and $wpd_{norm}$ is explored in designs where there is no difference in distribution between x and facet categories.
+We have considered different initial distributions to study the impact of initial distribution under the null setup.
+Using two types of distributions, viz.
+normal and gamma (non-normal), we generated observations for each combination of $nx$ and $nfacet$ from the following sets: $nx = \{2, 3, 5, 7, 14, 20, 31, 50\}$ and $nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
+Each combination is being referred to as a _panel_.
+That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$.
+For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
+That is, if we consider the panel  $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
+The values of $\lambda$ is set to $0.67$, since we want to up-weigh the within-facet distances and that of $\omega$ is set to $0$, since there is no significant differences between distributions in the null case.
+Observations were generated for each type of distribution changing the shape and scale to study the effect of shape, scale and type of distribution on wpd.
+The set of distributions considered for this purpose is ${N(0,1), N(5, 1), N(0,5), \Gamma(0.5, 1), \Gamma(2, 1)}$.
+Each of the scenario is run $nsim = 200$ times to see the distribution of wpd values for each scenario.
+
+Secondly, the behavior of raw and normalized wpd is explored in designs where there is in fact difference in distribution between facet categories ($D_{var_f}$) or across x-categories ($D_{var_x}$) or both ($D_{var_{all}}$).
+Using $\omega =  \{1, 2, \dots, 10\}$ and $\lambda = seq(from  = 0.1, to = 0.9, by = 0.05)$, observations are drawn from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet =  \{2, 3, 5, 7, 14, 20, 31, 50\}$.
+$ntimes = 500$ is assumed for this setup as well.
+Furthermore, to generate different distributions across different combination of facet and x levels, the following method is deployed - suppose the distribution of the combination of first levels of x and facet category is $N(\mu,\sigma)$ and $\mu_{jk}$ denotes the mean of the combination $(a_jb_k)$, then $\mu_{j.} = \mu + j\omega$ (for design $D_{var_x}$) and $\mu_{.k} = \mu + k\omega$ (for design $D_{var_f}$).
+
+The tabulated values and graphical representations of the simulation results are provided in Appendix. The learning from the simulations are as follows:
+The values of the measure $wpd_{raw}$ is least for $D_{null}$, followed by 
+$D_{var_f}$, $D_{var_x}$) and $D_{var_{all}}$). This is a desirable result since the measure $wpd_{raw}$ was designed such that this relationship holds.
+Furthermore, the distribution of the measure $wpd_{raw}$ changes for different facet and x categories.
+The location of the distribution shifts to the right and it also becomes more skewed for more higher facet and x-axis categories.
+Now this is not desirable, as it would mean that we can't compare the $wpd_{raw}$ values across different panels.
+The distribution of $wpd_{norm}$ looks more similar with at least the mean and standard of the distributions being uniform across panels.
+This means,  $wpd_{norm}$ could be used to measure differences in distribution across panels.
+Also, note that since the data is processed using normal-quantile-transform, this measure is independent of the initial distribution of the underlying data and hence is also comparable across different data sets.
+This is valid for the case when sample size $ntimes$ for each combination of categories is at least 30 and  $nperm$ used for computing $wpd_{norm}$ is at least 100.
+More detailed results about the properties of $wpd_{raw}$ and $wpd_{norm}$ could be found in Appendix.

### 2021-02-23 paper/main.Rmd
writing the residential smart meter

@@
 library(here)
+library(ggplot2)
+library(patchwork)
 
@@
 
-```{r calendar-elec, fig.height = 10.5, fig.cap="Calendar display."}
+```{r calendar- <- , fig.height = 10.5, fig.cap="Calendar display."}
 elec <- read_rds(here("paper/data/elec.rds")) %>% 
@@
 
-The measure $wpd_{glm-scaled}$ seems to roughly follow a normal distribution except in the tails as could be seen in Figure \ref{fig:hist-qq} and the very method of permutation approach ensures that $wpd_permutation$ is also normally distributed.
+The measure $wpd_{glm-scaled}$ seems to roughly follow a normal distribution except in the tails as could be seen in Figure \ref{fig:hist-qq} and the very method of permutation approach ensures that $wpd_{permutation}$ is also normally distributed.
 Further, they are brought to the similar scale and location and hence could be compared.
@@
 
-# Application in residential smart meter data {#sec:application}
+# Application to smart meter datasets {#sec:application}
+
+## Residential smart meter dataset
+
+The smart meter data set from four households in Melbourne referred in @wang2020calendar has been utilized to see the use of the distance measure proposed in the paper.
+The data contains half-hourly electricity consumption from Jan-2018 to Jun-2018 for each of the households, which is procured by them by downloading their data from the energy supplier/retailer.
+Demand data for two households (id 2 and 4) are shown in a linear time scale in \ref{fig:linear-scale}.
+It is evident from the range of the demand data that these households vary in consumption levels as in their temporal patterns.
+In panel A (left), the linear representation of the entire time period is shown, whereas in panel B (right) a particular month is shown and furthermore a week has been highlighted to inspect if there is any daily or weekly periodic patterns in their behavior that is evident from the linear representation of the time series.
+We pick household id 2 and 4 for our analysis to see which periodic patterns are important in their behavior, if they are same or different and if it makes sense using our distance metric.
+
+```{r linear-scale}
+library(scales)
+library(tidyquant)
+library(gghighlight)
+
+elec$date_time <- as.Date(elec$date_time)
+
+elec_linear <- elec %>% 
+  ggplot() +
+  geom_line(aes(x = date_time, y = kwh, group = time)) +
+  facet_wrap(~id, nrow = 4, labeller = "label_both",
+             strip.position =  "right",
+             scales = "free_y") +
+  theme_pubclean() 
+#+
+ # geom_rect(aes(xmin = as.Date("2018-02-01"), xmax = as.Date("2018-02-28"), ymin = -Inf, ymax = Inf),colour="white", size=0.5, alpha=0.02)
+
+elec_zoom <- elec_linear + 
+  coord_x_date(xlim = c("2018-02-01", "2018-02-28")) +
+  gghighlight(date >as.Date("2018-02-05") & date < (as.Date("2018-02-12")),
+              unhighlighted_params = list(colour = "grey")) + geom_line(aes(x = date_time, y = kwh, group = time))
+
+elec_linear + elec_zoom +
+   xlab("Date") +
+  ylab("demand(in kwh)")
+# elec %>% dplyr::filter(date> as.Date("2018-02-01") & date<as.Date("2018-02-28"))
+
+```
+### Data preprocessing
+
+**Normal-quantile-transform**
+
+Let $y_{i, t}$ denote the electricity demand for $i^{th}$ household for time period $t$.
+This is expected to have an assymmetrical distribution as could be seen in \ref{fig:raw-nqt} and the Normal score transform has been applied to make it more treatable.
+Let $y*_{i, t}$ denote the normal-quantile transformed electricity demand for $i^{th}$ household for time period $t$.
+
+**Characterizing empirical distributions through quantiles**
+
+Let $A = \{ a_j: j = 1, 2, \dots, J\}$ be a cyclic granularity of interest. Let 
+$q^{i, p}_{A, j}$ is the quantile with probability $p$ for the $j^{th}$ category of the cyclic granularity $A$ of the $i^{th}$ household.
+Sample quantiles were computed at $p = 0.01, 0.02, \dots, 0.99$ for each household $i \in i = 1, 2, 3, 4$  for each category $j \in j = 1, 2, \dots, J$ and all $A \in N_C$.
+
+**Computing JS distances between harmonies for each categories of the cyclic granularity involved**
+
+```{r raw-nqt}
+elec_raw <- elec %>% 
+  ggplot() +
+  geom_density(aes(x = kwh)) +
+  facet_wrap(~id, scales = "free_y") +
+  xlab("demand (in kwh)")
+
+elec_nqt <- elec %>% 
+  dplyr::mutate(kwh_transformed = stats::qqnorm(kwh, plot.it = FALSE)$x) %>% 
+  ggplot() +
+  geom_density(aes(x = kwh_transformed))+
+  facet_wrap(~id, scales = "free_y") +
+  xlab("NQT demand (in kwh)")
+
+# hour_day_raw <- elec %>% 
+#   tsibble::as_tsibble(index = date_time, key = id) %>% 
+#     create_gran("hour_day") %>% 
+#     ggplot() + 
+#     ggridges::geom_density_ridges(aes(y=hour_day, x = kwh))
+#   
+# hour_day_trans <- elec %>% 
+#   tsibble::as_tsibble(index = date_time, key = id) %>% 
+#     create_gran("hour_day") %>% 
+#   dplyr::mutate(kwh_transformed = stats::qqnorm(kwh, plot.it = FALSE)$x) %>% 
+#   ggplot() +
+#   ggridges::geom_density_ridges(aes(y=hour_day, x = kwh_transformed))
+
+elec_raw + elec_nqt
+
+```
 
 ```{r household2and4}
+elec <- read_rds(here("paper/data/elec.rds")) %>% 
+  filter(date >= ymd("20180101"), date < ymd("20180701"))
+rdbl <- c("Weekday" = "#d7191c", "Weekend" = "#2c7bb6")
+
 id2_tsibble <- elec %>% 
@@
 tic()
-all_harmony4 <- hakear::select_harmonies(id2_tsibble,
-   harmony_tbl = harmonies2,
+all_harmony4 <- hakear::select_harmonies(id4_tsibble,
+   harmony_tbl = harmonies4,
    response = kwh,
@@
 ```
+
+```{r}
+all_harmony2 %>% kable()
+all_harmony4 %>% kable()
+```
+
+## Australian smart meter data set
 

### 2021-02-23 paper/main.Rmd
adding application

@@
 
-```{r linear-scale}
+```{r linear-scale, fig.cap = "Electricity demand for four households are shown in different facets from Jan-18 to Jun-18 in Fig a and it has been zoomed in for Feb-18 in Fig b, where a week in Feb-18 has been highlighted.
+From the scales of Fig a, it is apparent that they have different level of consumption but all of them have some periodic behavior in terms of regular peaks and troughs.
+It is not clear which all periodic patterns exist.
+In fig b, periodic pattern is zoomed in for a month and we can see weekly patterns for the entire period and daily pattern for the highlighted week."}
 library(scales)
@@
 
-elec_zoom <- elec_linear + 
-  coord_x_date(xlim = c("2018-02-01", "2018-02-28")) +
-  gghighlight(date >as.Date("2018-02-05") & date < (as.Date("2018-02-12")),
-              unhighlighted_params = list(colour = "grey")) + geom_line(aes(x = date_time, y = kwh, group = time))
+elec_zoom <-  elec %>% 
+  filter(date >as.Date("2018-02-01") & date < (as.Date("2018-02-28"))) %>% 
+  ggplot(aes(x=date_time, y = kwh)) +
+  facet_wrap(~id, scales = "free_y", ncol = 1, strip.position =  "right") +
+  geom_smooth() +
+  geom_point(alpha = 0.5, size = 0.1) +
+  gghighlight(date >as.Date("2018-02-05") & date < (as.Date("2018-02-12")))
+
+  # geom_rect(xmin = as.Date("2018-02-02"), xmax = as.Date("2018-02-04"), ymin = -Inf, ymax = Inf, fill = "pink", colour = pink)
+
+# elec_zoom <- elec_linear + 
+#   coord_x_date(xlim = c("2018-02-01", "2018-02-28")) +
+#   gghighlight(date >as.Date("2018-02-05") & date < (as.Date("2018-02-12")),
+#               unhighlighted_params = list(colour = "grey")) + geom_line(aes(x = date_time, y = kwh, group = time))
 
@@
 
-**Characterizing empirical distributions through quantiles**
+**Characterizing empirical distributions through quantiles** ( write in the methodology maybe)
 
@@
   geom_density(aes(x = kwh)) +
-  facet_wrap(~id, scales = "free_y") +
+  facet_wrap(~id, scales = "free_y", ncol = 1) +
   xlab("demand (in kwh)")
@@
   geom_density(aes(x = kwh_transformed))+
-  facet_wrap(~id, scales = "free_y") +
+  facet_wrap(~id, scales = "free_y", ncol = 1) +
   xlab("NQT demand (in kwh)")
@@
 
+```{r rank-household2and4}
+elec <- read_rds(here("paper/data/elec.rds")) %>% 
+  filter(date >= ymd("20180101"), date < ymd("20180701"))
+rdbl <- c("Weekday" = "#d7191c", "Weekend" = "#2c7bb6")
+
+id2_tsibble <- elec %>% 
+   filter(id == 2) %>% 
+   as_tsibble(index = date_time)
+
+id4_tsibble <- elec %>% 
+   filter(id == 4) %>% 
+   as_tsibble(index = date_time)
+
+harmonies2 <- id2_tsibble %>%
+  harmony(
+    ugran = "month",
+    filter_in = "wknd_wday",
+    filter_out = c("hhour", "fortnight")
+  )
+
+harmonies4 <- id4_tsibble %>%
+  harmony(
+    ugran = "month",
+    filter_in = "wknd_wday",
+    filter_out = c("hhour", "fortnight")
+  )
+
+library(tictoc)
+tic()
+
+all_harmony2 <- hakear::rank_harmonies(id2_tsibble,
+   harmony_tbl = harmonies2,
+   response = kwh,
+   nperm = 200
+ )
+
+toc()
+
+library(tictoc)
+tic()
+all_harmony4 <- hakear::rank_harmonies(id4_tsibble,
+   harmony_tbl = harmonies4,
+   response = kwh,
+   nperm = 200
+ )
+toc()
+
+```
+
+```{r rank-harmonies}
+all_harmony2 %>% kable()
+all_harmony4 %>% kable()
+```
+
 ```{r household2and4}

### 2021-02-24 paper/main.Rmd
application section

@@
 
-```{r size}
+```{r size, eval = FALSE}
 library(readr)
@@
 
-```{r power}
+```{r power, eval = FALSE}
 library(readr)
@@
 
-#### Characteristics under different simulation designs   
-A set of simulation runs that are conducted and some outputs of which are reported.
-
-```{r sim_all, echo = FALSE}
+```{r sim_all, echo = FALSE, eval = FALSE}
 bind_files = readr::read_rds("../hakear-drake/data/compute_p_value.rds")
@@
 
-# Application to smart meter datasets {#sec:application}
-
-## Residential smart meter dataset
+# Application to residential smart meter dataset {#sec:application}
 
 The smart meter data set from four households in Melbourne referred in @wang2020calendar has been utilized to see the use of the distance measure proposed in the paper.
-The data contains half-hourly electricity consumption from Jan-2018 to Jun-2018 for each of the households, which is procured by them by downloading their data from the energy supplier/retailer.
-Demand data for two households (id 2 and 4) are shown in a linear time scale in \ref{fig:linear-scale}.
-It is evident from the range of the demand data that these households vary in consumption levels as in their temporal patterns.
-In panel A (left), the linear representation of the entire time period is shown, whereas in panel B (right) a particular month is shown and furthermore a week has been highlighted to inspect if there is any daily or weekly periodic patterns in their behavior that is evident from the linear representation of the time series.
-We pick household id 2 and 4 for our analysis to see which periodic patterns are important in their behavior, if they are same or different and if it makes sense using our distance metric.
+The data is a tsibble  containing half-hourly electricity consumption from Jan-2018 to Jun-2018 for each of the households, which is procured by them by downloading their data from the energy supplier/retailer.
+Demand data for these households are shown in a linear time scale in \autoref{fig:linear-scale}.
+It is evident from the range of the demand data that these households vary in consumption levels as well as in their temporal patterns.
+In the left panel of \autoref{fig:linear-scale} (a), the linear representation of the entire time period is shown, whereas in panel B (right) a particular month is shown and furthermore a week has been highlighted to inspect if there is any daily or weekly periodic patterns in their behavior that is evident from the linear representation of the time series.
+We pick household id 2 and 4 for our analysis to see which periodic patterns are important in their behavior, if they are same or different and if it makes sense using our distance metric to select and rank the important harmonies.
 
@@
 ```
-### Data preprocessing
-
-**Normal-quantile-transform**
-
-Let $y_{i, t}$ denote the electricity demand for $i^{th}$ household for time period $t$.
-This is expected to have an assymmetrical distribution as could be seen in \ref{fig:raw-nqt} and the Normal score transform has been applied to make it more treatable.
-Let $y*_{i, t}$ denote the normal-quantile transformed electricity demand for $i^{th}$ household for time period $t$.
-
-**Characterizing empirical distributions through quantiles** ( write in the methodology maybe)
-
-Let $A = \{ a_j: j = 1, 2, \dots, J\}$ be a cyclic granularity of interest. Let 
-$q^{i, p}_{A, j}$ is the quantile with probability $p$ for the $j^{th}$ category of the cyclic granularity $A$ of the $i^{th}$ household.
-Sample quantiles were computed at $p = 0.01, 0.02, \dots, 0.99$ for each household $i \in i = 1, 2, 3, 4$  for each category $j \in j = 1, 2, \dots, J$ and all $A \in N_C$.
-
-**Computing JS distances between harmonies for each categories of the cyclic granularity involved**
+
+<!-- **Normal-quantile-transform**  -->
+
+<!-- **Characterizing empirical distributions through quantiles** ( write in the methodology maybe) -->
+
+<!-- **Computing JS distances between harmonies for each categories of the cyclic granularity involved** -->
 
@@
 
-```{r rank-household2and4}
+Let $y_{i, t}$ denote the electricity demand for $i^{th}$ household for time period $t$.
+This is expected to have an assymmetrical distribution as could be seen in \ref{fig:raw-nqt} and the Normal score transform has been applied to make it more symmetric.
+Let $y*_{i, t}$ denote the normal-quantile transformed electricity demand for $i^{th}$ household for time period $t$.
+Technically, this $y*_{i, t}$ is the linear granularity corresponding to half-hour since the interval of this data is 30 minutes.
+We consider coarser linear granularities like hour, day, week and month from the commonly used Gregorian calendar.
+Considering 4 linear granularities hour, day, week, month in the hierarchy table, the number of cyclic granularities is $N_C = (4 * 3/2) = 6$.
+We obtain cyclic granularities namely “hour_day”, “hour_week”, “hour_month”, “day_ week”, “day_month” and “week_month”, read as “hour of the day”, etc.
+Further, we add cyclic granularity day-type( “wknd wday”) to capture weekend and weekday behavior.
+Thus, we consider 7 cyclic granularities in the set of cyclic granularities of interest defined by $C_{N_C}$.
+We then compute the set of harmonies $H_{N_C}$  from $C_{N_C}$ by choosing pairs of cyclic granularities that are not clashes using procedures described in [@Gupta2020-vo].
+The paper also shows how the number of harmonies could be identified among 42 pair of granularities by removing clashes.
+This section shows how we could refine the search further by only looking at significant harmonies.
+
+Suppose $(A, B) \in H_{N_C}$ be a harmony pair where  $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.
+Suppose $q^{i, p}_{A, j}$ denote the quantiles with probability $p$ for the of the $i^{th}$ household for $j^{th}$ category of the cyclic granularity $A$.
+Similarly, $q^{i, p}_{B, k}$ denotes the same for the $k^{th}$ category of the cyclic granularity $B$.
+Sample quantiles were computed at $p = 0.01, 0.02, \dots, 0.99$.
+Jensen-Shannon distances are computed between $q^{i, p}_{A, j}$ and $q^{i, p}_{B, k}$ for each ${j \in J, k \in K}$ to obtain within-facet and between-facet distances.
+A tuning parameter of $\lambda = 0.67$ has been considered to upweigh the within-facet distances and down-weigh the between facet distances and the maximum of them are obtained to compute $wpd_{raw}$.
+It is further normalised using the approach described in Section \ref{sec:normalization}.
+This entire process is repeated for all harmony pairs $(A, B) \in H_{N_C}$ and for each households $i \in i = \{1, 2, 3, 4\}$.
+The harmony pairs are then arranged in descending order and the important ones with significance level 1%, 5% and 10% are highlighted with `***`, `**` and `*` respectively.
+
+Table \ref{tab:} shows the rank of the harmonies for different households
+\autoref{fig:} shows the bubble chart for the four households with size as the value of wpd and color indicating how significant they are.
+This is a quick summary of which harmonies are significant and also which cyclic granularities are important for the context.
+
+```{r rank-household-mclapply}
 elec <- read_rds(here("paper/data/elec.rds")) %>% 
@@
 
-id2_tsibble <- elec %>% 
-   filter(id == 2) %>% 
+library(tictoc)
+#tic()
+elec_split = elec %>% group_split(id)
+
+elec_select_harmony = parallel::mclapply(1:4, function(x){
+
+  data_id <-  elec_split %>% magrittr::extract2(x) %>% 
     as_tsibble(index = date_time)
 
-id4_tsibble <- elec %>% 
-   filter(id == 4) %>% 
-   as_tsibble(index = date_time)
-
-harmonies2 <- id2_tsibble %>%
+harmonies <- data_id %>%
   harmony(
@@
 
-harmonies4 <- id4_tsibble %>%
-  harmony(
-    ugran = "month",
-    filter_in = "wknd_wday",
-    filter_out = c("hhour", "fortnight")
-  )
-
-library(tictoc)
-tic()
-
-all_harmony2 <- hakear::rank_harmonies(id2_tsibble,
-   harmony_tbl = harmonies2,
+ hakear::select_harmonies(data_id,
+   harmony_tbl = harmonies,
    response = kwh,
-   nperm = 200
- )
-
-toc()
-
-library(tictoc)
-tic()
-all_harmony4 <- hakear::rank_harmonies(id4_tsibble,
-   harmony_tbl = harmonies4,
-   response = kwh,
-   nperm = 200
- )
-toc()
-
-```
-
-```{r rank-harmonies}
-all_harmony2 %>% kable()
-all_harmony4 %>% kable()
-```
-
-```{r household2and4}
+   nperm = 2,
+   nsamp = 2
+ )
+
+}, mc.cores = parallel::detectCores() - 1, mc.preschedule = FALSE, mc.set.seed = FALSE)
+#toc()
+```
+
+```{r elec_select_harmony}
+elec_harmony_all <- elec_select_harmony %>% 
+  bind_rows(.id = "id") %>% 
+  mutate(facet_variable = case_when(
+    facet_variable == "hour_day" ~ "hod" ,
+    facet_variable == "day_month" ~ "dom" ,
+    facet_variable == "day_week" ~ "dow" ,
+    facet_variable == "week_month" ~ "wom" ,
+    facet_variable == "wknd_wday" ~ "wdwnd"
+  )) %>% 
+  mutate(x_variable = case_when(
+    x_variable == "hour_day" ~ "hod" ,
+    x_variable == "day_month" ~ "dom" ,
+    x_variable == "day_week" ~ "dow" ,
+    x_variable == "week_month" ~ "wom" ,
+    x_variable == "wknd_wday" ~ "wdwnd"
+  )) %>% 
+  mutate(id = paste("id", id, sep = " ")) %>% 
+  group_by(id) %>% 
+  mutate(rank = row_number())
+
+```
+
+```{r dotplot, fig.cap = "Harmony pairs are shown for all household ids.
+The size represent how important the pair is and the colour represents if the harmonies are at all important or not.
+Visualizing the pairs in this way helps us to see the important cyclic granularities along the x-axis and facet along with the information that which ones amongst them should be analyzed together." }
+elec_sig_split <- elec_harmony_all %>%
+  mutate(select_split =  str_split(select_harmony, " ", simplify = TRUE)[,2]) %>% 
+  mutate(significant = case_when(
+    select_split == "***" ~ "highest",
+    select_split == "**" ~ "high",
+    select_split == "*" ~ "medium",
+    select_split == "" ~ "low"
+  )) %>% 
+   mutate(rank = case_when(
+    select_split == "***" ~ paste(rank, "***", sep = " "),
+    select_split == "**" ~  paste(rank, "**", sep = " "),
+    select_split == "*" ~  paste(rank, "*", sep = " "),
+    select_split == "" ~  paste(rank, "", sep = " ")
+  ))
+
+elec_sig_split$significant <- 
+  factor(elec_sig_split$significant, levels = c("highest", "high", "medium", "low"))
+
+dotplot <- elec_sig_split %>% 
+  ggplot() +
+  geom_point(aes(x = x_variable,
+                 y = facet_variable, 
+                 size = wpd, 
+                 fill = significant),
+             shape=21,
+             alpha= 0.8) +
+  scale_size_continuous() +
+  theme(legend.position = "bottom") +
+  scale_fill_viridis(discrete = TRUE, direction = 1) +
+  facet_wrap(~id, nrow = 1) +
+  guides(fill = guide_legend(), 
+         size = guide_legend()) +
+  theme_gray(base_size = 12, base_family = "Times") +
+   theme(legend.position = "bottom")
+
+dotplot
+```
+
+```{r tab-rank}
+elec_rank <- elec_sig_split %>% 
+  select(-c(6,7, 9, 10)) %>% 
+  pivot_wider(
+              names_from = id,
+                values_from = rank) %>% 
+  rename("facet variable" = "facet_variable",
+         "x variable" = "x_variable",
+         "facet levels" = "x_levels",
+         "x levels" = "x_levels") %>% 
+  slice(1:4)
+
+elec_rank %>% kable(format = "markdown", caption = "Ranking of the harmonies for the four households are shown.
+The first four harmonies are unanimously important for all households, after which there is differences in the rankings for most households.")
+```
+
+```{r rank-harmonies, eval = FALSE}
+all_harmony2 %>%
+  mutate(rank = row_number()) %>% 
+  left_join(all_harmony4 %>%  mutate(rank = row_number()), by = c("facet_variable", "x_variable")) %>% 
+  select(facet_variable, x_variable,
+          rank.x, rank.y, wpd.x, wpd.y) %>% 
+  mutate(rank.x = if_else(rank.x<=3, paste(rank.x, "***",sep = ""),as.character(rank.x))) %>% 
+   mutate(rank.y = if_else(rank.y<=3, paste(rank.y, "***",sep = ""),as.character(rank.y))) %>% 
+  mutate(wpd.x = round(wpd.x, 3),
+         wpd.y = round(wpd.y, 3)) %>% 
+  rename("rank:id2" = "rank.x",
+         "rank:id4" = "rank.y",
+         "wpd:id2" = "wpd.x",
+         "wpd:id4" = "wpd.y"
+         )  %>% 
+  kable()
+```
+
+```{r household2and4, eval = FALSE}
 elec <- read_rds(here("paper/data/elec.rds")) %>% 
@@
 
-```{r}
+```{r, eval = FALSE}
 all_harmony2 %>% kable()
@@
 
-## Australian smart meter data set
+```{r gravitas-plot, message = FALSE, warning=FALSE, fig.cap="Distribution of energy demand shown for household id: 2 across hod in x-axis and wd-wnd in facets in a) and just the reverse in b).
+In c), distribution of energy demand for household id:4 shown across hod and wd-wnd.
+It can be seen that the differences in distributions are more apparent when viewed in a) as compared to b).
+It seems like there is more difference in the distributions of hod for b) compared to c).
+This also confers with the value of the normalised measure shown in Figure 11."}
+p1 <- id2_tsibble %>%
+   prob_plot("hour_day",
+             "wknd_wday",
+             response = "kwh",
+             plot_type = "quantile",
+             symmetric = FALSE,
+             quantile_prob = c(0.25,0.5,0.75)) +
+  ggtitle("a") + 
+  scale_colour_brewer(name = "", palette = "Set2") +
+  theme(legend.position = "none",
+        strip.text = element_text(size = 7, margin = margin()))
+
+p2 <- id2_tsibble %>%
+   prob_plot("wknd_wday",
+             "hour_day",
+             response = "kwh",
+             plot_type = "quantile",
+             symmetric = FALSE,
+             quantile_prob = c(0.25,0.5,0.75)) +
+  ggtitle("b") +
+  scale_colour_brewer(name = "", palette = "Set2")   +
+  theme(legend.position = "none",
+        strip.text = element_text(size = 7, margin = margin())) + xlab("")
+
+p3 <- id4_tsibble %>%
+   prob_plot("wknd_wday",
+             "hour_day",
+             response = "kwh",
+             plot_type = "quantile",
+             symmetric = FALSE,
+             quantile_prob = 
+               c(0.25,0.5,0.75)) +
+  ggtitle("c") +
+  scale_colour_brewer(name = "", palette = "Set2") +
+  theme(
+        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + theme(legend.position = "bottom",
+        strip.text = element_text(size = 7, margin = margin()))
+
+p1 + p2/p3
+
+```
 

### 2021-02-24 paper/main.Rmd
deleted extra codes

@@
 
-```{r rank-harmonies, eval = FALSE}
-all_harmony2 %>%
-  mutate(rank = row_number()) %>% 
-  left_join(all_harmony4 %>%  mutate(rank = row_number()), by = c("facet_variable", "x_variable")) %>% 
-  select(facet_variable, x_variable,
-          rank.x, rank.y, wpd.x, wpd.y) %>% 
-  mutate(rank.x = if_else(rank.x<=3, paste(rank.x, "***",sep = ""),as.character(rank.x))) %>% 
-   mutate(rank.y = if_else(rank.y<=3, paste(rank.y, "***",sep = ""),as.character(rank.y))) %>% 
-  mutate(wpd.x = round(wpd.x, 3),
-         wpd.y = round(wpd.y, 3)) %>% 
-  rename("rank:id2" = "rank.x",
-         "rank:id4" = "rank.y",
-         "wpd:id2" = "wpd.x",
-         "wpd:id4" = "wpd.y"
-         )  %>% 
-  kable()
-```
-
-```{r household2and4, eval = FALSE}
-elec <- read_rds(here("paper/data/elec.rds")) %>% 
-  filter(date >= ymd("20180101"), date < ymd("20180701"))
-rdbl <- c("Weekday" = "#d7191c", "Weekend" = "#2c7bb6")
-
-id2_tsibble <- elec %>% 
-   filter(id == 2) %>% 
-   as_tsibble(index = date_time)
-
-id4_tsibble <- elec %>% 
-   filter(id == 4) %>% 
-   as_tsibble(index = date_time)
-
-harmonies2 <- id2_tsibble %>%
-  harmony(
-    ugran = "month",
-    filter_in = "wknd_wday",
-    filter_out = c("hhour", "fortnight")
-  )
-
-harmonies4 <- id4_tsibble %>%
-  harmony(
-    ugran = "month",
-    filter_in = "wknd_wday",
-    filter_out = c("hhour", "fortnight")
-  )
-
-library(tictoc)
-tic()
-
-all_harmony2 <- hakear::select_harmonies(id2_tsibble,
-   harmony_tbl = harmonies2,
-   response = kwh,
-   nperm = 200,
-   nsamp = 200
- )
-
-toc()
-
-library(tictoc)
-tic()
-all_harmony4 <- hakear::select_harmonies(id4_tsibble,
-   harmony_tbl = harmonies4,
-   response = kwh,
-   nperm = 200,
-   nsamp = 20
- )
-toc()
-
-```
-
-```{r, eval = FALSE}
-all_harmony2 %>% kable()
-all_harmony4 %>% kable()
-```
-
 ```{r gravitas-plot, message = FALSE, warning=FALSE, fig.cap="Distribution of energy demand shown for household id: 2 across hod in x-axis and wd-wnd in facets in a) and just the reverse in b).

### 2021-02-24 paper/main.Rmd
for 8 households shown in appendix

@@
    response = kwh,
-   nperm = 2,
-   nsamp = 2
+   nperm = 200,
+   nsamp = 200
  )
@@
 # Appendix
+
+## Smart meter application to 8 datasets from energy competition
+
+```{r linear-scale-8, fig.cap = "Electricity demand for four households are shown in different facets from Jan-18 to Jun-18 in Fig a and it has been zoomed in for Feb-18 in Fig b, where a week in Feb-18 has been highlighted.
+From the scales of Fig a, it is apparent that they have different level of consumption but all of them have some periodic behavior in terms of regular peaks and troughs.
+It is not clear which all periodic patterns exist.
+In fig b, periodic pattern is zoomed in for a month and we can see weekly patterns for the entire period and daily pattern for the highlighted week."}
+library(scales)
+library(tidyquant)
+library(gghighlight)
+library(lubridate)
+
+elec <- read_rds(here("paper/data/elec_all-8.rds")) %>% 
+  dplyr::filter(date(reading_datetime) >= ymd("20190701"), date(reading_datetime) < ymd("20191231"), meter_id==1) %>% 
+  select(-meter_id) %>% 
+  rename("id" = "household_id",
+         "date_time" = "reading_datetime")
+
+elec_linear <- elec %>% 
+  ggplot() +
+  geom_line(aes(x = reading_datetime, y = kwh)) +
+  facet_wrap(~household_id, nrow = 8, labeller = "label_both",
+             strip.position =  "right",
+             scales = "free_y") 
+#+
+ # geom_rect(aes(xmin = as.Date("2018-02-01"), xmax = as.Date("2018-02-28"), ymin = -Inf, ymax = Inf),colour="white", size=0.5, alpha=0.02)
+
+  # geom_rect(xmin = as.Date("2018-02-02"), xmax = as.Date("2018-02-04"), ymin = -Inf, ymax = Inf, fill = "pink", colour = pink)
+
+# elec_zoom <- elec_linear + 
+#   coord_x_date(xlim = c("2018-02-01", "2018-02-28")) +
+#   gghighlight(date >as.Date("2018-02-05") & date < (as.Date("2018-02-12")),
+#               unhighlighted_params = list(colour = "grey")) + geom_line(aes(x = date_time, y = kwh, group = time))
+
+# elec %>% dplyr::filter(date> as.Date("2018-02-01") & date<as.Date("2018-02-28"))
+
+```
+
+<!-- **Normal-quantile-transform**  -->
+
+<!-- **Characterizing empirical distributions through quantiles** ( write in the methodology maybe) -->
+
+<!-- **Computing JS distances between harmonies for each categories of the cyclic granularity involved** -->
+
+```{r raw-nqt-8}
+elec_raw <- elec %>% 
+  ggplot() +
+  geom_density(aes(x = kwh)) +
+  facet_wrap(~id, scales = "free_y", ncol = 1) +
+  xlab("demand (in kwh)")
+
+elec_nqt <- elec %>% 
+  dplyr::mutate(kwh_transformed = stats::qqnorm(kwh, plot.it = FALSE)$x) %>% 
+  ggplot() +
+  geom_density(aes(x = kwh_transformed))+
+  facet_wrap(~id, scales = "free_y", ncol = 1) +
+  xlab("NQT demand (in kwh)")
+
+# hour_day_raw <- elec %>% 
+#   tsibble::as_tsibble(index = date_time, key = id) %>% 
+#     create_gran("hour_day") %>% 
+#     ggplot() + 
+#     ggridges::geom_density_ridges(aes(y=hour_day, x = kwh))
+#   
+# hour_day_trans <- elec %>% 
+#   tsibble::as_tsibble(index = date_time, key = id) %>% 
+#     create_gran("hour_day") %>% 
+#   dplyr::mutate(kwh_transformed = stats::qqnorm(kwh, plot.it = FALSE)$x) %>% 
+#   ggplot() +
+#   ggridges::geom_density_ridges(aes(y=hour_day, x = kwh_transformed))
+
+elec_raw + elec_nqt
+
+```
+
+```{r rank-household-mclapply-8}
+elec <- read_rds(here("paper/data/elec_all-8.rds")) %>% 
+  dplyr::filter(date(reading_datetime) >= ymd("20190701"), date(reading_datetime) < ymd("20191231"), meter_id==1) %>% 
+  select(-meter_id) %>% 
+  rename("id" = "household_id",
+         "date_time" = "reading_datetime")
+
+library(tictoc)
+#tic()
+elec_split = elec %>% group_split(id)
+
+elec_select_harmony = parallel::mclapply(1:8, function(x){
+
+  data_id <-  elec_split %>% magrittr::extract2(x) %>% 
+    as_tsibble(index = date_time)
+
+harmonies <- data_id %>%
+  harmony(
+    ugran = "month",
+    filter_in = "wknd_wday",
+    filter_out = c("hhour", "fortnight")
+  )
+
+ hakear::select_harmonies(data_id,
+   harmony_tbl = harmonies,
+   response = kwh,
+   nperm = 200,
+   nsamp = 200
+ )
+
+}, mc.cores = parallel::detectCores() - 1, mc.preschedule = FALSE, mc.set.seed = FALSE)
+#toc()
+```
+
+```{r elec_select_harmony-8}
+elec_harmony_all <- elec_select_harmony %>% 
+  bind_rows(.id = "id") %>% 
+  mutate(facet_variable = case_when(
+    facet_variable == "hour_day" ~ "hod" ,
+    facet_variable == "day_month" ~ "dom" ,
+    facet_variable == "day_week" ~ "dow" ,
+    facet_variable == "week_month" ~ "wom" ,
+    facet_variable == "wknd_wday" ~ "wdwnd"
+  )) %>% 
+  mutate(x_variable = case_when(
+    x_variable == "hour_day" ~ "hod" ,
+    x_variable == "day_month" ~ "dom" ,
+    x_variable == "day_week" ~ "dow" ,
+    x_variable == "week_month" ~ "wom" ,
+    x_variable == "wknd_wday" ~ "wdwnd"
+  )) %>% 
+  mutate(id = paste("id", id, sep = " ")) %>% 
+  group_by(id) %>% 
+  mutate(rank = row_number())
+
+```
+
+```{r dotplot-8, fig.cap = "Harmony pairs are shown for all household ids.
+The size represent how important the pair is and the colour represents if the harmonies are at all important or not.
+Visualizing the pairs in this way helps us to see the important cyclic granularities along the x-axis and facet along with the information that which ones amongst them should be analyzed together." }
+elec_sig_split <- elec_harmony_all %>%
+  mutate(select_split =  str_split(select_harmony, " ", simplify = TRUE)[,2]) %>% 
+  mutate(significant = case_when(
+    select_split == "***" ~ "highest",
+    select_split == "**" ~ "high",
+    select_split == "*" ~ "medium",
+    select_split == "" ~ "low"
+  )) %>% 
+   mutate(rank = case_when(
+    select_split == "***" ~ paste(rank, "***", sep = " "),
+    select_split == "**" ~  paste(rank, "**", sep = " "),
+    select_split == "*" ~  paste(rank, "*", sep = " "),
+    select_split == "" ~  paste(rank, "", sep = " ")
+  ))
+
+elec_sig_split$significant <- 
+  factor(elec_sig_split$significant, levels = c("highest", "high", "medium", "low"))
+
+dotplot <- elec_sig_split %>% 
+  ggplot() +
+  geom_point(aes(x = x_variable,
+                 y = facet_variable, 
+                 size = wpd, 
+                 fill = significant),
+             shape=21,
+             alpha= 0.8) +
+  scale_size_continuous() +
+  theme(legend.position = "bottom") +
+  scale_fill_viridis(discrete = TRUE, direction = 1) +
+  facet_wrap(~id, nrow = 1) +
+  guides(fill = guide_legend(), 
+         size = guide_legend()) +
+  theme_gray(base_size = 12, base_family = "Times") +
+   theme(legend.position = "bottom")
+
+dotplot
+```
+
+```{r tab-rank-8}
+elec_rank <- elec_sig_split %>% 
+  select(-c(6,7, 9, 10)) %>% 
+  pivot_wider(
+              names_from = id,
+                values_from = rank) %>% 
+  rename("facet variable" = "facet_variable",
+         "x variable" = "x_variable",
+         "facet levels" = "x_levels",
+         "x levels" = "x_levels") %>% 
+  slice(1:4)
+
+elec_rank %>% kable(format = "markdown", caption = "Ranking of the harmonies for the four households are shown.
+The first four harmonies are unanimously important for all households, after which there is differences in the rankings for most households.")
+```
+
+```{r gravitas-plot-8, message = FALSE, warning=FALSE, fig.cap="Distribution of energy demand shown for household id: 2 across hod in x-axis and wd-wnd in facets in a) and just the reverse in b).
+In c), distribution of energy demand for household id:4 shown across hod and wd-wnd.
+It can be seen that the differences in distributions are more apparent when viewed in a) as compared to b).
+It seems like there is more difference in the distributions of hod for b) compared to c).
+This also confers with the value of the normalised measure shown in Figure 11."}
+p1 <- id2_tsibble %>%
+   prob_plot("hour_day",
+             "wknd_wday",
+             response = "kwh",
+             plot_type = "quantile",
+             symmetric = FALSE,
+             quantile_prob = c(0.25,0.5,0.75)) +
+  ggtitle("a") + 
+  scale_colour_brewer(name = "", palette = "Set2") +
+  theme(legend.position = "none",
+        strip.text = element_text(size = 7, margin = margin()))
+
+p2 <- id2_tsibble %>%
+   prob_plot("wknd_wday",
+             "hour_day",
+             response = "kwh",
+             plot_type = "quantile",
+             symmetric = FALSE,
+             quantile_prob = c(0.25,0.5,0.75)) +
+  ggtitle("b") +
+  scale_colour_brewer(name = "", palette = "Set2")   +
+  theme(legend.position = "none",
+        strip.text = element_text(size = 7, margin = margin())) + xlab("")
+
+p3 <- id4_tsibble %>%
+   prob_plot("wknd_wday",
+             "hour_day",
+             response = "kwh",
+             plot_type = "quantile",
+             symmetric = FALSE,
+             quantile_prob = 
+               c(0.25,0.5,0.75)) +
+  ggtitle("c") +
+  scale_colour_brewer(name = "", palette = "Set2") +
+  theme(
+        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + theme(legend.position = "bottom",
+        strip.text = element_text(size = 7, margin = margin()))
+
+p1 + p2/p3
+
+```
 

### 2021-02-24 paper/main.Rmd
added example wpds

@@
 Display b and c are more interesting than a since there is a change in distribution either across facets(b) or x-axis(a).
-Display d is most interesting as distribution of the rv changes across both facet and x-axis variable.", eval = FALSE}
-
-# sim_varf_dist1 = function(nx, nfacet){
-#   rep(dist_normal(seq(mean,mean*nfacet, by = mean), sd), each = nx)}
-
-p1 <- sim_panel(nx = 2, nfacet = 3, ntimes = 500) %>%
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
-
-simulated_data <- sim_panel(nx = 2,
+Display d is most interesting as distribution of the rv changes across both facet and x-axis variable."}
+
+sim_varall_normal <- function(nx, nfacet, mean, sd, w) {
+  dist_normal((mean + seq(0,
+    (nx *
+      nfacet - 1),
+    by = 1
+  ) * w), sd)
+}
+sim_panel_varall <- sim_panel(
+  nx = 2, nfacet = 3,
+  ntimes = 500,
+  sim_dist = sim_varall_normal(2, 3, 5, 10, 5)
+) %>% unnest(data)
+
+p_varall <- sim_panel_varall %>%
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
+  ggtitle("")
+
+sim_varx_normal <- function(nx, nfacet, mean, sd, w) {
+   rep(dist_normal((mean + seq(0, nx - 1, by = 1) * w), sd), nfacet)
+ }
+
+sim_panel_varx <- sim_panel(
+   nx = 2, nfacet = 3,
+   ntimes = 500,
+   sim_dist = sim_varx_normal(2, 3, 5, 10, 5)
+ ) %>% unnest(data)
+
+p_varx <- sim_panel_varx %>%
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
+    ggtitle("")
+
+sim_varf_normal <- function(nx, nfacet, mean, sd, w) {
+  rep(dist_normal((mean + seq(0, nfacet - 1, by = 1) * w), sd), each = nx)
+}
+
+sim_panel_varf <- sim_panel(
+  nx = 2, nfacet = 3,
+  ntimes = 500,
+  sim_dist = sim_varf_normal(2, 3, 5, 10, 5)
+) %>% unnest(data)
+
+p_varf <- sim_panel_varf %>%
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
+    ggtitle("")
+
+sim_panel_null <- sim_panel(
+   nx = 2,
    nfacet = 3,
    ntimes = 500,
-          sim_dist = rep(dist_normal(seq(5, 15, 5), 5), each = 2))
-
-p2 <- simulated_data %>% ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
-
-p3 <- simulated_data %>% ggplot(aes(x = as.factor(id_facet), y = sim_data)) + facet_wrap(~id_x) + geom_boxplot()
-
-p4 <- sim_panel(nx = 2,
-          nfacet = 3,
-          ntimes = 500,
-          sim_dist = dist_normal(seq(5,30, 5), 5)) %>% 
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
-
-ggpubr::ggarrange(p1, p2, p3, p4, nrow = 2, ncol = 2,
+   sim_dist = distributional
+   ::dist_normal(5, 10)
+) %>% unnest(c(data))
+
+set.seed(9999)
+
+null <- compute_pairwise_norm(sim_panel_null, 
+                           gran_x = "id_x",
+                           gran_facet = "id_facet",
+                           response = sim_data, 
+                           nperm = 200
+)
+
+p_null <- sim_panel_null %>%
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
+    ggtitle("")
+
+ggpubr::ggarrange(p_null, p_varf,  p_varx, p_varall, nrow = 2, ncol = 2,
                   common.legend = TRUE,
@@
 
-*incorporate from the document combining_normalisation_method.Rmd*
-
 ### Modelling approach
@@
 
+## Algorithm
+
 1. Given the data; $\{v_t: t=0, 1, 2, \dots, T-1\}$, the $wpd_{norm}$ is computed and is represented by $wpd_{obs}$.
@@
 
-```{r varall}
+## Results
+
+```{r varall-new}
 
@@
   ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
-  ggtitle(paste("Design $D_{var_{all}}$:", varall))
-```
-
-```{r varx}
+  ggtitle(paste("d", round(varall, 2)))
+```
+
+```{r varx-new}
 sim_varx_normal <- function(nx, nfacet, mean, sd, w) {
@@
    nx = 2, nfacet = 3,
-   ntimes = 5,
+   ntimes = 500,
    sim_dist = sim_varx_normal(2, 3, 0, 1, 10)
@@
   ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
-    ggtitle(paste("Design $D_{var_x}$:", varx))
-```
-
-```{r varf}
+    ggtitle(paste("c", round(varx, 2)))
+```
+
+```{r varf-new}
 sim_varf_normal <- function(nx, nfacet, mean, sd, w) {
@@
   nx = 2, nfacet = 3,
-  ntimes = 5,
+  ntimes = 500,
   sim_dist = sim_varf_normal(2, 3, 0, 1, 10)
@@
   ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
-    ggtitle(paste("Design $D_{var_f}$:", varf))
-```
-
-```{r null}
+    ggtitle(paste("b", round(varf, 2)))
+```
+
+```{r null-new}
 sim_panel_null <- sim_panel(
@@
   ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
-    ggtitle(paste("Design $D_{null}$:", null))
-```
-
-```{r plot-all}
+    ggtitle(paste("a", round(null, 2)))
+```
+
+```{r plot-all-new2}
 library(patchwork)
 (p_null + p_varf)/(p_varx + p_varall)
-```
-
-The p-value of the design $D_{null}$ is size.
-The p-value of other designs is power.
-Confidence interval of the
-
-```{r, eval = FALSE, echo = FALSE}
-smart_harmony <-read_rds("data/smart_harmony_nonst.rds")
-smart_harmony
-```
-
-```{r smart_harmony,eval = FALSE, echo = FALSE}
-
-sm <- smart_meter10 %>% dplyr::filter(customer_id %in% c("10017936"))
-
-harmonies <- sm %>% 
-  harmony(ugran = "month",
-          filter_in = "wknd_wday",
-          filter_out = c("hhour", "fortnight"))
-
-harmony_tbl =  harmonies
-
-smart_harmony <- sm %>% 
-  rank_harmony(harmony_tbl = harmonies,
-               response = "general_supply_kwh", 
-               dist_ordered = TRUE)
-
-smart_harmony %>% 
-  mutate(MMPD = round(MMPD, 3), max_pd = round(max_pd, 3)) %>% 
-  mutate(rankn = row_number()) %>%
-  rename("rankun" = "r") %>% kable()
-```
-
-The p-value is almost always greater than 0.05, which means there is no significant differences between the different categories, which is true from the simulation design.
-
-```{r size, eval = FALSE}
-library(readr)
-library(tidyverse)
-data_N01 <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds"))
-
-data_N01_obs <- data_N01 %>% filter(perm_id==1)
-data_N01_samp <- data_N01 %>% filter(perm_id!=1)
-
-#plot_mmpd_null_grid(data_N01_samp, data_N01_obs)
-
-mmpd_dist_null_grid  = data_N01_samp
-
-mmpd_null_orig = data_N01_obs
-compute_p_value <- left_join(mmpd_dist_null_grid, mmpd_null_orig,
-                               by = c("nx", "nfacet")) %>% 
-    group_by(nx, nfacet) %>% 
-    summarise(p_value = sum(if_else(abs(value.x)>abs(value.y),1,0))/n(), .groups = 'drop')
-
-  ggplot() + 
-    geom_histogram(data = mmpd_dist_null_grid, aes(x = value))  + 
-    geom_vline(data = mmpd_null_orig, aes(xintercept = value),colour = "red") +
-    geom_text(data = round(compute_p_value, 3), size = 3,  
-              aes(x = -Inf,
-                  y =  Inf,
-                  label = paste("p-value:",p_value),
-                  hjust   = 0,
-                  vjust   = 1)) + 
-    facet_grid(nx ~ nfacet)
-```
-
-```{r power, eval = FALSE}
-library(readr)
-library(tidyverse)
-data_N01 <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds"))
-
-data_N01_obs <- data_N01 %>% filter(perm_id==1)
-data_N01_samp <- data_N01 %>% filter(perm_id!=1)
-
-#plot_mmpd_null_grid(data_N01_samp, data_N01_obs)
-
-mmpd_dist_null_grid  = data_N01_samp
-
-mmpd_null_orig = data_N01_obs
-compute_p_value <- left_join(mmpd_dist_null_grid, mmpd_null_orig,
-                               by = c("nx", "nfacet")) %>% 
-    group_by(nx, nfacet) %>% 
-    summarise(p_value = sum(if_else(abs(value.x)>abs(value.y),1,0))/n(), .groups = 'drop')
-
-  ggplot() + 
-    geom_histogram(data = mmpd_dist_null_grid, aes(x = value))  + 
-    geom_vline(data = mmpd_null_orig, aes(xintercept = value),colour = "red") +
-    geom_text(data = round(compute_p_value, 3), size = 3,  
-              aes(x = -Inf,
-                  y =  Inf,
-                  label = paste("p-value:",p_value),
-                  hjust   = 0,
-                  vjust   = 1)) + 
-    facet_grid(nx ~ nfacet)
-```
-
-```{r sim_all, echo = FALSE, eval = FALSE}
-bind_files = readr::read_rds("../hakear-drake/data/compute_p_value.rds")
-
-bind_files$design = 
-  factor(bind_files$design,
-         levels = c("null","vary_f", "vary_x", "vary_all"), labels = c("D1", "D2", "D3", "D4"))
-
-ggplot(bind_files %>% 
-         filter(distribution == "normal")) +
-  geom_point(aes(x=design, y = p_value),
-                 alpha = 0.5)+
-  facet_grid(nx~nfacet) +
-  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
-
-ggplot(bind_files %>% 
-         filter(distribution == "exponential")) +
-  geom_point(aes(x=design, y = p_value),
-                 alpha = 0.5)+
-  facet_grid(nx~nfacet) +
-  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
-
-ggplot(bind_files %>% 
-         filter(distribution == "gamma")) +
-  geom_point(aes(x=design, y = p_value),
-                 alpha = 0.5)+
-  facet_grid(nx~nfacet) +
-  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
-
-ggplot(bind_files %>% 
-         filter(distribution == "weibull")) +
-  geom_point(aes(x=design, y = p_value),
-                 alpha = 0.5)+
-  facet_grid(nx~nfacet) +
-  geom_line(aes(x = design, y = p_value, group = distribution, color = distribution))
-```
-
-```{r sim_conf, echo = FALSE, eval = FALSE}
-library(dplyr)
-library(ggplot2)
-ggplot2::ggplot(design_all %>% 
-                      filter(design == "D1", distribution == "norm")) +
-  geom_boxplot(aes(x = as.factor(nx), 
-                   y = mmpd.x), width = 0.1) + 
-  facet_wrap(~nfacet) +
-  scale_fill_viridis_d() +
-  xlab("number of x levels") +
-  coord_flip()
-
 ```
@@
 A tuning parameter of $\lambda = 0.67$ has been considered to upweigh the within-facet distances and down-weigh the between facet distances and the maximum of them are obtained to compute $wpd_{raw}$.
-It is further normalised using the approach described in Section \ref{sec:normalization}.
+It is further normalized using the approach described in Section \ref{sec:normalization}.
 This entire process is repeated for all harmony pairs $(A, B) \in H_{N_C}$ and for each households $i \in i = \{1, 2, 3, 4\}$.
@@
   ggplot() +
-  geom_line(aes(x = reading_datetime, y = kwh)) +
-  facet_wrap(~household_id, nrow = 8, labeller = "label_both",
+  geom_line(aes(x = date_time, y = kwh)) +
+  facet_wrap(~id, nrow = 8, labeller = "label_both",
              strip.position =  "right",
              scales = "free_y") 
+elec_linear
 #+
@@
   scale_fill_viridis(discrete = TRUE, direction = 1) +
-  facet_wrap(~id, nrow = 1) +
+  facet_wrap(~id, nrow = 2) +
   guides(fill = guide_legend(), 
@@
          "facet levels" = "x_levels",
-         "x levels" = "x_levels") %>% 
-  slice(1:4)
+         "x levels" = "x_levels")
 

### 2021-02-28 paper/main.Rmd
idea section - first para of distance measure re-written

@@
 ---
-title: An automatic approach to find all possible calendar effects (periodic patterns) for an univariate time series
+title: A new metric for automatic discovery of periodic patterns in time series
 authors:
@@
 
-# The distance measure for quantifying patterns in harmonies
-
-We are interested in assessing structure in probability distributions of the measured variable across bivariate cyclic granularities.
-We propose a measure called Weighted Maximum Pairwise Distances (wpd) to evaluate structure in such a design.
-
-## Idea {#sec:idea}
-
-The principle employed for building a new metric is explained through a simple example explained in Figure \ref{fig:null4by2}.
-Each of these figures have the same panel design with 2 x-axis categories and 4 facet levels.
+# A distance measure for quantifying patterns in harmonies
+
+We are interested in assessing the structure in probability distributions of the measured variable across bivariate cyclic granularities.
+We propose a measure called Weighted Maximum Pairwise Distances (wpd) to quantify the structure in such a design.
+The principle employed towards this goal is explained through a simple example explained in Figure \ref{fig:null4by2}.
+Each of these figures have the same panel design with $2$ x-axis categories and $3$ facet levels.
 Figure \ref{fig:null4by2}a has all x categories drawn from N(5, 10) distribution for each facet.
 It is not an interesting display particularly, as distributions do not vary across x-axis or facet categories.
-Figure \ref{fig:null4by2}b has x categories drawn from the same distribution within a facet and different for different facet categories.
-Figure \ref{fig:null4by2}b exhibits an exact opposite situation where distribution between the x-axis categories within each facet is different but they are same across facets.
+Figure \ref{fig:null4by2}b has x categories drawn from the same distribution within a facet but the mean has been incremented by $5$ units for every consecutive facets.
+Figure \ref{fig:null4by2}c exhibits an exact opposite situation where distribution between the x-axis categories within each facet is different but they are same across facets.
+For this situation, mean of only the x-axis categories are increased by $5$ units for each consecutive category.
 Figure \ref{fig:null4by2}d takes a step further by varying the distribution across both facet and x-axis categories.
-If we are asked to rank the displays in order of importance from minimum to maximum, we might order it as a, b, c and then d.
-It might be argued that it is not clear if b should precede or succeed c.
+If the displays are to be ranked in order of importance from minimum to maximum, then an obvious choice would be placing a followed by b, c and then d.
+It might be argued that it is not clear if b should precede or succeed c in the ranking.
 Gestalt theory suggests that when items are placed in close proximity, people assume that they are in the same group because they are close to one another and apart from other groups.
 Hence, displays that capture more variation within different categories in the same group would be important to bring out different patterns of the data.
-With this principle, display b could be considered less informative as compared to display c.
-
-With reference to the graphical design in \ref{@Gupta2020-vo}, therefore the idea would be to rate a harmony pair higher if the variation between different levels of the x-axis variable is higher on an average across all levels of the facet variables.
-Thus the metric could be obtained by computing maximum pairwise distances between distributions of the continuous random variable across x-axis categories for all facets and then taking the median of those maximum pairwise distances across facets.
-This would help capture the average maximum difference in distribution of the measurement variable explained by the two cyclic granularities together.
-We call this metric wpd which stands for Median Maximum Pairwise Distances.
-In the next section we shall see how we go about computing this measure.
+With this principle in mind, display b is considered less informative as compared to display c.
+Hence, with reference to the graphical design in @Gupta2020-vo, therefore the idea would be to rate a harmony pair higher if the variation between different levels of the x-axis variable is higher on an average across all levels of the facet variables.
+
+Intuitively, while finding a structure or measuring the strength of patterns in Figure \ref{fig:null4by2}, it makes sense to look for within-group and between-group variation.
+Larger variation would imply stronger patterns, whereas small variation would imply the underlying structure is not changing within or between group.
+Thus, a distance measure aimed to capture this structure should ideally estimate these within-group and between-group variations.
+One of the potential ways to do this is to measure the distances between distributions of the continuous random variable measured within and between groups, weigh them basis if they are within or between groups and then take the maximum of those distances as an estimate of the strength of the structure.
+We call this metric $wpd$ which stands for Weighted Pairwise Distances.
+This section starts with possible ways of characterizing distributions and computing distances between them and then describe in details how
+the measure $wpd$ is defined.
 
@@
 
-```{r null4by2,fig.cap=" A graphical display with two categories mapped to x-axis and 4 categories mapped to facets with the distribution of a continuous random variable plotted on the y-axis.
-Display a is not interesting as the distribution of the continuous rv does not depend across x-axis or facet categories.
-Display b and c are more interesting than a since there is a change in distribution either across facets(b) or x-axis(a).
-Display d is most interesting as distribution of the rv changes across both facet and x-axis variable."}
+```{r null4by2,fig.cap = "A graphical display with two categories mapped to x-axis and 3 categories mapped to facets with the distribution of a continuous random variable plotted on the y-axis.
+Display a is not interesting as the distribution of the variable does not depend on x or facet categories.
+Display b and c are more interesting than a since there is a change in distribution either across facets (b) or x-axis (c).
+Display d is most interesting in terms of displaying the strongest pattern as distribution of the variable changes across both facet and x-axis variable."}
 
@@
 p_varall <- sim_panel_varall %>%
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
-  ggtitle("")
+  rename("facet level" = "id_facet" ) %>% 
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + 
+  facet_wrap(~`facet level`,labeller = "label_both") + 
+  geom_boxplot() +
+  ggtitle("") +
+  xlab("x level") +
+  ylab("")
 
@@
 p_varx <- sim_panel_varx %>%
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
-    ggtitle("")
+  rename("facet level" = "id_facet" ) %>% 
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) + 
+  facet_wrap(~`facet level`,labeller = "label_both") + 
+  ggtitle("") +
+  geom_boxplot() +
+  xlab("x level") +
+  ylab("simulated response")
 
@@
 p_varf <- sim_panel_varf %>%
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
-    ggtitle("")
+  rename("facet level" = "id_facet" ) %>% 
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) +
+  facet_wrap(~`facet level`,labeller = "label_both") + 
+  geom_boxplot() +
+  ggtitle("") +
+  xlab("x level") +
+  ylab("")
 
@@
 
-null <- compute_pairwise_norm(sim_panel_null, 
-                           gran_x = "id_x",
-                           gran_facet = "id_facet",
-                           response = sim_data, 
-                           nperm = 200
-)
-
 p_null <- sim_panel_null %>%
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
-    ggtitle("")
+  rename("facet level" = "id_facet" ) %>% 
+  ggplot(aes(x = as.factor(id_x), y = sim_data)) +
+  facet_wrap(~`facet level`,labeller = "label_both") +
+  geom_boxplot() +
+  ggtitle("") +
+  xlab("x level") +
+  ylab("simulated response")
 
@@
 
-# Normalized distance measure
+# Normalization for the number of comparisons
 
@@
 
+In this section, we provide a method to select important harmonies by eliminating all harmonies for which patterns are not significant across x or facet categories through randomization test.
+Randomization tests (permutation tests) generates a random distribution by re-ordering our observed data and allow to test if the observed data is significantly different from any random distribution.
 Complete randomness in the measured variable indicates that the process follows a homogeneous underlying distribution over the whole time series, which essentially implies there is no interesting distinction across any different categories of the cyclic granularities.
+
+## Choosing a threshold
+
+Typically, a randomization test involves calculating a test statistic, randomly shuffling the data and calculating the test statistic several times to obtain a distribution of the test statistic.
+We will use this procedure to test if there is any interesting pattern captured by the harmonies, which essentially implies if $wpd_{norm}$ is significantly different from zero.
+The percentages of times the $wpd_{norm}$ obtained from the permuted data is greater than or equal to the observed $wpd_{norm}$ is the p-value.
+The randomization test is described as follows:
+
+<!-- <!-- We can remove the harmonies for which no interesting patterns are observed through a randomization permutation method. --> 
+<!-- Essentially, the assumption is that under the null hypothesis, there is no difference in categories between the pair of cyclic granularities in the chosen harmony.
+This method is based on the generation of randomly chosen reassignments (permutations) of the data across different cyclic granularities and the computation of  -->
+<!-- $wpd_{norm}$ for each of these reassignments. -->
+
+<!-- **Assumption:** random permutation of the data keeping the categories of the cyclic granularities constant. -->
+
+- **Input:** All harmonies of the form $\{(A, B), A = \{ a_j: j = 1, 2, \dots, J\}, B = \{ b_k: k = 1, 2, \dots, K\}\}$  with $A$ placed across x-axis and $B$ across facets $\forall (A, B) \in N_C$.
+
+- **Output:** Harmony pairs $(A, B)$ for which $wpd_{norm}$ is significant.
+
+1. Fix harmony pair $(A, B)$.
+
+2. Given the data; $\{v_t: t=0, 1, 2, \dots, T-1\}$, the $wpd_{norm}$ is computed and is represented by $wpd_{obs}$.
+
+3. From the original sequence a random permutation is obtained: $\{v_t^*: t=0, 1, 2, \dots, T-1\}$.
+
+4. $wpd_{norm}$ is computed for the permuted sequence of the data and is represented by $wpd_{perm_1}$.
+
+5.  Steps (3) and (4) are repeated a large number
+of times M (M = 200).
+
+6. For each permutation, one $wpd_{perm_i}$ is obtained. Define $wpd_{sample} = \{wpd_{perm_1}, wpd_{perm_2}, \dots, wpd_{perm_M}\}$.
+
+7. Repeat Steps (1-6) for all harmony pairs.
+
+8. $95^{th}$ percentile of $wpd_{sample}$ obtained for all harmony pairs is computed and stored in $wpd_{threshold}$.
+
+7. If $wpd_{obs_{A, B}}> wpd_{threshold}$, harmony pair $(A, B)$ is selected, otherwise rejected.
+
+<!-- Complete randomness in the measured variable indicates that the process follows a homogeneous underlying distribution over the whole time series, which essentially implies there is no interesting distinction across any different categories of the cyclic granularities.
 We can remove the harmonies for which no interesting patterns are observed through a randomization permutation method.
 Essentially, the assumption is that under the null hypothesis, there is no difference in categories between the pair of cyclic granularities in the chosen harmony.
-This method is based on the generation of randomly chosen reassignments (permutations) of the data across different cyclic granularities and the computation of
-$wpd_{norm}$ for each of these reassignments.
+This method is based on the generation of randomly chosen reassignments (permutations) of the data across different cyclic granularities and the computation of  -->
+<!-- $wpd_{norm}$ for each of these reassignments.
 The percentages of times the theoretical distribution greater than or equal to the respective observed $wpd_{norm}$ values are calculated and are used to obtain the P value.
-The procedure for the permutation test is:
+The procedure for the permutation test is: -->
 
@@
 
-## Algorithm
-
-1. Given the data; $\{v_t: t=0, 1, 2, \dots, T-1\}$, the $wpd_{norm}$ is computed and is represented by $wpd_{obs}$.
-
-2. From the original sequence a random permutation is obtained: $\{v_t^*: t=0, 1, 2, \dots, T-1\}$.
-
-3. $wpd_{norm}$ is computed for the permuted sequence of the data and is represented by $wpd_{perm_1}$.
-
-4.  Steps (2) and (3) are repeated a large number
-of times M (M = 200).
-
-5. For each permutation, one $wpd_{perm_i}$ is obtained. Define $wpd_{sample} = \{wpd_{perm_1}, wpd_{perm_2}, \dots, wpd_{perm_M}\}$.
-
-6. $95^{th}$ percentile of this $wpd_{sample}$ distribution is computed and stored in $wpd_{threshold}$.
-
-7. If $wpd_{obs}> wpd_{threshold}$, harmony pairs are accepted. Only one threshold for all harmony pairs.
+<!-- 1. Given the data; $\{v_t: t=0, 1, 2, \dots, T-1\}$, the $wpd_{norm}$ is computed and is represented by $wpd_{obs}$. -->
+
+<!-- 2. From the original sequence a random permutation is obtained: $\{v_t^*: t=0, 1, 2, \dots, T-1\}$. -->
+
+<!-- 3. $wpd_{norm}$ is computed for the permuted sequence of the data and is represented by $wpd_{perm_1}$. -->
+
+<!-- 4.  Steps (2) and (3) are repeated a large number -->
+<!-- of times M (M = 200). -->
+
+<!-- 5. For each permutation, one $wpd_{perm_i}$ is obtained. Define $wpd_{sample} = \{wpd_{perm_1}, wpd_{perm_2}, \dots, wpd_{perm_M}\}$. -->
+
+<!-- 6. $95^{th}$ percentile of this $wpd_{sample}$ distribution is computed and stored in $wpd_{threshold}$. -->
+
+<!-- 7. If $wpd_{obs}> wpd_{threshold}$, harmony pairs are accepted. Only one threshold for all harmony pairs. -->
 
@@
 
-# Discussion points and future work
+# Discussion
 
@@
 
+```
+
+```{r mds}
+set.seed(7777)
+library(gravitas)
+library(tsibble)
+library(lubridate)
+library(readr)
+
+all_data <- read_rds(here("paper/sim_table/all_data.rds"))
+sm_cust_data <- read_rds(here("paper/data/sm_cust_data.rds")) %>% 
+  as_tsibble(index = reading_datetime,
+             key = customer_id)
+
+sm_unique_cust <- sm_cust_data %>% distinct(customer_id)
+
+#sm_30 <- sample(sm_unique_cust$customer_id, 30)
+sm_cust_samp <- sm_cust_data %>% 
+  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
+  filter(year(reading_datetime) == 2012)  %>% 
+  create_gran("day_week") %>% 
+  create_gran("hour_day")
+
+#all_data <- write_rds(all_data, "paper/sim_table/all_data.rds")
+
+facet_variable = "day_week"
+x_variable = "hour_day"
+
+one_harmony_data <- all_data %>%
+  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
+  filter(facet_variable == "day_week",
+                    x_variable == "hour_day") %>% 
+  mutate(customer_id = as.character(customer_id))
+
+mds<- one_harmony_data %>%
+  select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
+  dist() %>%          
+  cmdscale() %>%
+  as_tibble()
+
+colnames(mds) <- c("Dim.1", "Dim.2")
+rownames(mds) <- unique(one_harmony_data$customer_id)
+mds <- mds %>%
+  mutate(customer_id = as.character(unique(one_harmony_data$customer_id))) %>%
+  select((customer_id)
+         , Dim.1, Dim.2)
+```
+
+```{r clustering}
+# K-means clustering
+clust <- kmeans(mds, 3)$cluster %>%
+  as.factor()
+mds <- mds %>%
+  mutate(groups = clust)
+
+# Plot and color by groups
+q1 <- ggpubr::ggscatter(mds, x = "Dim.1", y = "Dim.2", 
+          label = rownames(mds),
+          color = "groups",
+          palette = "jco",
+          size = 1, 
+          ellipse = TRUE,
+          ellipse.type = "convex",
+          repel = TRUE)
+
+```
+
+- check transformation and scalar approaches are same
+
+```{r scalar-approach}
+set.seed(7777)
+all_data <- read_rds(here("paper/sim_table/all_data_scalar.rds"))
+sm_cust_data <- read_rds(here("paper/data/sm_cust_data.rds"))
+set.seed(7777)
+sm_unique_cust <- sm_cust_data %>% distinct(customer_id)
+sm_cust_samp <- sm_cust_data %>% 
+  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
+  #filter(year(reading_datetime) == 2012) %>% #for demo just show one column
+  as_tsibble(index = reading_datetime,
+             key = customer_id) %>% 
+  create_gran("day_week") %>% 
+  create_gran("hour_day")
+
+#all_data <- write_rds(all_data, "paper/sim_table/all_data.rds")
+
+facet_variable = "day_week"
+x_variable = "hour_day"
+
+one_harmony_data <- all_data %>%
+  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
+  filter(facet_variable == "day_week",
+         x_variable == "hour_day") %>% 
+  mutate(customer_id = as.character(customer_id))
+
+mds<- one_harmony_data %>%
+  select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
+  dist() %>%          
+  cmdscale() %>%
+  as_tibble()
+
+colnames(mds) <- c("Dim.1", "Dim.2")
+rownames(mds) <- unique(one_harmony_data$customer_id)
+mds <- mds %>%
+  mutate(customer_id = as.character(unique(one_harmony_data$customer_id))) %>%
+  select((customer_id)
+         , Dim.1, Dim.2)
+
+ggpubr::ggscatter(mds,
+                  x = "Dim.1",
+                  y = "Dim.2", 
+                  label = rownames(mds),
+                  size = 1,
+                  repel = TRUE)
+
+# clustering as well
+
+d = one_harmony_data %>%
+  select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
+  dist()
+
+hc = stats::hclust(d,method="complete")
+#plot(hc)
+groups<-cutree(hc, k=3)
+
+all_data_cluster <- cbind(one_harmony_data, groups) %>% 
+  left_join(mds, by = "customer_id") %>% 
+  mutate(groups = as.factor(groups))
+
+q2 <- ggpubr::ggscatter(all_data_cluster,
+                  x = "Dim.1",
+                  y = "Dim.2", 
+                  label = rownames(mds),
+                  color = "groups",
+                  size = 1,
+                  repel = TRUE)
+
+q1 + q2
 ```

### 2021-02-28 paper/main.Rmd
notations and characterising distribution section re-written

@@
 
+## Notations
+
+Consider two cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.
+Let $v = \{v_t: t = 0, 1, 2, \dots, T-1\}$ be a continuous variable observed across $T$ time points.
+Let the four elementary designs as described in Figure \ref{fig:null4by2} be $D_{null}$ where there is no difference in distribution of $v$ for $A$ or $B$, $D_{var_f}$ denotes the set of designs where there is difference in distribution of $v$ for $B$ and not for $A$.
+Similarly, $D_{var_x}$ denotes the set of designs where difference is observed only across A.
+Finally, $D_{var_{all}}$ denotes those designs for which difference is observed across both $A$ and $B$.
+
 ## Characterising distributions
 
-Each of the data subsets in the data structure have multiple observations and may vary widely across different subsets due to the structure of the calendar, missing observations or uneven locations of events in the time domain.
-The set of observations corresponding to each combination is assumed to be a sample from an unknown probability density function.
-While the whole population of observations has certain characteristics, we can typically never measure all of them.
+Multiple observations of $v$ correspond to the subset  $v_{jk} = \{s: A(s) = j, B(s) = k\}$.
+The number of observations and the structure might vary widely across subsets due to the structure of the calendar, missing observations or uneven locations of events in the time domain.
+Each $v_{jk} : j\in \{1, 2, \dots, J\}, k\in \{1, 2, \dots, K\}\}$ is assumed to be drawn from a continuous probability distribution and have certain characteristics.
 Often shape, central tendency, and variability are the common characteristics used to describe the distribution.
-Another way to describe the probability distribution is through quantiles.
-(Define quantiles here) <!--There are two broad approaches to quantile estimation, viz, parameteric and non-parameteric.
-The benefit of using a non-parametric estimator is that there are less rigid assumptions made about the nature of the underlying distribution of the data.--> Sample quantiles could be thought to estimate the population quantiles.
-But there are a large number of different definitions used for sample quantiles.
-The median-unbiased estimator is recommended (Rob's paper) because of its desirable properties of a quantile estimator and can be defined independently of the underlying distribution.
+Mean, median or mode are generally used to describe the center of the distribution, while range, standard deviation, quantiles, standard errors and confidence intervals are often used to describe variability in the distribution.
+Quantiles are chosen as a way to characterize distributions in this paper.
+
+The quantile of a distribution with probability $p$ is defined as $Q(p)=F^{-1}(p) = inf\{x: F(x) >p\}$, $0<p< 1$ where $F(x)$ is the distribution function.
+There are two broad approaches to quantile estimation, viz, parameteric and non-parameteric.
+The benefit of using a non-parametric estimator is that there are less rigid assumptions made about the nature of the underlying distribution of the data.
+Sample quantiles could be used for estimation in a non-parametric setup.
+@Hyndman1996-ty describes the difficulty in defining sample quantiles and recommends the use of median-unbiased estimator because of "desirable properties of a quantile estimator and can be defined independently of the underlying distribution.".
+The `stats::quantile()` function in @R-language could be used for practical implementation where type = 8 refers to the algorithm corresponding to the median-unbiased estimator.
 

### 2021-02-28 paper/main.Rmd
distance between distributions

@@
 We call this metric $wpd$ which stands for Weighted Pairwise Distances.
-This section starts with possible ways of characterizing distributions and computing distances between them and then describe in details how
-the measure $wpd$ is defined.
+This section starts with possible ways of characterizing distributions and computing distances between them and then describe in details how the measure $wpd$ is defined.
+This is similar to @ieee-irish where the authors compute the Jensen Shannon distance between two density estimates by computing percentiles and stresses the advantages to working with percentiles rather than the data directly in case of missing observations or even unsynchronized time series.
 
@@
 The quantile of a distribution with probability $p$ is defined as $Q(p)=F^{-1}(p) = inf\{x: F(x) >p\}$, $0<p< 1$ where $F(x)$ is the distribution function.
-There are two broad approaches to quantile estimation, viz, parameteric and non-parameteric.
+There are two broad approaches to quantile estimation, viz, parametric and non-parameteric.
 The benefit of using a non-parametric estimator is that there are less rigid assumptions made about the nature of the underlying distribution of the data.
 Sample quantiles could be used for estimation in a non-parametric setup.
-@Hyndman1996-ty describes the difficulty in defining sample quantiles and recommends the use of median-unbiased estimator because of "desirable properties of a quantile estimator and can be defined independently of the underlying distribution.".
+@Hyndman1996-ty describes the difficulty in defining sample quantiles and recommends the use of median-unbiased estimator because of _*"desirable properties of a quantile estimator and can be defined independently of the underlying distribution."*_.
 The `stats::quantile()` function in @R-language could be used for practical implementation where type = 8 refers to the algorithm corresponding to the median-unbiased estimator.
+The default quantile chosen in this paper is percentiles computed for $p = {0.01, 0.02, \dots, 0.99}$, where for example, the $99^{th}$ percentile would be the value corresponding to $p=0.99$ and hence 99% of the observations would lie below that.
 
@@
 
-The most common divergence measure between distributions is the Kullback-Leibler (KL) divergence[@Kullback1951-jy] introduced by Solomon Kullback and Richard Leibler in 1951.
-The KL divergence, denoted $D(p(x), q(x))$ is a non-symmetric measure of the difference between two probability distributions $p(x)$ and $q(x)$ and is interpreted as the amount of information lost when $q(x)$ is used to approximate $p(x)$.
+The most common divergence measure between distributions is the Kullback-Leibler (KL) divergence [@Kullback1951-jy] introduced by Solomon Kullback and Richard Leibler in 1951.
+The KL divergence denoted by $D(q_1||q_2)$ is a non-symmetric measure of the difference between two probability distributions $q_1$ and $q_2$ and is interpreted as the amount of information lost when $q_2$ is used to approximate $q_1$.
 Although the KL divergence measures the “distance” between two distributions, it is not a distance measure since it is not symmetric and does not satisfy the triangle inequality.
@@
 The square root of the Jensen-Shannon divergence is a metric, often referred to as Jensen-Shannon distance.
-Other common measures of distance are Hellinger distance, total variation distance and Fisher information metric.
-
-In the context of this paper, the pairwise distances between the distributions of the measured variable are computed through Jensen-Shannon distance (JSD) which is based on Kullback-Leibler divergence and is defined by,
-
-$$JSD(P||Q) = \frac{1}{2}D(P||M) + \frac{1}{2}D(Q||M)$$
-where $M = \frac{P+Q}{2}$ and 
-$D(P||Q) := \int^\infty_{-\infty} p(x)f(\frac{p(x)}{q(x)})$ is the KL divergence between distributions $p(x)$ and $q(x)$.
-Probability distributions are estimated through quantiles instead of kernel density so that there is minimal dependency on selecting kernel or bandwidth.
+Other common measures of distance between distributions are Hellinger distance, total variation distance and Fisher information metric.
+
+In this paper, the pairwise distances between the distributions of the measured variable are computed through Jensen-Shannon distance (JSD), defined by,
+
+$$JSD(q_1||q_2) = \frac{1}{2}D(q_1||M) + \frac{1}{2}D(q_2||M)$$
+where $M = \frac{q_1+q_2}{2}$ and 
+$D(q_1||q_2) := \int^\infty_{-\infty} q_1(x)f(\frac{q_1(x)}{q_2(x)})$ is the KL divergence between distributions $q_1$ and $q_2$.
+
+Furthermore, these distances are distributed as chi-squared with $m$ degrees of freedom (Menendez1997-in), where the continuous distribution is being discretized with $m$ discrete values.
+Taking sample percentiles to approximate the integral would mean taking $m = 99$.
+As the degrees of freedom $m$ get larger, the chi-square distribution approaches the normal distribution.
+
+  <!-- Thus, by CLT, ${\chi^2}_{m} \tilde{} N(m, 2m)$, which would depend on the number of discretization used to approximate the continuous distribution.  -->
+  <!-- Then $b_n = 1-1/n$ quantile of the normal distribution and $a_n = 1/[n*\phi(b_n)]$ where $\phi$ is the normal density function. $n$ is the number of pairwise comparisons being made. -->
 

### 2021-02-28 paper/main.Rmd
re-writing computation section

@@
 
-## Definition
-
-Consider two cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.
-Let the pairwise distances between pairs $(a_{j} b_{k}, a_{j'}b_{k'})$ be denoted as $d_{(jk, j'k')} = JSD(a_{j}b_{k}, a_{j'}b_{k'})$.
+## Computation
+
+The distance measure $wpd$ between two cyclic granularities $A$ and $B$ is aimed to capture the strength of the structure by estimating the maximum within-group and between-group variations.
+The steps employed for computing the distance measure is summarized as follows:
+
+<!-- Hence, differences in distributions of the measured variable are computed between all pairs of categories $(a_{j} b_{k}, a_{j'}b_{k'}): j = 1, 2, \dots, J\}, B = \{ b_k: k = 1, 2, \dots, K\}$.
+Percentiles of $v_{jk}$ and $v_{j'k'}$ are computed and stored in $q_{jk}$ and $q_{j'k'}$ respectively.
+Then the pairwise distances between pairs $(a_{j} b_{k}, a_{j'}b_{k'})$ be denoted as $d_{(jk, j'k')} = JSD(q_{jk}, q_{j'k'})$ is computed.
 Pairwise distances could be within-facets or between-facets.
@@
 Pairwise distances are between-facets ($d_{b}$) when they are considered between pairs of the form $(a_{j}b_{k}, a_{j}b_{k'})$.
+Number of between-facet distances would be $^{K}C_2*J$ and number of within-facet distances are $K*(J-1)$ (ordered) and $^{J}C_2*K$ (un-ordered).
+The pairwise distances $d_{(jk, j'k')}$ are transformed using a suitable tuning parameter ($0<\lambda<1$) depending on if they are $d_{b}$ or $d_{w}$ as follows: -->
 
@@
 
-From Section \ref{sec:idea}, the idea is to put more weights on within-facet distances than between-facet distances.
-Hence, for a suitable tuning parameter $0<\lambda<1$, the pairwise distances $d_{(jk, j'k')}$ are transformed based on the distance type as follows:
+1. Fix harmony pair $(A, B)$.
+
+<!-- The set of pairs of categories is of the form $(a_{j} b_{k}, a_{j'}b_{k'}): j = 1, 2, \dots, J\}, B = \{ b_k: k = 1, 2, \dots, K\}$. -->
+
+2. Percentiles of $v_{jk}$ are computed and stored in $q_{jk}$. Repeat for all pairs of categories of the form $(a_{j} b_{k}, a_{j'}b_{k'}): j = 1, 2, \dots, J\}, B = \{ b_k: k = 1, 2, \dots, K\}$.
+
+3. The pairwise distances between pairs $(a_{j} b_{k}, a_{j'}b_{k'})$  denoted by $d_{(jk, j'k')} = JSD(q_{jk}, q_{j'k'})$ is computed.
+
+4. The pairwise distances $d_{(jk, j'k')}$ is transformed using a suitable tuning parameter ($0<\lambda<1$) depending on if they are within-facet($d_w$) or between-facets($d_b$) as follows:
 
@@
 
-The maximum weighted pairwise distances are defined as:
-$$wpd = max_{j, j', k, k'}(d*_{(jk), (j'k')})
-\forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}$$.
+5. The wpd is then computed as $wpd = max_{j, j', k, k'}(d*_{(jk), (j'k')}) \forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}$.
+
+6. Repeat for all harmony pairs in $N_C$.
+
+\noindent Pairwise distances could be within-facets or between-facets.
+Figure \ref{fig:distance-explain} illustrates how the within-facet or between-facet distances are defined.
+Pairwise distances are within-facets when $b_{k} = b_{k'}$, that is, between pairs of the form $(a_{j}b_{k}, a_{j'}b_{k})$ as shown in panel (3) of Figure \ref{fig:distance-explain}.
+If categories are ordered (like all temporal cyclic granularities), then only distances between pairs where $a_{j'} = (a_{j+1})$ are considered (panel (4)).
+Pairwise distances are between-facets when they are considered between pairs of the form $(a_{j}b_{k}, a_{j}b_{k'})$.
+Number of between-facet distances would be $^{K}C_2*J$ and number of within-facet distances are $K*(J-1)$ (ordered) and $^{J}C_2*K$ (un-ordered).
+If the measure is intended to put more importance in pointing towards distributional differences between x categories, a $\lambda>0.5$ should be chosen.
+
+<!-- 5. Compute distribution of maximum distance ($M$) by shuffling the data $200$ times and finishing Steps1-4 in each case. Scale $M$ using the mean and sd of the distribution.
+
+5. Use Steps 1-4 to compute maximum distance for $\forall k \in  \{1, 2, \ldots, K\}$.
+
+6. Compute the distance measure MMPD_raw = median $(M_1, M_2, \dots, M_K)$.
+
+<!-- All of these distances are then aggregated by taking the maximum from these distances to obtain $wpd$. -->
 

### 2021-02-28 paper/main.Rmd
intro of normalisation and methodology re-written

@@
 The distance measure $wpd$ between two cyclic granularities $A$ and $B$ is aimed to capture the strength of the structure by estimating the maximum within-group and between-group variations.
+Furthermore, the intended aim of $wpd$ is to capture differences in categories irrespective of the distribution from which the data is generated.
+Hence, as a pre-processing step,the raw data is normal quantile transformed so that the quantile of the transformed data follows a standard normal distribution.
 The steps employed for computing the distance measure is summarized as follows:
+
+<!-- The values of $wpd$ indeed depend upon the underlying distribution.
+This is also not desirable as the intended aim of $wpd$ is to capture differences in categories irrespective of the distribution from which the data is generated.
+The steps employed for computing the distance measure is summarized as follows: -->
 
@@
 
-1. Fix harmony pair $(A, B)$.
+1. Perform NQT on the measured variable $v_t$ to obtain $v^*_t$.
+
+2. Fix harmony pair $(A, B)$.
 
@@
 
-2. Percentiles of $v_{jk}$ are computed and stored in $q_{jk}$. Repeat for all pairs of categories of the form $(a_{j} b_{k}, a_{j'}b_{k'}): j = 1, 2, \dots, J\}, B = \{ b_k: k = 1, 2, \dots, K\}$.
-
-3. The pairwise distances between pairs $(a_{j} b_{k}, a_{j'}b_{k'})$  denoted by $d_{(jk, j'k')} = JSD(q_{jk}, q_{j'k'})$ is computed.
-
-4. The pairwise distances $d_{(jk, j'k')}$ is transformed using a suitable tuning parameter ($0<\lambda<1$) depending on if they are within-facet($d_w$) or between-facets($d_b$) as follows:
+3. Percentiles of $v^*_{jk}$ are computed and stored in $q_{jk}$. Repeat for all pairs of categories of the form $(a_{j} b_{k}, a_{j'}b_{k'}): j = 1, 2, \dots, J\}, B = \{ b_k: k = 1, 2, \dots, K\}$.
+
+4. The pairwise distances between pairs $(a_{j} b_{k}, a_{j'}b_{k'})$  denoted by $d_{(jk, j'k')} = JSD(q_{jk}, q_{j'k'})$ is computed.
+
+5. The pairwise distances $d_{(jk, j'k')}$ is transformed using a suitable tuning parameter ($0<\lambda<1$) depending on if they are within-facet($d_w$) or between-facets($d_b$) as follows:
 
@@
 
-6. Repeat for all harmony pairs in $N_C$.
+6. Repeat Steps 2-5 for all harmony pairs in $N_C$.
 
@@
 
-A simulation study is carried out to explore how $wpd$ performs under various designs, its parameters and limitations.
-To this end, simulations were carried out for four different designs and the following factors that could potentially have an impact on the values of $wpd$:
+Simulations were carried out to explore the behavior of $wpd$ under the following factors that could potentially impact the values of $wpd$:
 
@@
 - $n$ (sample size for each combination of categories)
-- $nsim$ (number of simulations)
-- $nperm$ (number of permutations of data)  
-- $designs$  
-$D_{null}$  (No difference in distribution)  
-$D_{var_f}$ (Difference in distribution only across facets)  
-$D_{var_x}$ (Difference in distribution only across x-axis)  
-$D_{var_{all}}$ (Difference in distribution in both facets and x-axis)
+- $designs$ ($D_{null}$, $D_{var_f}$, $D_{var_x}$ and $D_{var_{all}}$)
+
+<!-- - $nsim$ (number of simulations) -->
+<!-- - $nperm$ (number of permutations of data)   -->
 
@@
 The dependence of $wpd$ on $nx$ and $nfacet$ under $D_{null}$ is presented here, which lays the foundation for the next section.
-The rest of the results that discusses the relationship of the $wpd$ with other factors is presented in the Supplementary section of the paper.
-
-### Design of the simulation study
+The rest of the results that discusses the relationship of the $wpd$ with other factors is presented in details in the Supplementary section of the paper.
+They show that the designs $D_{var_f}$ and $D_{var_x}$ intersect at $\lambda = 0.5$ and hence for up-weighing designs of the form $D_{var_x}$, $\lambda = 0.67$ has been considered for computation of $wpd$ in the rest of the paper.
+
+### Simulation design
 
@@
 That is, if we consider the panel  $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
-The values of $\lambda$ is set to $0.67$ and values of raw wpd $wpd$ is obtained.
-This entire design applies to the null cases and hence there is no difference in distribution between any categories in the panel.
+The values
+of $wpd$ is obtained for each of the panels.
+This design corresponds to $D_{null}$ as each combination of categories in a panel are drawn from the same distribution.
+Furthermore, the data is simulated for each of the panels $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
 
@@
 
-Figure \ref{fig:raw} shows the distribution of $wpd$ plotted across different nx and nfacet categories.
-Both shape and scale of the distributions change across panels.
-This is not desirable as it would mean we would not be able to compare $wpd$ across different $nx$ and $nfacet$ as each of them are drawn from distributions with different locations and scale.
-In Figure \ref{fig:quadratic}, we see how the median of $wpd_{raw}$ varies with the total number of distances $nx*nfacet$ for each panel.
+Figure \ref{fig:raw} shows the distribution of $wpd$ plotted across different $nx$ and $nfacet$ categories.
+Since under $D_{null}$, there is no difference in distributions across different categories, we expect the distance measure $wpd$ to reflect that as well and have the same null distribution across categories.
+But Figure \ref{fig:raw} shows that both the location and scale of the distributions change across panels.
+This is not desirable under $D_{null}$ as it would mean comparisons of $wpd$ values is not appropriate across different $nx$ and $nfacet$.
+Figure \ref{fig:quadratic} shows how the median of $wpd_{raw}$ varies with the total number of distances $nx*nfacet$ for each panel.
 The median increases abruptly for lower values of $nx*nfacet$ and slowly for higher $nx*nfacet$.
 
-```{r raw, fig.cap = "Distribution of raw wpd is plotted across different nx and nfacet categories. Both shape and scale of the distribution changes for different nx and nfacet categories."}
+<!-- Furthermore, simulation results also show that the values of $wpd$ indeed depend upon the underlying distribution.
+This is also not desirable as the intended aim of $wpd$ is to capture differences in categories irrespective of the distribution from which the data is generated.
+-->
+
+```{r raw, fig.cap = "Distribution of $wpd$ is plotted across different $nx$ and $nfacet$ categories. Both shape and scale of the distribution changes for different nx and nfacet categories."}
 G21 <- read_rds("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds")
@@
   scale_x_continuous(breaks = scales::breaks_extended(3)) + 
-  xlab("raw wpd")
-```
-
-```{r quadratic, fig.cap = "$wpd_{raw}$ is plotted against nx*nfacet and the blue line represents the median of the multiple values for each nx*nfacet levels."}
+  xlab("wpd")
+```
+
+```{r quadratic, fig.cap = "$wpd$ is plotted against $nx*nfacet$ (the maximum number of pairwise comparisons) and the blue line represents the median of the multiple values for each $nx*nfacet$ levels.
+The median increases abruptly for lower values of $nx*nfacet$ and slowly for higher $nx*nfacet$."}
 G21 %>% 
   ggplot(aes(x=nx*nfacet, y = value)) +
-  geom_point() + stat_summary(fun=median, geom="line", aes(group=1), color = "blue") + xlab("nx*nfacet") + ylab("raw wpd")
+  geom_point() + stat_summary(fun=median, geom="line", aes(group=1), color = "blue") + xlab("nx*nfacet") + ylab("wpd")
 
@@
 
-The distribution of wpd is different for different levels of facets and x-axis levels.
-This is because the statistic maximum which is used to define $wpd$ is affected by the number of categories.
+The distribution of $wpd$ is different for different levels of facets and x-axis levels.
+This is because the statistics maximum which is used to define $wpd$ is affected by the number of comparisons (resulting pairwise distances).
 The measure would have higher values if $A$ or $B$ has higher levels.
-However, we would ideally want a higher value of the measure only if there is significant difference between distributions across facet or x-axis categories, and not because the number of categories $J$ or $K$ is high.
-Therefore, in order to compare $wpd$ across different combinations of facet and x-axis levels, we need to eliminate the impact of different levels of the facets and x-axis first and get a normalized measure.
-Henceforth we call the measure already discussed as $wpd_{raw}$ and the normalized measure as $wpd_{norm}$.
-The measure $wpd_{norm}$ could potentially lead to comparison of the measure across different panels and also identifying only the interesting panels from a data set.
+However, we would ideally want a higher value of the measure only if there is a significant difference between distributions across facet or x-axis categories, and not because the number of categories $J$ or $K$ is high.
+Therefore, in order to compare $wpd$ across different combinations of facet and x-axis levels, we need to eliminate the impact of different number of comparisons and get a normalized measure.
+Henceforth, we call the normalized measure as $wpd_{norm}$.
+The measure $wpd_{norm}$ could potentially lead to comparison of the measure across different panels and also help distinguishing the interesting panels from a data set.
 We discuss two approaches for normalization, both of which are based on the simulation results.
@@
 
-## Simulation environment
-
-Simulation studies were carried out to study the behavior of $wpd$, build the normalization method as well as compare and evaluate different normalization approaches.
-R version 4.0.1 (2020-06-06) is used with the platform: x86_64-apple-darwin17.0 (64-bit) running under: macOS Mojave 10.14.6 and MonaRCH, which is a next-generation HPC/HTC Cluster, designed from the ground up to address the computing needs of the Monash HPC community.
-
 ## Methodology
@@
 We need a transformation on ${wpd}$ which will make it independent of the values of $nx*nfacet$.
-Two approaches have been employed for that purpose, the first one involves fitting a model and the latter involves a permutation method to make the distribution of the transformed $wpd$ similar across different $nx$ and $nfacet$.
+Two approaches have been employed for that purpose, the first one involves fitting a model and the latter involves a permutation method to make the distribution of the transformed $wpd$ similar for different comparisons.
 
@@
 
-The permutation approach ensures that the distribution of the normalized distance measure has the same mean and standard deviation across all combinations of $nx_i$ and $nfacet_j$.
-The normalized distances through permutation is computed as follows: $x^{perm}_{k} =  (x_{k} - mean_l(x_{k,l}))/sd_l(x_{k, l})$,  $x^{perm}_{k}$ is the value of the $wpd_{perm}$ for the $k^{th}$ panel.
-Standardizing the variable $wpd_{perm}$ in this approach leads to $location = 0$ and $scale = 1$ for this variable.
-
-While this works successfully to make the mean and standard deviation across different $nx$ and $nfacet$ (as seen in Figure \ref{fig:}), it is computationally heavy and time consuming, and hence less user friendly when being actually used in practice.
+This method is somewhat similar in spirit to bootstrap or permutation tests, where the goal is to test the hypothesis that the groups under study have identical distributions.
+This method, in essence, accomplishes a different goal of making the location and scale of different groups (panels) same under $D_{null}$.
+The steps are as follows:
+
+1. Compute $wpd$ for a harmony pair (A, B) for the original measured variable $v_t$ and store it in $wpd^{orig}$.
+
+2. Consider a permutation of the original measured variable $v_t^{perm_1}$ and again compute $wpd$ for the permuted data. Store it in $wpd^{perm_1}$.
+
+3.
+Repeat Step 2 for a large number ($nperm = 200$) of random permutations of the data yielding $nperm$ values : $wpd^{perm_1}, wpd^{perm_2}, \dots, wpd^{perm_{nperm}}$.
+Store the vector in $wpd^{perm}$.
+
+4. Define $wpd^{perm}_{norm} = \frac{(wpd^{orig} - \bar{wpd^{perm}})}{sd(wpd^{perm})}$, where $\bar{wpd^{perm}}$ and $sd(wpd^{perm})$ are the mean and standard deviation of $wpd^{perm}$ respectively.
+
+<!-- Let $\{x_{k,l}, k = 1, 2, \dots, nx*nfacet, l = 1, 2, \dots, nsim\}$ denote the values of $wpd$ obtained from the simulation study for $k^{th}$ panel in the $i^{th}$ simulation.
+Hence, for each of those $k$ panel, we have $nsim$ values of $wpd$.combinations of $nx_i$ and $nfacet_j$.
+The normalized distances through permutation is computed as follows: $x^{perm}_{k} =  (x_{k} - mean_l(x_{k,l}))/sd_l(x_{k, l})$,  $x^{perm}_{k}$ is the value of the $wpd_{perm}$ for the $k^{th}$ panel-->
+
+Standardizing the variable $wpd$ in the permutation approach ensures that the distribution of $wpd^{perm}_{norm}$ has the same $mean = 0$ and $sd = 1$ across all comparisons under $D_{null}$.
+While this works successfully to make the location and scale similar across different $nx$ and $nfacet$ (as seen in Figure \ref{fig:norm}), it is computationally heavy and time consuming, and hence less user friendly when being actually used in practice.
 Hence, we propose another approach to normalization which is more approximate than exact but still has the same accuracy when compared to the permutation approach.
+
+```{r norm, fig.cap = "Distribution of $wpd^{perm}_{norm}$ is plotted across different $nx$ and $nfacet$ categories.
+Both shape and scale of the distributions are now similar for different panels under the null design."}
+G21_norm <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_Gamma21.rds"))
+
+G21_norm %>% 
+  ggplot(aes(x = value)) + 
+  geom_density(fill = "blue") +
+  facet_grid(nx~nfacet,
+             labeller = "label_both") + 
+  scale_x_continuous(breaks = scales::breaks_extended(3)) + 
+  xlab("wpd normalised using permutation approach")
+```
 
@@
 ```
+
+# Simulation environment
+
+Simulation studies were carried out to study the behavior of $wpd$, build the normalization method as well as compare and evaluate different normalization approaches.
+R version 4.0.1 (2020-06-06) is used with the platform: x86_64-apple-darwin17.0 (64-bit) running under: macOS Mojave 10.14.6 and MonaRCH, which is a next-generation HPC/HTC Cluster, designed from the ground up to address the computing needs of the Monash HPC community.
 

### 2021-02-28 paper/main.Rmd
modeling approach to normalization

@@
 Furthermore, the data is simulated for each of the panels $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
+$wpd_{l, s}$ denotes the value of $wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.
 
@@
 This is not desirable under $D_{null}$ as it would mean comparisons of $wpd$ values is not appropriate across different $nx$ and $nfacet$.
-Figure \ref{fig:quadratic} shows how the median of $wpd_{raw}$ varies with the total number of distances $nx*nfacet$ for each panel.
+Figure \ref{fig:quadratic} shows how the median of $wpd$ varies with the total number of distances $nx*nfacet$ for each panel.
 The median increases abruptly for lower values of $nx*nfacet$ and slowly for higher $nx*nfacet$.
@@
 
-A log-linear model is fitted to see how the values of $wpd_{raw}$ changes with the values of $nx$ and $nfacet$.
-The model is of the form $$y_k = a+b*log(z_k) + e_k$$, where, $y_k = median_l(x_{k, l})$ and $e_k$ are idiosyncratic errors.
-We have gone with the approach of fitting a linear regression model to estimate the parameters $a$ and $b$.
+A linear model is fitted to model the relationship between $wpd$ and $nx*nfacet$.
+The model is of the form $$y_l = a+b*log(z_l) + e_l$$, where, $y_l = median_m(x_{l, m})$, $z_l$ is the $l^{th}$ panel and $e_l$ are idiosyncratic errors, with parameters $a$ and $b$ being estimated from the data generated through the simulation study described in Section \ref{sec:sim-study}.
 The estimates and other model summary is given in \ref{tab:linear-model}.
@@
 ```{r linear-model, message=FALSE}
-G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds"))
+G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds"))
 
@@
 # fit model median to log(nx*nfacet)
-fit_lm2 <- lm(actual ~ poly(log(`nx * nfacet`) ,1, raw=TRUE), data = G21_median)
-
-summary(fit_lm2)
-```
-
-The final idea is to find a transformation on $wpd_{raw}$ which would remove the effect of $nx*nfacet$ on $wpd_{raw}$ and thus is defined as follows:
-$y^* =  y - \hat b*log(z)$, where 
-$y^*$ is the $median(wpd_{norm})$, 
-$y$ is the $median(wpd_{raw})$,
-$\hat b$ is the estimated value of the parameter $b$, 
-and $z = nx*nfacet$.
-
-The above takes care of the mean and the heterogeneity of the median transformed measure.
-But, the original distribution will still have some dissimilarities in shape and location specially for small values of $nx$ and $nfacet$ as could be seen in \ref{fig:}
-
-```{r}
+fit_lm2 <- lm(actual ~ log(`nx * nfacet`) , data = G21_median)
+
+broom::tidy(fit_lm2) %>% kable(caption = "Results of linear model to capture the relationship between wpd and number of comparisons.")
+```
+
+<!-- # ```{r} -->
+<!-- # results3 <- broom::tidy(fit_lm2) -->
+<!-- # library(ggfortify) -->
+<!-- # autoplot(fit_lm2, which = 1:6) + theme_minimal() -->
+<!-- # ``` -->
+
+The idea is to find a transformation on $wpd$ which would remove the effect of $nx*nfacet$ on $wpd$ and thus is defined as the residuals:
+$y^* =  y - \hat a -  \hat b*log(z)$, where 
+$y^*$ is the $wpd_{norm}^{linear}$, 
+$\hat a$ and $\hat b$ are the estimated values of the parameter $a$ and $b$ and $z = nx*nfacet$.
+
+Defining $wpd_{norm}^{linear}$ in this way forces the mean to be zero and variability to be uniform across the median $wpd$ values as could be seen in Figure \ref{fig:resi-linear}.  
+<!-- But, the original distribution will still have some dissimilarities in shape and location specially for small values of $nx$ and $nfacet$ as could be seen in \ref{fig:} -->
+
+```{r resi-linear, fig.cap = "$wpd_{norm}^{linear}$ which are defined as the residuals of the linear model have mean zero and are homogenous.
+Further, by design they are independent of the $nx*nfacet$ and hence could be a potential candidate for $wpd_norm$."}
 
@@
   geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
-  ylab("wpd_norm =  wpd_raw - slope*log(nx*nfacet)")
+  ylab("wpd normalised using linear modelling approach")
 
@@
 
-In the linear model approach, $wpd_{raw} \in R$ was assumed, whereas, $wpd_{raw}$, Jensen-Shannon Distance (JSD) lies between 0 and 1.
-Furthermore, JSD follows a Chi-square distribution, which is a special case of Gamma distribution and hence belongs to exponential family of distributions.
-Therefore, we can fit a generalized linear model instead of a linear model to allow for the response variable to follow a Gamma distribution.
-The inverse link is used when we know that the mean response is bounded, which is applicable in our case since $0 \leq wpd_{raw}\leq 1$.
+In the linear model approach, $wpd\in R$ was assumed, whereas, $wpd$, Jensen-Shannon Distance (JSD) lies between 0 and 1.
+Furthermore, JSD follows a Chi-square distribution, which is a special case of Gamma distribution.
+Therefore, a generalized linear model could be fitted instead of a linear model to allow for the response variable to follow a Gamma distribution.
+The inverse link is used when we know that the mean response is bounded, which is applicable in our case since $0 \leq wpd\leq 1$.
 
 We fit a Gamma generalized linear model with the inverse link which is of the form:  
-$$y = a+b*log(x) + e$$, where $y = median(wpd_{raw})$, $x = nx*nfacet$.
-Let $E(y) = \mu$ and $a + b*log(x) = g(\mu)$ where $g$ is the link function.
-Then $g(\mu)=  1/mu$ and $\hat \mu  = 1/(\hat a + \hat b log(x))$.
-The residuals from this model $(y-\hat y) = (y-1/(\hat a + \hat b log(x)))$ would be expected to have no dependency on $x$.
-Thus,  $wpd_{glm}$ is chosen as the residuals from this model and is defined as:
-$wpd_{glm} = wpd_{raw} - 1/(\hat a + \hat b*log(nx*nfacet))$.
+$$y_l = a+b*log(z_l) + e_l$$, where $y_l = median_m(x_{l, m})$, $z_l$ is the $l^{th}$ panel and $e_l$ are idiosyncratic errors.
+Let $E(y) = \mu$ and $a + b*log(z) = g(\mu)$ where $g$ is the link function.
+Then $g(\mu)=  1/\mu$ and $\hat \mu  = 1/(\hat a + \hat b log(z))$.
+The residuals from this model $(y-\hat y) = (y-1/(\hat a + \hat b log(z)))$ would be expected to have no dependency on $z$.
+Thus,  $wpd_{norm}^{glm}$ is chosen as the residuals from this model and is defined as:
+$wpd_{glm} = wpd - 1/(\hat a + \hat b*log(nx*nfacet))$.
 
@@
 
-G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds"))
+G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds"))
 
@@
   geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
-  ylab("wpd_glm = wpd_raw - 1/(a  + b*log(nx*nfacet))")
+  ylab("wpd_glm = wpd - 1/(a  + b*log(nx*nfacet))")
+```
+
+```{r glm-tab}
+broom::tidy(glm_fit) %>% kable(caption = "Results of generalised linear model to capture the relationship between wpd and number of comparisons.")
 ```
@@
 
-G21_glm$wpd_glm_scaled %>% sd()
+#G21_glm$wpd_glm_scaled %>% sd()
 
@@
 Hence, the computational load of permutation approach could be alleviated by using the modeling approach for the higher $nx$ and $nfacet$, however, it is important that we use the permutation approach for lower $nx$ and $nfacet$.
-However, it is  difficult to compare the transformed $wpd$ from both of these approaches, since each of the variables is measured on a different scale (each of them have location 0).
+However, it is  difficult to compare the transformed measure from both of these approaches, since each of the variables is measured on a different scale (although each of them have location 0).
 The transformed variables from the two approaches could be brought to the same scale so that for smaller categories, permutation approach is used and for larger categories, we can stick to modeling approach.
-These could be done through the following:
-
- - Making the range of both the variables same by using min-max scaling method.
-In practice, however, we would only have one value of $wpd_{raw}$ which we need to transform using the modeling approach.
+
+<!-- These could be done through the following: -->
+
+<!--  - Making the range of both the variables same by using min-max scaling method.
+In practice, however, we would only have one value of $wpd$ which we need to transform using the modeling approach.
 Hence, min-max scaling approach could not be used here.
-
- - Standardizing the variables and expressing scores at standard deviation units.
+-->
+
+<!--  - Standardizing the variables and expressing scores at standard deviation units.
 Again in practice, however, we would only have one value of $wpd_{raw}$ which we need to transform using the modeling approach.
 Hence, standardizing scores could not be used here as we do not have the mean and standard deviation of a series while using transformation using modeling.
-
-- Make the location and scale of both the approaches similar so that they could be compared.
-Please note that the range of values could be different in this case, however location and scale are brought to same levels.)
-
-The measure $wpd_{glm}$ has location 0 and standard deviation ~ 0.003, whereas the measure $wpd_{permutation}$ which is a z-score, has a normal distribution with location 0 and standard deviation 1.
-To bring them to the same scale, we have defined $wpd_{glm-scaled} = wpd_{glm}*300$, which brings the standard deviation of $wpd_{glm-scaled}$ to almost 1, without changing the location.
-
-The measure $wpd_{glm-scaled}$ seems to roughly follow a normal distribution except in the tails as could be seen in Figure \ref{fig:hist-qq} and the very method of permutation approach ensures that $wpd_{permutation}$ is also normally distributed.
+-->
+
+<!-- - Make the location and scale of both the approaches similar so that they could be compared.
+Please note that the range of values could be different in this case, however location and scale are brought to same levels.) -->
+
+The measure $wpd_{glm}$ has an estimated location of 0 and standard deviation ~ $0.003$, whereas the measure $wpd_{perm}$ which is a z-score, has a normal distribution with location 0 and standard deviation 1.
+To bring them to the same scale, we have defined $wpd_{glm-scaled} = wpd_{glm}*320$, which brings the standard deviation of $wpd_{glm-scaled}$ to almost 1, without changing the location.
+The measure $wpd_{glm-scaled}$ seems to roughly follow a normal distribution except in the tails as could be seen in Figure \ref{fig:hist-qq} and the very method of permutation approach ensures that $wpd_{perm}$ is also normally distributed.
 Further, they are brought to the similar scale and location and hence could be compared.
 
-```{r hist-qq, fig.cap = "In panel a, the histogram of $wpd_{glm-scaled}$ is plotted.
-In parl b, the QQ plot is shown with the theoretical quantiles on the x-axis and $wpd_{glm-scaled}$ quantiles on the y-axis.
+```{r hist-qq, fig.cap = "In panel a, the histogram of $wpd_{glm-scaled}^{norm}$ is plotted.
+In part b, the QQ plot is shown with the theoretical quantiles on the x-axis and $wpd_{glm-scaled}$ quantiles on the y-axis.
 The distribution looks symmetric and looks like normal except in the tails."}
@@
   geom_histogram(aes(x = wpd_glm_scaled)) +
-  ggtitle("a")
+  ggtitle("a") + xlab("transformed wpd using glm approach")
 
@@
 
-```{r dist-new-same-scale-link, fig.cap="w$pd_permutation$ and $wpd_{glm-scaled}$ are plotted together on the same scale.
+```{r dist-new-same-scale-link, fig.cap="wpd_perm$ and $wpd_{glm-scaled}$ are plotted together on the same scale.
 They also have the same location and hence the values from these two approaches could be compared across panels.
@@
 #
-# G21_permutation <- read_rds("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_Gamma21.rds") %>%
-#   rename("wpd_permutation" = "value")
-# 
-# 
+G21_permutation <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds")) %>%
+  rename("wpd_permutation" = "value")
+
 # G21_model_data <- G21 %>%
@@
 G21_all_data <- G21_permutation %>% 
-  left_join(G21_lm, by = c("nx", "nfacet", "perm_id")) %>% 
+  # left_join(G21_lm, by = c("nx", "nfacet", "perm_id")) %>% 
   left_join(G21_glm, by = c("nx", "nfacet", "perm_id")) %>% 
-  pivot_longer(cols = c(3, 10),
+  pivot_longer(cols = c(3, 7),
                names_to = "type_estimate",
@@
 
+Thus, the $wpd_{norm}$ is defined as follows:
+
+\begin{equation}
+wpd_{norm} =
+\begin{cases}
+wpd_{norm}^{perm},& \text{if } J, K <=5\\
+wpd_{norm}^{glm-scaled},              & \text{otherwise}\\
+\end{cases}
+\end{equation}
+
 ## Properties
 
-This section reports the results of a simulation study that was carried out to evaluate the behavior of $wpd_{norm}$.
+This section reports the results of a simulation study that was carried out to evaluate the behavior of $wpd_{norm}$ under different designs and other potential factors.
 The behavior of $wpd_{norm}$ is explored in designs where there is in fact difference in distribution between facet categories ($D_{var_f}$) or across x-categories ($D_{var_x}$) or both ($D_{var_{all}}$).
@@
 
-The tabulated values and graphical representations of the simulation results are provided in Appendix.
+The tabulated values and graphical representations of the simulation results are provided in the Supplementary paper.
 The learning from the simulations are as follows: The values of $wpd_{norm}$ is least for $D_{null}$, followed by
-$D_{var_f}$, $D_{var_x}$) and $D_{var_{all}}$). This is a desirable result since the measure $wpd_{norm}$ was designed such that this relationship holds.
+$D_{var_f}$, $D_{var_x}$) and $D_{var_{all}}$).
+This is a desirable result since the measure $wpd_{norm}$ was designed such that this relationship holds.
 Furthermore, the distribution of the measure $wpd_{norm}$ does not change for different facet and x categories.
 The distribution of $wpd_{norm}$ looks similar with at least the mean and standard of the distributions being uniform across panels.
-This means,  $wpd_{norm}$ could be used to measure differences in distribution across panels.
+This means $wpd_{norm}$ could be used to measure differences in distribution across panels.
 Also, note that since the data is processed using normal-quantile-transform, this measure is independent of the initial distribution of the underlying data and hence is also comparable across different data sets.
 This is valid for the case when sample size $ntimes$ for each combination of categories is at least 30 and  $nperm$ used for computing $wpd_{norm}$ is at least 100.
-More detailed results about the properties of $wpd_{raw}$ and $wpd_{norm}$ could be found in Appendix.
+More detailed results about the properties of $wpd_{norm}$ could be found in the Supplementary paper.
 

### 2021-02-28 size.R

@@ -1,0 +1,85 @@
+library(readr)
+library(dplyr)
+library(hakear)
+library(distributional)
+library(gravitas)
+library(here)
+sample_seed = seq(1000,2999, by = 10)
+nperm = 200
+simtable<-read_csv(here::here('simulations/sim_table/sim_table.csv'))
+# simulate one big data which will have all categories generated on the #fly
+
+
+
+all_seed <- lapply(sample_seed, function(x){
+  
+  set.seed(x)
+  
+  library(distributional)
+  sim_dist <- distributional::dist_normal(0,1)
+  sim_orig <-  distributional::generate(sim_dist, 50000)
+  sim_orig <- sim_orig[[1]]
+  lensim <- length(sim_orig)
+  
+  # for each row of the sim table
+  each_seed <- lapply(seq_len(nrow(simtable)), 
+                      function(scen){
+                        
+                        simj<-simtable[scen,] 
+                        nfacetj<-simj$nfacet
+                        nxj<-simj$nx
+                        
+                        id_x <- rep_len(seq_len(nxj), length.out = lensim) 
+                        id_facet <- rep_len(rep(seq_len(nfacetj), each = nxj), length.out = lensim) 
+                        
+                        sim_panel_orig <- bind_cols(id_x = id_x, id_facet = id_facet, sim_data = sim_orig)
+                        
+                        wpd_orig = compute_pairwise_norm_scalar(sim_panel_orig, 
+                                                                gran_x = "id_x",
+                                                                gran_facet = "id_facet",
+                                                                response = sim_data)
+                        
+                        wpd_sample <- lapply(seq_len(nperm), function(x){
+                          
+                          sample_data <- sample(sim_orig, size =  lensim)
+                          
+                          sim_panel_sample <- bind_cols(id_x = id_x, 
+                                                        id_facet = id_facet, 
+                                                        sim_data = sample_data)
+                          
+                          wpd =  compute_pairwise_norm_scalar(sim_panel_sample, 
+                                                              gran_x = "id_x",
+                                                              gran_facet = "id_facet",
+                                                              response = sim_data) %>% 
+                            as_tibble() %>% mutate(perm_id = x)
+                          
+                        }) %>% bind_rows()
+                        
[…]

### 2021-02-28 paper/main.Rmd
minor addition on properties of wpd-norm

@@
 
-```{r dist-new-same-scale-link, fig.cap="wpd_perm$ and $wpd_{glm-scaled}$ are plotted together on the same scale.
+```{r dist-new-same-scale-link, fig.cap = "$wpd_perm$ and $wpd_{glm-scaled}$ are plotted together on the same scale.
 They also have the same location and hence the values from these two approaches could be compared across panels.
 $wpd_{glm-scaled}$ would be used to normalise $wpd_{raw}$ for higher $nx$ and $nfacet$ and $wpd_{glm-scaled}$ would be used for smaller levels to alleviate the problem of computational time."}
-#
+
 G21_permutation <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds")) %>%
@@
 \begin{cases}
-wpd_{norm}^{perm},& \text{if } J, K <=5\\
-wpd_{norm}^{glm-scaled},              & \text{otherwise}\\
+wpd_{perm},& \text{if } J, K <=5\\
+wpd_{glm-scaled},              & \text{otherwise}\\
 \end{cases}

### 2021-03-01 paper/main.Rmd
replace existing application with 8 households

@@
 
-elec$date_time <- as.Date(elec$date_time)
-
 elec_linear <- elec %>% 
   ggplot() +
-  geom_line(aes(x = date_time, y = kwh, group = time)) +
+  geom_line(aes(x = date_time, y = kwh)) +
   facet_wrap(~id, nrow = 4, labeller = "label_both",
@@
   ggplot(aes(x=date_time, y = kwh)) +
+  geom_line(alpha = 0.5, size = 0.1) +
   facet_wrap(~id, scales = "free_y", ncol = 1, strip.position =  "right") +
-  geom_smooth() +
-  geom_point(alpha = 0.5, size = 0.1) +
-  gghighlight(date >as.Date("2018-02-05") & date < (as.Date("2018-02-12")))
+  gghighlight(date >as.Date("2018-02-05") & date < (as.Date("2018-02-12")), unhighlighted_params = list(colour = "blue"))
 
@@
 
-dotplot
+#myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
+
+heatplot <- elec_sig_split %>% 
+  ggplot() +
+  geom_tile(aes(x = x_variable,
+                 y = facet_variable, 
+                 fill = wpd)) + 
+  scale_fill_gradient2() +
+  theme(legend.position = "bottom") +
+  facet_wrap(~id, nrow = 1) +
+  coord_fixed() + 
+  guides(fill = guide_legend()) +
+  theme_void() +
+  theme_gray(base_size = 12, base_family = "Times") +
+  theme(panel.grid = element_blank(),
+        axis.text.x = element_text(angle = 60, hjust=1)
+        , legend.position = "bottom")
+  heatplot
 ```
@@
   rename("id" = "household_id",
-         "date_time" = "reading_datetime")
+         "date_time" = "reading_datetime") %>% 
+  mutate(date = date(date_time))
 
@@
   ggplot() +
-  geom_line(aes(x = date_time, y = kwh)) +
+  geom_line(aes(x = date_time, y = kwh),alpha = 0.7) +
   facet_wrap(~id, nrow = 8, labeller = "label_both",
@@
              scales = "free_y")
-elec_linear
-#+
- # geom_rect(aes(xmin = as.Date("2018-02-01"), xmax = as.Date("2018-02-28"), ymin = -Inf, ymax = Inf),colour="white", size=0.5, alpha=0.02)
-
-  # geom_rect(xmin = as.Date("2018-02-02"), xmax = as.Date("2018-02-04"), ymin = -Inf, ymax = Inf, fill = "pink", colour = pink)
-
-# elec_zoom <- elec_linear + 
-#   coord_x_date(xlim = c("2018-02-01", "2018-02-28")) +
-#   gghighlight(date >as.Date("2018-02-05") & date < (as.Date("2018-02-12")),
-#               unhighlighted_params = list(colour = "grey")) + geom_line(aes(x = date_time, y = kwh, group = time))
-
-# elec %>% dplyr::filter(date> as.Date("2018-02-01") & date<as.Date("2018-02-28"))
+
+elec_zoom <-  elec %>%
+  as_tibble() %>% 
+  filter(date >as.Date("2019-09-01") & date < (as.Date("2019-09-30"))) %>% 
+  ggplot(aes(x=date_time, y = kwh)) +
+  geom_line(size = 0.1, colour = "blue") +
+  facet_wrap(~id, 
+             scales = "free_y",
+             ncol = 1,
+             strip.position =  "right") +
+  gghighlight(date > as.Date("2019-09-15") & date < (as.Date("2019-09-21")), unhighlighted_params = list(colour = "black"))
+
+elec_linear + elec_zoom
 
@@
 
-dotplot <- elec_sig_split %>% 
+heatplot <- elec_sig_split %>% 
   ggplot() +
-  geom_point(aes(x = x_variable,
+  geom_tile(aes(x = x_variable,
                  y = facet_variable, 
-                 size = wpd, 
-                 fill = significant),
-             shape=21,
-             alpha= 0.8) +
-  scale_size_continuous() +
+                 fill = wpd)) + 
+  scale_fill_gradient2() +
   theme(legend.position = "bottom") +
-  scale_fill_viridis(discrete = TRUE, direction = 1) +
   facet_wrap(~id, nrow = 2) +
-  guides(fill = guide_legend(), 
-         size = guide_legend()) +
+  coord_fixed() + 
+  guides(fill = guide_legend()) +
+  theme_void() +
   theme_gray(base_size = 12, base_family = "Times") +
-   theme(legend.position = "bottom")
-
-dotplot
+  theme(panel.grid = element_blank(),
+        axis.text.x = element_text(angle = 60, hjust=1),legend.position = "bottom")
+  heatplot
+#            
+# dotplot <- elec_sig_split %>% 
+#   ggplot() +
+#   geom_point(aes(x = x_variable,
+#                  y = facet_variable, 
+#                  size = wpd, 
+#                  fill = significant),
+#              shape=21,
+#              alpha= 0.8) +
+#   scale_size_continuous() +
+#   theme(legend.position = "bottom") +
+#   scale_fill_viridis(discrete = TRUE, direction = 1) +
+#   facet_wrap(~id, nrow = 2) +
+#   guides(fill = guide_legend(), 
+#          size = guide_legend()) +
+#   theme_gray(base_size = 12, base_family = "Times") +
+#    theme(legend.position = "bottom")
 ```

### 2021-03-01 paper/main.Rmd
application section re-write

@@
 
-The smart meter data set from four households in Melbourne referred in @wang2020calendar has been utilized to see the use of the distance measure proposed in the paper.
-The data is a tsibble  containing half-hourly electricity consumption from Jan-2018 to Jun-2018 for each of the households, which is procured by them by downloading their data from the energy supplier/retailer.
-Demand data for these households are shown in a linear time scale in \autoref{fig:linear-scale}.
+The smart meter data set for eight households in Melbourne has been utilized to see the use of the $wpd_{norm}$ proposed in the paper.
+The data has been cleaned to be a `tsibble` (@wang2019tsibble) containing half-hourly electricity consumption from Jul-2019 to Dec-2019 for each of the households, which is procured by them by downloading their data from the energy supplier/retailer.
+Demand data for these households are shown in a linear time scale in \autoref{fig:linear-scale-8}.
 It is evident from the range of the demand data that these households vary in consumption levels as well as in their temporal patterns.
-In the left panel of \autoref{fig:linear-scale} (a), the linear representation of the entire time period is shown, whereas in panel B (right) a particular month is shown and furthermore a week has been highlighted to inspect if there is any daily or weekly periodic patterns in their behavior that is evident from the linear representation of the time series.
-We pick household id 2 and 4 for our analysis to see which periodic patterns are important in their behavior, if they are same or different and if it makes sense using our distance metric to select and rank the important harmonies.
-
-```{r linear-scale, fig.cap = "Electricity demand for four households are shown in different facets from Jan-18 to Jun-18 in Fig a and it has been zoomed in for Feb-18 in Fig b, where a week in Feb-18 has been highlighted.
-From the scales of Fig a, it is apparent that they have different level of consumption but all of them have some periodic behavior in terms of regular peaks and troughs.
-It is not clear which all periodic patterns exist.
-In fig b, periodic pattern is zoomed in for a month and we can see weekly patterns for the entire period and daily pattern for the highlighted week."}
-library(scales)
-library(tidyquant)
-library(gghighlight)
-
-elec_linear <- elec %>% 
-  ggplot() +
-  geom_line(aes(x = date_time, y = kwh)) +
-  facet_wrap(~id, nrow = 4, labeller = "label_both",
-             strip.position =  "right",
-             scales = "free_y") +
-  theme_pubclean() 
-#+
- # geom_rect(aes(xmin = as.Date("2018-02-01"), xmax = as.Date("2018-02-28"), ymin = -Inf, ymax = Inf),colour="white", size=0.5, alpha=0.02)
-
-elec_zoom <-  elec %>%
-  filter(date >as.Date("2018-02-01") & date < (as.Date("2018-02-28"))) %>% 
-  ggplot(aes(x=date_time, y = kwh)) +
-  geom_line(alpha = 0.5, size = 0.1) +
-  facet_wrap(~id, scales = "free_y", ncol = 1, strip.position =  "right") +
-  gghighlight(date >as.Date("2018-02-05") & date < (as.Date("2018-02-12")), unhighlighted_params = list(colour = "blue"))
-
-  # geom_rect(xmin = as.Date("2018-02-02"), xmax = as.Date("2018-02-04"), ymin = -Inf, ymax = Inf, fill = "pink", colour = pink)
-
-# elec_zoom <- elec_linear + 
-#   coord_x_date(xlim = c("2018-02-01", "2018-02-28")) +
-#   gghighlight(date >as.Date("2018-02-05") & date < (as.Date("2018-02-12")),
-#               unhighlighted_params = list(colour = "grey")) + geom_line(aes(x = date_time, y = kwh, group = time))
-
-elec_linear + elec_zoom +
-   xlab("Date") +
-  ylab("demand(in kwh)")
-# elec %>% dplyr::filter(date> as.Date("2018-02-01") & date<as.Date("2018-02-28"))
-
-```
-
-<!-- **Normal-quantile-transform**  -->
-
-<!-- **Characterizing empirical distributions through quantiles** ( write in the methodology maybe) -->
-
-<!-- **Computing JS distances between harmonies for each categories of the cyclic granularity involved** -->
-
-```{r raw-nqt}
-elec_raw <- elec %>% 
-  ggplot() +
-  geom_density(aes(x = kwh)) +
-  facet_wrap(~id, scales = "free_y", ncol = 1) +
-  xlab("demand (in kwh)")
-
-elec_nqt <- elec %>% 
-  dplyr::mutate(kwh_transformed = stats::qqnorm(kwh, plot.it = FALSE)$x) %>% 
-  ggplot() +
-  geom_density(aes(x = kwh_transformed))+
-  facet_wrap(~id, scales = "free_y", ncol = 1) +
-  xlab("NQT demand (in kwh)")
-
-# hour_day_raw <- elec %>% 
-#   tsibble::as_tsibble(index = date_time, key = id) %>% 
-#     create_gran("hour_day") %>% 
-#     ggplot() + 
-#     ggridges::geom_density_ridges(aes(y=hour_day, x = kwh))
-#   
-# hour_day_trans <- elec %>% 
-#   tsibble::as_tsibble(index = date_time, key = id) %>% 
-#     create_gran("hour_day") %>% 
-#   dplyr::mutate(kwh_transformed = stats::qqnorm(kwh, plot.it = FALSE)$x) %>% 
-#   ggplot() +
-#   ggridges::geom_density_ridges(aes(y=hour_day, x = kwh_transformed))
-
-elec_raw + elec_nqt
-
-```
-
-Let $y_{i, t}$ denote the electricity demand for $i^{th}$ household for time period $t$.
-This is expected to have an assymmetrical distribution as could be seen in \ref{fig:raw-nqt} and the Normal score transform has been applied to make it more symmetric.
-Let $y*_{i, t}$ denote the normal-quantile transformed electricity demand for $i^{th}$ household for time period $t$.
-Technically, this $y*_{i, t}$ is the linear granularity corresponding to half-hour since the interval of this data is 30 minutes.
-We consider coarser linear granularities like hour, day, week and month from the commonly used Gregorian calendar.
-Considering 4 linear granularities hour, day, week, month in the hierarchy table, the number of cyclic granularities is $N_C = (4 * 3/2) = 6$.
-We obtain cyclic granularities namely “hour_day”, “hour_week”, “hour_month”, “day_ week”, “day_month” and “week_month”, read as “hour of the day”, etc.
-Further, we add cyclic granularity day-type( “wknd wday”) to capture weekend and weekday behavior.
-Thus, we consider 7 cyclic granularities in the set of cyclic granularities of interest defined by $C_{N_C}$.
-We then compute the set of harmonies $H_{N_C}$  from $C_{N_C}$ by choosing pairs of cyclic granularities that are not clashes using procedures described in [@Gupta2020-vo].
-The paper also shows how the number of harmonies could be identified among 42 pair of granularities by removing clashes.
-This section shows how we could refine the search further by only looking at significant harmonies.
-
-Suppose $(A, B) \in H_{N_C}$ be a harmony pair where  $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.
-Suppose $q^{i, p}_{A, j}$ denote the quantiles with probability $p$ for the of the $i^{th}$ household for $j^{th}$ category of the cyclic granularity $A$.
-Similarly, $q^{i, p}_{B, k}$ denotes the same for the $k^{th}$ category of the cyclic granularity $B$.
-Sample quantiles were computed at $p = 0.01, 0.02, \dots, 0.99$.
-Jensen-Shannon distances are computed between $q^{i, p}_{A, j}$ and $q^{i, p}_{B, k}$ for each ${j \in J, k \in K}$ to obtain within-facet and between-facet distances.
-A tuning parameter of $\lambda = 0.67$ has been considered to upweigh the within-facet distances and down-weigh the between facet distances and the maximum of them are obtained to compute $wpd_{raw}$.
-It is further normalized using the approach described in Section \ref{sec:normalization}.
-This entire process is repeated for all harmony pairs $(A, B) \in H_{N_C}$ and for each households $i \in i = \{1, 2, 3, 4\}$.
-The harmony pairs are then arranged in descending order and the important ones with significance level 1%, 5% and 10% are highlighted with `***`, `**` and `*` respectively.
-
-Table \ref{tab:} shows the rank of the harmonies for different households
-\autoref{fig:} shows the bubble chart for the four households with size as the value of wpd and color indicating how significant they are.
-This is a quick summary of which harmonies are significant and also which cyclic granularities are important for the context.
-
-```{r rank-household-mclapply}
-elec <- read_rds(here("paper/data/elec.rds")) %>% 
-  filter(date >= ymd("20180101"), date < ymd("20180701"))
-rdbl <- c("Weekday" = "#d7191c", "Weekend" = "#2c7bb6")
-
-library(tictoc)
-#tic()
-elec_split = elec %>% group_split(id)
-
-elec_select_harmony = parallel::mclapply(1:4, function(x){
-
-  data_id <-  elec_split %>% magrittr::extract2(x) %>% 
-    as_tsibble(index = date_time)
-
-harmonies <- data_id %>%
-  harmony(
-    ugran = "month",
-    filter_in = "wknd_wday",
-    filter_out = c("hhour", "fortnight")
-  )
-
- hakear::select_harmonies(data_id,
-   harmony_tbl = harmonies,
-   response = kwh,
-   nperm = 200,
-   nsamp = 200
- )
-
-}, mc.cores = parallel::detectCores() - 1, mc.preschedule = FALSE, mc.set.seed = FALSE)
-#toc()
-```
-
-```{r elec_select_harmony}
-elec_harmony_all <- elec_select_harmony %>% 
-  bind_rows(.id = "id") %>% 
-  mutate(facet_variable = case_when(
-    facet_variable == "hour_day" ~ "hod" ,
-    facet_variable == "day_month" ~ "dom" ,
-    facet_variable == "day_week" ~ "dow" ,
-    facet_variable == "week_month" ~ "wom" ,
-    facet_variable == "wknd_wday" ~ "wdwnd"
-  )) %>% 
-  mutate(x_variable = case_when(
-    x_variable == "hour_day" ~ "hod" ,
-    x_variable == "day_month" ~ "dom" ,
-    x_variable == "day_week" ~ "dow" ,
-    x_variable == "week_month" ~ "wom" ,
-    x_variable == "wknd_wday" ~ "wdwnd"
-  )) %>% 
-  mutate(id = paste("id", id, sep = " ")) %>% 
-  group_by(id) %>% 
-  mutate(rank = row_number())
-
-```
-
-```{r dotplot, fig.cap = "Harmony pairs are shown for all household ids.
-The size represent how important the pair is and the colour represents if the harmonies are at all important or not.
-Visualizing the pairs in this way helps us to see the important cyclic granularities along the x-axis and facet along with the information that which ones amongst them should be analyzed together." }
-elec_sig_split <- elec_harmony_all %>%
-  mutate(select_split =  str_split(select_harmony, " ", simplify = TRUE)[,2]) %>% 
-  mutate(significant = case_when(
-    select_split == "***" ~ "highest",
-    select_split == "**" ~ "high",
-    select_split == "*" ~ "medium",
-    select_split == "" ~ "low"
-  )) %>% 
-   mutate(rank = case_when(
-    select_split == "***" ~ paste(rank, "***", sep = " "),
-    select_split == "**" ~  paste(rank, "**", sep = " "),
-    select_split == "*" ~  paste(rank, "*", sep = " "),
-    select_split == "" ~  paste(rank, "", sep = " ")
-  ))
-
-elec_sig_split$significant <- 
-  factor(elec_sig_split$significant, levels = c("highest", "high", "medium", "low"))
-
-dotplot <- elec_sig_split %>% 
-  ggplot() +
-  geom_point(aes(x = x_variable,
-                 y = facet_variable, 
-                 size = wpd, 
-                 fill = significant),
-             shape=21,
-             alpha= 0.8) +
-  scale_size_continuous() +
-  theme(legend.position = "bottom") +
-  scale_fill_viridis(discrete = TRUE, direction = 1) +
-  facet_wrap(~id, nrow = 1) +
-  guides(fill = guide_legend(), 
-         size = guide_legend()) +
-  theme_gray(base_size = 12, base_family = "Times") +
-   theme(legend.position = "bottom")
-
-#myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
-
-heatplot <- elec_sig_split %>% 
-  ggplot() +
-  geom_tile(aes(x = x_variable,
-                 y = facet_variable, 
-                 fill = wpd)) + 
-  scale_fill_gradient2() +
-  theme(legend.position = "bottom") +
-  facet_wrap(~id, nrow = 1) +
-  coord_fixed() + 
-  guides(fill = guide_legend()) +
-  theme_void() +
-  theme_gray(base_size = 12, base_family = "Times") +
-  theme(panel.grid = element_blank(),
-        axis.text.x = element_text(angle = 60, hjust=1)
-        , legend.position = "bottom")
-  heatplot
-```
-
-```{r tab-rank}
-elec_rank <- elec_sig_split %>% 
-  select(-c(6,7, 9, 10)) %>% 
-  pivot_wider(
-              names_from = id,
-                values_from = rank) %>% 
-  rename("facet variable" = "facet_variable",
-         "x variable" = "x_variable",
-         "facet levels" = "x_levels",
-         "x levels" = "x_levels") %>% 
-  slice(1:4)
-
-elec_rank %>% kable(format = "markdown", caption = "Ranking of the harmonies for the four households are shown.
-The first four harmonies are unanimously important for all households, after which there is differences in the rankings for most households.")
-```
-
-```{r gravitas-plot, message = FALSE, warning=FALSE, fig.cap="Distribution of energy demand shown for household id: 2 across hod in x-axis and wd-wnd in facets in a) and just the reverse in b).
-In c), distribution of energy demand for household id:4 shown across hod and wd-wnd.
-It can be seen that the differences in distributions are more apparent when viewed in a) as compared to b).
-It seems like there is more difference in the distributions of hod for b) compared to c).
-This also confers with the value of the normalised measure shown in Figure 11."}
-p1 <- id2_tsibble %>%
-   prob_plot("hour_day",
-             "wknd_wday",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = FALSE,
-             quantile_prob = c(0.25,0.5,0.75)) +
-  ggtitle("a") + 
-  scale_colour_brewer(name = "", palette = "Set2") +
-  theme(legend.position = "none",
-        strip.text = element_text(size = 7, margin = margin()))
-
-p2 <- id2_tsibble %>%
-   prob_plot("wknd_wday",
-             "hour_day",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = FALSE,
-             quantile_prob = c(0.25,0.5,0.75)) +
-  ggtitle("b") +
-  scale_colour_brewer(name = "", palette = "Set2")   +
-  theme(legend.position = "none",
-        strip.text = element_text(size = 7, margin = margin())) + xlab("")
-
-p3 <- id4_tsibble %>%
-   prob_plot("wknd_wday",
-             "hour_day",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = FALSE,
-             quantile_prob = 
-               c(0.25,0.5,0.75)) +
-  ggtitle("c") +
-  scale_colour_brewer(name = "", palette = "Set2") +
-  theme(
-        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + theme(legend.position = "bottom",
-        strip.text = element_text(size = 7, margin = margin()))
-
-p1 + p2/p3
-
-```
-
-# Discussion
-
-Exploratory data analysis involve many iterations of finding and summarizing patterns.
-With temporal data available at ever finer scales, exploring periodicity has become overwhelming with so many possible granularities to explore.
-This work refines the selection of appropriate pairs of granularities by identifying those for which the differences between the displayed distributions is greatest, and rating these selected harmony pairs in order of importance for exploration.
-
-A future direction of work could be to look at more individuals/subjects and group them according to similar periodic behavior.
-Behaviors across different cyclic granularities would be different for different subjects and one way to find groups would be to actually locate clusters who have similar periodic behavior.
-
-<!-- patterns are interesting and others are not.
-The subjects for which behaviors across a group of cyclic granularities are similar, could be grouped together as their periodic behavior is similar.
-to group subjects  -->
-
-# Appendix
-
-## Smart meter application to 8 datasets from energy competition
+In the left panel of \autoref{fig:linear-scale} (a), the linear representation of the entire time period is shown, whereas in the right panel (b) a particular month is shown and furthermore a week has been highlighted to inspect if there is any daily or weekly periodic patterns in their behavior that is reflected when we zoom into the the linear representation of the time series.
+We start by asking if the ranking of the harmonies make sense for the households, then compare households to get more insights of what these rankings imply and if they could be used to remove some non-interesting harmonies.
+Furthermore, we see if the display of the significant harmonies could be validated by zooming in the linear representation of the time series.
+
+<!-- if we are benefiting by moving from a linear to cyclic representation of time to . -->
 
@@
 
-<!-- **Normal-quantile-transform**  -->
-
-<!-- **Characterizing empirical distributions through quantiles** ( write in the methodology maybe) -->
-
-<!-- **Computing JS distances between harmonies for each categories of the cyclic granularity involved** -->
+_Choosing cyclic granularities of interest and removing clashes_
+
+Let $v_{i, t}$ denote the electricity demand for $i^{th}$ household for time period $t$.
+The series $v_{i, t}$ is the linear granularity corresponding to half-hour since the interval of this data is 30 minutes.
+We consider coarser linear granularities like hour, day, week and month from the commonly used Gregorian calendar.
+Considering $4$ linear granularities hour, day, week, month in the hierarchy table, the number of cyclic granularities is $N_C = (4 * 3/2) = 6$.
+We obtain cyclic granularities namely “hour_day”, “hour_week”, “hour_month”, “day_ week”, “day_month” and “week_month”, read as “hour of the day”, etc.
+Further, we add cyclic granularity day-type( “wknd wday”) to capture weekend and weekday behavior.
+Thus, $7$ cyclic granularities are considered to be of interest.
+The set consisting of pairs of cyclic granularities ($C_{N_C}$) will have $7_{P_2}=42$ elements which could be analysed for detecting possible periodicities.
+The set of possible harmonies $H_{N_C}$ from $C_{N_C}$ are chosen by removing clashes using procedures described in [@Gupta2020-vo].
+
+ <!-- The paper also shows how the number of harmonies could be identified among  by removing clashes.
+This section shows how we could refine the search further by only looking at significant harmonies.
+-->
+
+_Choosing and Ranking harmonies for all households_
+
+_Validating ranks of one household_
+
+_Comparing households_
+
+_Validating patterns from linear display_
+
+This is expected to have an assymmetrical distribution as could be seen in \ref{fig:raw-nqt} and the Normal score transform has been applied to make it more symmetric.
+Let $v*_{i, t}$ denote the normal-quantile transformed electricity demand for $i^{th}$ household for time period $t$.
+
+Suppose $(A, B) \in H_{N_C}$ be a harmony pair where  $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.
+Suppose $q^{i, p}_{A, j}$ denote the quantiles with probability $p$ for the of the $i^{th}$ household for $j^{th}$ category of the cyclic granularity $A$.
+Similarly, $q^{i, p}_{B, k}$ denotes the same for the $k^{th}$ category of the cyclic granularity $B$.
+Sample quantiles were computed at $p = 0.01, 0.02, \dots, 0.99$.
+Jensen-Shannon distances are computed between $q^{i, p}_{A, j}$ and $q^{i, p}_{B, k}$ for each ${j \in J, k \in K}$ to obtain within-facet and between-facet distances.
+A tuning parameter of $\lambda = 0.67$ has been considered to upweigh the within-facet distances and down-weigh the between facet distances and the maximum of them are obtained to compute $wpd_{raw}$.
+It is further normalized using the approach described in Section \ref{sec:normalization}.
+This entire process is repeated for all harmony pairs $(A, B) \in H_{N_C}$ and for each households $i \in i = \{1, 2, 3, 4\}$.
+The harmony pairs are then arranged in descending order and the important ones with significance level 1%, 5% and 10% are highlighted with `***`, `**` and `*` respectively.
+
+Table \ref{tab:} shows the rank of the harmonies for different households
+\autoref{fig:} shows the bubble chart for the four households with size as the value of wpd and color indicating how significant they are.
+This is a quick summary of which harmonies are significant and also which cyclic granularities are important for the context.
 
@@
 
+# Discussion
+
+Exploratory data analysis involve many iterations of finding and summarizing patterns.
+With temporal data available at ever finer scales, exploring periodicity has become overwhelming with so many possible granularities to explore.
+This work refines the selection of appropriate pairs of granularities by identifying those for which the differences between the displayed distributions is greatest, and rating these selected harmony pairs in order of importance for exploration.
+
+A future direction of work could be to look at more individuals/subjects and group them according to similar periodic behavior.
+Behaviors across different cyclic granularities would be different for different subjects and one way to find groups would be to actually locate clusters who have similar periodic behavior.
+
+<!-- patterns are interesting and others are not.
+The subjects for which behaviors across a group of cyclic granularities are similar, could be grouped together as their periodic behavior is similar.
+to group subjects  -->
+
+# Appendix
+
 ```{r mds}
@@
 q1 + q2
+```
+
+# application to 4 households
+
+The smart meter data set from four households in Melbourne referred in @wang2020calendar has been utilized to see the use of the distance measure proposed in the paper.
+The data is a tsibble  containing half-hourly electricity consumption from Jan-2018 to Jun-2018 for each of the households, which is procured by them by downloading their data from the energy supplier/retailer.
+Demand data for these households are shown in a linear time scale in \autoref{fig:linear-scale}.
+It is evident from the range of the demand data that these households vary in consumption levels as well as in their temporal patterns.
+In the left panel of \autoref{fig:linear-scale} (a), the linear representation of the entire time period is shown, whereas in panel B (right) a particular month is shown and furthermore a week has been highlighted to inspect if there is any daily or weekly periodic patterns in their behavior that is evident from the linear representation of the time series.
+We pick household id 2 and 4 for our analysis to see which periodic patterns are important in their behavior, if they are same or different and if it makes sense using our distance metric to select and rank the important harmonies.
+
+```{r linear-scale, fig.cap = "Electricity demand for four households are shown in different facets from Jan-18 to Jun-18 in Fig a and it has been zoomed in for Feb-18 in Fig b, where a week in Feb-18 has been highlighted.
+From the scales of Fig a, it is apparent that they have different level of consumption but all of them have some periodic behavior in terms of regular peaks and troughs.
+It is not clear which all periodic patterns exist.
+In fig b, periodic pattern is zoomed in for a month and we can see weekly patterns for the entire period and daily pattern for the highlighted week."}
+library(scales)
+library(tidyquant)
+library(gghighlight)
+
+elec_linear <- elec %>% 
+  ggplot() +
+  geom_line(aes(x = date_time, y = kwh)) +
+  facet_wrap(~id, nrow = 4, labeller = "label_both",
+             strip.position =  "right",
+             scales = "free_y") +
+  theme_pubclean() 
+#+
+ # geom_rect(aes(xmin = as.Date("2018-02-01"), xmax = as.Date("2018-02-28"), ymin = -Inf, ymax = Inf),colour="white", size=0.5, alpha=0.02)
+
+elec_zoom <-  elec %>%
+  filter(date >as.Date("2018-02-01") & date < (as.Date("2018-02-28"))) %>% 
+  ggplot(aes(x=date_time, y = kwh)) +
+  geom_line(alpha = 0.5, size = 0.1) +
+  facet_wrap(~id, scales = "free_y", ncol = 1, strip.position =  "right") +
+  gghighlight(date >as.Date("2018-02-05") & date < (as.Date("2018-02-12")), unhighlighted_params = list(colour = "blue"))
+
+  # geom_rect(xmin = as.Date("2018-02-02"), xmax = as.Date("2018-02-04"), ymin = -Inf, ymax = Inf, fill = "pink", colour = pink)
+
+# elec_zoom <- elec_linear + 
+#   coord_x_date(xlim = c("2018-02-01", "2018-02-28")) +
+#   gghighlight(date >as.Date("2018-02-05") & date < (as.Date("2018-02-12")),
+#               unhighlighted_params = list(colour = "grey")) + geom_line(aes(x = date_time, y = kwh, group = time))
+
+elec_linear + elec_zoom +
+   xlab("Date") +
+  ylab("demand(in kwh)")
+# elec %>% dplyr::filter(date> as.Date("2018-02-01") & date<as.Date("2018-02-28"))
+
+```
+
+<!-- **Normal-quantile-transform**  -->
+
+<!-- **Characterizing empirical distributions through quantiles** ( write in the methodology maybe) -->
+
+<!-- **Computing JS distances between harmonies for each categories of the cyclic granularity involved** -->
+
+```{r raw-nqt}
+elec_raw <- elec %>% 
+  ggplot() +
+  geom_density(aes(x = kwh)) +
+  facet_wrap(~id, scales = "free_y", ncol = 1) +
+  xlab("demand (in kwh)")
+
+elec_nqt <- elec %>% 
+  dplyr::mutate(kwh_transformed = stats::qqnorm(kwh, plot.it = FALSE)$x) %>% 
+  ggplot() +
+  geom_density(aes(x = kwh_transformed))+
+  facet_wrap(~id, scales = "free_y", ncol = 1) +
+  xlab("NQT demand (in kwh)")
+
+# hour_day_raw <- elec %>% 
+#   tsibble::as_tsibble(index = date_time, key = id) %>% 
+#     create_gran("hour_day") %>% 
+#     ggplot() + 
+#     ggridges::geom_density_ridges(aes(y=hour_day, x = kwh))
+#   
+# hour_day_trans <- elec %>% 
+#   tsibble::as_tsibble(index = date_time, key = id) %>% 
+#     create_gran("hour_day") %>% 
+#   dplyr::mutate(kwh_transformed = stats::qqnorm(kwh, plot.it = FALSE)$x) %>% 
+#   ggplot() +
+#   ggridges::geom_density_ridges(aes(y=hour_day, x = kwh_transformed))
+
+elec_raw + elec_nqt
+
+```
+
+Let $y_{i, t}$ denote the electricity demand for $i^{th}$ household for time period $t$.
+This is expected to have an assymmetrical distribution as could be seen in \ref{fig:raw-nqt} and the Normal score transform has been applied to make it more symmetric.
+Let $y*_{i, t}$ denote the normal-quantile transformed electricity demand for $i^{th}$ household for time period $t$.
+Technically, this $y*_{i, t}$ is the linear granularity corresponding to half-hour since the interval of this data is 30 minutes.
+We consider coarser linear granularities like hour, day, week and month from the commonly used Gregorian calendar.
+Considering 4 linear granularities hour, day, week, month in the hierarchy table, the number of cyclic granularities is $N_C = (4 * 3/2) = 6$.
+We obtain cyclic granularities namely “hour_day”, “hour_week”, “hour_month”, “day_ week”, “day_month” and “week_month”, read as “hour of the day”, etc.
+Further, we add cyclic granularity day-type( “wknd wday”) to capture weekend and weekday behavior.
+Thus, we consider 7 cyclic granularities in the set of cyclic granularities of interest defined by $C_{N_C}$.
+We then compute the set of harmonies $H_{N_C}$  from $C_{N_C}$ by choosing pairs of cyclic granularities that are not clashes using procedures described in [@Gupta2020-vo].
+The paper also shows how the number of harmonies could be identified among 42 pair of granularities by removing clashes.
+This section shows how we could refine the search further by only looking at significant harmonies.
+
+Suppose $(A, B) \in H_{N_C}$ be a harmony pair where  $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.
+Suppose $q^{i, p}_{A, j}$ denote the quantiles with probability $p$ for the of the $i^{th}$ household for $j^{th}$ category of the cyclic granularity $A$.
+Similarly, $q^{i, p}_{B, k}$ denotes the same for the $k^{th}$ category of the cyclic granularity $B$.
+Sample quantiles were computed at $p = 0.01, 0.02, \dots, 0.99$.
+Jensen-Shannon distances are computed between $q^{i, p}_{A, j}$ and $q^{i, p}_{B, k}$ for each ${j \in J, k \in K}$ to obtain within-facet and between-facet distances.
+A tuning parameter of $\lambda = 0.67$ has been considered to upweigh the within-facet distances and down-weigh the between facet distances and the maximum of them are obtained to compute $wpd_{raw}$.
+It is further normalized using the approach described in Section \ref{sec:normalization}.
+This entire process is repeated for all harmony pairs $(A, B) \in H_{N_C}$ and for each households $i \in i = \{1, 2, 3, 4\}$.
+The harmony pairs are then arranged in descending order and the important ones with significance level 1%, 5% and 10% are highlighted with `***`, `**` and `*` respectively.
+
+Table \ref{tab:} shows the rank of the harmonies for different households
+\autoref{fig:} shows the bubble chart for the four households with size as the value of wpd and color indicating how significant they are.
+This is a quick summary of which harmonies are significant and also which cyclic granularities are important for the context.
+
+```{r rank-household-mclapply}
+elec <- read_rds(here("paper/data/elec.rds")) %>% 
+  filter(date >= ymd("20180101"), date < ymd("20180701"))
+rdbl <- c("Weekday" = "#d7191c", "Weekend" = "#2c7bb6")
+
+library(tictoc)
+#tic()
+elec_split = elec %>% group_split(id)
+
+elec_select_harmony = parallel::mclapply(1:4, function(x){
+
+  data_id <-  elec_split %>% magrittr::extract2(x) %>% 
+    as_tsibble(index = date_time)
+
+harmonies <- data_id %>%
+  harmony(
+    ugran = "month",
+    filter_in = "wknd_wday",
+    filter_out = c("hhour", "fortnight")
+  )
+
+ hakear::select_harmonies(data_id,
+   harmony_tbl = harmonies,
+   response = kwh,
+   nperm = 200,
+   nsamp = 200
+ )
+
+}, mc.cores = parallel::detectCores() - 1, mc.preschedule = FALSE, mc.set.seed = FALSE)
+#toc()
+```
+
+```{r elec_select_harmony}
+elec_harmony_all <- elec_select_harmony %>% 
+  bind_rows(.id = "id") %>% 
+  mutate(facet_variable = case_when(
+    facet_variable == "hour_day" ~ "hod" ,
+    facet_variable == "day_month" ~ "dom" ,
+    facet_variable == "day_week" ~ "dow" ,
+    facet_variable == "week_month" ~ "wom" ,
+    facet_variable == "wknd_wday" ~ "wdwnd"
+  )) %>% 
+  mutate(x_variable = case_when(
+    x_variable == "hour_day" ~ "hod" ,
+    x_variable == "day_month" ~ "dom" ,
+    x_variable == "day_week" ~ "dow" ,
+    x_variable == "week_month" ~ "wom" ,
+    x_variable == "wknd_wday" ~ "wdwnd"
+  )) %>% 
+  mutate(id = paste("id", id, sep = " ")) %>% 
+  group_by(id) %>% 
+  mutate(rank = row_number())
+
+```
+
+```{r dotplot, fig.cap = "Harmony pairs are shown for all household ids.
+The size represent how important the pair is and the colour represents if the harmonies are at all important or not.
+Visualizing the pairs in this way helps us to see the important cyclic granularities along the x-axis and facet along with the information that which ones amongst them should be analyzed together." }
+elec_sig_split <- elec_harmony_all %>%
+  mutate(select_split =  str_split(select_harmony, " ", simplify = TRUE)[,2]) %>% 
+  mutate(significant = case_when(
+    select_split == "***" ~ "highest",
+    select_split == "**" ~ "high",
+    select_split == "*" ~ "medium",
+    select_split == "" ~ "low"
+  )) %>% 
+   mutate(rank = case_when(
+    select_split == "***" ~ paste(rank, "***", sep = " "),
+    select_split == "**" ~  paste(rank, "**", sep = " "),
+    select_split == "*" ~  paste(rank, "*", sep = " "),
+    select_split == "" ~  paste(rank, "", sep = " ")
+  ))
+
+elec_sig_split$significant <- 
+  factor(elec_sig_split$significant, levels = c("highest", "high", "medium", "low"))
+
+dotplot <- elec_sig_split %>% 
+  ggplot() +
+  geom_point(aes(x = x_variable,
+                 y = facet_variable, 
+                 size = wpd, 
+                 fill = significant),
+             shape=21,
+             alpha= 0.8) +
+  scale_size_continuous() +
+  theme(legend.position = "bottom") +
+  scale_fill_viridis(discrete = TRUE, direction = 1) +
+  facet_wrap(~id, nrow = 1) +
+  guides(fill = guide_legend(), 
+         size = guide_legend()) +
+  theme_gray(base_size = 12, base_family = "Times") +
+   theme(legend.position = "bottom")
+
+#myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
+
+heatplot <- elec_sig_split %>% 
+  ggplot() +
+  geom_tile(aes(x = x_variable,
+                 y = facet_variable, 
+                 fill = wpd)) + 
+  scale_fill_gradient2() +
+  theme(legend.position = "bottom") +
+  facet_wrap(~id, nrow = 1) +
+  coord_fixed() + 
+  guides(fill = guide_legend()) +
+  theme_void() +
+  theme_gray(base_size = 12, base_family = "Times") +
+  theme(panel.grid = element_blank(),
+        axis.text.x = element_text(angle = 60, hjust=1)
+        , legend.position = "bottom")
+  heatplot
+```
+
+```{r tab-rank}
+elec_rank <- elec_sig_split %>% 
+  select(-c(6,7, 9, 10)) %>% 
+  pivot_wider(
+              names_from = id,
+                values_from = rank) %>% 
+  rename("facet variable" = "facet_variable",
+         "x variable" = "x_variable",
+         "facet levels" = "x_levels",
+         "x levels" = "x_levels") %>% 
+  slice(1:4)
+
+elec_rank %>% kable(format = "markdown", caption = "Ranking of the harmonies for the four households are shown.
+The first four harmonies are unanimously important for all households, after which there is differences in the rankings for most households.")
+```
+
+```{r gravitas-plot, message = FALSE, warning=FALSE, fig.cap="Distribution of energy demand shown for household id: 2 across hod in x-axis and wd-wnd in facets in a) and just the reverse in b).
+In c), distribution of energy demand for household id:4 shown across hod and wd-wnd.
+It can be seen that the differences in distributions are more apparent when viewed in a) as compared to b).
+It seems like there is more difference in the distributions of hod for b) compared to c).
+This also confers with the value of the normalised measure shown in Figure 11."}
+p1 <- id2_tsibble %>%
+   prob_plot("hour_day",
+             "wknd_wday",
+             response = "kwh",
+             plot_type = "quantile",
+             symmetric = FALSE,
+             quantile_prob = c(0.25,0.5,0.75)) +
+  ggtitle("a") + 
+  scale_colour_brewer(name = "", palette = "Set2") +
+  theme(legend.position = "none",
+        strip.text = element_text(size = 7, margin = margin()))
+
+p2 <- id2_tsibble %>%
+   prob_plot("wknd_wday",
+             "hour_day",
+             response = "kwh",
+             plot_type = "quantile",
+             symmetric = FALSE,
+             quantile_prob = c(0.25,0.5,0.75)) +
+  ggtitle("b") +
+  scale_colour_brewer(name = "", palette = "Set2")   +
+  theme(legend.position = "none",
+        strip.text = element_text(size = 7, margin = margin())) + xlab("")
+
+p3 <- id4_tsibble %>%
+   prob_plot("wknd_wday",
+             "hour_day",
+             response = "kwh",
+             plot_type = "quantile",
+             symmetric = FALSE,
+             quantile_prob = 
+               c(0.25,0.5,0.75)) +
+  ggtitle("c") +
+  scale_colour_brewer(name = "", palette = "Set2") +
+  theme(
+        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + theme(legend.position = "bottom",
+        strip.text = element_text(size = 7, margin = margin()))
+
+p1 + p2/p3
+
 ```

### 2021-03-02 paper/main.Rmd
working on introduction

@@
 Exploratory data analysis, as coined by John W.
-Tukey (Tukey 1965) involves many iterations of finding structures and patterns that allows the data to be informative.
+Tukey (Tukey 1965) involves many iterations of finding structures and patterns that allow the data to be informative.
 With temporal data available at finer scales, exploring periodicity and their relationships can become overwhelming with so many possible cyclic temporal granularities [@Gupta2020-vo] to explore.
 
-```{r calendar- <- , fig.height = 10.5, fig.cap="Calendar display."}
+```{r calendar-elec, fig.height = 10.5, fig.cap="Calendar display."}
 elec <- read_rds(here("paper/data/elec.rds")) %>% 
@@
 
-\noindent Take the example of the calendar display of electricity smart meter data (\ref{fig:calendar-elec}) used in @wang2020calendar for four households in Melbourne, Australia.
-The authors show how hour-of-the-day interact with weekday and weekends and then move on to use calendar display to show daily schedules.
-The calendar display has several components in it, which helps us look at energy consumption across hour-of-the-day, day-of-the-week, week-of-the-month, and month-of-the-year at once.
-Some interaction of these cyclic granularities could also be interpreted from this display.
-This is a great start to have an overview of the energy consumption.
-However, if one wants to understand the periodicities in energy behavior and how the periodicities interact in greater details, it is not easy to comprehend the interactions of some periodicities' from this display, due to the combination of linear and cyclic representation of time.
-For example, this display might not be the best to understand how hour-of-the-day varies and month-of-year varies across week-of-the-month.
-Further, it is not clear what all interactions of cyclic granularities should be read from this display as there could be many combinations that one can look at.
-Moreover, calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions (@Gupta2020-vo) and could include other cyclic granularities like hour-of-week or day-of-fortnight, which could potentially become useful depending on the context.
+\noindent Take the example of the calendar display of electricity smart meter data in Figure (\ref{fig:calendar-elec}) used in @wang2020calendar for four households in Melbourne, Australia.
+The authors show how hour-of-the-day interact with weekdays and weekends and then move on to use calendar display to show daily schedules.
+The calendar display has several components in it, which helps us to look at energy consumption across hour-of-the-day, day-of-the-week, week-of-the-month, and month-of-the-year at once.
+Some interaction of these cyclic granularities, for example, how  day-of-week relates to month-of-year, could also be interpreted from this display.
+This is a great way for having an overview of energy consumption.
+However, if one wants to understand the periodicities in energy behavior and how the periodicities interact in greater detail, it is not easy to comprehend the interactions of some periodicities' from this display, due to the combination of linear and cyclic representation of time.
+For example, this display might not be the best to understand how hour-of-the-day or month-of-year varies across week-of-the-month as well as with each other.
+Furthermore, it is not clear what all interactions of cyclic granularities should be read from this display as there could be many combinations that one can look at.
+Moreover, _"calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions"_ (@Gupta2020-vo) and could include other cyclic granularities like hour-of-week or day-of-fortnight, which could potentially become useful depending on the context.
 
@@
 
-# wknd_wday and week_month (important pair) id2's behavior across different hours of the day very different across months, but for id4 behavior across different hours of the day is not likely a function of month.
-
 p3 <- id2_tsibble %>%
@@
    ggtitle("") +
-#scale_x_discrete(breaks = seq(0, 23, 4))  + theme(
+
         theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
@@
 
-```{r id4, fig.cap = "something2"}
+```{r id4, fig.cap = "something2", eval = FALSE}
 ggpubr::ggarrange(p3, p4, ncol = 2)
@@
 
-Moreover, there might be specific interactions that are interesting and others that are not and that too will vary with different households.
-For example, area distribution quantiles are plotted for household 2 and 4 in Figure \ref{fig:id2}a and b respectively.
-For the first household, the 75th and 90th percentile for Jan, Feb and July are very close, implying that energy usage for these months are generally on a much higher side due to the usage of air conditioners (in Jan and Feb) and heaters (in July).
-The energy consumption for household 2 is also higher relative to its own consumption for Jan, Feb and March but the 75th and 90th percentile are apart implying that contrary to the first household, the second household resorts to air conditioners and heaters much less regularly than the first one.
-Moreover, the 75th percentile distribution is not bimodal across hours of the day for the first household in those months, but the distribution looks similar for all months for the second household.
-Difference in the energy consumption seem to be varying both across month-of-year (facets) and hour-of-day (x-axis).
-And thus, both the cyclic granularities would deem important while studying the periodicities in the first household.
-However, it seems like energy consumption across hours of the day are not that different across different months for the second household.
-Differences seem to be more prominent across month-of-year (facets) than hour-of-day (x-axis).
-Again, look at \ref{fig:} c and d, where energy consumption for these two households are plotted against (weekend/weekday, week-of-month).
+Additionally, even when it is known which all interactions to look at, all of them would not be interesting and that too will vary across different households.
+For example, area distribution quantiles are plotted for household 2 and 4 in Figure \ref{fig:id2}a and b respectively across month-of-year on facets and hour-of-day on x-axis.
+For the first household, the 75th and 90th percentile for January and February are very close, implying that energy usage for these months are generally on a much higher side, possibly due to the usage of air conditioners (January and February are peak summer in Australia), however for other months (Autumn and winter), the difference between the percentiles are not high, implying this household do not use so much heater as compared to air conditioner.
+Also, a lot of households in Victoria use gas heating and hence the usage of heaters might not be reflected here.
+The energy consumption for household 2 is also higher in summer months relative to autumn or winter, but the 75th and 90th percentile are far apart in all months, implying that the second household resorts to air conditioners much less regularly than the first one.
+Moreover, the 75th percentile distribution does not follow the same pattern as 90th percentile for all months for the first household, whereas, the pattern looks pretty similar for all months for the second household.
+Difference in the energy consumption could vary both across month-of-year (facets) and hour-of-day (x-axis).
+For the first household, both these cyclic granularities would deem important.
+Although, it seems like energy consumption across hours of the day are not that different across different months for the second household or atleast differences seem to be more prominent across month-of-year (facets) than hour-of-day (x-axis).
+It could be immensely useful to make the transition from all possible ways to only ways that could potentially be informative given a household.
+
+<!-- Again, look at \ref{fig:} c and d, where energy consumption for these two households are plotted against (weekend/weekday, week-of-month).
 Here, for both households, the pattern of energy consumption vary  across different weeks of the month irrespective of the fact it is a weekday or weekend.
 In that respect, the harmony pair (month-of-year, hour-of-day) seems to be more informative than (weekend/weekday, week-of-month) for the first household.
-It could be immensely useful to make the transition from all possible ways to only ways that could potentially be informative given a household.
+-->
 
@@
 
+### Simulation design
+
+Observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$.
+For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
+The values of $wpd_{norm}$ is obtained for each of the panels for the designs $D_{null}$, $D_{var_x}$, $D_{var_f}$ and $D_{var_{all}}$.
+$wpd_{threshold}$ is computed from all of these panels together and the number of times a harmony pair $(A, B) \in H_{N_C}$ is selected when in fact it was of the design $D_{null}$ is noted.
+This entire process is repeated for several null data sets to see the number of times any harmony pair $(A, B) \in H_{N_C}$ is selected under null.
+
+nx = (3, 7, 14)
+nfacet = (2, 9, 10)
+
+(3, 2), (7,9), (14, 10) being null sets and others under some other design. Generate 200 repitions of different data sets with the same design for all the pairs and compute size and power.
+
+### Results
+
+Figure \ref{fig:raw} shows the distribution of $wpd$ plotted across different $nx$ and $nfacet$ categories.
+Since under $D_{null}$, there is no difference in distributions across different categories, we expect the distance measure $wpd$ to reflect that as well and have the same null distribution across categories.
+But Figure \ref{fig:raw} shows that both the location and scale of the distributions change across panels.
+This is not desirable under $D_{null}$ as it would mean comparisons of $wpd$ values is not appropriate across different $nx$ and $nfacet$.
+Figure \ref{fig:quadratic} shows how the median of $wpd$ varies with the total number of distances $nx*nfacet$ for each panel.
+The median increases abruptly for lower values of $nx*nfacet$ and slowly for higher $nx*nfacet$.
+
 # Simulation environment
@@
 The data has been cleaned to be a `tsibble` (@wang2019tsibble) containing half-hourly electricity consumption from Jul-2019 to Dec-2019 for each of the households, which is procured by them by downloading their data from the energy supplier/retailer.
-Demand data for these households are shown in a linear time scale in \autoref{fig:linear-scale-8}.
+Demand data for these households are shown in a linear time scale in Figure \ref{fig:linear-scale-8}.
 It is evident from the range of the demand data that these households vary in consumption levels as well as in their temporal patterns.
-In the left panel of \autoref{fig:linear-scale} (a), the linear representation of the entire time period is shown, whereas in the right panel (b) a particular month is shown and furthermore a week has been highlighted to inspect if there is any daily or weekly periodic patterns in their behavior that is reflected when we zoom into the the linear representation of the time series.
-We start by asking if the ranking of the harmonies make sense for the households, then compare households to get more insights of what these rankings imply and if they could be used to remove some non-interesting harmonies.
+In the left panel of Figure \ref{fig:linear-scale-8} (a), the linear representation of the entire time period is shown, whereas in the right panel (b) a particular month is shown and furthermore a week has been highlighted to inspect if there is any daily or weekly periodic patterns in their behavior that is reflected when we zoom into the the linear representation of the time series.
+We start the analysis by asking if the ranking of the harmonies make sense for the households, then compare households to get more insights of what these rankings imply and if they could be used to remove some non-interesting harmonies.
 Furthermore, we see if the display of the significant harmonies could be validated by zooming in the linear representation of the time series.
@@
 
-```{r linear-scale-8, fig.cap = "Electricity demand for four households are shown in different facets from Jan-18 to Jun-18 in Fig a and it has been zoomed in for Feb-18 in Fig b, where a week in Feb-18 has been highlighted.
+```{r linear-scale-8, fig.cap = "Electricity demand for eight households are shown in different facets from Jul-19 to Dec-19 in Fig a and it has been zoomed in for Sep-19 in Fig b, where a week in Sep-19 has been highlighted.
 From the scales of Fig a, it is apparent that they have different level of consumption but all of them have some periodic behavior in terms of regular peaks and troughs.
@@
 The set of possible harmonies $H_{N_C}$ from $C_{N_C}$ are chosen by removing clashes using procedures described in [@Gupta2020-vo].
+Table \ref{tab:tab-rank-8}  shows $14$ harmony pairs that belong to $H_{N_C}$.
 
@@
 
-_Validating ranks of one household_
-
-_Comparing households_
-
-_Validating patterns from linear display_
-
-This is expected to have an assymmetrical distribution as could be seen in \ref{fig:raw-nqt} and the Normal score transform has been applied to make it more symmetric.
+$v{i, t}$ has a asymmetrical distribution as could be seen in \ref{fig:raw-nqt-8} and the Normal score transform has been applied to make it more symmetric.
 Let $v*_{i, t}$ denote the normal-quantile transformed electricity demand for $i^{th}$ household for time period $t$.
-
 Suppose $(A, B) \in H_{N_C}$ be a harmony pair where  $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.
@@
 Jensen-Shannon distances are computed between $q^{i, p}_{A, j}$ and $q^{i, p}_{B, k}$ for each ${j \in J, k \in K}$ to obtain within-facet and between-facet distances.
-A tuning parameter of $\lambda = 0.67$ has been considered to upweigh the within-facet distances and down-weigh the between facet distances and the maximum of them are obtained to compute $wpd_{raw}$.
+A tuning parameter of $\lambda = 0.67$ has been considered to upweigh the within-facet distances and down-weigh the between facet distances and the maximum of them are obtained to compute $wpd$.
 It is further normalized using the approach described in Section \ref{sec:normalization}.
-This entire process is repeated for all harmony pairs $(A, B) \in H_{N_C}$ and for each households $i \in i = \{1, 2, 3, 4\}$.
+This entire process is repeated for all harmony pairs $\in H_{N_C}$ and for each households $i \in i = \{1, 2, \dots, 8\}$.
 The harmony pairs are then arranged in descending order and the important ones with significance level 1%, 5% and 10% are highlighted with `***`, `**` and `*` respectively.
-
-Table \ref{tab:} shows the rank of the harmonies for different households
-\autoref{fig:} shows the bubble chart for the four households with size as the value of wpd and color indicating how significant they are.
-This is a quick summary of which harmonies are significant and also which cyclic granularities are important for the context.
-
-```{r raw-nqt-8}
+Table \ref{tab:tab-rank-8} shows the rank of the harmonies for different households
+\ref{fig:dotplot-8} shows the heatmap for the eight households
+with the value of $wpd_{norm}$ filled as colors.
+
+_Validating rank of household id:1_
+
+From table \ref{tab:tab-rank-8}, it could be seen that 
+for household id:1, (hod, wdwnd) has been ranked higher than (wdwnd, hod), both of these being significant.
+Further, we see that (wom, wdwnd) has been ranked $5^{th}$ and tagged as an insignificant pair.
+Figure \ref{fig:gravitas-plot-8} is used to show
+if this selection and ranking of harmony pairs makes sense for this household.
+Panel a) of  Figure \ref{fig:gravitas-plot-8} shows the distribution of energy demand with weekday/weekend as the x-axis and hour-of-day as the facets and helps to compare the weekend/weekday patterns for different hours of the day.
+It could be observed that the difference between weekend and weekday is the highest from 15 to 19 hours of the day.
+Panel b) shows the distribution of energy demand with the variables swapped and helps to compare the daily patterns within weekday and weekend.
+It could be observed that the daily pattern is similar for weekdays and weekends with a morning and evening peak.
+However,the difference between morning and evening peaks are higher for weekends.
+Since $wpd_{norm}$ is designed to put more weightage on within-facet differences, it makes sense that the pair (hod, wdwnd) has been ranked higher than (wdwnd, hod).
+Panel c) shows the distribution of energy demand with weekday/weekend as the x-axis and week-of-month as the facets.
+Although the differences might seem significant at first, with closer inspection it could be seen that the range of the demand is low in this case and hence the differences are not large enough to cross the threshold for significance.
+
+```{r gravitas-plot-8, message = FALSE, warning=FALSE, fig.cap="Distribution of energy demand shown for household id 1 across hod in x-axis and wd-wnd in facets in a) and just the reverse in b).
+In c), distribution of energy demand for household id:4 shown across hod and wd-wnd.
+It can be seen that the differences in distributions are more apparent when viewed in a) as compared to b).
+It seems like there is more difference in the distributions of hod for b) compared to c).
+This also confers with the value of the normalised measure shown in Figure 11."}
+
+id1_tsibble <- elec %>%
+  filter(id== 1)
+
+p1 <- id1_tsibble %>% 
+   prob_plot("hour_day",
+             "wknd_wday",
+             response = "kwh",
+             plot_type = "quantile",
+             symmetric = FALSE,
+             quantile_prob = c(0.25, 0.5, 0.75)) +
+  ggtitle("a) hod vs wdwnd (Rank 1)") + 
+  scale_colour_brewer(name = "", palette = "Set2") +
+  theme(legend.position = "none",
+        strip.text = element_text(size = 7, margin = margin()),)
+
+p2 <- id1_tsibble %>%
+   prob_plot("wknd_wday",
+             "hour_day",
+             response = "kwh",
+             plot_type = "quantile",
+             symmetric = FALSE,
+             quantile_prob = c(0.25,0.5,0.75)) +
+  ggtitle("b) wdwnd vs hod (Rank 3)") +
+  scale_colour_brewer(name = "", palette = "Set2")   +
+  theme(legend.position = "none",
+        strip.text = element_text(size = 7, margin = margin()))
+
+p3 <- id1_tsibble %>%
+   prob_plot("week_month",
+             "wknd_wday",
+             response = "kwh",
+             plot_type = "quantile",
+             symmetric = FALSE,
+             quantile_prob = 
+               c(0.25,0.5,0.75)) +
+  scale_colour_brewer(name = "", palette = "Set2") +
+  theme(
+        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + theme(legend.position = "bottom",
+        strip.text = element_text(size = 7, margin = margin())) +
+  ggtitle("c) wom vs wdwnd (insignificant)")
+
+p1 + p2/p3
+
+```
+
+From Figure \ref{fig:gravitas-plot-8-id5}, it could further be observed that id5 has only one significant harmony $(hod, dow)$.
+Apparently, $(hod, wnd/wday)$ which is an important harmony for most households is not important for this one.
+
+_Comparing similar households and spotting anomalous ones_
+
+```{r gravitas-plot-8-id5, message = FALSE, warning=FALSE, fig.cap="something"}
+
+id5_tsibble <- elec %>%
+  filter(id== 5)
+
+p1 <- id5_tsibble %>% 
+   prob_plot("hour_day",
+             "day_week",
+             response = "kwh",
+             plot_type = "violin",
+             symmetric = FALSE,
+             quantile_prob = seq(0.1, 0.9, 0.01),
+             fill = "blue") +
+  ggtitle("a) hod vs dow (Rank 1)") + 
+  scale_colour_brewer(name = "", palette = "Set2") +
+  theme(legend.position = "none",
+        strip.text = element_text(size = 7, margin = margin()), axis.text.x = element_text(angle = 60, hjust=1))
+
+p2 <- id5_tsibble %>% 
+   prob_plot("hour_day",
+             "wknd_wday",
+             response = "kwh",
+             plot_type = "violin",
+             symmetric = FALSE,
+             quantile_prob = seq(0.1, 0.9, 0.01),
+             fill = "blue") +
+  ggtitle("a) hod vs wdwnd (insignificant)") + 
+  scale_colour_brewer(name = "", palette = "Set2") +
+  theme(legend.position = "none",
+        strip.text = element_text(size = 7, margin = margin()), axis.text.x = element_text(angle = 60, hjust=1))
+
+p1 + p2
+```
+
+_Validating patterns from linear display_
+
+```{r raw-nqt-8, fig.cap="The raw density of the half-hourly demand for the eight households in Panel a.
+Panel b shows the normal-score-transform half-hourly demand for the same households which has resulted in more symmetric distribution of half-hourly demand."}
 elec_raw <- elec %>% 
@@
 ```{r dotplot-8, fig.cap = "Harmony pairs are shown for all household ids.
-The size represent how important the pair is and the colour represents if the harmonies are at all important or not.
+The darker the colour, the higher the importance of the harmony.
 Visualizing the pairs in this way helps us to see the important cyclic granularities along the x-axis and facet along with the information that which ones amongst them should be analyzed together." }
@@
                  y = facet_variable, 
-                 fill = wpd)) + 
-  scale_fill_gradient2() +
+                 fill = wpd,
+                size = significant)) + 
+  scale_fill_continuous(type = "gradient") +
   theme(legend.position = "bottom") +
@@
 
-```{r gravitas-plot-8, message = FALSE, warning=FALSE, fig.cap="Distribution of energy demand shown for household id: 2 across hod in x-axis and wd-wnd in facets in a) and just the reverse in b).
-In c), distribution of energy demand for household id:4 shown across hod and wd-wnd.
-It can be seen that the differences in distributions are more apparent when viewed in a) as compared to b).
-It seems like there is more difference in the distributions of hod for b) compared to c).
-This also confers with the value of the normalised measure shown in Figure 11."}
-p1 <- id2_tsibble %>%
-   prob_plot("hour_day",
-             "wknd_wday",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = FALSE,
-             quantile_prob = c(0.25,0.5,0.75)) +
-  ggtitle("a") + 
-  scale_colour_brewer(name = "", palette = "Set2") +
-  theme(legend.position = "none",
-        strip.text = element_text(size = 7, margin = margin()))
-
-p2 <- id2_tsibble %>%
-   prob_plot("wknd_wday",
-             "hour_day",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = FALSE,
-             quantile_prob = c(0.25,0.5,0.75)) +
-  ggtitle("b") +
-  scale_colour_brewer(name = "", palette = "Set2")   +
-  theme(legend.position = "none",
-        strip.text = element_text(size = 7, margin = margin())) + xlab("")
-
-p3 <- id4_tsibble %>%
-   prob_plot("wknd_wday",
-             "hour_day",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = FALSE,
-             quantile_prob = 
-               c(0.25,0.5,0.75)) +
-  ggtitle("c") +
-  scale_colour_brewer(name = "", palette = "Set2") +
-  theme(
-        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + theme(legend.position = "bottom",
-        strip.text = element_text(size = 7, margin = margin()))
-
-p1 + p2/p3
-
-```
-
 # Discussion
@@
 Behaviors across different cyclic granularities would be different for different subjects and one way to find groups would be to actually locate clusters who have similar periodic behavior.
+
+A context when it could be useful is monitoring heart rates.
+There are devices that can detect each heartbeat and transfer the data to a receiver such as a watch or phone.
+These data could be available for a temporal scale as fine as a minute and it could be of interest to see regular patterns across any deconstruction of time coarser than a minute.
 
@@
                  fill = wpd)) + 
-  scale_fill_gradient2() +
+  scale_fill_continuous(type = "gradient") +
   theme(legend.position = "bottom") +

### 2021-03-02 paper/main.Rmd
introduction done except timeseer

@@
 Moreover, _"calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions"_ (@Gupta2020-vo) and could include other cyclic granularities like hour-of-week or day-of-fortnight, which could potentially become useful depending on the context.
+Possible areas where it is useful are monitoring heart rates which could record number of heartbeats every minute or analyze web search data for which data is available for a temporal scale as fine as second.
+
+<!-- context when it could be useful is monitoring heart rates.
+There are devices that can detect each heartbeat and transfer the data to a receiver such as a watch or phone.
+These data could be available for a temporal scale as fine as a minute and it could be of interest to see regular patterns across any deconstruction of time coarser than a minute.
+-->
 
@@
 
-Additionally, even when it is known which all interactions to look at, all of them would not be interesting and that too will vary across different households.
-For example, area distribution quantiles are plotted for household 2 and 4 in Figure \ref{fig:id2}a and b respectively across month-of-year on facets and hour-of-day on x-axis.
+Even when it is known which all interactions to look at, all of them would not be interesting and that too will vary across different households.
+For example, area distribution quantiles are plotted for household 2 and 4 in Figure \ref{fig:id2}a and \ref{fig:id2}b respectively across month-of-year on facets and hour-of-day on x-axis.
 For the first household, the 75th and 90th percentile for January and February are very close, implying that energy usage for these months are generally on a much higher side, possibly due to the usage of air conditioners (January and February are peak summer in Australia), however for other months (Autumn and winter), the difference between the percentiles are not high, implying this household do not use so much heater as compared to air conditioner.
@@
 Although, it seems like energy consumption across hours of the day are not that different across different months for the second household or atleast differences seem to be more prominent across month-of-year (facets) than hour-of-day (x-axis).
-It could be immensely useful to make the transition from all possible ways to only ways that could potentially be informative given a household.
+It could be immensely useful to make the transition from all possible ways to only ways that could potentially be informative.
 
@@
 
+<!-- If we have $n$ periodic linear granularities in the hierarchy table, then $n(n-1)/2$ circular or quasi-circular cyclic granularities could be constructed.  -->
+
 <!-- what is the dimension of the problem -->
 The paper @Gupta2020-vo describes how we can compute all possible combinations of cyclic time granularities.
-If we have $n$ periodic linear granularities in the hierarchy table, then $n(n-1)/2$ circular or quasi-circular cyclic granularities could be constructed.
-Let $N_C$ be the total number of contextual circular, quasi-circular and aperiodic cyclic granularities that can originate from the underlying periodic and aperiodic linear granularities.
-The mapping of the graphical elements chosen in the paper implies that, for a numeric response variable, the graphics display distributions across combinations of cyclic granularities, one placed at x-axis and the other on the facet.
+Let $N_C$ be the total number of contextual circular, quasi-circular and aperiodic cyclic granularities that can originate from the underlying linear granularities.
+The graphical mapping is such that distributions of a numeric response variable is displayed across combinations of cyclic granularities, one placed at x-axis and the other on the facet.
 That essentially implies there are $^{N_C}P_2$ possible pairwise plots exhaustively, where each plot would display a pair of cyclic granularities.
-This is large and overwhelming for human consumption.
-
-<!-- Scagnostics literature -->
-This is similar to Scagnostics (Scatterplot Diagnostics) by @tukey1988computer, which is used to discern meaningful patterns in large collections of scatterplots.
+This is large and overwhelming for human consumption.<!-- Scagnostics literature --> This problem is similar to Scagnostics (Scatterplot Diagnostics) by @tukey1988computer, which is used to discern meaningful patterns in large collections of scatterplots.
 Given a set of $v$ variables, there are $v(v-1)/2$ pairs of variables, and thus the same number of possible pairwise scatterplots.
-Therefore
-for even small $v$, the number of scatterplots can be
-large, and scatterplot matrices (SPLOMs) could easily run out of pixels when presenting high-dimensional data.
-@Dang2014-tw and @wilkinson2005graph provides potential solutions to this, where few characterizations help us to locate anomalies for defining several measures aimed to detect anomalies in density, shape, trend, and
-other features in the 2D point scatters.
+Therefore, even for small $v$, the number of scatterplots can be large, and scatterplot matrices (SPLOMs) could easily run out of pixels when presenting high-dimensional data.
+@Dang2014-tw and @wilkinson2005graph provides potential solutions to this, where few characterizations help us to locate anomalies in density, shape, trend, and other features in the 2D point scatters.
 
 <!-- harmonies and why it is not enough -->
-The paper (@Gupta2020-vo) narrows down the search from $^{N_C}P_2$ plots by identifying pairs of granularities that can be meaningfully examined together (a "harmony"), or when they cannot (a "clash").
+This work is a natural extension of our work (@Gupta2020-vo), which narrows down the search from $^{N_C}P_2$ plots by identifying pairs of granularities that can be meaningfully examined together (a "harmony"), or when they cannot (a "clash").
 However, even after excluding clashes, the list of harmonies left could be enormous for exhaustive exploration.
 Hence, there is a need to reduce the search even further by including only those harmonies which are informative enough.
-Also, ranking the remaining harmony pairs based on how well they capture the variation in the measured variable could be potentially useful.
-
-In this paper, we aim to build a new measure to follow through these two main objectives:
-
-- To choose harmonies for which distributions of categories are significantly different 
-- To rank the selected harmonies from highest to lowest variation in the distribution of their categories.
+@inference and @Majumder2013-hb present some methods to quantify the strength of pattern and noise through visual inference, similar to numerical testing.
+But this is an evolving field as human cognition (which act as the statistical tests in visual inference) might vary across humans even for the same plots.
+In this paper, we build a new distance measure which could be used to detect automatically detect significant periodic patterns.
+
+Our contributions in this paper are:
+
+ * We introduce a new distance measure for detecting periodic interactions. This induces data reduction which allows for identification of patterns, if any, in the time series data.
+
+ * We show that the distance metric could be used to rank the periodic patterns based on how well they capture the variation in the measured variable as they have been normalized for different number of comparisons.
+
+ * We device a framework for choosing a threshold, which will result in detection of only significantly interesting periodic patterns in the time series data.
+
+The article is organized as follows.
+Section \ref{sec:computation-wpd} introduces a new distance measure, discusses the reasoning behind choosing such a measure and presents some results to study the behavior of the measure.
+Section \ref{sec:norm-wpd} describes a methodology to normalize the distance measure so that it can qualify as a measure that can be compared across different comparisons and datasets.
+Section \ref{sec:rank-wpd} discusses how to choose a threshold to select only significant harmonies.
+Section \ref{sec:application-wpd} presents an application to a residential smart meter data in Melbourne to show how this distance measure acts as a way to automatically detect periodic patterns in time series.
+
+<!-- Also, ranking the remaining harmony pairs based on how well they capture the variation in the measured variable could be potentially useful.   -->
 
@@
 
-# A distance measure for quantifying patterns in harmonies
+# A distance measure for quantifying patterns in harmonies {#sec:computation-wpd}
 
@@
 
-# Normalization for the number of comparisons
+# Normalization for the number of comparisons {#sec:norm-wpd}
 
@@
 
-# Ranking and selecting significant harmonies
+# Ranking and selecting significant harmonies {#sec:rank-wpd}
 
@@
 
-## Results
+## Simulation design
+
+Observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$.
+For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
+The values of $wpd_{norm}$ is obtained for each of the panels for the designs $D_{null}$, $D_{var_x}$, $D_{var_f}$ and $D_{var_{all}}$.
+$wpd_{threshold}$ is computed from all of these panels together and the number of times a harmony pair $(A, B) \in H_{N_C}$ is selected when in fact it was of the design $D_{null}$ is noted.
+This entire process is repeated for several null data sets to see the number of times any harmony pair $(A, B) \in H_{N_C}$ is selected under null.
+
+nx = (3, 7, 14)
+nfacet = (2, 9, 10)
+
+(3, 2), (7,9), (14, 10) being null sets and others under some other design. Generate 200 repitions of different data sets with the same design for all the pairs and compute size and power.
+
+### Results
+
+Figure \ref{fig:raw} shows the distribution of $wpd$ plotted across different $nx$ and $nfacet$ categories.
+Since under $D_{null}$, there is no difference in distributions across different categories, we expect the distance measure $wpd$ to reflect that as well and have the same null distribution across categories.
+But Figure \ref{fig:raw} shows that both the location and scale of the distributions change across panels.
+This is not desirable under $D_{null}$ as it would mean comparisons of $wpd$ values is not appropriate across different $nx$ and $nfacet$.
+Figure \ref{fig:quadratic} shows how the median of $wpd$ varies with the total number of distances $nx*nfacet$ for each panel.
+The median increases abruptly for lower values of $nx*nfacet$ and slowly for higher $nx*nfacet$.
 
@@
 
-### Simulation design
-
-Observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$.
-For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
-The values of $wpd_{norm}$ is obtained for each of the panels for the designs $D_{null}$, $D_{var_x}$, $D_{var_f}$ and $D_{var_{all}}$.
-$wpd_{threshold}$ is computed from all of these panels together and the number of times a harmony pair $(A, B) \in H_{N_C}$ is selected when in fact it was of the design $D_{null}$ is noted.
-This entire process is repeated for several null data sets to see the number of times any harmony pair $(A, B) \in H_{N_C}$ is selected under null.
-
-nx = (3, 7, 14)
-nfacet = (2, 9, 10)
-
-(3, 2), (7,9), (14, 10) being null sets and others under some other design. Generate 200 repitions of different data sets with the same design for all the pairs and compute size and power.
-
-### Results
-
-Figure \ref{fig:raw} shows the distribution of $wpd$ plotted across different $nx$ and $nfacet$ categories.
-Since under $D_{null}$, there is no difference in distributions across different categories, we expect the distance measure $wpd$ to reflect that as well and have the same null distribution across categories.
-But Figure \ref{fig:raw} shows that both the location and scale of the distributions change across panels.
-This is not desirable under $D_{null}$ as it would mean comparisons of $wpd$ values is not appropriate across different $nx$ and $nfacet$.
-Figure \ref{fig:quadratic} shows how the median of $wpd$ varies with the total number of distances $nx*nfacet$ for each panel.
-The median increases abruptly for lower values of $nx*nfacet$ and slowly for higher $nx*nfacet$.
-
-# Simulation environment
+## Simulation environment
 
@@
 
-# Application to residential smart meter dataset {#sec:application}
+# Application to residential smart meter dataset {#sec:application-wpd}
 
@@
 
-A context when it could be useful is monitoring heart rates.
-There are devices that can detect each heartbeat and transfer the data to a receiver such as a watch or phone.
-These data could be available for a temporal scale as fine as a minute and it could be of interest to see regular patterns across any deconstruction of time coarser than a minute.
+ A common remedy would be to zoom into “interesting” segments, but how do we identify “interesting” segments?
 

### 2021-03-02 paper/main.Rmd
intro change

@@
 to group subjects  -->
-
-# Appendix
-
-```{r mds}
-set.seed(7777)
-library(gravitas)
-library(tsibble)
-library(lubridate)
-library(readr)
-
-all_data <- read_rds(here("paper/sim_table/all_data.rds"))
-sm_cust_data <- read_rds(here("paper/data/sm_cust_data.rds")) %>% 
-  as_tsibble(index = reading_datetime,
-             key = customer_id)
-
-sm_unique_cust <- sm_cust_data %>% distinct(customer_id)
-
-#sm_30 <- sample(sm_unique_cust$customer_id, 30)
-sm_cust_samp <- sm_cust_data %>% 
-  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
-  filter(year(reading_datetime) == 2012)  %>% 
-  create_gran("day_week") %>% 
-  create_gran("hour_day")
-
-#all_data <- write_rds(all_data, "paper/sim_table/all_data.rds")
-
-facet_variable = "day_week"
-x_variable = "hour_day"
-
-one_harmony_data <- all_data %>%
-  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
-  filter(facet_variable == "day_week",
-                    x_variable == "hour_day") %>% 
-  mutate(customer_id = as.character(customer_id))
-
-mds<- one_harmony_data %>%
-  select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
-  dist() %>%          
-  cmdscale() %>%
-  as_tibble()
-
-colnames(mds) <- c("Dim.1", "Dim.2")
-rownames(mds) <- unique(one_harmony_data$customer_id)
-mds <- mds %>%
-  mutate(customer_id = as.character(unique(one_harmony_data$customer_id))) %>%
-  select((customer_id)
-         , Dim.1, Dim.2)
-```
-
-```{r clustering}
-# K-means clustering
-clust <- kmeans(mds, 3)$cluster %>%
-  as.factor()
-mds <- mds %>%
-  mutate(groups = clust)
-
-# Plot and color by groups
-q1 <- ggpubr::ggscatter(mds, x = "Dim.1", y = "Dim.2", 
-          label = rownames(mds),
-          color = "groups",
-          palette = "jco",
-          size = 1, 
-          ellipse = TRUE,
-          ellipse.type = "convex",
-          repel = TRUE)
-
-```
-
-- check transformation and scalar approaches are same
-
-```{r scalar-approach}
-set.seed(7777)
-all_data <- read_rds(here("paper/sim_table/all_data_scalar.rds"))
-sm_cust_data <- read_rds(here("paper/data/sm_cust_data.rds"))
-set.seed(7777)
-sm_unique_cust <- sm_cust_data %>% distinct(customer_id)
-sm_cust_samp <- sm_cust_data %>% 
-  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
-  #filter(year(reading_datetime) == 2012) %>% #for demo just show one column
-  as_tsibble(index = reading_datetime,
-             key = customer_id) %>% 
-  create_gran("day_week") %>% 
-  create_gran("hour_day")
-
-#all_data <- write_rds(all_data, "paper/sim_table/all_data.rds")
-
-facet_variable = "day_week"
-x_variable = "hour_day"
-
-one_harmony_data <- all_data %>%
-  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
-  filter(facet_variable == "day_week",
-         x_variable == "hour_day") %>% 
-  mutate(customer_id = as.character(customer_id))
-
-mds<- one_harmony_data %>%
-  select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
-  dist() %>%          
-  cmdscale() %>%
-  as_tibble()
-
-colnames(mds) <- c("Dim.1", "Dim.2")
-rownames(mds) <- unique(one_harmony_data$customer_id)
-mds <- mds %>%
-  mutate(customer_id = as.character(unique(one_harmony_data$customer_id))) %>%
-  select((customer_id)
-         , Dim.1, Dim.2)
-
-ggpubr::ggscatter(mds,
-                  x = "Dim.1",
-                  y = "Dim.2", 
-                  label = rownames(mds),
-                  size = 1,
-                  repel = TRUE)
-
-# clustering as well
-
-d = one_harmony_data %>%
-  select(customer_id, facet_variable, x_variable, wpd_norm) %>% 
-  dist()
-
-hc = stats::hclust(d,method="complete")
-#plot(hc)
-groups<-cutree(hc, k=3)
-
-all_data_cluster <- cbind(one_harmony_data, groups) %>% 
-  left_join(mds, by = "customer_id") %>% 
-  mutate(groups = as.factor(groups))
-
-q2 <- ggpubr::ggscatter(all_data_cluster,
-                  x = "Dim.1",
-                  y = "Dim.2", 
-                  label = rownames(mds),
-                  color = "groups",
-                  size = 1,
-                  repel = TRUE)
-
-q1 + q2
-```
-
-# application to 4 households
-
-The smart meter data set from four households in Melbourne referred in @wang2020calendar has been utilized to see the use of the distance measure proposed in the paper.
-The data is a tsibble  containing half-hourly electricity consumption from Jan-2018 to Jun-2018 for each of the households, which is procured by them by downloading their data from the energy supplier/retailer.
-Demand data for these households are shown in a linear time scale in \autoref{fig:linear-scale}.
-It is evident from the range of the demand data that these households vary in consumption levels as well as in their temporal patterns.
-In the left panel of \autoref{fig:linear-scale} (a), the linear representation of the entire time period is shown, whereas in panel B (right) a particular month is shown and furthermore a week has been highlighted to inspect if there is any daily or weekly periodic patterns in their behavior that is evident from the linear representation of the time series.
-We pick household id 2 and 4 for our analysis to see which periodic patterns are important in their behavior, if they are same or different and if it makes sense using our distance metric to select and rank the important harmonies.
-
-```{r linear-scale, fig.cap = "Electricity demand for four households are shown in different facets from Jan-18 to Jun-18 in Fig a and it has been zoomed in for Feb-18 in Fig b, where a week in Feb-18 has been highlighted.
-From the scales of Fig a, it is apparent that they have different level of consumption but all of them have some periodic behavior in terms of regular peaks and troughs.
-It is not clear which all periodic patterns exist.
-In fig b, periodic pattern is zoomed in for a month and we can see weekly patterns for the entire period and daily pattern for the highlighted week."}
-library(scales)
-library(tidyquant)
-library(gghighlight)
-
-elec_linear <- elec %>% 
-  ggplot() +
-  geom_line(aes(x = date_time, y = kwh)) +
-  facet_wrap(~id, nrow = 4, labeller = "label_both",
-             strip.position =  "right",
-             scales = "free_y") +
-  theme_pubclean() 
-#+
- # geom_rect(aes(xmin = as.Date("2018-02-01"), xmax = as.Date("2018-02-28"), ymin = -Inf, ymax = Inf),colour="white", size=0.5, alpha=0.02)
-
-elec_zoom <-  elec %>%
-  filter(date >as.Date("2018-02-01") & date < (as.Date("2018-02-28"))) %>% 
-  ggplot(aes(x=date_time, y = kwh)) +
-  geom_line(alpha = 0.5, size = 0.1) +
-  facet_wrap(~id, scales = "free_y", ncol = 1, strip.position =  "right") +
-  gghighlight(date >as.Date("2018-02-05") & date < (as.Date("2018-02-12")), unhighlighted_params = list(colour = "blue"))
-
-  # geom_rect(xmin = as.Date("2018-02-02"), xmax = as.Date("2018-02-04"), ymin = -Inf, ymax = Inf, fill = "pink", colour = pink)
-
-# elec_zoom <- elec_linear + 
-#   coord_x_date(xlim = c("2018-02-01", "2018-02-28")) +
-#   gghighlight(date >as.Date("2018-02-05") & date < (as.Date("2018-02-12")),
-#               unhighlighted_params = list(colour = "grey")) + geom_line(aes(x = date_time, y = kwh, group = time))
-
-elec_linear + elec_zoom +
-   xlab("Date") +
-  ylab("demand(in kwh)")
-# elec %>% dplyr::filter(date> as.Date("2018-02-01") & date<as.Date("2018-02-28"))
-
-```
-
-<!-- **Normal-quantile-transform**  -->
-
-<!-- **Characterizing empirical distributions through quantiles** ( write in the methodology maybe) -->
-
-<!-- **Computing JS distances between harmonies for each categories of the cyclic granularity involved** -->
-
-```{r raw-nqt}
-elec_raw <- elec %>% 
-  ggplot() +
-  geom_density(aes(x = kwh)) +
-  facet_wrap(~id, scales = "free_y", ncol = 1) +
-  xlab("demand (in kwh)")
-
-elec_nqt <- elec %>% 
-  dplyr::mutate(kwh_transformed = stats::qqnorm(kwh, plot.it = FALSE)$x) %>% 
-  ggplot() +
-  geom_density(aes(x = kwh_transformed))+
-  facet_wrap(~id, scales = "free_y", ncol = 1) +
-  xlab("NQT demand (in kwh)")
-
-# hour_day_raw <- elec %>% 
-#   tsibble::as_tsibble(index = date_time, key = id) %>% 
-#     create_gran("hour_day") %>% 
-#     ggplot() + 
-#     ggridges::geom_density_ridges(aes(y=hour_day, x = kwh))
-#   
-# hour_day_trans <- elec %>% 
-#   tsibble::as_tsibble(index = date_time, key = id) %>% 
-#     create_gran("hour_day") %>% 
-#   dplyr::mutate(kwh_transformed = stats::qqnorm(kwh, plot.it = FALSE)$x) %>% 
-#   ggplot() +
-#   ggridges::geom_density_ridges(aes(y=hour_day, x = kwh_transformed))
-
-elec_raw + elec_nqt
-
-```
-
-Let $y_{i, t}$ denote the electricity demand for $i^{th}$ household for time period $t$.
-This is expected to have an assymmetrical distribution as could be seen in \ref{fig:raw-nqt} and the Normal score transform has been applied to make it more symmetric.
-Let $y*_{i, t}$ denote the normal-quantile transformed electricity demand for $i^{th}$ household for time period $t$.
-Technically, this $y*_{i, t}$ is the linear granularity corresponding to half-hour since the interval of this data is 30 minutes.
-We consider coarser linear granularities like hour, day, week and month from the commonly used Gregorian calendar.
-Considering 4 linear granularities hour, day, week, month in the hierarchy table, the number of cyclic granularities is $N_C = (4 * 3/2) = 6$.
-We obtain cyclic granularities namely “hour_day”, “hour_week”, “hour_month”, “day_ week”, “day_month” and “week_month”, read as “hour of the day”, etc.
-Further, we add cyclic granularity day-type( “wknd wday”) to capture weekend and weekday behavior.
-Thus, we consider 7 cyclic granularities in the set of cyclic granularities of interest defined by $C_{N_C}$.
-We then compute the set of harmonies $H_{N_C}$  from $C_{N_C}$ by choosing pairs of cyclic granularities that are not clashes using procedures described in [@Gupta2020-vo].
-The paper also shows how the number of harmonies could be identified among 42 pair of granularities by removing clashes.
-This section shows how we could refine the search further by only looking at significant harmonies.
-
-Suppose $(A, B) \in H_{N_C}$ be a harmony pair where  $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.
-Suppose $q^{i, p}_{A, j}$ denote the quantiles with probability $p$ for the of the $i^{th}$ household for $j^{th}$ category of the cyclic granularity $A$.
-Similarly, $q^{i, p}_{B, k}$ denotes the same for the $k^{th}$ category of the cyclic granularity $B$.
-Sample quantiles were computed at $p = 0.01, 0.02, \dots, 0.99$.
-Jensen-Shannon distances are computed between $q^{i, p}_{A, j}$ and $q^{i, p}_{B, k}$ for each ${j \in J, k \in K}$ to obtain within-facet and between-facet distances.
-A tuning parameter of $\lambda = 0.67$ has been considered to upweigh the within-facet distances and down-weigh the between facet distances and the maximum of them are obtained to compute $wpd_{raw}$.
-It is further normalized using the approach described in Section \ref{sec:normalization}.
-This entire process is repeated for all harmony pairs $(A, B) \in H_{N_C}$ and for each households $i \in i = \{1, 2, 3, 4\}$.
-The harmony pairs are then arranged in descending order and the important ones with significance level 1%, 5% and 10% are highlighted with `***`, `**` and `*` respectively.
-
-Table \ref{tab:} shows the rank of the harmonies for different households
-\autoref{fig:} shows the bubble chart for the four households with size as the value of wpd and color indicating how significant they are.
-This is a quick summary of which harmonies are significant and also which cyclic granularities are important for the context.
-
-```{r rank-household-mclapply}
-elec <- read_rds(here("paper/data/elec.rds")) %>% 
-  filter(date >= ymd("20180101"), date < ymd("20180701"))
-rdbl <- c("Weekday" = "#d7191c", "Weekend" = "#2c7bb6")
-
-library(tictoc)
-#tic()
-elec_split = elec %>% group_split(id)
-
-elec_select_harmony = parallel::mclapply(1:4, function(x){
-
-  data_id <-  elec_split %>% magrittr::extract2(x) %>% 
-    as_tsibble(index = date_time)
-
-harmonies <- data_id %>%
-  harmony(
-    ugran = "month",
-    filter_in = "wknd_wday",
-    filter_out = c("hhour", "fortnight")
-  )
-
- hakear::select_harmonies(data_id,
-   harmony_tbl = harmonies,
-   response = kwh,
-   nperm = 200,
-   nsamp = 200
- )
-
-}, mc.cores = parallel::detectCores() - 1, mc.preschedule = FALSE, mc.set.seed = FALSE)
-#toc()
-```
-
-```{r elec_select_harmony}
-elec_harmony_all <- elec_select_harmony %>% 
-  bind_rows(.id = "id") %>% 
-  mutate(facet_variable = case_when(
-    facet_variable == "hour_day" ~ "hod" ,
-    facet_variable == "day_month" ~ "dom" ,
-    facet_variable == "day_week" ~ "dow" ,
-    facet_variable == "week_month" ~ "wom" ,
-    facet_variable == "wknd_wday" ~ "wdwnd"
-  )) %>% 
-  mutate(x_variable = case_when(
-    x_variable == "hour_day" ~ "hod" ,
-    x_variable == "day_month" ~ "dom" ,
-    x_variable == "day_week" ~ "dow" ,
-    x_variable == "week_month" ~ "wom" ,
-    x_variable == "wknd_wday" ~ "wdwnd"
-  )) %>% 
-  mutate(id = paste("id", id, sep = " ")) %>% 
-  group_by(id) %>% 
-  mutate(rank = row_number())
-
-```
-
-```{r dotplot, fig.cap = "Harmony pairs are shown for all household ids.
-The size represent how important the pair is and the colour represents if the harmonies are at all important or not.
-Visualizing the pairs in this way helps us to see the important cyclic granularities along the x-axis and facet along with the information that which ones amongst them should be analyzed together." }
-elec_sig_split <- elec_harmony_all %>%
-  mutate(select_split =  str_split(select_harmony, " ", simplify = TRUE)[,2]) %>% 
-  mutate(significant = case_when(
-    select_split == "***" ~ "highest",
-    select_split == "**" ~ "high",
-    select_split == "*" ~ "medium",
-    select_split == "" ~ "low"
-  )) %>% 
-   mutate(rank = case_when(
-    select_split == "***" ~ paste(rank, "***", sep = " "),
-    select_split == "**" ~  paste(rank, "**", sep = " "),
-    select_split == "*" ~  paste(rank, "*", sep = " "),
-    select_split == "" ~  paste(rank, "", sep = " ")
-  ))
-
-elec_sig_split$significant <- 
-  factor(elec_sig_split$significant, levels = c("highest", "high", "medium", "low"))
-
-dotplot <- elec_sig_split %>% 
-  ggplot() +
-  geom_point(aes(x = x_variable,
-                 y = facet_variable, 
-                 size = wpd, 
-                 fill = significant),
-             shape=21,
-             alpha= 0.8) +
-  scale_size_continuous() +
-  theme(legend.position = "bottom") +
-  scale_fill_viridis(discrete = TRUE, direction = 1) +
-  facet_wrap(~id, nrow = 1) +
-  guides(fill = guide_legend(), 
-         size = guide_legend()) +
-  theme_gray(base_size = 12, base_family = "Times") +
-   theme(legend.position = "bottom")
-
-#myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
-
-heatplot <- elec_sig_split %>% 
-  ggplot() +
-  geom_tile(aes(x = x_variable,
-                 y = facet_variable, 
-                 fill = wpd)) + 
-  scale_fill_continuous(type = "gradient") +
-  theme(legend.position = "bottom") +
-  facet_wrap(~id, nrow = 1) +
-  coord_fixed() + 
-  guides(fill = guide_legend()) +
-  theme_void() +
-  theme_gray(base_size = 12, base_family = "Times") +
-  theme(panel.grid = element_blank(),
-        axis.text.x = element_text(angle = 60, hjust=1)
-        , legend.position = "bottom")
-  heatplot
-```
-
-```{r tab-rank}
-elec_rank <- elec_sig_split %>% 
-  select(-c(6,7, 9, 10)) %>% 
-  pivot_wider(
-              names_from = id,
-                values_from = rank) %>% 
-  rename("facet variable" = "facet_variable",
-         "x variable" = "x_variable",
-         "facet levels" = "x_levels",
-         "x levels" = "x_levels")
-
-elec_rank %>% kable(format = "markdown", caption = "Ranking of the harmonies for the four households are shown.
-The first four harmonies are unanimously important for all households, after which there is differences in the rankings for most households.")
-```
-
-```{r gravitas-plot, message = FALSE, warning=FALSE, fig.cap="Distribution of energy demand shown for household id: 2 across hod in x-axis and wd-wnd in facets in a) and just the reverse in b).
-In c), distribution of energy demand for household id:4 shown across hod and wd-wnd.
-It can be seen that the differences in distributions are more apparent when viewed in a) as compared to b).
-It seems like there is more difference in the distributions of hod for b) compared to c).
-This also confers with the value of the normalised measure shown in Figure 11."}
-p1 <- id2_tsibble %>%
-   prob_plot("hour_day",
-             "wknd_wday",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = FALSE,
-             quantile_prob = c(0.25,0.5,0.75)) +
-  ggtitle("a") + 
-  scale_colour_brewer(name = "", palette = "Set2") +
-  theme(legend.position = "none",
-        strip.text = element_text(size = 7, margin = margin()))
-
-p2 <- id2_tsibble %>%
-   prob_plot("wknd_wday",
-             "hour_day",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = FALSE,
-             quantile_prob = c(0.25,0.5,0.75)) +
-  ggtitle("b") +
-  scale_colour_brewer(name = "", palette = "Set2")   +
-  theme(legend.position = "none",
-        strip.text = element_text(size = 7, margin = margin())) + xlab("")
-
-p3 <- id4_tsibble %>%
-   prob_plot("wknd_wday",
-             "hour_day",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = FALSE,
-             quantile_prob = 
-               c(0.25,0.5,0.75)) +
-  ggtitle("c") +
-  scale_colour_brewer(name = "", palette = "Set2") +
-  theme(
-        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + theme(legend.position = "bottom",
-        strip.text = element_text(size = 7, margin = margin()))
-
-p1 + p2/p3
-
-```
-
-## Null distribution
-
-### Size: Simulated same distribution for all combinations of categories for all harmony pairs.
-
-Failure to reject the null hypothesis when there is in fact no significant effect.
-
-### Normalised maximum distances follow standard Gumbel distribution
-
-### Limiting distribution of median of normalised maximum distances is normal
-
-Let a continuous population be given with cdf F(x) (cumulative distribution function) and median $\xi$ (assumed to exist uniquely).
-For a sample of size $2n + 1$, let $\tilde{x}$ denote the sample median.
-The distribution of $\tilde{x}$,under certain conditions, to be asymptotically normal with mean $\xi$ and variance $\sigma_n^2 = \frac{1}{4} [f(\xi)]^2(2n + 1)$, where $f(x) = F'(x)$ is the pdf (probability density function).
-
-<!-- ### Confidence interval of test statistic -->
-
-## Power
-
-## Confidence interval
-
-Failure to reject the null hypothesis when there is in fact a significant effect.
-
-To estimate the sampling distribution of the test statistic we need many samples generated under the null hypothesis.
-If the null hypothesis is true, changing the exposure would have no effect on the outcome.
-By randomly shuffling the exposures we can make up as many data sets as we like.
-If the null hypothesis is true the shuffled data sets should look like the real data, otherwise they should look different from the
-real data. The ranking of the real test statistic among the shuffled test statistics gives a p-value.
-
-<!-- Consider two cyclic granularities $A$ and $B$ with $2$ and $3$categories.
-Thus, the harmony table consisting of all possible harmony pairs (assuming all pairs are harmonies), would look like the following: -->
-
-```{r harmony_min}
-# harmonies <- tibble::tibble(facet_variable = c("A", "B", "A", "C", "B", "C"),
-#                             x_variable  = c("B","A", "C", "A", "C", "B"),
-#                             facet_levels = c(2, 3, 2, 4, 3, 4),
-#                             x_levels = c(3, 2, 4, 2, 4, 3))
-# 
-# harmonies <- tibble::tibble(facet_variable = c("A", "B"),
-#                             x_variable  = c("B","A"),
-#                             facet_levels = c(2, 3),
-#                             x_levels = c(3, 2))
-#                             
-# harmonies %>% knitr::kable()
-```
-
-<!-- The output table has the value of MMPD (normalized median maximum pairwise distances), gt_MMPD(global threshold of MMPD indicator). -->
-
-<!-- # ```{r samenull_2by4, eval = FALSE} -->
-<!-- #  -->
-<!-- # ``` -->
-
-<!-- # ```{r normalv21_power} -->
-<!-- #  -->
-<!-- # ``` -->
-<!-- #  -->
-<!-- #  -->
-<!-- # ```{r normalv22_power} -->
-<!-- #  -->
-<!-- # ``` -->
-
-### Varying distribution across facet
-### Varying distribution across x-axis
-### Varying distribution across both facets and x-axis
-### Repeat all with varying facet and x-axis levels
-
-<!-- ### Power: Simulated same distribution for all combinations of categories for all harmony pairs. -->
-
-<!-- # ```{r normalv23_power} -->
-<!-- #  -->
-<!-- # ``` -->
-<!-- #  -->
-<!-- #  -->
-<!-- # ```{r normalv24_power} -->
-<!-- #  -->
-<!-- # ``` -->
-
-*Conclusion*: The test should reject the null hypothesis if distributions are different.
-
-<!-- ### Scenario 2: Simulated different distributions for all combinations of categories for harmony pairs for few levels. -->
-
-<!-- ```{r diffnull_2by4, eval = FALSE} -->
-
-<!-- ``` -->
-
-<!-- *Conclusion*: The test select the harmony pair for which distribution of x-axis categories are significantly different -->
-
-<!-- ### Scenario 3: Simulated different distributions for all combinations of categories for all harmony pairs with many levels. -->
-
-<!-- ```{r diffnull_7by11, eval = FALSE} -->
-<!-- ``` -->
-
-<!-- *Conclusion*: The test indicates that both harmony pairs do not have significant variation. -->
-
-<!-- ### Scenario 4: Simulated different distributions for all combinations of categories for all harmony pairs with many levels - very different distribution across x-axis -->
-
-<!-- ```{r diffnull_7by11normal, eval = FALSE} -->
-<!-- ``` -->
-
-<!-- *Conclusion*: The test indicates that only the first harmony pair has significant variation. -->
-
-<!-- ### Scenario 5: Simulated different distributions for all combinations of categories for all harmony pairs with many levels - very different distribution across facets -->
-
-<!-- ```{r diffnull_7by11normal2, eval = FALSE} -->
-<!-- ``` -->
-
-<!-- *Conclusion*:  -->
-
-<!-- ## Scenario 4: Cumulative 3 levels with 2, 7 and 11 and testing level and power -->
-
-<!-- ```{r samenull_3levels} -->
-
-<!-- ``` -->
-
-<!-- *Conclusion*: With 3 levels the test incorrectly chooses 1 harmony pair with similar distribution. The harmony pair which is displayed. -->
-
-<!-- <!-- ```{r diffnull_3levels} -->
-
-<!-- <!-- ``` -->
-
-<!-- *Conclusion*: The test with MMPD selects just one pair, as opposed to the test with maximum.
-This needs to be checked against what we expect from the test.
-The harmony pairs which are selected (either through MMPD or maximum) are displayed.
--->
-
-<!-- # ```{r} -->
-<!-- # harmonies <- tibble::tibble(facet_variable = c("A", "B"),x_variable  = c("B","A"), facet_levels = c(2, 3),x_levels = c(3, 2)) -->
-<!-- #  -->
-<!-- # har1 <- harmonies[1,] -->
-<!-- #  -->
-<!-- # sim_dist1 = c(rep(distributional::dist_normal(mu = 10, sigma = 5),2),rep(distributional::dist_exponential(10),2), rep(distributional::dist_weibull(0.5, 2),2)) -->
-<!-- #  -->
-<!-- # data1 <- sim_distharmony1(har1, sim_dist = sim_dist1) -->
-<!-- # data1 -->
-<!-- #  -->
-<!-- # data1 %>% unnest(sim_dist) %>% -->
-<!-- #   ggplot(aes(x = Var2, y = sim_dist)) + -->
-<!-- #   facet_wrap(~Var1) + geom_boxplot() + ggtitle("Same distribution 2 by 3") -->
-<!-- #  -->
-<!-- # response = "sim_dist" -->
-<!-- #  -->
-<!-- # MMPD_distribution <- data1 %>% -->
-<!-- #   select(-dist) %>%  -->
-<!-- #   unnest(sim_dist) %>%  -->
-<!-- #   list() %>%  -->
-<!-- #   global_threshold(harmony_tbl = har1, -->
-<!-- #                    response = "sim_dist", -->
-<!-- #                    dist_distribution = "normal", -->
-<!-- #                    dist_ordered = TRUE, -->
-<!-- #                    create_gran_data = FALSE, nsamp = 20) -->
-<!-- #  -->
-<!-- # # as_tibble(sample_MMPD) %>% mutate(id = row_number()) %>%  -->
-<!-- # #   ggplot() + geom_histogram(aes(x = value)) -->
-<!-- #  -->
-<!-- # ``` -->
-<!-- #  -->
-
-<!-- # Visualisation -->
-
-<!-- Leader plots like in Scagnostics paper -->

### 2021-03-03 paper/main.Rmd
nomenclature table added

@@
 With temporal data available at finer scales, exploring periodicity and their relationships can become overwhelming with so many possible cyclic temporal granularities [@Gupta2020-vo] to explore.
-
-```{r calendar-elec, fig.height = 10.5, fig.cap="Calendar display."}
+\noindent Take the example of the calendar display of electricity smart meter data in Figure (\ref{fig:calendar-elec}) used in @wang2020calendar for four households in Melbourne, Australia.
+The authors show how hour-of-the-day interact with weekdays and weekends and then move on to use calendar display to show daily schedules.
+The calendar display has several components in it, which helps us to look at energy consumption across hour-of-the-day, day-of-the-week, week-of-the-month, and month-of-the-year at once.
+Some interaction of these cyclic granularities, for example, how  day-of-week relates to month-of-year, could also be interpreted from this display.
+This is a great way for having an overview of energy consumption.
+However, if one wants to understand the periodicities in energy behavior and how the periodicities interact in greater detail, it is not easy to comprehend the interactions of some periodicities' from this display, due to the combination of linear and cyclic representation of time.
+For example, this display might not be the best to understand how hour-of-the-day or month-of-year varies across week-of-the-month as well as with each other.
+Furthermore, it is not clear what all interactions of cyclic granularities should be read from this display as there could be many combinations that one can look at.
+Moreover, _"calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions"_ (@Gupta2020-vo) and could include other cyclic granularities like hour-of-week or day-of-fortnight, which could potentially become useful depending on the context.
+Possible areas where it is useful are monitoring heart rates which could record number of heartbeats every minute or analyze web search data for which data is available for a temporal scale as fine as second.
+
+```{r calendar-elec, fig.height = 8, fig.cap = "Calendar displays faceted by two households are shown.
+The calendar displays are rich in information and has several components.
+For example, it can be observed easily that the level of energy consumption by household 2 is higher than household 4.
+Also, it gives an overview on when these households are away for holidays and which months consumptions are highest (Jan, Feb).
+However,when it comes to discerning periodic patterns, analyzing all possible periodic patterns through this display is overwhelming due to combination of linear and cyclic representation of time.
+For example, there is more going on in terms of peaks and troughs in id 2 compared to id 4, but it is not clear which all periodic patterns are dominant and if it differs between households."}
 elec <- read_rds(here("paper/data/elec.rds")) %>% 
@@
 
-\noindent Take the example of the calendar display of electricity smart meter data in Figure (\ref{fig:calendar-elec}) used in @wang2020calendar for four households in Melbourne, Australia.
-The authors show how hour-of-the-day interact with weekdays and weekends and then move on to use calendar display to show daily schedules.
-The calendar display has several components in it, which helps us to look at energy consumption across hour-of-the-day, day-of-the-week, week-of-the-month, and month-of-the-year at once.
-Some interaction of these cyclic granularities, for example, how  day-of-week relates to month-of-year, could also be interpreted from this display.
-This is a great way for having an overview of energy consumption.
-However, if one wants to understand the periodicities in energy behavior and how the periodicities interact in greater detail, it is not easy to comprehend the interactions of some periodicities' from this display, due to the combination of linear and cyclic representation of time.
-For example, this display might not be the best to understand how hour-of-the-day or month-of-year varies across week-of-the-month as well as with each other.
-Furthermore, it is not clear what all interactions of cyclic granularities should be read from this display as there could be many combinations that one can look at.
-Moreover, _"calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions"_ (@Gupta2020-vo) and could include other cyclic granularities like hour-of-week or day-of-fortnight, which could potentially become useful depending on the context.
-Possible areas where it is useful are monitoring heart rates which could record number of heartbeats every minute or analyze web search data for which data is available for a temporal scale as fine as second.
-
 <!-- context when it could be useful is monitoring heart rates.
@@
              quantile_prob = c(0.1, 0.25,0.5,0.75, 0.9)) + 
-  ggtitle("") + theme(
+  ggtitle("a") + theme(
         strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
@@
              quantile_prob = c(0.25,0.5,0.75)) +
-  ggtitle("") +  #+ scale_x_discrete(breaks = seq(0, 23, 4)) + 
+  ggtitle("b") +  #+ scale_x_discrete(breaks = seq(0, 23, 4)) + 
 theme(
@@
 
-```{r id2, fig.cap = "something"}
+```{r id2, fig.cap = "Distribution of energy consumption displayed through area quantile plots across two cyclic granularities month-of-year and hour-of-day for id2 (a) and id4 (b).
+The black line is the median, whereas the purple band covers the 25th to 75th percentile, the orange band covers the 10th to 90th percentile, and the green band covers the 1st to 99th percentile.
+Difference between 90th and 75th quantiles less for (Jan, Feb) in a) suggesting that it is a more frequent user of air conditioner than b).
+Energy consumption in a) changes across both granularities, whereas for b) daily pattern stays same irrespective of the months."}
 ggpubr::ggarrange(p1, p2, ncol = 2)
@@
 Finally, $D_{var_{all}}$ denotes those designs for which difference is observed across both $A$ and $B$.
+
+```{r}
+d1 <- tibble (variable = c("nx", "nfacet", "$N_C$", "$H_{N_C}$", "$lambda$", "$omega$", "$wpd$","$nperm$", "$nsim$"),  description = c("number of x categories", "number of facet categories","number of cyclic granularities", "set of harmonies", "tuning parameter", "mean increment", "raw distance measure", "number of permutations for threshold/normalization", "number of simulations"))
+
+d2 <- tibble(variable =  c("$wpd_{norm}$", 
+                           "$wpd_{threshold}$",
+                           "$D_{null}$",
+                           "$D_{var_f}$", 
+                           "$D_{var_x}$",
+                           "$D_{var_{all}}$"), 
+             description = c("normalized distance measure",
+                             "threshold for significance",
+                             "null design",
+                             "design with varying facets only", 
+                             "design with varying x only", 
+                             "design with varying both facets and x"))
+
+d <- bind_rows(d1, d2)
+knitr::kable(d, format = "markdown", escape = FALSE, caption = "Nomenclature table")
+
+```
 

### 2021-03-03 paper/main.Rmd
spell check done

@@
 The quantile of a distribution with probability $p$ is defined as $Q(p)=F^{-1}(p) = inf\{x: F(x) >p\}$, $0<p< 1$ where $F(x)$ is the distribution function.
-There are two broad approaches to quantile estimation, viz, parametric and non-parameteric.
+There are two broad approaches to quantile estimation, viz, parametric and non-parametric.
 The benefit of using a non-parametric estimator is that there are less rigid assumptions made about the nature of the underlying distribution of the data.
@@
 
-_Generalised linear model_
+_Generalized linear model_
 
@@
 
-(3, 2), (7,9), (14, 10) being null sets and others under some other design. Generate 200 repitions of different data sets with the same design for all the pairs and compute size and power.
+(3, 2), (7,9), (14, 10) being null sets and others under some other design. Generate 200 repetitions of different data sets with the same design for all the pairs and compute size and power.
 
@@
 Thus, $7$ cyclic granularities are considered to be of interest.
-The set consisting of pairs of cyclic granularities ($C_{N_C}$) will have $7_{P_2}=42$ elements which could be analysed for detecting possible periodicities.
+The set consisting of pairs of cyclic granularities ($C_{N_C}$) will have $7_{P_2}=42$ elements which could be analyzed for detecting possible periodicities.
 The set of possible harmonies $H_{N_C}$ from $C_{N_C}$ are chosen by removing clashes using procedures described in [@Gupta2020-vo].

### 2021-03-03 paper/main.Rmd
proof-read 1 till permutation approach

@@
 
-We are interested in assessing the structure in probability distributions of the measured variable across bivariate cyclic granularities.
+We are interested in assessing the structure of the measured variable across bivariate cyclic granularities.
 We propose a measure called Weighted Maximum Pairwise Distances (wpd) to quantify the structure in such a design.
@@
 
-Intuitively, while finding a structure or measuring the strength of patterns in Figure \ref{fig:null4by2}, it makes sense to look for within-group and between-group variation.
+Intuitively, while finding a structure or measuring the strength of patterns in Figure \ref{fig:null4by2}, it makes sense to look for within-group and between-group variations.
 Larger variation would imply stronger patterns, whereas small variation would imply the underlying structure is not changing within or between group.
 Thus, a distance measure aimed to capture this structure should ideally estimate these within-group and between-group variations.
-One of the potential ways to do this is to measure the distances between distributions of the continuous random variable measured within and between groups, weigh them basis if they are within or between groups and then take the maximum of those distances as an estimate of the strength of the structure.
-We call this metric $wpd$ which stands for Weighted Pairwise Distances.
+One of the potential ways to do this is to measure the distances between distributions of the continuous random variable measured within and between groups, weigh them basis if they are within or between groups and then take the maximum of those distances as an estimate of the maximum variation in the structure.
 This section starts with possible ways of characterizing distributions and computing distances between them and then describe in details how the measure $wpd$ is defined.
-This is similar to @ieee-irish where the authors compute the Jensen Shannon distance between two density estimates by computing percentiles and stresses the advantages to working with percentiles rather than the data directly in case of missing observations or even unsynchronized time series.
+This is similar to @ieee-irish where the authors compute the Jensen Shannon distance between two density estimates by computing percentiles and stresses the advantages to working with percentiles rather than the raw data directly in case of missing observations.
+Working with quantiles also ensure that unsynchronized time series could be handled.
 
@@
 The number of observations and the structure might vary widely across subsets due to the structure of the calendar, missing observations or uneven locations of events in the time domain.
-Each $v_{jk} : j\in \{1, 2, \dots, J\}, k\in \{1, 2, \dots, K\}\}$ is assumed to be drawn from a continuous probability distribution and have certain characteristics.
-Often shape, central tendency, and variability are the common characteristics used to describe the distribution.
-Mean, median or mode are generally used to describe the center of the distribution, while range, standard deviation, quantiles, standard errors and confidence intervals are often used to describe variability in the distribution.
+Each $v_{jk}$'s $\forall j\in \{1, 2, \dots, J\}, k\in \{1, 2, \dots, K\}\}$ are assumed to be drawn from a continuous probability distribution and have certain characteristics.
+Often shape, central tendency, and variability are the common characteristics used to describe a distribution.
+Mean, median or mode are generally used to describe the center of the distribution, while range, standard deviation, quantiles, standard errors and confidence intervals are used to describe variability.
 Quantiles are chosen as a way to characterize distributions in this paper.
@@
 The benefit of using a non-parametric estimator is that there are less rigid assumptions made about the nature of the underlying distribution of the data.
-Sample quantiles could be used for estimation in a non-parametric setup.
-@Hyndman1996-ty describes the difficulty in defining sample quantiles and recommends the use of median-unbiased estimator because of _*"desirable properties of a quantile estimator and can be defined independently of the underlying distribution."*_.
+Sample quantiles could be used for estimating population quantiles in a non-parametric setup.
+@Hyndman1996-ty describes the many ways of defining sample quantiles and recommends the use of median-unbiased estimator because of _desirable properties of a quantile estimator and can be defined independently of the underlying distribution._.
 The `stats::quantile()` function in @R-language could be used for practical implementation where type = 8 refers to the algorithm corresponding to the median-unbiased estimator.
@@
 
-In this paper, the pairwise distances between the distributions of the measured variable are computed through Jensen-Shannon distance (JSD), defined by,
+In this paper, we propose to use the pairwise distances between the distributions of the measured variable through Jensen-Shannon distance (JSD), defined by,
 
@@
 
-Furthermore, these distances are distributed as chi-squared with $m$ degrees of freedom (Menendez1997-in), where the continuous distribution is being discretized with $m$ discrete values.
+Furthermore, these distances are distributed as chi-squared with $m$ degrees of freedom (Menendez1997-in), if the continuous distribution is being discretized with $m$ discrete values.
 Taking sample percentiles to approximate the integral would mean taking $m = 99$.
@@
 Furthermore, the intended aim of $wpd$ is to capture differences in categories irrespective of the distribution from which the data is generated.
-Hence, as a pre-processing step,the raw data is normal quantile transformed so that the quantile of the transformed data follows a standard normal distribution.
+Hence, as a pre-processing step,the raw data is normal quantile transformed (reference) so that the quantiles of the transformed data follows a standard normal distribution.
 The steps employed for computing the distance measure is summarized as follows:
@@
 
-3. Percentiles of $v^*_{jk}$ are computed and stored in $q_{jk}$. Repeat for all pairs of categories of the form $(a_{j} b_{k}, a_{j'}b_{k'}): j = 1, 2, \dots, J\}, B = \{ b_k: k = 1, 2, \dots, K\}$.
+3.
+Percentiles of $v^*_{jk}$ are computed and stored in $q_{jk}$.
+Repeat for all pairs of categories of the form $(a_{j} b_{k}, a_{j'}b_{k'}): \{a_j: j = 1, 2, \dots, J\}, B = \{ b_k: k = 1, 2, \dots, K\}$.
 
@@
 
-6. Repeat Steps 2-5 for all harmony pairs in $N_C$.
+6. Repeat Steps 2-5 for all harmony pairs in $H_{N_C}$.
 
@@
 
-Simulations were carried out to explore the behavior of $wpd$ under the following factors that could potentially impact the values of $wpd$:
-
-- $nx$ (number of levels of x-axis)
-- $nfacet$ (number of levels of facets)
-- $\lambda$ (tuning parameter)
-- $\omega$ (increment in each panel design)
-- $dist$ (normal/non-normal distributions with different location and scale)
-- $n$ (sample size for each combination of categories)
-- $designs$ ($D_{null}$, $D_{var_f}$, $D_{var_x}$ and $D_{var_{all}}$)
+Simulations were carried out to explore the behavior of $wpd$ under the following factors that could potentially impact the values of $wpd$: $nx$, $nfacet$, $\lambda$, $\omega$, $dist$ (normal/non-normal distributions with different location and scale), $ntimes$, and $designs$ and results are presented in two parts.
+The dependence of $wpd$ on $nx$ and $nfacet$ under $D_{null}$ is presented here, which lays the foundation for the next section.
+The rest of the results that discuss the relationship of the $wpd$ with other factors is presented in details in the Supplementary section of the paper.
+They show that the designs $D_{var_f}$ and $D_{var_x}$ intersect at $\lambda = 0.5$ and hence for up-weighing designs of the form $D_{var_x}$, $\lambda = 0.67$ has been considered for computation of $wpd$ in the rest of the paper.
+
+<!-- - $nx$ (number of levels of x-axis) -->
+<!-- - $nfacet$ (number of levels of facets) -->
+<!-- - $\lambda$ (tuning parameter) -->
+<!-- - $\omega$ (increment in each panel design) -->
+<!-- - $dist$ (normal/non-normal distributions with different location and scale) -->
+<!-- - $n$ (sample size for each combination of categories) -->
+<!-- - $designs$ ($D_{null}$, $D_{var_f}$, $D_{var_x}$ and $D_{var_{all}}$) -->
 
@@
 <!-- - $nperm$ (number of permutations of data)   -->
-
-Results are presented in two parts.
-The dependence of $wpd$ on $nx$ and $nfacet$ under $D_{null}$ is presented here, which lays the foundation for the next section.
-The rest of the results that discusses the relationship of the $wpd$ with other factors is presented in details in the Supplementary section of the paper.
-They show that the designs $D_{var_f}$ and $D_{var_x}$ intersect at $\lambda = 0.5$ and hence for up-weighing designs of the form $D_{var_x}$, $\lambda = 0.67$ has been considered for computation of $wpd$ in the rest of the paper.
 
@@
 Figure \ref{fig:raw} shows the distribution of $wpd$ plotted across different $nx$ and $nfacet$ categories.
-Since under $D_{null}$, there is no difference in distributions across different categories, we expect the distance measure $wpd$ to reflect that as well and have the same null distribution across categories.
+Since under $D_{null}$, there is no difference in distributions across different categories, we expect the distance measure $wpd$ to reflect that as well and have the same distribution across categories.
 But Figure \ref{fig:raw} shows that both the location and scale of the distributions change across panels.
@@
 
-```{r raw, fig.cap = "Distribution of $wpd$ is plotted across different $nx$ and $nfacet$ categories. Both shape and scale of the distribution changes for different nx and nfacet categories."}
+```{r raw, fig.cap = "Distribution of $wpd$ is plotted across different $nx$ and $nfacet$ categories under $D_{null}$.
+Both shape and scale of the distribution changes for different comparisons.
+This is not desirable since under null design, the distribution of the distance measure is not expected to capture any differences."}
 G21 <- read_rds("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds")
@@
 
-```{r quadratic, fig.cap = "$wpd$ is plotted against $nx*nfacet$ (the maximum number of pairwise comparisons) and the blue line represents the median of the multiple values for each $nx*nfacet$ levels.
-The median increases abruptly for lower values of $nx*nfacet$ and slowly for higher $nx*nfacet$."}
+```{r quadratic, fig.cap = "$wpd$ is plotted against $nx*nfacet$ (the maximum number of pairwise comparisons) and the blue line represents the median of the multiple values for each $nx*nfacet$.
+The median increases abruptly for lower values of $nx*nfacet$ and slowly for higher $nx*nfacet$.
+Thus, the measure will have higher values for higher levels in $nx$ or $nfacet$."}
 G21 %>% 
   ggplot(aes(x=nx*nfacet, y = value)) +
-  geom_point() + stat_summary(fun=median, geom="line", aes(group=1), color = "blue") + xlab("nx*nfacet") + ylab("wpd")
+  geom_point(alpha = 0.5, size = 0.5) + stat_summary(fun=median, geom="line", aes(group=1), color = "blue") + xlab("nx*nfacet") + ylab("wpd")
 
@@
 The measure $wpd_{norm}$ could potentially lead to comparison of the measure across different panels and also help distinguishing the interesting panels from a data set.
-We discuss two approaches for normalization, both of which are based on the simulation results.
+We discuss two approaches for normalization, both of which are substantiated using simulations.
 
@@
 
-We need a transformation on ${wpd}$ which will make it independent of the values of $nx*nfacet$.
-Two approaches have been employed for that purpose, the first one involves fitting a model and the latter involves a permutation method to make the distribution of the transformed $wpd$ similar for different comparisons.
+The transformed ${wpd}$ which is normalized for the values of $nx$ and $nfacet$ is denoted by $wpd_{norm}$.
+Two approaches have been employed - the first one involves a permutation method to make the distribution of the transformed $wpd$ similar for different comparisons and the second one fits a model to represent the relationship between the two variables and defines ${wpd_norm}$ as the residual of the model.
 
@@
 
-This method is somewhat similar in spirit to bootstrap or permutation tests, where the goal is to test the hypothesis that the groups under study have identical distributions.
+This method is somewhat similar in spirit to bootstrap (reference) or permutation (reference) tests, where the goal is to test the hypothesis that the groups under study have identical distributions.
 This method, in essence, accomplishes a different goal of making the location and scale of different groups (panels) same under $D_{null}$.
@@
 
-1. Compute $wpd$ for a harmony pair (A, B) for the original measured variable $v_t$ and store it in $wpd^{orig}$.
-
-2. Consider a permutation of the original measured variable $v_t^{perm_1}$ and again compute $wpd$ for the permuted data. Store it in $wpd^{perm_1}$.
+1. Compute $wpd$ for a harmony pair (A, B) for the original measured variable $v_t$ and store it in $wpd_{orig}$.
+
+2. Consider a permutation of the original measured variable $v_{perm_1}$ and again compute $wpd$ for the permuted data. Store it in $wpd_{perm_1}$.
 
 3.
-Repeat Step 2 for a large number ($nperm = 200$) of random permutations of the data yielding $nperm$ values : $wpd^{perm_1}, wpd^{perm_2}, \dots, wpd^{perm_{nperm}}$.
-Store the vector in $wpd^{perm}$.
-
-4. Define $wpd^{perm}_{norm} = \frac{(wpd^{orig} - \bar{wpd^{perm}})}{sd(wpd^{perm})}$, where $\bar{wpd^{perm}}$ and $sd(wpd^{perm})$ are the mean and standard deviation of $wpd^{perm}$ respectively.
+Repeat Step 2 for a large number ($nperm = 200$) of random permutations of the data yielding $nperm$ values : $wpd_{perm_1}, wpd_{perm_2}, \dots, wpd_{perm_{nperm}}$.
+Store the vector in $wpd_{perm}$.
+
+4. Define $wpd_{perm} = \frac{(wpd_{orig} - \bar{wpd_{perm}})}{sd(wpd_{perm})}$, where $\bar{wpd_{perm}}$ and $sd(wpd_{perm})$ are the mean and standard deviation of $wpd_{perm}$ respectively.
 
@@
 
-Standardizing the variable $wpd$ in the permutation approach ensures that the distribution of $wpd^{perm}_{norm}$ has the same $mean = 0$ and $sd = 1$ across all comparisons under $D_{null}$.
+Standardizing  $wpd$ in the permutation approach ensures that the distribution of $wpd_{perm}$ has the same $mean = 0$ and $sd = 1$ across all comparisons under $D_{null}$.
 While this works successfully to make the location and scale similar across different $nx$ and $nfacet$ (as seen in Figure \ref{fig:norm}), it is computationally heavy and time consuming, and hence less user friendly when being actually used in practice.
-Hence, we propose another approach to normalization which is more approximate than exact but still has the same accuracy when compared to the permutation approach.
+Hence, we propose another approach to normalization which is more approximate than exact but still has the similar accuracy when compared to the permutation approach.
 

### 2021-03-03 paper/main.Rmd
till choosing threshold

@@
 
-### Simulation design
+### Simulation design{#sec:sim-study}
 
@@
 The transformed ${wpd}$ which is normalized for the values of $nx$ and $nfacet$ is denoted by $wpd_{norm}$.
-Two approaches have been employed - the first one involves a permutation method to make the distribution of the transformed $wpd$ similar for different comparisons and the second one fits a model to represent the relationship between the two variables and defines ${wpd_norm}$ as the residual of the model.
+Two approaches have been employed - the first one involves a permutation method to make the distribution of the transformed $wpd$ similar for different comparisons and the second one fits a model to represent the relationship between the two variables and defines $wpd_{norm}$ as the residual of the model.
 
@@
 
-```{r norm, fig.cap = "Distribution of $wpd^{perm}_{norm}$ is plotted across different $nx$ and $nfacet$ categories.
+```{r norm, fig.cap = "Distribution of $wpd_{perm}$ is plotted across different $nx$ and $nfacet$ categories.
 Both shape and scale of the distributions are now similar for different panels under the null design."}
@@
 A linear model is fitted to model the relationship between $wpd$ and $nx*nfacet$.
-The model is of the form $$y_l = a+b*log(z_l) + e_l$$, where, $y_l = median_m(x_{l, m})$, $z_l$ is the $l^{th}$ panel and $e_l$ are idiosyncratic errors, with parameters $a$ and $b$ being estimated from the data generated through the simulation study described in Section \ref{sec:sim-study}.
-The estimates and other model summary is given in \ref{tab:linear-model}.
+The model is of the form $$y_l = a+b*log(z_l) + e_l$$, where, $y_l = median_m(wpd_{l, m})$, $z_l$ is the $l^{th}$ panel and $e_l$ are idiosyncratic errors, with parameters $a$ and $b$ being estimated from the data generated through the simulation study described in Section \ref{sec:sim-study}.
+The estimates and other model summary is given in Table \ref{tab:linear-model}.
 
@@
 $y^* =  y - \hat a -  \hat b*log(z)$, where 
-$y^*$ is the $wpd_{norm}^{linear}$, 
+$y^*$ is the $wpd_{linear}$, 
 $\hat a$ and $\hat b$ are the estimated values of the parameter $a$ and $b$ and $z = nx*nfacet$.
 
-Defining $wpd_{norm}^{linear}$ in this way forces the mean to be zero and variability to be uniform across the median $wpd$ values as could be seen in Figure \ref{fig:resi-linear}.  
+Defining $wpd_{linear}$ in this way forces the mean to be zero and variability to be uniform across the median $wpd$ values as could be seen in Figure \ref{fig:resi-linear}.  
 <!-- But, the original distribution will still have some dissimilarities in shape and location specially for small values of $nx$ and $nfacet$ as could be seen in \ref{fig:} -->
@@
   ggplot(aes(x=log(nx*nfacet), y = (value - slope*log(nx*nfacet)))) +
-  geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
+  geom_point(alpha = 0.5, size = 0.5) + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
   ylab("wpd normalised using linear modelling approach")
-
 ```
@@
 
-In the linear model approach, $wpd\in R$ was assumed, whereas, $wpd$, Jensen-Shannon Distance (JSD) lies between 0 and 1.
+In the linear model approach, $wpd\in R$ was assumed, whereas, $wpd$ is a  Jensen-Shannon Distance (JSD) and lies between 0 and 1 (reference).
 Furthermore, JSD follows a Chi-square distribution, which is a special case of Gamma distribution.
@@
 We fit a Gamma generalized linear model with the inverse link which is of the form:  
-$$y_l = a+b*log(z_l) + e_l$$, where $y_l = median_m(x_{l, m})$, $z_l$ is the $l^{th}$ panel and $e_l$ are idiosyncratic errors.
+$$y_l = a+b*log(z_l) + e_l$$, where $y_l = median_m(wpd_{l, m})$, $z_l$ is the $l^{th}$ panel and $e_l$ are idiosyncratic errors.
 Let $E(y) = \mu$ and $a + b*log(z) = g(\mu)$ where $g$ is the link function.
@@
 The residuals from this model $(y-\hat y) = (y-1/(\hat a + \hat b log(z)))$ would be expected to have no dependency on $z$.
-Thus,  $wpd_{norm}^{glm}$ is chosen as the residuals from this model and is defined as:
+Thus, $wpd_{glm}$ is chosen as the residuals from this model and is defined as:
 $wpd_{glm} = wpd - 1/(\hat a + \hat b*log(nx*nfacet))$.
@@
 
-```{r wpd-glm-horizontal, echo = FALSE, message=FALSE, fig.caption = "$wpd_{glm}$ is plotted against log(nx*nfacet) and this transformation leads to the median of $wpd_{glm}$ to have no relationship with log(nx*nfacet)"}
+```{r wpd-glm-horizontal, echo = FALSE, message=FALSE, fig.caption = "$wpd_{glm}$ is plotted against log(nx*nfacet) and this transformation causes the median of $wpd_{glm}$ to have no relationship with log(nx*nfacet)"}
 
@@
 
-We see that the transformation through the modeling approach leads to very similar distribution across high $nx$ and $nfacet$ (higher than 7) and not so much for lower $nx$ and $nfacet$.
+We see that the transformation through the modeling approach leads to very similar distribution across high $nx$ and $nfacet$ (higher than $5$) and not so much for lower $nx$ and $nfacet$.
 Hence, the computational load of permutation approach could be alleviated by using the modeling approach for the higher $nx$ and $nfacet$, however, it is important that we use the permutation approach for lower $nx$ and $nfacet$.
-However, it is  difficult to compare the transformed measure from both of these approaches, since each of the variables is measured on a different scale (although each of them have location 0).
-The transformed variables from the two approaches could be brought to the same scale so that for smaller categories, permutation approach is used and for larger categories, we can stick to modeling approach.
+It is difficult to compare and use the transformed measure from both of these approaches alternatively without bringing them to the same scale.
+The transformed variables from the two approaches have to be brought to the same scale so that for smaller categories, permutation approach is used and for larger categories, modeling approach is used.
 
@@
 
-The measure $wpd_{glm}$ has an estimated location of 0 and standard deviation ~ $0.003$, whereas the measure $wpd_{perm}$ which is a z-score, has a normal distribution with location 0 and standard deviation 1.
-To bring them to the same scale, we have defined $wpd_{glm-scaled} = wpd_{glm}*320$, which brings the standard deviation of $wpd_{glm-scaled}$ to almost 1, without changing the location.
+The measure $wpd_{glm}$ has a $\hat \mu_{glm} = 0$ and $\hat sd_{glm} = 0.003$ whereas the measure $wpd_{perm}$ which is a z-score, has an expected normal distribution with  $\hat \mu_{perm} = 0$ and $\hat sd_{perm} = 1$.
+To bring them to the same scale, we have defined $wpd_{glm-scaled} = wpd_{glm}*\frac{\hat sd_{perm}}{\hat sd_{glm}}$, which changes the scale of $wpd_{glm}$ without changing the location.
 The measure $wpd_{glm-scaled}$ seems to roughly follow a normal distribution except in the tails as could be seen in Figure \ref{fig:hist-qq} and the very method of permutation approach ensures that $wpd_{perm}$ is also normally distributed.
-Further, they are brought to the similar scale and location and hence could be compared.
-
-```{r hist-qq, fig.cap = "In panel a, the histogram of $wpd_{glm-scaled}^{norm}$ is plotted.
+Further, they are brought to similar scale and location and hence could be compared or used interchangeably for different comparisons based on their performance.
+
+```{r hist-qq, fig.cap = "In panel a, the histogram of $wpd_{glm-scaled}$ is plotted.
 In part b, the QQ plot is shown with the theoretical quantiles on the x-axis and $wpd_{glm-scaled}$ quantiles on the y-axis.
@@
 wpd_{perm},& \text{if } J, K <=5\\
-wpd_{glm-scaled},              & \text{otherwise}\\
+wpd_{glm-scaled}             & \text{otherwise}\\
 \end{cases}
@@
 The learning from the simulations are as follows: The values of $wpd_{norm}$ is least for $D_{null}$, followed by
-$D_{var_f}$, $D_{var_x}$) and $D_{var_{all}}$).
+$D_{var_f}$, $D_{var_x}$ and $D_{var_{all}}$.
 This is a desirable result since the measure $wpd_{norm}$ was designed such that this relationship holds.
@@
 
-7. Repeat Steps (1-6) for all harmony pairs.
-
-8. $95^{th}$ percentile of $wpd_{sample}$ obtained for all harmony pairs is computed and stored in $wpd_{threshold}$.
+7. Repeat Steps (1-6) for all harmony pairs $(A, B) \in H_{N_C}$ and store it in $wpd^{all}_{sample}$.
+
+8. $95^{th}$ percentile of $wpd^{all}_{sample}$ is computed and stored in $wpd_{threshold}$.
 

### 2021-03-03 paper/main.Rmd
before application section

@@
 
-In this section, we provide a method to select important harmonies by eliminating all harmonies for which patterns are not significant across x or facet categories through randomization test.
+In this section, we provide a method to select important harmonies by eliminating all harmonies for which patterns are not significant by employing randomization test.
 Randomization tests (permutation tests) generates a random distribution by re-ordering our observed data and allow to test if the observed data is significantly different from any random distribution.
@@
 
-Typically, a randomization test involves calculating a test statistic, randomly shuffling the data and calculating the test statistic several times to obtain a distribution of the test statistic.
-We will use this procedure to test if there is any interesting pattern captured by the harmonies, which essentially implies if $wpd_{norm}$ is significantly different from zero.
+A randomization test involves calculating a test statistic, randomly shuffling the data and calculating the test statistic several times to obtain a distribution of the test statistic.
+But we will use this procedure to obtain a threshold such that harmony pairs with a $wpd_{norm}$ value higher than this threshold will only be considered significant.
+The process of choosing a threshold is described as follows:
+
+<!-- to test if there is any interesting pattern captured by the harmonies, which essentially implies if $wpd_{norm}$ is significantly different from zero.
 The percentages of times the $wpd_{norm}$ obtained from the permuted data is greater than or equal to the observed $wpd_{norm}$ is the p-value.
-The randomization test is described as follows:
+The randomization test is described as follows: -->
 
@@
 5.  Steps (3) and (4) are repeated a large number
-of times M (M = 200).
+of times $M$ (M = 200).
 
@@
 
-8. $95^{th}$ percentile of $wpd^{all}_{sample}$ is computed and stored in $wpd_{threshold}$.
-
-7. If $wpd_{obs_{A, B}}> wpd_{threshold}$, harmony pair $(A, B)$ is selected, otherwise rejected.
+8. $99^{th}$ percentiles of $wpd^{all}_{sample}$ is computed and stored in $wpd_{threshold99}$
+
+7. If $wpd_{obs_{A, B}} > wpd_{threshold99}$, harmony pair $(A, B)$ is selected with a 99% level of significance and otherwise rejected.
+
+Similarly, a harmony pair $(A, B)$ is selected with a 95% and 90% level of significance if $wpd_{obs_{A, B}} > wpd_{threshold95}$ and $wpd_{obs_{A, B}} > wpd_{threshold90}$, where  $wpd_{threshold95}$ and $wpd_{threshold90}$ denote the $95^{th}$ and $90^{th}$ percentile of $wpd^{all}_{sample}$ respectively.
 
@@
 
-Observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$.
+Observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx =  \{3, 7, 14}$ and $nfacet = (2, 9, 10)$.
+The panel $(3, 2), (7,9), (14, 10)$ are considered to have design $D_{null}$.
+The panels $(7, 2), (14, 9)$ have design of the form $D_{var_f}$.
+$(14, 2), (3, 10)$ have design of the form $D_{var_x}$ and the rest are under $D_{var_{null}}$.
+We generate only one data set for which all these designs were simulated and consider this as the original data set.
+We generate $200$ repetitions of this experiment with different seeds and compute the proportion of times a panel is rejected when it is under $D_{null}$.
+We also compute the proportion of times a panel is rejected when it actually belongs to a non-null design.
+The first proportion is desired to be as small as possible and a higher value of the later is expected.
+Also, these would consitute to be the estimated size and power of the test.
+
+<!-- 14, 20, 31, 50\}$.
 For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
@@
 This entire process is repeated for several null data sets to see the number of times any harmony pair $(A, B) \in H_{N_C}$ is selected under null.
-
-nx = (3, 7, 14)
-nfacet = (2, 9, 10)
-
-(3, 2), (7,9), (14, 10) being null sets and others under some other design. Generate 200 repetitions of different data sets with the same design for all the pairs and compute size and power.
+-->
+
+<!-- nx = (3, 7, 14) -->
+<!-- nfacet = (2, 9, 10) -->
+
+<!-- (3, 2), (7,9), (14, 10) being null sets and others under some other design.  -->
 
@@
 
-Figure \ref{fig:raw} shows the distribution of $wpd$ plotted across different $nx$ and $nfacet$ categories.
-Since under $D_{null}$, there is no difference in distributions across different categories, we expect the distance measure $wpd$ to reflect that as well and have the same null distribution across categories.
-But Figure \ref{fig:raw} shows that both the location and scale of the distributions change across panels.
-This is not desirable under $D_{null}$ as it would mean comparisons of $wpd$ values is not appropriate across different $nx$ and $nfacet$.
-Figure \ref{fig:quadratic} shows how the median of $wpd$ varies with the total number of distances $nx*nfacet$ for each panel.
-The median increases abruptly for lower values of $nx*nfacet$ and slowly for higher $nx*nfacet$.
+The results for this section is WIP and to be included in details in the Supplementary paper.
+Also, Figure \ref{fig:plot-all-new2} presents the results of $wpd_{norm}$ from the illustrative designs in Section \ref{sec:computation-wpd}.
+As expected, the value of $wpd_{norm}$ under null design is the least (a), followed by (b, c and d).
+Moreover, note the the relative difference in $wpd_{norm}$ values as we move from  a to d, which aligns with the idea of $wpd_{norm}$, since the differences between x categories are up-weighed by design.
 
@@
 
-```{r plot-all-new2}
+```{r plot-all-new2, fig.cap="$wpd_{norm} values for the four illustrative designs are presented here.
+As expected, the value of wpd_{norm} under null design is the least (a), followed by (b, c and d).
+Moreover, the relative difference is interesting as c is closer to d than b, since the differences between x categories are up-weighed by design."}
 library(patchwork)

### 2021-03-03 paper/main.Rmd
till choosing ranking harmonies

@@
   ) +
-  geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
+  geom_point(alpha = 0.5, size = 0.5) + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
   ylab("wpd_glm = wpd - 1/(a  + b*log(nx*nfacet))")
@@
 
-Observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx =  \{3, 7, 14}$ and $nfacet = (2, 9, 10)$.
+Observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = \{3, 7, 14\}$ and $nfacet = \{2, 9, 10\}$.
 The panel $(3, 2), (7,9), (14, 10)$ are considered to have design $D_{null}$.
@@
 The first proportion is desired to be as small as possible and a higher value of the later is expected.
-Also, these would consitute to be the estimated size and power of the test.
+Also, these would constitute to be the estimated size and power of the test.
 
@@
 -->
-
-<!-- nx = (3, 7, 14) -->
-<!-- nfacet = (2, 9, 10) -->
-
-<!-- (3, 2), (7,9), (14, 10) being null sets and others under some other design.  -->
 
@@
 
-```{r plot-all-new2, fig.cap="$wpd_{norm} values for the four illustrative designs are presented here.
-As expected, the value of wpd_{norm} under null design is the least (a), followed by (b, c and d).
+```{r plot-all-new2, fig.cap = "$wpd_{norm}$ values for the four illustrative designs are presented here.
+As expected, the value of $wpd_{norm}$ under null design is the least (a), followed by (b, c and d).
 Moreover, the relative difference is interesting as c is closer to d than b, since the differences between x categories are up-weighed by design."}
@@
              strip.position =  "right",
-             scales = "free_y")
+             scales = "free_y") + ggtitle("a")
 
@@
              strip.position =  "right") +
-  gghighlight(date > as.Date("2019-09-15") & date < (as.Date("2019-09-21")), unhighlighted_params = list(colour = "black"))
+  gghighlight(date > as.Date("2019-09-15") & date < (as.Date("2019-09-21")), unhighlighted_params = list(colour = "black")) + ggtitle("b")
 
@@
 
-$v{i, t}$ has a asymmetrical distribution as could be seen in \ref{fig:raw-nqt-8} and the Normal score transform has been applied to make it more symmetric.
+$v_{i, t}$ has a asymmetrical distribution as could be seen in \ref{fig:raw-nqt-8} and the Normal score transform has been applied to make it more symmetric.
 Let $v*_{i, t}$ denote the normal-quantile transformed electricity demand for $i^{th}$ household for time period $t$.
@@
 A tuning parameter of $\lambda = 0.67$ has been considered to upweigh the within-facet distances and down-weigh the between facet distances and the maximum of them are obtained to compute $wpd$.
-It is further normalized using the approach described in Section \ref{sec:normalization}.
+It is further normalized using the approach described in Section \ref{sec:norm-wpd}.
 This entire process is repeated for all harmony pairs $\in H_{N_C}$ and for each households $i \in i = \{1, 2, \dots, 8\}$.

### 2021-03-03 paper/main.Rmd
heatmap changed and discussion added

@@
 title: A new metric for automatic discovery of periodic patterns in time series
+
+# to produce blinded version set to 1
+blinded: 0
+
 authors:
 - name: Sayani Gupta
-  affiliation: Department of Econometrics and Business Statistics, Monash University
-  email: Sayani.Gupta@monash.edu
+  thanks: "Email: Sayani.Gupta@monash.edu"
+  affiliation: Department of Econometrics and Business Statistics, Monash University, Australia
+
+- name: Rob J Hyndman
+  affiliation: Department of Econometrics and Business Statistics, Monash University, Australia
+
+- name: Dianne Cook
+  affiliation: Department of Econometrics and Business Statistics, Monash University, Australia
 
@@
 
-The smart meter data set for eight households in Melbourne has been utilized to see the use of the $wpd_{norm}$ proposed in the paper.
+The smart meter data set for eight households in Melbourne has been utilized to see the use of $wpd_{norm}$ proposed in the paper.
 The data has been cleaned to be a `tsibble` (@wang2019tsibble) containing half-hourly electricity consumption from Jul-2019 to Dec-2019 for each of the households, which is procured by them by downloading their data from the energy supplier/retailer.
@@
 In the left panel of Figure \ref{fig:linear-scale-8} (a), the linear representation of the entire time period is shown, whereas in the right panel (b) a particular month is shown and furthermore a week has been highlighted to inspect if there is any daily or weekly periodic patterns in their behavior that is reflected when we zoom into the the linear representation of the time series.
+We have some additional demographics data in terms of the number of members in the household and presence of kids/elderly parents and their profession.
+
+```{r}
+demography <- tibble(id = c(1, 2, 3, 4, 5,6, 7, 8), 
+       profession = c("academia", "mixed", "industry", "industry", "mixed", "mixed", "academia", "industry"),
+       total_members = c(2, 3, 5, 5, 2, 2, 2, 6),
+       kids = c("no", "no", "yes", "yes", "no", "no", "no", "yes"),
+       old_parents = c("no", "yes", "yes", "yes", "no", "no", "no", "yes"),
+       PhD_student = c("no", "yes", "no", "no", "yes", "yes", "yes", "no"))
+
+demography %>% kable(format  = "markdown", caption = "Demographics of the eight households chosen for study")
+```
+
 We start the analysis by asking if the ranking of the harmonies make sense for the households, then compare households to get more insights of what these rankings imply and if they could be used to remove some non-interesting harmonies.
@@
 
+```{r raw-nqt-8, fig.height = 5, fig.cap="The raw density of the half-hourly demand for the eight households in Panel a.
+Panel b shows the normal-score-transform half-hourly demand for the same households which has resulted in more symmetric distribution of half-hourly demand."}
+elec_raw <- elec %>% 
+  ggplot() +
+  geom_density(aes(x = kwh)) +
+  facet_wrap(~id, scales = "free_y", ncol = 1) +
+  xlab("demand (in kwh)") + ggtitle("a") +
+  theme(
+        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
+
+elec_nqt <- elec %>% 
+  dplyr::mutate(kwh_transformed = stats::qqnorm(kwh, plot.it = FALSE)$x) %>% 
+  ggplot() +
+  geom_density(aes(x = kwh_transformed))+
+  facet_wrap(~id, scales = "free_y", ncol = 1) +
+  xlab("NQT demand (in kwh)") + ggtitle("b") + theme(
+        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
+
+# hour_day_raw <- elec %>% 
+#   tsibble::as_tsibble(index = date_time, key = id) %>% 
+#     create_gran("hour_day") %>% 
+#     ggplot() + 
+#     ggridges::geom_density_ridges(aes(y=hour_day, x = kwh))
+#   
+# hour_day_trans <- elec %>% 
+#   tsibble::as_tsibble(index = date_time, key = id) %>% 
+#     create_gran("hour_day") %>% 
+#   dplyr::mutate(kwh_transformed = stats::qqnorm(kwh, plot.it = FALSE)$x) %>% 
+#   ggplot() +
+#   ggridges::geom_density_ridges(aes(y=hour_day, x = kwh_transformed))
+
+elec_raw + elec_nqt
+
+```
+
 _Choosing cyclic granularities of interest and removing clashes_
@@
 
-_Choosing and Ranking harmonies for all households_
+_Selecting and Ranking harmonies for all households_
 
@@
 
-```{r gravitas-plot-8, message = FALSE, warning=FALSE, fig.cap="Distribution of energy demand shown for household id 1 across hod in x-axis and wd-wnd in facets in a) and just the reverse in b).
+```{r gravitas-plot-8, message = FALSE, warning=FALSE,fig.cap="Distribution of energy demand shown for household id 1 across hod in x-axis and wd-wnd in facets in a) and just the reverse in b).
 In c), distribution of energy demand for household id:4 shown across hod and wd-wnd.
@@
 
-From Figure \ref{fig:gravitas-plot-8-id5}, it could further be observed that id5 has only one significant harmony $(hod, dow)$.
+<!-- From Figure \ref{fig:gravitas-plot-8-id5}, it could further be observed that id5 has only one significant harmony $(hod, dow)$.
 Apparently, $(hod, wnd/wday)$ which is an important harmony for most households is not important for this one.
-
-_Comparing similar households and spotting anomalous ones_
-
-```{r gravitas-plot-8-id5, message = FALSE, warning=FALSE, fig.cap="something"}
+-->
+
+_Comparing households and validating patterns from linear display_
+
+Figure \ref{fig:dotplot-8} helps to compare between households through the heatmap (b) and validate the results of the heatmap through linear display in (a) .
+The top panel contains the raw data for a month (Sep-2019).
+The darker the color of a cell in the heatmap, the more significant a harmony pair it is.
+Also, the ones with red borders are significant at 95% significance.
+This plot suggests that there is no significant periodic patterns for id 5, even when the demographics of id 5 is very similar to id 6 and 7.
+Household id 6 and 7 differ in the sense that for id 6, difference in patterns only during weekday/weekends (two members are in mixed profession), whereas for id 7, all or few other days of the week are also important (members are in academia and hence more flexible routines).
+The periodic pattern is very similar to id 8, which has a very different demographic property.
+Both from the linear representation and heatmap, it is clear that id 2 and 3 are similar, both in term of periodic pattern as well as demographics.
+
+```{r gravitas-plot-8-id5, message = FALSE, warning=FALSE, fig.cap="something", eval = FALSE}
 
@@
 p1 + p2
-```
-
-_Validating patterns from linear display_
-
-```{r raw-nqt-8, fig.cap="The raw density of the half-hourly demand for the eight households in Panel a.
-Panel b shows the normal-score-transform half-hourly demand for the same households which has resulted in more symmetric distribution of half-hourly demand."}
-elec_raw <- elec %>% 
-  ggplot() +
-  geom_density(aes(x = kwh)) +
-  facet_wrap(~id, scales = "free_y", ncol = 1) +
-  xlab("demand (in kwh)")
-
-elec_nqt <- elec %>% 
-  dplyr::mutate(kwh_transformed = stats::qqnorm(kwh, plot.it = FALSE)$x) %>% 
-  ggplot() +
-  geom_density(aes(x = kwh_transformed))+
-  facet_wrap(~id, scales = "free_y", ncol = 1) +
-  xlab("NQT demand (in kwh)")
-
-# hour_day_raw <- elec %>% 
-#   tsibble::as_tsibble(index = date_time, key = id) %>% 
-#     create_gran("hour_day") %>% 
-#     ggplot() + 
-#     ggridges::geom_density_ridges(aes(y=hour_day, x = kwh))
-#   
-# hour_day_trans <- elec %>% 
-#   tsibble::as_tsibble(index = date_time, key = id) %>% 
-#     create_gran("hour_day") %>% 
-#   dplyr::mutate(kwh_transformed = stats::qqnorm(kwh, plot.it = FALSE)$x) %>% 
-#   ggplot() +
-#   ggridges::geom_density_ridges(aes(y=hour_day, x = kwh_transformed))
-
-elec_raw + elec_nqt
-
 ```
@@
 The darker the colour, the higher the importance of the harmony.
-Visualizing the pairs in this way helps us to see the important cyclic granularities along the x-axis and facet along with the information that which ones amongst them should be analyzed together." }
+Also, the ones bordered red are selected with 90 percent significance level.
+Visualizing the pairs in this way helps us to see the important cyclic granularities along the x-axis and facet along with the information that which households should be analyzed together." }
 elec_sig_split <- elec_harmony_all %>%
@@
 heatplot <- elec_sig_split %>% 
+  mutate(significance_95 = if_else(significant %in% c("high", "highest"), "yes", "no")) %>% 
   ggplot() +
@@
                  y = facet_variable, 
-                 fill = wpd,
-                size = significant)) + 
-  scale_fill_continuous(type = "gradient") +
+                 fill = wpd, color = significance_95), size = 1) + 
+  #scale_fill_gradient(low = "white",high = "steelblue") +
+  scale_fill_gradient2() +
+  scale_colour_manual(values = c("white","red")) + 
   theme(legend.position = "bottom") +
-  facet_wrap(~id, nrow = 2) +
+  facet_wrap(~id, nrow = 1, strip.position = "bottom") +
   coord_fixed() + 
@@
   theme(panel.grid = element_blank(),
-        axis.text.x = element_text(angle = 60, hjust=1),legend.position = "bottom")
-  heatplot
+        axis.text.x = element_text(angle = 60, hjust=1),legend.position = "bottom") + ggtitle("b")
+
+elec <- read_rds(here("paper/data/elec_all-8.rds")) %>% 
+  dplyr::filter(date(reading_datetime) >= ymd("20190701"), date(reading_datetime) < ymd("20191231"), meter_id==1) %>% 
+  select(-meter_id) %>% 
+  rename("id" = "household_id",
+         "date_time" = "reading_datetime")
+
+elec_zoom <-  elec %>%
+  as_tibble() %>% 
+  dplyr::filter(date(date_time) > as.Date("2019-09-01") & date(date_time) < (as.Date("2019-09-30"))) %>%
+  ggplot(aes(x=date_time, y = kwh)) +
+  #geom_point(size = 0.1, colour = "black", alpha = 0.3) +
+  geom_line(size = 0.1, colour = "blue", alpha = 0.2) +
+  facet_wrap(~id, 
+             scales = "free_y",
+             nrow = 1,
+             strip.position =  "top") + xlab("") + 
+  theme_void() + theme(strip.text.x = element_blank()) +
+  ylab("energy demand in September (kwh)") + ggtitle("a")
+
+elec_zoom/heatplot
+
 #            
@@
 
-elec_rank %>% kable(format = "markdown", caption = "Ranking of the harmonies for the four households are shown.
-The first four harmonies are unanimously important for all households, after which there is differences in the rankings for most households.")
+elec_rank %>% kable(format = "markdown", caption = "Ranking of harmonies for the eight households with significance levels.")
 ```
@@
 Exploratory data analysis involve many iterations of finding and summarizing patterns.
-With temporal data available at ever finer scales, exploring periodicity has become overwhelming with so many possible granularities to explore.
-This work refines the selection of appropriate pairs of granularities by identifying those for which the differences between the displayed distributions is greatest, and rating these selected harmony pairs in order of importance for exploration.
+With temporal data available at more and more finer scales, exploring periodicity has become overwhelming with so many possible granularities to explore.
+A common solution would be to zoom into “interesting” segments, but there is no way to know the “interesting” segments a priori.
+This work refines the search of periodic patterns by identifying those for which the differences between the displayed distributions is greatest, and rating them in order of importance for exploration.
 
 A future direction of work could be to look at more individuals/subjects and group them according to similar periodic behavior.
-Behaviors across different cyclic granularities would be different for different subjects and one way to find groups would be to actually locate clusters who have similar periodic behavior.
-
- A common remedy would be to zoom into “interesting” segments, but how do we identify “interesting” segments?
+Behaviors across different harmonies would be varying for subjects and it would be hard to track the behavior when the number of individuals rise.
+One way to find groups would be to actually locate clusters who have similar periodic behavior.
 
@@
 to group subjects  -->
+
+# Bibliography
+
+```{r write-bib, eval = FALSE}
+write_bib(c("rmarkdown", "bookdown", "rticles", "knitr", "ggplot2", "dplyr", "tsibble", "gravitas", "ggpubr", "kableExtra", "magrittr", "readr", "lubridate", "renv", "archive", "hakear", "patchwork", "ggpubr"), file = "rpkgs.bib")
+```

### 2021-03-03 paper/main.Rmd
keywords fix

@@
   affiliation: Department of Econometrics and Business Statistics, Monash University, Australia
-
-bibliography: bibliography.bib
+keywords:
+- data visualization
+- periodicities
+- time granularities
+- cyclic granularities
+- permutation tests
+- Jensen-Shannon distances
+- smart meter data
+- R
+
+abstract: |
+ Deconstructing a time index into time granularities can assist in exploration and automated analysis of large temporal data sets.
+This paper describes classes of time deconstructions using linear and cyclic time granularities.
+Linear granularities respect the linear progression of time such as hours, days, weeks and months.
+Cyclic granularities can be circular such as hour-of-the-day, quasi-circular such as day-of-the-month, and aperiodic such as public holidays.
+The hierarchical structure of granularities creates a nested ordering: hour-of-the-day and second-of-the-minute are single-order-up.
+Hour-of-the-week is multiple-order-up, because it passes over day-of-the-week.
+Methods are provided for creating all possible granularities for a time index.
+A recommendation algorithm provides an indication whether a pair of granularities can be meaningfully examined together (a "harmony"), or when they cannot (a "clash").
+
+ Time granularities can be used to create data visualizations to explore for periodicities, associations and anomalies.
+The granularities form categorical variables (ordered or unordered) which induce groupings of the observations.
+Assuming a numeric response variable, the resulting graphics are then displays of distributions compared across combinations of categorical variables.
+
+ The methods implemented in the open source R package `gravitas` are consistent with a tidy workflow, with probability distributions examined using the range of graphics available in `ggplot2`.
+
+bibliography: [bibliography.bib]
 preamble: >
-  \usepackage{mathtools,booktabs,amsthm,todonotes,colortbl}
+  \usepackage{mathtools,amssymb,booktabs,amsthm,todonotes,colortbl}
   \def\mod{~\text{mod}~}
@@
   \usepackage{caption}
-  \usepackage{algorithm}
-  \usepackage{algorithmicx}
-  \usepackage{algpseudocode}
   \DeclareCaptionStyle{italic}{labelfont={bf},textfont={it},labelsep=colon}
@@
   bookdown::pdf_book:
-    #base_format: rticles::asa_article
+    base_format: rticles::asa_article
     fig_height: 5
@@
     dev: "pdf"
+    keep_tex: yes
 ---

### 2021-03-03 paper/main.Rmd
abstract added

--- 2021-03-03 paper/main.Rmd
@@
   affiliation: Department of Econometrics and Business Statistics, Monash University, Australia
-
-bibliography: bibliography.bib
+keywords:
+- data visualization
+- periodicities
+- time granularities
+- cyclic granularities
+- permutation tests
+- Jensen-Shannon distances
+- smart meter data
+- R
+
+abstract: |
+ Periodic patterns or associations in large univariate time series data could be discerned by analysing the behaviour across cyclic temporal granularities, which are temporal deconstructions accounting for repetitive behaviour.
+The temporal granularities form ordered categorical variables and display of distributions of the univariate response variable across two or more combinations of these categorical variable can help explore periodicities, patterns and anomalies.
+A  pair of granularities that can be meaningfully examined together are called “harmonies” and the ones which cannot be are called “clashes”.
+Even after excluding clashes, the list of harmonies that could potentially be displayed is huge and hence overwhelming for human consumption.
+This work provides a methodology to screen the most informative graphics from the plethora of choices by introducing a distance measure that could be compared across harmonies with varied levels and data sets.
+Moreover, this distance measure could also be used to rank the selected harmonies basis how well they capture the variation in the measured variable.
+All the methods are implemented in the open source R package `hakear`.
+
+bibliography: [bibliography.bib]
 preamble: >
-  \usepackage{mathtools,booktabs,amsthm,todonotes,colortbl}
+  \usepackage{mathtools,amssymb,booktabs,amsthm,todonotes,colortbl}
   \def\mod{~\text{mod}~}

### 2021-03-03 doc/choosing_significant_harmonies.Rmd
cleaning folder

--- 2021-02-21 choosing_significant_harmonies.Rmd
@@
 ```{r, eval = FALSE, echo = FALSE}
-set.seed(12345)
+sample_seed = seq(1000, 2999, by = 10)
+nperm = 200
+simtable<-read_csv(here::here('simulations/sim_table/sim_table.csv'))
+# simulate one big data which will have all categories generated on the #fly
 
-# simulate one big data which will have all categories generated on the #fly
+all_seed <- lapply(seq_len(sample_seed), function(x){
+
+  set.seed(sample_seed[x])
 
@@
 
-simtable<-read_csv(here::here('simulations/sim_table/sim_table.csv'))
-
-lapply(1:2, 
+# for each row of the sim table
+each_seed <- lapply(nrow(simtable), 
                            function(scen){
@@
 nxj<-simj$nx
-nperm = 20
 
 id_x <- rep_len(seq_len(nxj), length.out = lensim) 
-id_facet <- rep_len(seq_len(nfacetj), length.out = lensim)
+id_facet <- rep_len(rep(seq_len(nfacetj), each = nxj), length.out = lensim)
 
@@
 
-wpd_orig = compute_pairwise_max(sim_panel_data, 
+wpd_orig = compute_pairwise_norm_scalar(sim_panel_orig, 
                                 gran_x = "id_x",
@@
 
-  wpd =  compute_pairwise_max(sim_panel_sample, 
+  wpd =  compute_pairwise_norm_scalar(sim_panel_sample, 
                               gran_x = "id_x",
@@
   mutate(perm_id = 0) %>% 
-  bind_rows(wpd_sample)
+  bind_rows(wpd_sample) %>% 
+  bind_cols(nx = nxj, nfacet = nfacetj)
 
-saveRDS(wpd_all,
-        paste0('simulations/supplementary/test/wpd_N01/data-ind/',
-               nxj,'-',
-               #"nfacetj-",
-               nfacetj,"-",
-               '-wpd-test.rds'))
-})
+wpd_all
+}) %>% bind_rows()
+
+# find threshold
+
+threshold <- each_seed %>% mutate(
+  threshold = quantile(each_seed$value, probs = 0.95))
+
+# conduct test
+
+threshold %>% 
+  dplyr::filter(perm_id == 0) %>% 
+  mutate(select = if_else(value>threshold, "yes", "no"))
+
+}) %>% bind_rows(.id = "seed_id")
+
+saveRDS(all_seed,
+        paste0('simulations/supplementary/test/wpd_N01/null_all_seed_threshold.rds')
+
 ```
-
-The p-value of the design $D_{null}$ is size.
-The p-value of other designs is power.
-Confidence interval of the
 

### 2021-03-03 doc/combining_normalisation_method.Rmd
cleaning folder

--- 2021-02-16 combining_normalisation_method.Rmd
@@
 
+G21_sd  = G21 %>% 
+    mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
+    )
+    )
+    ))
+
+scale_fac <- 1/G21_sd$wpd_glm %>% sd()
+
 # checking the fit of the residuals from glm fit
@@
              ),
-         wpd_glm_scaled = ((wpd_glm*300)))
+         wpd_glm_scaled = ((wpd_glm*320)))
+
+G21_glm$wpd_glm_scaled %>% sd()
 

### 2021-03-03 doc/comparison_perm_scalar.Rmd
cleaning folder

--- 2021-02-16 combining_perm-model.Rmd
@@
 ---
-title: "Permutation and scalar transformation approaches to normalisation and combining them"
+title: "Compare permutation and scalar transformation approaches on simulated and real data"
 author: "Sayani Gupta"
@@
 library(here)
-library(patchwork)
 ```
 
-# Data generation
+# Simulated data
+
+## Data generation
 
@@
 
-Figure \ref{Fig:raw} shows the distribution of $wpd_{raw}$ is plotted across different nx and nfacet categories.
-Both shape and scale of the distribution changes for different $nx$ and $nfacet$ categories.
-This is not desirable as it would mean we would not be able to compare $wpd_{raw}$ across different $nx$ and $nfacet$ as each of them are drawn from distributions of different locations and scale.
-In Figure \ref{fig:quadratic} we see how the median of $wpd_{raw}$ varies with the total number of distances $nx_i*nfacet_j$ for a panel with $nx = nx_i$ categories and $nfacet = nfacet_j$ categories.
-The median increases abruptly for lower values of $nx_i*nfacet_j$ and the increase becomes more gradual for higher $nx_i*nfacet_j$.
+ - Plot the values of raw wpd against nx*nfacet to see the rough relationship (\ref{fig:quadratic}).
 
@@
 ```
-
-We need a transformation on $raw_{wpd}$ which will make it independent of the values of $nx*nfacet$.
-Two approaches have been employed for that purpose, the first one involves fitting a model and the latter involves a permutation method to make the distribution of the transformed $wpd$ similar across different $nx$ and $nfacet$.
 
@@
 
-#summary(fit_lm2)
+summary(fit_lm2)
 
@@
 
+The measure $wpd_{glm}$ seems to follow a normal distribution.
+
+```{r}
+ggplot(G21_glm) +
+  geom_histogram(aes(x = wpd_glm))
+
+p <- ggplot(G21_glm, aes(sample = wpd_glm))
+p + stat_qq() + stat_qq_line()
+
+# G21_glm <- G21 %>% 
+#     mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
+#     )
+#     )
+#     ),
+#     wpd_glm_trans = 300*(wpd_glm))
+
+ G21_glm$wpd_glm_trans %>% 
+   range()
+
+```
+
 ## Permutation approach to normalisation
@@
     ggplot() +
-  geom_density(aes(x = wpd_permutation), 
+  geom_density(aes(x = perm_trans), 
                    fill = "blue") +
@@
 
- - Making the range of both the variables same by using min-max scaling method.
-In practice, however, we would only have one value of $wpd_{raw}$ which we need to transform using the modeling appraoch.
-Hence, min-max scaling approach could not be used here.
+ - Converting each scale to have the same lower and upper levels
+ - Standardizing the variables and expressing scores at standard deviation units
 
- - Standardizing the variables and expressing scores at standard deviation units.
-Again in practice, however, we would only have one value of $wpd_{raw}$ which we need to transform using the modeling appraoch.
-Hence, standardizing scores could not be used here as we do not have the mean and standard deviation of a series while using transfomation using modeling.
-
-- Make the location and scale of both the approaches similar so that they could be compared.
-Please note that the range of values could be different in this case, however location and scale are brought to same levels.)
-
-The measure $wpd_{glm}$ seems to roughly follow a normal distribution except in the tails as could be seen in Figure \ref{fig:hist-qq} and the very method of permuation approach ensures that $wpd_permutation$ is also normally distributed.
-Further, they are brought to the similar scale and location and hence could be compared.
-
-```{r hist-qq, fig.cap = "In panel a, the histogram of $wpd_glm_trans$ is plotted.
-In parl b, the QQ plot is shown with the theoretical quantiles on the x-axis and $wpd_glm_trans$ quantiles on the y-axis.
-The distribution looks symmetric and looks like normal except in the tails."}
-hist <- ggplot(G21_glm) +
-  geom_histogram(aes(x = wpd_glm_trans)) +
-  ggtitle("a")
-
-p <- ggplot(G21_glm, aes(sample = wpd_glm_trans))
-qqplot <-  p + geom_qq() + geom_qq_line() + coord_fixed(ratio = 4/5) +
-  ggtitle("b")
-
-# G21_glm <- G21 %>% 
-#     mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
-#     )
-#     )
-#     ),
-#     wpd_glm_trans = 300*(wpd_glm))
-
- # G21_glm$wpd_glm_trans %>% 
- #   range()
-hist + qqplot
-```
+- making the range of both the variables same (additional advantage that we can have a bound for the normalised measure which could be compared across normalizing approaches and data sets.)
 

### 2021-03-07 paper-supplementary.Rmd
working on supplementary section

--- 2021-01-20 paper/supplementary.Rmd
@@
 ---
-title: Supplementary materials 
+title: "<small> Supplementary materials for the main submission entitled - <br><br> A new metric for automatic discovery of periodic patterns in time series"
 authors:
 - name: Sayani Gupta
-  affiliation: Department of Econometrics and Business Statistics, Monash University
-  email: Sayani.Gupta@monash.edu
+  thanks: "Email: Sayani.Gupta@monash.edu"
+  affiliation: Department of Econometrics and Business Statistics, Monash University, Australia
 
-bibliography: bibliography.bib
+- name: Rob J Hyndman
+  affiliation: Department of Econometrics and Business Statistics, Monash University, Australia
+
+- name: Dianne Cook
+  affiliation: Department of Econometrics and Business Statistics, Monash University, Australia
+
+bibliography: [bibliography.bib]
 preamble: >
-  \usepackage{mathtools,booktabs,amsthm,todonotes,colortbl}
+  \usepackage{mathtools,amssymb,booktabs,amsthm,todonotes,colortbl}
   \def\mod{~\text{mod}~}
@@
     dev: "pdf"
+    keep_tex: yes
 ---
 
-```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
-options("knitr.graphics.auto_pdf" = TRUE,
-        tinytex.verbose = FALSE)
-library(knitr)
-library(tidyverse)
-library(lubridate)
-library(lvplot)
-library(ggridges)
-library(viridis)
-library(tsibble)
-library(gravitas)
-library(ggpubr)
-library(readr)
-library(kableExtra)
-library(distributional)
-library(ggplot2)
-library(sugrrants)
-library(here)
+Appendix A recalls the necessary notations and
 
-opts_chunk$set(
-  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
-  fig.path = "figure/", fig.align = "center", fig.show = "hold",
-  cache = TRUE, cache.path = "cache/",
-  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
-)
-knitr::opts_knit$set(root.dir = here::here())
-#                                                                read_chunk('main.R')
-here::here()
-read_chunk(here::here("paper/R/", "null_distribution.R"))
-read_chunk(here::here("paper/R/", "mean_null.R"))
-source(here::here("paper/R/sim_panel.R"))
-# Set up plan
-#source("_drake.R")
-# Run all code required
-#drake::r_make()
-# load each object as required
-# loadd()
+# Necessary notations
+
+# Behavior of raw weighted distance measure
+
+## NQT works
+
+### without NQT
+```{r gamma-diff-wotrans, fig.cap="Ridge plots of raw wpd is shown for Gamma(0.5,1), Gamma(2,1) distribution.
+The densities change across different facet and x levels and also looks different for the two distributions, which implies wpd value is affected by the change in the shape paramter of the gamma distribution."}
+knitr::include_graphics(here::here("simulations/raw/null_design_scale/figs/gamma_ridge_nxbynfacet.png"))
 ```
 
-# Notations and Definitions
+### with NQT
 
-Consider two cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.
-Let the pairwise distances between pairs $(a_{j} b_{k}, a_{j'}b_{k'})$ b   e denoted as $d_{(jk, j'k')} = JSD(a_{j}b_{k}, a_{j'}b_{k'})$.
-Pairwise distances could be within-facets or between-facets.
-Figure \ref{fig:distance-explain} illustrates how the within-facet or between-facet distances are defined.
-Pairwise distances are within-facets ($d_{w}$) when $b_{k} = b_{k'}$, that is, between pairs of the form $(a_{j}b_{k}, a_{j'}b_{k})$ as shown in panel (3) of Figure \ref{fig:distance-explain}.
-If categories are ordered (like all temporal cyclic granularities), then only distances between pairs where $a_{j'} = (a_{j+1})$ are considered (panel (4)).
-Pairwise distances are between-facets ($d_{b}$) when they are considered between pairs of the form $(a_{j}b_{k}, a_{j}b_{k'})$.
-
-```{r distance-explain, fig.cap = "Within and between-facet distances shown for two cyclic granularities A and B, where A is mapped to x-axis and B is mapped to facets.
-The dotted lines represent the distances between different categories.
-Panel 1) and 2) show the between-facet distances.
-Panel 3) and 4) are used to illustrate within-facet distances when categories are un-ordered or ordered respectively.
-When categories are ordered, distances should only be considered for consecutive x-axis categories.
-Between-facet distances are distances between different facet levels for the same x-axis category, for example, distances between {($a_1$,$b_1$) and ($a_1$, $b_2$)} or {($a_1$,$b_1$) and ($a_1$, $b_3$)}."}
-knitr::include_graphics(here::here("paper/Figs/dist_explain.png"))
+```{r gamma-diff-quantrans, fig.cap="Ridge plots of raw wpd is shown for Gamma(0.5,1), Gamma(2,1) distribution.
+The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change in the shape paramter of the gamma distribution"}
+knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_gamma.png"))
 ```
 
-# Behavior of raw wpd
-
-Most of the behavior of the measure wpd was studied via simulation.
-The simulations explore how wpd performs under various designs and parameters and its limitations.
-To study the behavior of wpd, simulations were carried out for four different designs and the following factors that could potentially have an impact on the values of wpd:
-
-<!-- Numerous simulations were carried out in a wide range of scenarios. -->
-
-<!-- Same scenarios were used, when possible with normalized wpd, keeping all other simulation variables constant. -->
-
-- $nx$ (number of levels of x-axis)
-- $nfacet$ (number of levels of facets)
-- $\lambda$ (tuning parameter)
-- $\omega$ (increment in each panel design)
-- $dist$ (normal/non-normal distributions with different location and scale)
-- $n$ (sample size for each combination of categories)
-- $nsim$ (number of simulations)
-- $nperm$ (number of permutations of data)  
-- $designs$  
-$D_{null}$  (No difference in distribution)  
-$D_{var_f}$ (Difference in distribution only across facets)  
-$D_{var_x}$ (Difference in distribution only across x-axis)  
-$D_{var_{all}}$ (Difference in distribution in both facets and x-axis)
-
-```{r simtable, eval = FALSE}
-variable = c("nx", "nfacet", "lambda", "omega", "dist", "n", "nsim", "nperm", "design")
-
-description = c("number of levels of x-axis", "number of levels of facets",
-                "tuning parameter","increment in each panel design", "normal/non-normal distributions with different location and scale", "sample size", "number of simulations", "number of permutations of data",
-                "$D_{null}$ (No difference in distribution), $D_{var_f}$ (Difference in distribution only across facets), $D_{var_x}$ (Difference in distribution only across x-axis), $D_{var_all}$ (Difference in distribution in both facets and x-axis)")
-table = tibble::tibble(variable, description)
-
-table %>% 
-knitr::kable(format = "latex",
-             escape = TRUE) %>% 
-  kableExtra::kable_styling(
-    bootstrap_options = "striped", 
-    full_width = F, 
-    font_size = 7)
-
-```
-
-## Null design
-
-This section explores the behavior of wpd in designs where there is no difference in distribution between x and facet categories.
-We have considered different initial distributions to study the impact of initial distribution under the null setup.
-Since the measure wpd is essentially set up to detect differences in distributions irrespective of underlying distribution, it would be ideal if it has minimal dependency on the type, location and scale of the initial distribution.
-To that end, some pre-processing of the data is preferred to bring it to the same scale, location and type.
-The Normal Score Transform or NQT has been applied in various fields of geo-statistics in order to make most asymmetrical distributed real world measured variables more
-treatable and normal-like.
-
-Following the work of Krzysztofowicz (1997) the empirical NQT involves the following steps:
-1. Sort the sample of measured variable $X$ from the smallest to the largest observation $x_{(1)},\dots, x_{(i)}, .., x_{(n)}$.
-2. Estimate the cumulative probabilities $p_{(1)},\dots, p_{(i)}, .., p_{(n)}$.
-using a plotting position like $i/(n + 1)$ such that $p_{(i)} = P(X \leq x_{(i)})$.
-3. Transforming each observation $x_(i)$ of $X$ into observation $y(i) = Q^{-1}(p(i))$ of the standard normal variate $Y$ , with $Q$ denoting the standard normal distribution and
-$Q^{-1}$ its inverse, applying discrete mapping.
-
-Further, we want to study the distribution of wpd for different $nx$ and $nfacet$.
-
-### Simulation setup
-
-<!-- Study the behavior of wpd under different initial distributions for different $nx$ and $nfacet$ -->
-
-Using two types of distributions, viz.
-normal and gamma (non-normal), we generated observations for each combination of $nx$ and $nfacet$ from the following sets: $nx = \{2, 3, 5, 7, 14, 20, 31, 50\}$ and $nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
-Each combination is being referred to as a _panel_.
-That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$.
-For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
-That is, if we consider the panel  $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
-The values of $\lambda$ is set to $0.67$, since we want to up-weigh the within-facet distances and that of $\omega$ is set to $0$, since there is no significant differences between distributions in the null case.
-Observations were generated for each type of distribution changing the shape and scale to study the effect of shape, scale and type of distribution on wpd.
-The set of distributions considered for this purpose is ${N(0,1), N(5, 1), N(0,5), \Gamma(0.5, 1), \Gamma(2, 1)}$.
-Each of the scenario is run $nsim = 200$ times to see the distribution of wpd values for each scenario.
-
-<!-- wpd is computed for different normal and non-normal distributions to see how the underlying distribution has a role to play in the value of wpd.
-Since we are concerned with detecting the differences in distributions, it would be ideal if wpd has minimal dependency on the type, location and scale of the  underlying distribution.
-To that end, some pre-processing of the data is preferred to bring it to the same scale, location and type.
--->
-
-<!-- Null design only where all combinations are equal for fixed values of $\mu$ and $\sigma$ -->
-<!-- Dist 1: $N(0,1)$ individual graph -->
-<!-- Dist 2: $N(\mu, 1)$ (faceted with different values of $\mu$: not yet just for one value now) -->
-<!-- Dist 3: $N(0, \sigma)$ (faceted with different values of $\sigma$: not yet just for one value now) -->
-<!-- Dist 4: $N(\mu, \sigma)$ faceted with different values of mu and sigma, for all levels of x and facet to see how value of wpd changes with that of change in parameters. -->
-
-<!-- **Assumptions:** There is no difference in distribution between any facet or x-category -->
-<!-- nsim = 200 -->
-<!-- lambda = 0.67 -->
-
-<!-- **Questions:**  -->
-<!-- - How raw value of wpd changes with different nx and nfacet for different location and scale of a Normal and non-normal distribution -->
-
-Figure \ref{fig:normal-diff-quantrans} and \ref{fig:gamma-diff-quantrans} show distribution of wpd for different initial normal and gamma distribution to study the effect of changing location and scale on the distribution of wpd.
-It seems like the  distribution changes across different facet and x levels but look the same for each panel, which implies wpd value is unaffected by the change in location and scale of the the normal distribution.
-Figure \ref{fig:mean-sd-ns-nfacet} shows how mean and sd of the distribution of wpd changes with the increasing x and facet levels.
-It seems like both mean and standard deviation are affected more by change in the x-axis levels than the facet levels.
-Figure \ref{fig:nxbyfacet-ridge-N05} gives another way to look at the effect of changing facet and x levels on the distribution of wpd for an initial distribution $N(0,5)$.
-Clearly, the location of the distribution shifts to the right for increasing x levels and scale is different for low and high values of facet levels with a longer left tail for lower facet levels.
-We have considered alternate distribution, location and scale for this simulation setting, but do not present the results as they are behaviorally similar.
-
-<!-- # ```{r normal-diff, fig.cap="Ridge plots of raw wpd is shown for N(0,1) and N(5,1) distribution.
-The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change in mean and standard deviation of the normal distribution", eval = FALSE} -->
-<!-- # knitr::include_graphics(here::here("simulations/null_design/figs/normal_ridge_nxbynfacet_wpd_N01.png")) -->
-<!-- # ``` -->
+## By distribution
 
@@
 
-```{r gamma-diff-quantrans, fig.cap="Ridge plots of raw wpd is shown for Gamma(0.5,1), Gamma(2,1) distribution.
-The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change in the shape paramter of the gamma distribution"}
-knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_gamma.png"))
-```
-
-```{r mean-sd-ns-nfacet, fig.cap="Movement of mean and sd for raw wpd is shown for different number of levels (nlevel) of x-axis and facets through line plots.
-Mean increases and sd decreases more sharply for increasing x-axis levels as compared to facet levels.
-It seems like both mean and standard deviation are affected more by change in the x-axis levels than the facet levels.", fig.pos="h"}
-knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/mean_sd_nx_nfacet.png"))
-
-```
+## By category levels
 
@@
 
-```{r gamma-diff, fig.cap="Ridge plots of raw wpd is shown for G(0.5,1) and G(2,1) distribution.
-The densities change across different facet and x levels and also for the two distributions, which implies wpd value is affected by the change in location value when distributions are not normal.", eval = FALSE}
-knitr::include_graphics(here::here("simulations/null_design/figs/gamma_ridge_nxbynfacet.png"))
+```{r dist-across-x, fig.cap = "Distribution of $MMPD_{raw}$ for different x levels are shown.
+The scale of the distribution becomes less and less implying that as the number of x levels increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained as the spread of the distribution decreases.
+", eval = FALSE}
+knitr::include_graphics(here::here("simulations/result_report/","nfacet_by_nx_raw.png"))
 ```
 
-```{r gamma-diff-trans, fig.cap="Ridge plots of raw wpd is shown for G(0.5,1) and G(2,1) distribution after quantile transformation looks similar and hence is unaffected by change in location.", fig.pos="h"}
-knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_gamma.png"))
-```
-
-<!-- ### Choice of alternate designs -->
-
-<!-- A normal distribution is taken for this purpose. We would calibrate the values of $WPD$ for different designs illustrated in Section \ref{sec:idea}. -->
-
-<!-- $$\mu_{j.} = \mu + j\omega$$ -->
-<!-- or, $$\mu_{.k} = \mu + k\omega$$ where,    -->
-<!-- $j$ and $k$ are the index of the x and facet category respectively  -->
-<!-- $\mu$ is the mean of the first category and $\omega$ is the increment from the starting value. -->
-
-<!-- mean = 0 -->
-<!-- range_mean = c(0, 1, 3,  5, 7, 15, 20) -->
-<!-- sd = 1 -->
-<!-- range_sd = c(1, 3,  5, 7, 15, 20) -->
-<!-- range_w =  c(1, 2, 3, 4, 5) -->
-<!-- range_lambda = seq(0.1, 0.9, 0.05) -->
-
-## Alternate designs
-
-This section explores the behavior of wpd in designs where there is infact difference in distribution between facet categories ($D_{var_f}$) or across x-categories ($D_{var_x}$) or both ($D_{var_{all}}$).
-Since it is established in the last section that after preprocessing the data through NQT, the initial distribution does not have a role to play in the values of wpd, we proceed with a N(0,1) distribution only.
-Supposably, the tuning parameter ($\lambda$) and increment parameter ($\omega$) should impact the values of wpd.
-
-### Simulation setup
-
-Using $\omega =  \{1, 2, \dots, 10\}$ and $\lambda = seq(from  = 0.1, to = 0.9, by = 0.05)$, observations are drawn from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet =  \{2, 3, 5, 7, 14, 20, 31, 50\}$.
-$ntimes = 500$ is assumed for this setup as well.
-Furthermore, to generate different distributions across different combination of facet and x levels, the following method is deployed - suppose the distribution of the combination of first levels of x and facet category is $N(\mu,\sigma)$ and $\mu_{jk}$ denotes the mean of the combination $(a_jb_k)$, then $\mu_{j.} = \mu + j\omega$ (for design $D_{var_x}$) and $\mu_{.k} = \mu + k\omega$ (for design $D_{var_f}$).
-Table \ref{tab:explain-design} shows an example of how initial distributions are assigned in a panel with $nfacet = 3$ and $nx = 2$ for different designs using $\omega = 1$.
-
-```{r explain-design}
-sim_varx_normal = function(nx, nfacet, mean, sd, w)
-{
-  rep(dist_normal((mean + seq(0, nx-1, by  = 1)*w), sd), nfacet)
-}
-
-sim_varf_normal = function(nx, nfacet, mean, sd, w)
-{
-  rep(dist_normal((mean + seq(0, nfacet-1, by  = 1)*w), sd), each = nx)
-}
-  sim_varall_normal = function(nx, nfacet, mean, sd, w)
-  {
-    dist_normal((mean + seq(0, (nx*nfacet - 1), by  = 1)*w), sd)
-  }
-
-mean = 0
-sd = 1
-w = 1
-nx = 2
-nfacet = 3
-
-raw_levels = expand.grid(facet = c("$b_1$", "$b_2$", "$b_3$"),
-                         x = c("$a_1$", "$a_2$"))
-
-facet = rep(c("$b_1$", "$b_2$", "$b_3$"), each = nx)
-x =  rep(c("$a_1$", "$a_2$"), nfacet)
-
-vary_f <-  sim_varf_normal(nx, nfacet, mean, sd, w) %>% tibble()
-vary_x <-  sim_varx_normal(nx, nfacet, mean, sd, w) %>% tibble()
-vary_all <-  sim_varall_normal(nx, nfacet, mean, sd, w) %>% tibble()
-
-raw_table <- bind_cols(x = x, 
-                       facet = facet, 
-                       vary_f = vary_f, 
-                       vary_x = vary_x, 
-                       vary_all = vary_all) %>% 
-  tibble() 
-names(raw_table) = c("x", "facet", "$D_{var_f}$", "$D_{var_x}$", "$D_{var_{all}}$" )
-raw_table %>% 
-  kable(format = "latex",
-    booktabs = TRUE, 
-    escape = FALSE,
-    caption = "Simulation setup for a panel with 3 facet levels and 2 x-axis levels for different designs starting from an initial distribution N(0, 1) for the combination $(a_1, b_1)$.") %>% kable_styling()
-```
-
-<!--  - Exploring the effect of tuning parameter $\lambda$: -->
-
-We now discuss the effect of different tuning parameters $\lambda$  with the help of two alternate designs ($D_{var_x}$ and $D_{var_f}$) and $\omega$.
-\autoref{fig:tuning-oneomega} displays different values of $\lambda$ for a relatively small and higher $\omega$ for $nx = nfacet =  \{2, 3, 5, 7, 9\}$.
-The $\lambda$ for which the two designs intersect will then be chosen as the optimal $\lambda$ that could then be weighed appropriately to up-weigh the within-facet distances and down-weigh the between-facet distances.
-The design $D_{var_x}$ increases linearly with increasing $\lambda$, whereas $D_{var_f}$ decreases linearly with increasing $\lambda$.
-This is expected as wpd has a linear relationship with $\lambda$ by construction.
-The two designs mostly intersect at $\lambda = 0.5$ for a higher value of $\omega$.
-\autoref{fig:tuning-parameter-inter} shows how the value of $\lambda$ changes with increasing $\omega$ for $\omega =  \{1, 2, \dots, 10\}$ and $\lambda = seq(from  = 0.1, to = 0.9, by = 0.05)$.
-
-<!-- Assumptions: The initial combination has a $N(\mu,\sigma)$ distribution and then every combination increases as follows: -->
-<!-- - $$\mu_{j.} = \mu + j\omega$$ (for design vary_x) -->
-<!-- - $$\mu_{.k} = \mu + k\omega$$ (for design vary_f) -->
-<!-- Value of the parameters chosen for this simulation are $\mu = 0$, $\sigma = 1$ and $\omega = {1, 2, \dots, 10}$ -->
+## Tuning parameter
 
@@
 
-We now discuss the values wpd takes for different designs.
-Ideally the wpd should have the higherst values for $D_{var_{all}}$, followed by $D_{var_x}$ and $D_{var_y}$ for $\lambda \geq 0.5$.
-We test this for lower and higher values of $\omega = c(1, 8, 15, 50)$
+## Increment
 
-```{r all-design-relative, fig.cap = "Distribution of wpd under different designs are overlapped to see how they measure relative to each other.
-We would have expected values of wpd to be such that vary_facet is less than vary_x is less than vary_all but distribution of vary_x to lie above vary_facet."}
+# Behavior of normalised distance measure
 
-library(readr)
-library(tidyverse)
+## sample size
 
-vary_x <- read_rds("simulations/vary_x/null_design_quantrans/data-agg/all_data_wpd_N01.rds")
+## number of permutations
 
-vary_all <- read_rds("simulations/vary_all/raw/data-agg/all_data_wpd_N01.rds")
+## designs
 
-vary_facet <- read_rds("simulations/vary_facet/raw/data-agg/all_data_wpd_N01.rds")
-
-all_design <- bind_rows(vary_facet, vary_x, vary_all, .id = "design") %>% 
-  mutate(design = case_when(
-    design=="1" ~ "vary_facet",
-    design=="2" ~ "vary_x",
-    design=="3" ~ "vary_all",
-    TRUE ~ as.character(design)                                                                 ))
-
-all_design %>% 
-  ggplot() +
-  geom_histogram(aes(x=value, fill = design), 
-                 alpha = 0.7) +
-  scale_fill_brewer(palette = "Dark2")  +
-  facet_wrap(~w, labeller = "label_both")
-```
-
-<!-- How value of lambda changes with increasing omega and mean for fixed nx, nfacet and standard deviation? -->
-
-<!-- # ```{r lambda-omega-mean, eval = FALSE} -->
-<!-- # knitr::include_graphics(here::here("simulations/result_report/lambda_omega_mean_3_2.png")) -->
-<!-- # ``` -->
-<!-- #  -->
-<!-- # How value of lambda changes with increasing omega and sd for fixed nx, nfacet and mean? -->
-<!-- #  -->
-<!-- # ```{r lambda-omega-sd, eval = FALSE} -->
-<!-- # knitr::include_graphics(here::here("simulations/result_report/lambda_omega_sd_3_2.png")) -->
-<!-- # ``` -->
-<!-- #  -->
-<!-- # ```{r lamba-omega-alternate-design} -->
-<!-- # knitr::include_graphics((here::here("simulations/result_report/wpd_alterate_designs.png"))) -->
-<!-- # ``` -->
-
- <!-- Distribution across facet and x categories -->
-<!-- ### Need for normalisation -->
-
-### Discussion
-
-The distribution of wpd is different for different levels of facets and x-axis levels.
-This is because the statistic maximum which is used to define wpd is affected by the number of categories.
-The measure would have higher values if $C_i$ or $C_j$ has higher levels.
-However, we would ideally want a higher value of the measure only if there is significant difference between distributions across facet or x-axis categories, and not because the number of categories are higher.
-Therefore, in order to compare wpd across different combinations of facet and x-axis levels, we need to eliminate the impact of different levels of the facets and x-axis first and get a normalized measure.
-Henceforth we call the measure discussed as $wpd_{raw}$ and the normalised measure as $wpd_{norm}$.
-The measure $wpd_{norm}$ could potentially lead to comparison of the measure across different panels and also identifying only the interesting panels from a dataset.
-
-<!-- In Figures \ref{fig:dist-across-facets} and \ref{fig:dist-across-x}, both the cyclic granularities $C_i$ and $C_j$ are considered such that their levels vary in the range $(2, 5,7 ,9, 14, 21, 30, 45)$.
-Each of these combinations is considered a panel for each of which $MMPD_{raw}$ has been constructed $100$ times to compute the distribution.
-<!--More specifically, Figure \ref{fig:mean-sd-max} shows the marginal contribution of increasing levels of $C_i$ and $C_j$ on distribution of $MMPD_raw$.
-This shows that with the increase in the number of levels of $C_i$, the location of the distribution shift rightward, whereas for increasing x-axis levels, the scale of the distribution decreases.-->
-
-```{r hist-nx-nfacet, eval = FALSE}
-knitr::include_graphics(here::here("simulations/result_report/hist_nxbyfacet.png"))
-```
-
-```{r dist-across-facets, fig.cap = "Distribution of $MMPD_{raw}$ for different facet levels are shown.
-The location of the distribution shifts rightwards implying that as the number of facets increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained.", eval = FALSE}
-here::here()
-knitr::include_graphics(here::here("simulations/result_report","nx_by_facet_raw.png"))
-```
-
-<!-- # ```{r dist-across-facets, fig.cap = "Distribution of $MMPD_{raw}$ for different facet levels are shown.
-The location of the distribution shifts rightwards implying that as the number of facets increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained.
-"} -->
-<!-- # mmpd_raw = read_rds("../hakear-drake/data/data_all23457914n.rds")  -->
-<!-- # mmpd_xmore = read_rds("../hakear-drake/data/data_all213045x.rds")  -->
-<!-- # mmpd_fmore = read_rds("../hakear-drake/data/data_all_213045f_allx.rds") -->
-<!-- #  -->
-<!-- # data_all = bind_rows(mmpd_raw, mmpd_xmore) -->
-<!-- #  -->
-<!-- # data_long = data_all %>% pivot_longer(c(1:2), names_to = "category", values_to = "levels") -->
-<!-- #  -->
-<!-- # g1 <- data_all %>%  -->
-<!-- #   filter(!(nx %in% c(3, 4))) %>%  -->
-<!-- #   ggplot() + -->
-<!-- #   ggridges::geom_density_ridges(aes(x = raw_mmpd,  -->
-<!-- #                                     y = as.factor(nfacet))) + -->
-<!-- #   facet_wrap(~nx, nrow = 2) -->
-<!-- # g1 -->
-<!-- # ``` -->
-
-```{r dist-across-x, fig.cap = "Distribution of $MMPD_{raw}$ for different x levels are shown.
-The scale of the distribution becomes less and less implying that as the number of x levels increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained as the spread of the distribution decreases.
-", eval = FALSE}
-knitr::include_graphics(here::here("simulations/result_report/","nfacet_by_nx_raw.png"))
-```
-
-<!-- # ```{r dist-across-x, fig.cap = "Distribution of $MMPD_{raw}$ for different x levels are shown.
-The scale of the distribution becomes less and less implying that as the number of x levels increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained as the spread of the distribution decreases.
-"} -->
-<!-- # g2 <- data_all %>%  -->
-<!-- #   filter(nfacet<=14, nfacet!=3) %>%  -->
-<!-- #   ggplot() + -->
-<!-- #   geom_boxplot(aes(y = raw_mmpd,  -->
-<!-- #                                     x = as.factor(nx))) + -->
-<!-- #   facet_wrap(~nfacet) + coord_flip() -->
-<!-- #  -->
-<!-- # #  hist_plot = data_all %>%  -->
-<!-- # #       ggplot() + -->
-<!-- # #       geom_density(aes(x = raw_mmpd), fill = "blue") + -->
-<!-- # #       facet_grid(nx~nfacet) -->
-<!-- # # hist_plot -->
-<!-- # g2 -->
-<!-- # ``` -->
-
-<!-- both mean and standard deviation of the distribution of maximum and median varies for different sample sizes ($n$).
-There is a rightward shift in the location and decrease in scale with increasing $n$.
--->
-
-# Normalisation
-
-In an attempt to make the densities \ref{fig:hist_plot} same across different levels, we want to start by making their scale and location same.
-In that regard, we shuffle the data multiple times and compute the sampling distribution of  for each combination of facet and x-axis levels.
-
-The null hypothesis is that the two cyclic granularities do not differ on the outcome (i.e., that the outcome is observed independently of treatment assignment).
-When we permute the outcome values during the test, we therefore see all of the possible alternative treatment assignments we could have had and where the mean-difference in our observed data falls relative to all of the differences we could have seen if the outcome was independent of treatment assignment.
-While a permutation test requires that we see all possible permutations of the data (which can become quite large), we can easily conduct “approximate permutation tests” by simply conducting a vary large number of resamples.
-That process should, in expectation, approximate the permutation distribution.
-
-Finally, we run some simulation experiments to see if normalisation works. If normalisation has worked, it should work for both x levle and facet-levels.
-
-Thus these median maximum pairwise distances need to be normalized for different harmonies in a way that eliminates the effect of different levels, consequently enabling comparison across different harmonies.
-The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.
-
-```{r normal01-norm, fig.cap="Density plots of normalised wpd is shown for Normal(0,1) distribution.
-The mean and sd of the distribution looks almost similar for different facet and x-axis categories.", fig.pos="h"}
-
-knitr::include_graphics(here::here("simulations/norm/null_design_quantrans_nperm/figs/nxbyfacet_density_wpd_N01.png"))
-```
-
-## Methodology
-
-The mean and sd for each combination of facet and x levels could be computed by shuffling the data repeatedly and obtaining the distribution of $MMPD_{raw}$ for different combinations.
-If $MMPD_{raw}$ is then adjusted by the location and scale of this distribution, we could assume that the distribution of the resultant $MMPD_{norm}$ will have same distribution across different combinations of x and facet levels.
-All data is repeatedly shuffled $nperm$ times in random manner to obtain the measure $MMPD_{raw}$.
-Then the $MMPD_{norm}$ is obtained by scaling the observed value by the mean and sd of the distribution of $MMPD_{raw}$ obtained from the permuted data.
-
-\noindent Step 7 in the Algorithm defined in Section \ref{sec:} need to be revised in order to compute $MMPD_{norm}$ instead of $MMPD_{raw}$.
-Step 1-6 stays the same.
-The entire algorithm will have to repeated for all harmony pairs considered in the context.
-
-A simulation study is conducted to see if this methodology is working.
-
-## Null design
-
-## Alternate designs
-
-The behavior of the measure is monitored and understood through simulation experiments.
-A single simulation consisting of computational operations on a panel generating MMPD the value of which represents to what extent a pair of cyclic granularities would be interesting when displayed in the design.
-In comparing different simulation runs, we distinguish between different distributions and simulation scenarios (also iterations may be).
-
-### Simulated designs
-
- D1. Same distribution of the measured variable across all x-axis and facet categories
- D2. Different distribution across facet categories but same across x-axis categories
- D3. Different distribution across x-axis categories but same across facet categories
- D4. Different across both x-axis and facet categories
-
-Each of these case scenarios tried against Normal and a non-normal (Gamma) distribution to check if underlying distribution has a role to play.
-
-### Environment
-
-R version 4.0.1 (2020-06-06) is used with platform: x86_64-apple-darwin17.0 (64-bit) running under: macOS Mojave 10.14.6
-
-## Sample size
-
-How smaller or different sample size play a role in the distribution of the measure.
-
-## Number of permutations
-
-Find the number of permutations which are sufficient for consistent estimation of mean and standard deviation
+# Ranking and selecting harmonies

### 2021-03-07 paper/paper-supplementary.Rmd
working on supplementary section

--- 2021-01-20 paper/supplementary.Rmd
@@
 
-# Notations and Definitions
+Appendix A recalls the necessary notations and
+
+# Recalling notations
 
 Consider two cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.
-Let the pairwise distances between pairs $(a_{j} b_{k}, a_{j'}b_{k'})$ b   e denoted as $d_{(jk, j'k')} = JSD(a_{j}b_{k}, a_{j'}b_{k'})$.
-Pairwise distances could be within-facets or between-facets.
-Figure \ref{fig:distance-explain} illustrates how the within-facet or between-facet distances are defined.
-Pairwise distances are within-facets ($d_{w}$) when $b_{k} = b_{k'}$, that is, between pairs of the form $(a_{j}b_{k}, a_{j'}b_{k})$ as shown in panel (3) of Figure \ref{fig:distance-explain}.
-If categories are ordered (like all temporal cyclic granularities), then only distances between pairs where $a_{j'} = (a_{j+1})$ are considered (panel (4)).
-Pairwise distances are between-facets ($d_{b}$) when they are considered between pairs of the form $(a_{j}b_{k}, a_{j}b_{k'})$.
+Let $v = \{v_t: t = 0, 1, 2, \dots, T-1\}$ be a continuous variable observed across $T$ time points.
+Let the four elementary designs as described in Figure \ref{fig:null4by2} be $D_{null}$ where there is no difference in distribution of $v$ for $A$ or $B$, $D_{var_f}$ denotes the set of designs where there is difference in distribution of $v$ for $B$ and not for $A$.
+Similarly, $D_{var_x}$ denotes the set of designs where difference is observed only across A.
+Finally, $D_{var_{all}}$ denotes those designs for which difference is observed across both $A$ and $B$.
 
-```{r distance-explain, fig.cap = "Within and between-facet distances shown for two cyclic granularities A and B, where A is mapped to x-axis and B is mapped to facets.
-The dotted lines represent the distances between different categories.
-Panel 1) and 2) show the between-facet distances.
-Panel 3) and 4) are used to illustrate within-facet distances when categories are un-ordered or ordered respectively.
-When categories are ordered, distances should only be considered for consecutive x-axis categories.
-Between-facet distances are distances between different facet levels for the same x-axis category, for example, distances between {($a_1$,$b_1$) and ($a_1$, $b_2$)} or {($a_1$,$b_1$) and ($a_1$, $b_3$)}."}
-knitr::include_graphics(here::here("paper/Figs/dist_explain.png"))
-```
+# Simulation design
 
-# Behavior of raw wpd
+Observations are generated from Gamma(2,1), G(0.5, 1), N(0,1), N(0, 5) and N(5, 1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
+Each combination is being referred to as a _panel_.
+That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$.
+For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
+That is, if we consider the panel $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
+The values
+of $wpd$ is obtained for each of the panels.
+This design corresponds to $D_{null}$ as each combination of categories in a panel are drawn from the same distribution.
+Furthermore, the data is simulated for each of the panels $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
 
-Most of the behavior of the measure wpd was studied via simulation.
-The simulations explore how wpd performs under various designs and parameters and its limitations.
-To study the behavior of wpd, simulations were carried out for four different designs and the following factors that could potentially have an impact on the values of wpd:
+# Behavior of raw weighted distance measure
 
-<!-- Numerous simulations were carried out in a wide range of scenarios. -->
-
-<!-- Same scenarios were used, when possible with normalized wpd, keeping all other simulation variables constant. -->
-
-- $nx$ (number of levels of x-axis)
-- $nfacet$ (number of levels of facets)
-- $\lambda$ (tuning parameter)
-- $\omega$ (increment in each panel design)
-- $dist$ (normal/non-normal distributions with different location and scale)
-- $n$ (sample size for each combination of categories)
-- $nsim$ (number of simulations)
-- $nperm$ (number of permutations of data)  
-- $designs$  
-$D_{null}$  (No difference in distribution)  
-$D_{var_f}$ (Difference in distribution only across facets)  
-$D_{var_x}$ (Difference in distribution only across x-axis)  
-$D_{var_{all}}$ (Difference in distribution in both facets and x-axis)
-
-```{r simtable, eval = FALSE}
-variable = c("nx", "nfacet", "lambda", "omega", "dist", "n", "nsim", "nperm", "design")
-
-description = c("number of levels of x-axis", "number of levels of facets",
-                "tuning parameter","increment in each panel design", "normal/non-normal distributions with different location and scale", "sample size", "number of simulations", "number of permutations of data",
-                "$D_{null}$ (No difference in distribution), $D_{var_f}$ (Difference in distribution only across facets), $D_{var_x}$ (Difference in distribution only across x-axis), $D_{var_all}$ (Difference in distribution in both facets and x-axis)")
-table = tibble::tibble(variable, description)
-
-table %>% 
-knitr::kable(format = "latex",
-             escape = TRUE) %>% 
-  kableExtra::kable_styling(
-    bootstrap_options = "striped", 
-    full_width = F, 
-    font_size = 7)
-
-```
-
-## Null design
-
-This section explores the behavior of wpd in designs where there is no difference in distribution between x and facet categories.
-We have considered different initial distributions to study the impact of initial distribution under the null setup.
 Since the measure wpd is essentially set up to detect differences in distributions irrespective of underlying distribution, it would be ideal if it has minimal dependency on the type, location and scale of the initial distribution.
 To that end, some pre-processing of the data is preferred to bring it to the same scale, location and type.
-The Normal Score Transform or NQT has been applied in various fields of geo-statistics in order to make most asymmetrical distributed real world measured variables more
-treatable and normal-like.
+The Normal Score Transform or NQT has been applied in various fields of geo-statistics in order to make most asymmetrical distributed real world measured variables more treatable and normal-like.
 
@@
 
-Further, we want to study the distribution of wpd for different $nx$ and $nfacet$.
+Firstly, we show that NQT works to make the distribution within each panel same. Next, we study the distribution of $wpd$ for different $nx$ and $nfacet$ in various ways.
 
-### Simulation setup
+## NQT works
 
-<!-- Study the behavior of wpd under different initial distributions for different $nx$ and $nfacet$ -->
+```{r gamma-diff-wotrans, fig.cap="Ridge plots of raw wpd is shown for Gamma(0.5,1), Gamma(2,1) distribution without NQT.
+The densities change across different facet and x levels and also looks different for the two distributions, which implies wpd value is affected by the change in the shape paramter of the gamma distribution."}
+knitr::include_graphics(here::here("simulations/raw/null_design_scale/figs/gamma_ridge_nxbynfacet.png"))
+```
 
-Using two types of distributions, viz.
-normal and gamma (non-normal), we generated observations for each combination of $nx$ and $nfacet$ from the following sets: $nx = \{2, 3, 5, 7, 14, 20, 31, 50\}$ and $nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
-Each combination is being referred to as a _panel_.
-That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$.
-For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
-That is, if we consider the panel  $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
-The values of $\lambda$ is set to $0.67$, since we want to up-weigh the within-facet distances and that of $\omega$ is set to $0$, since there is no significant differences between distributions in the null case.
-Observations were generated for each type of distribution changing the shape and scale to study the effect of shape, scale and type of distribution on wpd.
-The set of distributions considered for this purpose is ${N(0,1), N(5, 1), N(0,5), \Gamma(0.5, 1), \Gamma(2, 1)}$.
-Each of the scenario is run $nsim = 200$ times to see the distribution of wpd values for each scenario.
-
-<!-- wpd is computed for different normal and non-normal distributions to see how the underlying distribution has a role to play in the value of wpd.
-Since we are concerned with detecting the differences in distributions, it would be ideal if wpd has minimal dependency on the type, location and scale of the  underlying distribution.
-To that end, some pre-processing of the data is preferred to bring it to the same scale, location and type.
--->
-
-<!-- Null design only where all combinations are equal for fixed values of $\mu$ and $\sigma$ -->
-<!-- Dist 1: $N(0,1)$ individual graph -->
-<!-- Dist 2: $N(\mu, 1)$ (faceted with different values of $\mu$: not yet just for one value now) -->
-<!-- Dist 3: $N(0, \sigma)$ (faceted with different values of $\sigma$: not yet just for one value now) -->
-<!-- Dist 4: $N(\mu, \sigma)$ faceted with different values of mu and sigma, for all levels of x and facet to see how value of wpd changes with that of change in parameters. -->
-
-<!-- **Assumptions:** There is no difference in distribution between any facet or x-category -->
-<!-- nsim = 200 -->
-<!-- lambda = 0.67 -->
-
-<!-- **Questions:**  -->
-<!-- - How raw value of wpd changes with different nx and nfacet for different location and scale of a Normal and non-normal distribution -->
-
-Figure \ref{fig:normal-diff-quantrans} and \ref{fig:gamma-diff-quantrans} show distribution of wpd for different initial normal and gamma distribution to study the effect of changing location and scale on the distribution of wpd.
-It seems like the  distribution changes across different facet and x levels but look the same for each panel, which implies wpd value is unaffected by the change in location and scale of the the normal distribution.
-Figure \ref{fig:mean-sd-ns-nfacet} shows how mean and sd of the distribution of wpd changes with the increasing x and facet levels.
-It seems like both mean and standard deviation are affected more by change in the x-axis levels than the facet levels.
-Figure \ref{fig:nxbyfacet-ridge-N05} gives another way to look at the effect of changing facet and x levels on the distribution of wpd for an initial distribution $N(0,5)$.
-Clearly, the location of the distribution shifts to the right for increasing x levels and scale is different for low and high values of facet levels with a longer left tail for lower facet levels.
-We have considered alternate distribution, location and scale for this simulation setting, but do not present the results as they are behaviorally similar.
-
-<!-- # ```{r normal-diff, fig.cap="Ridge plots of raw wpd is shown for N(0,1) and N(5,1) distribution.
-The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change in mean and standard deviation of the normal distribution", eval = FALSE} -->
-<!-- # knitr::include_graphics(here::here("simulations/null_design/figs/normal_ridge_nxbynfacet_wpd_N01.png")) -->
-<!-- # ``` -->
-
-```{r normal-diff-quantrans, fig.cap = "Ridge plots of raw wpd is shown for N(0,1), N(5,1) and N(0,5) distribution.
-The densities change across different facet and x levels but look same for each panel, which implies wpd value is unaffected by the change in mean and standard deviation of the normal distribution"}
-knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_normal.png"))
-```
+### with NQT
 
@@
 
-```{r mean-sd-ns-nfacet, fig.cap="Movement of mean and sd for raw wpd is shown for different number of levels (nlevel) of x-axis and facets through line plots.
-Mean increases and sd decreases more sharply for increasing x-axis levels as compared to facet levels.
-It seems like both mean and standard deviation are affected more by change in the x-axis levels than the facet levels.", fig.pos="h"}
-knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/mean_sd_nx_nfacet.png"))
+## By distribution
 
+```{r normal-diff-quantrans, fig.cap = "Ridge plots of raw wpd is shown for N(0,1), N(5,1) and N(0,5) distribution.
+The densities change across different facet and x levels but look same for each panel, which implies wpd value is unaffected by the change in mean and standard deviation of the normal distribution", eval = FALSE}
+knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_normal.png"))
 ```
+
+## By category levels
 

### 2021-03-07 paper/supplementary.Rmd
working on supplementary section

@@
 To that end, some pre-processing of the data is preferred to bring it to the same scale, location and type.
-The Normal Score Transform or NQT has been applied in various fields of geo-statistics in order to make most asymmetrical distributed real world measured variables more
-treatable and normal-like.
+The Normal Score Transform or NQT has been applied in various fields of geo-statistics in order to make most asymmetrical distributed real world measured variables more treatable and normal-like.
 
@@
 knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_normal.png"))
+```
+
+```{r gamma-diff-wotrans, fig.cap="Ridge plots of raw wpd is shown for Gamma(0.5,1), Gamma(2,1) distribution.
+The densities change across different facet and x levels and also looks different for the two distributions, which implies wpd value is affected by the change in the shape paramter of the gamma distribution."}
+knitr::include_graphics(here::here("simulations/raw/null_design_scale/figs/gamma_ridge_nxbynfacet.png"))
 ```

### 2021-03-07 size_small.R

@@ -1,3 +1,7 @@
+# This constitutes the simulation for checking if harmonies are being ranked properly
+# 
+# Observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = \{3, 7, 14\}$ and $nfacet = \{2, 9, 10\}$. The panel $(3, 2), (7,9), (14, 10)$ are considered to have design $D_{null}$. The panels $(7, 2), (14, 9)$ have design of the form $D_{var_f}$. $(14, 2), (3, 10)$ have design of the form $D_{var_x}$ and the rest are under $D_{var_{null}}$. We generate only one data set for which all these designs were simulated and consider this as the original data set. We generate $200$ repetitions of this experiment with different seeds and compute the proportion of times a panel is rejected when it is under $D_{null}$. We also compute the proportion of times a panel is rejected when it actually belongs to a non-null design. The first proportion is desired to be as small as possible and a higher value of the later is expected. Also, these would constitute to be the estimated size and power of the test.
+
 library(readr)
 library(dplyr)
 library(hakear)
@@ -5,10 +9,28 @@ library(distributional)
 library(gravitas)
 library(here)
 library(tidyr)
-sample_seed = seq(1000,2999, by = 10)
-nperm = 200
-simtable <- read_csv(here::here('simulations/sim_table/sim_table.csv'))
+library(tidyverse)
+library(parallel)
 
+# set values of parameters
+sample_seed = seq(1000, 2999, by = 10) # number of  sample to compute p-value
+nperm = 200 # number of permutations to compute wpd threshold
+nx_range <- c(3, 7, 14)
+nfacet_range <- c(2, 9, 10)
+design_range <- c("null", "var_f", "var_x","var_all", "null", "var_f", "var_x","var_all", "null")
+
+# simulation table for which threshold is computed
+
+sim_table <- expand.grid(nx = nx_range,
+                         nfacet = nfacet_range
+) %>%
+  tibble()
+
+simtable <- sim_table %>%
+  bind_cols(design = design_range)
+
+
+# define functions for different designs
 sim_varx_normal <- function(nx, nfacet, mean, sd, w) {
   rep(dist_normal((mean + seq(0, nx - 1, by = 1) * w), sd), nfacet)
 }
@@ -16,7 +38,6 @@ sim_varx_normal <- function(nx, nfacet, mean, sd, w) {
 sim_varf_normal <- function(nx, nfacet, mean, sd, w) {
[…]

### 2021-03-09 paper/main.Rmd
fixed the heatplot and raw data

@@
 
-\begin{equation}
+\begin{equation}\label{def:raw-wpd}
 d*_{(j,k), (j'k')} =
@@
 Let $v_{i, t}$ denote the electricity demand for $i^{th}$ household for time period $t$.
-The series $v_{i, t}$ is the linear granularity corresponding to half-hour since the interval of this data is 30 minutes.
+The series $v_{i, t}$ is the linear granularity corresponding to half-hour since the interval of the tsibble is 30 minutes.
 We consider coarser linear granularities like hour, day, week and month from the commonly used Gregorian calendar.
@@
 
-$v_{i, t}$ has a asymmetrical distribution as could be seen in \ref{fig:raw-nqt-8} and the Normal score transform has been applied to make it more symmetric.
+$v_{i, t}$ has a asymmetrical distribution as could be seen in Figure \ref{fig:raw-nqt-8} and the Normal score transform has been applied to make it more symmetric.
 Let $v*_{i, t}$ denote the normal-quantile transformed electricity demand for $i^{th}$ household for time period $t$.
@@
 Sample quantiles were computed at $p = 0.01, 0.02, \dots, 0.99$.
-Jensen-Shannon distances are computed between $q^{i, p}_{A, j}$ and $q^{i, p}_{B, k}$ for each ${j \in J, k \in K}$ to obtain within-facet and between-facet distances.
-A tuning parameter of $\lambda = 0.67$ has been considered to upweigh the within-facet distances and down-weigh the between facet distances and the maximum of them are obtained to compute $wpd$.
+Jensen-Shannon distances are computed between $q^{i, p}_{A, j}$ and $q^{i, p}_{B, k}$ for each ${j \in J, k \in K}$ to obtain the relevant within-facet and between-facet distances.
+A tuning parameter of $\lambda = 0.67$ has been considered in Equation \ref{def:raw-wpd} to compute $wpd$.
 It is further normalized using the approach described in Section \ref{sec:norm-wpd}.
@@
 The harmony pairs are then arranged in descending order and the important ones with significance level 1%, 5% and 10% are highlighted with `***`, `**` and `*` respectively.
-Table \ref{tab:tab-rank-8} shows the rank of the harmonies for different households
-\ref{fig:dotplot-8} shows the heatmap for the eight households
+Table \ref{tab:tab-rank-8} shows the rank of the harmonies for different households.
+Figure \ref{fig:dotplot-8} shows the heatmap for the eight households
 with the value of $wpd_{norm}$ filled as colors.
@@
 It could be observed that the daily pattern is similar for weekdays and weekends with a morning and evening peak.
-However,the difference between morning and evening peaks are higher for weekends.
+However, the difference between morning and evening peaks are higher for weekends.
 Since $wpd_{norm}$ is designed to put more weightage on within-facet differences, it makes sense that the pair (hod, wdwnd) has been ranked higher than (wdwnd, hod).
 Panel c) shows the distribution of energy demand with weekday/weekend as the x-axis and week-of-month as the facets.
-Although the differences might seem significant at first, with closer inspection it could be seen that the range of the demand is low in this case and hence the differences are not large enough to cross the threshold for significance.
+Although the differences might seem significant at first, with closer inspection it could be seen that the scale of the demand is lower in this case and hence the differences are not large enough to cross the threshold for significance.
 
@@
 Also, the ones bordered red are selected with 90 percent significance level.
-Visualizing the pairs in this way helps us to see the important cyclic granularities along the x-axis and facet along with the information that which households should be analyzed together." }
+Visualizing the pairs in this way helps us to see the important cyclic granularities along the x-axis and facet along with the information that which households should be analyzed together.", fig.height = 8}
+# elec_sig_split <- elec_harmony_all %>%
+#   mutate(select_split =  str_split(select_harmony, " ", simplify = TRUE)[,2]) %>% 
+#   
+  select_split <- str_split(elec_harmony_all$select_harmony, " ", simplify = TRUE)[,2]
+
   elec_sig_split <- elec_harmony_all %>% 
-  mutate(select_split =  str_split(select_harmony, " ", simplify = TRUE)[,2]) %>% 
+    bind_cols(select_split = select_split) %>% 
   mutate(significant = case_when(
@@
 heatplot <- elec_sig_split %>% 
-  mutate(significance_95 = if_else(significant %in% c("high", "highest"), "yes", "no")) %>% 
-  ggplot() +
-  geom_tile(aes(x = x_variable,
-                 y = facet_variable, 
-                 fill = wpd, color = significance_95), size = 1) + 
-  #scale_fill_gradient(low = "white",high = "steelblue") +
-  scale_fill_gradient2() +
-  scale_colour_manual(values = c("white","red")) + 
+  mutate(significance_95 = if_else(significant %in% c("high", "highest"), "*", "")) %>% 
+  ggplot(aes(x = x_variable,
+                 y = facet_variable)) +
+  geom_tile(aes(fill = wpd)) + 
+                #color = as.factor(significance_95)),
+            #size = 0.3) +
+  geom_text(aes(label = significance_95), color = "#42275a") +
+  scale_fill_gradient(low = "white",high = "#ba5370") +
+  #scale_fill_manual(palette = "Dark2") +
+  #scale_colour_manual(values = c("white","red")) + 
   theme(legend.position = "bottom") +
-  facet_wrap(~id, nrow = 1, strip.position = "bottom") +
   coord_fixed() + 
@@
   theme(panel.grid = element_blank(),
-        axis.text.x = element_text(angle = 60, hjust=1),legend.position = "bottom") + ggtitle("b")
+        axis.text.x = element_text(angle = 60, hjust=1),legend.position = "bottom") + ggtitle("a") +
+  theme(
+    strip.background = element_blank(),
+    strip.text.y  = element_blank(), plot.margin = unit(c(0, -2, 0, 0), "cm"))
 
@@
   #geom_point(size = 0.1, colour = "black", alpha = 0.3) +
-  geom_line(size = 0.1, colour = "blue", alpha = 0.2) +
+  geom_line(size = 0.1, colour = "blue", alpha = 0.6) +
   facet_wrap(~id, 
              scales = "free_y",
-             nrow = 1,
-             strip.position =  "top") + xlab("") + 
-  theme_void() + theme(strip.text.x = element_blank()) +
-  ylab("energy demand in September (kwh)") + ggtitle("a")
-
-elec_zoom/heatplot
+             ncol = 1,
+             strip.position =  "right",labeller = "label_both") + xlab("Time [30m]") + 
+  theme_minimal() + 
+  ylab("linear energy demand (kwh) for September") + ggtitle("b")
+
+heatplot +  facet_grid(id~.) + elec_zoom +
+  theme(
+    strip.background = element_blank(),
+    strip.text.y  = element_blank(), plot.margin = unit(c(0, 0, 0, 0), "cm")) +
+  plot_layout(widths = c(1, 2))
 

### 2021-03-09 size-small.sh

@@ -1,0 +1,14 @@
+#! /bin/bash
+#SBATCH --job-name=size_small
+#SBATCH --output=trace_%a.out
+#SBATCH --error=error_%a.err
+#SBATCH --mem-per-cpu=4096
+#SBATCH --time=168:00:00
+#SBATCH --ntasks=1
+#SBATCH --constraint=Xeon-Platinum-8260
+#SBATCH --cpus-per-task=1
+#SBATCH --mail-type=BEGIN,END,FAIL
+#SBATCH --mail-user=Sayani.Gupta@monash.edu
+#SBATCH --export=NONE
+module load R/4.0.0-openblas
+Rscript size_small.R 

### 2021-03-09 paper/main.Rmd
table updated and theme of raw plot

@@
              ncol = 1,
-             strip.position =  "right",labeller = "label_both") + xlab("Time [30m]") + 
-  theme_minimal() + 
+             strip.position =  "right",
+             labeller = "label_both") + 
+  xlab("Time [30m]") + 
+  theme_grey() + 
   ylab("linear energy demand (kwh) for September") + ggtitle("b")
@@
 heatplot +  facet_grid(id~.) + elec_zoom +
-  theme(
-    strip.background = element_blank(),
-    strip.text.y  = element_blank(), plot.margin = unit(c(0, 0, 0, 0), "cm")) +
+  theme( plot.margin = unit(c(0, 0, 0, 0), "cm")) +
   plot_layout(widths = c(1, 2))
@@
   rename("facet variable" = "facet_variable",
-         "x variable" = "x_variable",
-         "facet levels" = "x_levels",
-         "x levels" = "x_levels")
+         "x variable" = "x_variable") %>% 
+  select(-facet_levels, -x_levels)
 

### 2021-03-10 paper/main.Rmd
updating figures

@@
 preamble: >
+  \setlength {\marginparwidth }{2cm}
   \usepackage{mathtools,amssymb,booktabs,amsthm,todonotes,colortbl}
@@
 Also, it gives an overview on when these households are away for holidays and which months consumptions are highest (Jan, Feb).
-However,when it comes to discerning periodic patterns, analyzing all possible periodic patterns through this display is overwhelming due to combination of linear and cyclic representation of time.
+However, when it comes to discerning periodic patterns, analyzing all possible periodic patterns through this display is overwhelming due to combination of linear and cyclic representation of time.
 For example, there is more going on in terms of peaks and troughs in id 2 compared to id 4, but it is not clear which all periodic patterns are dominant and if it differs between households."}
@@
 
-```{r id2, fig.cap = "Distribution of energy consumption displayed through area quantile plots across two cyclic granularities month-of-year and hour-of-day for id2 (a) and id4 (b).
-The black line is the median, whereas the purple band covers the 25th to 75th percentile, the orange band covers the 10th to 90th percentile, and the green band covers the 1st to 99th percentile.
-Difference between 90th and 75th quantiles less for (Jan, Feb) in a) suggesting that it is a more frequent user of air conditioner than b).
-Energy consumption in a) changes across both granularities, whereas for b) daily pattern stays same irrespective of the months."}
+```{r id2, fig.cap = "Distribution of energy consumption displayed through area quantile plots across two cyclic granularities month-of-year and hour-of-day for id2 (left) and id4 (right).
+The black line is the median, whereas the orange band covers the 25th to 75th percentile and the green band covers the 10th to 90th percentile.
+Difference between the 90th and 75th quantiles is less for (Jan, Feb) in id2 suggesting that it is a more frequent user of air conditioner than id4.
+Energy consumption for id2 changes across both granularities, whereas for id4 daily pattern stays same irrespective of the months."}
 ggpubr::ggarrange(p1, p2, ncol = 2)
@@
 
- * We introduce a new distance measure for detecting periodic interactions. This induces data reduction which allows for identification of patterns, if any, in the time series data.
-
- * We show that the distance metric could be used to rank the periodic patterns based on how well they capture the variation in the measured variable as they have been normalized for different number of comparisons.
-
- * We device a framework for choosing a threshold, which will result in detection of only significantly interesting periodic patterns in the time series data.
+ <!-- * We introduce a new distance measure for detecting periodic interactions. This induces data reduction which allows for identification of patterns, if any, in the time series data. -->
+
+ <!-- * We show that the distance metric could be used to rank the periodic patterns based on how well they capture the variation in the measured variable as they have been normalized for different number of comparisons.
+-->
+
+ <!-- * We device a framework for choosing a threshold, which will result in detection of only significantly interesting periodic patterns in the time series data. -->
+
+ * introduce a new distance measure for quantifying periodic interactions, which allows for identification
+of patterns in the time series data;
+ * device a framework for choosing a threshold, which results in detection of only significantly interesting
+periodic patterns;
+ * show that the proposed distance metric could be used to rank the periodic patterns based on
+how well they capture the variation in the measured variable since they have been normalized for
+relevant parameters.
 
@@
 
-Furthermore, these distances are distributed as chi-squared with $m$ degrees of freedom (Menendez1997-in), if the continuous distribution is being discretized with $m$ discrete values.
+Furthermore, these distances are distributed as chi-squared with $m$ degrees of freedom (@Menendez1997-in), if the continuous distribution is being discretized with $m$ discrete values.
 Taking sample percentiles to approximate the integral would mean taking $m = 99$.
@@
 Furthermore, the intended aim of $wpd$ is to capture differences in categories irrespective of the distribution from which the data is generated.
-Hence, as a pre-processing step,the raw data is normal quantile transformed (reference) so that the quantiles of the transformed data follows a standard normal distribution.
+Hence, as a pre-processing step,the raw data is normal quantile transformed (@Bogner2012-az) so that the quantiles of the transformed data follows a standard normal distribution.
 The steps employed for computing the distance measure is summarized as follows:
@@
 The measure would have higher values if $A$ or $B$ has higher levels.
-However, we would ideally want a higher value of the measure only if there is a significant difference between distributions across facet or x-axis categories, and not because the number of categories $J$ or $K$ is high.
+However, we would ideally want a higher value of the measure only if there are a significant difference between distributions across facet or x-axis categories, and not because the number of categories $J$ or $K$ is high.
 Therefore, in order to compare $wpd$ across different combinations of facet and x-axis levels, we need to eliminate the impact of different number of comparisons and get a normalized measure.
@@
 
-This method is somewhat similar in spirit to bootstrap (reference) or permutation (reference) tests, where the goal is to test the hypothesis that the groups under study have identical distributions.
+This method is somewhat similar in spirit to bootstrap or permutation tests, where the goal is to test the hypothesis that the groups under study have identical distributions.
 This method, in essence, accomplishes a different goal of making the location and scale of different groups (panels) same under $D_{null}$.
@@
 
-In the linear model approach, $wpd\in R$ was assumed, whereas, $wpd$ is a  Jensen-Shannon Distance (JSD) and lies between 0 and 1 (reference).
+In the linear model approach, $wpd\in R$ was assumed, whereas, $wpd$ is a Jensen-Shannon Distance (JSD) and lies between 0 and 1 (@JSD).
 Furthermore, JSD follows a Chi-square distribution, which is a special case of Gamma distribution.
@@
 The results for this section is WIP and to be included in details in the Supplementary paper.
-Also, Figure \ref{fig:plot-all-new2} presents the results of $wpd_{norm}$ from the illustrative designs in Section \ref{sec:computation-wpd}.
+Also, Figure \ref{fig:plot-all-new3} presents the results of $wpd_{norm}$ from the illustrative designs in Section \ref{sec:computation-wpd}.
 As expected, the value of $wpd_{norm}$ under null design is the least (a), followed by (b, c and d).
-Moreover, note the the relative difference in $wpd_{norm}$ values as we move from  a to d, which aligns with the idea of $wpd_{norm}$, since the differences between x categories are up-weighed by design.
+Moreover, note the relative difference in $wpd_{norm}$ values as we move from  a to d, which aligns with the idea of $wpd_{norm}$, since the differences between x categories are up-weighed by design.
 
@@
   ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
-  ggtitle(paste("d", round(varall, 2)))
+  ggtitle(paste("d", round(varall, 2))) + xlab("x level")
 ```
@@
   ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
-    ggtitle(paste("c", round(varx, 2)))
+    ggtitle(paste("c", round(varx, 2))) + xlab("x level")
 ```
@@
   ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
-    ggtitle(paste("b", round(varf, 2)))
+    ggtitle(paste("b", round(varf, 2))) + xlab("x level")
 ```
@@
   ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
-    ggtitle(paste("a", round(null, 2)))
-```
-
-```{r plot-all-new2, fig.cap = "$wpd_{norm}$ values for the four illustrative designs are presented here.
+    ggtitle(paste("a", round(null, 2))) + xlab("x level") 
+```
+
+```{r plot-all-new3, fig.cap = "$wpd_{norm}$ values for the four illustrative designs are presented here.
 As expected, the value of $wpd_{norm}$ under null design is the least (a), followed by (b, c and d).
@@
 The data has been cleaned to be a `tsibble` (@wang2019tsibble) containing half-hourly electricity consumption from Jul-2019 to Dec-2019 for each of the households, which is procured by them by downloading their data from the energy supplier/retailer.
+We also have some additional demographics data in terms of the number of members in the household and the presence of kids/elderly parents and their profession.
+
 Demand data for these households are shown in a linear time scale in Figure \ref{fig:linear-scale-8}.
-It is evident from the range of the demand data that these households vary in consumption levels as well as in their temporal patterns.
-In the left panel of Figure \ref{fig:linear-scale-8} (a), the linear representation of the entire time period is shown, whereas in the right panel (b) a particular month is shown and furthermore a week has been highlighted to inspect if there is any daily or weekly periodic patterns in their behavior that is reflected when we zoom into the the linear representation of the time series.
-We have some additional demographics data in terms of the number of members in the household and presence of kids/elderly parents and their profession.
-
-```{r}
+In the left panel of Figure \ref{fig:linear-scale-8} (a), the linear representation of the entire time period is shown, whereas in the right panel (b) a particular month is shown and furthermore a week has been highlighted.
+It is evident from the range of the demand data in  Figure \ref{fig:linear-scale-8} (a), that these households vary in consumption levels, but all their periodic patterns have been squeezed with this representation.
+When we zoom into the linear representation of this series in Figure \ref{fig:linear-scale-8} (b), some patterns are visible in terms of peaks and troughs, but we do not know if they are regular or what is their period.
+Electricity demand, in general, has a daily and weekly periodic pattern.
+However, it is not apparent from this view if all of these households have those patterns and in case they have if they are significant enough.
+Also, it is not clear if any other periodic patterns are present in any household which might have been hidden with this view.
+We start the analysis by asking if the ranking of the harmonies make sense for the households, then compare households to get more insights of what these rankings imply and if they could be used to remove some non-interesting harmonies.
+Furthermore, we see if the display of the significant harmonies could be validated by zooming in the linear representation of the time series.
+
+```{r tab-demography}
 demography <- tibble(id = c(1, 2, 3, 4, 5,6, 7, 8), 
@@
 
-We start the analysis by asking if the ranking of the harmonies make sense for the households, then compare households to get more insights of what these rankings imply and if they could be used to remove some non-interesting harmonies.
-Furthermore, we see if the display of the significant harmonies could be validated by zooming in the linear representation of the time series.
-
 <!-- if we are benefiting by moving from a linear to cyclic representation of time to . -->
 
-```{r linear-scale-8, fig.cap = "Electricity demand for eight households are shown in different facets from Jul-19 to Dec-19 in Fig a and it has been zoomed in for Sep-19 in Fig b, where a week in Sep-19 has been highlighted.
-From the scales of Fig a, it is apparent that they have different level of consumption but all of them have some periodic behavior in terms of regular peaks and troughs.
-It is not clear which all periodic patterns exist.
-In fig b, periodic pattern is zoomed in for a month and we can see weekly patterns for the entire period and daily pattern for the highlighted week."}
+```{r linear-scale-8, fig.cap = "Electricity demand for eight households is shown in different facets from Jul-19 to Dec-19 in Fig a and it has been zoomed in for Sep-19 in Fig b, where a week in Sep-19 has been highlighted.
+From the scales of Fig a, it is apparent that these households vary in consumption levels, but all their periodic patterns have been squeezed with this representation.
+In fig b, we can see some weekly patterns for the entire period and daily patterns for the highlighted week and there could be some other patterns visible in terms of peaks and troughs, but it is not clear if they are regular or significant.", fig.height=8}
 library(scales)
@@
 
-```{r raw-nqt-8, fig.height = 5, fig.cap="The raw density of the half-hourly demand for the eight households in Panel a.
-Panel b shows the normal-score-transform half-hourly demand for the same households which has resulted in more symmetric distribution of half-hourly demand."}
+```{r raw-nqt-8, fig.height = 5, fig.cap="The raw density of the half-hourly demand for the eight households is shown in Fig a.
+Fig b shows the normal-score-transformed half-hourly demand for the same households which has resulted in more symmetric distribution of half-hourly demand."}
 elec_raw <- elec %>% 
@@
 However, the difference between morning and evening peaks are higher for weekends.
-Since $wpd_{norm}$ is designed to put more weightage on within-facet differences, it makes sense that the pair (hod, wdwnd) has been ranked higher than (wdwnd, hod).
+Since $wpd_{norm}$ is designed to put more weightage on within-facet differences for $\lambda>0.5$, it makes sense that the pair (hod, wdwnd) has been ranked higher than (wdwnd, hod).
 Panel c) shows the distribution of energy demand with weekday/weekend as the x-axis and week-of-month as the facets.
@@
 
-Figure \ref{fig:dotplot-8} helps to compare between households through the heatmap (b) and validate the results of the heatmap through linear display in (a) .
+Figure \ref{fig:dotplot-8} helps to compare households through the heatmap (a) and validate the results of the heatmap through linear display in (b).
 The top panel contains the raw data for a month (Sep-2019).
 The darker the color of a cell in the heatmap, the more significant a harmony pair it is.
-Also, the ones with red borders are significant at 95% significance.
-This plot suggests that there is no significant periodic patterns for id 5, even when the demographics of id 5 is very similar to id 6 and 7.
-Household id 6 and 7 differ in the sense that for id 6, difference in patterns only during weekday/weekends (two members are in mixed profession), whereas for id 7, all or few other days of the week are also important (members are in academia and hence more flexible routines).
+Also, the ones with `*` are significant at 95% level This plot suggests that there are no significant periodic patterns for id 5, even when the demographics of id 5 are very similar to id 6 and 7.
+Household id 6 and 7 differ in the sense that for id 6, the difference in patterns only during weekday/weekends (two members are in the mixed profession), whereas for id 7, all or few other days of the week are also important (members are in academia and hence might have more flexible routines).
 The periodic pattern is very similar to id 8, which has a very different demographic property.
-Both from the linear representation and heatmap, it is clear that id 2 and 3 are similar, both in term of periodic pattern as well as demographics.
+Households id 2 and 3 are similar, in terms of linear display, periodic patterns as well as demographics.
+Different periodic behavior could be observed in households with very similar demographics (id 5 compared to 6 and 7 - only the variable `profession` is different) and similar periodic behavior can stem from households with very different demographics (id 7 and 8 - differs in all variables in \ref{tab:tab-demography}).
+This could also be verified from the corresponding linear representation in \ref{fig:dotplot-8}(b).
 

### 2021-05-04 paper/main.Rmd
updating supplementary section

@@
 This work provides a methodology to screen the most informative graphics from the plethora of choices by introducing a distance measure that could be compared across harmonies with varied levels and data sets.
-Moreover, this distance measure could also be used to rank the selected harmonies basis how well they capture the variation in the measured variable.
+Moreover, this distance measure could also be used to rank the s = ted harmonies basis how well they capture the variation in the measured variable.
 All the methods are implemented in the open source R package `hakear`.
@@
 library(lvplot)
-library(ggridges)
+#library(ggridges)
 library(viridis)
@@
 
+```{r}
+id2_tsibble %>%
+  create_gran("month_year") %>% 
+  ggplot() +
+  geom_lv(aes(x = month_year, y = kwh))
+
+   prob_plot("month_year",
+             "hour_day",
+             response = "kwh",
+             plot_type = "quantile",
+             symmetric = TRUE,
+             quantile_prob = c(0.1, 0.25,0.5,0.75, 0.9)) +
+  ggtitle("") + theme(
+        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + 
+  scale_colour_brewer(name = "", palette = "PiYG")
+```
+
 ```{r id2, fig.cap = "Distribution of energy consumption displayed through area quantile plots across two cyclic granularities month-of-year and hour-of-day for id2 (left) and id4 (right).
@@
 
-demography %>% kable(format  = "markdown", caption = "Demographics of the eight households chosen for study")
+demography <- demography %>% kable(format  = "markdown", caption = "Demographics of the eight households chosen for study")
+
+demography %>% add_footnote(label = "***: 99% significant, **: 95% and *: 90%")
 ```
@@
              "wknd_wday",
+             response = "kwh",
+             plot_type = "quantile",
+             symmetric = FALSE,
+             quantile_prob = 
+               c(0.25,0.5,0.75)) +
+  scale_colour_brewer(name = "", palette = "Set2") +
+  theme(
+        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + theme(legend.position = "bottom",
+        strip.text = element_text(size = 7, margin = margin())) +
+  ggtitle("c) wom vs wdwnd (insignificant)")
+
+p4 <- id1_tsibble %>%
+   prob_plot("day_month",
+             "hour_day",
              response = "kwh",
@@
   plot_layout(widths = c(1, 2)) 
-
-#            
-# dotplot <- elec_sig_split %>% 
-#   ggplot() +
-#   geom_point(aes(x = x_variable,
-#                  y = facet_variable, 
-#                  size = wpd, 
-#                  fill = significant),
-#              shape=21,
-#              alpha= 0.8) +
-#   scale_size_continuous() +
-#   theme(legend.position = "bottom") +
-#   scale_fill_viridis(discrete = TRUE, direction = 1) +
-#   facet_wrap(~id, nrow = 2) +
-#   guides(fill = guide_legend(), 
-#          size = guide_legend()) +
-#   theme_gray(base_size = 12, base_family = "Times") +
-#    theme(legend.position = "bottom")
 ```

### 2021-05-04 paper/paper-supplementary.Rmd
updating supplementary section

@@
 Consider two cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.
-Let $v = \{v_t: t = 0, 1, 2, \dots, T-1\}$ be a continuous variable observed across $T$ time points.
-Let the four elementary designs as described in Figure \ref{fig:null4by2} be $D_{null}$ where there is no difference in distribution of $v$ for $A$ or $B$, $D_{var_f}$ denotes the set of designs where there is difference in distribution of $v$ for $B$ and not for $A$.
-Similarly, $D_{var_x}$ denotes the set of designs where difference is observed only across A.
+Let $v = \{v_t: t = 0, 1, 2, \dots, T-1\}$ be a continuous measured variable observed across $T$ time points.
+Let the four elementary designs be $D_{null}$ where there is no difference in distribution of $v$ for $A$ or $B$, $D_{var_f}$ denotes the set of designs where there is difference in distribution of $v$ for $B$ and not for $A$.
+Similarly, $D_{var_x}$ denotes the set of designs where difference is observed only across $A$.
 Finally, $D_{var_{all}}$ denotes those designs for which difference is observed across both $A$ and $B$.
@@
 of $wpd$ is obtained for each of the panels.
-This design corresponds to $D_{null}$ as each combination of categories in a panel are drawn from the same distribution.
-Furthermore, the data is simulated for each of the panels $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
+The measurement variable for each combination of categories in a panel are drawn from the same distribution and hence the design corresponds to $D_{null}$ .
+Furthermore, this entire method is repeated for each panels $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
 
 # Behavior of raw weighted distance measure
-
-Since the measure wpd is essentially set up to detect differences in distributions irrespective of underlying distribution, it would be ideal if it has minimal dependency on the type, location and scale of the initial distribution.
-To that end, some pre-processing of the data is preferred to bring it to the same scale, location and type.
-The Normal Score Transform or NQT has been applied in various fields of geo-statistics in order to make most asymmetrical distributed real world measured variables more treatable and normal-like.
 
@@
 
-## NQT works
+## Normal quantile transform
+
+Since the measure $wpd$ is essentially set up to detect "differences" in distributions irrespective of underlying distribution, it would be ideal if it has minimal dependency on the type, location and scale of the initial distribution.
+To that end, some data pre-processing through the Normal Score Transform (NQT) has been applied in order to make most asymmetrical distributed measured variables more normal-like.
+Figure \ref{fig:gamma-diff-wotrans} shows ridge plots of raw $wpd$ for a Gamma(0.5,1), Gamma(2,1) before NQT.
+It is observed that for the underlying distribution Gamma(2,1), location and scale of the distribution of wpd changes from top-left panel to bottom-right panel.
+Moreover, the location and scale of the distribution of $wpd$ fir different underlying distribution Gamma(0.5,1), Gamma(2,1).
+Figure \ref{fig:gamma-diff-quantrans} shows the the distributions of $wpd$ under same underlying distributions but after performing NQT.
+It is observed that within each panel, the distributions of the $wpd$ looks same, however, the distributions change from extreme top-left panel to bottom-right panels.
+This implies, NQT has atleast been able to bridge the gap in distribution of $wpd$ for different non-normal underlying distributions.
 
@@
 ```
-
-### with NQT
 

### 2021-05-04 paper/paper-supplementary.Rmd
supplementary section tuning paramter sim study update

@@
 
-# Simulation design
+# Behavior of raw weighted distance measure
+
+## Tuning parameter
+
+How does the tuning parameter affects the value of $wpd$ under different designs?
+The tuning parameter is used to put relative weight-age to the difference in distributions within and between facets.
+So it is interesting to see how the value of $wpd$ changes for these two designs.
+
+### Simulation design
+
+Observations are generated from Normal(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20\}$. 
+Let $\omega = \{1, 2, \dots, 10\}$ denotes the variable denoting the increment in mean of the distribution.
+The values of lambda ranges from ${0.1, 0.2, \dots, 0.9}$.
+Two designs are considered $D_{var_x}$ and $D_{var_f}$ and the values of $wpd$ is being computed for all these different values of the considered variable.
+
+### Results
+
+Figure \ref{fig:tuning-oneomega} shows how the value of $wpd$ changes for $\lambda = {0.1, 0.2, \dots, 0.9}$ for the two different designs $D_{var_x}$ and $D_{var_f}$ for two values of increment in mean $\omega = {1, 8}$.
+For a lower value of $\omega$, the two designs intersect at $\lambda > 0.7$ and for a higher $\omega$, the two designs intersect at $\lambda =  0.5$.
+The value of $wpd$ increases with $\lambda$ for $D_{var_x}$ and decreases with increasing $\lambda$ for 
+$D_{var_f}$.
+Figure \ref{fig:tuning-parameter-inter} shows the value of $\lambda$ for which the two designs intersect across different values of $\omega$.
+It can be observed that as the value of $\omega$ ($\omega > 4$) increase, the value of $\lambda$ at which the two designs intersect converge is $\lambda = 0.5$.
+
+```{r tuning-oneomega, fig.caption = "WPD from two designs are plotted for different values of lambda for different x and facet categories.
+For omega = 1, the designs intersect for 0.6<lamba<=0.75, whereas for higher omega, design intersects at lambda = 0.5"}
+knitr::include_graphics(here::here("simulations/tuning_param/figs/fixed_omega.png"))
+```
+```{r tuning-parameter-inter, fig.cap ="For most panels it is observed that the most common value of the tuning paramter for which the designs interact is 0.5, which implies any value greater than 0.5 could be chosen to up-weigh the within-facet distances and down-weigh the between-facet distances for most sitatuions."}
+knitr::include_graphics(here::here("simulations/tuning_param/figs/intersection_plot.png"))
+```
+
+# Normalization
+
+## Simulation design
 
@@
 
-# Behavior of raw weighted distance measure
-
-Following the work of Krzysztofowicz (1997) the empirical NQT involves the following steps:
-1. Sort the sample of measured variable $X$ from the smallest to the largest observation $x_{(1)},\dots, x_{(i)}, .., x_{(n)}$.
-2. Estimate the cumulative probabilities $p_{(1)},\dots, p_{(i)}, .., p_{(n)}$.
-using a plotting position like $i/(n + 1)$ such that $p_{(i)} = P(X \leq x_{(i)})$.
-3. Transforming each observation $x_(i)$ of $X$ into observation $y(i) = Q^{-1}(p(i))$ of the standard normal variate $Y$ , with $Q$ denoting the standard normal distribution and
-$Q^{-1}$ its inverse, applying discrete mapping.
-
-Firstly, we show that NQT works to make the distribution within each panel same. Next, we study the distribution of $wpd$ for different $nx$ and $nfacet$ in various ways.
-
-## Normal quantile transform
+## Different underlying distributions
 
@@
 It is observed that for the underlying distribution Gamma(2,1), location and scale of the distribution of wpd changes from top-left panel to bottom-right panel.
-Moreover, the location and scale of the distribution of $wpd$ fir different underlying distribution Gamma(0.5,1), Gamma(2,1).
+Moreover, the location and scale of the distribution of $wpd$ for different underlying distribution Gamma(0.5,1), Gamma(2,1).
 Figure \ref{fig:gamma-diff-quantrans} shows the the distributions of $wpd$ under same underlying distributions but after performing NQT.
 It is observed that within each panel, the distributions of the $wpd$ looks same, however, the distributions change from extreme top-left panel to bottom-right panels.
+Similar observations could be made in Figure \ref{fig:normal-diff-quantrans} for different underlying normal distributions  N(0,1), N(5,1) and N(0,5).
 This implies, NQT has atleast been able to bridge the gap in distribution of $wpd$ for different non-normal underlying distributions.
@@
 
-## By distribution
-
 ```{r normal-diff-quantrans, fig.cap = "Ridge plots of raw wpd is shown for N(0,1), N(5,1) and N(0,5) distribution.
@@
 ```
+## Different number of comparisons
 
-## By category levels
+# Location and scale
+
+Next, we study the distribution of $wpd$ for different $nx$ and $nfacet$ in various ways.
 
@@
 
-## Tuning parameter
+<!-- Following the work of Krzysztofowicz (1997) the empirical NQT involves the following steps: -->
+<!-- 1. Sort the sample of measured variable $X$ from the smallest to the largest observation $x_{(1)},\dots, x_{(i)}, .., x_{(n)}$. -->
+<!-- 2. Estimate the cumulative probabilities $p_{(1)},\dots, p_{(i)}, .., p_{(n)}$. -->
+<!-- using a plotting position like $i/(n + 1)$ such that $p_{(i)} = P(X \leq x_{(i)})$. -->
+<!-- 3. Transforming each observation $x_(i)$ of $X$ into observation $y(i) = Q^{-1}(p(i))$ of the standard normal variate $Y$ , with $Q$ denoting the standard normal distribution and -->
+<!-- $Q^{-1}$ its inverse, applying discrete mapping. -->
 
-```{r tuning-oneomega, fig.caption = "WPD from two designs are plotted for different values of lambda for different x and facet categories.
-For omega = 1, the designs intersect for 0.6<lamba<=0.75, whereas for higher omega, design intersects at lambda = 0.5"}
-knitr::include_graphics(here::here("simulations/tuning_param/figs/fixed_omega.png"))
-```
-
-```{r tuning-parameter-inter, fig.cap ="For most panels it is observed that the most common value of the tuning paramter for which the designs interact is 0.5, which implies any value greater than 0.5 could be chosen to up-weigh the within-facet distances and down-weigh the between-facet distances for most sitatuions."}
-knitr::include_graphics(here::here("simulations/tuning_param/figs/intersection_plot.png"))
-```
+<!-- Firstly, we show that NQT works to make the distribution within each panel same. . -->
 

### 2021-05-04 paper/paper-supplementary.Rmd
structure revisited

@@
 
-Appendix A recalls the necessary notations and
+<!-- Appendix A recalls the necessary notations and  -->
 
@@
 
-# Location and scale
-
 Next, we study the distribution of $wpd$ for different $nx$ and $nfacet$ in various ways.
@@
 
-## Increment
-
-# Behavior of normalised distance measure
+# Normalised distance measure
 
@@
 # Ranking and selecting harmonies
+
+## Simulation design
+
+Observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = \{3, 7, 14\}$ and $nfacet = \{2, 9, 10\}$.
+The panel $(3, 2), (7,9), (14, 10)$ are considered to have design $D_{null}$.
+The panels $(7, 2), (14, 9)$ have design of the form $D_{var_f}$.
+$(14, 2), (3, 10)$ have design of the form $D_{var_x}$ and the rest are under $D_{var_{null}}$.
+We generate only one data set for which all these designs were simulated and consider this as the original data set.
+We generate $200$ repetitions of this experiment with different seeds and compute the proportion of times a panel is rejected when it is under $D_{null}$.
+We also compute the proportion of times a panel is rejected when it actually belongs to a non-null design.
+The first proportion is desired to be as small as possible and a higher value of the later is expected.
+Also, these would constitute to be the estimated size and power of the test.
+
+## Results

### 2021-05-05 paper/paper-supplementary.Rmd
updating tuning paramter section

@@
 Let $v = \{v_t: t = 0, 1, 2, \dots, T-1\}$ be a continuous measured variable observed across $T$ time points.
-Let the four elementary designs be $D_{null}$ where there is no difference in distribution of $v$ for $A$ or $B$, $D_{var_f}$ denotes the set of designs where there is difference in distribution of $v$ for $B$ and not for $A$.
+The pairwise distances between pairs ($a_jb_k,a_j'b_k'$) could be within-facets or within-facets a seen in Figure 4 of the main paper.
+Let the four elementary designs be $D_{null}$ where there is no pairwise difference in distribution of $v$ across $A$ or $B$, $D_{var_f}$ denotes the set of designs where there is difference in distribution of $v$ for $B$ and not for $A$.
 Similarly, $D_{var_x}$ denotes the set of designs where difference is observed only across $A$.
 Finally, $D_{var_{all}}$ denotes those designs for which difference is observed across both $A$ and $B$.
+The following method is deployed for generating different distributions across different combinations for non-null designs - suppose the distribution of the combination of first levels of x and facet category is $N(\mu,\sigma)$ and $\mu_{jk}$ denotes the mean of the combination $(a_jb_k)$, then $\mu_{j.} = \mu + j\omega$ (for design $D_{var_x}$) and $\mu_{.k} = \mu + k\omega$ (for design $D_{var_f}$).
+Table \ref{tab:explain-design} shows an example of how initial distributions are assigned in a panel with $nfacet = 3$ and $nx = 2$ for different designs using $\omega = 1$.
+
+```{r explain-design}
+sim_varx_normal = function(nx, nfacet, mean, sd, w)
+{
+  rep(dist_normal((mean + seq(0, nx-1, by  = 1)*w), sd), nfacet)
+}
+
+sim_varf_normal = function(nx, nfacet, mean, sd, w)
+{
+  rep(dist_normal((mean + seq(0, nfacet-1, by  = 1)*w), sd), each = nx)
+}
+  sim_varall_normal = function(nx, nfacet, mean, sd, w)
+  {
+    dist_normal((mean + seq(0, (nx*nfacet - 1), by  = 1)*w), sd)
+  }
+
+mean = 0
+sd = 1
+w = 1
+nx = 2
+nfacet = 3
+
+raw_levels = expand.grid(facet = c("$b_1$", "$b_2$", "$b_3$"),
+                         x = c("$a_1$", "$a_2$"))
+
+facet = rep(c("$b_1$", "$b_2$", "$b_3$"), each = nx)
+x =  rep(c("$a_1$", "$a_2$"), nfacet)
+
+vary_f <-  sim_varf_normal(nx, nfacet, mean, sd, w) %>% tibble()
+vary_x <-  sim_varx_normal(nx, nfacet, mean, sd, w) %>% tibble()
+vary_all <-  sim_varall_normal(nx, nfacet, mean, sd, w) %>% tibble()
+
+raw_table <- bind_cols(x = x, 
+                       facet = facet, 
+                       vary_f = vary_f, 
+                       vary_x = vary_x, 
+                       vary_all = vary_all) %>% 
+  tibble() 
+names(raw_table) = c("x", "facet", "$D_{var_f}$", "$D_{var_x}$", "$D_{var_{all}}$" )
+raw_table %>% 
+  kable(format = "latex",
+    booktabs = TRUE, 
+    escape = FALSE,
+    caption = "Simulation setup for a panel with 3 facet levels and 2 x-axis levels for different designs starting from an initial distribution N(0, 1) for the combination $(a_1, b_1)$.") %>% kable_styling()
+```
 
@@
 So it is interesting to see how the value of $wpd$ changes for these two designs.
+But the tuning parameter might have a different impact depending on the value of $\omega$ and different levels of x and facets.
+Hence, a simulation study is conducted to see the impact of $\omega$, $nx$, $nfacet$ and $\lambda$ together on the values of $nx$ and $nfacet$.
 
@@
 ```
+
+## Number of comparison
 

### 2021-05-05 paper/paper-supplementary.Rmd
structure update

@@
 
-## Different underlying distributions
+## Underlying distributions
 
@@
 ```
-## Different number of comparisons
+## Number of comparisons
 
@@
 
-# Normalised distance measure
-
 ## sample size

### 2021-05-11 paper/main.Rmd
separating codes from text

@@
 ---
-title: A new metric for automatic discovery of periodic patterns in time series
+title: A new metric for automatic data visualization for distributional difference in time series
 
@@
 library(knitr)
-library(tidyverse)
-library(lubridate)
-library(lvplot)
-#library(ggridges)
-library(viridis)
-library(tsibble)
-library(gravitas)
-library(ggpubr)
-library(readr)
-library(kableExtra)
-library(distributional)
-library(ggplot2)
-library(sugrrants)
-library(here)
-library(ggplot2)
-library(patchwork)
-
 opts_chunk$set(
@@
 #                                                     read_chunk('main.R')
-here::here()
 #knitr::read_chunk(here::here("paper/R/", "null_distribution.R"))
@@
 # loadd()
+```
+
+```{r external, include = FALSE, cache = FALSE}
+read_chunk("paper/scripts/main.R")
+```
+
+```{r load}
 ```
@@
 For example, there is more going on in terms of peaks and troughs in id 2 compared to id 4, but it is not clear which all periodic patterns are dominant and if it differs between households."}
-elec <- read_rds(here("paper/data/elec.rds")) %>% 
-  filter(date >= ymd("20180101"), date < ymd("20180701"))
-rdbl <- c("Weekday" = "#d7191c", "Weekend" = "#2c7bb6")
-
-elec <- elec %>% 
-  mutate(
-    wday = wday(date, label = TRUE, week_start = 1),
-    weekday = if_else(wday %in% c("Sat", "Sun"), "Weekend", "Weekday")
-  )
-p_cal_elec <- elec %>% 
-  filter(id %in% c(2, 4)) %>% 
-  frame_calendar(x = time, y = kwh, date = date, nrow = 1) %>% 
-    ggplot(aes(x = .time, y = .kwh, group = date)) +
-    geom_line(aes(colour = as.factor(id)), size = 0.5) +
-    scale_colour_brewer(name = "", palette = "Dark2", direction = 1) +
-    facet_grid(id ~ ., labeller = label_both) +
-    theme(legend.position = "bottom")
-prettify(p_cal_elec, size = 2.5, label.padding = unit(0.1, "lines"))
+
 ```
@@
 
-id2_tsibble <- elec %>% 
-   filter(id == 2) %>% 
-   as_tsibble(index = date_time)
-
-id4_tsibble <- elec %>% 
-   filter(id == 4) %>% 
-   as_tsibble(index = date_time)
-
-# hour-of-day and month-of-year (important pair) id2's behavior across different hours of the day very different across months, but for id4 behavior across different hours of the day is not likely a function of month.
-p1 <- id2_tsibble %>%
+```
+
+```{r}
+id2_tsibble %>%
+  create_gran("month_year") %>%
    prob_plot("month_year",
@@
   scale_colour_brewer(name = "", palette = "PiYG")
-
-p2 <- id4_tsibble %>%
-   prob_plot("month_year",
-             "hour_day",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = TRUE,
-             quantile_prob = c(0.1, 0.25,0.5,0.75, 0.9)) + 
-  ggtitle("a") + theme(
-        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
-
-p3 <- id2_tsibble %>%
-  create_gran("week_month") %>% 
-  filter(week_month != 5) %>% 
-   prob_plot("wknd_wday",
-             "week_month",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = FALSE,
-             quantile_prob = c(0.25,0.5,0.75)) +
-   ggtitle("") +
-
-        theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
-
-p4 <- id4_tsibble %>%
-    create_gran("week_month") %>% 
-  filter(week_month != 5) %>% 
-   prob_plot("wknd_wday",
-             "week_month",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = FALSE,
-             quantile_prob = c(0.25,0.5,0.75)) +
-  ggtitle("b") +  #+ scale_x_discrete(breaks = seq(0, 23, 4)) + 
-theme(
-        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
-
-```
-
-```{r}
-id2_tsibble %>%
-  create_gran("month_year") %>% 
-  ggplot() +
-  geom_lv(aes(x = month_year, y = kwh))
-
-   prob_plot("month_year",
-             "hour_day",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = TRUE,
-             quantile_prob = c(0.1, 0.25,0.5,0.75, 0.9)) +
-  ggtitle("") + theme(
-        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + 
-  scale_colour_brewer(name = "", palette = "PiYG")
 ```
@@
 Energy consumption for id2 changes across both granularities, whereas for id4 daily pattern stays same irrespective of the months."}
-ggpubr::ggarrange(p1, p2, ncol = 2)
 ```
@@
 ```{r id4, fig.cap = "something2", eval = FALSE}
-ggpubr::ggarrange(p3, p4, ncol = 2)
+
 ```
@@
 
-sim_varall_normal <- function(nx, nfacet, mean, sd, w) {
-  dist_normal((mean + seq(0,
-    (nx *
-      nfacet - 1),
-    by = 1
-  ) * w), sd)
-}
-sim_panel_varall <- sim_panel(
-  nx = 2, nfacet = 3,
-  ntimes = 500,
-  sim_dist = sim_varall_normal(2, 3, 5, 10, 5)
-) %>% unnest(data)
-
-p_varall <- sim_panel_varall %>%
-  rename("facet level" = "id_facet" ) %>% 
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + 
-  facet_wrap(~`facet level`,labeller = "label_both") + 
-  geom_boxplot() +
-  ggtitle("") +
-  xlab("x level") +
-  ylab("")
-
-sim_varx_normal <- function(nx, nfacet, mean, sd, w) {
-   rep(dist_normal((mean + seq(0, nx - 1, by = 1) * w), sd), nfacet)
- }
-
-sim_panel_varx <- sim_panel(
-   nx = 2, nfacet = 3,
-   ntimes = 500,
-   sim_dist = sim_varx_normal(2, 3, 5, 10, 5)
- ) %>% unnest(data)
-
-p_varx <- sim_panel_varx %>%
-  rename("facet level" = "id_facet" ) %>% 
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + 
-  facet_wrap(~`facet level`,labeller = "label_both") + 
-  ggtitle("") +
-  geom_boxplot() +
-  xlab("x level") +
-  ylab("simulated response")
-
-sim_varf_normal <- function(nx, nfacet, mean, sd, w) {
-  rep(dist_normal((mean + seq(0, nfacet - 1, by = 1) * w), sd), each = nx)
-}
-
-sim_panel_varf <- sim_panel(
-  nx = 2, nfacet = 3,
-  ntimes = 500,
-  sim_dist = sim_varf_normal(2, 3, 5, 10, 5)
-) %>% unnest(data)
-
-p_varf <- sim_panel_varf %>%
-  rename("facet level" = "id_facet" ) %>% 
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) +
-  facet_wrap(~`facet level`,labeller = "label_both") + 
-  geom_boxplot() +
-  ggtitle("") +
-  xlab("x level") +
-  ylab("")
-
-sim_panel_null <- sim_panel(
-   nx = 2,
-   nfacet = 3,
-   ntimes = 500,
-   sim_dist = distributional
-   ::dist_normal(5, 10)
-) %>% unnest(c(data))
-
-set.seed(9999)
-
-p_null <- sim_panel_null %>%
-  rename("facet level" = "id_facet" ) %>% 
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) +
-  facet_wrap(~`facet level`,labeller = "label_both") +
-  geom_boxplot() +
-  ggtitle("") +
-  xlab("x level") +
-  ylab("simulated response")
-
-ggpubr::ggarrange(p_null, p_varf,  p_varx, p_varall, nrow = 2, ncol = 2,
-                  common.legend = TRUE,
-                  labels = c("a", "b", "c", "d"))
-
 ```
@@
 
-```{r}
-d1 <- tibble (variable = c("nx", "nfacet", "$N_C$", "$H_{N_C}$", "$lambda$", "$omega$", "$wpd$","$nperm$", "$nsim$"),  description = c("number of x categories", "number of facet categories","number of cyclic granularities", "set of harmonies", "tuning parameter", "mean increment", "raw distance measure", "number of permutations for threshold/normalization", "number of simulations"))
-
-d2 <- tibble(variable =  c("$wpd_{norm}$", 
-                           "$wpd_{threshold}$",
-                           "$D_{null}$",
-                           "$D_{var_f}$", 
-                           "$D_{var_x}$",
-                           "$D_{var_{all}}$"), 
-             description = c("normalized distance measure",
-                             "threshold for significance",
-                             "null design",
-                             "design with varying facets only", 
-                             "design with varying x only", 
-                             "design with varying both facets and x"))
-
-d <- bind_rows(d1, d2)
-knitr::kable(d, format = "markdown", escape = FALSE, caption = "Nomenclature table")
+```{r notations}
 
@@
 Between-facet distances are distances between different facet levels for the same x-axis category, for example, distances between {($a_1$,$b_1$) and ($a_1$, $b_2$)} or {($a_1$,$b_1$) and ($a_1$, $b_3$)}."}
-knitr::include_graphics(here::here("paper/Figs/dist_explain.png"))
+
 ```
@@
 This is not desirable since under null design, the distribution of the distance measure is not expected to capture any differences."}
-G21 <- read_rds("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds")
-
-G21 %>% 
-  ggplot(aes(x = value)) + 
-  geom_density(fill = "blue") +
-  facet_grid(nx~nfacet,
-             labeller = "label_both") + 
-  scale_x_continuous(breaks = scales::breaks_extended(3)) + 
-  xlab("wpd")
+
 ```
@@
 Thus, the measure will have higher values for higher levels in $nx$ or $nfacet$."}
-G21 %>% 
-  ggplot(aes(x=nx*nfacet, y = value)) +
-  geom_point(alpha = 0.5, size = 0.5) + stat_summary(fun=median, geom="line", aes(group=1), color = "blue") + xlab("nx*nfacet") + ylab("wpd")
-
 ```
@@
 Both shape and scale of the distributions are now similar for different panels under the null design."}
-G21_norm <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_Gamma21.rds"))
-
-G21_norm %>% 
-  ggplot(aes(x = value)) + 
-  geom_density(fill = "blue") +
-  facet_grid(nx~nfacet,
-             labeller = "label_both") + 
-  scale_x_continuous(breaks = scales::breaks_extended(3)) + 
-  xlab("wpd normalised using permutation approach")
 ```
@@
 ```{r linear-model, message=FALSE}
-G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds"))
-
-G21_median <- G21 %>% 
-  group_by(nx*nfacet) %>% 
-  summarise(actual = median(value))
-
-# fit model median to log(nx*nfacet)
-fit_lm2 <- lm(actual ~ log(`nx * nfacet`) , data = G21_median)
-
-broom::tidy(fit_lm2) %>% kable(caption = "Results of linear model to capture the relationship between wpd and number of comparisons.")
+
 ```
@@
 Further, by design they are independent of the $nx*nfacet$ and hence could be a potential candidate for $wpd_norm$."}
-
-intercept <- fit_lm2$coefficients[1]
-slope <- fit_lm2$coefficients[2]
-
-G21 %>% 
-  ggplot(aes(x=log(nx*nfacet), y = (value - slope*log(nx*nfacet)))) +
-  geom_point(alpha = 0.5, size = 0.5) + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
-  ylab("wpd normalised using linear modelling approach")
 ```
@@
 
-```{r wpd-glm-horizontal, echo = FALSE, message=FALSE, fig.caption = "$wpd_{glm}$ is plotted against log(nx*nfacet) and this transformation causes the median of $wpd_{glm}$ to have no relationship with log(nx*nfacet)"}
-
-G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds"))
-
-G21_median <- G21 %>% 
-  group_by(nx*nfacet) %>% 
-  summarise(actual = median(value))
-
-glm_fit <- glm(actual ~ log(`nx * nfacet`),
-              family = Gamma(link = "inverse"),
-              data = G21_median)
-
-intercept <- glm_fit$coefficients[1]
-slope <- glm_fit$coefficients[2]
-
-G21_sd  = G21 %>% 
-    mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
-    )
-    )
-    ))
-
-scale_fac <- 1/G21_sd$wpd_glm %>% sd()
-
-# checking the fit of the residuals from glm fit
-
-# fitted_glm <- fitted(glm_fit, type = "response")
-# residuals <- residuals.glm(glm_fit, type = "response")
-# hist(residuals)
-
-#h = augment(glm_fit)
-# ggplot(h) +
-#   geom_histogram(aes(x = .resid))
-
-# residual <- G21_median$actual  - fitted_glm
-# 
-# hist(residual)
-
-G21 %>% 
-  ggplot(aes(x=log(nx*nfacet),
-             y = (value - (1/(intercept + slope*log(nx*nfacet)
-                    )
-                    )
-             )
-  )
-  ) +
-  geom_point(alpha = 0.5, size = 0.5) + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
-  ylab("wpd_glm = wpd - 1/(a  + b*log(nx*nfacet))")
-```
-
 ```{r glm-tab}
@@
 
-G21_glm <- G21 %>% 
-  mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
-                    )
-                    )
-             ),
-         wpd_glm_scaled = ((wpd_glm*320)))
-
-#G21_glm$wpd_glm_scaled %>% sd()
-
-G21_glm %>% 
-  ggplot() +
-  geom_density(aes(x = wpd_glm), 
-                   fill = "blue") +
-  facet_grid(nx~nfacet,
-             labeller = "label_both") +
-  theme(legend.position = "bottom") 
 ```
@@
 The distribution looks symmetric and looks like normal except in the tails."}
-hist <- ggplot(G21_glm) +
-  geom_histogram(aes(x = wpd_glm_scaled)) +
-  ggtitle("a") + xlab("transformed wpd using glm approach")
-
-p <- ggplot(G21_glm, aes(sample = wpd_glm_scaled))
-qqplot <-  p + geom_qq() + geom_qq_line() + coord_fixed(ratio = 4/5) +
-  ggtitle("b")
-
-# G21_glm <- G21 %>% 
-#     mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
-#     )
-#     )
-#     ),
-#     wpd_glm_scaled = 300*(wpd_glm))
-
- # G21_glm$wpd_glm_scaled %>% 
- #   range()
-hist + qqplot
+
 ```
@@
 
-G21_permutation <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds")) %>%
-  rename("wpd_permutation" = "value")
-
-# G21_model_data <- G21 %>%
-#   mutate(model =
-#            ((1/value)
-#                   - intercept -
-#                     slope*log(nx*nfacet))/slope) %>%
-#   mutate(model_trans =
-#            (model - mean(model))/sd(model))
-
-# G21_model_data$model %>% summary()
-
-G21_all_data <- G21_permutation %>% 
-  # left_join(G21_lm, by = c("nx", "nfacet", "perm_id")) %>% 
-  left_join(G21_glm, by = c("nx", "nfacet", "perm_id")) %>% 
-  pivot_longer(cols = c(3, 7),
-               names_to = "type_estimate",
-               values_to = "value_estimate")
-G21_all_data$type_estimate = factor(G21_all_data$type_estimate , levels = c( "wpd_permutation", "wpd_glm_scaled"))
-
-G21_all_data %>% 
-  filter(type_estimate %in% c("wpd_glm_scaled", "wpd_permutation")) %>% 
-  ggplot() +
-  geom_density(aes(x = value_estimate, 
-                   fill = type_estimate), alpha = 0.5) +
-  facet_grid(nx~nfacet,
-             labeller = "label_both") +
-  theme(legend.position = "bottom") +
-  scale_fill_manual(values = c( "#D55E00", "#0072B2")) +
-  xlab("wpd_norm2") +
-  scale_x_continuous(breaks = c(-5, -3, 0, 3, 5))
-
-# G21_all_data %>% 
-#   filter(type_estimate %in% c("wpd_permutation", "wpd_glm")) %>% 
-#   ggplot() +
-#   geom_density(aes(x = value_estimate, 
-#                    fill = type_estimate), 
-#                alpha = 0.7) +
-#   facet_grid(nx~nfacet,
-#              labeller = "label_both") +
-#   theme(legend.position = "bottom") +
-#   scale_fill_manual(values = c("#CC79A7", "#0072B2")) +
-#   xlab("wpd_norm2")
-
-# are scales same
-# 
-# G21_model_data %>%
-#   group_by(nx, nfacet) %>% 
-#   summarize(sd_model = sd(model))
-#   
-# G21_all_data %>%
-#   filter(type_estimate == c("perm_trans")) %>% 
-#   select(value_estimate) %>% 
-#   range()
-# 
-# G21_all_data %>%
-#   filter(type_estimate == c("wpd_glm_scaled")) %>% 
-#   select(value_estimate) %>% 
-#   range()
 ```
@@
 
-sim_varall_normal <- function(nx, nfacet, mean, sd, w) {
-  dist_normal((mean + seq(0,
-    (nx *
-      nfacet - 1),
-    by = 1
-  ) * w), sd)
-}
-sim_panel_varall <- sim_panel(
-  nx = 2, nfacet = 3,
-  ntimes = 500,
-  sim_dist = sim_varall_normal(2, 3, 0, 1, 10)
-) %>% unnest(data)
-
-set.seed(9999)
-varall <- compute_pairwise_norm(sim_panel_varall, 
-                           gran_x = "id_x",
-                           gran_facet = "id_facet",
-                           response = sim_data, 
-                           nperm = 200
-)
-
-# plot
-p_varall <- sim_panel_varall %>%
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
-  ggtitle(paste("d", round(varall, 2))) + xlab("x level")
 ```
@@
 ```{r varx-new}
-sim_varx_normal <- function(nx, nfacet, mean, sd, w) {
-   rep(dist_normal((mean + seq(0, nx - 1, by = 1) * w), sd), nfacet)
- }
-
-sim_panel_varx <- sim_panel(
-   nx = 2, nfacet = 3,
-   ntimes = 500,
-   sim_dist = sim_varx_normal(2, 3, 0, 1, 10)
- ) %>% unnest(data)
-
-set.seed(9999)
-varx <- compute_pairwise_norm(sim_panel_varx, 
-                           gran_x = "id_x",
-                           gran_facet = "id_facet",
-                           response = sim_data, 
-                           nperm = 200
-)
-
-# plot
-p_varx <- sim_panel_varx %>%
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
-    ggtitle(paste("c", round(varx, 2))) + xlab("x level")
+
 ```
@@
 ```{r varf-new}
-sim_varf_normal <- function(nx, nfacet, mean, sd, w) {
-  rep(dist_normal((mean + seq(0, nfacet - 1, by = 1) * w), sd), each = nx)
-}
-sim_panel_varf <- sim_panel(
-  nx = 2, nfacet = 3,
-  ntimes = 500,
-  sim_dist = sim_varf_normal(2, 3, 0, 1, 10)
-) %>% unnest(data)
-
-set.seed(9999)
-varf <- compute_pairwise_norm(sim_panel_varf, 
-                           gran_x = "id_x",
-                           gran_facet = "id_facet",
-                           response = sim_data, 
-                           nperm = 200
-)
-
-p_varf <- sim_panel_varf %>%
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
-    ggtitle(paste("b", round(varf, 2))) + xlab("x level")
 ```
@@
 ```{r null-new}
-sim_panel_null <- sim_panel(
-   nx = 2,
-   nfacet = 3,
-   ntimes = 500,
-   sim_dist = distributional
-   ::dist_normal(0, 1)
-) %>% unnest(c(data))
-
-set.seed(9999)
-
-null <- compute_pairwise_norm(sim_panel_null, 
-                           gran_x = "id_x",
-                           gran_facet = "id_facet",
-                           response = sim_data, 
-                           nperm = 200
-)
-
-p_null <- sim_panel_null %>%
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
-    ggtitle(paste("a", round(null, 2))) + xlab("x level") 
+
 ```
@@
 Moreover, the relative difference is interesting as c is closer to d than b, since the differences between x categories are up-weighed by design."}
-library(patchwork)
-(p_null + p_varf)/(p_varx + p_varall)
+
 ```

### 2021-05-19 paper/main-old.Rmd
fixed wrong plots

--- 2021-05-11 paper/main.Rmd
@@
 
-```{r glm-tab}
+```{r glm-tab,eval=FALSE}
 broom::tidy(glm_fit) %>% kable(caption = "Results of generalised linear model to capture the relationship between wpd and number of comparisons.")

### 2021-05-19 paper/main.Rmd
fig ref fix

@@
 ---
-title: A new metric for automatic data visualization for distributional difference in time series
+title: Detecting distributional differences between temporal granularities for exploratory time series analysis
 
@@
 - periodicities
-- time granularities
 - cyclic granularities
@@
   \def\mod{~\text{mod}~}
-  \newtheorem{definition}{Definition}
   \usepackage{mathptmx}
   \usepackage{caption}
+  \usepackage{longtable}
   \DeclareCaptionStyle{italic}{labelfont={bf},textfont={it},labelsep=colon}
@@
 Tukey (Tukey 1965) involves many iterations of finding structures and patterns that allow the data to be informative.
-With temporal data available at finer scales, exploring periodicity and their relationships can become overwhelming with so many possible cyclic temporal granularities [@Gupta2020-vo] to explore.
-\noindent Take the example of the calendar display of electricity smart meter data in Figure (\ref{fig:calendar-elec}) used in @wang2020calendar for four households in Melbourne, Australia.
-The authors show how hour-of-the-day interact with weekdays and weekends and then move on to use calendar display to show daily schedules.
-The calendar display has several components in it, which helps us to look at energy consumption across hour-of-the-day, day-of-the-week, week-of-the-month, and month-of-the-year at once.
-Some interaction of these cyclic granularities, for example, how  day-of-week relates to month-of-year, could also be interpreted from this display.
-This is a great way for having an overview of energy consumption.
-However, if one wants to understand the periodicities in energy behavior and how the periodicities interact in greater detail, it is not easy to comprehend the interactions of some periodicities' from this display, due to the combination of linear and cyclic representation of time.
-For example, this display might not be the best to understand how hour-of-the-day or month-of-year varies across week-of-the-month as well as with each other.
-Furthermore, it is not clear what all interactions of cyclic granularities should be read from this display as there could be many combinations that one can look at.
-Moreover, _"calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions"_ (@Gupta2020-vo) and could include other cyclic granularities like hour-of-week or day-of-fortnight, which could potentially become useful depending on the context.
-Possible areas where it is useful are monitoring heart rates which could record number of heartbeats every minute or analyze web search data for which data is available for a temporal scale as fine as second.
+With temporal data available at finer scales, exploring time series data can become overwhelming with so many possible cyclic temporal granularities [@Gupta2020-vo], which are temporal deconstructions that represent cyclic repetitions in time, e.g.
+hour-of-day, day-of-month, or any public holidays.
+These granularities form ordered (for eg.
+day-of-week where Tue is always followed by Wed, which again is followed by Thu and so on) or unordered categorical variables.
+Therefore, exploring univariate time series data amounts to exploring the distribution of the measured variable across different categories of the cyclic granularities.
+\noindent Take the example of the electricity smart meter data used in @wang2020calendar for four households in Melbourne, Australia.
+Figure \ref{fig:onegran} shows the distribution of energy usage of one household (id 2) across cyclic granularity a) hour-of-day and b) month-of-year.
+Potentially many such displays could be drawn across day-of-week, day-of-month, weekday/weekend, or any other chosen cyclic granularities of interest.
+However, all of them would not be interesting to discern important patterns in the energy usage.
+Only those displays, which have "significant" distributional differences between categories of the cyclic granularity would be informative and consequently, the corresponding cyclic granularity can be tagged as a "significant" one.
 
@@
 
+```{r onegran, fig.cap="something"}
+```
+
+<!-- comparing one and two grans for one households -->
+\noindent Exploring the distribution of the measured variable across two cyclic granularities tend to provide more detailed information on its structure.
+Figure \ref{fig:id2}(a) shows that energy consumption is higher during the morning hours (5-8) when members in the household wake up and then again in the evening hours (17-20) possibly when members get back from work with maximum variation (large inter-quartile range) in behavior in the afternoon hours (12-16).
+Figure \ref{fig:id2}(b) shows the distribution of energy consumption across months January to June.
+The median and quartile deviation of energy usage in Jan and Feb are generally on a much higher side, possibly due to the usage of air conditioners (Jan, Feb are peak summer in Australia), however for other months (Mar-Jun, autumn and winter), the smaller median and quartile deviation indicate a more regular behavior.
+It also implies this household do not use as much heater as compared to air conditioner.
+A lot of households in Victoria use gas heating and hence the usage of heaters might not be reflected here.
+Figure \ref{fig:id2}a slice it down further by showing the usage distribution across hour-of-day conditional on month-of-year.
+It shows the hourly usage over a day do not remain across months.
+Unlike other months, the 75th and 90th percentile for all hours of the day in January are high, pretty close and are not characterized by a morning and evening peak.
+This implies usage of air conditioners is pretty common for this household.
+The household in Figure \ref{fig:id2}a has 90th percentile consumption higher in summer months relative to autumn or winter, but the 75th and 90th percentile are far apart in all months, implying that the second household resorts to air conditioning much less regularly than the first one.
+The differences seem to be more prominent across month-of-year (facets) than hour-of-day (x-axis) for this households, whereas they are prominent for both cyclic granularities for the first household.
+It could be immensely useful to make the transition from all potential displays to the ones that are informative across atleast one cyclic granularity.
+
+<!-- Moreover, the volatility in consumption are almost equal and high for all hours in Jan, whereas variability is most in the evening hours for other months.
+The distribution of consumption across different hours of the day look similar for Apr, May and Jun, characterized by a distinct morning, afternoon and evening peaks and higher variability in evening hours -->
+
+<!-- months Jan and Feb not only have a high median consumption, but also more variability, possibly due to the usage of air conditioning.
+The other months shows more consistent behavior with the energy consumption rising in May and June.
+-->
+
+<!-- what is the dimension of the problem -->
+\noindent The dimension of this problem, however, increases when considering two cyclic granularities.
+Let $N_C$ be the total number of cyclic granularities of interest.
+That essentially implies there are $^{N_C}P_2$ possible pairwise plots exhaustively, with one of the two cyclic granularities acting as the conditioning variable.
+This is large and overwhelming for human consumption.<!-- Scagnostics literature --> This problem is similar to Scagnostics (Scatterplot Diagnostics) by @tukey1988computer, which is used to identify meaningful patterns in large collections of scatterplots.
+Given a set of $v$ variables, there are $v(v-1)/2$ pairs of variables, and thus the same number of possible pairwise scatterplots.
+Therefore, even for small $v$, the number of scatterplots can be large, and scatterplot matrices (SPLOMs) could easily run out of pixels when presenting high-dimensional data.
+@Dang2014-tw and @wilkinson2005graph provides potential solutions to this, where few characterizations can be used to locate anomalies in density, shape, trend, and other features in the 2D point scatters.
+
+<!-- \ref{fig:id2} shows the distribution of energy consumption across hour-of-day conditional on month-of-year.
+\ref{fig:id2}(a) shows that energy consumption is higher during the morning hours when members in the household wake up and then again higher in the evening hours possibly when members are back from work with them showing maximum variable behavior in the afternoon hours.
+\ref{fig:id2}(b) shows the months Jan and Feb not only have a high median consumption, but also more variability, possibly due to the usage of air conditioning.
+The other months shows more consistent behavior with the energy consumption rising in May and June.
+\ref{fig:id2} adds to this information, by showing that hours in Jan do not necessarily follow the same pattern across the day (due to Holidays, people visiting).
+Moreover, the volatility in consumption are almost equal and high for all hours in Jan, whereas variability is most in the evening hours for other months.
+The distribution of consumption across different hours of the day look similar for Apr, May and Jun, characterized by a distinct morning, afternoon and evening peaks and higher variability in evening hours.
+-->
+
+<!-- # interaction for two households, importance could be across one -->
+
+<!-- Even when it is known which all interactions to look at, all of them would not be interesting and that too will vary across different households.  -->
+
+<!-- calendar plots -->
+<!-- The authors show how hour-of-the-day interact with weekdays and weekends and then move on to use calendar display to show daily schedules.
+The calendar display has several components in it, which helps us to look at energy consumption across hour-of-day, day-of-week, week-of-month, and month-of-year at once.
+Some interaction of these cyclic granularities, for example, how  day-of-week relates to month-of-year, could also be interpreted from this display.
+This is a great way for having an overview of energy consumption.
+However, if one wants to understand the repetitiveness in energy behavior and how they interact in greater detail, it is not easy to comprehend the interactions of all cyclic granularities from this display, due to the combination of linear and cyclic representation of time.
+For example, this display might not be the best to understand how hour-of-the-day or month-of-year varies across week-of-the-month as well as with each other.
+Furthermore, it is not clear what all interactions of cyclic granularities should be read from this display as there could be many combinations that one can look at.
+Moreover, there could be non-conventional cyclic granularities, which could potentially become useful depending on the context.
+-->
+
 <!-- context when it could be useful is monitoring heart rates.
@@
 
-```
-
-```{r}
-id2_tsibble %>%
-  create_gran("month_year") %>%
-   prob_plot("month_year",
-             "hour_day",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = TRUE,
-             quantile_prob = c(0.1, 0.25,0.5,0.75, 0.9)) +
-  ggtitle("") + theme(
-        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + 
-  scale_colour_brewer(name = "", palette = "PiYG")
 ```
@@
 ```
-
-Even when it is known which all interactions to look at, all of them would not be interesting and that too will vary across different households.
-For example, area distribution quantiles are plotted for household 2 and 4 in Figure \ref{fig:id2}a and \ref{fig:id2}b respectively across month-of-year on facets and hour-of-day on x-axis.
-For the first household, the 75th and 90th percentile for January and February are very close, implying that energy usage for these months are generally on a much higher side, possibly due to the usage of air conditioners (January and February are peak summer in Australia), however for other months (Autumn and winter), the difference between the percentiles are not high, implying this household do not use so much heater as compared to air conditioner.
-Also, a lot of households in Victoria use gas heating and hence the usage of heaters might not be reflected here.
-The energy consumption for household 2 is also higher in summer months relative to autumn or winter, but the 75th and 90th percentile are far apart in all months, implying that the second household resorts to air conditioners much less regularly than the first one.
-Moreover, the 75th percentile distribution does not follow the same pattern as 90th percentile for all months for the first household, whereas, the pattern looks pretty similar for all months for the second household.
-Difference in the energy consumption could vary both across month-of-year (facets) and hour-of-day (x-axis).
-For the first household, both these cyclic granularities would deem important.
-Although, it seems like energy consumption across hours of the day are not that different across different months for the second household or atleast differences seem to be more prominent across month-of-year (facets) than hour-of-day (x-axis).
-It could be immensely useful to make the transition from all possible ways to only ways that could potentially be informative.
 
@@
 
-<!-- what is the dimension of the problem -->
-The paper @Gupta2020-vo describes how we can compute all possible combinations of cyclic time granularities.
-Let $N_C$ be the total number of contextual circular, quasi-circular and aperiodic cyclic granularities that can originate from the underlying linear granularities.
-The graphical mapping is such that distributions of a numeric response variable is displayed across combinations of cyclic granularities, one placed at x-axis and the other on the facet.
-That essentially implies there are $^{N_C}P_2$ possible pairwise plots exhaustively, where each plot would display a pair of cyclic granularities.
-This is large and overwhelming for human consumption.<!-- Scagnostics literature --> This problem is similar to Scagnostics (Scatterplot Diagnostics) by @tukey1988computer, which is used to discern meaningful patterns in large collections of scatterplots.
-Given a set of $v$ variables, there are $v(v-1)/2$ pairs of variables, and thus the same number of possible pairwise scatterplots.
-Therefore, even for small $v$, the number of scatterplots can be large, and scatterplot matrices (SPLOMs) could easily run out of pixels when presenting high-dimensional data.
-@Dang2014-tw and @wilkinson2005graph provides potential solutions to this, where few characterizations help us to locate anomalies in density, shape, trend, and other features in the 2D point scatters.
-
 <!-- harmonies and why it is not enough -->
-This work is a natural extension of our work (@Gupta2020-vo), which narrows down the search from $^{N_C}P_2$ plots by identifying pairs of granularities that can be meaningfully examined together (a "harmony"), or when they cannot (a "clash").
+\noindent This work is a natural extension of our work that narrows down the search from $^{N_C}P_2$ plots by identifying pairs of granularities that can be meaningfully examined together (a "harmony"), or when they cannot (a "clash").
 However, even after excluding clashes, the list of harmonies left could be enormous for exhaustive exploration.
 Hence, there is a need to reduce the search even further by including only those harmonies which are informative enough.
-@inference and @Majumder2013-hb present some methods to quantify the strength of pattern and noise through visual inference, similar to numerical testing.
+@inference and @Majumder2013-hb present methods for statistical significance testing of visual findings using human cognition as the statistical tests.
+<!-- present some methods to quantify the strength of pattern and noise through visual inference, similar to numerical testing.
 But this is an evolving field as human cognition (which act as the statistical tests in visual inference) might vary across humans even for the same plots.
-In this paper, we build a new distance measure which could be used to detect automatically detect significant periodic patterns.
+--> In this paper, a new distance measure is introduced to enable visual findings that detect significant distributional differences between harmonies.
 
@@
 
- * introduce a new distance measure for quantifying periodic interactions, which allows for identification
+ * introduce a distance measure for detecting distributional difference in temporal granularities, which enables identification
 of patterns in the time series data;
- * device a framework for choosing a threshold, which results in detection of only significantly interesting
-periodic patterns;
- * show that the proposed distance metric could be used to rank the periodic patterns based on
-how well they capture the variation in the measured variable since they have been normalized for
-relevant parameters.
+
+ * devise a framework for choosing a threshold, which results in detection of only significantly interesting patterns;
+
+ * show that the proposed distance metric could be used to rank the interesting patterns based on how well they capture the variation in the measured variable since they have been normalized for relevant parameters.
 
@@
 
-# A distance measure for quantifying patterns in harmonies {#sec:computation-wpd}
-
-We are interested in assessing the structure of the measured variable across bivariate cyclic granularities.
-We propose a measure called Weighted Maximum Pairwise Distances (wpd) to quantify the structure in such a design.
-The principle employed towards this goal is explained through a simple example explained in Figure \ref{fig:null4by2}.
-Each of these figures have the same panel design with $2$ x-axis categories and $3$ facet levels.
-Figure \ref{fig:null4by2}a has all x categories drawn from N(5, 10) distribution for each facet.
+# A distance measure for distributional differences in harmonies {#sec:computation-wpd}
+
+We propose a measure called Weighted Pairwise Distances ($wpd$) to assess structure in the measured variable across two cyclic granularities.
+
+## Principle
+
+The principle behind the construction of $wpd$ is explained through a simple example explained in Figure \ref{fig:null4by2}.
+Each of these figures describes a panel with $2$ x-axis categories and $3$ facet levels, but with different designs.
+Figure \ref{fig:null4by2}a has all categories drawn from N(5, 10) distribution for each facet.
 It is not an interesting display particularly, as distributions do not vary across x-axis or facet categories.
-Figure \ref{fig:null4by2}b has x categories drawn from the same distribution within a facet but the mean has been incremented by $5$ units for every consecutive facets.
-Figure \ref{fig:null4by2}c exhibits an exact opposite situation where distribution between the x-axis categories within each facet is different but they are same across facets.
-For this situation, mean of only the x-axis categories are increased by $5$ units for each consecutive category.
-Figure \ref{fig:null4by2}d takes a step further by varying the distribution across both facet and x-axis categories.
-If the displays are to be ranked in order of importance from minimum to maximum, then an obvious choice would be placing a followed by b, c and then d.
-It might be argued that it is not clear if b should precede or succeed c in the ranking.
+Figure \ref{fig:null4by2}b has x categories drawn from the same distribution within a facet but the mean and sd incremented by $5$ units for every consecutive facets.
+Figure \ref{fig:null4by2}c exhibits an exact opposite situation where distribution between the x-axis categories within each facet is different but they are same across facets (mean by +5, sd by -2 for consecutive x categories).
+Figure \ref{fig:null4by2}d takes a step further by varying the distribution across both facet and x-axis categories (mean by +5 and sd by -1.5 for consecutive categories).
+If the panels are to be ranked in order of capturing maximum variation in the measured variable from minimum to maximum, then an obvious choice would be placing (a) followed by (b), (c) and then (d).
+It might be argued that it is not clear if (b) should precede or succeed (c) in the ranking.
 Gestalt theory suggests that when items are placed in close proximity, people assume that they are in the same group because they are close to one another and apart from other groups.
-Hence, displays that capture more variation within different categories in the same group would be important to bring out different patterns of the data.
-With this principle in mind, display b is considered less informative as compared to display c.
-Hence, with reference to the graphical design in @Gupta2020-vo, therefore the idea would be to rate a harmony pair higher if the variation between different levels of the x-axis variable is higher on an average across all levels of the facet variables.
-
-Intuitively, while finding a structure or measuring the strength of patterns in Figure \ref{fig:null4by2}, it makes sense to look for within-group and between-group variations.
+With this principle in mind, display (b) is considered less informative as compared to display (c) in emphasizing the distributional differences.
+The proposed measure $wpd$ is constructed in a way so that it could be used to rank panels of different designs as well as test if a design is interesting.
+This measure is an estimate of the maximum variation in the measured variable explained by the panel.
+A higher value of  $wpd$ would indicate that the panel is interesting to look at, whereas a lower value would indicate otherwise.
+
+<!-- To compute the maximum variation of the measured variable within each panel, the distributional differences need to be measured for both within-group and between-group categories.
+Moreover, a tuning parameter specifying the weightage given to within-facet or between-facet categories can help to choose between designs like \ref{fig:null4by2}b and c.
+The maximum of all these weighted differences serves as an estimate of the maximum variation in the panel and is taken as the value of $wpd$.
+-->
+
+<!-- Larger differences imply stronger patterns, whereas small difference would imply that the underlying structure is not changing within or between group. -->
+
+<!-- A distance measure aimed to capture the structure of the measured variable in designs like \ref{fig:null4by2}, should ideally estimate these within-group and between-group variations. -->
+
+<!-- \noindent Intuitively, while finding a structure or measuring the strength of patterns in Figure \ref{fig:null4by2}, it makes sense to look for within-group and between-group variations.
 Larger variation would imply stronger patterns, whereas small variation would imply the underlying structure is not changing within or between group.
-Thus, a distance measure aimed to capture this structure should ideally estimate these within-group and between-group variations.
+-->
+<!-- Thus, a distance measure aimed to capture this structure should ideally estimate these within-group and between-group variations.
 One of the potential ways to do this is to measure the distances between distributions of the continuous random variable measured within and between groups, weigh them basis if they are within or between groups and then take the maximum of those distances as an estimate of the maximum variation in the structure.
 This section starts with possible ways of characterizing distributions and computing distances between them and then describe in details how the measure $wpd$ is defined.
-This is similar to @ieee-irish where the authors compute the Jensen Shannon distance between two density estimates by computing percentiles and stresses the advantages to working with percentiles rather than the raw data directly in case of missing observations.
+-->
+
+<!-- This is similar to @ieee-irish where the authors compute the Jensen Shannon distance between two density estimates by computing percentiles and stresses the advantages to working with percentiles rather than the raw data directly in case of missing observations.
 Working with quantiles also ensure that unsynchronized time series could be handled.
+-->
+
+<!-- Hence, with reference to the graphical design in @Gupta2020-vo, therefore the idea would be to rate a harmony pair higher if the variation between different levels of the x-axis variable is higher on an average across all levels of the facet variables.
+-->
 
@@
 
+<!-- A "significant" cyclic granularity have at least two categories which are significantly different from each other.
+It does not tell you which categories are statistically significantly different from each other -->
+
 <!-- in the same group would be important to bring out different patterns of the data. -->
@@
 
-## Characterising distributions
+  <!-- Thus, by CLT, ${\chi^2}_{m} \tilde{} N(m, 2m)$, which would depend on the number of discretization used to approximate the continuous distribution.  -->
+  <!-- Then $b_n = 1-1/n$ quantile of the normal distribution and $a_n = 1/[n*\phi(b_n)]$ where $\phi$ is the normal density function. $n$ is the number of pairwise comparisons being made. -->
+
+<!-- The Jensen-Shanon distance between two probability distribution $p_1$ and $p_2$ is given by $$d = [D(p_1, r) + D(p_2, r)]/2 \quad where \quad r = (p_1 + p_2)/2$$ where, -->
+<!-- $$D(p_1,p_2) = \int^{\infty}_{-\infty}p_1(x)log\frac{p_1(x)}{p_2(x)}\,dx$$ is the Kullback-Leibler divergence between $p_1$ and $p_2$.   -->
+
+<!-- We call this measure of variation as  Median Maximum Pairwise Distances (MMPD). -->
+
+<!-- #### Distribution of Jensen-Shannon distances -->
+
+<!-- Jensen-Shannon distances (JSD) are distributed as chi-squared with $m$ df where we discretize the continuous distribution with $m$ discrete values.
+Taking sample percentiles to approximate the integral would mean taking $m = 99$.
+-->
+<!-- With large $m$, chi-squared is asymptotically normal by the CLT.
+Thus, by CLT, ${\chi^2}_{m} \tilde{} N(m, 2m)$, which would depend on the number of discretization used to approximate the continuous distribution.
+Then $b_n = 1-1/n$ quantile of the normal distribution and $a_n = 1/[n*\phi(b_n)]$ where $\phi$ is the normal density function.
+$n$ is the number of pairwise comparisons being made.
+-->
+
+## Computation
+
+The distance measure $wpd$ between two cyclic granularities $A$ and $B$ is aimed to capture structure and patterns by estimating the maximum variation of the measured variable within a panel.
+The computation of $wpd$
+involves characterizing distributions, computing distances between distributions, choosing a tuning parameter to specify the weightage given to within-facet or between-facet distances.
+Furthermore, the intended aim of $wpd$ is to capture differences in categories irrespective of the distribution from which the data is generated.
+Hence, as a pre-processing step, the raw data is normal quantile transformed (@Bogner2012-az) so that the quantiles of the transformed data follows a standard normal distribution.
+
+<!-- the distributional differences need to be measured for both within-group and between-group categories.
+Moreover, a tuning parameter specifying the weightage given to within-facet or between-facet categories can help to choose between designs like \ref{fig:null4by2}b and c.
+The maximum of all these weighted differences serves as an estimate of the maximum variation in the panel and is taken as the value of $wpd$.
+-->
+
+### Characterising distributions
 
 Multiple observations of $v$ correspond to the subset  $v_{jk} = \{s: A(s) = j, B(s) = k\}$.
-The number of observations and the structure might vary widely across subsets due to the structure of the calendar, missing observations or uneven locations of events in the time domain.
-Each $v_{jk}$'s $\forall j\in \{1, 2, \dots, J\}, k\in \{1, 2, \dots, K\}\}$ are assumed to be drawn from a continuous probability distribution and have certain characteristics.
-Often shape, central tendency, and variability are the common characteristics used to describe a distribution.
-Mean, median or mode are generally used to describe the center of the distribution, while range, standard deviation, quantiles, standard errors and confidence intervals are used to describe variability.
-Quantiles are chosen as a way to characterize distributions in this paper.
-
+The number of observations might vary widely across subsets due to the structure of the calendar, missing observations or uneven locations of events in the time domain.
+Quantiles of $v_{jk}$'s are chosen as a way to characterize distributions for the category $(a_j, b_k)$ in the paper $\forall j\in \{1, 2, \dots, J\}, k\in \{1, 2, \dots, K\}\}$.
 The quantile of a distribution with probability $p$ is defined as $Q(p)=F^{-1}(p) = inf\{x: F(x) >p\}$, $0<p< 1$ where $F(x)$ is the distribution function.
+There are two broad approaches to quantile estimation, viz, parametric and non-parametric.
+Sample quantiles (@Hyndman1996-ty) are used for estimating population quantiles in a non-parametric setup, which is desirable because of less rigid assumptions made about the nature of the underlying distribution of the data.
+The default quantile chosen in this paper is percentiles computed for $p = {0.01, 0.02, \dots, 0.99}$, where for example, the $99^{th}$ percentile would be the value corresponding to $p=0.99$ and hence 99% of the observations would lie below that.
+
+<!-- The benefit of using a non-parametric estimator is that there are less rigid assumptions made about the nature of the underlying distribution of the data.
+Sample quantiles could be used for estimating population quantiles in a non-parametric setup.
+describes the many ways of defining sample quantiles and recommends the use of median-unbiased estimator because of _desirable properties of a quantile estimator and can be defined independently of the underlying distribution._.
+-->
+
+<!-- in this paper. -->
+
+<!-- Each $v_{jk}$'s $\forall j\in \{1, 2, \dots, J\}, k\in \{1, 2, \dots, K\}\}$ are assumed to be drawn from a continuous probability distribution and have certain characteristics.
+Shape, central tendency, and variability are the common characteristics used to describe a distribution.
+-->
+
+<!-- Mean, median or mode are generally used to describe the center of the distribution, while range, standard deviation, quantiles, standard errors and confidence intervals are used to describe variability.
+-->
+
+<!-- The quantile of a distribution with probability $p$ is defined as $Q(p)=F^{-1}(p) = inf\{x: F(x) >p\}$, $0<p< 1$ where $F(x)$ is the distribution function.
 There are two broad approaches to quantile estimation, viz, parametric and non-parametric.
@@
 The default quantile chosen in this paper is percentiles computed for $p = {0.01, 0.02, \dots, 0.99}$, where for example, the $99^{th}$ percentile would be the value corresponding to $p=0.99$ and hence 99% of the observations would lie below that.
-
-## Distance between distributions
+-->
+
+### Distance between distributions
 
@@
 
-The most common divergence measure between distributions is the Kullback-Leibler (KL) divergence [@Kullback1951-jy] introduced by Solomon Kullback and Richard Leibler in 1951.
+Most common way to measure divergence between distributions is the Kullback-Leibler (KL) divergence [@Kullback1951-jy].
 The KL divergence denoted by $D(q_1||q_2)$ is a non-symmetric measure of the difference between two probability distributions $q_1$ and $q_2$ and is interpreted as the amount of information lost when $q_2$ is used to approximate $q_1$.
@@
 Other common measures of distance between distributions are Hellinger distance, total variation distance and Fisher information metric.
-
-In this paper, we propose to use the pairwise distances between the distributions of the measured variable through Jensen-Shannon distance (JSD), defined by,
+In this paper, the pairwise distances between the distributions of the measured variable are obtained through Jensen-Shannon distance (JSD), defined by,
 
@@
 
-  <!-- Thus, by CLT, ${\chi^2}_{m} \tilde{} N(m, 2m)$, which would depend on the number of discretization used to approximate the continuous distribution.  -->
-  <!-- Then $b_n = 1-1/n$ quantile of the normal distribution and $a_n = 1/[n*\phi(b_n)]$ where $\phi$ is the normal density function. $n$ is the number of pairwise comparisons being made. -->
-
-<!-- The Jensen-Shanon distance between two probability distribution $p_1$ and $p_2$ is given by $$d = [D(p_1, r) + D(p_2, r)]/2 \quad where \quad r = (p_1 + p_2)/2$$ where, -->
-<!-- $$D(p_1,p_2) = \int^{\infty}_{-\infty}p_1(x)log\frac{p_1(x)}{p_2(x)}\,dx$$ is the Kullback-Leibler divergence between $p_1$ and $p_2$.   -->
-
-<!-- We call this measure of variation as  Median Maximum Pairwise Distances (MMPD). -->
-
-<!-- #### Distribution of Jensen-Shannon distances -->
-
-<!-- Jensen-Shannon distances (JSD) are distributed as chi-squared with $m$ df where we discretize the continuous distribution with $m$ discrete values.
-Taking sample percentiles to approximate the integral would mean taking $m = 99$.
--->
-<!-- With large $m$, chi-squared is asymptotically normal by the CLT.
-Thus, by CLT, ${\chi^2}_{m} \tilde{} N(m, 2m)$, which would depend on the number of discretization used to approximate the continuous distribution.
-Then $b_n = 1-1/n$ quantile of the normal distribution and $a_n = 1/[n*\phi(b_n)]$ where $\phi$ is the normal density function.
-$n$ is the number of pairwise comparisons being made.
--->
-
-## Computation
-
-The distance measure $wpd$ between two cyclic granularities $A$ and $B$ is aimed to capture the strength of the structure by estimating the maximum within-group and between-group variations.
-Furthermore, the intended aim of $wpd$ is to capture differences in categories irrespective of the distribution from which the data is generated.
-Hence, as a pre-processing step,the raw data is normal quantile transformed (@Bogner2012-az) so that the quantiles of the transformed data follows a standard normal distribution.
-The steps employed for computing the distance measure is summarized as follows:
+### Within-facet and between-facet distances
+
+\noindent Pairwise distances could be within-facets or between-facets.
+Figure \ref{fig:distance-explain} illustrates how the within-facet or between-facet distances are defined.
+Pairwise distances are within-facets when $b_{k} = b_{k'}$, that is, between pairs of the form $(a_{j}b_{k}, a_{j'}b_{k})$ as shown in panel (3) of Figure \ref{fig:distance-explain}.
+If categories are ordered (like all temporal cyclic granularities), then only distances between pairs where $a_{j'} = (a_{j+1})$ are considered (panel (4)).
+Pairwise distances are between-facets when they are considered between pairs of the form $(a_{j}b_{k}, a_{j}b_{k'})$.
+Number of between-facet distances would be $^{K}C_2*J$ and number of within-facet distances are $K*(J-1)$ (ordered) and $^{J}C_2*K$ (un-ordered).
+
+### Tuning parameter
+
+A tuning parameter specifying the weightage given to the within-facet or between-facet categories can help to choose between designs like \ref{fig:null4by2}(b) and (c).
+Following the principle of Gestalt theory, the
+relative importance of within-facet and between-facet distances are taken to be $2:1$ and hence $\lambda = \frac{2}{3} = 0.67$.
+No human experiment is conducted to justify this ratio, however, typically a tuning parameter $\lambda>0.5$ would tend to upweigh the within-facet distances and that with $<0.5$ would upweigh the between-facet distances (refer to the Supplementary section of the paper for more details).
+
+### Normal Quantile transform
+
+The intended aim of $wpd$ is to capture differences in categories irrespective of the distribution from which the data is generated.
+Hence, as a pre-processing step, the raw data is normal quantile transformed (@Bogner2012-az) so that the quantiles of the transformed data follows a standard normal distribution.
+
+### Algorithm
+
+<!-- The distance measure $wpd$ between two cyclic granularities $A$ and $B$ is aimed to capture the strength of the structure by estimating the maximum within-group and between-group variations.
+Furthermore,  -->
+
+The steps employed for computing $wpd$ is summarized as follows:
 
@@
 
-\noindent Pairwise distances could be within-facets or between-facets.
-Figure \ref{fig:distance-explain} illustrates how the within-facet or between-facet distances are defined.
-Pairwise distances are within-facets when $b_{k} = b_{k'}$, that is, between pairs of the form $(a_{j}b_{k}, a_{j'}b_{k})$ as shown in panel (3) of Figure \ref{fig:distance-explain}.
-If categories are ordered (like all temporal cyclic granularities), then only distances between pairs where $a_{j'} = (a_{j+1})$ are considered (panel (4)).
-Pairwise distances are between-facets when they are considered between pairs of the form $(a_{j}b_{k}, a_{j}b_{k'})$.
-Number of between-facet distances would be $^{K}C_2*J$ and number of within-facet distances are $K*(J-1)$ (ordered) and $^{J}C_2*K$ (un-ordered).
-If the measure is intended to put more importance in pointing towards distributional differences between x categories, a $\lambda>0.5$ should be chosen.
-
 <!-- 5. Compute distribution of maximum distance ($M$) by shuffling the data $200$ times and finishing Steps1-4 in each case. Scale $M$ using the mean and sd of the distribution.
@@
 
-_Linear model_
-
-A linear model is fitted to model the relationship between $wpd$ and $nx*nfacet$.
+<!-- CONTENT DELETE: linear model -->
+<!-- _Linear model_   -->
+
+<!-- A linear model is fitted to model the relationship between $wpd$ and $nx*nfacet$.
 The model is of the form $$y_l = a+b*log(z_l) + e_l$$, where, $y_l = median_m(wpd_{l, m})$, $z_l$ is the $l^{th}$ panel and $e_l$ are idiosyncratic errors, with parameters $a$ and $b$ being estimated from the data generated through the simulation study described in Section \ref{sec:sim-study}.
 The estimates and other model summary is given in Table \ref{tab:linear-model}.
-
-```{r linear-model, message=FALSE}
-
-```
-
-<!-- # ```{r} -->
-<!-- # results3 <- broom::tidy(fit_lm2) -->
-<!-- # library(ggfortify) -->
-<!-- # autoplot(fit_lm2, which = 1:6) + theme_minimal() -->
-<!-- # ``` -->
-
-The idea is to find a transformation on $wpd$ which would remove the effect of $nx*nfacet$ on $wpd$ and thus is defined as the residuals:
-$y^* =  y - \hat a -  \hat b*log(z)$, where 
-$y^*$ is the $wpd_{linear}$, 
-$\hat a$ and $\hat b$ are the estimated values of the parameter $a$ and $b$ and $z = nx*nfacet$.
-
-Defining $wpd_{linear}$ in this way forces the mean to be zero and variability to be uniform across the median $wpd$ values as could be seen in Figure \ref{fig:resi-linear}.  
-<!-- But, the original distribution will still have some dissimilarities in shape and location specially for small values of $nx$ and $nfacet$ as could be seen in \ref{fig:} -->
-
-```{r resi-linear, fig.cap = "$wpd_{norm}^{linear}$ which are defined as the residuals of the linear model have mean zero and are homogenous.
-Further, by design they are independent of the $nx*nfacet$ and hence could be a potential candidate for $wpd_norm$."}
-```
-
-<!-- Let ${x_p, p = 1, 2, \dots, npanel}$ denote the total number of distances $nx*nfacet$ obtained in each panel. So for each $nx*nfacet$, we have $nsim = 200$ values of ${y_i}$. -->
-
-<!-- from $nx_{i}$ x-categories and $nfacet_{j}$ facet-categories is $nx_{i}*nfacet_{j}$ and  -->
+-->
+
+<!-- ```{r linear-model, message=FALSE} -->
+
+<!-- ``` -->
+
+<!-- The idea is to find a transformation on $wpd$ which would remove the effect of $nx*nfacet$ on $wpd$ and thus is defined as the residuals: -->
+<!-- $y^* =  y - \hat a -  \hat b*log(z)$, where  -->
+<!-- $y^*$ is the $wpd_{linear}$,  -->
+<!-- $\hat a$ and $\hat b$ are the estimated values of the parameter $a$ and $b$ and $z = nx*nfacet$. -->
+
+<!-- Defining $wpd_{linear}$ in this way forces the mean to be zero and variability to be uniform across the median $wpd$ values as could be seen in Figure \ref{fig:resi-linear}.   -->
+
+<!-- ```{r resi-linear, fig.cap = "$wpd_{norm}^{linear}$ which are defined as the residuals of the linear model have mean zero and are homogeneous.
+Further, by design they are independent of the $nx*nfacet$ and hence could be a potential candidate for $wpd_norm$."} -->
+<!-- ``` -->
 
@@
 
-```{r hist-qq, fig.cap = "In panel a, the histogram of $wpd_{glm-scaled}$ is plotted.
+```{r hist-qq-new, fig.cap = "In panel a, the histogram of $wpd_{glm-scaled}$ is plotted.
 In part b, the QQ plot is shown with the theoretical quantiles on the x-axis and $wpd_{glm-scaled}$ quantiles on the y-axis.
@@
 
+# 
+# elec %>% 
+#   filter(id == "1") %>% 
+#   prob_plot("hour_day", 
+#             "day_week",
+#             response = "kwh",
+#             plot_type = "violin", fill = "blue")
+#   
+elec1 <- elec %>% 
+  filter(id == "1") %>% 
+  create_gran("day_week") %>% 
+  create_gran("hour_day") %>% 
+  mutate(day_week = as.numeric(day_week),
+         hour_day = as.numeric(hour_day),
+         id = as.numeric(id))
+
+# temp.gly <- glyphs(elec1, "day_week", "hour_day", "id","kwh", height = 2.5)
+# 
+# ggplot(temp.gly, ggplot2::aes(gx, gy, group = gid)) +
+#   add_ref_lines(temp.gly, color = "grey90") +
+#   add_ref_boxes(temp.gly, color = "grey90") +
+#   geom_path() +
+#   theme_bw() +
+#   labs(x = "", y = "")
+
 elec_zoom <-  elec %>%

### 2021-05-20 paper/main.Rmd
NQT steps updated

@@
 
-### Normal Quantile transform
+### Data transformation
 
 The intended aim of $wpd$ is to capture differences in categories irrespective of the distribution from which the data is generated.
-Hence, as a pre-processing step, the raw data is normal quantile transformed (@Bogner2012-az) so that the quantiles of the transformed data follows a standard normal distribution.
+Hence, as a pre-processing step, the raw data is normal-quantile transformed (NQT) (@Krzysztofowicz1997-bv), so that the quantiles of the transformed data follows a standard normal distribution.
+This sort of transformation is common in the fields of geo-statistics to make most asymmetrical distributed real world measured variables more treatable and normal-like (@Bogner2012-az).The empirical NQT involves the following steps:
+ 1. The sample of measured variable $v$ is sorted from the smallest to the largest observation $v_{(1)},\dots, v_{(i)}, .., v_{(n)}$.  
+ 2. The cumulative probabilities $p_{(1)},\dots, p_{(i)}, .., p_{(n)}$ are estimated using a plotting position like $i/(n + 1)$ such that $p_{(i)} = P(v \leq v_{(i)})$.  
+ 3.
+Each observation $v_{(i)}$ of $v$ is transformed into observation $v^*(i) = Q^{-1}(p(i))$ of the standard normal variate $v^*$, with $Q$ denoting the standard normal distribution and $Q^{-1}$ its inverse.
 

### 2021-05-20 paper/main.Rmd
deleted application 2 pictures and a table - fixing pg numbers

@@
 
-## Properties
+## Properties of $wpd$
 
@@
 
-# Normalization for the number of comparisons {#sec:norm-wpd}
+# Adjusting for the number of comparisons {#sec:norm-wpd}
 
@@
 
-```{r tab-demography}
+```{r tab-demography, eval = FALSE}
 demography <- tibble(id = c(1, 2, 3, 4, 5,6, 7, 8), 
@@
 From the scales of Fig a, it is apparent that these households vary in consumption levels, but all their periodic patterns have been squeezed with this representation.
-In fig b, we can see some weekly patterns for the entire period and daily patterns for the highlighted week and there could be some other patterns visible in terms of peaks and troughs, but it is not clear if they are regular or significant.", fig.height=8}
+In fig b, we can see some weekly patterns for the entire period and daily patterns for the highlighted week and there could be some other patterns visible in terms of peaks and troughs, but it is not clear if they are regular or significant.", fig.height=8, eval = FALSE}
 library(scales)
@@
 ```{r raw-nqt-8, fig.height = 5, fig.cap="The raw density of the half-hourly demand for the eight households is shown in Fig a.
-Fig b shows the normal-score-transformed half-hourly demand for the same households which has resulted in more symmetric distribution of half-hourly demand."}
+Fig b shows the normal-score-transformed half-hourly demand for the same households which has resulted in more symmetric distribution of half-hourly demand.", eval = FALSE}
 elec_raw <- elec %>% 

### 2021-05-24 paper/main.Rmd
changed diagram - principle

@@
   theme_grey() + 
-  ylab("linear energy demand (kwh) for September") + ggtitle("b")
+  ylab("linear energy demand (kwh) for September") + ggtitle("b") +
+  theme(panel.grid.major.x = element_blank())
 

### 2021-05-25 paper/main.Rmd
deleted orig permutation approach section

@@
 
+### Adjusting for the number of comparisons {#sec:norm-wpd}
+
+The distribution of $wpd$ is different for different levels of facets and x-axis levels.
+This is because the statistics maximum which is used to define $wpd$ is affected by the number of comparisons (resulting pairwise distances).
+For example, for a $(2, 3)$ panel denoting 2 facet levels and 3 x-axis levels, there are $2*3=6$ possible subsets of obervations corresponding to the combinations $(a_1, b_1), (a_1, b_2), (a_1, b_3), (a_2 ,b_1), (a_2 ,b_2), (a_2, b_3)$, whereas for a $(2, 2)$ panel, $2*2 = 4$ possible subsets are $(a_1, b_1), (a_1, b_2), (a_2 ,b_1), (a_2 ,b_2)$.
+Consequently the number of pairwise distances that could be considered for these subsets are also varying.
+Hence, the measure would have higher values if $A$ or $B$ has higher levels since maximum is taken over higher number of pairwise distances.
+However, ideally it is desired that $wpd$ takes a higher value only if there are a significant difference between distributions across facet or x-axis categories, and not because the number of categories $J$ or $K$ is high.
+Therefore, in order to compare $wpd$ across different levels of facet and x-axis levels, the impact of different number of comparisons need to be eliminated through some adjustment.
+Henceforth, we call the adjusted measure as $wpd_{norm}$.
+\noindent Two approaches for normalizing for the number of comparions are discussed, both of which are substantiated using simulations.
+The first one, denoted as $wpd_{perm}$, involves a permutation method to make the distribution of the adjusted distance measure similar for different comparisons.
+The second one ($wpd_{glm-scaled}$) fits a model to represent the relationship between $wpd_{raw}$ and number of comparisons and defines the adjusted measure as the residual from the model.
+
+\noindent _Simulation design_
+
+ Observations are generated from a Gamma(2,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
+Each combination is being referred to as a _panel_.
+That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$.
+For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
+That is, if we consider the panel $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
+The values
+of $wpd$ is obtained for each of the panels.
+This design corresponds to $D_{null}$ as each combination of categories in a panel are drawn from the same distribution.
+Furthermore, the data is simulated for each of the panels $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
+$wpd_{l, s}$ denotes the value of $wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.
+
+- _Permutation approach:_ This method is somewhat similar in spirit to bootstrap or permutation tests, where the goal is to test the hypothesis that the groups under study have identical distributions.
+This method, in essence, accomplishes a different goal of making the distribution of the different groups (panels in our case) same under $D_{null}$.
+$wpd_{perm} = \frac{(wpd_{raw} - \bar{wpd_{perm-data}})}{sd(wpd_{perm-data})}$, where $\bar{wpd_{perm-data}}$ and $sd(wpd_{perm-data})$ are the mean and standard deviation of $wpd_{perm-data}$ respectively and $wpd_{perm-data}$ are the values of $wpd_{raw}$ computed on the many permuted data sets.
+Standardizing  $wpd$ in the permutation approach ensures that the distribution of $wpd_{perm}$ has the same $mean = 0$ and $sd = 1$ across all comparisons under $D_{null}$.
+While this works successfully to make the location and scale similar across different $nx$ and $nfacet$ (as seen in Figure \ref{fig:norm}), it is computationally heavy and time consuming, and hence less user friendly when being actually used in practice.
+Hence, another approach to adjustment, with potentially less computational time, is proposed.
+
+- _Modelling approach:_  $wpd_{raw}$ being a Jensen-Shannon distance, follows a Chi-square distribution (@JSD), which is a special case of Gamma distribution.
+Hence, a Gamma generalized linear model (GLM) for $wpd_{raw}$ is fitted with number of comparisons as the explanatory variable, which is of the following form:
+
+$$y_l = a+b*log(z_l) + e_l , \quad l = (1, 2, \dots, L)$$,
+
+\noindent where $y_l = median_s(wpd_{l, s})$, $wpd_{l, s}$ denotes the value of $wpd_{raw}$ obtained for the $l^{th}$ panel and $s^{th}$ simulation, $z_l$ is the number of groups $(nx*nfacet)$ in the $l^{th}$ panel and $e_l$ are idiosyncratic errors.
+Let $E(y) = \mu$ and $a + b*log(z) = g(\mu)$ where $g$ is the link function.
+Then $g(\mu)=  1/\mu$ and $\hat \mu  = 1/(\hat a + \hat b log(z))$.
+The residuals from this model $(y-\hat y) = (y-1/(\hat a + \hat b log(z)))$ would be expected to have no dependency on $z$.
+Thus, $wpd_{glm}$ is chosen as the residuals from this model and is defined as:
+$wpd_{glm} = wpd_{raw} - 1/(\hat a + \hat b*log(nx*nfacet))$.
+
+- _Combination approach:_ The simulation results show that adjustment through the modeling approach leads to very similar distribution across high $nx$ and $nfacet$ (higher than $5$) and not so much for lower $nx$ and $nfacet$.
+Hence, the computational load of permutation approach could be alleviated by using the modeling approach for the higher $nx$ and $nfacet$, however, it is important that we use the permutation approach for lower $nx$ and $nfacet$.
+The adjusted variables from the two approaches have to be brought to the same scale so that for smaller categories, permutation approach is used and for larger categories, modeling approach is used.
+The adjusted measure from the combination approach, denoted by $wpd_{norm}$ is defined as follows:
+
+\begin{equation}
+wpd_{norm} =
+\begin{cases}
+wpd_{perm},& \text{if } J, K <=5\\
+wpd_{glm-scaled}             & \text{otherwise}\\
+\end{cases}
+\end{equation},
+
+where $wpd_{glm-scaled}$ is the transformed wpd_{glm} with a similar scale as $wpd_{perm}.
+
 ### Algorithm
@@
 
-# Adjusting for the number of comparisons {#sec:norm-wpd}
-
-The distribution of $wpd$ is different for different levels of facets and x-axis levels.
-This is because the statistics maximum which is used to define $wpd$ is affected by the number of comparisons (resulting pairwise distances).
-The measure would have higher values if $A$ or $B$ has higher levels.
-However, we would ideally want a higher value of the measure only if there are a significant difference between distributions across facet or x-axis categories, and not because the number of categories $J$ or $K$ is high.
-Therefore, in order to compare $wpd$ across different combinations of facet and x-axis levels, we need to eliminate the impact of different number of comparisons and get a normalized measure.
-Henceforth, we call the normalized measure as $wpd_{norm}$.
-The measure $wpd_{norm}$ could potentially lead to comparison of the measure across different panels and also help distinguishing the interesting panels from a data set.
+<!-- last writeup -->
+<!-- In the linear model approach, $wpd\in R$ was assumed, whereas, $wpd$ is a Jensen-Shannon Distance (JSD) and lies between 0 and 1 (@JSD).
+Furthermore, JSD follows a Chi-square distribution, which is a special case of Gamma distribution.
+Therefore, a generalized linear model could be fitted instead of a linear model to allow for the response variable to follow a Gamma distribution.
+The inverse link is used when we know that the mean response is bounded, which is applicable in our case since $0 \leq wpd\leq 1$.
+-->
+
+<!-- We fit a Gamma generalized linear model with the inverse link which is of the form:   -->
+<!-- $$y_l = a+b*log(z_l) + e_l$$, where $y_l = median_m(wpd_{l, m})$, $z_l$ is the $l^{th}$ panel and $e_l$ are idiosyncratic errors.
+Let $E(y) = \mu$ and $a + b*log(z) = g(\mu)$ where $g$ is the link function.
+Then $g(\mu)=  1/\mu$ and $\hat \mu  = 1/(\hat a + \hat b log(z))$.
+The residuals from this model $(y-\hat y) = (y-1/(\hat a + \hat b log(z)))$ would be expected to have no dependency on $z$.
+Thus, $wpd_{glm}$ is chosen as the residuals from this model and is defined as: -->
+<!-- $wpd_{glm} = wpd - 1/(\hat a + \hat b*log(nx*nfacet))$. -->
+
+<!-- which is more approximate than exact but still has the similar accuracy when compared to the permutation approach. -->
+
+<!-- use later -->
+<!-- The measure $wpd_{norm}$ could potentially lead to comparison of the measure across different panels and also help distinguishing the interesting panels from a data set.
 We discuss two approaches for normalization, both of which are substantiated using simulations.
-
-<!-- The nodes and the storage used are as follows: -->
+-->
 
@@
 
-### Permutation approach
-
-This method is somewhat similar in spirit to bootstrap or permutation tests, where the goal is to test the hypothesis that the groups under study have identical distributions.
-This method, in essence, accomplishes a different goal of making the location and scale of different groups (panels) same under $D_{null}$.
-The steps are as follows:
-
-1. Compute $wpd$ for a harmony pair (A, B) for the original measured variable $v_t$ and store it in $wpd_{orig}$.
-
-2. Consider a permutation of the original measured variable $v_{perm_1}$ and again compute $wpd$ for the permuted data. Store it in $wpd_{perm_1}$.
-
-3.
-Repeat Step 2 for a large number ($nperm = 200$) of random permutations of the data yielding $nperm$ values : $wpd_{perm_1}, wpd_{perm_2}, \dots, wpd_{perm_{nperm}}$.
-Store the vector in $wpd_{perm}$.
-
-4. Define $wpd_{perm} = \frac{(wpd_{orig} - \bar{wpd_{perm}})}{sd(wpd_{perm})}$, where $\bar{wpd_{perm}}$ and $sd(wpd_{perm})$ are the mean and standard deviation of $wpd_{perm}$ respectively.
-
-<!-- Let $\{x_{k,l}, k = 1, 2, \dots, nx*nfacet, l = 1, 2, \dots, nsim\}$ denote the values of $wpd$ obtained from the simulation study for $k^{th}$ panel in the $i^{th}$ simulation.
-Hence, for each of those $k$ panel, we have $nsim$ values of $wpd$.combinations of $nx_i$ and $nfacet_j$.
-The normalized distances through permutation is computed as follows: $x^{perm}_{k} =  (x_{k} - mean_l(x_{k,l}))/sd_l(x_{k, l})$,  $x^{perm}_{k}$ is the value of the $wpd_{perm}$ for the $k^{th}$ panel-->
-
-Standardizing  $wpd$ in the permutation approach ensures that the distribution of $wpd_{perm}$ has the same $mean = 0$ and $sd = 1$ across all comparisons under $D_{null}$.
-While this works successfully to make the location and scale similar across different $nx$ and $nfacet$ (as seen in Figure \ref{fig:norm}), it is computationally heavy and time consuming, and hence less user friendly when being actually used in practice.
-Hence, we propose another approach to normalization which is more approximate than exact but still has the similar accuracy when compared to the permutation approach.
-
 ```{r norm, fig.cap = "Distribution of $wpd_{perm}$ is plotted across different $nx$ and $nfacet$ categories.
@@
 In part b, the QQ plot is shown with the theoretical quantiles on the x-axis and $wpd_{glm-scaled}$ quantiles on the y-axis.
-The distribution looks symmetric and looks like normal except in the tails."}
+The distribution looks symmetric and looks like normal except in the tails.", eval = FALSE}
 

### 2021-05-25 paper/main.Rmd
deleted orig modeling approach

@@
 
-### Modelling approach
-
-<!-- CONTENT DELETE: linear model -->
-<!-- _Linear model_   -->
-
-<!-- A linear model is fitted to model the relationship between $wpd$ and $nx*nfacet$.
-The model is of the form $$y_l = a+b*log(z_l) + e_l$$, where, $y_l = median_m(wpd_{l, m})$, $z_l$ is the $l^{th}$ panel and $e_l$ are idiosyncratic errors, with parameters $a$ and $b$ being estimated from the data generated through the simulation study described in Section \ref{sec:sim-study}.
-The estimates and other model summary is given in Table \ref{tab:linear-model}.
--->
-
-<!-- ```{r linear-model, message=FALSE} -->
-
-<!-- ``` -->
-
-<!-- The idea is to find a transformation on $wpd$ which would remove the effect of $nx*nfacet$ on $wpd$ and thus is defined as the residuals: -->
-<!-- $y^* =  y - \hat a -  \hat b*log(z)$, where  -->
-<!-- $y^*$ is the $wpd_{linear}$,  -->
-<!-- $\hat a$ and $\hat b$ are the estimated values of the parameter $a$ and $b$ and $z = nx*nfacet$. -->
-
-<!-- Defining $wpd_{linear}$ in this way forces the mean to be zero and variability to be uniform across the median $wpd$ values as could be seen in Figure \ref{fig:resi-linear}.   -->
-
-<!-- ```{r resi-linear, fig.cap = "$wpd_{norm}^{linear}$ which are defined as the residuals of the linear model have mean zero and are homogeneous.
-Further, by design they are independent of the $nx*nfacet$ and hence could be a potential candidate for $wpd_norm$."} -->
-<!-- ``` -->
-
-_Generalized linear model_
-
-In the linear model approach, $wpd\in R$ was assumed, whereas, $wpd$ is a Jensen-Shannon Distance (JSD) and lies between 0 and 1 (@JSD).
-Furthermore, JSD follows a Chi-square distribution, which is a special case of Gamma distribution.
-Therefore, a generalized linear model could be fitted instead of a linear model to allow for the response variable to follow a Gamma distribution.
-The inverse link is used when we know that the mean response is bounded, which is applicable in our case since $0 \leq wpd\leq 1$.
-
-We fit a Gamma generalized linear model with the inverse link which is of the form:  
-$$y_l = a+b*log(z_l) + e_l$$, where $y_l = median_m(wpd_{l, m})$, $z_l$ is the $l^{th}$ panel and $e_l$ are idiosyncratic errors.
-Let $E(y) = \mu$ and $a + b*log(z) = g(\mu)$ where $g$ is the link function.
-Then $g(\mu)=  1/\mu$ and $\hat \mu  = 1/(\hat a + \hat b log(z))$.
-The residuals from this model $(y-\hat y) = (y-1/(\hat a + \hat b log(z)))$ would be expected to have no dependency on $z$.
-Thus, $wpd_{glm}$ is chosen as the residuals from this model and is defined as:
-$wpd_{glm} = wpd - 1/(\hat a + \hat b*log(nx*nfacet))$.
-
-<!-- Please note: -->
-
-<!-- - subtracting the intercept brings the location of the transformed variable to 0 for either case -->
-<!-- - heterogeneity is higher for this case after normalization as compared to the earlier one. -->
-
 ```{r glm-tab}

### 2021-05-25 paper/main.Rmd
deleted orig combination approach section

@@
 
-## Combining normalizing approaches
-
-We see that the transformation through the modeling approach leads to very similar distribution across high $nx$ and $nfacet$ (higher than $5$) and not so much for lower $nx$ and $nfacet$.
-Hence, the computational load of permutation approach could be alleviated by using the modeling approach for the higher $nx$ and $nfacet$, however, it is important that we use the permutation approach for lower $nx$ and $nfacet$.
-It is difficult to compare and use the transformed measure from both of these approaches alternatively without bringing them to the same scale.
-The transformed variables from the two approaches have to be brought to the same scale so that for smaller categories, permutation approach is used and for larger categories, modeling approach is used.
-
-<!-- These could be done through the following: -->
-
-<!--  - Making the range of both the variables same by using min-max scaling method.
-In practice, however, we would only have one value of $wpd$ which we need to transform using the modeling approach.
-Hence, min-max scaling approach could not be used here.
--->
-
-<!--  - Standardizing the variables and expressing scores at standard deviation units.
-Again in practice, however, we would only have one value of $wpd_{raw}$ which we need to transform using the modeling approach.
-Hence, standardizing scores could not be used here as we do not have the mean and standard deviation of a series while using transformation using modeling.
--->
-
-<!-- - Make the location and scale of both the approaches similar so that they could be compared.
-Please note that the range of values could be different in this case, however location and scale are brought to same levels.) -->
-
-The measure $wpd_{glm}$ has a $\hat \mu_{glm} = 0$ and $\hat sd_{glm} = 0.003$ whereas the measure $wpd_{perm}$ which is a z-score, has an expected normal distribution with  $\hat \mu_{perm} = 0$ and $\hat sd_{perm} = 1$.
-To bring them to the same scale, we have defined $wpd_{glm-scaled} = wpd_{glm}*\frac{\hat sd_{perm}}{\hat sd_{glm}}$, which changes the scale of $wpd_{glm}$ without changing the location.
-The measure $wpd_{glm-scaled}$ seems to roughly follow a normal distribution except in the tails as could be seen in Figure \ref{fig:hist-qq} and the very method of permutation approach ensures that $wpd_{perm}$ is also normally distributed.
-Further, they are brought to similar scale and location and hence could be compared or used interchangeably for different comparisons based on their performance.
-
 ```{r hist-qq-new, fig.cap = "In panel a, the histogram of $wpd_{glm-scaled}$ is plotted.
@@
 ```
-
-Thus, the $wpd_{norm}$ is defined as follows:
-
-\begin{equation}
-wpd_{norm} =
-\begin{cases}
-wpd_{perm},& \text{if } J, K <=5\\
-wpd_{glm-scaled}             & \text{otherwise}\\
-\end{cases}
-\end{equation}
 

### 2021-05-25 paper/main.Rmd
major revision - adjusted distance measure in computation section

@@
 Let $v = \{v_t: t = 0, 1, 2, \dots, T-1\}$ be a continuous variable observed across $T$ time points.
+This  data structure with $J$ x-axis levels and $K$ facet levels is referred to as a $(K, J)$ panel.
+For example, a $(2, 3)$ panel will have cyclic granularities with 2 x-axis levels and 3 facet levels.
 Let the four elementary designs as described in Figure \ref{fig:null4by2} be $D_{null}$ where there is no difference in distribution of $v$ for $A$ or $B$, $D_{var_f}$ denotes the set of designs where there is difference in distribution of $v$ for $B$ and not for $A$.
@@
 -->
+
+### Data transformation
+
+The intended aim of $wpd$ is to capture differences in categories irrespective of the distribution from which the data is generated.
+Hence, as a pre-processing step, the raw data is normal-quantile transformed (NQT) (@Krzysztofowicz1997-bv), so that the quantiles of the transformed data follows a standard normal distribution.
+This sort of transformation is common in the fields of geo-statistics to make most asymmetrical distributed real world measured variables more treatable and normal-like (@Bogner2012-az).The empirical NQT involves the following steps:
+ 1. The sample of measured variable $v$ is sorted from the smallest to the largest observation $v_{(1)},\dots, v_{(i)}, .., v_{(n)}$.  
+ 2. The cumulative probabilities $p_{(1)},\dots, p_{(i)}, .., p_{(n)}$ are estimated using a plotting position like $i/(n + 1)$ such that $p_{(i)} = P(v \leq v_{(i)})$.  
+ 3.
+Each observation $v_{(i)}$ of $v$ is transformed into observation $v^*(i) = Q^{-1}(p(i))$ of the standard normal variate $v^*$, with $Q$ denoting the standard normal distribution and $Q^{-1}$ its inverse.
 
@@
 
-### Data transformation
-
-The intended aim of $wpd$ is to capture differences in categories irrespective of the distribution from which the data is generated.
-Hence, as a pre-processing step, the raw data is normal-quantile transformed (NQT) (@Krzysztofowicz1997-bv), so that the quantiles of the transformed data follows a standard normal distribution.
-This sort of transformation is common in the fields of geo-statistics to make most asymmetrical distributed real world measured variables more treatable and normal-like (@Bogner2012-az).The empirical NQT involves the following steps:
- 1. The sample of measured variable $v$ is sorted from the smallest to the largest observation $v_{(1)},\dots, v_{(i)}, .., v_{(n)}$.  
- 2. The cumulative probabilities $p_{(1)},\dots, p_{(i)}, .., p_{(n)}$ are estimated using a plotting position like $i/(n + 1)$ such that $p_{(i)} = P(v \leq v_{(i)})$.  
- 3.
-Each observation $v_{(i)}$ of $v$ is transformed into observation $v^*(i) = Q^{-1}(p(i))$ of the standard normal variate $v^*$, with $Q$ denoting the standard normal distribution and $Q^{-1}$ its inverse.
+### Raw distance measure
+
+The raw distance measure, denoted by $wpd_{raw}$, is computed after combining all the weighted distance measures appropriately.
+First, NQT is performed on the measured variable $v_t$ to obtain $v^*_t$ (_data transformation_).
+Then, for a fixed harmony pair $(A, B)$, percentiles of $v^*_{jk}$ are computed and stored in $q_{jk}$ (_distribution characterization_).
+This is repeated for all pairs of categories of the form $(a_{j} b_{k}, a_{j'}b_{k'}): \{a_j: j = 1, 2, \dots, J\}, B = \{ b_k: k = 1, 2, \dots, K\}$.
+The pairwise distances between pairs $(a_{j} b_{k}, a_{j'}b_{k'})$  denoted by $d_{(jk, j'k')} = JSD(q_{jk}, q_{j'k'})$ is computed (_distance between distributions_).
+The pairwise distances (_Within-facet and between-facet_) are transformed using a suitable tuning parameter ($0<\lambda<1$) depending on if they are within-facet($d_w$) or between-facets($d_b$) as follows:
+\begin{equation}\label{def:raw-wpd}
+d*_{(j,k), (j'k')} =
+\begin{cases}
+\lambda d_{(jk), (j'k')},& \text{if } d = d_w\\
+(1-\lambda)  d_{(jk), (j'k')},              & \text{if } d = d_b\\
+\end{cases}
+\end{equation}
+
+\noindent The $wpd_{raw}$ is then computed as $$wpd = max_{j, j', k, k'}(d*_{(jk), (j'k')}) \forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}$$
+
+\noindent The statistic "maximum" is chosen to combine the weighted pairwise distances since the distance measure is aimed at capturing the maximum variation of the measured variable within a panel.
+The statistic "maximum" is, however, affected by the number of comparisons (resulting pairwise distances).
+For example, for a $(2, 3)$ panel, there are $6$ possible subsets of obervations corresponding to the combinations $(a_1, b_1), (a_1, b_2), (a_1, b_3), (a_2 ,b_1), (a_2 ,b_2), (a_2, b_3)$, whereas for a $(2, 2)$ panel, there are only $4$ possible subsets $(a_1, b_1), (a_1, b_2), (a_2 ,b_1), (a_2 ,b_2)$.
+Consequently, the measure would have higher values for the panel $(2, 3)$ as compared to $(2, 2)$, since maximum is taken over higher number of pairwise distances.
 
@@
 
-The distribution of $wpd$ is different for different levels of facets and x-axis levels.
-This is because the statistics maximum which is used to define $wpd$ is affected by the number of comparisons (resulting pairwise distances).
-For example, for a $(2, 3)$ panel denoting 2 facet levels and 3 x-axis levels, there are $2*3=6$ possible subsets of obervations corresponding to the combinations $(a_1, b_1), (a_1, b_2), (a_1, b_3), (a_2 ,b_1), (a_2 ,b_2), (a_2, b_3)$, whereas for a $(2, 2)$ panel, $2*2 = 4$ possible subsets are $(a_1, b_1), (a_1, b_2), (a_2 ,b_1), (a_2 ,b_2)$.
-Consequently the number of pairwise distances that could be considered for these subsets are also varying.
-Hence, the measure would have higher values if $A$ or $B$ has higher levels since maximum is taken over higher number of pairwise distances.
-However, ideally it is desired that $wpd$ takes a higher value only if there are a significant difference between distributions across facet or x-axis categories, and not because the number of categories $J$ or $K$ is high.
-Therefore, in order to compare $wpd$ across different levels of facet and x-axis levels, the impact of different number of comparisons need to be eliminated through some adjustment.
+Ideally it is desired that $wpd$ takes a higher value only if there is a significant difference between distributions across facet or x-axis categories, and not because the number of categories $J$ or $K$ is high.
+Therefore, in order to compare $wpd$ across panels with different levels, the impact of different number of comparisons need to be eliminated through some adjustment.
 Henceforth, we call the adjusted measure as $wpd_{norm}$.
-\noindent Two approaches for normalizing for the number of comparions are discussed, both of which are substantiated using simulations.
+Two approaches for adjusting for the number of comparisons are discussed, both of which are substantiated using simulations.
 The first one, denoted as $wpd_{perm}$, involves a permutation method to make the distribution of the adjusted distance measure similar for different comparisons.
@@
  Observations are generated from a Gamma(2,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
-Each combination is being referred to as a _panel_.
-That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$.
+That is, data is being generated for each of the panels $(2, 2), (2, 3), (2, 5) \dots, (50, 31), (50, 50)$.
 For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
-That is, if we consider the panel $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
-The values
-of $wpd$ is obtained for each of the panels.
+That is, if we consider a $(2, 2)$ panel, $500$ observations are generated for each of the possible subsets, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
+The values of $wpd$ is obtained for each of the panels.
 This design corresponds to $D_{null}$ as each combination of categories in a panel are drawn from the same distribution.
@@
 This method, in essence, accomplishes a different goal of making the distribution of the different groups (panels in our case) same under $D_{null}$.
-$wpd_{perm} = \frac{(wpd_{raw} - \bar{wpd_{perm-data}})}{sd(wpd_{perm-data})}$, where $\bar{wpd_{perm-data}}$ and $sd(wpd_{perm-data})$ are the mean and standard deviation of $wpd_{perm-data}$ respectively and $wpd_{perm-data}$ are the values of $wpd_{raw}$ computed on the many permuted data sets.
+The values of $wpd_{raw}$ is computed on many permuted ($nperm$) data sets for the $l^{th}$ panel and stored in $wpd_{perm-data}$.
+$nperm=100$ is considered and the adjusted distance measure
+$wpd_{perm}$ is computed as follows:
+
+$$wpd_{perm} = \frac{(wpd_{raw} - \bar{wpd_{perm-data}})}{sd(wpd_{perm-data})}$$
+where $\bar{wpd_{perm-data}}$ and $sd(wpd_{perm-data})$ are the mean and standard deviation of $wpd_{perm-data}$ respectively.
 Standardizing  $wpd$ in the permutation approach ensures that the distribution of $wpd_{perm}$ has the same $mean = 0$ and $sd = 1$ across all comparisons under $D_{null}$.
@@
 \end{cases}
-\end{equation},
-
-where $wpd_{glm-scaled}$ is the transformed wpd_{glm} with a similar scale as $wpd_{perm}.
-
-### Algorithm
+\end{equation}
+where $wpd_{glm-scaled}$ is the transformed $wpd_{glm}$ with a similar scale as $wpd_{perm}$.
+
+<!-- ### Algorithm -->
 
@@
 
-The steps employed for computing $wpd$ is summarized as follows:
+<!-- The steps employed for computing $wpd$ is summarized as follows: -->
 
@@
 
-1. Perform NQT on the measured variable $v_t$ to obtain $v^*_t$.
-
-2. Fix harmony pair $(A, B)$.
-
-<!-- The set of pairs of categories is of the form $(a_{j} b_{k}, a_{j'}b_{k'}): j = 1, 2, \dots, J\}, B = \{ b_k: k = 1, 2, \dots, K\}$. -->
-
-3.
-Percentiles of $v^*_{jk}$ are computed and stored in $q_{jk}$.
-Repeat for all pairs of categories of the form $(a_{j} b_{k}, a_{j'}b_{k'}): \{a_j: j = 1, 2, \dots, J\}, B = \{ b_k: k = 1, 2, \dots, K\}$.
-
-4. The pairwise distances between pairs $(a_{j} b_{k}, a_{j'}b_{k'})$  denoted by $d_{(jk, j'k')} = JSD(q_{jk}, q_{j'k'})$ is computed.
-
-5. The pairwise distances $d_{(jk, j'k')}$ is transformed using a suitable tuning parameter ($0<\lambda<1$) depending on if they are within-facet($d_w$) or between-facets($d_b$) as follows:
-
-\begin{equation}\label{def:raw-wpd}
-d*_{(j,k), (j'k')} =
-\begin{cases}
-\lambda d_{(jk), (j'k')},& \text{if } d = d_w\\
-(1-\lambda)  d_{(jk), (j'k')},              & \text{if } d = d_b\\
-\end{cases}
-\end{equation}
-
-5. The wpd is then computed as $wpd = max_{j, j', k, k'}(d*_{(jk), (j'k')}) \forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}$.
-
-6. Repeat Steps 2-5 for all harmony pairs in $H_{N_C}$.
-
 <!-- 5. Compute distribution of maximum distance ($M$) by shuffling the data $200$ times and finishing Steps1-4 in each case. Scale $M$ using the mean and sd of the distribution.
@@
 
-## Properties of $wpd$
-
-Simulations were carried out to explore the behavior of $wpd$ under the following factors that could potentially impact the values of $wpd$: $nx$, $nfacet$, $\lambda$, $\omega$, $dist$ (normal/non-normal distributions with different location and scale), $ntimes$, and $designs$ and results are presented in two parts.
+<!-- ## Properties of $wpd$ -->
+
+<!-- Simulations were carried out to explore the behavior of $wpd$ under the following factors that could potentially impact the values of $wpd$: $nx$, $nfacet$, $\lambda$, $\omega$, $dist$ (normal/non-normal distributions with different location and scale), $ntimes$, and $designs$ and results are presented in two parts.
 The dependence of $wpd$ on $nx$ and $nfacet$ under $D_{null}$ is presented here, which lays the foundation for the next section.
@@
 They show that the designs $D_{var_f}$ and $D_{var_x}$ intersect at $\lambda = 0.5$ and hence for up-weighing designs of the form $D_{var_x}$, $\lambda = 0.67$ has been considered for computation of $wpd$ in the rest of the paper.
+-->
 
@@
 
-### Simulation design{#sec:sim-study}
-
-Observations are generated from a Gamma(2,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
+<!-- ### Simulation design{#sec:sim-study} -->
+
+<!-- Observations are generated from a Gamma(2,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
 Each combination is being referred to as a _panel_.
@@
 That is, if we consider the panel $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
-The values
-of $wpd$ is obtained for each of the panels.
+The values -->
+<!-- of $wpd$ is obtained for each of the panels.
 This design corresponds to $D_{null}$ as each combination of categories in a panel are drawn from the same distribution.
@@
 $wpd_{l, s}$ denotes the value of $wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.
-
-### Results
-
-Figure \ref{fig:raw} shows the distribution of $wpd$ plotted across different $nx$ and $nfacet$ categories.
+-->
+
+<!-- ### Results -->
+
+<!-- Figure \ref{fig:raw} shows the distribution of $wpd$ plotted across different $nx$ and $nfacet$ categories.
 Since under $D_{null}$, there is no difference in distributions across different categories, we expect the distance measure $wpd$ to reflect that as well and have the same distribution across categories.
@@
 The median increases abruptly for lower values of $nx*nfacet$ and slowly for higher $nx*nfacet$.
+-->
 
@@
 
-## Methodology
-
-The transformed ${wpd}$ which is normalized for the values of $nx$ and $nfacet$ is denoted by $wpd_{norm}$.
+<!-- ## Methodology -->
+
+<!-- The transformed ${wpd}$ which is normalized for the values of $nx$ and $nfacet$ is denoted by $wpd_{norm}$.
 Two approaches have been employed - the first one involves a permutation method to make the distribution of the transformed $wpd$ similar for different comparisons and the second one fits a model to represent the relationship between the two variables and defines $wpd_{norm}$ as the residual of the model.
+-->
 
@@
 
-## Properties
-
-This section reports the results of a simulation study that was carried out to evaluate the behavior of $wpd_{norm}$ under different designs and other potential factors.
+<!-- use soon -->
+<!-- ## Properties -->
+
+<!-- This section reports the results of a simulation study that was carried out to evaluate the behavior of $wpd_{norm}$ under different designs and other potential factors.
 The behavior of $wpd_{norm}$ is explored in designs where there is in fact difference in distribution between facet categories ($D_{var_f}$) or across x-categories ($D_{var_x}$) or both ($D_{var_{all}}$).
@@
 Furthermore, to generate different distributions across different combination of facet and x levels, the following method is deployed - suppose the distribution of the combination of first levels of $x$ and $facet$ category is $N(\mu,\sigma)$ and $\mu_{jk}$ denotes the mean of the combination $(a_jb_k)$, then $\mu_{j.} = \mu + j\omega$ (for design $D_{var_x}$) and $\mu_{.k} = \mu + k\omega$ (for design $D_{var_f}$).
-
-The tabulated values and graphical representations of the simulation results are provided in the Supplementary paper.
-The learning from the simulations are as follows: The values of $wpd_{norm}$ is least for $D_{null}$, followed by
-$D_{var_f}$, $D_{var_x}$ and $D_{var_{all}}$.
+-->
+
+<!-- The tabulated values and graphical representations of the simulation results are provided in the Supplementary paper.
+The learning from the simulations are as follows: The values of $wpd_{norm}$ is least for $D_{null}$, followed by -->
+<!-- $D_{var_f}$, $D_{var_x}$ and $D_{var_{all}}$.
 This is a desirable result since the measure $wpd_{norm}$ was designed such that this relationship holds.
@@
 More detailed results about the properties of $wpd_{norm}$ could be found in the Supplementary paper.
+-->
 

### 2021-05-25 paper/main.Rmd
down to 30 pages (need to remove figs)

@@
 
-- _Modelling approach:_  $wpd_{raw}$ being a Jensen-Shannon distance, follows a Chi-square distribution (@JSD), which is a special case of Gamma distribution.
+- _Modeling approach:_  $wpd_{raw}$ being a Jensen-Shannon distance, follows a Chi-square distribution (@JSD), which is a special case of Gamma distribution.
 Hence, a Gamma generalized linear model (GLM) for $wpd_{raw}$ is fitted with number of comparisons as the explanatory variable, which is of the following form:

### 2021-05-25 paper/main.Rmd
illustration of principle - made into one and 2 sd apart from mean

@@
 As expected, the value of $wpd_{norm}$ under null design is the least (a), followed by (b, c and d).
-Moreover, the relative difference is interesting as c is closer to d than b, since the differences between x categories are up-weighed by design."}
+Moreover, the relative difference is interesting as c is closer to d than b, since the differences between x categories are up-weighed by design.", dependson= "null4by2"}
 

### 2021-05-25 paper/scripts/main.R

@@ -147,39 +147,41 @@ sim_varall_normal <- function(nx, nfacet, mean, sd, w1, w2) {
 sim_panel_varall <- sim_panel(
   nx = 2, nfacet = 3,
   ntimes = 500,
-  sim_dist = sim_varall_normal(2, 3, 5, 10, 5, -1.5)
+  #sim_dist = sim_varall_normal(2, 3, 5, 10, 5, -1.5)
+  sim_dist = sim_varall_normal(2, 3, 0, 1, 3, 0)
 ) %>% unnest(data)
 
-p_varall <- sim_panel_varall %>%
-  rename("facet level" = "id_facet" ) %>% 
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + 
-  facet_wrap(~`facet level`,labeller = "label_both") + 
-  geom_boxplot() +
-  ggtitle("") +
-  xlab("x level") +
-  ylab("")
+# p_varall <- sim_panel_varall %>%
+#   rename("facet level" = "id_facet" ) %>% 
+#   ggplot(aes(x = as.factor(id_x), y = sim_data)) + 
+#   facet_wrap(~`facet level`,labeller = "label_both") + 
+#   geom_boxplot() +
+#   ggtitle("") +
+#   xlab("x level") +
+#   ylab("")
 
 
 sim_varx_normal <- function(nx, nfacet, mean, sd, w1, w2) {
-  rep(dist_normal((mean + seq(0, nx - 1, by = 1) * w1), (mean + seq(0, nx - 1, by = 1) * w2)), nfacet)
+  rep(dist_normal((mean + seq(0, nx - 1, by = 1) * w1), (sd + seq(0, nx - 1, by = 1) * w2)), nfacet)
 }
 
 sim_panel_varx <- sim_panel(
   nx = 2, nfacet = 3,
   ntimes = 500,
-  sim_dist = sim_varx_normal(2, 3, 5, 10, 5, -1.5)
+  # sim_dist = sim_varx_normal(2, 3, 5, 10, 5, -1.5)
+  sim_dist = sim_varx_normal(2, 3, 0, 1, 3, 0)
 ) %>% unnest(data)
 
 
-p_varx <- sim_panel_varx %>%
-  rename("facet level" = "id_facet" ) %>% 
-  ggplot(aes(x = as.factor(id_x), y = sim_data)) + 
-  facet_wrap(~`facet level`,labeller = "label_both") + 
-  ggtitle("") +
[…]

### 2021-05-25 paper/main.Rmd
illustration principle caption added

@@
 
-```{r null4by2,fig.cap = "A graphical display with two categories mapped to x-axis and 3 categories mapped to facets with the distribution of a continuous random variable plotted on the y-axis.
-Display a is not interesting as the distribution of the variable does not depend on x or facet categories.
-Display b and c are more interesting than a since there is a change in distribution either across facets (b) or x-axis (c).
-Display d is most interesting in terms of displaying the strongest pattern as distribution of the variable changes across both facet and x-axis variable."}
-
+```{r null4by2,fig.cap = "An example illustrating the principle of the proposed distance measure, displaying the distribution of a normally distributed variable in four panels each with $2$ x-axis categories and $3$ facet levels, but with different designs.
+Display (a) is not interesting as the distribution of the variable does not depend on x or facet categories.
+Display (b) and (c) are more interesting than (a) since there is a change in distribution either across facets (b) or x-axis (c).
+Display (d) is most interesting in terms of capturing structure in the variable as the distribution of the variable changes across both facet and x-axis variable.
+The value of our proposed distance measure is presented for each panel, the relative differences between which will be explained later in Section 3.2."}
 ```

### 2021-05-25 paper/scripts/main.R

@@ -240,7 +240,7 @@ varall <- compute_pairwise_norm(sim_panel_varall,
 # plot
 p_varall <- sim_panel_varall %>%
   ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
-  ggtitle(paste("d", round(varall, 2))) + xlab("x level")
+  ggtitle(paste("(d)", round(varall, 2))) + xlab("x level")
 
 
 set.seed(99999)
@@ -254,7 +254,7 @@ null <- compute_pairwise_norm(sim_panel_null,
 
 p_null <- sim_panel_null %>%
   ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
-  ggtitle(paste("a", round(null, 2))) + xlab("x level") 
+  ggtitle(paste("(a)", round(null, 2))) + xlab("x level") 
 
 
 
@@ -269,7 +269,7 @@ varf <- compute_pairwise_norm(sim_panel_varf,
 
 p_varf <- sim_panel_varf %>%
   ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
-  ggtitle(paste("b", round(varf, 2))) + xlab("x level")
+  ggtitle(paste("(b)", round(varf, 2))) + xlab("x level")
 
 
 set.seed(99999)
@@ -283,7 +283,7 @@ varx <- compute_pairwise_norm(sim_panel_varx,
 # plot
 p_varx <- sim_panel_varx %>%
   ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +
-  ggtitle(paste("c", round(varx, 2))) + xlab("x level")
+  ggtitle(paste("(c)", round(varx, 2))) + xlab("x level")
 
 
 

### 2021-05-25 paper/main.Rmd
application structure change

@@
 Each of these figures describes a panel with $2$ x-axis categories and $3$ facet levels, but with different designs.
-Figure \ref{fig:null4by2}a has all categories drawn from N(5, 10) distribution for each facet.
+Figure \ref{fig:null4by2}a has all categories drawn from N(0, 1) distribution for each facet.
 It is not an interesting display particularly, as distributions do not vary across x-axis or facet categories.
-Figure \ref{fig:null4by2}b has x categories drawn from the same distribution within a facet but the mean and sd incremented by $5$ units for every consecutive facets.
-Figure \ref{fig:null4by2}c exhibits an exact opposite situation where distribution between the x-axis categories within each facet is different but they are same across facets (mean by +5, sd by -2 for consecutive x categories).
-Figure \ref{fig:null4by2}d takes a step further by varying the distribution across both facet and x-axis categories (mean by +5 and sd by -1.5 for consecutive categories).
+Figure \ref{fig:null4by2}b has x categories drawn from the same distribution, but across facets the distributions are $3$ standard deviations apart.
+Figure \ref{fig:null4by2}c exhibits an exact opposite situation where distribution between the x-axis categories
+are $3$ standard deviations apart, but they do not change across facets.
+\ref{fig:null4by2}d takes a step further by varying the distribution across both facet and x-axis categories by  $3$ standard deviations.
 If the panels are to be ranked in order of capturing maximum variation in the measured variable from minimum to maximum, then an obvious choice would be placing (a) followed by (b), (c) and then (d).
@@
 
-The distance measure $wpd$ between two cyclic granularities $A$ and $B$ is aimed to capture structure and patterns by estimating the maximum variation of the measured variable within a panel.
-The computation of $wpd$
-involves characterizing distributions, computing distances between distributions, choosing a tuning parameter to specify the weightage given to within-facet or between-facet distances.
-Furthermore, the intended aim of $wpd$ is to capture differences in categories irrespective of the distribution from which the data is generated.
-Hence, as a pre-processing step, the raw data is normal quantile transformed (@Bogner2012-az) so that the quantiles of the transformed data follows a standard normal distribution.
+The computation of the distance measure $wpd$ for a panel involves characterizing distributions, computing distances between distributions, choosing a tuning parameter to specify the weightage for different group of distances.
+Furthermore, the data needs to be appropriately transformed to ensure that the value of $wpd$ emphasizes distributional differences across categories and not across different data generating processes.
+
+<!-- irrespective of the distribution from which the data is generated. -->
+
+<!-- is aimed to capture structure and patterns by estimating the maximum variation of the measured variable within a panel.  $wpd$ -->
 
@@
 The data has been cleaned to be a `tsibble` (@wang2019tsibble) containing half-hourly electricity consumption from Jul-2019 to Dec-2019 for each of the households, which is procured by them by downloading their data from the energy supplier/retailer.
-We also have some additional demographics data in terms of the number of members in the household and the presence of kids/elderly parents and their profession.
-
-Demand data for these households are shown in a linear time scale in Figure \ref{fig:linear-scale-8}.
-In the left panel of Figure \ref{fig:linear-scale-8} (a), the linear representation of the entire time period is shown, whereas in the right panel (b) a particular month is shown and furthermore a week has been highlighted.
-It is evident from the range of the demand data in  Figure \ref{fig:linear-scale-8} (a), that these households vary in consumption levels, but all their periodic patterns have been squeezed with this representation.
-When we zoom into the linear representation of this series in Figure \ref{fig:linear-scale-8} (b), some patterns are visible in terms of peaks and troughs, but we do not know if they are regular or what is their period.
+The line display of
+energy usage will have too many measurements squeezed in a linear representation.
+No behavioral pattern is likely to be discerned from this view.
+When we zoom into the linear representation of this series in Figure \ref{fig:linear-scale-8} (b) for September, some patterns are visible in terms of peaks and troughs, but we do not know if they are regular or what is their period.
 Electricity demand, in general, has a daily and weekly periodic pattern.
@@
 Also, it is not clear if any other periodic patterns are present in any household which might have been hidden with this view.
-We start the analysis by asking if the ranking of the harmonies make sense for the households, then compare households to get more insights of what these rankings imply and if they could be used to remove some non-interesting harmonies.
-Furthermore, we see if the display of the significant harmonies could be validated by zooming in the linear representation of the time series.
+We start the analysis by choosing few harmonies, ranking them for each for these households, compare households to get more insights into\ what these rankings imply and if they could be used to remove some non-interesting harmonies.
+Furthermore, the ranking and selection of significant harmonies could be validated by analyzing the distribution of the energy usage across significant harmonies.
 
@@
 
-$v_{i, t}$ has a asymmetrical distribution as could be seen in Figure \ref{fig:raw-nqt-8} and the Normal score transform has been applied to make it more symmetric.
-Let $v*_{i, t}$ denote the normal-quantile transformed electricity demand for $i^{th}$ household for time period $t$.
-Suppose $(A, B) \in H_{N_C}$ be a harmony pair where  $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.
-Suppose $q^{i, p}_{A, j}$ denote the quantiles with probability $p$ for the of the $i^{th}$ household for $j^{th}$ category of the cyclic granularity $A$.
-Similarly, $q^{i, p}_{B, k}$ denotes the same for the $k^{th}$ category of the cyclic granularity $B$.
-Sample quantiles were computed at $p = 0.01, 0.02, \dots, 0.99$.
-Jensen-Shannon distances are computed between $q^{i, p}_{A, j}$ and $q^{i, p}_{B, k}$ for each ${j \in J, k \in K}$ to obtain the relevant within-facet and between-facet distances.
-A tuning parameter of $\lambda = 0.67$ has been considered in Equation \ref{def:raw-wpd} to compute $wpd$.
-It is further normalized using the approach described in Section \ref{sec:norm-wpd}.
-This entire process is repeated for all harmony pairs $\in H_{N_C}$ and for each households $i \in i = \{1, 2, \dots, 8\}$.
+ $wpd_{norm}$ is computed for all harmony pairs $\in H_{N_C}$ and for each households $i \in i = \{1, 2, \dots, 8\}$.
 The harmony pairs are then arranged in descending order and the important ones with significance level 1%, 5% and 10% are highlighted with `***`, `**` and `*` respectively.
 Table \ref{tab:tab-rank-8} shows the rank of the harmonies for different households.
-Figure \ref{fig:dotplot-8} shows the heatmap for the eight households
-with the value of $wpd_{norm}$ filled as colors.
-
-_Validating rank of household id:1_
-
-From table \ref{tab:tab-rank-8}, it could be seen that 
-for household id:1, (hod, wdwnd) has been ranked higher than (wdwnd, hod), both of these being significant.
-Further, we see that (wom, wdwnd) has been ranked $5^{th}$ and tagged as an insignificant pair.
-Figure \ref{fig:gravitas-plot-8} is used to show
-if this selection and ranking of harmony pairs makes sense for this household.
-Panel a) of  Figure \ref{fig:gravitas-plot-8} shows the distribution of energy demand with weekday/weekend as the x-axis and hour-of-day as the facets and helps to compare the weekend/weekday patterns for different hours of the day.
-It could be observed that the difference between weekend and weekday is the highest from 15 to 19 hours of the day.
-Panel b) shows the distribution of energy demand with the variables swapped and helps to compare the daily patterns within weekday and weekend.
-It could be observed that the daily pattern is similar for weekdays and weekends with a morning and evening peak.
-However, the difference between morning and evening peaks are higher for weekends.
-Since $wpd_{norm}$ is designed to put more weightage on within-facet differences for $\lambda>0.5$, it makes sense that the pair (hod, wdwnd) has been ranked higher than (wdwnd, hod).
-Panel c) shows the distribution of energy demand with weekday/weekend as the x-axis and week-of-month as the facets.
-Although the differences might seem significant at first, with closer inspection it could be seen that the scale of the demand is lower in this case and hence the differences are not large enough to cross the threshold for significance.
-
-```{r gravitas-plot-8, message = FALSE, warning=FALSE,fig.cap="Distribution of energy demand shown for household id 1 across hod in x-axis and wd-wnd in facets in a) and just the reverse in b).
-In c), distribution of energy demand for household id:4 shown across hod and wd-wnd.
-It can be seen that the differences in distributions are more apparent when viewed in a) as compared to b).
-It seems like there is more difference in the distributions of hod for b) compared to c).
-This also confers with the value of the normalised measure shown in Figure 11."}
-
-id1_tsibble <- elec %>%
-  filter(id== 1)
-
-p1 <- id1_tsibble %>% 
-   prob_plot("hour_day",
-             "wknd_wday",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = FALSE,
-             quantile_prob = c(0.25, 0.5, 0.75)) +
-  ggtitle("a) hod vs wdwnd (Rank 1)") + 
-  scale_colour_brewer(name = "", palette = "Set2") +
-  theme(legend.position = "none",
-        strip.text = element_text(size = 7, margin = margin()),)
-
-p2 <- id1_tsibble %>%
-   prob_plot("wknd_wday",
-             "hour_day",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = FALSE,
-             quantile_prob = c(0.25,0.5,0.75)) +
-  ggtitle("b) wdwnd vs hod (Rank 3)") +
-  scale_colour_brewer(name = "", palette = "Set2")   +
-  theme(legend.position = "none",
-        strip.text = element_text(size = 7, margin = margin()))
-
-p3 <- id1_tsibble %>%
-   prob_plot("week_month",
-             "wknd_wday",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = FALSE,
-             quantile_prob = 
-               c(0.25,0.5,0.75)) +
-  scale_colour_brewer(name = "", palette = "Set2") +
-  theme(
-        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + theme(legend.position = "bottom",
-        strip.text = element_text(size = 7, margin = margin())) +
-  ggtitle("c) wom vs wdwnd (insignificant)")
-
-p4 <- id1_tsibble %>%
-   prob_plot("day_month",
-             "hour_day",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = FALSE,
-             quantile_prob = 
-               c(0.25,0.5,0.75)) +
-  scale_colour_brewer(name = "", palette = "Set2") +
-  theme(
-        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + theme(legend.position = "bottom",
-        strip.text = element_text(size = 7, margin = margin())) +
-  ggtitle("c) wom vs wdwnd (insignificant)")
-
-p1 + p2/p3
-
-```
-
-<!-- From Figure \ref{fig:gravitas-plot-8-id5}, it could further be observed that id5 has only one significant harmony $(hod, dow)$.
-Apparently, $(hod, wnd/wday)$ which is an important harmony for most households is not important for this one.
--->
+The rankings are different for different households, which is a reflection of their varied behaviors.
+Most importantly, there are at most $3$ harmonies that are significant for any household.
+This is a huge reduction in number of potential harmonies to explore closely, starting from $42$.
 
@@
  Figure \ref{fig:dotplot-8} helps to compare households through the heatmap (a) and validate the results of the heatmap through linear display in (b).
-The top panel contains the raw data for a month (Sep-2019).
-The darker the color of a cell in the heatmap, the more significant a harmony pair it is.
-Also, the ones with `*` are significant at 95% level This plot suggests that there are no significant periodic patterns for id 5, even when the demographics of id 5 are very similar to id 6 and 7.
-Household id 6 and 7 differ in the sense that for id 6, the difference in patterns only during weekday/weekends (two members are in the mixed profession), whereas for id 7, all or few other days of the week are also important (members are in academia and hence might have more flexible routines).
-The periodic pattern is very similar to id 8, which has a very different demographic property.
-Households id 2 and 3 are similar, in terms of linear display, periodic patterns as well as demographics.
-Different periodic behavior could be observed in households with very similar demographics (id 5 compared to 6 and 7 - only the variable `profession` is different) and similar periodic behavior can stem from households with very different demographics (id 7 and 8 - differs in all variables in \ref{tab:tab-demography}).
-This could also be verified from the corresponding linear representation in \ref{fig:dotplot-8}(b).
+(b) contains the raw data for a month (Sep-2019).
+In (a), the value of $wpd_{norm}$ filled as colors, implying darker cells correspond to more significant a harmony pair.
+Also, the ones with `*` are significant at 95% level.
+This plot suggests that there are no significant periodic patterns for id 5.
+Household id 6 and 7 differ in the sense that for id 6, the difference in patterns only during weekday/weekends, whereas for id 7, all or few other days of the week are also important.
+This might be due to their flexible work routines or different day-off.
+The periodic pattern is very similar to id 8, which has a very different total energy usage.
+Households id 2 and 3 are similar, in terms of linear display and heatmap, which implies that similar periodic behavior can stem from households with different demographics.
 
@@
 
+_Validating rank of household id:4 and 5_
+
+From table \ref{tab:tab-rank-8}, it could be seen that the harmony pair (dow, hod) is significant for household id 4, but for 5 it has been tagged as an insignificant pair.
+The distribution of energy demand with dow as the x-axis and hod as the facets for both of these households can help justify the selection.
+Figure \ref{fig:gravitas-plot-8} show that the distribution of energy consumption changes across both dow and hod for id 4, but it is not so different for id 5, as apparent from the scale of the usage.
+Although the differences might seem significant at first, with closer inspection it could be seen that the scale of the demand is lower in this case and hence the differences are not large enough to cross the threshold for significance.
+
+<!-- Figure \ref{fig:gravitas-plot-8} is used to show -->
+<!-- if this selection and ranking of harmony pairs makes sense for this household.
+Panel a) of  Figure \ref{fig:gravitas-plot-8} shows the distribution of energy demand with weekday/weekend as the x-axis and hour-of-day as the facets and helps to compare the weekend/weekday patterns for different hours of the day.
+It could be observed that the difference between weekend and weekday is the highest from 15 to 19 hours of the day.
+Panel b) shows the distribution of energy demand with the variables swapped and helps to compare the daily patterns within weekday and weekend.
+It could be observed that the daily pattern is similar for weekdays and weekends with a morning and evening peak.
+However, the difference between morning and evening peaks are higher for weekends.
+Since $wpd_{norm}$ is designed to put more weightage on within-facet differences for $\lambda>0.5$, it makes sense that the pair (hod, wdwnd) has been ranked higher than (wdwnd, hod).
+Panel c) shows the distribution of energy demand with weekday/weekend as the x-axis and week-of-month as the facets.
+Although the differences might seem significant at first, with closer inspection it could be seen that the scale of the demand is lower in this case and hence the differences are not large enough to cross the threshold for significance.
+-->
+
+```{r gravitas-plot-8, message = FALSE, warning=FALSE,fig.cap="Distribution of energy demand shown for household id 1 across hod in x-axis and wd-wnd in facets in a) and just the reverse in b).
+In c), distribution of energy demand for household id:4 shown across hod and wd-wnd.
+It can be seen that the differences in distributions are more apparent when viewed in a) as compared to b).
+It seems like there is more difference in the distributions of hod for b) compared to c).
+This also confers with the value of the normalised measure shown in Figure 11."}
+
+id4_tsibble <- elec %>%
+  filter(id== 4)
+
+id5_tsibble <- elec %>%
+  filter(id== 5)
+
+p1 <- id4_tsibble %>% 
+   prob_plot("hour_day",
+             "day_week",
+             response = "kwh",
+             plot_type = "quantile",
+             symmetric = TRUE,
+             quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)) +
+  ggtitle("a) hod vs dow (id:4)") + 
+  #scale_colour_brewer(name = "", palette = "Set2") +
+  theme(legend.position = "none",
+        strip.text = element_text(size = 7, margin = margin()),)
+
+p2 <- id5_tsibble %>%
+   prob_plot("hour_day",
+             "day_week",
+             response = "kwh",
+             plot_type = "quantile",
+             symmetric = TRUE,
+             quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)) +
+  ggtitle("a) hod vs dow (id:5)") +
+  #scale_colour_brewer(name = "", palette = "Set2")   +
+  theme(legend.position = "none",
+        strip.text = element_text(size = 7, margin = margin()))
+
+p1 + p2
+
+```
+
+<!-- From Figure \ref{fig:gravitas-plot-8-id5}, it could further be observed that id5 has only one significant harmony $(hod, dow)$.
+Apparently, $(hod, wnd/wday)$ which is an important harmony for most households is not important for this one.
+-->
+
 # Discussion

### 2021-05-25 simulations/supplementary/test-hpc/R-ind/size-supplementary.R

@@ -1,0 +1,111 @@
+library(readr)
+library(dplyr)
+library(distributional)
+library(gravitas)
+library(here)
+library(purrr)
+library(tidyverse)
+library(purrr)
+library(hakear)
+
+#simtable<-read_csv(here::here('simulations/sim_table/sim_table.csv'))
+simtable <-  expand.grid(x_levels = c(3, 7, 14),
+                         facet_levels = c(2, 9, 10)) %>%
+  mutate(design = c("null", "varf","varx", "varall", "null", "varf", "varx", "varall", "null"))
+
+sample_seed = seq(1000, 10999, by = 1000)
+npermj <- 200
+ntimesj <- 500
+nsampj <- 10
+wj <- 2
+# distj <- simj$dist
+# seedj <- simj$seed
+# typej <- simj$type
+
+# different designs
+
+sim_null <- function(nxj, nfacetj, mean, sd, w = 0){
+  rep(distributional::dist_normal(mu = mean, sigma = sd),
+      times = nxj*nfacetj)}
+
+sim_varx <- function(nx, nfacet, mean, sd, w)
+{
+  rep(dist_normal((mean + seq(0, nx-1, by  = 1)*w), sd), nfacet)
+}
+
+sim_varf <- function(nx, nfacet, mean, sd, w)
+{
+  rep(dist_normal((mean + seq(0, nfacet-1, by  = 1)*w), sd), each = nx)
+}
+
+sim_varall <- function(nx, nfacet, mean, sd, w)
+{
+  dist_normal((mean + seq(0,
+                          (nx*
+                             nfacet - 1), by  = 1)*w), sd)
+}
+
+
+
+sim_harmony_sim <-   map(seq_len(length(sample_seed)),
+                         function(seedj){
+                           set.seed(seedj) 
+  ## code for one harmony table starts
+  sim_data_all <- map(seq_len(nrow(simtable)),
+                      function(x){
+                        y = simtable %>% magrittr::extract(x,)
+                        
+                        # assigning different rows for different design
+                        
+                        # setting value of parameters
+                        designj = y$design
+                        nfacetj<- y$facet_levels # Which nfacet level
+                        nxj<- y$x_levels
+                    
+                        
+                        if(designj=="null")
+                          sim_function = sim_null
+                        else if(designj=="varx")
+                          sim_function =  sim_varx
+                        else if(designj=="varf")
+                          sim_function =  sim_varf
+                        else
+                          sim_function =  sim_varall
+                        
[…]

### 2021-05-26 paper/main.Rmd
choosing and ranking harmonies re-written

@@
 The computation of the distance measure $wpd$ for a panel involves characterizing distributions, computing distances between distributions, choosing a tuning parameter to specify the weightage for different group of distances.
-Furthermore, the data needs to be appropriately transformed to ensure that the value of $wpd$ emphasizes distributional differences across categories and not across different data generating processes.
+Furthermore, the data needs to be appropriately transformed to ensure that the value of $wpd$ detect distributional differences across categories and not across different data generating processes.
+
+<!-- but not when underlying distributions are different -->
 
@@
 
-Most common way to measure divergence between distributions is the Kullback-Leibler (KL) divergence [@Kullback1951-jy].
+One of the most common ways to measure divergence between distributions is the Kullback-Leibler (KL) divergence [@Kullback1951-jy].
 The KL divergence denoted by $D(q_1||q_2)$ is a non-symmetric measure of the difference between two probability distributions $q_1$ and $q_2$ and is interpreted as the amount of information lost when $q_2$ is used to approximate $q_1$.
@@
 
-In this section, we provide a method to select important harmonies by eliminating all harmonies for which patterns are not significant by employing randomization test.
+A harmony is referred to as "significant" if there is a significant distributional difference of the measured variable between different categories of the harmony.
+In this section, a selection criterion to choose significant harmonies is provided, thereby eliminating all harmonies that exhibit complete randomness in the measured variable.
+The distance measure $wpd_{norm}$ is used as a test statistic to test the null hypothesis that any given harmony is not significant.
+We select only those harmonies for which the test fails.
+The significant harmonies are then ranked basis how well they capture variation in the measured variable.
+
+<!-- .
+Randomization tests (permutation tests) generates a random distribution by re-ordering the observed data and allows us to test if the observed data is significantly different from any random distribution.
+-->
+<!-- the harmonies are not significant under null hypothesis and then test if our hypotheses are true: -->
+
+<!--   $H_0$: harmonies are not significant -->
+<!--   $H_1$: at least one harmony is significant -->
+
+<!-- we provide a method to select important harmonies by eliminating all harmonies for which patterns are not significant by employing randomization test.
 Randomization tests (permutation tests) generates a random distribution by re-ordering our observed data and allow to test if the observed data is significantly different from any random distribution.
 Complete randomness in the measured variable indicates that the process follows a homogeneous underlying distribution over the whole time series, which essentially implies there is no interesting distinction across any different categories of the cyclic granularities.
-
-## Choosing a threshold
-
-A randomization test involves calculating a test statistic, randomly shuffling the data and calculating the test statistic several times to obtain a distribution of the test statistic.
+-->
+
+## Choosing a threshold and selection criterion
+
+<!-- Under the null hypothesis, the harmonies are not significant. -->
+
+A threshold and consequently a selection criterion is chosen using the notion of Randomization tests.
+The data is permuted several times and $wpd_{norm}$ is computed for each of the permuted data sets to obtain the sampling distribution of $wpd_{norm}$ under the null hypothesis.
+If the null hypothesis is true, then $wpd_{norm}$ obtained from the original data set would be a likely value in the sampling distribution.
+But in case the null hypothesis is not true, then it is less probable that $wpd_{norm}$ obtained for the original data will be from the same distribution.
+This idea is utilized to come up with a threshold for selection, denoted by $wpd_{threshold}$, defined as the $99^{th}$ percentile of the sampling distribution.
+A harmony is selected if the value of $wpd_{norm}$ for that harmony is greater than the chosen threshold.
+The detailed algorithm for choosing a threshold and selection procedure is listed as follows:
+
+<!-- The selection criterion is stated as follows: for $(i \in {1, 2, \dots, H_{N_C}})$, select $H_i$ if $wpd_i > wpd_{threshold}$, else reject. -->
+
+- **Input:** All harmonies of the form $\{(A, B), A = \{ a_j: j = 1, 2, \dots, J\}, B = \{ b_k: k = 1, 2, \dots, K\}\}$, $\forall (A, B) \in H_{N_C}$.
+
+- **Output:** Harmony pairs $(A, B)$ for which $wpd_{norm}$ is significant.
+
+1. Fix harmony pair $(A, B)$.
+
+2. Given the measured variable; $\{v_t: t=0, 1, 2, \dots, T-1\}$, $wpd_{norm}$ is computed and is represented by $wpd^{A, B}_{obs}$.
+
+3. From the original sequence a random permutation is obtained: $\{v_t^{1}: t=0, 1, 2, \dots, T-1\}$.
+
+4. $wpd_{norm}$ is computed for the permuted sequence of the data and is represented by $wpd^{A, B}_{1}$.
+
+5.  Steps (3) and (4) are repeated a large number of times $M$ ($M = 200$).
+
+6. For each permutation, one $wpd^{A, B}_{i}$ is obtained. Define $wpd_{sample} = \{wpd^{A, B}_{1} wpd^{A, B}_{2}, \dots, wpd^{A, B}_{M}\}$.
+
+7. Repeat Steps (1-6) for all harmony pairs $(A, B) \in H_{N_C}$ and stored $wpd^{all}_{sample}$.
+
+8. $99^{th}$ percentiles of $wpd^{all}_{sample}$ is computed and stored in $wpd_{threshold99}$
+
+7. If $wpd^{A, B}_{obs} > wpd_{threshold99}$, harmony pair $(A, B)$ is selected with a 1% level of significance, otherwise rejected.
+
+Similarly, a harmony pair $(A, B)$ is selected with a 5% and 10% level of significance if $wpd^{A, B}_{obs} > wpd_{threshold95}$ and $wpd^{A, B}_{obs} > wpd_{threshold90}$, where  $wpd_{threshold95}$ and $wpd_{threshold90}$ denote the $95^{th}$ and $90^{th}$ percentile of $wpd^{all}_{sample}$ respectively.
+A harmony significant at 1%, 5% and 10% levels are tagged as \*\*\*, \*\*, \* respectively.
+
+## Ranking
+
+The distribution of $wpd_{norm}$ is expected to be similar for all harmonies under the null hypothesis, since they have been adjusted for different number of categories for the harmonies or underlying distribution of the measured variable.
+Hence, the values of $wpd_{norm}$ for different harmonies are comparable and can be used to rank the significant harmonies.
+A higher value of $wpd_{norm}$ for a harmony indicates that higher maximum variation in the measured variable is captured through that harmony.
+Figure \ref{fig:null4by2} presents the results of $wpd_{norm}$ from the illustrative designs in Section \ref{sec:computation-wpd}.
+The value of $wpd_{norm}$ under null design (a) is the least, followed by (b), (c) and (d).
+This aligns with the principle of $wpd_{norm}$, which is expected to have lowest value for null designs and highest for designs of the form $D_{var_{all}}$ (d).
+Moreover, note the relative differences in $wpd_{norm}$  values between (b) and (c).
+The value of the tuning parameter $\lambda$ is set to $0.67$, which has resulted in giving more emphasis to differences in x-axis categories.
+
+<!-- ## Choosing a threshold -->
+
+<!-- A randomization test involves calculating a test statistic, randomly shuffling the data and calculating the test statistic several times to obtain a distribution of the test statistic.
 But we will use this procedure to obtain a threshold such that harmony pairs with a $wpd_{norm}$ value higher than this threshold will only be considered significant.
-The process of choosing a threshold is described as follows:
+The process of choosing a threshold is described as follows: -->
 
@@
 <!-- **Assumption:** random permutation of the data keeping the categories of the cyclic granularities constant. -->
-
-- **Input:** All harmonies of the form $\{(A, B), A = \{ a_j: j = 1, 2, \dots, J\}, B = \{ b_k: k = 1, 2, \dots, K\}\}$  with $A$ placed across x-axis and $B$ across facets $\forall (A, B) \in N_C$.
-
-- **Output:** Harmony pairs $(A, B)$ for which $wpd_{norm}$ is significant.
-
-1. Fix harmony pair $(A, B)$.
-
-2. Given the data; $\{v_t: t=0, 1, 2, \dots, T-1\}$, the $wpd_{norm}$ is computed and is represented by $wpd_{obs}$.
-
-3. From the original sequence a random permutation is obtained: $\{v_t^*: t=0, 1, 2, \dots, T-1\}$.
-
-4. $wpd_{norm}$ is computed for the permuted sequence of the data and is represented by $wpd_{perm_1}$.
-
-5.  Steps (3) and (4) are repeated a large number
-of times $M$ (M = 200).
-
-6. For each permutation, one $wpd_{perm_i}$ is obtained.   Define $wpd_{sample} = \{wpd_{perm_1}, wpd_{perm_2}, \dots, wpd_{perm_M}\}$.
-
-7. Repeat Steps (1-6) for all harmony pairs $(A, B) \in H_{N_C}$ and store it in $wpd^{all}_{sample}$.
-
-8. $99^{th}$ percentiles of $wpd^{all}_{sample}$ is computed and stored in $wpd_{threshold99}$
-
-7. If $wpd_{obs_{A, B}} > wpd_{threshold99}$, harmony pair $(A, B)$ is selected with a 99% level of significance and otherwise rejected.
-
-Similarly, a harmony pair $(A, B)$ is selected with a 95% and 90% level of significance if $wpd_{obs_{A, B}} > wpd_{threshold95}$ and $wpd_{obs_{A, B}} > wpd_{threshold90}$, where  $wpd_{threshold95}$ and $wpd_{threshold90}$ denote the $95^{th}$ and $90^{th}$ percentile of $wpd^{all}_{sample}$ respectively.
 
@@
 
-<!-- 1. Given the data; $\{v_t: t=0, 1, 2, \dots, T-1\}$, the $wpd_{norm}$ is computed and is represented by $wpd_{obs}$. -->
-
-<!-- 2. From the original sequence a random permutation is obtained: $\{v_t^*: t=0, 1, 2, \dots, T-1\}$. -->
-
-<!-- 3. $wpd_{norm}$ is computed for the permuted sequence of the data and is represented by $wpd_{perm_1}$. -->
-
-<!-- 4.  Steps (2) and (3) are repeated a large number -->
-<!-- of times M (M = 200). -->
-
-<!-- 5. For each permutation, one $wpd_{perm_i}$ is obtained. Define $wpd_{sample} = \{wpd_{perm_1}, wpd_{perm_2}, \dots, wpd_{perm_M}\}$. -->
-
-<!-- 6. $95^{th}$ percentile of this $wpd_{sample}$ distribution is computed and stored in $wpd_{threshold}$. -->
-
-<!-- 7. If $wpd_{obs}> wpd_{threshold}$, harmony pairs are accepted. Only one threshold for all harmony pairs. -->
-
-## Simulation design
-
+## Simulations
+
+Simulations are conducted to understand the efficacy of the test.
 Observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = \{3, 7, 14\}$ and $nfacet = \{2, 9, 10\}$.
@@
 Also, these would constitute to be the estimated size and power of the test.
+The results are included in details in the Supplementary paper.
 
@@
 
-### Results
-
-The results for this section is WIP and to be included in details in the Supplementary paper.
-Also, Figure \ref{fig:plot-all-new3} presents the results of $wpd_{norm}$ from the illustrative designs in Section \ref{sec:computation-wpd}.
-As expected, the value of $wpd_{norm}$ under null design is the least (a), followed by (b, c and d).
-Moreover, note the relative difference in $wpd_{norm}$ values as we move from  a to d, which aligns with the idea of $wpd_{norm}$, since the differences between x categories are up-weighed by design.
+<!-- ### Results -->
 
@@
 Simulation studies were carried out to study the behavior of $wpd$, build the normalization method as well as compare and evaluate different normalization approaches.
-R version 4.0.1 (2020-06-06) is used with the platform: x86_64-apple-darwin17.0 (64-bit) running under: macOS Mojave 10.14.6 and MonaRCH, which is a next-generation HPC/HTC Cluster, designed from the ground up to address the computing needs of the Monash HPC community.
+R version 4.0.1 (2020-06-06) is used with the platform: x86_64-apple-darwin17.0 (64-bit) running under: macOS Mojave 10.14.6 and MonaRCH, which is a next-generation High Power Computing (HPC) Cluster, addressing the needs of the Monash HPC community.
 
@@
 id4_tsibble <- elec %>%
-  filter(id== 4)
+  filter(id == 4)
 
 id5_tsibble <- elec %>%
-  filter(id== 5)
+  filter(id == 5)
 

### 2021-05-26 simulations/supplementary/test-hpc/R-ind/size-supplementary.R

@@ -13,10 +13,10 @@ simtable <-  expand.grid(x_levels = c(3, 7, 14),
                          facet_levels = c(2, 9, 10)) %>%
   mutate(design = c("null", "varf","varx", "varall", "null", "varf", "varx", "varall", "null"))
 
-sample_seed = seq(1000, 10999, by = 1000)
+sample_seed = seq(1000, 10999, by = 10)
 npermj <- 200
 ntimesj <- 500
-nsampj <- 10
+nsampj <- 100
 wj <- 2
 # distj <- simj$dist
 # seedj <- simj$seed

### 2021-05-26 paper/main.Rmd
Introduction minor changes

@@
 However, all of them would not be interesting to discern important patterns in the energy usage.
-Only those displays, which have "significant" distributional differences between categories of the cyclic granularity would be informative and consequently, the corresponding cyclic granularity can be tagged as a "significant" one.
+Only those displays, which have "significant" distributional differences between categories of the cyclic granularity would be informative.
 
@@
 Figure \ref{fig:id2}(b) shows the distribution of energy consumption across months January to June.
-The median and quartile deviation of energy usage in Jan and Feb are generally on a much higher side, possibly due to the usage of air conditioners (Jan, Feb are peak summer in Australia), however for other months (Mar-Jun, autumn and winter), the smaller median and quartile deviation indicate a more regular behavior.
-It also implies this household do not use as much heater as compared to air conditioner.
+The median and quartile deviation of energy usage in Jan and Feb are generally on a much higher side, possibly due to the usage of air conditioners (Jan, Feb are peak summer in Australia), however for other months (Mar-Jun, autumn and winter), the smaller median and quartile deviation indicate a more consistent behavior.
+It might also imply thats this household do not use as much heater as compared to air conditioner.
 A lot of households in Victoria use gas heating and hence the usage of heaters might not be reflected here.
-Figure \ref{fig:id2}a slice it down further by showing the usage distribution across hour-of-day conditional on month-of-year.
-It shows the hourly usage over a day do not remain across months.
+Figure \ref{fig:id2}(a) slice it down further by showing the usage distribution across hour-of-day conditional on month-of-year.
+It shows the hourly usage over a day do not remain same across months.
 Unlike other months, the 75th and 90th percentile for all hours of the day in January are high, pretty close and are not characterized by a morning and evening peak.
-This implies usage of air conditioners is pretty common for this household.
-The household in Figure \ref{fig:id2}a has 90th percentile consumption higher in summer months relative to autumn or winter, but the 75th and 90th percentile are far apart in all months, implying that the second household resorts to air conditioning much less regularly than the first one.
+The household in Figure \ref{fig:id2}(b) has 90th percentile consumption higher in summer months relative to autumn or winter, but the 75th and 90th percentile are far apart in all months, implying that the second household resorts to air conditioning much less regularly than the first one.
 The differences seem to be more prominent across month-of-year (facets) than hour-of-day (x-axis) for this households, whereas they are prominent for both cyclic granularities for the first household.
@@
 
- * devise a framework for choosing a threshold, which results in detection of only significantly interesting patterns;
-
- * show that the proposed distance metric could be used to rank the interesting patterns based on how well they capture the variation in the measured variable since they have been normalized for relevant parameters.
+ * devise a selection criterion by choosing a threshold, which results in detection of only significantly interesting patterns;
+
+ * show that the proposed distance metric could be used to rank the interesting patterns across different datasets and temporal granularities since they have been normalized for relevant parameters.
 
 The article is organized as follows.
-Section \ref{sec:computation-wpd} introduces a new distance measure, discusses the reasoning behind choosing such a measure and presents some results to study the behavior of the measure.
-Section \ref{sec:norm-wpd} describes a methodology to normalize the distance measure so that it can qualify as a measure that can be compared across different comparisons and datasets.
+Section \ref{sec:computation-wpd} introduces a new distance measure, discusses the reasoning and details the computation.
 Section \ref{sec:rank-wpd} discusses how to choose a threshold to select only significant harmonies.

### 2021-05-26 paper/main.Rmd
till distance between distributions

@@
 It might be argued that it is not clear if (b) should precede or succeed (c) in the ranking.
-Gestalt theory suggests that when items are placed in close proximity, people assume that they are in the same group because they are close to one another and apart from other groups.
+Gestalt theory suggests items placed at close proximity can be compared more easily, because people assume that they are in the same group and apart from other groups.
 With this principle in mind, display (b) is considered less informative as compared to display (c) in emphasizing the distributional differences.
@@
 Let $v = \{v_t: t = 0, 1, 2, \dots, T-1\}$ be a continuous variable observed across $T$ time points.
-This  data structure with $J$ x-axis levels and $K$ facet levels is referred to as a $(K, J)$ panel.
+This  data structure with $J$ x-axis levels and $K$ facet levels is referred to as a $(J, K)$ panel.
 For example, a $(2, 3)$ panel will have cyclic granularities with 2 x-axis levels and 3 facet levels.
@@
 
-The computation of the distance measure $wpd$ for a panel involves characterizing distributions, computing distances between distributions, choosing a tuning parameter to specify the weightage for different group of distances.
+The computation of the distance measure $wpd$ for a panel involves characterizing distributions, computing distances between distributions, choosing a tuning parameter to specify the weightage for different group of distances and summarizing those weighted distances appropriately to estimate maximum variation.
 Furthermore, the data needs to be appropriately transformed to ensure that the value of $wpd$ detect distributional differences across categories and not across different data generating processes.
@@
 The KL divergence denoted by $D(q_1||q_2)$ is a non-symmetric measure of the difference between two probability distributions $q_1$ and $q_2$ and is interpreted as the amount of information lost when $q_2$ is used to approximate $q_1$.
-Although the KL divergence measures the “distance” between two distributions, it is not a distance measure since it is not symmetric and does not satisfy the triangle inequality.
+Although the KL divergence measures the “distance” between two distributions, it is not a distance measure since it is not symmetric.
 The Jensen-Shannon divergence [@Menendez1997-in] based on the Kullback-Leibler divergence is symmetric and it always has a finite value.
-The square root of the Jensen-Shannon divergence is a metric, often referred to as Jensen-Shannon distance.
-Other common measures of distance between distributions are Hellinger distance, total variation distance and Fisher information metric.
-In this paper, the pairwise distances between the distributions of the measured variable are obtained through Jensen-Shannon distance (JSD), defined by,
+In this paper, the pairwise distances between the distributions of the measured variable are obtained through the square root of the Jensen-Shannon divergence, called Jensen-Shannon distance (JSD) and is defined by,
 
@@
 $D(q_1||q_2) := \int^\infty_{-\infty} q_1(x)f(\frac{q_1(x)}{q_2(x)})$ is the KL divergence between distributions $q_1$ and $q_2$.
+Other common measures of distance between distributions are Hellinger distance, total variation distance and Fisher information metric.
 

### 2021-05-26 paper/main.Rmd
major and minor axis change

@@
 Therefore, exploring univariate time series data amounts to exploring the distribution of the measured variable across different categories of the cyclic granularities.
-\noindent Take the example of the electricity smart meter data used in @wang2020calendar for four households in Melbourne, Australia.
+\noindent Take the example of the  = tricity smart meter data used in @wang2020calendar for four households in Melbourne, Australia.
 Figure \ref{fig:onegran} shows the distribution of energy usage of one household (id 2) across cyclic granularity a) hour-of-day and b) month-of-year.
@@
     strip.background = element_blank(),
-    strip.text.y  = element_blank(), plot.margin = unit(c(0, -2, 0, 0), "cm"))
+    strip.text.y  = element_blank(), plot.margin = unit(c(0, -2, 0, 0), "cm")) + ggtitle("(a)")
 
@@
   #geom_point(size = 0.1, colour = "black", alpha = 0.3) +
-  geom_line(size = 0.1, colour = "blue", alpha = 0.6) +
+  geom_line(size = 0.1, colour = "blue") +
   facet_wrap(~id, 
@@
   theme_grey() + 
-  ylab("linear energy demand (kwh) for September") + ggtitle("b") +
-  theme(panel.grid.major.x = element_blank())
+  ylab("linear energy demand (kwh) for September") + ggtitle("(b)") +
+  theme(panel.grid.major.x = element_blank()) +
+  scale_x_datetime("Date", date_labels = "%b %d",
+                   breaks = "1 week",
+                   date_minor_breaks = "1 day")  + theme_bw() +
+  theme(panel.grid.major.x =  element_line(colour = "#A9A9A9"),
+        panel.grid.minor.x =  element_line(colour = "#D3D3D3"))
 

### 2021-05-26 paper/main.Rmd
application fig descr change

@@
 
-_Comparing households and validating patterns from linear display_
-
- Figure \ref{fig:dotplot-8} helps to compare households through the heatmap (a) and validate the results of the heatmap through linear display in (b).
-(b) contains the raw data for a month (Sep-2019).
+_Detecting patterns for households not apparent from linear display_
+
+\noindent Figure \ref{fig:dotplot-8} helps to compare households through the heatmap (a) and emphasizes patterns not discernible through linear display in (b).
+(b) contains the raw data for a month (Sep-2019), where the major and minor x-axis corresponds to weeks and days respectively.
 In (a), the value of $wpd_{norm}$ filled as colors, implying darker cells correspond to more significant a harmony pair.
@@
 This might be due to their flexible work routines or different day-off.
-The periodic pattern is very similar to id 8, which has a very different total energy usage.
-Households id 2 and 3 are similar, in terms of linear display and heatmap, which implies that similar periodic behavior can stem from households with different demographics.
+id 7 and 8 have same significant harmonies inspite of having very different total energy usage.
+Note that the $wpd_{norm}$ values are computed over the entire range, but the linear display is zoomed into September, which might throw some light on repetitive patterns in the households.
+
+<!-- Households id 2 and 3 are similar, in terms of linear display and heatmap, which implies that similar periodic behavior can stem from households with different demographics. -->
 
@@
 
-```{r dotplot-8, fig.cap = "Harmony pairs are shown for all household ids.
-The darker the colour, the higher the importance of the harmony.
-Also, the ones bordered red are selected with 90 percent significance level.
-Visualizing the pairs in this way helps us to see the important cyclic granularities along the x-axis and facet along with the information that which households should be analyzed together.", fig.height = 8}
+```{r dotplot-8, fig.cap = " A heatmap across harmonies (a) and line plot (b) showing energy usage for all household ids.
+The darker the colour in (a), the higher the harmony is ranked.
+Visualizing the harmony pairs in this way helps us to see the important cyclic granularities along the x-axis, facet or both.
+It further shows which households have significant patterns across similar temporal granularities.
+For eg, id 7 and 8 have significant patterns across (hod, dow) and (dow, hod), which was not apparent in (a).", fig.height = 8}
 # elec_sig_split <- elec_harmony_all %>%
@@
 The distribution of energy demand with dow as the x-axis and hod as the facets for both of these households can help justify the selection.
-Figure \ref{fig:gravitas-plot-8} show that the distribution of energy consumption changes across both dow and hod for id 4, but it is not so different for id 5, as apparent from the scale of the usage.
-Although the differences might seem significant at first, with closer inspection it could be seen that the scale of the demand is lower in this case and hence the differences are not large enough to cross the threshold for significance.
+Figure \ref{fig:gravitas-plot-8} show that the distribution of energy consumption changes across both dow and hod for id 4 for most hours, but it is not so different for id 5 for as many hours.
+
+<!-- Although the differences might seem significant at first, with closer inspection it could be seen that the scale of the demand is lower in this case and hence the differences are not large enough to cross the threshold for significance.
+-->
 

### 2021-05-27 paper/main.Rmd
bringing all results in simulation

@@
 
-\noindent _Simulation design_
-
- Observations are generated from a Gamma(2,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
-That is, data is being generated for each of the panels $(2, 2), (2, 3), (2, 5) \dots, (50, 31), (50, 50)$.
-For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
-That is, if we consider a $(2, 2)$ panel, $500$ observations are generated for each of the possible subsets, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
-The values of $wpd$ is obtained for each of the panels.
-This design corresponds to $D_{null}$ as each combination of categories in a panel are drawn from the same distribution.
-Furthermore, the data is simulated for each of the panels $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
-$wpd_{l, s}$ denotes the value of $wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.
-
 - _Permutation approach:_ This method is somewhat similar in spirit to bootstrap or permutation tests, where the goal is to test the hypothesis that the groups under study have identical distributions.
@@
 This design corresponds to $D_{null}$ as each combination of categories in a panel are drawn from the same distribution.
-Furthermore, the data is simulated for each of the panels $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
+Furthermore, the data is simulated for each of the panels $nsim=200$ times, so that the distribution oaf $wpd$ under $D_{null}$ could be observed.
 $wpd_{l, s}$ denotes the value of $wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.
@@
 -->
-
-```{r raw, fig.cap = "Distribution of $wpd$ is plotted across different $nx$ and $nfacet$ categories under $D_{null}$.
-Both shape and scale of the distribution changes for different comparisons.
-This is not desirable since under null design, the distribution of the distance measure is not expected to capture any differences."}
-
-```
-
-```{r quadratic, fig.cap = "$wpd$ is plotted against $nx*nfacet$ (the maximum number of pairwise comparisons) and the blue line represents the median of the multiple values for each $nx*nfacet$.
-The median increases abruptly for lower values of $nx*nfacet$ and slowly for higher $nx*nfacet$.
-Thus, the measure will have higher values for higher levels in $nx$ or $nfacet$."}
-```
 
@@
 -->
-
-```{r norm, fig.cap = "Distribution of $wpd_{perm}$ is plotted across different $nx$ and $nfacet$ categories.
-Both shape and scale of the distributions are now similar for different panels under the null design."}
-```
-
-```{r glm-tab}
-broom::tidy(glm_fit) %>% kable(caption = "Results of generalised linear model to capture the relationship between wpd and number of comparisons.")
-```
-
-```{r wpd-glm-dist, fig.cap = " The distribution of $wpd_{glm}$ is plotted. The distributions are more similar across higher nx and nfacet and dissimilar for fewer nc and nfacets."}
-
-```
-
-```{r hist-qq-new, fig.cap = "In panel a, the histogram of $wpd_{glm-scaled}$ is plotted.
-In part b, the QQ plot is shown with the theoretical quantiles on the x-axis and $wpd_{glm-scaled}$ quantiles on the y-axis.
-The distribution looks symmetric and looks like normal except in the tails.", eval = FALSE}
-
-```
-
-```{r dist-new-same-scale-link, fig.cap = "$wpd_perm$ and $wpd_{glm-scaled}$ are plotted together on the same scale.
-They also have the same location and hence the values from these two approaches could be compared across panels.
-$wpd_{glm-scaled}$ would be used to normalise $wpd_{raw}$ for higher $nx$ and $nfacet$ and $wpd_{glm-scaled}$ would be used for smaller levels to alleviate the problem of computational time."}
-
-```
 
@@
 
-## Simulations
+<!-- 14, 20, 31, 50\}$.
+For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
+The values of $wpd_{norm}$ is obtained for each of the panels for the designs $D_{null}$, $D_{var_x}$, $D_{var_f}$ and $D_{var_{all}}$.
+$wpd_{threshold}$ is computed from all of these panels together and the number of times a harmony pair $(A, B) \in H_{N_C}$ is selected when in fact it was of the design $D_{null}$ is noted.
+This entire process is repeated for several null data sets to see the number of times any harmony pair $(A, B) \in H_{N_C}$ is selected under null.
+-->
+
+<!-- ### Results -->
+
+```{r varall-new}
+
+```
+
+```{r varx-new}
+
+```
+
+```{r varf-new}
+```
+
+```{r null-new}
+
+```
+
+```{r plot-all-new3, fig.cap = "$wpd_{norm}$ values for the four illustrative designs are presented here.
+As expected, the value of $wpd_{norm}$ under null design is the least (a), followed by (b, c and d).
+Moreover, the relative difference is interesting as c is closer to d than b, since the differences between x categories are up-weighed by design.", dependson= "null4by2"}
+
+```
+
+# Simulations
+
+## Behavior of distance measures
+
+\noindent _Simulation design_
+
+\noindent Observations are generated from a Gamma(2,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
+That is, data is being generated for each of the panels $(2, 2), (2, 3), (2, 5) \dots, (50, 31), (50, 50)$.
+For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
+That is, if we consider a $(2, 2)$ panel, $500$ observations are generated for each of the possible subsets, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
+The values of $wpd$ is obtained for each of the panels.
+This design corresponds to $D_{null}$ as each combination of categories in a panel are drawn from the same distribution.
+Furthermore, the data is simulated for each of the panels $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
+$wpd_{l, s}$ denotes the value of $wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.
+
+\noindent _Results_
+
+Figure \ref{fig:raw} shows that both the location and scale of the distributions change across panels.
+This is not desirable under $D_{null}$ as it would mean comparisons of $wpd$ values is not appropriate across different $nx$ and $nfacet$.
+Figure \ref{fig:norm} shows the location and scale similar across different $nx$ and $nfacet$ are same by using $wpd_{perm}$.Figure \ref{fig:wpd-glm-dist} shows the modeling approach brings the distribution of measures for different panels similar for higher values of $nx$ and $nfacet$.
+Finally, Figure \ref{fig:dist-new-same-scale-link} shows the distribution of $wpd_perm$ and $wpd_{glm-scaled}$ in the same scale to show that a combination approach could be used for higher values of levels to alleviate the computational time of permutation approach.
+
+```{r raw, fig.cap = "Distribution of $wpd$ is plotted across different $nx$ and $nfacet$ categories under $D_{null}$.
+Both shape and scale of the distribution changes for different comparisons.
+This is not desirable since under null design, the distribution of the distance measure is not expected to capture any differences."}
+```
+
+```{r quadratic, fig.cap = "$wpd$ is plotted against $nx*nfacet$ (the maximum number of pairwise comparisons) and the blue line represents the median of the multiple values for each $nx*nfacet$.
+The median increases abruptly for lower values of $nx*nfacet$ and slowly for higher $nx*nfacet$.
+Thus, the measure will have higher values for higher levels in $nx$ or $nfacet$.", eval = FALSE}
+```
+
+```{r norm, fig.cap = "Distribution of $wpd_{perm}$ is plotted across different $nx$ and $nfacet$ categories.
+Both shape and scale of the distributions are now similar for different panels under the null design."}
+```
+
+```{r wpd-glm-dist, fig.cap = " The distribution of $wpd_{glm}$ is plotted. The distributions are more similar across higher nx and nfacet and dissimilar for fewer nc and nfacets."}
+
+```
+
+```{r hist-qq-new, fig.cap = "In panel a, the histogram of $wpd_{glm-scaled}$ is plotted.
+In part b, the QQ plot is shown with the theoretical quantiles on the x-axis and $wpd_{glm-scaled}$ quantiles on the y-axis.
+The distribution looks symmetric and looks like normal except in the tails.", eval = FALSE}
+
+```
+
+```{r dist-new-same-scale-link, fig.cap = "$wpd_perm$ and $wpd_{glm-scaled}$ are plotted together on the same scale.
+They also have the same location and hence the values from these two approaches could be compared across panels.
+$wpd_{glm-scaled}$ would be used to normalise $wpd_{raw}$ for higher $nx$ and $nfacet$ and $wpd_{glm-scaled}$ would be used for smaller levels to alleviate the problem of computational time."}
+```
+
+## Choosing threshold
+
+```{r glm-tab}
+broom::tidy(glm_fit) %>% kable(caption = "Results of generalised linear model to capture the relationship between wpd and number of comparisons.")
+```
+
+### Design
 
@@
 
-<!-- 14, 20, 31, 50\}$.
-For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
-The values of $wpd_{norm}$ is obtained for each of the panels for the designs $D_{null}$, $D_{var_x}$, $D_{var_f}$ and $D_{var_{all}}$.
-$wpd_{threshold}$ is computed from all of these panels together and the number of times a harmony pair $(A, B) \in H_{N_C}$ is selected when in fact it was of the design $D_{null}$ is noted.
-This entire process is repeated for several null data sets to see the number of times any harmony pair $(A, B) \in H_{N_C}$ is selected under null.
--->
-
-<!-- ### Results -->
-
-```{r varall-new}
-
-```
-
-```{r varx-new}
-
-```
-
-```{r varf-new}
-```
-
-```{r null-new}
-
-```
-
-```{r plot-all-new3, fig.cap = "$wpd_{norm}$ values for the four illustrative designs are presented here.
-As expected, the value of $wpd_{norm}$ under null design is the least (a), followed by (b, c and d).
-Moreover, the relative difference is interesting as c is closer to d than b, since the differences between x categories are up-weighed by design.", dependson= "null4by2"}
-
-```
-
-## Simulation environment
+## Environment
 
@@
 
-```{r gravitas-plot-8, message = FALSE, warning=FALSE,fig.cap="Distribution of energy demand shown for household id 1 across hod in x-axis and wd-wnd in facets in a) and just the reverse in b).
-In c), distribution of energy demand for household id:4 shown across hod and wd-wnd.
-It can be seen that the differences in distributions are more apparent when viewed in a) as compared to b).
-It seems like there is more difference in the distributions of hod for b) compared to c).
-This also confers with the value of the normalised measure shown in Figure 11."}
+```{r gravitas-plot-8, message = FALSE, warning=FALSE,fig.cap="Distribution of energy demand shown for household id 4 (a) and 5 (b) across dow in x-axis and hod in facets.
+The value of the normalised measure suggests that the harmony pair (dow, hod) is significant for household id 4, but not for 5.
+This implies that distributional differences are captured more by this harmony for id 4, which is apparent from the display with more fluctuations across median and 75th percentile."}
 

### 2021-05-30 paper/main.Rmd
changing abstract

@@
 abstract: |
- Periodic patterns or associations in large univariate time series data could be discerned by analysing the behaviour across cyclic temporal granularities, which are temporal deconstructions accounting for repetitive behaviour.
-The temporal granularities form ordered categorical variables and display of distributions of the univariate response variable across two or more combinations of these categorical variable can help explore periodicities, patterns and anomalies.
-A  pair of granularities that can be meaningfully examined together are called “harmonies” and the ones which cannot be are called “clashes”.
-Even after excluding clashes, the list of harmonies that could potentially be displayed is huge and hence overwhelming for human consumption.
-This work provides a methodology to screen the most informative graphics from the plethora of choices by introducing a distance measure that could be compared across harmonies with varied levels and data sets.
-Moreover, this distance measure could also be used to rank the s = ted harmonies basis how well they capture the variation in the measured variable.
-All the methods are implemented in the open source R package `hakear`.
+ Patterns or associations in large univariate time series data could be explored by analyzing the behavior across cyclic temporal granularities, which are temporal deconstructions accounting for repetitive behavior, for eg, hour-of-the-day, work-day/weekend, or holidays.
+This way of exploring time series analysis, however, presents itself with a plethora of displays that are potentially overwhelming for human consumption.
+This work provides a methodology to screen and rank the displays that are most informative in discerning distributional differences.
+This is done by introducing a distance measure for one or a pair of cyclic granularities that could be compared across different levels and data sets.
+All the methods are implemented in the open-source R package `hakear`.
 

### 2021-05-30 simulations/supplementary/one-gran/raw/null_design_quantrans/R-ind/raw_pairwise_N01.R

@@ -1,0 +1,63 @@
+#This script calculates raw mmpd for each simulation scenario
+##Read Simulation Table
+
+.libPaths(c("~/R/libs", .libPaths()))
+library(distributional)
+library(readr)
+library(drake)
+library(tidyverse)
+library(hakear)
+
+set.seed(9999)
+
+nsim = 200
+# change path while running it on HPC
+simtable<-read_csv(here::here('simulations/supplementary/one-gran/sim_table.csv'))
+#simtable<-read_csv('../../../sim_table/sim_table.csv')
+
+### Extract flags from simulation scenario
+
+#scen<- 2 #If running within R uncomment this.  This will only run first scenario
+scen<-as.numeric(commandArgs()[[6]]) # If running batch job uncomment this
+
+simj<-simtable[scen,] #Extract row of table
+nfacetj<-simj$nfacet # Which nfacet level
+nxj<-simj$nx #Which nx level
+
+#create data for each row for null normal
+
+sim_null_normal = function(nxj, nfacetj){
+  rep(distributional::dist_normal(0, 1), 
+      times = nxj*nfacetj)
+}
+
+sim_panel_data = 
+  hakear::sim_panel(nx = nxj,
+                    nfacet = nfacetj, 
+                    ntimes = 500, 
+                    sim_dist = sim_null_normal(nxj, nfacetj)) %>% 
+  unnest(c(data)) %>% ungroup()
+
+set.seed(1111)
+
+  raw_dist <- map(seq_len(nsim), function(i)
+{
+  new_sim_data = sample(sim_panel_data$sim_data, 
+                        size = nrow(sim_panel_data))
+  new_data = sim_panel_data %>% 
+    select(-sim_data) %>% 
+    mutate(sim_data = new_sim_data)
+  
+  # for creating one raw mmpd
+  raw_mmpd = compute_pairwise_max(new_data, 
+                                 gran_x = "id_x",
+                                 gran_facet = "id_facet",
+                                 response = sim_data) %>% 
+    as_tibble() %>% mutate(perm_id = i)
+  
+}) %>% bind_rows()
+
+saveRDS(raw_dist,
+          paste0('simulations/supplementary/one-gran/raw/null_design_quantrans/data-ind/wpd_N01/',
+                 nxj,'_',
+                 nfacetj,'_wpd.rds'))

### 2021-05-30 paper/main.Rmd
changed discussion

@@
 
-Exploratory data analysis involve many iterations of finding and summarizing patterns.
-With temporal data available at more and more finer scales, exploring periodicity has become overwhelming with so many possible granularities to explore.
-A common solution would be to zoom into “interesting” segments, but there is no way to know the “interesting” segments a priori.
-This work refines the search of periodic patterns by identifying those for which the differences between the displayed distributions is greatest, and rating them in order of importance for exploration.
-
-A future direction of work could be to look at more individuals/subjects and group them according to similar periodic behavior.
-Behaviors across different harmonies would be varying for subjects and it would be hard to track the behavior when the number of individuals rise.
-One way to find groups would be to actually locate clusters who have similar periodic behavior.
+Exploratory data analysis involves many iterations of finding and summarizing patterns.
+With temporal data available at finer scales, exploring time series has become overwhelming with so many possible granularities to explore.
+A common solution is to aggregate and look at the patterns across usual granularities like hour-of-day or day-of-week, but there is no way to know the “interesting” granularities a priori.
+A huge number of displays need to be analyzed or we might end up missing informative granularities.
+This work refines the search of informative granularities by identifying those for which the differences between the displayed distributions are greatest and rating them in order of importance of capturing maximum variation.
+
+The significant granularities across different datasets (individuals/subjects) do not imply similar patterns across different datasets.
+They simply mean that maximum distributional differences are being captured across those granularities.
+A future direction of work is to be able to explore and compare many individuals/subjects together for similar patterns across significant granularities.
 

### 2021-05-30 paper/main.Rmd
captions change

@@
 Therefore, exploring univariate time series data amounts to exploring the distribution of the measured variable across different categories of the cyclic granularities.
-\noindent Take the example of the  = tricity smart meter data used in @wang2020calendar for four households in Melbourne, Australia.
+\noindent Take the example of the  electricity smart meter data used in @wang2020calendar for four households in Melbourne, Australia.
 Figure \ref{fig:onegran} shows the distribution of energy usage of one household (id 2) across cyclic granularity a) hour-of-day and b) month-of-year.
@@
 
-```{r onegran, fig.cap="something"}
+```{r onegran, fig.cap="Boxplots showing the distribution of one household across one cyclic granularity at a time - (a) hour-of-day and (b) and month-of-year.
+The daily and annual periodic behavior of energy is apparent in (a) and (b) respectively, with daily peaks occuring in morning and evening hours when members in the house are present and active, more volatility (usage of air conditioner) in summer months (jan, feb) due to air conditioners and more consistent behavior in winter and autumn months (mar, apr, may, june).
+"}
 ```
@@
 <!-- what is the dimension of the problem -->
-\noindent The dimension of this problem, however, increases when considering two cyclic granularities.
+\noindent The dimension of this problem, however, increases when considering more than one cyclic granularity.
 Let $N_C$ be the total number of cyclic granularities of interest.
-That essentially implies there are $^{N_C}P_2$ possible pairwise plots exhaustively, with one of the two cyclic granularities acting as the conditioning variable.
+That essentially implies ,  for two cyclic granularities, there are $^{N_C}P_2$ possible pairwise plots exhaustively, with one of the two cyclic granularities acting as the conditioning variable.
 This is large and overwhelming for human consumption.<!-- Scagnostics literature --> This problem is similar to Scagnostics (Scatterplot Diagnostics) by @tukey1988computer, which is used to identify meaningful patterns in large collections of scatterplots.
@@
 
-```{r id2, fig.cap = "Distribution of energy consumption displayed through area quantile plots across two cyclic granularities month-of-year and hour-of-day for id2 (left) and id4 (right).
+```{r id2, fig.cap = "Distribution of energy consumption displayed through area quantile plots across two cyclic granularities month-of-year and hour-of-day and two households.
 The black line is the median, whereas the orange band covers the 25th to 75th percentile and the green band covers the 10th to 90th percentile.
-Difference between the 90th and 75th quantiles is less for (Jan, Feb) in id2 suggesting that it is a more frequent user of air conditioner than id4.
-Energy consumption for id2 changes across both granularities, whereas for id4 daily pattern stays same irrespective of the months."}
+Difference between the 90th and 75th quantiles is less for (Jan, Feb) for the first household (a), suggesting that it is a more frequent user of air conditioner than the second household (b).
+Energy consumption for in (a) changes across both granularities, whereas for (b) daily pattern stays same irrespective of the months."}
 ```

### 2021-05-31 paper/main.Rmd
till combination approach

@@
 
-# A distance measure for distributional differences in harmonies {#sec:computation-wpd}
-
-We propose a measure called Weighted Pairwise Distances ($wpd$) to assess structure in the measured variable across two cyclic granularities.
+# Proposed distance measure {#sec:computation-wpd}
+
+We propose a measure called Weighted Pairwise Distances ($wpd$) to detect distributional differences in the measured variable across cyclic granularities.
 
@@
 are $3$ standard deviations apart, but they do not change across facets.
-\ref{fig:null4by2}d takes a step further by varying the distribution across both facet and x-axis categories by  $3$ standard deviations.
+Figure \ref{fig:null4by2}d takes a step further by varying the distribution across both facet and x-axis categories by  $3$ standard deviations.
 If the panels are to be ranked in order of capturing maximum variation in the measured variable from minimum to maximum, then an obvious choice would be placing (a) followed by (b), (c) and then (d).
@@
 With this principle in mind, display (b) is considered less informative as compared to display (c) in emphasizing the distributional differences.
+Considering one cyclic granularity, we would have only two design choices similar to (a) and (c), corresponding to no difference and significant differences between categories of that cyclic granularity only.
 The proposed measure $wpd$ is constructed in a way so that it could be used to rank panels of different designs as well as test if a design is interesting.
-This measure is an estimate of the maximum variation in the measured variable explained by the panel.
+This measure is aimed to be an estimate of the maximum variation in the measured variable explained by the panel.
 A higher value of  $wpd$ would indicate that the panel is interesting to look at, whereas a lower value would indicate otherwise.
@@
 
+\noindent Let the number of cyclic granularities considered in the display be $m$.
+The notations and methodology are described in detail for $m=2$.
+But it can be easily extended to $m>2$.
 Consider two cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.
@@
 Finally, $D_{var_{all}}$ denotes those designs for which difference is observed across both $A$ and $B$.
+$m = 1$ is a special case of $m = 2$ with $J = 1$.
 
@@
 The computation of the distance measure $wpd$ for a panel involves characterizing distributions, computing distances between distributions, choosing a tuning parameter to specify the weightage for different group of distances and summarizing those weighted distances appropriately to estimate maximum variation.
-Furthermore, the data needs to be appropriately transformed to ensure that the value of $wpd$ detect distributional differences across categories and not across different data generating processes.
+Furthermore, the data needs to be appropriately transformed to ensure that the value of $wpd$ emphasizes detection of distributional differences across categories and not across different data generating processes.
 
@@
 The number of observations might vary widely across subsets due to the structure of the calendar, missing observations or uneven locations of events in the time domain.
-Quantiles of $v_{jk}$'s are chosen as a way to characterize distributions for the category $(a_j, b_k)$ in the paper $\forall j\in \{1, 2, \dots, J\}, k\in \{1, 2, \dots, K\}\}$.
+in this paper, quantiles of $v_{jk}$'s are chosen as a way to characterize distributions for the category $(a_j, b_k)$, $\forall j\in \{1, 2, \dots, J\}, k\in \{1, 2, \dots, K\}\}$.
 The quantile of a distribution with probability $p$ is defined as $Q(p)=F^{-1}(p) = inf\{x: F(x) >p\}$, $0<p< 1$ where $F(x)$ is the distribution function.
@@
 The KL divergence denoted by $D(q_1||q_2)$ is a non-symmetric measure of the difference between two probability distributions $q_1$ and $q_2$ and is interpreted as the amount of information lost when $q_2$ is used to approximate $q_1$.
-Although the KL divergence measures the “distance” between two distributions, it is not a distance measure since it is not symmetric.
-The Jensen-Shannon divergence [@Menendez1997-in] based on the Kullback-Leibler divergence is symmetric and it always has a finite value.
-In this paper, the pairwise distances between the distributions of the measured variable are obtained through the square root of the Jensen-Shannon divergence, called Jensen-Shannon distance (JSD) and is defined by,
+The KL divergence, however, is not symmetric and hence can not be considered as a "distance" measure.
+The Jensen-Shannon divergence [@Menendez1997-in] based on the Kullback-Leibler divergence is symmetric and has a finite value.
+Hence, in this paper, the pairwise distances between the distributions of the measured variable are obtained through the square root of the Jensen-Shannon divergence, called Jensen-Shannon distance (JSD) and is defined by,
 
@@
 
-Furthermore, these distances are distributed as chi-squared with $m$ degrees of freedom (@Menendez1997-in), if the continuous distribution is being discretized with $m$ discrete values.
+<!-- Furthermore, these distances are distributed as chi-squared with $m$ degrees of freedom (@Menendez1997-in), if the continuous distribution is being discretized with $m$ discrete values.
 Taking sample percentiles to approximate the integral would mean taking $m = 99$.
 As the degrees of freedom $m$ get larger, the chi-square distribution approaches the normal distribution.
+-->
 
@@
 \noindent Pairwise distances could be within-facets or between-facets.
-Figure \ref{fig:distance-explain} illustrates how the within-facet or between-facet distances are defined.
+Figure \ref{fig:distance-explain} illustrates how they are defined.
 Pairwise distances are within-facets when $b_{k} = b_{k'}$, that is, between pairs of the form $(a_{j}b_{k}, a_{j'}b_{k})$ as shown in panel (3) of Figure \ref{fig:distance-explain}.
@@
 A tuning parameter specifying the weightage given to the within-facet or between-facet categories can help to choose between designs like \ref{fig:null4by2}(b) and (c).
-Following the principle of Gestalt theory, the
-relative importance of within-facet and between-facet distances are taken to be $2:1$ and hence $\lambda = \frac{2}{3} = 0.67$.
+The tuning parameters should be chosen such that $\sum_{i=1}^m \lambda_i = 1$.
+When $m=2$, following the principle of Gestalt theory, $\lambda = \frac{2}{3} = 0.67$ is chosen to put a relative weightage of $2:1$ for within-facet and between-facet distances.
 No human experiment is conducted to justify this ratio, however, typically a tuning parameter $\lambda>0.5$ would tend to upweigh the within-facet distances and that with $<0.5$ would upweigh the between-facet distances (refer to the Supplementary section of the paper for more details).
@@
 
-Ideally it is desired that $wpd$ takes a higher value only if there is a significant difference between distributions across facet or x-axis categories, and not because the number of categories $J$ or $K$ is high.
-Therefore, in order to compare $wpd$ across panels with different levels, the impact of different number of comparisons need to be eliminated through some adjustment.
-Henceforth, we call the adjusted measure as $wpd_{norm}$.
-Two approaches for adjusting for the number of comparisons are discussed, both of which are substantiated using simulations.
-The first one, denoted as $wpd_{perm}$, involves a permutation method to make the distribution of the adjusted distance measure similar for different comparisons.
-The second one ($wpd_{glm-scaled}$) fits a model to represent the relationship between $wpd_{raw}$ and number of comparisons and defines the adjusted measure as the residual from the model.
-
-- _Permutation approach:_ This method is somewhat similar in spirit to bootstrap or permutation tests, where the goal is to test the hypothesis that the groups under study have identical distributions.
-This method, in essence, accomplishes a different goal of making the distribution of the different groups (panels in our case) same under $D_{null}$.
-The values of $wpd_{raw}$ is computed on many permuted ($nperm$) data sets for the $l^{th}$ panel and stored in $wpd_{perm-data}$.
-$nperm=100$ is considered and the adjusted distance measure
-$wpd_{perm}$ is computed as follows:
-
-$$wpd_{perm} = \frac{(wpd_{raw} - \bar{wpd_{perm-data}})}{sd(wpd_{perm-data})}$$
-where $\bar{wpd_{perm-data}}$ and $sd(wpd_{perm-data})$ are the mean and standard deviation of $wpd_{perm-data}$ respectively.
+Ideally it is desired that $wpd$ takes a higher value only if there is a significant difference between distributions across categories, and not because the number of categories $J$ or $K$ is high.
+That is, under designs like $D_{null}$, the distribution of the $wpd$ values should not differ for
+different number of categories.
+Only then the distance measure could be compared across panels with different levels.
+This calls for an adjusted measure, which normalizes for the different number of comparisons.
+We denote it by $wpd_{norm}$.
+Two approaches for adjusting the number of comparisons are discussed, both of which are substantiated using simulations.
+The first one defines an adjusted measure $wpd_{perm}$ based on permutation method to remove the effect of different comparisons.
+The second approach fits a model to represent the relationship between $wpd_{raw}$ and number of comparisons and defines the adjusted measure ($wpd_{glm-scaled}$) as the residual from the model.
+
+_Permutation approach_
+
+This method is somewhat similar in spirit to bootstrap or permutation tests, where the goal is to test the hypothesis that the groups under study have identical distributions.
+This method accomplishes a different goal of finding the null distribution for different groups (panels in our case) and standardizing the raw values using that distribution.
+The values of $wpd_{raw}$ is computed on many ($nperm$) permuted data sets stored in $wpd_{perm-data}$.
+Then $wpd_{perm}$ is computed as follows:
+
+\begin{align*}
+wpd_{perm} = \frac{(wpd_{raw} - \bar{wpd_{perm-data}})}{sd(wpd_{perm-data})}
+\end{align*}
+
+\noindent where $\bar{wpd_{perm-data}}$ and $sd(wpd_{perm-data})$ are the mean and standard deviation of $wpd_{perm-data}$ respectively.
 Standardizing  $wpd$ in the permutation approach ensures that the distribution of $wpd_{perm}$ has the same $mean = 0$ and $sd = 1$ across all comparisons under $D_{null}$.
-While this works successfully to make the location and scale similar across different $nx$ and $nfacet$ (as seen in Figure \ref{fig:norm}), it is computationally heavy and time consuming, and hence less user friendly when being actually used in practice.
+While this works successfully to make the location and scale similar across different $nx$ and $nfacet$, it is computationally heavy and time consuming, and hence less user friendly when being actually used in practice.
 Hence, another approach to adjustment, with potentially less computational time, is proposed.
 
-- _Modeling approach:_  $wpd_{raw}$ being a Jensen-Shannon distance, follows a Chi-square distribution (@JSD), which is a special case of Gamma distribution.
-Hence, a Gamma generalized linear model (GLM) for $wpd_{raw}$ is fitted with number of comparisons as the explanatory variable, which is of the following form:
-
-$$y_l = a+b*log(z_l) + e_l , \quad l = (1, 2, \dots, L)$$,
-
-\noindent where $y_l = median_s(wpd_{l, s})$, $wpd_{l, s}$ denotes the value of $wpd_{raw}$ obtained for the $l^{th}$ panel and $s^{th}$ simulation, $z_l$ is the number of groups $(nx*nfacet)$ in the $l^{th}$ panel and $e_l$ are idiosyncratic errors.
+<!-- for the $l^{th}$ panel and -->
+
+_Modeling approach_
+
+In this approach, a Gamma generalized linear model (GLM) for $wpd_{raw}$ is fitted with number of comparisons as the explanatory variable.
+Since, $wpd_{raw}$ is a Jensen-Shannon distance, it follows a Chi-square distribution (@Menendez1997-in), which is a special case of Gamma distribution.
+Furthermore, the mean response is bounded, since any JSD is bounded by $1$ given that base $2$ logarithm is used (@Lin1991-pt).
+Hence, by @Faraway2016-uk, an inverse link is used for the model, which is of the following form:
+
+$$y = a+b*log(z) + e$$ ,
+
+\noindent where $y = wpd_{raw}$, $z = (nx*nfacet)$ is the number of groups and $e$ are idiosyncratic errors.
 Let $E(y) = \mu$ and $a + b*log(z) = g(\mu)$ where $g$ is the link function.
@@
 
-- _Combination approach:_ The simulation results show that adjustment through the modeling approach leads to very similar distribution across high $nx$ and $nfacet$ (higher than $5$) and not so much for lower $nx$ and $nfacet$.
-Hence, the computational load of permutation approach could be alleviated by using the modeling approach for the higher $nx$ and $nfacet$, however, it is important that we use the permutation approach for lower $nx$ and $nfacet$.
+_Combination approach_
+
+The simulation results (\ref{Sec:}) show that adjustment through the modeling approach leads to very similar distribution across high $nx$ and $nfacet$ (higher than $5$) and not so much for lower $nx$ and $nfacet$.
+Hence, the computational load of permutation approach is alleviated by using the modeling approach for the higher $nx$ and $nfacet$, however, it is important that we use the permutation approach for lower $nx$ and $nfacet$.
 The adjusted variables from the two approaches have to be brought to the same scale so that for smaller categories, permutation approach is used and for larger categories, modeling approach is used.
@@
 ```
+
+$$y_l = a+b*log(z_l) + e_l , \quad l = (1, 2, \dots, L)$$,
+
+\noindent where $y_l = median_s(wpd_{l, s})$, $wpd_{l, s}$ denotes the value of $wpd_{raw}$ obtained for the $l^{th}$ panel and $s^{th}$ simulation, $z_l$ is the number of groups $(nx*nfacet)$ in the $l^{th}$ panel and $e_l$ are idiosyncratic errors.
+Let $E(y) = \mu$ and $a + b*log(z) = g(\mu)$ where $g$ is the link function.
+Then $g(\mu)=  1/\mu$ and $\hat \mu  = 1/(\hat a + \hat b log(z))$.
+The residuals from this model $(y-\hat y) = (y-1/(\hat a + \hat b log(z)))$ would be expected to have no dependency on $z$.
+Thus, $wpd_{glm}$ is chosen as the residuals from this model and is defined as:
+$wpd_{glm} = wpd_{raw} - 1/(\hat a + \hat b*log(nx*nfacet))$.
 

### 2021-05-31 paper/main.Rmd
upto section 2 done

@@
 The median and quartile deviation of energy usage in Jan and Feb are generally on a much higher side, possibly due to the usage of air conditioners (Jan, Feb are peak summer in Australia), however for other months (Mar-Jun, autumn and winter), the smaller median and quartile deviation indicate a more consistent behavior.
-It might also imply thats this household do not use as much heater as compared to air conditioner.
+It might also imply that this household do not use as much heater as compared to air conditioner.
 A lot of households in Victoria use gas heating and hence the usage of heaters might not be reflected here.
@@
 
-Ideally it is desired that $wpd$ takes a higher value only if there is a significant difference between distributions across categories, and not because the number of categories $J$ or $K$ is high.
-That is, under designs like $D_{null}$, the distribution of the $wpd$ values should not differ for
-different number of categories.
+Ideally, it is desired that $wpd$ takes a higher value only if there is a significant difference between distributions across categories, and not because the number of categories $J$ or $K$ is high.
+That is, under designs like $D_{null}$, the distribution of the $wpd$ values should not differ for a different number of categories.
 Only then the distance measure could be compared across panels with different levels.
 This calls for an adjusted measure, which normalizes for the different number of comparisons.
-We denote it by $wpd_{norm}$.
+We denote it by $wpd$.
 Two approaches for adjusting the number of comparisons are discussed, both of which are substantiated using simulations.
-The first one defines an adjusted measure $wpd_{perm}$ based on permutation method to remove the effect of different comparisons.
-The second approach fits a model to represent the relationship between $wpd_{raw}$ and number of comparisons and defines the adjusted measure ($wpd_{glm-scaled}$) as the residual from the model.
+The first one defines an adjusted measure $wpd_{perm}$ based on the permutation method to remove the effect of different comparisons.
+The second approach fits a model to represent the relationship between $wpd_{raw}$ and the number of comparisons and defines the adjusted measure ($wpd_{glm-scaled}$) as the residual from the model.
 
@@
 \noindent where $\bar{wpd_{perm-data}}$ and $sd(wpd_{perm-data})$ are the mean and standard deviation of $wpd_{perm-data}$ respectively.
-Standardizing  $wpd$ in the permutation approach ensures that the distribution of $wpd_{perm}$ has the same $mean = 0$ and $sd = 1$ across all comparisons under $D_{null}$.
+Standardizing  $wpd$ in the permutation approach ensures that the distribution of $wpd_{perm}$ under $D_{null}$ has the same $mean = 0$ and $\sigma^2_{perm} = 1$ across all comparisons.
 While this works successfully to make the location and scale similar across different $nx$ and $nfacet$, it is computationally heavy and time consuming, and hence less user friendly when being actually used in practice.
@@
 Furthermore, the mean response is bounded, since any JSD is bounded by $1$ given that base $2$ logarithm is used (@Lin1991-pt).
-Hence, by @Faraway2016-uk, an inverse link is used for the model, which is of the following form:
-
-$$y = a+b*log(z) + e$$ ,
-
-\noindent where $y = wpd_{raw}$, $z = (nx*nfacet)$ is the number of groups and $e$ are idiosyncratic errors.
+Hence, by @Faraway2016-uk, an inverse link is used for the model, which is of the  form $y = a+b*log(z) + e$, where $y = wpd_{raw}$, $z = (nx*nfacet)$ is the number of groups and $e$ are idiosyncratic errors.
 Let $E(y) = \mu$ and $a + b*log(z) = g(\mu)$ where $g$ is the link function.
@@
 Thus, $wpd_{glm}$ is chosen as the residuals from this model and is defined as:
-$wpd_{glm} = wpd_{raw} - 1/(\hat a + \hat b*log(nx*nfacet))$.
+$$wpd_{glm} = wpd_{raw} - 1/(\hat a + \hat b*log(nx*nfacet))$$
+The distribution of $wpd_{glm}$ under $D_{null}$ will have $mean = 0$, since it is the residuals from the model, and a constant variance $\sigma^2_{glm}$, which might not equal 1.
 
@@
 
-The simulation results (\ref{Sec:}) show that adjustment through the modeling approach leads to very similar distribution across high $nx$ and $nfacet$ (higher than $5$) and not so much for lower $nx$ and $nfacet$.
-Hence, the computational load of permutation approach is alleviated by using the modeling approach for the higher $nx$ and $nfacet$, however, it is important that we use the permutation approach for lower $nx$ and $nfacet$.
-The adjusted variables from the two approaches have to be brought to the same scale so that for smaller categories, permutation approach is used and for larger categories, modeling approach is used.
-The adjusted measure from the combination approach, denoted by $wpd_{norm}$ is defined as follows:
+The simulation results (\ref{Sec:}) show that the distribution of $wpd_{glm}$ under null is similar for high $nx$ and $nfacet$ (levels higher than $5$) and not so much for lower $nx$ and $nfacet$.
+Hence, a combination approach is proposed which chooses permutation approach for categories with smaller levels and modeling approach for categories with higher levels.
+This ensures that the computational load of the permutation approach is alleviated while maintaining similar null distribution across different categories.
+This approach, however, requires that the adjusted variables from the two approaches are brought to the same scale.
+We define $wpd_{glm-scaled} = wpd_{glm}*\sigma^2_{perm}/\sigma^2_{glm}$ as the transformed $wpd_{glm}$ with a similar scale as $wpd_{perm}$.
+The adjusted measure from the combination approach, denoted by $wpd$ is then defined as follows:
 
 \begin{equation}
-wpd_{norm} =
+wpd =
 \begin{cases}
@@
 \end{equation}
-where $wpd_{glm-scaled}$ is the transformed $wpd_{glm}$ with a similar scale as $wpd_{perm}$.
 
@@
 <!-- use later -->
-<!-- The measure $wpd_{norm}$ could potentially lead to comparison of the measure across different panels and also help distinguishing the interesting panels from a data set.
+<!-- The measure $wpd$ could potentially lead to comparison of the measure across different panels and also help distinguishing the interesting panels from a data set.
 We discuss two approaches for normalization, both of which are substantiated using simulations.
@@
 
-<!-- The transformed ${wpd}$ which is normalized for the values of $nx$ and $nfacet$ is denoted by $wpd_{norm}$.
-Two approaches have been employed - the first one involves a permutation method to make the distribution of the transformed $wpd$ similar for different comparisons and the second one fits a model to represent the relationship between the two variables and defines $wpd_{norm}$ as the residual of the model.
+<!-- The transformed ${wpd}$ which is normalized for the values of $nx$ and $nfacet$ is denoted by $wpd$.
+Two approaches have been employed - the first one involves a permutation method to make the distribution of the transformed $wpd$ similar for different comparisons and the second one fits a model to represent the relationship between the two variables and defines $wpd$ as the residual of the model.
 -->
@@
 
-<!-- This section reports the results of a simulation study that was carried out to evaluate the behavior of $wpd_{norm}$ under different designs and other potential factors.
-The behavior of $wpd_{norm}$ is explored in designs where there is in fact difference in distribution between facet categories ($D_{var_f}$) or across x-categories ($D_{var_x}$) or both ($D_{var_{all}}$).
+<!-- This section reports the results of a simulation study that was carried out to evaluate the behavior of $wpd$ under different designs and other potential factors.
+The behavior of $wpd$ is explored in designs where there is in fact difference in distribution between facet categories ($D_{var_f}$) or across x-categories ($D_{var_x}$) or both ($D_{var_{all}}$).
 Using $\omega =  \{1, 2, \dots, 10\}$ and $\lambda = seq(from  = 0.1, to = 0.9, by = 0.05)$, observations are drawn from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet =  \{2, 3, 5, 7, 14, 20, 31, 50\}$.
@@
 <!-- The tabulated values and graphical representations of the simulation results are provided in the Supplementary paper.
-The learning from the simulations are as follows: The values of $wpd_{norm}$ is least for $D_{null}$, followed by -->
+The learning from the simulations are as follows: The values of $wpd$ is least for $D_{null}$, followed by -->
 <!-- $D_{var_f}$, $D_{var_x}$ and $D_{var_{all}}$.
-This is a desirable result since the measure $wpd_{norm}$ was designed such that this relationship holds.
-Furthermore, the distribution of the measure $wpd_{norm}$ does not change for different facet and x categories.
-The distribution of $wpd_{norm}$ looks similar with at least the mean and standard of the distributions being uniform across panels.
-This means $wpd_{norm}$ could be used to measure differences in distribution across panels.
+This is a desirable result since the measure $wpd$ was designed such that this relationship holds.
+Furthermore, the distribution of the measure $wpd$ does not change for different facet and x categories.
+The distribution of $wpd$ looks similar with at least the mean and standard of the distributions being uniform across panels.
+This means $wpd$ could be used to measure differences in distribution across panels.
 Also, note that since the data is processed using normal-quantile-transform, this measure is independent of the initial distribution of the underlying data and hence is also comparable across different data sets.
-This is valid for the case when sample size $ntimes$ for each combination of categories is at least 30 and  $nperm$ used for computing $wpd_{norm}$ is at least 100.
-More detailed results about the properties of $wpd_{norm}$ could be found in the Supplementary paper.
+This is valid for the case when sample size $ntimes$ for each combination of categories is at least 30 and  $nperm$ used for computing $wpd$ is at least 100.
+More detailed results about the properties of $wpd$ could be found in the Supplementary paper.
 -->
@@
 In this section, a selection criterion to choose significant harmonies is provided, thereby eliminating all harmonies that exhibit complete randomness in the measured variable.
-The distance measure $wpd_{norm}$ is used as a test statistic to test the null hypothesis that any given harmony is not significant.
+The distance measure $wpd$ is used as a test statistic to test the null hypothesis that any given harmony is not significant.
 We select only those harmonies for which the test fails.
@@
 A threshold and consequently a selection criterion is chosen using the notion of Randomization tests.
-The data is permuted several times and $wpd_{norm}$ is computed for each of the permuted data sets to obtain the sampling distribution of $wpd_{norm}$ under the null hypothesis.
-If the null hypothesis is true, then $wpd_{norm}$ obtained from the original data set would be a likely value in the sampling distribution.
-But in case the null hypothesis is not true, then it is less probable that $wpd_{norm}$ obtained for the original data will be from the same distribution.
+The data is permuted several times and $wpd$ is computed for each of the permuted data sets to obtain the sampling distribution of $wpd$ under the null hypothesis.
+If the null hypothesis is true, then $wpd$ obtained from the original data set would be a likely value in the sampling distribution.
+But in case the null hypothesis is not true, then it is less probable that $wpd$ obtained for the original data will be from the same distribution.
 This idea is utilized to come up with a threshold for selection, denoted by $wpd_{threshold}$, defined as the $99^{th}$ percentile of the sampling distribution.
-A harmony is selected if the value of $wpd_{norm}$ for that harmony is greater than the chosen threshold.
+A harmony is selected if the value of $wpd$ for that harmony is greater than the chosen threshold.
 The detailed algorithm for choosing a threshold and selection procedure is listed as follows:
@@
 
-- **Output:** Harmony pairs $(A, B)$ for which $wpd_{norm}$ is significant.
+- **Output:** Harmony pairs $(A, B)$ for which $wpd$ is significant.
 
@@
 
-2. Given the measured variable; $\{v_t: t=0, 1, 2, \dots, T-1\}$, $wpd_{norm}$ is computed and is represented by $wpd^{A, B}_{obs}$.
+2. Given the measured variable; $\{v_t: t=0, 1, 2, \dots, T-1\}$, $wpd$ is computed and is represented by $wpd^{A, B}_{obs}$.
 
@@
 
-4. $wpd_{norm}$ is computed for the permuted sequence of the data and is represented by $wpd^{A, B}_{1}$.
+4. $wpd$ is computed for the permuted sequence of the data and is represented by $wpd^{A, B}_{1}$.
 
@@
 
-The distribution of $wpd_{norm}$ is expected to be similar for all harmonies under the null hypothesis, since they have been adjusted for different number of categories for the harmonies or underlying distribution of the measured variable.
-Hence, the values of $wpd_{norm}$ for different harmonies are comparable and can be used to rank the significant harmonies.
-A higher value of $wpd_{norm}$ for a harmony indicates that higher maximum variation in the measured variable is captured through that harmony.
-Figure \ref{fig:null4by2} presents the results of $wpd_{norm}$ from the illustrative designs in Section \ref{sec:computation-wpd}.
-The value of $wpd_{norm}$ under null design (a) is the least, followed by (b), (c) and (d).
-This aligns with the principle of $wpd_{norm}$, which is expected to have lowest value for null designs and highest for designs of the form $D_{var_{all}}$ (d).
-Moreover, note the relative differences in $wpd_{norm}$  values between (b) and (c).
+The distribution of $wpd$ is expected to be similar for all harmonies under the null hypothesis, since they have been adjusted for different number of categories for the harmonies or underlying distribution of the measured variable.
+Hence, the values of $wpd$ for different harmonies are comparable and can be used to rank the significant harmonies.
+A higher value of $wpd$ for a harmony indicates that higher maximum variation in the measured variable is captured through that harmony.
+Figure \ref{fig:null4by2} presents the results of $wpd$ from the illustrative designs in Section \ref{sec:computation-wpd}.
+The value of $wpd$ under null design (a) is the least, followed by (b), (c) and (d).
+This aligns with the principle of $wpd$, which is expected to have lowest value for null designs and highest for designs of the form $D_{var_{all}}$ (d).
+Moreover, note the relative differences in $wpd$  values between (b) and (c).
 The value of the tuning parameter $\lambda$ is set to $0.67$, which has resulted in giving more emphasis to differences in x-axis categories.
@@
 <!-- A randomization test involves calculating a test statistic, randomly shuffling the data and calculating the test statistic several times to obtain a distribution of the test statistic.
-But we will use this procedure to obtain a threshold such that harmony pairs with a $wpd_{norm}$ value higher than this threshold will only be considered significant.
+But we will use this procedure to obtain a threshold such that harmony pairs with a $wpd$ value higher than this threshold will only be considered significant.
 The process of choosing a threshold is described as follows: -->
 
-<!-- to test if there is any interesting pattern captured by the harmonies, which essentially implies if $wpd_{norm}$ is significantly different from zero.
-The percentages of times the $wpd_{norm}$ obtained from the permuted data is greater than or equal to the observed $wpd_{norm}$ is the p-value.
+<!-- to test if there is any interesting pattern captured by the harmonies, which essentially implies if $wpd$ is significantly different from zero.
+The percentages of times the $wpd$ obtained from the permuted data is greater than or equal to the observed $wpd$ is the p-value.
 The randomization test is described as follows: -->
@@
 This method is based on the generation of randomly chosen reassignments (permutations) of the data across different cyclic granularities and the computation of  -->
-<!-- $wpd_{norm}$ for each of these reassignments. -->
+<!-- $wpd$ for each of these reassignments. -->
 
@@
 This method is based on the generation of randomly chosen reassignments (permutations) of the data across different cyclic granularities and the computation of  -->
-<!-- $wpd_{norm}$ for each of these reassignments.
-The percentages of times the theoretical distribution greater than or equal to the respective observed $wpd_{norm}$ values are calculated and are used to obtain the P value.
+<!-- $wpd$ for each of these reassignments.
+The percentages of times the theoretical distribution greater than or equal to the respective observed $wpd$ values are calculated and are used to obtain the P value.
 The procedure for the permutation test is: -->
@@
 For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
-The values of $wpd_{norm}$ is obtained for each of the panels for the designs $D_{null}$, $D_{var_x}$, $D_{var_f}$ and $D_{var_{all}}$.
+The values of $wpd$ is obtained for each of the panels for the designs $D_{null}$, $D_{var_x}$, $D_{var_f}$ and $D_{var_{all}}$.
 $wpd_{threshold}$ is computed from all of these panels together and the number of times a harmony pair $(A, B) \in H_{N_C}$ is selected when in fact it was of the design $D_{null}$ is noted.
@@
 
-```{r plot-all-new3, fig.cap = "$wpd_{norm}$ values for the four illustrative designs are presented here.
-As expected, the value of $wpd_{norm}$ under null design is the least (a), followed by (b, c and d).
+```{r plot-all-new3, fig.cap = "$wpd$ values for the four illustrative designs are presented here.
+As expected, the value of $wpd$ under null design is the least (a), followed by (b, c and d).
 Moreover, the relative difference is interesting as c is closer to d than b, since the differences between x categories are up-weighed by design.", dependson= "null4by2"}
@@
 
-The smart meter data set for eight households in Melbourne has been utilized to see the use of $wpd_{norm}$ proposed in the paper.
+The smart meter data set for eight households in Melbourne has been utilized to see the use of $wpd$ proposed in the paper.
 The data has been cleaned to be a `tsibble` (@wang2019tsibble) containing half-hourly electricity consumption from Jul-2019 to Dec-2019 for each of the households, which is procured by them by downloading their data from the energy supplier/retailer.
@@
 
- $wpd_{norm}$ is computed for all harmony pairs $\in H_{N_C}$ and for each households $i \in i = \{1, 2, \dots, 8\}$.
+ $wpd$ is computed for all harmony pairs $\in H_{N_C}$ and for each households $i \in i = \{1, 2, \dots, 8\}$.
 The harmony pairs are then arranged in descending order and the important ones with significance level 1%, 5% and 10% are highlighted with `***`, `**` and `*` respectively.
@@
 (b) contains the raw data for a month (Sep-2019), where the major and minor x-axis corresponds to weeks and days respectively.
-In (a), the value of $wpd_{norm}$ filled as colors, implying darker cells correspond to more significant a harmony pair.
+In (a), the value of $wpd$ filled as colors, implying darker cells correspond to more significant a harmony pair.
 Also, the ones with `*` are significant at 95% level.
@@
 id 7 and 8 have same significant harmonies inspite of having very different total energy usage.
-Note that the $wpd_{norm}$ values are computed over the entire range, but the linear display is zoomed into September, which might throw some light on repetitive patterns in the households.
+Note that the $wpd$ values are computed over the entire range, but the linear display is zoomed into September, which might throw some light on repetitive patterns in the households.
 
@@
 However, the difference between morning and evening peaks are higher for weekends.
-Since $wpd_{norm}$ is designed to put more weightage on within-facet differences for $\lambda>0.5$, it makes sense that the pair (hod, wdwnd) has been ranked higher than (wdwnd, hod).
+Since $wpd$ is designed to put more weightage on within-facet differences for $\lambda>0.5$, it makes sense that the pair (hod, wdwnd) has been ranked higher than (wdwnd, hod).
 Panel c) shows the distribution of energy demand with weekday/weekend as the x-axis and week-of-month as the facets.

### 2021-05-31 paper/main.Rmd
application section fix

@@
 No behavioral pattern is likely to be discerned from this view.
-When we zoom into the linear representation of this series in Figure \ref{fig:linear-scale-8} (b) for September, some patterns are visible in terms of peaks and troughs, but we do not know if they are regular or what is their period.
+When we zoom into the linear representation of this series in Figure \ref{fig:dotplot-8} (b) for September, some patterns are visible in terms of peaks and troughs, but we do not know if they are regular or what is their period.
 Electricity demand, in general, has a daily and weekly periodic pattern.
@@
 Also, it is not clear if any other periodic patterns are present in any household which might have been hidden with this view.
-We start the analysis by choosing few harmonies, ranking them for each for these households, compare households to get more insights into\ what these rankings imply and if they could be used to remove some non-interesting harmonies.
-Furthermore, the ranking and selection of significant harmonies could be validated by analyzing the distribution of the energy usage across significant harmonies.
+We start the analysis by choosing few harmonies, ranking them for each of these households, compare households to get more insights into what these rankings imply.
+Furthermore, the ranking and selection of significant harmonies could be validated by analyzing the distribution of energy usage across significant harmonies.
 
@@
 In fig b, we can see some weekly patterns for the entire period and daily patterns for the highlighted week and there could be some other patterns visible in terms of peaks and troughs, but it is not clear if they are regular or significant.", fig.height=8, eval = FALSE}
+
 library(scales)
@@
 Most importantly, there are at most $3$ harmonies that are significant for any household.
-This is a huge reduction in number of potential harmonies to explore closely, starting from $42$.
+This is a huge reduction in the number of potential harmonies to explore closely, starting from $42$.
 
@@
 (b) contains the raw data for a month (Sep-2019), where the major and minor x-axis corresponds to weeks and days respectively.
-In (a), the value of $wpd$ filled as colors, implying darker cells correspond to more significant a harmony pair.
+In (a), the value of $wpd$ filled as colors, implying darker cells correspond to more significant harmony pairs.
 Also, the ones with `*` are significant at 95% level.
@@
 This might be due to their flexible work routines or different day-off.
-id 7 and 8 have same significant harmonies inspite of having very different total energy usage.
-Note that the $wpd$ values are computed over the entire range, but the linear display is zoomed into September, which might throw some light on repetitive patterns in the households.
+id 7 and 8 have the same significant harmonies despite having very different total energy usage.
+Note that the $wpd$ values are computed over the entire range, but the linear display is zoomed into September.
 
@@
 The distribution of energy demand with dow as the x-axis and hod as the facets for both of these households can help justify the selection.
-Figure \ref{fig:gravitas-plot-8} show that the distribution of energy consumption changes across both dow and hod for id 4 for most hours, but it is not so different for id 5 for as many hours.
+Figure \ref{fig:gravitas-plot-8} show that the median (black) and quartile deviation (orange) of energy consumption changes across both dow and hod for id 4 for most hours, but it is not so different for id 5 with differences captured only for $90^{th}$ percentile.
 
@@
 
-```{r gravitas-plot-8, message = FALSE, warning=FALSE,fig.cap="Distribution of energy demand shown for household id 4 (a) and 5 (b) across dow in x-axis and hod in facets.
-The value of the normalised measure suggests that the harmony pair (dow, hod) is significant for household id 4, but not for 5.
-This implies that distributional differences are captured more by this harmony for id 4, which is apparent from the display with more fluctuations across median and 75th percentile."}
+```{r gravitas-plot-8, message = FALSE, warning=FALSE,fig.cap="Comparing distribution of energy demand shown for household id 4 (a) and 5 (b) across dow in x-axis and hod in facets through quantile area plots.
+The value of $wpd$ in Table 3 suggests that the harmony pair (dow, hod) is significant for household id 4, but not for 5.
+This implies that distributional differences are captured more by this harmony for id 4, which is apparent from the display with more fluctuations across median and 75th percentile.
+Here, the median is represented by the black line, the orange area corresponds to quartile deviation and the green area corresponds to area between $10^{th}$ and $90^{th}$ quantile."}
 

### 2021-05-31 paper/main.Rmd
deleted significance levels as it is leading to confusion

@@
 
-7. If $wpd^{A, B}_{obs} > wpd_{threshold99}$, harmony pair $(A, B)$ is selected with a 1% level of significance, otherwise rejected.
-
-Similarly, a harmony pair $(A, B)$ is selected with a 5% and 10% level of significance if $wpd^{A, B}_{obs} > wpd_{threshold95}$ and $wpd^{A, B}_{obs} > wpd_{threshold90}$, where  $wpd_{threshold95}$ and $wpd_{threshold90}$ denote the $95^{th}$ and $90^{th}$ percentile of $wpd^{all}_{sample}$ respectively.
-A harmony significant at 1%, 5% and 10% levels are tagged as \*\*\*, \*\*, \* respectively.
+7. If $wpd^{A, B}_{obs} > wpd_{threshold99}$, harmony pair $(A, B)$ is selected, otherwise rejected.
+
+Similarly, a harmony pair $(A, B)$ could be selected if $wpd^{A, B}_{obs} > wpd_{threshold95}$ and $wpd^{A, B}_{obs} > wpd_{threshold90}$, where  $wpd_{threshold95}$ and $wpd_{threshold90}$ denote the $95^{th}$ and $90^{th}$ percentile of $wpd^{all}_{sample}$ respectively.
+A harmony selected using $99^{th}$,  $95^{th}$  and  $90^{th}$ are tagged as \*\*\*, \*\*, \* respectively.
 
@@
  $wpd$ is computed for all harmony pairs $\in H_{N_C}$ and for each households $i \in i = \{1, 2, \dots, 8\}$.
-The harmony pairs are then arranged in descending order and the important ones with significance level 1%, 5% and 10% are highlighted with `***`, `**` and `*` respectively.
+The harmony pairs are then arranged in descending order and highlighted with `***`, `**` and `*` corresponding to the  $99^{th}$,  $99^{th}$ and $99^{th}$ percentile threshold.
 Table \ref{tab:tab-rank-8} shows the rank of the harmonies for different households.

### 2021-06-01 paper/main.Rmd
distance measure simulation update

@@
 Similarly, a harmony pair $(A, B)$ could be selected if $wpd^{A, B}_{obs} > wpd_{threshold95}$ and $wpd^{A, B}_{obs} > wpd_{threshold90}$, where  $wpd_{threshold95}$ and $wpd_{threshold90}$ denote the $95^{th}$ and $90^{th}$ percentile of $wpd^{all}_{sample}$ respectively.
-A harmony selected using $99^{th}$,  $95^{th}$  and  $90^{th}$ are tagged as \*\*\*, \*\*, \* respectively.
+A harmony selected using $99^{th}$,  $95^{th}$  and  $90^{th}$ threshold are tagged as \*\*\*, \*\*, \* respectively.
 
@@
 
-## Behavior of distance measures
+## Behavior of raw and adjuted distance measures
 
@@
 
-\noindent Observations are generated from a Gamma(2,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
+\noindent Observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
 That is, data is being generated for each of the panels $(2, 2), (2, 3), (2, 5) \dots, (50, 31), (50, 50)$.
@@
 This is not desirable under $D_{null}$ as it would mean comparisons of $wpd$ values is not appropriate across different $nx$ and $nfacet$.
-Figure \ref{fig:norm} shows the location and scale similar across different $nx$ and $nfacet$ are same by using $wpd_{perm}$.Figure \ref{fig:wpd-glm-dist} shows the modeling approach brings the distribution of measures for different panels similar for higher values of $nx$ and $nfacet$.
-Finally, Figure \ref{fig:dist-new-same-scale-link} shows the distribution of $wpd_perm$ and $wpd_{glm-scaled}$ in the same scale to show that a combination approach could be used for higher values of levels to alleviate the computational time of permutation approach.
-
-```{r raw, fig.cap = "Distribution of $wpd$ is plotted across different $nx$ and $nfacet$ categories under $D_{null}$.
-Both shape and scale of the distribution changes for different comparisons.
-This is not desirable since under null design, the distribution of the distance measure is not expected to capture any differences."}
-```
-
-```{r quadratic, fig.cap = "$wpd$ is plotted against $nx*nfacet$ (the maximum number of pairwise comparisons) and the blue line represents the median of the multiple values for each $nx*nfacet$.
-The median increases abruptly for lower values of $nx*nfacet$ and slowly for higher $nx*nfacet$.
-Thus, the measure will have higher values for higher levels in $nx$ or $nfacet$.", eval = FALSE}
-```
-
-```{r norm, fig.cap = "Distribution of $wpd_{perm}$ is plotted across different $nx$ and $nfacet$ categories.
-Both shape and scale of the distributions are now similar for different panels under the null design."}
-```
-
-```{r wpd-glm-dist, fig.cap = " The distribution of $wpd_{glm}$ is plotted. The distributions are more similar across higher nx and nfacet and dissimilar for fewer nc and nfacets."}
-
-```
-
-```{r hist-qq-new, fig.cap = "In panel a, the histogram of $wpd_{glm-scaled}$ is plotted.
-In part b, the QQ plot is shown with the theoretical quantiles on the x-axis and $wpd_{glm-scaled}$ quantiles on the y-axis.
-The distribution looks symmetric and looks like normal except in the tails.", eval = FALSE}
-
-```
-
-```{r dist-new-same-scale-link, fig.cap = "$wpd_perm$ and $wpd_{glm-scaled}$ are plotted together on the same scale.
-They also have the same location and hence the values from these two approaches could be compared across panels.
-$wpd_{glm-scaled}$ would be used to normalise $wpd_{raw}$ for higher $nx$ and $nfacet$ and $wpd_{glm-scaled}$ would be used for smaller levels to alleviate the problem of computational time."}
-```
-
-$$y_l = a+b*log(z_l) + e_l , \quad l = (1, 2, \dots, L)$$,
-
-\noindent where $y_l = median_s(wpd_{l, s})$, $wpd_{l, s}$ denotes the value of $wpd_{raw}$ obtained for the $l^{th}$ panel and $s^{th}$ simulation, $z_l$ is the number of groups $(nx*nfacet)$ in the $l^{th}$ panel and $e_l$ are idiosyncratic errors.
-Let $E(y) = \mu$ and $a + b*log(z) = g(\mu)$ where $g$ is the link function.
-Then $g(\mu)=  1/\mu$ and $\hat \mu  = 1/(\hat a + \hat b log(z))$.
-The residuals from this model $(y-\hat y) = (y-1/(\hat a + \hat b log(z)))$ would be expected to have no dependency on $z$.
-Thus, $wpd_{glm}$ is chosen as the residuals from this model and is defined as:
-$wpd_{glm} = wpd_{raw} - 1/(\hat a + \hat b*log(nx*nfacet))$.
+\ref{tab:glm-tab} gives the summary of the generalised linear model to capture the relationship between $wpd_{raw}$ and number of comparisons.
+Thus, the model considered is $wpd_{l,s} = 23.69448+-1.02357*log(nx * nfacet)) + e$.
+The intercepts are similar independent of the starting distribution (Please refer to supplementary).
+Figure \ref{fig:dist-new-same-scale-link} shows the distribution of $wpd_{perm}$ and $wpd_{glm-scaled}$ in the same scale to show that a combination approach could be used for higher values of levels to alleviate the computational time of permutation approach.
+
+```{r raw, fig.cap = "Distribution of $wpd_{raw}$ is plotted across different $nx$ and $nfacet$ categories under $D_{null}$ through density and rug plots.
+Both location (blue line) and scale (orange marks) of the distribution shifts for different panels.
+This is not desirable since under null design, the distribution  is not expected to capture any differences."}
+```
+
+```{r glm-tab}
+
+```
+
+```{r wpd-glm-dist}
+
+```
+
+```{r hist-qq-new, eval = FALSE}
+
+```
+
+```{r quadratic, eval=FALSE}
+```
+
+```{r norm, eval}
+```
+
+```{r dist-new-same-scale-link, fig.cap = "The distribution of $wpd_{perm}$ and $wpd_{glm-scaled}$ are overlaid to compare the location and scale across different $nx$ and $nfacet$.
+$wpd_{norm}$ takes the value of $wpd_{perm}$ for lower levels, and $wpd_{glm-scaled}$ for higher levels to to alleviate the problem of computational time in permutation approaches.
+This is possible as the distribution of the adjusted measure looks similar for both appraches for higher levels."}
+```
+
+```{r }
+```
 
 ## Choosing threshold
-
-```{r glm-tab}
-broom::tidy(glm_fit) %>% kable(caption = "Results of generalised linear model to capture the relationship between wpd and number of comparisons.")
-```
 

### 2021-06-01 paper/main.Rmd
updated all simulation files

@@
 Exploratory data analysis, as coined by John W.
-Tukey (Tukey 1965) involves many iterations of finding structures and patterns that allow the data to be informative.
+Tukey [@Tukey1977-jx] involves many iterations of finding structures and patterns that allow the data to be informative.
 With temporal data available at finer scales, exploring time series data can become overwhelming with so many possible cyclic temporal granularities [@Gupta2020-vo], which are temporal deconstructions that represent cyclic repetitions in time, e.g.
@@
 ```{r onegran, fig.cap="Boxplots showing the distribution of one household across one cyclic granularity at a time - (a) hour-of-day and (b) and month-of-year.
-The daily and annual periodic behavior of energy is apparent in (a) and (b) respectively, with daily peaks occuring in morning and evening hours when members in the house are present and active, more volatility (usage of air conditioner) in summer months (jan, feb) due to air conditioners and more consistent behavior in winter and autumn months (mar, apr, may, june).
-"}
+The daily and annual periodic behavior of energy is apparent in (a) and (b) respectively, with daily peaks occuring in morning and evening hours when members in the house are present and active, more volatility (usage of air conditioner) in summer months (Jan, Feb) due to air conditioners and more consistent behavior in winter and autumn months (Mar, Apr, May, June)."}
 ```
@@
 \noindent Exploring the distribution of the measured variable across two cyclic granularities tend to provide more detailed information on its structure.
-Figure \ref{fig:id2}(a) shows that energy consumption is higher during the morning hours (5-8) when members in the household wake up and then again in the evening hours (17-20) possibly when members get back from work with maximum variation (large inter-quartile range) in behavior in the afternoon hours (12-16).
-Figure \ref{fig:id2}(b) shows the distribution of energy consumption across months January to June.
+Figure \ref{fig:onegran}(a) shows that energy consumption is higher during the morning hours (5-8) when members in the household wake up and then again in the evening hours (17-20) possibly when members get back from work with maximum variation (large inter-quartile range) in behavior in the afternoon hours (12-16).
+Figure \ref{fig:onegran}(b) shows the distribution of energy consumption across months January to June.
 The median and quartile deviation of energy usage in Jan and Feb are generally on a much higher side, possibly due to the usage of air conditioners (Jan, Feb are peak summer in Australia), however for other months (Mar-Jun, autumn and winter), the smaller median and quartile deviation indicate a more consistent behavior.
@@
 A lot of households in Victoria use gas heating and hence the usage of heaters might not be reflected here.
-Figure \ref{fig:id2}(a) slice it down further by showing the usage distribution across hour-of-day conditional on month-of-year.
+Figure \ref{fig:id2}(a) slice it down further by showing the usage distribution across hour-of-day conditional on month-of-year across two households (id 2 and 4).
 It shows the hourly usage over a day do not remain same across months.
@@
 
-# Ranking and selecting significant harmonies {#sec:rank-wpd}
-
-A harmony is referred to as "significant" if there is a significant distributional difference of the measured variable between different categories of the harmony.
+# Ranking and selection of cyclic granularities {#sec:rank-wpd}
+
+A cyclic granularity is referred to as "significant" if there is a significant distributional difference of the measured variable between different categories of the harmony.
 In this section, a selection criterion to choose significant harmonies is provided, thereby eliminating all harmonies that exhibit complete randomness in the measured variable.
@@
 
-## Choosing a threshold and selection criterion
+## Selection
 
@@
 This is not desirable under $D_{null}$ as it would mean comparisons of $wpd$ values is not appropriate across different $nx$ and $nfacet$.
-\ref{tab:glm-tab} gives the summary of the generalised linear model to capture the relationship between $wpd_{raw}$ and number of comparisons.
+\ref{tab:glm-tab} gives the summary of the generalized linear model to capture the relationship between $wpd_{raw}$ and number of comparisons.
 Thus, the model considered is $wpd_{l,s} = 23.69448+-1.02357*log(nx * nfacet)) + e$.
@@
 
-### Design
-
-Simulations are conducted to understand the efficacy of the test.
+\noindent _Simulation design_
+
 Observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = \{3, 7, 14\}$ and $nfacet = \{2, 9, 10\}$.
-The panel $(3, 2), (7,9), (14, 10)$ are considered to have design $D_{null}$.
-The panels $(7, 2), (14, 9)$ have design of the form $D_{var_f}$.
-$(14, 2), (3, 10)$ have design of the form $D_{var_x}$ and the rest are under $D_{var_{null}}$.
-We generate only one data set for which all these designs were simulated and consider this as the original data set.
-We generate $200$ repetitions of this experiment with different seeds and compute the proportion of times a panel is rejected when it is under $D_{null}$.
+This would result in 9 panels, viz, $(3, 2), (3, 9), (3, 10), \dots, (14,9), (14, 10)$.
+Few experiments were conducted.
+In the first scenario, data for all panels are simulated using the null design  $D_{null}$.
+In other scenarios, data simulated from the panel $(14, 2)$ and $(3, 10)$ are under $D_{vary_{all}}$.
+Moreover, $\omega = \{0.5, 2, 5\}$ are considered to examine if the proposed test is able to capture subtle differences and non-subtle differences when we shift from the null design.
+In the last scenario, we consider the panel $(3, 2), (7,9), (14, 10)$ to be under $D_{null}$, the panels $(7, 2), (14, 9)$ to be under $D_{var_f}$.
+$(14, 2), (3, 10)$ under $D_{var_x}$ and the rest under $D_{var_{null}}$.
+This is done to check if the consequent ranking procedure leads to designs like $D_{vary_{all}}$ to be chosen first followed by $D_{vary_{all}}$.
+We generate only one data set each for which these scenarios were simulated and consider this as the original data set.
+We generate $1000$ repetitions of this experiment with different seeds.
+
+\noindent _Results_
+
+The proportion of times a panel is rejected when it is under $D_{null}$ is computed with $wpd_{threshold99}$ and it is around $0.1$.
+This is obvious, since if the level of significance for each test is less than $0.01$ (as a result of choosing $99^{th}$ percentile as the threshold) and we have $9$ tests, the size for the entire test should be close to $0.01 *9 \approx 0.1$.
 We also compute the proportion of times a panel is rejected when it actually belongs to a non-null design.
@@
 Also, these would constitute to be the estimated size and power of the test.
-The results are included in details in the Supplementary paper.
+It is found that as we increase from low to high changes from the null distribution, the power increased.
+The results and graphics are included in details in the Supplementary paper.
+
+```{r, eval = FALSE}
+all_data <- read_rds("simulations/supplementary/test-hpc/data-agg/all_data.rds")
+
+# computes size for 99 percentile threshold
+data_summary <- all_data %>%
+  mutate(sig = if_else(significance!=99, 0, 99)) %>% 
+  group_by(seed_id) %>% 
+  summarize(sumsig = sum(sig)) %>% 
+  count(sumsig==0) %>% 
+  mutate(p_value = n/sum(n)) %>% 
+  slice(1)
+
+# plots
+ggplot() + 
+  geom_histogram(data = all_data, aes(x = wpd))  + 
+  geom_vline(data = data_summary, aes(xintercept = p_value),colour = "red") +
+  facet_grid(x_levels~facet_levels)
+
+```
 

### 2021-06-01 paper/paper-supplementary.Rmd
updated all simulation files

@@
 ## Results
+
+```{r hist-qq-new, fig.cap = "In panel a, the histogram of $wpd_{glm-scaled}$ is plotted.
+In part b, the QQ plot is shown with the theoretical quantiles on the x-axis and $wpd_{glm-scaled}$ quantiles on the y-axis.
+The distribution looks symmetric and looks like normal except in the tails.", eval = FALSE}
+
+```
+
+```{r quadratic, fig.cap = "$wpd$ is plotted against $nx*nfacet$ (the maximum number of pairwise comparisons) and the blue line represents the median of the multiple values for each $nx*nfacet$.
+The median increases abruptly for lower values of $nx*nfacet$ and slowly for higher $nx*nfacet$.
+Thus, the measure will have higher values for higher levels in $nx$ or $nfacet$.", eval = FALSE}
+```
+
+```{r norm, fig.cap = "Distribution of $wpd_{perm}$ is plotted across different $nx$ and $nfacet$ categories.
+Both shape and scale of the distributions are now similar for different panels under the null design."}
+```
+
+```{r wpd-glm-dist, fig.cap = " The distribution of $wpd_{glm}$ is plotted. The distributions are more similar across higher nx and nfacet and dissimilar for fewer nc and nfacets."}
+
+```
+
+$$y_l = a+b*log(z_l) + e_l , \quad l = (1, 2, \dots, L)$$,
+
+\noindent where $y_l = median_s(wpd_{l, s})$, $wpd_{l, s}$ denotes the value of $wpd_{raw}$ obtained for the $l^{th}$ panel and $s^{th}$ simulation, $z_l$ is the number of groups $(nx*nfacet)$ in the $l^{th}$ panel and $e_l$ are idiosyncratic errors.
+Let $E(y) = \mu$ and $a + b*log(z) = g(\mu)$ where $g$ is the link function.
+Then $g(\mu)=  1/\mu$ and $\hat \mu  = 1/(\hat a + \hat b log(z))$.
+The residuals from this model $(y-\hat y) = (y-1/(\hat a + \hat b log(z)))$ would be expected to have no dependency on $z$.
+Thus, $wpd_{glm}$ is chosen as the residuals from this model and is defined as:
+$wpd_{glm} = wpd_{raw} - 1/(\hat a + \hat b*log(nx*nfacet))$.

### 2021-06-01 paper/scripts/main.R

@@ -363,15 +363,25 @@ knitr::include_graphics(here::here("paper/Figs/dist_explain.png"))
 
 
 ##----raw
-G21 <- read_rds("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds")
+G21 <- read_rds("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds")
+
+summary_data <- G21 %>% 
+  group_by(nx, nfacet) %>% 
+  summarise(mean = mean(value))
 
 G21 %>% 
   ggplot(aes(x = value)) + 
-  geom_density(fill = "blue") +
+  geom_density(fill = "#999999") +
   facet_grid(nx~nfacet,
              labeller = "label_both") + 
-  scale_x_continuous(breaks = scales::breaks_extended(3)) + 
-  xlab("wpd")
+  xlab("raw values of wpd") +
+  geom_vline(data = summary_data, aes(xintercept  = mean), color = "#0072B2") +
+  geom_rug(sides = "b", colour = "#D55E00") + 
+  # scale_x_continuous(breaks = scales::breaks_extended(2)) +
+  theme_bw() +
+  theme(panel.grid.major.x = element_blank()) +
+  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=0.5))
+
 
 ##----quadratic
 G21 %>% 
@@ -414,14 +424,7 @@ G21 %>%
   geom_point(alpha = 0.5, size = 0.5) + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
   ylab("wpd normalised using linear modelling approach")
 
-
-
-
-
-
 ## ---- glm-tab
-
-
 
 G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds"))
 G21_median <- G21 %>% 
@@ -437,7 +440,7 @@ G21_sd  = G21 %>%
   )
   )
   ))
-scale_fac <- 1/G21_sd$wpd_glm %>% sd()
+#scale_fac <- 1/G21_sd$wpd_glm %>% sd()
 # checking the fit of the residuals from glm fit
 # fitted_glm <- fitted(glm_fit, type = "response")
 # residuals <- residuals.glm(glm_fit, type = "response")
@@ -458,8 +461,7 @@ scale_fac <- 1/G21_sd$wpd_glm %>% sd()
 #   ) +
[…]

### 2021-06-01 simulations/raw/null_design_quantrans/R-agg/makegraph02.R

@@ -10,14 +10,21 @@ makegraph02 <- function(folder_name){
   
 all_data <- read_rds(paste0("simulations/raw/null_design_quantrans/data-agg/all_data_", folder_name, ".rds"))
   
+summary_data <- all_data %>% 
+  group_by(nx, nfacet) %>% 
+  summarise(mean = mean(value))
 
 nxbyfacet_density <- all_data %>% 
   ggplot(aes(x = value)) + 
-  geom_density(fill = "blue") +
+  geom_density(fill = "#999999") +
   facet_grid(nx~nfacet,
              labeller = "label_both") + 
   xlab("wpd") +
-  scale_x_continuous(breaks = scales::breaks_extended(3))
+  geom_vline(data = summary_data, aes(xintercept  = mean), color = "#0072B2") +
+  geom_rug(sides = "b", colour = "#D55E00") + 
+ # scale_x_continuous(breaks = scales::breaks_extended(2)) +
+  theme_bw() +
+  theme(panel.grid.major.x = element_blank()) 
 
 ggsave(nxbyfacet_density, filename = paste0("simulations/raw/null_design_quantrans/figs/", "nxbyfacet_density_", folder_name,".png"))
 

### 2021-06-01 simulations/supplementary/one-gran/raw/null_design_quantrans/R-agg/aggregate01.R

@@ -7,12 +7,17 @@ library(rlang)
 
 aggregate01 <-  function(folder_name){
   
-all_files = list.files(path = paste0("simulations/raw/null_design_quantrans/data-ind/", folder_name), 
+all_files = list.files(path = ("simulations/▸ ⁨supplement/one-gran/raw/null_design_quantrans/data-ind/wpd_N01/"))
+
+
+all_files = list.files(path = paste0("simulations/vary_all/raw/data-ind/", folder_name), 
                        pattern = ".rds")
+
+
 
 names_levels <- map_dfr(all_files, 
                         function(x){
-                          z = str_split(str_remove(x, "_dist.rds"), "_") %>% 
+                          z = str_split(str_remove(x, "_wpd.rds"), "_") %>% 
                             unlist()
                           bind_cols(nx = as.numeric(z[1]),
                                     nfacet = as.numeric(z[2]))
@@ -23,7 +28,7 @@ names_levels <- map_dfr(all_files,
 # names_rep <- names_levels %>% slice(rep(1:n(), each = nrow(len_file)))
 
   
-all_files_path <- paste0("simulations/raw/null_design_quantrans/data-ind/",folder_name,"/",
+all_files_path <- paste0("simulations/supplementary/one-gran/raw/null_design_quantrans/data-ind/",folder_name,"/",
          all_files)  
   
 
@@ -38,7 +43,7 @@ all_data <- lapply(1:length(all_files_path), function(x){
   }) %>% bind_rows() %>% 
     arrange(nfacet, nx)
     
-write_rds(all_data, paste0("simulations/raw/null_design_quantrans/data-agg/all_data_", folder_name, ".rds"))
+write_rds(all_data, paste0("simulations/supplementary/one-gran/raw/null_design_quantrans/data-agg/all_data_", folder_name, ".rds"))
 }
 
 

### 2021-06-01 simulations/supplementary/test-hpc/R-ind/power-one-alternate-low-inc.R

@@ -1,0 +1,120 @@
+# This script computes power of the test in our paper 
+# low increment : 0.5 , medium increment : 2, high increment: 5
+# initial dist : N(0, 1)
+# only one alternate considered 
+# since all the harmonies need to be run at once, you can only run the seeds parallely, not all the harmonies.
+# sim_table should only contain the seeds in that case
+
+library(readr)
+library(dplyr)
+library(distributional)
+library(gravitas)
+library(here)
+library(purrr)
+library(tidyverse)
+library(purrr)
+library(hakear)
+
+# harmony_table<-read_csv(here::here('simulations/sim_table/sim_table.csv'))
+
+sample_seed <- seq(1000, 10999, by = 10) %>% as_tibble()
+simtable <- sample_seed
+scen <- as.numeric(commandArgs()[[6]])
+#scen = 2 # testing if works for one seed
+simj <- simtable[scen, ] # Extract row of table
+seedj <- simj$value # which seed with which simulations should be run
+
+
+harmony_table <- expand.grid(
+  x_levels = c(3, 7, 14),
+  facet_levels = c(2, 9, 10)
+) %>%
+  mutate(design = c("null", "null", "varall", "null", "null", "null", "null", "null", "null"))
+
+# parameters and design used for this simulation
+npermj <- 2
+ntimesj <- 500
+nsampj <- 10
+wj <- 0.5 # change this to change increment
+
+sim_null <- function(nxj, nfacetj, mean, sd, w = 0) {
+  rep(distributional::dist_normal(mu = mean, sigma = sd),
+      times = nxj * nfacetj
+  )
+}
+sim_varall <- function(nx, nfacet, mean, sd, w)
+{
+  dist_normal((mean + seq(0,
+                          (nx*
+                             nfacet - 1), by  = 1)*w), sd)
+}
+
+set.seed(seedj)
+## code for one harmony table starts
+sim_data_all <- map(
+  seq_len(nrow(harmony_table)),
+  function(x) {
+    y <- harmony_table %>% magrittr::extract(x, )
+    
+    # assigning different rows for different design
+    
+    # setting value of parameters
+    designj <- y$design
+    nfacetj <- y$facet_levels # Which nfacet level
+    nxj <- y$x_levels
+    
+    
+    if (designj == "null") {
+      sim_function <- sim_null
+    } else if (designj == "varx") {
+      sim_function <- sim_varx
+    } else if (designj == "varf") {
+      sim_function <- sim_varf
+    } else {
[…]

### 2021-06-01 simulations/supplementary/test-hpc/R-ind/power-one-alternate-med-inc.R

@@ -1,0 +1,120 @@
+# This script computes power of the test in our paper 
+# low increment : 0.5 , medium increment : 2, high increment: 5
+# initial dist : N(0, 1)
+# only one alternate considered 
+# since all the harmonies need to be run at once, you can only run the seeds parallely, not all the harmonies.
+# sim_table should only contain the seeds in that case
+
+library(readr)
+library(dplyr)
+library(distributional)
+library(gravitas)
+library(here)
+library(purrr)
+library(tidyverse)
+library(purrr)
+library(hakear)
+
+# harmony_table<-read_csv(here::here('simulations/sim_table/sim_table.csv'))
+
+sample_seed <- seq(1000, 10999, by = 10) %>% as_tibble()
+simtable <- sample_seed
+scen <- as.numeric(commandArgs()[[6]])
+#scen = 2 # testing if works for one seed
+simj <- simtable[scen, ] # Extract row of table
+seedj <- simj$value # which seed with which simulations should be run
+
+
+harmony_table <- expand.grid(
+  x_levels = c(3, 7, 14),
+  facet_levels = c(2, 9, 10)
+) %>%
+  mutate(design = c("null", "null", "varall", "null", "null", "null", "null", "null", "null"))
+
+# parameters and design used for this simulation
+npermj <- 2
+ntimesj <- 500
+nsampj <- 10
+wj <- 2 # change this to change increment
+
+sim_null <- function(nxj, nfacetj, mean, sd, w = 0) {
+  rep(distributional::dist_normal(mu = mean, sigma = sd),
+      times = nxj * nfacetj
+  )
+}
+sim_varall <- function(nx, nfacet, mean, sd, w)
+{
+  dist_normal((mean + seq(0,
+                          (nx*
+                             nfacet - 1), by  = 1)*w), sd)
+}
+
+set.seed(seedj)
+## code for one harmony table starts
+sim_data_all <- map(
+  seq_len(nrow(harmony_table)),
+  function(x) {
+    y <- harmony_table %>% magrittr::extract(x, )
+    
+    # assigning different rows for different design
+    
+    # setting value of parameters
+    designj <- y$design
+    nfacetj <- y$facet_levels # Which nfacet level
+    nxj <- y$x_levels
+    
+    
+    if (designj == "null") {
+      sim_function <- sim_null
+    } else if (designj == "varx") {
+      sim_function <- sim_varx
+    } else if (designj == "varf") {
+      sim_function <- sim_varf
+    } else {
[…]

### 2021-06-01 simulations/supplementary/test-hpc/R-ind/power-two-alternate-high-inc.R

@@ -1,0 +1,120 @@
+# This script computes power of the test in our paper 
+# low increment : 0.5 , medium increment : 2, high increment: 5
+# initial dist : N(0, 1)
+# only one alternate considered 
+# since all the harmonies need to be run at once, you can only run the seeds parallely, not all the harmonies.
+# sim_table should only contain the seeds in that case
+
+library(readr)
+library(dplyr)
+library(distributional)
+library(gravitas)
+library(here)
+library(purrr)
+library(tidyverse)
+library(purrr)
+library(hakear)
+
+# harmony_table<-read_csv(here::here('simulations/sim_table/sim_table.csv'))
+
+sample_seed <- seq(1000, 10999, by = 10) %>% as_tibble()
+simtable <- sample_seed
+scen <- as.numeric(commandArgs()[[6]])
+#scen = 2 # testing if works for one seed
+simj <- simtable[scen, ] # Extract row of table
+seedj <- simj$value # which seed with which simulations should be run
+
+
+harmony_table <- expand.grid(
+  x_levels = c(3, 7, 14),
+  facet_levels = c(2, 9, 10)
+) %>%
+  mutate(design = c("null", "null", "varall", "null", "null", "null", "varall", "null", "null"))
+
+# parameters and design used for this simulation
+npermj <- 2
+ntimesj <- 500
+nsampj <- 10
+wj <- 5 # change this to change increment
+
+sim_null <- function(nxj, nfacetj, mean, sd, w = 0) {
+  rep(distributional::dist_normal(mu = mean, sigma = sd),
+      times = nxj * nfacetj
+  )
+}
+sim_varall <- function(nx, nfacet, mean, sd, w)
+{
+  dist_normal((mean + seq(0,
+                          (nx*
+                             nfacet - 1), by  = 1)*w), sd)
+}
+
+set.seed(seedj)
+## code for one harmony table starts
+sim_data_all <- map(
+  seq_len(nrow(harmony_table)),
+  function(x) {
+    y <- harmony_table %>% magrittr::extract(x, )
+    
+    # assigning different rows for different design
+    
+    # setting value of parameters
+    designj <- y$design
+    nfacetj <- y$facet_levels # Which nfacet level
+    nxj <- y$x_levels
+    
+    
+    if (designj == "null") {
+      sim_function <- sim_null
+    } else if (designj == "varx") {
+      sim_function <- sim_varx
+    } else if (designj == "varf") {
+      sim_function <- sim_varf
+    } else {
[…]

### 2021-06-02 paper/main.Rmd
intro fix

@@
 ```{r}
-set.seed(321)
+set.seed(3215)
 ```
@@
 Tukey [@Tukey1977-jx] involves many iterations of finding structures and patterns that allow the data to be informative.
-With temporal data available at finer scales, exploring time series data can become overwhelming with so many possible cyclic temporal granularities [@Gupta2020-vo], which are temporal deconstructions that represent cyclic repetitions in time, e.g.
+With temporal data available at finer scales, exploring time series data can become overwhelming with so many possible cyclic temporal granularities [@Bettini1998-ed, @Gupta2020-vo], which are temporal deconstructions that represent cyclic repetitions in time, e.g.
 hour-of-day, day-of-month, or any public holidays.
@@
 Figure \ref{fig:onegran} shows the distribution of energy usage of one household (id 2) across cyclic granularity a) hour-of-day and b) month-of-year.
+Figure \ref{fig:onegran}(a) shows that energy consumption is higher during the morning hours (5-8) when members in the household wake up and then again in the evening hours (17-20) possibly when members get back from work with maximum variation (large inter-quartile range) in behavior in the afternoon hours (12-16).
+Figure \ref{fig:onegran}(b) shows the distribution of energy consumption across months January to June.
+The median and quartile deviation of energy usage in Jan and Feb are generally on a much higher side, possibly due to the usage of air conditioners (Jan, Feb are peak summer in Australia), however for other months (Mar-Jun, autumn and winter), the smaller median and quartile deviation indicate a more consistent behavior.
+It might also imply that this household do not use as much heater as compared to air conditioner.
+A lot of households in Victoria use gas heating and hence the usage of heaters might not be reflected here.
 Potentially many such displays could be drawn across day-of-week, day-of-month, weekday/weekend, or any other chosen cyclic granularities of interest.
@@
 \noindent Exploring the distribution of the measured variable across two cyclic granularities tend to provide more detailed information on its structure.
-Figure \ref{fig:onegran}(a) shows that energy consumption is higher during the morning hours (5-8) when members in the household wake up and then again in the evening hours (17-20) possibly when members get back from work with maximum variation (large inter-quartile range) in behavior in the afternoon hours (12-16).
-Figure \ref{fig:onegran}(b) shows the distribution of energy consumption across months January to June.
-The median and quartile deviation of energy usage in Jan and Feb are generally on a much higher side, possibly due to the usage of air conditioners (Jan, Feb are peak summer in Australia), however for other months (Mar-Jun, autumn and winter), the smaller median and quartile deviation indicate a more consistent behavior.
-It might also imply that this household do not use as much heater as compared to air conditioner.
-A lot of households in Victoria use gas heating and hence the usage of heaters might not be reflected here.
-Figure \ref{fig:id2}(a) slice it down further by showing the usage distribution across hour-of-day conditional on month-of-year across two households (id 2 and 4).
+For example, Figure \ref{fig:id2-new}(a) slice down further by showing the usage distribution across hour-of-day conditional on month-of-year across two households (id 2 and 4).
 It shows the hourly usage over a day do not remain same across months.
 Unlike other months, the 75th and 90th percentile for all hours of the day in January are high, pretty close and are not characterized by a morning and evening peak.
-The household in Figure \ref{fig:id2}(b) has 90th percentile consumption higher in summer months relative to autumn or winter, but the 75th and 90th percentile are far apart in all months, implying that the second household resorts to air conditioning much less regularly than the first one.
-The differences seem to be more prominent across month-of-year (facets) than hour-of-day (x-axis) for this households, whereas they are prominent for both cyclic granularities for the first household.
+The household in Figure \ref{fig:id2-new}(b) has 90th percentile consumption higher in summer months relative to autumn or winter, but the 75th and 90th percentile are far apart in all months, implying that the second household resorts to air conditioning much less regularly than the first one.
+The differences seem to be more prominent across month-of-year (facets) than hour-of-day (x-axis) for this household, whereas they are prominent for both cyclic granularities for the first household.
 It could be immensely useful to make the transition from all potential displays to the ones that are informative across atleast one cyclic granularity.
@@
 @Dang2014-tw and @wilkinson2005graph provides potential solutions to this, where few characterizations can be used to locate anomalies in density, shape, trend, and other features in the 2D point scatters.
-
-<!-- \ref{fig:id2} shows the distribution of energy consumption across hour-of-day conditional on month-of-year.
-\ref{fig:id2}(a) shows that energy consumption is higher during the morning hours when members in the household wake up and then again higher in the evening hours possibly when members are back from work with them showing maximum variable behavior in the afternoon hours.
-\ref{fig:id2}(b) shows the months Jan and Feb not only have a high median consumption, but also more variability, possibly due to the usage of air conditioning.
+In this paper, we provide a solution to narrowing down the search from $^{N_C}P_2$ plots by introducing a new distance measure that can be used to detect significant distributional differences across cyclic granularities.
+
+<!-- \ref{fig:id2-new} shows the distribution of energy consumption across hour-of-day conditional on month-of-year.
+\ref{fig:id2-new}(a) shows that energy consumption is higher during the morning hours when members in the household wake up and then again higher in the evening hours possibly when members are back from work with them showing maximum variable behavior in the afternoon hours.
+\ref{fig:id2-new}(b) shows the months Jan and Feb not only have a high median consumption, but also more variability, possibly due to the usage of air conditioning.
 The other months shows more consistent behavior with the energy consumption rising in May and June.
-\ref{fig:id2} adds to this information, by showing that hours in Jan do not necessarily follow the same pattern across the day (due to Holidays, people visiting).
+\ref{fig:id2-new} adds to this information, by showing that hours in Jan do not necessarily follow the same pattern across the day (due to Holidays, people visiting).
 Moreover, the volatility in consumption are almost equal and high for all hours in Jan, whereas variability is most in the evening hours for other months.
@@
 
-```{r id2, fig.cap = "Distribution of energy consumption displayed through area quantile plots across two cyclic granularities month-of-year and hour-of-day and two households.
+```{r id2-new, fig.cap = "Distribution of energy consumption displayed through area quantile plots across two cyclic granularities month-of-year and hour-of-day and two households.
 The black line is the median, whereas the orange band covers the 25th to 75th percentile and the green band covers the 10th to 90th percentile.
@@
 <!-- harmonies and why it is not enough -->
-\noindent This work is a natural extension of our work that narrows down the search from $^{N_C}P_2$ plots by identifying pairs of granularities that can be meaningfully examined together (a "harmony"), or when they cannot (a "clash").
+\noindent This work is a natural extension of our previous work [@Gupta2020-vo] that narrows down the search from $^{N_C}P_2$ plots by identifying pairs of granularities that can be meaningfully examined together (a "harmony"), or when they cannot (a "clash").
 However, even after excluding clashes, the list of harmonies left could be enormous for exhaustive exploration.
@@
 @inference and @Majumder2013-hb present methods for statistical significance testing of visual findings using human cognition as the statistical tests.
-<!-- present some methods to quantify the strength of pattern and noise through visual inference, similar to numerical testing.
-But this is an evolving field as human cognition (which act as the statistical tests in visual inference) might vary across humans even for the same plots.
---> In this paper, a new distance measure is introduced to enable visual findings that detect significant distributional differences between harmonies.
+In this paper, the visual discovery of distributional differences is facilitated by choosing a threshold for the proposed numerical distance measure, eventually selecting only those cyclic granularities for which the distributional differences are sufficient to make it an interesting display.
 
@@
 Section \ref{sec:rank-wpd} discusses how to choose a threshold to select only significant harmonies.
+Section \ref{sec:simulations} provides some simulation study on the proposed methodology.
 Section \ref{sec:application-wpd} presents an application to a residential smart meter data in Melbourne to show how this distance measure acts as a way to automatically detect periodic patterns in time series.
@@
 
-# Simulations
+# Simulations {#sec:simulations}
 

### 2021-06-02 paper/main.Rmd
code out of Rmd

@@
 For example, a $(2, 3)$ panel will have cyclic granularities with 2 x-axis levels and 3 facet levels.
-Let the four elementary designs as described in Figure \ref{fig:null4by2} be $D_{null}$ where there is no difference in distribution of $v$ for $A$ or $B$, $D_{var_f}$ denotes the set of designs where there is difference in distribution of $v$ for $B$ and not for $A$.
+Let the four elementary designs as described in Figure \ref{fig:null4by2} be $D_{null}$ (referred to as "null distribution") where there is no difference in distribution of $v$ for $A$ or $B$, $D_{var_f}$ denotes the set of designs where there is difference in distribution of $v$ for $B$ and not for $A$.
 Similarly, $D_{var_x}$ denotes the set of designs where difference is observed only across A.
@@
 
-\noindent Pairwise distances could be within-facets or between-facets.
+\noindent Pairwise distances could be within-facets or between-facets for $m \geq 2$.
 Figure \ref{fig:distance-explain} illustrates how they are defined.
@@
 
-A tuning parameter specifying the weightage given to the within-facet or between-facet categories can help to choose between designs like \ref{fig:null4by2}(b) and (c).
+A tuning parameter specifying the weightage given to the within-facet or between-facet categories can help to balance weightage between designs like \ref{fig:null4by2}(b) and (c).
 The tuning parameters should be chosen such that $\sum_{i=1}^m \lambda_i = 1$.
@@
 No human experiment is conducted to justify this ratio, however, typically a tuning parameter $\lambda>0.5$ would tend to upweigh the within-facet distances and that with $<0.5$ would upweigh the between-facet distances (refer to the Supplementary section of the paper for more details).
+For $m = 1$, since there are no conditioning variables or groups, $\lambda = 1$.
 
@@
 
-The simulation results (\ref{Sec:}) show that the distribution of $wpd_{glm}$ under null is similar for high $nx$ and $nfacet$ (levels higher than $5$) and not so much for lower $nx$ and $nfacet$.
+The simulation results (\ref{sec:simulations}) show that the distribution of $wpd_{glm}$ under null is similar for high $nx$ and $nfacet$ (levels higher than $5$) and not so much for lower $nx$ and $nfacet$.
 Hence, a combination approach is proposed which chooses permutation approach for categories with smaller levels and modeling approach for categories with higher levels.
@@
 
-## Behavior of raw and adjuted distance measures
+## Behavior of raw and adjusted distance measures
 
@@
 The data has been cleaned to be a `tsibble` (@wang2019tsibble) containing half-hourly electricity consumption from Jul-2019 to Dec-2019 for each of the households, which is procured by them by downloading their data from the energy supplier/retailer.
-The line display of
-energy usage will have too many measurements squeezed in a linear representation.
-No behavioral pattern is likely to be discerned from this view.
+No behavioral pattern is likely to be discerned from the line display of 
+energy usage over the entire period, since the plot will have too many measurements squeezed in a linear representation.
 When we zoom into the linear representation of this series in Figure \ref{fig:dotplot-8} (b) for September, some patterns are visible in terms of peaks and troughs, but we do not know if they are regular or what is their period.
@@
 We start the analysis by choosing few harmonies, ranking them for each of these households, compare households to get more insights into what these rankings imply.
-Furthermore, the ranking and selection of significant harmonies could be validated by analyzing the distribution of energy usage across significant harmonies.
+Furthermore, the ranking and selection of significant harmonies is validated by analyzing the distribution of energy usage across significant harmonies.
 
@@
 In fig b, we can see some weekly patterns for the entire period and daily patterns for the highlighted week and there could be some other patterns visible in terms of peaks and troughs, but it is not clear if they are regular or significant.", fig.height=8, eval = FALSE}
-
-library(scales)
-library(tidyquant)
-library(gghighlight)
-library(lubridate)
-
-elec <- read_rds(here("paper/data/elec_all-8.rds")) %>% 
-  dplyr::filter(date(reading_datetime) >= ymd("20190701"), date(reading_datetime) < ymd("20191231"), meter_id==1) %>% 
-  select(-meter_id) %>% 
-  rename("id" = "household_id",
-         "date_time" = "reading_datetime") %>% 
-  mutate(date = date(date_time))
-
-elec_linear <- elec %>% 
-  ggplot() +
-  geom_line(aes(x = date_time, y = kwh),alpha = 0.7) +
-  facet_wrap(~id, nrow = 8, labeller = "label_both",
-             strip.position =  "right",
-             scales = "free_y") + ggtitle("a")
-
-elec_zoom <-  elec %>%
-  as_tibble() %>% 
-  filter(date >as.Date("2019-09-01") & date < (as.Date("2019-09-30"))) %>% 
-  ggplot(aes(x=date_time, y = kwh)) +
-  geom_line(size = 0.1, colour = "blue") +
-  facet_wrap(~id, 
-             scales = "free_y",
-             ncol = 1,
-             strip.position =  "right") +
-  gghighlight(date > as.Date("2019-09-15") & date < (as.Date("2019-09-21")), unhighlighted_params = list(colour = "black")) + ggtitle("b")
-
-elec_linear + elec_zoom
-
-```
-
-```{r raw-nqt-8, fig.height = 5, fig.cap="The raw density of the half-hourly demand for the eight households is shown in Fig a.
-Fig b shows the normal-score-transformed half-hourly demand for the same households which has resulted in more symmetric distribution of half-hourly demand.", eval = FALSE}
-elec_raw <- elec %>% 
-  ggplot() +
-  geom_density(aes(x = kwh)) +
-  facet_wrap(~id, scales = "free_y", ncol = 1) +
-  xlab("demand (in kwh)") + ggtitle("a") +
-  theme(
-        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
-
-elec_nqt <- elec %>% 
-  dplyr::mutate(kwh_transformed = stats::qqnorm(kwh, plot.it = FALSE)$x) %>% 
-  ggplot() +
-  geom_density(aes(x = kwh_transformed))+
-  facet_wrap(~id, scales = "free_y", ncol = 1) +
-  xlab("NQT demand (in kwh)") + ggtitle("b") + theme(
-        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
-
-# hour_day_raw <- elec %>% 
-#   tsibble::as_tsibble(index = date_time, key = id) %>% 
-#     create_gran("hour_day") %>% 
-#     ggplot() + 
-#     ggridges::geom_density_ridges(aes(y=hour_day, x = kwh))
-#   
-# hour_day_trans <- elec %>% 
-#   tsibble::as_tsibble(index = date_time, key = id) %>% 
-#     create_gran("hour_day") %>% 
-#   dplyr::mutate(kwh_transformed = stats::qqnorm(kwh, plot.it = FALSE)$x) %>% 
-#   ggplot() +
-#   ggridges::geom_density_ridges(aes(y=hour_day, x = kwh_transformed))
-
-elec_raw + elec_nqt
 
@@
 
- $wpd$ is computed for all harmony pairs $\in H_{N_C}$ and for each households $i \in i = \{1, 2, \dots, 8\}$.
-The harmony pairs are then arranged in descending order and highlighted with `***`, `**` and `*` corresponding to the  $99^{th}$,  $99^{th}$ and $99^{th}$ percentile threshold.
+$wpd_{i}$ is computed on $v_{i, t}$ for all harmony pairs $\in H_{N_C}$ and for each households $i \in i = \{1, 2, \dots, 8\}$.
+The harmony pairs are then arranged in descending order and highlighted with `***`, `**` and `*` corresponding to the  $99^{th}$,  $95^{th}$ and $90^{th}$ percentile threshold.
 Table \ref{tab:tab-rank-8} shows the rank of the harmonies for different households.
@@
 
-\noindent Figure \ref{fig:dotplot-8} helps to compare households through the heatmap (a) and emphasizes patterns not discernible through linear display in (b).
-(b) contains the raw data for a month (Sep-2019), where the major and minor x-axis corresponds to weeks and days respectively.
-In (a), the value of $wpd$ filled as colors, implying darker cells correspond to more significant harmony pairs.
-Also, the ones with `*` are significant at 95% level.
+\noindent Figure \ref{fig:dotplot-8} helps to compare households through the heatmap (a) 
+across harmony pairs with x-variable and facet variable plotted on the x-axis and y-axis of the heatmap.
+Here dom, dow, wdwnd are abbreviations for day-of-month, day-of-week and weekday/weekend and so on.
+(a) emphasizes patterns not discernible through (b), which is a linear display containing the raw data for one month (Sep-2019), with the major and minor x-axis corresponding to weeks and days respectively.
+In (a), the colors represent the value of $wpd$, implying darker cells correspond to more significant harmony pairs.
+Also, the ones with `*` corresponds to the ones above $wpd_{threshold95}$.
 This plot suggests that there are no significant periodic patterns for id 5.
@@
 The distribution of energy demand with dow as the x-axis and hod as the facets for both of these households can help justify the selection.
-Figure \ref{fig:gravitas-plot-8} show that the median (black) and quartile deviation (orange) of energy consumption changes across both dow and hod for id 4 for most hours, but it is not so different for id 5 with differences captured only for $90^{th}$ percentile.
+Figure \ref{fig:gravitas-plot-8} shows that the median (black) and quartile deviation (orange) of energy consumption changes across both dow and hod for id 4 for most hours, but it is not so different for id 5 with differences captured only for $90^{th}$ percentile.
 

### 2021-06-02 paper/main.Rmd
fix graph labels

@@
 \noindent Take the example of the  electricity smart meter data used in @wang2020calendar for four households in Melbourne, Australia.
-Figure \ref{fig:onegran} shows the distribution of energy usage of one household (id 2) across cyclic granularity a) hour-of-day and b) month-of-year.
-Figure \ref{fig:onegran}(a) shows that energy consumption is higher during the morning hours (5-8) when members in the household wake up and then again in the evening hours (17-20) possibly when members get back from work with maximum variation (large inter-quartile range) in behavior in the afternoon hours (12-16).
-Figure \ref{fig:onegran}(b) shows the distribution of energy consumption across months January to June.
+Figure \ref{fig:onegran-new} shows the distribution of energy usage of one household (id 2) across cyclic granularity a) hour-of-day and b) month-of-year.
+Figure \ref{fig:onegran-new}(a) shows that energy consumption is higher during the morning hours (5-8) when members in the household wake up and then again in the evening hours (17-20) possibly when members get back from work with maximum variation (large inter-quartile range) in behavior in the afternoon hours (12-16).
+Figure \ref{fig:onegran-new}(b) shows the distribution of energy consumption across months January to June.
 The median and quartile deviation of energy usage in Jan and Feb are generally on a much higher side, possibly due to the usage of air conditioners (Jan, Feb are peak summer in Australia), however for other months (Mar-Jun, autumn and winter), the smaller median and quartile deviation indicate a more consistent behavior.
@@
 
-```{r onegran, fig.cap="Boxplots showing the distribution of one household across one cyclic granularity at a time - (a) hour-of-day and (b) and month-of-year.
+```{r onegran-new, fig.cap="Boxplots showing the distribution of one household across one cyclic granularity at a time - (a) hour-of-day and (b) and month-of-year.
 The daily and annual periodic behavior of energy is apparent in (a) and (b) respectively, with daily peaks occuring in morning and evening hours when members in the house are present and active, more volatility (usage of air conditioner) in summer months (Jan, Feb) due to air conditioners and more consistent behavior in winter and autumn months (Mar, Apr, May, June)."}
@@
 \noindent Exploring the distribution of the measured variable across two cyclic granularities tend to provide more detailed information on its structure.
-For example, Figure \ref{fig:id2-new}(a) slice down further by showing the usage distribution across hour-of-day conditional on month-of-year across two households (id 2 and 4).
+For example, Figure \ref{fig:id2-new2}(a) slice down further by showing the usage distribution across hour-of-day conditional on month-of-year across two households (id 2 and 4).
 It shows the hourly usage over a day do not remain same across months.
 Unlike other months, the 75th and 90th percentile for all hours of the day in January are high, pretty close and are not characterized by a morning and evening peak.
-The household in Figure \ref{fig:id2-new}(b) has 90th percentile consumption higher in summer months relative to autumn or winter, but the 75th and 90th percentile are far apart in all months, implying that the second household resorts to air conditioning much less regularly than the first one.
+The household in Figure \ref{fig:id2-new2}(b) has 90th percentile consumption higher in summer months relative to autumn or winter, but the 75th and 90th percentile are far apart in all months, implying that the second household resorts to air conditioning much less regularly than the first one.
 The differences seem to be more prominent across month-of-year (facets) than hour-of-day (x-axis) for this household, whereas they are prominent for both cyclic granularities for the first household.
@@
 
-<!-- \ref{fig:id2-new} shows the distribution of energy consumption across hour-of-day conditional on month-of-year.
-\ref{fig:id2-new}(a) shows that energy consumption is higher during the morning hours when members in the household wake up and then again higher in the evening hours possibly when members are back from work with them showing maximum variable behavior in the afternoon hours.
-\ref{fig:id2-new}(b) shows the months Jan and Feb not only have a high median consumption, but also more variability, possibly due to the usage of air conditioning.
+<!-- \ref{fig:id2-new2} shows the distribution of energy consumption across hour-of-day conditional on month-of-year.
+\ref{fig:id2-new2}(a) shows that energy consumption is higher during the morning hours when members in the household wake up and then again higher in the evening hours possibly when members are back from work with them showing maximum variable behavior in the afternoon hours.
+\ref{fig:id2-new2}(b) shows the months Jan and Feb not only have a high median consumption, but also more variability, possibly due to the usage of air conditioning.
 The other months shows more consistent behavior with the energy consumption rising in May and June.
-\ref{fig:id2-new} adds to this information, by showing that hours in Jan do not necessarily follow the same pattern across the day (due to Holidays, people visiting).
+\ref{fig:id2-new2} adds to this information, by showing that hours in Jan do not necessarily follow the same pattern across the day (due to Holidays, people visiting).
 Moreover, the volatility in consumption are almost equal and high for all hours in Jan, whereas variability is most in the evening hours for other months.
@@
 
-```{r id2-new, fig.cap = "Distribution of energy consumption displayed through area quantile plots across two cyclic granularities month-of-year and hour-of-day and two households.
+```{r id2-new2, fig.cap = "Distribution of energy consumption displayed through area quantile plots across two cyclic granularities month-of-year and hour-of-day and two households.
 The black line is the median, whereas the orange band covers the 25th to 75th percentile and the green band covers the 10th to 90th percentile.
@@
 
-```{r tab-demography, eval = FALSE}
-demography <- tibble(id = c(1, 2, 3, 4, 5,6, 7, 8), 
-       profession = c("academia", "mixed", "industry", "industry", "mixed", "mixed", "academia", "industry"),
-       total_members = c(2, 3, 5, 5, 2, 2, 2, 6),
-       kids = c("no", "no", "yes", "yes", "no", "no", "no", "yes"),
-       old_parents = c("no", "yes", "yes", "yes", "no", "no", "no", "yes"),
-       PhD_student = c("no", "yes", "no", "no", "yes", "yes", "yes", "no"))
-
-demography <- demography %>% kable(format  = "markdown", caption = "Demographics of the eight households chosen for study")
-
-demography %>% add_footnote(label = "***: 99% significant, **: 95% and *: 90%")
-```
-
 <!-- if we are benefiting by moving from a linear to cyclic representation of time to . -->
@@
 \noindent Figure \ref{fig:dotplot-8} helps to compare households through the heatmap (a) 
-across harmony pairs with x-variable and facet variable plotted on the x-axis and y-axis of the heatmap.
+across harmony pairs with the cyclic granularity mapped to x-axis and facet being plotted on the x-axis and y-axis of the heatmap.
 Here dom, dow, wdwnd are abbreviations for day-of-month, day-of-week and weekday/weekend and so on.
@@
 For eg, id 7 and 8 have significant patterns across (hod, dow) and (dow, hod), which was not apparent in (a).", fig.height = 8}
-# elec_sig_split <- elec_harmony_all %>%
-#   mutate(select_split =  str_split(select_harmony, " ", simplify = TRUE)[,2]) %>% 
-#   
-  select_split <- str_split(elec_harmony_all$select_harmony, " ", simplify = TRUE)[,2]
-
-  elec_sig_split <- elec_harmony_all %>% 
-    bind_cols(select_split = select_split) %>% 
-  mutate(significant = case_when(
-    select_split == "***" ~ "highest",
-    select_split == "**" ~ "high",
-    select_split == "*" ~ "medium",
-    select_split == "" ~ "low"
-  )) %>% 
-   mutate(rank = case_when(
-    select_split == "***" ~ paste(rank, "***", sep = " "),
-    select_split == "**" ~  paste(rank, "**", sep = " "),
-    select_split == "*" ~  paste(rank, "*", sep = " "),
-    select_split == "" ~  paste(rank, "", sep = " ")
-  ))
-
-elec_sig_split$significant <- 
-  factor(elec_sig_split$significant, levels = c("highest", "high", "medium", "low"))
-
-heatplot <- elec_sig_split %>% 
-  mutate(significance_95 = if_else(significant %in% c("high", "highest"), "*", "")) %>% 
-  ggplot(aes(x = x_variable,
-                 y = facet_variable)) +
-  geom_tile(aes(fill = wpd)) + 
-                #color = as.factor(significance_95)),
-            #size = 0.3) +
-  geom_text(aes(label = significance_95), color = "#42275a") +
-  scale_fill_gradient(low = "white",high = "#ba5370") +
-  #scale_fill_manual(palette = "Dark2") +
-  #scale_colour_manual(values = c("white","red")) + 
-  theme(legend.position = "bottom") +
-  coord_fixed() + 
-  guides(fill = guide_legend()) +
-  theme_void() +
-  theme_gray(base_size = 12, base_family = "Times") +
-  theme(panel.grid = element_blank(),
-        axis.text.x = element_text(angle = 60, hjust=1),legend.position = "bottom") + ggtitle("a") +
-  theme(
-    strip.background = element_blank(),
-    strip.text.y  = element_blank(), plot.margin = unit(c(0, -2, 0, 0), "cm")) + ggtitle("(a)")
-
-elec <- read_rds(here("paper/data/elec_all-8.rds")) %>% 
-  dplyr::filter(date(reading_datetime) >= ymd("20190701"), date(reading_datetime) < ymd("20191231"), meter_id==1) %>% 
-  select(-meter_id) %>% 
-  rename("id" = "household_id",
-         "date_time" = "reading_datetime")
-
-# 
-# elec %>% 
-#   filter(id == "1") %>% 
-#   prob_plot("hour_day", 
-#             "day_week",
-#             response = "kwh",
-#             plot_type = "violin", fill = "blue")
-#   
-elec1 <- elec %>% 
-  filter(id == "1") %>% 
-  create_gran("day_week") %>% 
-  create_gran("hour_day") %>% 
-  mutate(day_week = as.numeric(day_week),
-         hour_day = as.numeric(hour_day),
-         id = as.numeric(id))
-
-# temp.gly <- glyphs(elec1, "day_week", "hour_day", "id","kwh", height = 2.5)
-# 
-# ggplot(temp.gly, ggplot2::aes(gx, gy, group = gid)) +
-#   add_ref_lines(temp.gly, color = "grey90") +
-#   add_ref_boxes(temp.gly, color = "grey90") +
-#   geom_path() +
-#   theme_bw() +
-#   labs(x = "", y = "")
-
-elec_zoom <-  elec %>%
-  as_tibble() %>% 
-  dplyr::filter(date(date_time) > as.Date("2019-09-01") & date(date_time) < (as.Date("2019-09-30"))) %>%
-  ggplot(aes(x=date_time, y = kwh)) +
-  #geom_point(size = 0.1, colour = "black", alpha = 0.3) +
-  geom_line(size = 0.1, colour = "blue") +
-  facet_wrap(~id, 
-             scales = "free_y",
-             ncol = 1,
-             strip.position =  "right",
-             labeller = "label_both") + 
-  xlab("Time [30m]") + 
-  theme_grey() + 
-  ylab("linear energy demand (kwh) for September") + ggtitle("(b)") +
-  theme(panel.grid.major.x = element_blank()) +
-  scale_x_datetime("Date", date_labels = "%b %d",
-                   breaks = "1 week",
-                   date_minor_breaks = "1 day")  + theme_bw() +
-  theme(panel.grid.major.x =  element_line(colour = "#A9A9A9"),
-        panel.grid.minor.x =  element_line(colour = "#D3D3D3"))
-
-heatplot +  facet_grid(id~.) + elec_zoom +
-  theme( plot.margin = unit(c(0, 0, 0, 0), "cm")) +
-  plot_layout(widths = c(1, 2)) 
 ```
@@
 ```{r tab-rank-8}
-elec_rank <- elec_sig_split %>% 
-  select(-c(6,7, 9, 10)) %>% 
-  pivot_wider(
-              names_from = id,
-                values_from = rank) %>% 
-  rename("facet variable" = "facet_variable",
-         "x variable" = "x_variable") %>% 
-  select(-facet_levels, -x_levels)
-
-elec_rank %>% kable(format = "markdown", caption = "Ranking of harmonies for the eight households with significance levels.")
 ```
@@
 
-id4_tsibble <- elec %>%
-  filter(id == 4)
-
-id5_tsibble <- elec %>%
-  filter(id == 5)
-
-p1 <- id4_tsibble %>% 
-   prob_plot("hour_day",
-             "day_week",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = TRUE,
-             quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)) +
-  ggtitle("a) hod vs dow (id:4)") + 
-  #scale_colour_brewer(name = "", palette = "Set2") +
-  theme(legend.position = "none",
-        strip.text = element_text(size = 7, margin = margin()),)
-
-p2 <- id5_tsibble %>%
-   prob_plot("hour_day",
-             "day_week",
-             response = "kwh",
-             plot_type = "quantile",
-             symmetric = TRUE,
-             quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)) +
-  ggtitle("a) hod vs dow (id:5)") +
-  #scale_colour_brewer(name = "", palette = "Set2")   +
-  theme(legend.position = "none",
-        strip.text = element_text(size = 7, margin = margin()))
-
-p1 + p2
-
 ```

### 2021-06-02 simulations/supplementary/one-gran/norm/null_design_quantrans_nperm/R-agg/aggregate01.R

@@ -5,9 +5,12 @@ library(here)
 library(readr)
 library(rlang)
 
+out_loc <- "simulations/supplementary/one-gran/norm/null_design_quantrans_nperm/data-agg/"
+in_loc <- "simulations/supplementary/one-gran/norm/null_design_quantrans_nperm/data-ind/"
+
 aggregate01 <-  function(folder_name){
   
-all_files = list.files(path = paste0("simulations/norm/null_design_quantrans_nperm/data-ind/", folder_name), 
+all_files = list.files(path = paste0(in_loc, folder_name), 
                        pattern = ".rds")
 
 names_levels <- map_dfr(all_files, 
@@ -23,7 +26,7 @@ names_levels <- map_dfr(all_files,
 # names_rep <- names_levels %>% slice(rep(1:n(), each = nrow(len_file)))
 
   
-all_files_path <- paste0("simulations/norm/null_design_quantrans_nperm/data-ind/",folder_name,"/",
+all_files_path <- paste0(in_loc,folder_name,"/",
          all_files)  
   
 
@@ -38,7 +41,7 @@ all_data <- lapply(1:length(all_files_path), function(x){
   }) %>% bind_rows() %>% 
     arrange(nfacet, nx)
     
-write_rds(all_data, paste0("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_", folder_name, ".rds"))
+write_rds(all_data, paste0(out_loc, "all_data_", folder_name, ".rds"))
 }
 
 

### 2021-06-02 simulations/supplementary/one-gran/raw/null_design_quantrans/R-agg/aggregate01.R

@@ -5,15 +5,16 @@ library(here)
 library(readr)
 library(rlang)
 
+
 aggregate01 <-  function(folder_name){
   
-all_files = list.files(path = ("simulations/▸ ⁨supplement/one-gran/raw/null_design_quantrans/data-ind/wpd_N01/"))
-
-
-all_files = list.files(path = paste0("simulations/vary_all/raw/data-ind/", folder_name), 
+all_files = list.files(path = paste0("simulations/supplementary/one-gran/raw/null_design_quantrans/data-ind/", folder_name), 
                        pattern = ".rds")
 
-
+# all_files = list.files(path = paste0("simulations/vary_all/raw/data-ind/", folder_name), 
+#                        pattern = ".rds")
+# 
+# 
 
 names_levels <- map_dfr(all_files, 
                         function(x){
@@ -22,11 +23,6 @@ names_levels <- map_dfr(all_files,
                           bind_cols(nx = as.numeric(z[1]),
                                     nfacet = as.numeric(z[2]))
                         })
-
-# len_file = read_rds(("simulations/results/norm/tuning_param/2_2_tuning_param.rds"))
-# 
-# names_rep <- names_levels %>% slice(rep(1:n(), each = nrow(len_file)))
-
   
 all_files_path <- paste0("simulations/supplementary/one-gran/raw/null_design_quantrans/data-ind/",folder_name,"/",
          all_files)  
@@ -50,12 +46,12 @@ write_rds(all_data, paste0("simulations/supplementary/one-gran/raw/null_design_q
 # use functions for all folders
 
 aggregate01(folder_name = "wpd_N01")
-aggregate01(folder_name = "wpd_N05")
-aggregate01(folder_name = "wpd_N51")
-aggregate01(folder_name = "wpd_N55")
-
-
-aggregate01(folder_name = "wpd_Gamma01")
-aggregate01(folder_name = "wpd_Gamma21")
-
-
+# aggregate01(folder_name = "wpd_N05")
+# aggregate01(folder_name = "wpd_N51")
+# aggregate01(folder_name = "wpd_N55")
+# 
+# 
+# aggregate01(folder_name = "wpd_Gamma01")
+# aggregate01(folder_name = "wpd_Gamma21")
+# 
+# 

### 2021-06-02 paper/main.Rmd
suppplementary paper upload

@@
 
-\noindent Observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
+$m=1$
+
+\noindent Observations are generated from a N(0,1) distribution for each $nx = \{2, 3, 5, 7, 9, 14, 17, 20, 24, 31, 42, 50\}$ to cover a wide range of levels from very low to moderately high.
+$ntimes = 500$ observations are drawn for each combination of the categories, that is, for a panel with $nx=3$, $500$ observations are simulated for each of the categories.
+This design corresponds to $D_{null}$ as each combination of categories in a panel are drawn from the same distribution.
+Furthermore, the data is simulated for each of the categories $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
+The values of $wpd$ is obtained for each of the panels.
+$wpd_{l, s}$ denotes the value of $wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.
+
+$m=2$  
+\noindent Similarly, observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$.
 That is, data is being generated for each of the panels $(2, 2), (2, 3), (2, 5) \dots, (50, 31), (50, 50)$.
@@
 That is, if we consider a $(2, 2)$ panel, $500$ observations are generated for each of the possible subsets, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
-The values of $wpd$ is obtained for each of the panels.
-This design corresponds to $D_{null}$ as each combination of categories in a panel are drawn from the same distribution.
-Furthermore, the data is simulated for each of the panels $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
-$wpd_{l, s}$ denotes the value of $wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.
 
@@
 This is possible as the distribution of the adjusted measure looks similar for both appraches for higher levels."}
-```
-
-```{r }
 ```

### 2021-06-02 paper/paper-supplementary.Rmd
suppplementary paper upload

@@
 ---
-title: "<small> Supplementary materials for the main submission entitled - <br><br> A new metric for automatic discovery of periodic patterns in time series"
+title: "<small> Supplementary materials for the main submission entitled - <br><br> Detecting distributional differences between temporal granularities for exploratory time series analysis"
 authors:
@@
 library(patchwork)
+library(readr)
+library(tidyverse)
+library(here)
+library(broom)
 
@@
 
-## Number of comparison
-
-# Normalization
-
-## Simulation design
-
-Observations are generated from Gamma(2,1), G(0.5, 1), N(0,1), N(0, 5) and N(5, 1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
-Each combination is being referred to as a _panel_.
-That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$.
-For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
-That is, if we consider the panel $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
-The values
-of $wpd$ is obtained for each of the panels.
-The measurement variable for each combination of categories in a panel are drawn from the same distribution and hence the design corresponds to $D_{null}$ .
-Furthermore, this entire method is repeated for each panels $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
-
 ## Underlying distributions
@@
 ```
-## Number of comparisons
 
-Next, we study the distribution of $wpd$ for different $nx$ and $nfacet$ in various ways.
+## Case: m = 1
 
-```{r nxbyfacet-ridge-N05, fig.cap="Ridge plots of raw wpd is shown for N(0,5) distribution.
+```{r nxbyfacet-ridge-N01-onegran, fig.cap="Ridge plots of raw wpd is shown for N(0,5) distribution.
 For each panel, it could be seen that the location shifts to the right for increasing x levels.
 Across each panel, the scale of the distribution seems to change for low/moderately lower values and higher values of nfacets and left tails are longer for lower facet levels."}
-knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/nxbyfacet_ridge_wpd_N05.png"))
+knitr::include_graphics(here::here("simulations/supplementary/one-gran/raw/null_design_quantrans/figs/nxbyfacet_ridge_wpd_N01.png"))
 ```
 
-```{r dist-across-x, fig.cap = "Distribution of $MMPD_{raw}$ for different x levels are shown.
-The scale of the distribution becomes less and less implying that as the number of x levels increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained as the spread of the distribution decreases.
-", eval = FALSE}
-knitr::include_graphics(here::here("simulations/result_report/","nfacet_by_nx_raw.png"))
+```{r nfacetbynx-onegran}
+knitr::include_graphics(here::here("simulations/supplementary/one-gran/raw/null_design_quantrans/figs/nfacetbynx_ridge_wpd_N01.png"))
 ```
 
-<!-- Following the work of Krzysztofowicz (1997) the empirical NQT involves the following steps: -->
-<!-- 1. Sort the sample of measured variable $X$ from the smallest to the largest observation $x_{(1)},\dots, x_{(i)}, .., x_{(n)}$. -->
-<!-- 2. Estimate the cumulative probabilities $p_{(1)},\dots, p_{(i)}, .., p_{(n)}$. -->
-<!-- using a plotting position like $i/(n + 1)$ such that $p_{(i)} = P(X \leq x_{(i)})$. -->
-<!-- 3. Transforming each observation $x_(i)$ of $X$ into observation $y(i) = Q^{-1}(p(i))$ of the standard normal variate $Y$ , with $Q$ denoting the standard normal distribution and -->
-<!-- $Q^{-1}$ its inverse, applying discrete mapping. -->
+```{r density-raw-onegran}
+knitr::include_graphics(here::here("simulations/supplementary/one-gran/raw/null_design_quantrans/figs/nxbyfacet_density_wpd_N01.png"))
+```
 
-<!-- Firstly, we show that NQT works to make the distribution within each panel same. . -->
+## Case: m = 2
 
-## sample size
+```{r nxbyfacet-ridge-N01, fig.cap="Ridge plots of raw wpd is shown for N(0,5) distribution.
+For each panel, it could be seen that the location shifts to the right for increasing x levels.
+Across each panel, the scale of the distribution seems to change for low/moderately lower values and higher values of nfacets and left tails are longer for lower facet levels."}
+knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/nxbyfacet_ridge_wpd_N01.png"))
+```
 
-## number of permutations
+```{r nfacetbynx}
+knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/nfacetbynx_ridge_wpd_N01.png"))
+```
 
-## designs
+```{r density-raw}
+knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/nxbyfacet_density_wpd_N01.png"))
+```
+
+# Adjusted wpd
+
+## Case: m = 1
+
+### Simulation design
+
+\noindent Observations are generated from a N(0,1) distribution for each $nx = \{2, 3, 5, 7, 9, 14, 17, 20, 24, 31, 42, 50\}$ to cover a wide range of levels from very low to moderately high.
+$ntimes = 500$ observations are drawn for each combination of the categories, that is, for a panel with $nx=3$, $500$ observations are simulated for each of the categories.
+This design corresponds to $D_{null}$ as each combination of categories in a panel are drawn from the same distribution.
+Furthermore, the data is simulated for each of the categories $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
+The values of $wpd$ is obtained for each of the panels.
+$wpd_{l, s}$ denotes the value of $wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.
+
+### Permutation approach
+
+```{r}
+include_graphics(here("simulations/supplementary/one-gran/raw/null_design_quantrans/figs/nxbyfacet_ridge_wpd_N01.png"))
+```
+
+### Modeling approach
+
+```{r}
+G21 <- read_rds(here("simulations/supplementary/one-gran/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds"))
+
+G21_median <- G21 %>% 
+  group_by(nx*nfacet) %>% 
+  summarise(actual = median(value))
+
+glm_fit <- glm(actual ~ log(`nx * nfacet`),
+               family = Gamma(link = "inverse"),
+               data = G21_median)
+
+intercept <- glm_fit$coefficients[1]
+slope <- glm_fit$coefficients[2]
+G21_sd  = G21 %>% 
+  mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
+  )
+  )
+  ))
+scale_fac <- 1/G21_sd$wpd_glm %>% sd()
+# checking the fit of the residuals from glm fit
+
+fitted_glm <- fitted(glm_fit, type = "response")
+residuals <- residuals.glm(glm_fit, type = "response")
+#hist(residuals)
+#h = augment(glm_fit)
+#ggplot(h) +
+#  geom_histogram(aes(x = .resid))
+residual <- G21_median$actual  - fitted_glm
+
+#hist(residual)
+G21 %>% 
+  ggplot(aes(x=log(nx*nfacet),
+             y = (value - (1/(intercept + slope*log(nx*nfacet)
+             )
+             )
+             )
+  )
+  ) +
+  geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
+  ylab("wpd_glm = wpd_raw - 1/(a  + b*log(nx*nfacet))")
+
+G21_glm <- G21 %>% 
+  mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
+  )
+  )
+  ),
+  wpd_glm_scaled = ((wpd_glm*261)))
+
+nxbyfacet_ridge <- G21_glm %>% 
+  ggplot(aes(x = wpd_glm_scaled, y = as.factor(nx))) +
+  ggridges::geom_density_ridges() +
+  facet_wrap(~nfacet, labeller = "label_both", nrow = 2) + 
+  xlab("mmpd") +
+  ylab("nx")
+
+nxbyfacet_ridge
+```
+
+### Combination approach
+
+```{r}
+G21_permutation <- read_rds(here("simulations/supplementary/one-gran/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds")) %>%
+  rename("wpd_permutation" = "value")
+
+# G21_model_data <- G21 %>%
+#   mutate(model =
+#            ((1/value)
+#                   - intercept -
+#                     slope*log(nx*nfacet))/slope) %>%
+#   mutate(model_trans =
+#            (model - mean(model))/sd(model))
+
+# G21_model_data$model %>% summary()
+
+G21_all_data <- G21_permutation %>% 
+  # left_join(G21_lm, by = c("nx", "nfacet", "perm_id")) %>% 
+  left_join(G21_glm, by = c("nx", "nfacet", "perm_id")) %>% 
+  pivot_longer(cols = c(3, 7),
+               names_to = "type_estimate",
+               values_to = "value_estimate")
+G21_all_data$type_estimate = factor(G21_all_data$type_estimate , levels = c( "wpd_permutation", "wpd_glm_scaled"))
+
+summary_data <- G21_all_data %>% 
+  group_by(nx, nfacet, type_estimate) %>% 
+  summarise(mean = mean(value_estimate)) %>% ungroup()
+
+G21_all_data %>% 
+  filter(type_estimate %in% c("wpd_glm_scaled", "wpd_permutation")) %>% 
+  ggplot(aes(x = value_estimate)) +
+  geom_density(aes(fill = type_estimate), alpha = 0.5, size = .5) +
+  geom_vline(data = summary_data, aes(xintercept = mean, color = type_estimate)) + 
+  geom_rug(aes(color = type_estimate), length = unit(0.09,"cm"), alpha = 0.5) +
+  #coord_cartesian(clip = "off") + 
+  facet_wrap(~nx,
+             labeller = "label_both") +
+  theme_bw() + 
+  theme(legend.position = "bottom") +
+  scale_fill_manual(values = c( "#D55E00", "#0072B2")) +
+  scale_color_manual(values = c( "#D55E00", "#0072B2")) +
+  xlab("adjusted values of wpd") 
+```
+
+## Case: m = 2
+
+### Simulation design
+
+Observations are generated from Gamma(2,1), G(0.5, 1), N(0,1), N(0, 5) and N(5, 1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
+Each combination is being referred to as a _panel_.
+That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$.
+For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
+That is, if we consider the panel $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
+The values
+of $wpd$ is obtained for each of the panels.
+The measurement variable for each combination of categories in a panel are drawn from the same distribution and hence the design corresponds to $D_{null}$ .
+Furthermore, this entire method is repeated for each panels $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
+
+### Permutation approach
+
+```{r norm, fig.cap = "Distribution of $wpd_{perm}$ is plotted across different $nx$ and $nfacet$ categories.
+Both shape and scale of the distributions are now similar for different panels under the null design."}
+G21_norm <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_Gamma21.rds"))
+
+G21_norm %>% 
+  ggplot(aes(x = value)) + 
+  geom_density(fill = "blue") +
+  facet_grid(nx~nfacet,
+             labeller = "label_both") + 
+  scale_x_continuous(breaks = scales::breaks_extended(3)) + 
+  xlab("wpd normalised using permutation approach")
+
+```
+
+### Modeling approach
+
+```{r wpd-glm-dist, fig.cap = " The distribution of $wpd_{glm}$ is plotted. The distributions are more similar across higher nx and nfacet and dissimilar for fewer nc and nfacets."}
+
+G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds"))
+G21_median <- G21 %>% 
+  group_by(nx*nfacet) %>% 
+  summarise(actual = median(value))
+glm_fit <- glm(actual ~ log(`nx * nfacet`),
+               family = Gamma(link = "inverse"),
+               data = G21_median)
+intercept <- glm_fit$coefficients[1]
+slope <- glm_fit$coefficients[2]
+G21_sd  = G21 %>% 
+  mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
+  )
+  )
+  ))
+#scale_fac <- 1/G21_sd$wpd_glm %>% sd()
+# checking the fit of the residuals from glm fit
+# fitted_glm <- fitted(glm_fit, type = "response")
+# residuals <- residuals.glm(glm_fit, type = "response")
+# hist(residuals)
+#h = augment(glm_fit)
+# ggplot(h) +
+#   geom_histogram(aes(x = .resid))
+# residual <- G21_median$actual  - fitted_glm
+# 
+# hist(residual)
+# G21 %>% 
+#   ggplot(aes(x=log(nx*nfacet),
+#              y = (value - (1/(intercept + slope*log(nx*nfacet)
+#              )
+#              )
+#              )
+#   )
+#   ) +
+#   geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
+#   ylab("wpd_glm = wpd_raw - 1/(a  + b*log(nx*nfacet))")
+broom::tidy(glm_fit) %>% kable(caption = "Results of generalised linear model to capture the relationship between $wpd_{raw}$ and number of comparisons.")
+
+G21_glm <- G21 %>% 
+  mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
+  )
+  )
+  ),
+  wpd_glm_scaled = ((wpd_glm*320)))
+
+G21_glm$wpd_glm_scaled %>% sd()
+
+G21_glm %>%
+  ggplot() +
+  geom_density(aes(x = wpd_glm),
+               fill = "blue") +
+  facet_grid(nx~nfacet,
+             labeller = "label_both") +
+  theme(legend.position = "bottom")
+
+```
+
+### Combination approach
+
+```{r dist-new-same-scale-link, fig.cap = "The distribution of $wpd_{perm}$ and $wpd_{glm-scaled}$ are overlaid to compare the location and scale across different $nx$ and $nfacet$.
+$wpd_{norm}$ takes the value of $wpd_{perm}$ for lower levels, and $wpd_{glm-scaled}$ for higher levels to to alleviate the problem of computational time in permutation approaches.
+This is possible as the distribution of the adjusted measure looks similar for both appraches for higher levels."}
+G21_permutation <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds")) %>%
+  rename("wpd_permutation" = "value")
+
+# G21_model_data <- G21 %>%
+#   mutate(model =
+#            ((1/value)
+#                   - intercept -
+#                     slope*log(nx*nfacet))/slope) %>%
+#   mutate(model_trans =
+#            (model - mean(model))/sd(model))
+
+# G21_model_data$model %>% summary()
+
+G21_all_data <- G21_permutation %>% 
+  # left_join(G21_lm, by = c("nx", "nfacet", "perm_id")) %>% 
+  left_join(G21_glm, by = c("nx", "nfacet", "perm_id")) %>% 
+  pivot_longer(cols = c(3, 7),
+               names_to = "type_estimate",
+               values_to = "value_estimate")
+G21_all_data$type_estimate = factor(G21_all_data$type_estimate , levels = c( "wpd_permutation", "wpd_glm_scaled"))
+
+summary_data <- G21_all_data %>% 
+  group_by(nx, nfacet, type_estimate) %>% 
+  summarise(mean = mean(value_estimate)) %>% ungroup()
+
+G21_all_data %>% 
+  filter(type_estimate %in% c("wpd_glm_scaled", "wpd_permutation")) %>% 
+  ggplot(aes(x = value_estimate)) +
+  geom_density(aes(fill = type_estimate), alpha = 0.5, size = .5) +
+  #geom_vline(data = summary_data, aes(xintercept = mean, color = type_estimate)) + 
+  geom_rug(aes(color = type_estimate), length = unit(0.09,"cm"), alpha = 0.5) +
+  #coord_cartesian(clip = "off") + 
+  facet_grid(nx~nfacet,
+             labeller = "label_both") +
+  theme_bw() + 
+  theme(legend.position = "bottom") +
+  scale_fill_manual(values = c( "#D55E00", "#0072B2")) +
+  scale_color_manual(values = c( "#D55E00", "#0072B2")) +
+  xlab("adjusted values of wpd") +
+  scale_x_continuous(breaks = c(-5, -3, 0, 3, 5))
+
+```
 
@@
 
-## Simulation design
+\noindent _Simulation design_
 
 Observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = \{3, 7, 14\}$ and $nfacet = \{2, 9, 10\}$.
-The panel $(3, 2), (7,9), (14, 10)$ are considered to have design $D_{null}$.
-The panels $(7, 2), (14, 9)$ have design of the form $D_{var_f}$.
-$(14, 2), (3, 10)$ have design of the form $D_{var_x}$ and the rest are under $D_{var_{null}}$.
-We generate only one data set for which all these designs were simulated and consider this as the original data set.
-We generate $200$ repetitions of this experiment with different seeds and compute the proportion of times a panel is rejected when it is under $D_{null}$.
-We also compute the proportion of times a panel is rejected when it actually belongs to a non-null design.
-The first proportion is desired to be as small as possible and a higher value of the later is expected.
-Also, these would constitute to be the estimated size and power of the test.
+This would result in 9 panels, viz, $(3, 2), (3, 9), (3, 10), \dots, (14,9), (14, 10)$.
+Few experiments were conducted.
+In the first scenario, data for all panels are simulated using the null design  $D_{null}$.
+In other scenarios, data simulated from the panel $(14, 2)$ and $(3, 10)$ are under $D_{vary_{all}}$.
+Moreover, $\omega = \{0.5, 2, 5\}$ are considered to examine if the proposed test is able to capture subtle differences and non-subtle differences when we shift from the null design.
+In the last scenario, we consider the panel $(3, 2), (7,9), (14, 10)$ to be under $D_{null}$, the panels $(7, 2), (14, 9)$ to be under $D_{var_f}$.
+$(14, 2), (3, 10)$ under $D_{var_x}$ and the rest under $D_{var_{null}}$.
+This is done to check if the consequent ranking procedure leads to designs like $D_{vary_{all}}$ to be chosen first followed by $D_{vary_{all}}$.
+We generate only one data set each for which these scenarios were simulated and consider this as the original data set.
+We generate $1000$ repetitions of this experiment with different seeds.
 
-## Results
+\noindent _Results_
+
+```{r}
+all_data <- read_rds("simulations/supplementary/test-hpc/data-agg/all_data.rds")
+
+# computes size for 99 percentile threshold
+data_summary <- all_data %>%
+  mutate(sig = if_else(significance!=99, 0, 99)) %>% 
+  group_by(seed_id) %>% 
+  summarize(sumsig = sum(sig)) %>% 
+  count(sumsig==0) %>% 
+  mutate(p_value = n/sum(n)) %>% 
+  slice(1)
+
+# plots
+ggplot() + 
+  geom_histogram(data = all_data, aes(x = wpd))  + 
+  geom_vline(data = data_summary, aes(xintercept = p_value),colour = "red")
+```
 
@@
 
-```{r norm, fig.cap = "Distribution of $wpd_{perm}$ is plotted across different $nx$ and $nfacet$ categories.
-Both shape and scale of the distributions are now similar for different panels under the null design."}
-```
+<!-- $$y_l = a+b*log(z_l) + e_l , \quad l = (1, 2, \dots, L)$$,  -->
 
-```{r wpd-glm-dist, fig.cap = " The distribution of $wpd_{glm}$ is plotted. The distributions are more similar across higher nx and nfacet and dissimilar for fewer nc and nfacets."}
-
-```
-
-$$y_l = a+b*log(z_l) + e_l , \quad l = (1, 2, \dots, L)$$,
-
-\noindent where $y_l = median_s(wpd_{l, s})$, $wpd_{l, s}$ denotes the value of $wpd_{raw}$ obtained for the $l^{th}$ panel and $s^{th}$ simulation, $z_l$ is the number of groups $(nx*nfacet)$ in the $l^{th}$ panel and $e_l$ are idiosyncratic errors.
+<!-- \noindent where $y_l = median_s(wpd_{l, s})$, $wpd_{l, s}$ denotes the value of $wpd_{raw}$ obtained for the $l^{th}$ panel and $s^{th}$ simulation, $z_l$ is the number of groups $(nx*nfacet)$ in the $l^{th}$ panel and $e_l$ are idiosyncratic errors.
 Let $E(y) = \mu$ and $a + b*log(z) = g(\mu)$ where $g$ is the link function.
@@
 The residuals from this model $(y-\hat y) = (y-1/(\hat a + \hat b log(z)))$ would be expected to have no dependency on $z$.
-Thus, $wpd_{glm}$ is chosen as the residuals from this model and is defined as:
-$wpd_{glm} = wpd_{raw} - 1/(\hat a + \hat b*log(nx*nfacet))$.
+Thus, $wpd_{glm}$ is chosen as the residuals from this model and is defined as: -->
+<!-- $wpd_{glm} = wpd_{raw} - 1/(\hat a + \hat b*log(nx*nfacet))$. -->

### 2021-06-02 paper/scripts/main.R

@@ -398,6 +398,29 @@ G21 %>%
   theme(panel.grid.major.x = element_blank()) +
   theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=0.5))
 
+##----raw-onegran
+G21 <- read_rds("simulations/supplementary/one-gran/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds")
+
+summary_data <- G21 %>% 
+  group_by(nx, nfacet) %>% 
+  summarise(mean = mean(value))
+
+G21 %>% 
+  ggplot(aes(x = value)) + 
+  geom_density(fill = "#999999") +
+  facet_wrap(~nx, ncol = 1,
+             labeller = "label_both", strip.position = "right") + 
+  xlab("raw values of wpd") +
+  geom_vline(data = summary_data, aes(xintercept  = mean), color = "#0072B2") +
+  geom_rug(sides = "b", colour = "#D55E00") + 
+  # scale_x_continuous(breaks = scales::breaks_extended(2)) +
+  theme_bw() +
+  theme(panel.grid.major.x = element_blank()) +
+  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=0.5))
+
+
+
+
 
 ##----quadratic
 G21 %>% 
@@ -442,7 +465,7 @@ G21 %>%
 
 ## ---- glm-tab
 
-G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds"))
+G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds"))
 G21_median <- G21 %>% 
   group_by(nx*nfacet) %>% 
   summarise(actual = median(value))
@@ -490,14 +513,14 @@ G21_glm <- G21 %>%
   wpd_glm_scaled = ((wpd_glm*320)))
 
 #G21_glm$wpd_glm_scaled %>% sd()
-
-# G21_glm %>% 
+# 
+# G21_glm %>%
 #   ggplot() +
-#   geom_density(aes(x = wpd_glm), 
+#   geom_density(aes(x = wpd_glm),
 #                fill = "blue") +
 #   facet_grid(nx~nfacet,
 #              labeller = "label_both") +
-#   theme(legend.position = "bottom") 
+#   theme(legend.position = "bottom")
 
 
 ##----hist-qq-new

### 2021-06-02 simulations/supplementary/test-hpc/R-agg/analysis.R

@@ -16,8 +16,7 @@ data_summary <- all_data %>%
 # plots
 ggplot() + 
   geom_histogram(data = all_data, aes(x = wpd))  + 
-  geom_vline(data = data_summary, aes(xintercept = p_value),colour = "red") +
-  facet_grid(x_levels~facet_levels)
+  geom_vline(data = data_summary, aes(xintercept = p_value),colour = "red")
 
 
 

### 2021-06-02 simulations/supplementary/test-hpc/R-ind/power-one-alternate-med-inc.R

@@ -32,9 +32,9 @@ harmony_table <- expand.grid(
   mutate(design = c("null", "null", "varall", "null", "null", "null", "null", "null", "null"))
 
 # parameters and design used for this simulation
-npermj <- 2
+npermj <- 200
 ntimesj <- 500
-nsampj <- 10
+nsampj <- 100
 wj <- 2 # change this to change increment
 
 sim_null <- function(nxj, nfacetj, mean, sd, w = 0) {

### 2021-06-02 simulations/supplementary/test-hpc/R-ind/size-nullonly.R

@@ -28,7 +28,7 @@ harmony_table <- expand.grid(
   mutate(design = c("null", "null", "null", "null", "null", "null", "null", "null", "null"))
 
 # parameters and design used for this simulation
-npermj <- 20
+npermj <- 200
 ntimesj <- 500
 nsampj <- 100
 wj <- 2

### 2021-06-02 paper/main.Rmd
wpd of all introduction examples included

@@
 The value of the tuning parameter $\lambda$ is set to $0.67$, which has resulted in giving more emphasis to differences in x-axis categories.
+Again consider \ref{fig:onegran-new}(a) and \ref{fig:onegran-new}(b) with a $wpd$ value of 20.5 and 145 respectively.
+This is because there is more gradual increase across hours of the day than months of the year.
+If order is not considered, they result in a $wpd$ value of $97.8$ and $161$ respectively, which follows from the fact that if we consider difference between any hours of the day, the maginitude will be much larger than if we consider difference between consecutive categories.
+Simularly, for \ref{fig:onegran-new}(a) and (b) has $110.79$ and $125.82$ as the $wpd$ values and both are significant.
+The ranking implies that the distributional differences are more prominent for the second household, as is also seen from the bigger fluctuations in the $90^{th}$ percentile than the first household.
 

### 2021-06-10 paper/main.Rmd
added acknowledgment and supplementary section

@@
 
+# Acknowledgments {-}
+
+The Australian authors thank the ARC Centre of Excellence for Mathematical and Statistical Frontiers [(ACEMS)](https://acems.org.au/home) for supporting this research.
+Sayani Gupta was partially funded by [Data61 CSIRO](https://data61.csiro.au/) during her PhD.
+The Github repository,  [github.com/Sayani07/paper-hakear](https://github.com/Sayani07/paper-gravitas), contains all materials required to reproduce this article and the code is also available online in the supplemental materials.
+This article was created with R [@R-language], `knitr` [@knitr2015, @R-knitr] and `rmarkdown` [@rmarkdown2018, @R-rmarkdown].
+
+# Supplementary Materials
+
+**Data and scripts:** Data sets and R code to reproduce all figures in this article (main.R).
+
+\noindent
+**Simulation results and scripts:** All simulation table, graphics and and R code to reproduce it (paper-supplementary.pdf, paper-supplementary.Rmd)
+
+\noindent
+**R-package:** The open-source R [@R-language] package `hakear` [@R-hakear] is available on Github (https://github.com/Sayani07/hakear) to implement ideas presented in this paper.
+
 # Bibliography

### 2021-06-11 paper/paper-supplementary.Rmd
supplementary paper added

@@
   bookdown::pdf_book:
+    MonashEBSTemplates::workingpaper:
     #base_format: rticles::asa_article
@@
   echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
-  fig.path = "figure/", fig.align = "center", fig.show = "hold",
+  fig.path = "figure/", fig.align = "center", fig.show = "hold", fig.pos = "h",
   cache = TRUE, cache.path = "cache/",
@@
 
-Consider two cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.
 Let $v = \{v_t: t = 0, 1, 2, \dots, T-1\}$ be a continuous measured variable observed across $T$ time points.
-The pairwise distances between pairs ($a_jb_k,a_j'b_k'$) could be within-facets or within-facets a seen in Figure 4 of the main paper.
+The number of cyclic granularities considered in the display/analysis is $m$.
+Consider cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$.
+For $m=1$, only one of $A$ or $B$ is plotted at once and a _panel_ refers to a display of distributions of $v$ across $J$ or $K$ levels on the x-axis.
+For $m=2$, the distribution display of $v$ with $A$ placed across x-axis and $B$ across facets is referred to as a $(J, K)$ _panel_ ($J$ x-axis levels and $K$ facet levels).
+The pairwise distances between pairs ($a_jb_k,a_j'b_k'$) could be within-facets or between-facets as seen in Figure 4 of the main paper.
+The tuning parameter, used to put relative weight-age to the pairwise distances within and between facets is denoted by $\lambda$.
 Let the four elementary designs be $D_{null}$ where there is no pairwise difference in distribution of $v$ across $A$ or $B$, $D_{var_f}$ denotes the set of designs where there is difference in distribution of $v$ for $B$ and not for $A$.
@@
 Finally, $D_{var_{all}}$ denotes those designs for which difference is observed across both $A$ and $B$.
-The following method is deployed for generating different distributions across different combinations for non-null designs - suppose the distribution of the combination of first levels of x and facet category is $N(\mu,\sigma)$ and $\mu_{jk}$ denotes the mean of the combination $(a_jb_k)$, then $\mu_{j.} = \mu + j\omega$ (for design $D_{var_x}$) and $\mu_{.k} = \mu + k\omega$ (for design $D_{var_f}$).
-Table \ref{tab:explain-design} shows an example of how initial distributions are assigned in a panel with $nfacet = 3$ and $nx = 2$ for different designs using $\omega = 1$.
+The following method is deployed for generating different distributions across different combinations for non-null designs - suppose the distribution of the combination of first levels of x and facet category is $N(\mu,\sigma)$ and $\mu_{jk}$ denotes the mean of the combination $(a_jb_k)$, then $\mu_{j.} = \mu + j\omega$ (for design $D_{var_x}$) and $\mu_{.k} = \mu + k\omega$ (for design $D_{var_f}$), where $\omega$ denotes the increment in mean.
+Table \ref{tab:explain-design} shows an example of how designs are defined for a $(2, 3)$ panel using $\omega = 3$.
+$nx$ and $nfacet$ denotes the number of categories placed on x-axis and facets respectively.
+$wpd_{raw}$ and $wpd$ denote the raw and normalized weighted pairwise distances.
 
-```{r explain-design}
+```{r explain-design, fig.pos="h"}
 sim_varx_normal = function(nx, nfacet, mean, sd, w)
@@
 sd = 1
-w = 1
+w = 3
 nx = 2
@@
 
+null <-  sim_varall_normal(nx, nfacet, mean, sd, w=0) %>% tibble()
 vary_f <-  sim_varf_normal(nx, nfacet, mean, sd, w) %>% tibble()
@@
                        facet = facet, 
+                       null = null,
                        vary_f = vary_f, 
@@
   tibble() 
-names(raw_table) = c("x", "facet", "$D_{var_f}$", "$D_{var_x}$", "$D_{var_{all}}$" )
+names(raw_table) = c("x levels", "facet levels", "$D_{null}$",  "$D_{var_f}$", "$D_{var_x}$", "$D_{var_{all}}$" )
 raw_table %>% 
@@
     escape = FALSE,
-    caption = "Simulation setup for a panel with 3 facet levels and 2 x-axis levels for different designs starting from an initial distribution N(0, 1) for the combination $(a_1, b_1)$.") %>% kable_styling()
+    caption = "Simulation setup for a panel with 3 facet levels and 2 x-axis levels for different designs starting from an initial distribution N(0, 1) for the combination $(a_1, b_1)$ and $\\omega=1$.") %>% kable_styling()
 ```
 
-# Behavior of raw weighted distance measure
+# Raw weighted pairwise distance
 
@@
 
-How does the tuning parameter affects the value of $wpd$ under different designs?
-The tuning parameter is used to put relative weight-age to the difference in distributions within and between facets.
-So it is interesting to see how the value of $wpd$ changes for these two designs.
-But the tuning parameter might have a different impact depending on the value of $\omega$ and different levels of x and facets.
-Hence, a simulation study is conducted to see the impact of $\omega$, $nx$, $nfacet$ and $\lambda$ together on the values of $nx$ and $nfacet$.
+For $m=1$, pairwise distances could be defined only between different categories of the cyclic granularity considered.
+So no tuning parameter is applicable for this case.
+For $m=2$, $\lambda$ might impact $wpd_{raw}$ differently depending on the value of $\omega$ and different values of $nx$, $nfacet$ and designs.
+The following simulation study sees the impact of $\lambda$ for different $\omega$, $nx$, $nfacet$ and designs.
 
-### Simulation design
+_Simulation design_
 
-Observations are generated from Normal(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20\}$. 
-Let $\omega = \{1, 2, \dots, 10\}$ denotes the variable denoting the increment in mean of the distribution.
-The values of lambda ranges from ${0.1, 0.2, \dots, 0.9}$.
-Two designs are considered $D_{var_x}$ and $D_{var_f}$ and the values of $wpd$ is being computed for all these different values of the considered variable.
+Observations are generated from Normal(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7\}$ and $wpd_{raw}$ is computed for $\lambda = {0.1, 0.2, \dots, 0.9}$ under two designs $D_{var_x}$ and $D_{var_f}$ for $\omega = \{1, 8\}$  to observe how the value of $wpd_{raw}$ changes for different designs.
+Moreover, to observe for which value of $\lambda$ the two designs intersect, we generate observations from Normal(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20\}$ and $\omega = \{1, 2, \dots, 10\}$ under the same two designs.
 
-### Results
+<!-- and the values of $wpd$ is computed for all these different values of the variables $nx$, $nfacet$, $\lambda$ and $\omega$ under two different designs $D_{var_x}$ and $D_{var_f}$ .  -->
+
+_Results_
 
@@
 For a lower value of $\omega$, the two designs intersect at $\lambda > 0.7$ and for a higher $\omega$, the two designs intersect at $\lambda =  0.5$.
-The value of $wpd$ increases with $\lambda$ for $D_{var_x}$ and decreases with increasing $\lambda$ for 
-$D_{var_f}$.
-Figure \ref{fig:tuning-parameter-inter} shows the value of $\lambda$ for which the two designs intersect across different values of $\omega$.
+The value of $wpd$ increases with $\lambda$ for $D_{var_x}$ and decreases with increasing $\lambda$ for $D_{var_f}$.
+
+```{r tuning-oneomega, fig.cap = " $wpd_{raw}$ from two designs are plotted for different values of $\\lambda$ $nx$ and $nfacet$.
+For $\\omega = 1$, the designs intersect for $0.6<\\lambda<=0.75$, whereas for higher omega, design intersects at $\\lambda = 0.5$."}
+knitr::include_graphics(here::here("simulations/tuning_param/figs/fixed_omega.png"))
+```
+
+\noindent Figure \ref{fig:tuning-parameter-inter} shows the value of $\lambda$ for which the two designs intersect for different values of $\omega$.
 It can be observed that as the value of $\omega$ ($\omega > 4$) increase, the value of $\lambda$ at which the two designs intersect converge is $\lambda = 0.5$.
 
-```{r tuning-oneomega, fig.caption = "WPD from two designs are plotted for different values of lambda for different x and facet categories.
-For omega = 1, the designs intersect for 0.6<lamba<=0.75, whereas for higher omega, design intersects at lambda = 0.5"}
-knitr::include_graphics(here::here("simulations/tuning_param/figs/fixed_omega.png"))
-```
-```{r tuning-parameter-inter, fig.cap ="For most panels it is observed that the most common value of the tuning paramter for which the designs interact is 0.5, which implies any value greater than 0.5 could be chosen to up-weigh the within-facet distances and down-weigh the between-facet distances for most sitatuions."}
+```{r tuning-parameter-inter, fig.cap ="The point of intersection of $wpd_{raw}$ values under the designs $D_{var_f}$ and $D_{var_x}$ are plotted across different $\\omega$ and $\\lambda$.
+For most panels it is observed that a common value of $\\lambda$ for which the designs interact is $0.5$ for $\\omega >= 4$, which implies any value greater than $0.5$ could be chosen to up-weigh the within-facet distances and down-weigh the between-facet distances.
+The value of $\\lambda$ is higher for  $\\omega<4$ could be anywhere between 0.6 and 0.75."}
 knitr::include_graphics(here::here("simulations/tuning_param/figs/intersection_plot.png"))
@@
 
-Since the measure $wpd$ is essentially set up to detect "differences" in distributions irrespective of underlying distribution, it would be ideal if it has minimal dependency on the type, location and scale of the initial distribution.
-To that end, some data pre-processing through the Normal Score Transform (NQT) has been applied in order to make most asymmetrical distributed measured variables more normal-like.
-Figure \ref{fig:gamma-diff-wotrans} shows ridge plots of raw $wpd$ for a Gamma(0.5,1), Gamma(2,1) before NQT.
+The following simulation study sees the impact of different underlying distributions on $wpd_{raw}$ for different $nx$ and $nfacet$ before and after performing Normal Quantile Transformation.
+
+_Simulation design_
+
+Observations are generated from Normal(0,1), N(5, 1), N(0, 5), Gamma(0.5, 1) and Gamma(2, 1) distributions for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ and $wpd_{raw}$ is computed with $\lambda = 0.67$ with (scenario 1) and without (scenario 1) NQT.
+
+_Results_
+
+Figure \ref{fig:gamma-diff-wotrans} shows ridge plots of $wpd_{raw}$ for a Gamma(0.5,1), Gamma(2,1) before NQT.
 It is observed that for the underlying distribution Gamma(2,1), location and scale of the distribution of wpd changes from top-left panel to bottom-right panel.
-Moreover, the location and scale of the distribution of $wpd$ for different underlying distribution Gamma(0.5,1), Gamma(2,1).
-Figure \ref{fig:gamma-diff-quantrans} shows the the distributions of $wpd$ under same underlying distributions but after performing NQT.
+Figure \ref{fig:gamma-diff-quantrans} shows the the distributions of $wpd$ under same underlying distributions after performing NQT.
 It is observed that within each panel, the distributions of the $wpd$ looks same, however, the distributions change from extreme top-left panel to bottom-right panels.
 Similar observations could be made in Figure \ref{fig:normal-diff-quantrans} for different underlying normal distributions  N(0,1), N(5,1) and N(0,5).
-This implies, NQT has atleast been able to bridge the gap in distribution of $wpd$ for different non-normal underlying distributions.
+This implies, NQT has atleast been able to make the location and scale of the distribution of $wpd_{raw}$ same for different underlying distributions.
+
+<!-- Since the measure $wpd$ is essentially set up to detect "differences" in distributions irrespective of underlying distribution, it would be ideal if it has minimal dependency on the type, location and scale of the initial distribution.
+To that end, some data pre-processing through the Normal Score Transform (NQT) has been applied in order to make most asymmetrical distributed measured variables more normal-like.
+-->
 
@@
 ```{r normal-diff-quantrans, fig.cap = "Ridge plots of raw wpd is shown for N(0,1), N(5,1) and N(0,5) distribution.
-The densities change across different facet and x levels but look same for each panel, which implies wpd value is unaffected by the change in mean and standard deviation of the normal distribution", eval = FALSE}
+The densities change across different facet and x levels but look same for each panel, which implies wpd value is unaffected by the change in mean and standard deviation of the normal distribution."}
 knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_normal.png"))
@@
 
-## Case: m = 1
+## Number of comparisons
 
-```{r nxbyfacet-ridge-N01-onegran, fig.cap="Ridge plots of raw wpd is shown for N(0,5) distribution.
-For each panel, it could be seen that the location shifts to the right for increasing x levels.
-Across each panel, the scale of the distribution seems to change for low/moderately lower values and higher values of nfacets and left tails are longer for lower facet levels."}
-knitr::include_graphics(here::here("simulations/supplementary/one-gran/raw/null_design_quantrans/figs/nxbyfacet_ridge_wpd_N01.png"))
-```
+### Case: m = 1
 
-```{r nfacetbynx-onegran}
-knitr::include_graphics(here::here("simulations/supplementary/one-gran/raw/null_design_quantrans/figs/nfacetbynx_ridge_wpd_N01.png"))
-```
-
-```{r density-raw-onegran}
-knitr::include_graphics(here::here("simulations/supplementary/one-gran/raw/null_design_quantrans/figs/nxbyfacet_density_wpd_N01.png"))
-```
-
-## Case: m = 2
-
-```{r nxbyfacet-ridge-N01, fig.cap="Ridge plots of raw wpd is shown for N(0,5) distribution.
-For each panel, it could be seen that the location shifts to the right for increasing x levels.
-Across each panel, the scale of the distribution seems to change for low/moderately lower values and higher values of nfacets and left tails are longer for lower facet levels."}
-knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/nxbyfacet_ridge_wpd_N01.png"))
-```
-
-```{r nfacetbynx}
-knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/nfacetbynx_ridge_wpd_N01.png"))
-```
-
-```{r density-raw}
-knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/nxbyfacet_density_wpd_N01.png"))
-```
-
-# Adjusted wpd
-
-## Case: m = 1
-
-### Simulation design
+_Simulation design_
 
@@
 
-### Permutation approach
+_Results_
 
-```{r}
-include_graphics(here("simulations/supplementary/one-gran/raw/null_design_quantrans/figs/nxbyfacet_ridge_wpd_N01.png"))
+Figure \ref{fig:nxbyfacet-ridge-N01-onegran} shows ridge plots of $wpd_{raw}$ for an underlying N(0,1) distribution.
+For each panel, it could be seen that the location shifts to the right for increasing x levels.
+Across each panel, the scale of the distribution seems to change for low/moderately from lower values  to higher values of $nx$ and left tails are longer for lower facet levels.
+
+```{r nxbyfacet-ridge-N01-onegran, fig.cap="Ridge plots of raw wpd is shown for N(0,5) distribution.
+For each panel, it could be seen that the location shifts to the right for increasing x levels.
+Across each panel, the scale of the distribution seems to change for low/moderately lower values and higher values of nfacets and left tails are longer for lower facet levels."}
+knitr::include_graphics(here::here("simulations/supplementary/one-gran/raw/null_design_quantrans/figs/nxbyfacet_ridge_wpd_N01.png"))
 ```
 
-### Modeling approach
+```{r nfacetbynx-onegran, fig.cap="Ridge plots of raw wpd is shown for N(0,1) distribution. For each panel, it could be seen that the peakedness shifts for increasing x levels."}
+knitr::include_graphics(here::here("simulations/supplementary/one-gran/raw/null_design_quantrans/figs/nfacetbynx_ridge_wpd_N01.png"))
+```
+
+```{r density-raw-onegran, eval = FALSE}
+knitr::include_graphics(here::here("simulations/supplementary/one-gran/raw/null_design_quantrans/figs/nxbyfacet_density_wpd_N01.png"))
+```
+
+### Case: m = 2
+
+_Simulation design_
+
+\noindent Similarly, observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$.
+That is, data is being generated for each of the panels $(2, 2), (2, 3), (2, 5) \dots, (50, 31), (50, 50)$.
+For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
+That is, if we consider a $(2, 2)$ panel, $500$ observations are generated for each of the possible subsets, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
+
+Observations are generated from Gamma(2,1), G(0.5, 1), N(0,1), N(0, 5) and N(5, 1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
+Each combination is being referred to as a _panel_.
+That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$.
+For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
+That is, if we consider the panel $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
+The values
+of $wpd$ is obtained for each of the panels.
+The measurement variable for each combination of categories in a panel are drawn from the same distribution and hence the design corresponds to $D_{null}$ .
+Furthermore, this entire method is repeated for each panels $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
+
+_Results_
+
+Figure \ref{fig:nxbyfacet-ridge-N01}, \ref{fig:nfacetbynx} and  \ref{fig:density-raw} shows the ridge plot of $wpd_{raw}$ with $nx$ as facets, $nfacet$ as facets and the density plot of $wpd_{raw}$ with $nx$ on the x-axis and $nfacet$ on the facets.
+
+```{r nxbyfacet-ridge-N01, fig.cap="Ridge plots of raw wpd is shown for N(0,5) distribution.
+For each panel, it could be seen that the location shifts to the right for increasing x levels.
+Across each panel, the scale of the distribution seems to change for low/moderately lower values and higher values of nfacets and left tails are longer for lower facet levels."}
+knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/nxbyfacet_ridge_wpd_N01.png"))
+```
+
+```{r nfacetbynx, fig.cap="something1"}
+knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/nfacetbynx_ridge_wpd_N01.png"))
+```
+
+```{r density-raw, fig.cap="something2"}
+knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/nxbyfacet_density_wpd_N01.png"))
+```
+
+# Adjusted weighted pairwise distances
+
+_Simulation design_
+
+This sections shows the result from the different approaches of adjusting for the number of comparisons.Simulation design is the same as for raw weighted pairwise distances for $m=1$ and $m=2$.
+In place of $wpd_{raw}$, $wpd_{perm}$, $wpd_{glm}$ and $wpd$ is computed for all panel.
+
+<!-- \noindent Observations are generated from a N(0,1) distribution for each $nx = \{2, 3, 5, 7, 9, 14, 17, 20, 24, 31, 42, 50\}$ to cover a wide range of levels from very low to moderately high.
+$ntimes = 500$ observations are drawn for each combination of the categories, that is, for a panel with $nx=3$, $500$ observations are simulated for each of the categories.
+This design corresponds to $D_{null}$ as each combination of categories in a panel are drawn from the same distribution.
+Furthermore, the data is simulated for each of the categories $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
+The values of $wpd$ is obtained for each of the panels.
+$wpd_{l, s}$ denotes the value of $wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.
+-->
+
+## Permutation approach
+
+Figure \ref{fig:one-gran-nxnyfacet} and \ref{fig:norm} show the normalized ${wpd}$ for $m=1$ and $m=2$ respectively.
+The location and scale are brought to similar values for increasing values of $nx$ or $nfacet$.
+Due to heavy computational load, $wpd_{perm}$ for few panels with very high value of $nx$ or $nfacet$ are not computed.
+
+```{r one-gran-nxnyfacet, fig.cap="something3"}
+include_graphics(here("simulations/supplementary/one-gran/norm/null_design_quantrans_nperm/figs/nxbyfacet_ridge_wpd_N01.png"))
+```
+
+```{r norm, fig.cap = "Distribution of $wpd_{perm}$ is plotted across different $nx$ and $nfacet$ categories.
+Both shape and scale of the distributions are now similar for different panels under the null design."}
+G21_norm <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_Gamma21.rds"))
+
+G21_norm %>% 
+  ggplot(aes(x = value)) + 
+  geom_density(fill = "blue") +
+  facet_grid(nx~nfacet,
+             labeller = "label_both") + 
+  scale_x_continuous(breaks = scales::breaks_extended(3)) + 
+  xlab("wpd normalised using permutation approach")
+
+```
+
+## Modeling approach
 
@@
                data = G21_median)
+tidy(glm_fit)
 
@@
 
-### Combination approach
+### Case: m = 2
+
+```{r}
+G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds"))
+G01 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma01.rds"))
+N01 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds"))
+N05 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N05.rds"))
+N51 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N51.rds"))
+N55 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N55.rds"))
+
+all_data <- bind_rows(G21 = G21, G01 = G01, N01= N01, N05 = N05, N51= N51, N55 = N55, .id = "group")
+
+all_median <- all_data %>% 
+  group_by(group, nx*nfacet) %>% 
+    summarise(actual = median(value))
+
+glm_model <- function(df) {
+  glm(actual ~ log(`nx * nfacet`), 
+               family = Gamma(link = "inverse"), data = df)
+}
+
+glm_fit <- all_median %>% 
+  group_by(group) %>% 
+  nest()
+
+models <- map(glm_fit$data, glm_model)
+
+by_dist <- glm_fit %>% 
+  mutate(model = map(data, glm_model))
+
+tidy_obs <- by_dist %>%
+  mutate(tidy = map(model, tidy)) %>%
+  unnest(cols = c(tidy)) %>% 
+  mutate(estimate = round(estimate, 2),
+         std.error = round(std.error, 3),
+         statistic = round(statistic, 2))%>% 
+  mutate(distribution = case_when(
+    group== "G01" ~ "Gamma(0.5, 1)",
+    group== "G21" ~ "Gamma(2, 1)",
+    group== "N01" ~ "Normal(0, 1)",
+    group== "N05" ~ "Normal(0, 5)",
+    group== "N51" ~ "Normal(5, 1)",
+    group== "N55" ~ "Normal(5, 5)",
+    TRUE~ as.character(group)
+    )) %>% ungroup() %>% 
+  select(-data, -model, - group) %>% 
+     select(distribution, everything())
+
+tidy_obs %>% kable(caption = "Results of generalised linear model to capture the relationship between $wpd_{raw}$ and number of comparisons for different underlying distribution.")
+```
+
+```{r}
+
+G21_median <- N01 %>%
+  group_by(nx*nfacet) %>%
+  summarise(actual = median(value))
+
+glm_fit <- glm(actual ~ log(`nx * nfacet`),
+               family = Gamma(link = "inverse"),
+               data = G21_median)
+# tidy(glm_fit)
+
+```
+
+## Combination approach
+
+### Case: m = 1
+
+### Case: m = 2
+
+```{r dist-new-same-scale-link, fig.cap = "The distribution of $wpd_{perm}$ and $wpd_{glm-scaled}$ are overlaid to compare the location and scale across different $nx$ and $nfacet$.
+$wpd_{norm}$ takes the value of $wpd_{perm}$ for lower levels, and $wpd_{glm-scaled}$ for higher levels to to alleviate the problem of computational time in permutation approaches.
+This is possible as the distribution of the adjusted measure looks similar for both appraches for higher levels."}
+G21_permutation <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds")) %>%
+  rename("wpd_permutation" = "value")
+
+# G21_model_data <- G21 %>%
+#   mutate(model =
+#            ((1/value)
+#                   - intercept -
+#                     slope*log(nx*nfacet))/slope) %>%
+#   mutate(model_trans =
+#            (model - mean(model))/sd(model))
+
+# G21_model_data$model %>% summary()
+
+G21_all_data <- G21_permutation %>% 
+  # left_join(G21_lm, by = c("nx", "nfacet", "perm_id")) %>% 
+  left_join(G21_glm, by = c("nx", "nfacet", "perm_id")) %>% 
+  pivot_longer(cols = c(3, 7),
+               names_to = "type_estimate",
+               values_to = "value_estimate")
+G21_all_data$type_estimate = factor(G21_all_data$type_estimate , levels = c( "wpd_permutation", "wpd_glm_scaled"))
+
+summary_data <- G21_all_data %>% 
+  group_by(nx, nfacet, type_estimate) %>% 
+  summarise(mean = mean(value_estimate)) %>% ungroup()
+
+G21_all_data %>% 
+  filter(type_estimate %in% c("wpd_glm_scaled", "wpd_permutation")) %>% 
+  ggplot(aes(x = value_estimate)) +
+  geom_density(aes(fill = type_estimate), alpha = 0.5, size = .5) +
+  #geom_vline(data = summary_data, aes(xintercept = mean, color = type_estimate)) + 
+  geom_rug(aes(color = type_estimate), length = unit(0.09,"cm"), alpha = 0.5) +
+  #coord_cartesian(clip = "off") + 
+  facet_grid(nx~nfacet,
+             labeller = "label_both") +
+  theme_bw() + 
+  theme(legend.position = "bottom") +
+  scale_fill_manual(values = c( "#D55E00", "#0072B2")) +
+  scale_color_manual(values = c( "#D55E00", "#0072B2")) +
+  xlab("adjusted values of wpd") +
+  scale_x_continuous(breaks = c(-5, -3, 0, 3, 5))
+
+```
 
@@
 
-## Case: m = 2
-
 ### Simulation design
@@
 Furthermore, this entire method is repeated for each panels $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
-
-### Permutation approach
-
-```{r norm, fig.cap = "Distribution of $wpd_{perm}$ is plotted across different $nx$ and $nfacet$ categories.
-Both shape and scale of the distributions are now similar for different panels under the null design."}
-G21_norm <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_Gamma21.rds"))
-
-G21_norm %>% 
-  ggplot(aes(x = value)) + 
-  geom_density(fill = "blue") +
-  facet_grid(nx~nfacet,
-             labeller = "label_both") + 
-  scale_x_continuous(breaks = scales::breaks_extended(3)) + 
-  xlab("wpd normalised using permutation approach")
-
-```
-
-### Modeling approach
 
@@
 
-### Combination approach
+# Ranking and selecting harmonies
 
-```{r dist-new-same-scale-link, fig.cap = "The distribution of $wpd_{perm}$ and $wpd_{glm-scaled}$ are overlaid to compare the location and scale across different $nx$ and $nfacet$.
-$wpd_{norm}$ takes the value of $wpd_{perm}$ for lower levels, and $wpd_{glm-scaled}$ for higher levels to to alleviate the problem of computational time in permutation approaches.
-This is possible as the distribution of the adjusted measure looks similar for both appraches for higher levels."}
-G21_permutation <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds")) %>%
-  rename("wpd_permutation" = "value")
-
-# G21_model_data <- G21 %>%
-#   mutate(model =
-#            ((1/value)
-#                   - intercept -
-#                     slope*log(nx*nfacet))/slope) %>%
-#   mutate(model_trans =
-#            (model - mean(model))/sd(model))
-
-# G21_model_data$model %>% summary()
-
-G21_all_data <- G21_permutation %>% 
-  # left_join(G21_lm, by = c("nx", "nfacet", "perm_id")) %>% 
-  left_join(G21_glm, by = c("nx", "nfacet", "perm_id")) %>% 
-  pivot_longer(cols = c(3, 7),
-               names_to = "type_estimate",
-               values_to = "value_estimate")
-G21_all_data$type_estimate = factor(G21_all_data$type_estimate , levels = c( "wpd_permutation", "wpd_glm_scaled"))
-
-summary_data <- G21_all_data %>% 
-  group_by(nx, nfacet, type_estimate) %>% 
-  summarise(mean = mean(value_estimate)) %>% ungroup()
-
-G21_all_data %>% 
-  filter(type_estimate %in% c("wpd_glm_scaled", "wpd_permutation")) %>% 
-  ggplot(aes(x = value_estimate)) +
-  geom_density(aes(fill = type_estimate), alpha = 0.5, size = .5) +
-  #geom_vline(data = summary_data, aes(xintercept = mean, color = type_estimate)) + 
-  geom_rug(aes(color = type_estimate), length = unit(0.09,"cm"), alpha = 0.5) +
-  #coord_cartesian(clip = "off") + 
-  facet_grid(nx~nfacet,
-             labeller = "label_both") +
-  theme_bw() + 
-  theme(legend.position = "bottom") +
-  scale_fill_manual(values = c( "#D55E00", "#0072B2")) +
-  scale_color_manual(values = c( "#D55E00", "#0072B2")) +
-  xlab("adjusted values of wpd") +
-  scale_x_continuous(breaks = c(-5, -3, 0, 3, 5))
-
-```
-
-# Ranking and selecting harmonies
+## Size
 
@@
 
+## Power
+
 ```{r hist-qq-new, fig.cap = "In panel a, the histogram of $wpd_{glm-scaled}$ is plotted.

### 2021-06-11 paper/paper-supplementary.Rmd
fine-tining tuning paramter graphs

@@
 
+### Case: m = 1
+
+Figure \ref{fig:glm-horizontal-onegran} shows the scatterplot of $wpd_{raw}$ against different values of $nx$ and also the display of residuals from the model.
+Figure \ref{fig:glm-density-onegran} shows the distribution of $wpd_{glm}$ for different $nx$.
+
 ```{r}
+G21_onegran <- read_rds(here("simulations/supplementary/one-gran/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds"))
+
+G21_median_onegran  <- G21_onegran  %>% 
+  group_by(nx*nfacet) %>% 
+  summarise(actual = median(value))
+
+glm_fit_onegran  <- glm(actual ~ log(`nx * nfacet`),
+               family = Gamma(link = "inverse"),
+               data = G21_median_onegran)
+
+bind_cols(distribution = "Normal (0, 1)", broom::tidy(glm_fit_onegran)) %>% kable(caption = "Results of generalised linear model to capture the relationship between $wpd_{raw}$ and number of comparisons for $m=1$.")
+
+```
+
+```{r glm-horizontal-onegran, fig.cap = "Residuals from the model is plotted across different $nx$. Residuals seem to be indeoendent of $nx$ and have been defined as $wpd_{glm}$ in the paper."}
+
 G21 <- read_rds(here("simulations/supplementary/one-gran/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds"))
@@
                data = G21_median)
-tidy(glm_fit)
 
@@
   ylab("wpd_glm = wpd_raw - 1/(a  + b*log(nx*nfacet))")
+```
 
+```{r glm-density-onegran, fig.cap = "Distribution of $wpd_{glm}$ is plotted across different $nx$. Both shape and scale of the distributions are different for lower $nx$ than for higher $nx$."}
 G21_glm <- G21 %>% 
@@
   ggridges::geom_density_ridges()  + 
-  facet_wrap(~nfacet, labeller = "label_both", nrow = 2) + 
   xlab("mmpd") +
@@
 
-```{r}
+Figure \ref{fig:glm-horizontal-onegran} shows the scatterplot of $wpd_{raw}$ against different values of $nx$ and also the display of residuals from the model.
+Figure \ref{fig:wpd-glm-dist} shows the distribution of $wpd_{glm}$ for different $nx$.
+
+```{r tab-models}
 G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds"))
@@
 
-```{r}
+<!-- # ```{r} -->
+<!-- #  -->
+<!-- # G21_median <- N01 %>% -->
+<!-- #   group_by(nx*nfacet) %>% -->
+<!-- #   summarise(actual = median(value)) -->
+<!-- #  -->
+<!-- #  -->
+<!-- # glm_fit <- glm(actual ~ log(`nx * nfacet`), -->
+<!-- #                family = Gamma(link = "inverse"), -->
+<!-- #                data = G21_median) -->
+<!-- # # tidy(glm_fit) -->
+<!-- #  -->
+<!-- # ``` -->
 
-G21_median <- N01 %>%
+```{r glm-horizontal-twogran, fig.cap = "Residuals from the model is plotted across different $nx$ and $nfacet$.
+Residuals seem to be independent of $log(nx*nfacet)$ and have been defined as $wpd_{glm}$ in the paper."}
+
+G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds"))
+G21_median <- G21 %>% 
   group_by(nx*nfacet) %>% 
   summarise(actual = median(value))
-
 glm_fit <- glm(actual ~ log(`nx * nfacet`),
@@
                data = G21_median)
-# tidy(glm_fit)
+intercept <- glm_fit$coefficients[1]
+slope <- glm_fit$coefficients[2]
+G21_sd  = G21 %>% 
+  mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
+  )
+  )
+  ))
+#scale_fac <- 1/G21_sd$wpd_glm %>% sd()
+# checking the fit of the residuals from glm fit
+# fitted_glm <- fitted(glm_fit, type = "response")
+# residuals <- residuals.glm(glm_fit, type = "response")
+# hist(residuals)
+#h = augment(glm_fit)
+# ggplot(h) +
+#   geom_histogram(aes(x = .resid))
+# residual <- G21_median$actual  - fitted_glm
+# 
+# hist(residual)
+G21 %>%
+  ggplot(aes(x=log(nx*nfacet),
+             y = (value - (1/(intercept + slope*log(nx*nfacet)
+             )
+             )
+             )
+  )
+  ) +
+  geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") +
+  ylab("wpd_glm = wpd_raw - 1/(a  + b*log(nx*nfacet))")
+broom::tidy(glm_fit) %>% kable(caption = "Results of generalised linear model to capture the relationship between $wpd_{raw}$ and number of comparisons.")
+```
+
+```{r wpd-glm-dist, fig.cap = " The distribution of $wpd_{glm}$ is plotted. The distributions are more similar across higher $nx$ and nfacet and dissimilar for fewer $nx$ and $nfacet$."}
+G21_glm <- G21 %>% 
+  mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
+  )
+  )
+  ),
+  wpd_glm_scaled = ((wpd_glm*320)))
+
+G21_glm$wpd_glm_scaled %>% sd()
+
+G21_glm %>%
+  ggplot() +
+  geom_density(aes(x = wpd_glm),
+               fill = "blue") +
+  facet_grid(nx~nfacet,
+             labeller = "label_both") +
+  theme(legend.position = "bottom")
 
@@
 
-### Case: m = 1
+```{r dist-same-scale-onegran, fig.cap = "The distribution of $wpd_{perm}$ and $wpd_{glm-scaled}$ are overlaid to compare the location and scale across different $nx$ for $m=1$.
+The distribution of the adjusted measure looks similar for both appraches for higher levels."}
+G21_permutation <- read_rds(here("simulations/supplementary/one-gran/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds")) %>%
+  rename("wpd_permutation" = "value")
 
-### Case: m = 2
+# G21_model_data <- G21 %>%
+#   mutate(model =
+#            ((1/value)
+#                   - intercept -
+#                     slope*log(nx*nfacet))/slope) %>%
+#   mutate(model_trans =
+#            (model - mean(model))/sd(model))
 
-```{r dist-new-same-scale-link, fig.cap = "The distribution of $wpd_{perm}$ and $wpd_{glm-scaled}$ are overlaid to compare the location and scale across different $nx$ and $nfacet$.
+# G21_model_data$model %>% summary()
+
+G21_all_data <- G21_permutation %>% 
+  # left_join(G21_lm, by = c("nx", "nfacet", "perm_id")) %>% 
+  left_join(G21_glm, by = c("nx", "nfacet", "perm_id")) %>% 
+  pivot_longer(cols = c(3, 7),
+               names_to = "type_estimate",
+               values_to = "value_estimate")
+G21_all_data$type_estimate = factor(G21_all_data$type_estimate , levels = c( "wpd_permutation", "wpd_glm_scaled"))
+
+summary_data <- G21_all_data %>% 
+  group_by(nx, nfacet, type_estimate) %>% 
+  summarise(mean = mean(value_estimate)) %>% ungroup()
+
+G21_all_data %>% 
+  filter(type_estimate %in% c("wpd_glm_scaled", "wpd_permutation")) %>% 
+  ggplot(aes(x = value_estimate)) +
+  geom_density(aes(fill = type_estimate), alpha = 0.5, size = .5) +
+  geom_vline(data = summary_data, aes(xintercept = mean, color = type_estimate)) + 
+  geom_rug(aes(color = type_estimate), length = unit(0.09,"cm"), alpha = 0.5) +
+  #coord_cartesian(clip = "off") + 
+  facet_wrap(~nx,
+             labeller = "label_both") +
+  theme_bw() + 
+  theme(legend.position = "bottom") +
+  scale_fill_manual(values = c( "#D55E00", "#0072B2")) +
+  scale_color_manual(values = c( "#D55E00", "#0072B2")) +
+  xlab("adjusted values of wpd") 
+```
+
+```{r dist-new-same-scale-link, fig.cap = "The distribution of $wpd_{perm}$ and $wpd_{glm-scaled}$ are overlaid to compare the location and scale across different $nx$ and $nfacet$ for $m=2$.
 $wpd_{norm}$ takes the value of $wpd_{perm}$ for lower levels, and $wpd_{glm-scaled}$ for higher levels to to alleviate the problem of computational time in permutation approaches.
 This is possible as the distribution of the adjusted measure looks similar for both appraches for higher levels."}
+
+G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds"))
+G21_median <- G21 %>% 
+  group_by(nx*nfacet) %>% 
+  summarise(actual = median(value))
+glm_fit <- glm(actual ~ log(`nx * nfacet`),
+               family = Gamma(link = "inverse"),
+               data = G21_median)
+intercept <- glm_fit$coefficients[1]
+slope <- glm_fit$coefficients[2]
+
+G21_glm <- G21_glm <- G21 %>% 
+  mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
+  )
+  )
+  ),
+  wpd_glm_scaled = ((wpd_glm*320)))
+
 G21_permutation <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds")) %>%
@@
 
-```{r}
-G21_permutation <- read_rds(here("simulations/supplementary/one-gran/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds")) %>%
-  rename("wpd_permutation" = "value")
-
-# G21_model_data <- G21 %>%
-#   mutate(model =
-#            ((1/value)
-#                   - intercept -
-#                     slope*log(nx*nfacet))/slope) %>%
-#   mutate(model_trans =
-#            (model - mean(model))/sd(model))
-
-# G21_model_data$model %>% summary()
-
-G21_all_data <- G21_permutation %>% 
-  # left_join(G21_lm, by = c("nx", "nfacet", "perm_id")) %>% 
-  left_join(G21_glm, by = c("nx", "nfacet", "perm_id")) %>% 
-  pivot_longer(cols = c(3, 7),
-               names_to = "type_estimate",
-               values_to = "value_estimate")
-G21_all_data$type_estimate = factor(G21_all_data$type_estimate , levels = c( "wpd_permutation", "wpd_glm_scaled"))
-
-summary_data <- G21_all_data %>% 
-  group_by(nx, nfacet, type_estimate) %>% 
-  summarise(mean = mean(value_estimate)) %>% ungroup()
-
-G21_all_data %>% 
-  filter(type_estimate %in% c("wpd_glm_scaled", "wpd_permutation")) %>% 
-  ggplot(aes(x = value_estimate)) +
-  geom_density(aes(fill = type_estimate), alpha = 0.5, size = .5) +
-  geom_vline(data = summary_data, aes(xintercept = mean, color = type_estimate)) + 
-  geom_rug(aes(color = type_estimate), length = unit(0.09,"cm"), alpha = 0.5) +
-  #coord_cartesian(clip = "off") + 
-  facet_wrap(~nx,
-             labeller = "label_both") +
-  theme_bw() + 
-  theme(legend.position = "bottom") +
-  scale_fill_manual(values = c( "#D55E00", "#0072B2")) +
-  scale_color_manual(values = c( "#D55E00", "#0072B2")) +
-  xlab("adjusted values of wpd") 
-```
-
 ### Simulation design
@@
 Furthermore, this entire method is repeated for each panels $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
-
-```{r wpd-glm-dist, fig.cap = " The distribution of $wpd_{glm}$ is plotted. The distributions are more similar across higher nx and nfacet and dissimilar for fewer nc and nfacets."}
-
-G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds"))
-G21_median <- G21 %>% 
-  group_by(nx*nfacet) %>% 
-  summarise(actual = median(value))
-glm_fit <- glm(actual ~ log(`nx * nfacet`),
-               family = Gamma(link = "inverse"),
-               data = G21_median)
-intercept <- glm_fit$coefficients[1]
-slope <- glm_fit$coefficients[2]
-G21_sd  = G21 %>% 
-  mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
-  )
-  )
-  ))
-#scale_fac <- 1/G21_sd$wpd_glm %>% sd()
-# checking the fit of the residuals from glm fit
-# fitted_glm <- fitted(glm_fit, type = "response")
-# residuals <- residuals.glm(glm_fit, type = "response")
-# hist(residuals)
-#h = augment(glm_fit)
-# ggplot(h) +
-#   geom_histogram(aes(x = .resid))
-# residual <- G21_median$actual  - fitted_glm
-# 
-# hist(residual)
-# G21 %>% 
-#   ggplot(aes(x=log(nx*nfacet),
-#              y = (value - (1/(intercept + slope*log(nx*nfacet)
-#              )
-#              )
-#              )
-#   )
-#   ) +
-#   geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
-#   ylab("wpd_glm = wpd_raw - 1/(a  + b*log(nx*nfacet))")
-broom::tidy(glm_fit) %>% kable(caption = "Results of generalised linear model to capture the relationship between $wpd_{raw}$ and number of comparisons.")
-
-G21_glm <- G21 %>% 
-  mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
-  )
-  )
-  ),
-  wpd_glm_scaled = ((wpd_glm*320)))
-
-G21_glm$wpd_glm_scaled %>% sd()
-
-G21_glm %>%
-  ggplot() +
-  geom_density(aes(x = wpd_glm),
-               fill = "blue") +
-  facet_grid(nx~nfacet,
-             labeller = "label_both") +
-  theme(legend.position = "bottom")
-
-```
 
@@
 # computes size for 99 percentile threshold
-data_summary <- all_data %>%
+all_data <- all_data %>%
+  filter(!is.na(x_levels), !is.na(facet_levels))
+
+data_summary <- all_data%>% 
+  mutate(sig = if_else(significance!=99, 0, 99)) %>% 
+  group_by(seed_id) %>% 
+  summarize(sumsig = sum(sig)) %>% 
+  count(sumsig==0) %>% 
+  mutate(p_value = n/sum(n)) %>% 
+  slice(1)
+
+data_summary_lowlev <- all_data%>% 
+  filter(x_levels==3, facet_levels ==2) %>% 
   mutate(sig = if_else(significance!=99, 0, 99)) %>% 
@@
 # plots
+
+global_threshold <-  tibble(threshold = "99", value = quantile(all_data$wpd, 0.99, na.rm = TRUE))
+```
+
+$wpd_{threshold99}$ is obtained as `r round(global_threshold$value, 2)` for this experiment, which leads to a p-value of `r round(data_summary$p_value, 3)`.
+Figure \ref{fig:global-size} shows the distribution of $wpd$ obtained from this experiment with the red line denoting $wpd_{threshold99}$.
+If we split the diplay of distribution between $nx$ and $nfacet$, then Figure \ref{fig:local-size} shows that the probability of rejecting the null when it is actually true is higher for smaller levels, however, it is still within limits (around `r round(data_summary_lowlev$p_value, 3)`).
+
+```{r global-size, fig.cap = "something"}
 ggplot() + 
   geom_histogram(data = all_data, aes(x = wpd))  + 
-  geom_vline(data = data_summary, aes(xintercept = p_value),colour = "red")
+  geom_vline(data = global_threshold, aes(xintercept =  value),colour = "red", size = 1.5) 
+```
+
+```{r local-size, fig.cap = "something"}
+ggplot() + 
+  geom_histogram(data = all_data, aes(x = wpd))  + 
+  geom_vline(data = global_threshold, aes(xintercept =  value),colour = "red", size = 1.5) +
+  facet_grid(x_levels~facet_levels)
 ```

### 2021-06-11 simulations/supplementary/test-hpc/R-agg/analysis.R

@@ -4,7 +4,7 @@ all_data <- read_rds("simulations/supplementary/test-hpc/data-agg/all_data.rds")
 
 
 # computes size for 99 percentile threshold
-data_summary <- all_data %>%
+data_summary <- all_data %>% 
   mutate(sig = if_else(significance!=99, 0, 99)) %>% 
   group_by(seed_id) %>% 
   summarize(sumsig = sum(sig)) %>% 
@@ -16,11 +16,7 @@ data_summary <- all_data %>%
 # plots
 ggplot() + 
   geom_histogram(data = all_data, aes(x = wpd))  + 
-  geom_vline(data = data_summary, aes(xintercept = p_value),colour = "red")
-
-
-
-
+  geom_vline(data = data_summary, aes(xintercept = p_value),colour = "red", size= 1.5) 
 
 
 # computes size for 95 percentile threshold
@@ -46,7 +42,6 @@ data_summary %>%
 
 # plot
   
-  
 # p_data <- all_data %>% 
 #     mutate(sig = if_else(significance!=99, 0, 99)) %>% 
 #     group_by(x_levels, facet_levels) %>% 
@@ -54,8 +49,6 @@ data_summary %>%
 #               .groups = 'drop') %>%
 #     summarise(p_value = sum(p_value))
 #     
-
-
 
 +
   geom_text(data = round(compute_p_value, 3), size = 3,  

### 2021-06-11 paper/paper-supplementary.Rmd
display correct till Figure 10 done

@@
 library(broom)
+library(latex2exp)
 
@@
 
-```{r nxbyfacet-ridge-N01-onegran, fig.cap="Ridge plots of raw wpd is shown for N(0,5) distribution.
+```{r nxbyfacet-ridge-N01-onegran, fig.cap="Ridge plots of raw wpd is shown for N(0,1) distribution.
 For each panel, it could be seen that the location shifts to the right for increasing x levels.

### 2021-06-11 simulations/raw/null_design_scale/R-agg/makegraph02.R

@@ -8,7 +8,8 @@ library(tidyverse)
 
 makegraph02 <- function(folder_name){
 all_data <- read_rds(paste0("simulations/null_design/data/all_data_", folder_name, ".rds"))
-  
+
+all_data <- read_rds(paste0("simulations/raw/null_design_scale/data-agg/all_data_wpd", folder_name, ".rds"))  
 
 nxbyfacet <- all_data %>% 
   ggplot(aes(x = value)) + 

### 2021-06-14 paper/main.Rmd
intro change a bit

@@
 This work provides a methodology to screen and rank the displays that are most informative in discerning distributional differences.
-This is done by introducing a distance measure for one or a pair of cyclic granularities that could be compared across different levels and data sets.
+This is done by introducing a distance measure for one or a pair of cyclic granularities that could be compared across different cyclic granularities and data sets.
 All the methods are implemented in the open-source R package `hakear`.
@@
 Figure \ref{fig:onegran-new} shows the distribution of energy usage of one household (id 2) across cyclic granularity a) hour-of-day and b) month-of-year.
-Figure \ref{fig:onegran-new}(a) shows that energy consumption is higher during the morning hours (5-8) when members in the household wake up and then again in the evening hours (17-20) possibly when members get back from work with maximum variation (large inter-quartile range) in behavior in the afternoon hours (12-16).
+Figure \ref{fig:onegran-new}(a) shows that energy consumption is higher during the morning hours (5-8) when members in the household wake up and then again in the evening hours (17-20) possibly when members get back from work with maximum variation (large interquartile range) in behavior in the afternoon hours (12-16).
 Figure \ref{fig:onegran-new}(b) shows the distribution of energy consumption across months January to June.
-The median and quartile deviation of energy usage in Jan and Feb are generally on a much higher side, possibly due to the usage of air conditioners (Jan, Feb are peak summer in Australia), however for other months (Mar-Jun, autumn and winter), the smaller median and quartile deviation indicate a more consistent behavior.
-It might also imply that this household do not use as much heater as compared to air conditioner.
+The median and quartile deviation of energy usage in Jan and Feb are generally on a much higher side, possibly due to the usage of air conditioners (Jan, Feb are peak summer in Australia), however, for other months (Mar-Jun, autumn and winter), the smaller median and quartile deviation indicate a more consistent behavior.
+It might also imply that this household does not use as much heater as compared to air conditioner.
 A lot of households in Victoria use gas heating and hence the usage of heaters might not be reflected here.
 Potentially many such displays could be drawn across day-of-week, day-of-month, weekday/weekend, or any other chosen cyclic granularities of interest.
-However, all of them would not be interesting to discern important patterns in the energy usage.
+However, all of them would not be interesting to discern important patterns in energy usage.
 Only those displays, which have "significant" distributional differences between categories of the cyclic granularity would be informative.
@@
 ```{r onegran-new, fig.cap="Boxplots showing the distribution of one household across one cyclic granularity at a time - (a) hour-of-day and (b) and month-of-year.
-The daily and annual periodic behavior of energy is apparent in (a) and (b) respectively, with daily peaks occuring in morning and evening hours when members in the house are present and active, more volatility (usage of air conditioner) in summer months (Jan, Feb) due to air conditioners and more consistent behavior in winter and autumn months (Mar, Apr, May, June)."}
+The daily and annual periodic behavior of energy is apparent in (a) and (b) respectively, with daily peaks occurring in morning and evening hours when members in the house are present and active, more volatility (usage of air conditioner) in summer months (Jan, Feb) due to air conditioners and more consistent behavior in winter and autumn months (Mar, Apr, May, June)."}
 ```
@@
 <!-- comparing one and two grans for one households -->
-\noindent Exploring the distribution of the measured variable across two cyclic granularities tend to provide more detailed information on its structure.
+\noindent Exploring the distribution of the measured variable across two cyclic granularities tends to provide more detailed information on its structure.
 For example, Figure \ref{fig:id2-new2}(a) slice down further by showing the usage distribution across hour-of-day conditional on month-of-year across two households (id 2 and 4).
-It shows the hourly usage over a day do not remain same across months.
-Unlike other months, the 75th and 90th percentile for all hours of the day in January are high, pretty close and are not characterized by a morning and evening peak.
+It shows the hourly usage over a day does not remain the same across months.
+Unlike other months, the 75th and 90th percentile for all hours of the day in January are    high, pretty close, and are not characterized by a morning and evening peak.
 The household in Figure \ref{fig:id2-new2}(b) has 90th percentile consumption higher in summer months relative to autumn or winter, but the 75th and 90th percentile are far apart in all months, implying that the second household resorts to air conditioning much less regularly than the first one.
 The differences seem to be more prominent across month-of-year (facets) than hour-of-day (x-axis) for this household, whereas they are prominent for both cyclic granularities for the first household.
+
+<!-- The problem and its dimension -->
+\noindent Are all of these four displays in Figures \ref{fig:onegran-new} and \ref{fig:id2-new2} useful in understanding the distributional difference in energy usage?
+Which ones are more useful than others?
+If $N_C$ is the total number of cyclic granularities of interest, the number of displays that could be potentially informative is $N_C$ when considering displays of the form in Figure \ref{fig:onegran-new}.
+The dimension of the problem, however, increases when considering more than one cyclic granularity.
+When considering displays of the form in Figure \ref{fig:id2-new2},
+there are $^{N_C}P_2$ possible pairwise plots exhaustively, with one of the two cyclic granularities acting as the conditioning variable. 
+This is huge and overwhelming for human consumption even for moderately large $N_C$.
 It could be immensely useful to make the transition from all potential displays to the ones that are informative across atleast one cyclic granularity.
@@
 
-<!-- what is the dimension of the problem -->
-\noindent The dimension of this problem, however, increases when considering more than one cyclic granularity.
-Let $N_C$ be the total number of cyclic granularities of interest.
-That essentially implies ,  for two cyclic granularities, there are $^{N_C}P_2$ possible pairwise plots exhaustively, with one of the two cyclic granularities acting as the conditioning variable.
-This is large and overwhelming for human consumption.<!-- Scagnostics literature --> This problem is similar to Scagnostics (Scatterplot Diagnostics) by @tukey1988computer, which is used to identify meaningful patterns in large collections of scatterplots.
+<!-- Scagnostics literature, other literature and why we need more/different -->
+
+\noindent This problem is similar to Scagnostics (Scatterplot Diagnostics) by @tukey1988computer, which is used to identify meaningful patterns in large collections of scatterplots.
 Given a set of $v$ variables, there are $v(v-1)/2$ pairs of variables, and thus the same number of possible pairwise scatterplots.
 Therefore, even for small $v$, the number of scatterplots can be large, and scatterplot matrices (SPLOMs) could easily run out of pixels when presenting high-dimensional data.
-@Dang2014-tw and @wilkinson2005graph provides potential solutions to this, where few characterizations can be used to locate anomalies in density, shape, trend, and other features in the 2D point scatters.
-In this paper, we provide a solution to narrowing down the search from $^{N_C}P_2$ plots by introducing a new distance measure that can be used to detect significant distributional differences across cyclic granularities.
+@Dang2014-tw and @wilkinson2005graph provide potential solutions to this, where few characterizations can be used to locate anomalies in density, shape, trend, and other features in the 2D point scatters.
+In this paper, we provide a solution to narrowing down the search from $^{N_C}P_2$ plots by introducing a new distance measure that can be used to detect significant distributional differences across cyclic granularities.<!-- harmonies and why it is not enough --> This work is a natural extension of our previous work [@Gupta2020-vo] that narrows down the search from $^{N_C}P_2$ plots by identifying pairs of granularities that can be meaningfully examined together (a "harmony"), or when they cannot (a "clash").
+However, even after excluding clashes, the list of harmonies left could be enormous for exhaustive exploration.
+Hence, there is a need to reduce the search even further by including only those harmonies which are informative enough.
+@inference and @Majumder2013-hb present methods for statistical significance testing of visual findings using human cognition as the statistical tests.
+In this paper, the visual discovery of distributional differences is facilitated by choosing a threshold for the proposed numerical distance measure, eventually selecting only those cyclic granularities for which the distributional differences are sufficient to make it an interesting display.
 
@@
 
-<!-- harmonies and why it is not enough -->
-\noindent This work is a natural extension of our previous work [@Gupta2020-vo] that narrows down the search from $^{N_C}P_2$ plots by identifying pairs of granularities that can be meaningfully examined together (a "harmony"), or when they cannot (a "clash").
-However, even after excluding clashes, the list of harmonies left could be enormous for exhaustive exploration.
-Hence, there is a need to reduce the search even further by including only those harmonies which are informative enough.
-@inference and @Majumder2013-hb present methods for statistical significance testing of visual findings using human cognition as the statistical tests.
-In this paper, the visual discovery of distributional differences is facilitated by choosing a threshold for the proposed numerical distance measure, eventually selecting only those cyclic granularities for which the distributional differences are sufficient to make it an interesting display.
-
 Our contributions in this paper are:
@@
 
-The article is organized as follows.
+\noindent The article is organized as follows.
 Section \ref{sec:computation-wpd} introduces a new distance measure, discusses the reasoning and details the computation.
-Section \ref{sec:rank-wpd} discusses how to choose a threshold to select only significant harmonies.
+Section \ref{sec:rank-wpd} discusses how to choose a threshold to select only useful displays.
 Section \ref{sec:simulations} provides some simulation study on the proposed methodology.
-Section \ref{sec:application-wpd} presents an application to a residential smart meter data in Melbourne to show how this distance measure acts as a way to automatically detect periodic patterns in time series.
+Section \ref{sec:application-wpd} presents an application to residential smart meter data in Melbourne to show how the proposed methodology can be used to automatically detect temporal granularities along which distributional differences are significant.
+
+<!-- acts as a way to automatically detect periodic patterns in time series. -->
 

### 2021-06-14 paper/main.Rmd
bib update

@@
 When $m=2$, following the principle of Gestalt theory, $\lambda = \frac{2}{3} = 0.67$ is chosen to put a relative weightage of $2:1$ for within-facet and between-facet distances.
-No human experiment is conducted to justify this ratio, however, typically a tuning parameter $\lambda>0.5$ would tend to upweigh the within-facet distances and that with $<0.5$ would upweigh the between-facet distances (refer to the Supplementary section of the paper for more details).
-For $m = 1$, since there are no conditioning variables or groups, $\lambda = 1$.
+No human experiment is conducted to justify this ratio, however, typically a tuning parameter $\lambda>0.5$ would tend to upweigh the within-facet distances and that with $<0.5$ would upweigh the between-facet distances (refer to the Supplementary paper for more details).
+For $m = 1$, there are no conditioning variables or groups, and hence $\lambda = 1$.
 
@@
 The pairwise distances between pairs $(a_{j} b_{k}, a_{j'}b_{k'})$  denoted by $d_{(jk, j'k')} = JSD(q_{jk}, q_{j'k'})$ is computed (_distance between distributions_).
-The pairwise distances (_Within-facet and between-facet_) are transformed using a suitable tuning parameter ($0<\lambda<1$) depending on if they are within-facet($d_w$) or between-facets($d_b$) as follows:
+The pairwise distances (_Within-facet and between-facet_) are transformed using a suitable _tuning parameter_ ($0<\lambda<1$) depending on if they are within-facet($d_w$) or between-facets($d_b$) as follows:
 \begin{equation}\label{def:raw-wpd}
@@
 
-Ideally, it is desired that $wpd$ takes a higher value only if there is a significant difference between distributions across categories, and not because the number of categories $J$ or $K$ is high.
-That is, under designs like $D_{null}$, the distribution of the $wpd$ values should not differ for a different number of categories.
+Ideally, it is desired that the proposed distance measure takes a higher value only if there is a significant difference between distributions across categories, and not because the number of categories $J$ or $K$ is high.
+That is, under designs like $D_{null}$, their distribution should not differ for a different number of categories.
 Only then the distance measure could be compared across panels with different levels.
@@
 The first one defines an adjusted measure $wpd_{perm}$ based on the permutation method to remove the effect of different comparisons.
-The second approach fits a model to represent the relationship between $wpd_{raw}$ and the number of comparisons and defines the adjusted measure ($wpd_{glm-scaled}$) as the residual from the model.
+The second approach fits a model to represent the relationship between $wpd_{raw}$ and the number of comparisons and defines the adjusted measure ($wpd_{glm}$) as the residual from the model.
 
@@
 This method accomplishes a different goal of finding the null distribution for different groups (panels in our case) and standardizing the raw values using that distribution.
-The values of $wpd_{raw}$ is computed on many ($nperm$) permuted data sets stored in $wpd_{perm-data}$.
+The values of $wpd_{raw}$ is computed on many ($nperm$) permuted data sets and stored in $wpd_{perm-data}$.
 Then $wpd_{perm}$ is computed as follows:
@@
 
-The simulation results (\ref{sec:simulations}) show that the distribution of $wpd_{glm}$ under null is similar for high $nx$ and $nfacet$ (levels higher than $5$) and not so much for lower $nx$ and $nfacet$.
+The simulation results (in Section \ref{sec:simulations}) show that the distribution of $wpd_{glm}$ under null is similar for high $nx$ and $nfacet$ (levels higher than $5$) and not so much for lower $nx$ and $nfacet$.
 Hence, a combination approach is proposed which chooses permutation approach for categories with smaller levels and modeling approach for categories with higher levels.
@@
 In this section, a selection criterion to choose significant harmonies is provided, thereby eliminating all harmonies that exhibit complete randomness in the measured variable.
-The distance measure $wpd$ is used as a test statistic to test the null hypothesis that any given harmony is not significant.
-We select only those harmonies for which the test fails.
-The significant harmonies are then ranked basis how well they capture variation in the measured variable.
+The distance measure $wpd$ is used as a test statistic to test the null hypothesis that no harmony/cyclic granularity is significant.
+We select only those harmonies/cyclic granularities for which the test fails.
+They are then ranked basis how well they capture variation in the measured variable.
 
@@
 
-A threshold and consequently a selection criterion is chosen using the notion of Randomization tests.
+A threshold and consequently a selection criterion is chosen using the notion of Randomization tests (@edgington2007randomization).
 The data is permuted several times and $wpd$ is computed for each of the permuted data sets to obtain the sampling distribution of $wpd$ under the null hypothesis.
@@
 A harmony is selected if the value of $wpd$ for that harmony is greater than the chosen threshold.
-The detailed algorithm for choosing a threshold and selection procedure is listed as follows:
+The detailed algorithm for choosing a threshold and selection procedure (for two cyclic granularities) is listed as follows:
 
@@
 
-5.  Steps (3) and (4) are repeated a large number of times $M$ ($M = 200$).
+5.  Steps (3) and (4) are repeated a large number of times $M$ (e.g. $M = 200$).
 
@@
 This is because there is more gradual increase across hours of the day than months of the year.
-If order is not considered, they result in a $wpd$ value of $97.8$ and $161$ respectively, which follows from the fact that if we consider difference between any hours of the day, the maginitude will be much larger than if we consider difference between consecutive categories.
-Simularly, for \ref{fig:onegran-new}(a) and (b) has $110.79$ and $125.82$ as the $wpd$ values and both are significant.
+If order of the categories is not considered, they result in a $wpd$ value of $97.8$ and $161$ respectively, which follows from the fact that if we consider difference between any hours of the day, the magnitude will be much larger than if we consider difference between consecutive categories.
+Similarly, \ref{fig:onegran-new}(a) and (b) have $wpd$ values of   $110.79$ and $125.82$ respectively.
 The ranking implies that the distributional differences are more prominent for the second household, as is also seen from the bigger fluctuations in the $90^{th}$ percentile than the first household.

### 2021-06-14 paper/main.Rmd
fine-tuning

@@
 
-\noindent Observations are generated from a N(0,1) distribution for each $nx = \{2, 3, 5, 7, 9, 14, 17, 20, 24, 31, 42, 50\}$ to cover a wide range of levels from very low to moderately high.
+\noindent Observations are generated from a N(0,1) distribution for a wide range of levels from very low to moderately high.
+$nx = \{2, 3, 5, 7, 9, 14, 17, 20, 24, 31, 42, 50\}$ is considered.
 $ntimes = 500$ observations are drawn for each combination of the categories, that is, for a panel with $nx=3$, $500$ observations are simulated for each of the categories.
@@
 This is not desirable under $D_{null}$ as it would mean comparisons of $wpd$ values is not appropriate across different $nx$ and $nfacet$.
-\ref{tab:glm-tab} gives the summary of the generalized linear model to capture the relationship between $wpd_{raw}$ and number of comparisons.
-Thus, the model considered is $wpd_{l,s} = 23.69448+-1.02357*log(nx * nfacet)) + e$.
-The intercepts are similar independent of the starting distribution (Please refer to supplementary).
+Table \ref{tab:glm-tab} gives the summary of the generalized linear model to capture the relationship between $wpd_{raw}$ and number of comparisons.
+For example, the model considered for $m = 2$ is $wpd_{l,s} = 23.4 - 0.96*log(nx * nfacet)) + e$.
+The intercepts and slopes are similar independent of the starting distributions (see supplementary paper for details) and hence the coefficients are shown for the case when observations are drawn from a N(0, 1) distribution.
 Figure \ref{fig:dist-new-same-scale-link} shows the distribution of $wpd_{perm}$ and $wpd_{glm-scaled}$ in the same scale to show that a combination approach could be used for higher values of levels to alleviate the computational time of permutation approach.

### 2021-06-14 paper/main.Rmd
cleaning file

@@
 - data visualization
+- cyclic granularities
 - periodicities
-- cyclic granularities
 - permutation tests
+- distributional difference
 - Jensen-Shannon distances
@@
 In the first scenario, data for all panels are simulated using the null design  $D_{null}$.
-In other scenarios, data simulated from the panel $(14, 2)$ and $(3, 10)$ are under $D_{vary_{all}}$.
+In other scenarios, data simulated from the panel $(14, 2)$ and $(3, 10)$ are considered under $D_{vary_{all}}$.
 Moreover, $\omega = \{0.5, 2, 5\}$ are considered to examine if the proposed test is able to capture subtle differences and non-subtle differences when we shift from the null design.
-In the last scenario, we consider the panel $(3, 2), (7,9), (14, 10)$ to be under $D_{null}$, the panels $(7, 2), (14, 9)$ to be under $D_{var_f}$.
+
+<!-- In the last scenario, we consider the panel $(3, 2), (7,9), (14, 10)$ to be under $D_{null}$, the panels $(7, 2), (14, 9)$ to be under $D_{var_f}$.
 $(14, 2), (3, 10)$ under $D_{var_x}$ and the rest under $D_{var_{null}}$.
@@
 We generate $1000$ repetitions of this experiment with different seeds.
+-->
 
@@
 
-The proportion of times a panel is rejected when it is under $D_{null}$ is computed with $wpd_{threshold99}$ and it is around $0.1$.
-This is obvious, since if the level of significance for each test is less than $0.01$ (as a result of choosing $99^{th}$ percentile as the threshold) and we have $9$ tests, the size for the entire test should be close to $0.01 *9 \approx 0.1$.
+For the first scenario, size of the test is obtained as $0.1$ with $wpd_{threshold99}$ as the threshold.
+This implies that the proportion of times a panel is rejected when it is under $D_{null}$ is $0.1$.
+The level of significance for each test is 1% (as a result of choosing $99^{th}$ percentile as the threshold) and we have $9$ multiple tests.
+Hence, it is reasonable
+that the level of significance of the composite tests would be larger than the individual tests.
 We also compute the proportion of times a panel is rejected when it actually belongs to a non-null design.
-The first proportion is desired to be as small as possible and a higher value of the later is expected.
-Also, these would constitute to be the estimated size and power of the test.
+These proportions constitute to be the estimated size and power of the test.
 It is found that as we increase from low to high changes from the null distribution, the power increased.
+The power also increases with increased sample size.
 The results and graphics are included in details in the Supplementary paper.
@@
 The data has been cleaned to be a `tsibble` (@wang2019tsibble) containing half-hourly electricity consumption from Jul-2019 to Dec-2019 for each of the households, which is procured by them by downloading their data from the energy supplier/retailer.
-No behavioral pattern is likely to be discerned from the line display of 
-energy usage over the entire period, since the plot will have too many measurements squeezed in a linear representation.
+No behavioral pattern is likely to be discerned from the line graph of energy usage over the entire period, since the plot will have too many measurements squeezed in a linear representation.
 When we zoom into the linear representation of this series in Figure \ref{fig:dotplot-8} (b) for September, some patterns are visible in terms of peaks and troughs, but we do not know if they are regular or what is their period.
@@
 We consider coarser linear granularities like hour, day, week and month from the commonly used Gregorian calendar.
-Considering $4$ linear granularities hour, day, week, month in the hierarchy table, the number of cyclic granularities is $N_C = (4 * 3/2) = 6$.
-We obtain cyclic granularities namely “hour_day”, “hour_week”, “hour_month”, “day_ week”, “day_month” and “week_month”, read as “hour of the day”, etc.
-Further, we add cyclic granularity day-type( “wknd wday”) to capture weekend and weekday behavior.
+Considering $4$ linear granularities hour, day, week, month, the number of cyclic granularities is $N_C = (4 * 3/2) = 6$.
+We obtain cyclic granularities namely "hour_day", "hour_week", "hour_month", "day_ week", "day_month" and "week_month", read as "hour of the day", etc.
+Further, we add cyclic granularity day-type ("wknd wday") to capture weekend and weekday behavior.
 Thus, $7$ cyclic granularities are considered to be of interest.
@@
 
-$wpd_{i}$ is computed on $v_{i, t}$ for all harmony pairs $\in H_{N_C}$ and for each households $i \in i = \{1, 2, \dots, 8\}$.
+$wpd_{i}$ is computed on $v_{i, t}$ for all harmony pairs $\in H_{N_C}$ and for each households $i \in \{1, 2, \dots, 8\}$.
 The harmony pairs are then arranged in descending order and highlighted with `***`, `**` and `*` corresponding to the  $99^{th}$,  $95^{th}$ and $90^{th}$ percentile threshold.
@@
 
-_Detecting patterns for households not apparent from linear display_
-
-\noindent Figure \ref{fig:dotplot-8} helps to compare households through the heatmap (a) 
-across harmony pairs with the cyclic granularity mapped to x-axis and facet being plotted on the x-axis and y-axis of the heatmap.
-Here dom, dow, wdwnd are abbreviations for day-of-month, day-of-week and weekday/weekend and so on.
-(a) emphasizes patterns not discernible through (b), which is a linear display containing the raw data for one month (Sep-2019), with the major and minor x-axis corresponding to weeks and days respectively.
-In (a), the colors represent the value of $wpd$, implying darker cells correspond to more significant harmony pairs.
+_Detecting patterns not apparent from linear display_
+
+\noindent Figure \ref{fig:dotplot-8} helps to compare households through the heatmap (a) across harmony pairs with the cyclic granularity mapped to x-axis and facet being plotted on the x-axis and y-axis of the heatmap.
+Here $dom$, $dow$, $wdwnd$ are abbreviations for day-of-month, day-of-week, weekday/weekend and so on.
+The colors represent the value of $wpd$.
+Darker cells correspond to more significant harmony pairs.
 Also, the ones with `*` corresponds to the ones above $wpd_{threshold95}$.
-This plot suggests that there are no significant periodic patterns for id 5.
-Household id 6 and 7 differ in the sense that for id 6, the difference in patterns only during weekday/weekends, whereas for id 7, all or few other days of the week are also important.
-This might be due to their flexible work routines or different day-off.
-id 7 and 8 have the same significant harmonies despite having very different total energy usage.
-Note that the $wpd$ values are computed over the entire range, but the linear display is zoomed into September.
+Few observations that emphasizes patterns not discernible through (b) includes - (1) id 7 and 8 have the same significant harmonies despite having very different total energy usage, (2) id 6 and 7 differ in the sense that for id 6, the difference in patterns only during weekday/weekends, whereas for id 7, all or few other days of the week are also important.
+This might be due to their flexible work routines or different day-off, (3) there are no significant periodic patterns for id 5 when we fix the threshold to $wpd_{threshold95}$.
+Note that the $wpd$ values are computed over the entire range, but the linear display in (b) is zoomed only for September, with the major and minor x-axis corresponding to weeks and days respectively.
 
 <!-- Households id 2 and 3 are similar, in terms of linear display and heatmap, which implies that similar periodic behavior can stem from households with different demographics. -->
-
-```{r gravitas-plot-8-id5, message = FALSE, warning=FALSE, fig.cap="something", eval = FALSE}
-
-id5_tsibble <- elec %>%
-  filter(id== 5)
-
-p1 <- id5_tsibble %>% 
-   prob_plot("hour_day",
-             "day_week",
-             response = "kwh",
-             plot_type = "violin",
-             symmetric = FALSE,
-             quantile_prob = seq(0.1, 0.9, 0.01),
-             fill = "blue") +
-  ggtitle("a) hod vs dow (Rank 1)") + 
-  scale_colour_brewer(name = "", palette = "Set2") +
-  theme(legend.position = "none",
-        strip.text = element_text(size = 7, margin = margin()), axis.text.x = element_text(angle = 60, hjust=1))
-
-p2 <- id5_tsibble %>% 
-   prob_plot("hour_day",
-             "wknd_wday",
-             response = "kwh",
-             plot_type = "violin",
-             symmetric = FALSE,
-             quantile_prob = seq(0.1, 0.9, 0.01),
-             fill = "blue") +
-  ggtitle("a) hod vs wdwnd (insignificant)") + 
-  scale_colour_brewer(name = "", palette = "Set2") +
-  theme(legend.position = "none",
-        strip.text = element_text(size = 7, margin = margin()), axis.text.x = element_text(angle = 60, hjust=1))
-
-p1 + p2
-```
 
@@
 
-_Validating rank of household id:4 and 5_
-
-From table \ref{tab:tab-rank-8}, it could be seen that the harmony pair (dow, hod) is significant for household id 4, but for 5 it has been tagged as an insignificant pair.
-The distribution of energy demand with dow as the x-axis and hod as the facets for both of these households can help justify the selection.
-Figure \ref{fig:gravitas-plot-8} shows that the median (black) and quartile deviation (orange) of energy consumption changes across both dow and hod for id 4 for most hours, but it is not so different for id 5 with differences captured only for $90^{th}$ percentile.
+_Validating rank of households_
+
+From table \ref{tab:tab-rank-8}, it could be seen that the harmony pair $(dow, hod)$ is significant for household id 4, but for id 5 it has been tagged as an insignificant pair.
+The distribution of energy demand with $dow$ as the x-axis and hod as the facets for both of these households can help justify the selection.
+Figure \ref{fig:gravitas-plot-8} shows that the median (black) and quartile deviation (orange) of energy consumption changes across both $dow$ and $hod$ for id 4 for most hours, but it is not so different for id 5 with differences captured only for $90^{th}$ percentile.
 

### 2021-06-14 paper/main.Rmd
delete redundant files and minor edits

@@
 These proportions constitute to be the estimated size and power of the test.
+Power can depend on many things like sample size, number of deviations from the null and extent of deviations from the null.
 It is found that as we increase from low to high changes from the null distribution, the power increased.
-The power also increases with increased sample size.
-The results and graphics are included in details in the Supplementary paper.
+<!---The power also increases with increased sample size, as is expected.---> The results and graphics are included in details in the Supplementary paper.
 
@@
 ```{r rank-household-mclapply-8}
-elec <- read_rds(here("paper/data/elec_all-8.rds")) %>% 
-  dplyr::filter(date(reading_datetime) >= ymd("20190701"), date(reading_datetime) < ymd("20191231"), meter_id==1) %>% 
-  select(-meter_id) %>% 
-  rename("id" = "household_id",
-         "date_time" = "reading_datetime")
-
-library(tictoc)
-#tic()
-elec_split = elec %>% group_split(id)
-
-elec_select_harmony = parallel::mclapply(1:8, function(x){
-
-  data_id <-  elec_split %>% magrittr::extract2(x) %>% 
-    as_tsibble(index = date_time)
-
-harmonies <- data_id %>%
-  harmony(
-    ugran = "month",
-    filter_in = "wknd_wday",
-    filter_out = c("hhour", "fortnight")
-  )
-
- hakear::select_harmonies(data_id,
-   harmony_tbl = harmonies,
-   response = kwh,
-   nperm = 200,
-   nsamp = 200
- )
-
-}, mc.cores = parallel::detectCores() - 1, mc.preschedule = FALSE, mc.set.seed = FALSE)
-#toc()
 ```
@@
 ```{r elec_select_harmony-8}
-elec_harmony_all <- elec_select_harmony %>% 
-  bind_rows(.id = "id") %>% 
-  mutate(facet_variable = case_when(
-    facet_variable == "hour_day" ~ "hod" ,
-    facet_variable == "day_month" ~ "dom" ,
-    facet_variable == "day_week" ~ "dow" ,
-    facet_variable == "week_month" ~ "wom" ,
-    facet_variable == "wknd_wday" ~ "wdwnd"
-  )) %>% 
-  mutate(x_variable = case_when(
-    x_variable == "hour_day" ~ "hod" ,
-    x_variable == "day_month" ~ "dom" ,
-    x_variable == "day_week" ~ "dow" ,
-    x_variable == "week_month" ~ "wom" ,
-    x_variable == "wknd_wday" ~ "wdwnd"
-  )) %>% 
-  mutate(id = paste("id", id, sep = " ")) %>% 
-  group_by(id) %>% 
-  mutate(rank = row_number())
-
 ```
@@
 This article was created with R [@R-language], `knitr` [@knitr2015, @R-knitr] and `rmarkdown` [@rmarkdown2018, @R-rmarkdown].
+Graphics are produced with @Wickham2009pk.
 

### 2021-06-14 paper/paper-supplementary.Rmd
delete redundant files and minor edits

@@
 Both shape and scale of the distributions are now similar for different panels under the null design."}
-G21_norm <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_Gamma21.rds"))
+G21_norm <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds"))
 
@@
   scale_x_continuous(breaks = scales::breaks_extended(3)) + 
-  xlab("wpd normalised using permutation approach")
+  xlab("wpd normalised using permutation approach") +    xlab(TeX("wpd_{perm}")) + theme_bw()
 

### 2021-06-14 paper/scripts/main.R

@@ -293,7 +293,7 @@ set.seed(9999)
 
 
 
-set.seed(99999)
+set.seed(9999)
 varall <- compute_pairwise_norm(sim_panel_varall, 
                                 gran_x = "id_x",
                                 gran_facet = "id_facet",
@@ -301,7 +301,7 @@ varall <- compute_pairwise_norm(sim_panel_varall,
                                 nperm = 200
 )
 
-set.seed(99999)
+set.seed(9999)
 varall_sd <- compute_pairwise_norm(sim_panel_varall_sd, 
                                    gran_x = "id_x",
                                    gran_facet = "id_facet",
@@ -316,7 +316,7 @@ p_varall <- sim_panel_varall %>%
   ylab ("simulated response")
 
 
-set.seed(99999)
+set.seed(9999)
 
 null <- compute_pairwise_norm(sim_panel_null, 
                               gran_x = "id_x",
@@ -352,7 +352,7 @@ p_null <- sim_panel_null %>%
 
 
 
-set.seed(99999)
+set.seed(9999)
 varf <- compute_pairwise_norm(sim_panel_varf, 
                               gran_x = "id_x",
                               gran_facet = "id_facet",
@@ -366,7 +366,7 @@ p_varf <- sim_panel_varf %>%
   ylab ("simulated response")
 
 
-set.seed(99999)
+set.seed(9999)
 varx <- compute_pairwise_norm(sim_panel_varx, 
                               gran_x = "id_x",
                               gran_facet = "id_facet",
@@ -818,12 +818,68 @@ demography <- demography %>% kable(format  = "markdown", caption = "Demographics
 demography %>% add_footnote(label = "***: 99% significant, **: 95% and *: 90%")
 
 
+## ---- rank-household-mclapply-8
+elec <- read_rds(here("paper/data/elec_all-8.rds")) %>% 
+  dplyr::filter(date(reading_datetime) >= ymd("20190701"), date(reading_datetime) < ymd("20191231"), meter_id==1) %>% 
+  select(-meter_id) %>% 
+  rename("id" = "household_id",
+         "date_time" = "reading_datetime")
+
+
+
+library(tictoc)
+#tic()
+elec_split = elec %>% group_split(id)
+
+elec_select_harmony = parallel::mclapply(1:8, function(x){
+  
[…]

### 2021-06-15 paper/paper-supplementary.Rmd
changing supplementary

@@
 Let $v = \{v_t: t = 0, 1, 2, \dots, T-1\}$ be a continuous measured variable observed across $T$ time points.
-The number of cyclic granularities considered in the display/analysis is $m$.
+The number of cyclic granularities considered in the display (at once) is $m$.
 Consider cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$.
@@
     escape = FALSE,
-    caption = "Simulation setup for a panel with 3 facet levels and 2 x-axis levels for different designs starting from an initial distribution N(0, 1) for the combination $(a_1, b_1)$ and $\\omega=1$.") %>% kable_styling()
+    caption = "Simulation setup for a panel with 3 facet levels and 2 x-axis levels for different designs starting from an initial distribution N(0, 1) for the combination $(a_1, b_1)$ and $\\omega=3$.") %>% kable_styling()
 ```
@@
 
-Observations are generated from Normal(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7\}$ and $wpd_{raw}$ is computed for $\lambda = {0.1, 0.2, \dots, 0.9}$ under two designs $D_{var_x}$ and $D_{var_f}$ for $\omega = \{1, 8\}$  to observe how the value of $wpd_{raw}$ changes for different designs.
-Moreover, to observe for which value of $\lambda$ the two designs intersect, we generate observations from Normal(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20\}$ and $\omega = \{1, 2, \dots, 10\}$ under the same two designs.
+Observations are generated from N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7\}$ and $wpd_{raw}$ is computed for $\lambda = {0.1, 0.2, \dots, 0.9}$ under two designs $D_{var_x}$ and $D_{var_f}$ for $\omega = \{1, 8\}$  to observe how the value of $wpd_{raw}$ changes for different designs.
+Moreover, to observe for which value of $\lambda$ the two designs intersect, we generate observations from N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20\}$ and $\omega = \{1, 2, \dots, 10\}$ under the same two designs.
 
@@
 The value of $wpd$ increases with $\lambda$ for $D_{var_x}$ and decreases with increasing $\lambda$ for $D_{var_f}$.
+\noindent Figure \ref{fig:tuning-parameter-inter} shows the value of $\lambda$ for which the two designs intersect for different values of $\omega$.
+It can be observed that as the value of $\omega$ ($\omega > 4$) increase, the value of $\lambda$ at which the two designs intersect converge is $\lambda = 0.5$ and for $\omega$ ($\omega <= 4$), designs interact between $\lambda = [0.6,0.75]$.
+Hence, $\lambda = 0.67$ for the rest of the paper, which is an average of the range of values $\lambda$ can take.
 
@@
 ```
-
-\noindent Figure \ref{fig:tuning-parameter-inter} shows the value of $\lambda$ for which the two designs intersect for different values of $\omega$.
-It can be observed that as the value of $\omega$ ($\omega > 4$) increase, the value of $\lambda$ at which the two designs intersect converge is $\lambda = 0.5$.
 
@@
 
-Observations are generated from Normal(0,1), N(5, 1), N(0, 5), Gamma(0.5, 1) and Gamma(2, 1) distributions for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ and $wpd_{raw}$ is computed with $\lambda = 0.67$ with (scenario 1) and without (scenario 1) NQT.
+Observations are generated from N(0,1), N(5, 1), N(0, 5), Gamma(0.5, 1) and Gamma(2, 1) distributions for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ and $wpd_{raw}$ is computed with $\lambda = 0.67$ with (scenario 1) and without (scenario 2) NQT.
 
@@
 
-```{r one-gran-nxnyfacet, fig.cap="something3"}
+```{r one-gran-nxnyfacet, fig.cap="Distribution of $wpd_{perm}$ are shown for different levels for $m=1$ under the null design. The distribution for different panels have similar location and scale."}
 include_graphics(here("simulations/supplementary/one-gran/norm/null_design_quantrans_nperm/figs/nxbyfacet_ridge_wpd_N01.png"))
@@
 
-```{r norm, fig.cap = "Distribution of $wpd_{perm}$ is plotted across different $nx$ and $nfacet$ categories.
-Both shape and scale of the distributions are now similar for different panels under the null design."}
+```{r norm, fig.cap = "Distribution of $wpd_{perm}$ are shown for different levels for $m=2$ under the null design. The distribution for different panels have similar location and scale."}
 G21_norm <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds"))
@@
 ```{r}
+library(here)
 G21_onegran <- read_rds(here("simulations/supplementary/one-gran/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds"))
@@
 
-bind_cols(distribution = "Normal (0, 1)", broom::tidy(glm_fit_onegran)) %>% kable(caption = "Results of generalised linear model to capture the relationship between $wpd_{raw}$ and number of comparisons for $m=1$.")
+bind_cols(distribution = "N(0, 1)", broom::tidy(glm_fit_onegran)) %>% kable(caption = "Results of generalised linear model to capture the relationship between $wpd_{raw}$ and number of comparisons for $m=1$.")
 
@@
 
-```{r glm-horizontal-onegran, fig.cap = "Residuals from the model is plotted across different $nx$. Residuals seem to be indeoendent of $nx$ and have been defined as $wpd_{glm}$ in the paper."}
+```{r glm-horizontal-onegran1-raw}
 
@@
 scale_fac <- 1/G21_sd$wpd_glm %>% sd()
-# checking the fit of the residuals from glm fit
 
@@
 residuals <- residuals.glm(glm_fit, type = "response")
-#hist(residuals)
-#h = augment(glm_fit)
-#ggplot(h) +
-#  geom_histogram(aes(x = .resid))
+
 residual <- G21_median$actual  - fitted_glm
 
-#hist(residual)
-G21 %>% 
+G21_horizontal <- G21 %>% 
   ggplot(aes(x=log(nx*nfacet),
@@
   ) +
-  geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
-  ylab("wpd_glm = wpd_raw - 1/(a  + b*log(nx*nfacet))")
+  geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue", size = 1) + 
+  ylab(TeX("wpd_{glm} = wpd_{raw} - 1/(a  + b*log(nx*nfacet))")) + xlab("log(nx)")
+
+#ggsave("figs/G21_horizontal.png")
 ```
 
-```{r glm-density-onegran, fig.cap = "Distribution of $wpd_{glm}$ is plotted across different $nx$. Both shape and scale of the distributions are different for lower $nx$ than for higher $nx$."}
+```{r glm-horizontal-onegran1, fig.cap = "Residuals from the model is plotted across different number of comparisons for $m=1$.
+Residuals seem to be independent of $nx$ and have been defined as $wpd_{glm}$."}
+knitr::include_graphics(here("paper/figs/G21_horizontal.png"))
+```
+
+```{r glm-density-onegran, fig.cap = "Distribution of $wpd_{glm}$ is plotted across different $nx$ for $m=1$.
+Both shape and scale of the distributions are different for lower $nx$ than for higher $nx$."}
 G21_glm <- G21 %>% 
@@
 
+mylabels <- G21_glm %>% 
+  group_by(nx) %>% 
+  summarise(mean = round(mean(wpd_glm), 3), sd = round(sd(wpd_glm), 3)) %>% 
+  mutate(label_glm = paste0("(", mean, ", " ,sd, ")"))
+
 nxbyfacet_ridge <- G21_glm %>% 
-  ggplot(aes(x = wpd_glm_scaled, y = as.factor(nx))) +
+  ggplot(aes(x = wpd_glm, y = as.factor(nx))) +
   ggridges::geom_density_ridges() +
-  xlab("mmpd") +
+  xlab(TeX("wpd_{glm}")) +
   ylab("nx") 
+  geom_label(data = mylabels,
+             aes(y = as.factor(nx),
+                 x = label_glm, 
+                 label = label_glm))
 
 nxbyfacet_ridge
+
 ```
@@
     group== "G21" ~ "Gamma(2, 1)",
-    group== "N01" ~ "Normal(0, 1)",
-    group== "N05" ~ "Normal(0, 5)",
-    group== "N51" ~ "Normal(5, 1)",
-    group== "N55" ~ "Normal(5, 5)",
+    group== "N01" ~ "N(0, 1)",
+    group== "N05" ~ "N(0, 5)",
+    group== "N51" ~ "N(5, 1)",
+    group== "N55" ~ "N(5, 5)",
     TRUE~ as.character(group)
@@
 G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_N01.rds"))
+
 G21_median <- G21 %>% 
@@
   summarise(actual = median(value))
+
 glm_fit <- glm(actual ~ log(`nx * nfacet`),
@@
                data = G21_median)
+
 intercept <- glm_fit$coefficients[1]
@@
 # hist(residual)
-G21 %>%
+G21_horizontal <- G21 %>%
   ggplot(aes(x=log(nx*nfacet),
@@
   ) +
-  geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") +
-  ylab("wpd_glm = wpd_raw - 1/(a  + b*log(nx*nfacet))")
-broom::tidy(glm_fit) %>% kable(caption = "Results of generalised linear model to capture the relationship between $wpd_{raw}$ and number of comparisons.")
+  geom_point() + 
+  stat_summary(fun=mean,
+               geom="line",
+               aes(group=1),
+               color = "blue",
+               size = 1) +
+  ylab(TeX("wpd_{glm} = wpd_{raw} - 1/(a  + b*log(nx*nfacet))"))
+
+# broom::tidy(glm_fit) %>% kable(caption = "Results of generalised linear model to capture the relationship between $wpd_{raw}$ and number of comparisons.")
+
+#ggsave("figs/G21_horizontal_m2.png")
 ```
 
-```{r wpd-glm-dist, fig.cap = " The distribution of $wpd_{glm}$ is plotted. The distributions are more similar across higher $nx$ and nfacet and dissimilar for fewer $nx$ and $nfacet$."}
+```{r glm-horizontal-twogran1, fig.cap = "Residuals from the model is plotted across different number of comparisons for $m=2$.
+Residuals seem to be independent of $nx$ and have been defined as $wpd_{glm}$."}
+knitr::include_graphics(here("paper/figs/G21_horizontal_m2.png"))
+```
+
+```{r wpd-glm-dist, fig.cap = "Distribution of $wpd_{glm}$ is plotted across different $nx$ for $m=2$. Both shape and scale of the distributions are different for lower $nx$ than for higher $nx$."}
 G21_glm <- G21 %>% 
@@
 
-global_threshold <-  tibble(threshold = "99", value = quantile(all_data$wpd, 0.99, na.rm = TRUE))
+global_threshold <-  tibble(threshold = "89.4", value = quantile(all_data$wpd, 0.894, na.rm = TRUE))
 ```
 
-$wpd_{threshold99}$ is obtained as `r round(global_threshold$value, 2)` for this experiment, which leads to a p-value of `r round(data_summary$p_value, 3)`.
+<!-- $wpd_{threshold99}$ is obtained as `r round(global_threshold$value, 2)` for this experiment, which leads to a p-value of `r round(data_summary$p_value, 3)`.
 Figure \ref{fig:global-size} shows the distribution of $wpd$ obtained from this experiment with the red line denoting $wpd_{threshold99}$.
 If we split the diplay of distribution between $nx$ and $nfacet$, then Figure \ref{fig:local-size} shows that the probability of rejecting the null when it is actually true is higher for smaller levels, however, it is still within limits (around `r round(data_summary_lowlev$p_value, 3)`).
+-->
 
-```{r global-size, fig.cap = "something"}
+(ref:foo) The distribution of $wpd$ for 9 null designs of different levels with each harmony being rejected if the correponding $wpd$ value is higher than $wpd_{threshold99}$.
+Although the level of significance for each test is 1%, the level of significance for multiple tests together is 10% as displayed through the red line.
+This means 10% of the times the null designs will be tagged as interesting even when there is actually nothing interesting going on.
+
+```{r foo, fig.cap='(ref:foo)'}
+
 ggplot() + 
@@
 
-```{r local-size, fig.cap = "something"}
+```{r local-size, fig.cap = "something", eval = FALSE}
 ggplot() + 

### 2021-06-15 paper/paper-supplementary.Rmd
minor changes of supplementary paper

@@
 
-Observations are generated from Gamma(2,1), G(0.5, 1), N(0,1), N(0, 5) and N(5, 1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
+<!-- Observations are generated from Gamma(2,1), G(0.5, 1), N(0,1), N(0, 5) and N(5, 1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
 Each combination is being referred to as a _panel_.
@@
 That is, if we consider the panel $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
-The values
-of $wpd$ is obtained for each of the panels.
+The values -->
+<!-- of $wpd$ is obtained for each of the panels.
 The measurement variable for each combination of categories in a panel are drawn from the same distribution and hence the design corresponds to $D_{null}$ .
 Furthermore, this entire method is repeated for each panels $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
+-->
 
@@
 
-Figure \ref{fig:nxbyfacet-ridge-N01}, \ref{fig:nfacetbynx} and  \ref{fig:density-raw} shows the ridge plot of $wpd_{raw}$ with $nx$ as facets, $nfacet$ as facets and the density plot of $wpd_{raw}$ with $nx$ on the x-axis and $nfacet$ on the facets.
+Figures \ref{fig:nxbyfacet-ridge-N01}, \ref{fig:nfacetbynx} and  \ref{fig:density-raw} shows the ridge plot of $wpd_{raw}$ with $nx$ as facets, $nfacet$ as facets and the density plot of $wpd_{raw}$ with $nx$ on the x-axis and $nfacet$ on the facets.
 
@@
 This sections shows the result from the different approaches of adjusting for the number of comparisons.Simulation design is the same as for raw weighted pairwise distances for $m=1$ and $m=2$.
-In place of $wpd_{raw}$, $wpd_{perm}$, $wpd_{glm}$ and $wpd$ is computed for all panel.
+In place of $wpd_{raw}$, $wpd_{perm}$, $wpd_{glm}$ and $wpd$ is computed for all panels.
 
@@
 
-### Case: m = 1
-
-Figure \ref{fig:glm-horizontal-onegran} shows the scatterplot of $wpd_{raw}$ against different values of $nx$ and also the display of residuals from the model.
-Figure \ref{fig:glm-density-onegran} shows the distribution of $wpd_{glm}$ for different $nx$.
+For for $m=1$, Figure \ref{fig:glm-horizontal-onegran1} shows the scatterplot of $wpd_{raw}$ against different values of $nx$ and also the display of residuals from the model and Figure \ref{fig:glm-density-onegran} shows the distribution of $wpd_{glm}$ for different $nx$.
+For $m=2$, Figure \ref{fig:glm-horizontal-twogran1} shows the scatterplot of $wpd_{raw}$ against different values of $nx$ and also the display of residuals from the model.
+Figure \ref{fig:wpd-glm-dist} shows the distribution of $wpd_{glm}$ for different $nx$.
 
@@
   ))
-scale_fac <- 1/G21_sd$wpd_glm %>% sd()
+#scale_fac <- 1/G21_sd$wpd_glm %>% sd()
 
@@
   ylab("nx") 
-  geom_label(data = mylabels,
-             aes(y = as.factor(nx),
-                 x = label_glm, 
-                 label = label_glm))
+  # geom_label(data = mylabels,
+  #            aes(y = as.factor(nx),
+  #                x = label_glm, 
+  #                label = label_glm))
 
@@
 ```
-
-### Case: m = 2
-
-Figure \ref{fig:glm-horizontal-onegran} shows the scatterplot of $wpd_{raw}$ against different values of $nx$ and also the display of residuals from the model.
-Figure \ref{fig:wpd-glm-dist} shows the distribution of $wpd_{glm}$ for different $nx$.
 
@@
 ## Combination approach
+
+### Results
 
@@
 
-### Simulation design
-
-Observations are generated from Gamma(2,1), G(0.5, 1), N(0,1), N(0, 5) and N(5, 1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
-Each combination is being referred to as a _panel_.
-That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$.
-For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
-That is, if we consider the panel $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
-The values
-of $wpd$ is obtained for each of the panels.
-The measurement variable for each combination of categories in a panel are drawn from the same distribution and hence the design corresponds to $D_{null}$ .
-Furthermore, this entire method is repeated for each panels $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
-
 # Ranking and selecting harmonies
-
-## Size
 
@@
 
-## Power
-
 ```{r hist-qq-new, fig.cap = "In panel a, the histogram of $wpd_{glm-scaled}$ is plotted.

### 2021-06-15 paper/paper-supplementary.Rmd
Figure 8, 9 and 10 caption fixed

@@
 It can be observed that as the value of $\omega$ ($\omega > 4$) increase, the value of $\lambda$ at which the two designs intersect converge is $\lambda = 0.5$ and for $\omega$ ($\omega <= 4$), designs interact between $\lambda = [0.6,0.75]$.
-Hence, $\lambda = 0.67$ for the rest of the paper, which is an average of the range of values $\lambda$ can take.
+Hence, $\lambda = 0.67$ is used for the rest of the paper, which is an average of the range of values $\lambda$ can take in order to have equal or more weightage for the within-facet distances.
 
@@
 Figures \ref{fig:nxbyfacet-ridge-N01}, \ref{fig:nfacetbynx} and  \ref{fig:density-raw} shows the ridge plot of $wpd_{raw}$ with $nx$ as facets, $nfacet$ as facets and the density plot of $wpd_{raw}$ with $nx$ on the x-axis and $nfacet$ on the facets.
+The right-ward shift in location can be clearly observed from all figures.
 
-```{r nxbyfacet-ridge-N01, fig.cap="Ridge plots of raw wpd is shown for N(0,5) distribution.
-For each panel, it could be seen that the location shifts to the right for increasing x levels.
-Across each panel, the scale of the distribution seems to change for low/moderately lower values and higher values of nfacets and left tails are longer for lower facet levels."}
+```{r nxbyfacet-ridge-N01, fig.cap="Ridge plots of raw wpd is shown for N(0,1) distribution with nfacets as facets.
+For each panel, it could be seen that the location shifts to the right for increasing nx levels."}
 knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/nxbyfacet_ridge_wpd_N01.png"))
@@
 
-```{r nfacetbynx, fig.cap="something1"}
+```{r nfacetbynx, fig.cap="Ridge plots of raw wpd is shown for N(0,1) distribution with nx as facets.
+For each panel, it could be seen that the location shifts to the right for increasing nfacet levels."}
 knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/nfacetbynx_ridge_wpd_N01.png"))
@@
 
-```{r density-raw, fig.cap="something2"}
+```{r density-raw, fig.cap="Density plot of raw wpd is shown for N(0,1) distribution with nx on x-axis and nfacet on facets.
+For each panel, it could be seen that the location as well as scale shifts as we move from top-left to bottom-right corner."}
 knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/nxbyfacet_density_wpd_N01.png"))
@@
 
+"The distribution of $wpd_{perm}$ and $wpd_{glm-scaled}$ are overlaid to compare the location and scale across different $nx$ and $nfacet$.
+$wpd_{norm}$ takes the value of $wpd_{perm}$ for lower levels
+$(<=5)$, and $wpd_{glm-scaled}$ for higher levels to to alleviate the problem of computational time in permutation approaches.
+This is possible as the distribution of the adjusted measure looks similar for both approaches for higher levels."
+
 ```{r dist-same-scale-onegran, fig.cap = "The distribution of $wpd_{perm}$ and $wpd_{glm-scaled}$ are overlaid to compare the location and scale across different $nx$ for $m=1$.
@@
 Figure \ref{fig:global-size} shows the distribution of $wpd$ obtained from this experiment with the red line denoting $wpd_{threshold99}$.
-If we split the diplay of distribution between $nx$ and $nfacet$, then Figure \ref{fig:local-size} shows that the probability of rejecting the null when it is actually true is higher for smaller levels, however, it is still within limits (around `r round(data_summary_lowlev$p_value, 3)`).
+If we split the display of distribution between $nx$ and $nfacet$, then Figure \ref{fig:local-size} shows that the probability of rejecting the null when it is actually true is higher for smaller levels, however, it is still within limits (around `r round(data_summary_lowlev$p_value, 3)`).
 -->
 
-(ref:foo) The distribution of $wpd$ for 9 null designs of different levels with each harmony being rejected if the correponding $wpd$ value is higher than $wpd_{threshold99}$.
+(ref:foo) The distribution of $wpd$ for 9 null designs of different levels with each harmony being rejected if the corresponding $wpd$ value is higher than $wpd_{threshold99}$.
 Although the level of significance for each test is 1%, the level of significance for multiple tests together is 10% as displayed through the red line.

### 2021-06-15 paper/main.Rmd
adding data

@@
 \noindent
-**R-package:** The open-source R [@R-language] package `hakear` [@R-hakear] is available on Github (https://github.com/Sayani07/hakear) to implement ideas presented in this paper.
+**R-package:** The open-source R [@R-language] package `hakear` is available on Github (https://github.com/Sayani07/hakear) to implement ideas presented in this paper.
 

### 2021-06-15 paper/paper-supplementary.Rmd
adding data

@@
   echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
-  fig.path = "figure/", fig.align = "center", fig.show = "hold", fig.pos = "h",
+  fig.path = "figure/", fig.align = "center", fig.show = "hold", fig.pos = "ht",
   cache = TRUE, cache.path = "cache/",
@@
 
-```{r explain-design, fig.pos="h"}
+```{r explain-design, fig.pos="ht"}
 sim_varx_normal = function(nx, nfacet, mean, sd, w)
@@
 
-This sections shows the result from the different approaches of adjusting for the number of comparisons.Simulation design is the same as for raw weighted pairwise distances for $m=1$ and $m=2$.
+This section shows results from the different approaches of adjusting for the number of comparisons.
+Simulation design is the same as for raw weighted pairwise distances for $m=1$ and $m=2$.
 In place of $wpd_{raw}$, $wpd_{perm}$, $wpd_{glm}$ and $wpd$ is computed for all panels.
@@
 Figure \ref{fig:one-gran-nxnyfacet} and \ref{fig:norm} show the normalized ${wpd}$ for $m=1$ and $m=2$ respectively.
-The location and scale are brought to similar values for increasing values of $nx$ or $nfacet$.
+The location and scale of the distribution of ${wpd}$ is similar for increasing values of $nx$ or $nfacet$.
 Due to heavy computational load, $wpd_{perm}$ for few panels with very high value of $nx$ or $nfacet$ are not computed.
@@
 For for $m=1$, Figure \ref{fig:glm-horizontal-onegran1} shows the scatterplot of $wpd_{raw}$ against different values of $nx$ and also the display of residuals from the model and Figure \ref{fig:glm-density-onegran} shows the distribution of $wpd_{glm}$ for different $nx$.
-For $m=2$, Figure \ref{fig:glm-horizontal-twogran1} shows the scatterplot of $wpd_{raw}$ against different values of $nx$ and also the display of residuals from the model.
-Figure \ref{fig:wpd-glm-dist} shows the distribution of $wpd_{glm}$ for different $nx$.
+For $m=2$, Figure \ref{fig:glm-horizontal-twogran1} shows the scatter plot of $wpd_{raw}$ against different values of $nx$ and $nfacet$ and also the display of residuals from the model.
+Figure \ref{fig:wpd-glm-dist} shows the distribution of $wpd_{glm}$ for different $nx$ and $nfacet$.
+Tables \ref{tab:tab-modelsm1} and \ref{tab:tab-models} show the GLM results for $m=1$ and $m=2$ respectively.
+All of these jointly show that the residuals from the model are independent of the number of comparisons.
+The location and scale of the distribution of $wpd_{glm}$ is similar for higher levels and distinctly different for lower levels.
 
-```{r}
+```{r tab-modelsm1}
 library(here)
@@
 
-bind_cols(distribution = "N(0, 1)", broom::tidy(glm_fit_onegran)) %>% kable(caption = "Results of generalised linear model to capture the relationship between $wpd_{raw}$ and number of comparisons for $m=1$.")
+bind_cols(distribution = "N(0, 1)", broom::tidy(glm_fit_onegran)) %>% 
+  mutate(estimate = round(estimate, 2),
+         std.error = round(std.error, 3),
+         statistic = round(statistic, 2),
+         p.value = round(p.value, 2)) %>% kable(caption = "Results of generalised linear model to capture the relationship between $wpd_{raw}$ and number of comparisons for $m=1$.")
 
@@
 
-```{r glm-horizontal-onegran1, fig.cap = "Residuals from the model is plotted across different number of comparisons for $m=1$.
+```{r glm-horizontal-onegran1, fig.cap = "$wpd_{raw}$ (points) and residuals (blue line) from the model is plotted across different number of comparisons for $m=1$.
 Residuals seem to be independent of $nx$ and have been defined as $wpd_{glm}$."}
@@
 ```{r glm-density-onegran, fig.cap = "Distribution of $wpd_{glm}$ is plotted across different $nx$ for $m=1$.
-Both shape and scale of the distributions are different for lower $nx$ than for higher $nx$."}
-G21_glm <- G21 %>% 
+Both shape and location of the distributions are different for lower $nx$ than for higher $nx$."}
+G21_glm_m1 <- G21 %>% 
   mutate(wpd_glm =  (value - (1/(intercept + slope*log(nx*nfacet)
@@
 
-mylabels <- G21_glm %>% 
+mylabels <- G21_glm_m1 %>% 
   group_by(nx) %>% 
@@
 
-nxbyfacet_ridge <- G21_glm %>% 
+nxbyfacet_ridge <- G21_glm_m1 %>% 
   ggplot(aes(x = wpd_glm, y = as.factor(nx))) +
@@
 nxbyfacet_ridge
-
 ```
@@
 
-```{r glm-horizontal-twogran1, fig.cap = "Residuals from the model is plotted across different number of comparisons for $m=2$.
+```{r glm-horizontal-twogran1, fig.cap = "$wpd_{raw}$ (points) and residuals (blue line) from the model is plotted across different number of comparisons for $m=2$.
 Residuals seem to be independent of $nx$ and have been defined as $wpd_{glm}$."}
@@
 
-### Results
-
-"The distribution of $wpd_{perm}$ and $wpd_{glm-scaled}$ are overlaid to compare the location and scale across different $nx$ and $nfacet$.
-$wpd_{norm}$ takes the value of $wpd_{perm}$ for lower levels
-$(<=5)$, and $wpd_{glm-scaled}$ for higher levels to to alleviate the problem of computational time in permutation approaches.
-This is possible as the distribution of the adjusted measure looks similar for both approaches for higher levels."
+Figure \ref{fig:dist-same-scale-onegran} and \ref{fig:dist-new-same-scale-link} show the distribution of $wpd_{perm}$ and $wpd_{glm-scaled}$ overlaid on each other for $m=1$ and $m=2$ respectively.
+$wpd$ takes the value of $wpd_{perm}$ for lower levels
+$(<=5)$, and $wpd_{glm-scaled}$ for higher levels so that we have similar location and scale across panels with different levels.
 
 ```{r dist-same-scale-onegran, fig.cap = "The distribution of $wpd_{perm}$ and $wpd_{glm-scaled}$ are overlaid to compare the location and scale across different $nx$ for $m=1$.
-The distribution of the adjusted measure looks similar for both appraches for higher levels."}
+The distribution of the adjusted measure looks similar for both approaches for higher levels, but for $nx=2$ both location and scale differs."}
 G21_permutation <- read_rds(here("simulations/supplementary/one-gran/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds")) %>%
@@
 
-# G21_model_data <- G21 %>%
-#   mutate(model =
-#            ((1/value)
-#                   - intercept -
-#                     slope*log(nx*nfacet))/slope) %>%
-#   mutate(model_trans =
-#            (model - mean(model))/sd(model))
-
-# G21_model_data$model %>% summary()
-
 G21_all_data <- G21_permutation %>% 
   # left_join(G21_lm, by = c("nx", "nfacet", "perm_id")) %>% 
-  left_join(G21_glm, by = c("nx", "nfacet", "perm_id")) %>% 
+  left_join(G21_glm_m1, by = c("nx", "nfacet", "perm_id")) %>% 
   pivot_longer(cols = c(3, 7),
@@
 ```{r dist-new-same-scale-link, fig.cap = "The distribution of $wpd_{perm}$ and $wpd_{glm-scaled}$ are overlaid to compare the location and scale across different $nx$ and $nfacet$ for $m=2$.
-$wpd_{norm}$ takes the value of $wpd_{perm}$ for lower levels, and $wpd_{glm-scaled}$ for higher levels to to alleviate the problem of computational time in permutation approaches.
-This is possible as the distribution of the adjusted measure looks similar for both appraches for higher levels."}
+$wpd$ takes the value of $wpd_{perm}$ for lower levels, and $wpd_{glm-scaled}$ for higher levels.
+"}
 
@@
   geom_density(aes(fill = type_estimate), alpha = 0.5, size = .5) +
-  #geom_vline(data = summary_data, aes(xintercept = mean, color = type_estimate)) + 
+  geom_vline(data = summary_data, aes(xintercept = mean, color = type_estimate)) + 
   geom_rug(aes(color = type_estimate), length = unit(0.09,"cm"), alpha = 0.5) +
@@
 $(14, 2), (3, 10)$ under $D_{var_x}$ and the rest under $D_{var_{null}}$.
-This is done to check if the consequent ranking procedure leads to designs like $D_{vary_{all}}$ to be chosen first followed by $D_{vary_{all}}$.
+This is done to check if the consequent ranking procedure leads to designs like $D_{vary_{f}}$ rank below $D_{vary_{all}}$.
 We generate only one data set each for which these scenarios were simulated and consider this as the original data set.
@@
 \noindent _Results_
+
+Figure \ref{fig:foo} shows the distribution of $wpd$ for the simulated $9$ null designs of different levels with each harmony being rejected if the corresponding $wpd$ value is higher than $wpd_{threshold99}$.
+Although the level of significance for each test is 1%, the level of significance for multiple tests together is 10% as displayed through the red line.
+This means that 10% of the times the null designs will be tagged as interesting even when there is actually nothing interesting going on.
 

### 2021-06-15 elec_all-8.R
cleaning folder

@@ -1,153 +1,0 @@
-preprocess <- function() {
-  
-id4 =  read_csv(here::here("paper/data-raw", "meter04.csv"),
-                  skip = 1,
-                  col_names = c("dtype","rc","rate_desc","start_date","end_date","kwh","register_val", "qual_flag")) %>% 
-    separate(start_date, sep = " ", into = c("date", "stamp")) %>% 
-    select(date, stamp, kwh)
-  
-  id_lookup = id4 %>%
-    distinct(stamp) %>% 
-    bind_cols(time = as.character(1:48))
-  
-  meter_id1 = read_csv(here::here("paper/data-raw", "meter01.csv"),
-                       skip=2,
-                       col_names = c("id", "date",  1:48),
-                       cols(`2` = col_double())) %>% 
-    filter(id == "300") %>% 
-    mutate(date = ymd(date)) %>% 
-    gather(time, kwh, -id, -date) %>% 
-    left_join(id_lookup) %>% 
-    mutate(reading_time = paste(date, stamp, ""), 
-           reading_time = ymd_hm(reading_time)) %>% 
-    select(reading_time, kwh)
-  
-  
-  meter_id2 = read_csv(here::here("paper/data-raw", "meter02.csv"), 
-                       skip=2,
-                       col_names = c("id", "date",  1:48),
-                       cols(`2` = col_double())) %>% 
-    filter(id == "300")%>% 
-    mutate(date = ymd(date)) %>% 
-    gather(time, kwh, -id, -date) %>% 
-    select(-id) %>% 
-    left_join(id_lookup) %>% 
-    mutate(reading_time = paste(date, stamp, ""), 
-           reading_time = ymd_hm(reading_time)) %>% 
-    select(reading_time, kwh)
-  
-  
-  meter_id3 = read_csv(here::here("paper/data-raw", "meter03.csv"),
-                       skip = 1,
-                       col_names = c("nmi","msn","gen","date","est",1:48)) %>% 
-    select(-c(nmi, msn, est, gen)) %>% 
-    gather(time, kwh, -date) %>% 
-    mutate(date = dmy(date))%>% 
-    left_join(id_lookup) %>% 
-    mutate(reading_time = paste(date, stamp, ""), 
-           reading_time = ymd_hm(reading_time)) %>% 
-    select(reading_time, kwh)
-  
-  
-  meter_id4 =  id4 %>% 
-    mutate(date = dmy(date),
-           reading_time = paste(date, stamp, ""), 
[…]

### 2021-07-13 paper/main.Rmd
cleaning folder
changes in last two figures

@@
 Tukey [@Tukey1977-jx] involves many iterations of finding structures and patterns that allow the data to be informative.
-With temporal data available at finer scales, exploring time series data can become overwhelming with so many possible cyclic temporal granularities [@Bettini1998-ed, @Gupta2020-vo], which are temporal deconstructions that represent cyclic repetitions in time, e.g.
+With temporal data available at finer scales, exploring time series data can become overwhelming with so many possible cyclic temporal granularities [@Bettini1998-ed, @Gupta2021-hd], which are temporal deconstructions that represent cyclic repetitions in time, e.g.
 hour-of-day, day-of-month, or any public holidays.
@@
 @Dang2014-tw and @wilkinson2005graph provide potential solutions to this, where few characterizations can be used to locate anomalies in density, shape, trend, and other features in the 2D point scatters.
-In this paper, we provide a solution to narrowing down the search from $^{N_C}P_2$ plots by introducing a new distance measure that can be used to detect significant distributional differences across cyclic granularities.<!-- harmonies and why it is not enough --> This work is a natural extension of our previous work [@Gupta2020-vo] that narrows down the search from $^{N_C}P_2$ plots by identifying pairs of granularities that can be meaningfully examined together (a "harmony"), or when they cannot (a "clash").
+In this paper, we provide a solution to narrowing down the search from $^{N_C}P_2$ plots by introducing a new distance measure that can be used to detect significant distributional differences across cyclic granularities.<!-- harmonies and why it is not enough --> This work is a natural extension of our previous work [@Gupta2021-hd] that narrows down the search from $^{N_C}P_2$ plots by identifying pairs of granularities that can be meaningfully examined together (a "harmony"), or when they cannot (a "clash").
 However, even after excluding clashes, the list of harmonies left could be enormous for exhaustive exploration.
@@
 
-<!-- Hence, with reference to the graphical design in @Gupta2020-vo, therefore the idea would be to rate a harmony pair higher if the variation between different levels of the x-axis variable is higher on an average across all levels of the facet variables.
+<!-- Hence, with reference to the graphical design in @Gupta2021-hd, therefore the idea would be to rate a harmony pair higher if the variation between different levels of the x-axis variable is higher on an average across all levels of the facet variables.
 -->
@@
 These proportions constitute to be the estimated size and power of the test.
-Power can depend on many things like sample size, number of deviations from the null and extent of deviations from the null.
+Power can depend on many things like sample size, number of designs that deviate from the null and extent to which from the null.
 It is found that as we increase from low to high changes from the null distribution, the power increased.
@@
 The set consisting of pairs of cyclic granularities ($C_{N_C}$) will have $7_{P_2}=42$ elements which could be analyzed for detecting possible periodicities.
-The set of possible harmonies $H_{N_C}$ from $C_{N_C}$ are chosen by removing clashes using procedures described in [@Gupta2020-vo].
+The set of possible harmonies $H_{N_C}$ from $C_{N_C}$ are chosen by removing clashes using procedures described in [@Gupta2021-hd].
 Table \ref{tab:tab-rank-8}  shows $14$ harmony pairs that belong to $H_{N_C}$.
@@
 
-```{r dotplot-8, fig.cap = " A heatmap across harmonies (a) and line plot (b) showing energy usage for all household ids.
+```{r dotplot-8, fig.cap = "An ensemble plot with a heatmap (a), line plot (b), parallel coordinate plot (c) to demonstrate energy behavior of the households in different ways.
+(b) is the zoomed-in raw demand series for September to highlight the repetitive patterns of energy demand.
+(a) shows $wpd$ values across harmonies with the x variable of harmony placed across x-axis and facet variable placed across y-axis.
 The darker the colour in (a), the higher the harmony is ranked.
-Visualizing the harmony pairs in this way helps us to see the important cyclic granularities along the x-axis, facet or both.
-It further shows which households have significant patterns across similar temporal granularities.
-For eg, id 7 and 8 have significant patterns across (hod, dow) and (dow, hod), which was not apparent in (a).", fig.height = 8}
+Visualizing harmonies through (a) allows to view the significant cyclic granularities along the x-axis, facet or both for each household.
+For eg, ids 7 and 8 have significant patterns across (hod, dow) and (dow, hod), which was not apparent through (a).
+(c) is useful for comparing households across harmonies, for eg, for the harmony (dow-hod), ids 1 and 7 have the least and highest wpd respectively.", fig.height = 7}
 ```
@@
 
-_Validating rank of households_
-
-From table \ref{tab:tab-rank-8}, it could be seen that the harmony pair $(dow, hod)$ is significant for household id 4, but for id 5 it has been tagged as an insignificant pair.
-The distribution of energy demand with $dow$ as the x-axis and hod as the facets for both of these households can help justify the selection.
-Figure \ref{fig:gravitas-plot-8} shows that the median (black) and quartile deviation (orange) of energy consumption changes across both $dow$ and $hod$ for id 4 for most hours, but it is not so different for id 5 with differences captured only for $90^{th}$ percentile.
+_Comparing households and validating rank of harmonies_
+
+According to Figure \ref{fig:dotplot-8}(c), for the harmony pair (dow-hod), household id 7 has the greatest value of $wpd$, while id 1 has the least.
+Also, from table \ref{tab:tab-rank-8} it could be seen that the harmony pair $(dow, hod)$ is important for id 7, however it has been labeled as an inconsequential pair for id 1.
+The distribution of energy demand for both of these households, with $dow$ as the facet and $hod$ on the x-axis, may help explain the choice.
+Figure \ref{fig:gravitas-plot-8} demonstrates that for id 7, the median (black) and quartile deviation (orange) of energy consumption fluctuates throughout for most hours of the day and day of the week, while for id 1, daily patterns are consistent within weekdays and weekends.
+As a result, for id 1, it is more appropriate to examine the distributional difference solely across (dow, wdwnd), which has been rated higher in Table \ref{tab:tab-rank-8}.
 
@@
 
-```{r gravitas-plot-8, message = FALSE, warning=FALSE,fig.cap="Comparing distribution of energy demand shown for household id 4 (a) and 5 (b) across dow in x-axis and hod in facets through quantile area plots.
-The value of $wpd$ in Table 3 suggests that the harmony pair (dow, hod) is significant for household id 4, but not for 5.
-This implies that distributional differences are captured more by this harmony for id 4, which is apparent from the display with more fluctuations across median and 75th percentile.
+```{r gravitas-plot-8, message = FALSE, warning=FALSE,fig.cap="Comparing distribution of energy demand shown for household id 1 (a) and 7 (b) across hod in x-axis and dow in facets through quantile area plots.
+The value of $wpd$ in Table 3 suggests that the harmony pair (dow, hod) is significant for household id 7, but not for 1.
+This implies that distributional differences are captured more by this harmony for id 7, which is apparent from this display with more fluctuations across median and 75th percentile for different hours of the day and day of week.
+For id 1, patterns look similar within weekdays and weekends.
 Here, the median is represented by the black line, the orange area corresponds to quartile deviation and the green area corresponds to area between $10^{th}$ and $90^{th}$ quantile."}

### 2021-07-13 paper/scripts/main.R

@@ -926,7 +926,7 @@ heatplot <- elec_sig_split %>%
         axis.text.x = element_text(angle = 60, hjust=1),legend.position = "bottom") + ggtitle("a") +
   theme(
     strip.background = element_blank(),
-    strip.text.y  = element_blank(), plot.margin = unit(c(0, -2, 0, 0), "cm")) + ggtitle("(a)") + xlab("x variable") + ylab("facet variable") 
+    strip.text.y  = element_blank(), plot.margin = unit(c(0, -2, 0, 0), "cm")) + ggtitle("(a)") + xlab("x") + ylab("facet") 
 
 elec <- read_rds(here("paper/data/elec_all-8.rds")) %>% 
   dplyr::filter(date(reading_datetime) >= ymd("20190701"), date(reading_datetime) < ymd("20191231"), meter_id==1) %>% 
@@ -957,14 +957,16 @@ elec_zoom <-  elec %>%
              labeller = "label_both") + 
   xlab("Time [30m]") + 
   theme_grey() + 
-  ylab("") + ggtitle("(b)") +
+  ylab("Energy demand (in Kwh)") + ggtitle("(b)") +
   theme(panel.grid.major.x = element_blank()) +
   scale_x_datetime("Date", date_labels = "%b %d",
                    breaks = "1 week",
                    date_minor_breaks = "1 day")  + theme_bw() +
   theme(panel.grid.major.x =  element_line(colour = "#A9A9A9"),
-        panel.grid.minor.x =  element_line(colour = "#D3D3D3"))
-
+        panel.grid.minor.x =  element_line(colour = "#D3D3D3")) +
+  theme(
+    strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) 
+ 
 
 
 ##parallel-coordinate-plot
@@ -989,7 +991,7 @@ parcoord <- GGally::ggparcoord(data_pcp,
                    columns = 2:ncol(data_pcp),
                    groupColumn = 1,
                    showPoints = TRUE, 
-                   title = "Parallel Coordinate Plot for the Iris Data",
+                   title = "(c)",
                    alphaLines = 0.8,
                    scale = "globalminmax"
 ) + ggplot2::theme_bw() +
@@ -997,15 +999,22 @@ parcoord <- GGally::ggparcoord(data_pcp,
   ggplot2::theme(
[…]

### 2021-07-13 paper/main.Rmd
deleted the contributions to paper paragraph

@@
 
-Our contributions in this paper are:
+<!-- Our contributions in this paper are: -->
 
@@
 
- * introduce a distance measure for detecting distributional difference in temporal granularities, which enables identification
-of patterns in the time series data;
-
- * devise a selection criterion by choosing a threshold, which results in detection of only significantly interesting patterns;
-
- * show that the proposed distance metric could be used to rank the interesting patterns across different datasets and temporal granularities since they have been normalized for relevant parameters.
+ <!-- *  -->
+
+ <!-- * ; -->
+
+ <!-- * show that the proposed distance metric could be used to rank the interesting patterns across different datasets and temporal granularities since they have been normalized for relevant parameters.
+-->
 
 \noindent The article is organized as follows.
-Section \ref{sec:computation-wpd} introduces a new distance measure, discusses the reasoning and details the computation.
-Section \ref{sec:rank-wpd} discusses how to choose a threshold to select only useful displays.
+Section \ref{sec:computation-wpd} introduces a distance measure for detecting distributional difference in temporal granularities, which enables identification of patterns in the time series data;
+Section \ref{sec:rank-wpd} devises a selection criterion by choosing a threshold, which results in detection of only significantly interesting patterns.
 Section \ref{sec:simulations} provides some simulation study on the proposed methodology.

### 2021-08-18 paper/main.Rmd
changes to abstract

@@
 abstract: |
- Patterns or associations in large univariate time series data could be explored by analyzing the behavior across cyclic temporal granularities, which are temporal deconstructions accounting for repetitive behavior, for eg, hour-of-the-day, work-day/weekend, or holidays.
-This way of exploring time series analysis, however, presents itself with a plethora of displays that are potentially overwhelming for human consumption.
-This work provides a methodology to screen and rank the displays that are most informative in discerning distributional differences.
-This is done by introducing a distance measure for one or a pair of cyclic granularities that could be compared across different cyclic granularities and data sets.
-All the methods are implemented in the open-source R package `hakear`.
+ Repetitive and dependency patterns in large univariate time series data can be measured by cyclic temporal granularities, which are temporal deconstructions such as hour-of-the-day, work-day/weekend, or holidays.
+This provides a new way to do exploratory analysis of time series data.
+However, especially when there are numerous granularities, it can present too many possible displays to process by a person.
+A new distance metric is proposed that provides a tool to screen and rank the possible displays.
+The distance measure is computed for a single or pairs of cyclic granularities can can be compared across different cyclic granularities and also on a collection of time series.
+These methods are implemented in the open-source R package `hakear`.
 

### 2021-08-18 paper/main.Rmd
workingon intro

@@
 
-Exploratory data analysis, as coined by John W.
-Tukey [@Tukey1977-jx] involves many iterations of finding structures and patterns that allow the data to be informative.
-With temporal data available at finer scales, exploring time series data can become overwhelming with so many possible cyclic temporal granularities [@Bettini1998-ed, @Gupta2021-hd], which are temporal deconstructions that represent cyclic repetitions in time, e.g.
-hour-of-day, day-of-month, or any public holidays.
-These granularities form ordered (for eg.
-day-of-week where Tue is always followed by Wed, which again is followed by Thu and so on) or unordered categorical variables.
-Therefore, exploring univariate time series data amounts to exploring the distribution of the measured variable across different categories of the cyclic granularities.
-\noindent Take the example of the electricity smart meter data used in @wang2020calendar for four households in Melbourne, Australia.
-Figure \ref{fig:onegran-new} shows the distribution of energy usage of one household (id 2) across cyclic granularity a) hour-of-day and b) month-of-year.
+<!--Exploratory data analysis, as coined by John W. Tukey [@Tukey1977-jx] involves many iterations of finding structures and patterns that allow the data to be informative.-->
+
+Cyclic temporal granularities [@Bettini1998-ed, @Gupta2021-hd] are theoretical temporal deconstructions that define cyclic repetitions in time, e.g.
+hour-of-day, day-of-month, or regularly scheduled public holidays.
+These granularities form ordered or unordered categorical variables.
+An example of an ordered granularity is day-of-week, where Tuesday is always followed by Wednesday, and so on.
+An unordered granularity might be XXX.
+Thus we can consider that exploring univariate time series using granularities to be examining the distribution of the measured variable across different categories of the cyclic granularities.
+
+As an example, Figure \ref{fig:onegran-new} shows electricity smart meter data for four households in Melbourne, Australia [@wang2020calendar].
+The distribution of energy usage of one household (id 2) across cyclic granularity a) hour-of-day and b) month-of-year.
 Figure \ref{fig:onegran-new}(a) shows that energy consumption is higher during the morning hours (5-8) when members in the household wake up and then again in the evening hours (17-20) possibly when members get back from work with maximum variation (large interquartile range) in behavior in the afternoon hours (12-16).

### 2021-08-26 paper/main.Rmd
sstill tweaking abstract

@@
 abstract: |
- Repetitive and dependency patterns in large univariate time series data can be measured by cyclic temporal granularities, which are temporal deconstructions such as hour-of-the-day, work-day/weekend, or holidays.
-This provides a new way to do exploratory analysis of time series data.
-However, especially when there are numerous granularities, it can present too many possible displays to process by a person.
-A new distance metric is proposed that provides a tool to screen and rank the possible displays.
+ Cyclic temporal granularities, which are temporal deconstructions of a time period into units such as hour-of-the-day, work-day/weekend, can be useful for measuring repetitive patterns in large univariate time series data.
+The granularities feed new approaches to exploring time series data.
+One use is to take pairs of granularities, and make plots of response values across the categories induced by the temporal deconstruction.
+However, when there are many granularities that can be constructed for a time period, there will also be too many possible displays to decide which might be the more interesting to display.
+This work proposes a new distance metric to screen and rank the possible granularities, and hence choose the most interesting ones to plot.
 The distance measure is computed for a single or pairs of cyclic granularities can can be compared across different cyclic granularities and also on a collection of time series.
-These methods are implemented in the open-source R package `hakear`.
+The methods are implemented in the open-source R package `hakear`.
 

### 2021-09-16 paper/main.Rmd
first two paragraphs and figure 1

@@
   \def\vspacing{\setlength{\aboverulesep}{0.4ex}\setlength{\belowrulesep}{0.65ex}}
+  \newcommand{\DC}[1]{\textcolor{red}{#1}}
 output:
@@
 
-Cyclic temporal granularities [@Bettini1998-ed, @Gupta2021-hd] are theoretical temporal deconstructions that define cyclic repetitions in time, e.g.
+Cyclic temporal granularities [@Bettini1998-ed, @Gupta2021-hd] are <!--theoretical--> temporal deconstructions that define cyclic repetitions in time, e.g.
 hour-of-day, day-of-month, or regularly scheduled public holidays.
@@
 An example of an ordered granularity is day-of-week, where Tuesday is always followed by Wednesday, and so on.
-An unordered granularity might be XXX.
-Thus we can consider that exploring univariate time series using granularities to be examining the distribution of the measured variable across different categories of the cyclic granularities.
-
-As an example, Figure \ref{fig:onegran-new} shows electricity smart meter data for four households in Melbourne, Australia [@wang2020calendar].
-The distribution of energy usage of one household (id 2) across cyclic granularity a) hour-of-day and b) month-of-year.
-Figure \ref{fig:onegran-new}(a) shows that energy consumption is higher during the morning hours (5-8) when members in the household wake up and then again in the evening hours (17-20) possibly when members get back from work with maximum variation (large interquartile range) in behavior in the afternoon hours (12-16).
-Figure \ref{fig:onegran-new}(b) shows the distribution of energy consumption across months January to June.
-The median and quartile deviation of energy usage in Jan and Feb are generally on a much higher side, possibly due to the usage of air conditioners (Jan, Feb are peak summer in Australia), however, for other months (Mar-Jun, autumn and winter), the smaller median and quartile deviation indicate a more consistent behavior.
-It might also imply that this household does not use as much heater as compared to air conditioner.
-A lot of households in Victoria use gas heating and hence the usage of heaters might not be reflected here.
-Potentially many such displays could be drawn across day-of-week, day-of-month, weekday/weekend, or any other chosen cyclic granularities of interest.
-However, all of them would not be interesting to discern important patterns in energy usage.
-Only those displays, which have "significant" distributional differences between categories of the cyclic granularity would be informative.
+An unordered granularity example is \DC{different week types in a semester, orientation, break, exam or regular classes in an academic calendar}.
+Using granularities to  explore patterns in univariate time series can be considered to be examining the distribution of the measured variable across different categories of the cyclic granularities.
+
+Figure \ref{fig:onegran-new} electricity smart meter data plotted against two granularities (hour-of-day, month-of-year).
+The data was collected on a single household in Melbourne, Australia, over a six month period, as was used in @wang2020calendar.
+The categorical variable (granularity) is mapped to the x-axis, and the distribution of response variable is displayed using both side-by-side jittered dotplots and boxplots.
+From plot (a) it can be seen that energy consumption is higher during the morning hours (5-8), when members in the household wake up, and again in the evening hours (17-20) possibly when members get back from work.
+In addition, the largest variation in energy use is in the afternoon hours (12-16), as perceived from sizes of the boxes.
+From plot (b) the variability in energy usage is higher in Jan and Feb, possibly due to the usage of air conditioners on some days.
+The median usage is highest in January, dips in February-April and rises again in May-June, although not to the height of January usage.
+This might imply that this household does not use as much energy for heating as it does for air conditioning.
+A lot of households in Victoria use gas heating and hence the heater use might not be reflected in the electricity data.
+Many, many different displays could be constructed using different granularities,  day-of-week, day-of-month, weekday/weekend, etc.
+However, only a few might be interesting, that is, reveal important patterns in energy usage.
+Determining which displays which have "significant" distributional differences between categories of the cyclic granularity, and plotting only these, would make for efficient exploration.
 
@@
 
-```{r onegran-new, fig.cap="Boxplots showing the distribution of one household across one cyclic granularity at a time - (a) hour-of-day and (b) and month-of-year.
-The daily and annual periodic behavior of energy is apparent in (a) and (b) respectively, with daily peaks occurring in morning and evening hours when members in the house are present and active, more volatility (usage of air conditioner) in summer months (Jan, Feb) due to air conditioners and more consistent behavior in winter and autumn months (Mar, Apr, May, June)."}
+```{r onegran-new, fig.cap="A cyclic granularity can be considered to be a categorical variable, and used to break the data into subsets.
+Here, side-by-side boxplots overlaid on jittered dotplots explore the distribution of of energy use by a household for two different cyclic granularities: (a) hour-of-day and (b) and month-of-year.
+Daily peaks occur in morning and evening hours, indicating a working household, where members leave for and return from work.
+More volatility of usage in summer months (Jan, Feb) is probably due air conditioner use on just some days ."}
 ```

### 2021-09-16 paper/main.Rmd
Citations changed from "To appear" to "published"

@@
 <!-- When we need to understand the interplay of different periodicities in a high frequency temporal datasets, we have many choices to consider.
-In [@wang2019tsibble] and [@wang2020calendar], periodicities are explored across hour of the day and day of the week or months.
+In [@wang2020tsibble] and [@wang2020calendar], periodicities are explored across hour of the day and day of the week or months.
 But calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions.
@@
 The smart meter data set for eight households in Melbourne has been utilized to see the use of $wpd$ proposed in the paper.
-The data has been cleaned to be a `tsibble` (@wang2019tsibble) containing half-hourly electricity consumption from Jul-2019 to Dec-2019 for each of the households, which is procured by them by downloading their data from the energy supplier/retailer.
+The data has been cleaned to be a `tsibble` (@wang2020tsibble) containing half-hourly electricity consumption from Jul-2019 to Dec-2019 for each of the households, which is procured by them by downloading their data from the energy supplier/retailer.
 No behavioral pattern is likely to be discerned from the line graph of energy usage over the entire period, since the plot will have too many measurements squeezed in a linear representation.

### 2021-10-27 paper/main.Rmd
Improved notation and wording to end of section 2

@@
 abstract: |
- Cyclic temporal granularities, which are temporal deconstructions of a time period into units such as hour-of-the-day, work-day/weekend, can be useful for measuring repetitive patterns in large univariate time series data.
-The granularities feed new approaches to exploring time series data.
+ Cyclic temporal granularities are temporal deconstructions of a time period into units such as hour-of-the-day and work-day/weekend.
+They can be useful for measuring repetitive patterns in large univariate time series data, and feed new approaches to exploring time series data.
 One use is to take pairs of granularities, and make plots of response values across the categories induced by the temporal deconstruction.
@@
 This work proposes a new distance metric to screen and rank the possible granularities, and hence choose the most interesting ones to plot.
-The distance measure is computed for a single or pairs of cyclic granularities can can be compared across different cyclic granularities and also on a collection of time series.
+The distance measure is computed for a single or pairs of cyclic granularities and can be compared across different cyclic granularities or on a collection of time series.
 The methods are implemented in the open-source R package `hakear`.
@@
  \usepackage{mathptmx}
-  \usepackage{caption}
+ \usepackage{caption,setspace}
  \usepackage{longtable}
  \DeclareCaptionStyle{italic}{labelfont={bf},textfont={it},labelsep=colon}
-  \captionsetup[figure]{style=italic,format=hang,singlelinecheck=true}
-  \captionsetup[table]{style=italic,format=hang,singlelinecheck=true}
+ \captionsetup[figure]{style=italic,format=hang,singlelinecheck=true,font={stretch=1.2}}
+ \captionsetup[table]{style=italic,format=hang,singlelinecheck=true,font={stretch=1.2}}
  \def\novspacing{\setlength{\aboverulesep}{0pt}\setlength{\belowrulesep}{0pt}}
@@
  \newcommand{\DC}[1]{\textcolor{red}{#1}}
+ \setcounter{topnumber}{2}
+ \setcounter{bottomnumber}{2}
+ \setcounter{totalnumber}{4}
+ \renewcommand{\topfraction}{0.85}
+ \renewcommand{\bottomfraction}{0.85}
+ \renewcommand{\textfraction}{0.15}
+ \renewcommand{\floatpagefraction}{0.7}
+ \def\wpd{\text{\textit{wpd}}}
+ \def\wpdsub#1{\text{\textit{wpd}}_{\text{#1}}}
+ \def\Dnull{D_{\emptyset}}
+ \def\Df{D_{\!f}}
+ \def\Dfx{D_{\!fx}}
+ \def\Dx{D_{x}}
+ \def\nsub#1{n_{\text{#1}}}
+ \def\nx{n_x}
+ \def\nf{n_{\!f}}
+
 output:
@@
 An example of an ordered granularity is day-of-week, where Tuesday is always followed by Wednesday, and so on.
-An unordered granularity example is \DC{different week types in a semester, orientation, break, exam or regular classes in an academic calendar}.
-Using granularities to  explore patterns in univariate time series can be considered to be examining the distribution of the measured variable across different categories of the cyclic granularities.
-
-Figure \ref{fig:onegran-new} electricity smart meter data plotted against two granularities (hour-of-day, month-of-year).
-The data was collected on a single household in Melbourne, Australia, over a six month period, as was used in @wang2020calendar.
-The categorical variable (granularity) is mapped to the x-axis, and the distribution of response variable is displayed using both side-by-side jittered dotplots and boxplots.
-From plot (a) it can be seen that energy consumption is higher during the morning hours (5-8), when members in the household wake up, and again in the evening hours (17-20) possibly when members get back from work.
-In addition, the largest variation in energy use is in the afternoon hours (12-16), as perceived from sizes of the boxes.
-From plot (b) the variability in energy usage is higher in Jan and Feb, possibly due to the usage of air conditioners on some days.
-The median usage is highest in January, dips in February-April and rises again in May-June, although not to the height of January usage.
-This might imply that this household does not use as much energy for heating as it does for air conditioning.
-A lot of households in Victoria use gas heating and hence the heater use might not be reflected in the electricity data.
-Many, many different displays could be constructed using different granularities,  day-of-week, day-of-month, weekday/weekend, etc.
-However, only a few might be interesting, that is, reveal important patterns in energy usage.
-Determining which displays which have "significant" distributional differences between categories of the cyclic granularity, and plotting only these, would make for efficient exploration.
+An unordered granularity example is \DC{week type in an academic semester: orientation, break, exam or regular classes}.
+We can use granularities to explore patterns in univariate time series by examining the distribution of the measured variable across different categories of the cyclic granularities.
 
@@
 Daily peaks occur in morning and evening hours, indicating a working household, where members leave for and return from work.
-More volatility of usage in summer months (Jan, Feb) is probably due air conditioner use on just some days ."}
+More volatility of usage in summer months (Jan, Feb) is probably due air conditioner use on just some days.", fig.pos="!b"}
+```
+
+As a motivating example, consider Figure \ref{fig:onegran-new} which shows electricity smart meter data plotted against two granularities (hour-of-day, month-of-year).
+The data was collected on a single household in Melbourne, Australia, over a six month period, and was previously used in @wang2020calendar.
+The categorical variable (granularity) is mapped to the x-axis, and the distribution of the response variable is displayed using both side-by-side jittered dotplots and boxplots.
+From panel (a) it can be seen that energy consumption is higher during the morning hours (5--8), when members in the household wake up, and again in the evening hours (17--20) possibly when members get back from work.
+In addition, the largest variation in energy use is in the afternoon hours (12--16), as seen in the length of the boxes.
+From panel (b), it is seen that the variability in energy usage is higher in Jan and Feb, probably due to the usage of air conditioners on some days.
+The median usage is highest in January, dips in February--April and rises again in May--June, although not to the height of January usage.
+This suggests that the household does not use as much electricity for heating as it does for air conditioning.
+A lot of households in Victoria use gas heating and hence the heater use might not be reflected in the electricity data.
+
+Many different displays could be constructed using different granularities including day-of-week, day-of-month, weekday/weekend, etc.
+However, only a few might be interesting and reveal important patterns in energy usage.
+Determining which displays have "significant" distributional differences between categories of the cyclic granularity, and plotting only these, would make for efficient exploration.
+
+```{r intro_all}
+
+```
+
+```{r id2-new2, fig.cap = "Distribution of energy consumption displayed through area quantile plots across two cyclic granularities month-of-year and hour-of-day and two households.
+The black line is the median, whereas the orange band covers the 25th to 75th percentile and the green band covers the 10th to 90th percentile.
+Difference between the 90th and 75th quantiles is less for (Jan, Feb) for the first household (a), suggesting that it is a more frequent user of air conditioner than the second household (b).
+Energy consumption for in (a) changes across both granularities, whereas for (b) daily pattern stays same irrespective of the months."}
 ```
@@
 <!-- comparing one and two grans for one households -->
-\noindent Exploring the distribution of the measured variable across two cyclic granularities tends to provide more detailed information on its structure.
-For example, Figure \ref{fig:id2-new2}(a) slice down further by showing the usage distribution across hour-of-day conditional on month-of-year across two households (id 2 and 4).
+Exploring the distribution of the measured variable across two cyclic granularities provides more detailed information on its structure.
+For example, Figure \ref{fig:id2-new2}(a) shows the usage distribution across hour-of-day conditional on month-of-year across two households.
 It shows the hourly usage over a day does not remain the same across months.
-Unlike other months, the 75th and 90th percentile for all hours of the day in January are    high, pretty close, and are not characterized by a morning and evening peak.
+Unlike other months, the 75th and 90th percentile for all hours of the day in January are high, similar, and are not characterized by a morning and evening peak.
 The household in Figure \ref{fig:id2-new2}(b) has 90th percentile consumption higher in summer months relative to autumn or winter, but the 75th and 90th percentile are far apart in all months, implying that the second household resorts to air conditioning much less regularly than the first one.
@@
 <!-- The problem and its dimension -->
-\noindent Are all of these four displays in Figures \ref{fig:onegran-new} and \ref{fig:id2-new2} useful in understanding the distributional difference in energy usage?
+Are all four displays in Figures \ref{fig:onegran-new} and \ref{fig:id2-new2} useful in understanding the distributional difference in energy usage?
 Which ones are more useful than others?
@@
 When considering displays of the form in Figure \ref{fig:id2-new2},
-there are $^{N_C}P_2$ possible pairwise plots exhaustively, with one of the two cyclic granularities acting as the conditioning variable. 
-This is huge and overwhelming for human consumption even for moderately large $N_C$.
-It could be immensely useful to make the transition from all potential displays to the ones that are informative across atleast one cyclic granularity.
+there are $N_C(N_C-1)$ possible pairwise plots exhaustively, with one of the two cyclic granularities acting as the conditioning variable.
+This can be overwhelming for human consumption even for moderately large $N_C$. It is therefore  useful to identify those displays that are informative across at least one cyclic granularity.
 
@@
 
-\noindent This problem is similar to Scagnostics (Scatterplot Diagnostics) by @tukey1988computer, which is used to identify meaningful patterns in large collections of scatterplots.
+This problem is similar to Scagnostics (Scatterplot Diagnostics) by @tukey1988computer, which are used to identify meaningful patterns in large collections of scatterplots.
 Given a set of $v$ variables, there are $v(v-1)/2$ pairs of variables, and thus the same number of possible pairwise scatterplots.
-Therefore, even for small $v$, the number of scatterplots can be large, and scatterplot matrices (SPLOMs) could easily run out of pixels when presenting high-dimensional data.
-@Dang2014-tw and @wilkinson2005graph provide potential solutions to this, where few characterizations can be used to locate anomalies in density, shape, trend, and other features in the 2D point scatters.
-In this paper, we provide a solution to narrowing down the search from $^{N_C}P_2$ plots by introducing a new distance measure that can be used to detect significant distributional differences across cyclic granularities.<!-- harmonies and why it is not enough --> This work is a natural extension of our previous work [@Gupta2021-hd] that narrows down the search from $^{N_C}P_2$ plots by identifying pairs of granularities that can be meaningfully examined together (a "harmony"), or when they cannot (a "clash").
-However, even after excluding clashes, the list of harmonies left could be enormous for exhaustive exploration.
-Hence, there is a need to reduce the search even further by including only those harmonies which are informative enough.
+Therefore, even for small $v$, the number of scatterplots can be large, and scatterplot matrices (SPLOMs) can easily run out of pixels when presenting high-dimensional data.
+@Dang2014-tw and @wilkinson2005graph provide potential solutions to this, where a few characterizations can be used to locate anomalies in density, shape, trend, and other features in the 2D point scatters.
+
+In this paper, we provide a solution to narrowing down the search from $N_C(N_C-1)$ conditional distribution plots by introducing a new distance measure that can be used to detect significant distributional differences across cyclic granularities.<!-- harmonies and why it is not enough --> This work is a natural extension of our previous work [@Gupta2021-hd] which narrows down the search from $N_C(N_C-1)$ plots by identifying pairs of granularities that can be meaningfully examined together (a "harmony"), or when they cannot (a "clash").
+However, even after excluding clashes, the list of harmonies left may be too large for exhaustive exploration.
+Hence, there is a need to reduce the search even further by including only those harmonies that contain useful information.
+
 @inference and @Majumder2013-hb present methods for statistical significance testing of visual findings using human cognition as the statistical tests.
@@
 
-```{r intro_all}
-
-```
-
-```{r id2-new2, fig.cap = "Distribution of energy consumption displayed through area quantile plots across two cyclic granularities month-of-year and hour-of-day and two households.
-The black line is the median, whereas the orange band covers the 25th to 75th percentile and the green band covers the 10th to 90th percentile.
-Difference between the 90th and 75th quantiles is less for (Jan, Feb) for the first household (a), suggesting that it is a more frequent user of air conditioner than the second household (b).
-Energy consumption for in (a) changes across both granularities, whereas for (b) daily pattern stays same irrespective of the months."}
-```
-
 ```{r id4, fig.cap = "something2", eval = FALSE}
@@
 
-\noindent The article is organized as follows.
+The article is organized as follows.
 Section \ref{sec:computation-wpd} introduces a distance measure for detecting distributional difference in temporal granularities, which enables identification of patterns in the time series data;
@@
 
-We propose a measure called Weighted Pairwise Distances ($wpd$) to detect distributional differences in the measured variable across cyclic granularities.
+We propose a measure called Weighted Pairwise Distances ($\wpd$) to detect distributional differences in the measured variable across cyclic granularities.
 
@@
 
-The principle behind the construction of $wpd$ is explained through a simple example explained in Figure \ref{fig:null4by2}.
-Each of these figures describes a panel with $2$ x-axis categories and $3$ facet levels, but with different designs.
-Figure \ref{fig:null4by2}a has all categories drawn from N(0, 1) distribution for each facet.
-It is not an interesting display particularly, as distributions do not vary across x-axis or facet categories.
-Figure \ref{fig:null4by2}b has x categories drawn from the same distribution, but across facets the distributions are $3$ standard deviations apart.
-Figure \ref{fig:null4by2}c exhibits an exact opposite situation where distribution between the x-axis categories
-are $3$ standard deviations apart, but they do not change across facets.
-Figure \ref{fig:null4by2}d takes a step further by varying the distribution across both facet and x-axis categories by  $3$ standard deviations.
-If the panels are to be ranked in order of capturing maximum variation in the measured variable from minimum to maximum, then an obvious choice would be placing (a) followed by (b), (c) and then (d).
+(ref:null4by2) An example illustrating the principle of the proposed distance measure, displaying the distribution of a normally distributed variable in four panels each with two x-axis categories and three facet levels, but with different designs.
+Panel (a) is not interesting as the distribution of the variable does not depend on x or facet categories.
+Panels (b) and (c) are more interesting than (a) since there is a change in distribution either across facets (b) or x-axis (c).
+Panel (d) is most interesting in terms of capturing structure in the variable as the distribution of the variable changes across both facet and x-axis variable.
+The value of our proposed distance measure is presented for each panel, the relative differences between which will be explained later in Section \@ref(sec:ranking).
+
+```{r null4by2, fig.cap = "(ref:null4by2)", fig.pos="!b"}
+```
+
+The principle behind the construction of $\wpd$ is explained through a simple example in Figure&nbsp;\ref{fig:null4by2}.
+Each of these figures describes a panel with two x-axis categories and three facet levels, but with different designs.
+Figure \ref{fig:null4by2}a has all categories drawn from a standard normal distribution for each facet.
+It is not a particularly interesting display, as the distributions do not vary across x-axis or facet categories.
+Figure \ref{fig:null4by2}b has x categories drawn from the same distribution, but across facets the distributions are three standard deviations apart.
+Figure \ref{fig:null4by2}c exhibits the opposite situation where distribution between the x-axis categories are three standard deviations apart, but they do not change across facets.
+In Figure \ref{fig:null4by2}d, the distribution varies across both facet and x-axis categories by three standard deviations.
+
+If the panels are to be ranked in order of capturing maximum variation in the measured variable from minimum to maximum, then an obvious choice would be (a) followed by (b), (c) and then (d).
 It might be argued that it is not clear if (b) should precede or succeed (c) in the ranking.
 Gestalt theory suggests items placed at close proximity can be compared more easily, because people assume that they are in the same group and apart from other groups.
-With this principle in mind, display (b) is considered less informative as compared to display (c) in emphasizing the distributional differences.
-Considering one cyclic granularity, we would have only two design choices similar to (a) and (c), corresponding to no difference and significant differences between categories of that cyclic granularity only.
-The proposed measure $wpd$ is constructed in a way so that it could be used to rank panels of different designs as well as test if a design is interesting.
+With this principle in mind, Panel (b) is considered less informative compared to Panel (c) in emphasizing the distributional differences.
+
+For displays showing a single cyclic granularity rather than pairs of granularities, we have only two design choices corresponding to no difference and significant differences between categories of that cyclic granularity.
+
+The proposed measure $\wpd$ is constructed in such a way that it can be used to rank panels of different designs as well as test if a design is interesting.
 This measure is aimed to be an estimate of the maximum variation in the measured variable explained by the panel.
-A higher value of  $wpd$ would indicate that the panel is interesting to look at, whereas a lower value would indicate otherwise.
+A higher value of $\wpd$ would indicate that the panel is interesting to look at, whereas a lower value would indicate otherwise.
 
@@
 Moreover, a tuning parameter specifying the weightage given to within-facet or between-facet categories can help to choose between designs like \ref{fig:null4by2}b and c.
-The maximum of all these weighted differences serves as an estimate of the maximum variation in the panel and is taken as the value of $wpd$.
+The maximum of all these weighted differences serves as an estimate of the maximum variation in the panel and is taken as the value of $\wpd$.
 -->
@@
 One of the potential ways to do this is to measure the distances between distributions of the continuous random variable measured within and between groups, weigh them basis if they are within or between groups and then take the maximum of those distances as an estimate of the maximum variation in the structure.
-This section starts with possible ways of characterizing distributions and computing distances between them and then describe in details how the measure $wpd$ is defined.
+This section starts with possible ways of characterizing distributions and computing distances between them and then describe in details how the measure $\wpd$ is defined.
 -->
@@
 For example, if there are 4 facet levels and 2 x-axis levels, data is generated in the way as described in Table \ref{}.
-Figure \ref{}b exhibits an exact opposite situation where the x-axis within facets are different but not across facets.
+Figure \ref{}b exhibits an opposite situation where the x-axis within facets are different but not across facets.
 -->
 <!-- Figure \ref{}d takes it further by varying the distribution across both facet and x-axis categories. -->
-
-```{r null4by2,fig.cap = "An example illustrating the principle of the proposed distance measure, displaying the distribution of a normally distributed variable in four panels each with $2$ x-axis categories and $3$ facet levels, but with different designs.
-Display (a) is not interesting as the distribution of the variable does not depend on x or facet categories.
-Display (b) and (c) are more interesting than (a) since there is a change in distribution either across facets (b) or x-axis (c).
-Display (d) is most interesting in terms of capturing structure in the variable as the distribution of the variable changes across both facet and x-axis variable.
-The value of our proposed distance measure is presented for each panel, the relative differences between which will be explained later in Section 3.2."}
-```
 
@@
 
-## Notations
-
-\noindent Let the number of cyclic granularities considered in the display be $m$.
+## Notation
+
+Let the number of cyclic granularities considered in the display be $m$.
 The notations and methodology are described in detail for $m=2$.
 But it can be easily extended to $m>2$.
-Consider two cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.
+Consider two cyclic granularities $A$ and $B$, such that $A = \{a_j: j = 1, 2, \dots, J\}$ and $B = \{b_k: k = 1, 2, \dots, K\}$ with $A$ placed across the x-axis and $B$ across facets.
 Let $v = \{v_t: t = 0, 1, 2, \dots, T-1\}$ be a continuous variable observed across $T$ time points.
 This data structure with $J$ x-axis levels and $K$ facet levels is referred to as a $(J, K)$ panel.
-For example, a $(2, 3)$ panel will have cyclic granularities with 2 x-axis levels and 3 facet levels.
-Let the four elementary designs as described in Figure \ref{fig:null4by2} be $D_{null}$ (referred to as "null distribution") where there is no difference in distribution of $v$ for $A$ or $B$, $D_{var_f}$ denotes the set of designs where there is difference in distribution of $v$ for $B$ and not for $A$.
-Similarly, $D_{var_x}$ denotes the set of designs where difference is observed only across A.
-Finally, $D_{var_{all}}$ denotes those designs for which difference is observed across both $A$ and $B$.
-$m = 1$ is a special case of $m = 2$ with $J = 1$.
+For example, a $(2, 3)$ panel will have cyclic granularities with two x-axis levels and three facet levels.
+Let the four elementary designs as described in Figure \ref{fig:null4by2} be $\Dnull$ (referred to as "null distribution") where there is no difference in distribution of $v$ for $A$ or $B$, $\Df$ denotes the set of designs where there is difference in distribution of $v$ for $B$ and not for $A$.
+Similarly, $\Dx$ denotes the set of designs where difference is observed only across A.
+Finally, $\Dfx$ denotes those designs for which difference is observed across both $A$ and $B$.
+We can consider a single granularity ($m = 1$) as a special case of two granularities with $J = 1$.
 
@@
 
-The computation of the distance measure $wpd$ for a panel involves characterizing distributions, computing distances between distributions, choosing a tuning parameter to specify the weightage for different group of distances and summarizing those weighted distances appropriately to estimate maximum variation.
-Furthermore, the data needs to be appropriately transformed to ensure that the value of $wpd$ emphasizes detection of distributional differences across categories and not across different data generating processes.
+The computation of the distance measure $\wpd$ for a panel involves characterizing distributions, computing distances between distributions, choosing a tuning parameter to specify the weight for different groups of distances and summarizing those weighted distances appropriately to estimate maximum variation.
+Furthermore, the data needs to be appropriately transformed to ensure that the value of $\wpd$ emphasizes detection of distributional differences across categories and not across different data generating processes.
 
@@
 
-<!-- is aimed to capture structure and patterns by estimating the maximum variation of the measured variable within a panel.  $wpd$ -->
+<!-- is aimed to capture structure and patterns by estimating the maximum variation of the measured variable within a panel. $\wpd$ -->
 
@@
 Moreover, a tuning parameter specifying the weightage given to within-facet or between-facet categories can help to choose between designs like \ref{fig:null4by2}b and c.
-The maximum of all these weighted differences serves as an estimate of the maximum variation in the panel and is taken as the value of $wpd$.
--->
-
-### Data transformation
-
-The intended aim of $wpd$ is to capture differences in categories irrespective of the distribution from which the data is generated.
-Hence, as a pre-processing step, the raw data is normal-quantile transformed (NQT) (@Krzysztofowicz1997-bv), so that the quantiles of the transformed data follows a standard normal distribution.
-This sort of transformation is common in the fields of geo-statistics to make most asymmetrical distributed real world measured variables more treatable and normal-like (@Bogner2012-az).The empirical NQT involves the following steps:
- 1. The sample of measured variable $v$ is sorted from the smallest to the largest observation $v_{(1)},\dots, v_{(i)}, .., v_{(n)}$.  
- 2. The cumulative probabilities $p_{(1)},\dots, p_{(i)}, .., p_{(n)}$ are estimated using a plotting position like $i/(n + 1)$ such that $p_{(i)} = P(v \leq v_{(i)})$.  
- 3.
-Each observation $v_{(i)}$ of $v$ is transformed into observation $v^*(i) = Q^{-1}(p(i))$ of the standard normal variate $v^*$, with $Q$ denoting the standard normal distribution and $Q^{-1}$ its inverse.
-
-### Characterising distributions
+The maximum of all these weighted differences serves as an estimate of the maximum variation in the panel and is taken as the value of $\wpd$.
+-->
+
+### Data transformation {-}
+
+The intended aim of $\wpd$ is to capture differences in categories irrespective of the distribution from which the data is generated.
+Hence, as a pre-processing step, the raw data is normal-quantile transformed (NQT) [@Krzysztofowicz1997-bv], so that the transformed data follows a standard normal distribution.
+The empirical NQT involves the following steps:
+
+ 1. The observations of measured variable $v$ are sorted from the smallest to the largest observation $v_{(1)},\dots, v_{(n)}$.
+ 2. The cumulative probabilities $p_{(1)},\dots, p_{(n)}$ are estimated using $p_{(i)} = i/(n + 1)$  [@Hyndman1996-ty] so that $p_{(i)} = \text{Pr}(v \leq v_{(i)})$.
+ 3. Each observation $v_{(i)}$ of $v$ is transformed into $v^*(i) = \Phi^{-1}(p(i))$, with $\Phi$ denoting the standard normal distribution function.
+
+### Characterizing distributions {-}
 
@@
 The number of observations might vary widely across subsets due to the structure of the calendar, missing observations or uneven locations of events in the time domain.
-in this paper, quantiles of $v_{jk}$'s are chosen as a way to characterize distributions for the category $(a_j, b_k)$, $\forall j\in \{1, 2, \dots, J\}, k\in \{1, 2, \dots, K\}\}$.
-The quantile of a distribution with probability $p$ is defined as $Q(p)=F^{-1}(p) = inf\{x: F(x) >p\}$, $0<p< 1$ where $F(x)$ is the distribution function.
-There are two broad approaches to quantile estimation, viz, parametric and non-parametric.
-Sample quantiles (@Hyndman1996-ty) are used for estimating population quantiles in a non-parametric setup, which is desirable because of less rigid assumptions made about the nature of the underlying distribution of the data.
-The default quantile chosen in this paper is percentiles computed for $p = {0.01, 0.02, \dots, 0.99}$, where for example, the $99^{th}$ percentile would be the value corresponding to $p=0.99$ and hence 99% of the observations would lie below that.
+In this paper, quantiles of $\{v_{jk}\}$ are chosen as a way to characterize distributions for the category $(a_j, b_k)$, $\forall j\in \{1, 2, \dots, J\}, k\in \{1, 2, \dots, K\}$.
+We use percentiles with $p = {0.01, 0.02, \dots, 0.99}$ to reduce the computational burden in summarising distributions.
 
@@
 
-### Distance between distributions
+### Distance between distributions {-}
 
@@
 The continuous version of f -divergence is given by -->
-<!-- $$D_f(P||Q) := \int q(x)f(\frac{p(x)}{q(x)})$$, where -->
+<!-- $$\Df(P||Q) := \int q(x)f(\frac{p(x)}{q(x)})$$, where -->
 <!-- $f : [0,\infty) \rightarrow R \cup \{\infty\}$ is a continuous convex function, and $f(1) = 0$. -->
 
-One of the most common ways to measure divergence between distributions is the Kullback-Leibler (KL) divergence [@Kullback1951-jy].
+A common way to measure divergence between distributions is the Kullback-Leibler (KL) divergence [@Kullback1951-jy].
 The KL divergence denoted by $D(q_1||q_2)$ is a non-symmetric measure of the difference between two probability distributions $q_1$ and $q_2$ and is interpreted as the amount of information lost when $q_2$ is used to approximate $q_1$.
-The KL divergence, however, is not symmetric and hence can not be considered as a "distance" measure.
+The KL divergence is not symmetric and hence can not be considered as a "distance" measure.
 The Jensen-Shannon divergence [@Menendez1997-in] based on the Kullback-Leibler divergence is symmetric and has a finite value.
-Hence, in this paper, the pairwise distances between the distributions of the measured variable are obtained through the square root of the Jensen-Shannon divergence, called Jensen-Shannon distance (JSD) and is defined by,
-
-$$JSD(q_1||q_2) = \frac{1}{2}D(q_1||M) + \frac{1}{2}D(q_2||M)$$
-where $M = \frac{q_1+q_2}{2}$ and 
-$D(q_1||q_2) := \int^\infty_{-\infty} q_1(x)f(\frac{q_1(x)}{q_2(x)})$ is the KL divergence between distributions $q_1$ and $q_2$.
+Hence, in this paper, the pairwise distances between the distributions of the measured variable are obtained through the square root of the Jensen-Shannon divergence, called Jensen-Shannon distance (JSD), and defined by,
+$$
+  JSD(q_1||q_2) = \frac{1}{2}D(q_1||M) + \frac{1}{2}D(q_2||M),
+$$
+where $M = \frac{q_1+q_2}{2}$ and $D(q_1||q_2) := \int^\infty_{-\infty} q_1(x)f(\frac{q_1(x)}{q_2(x)})$ is the KL divergence between distributions $q_1$ and $q_2$.
 Other common measures of distance between distributions are Hellinger distance, total variation distance and Fisher information metric.
 
-<!-- Furthermore, these distances are distributed as chi-squared with $m$ degrees of freedom (@Menendez1997-in), if the continuous distribution is being discretized with $m$ discrete values.
+<!-- Furthermore, these distances are distributed as chi-squared with $m$ degrees of freedom [@Menendez1997-in], if the continuous distribution is being discretized with $m$ discrete values.
 Taking sample percentiles to approximate the integral would mean taking $m = 99$.
@@
 
-### Within-facet and between-facet distances
-
-\noindent Pairwise distances could be within-facets or between-facets for $m \geq 2$.
+### Within-facet and between-facet distances {-}
+
+```{r distance-explain, fig.cap = "Within and between-facet distances shown for two cyclic granularities A and B, where A is mapped to x-axis and B is mapped to facets.
+The dotted lines represent the distances between different categories.
+Panels 1) and 2) show the between-facet distances.
+Panels 3) and 4) are used to illustrate within-facet distances when categories are un-ordered or ordered respectively.
+When categories are ordered, distances should only be considered for consecutive x-axis categories.
+Between-facet distances are distances between different facet levels for the same x-axis category, for example, distances between {($a_1$,$b_1$) and ($a_1$, $b_2$)} or {($a_1$,$b_1$) and ($a_1$, $b_3$)}.", fig.pos="!b"}
+
+```
+
+Pairwise distances could be within-facets or between-facets for $m \geq 2$.
 Figure \ref{fig:distance-explain} illustrates how they are defined.
@@
 Pairwise distances are between-facets when they are considered between pairs of the form $(a_{j}b_{k}, a_{j}b_{k'})$.
-Number of between-facet distances would be $^{K}C_2*J$ and number of within-facet distances are $K*(J-1)$ (ordered) and $^{J}C_2*K$ (un-ordered).
-
-### Tuning parameter
-
-A tuning parameter specifying the weightage given to the within-facet or between-facet categories can help to balance weightage between designs like \ref{fig:null4by2}(b) and (c).
-The tuning parameters should be chosen such that $\sum_{i=1}^m \lambda_i = 1$.
-When $m=2$, following the principle of Gestalt theory, $\lambda = \frac{2}{3} = 0.67$ is chosen to put a relative weightage of $2:1$ for within-facet and between-facet distances.
-No human experiment is conducted to justify this ratio, however, typically a tuning parameter $\lambda>0.5$ would tend to upweigh the within-facet distances and that with $<0.5$ would upweigh the between-facet distances (refer to the Supplementary paper for more details).
-For $m = 1$, there are no conditioning variables or groups, and hence $\lambda = 1$.
-
-### Raw distance measure
-
-The raw distance measure, denoted by $wpd_{raw}$, is computed after combining all the weighted distance measures appropriately.
+There are a total of ${K \choose 2}J$ between-facet distances, and ${J \choose 2}K$ within-facet distances if they are ordered and $K(J-1)$ within-facet distances if they are unordered.
+
+### Tuning parameter {-}
+
+For displays with $m>1$ granularities, we can use a tuning parameter to specify the relative weight given to each granularity.
+In general, the tuning parameters should be chosen such that $\sum_{i=1}^m \lambda_i = 1$.
+
+Following the general principles of Gestalt theory, we wish to weight more heavily granularities that are plotted closer together.
+For $m=2$ we choose  $\lambda_x = \frac{2}{3}$ for the granularity on the x-axis and $\lambda_f = \frac13$ for the granularity mapped to facets, giving a relative weight of $2:1$ for within-facet to between-facet distances.
+No human experiment has been conducted to justify this ratio.
+Specifying $\lambda_x>0.5$ will weight within-facet distances more heavily, while $\lambda_x <0.5$ would weight the between-facet distances more heavily.
+(See the supplements for more details.).
+
+### Raw distance measure {-}
+
+The raw distance measure, denoted by $\wpdsub{raw}$, is computed after combining all the weighted distance measures appropriately.
 First, NQT is performed on the measured variable $v_t$ to obtain $v^*_t$ (_data transformation_).
@@
 This is repeated for all pairs of categories of the form $(a_{j} b_{k}, a_{j'}b_{k'}): \{a_j: j = 1, 2, \dots, J\}, B = \{ b_k: k = 1, 2, \dots, K\}$.
-The pairwise distances between pairs $(a_{j} b_{k}, a_{j'}b_{k'})$  denoted by $d_{(jk, j'k')} = JSD(q_{jk}, q_{j'k'})$ is computed (_distance between distributions_).
-The pairwise distances (_Within-facet and between-facet_) are transformed using a suitable _tuning parameter_ ($0<\lambda<1$) depending on if they are within-facet($d_w$) or between-facets($d_b$) as follows:
+The pairwise distances between pairs $(a_{j} b_{k}, a_{j'}b_{k'})$ denoted by $d_{(jk, j'k')} = JSD(q_{jk}, q_{j'k'})$ are computed (_distance between distributions_).
+The pairwise distances (_within-facet and between-facet_) are transformed using a suitable _tuning parameter_ ($0<\lambda<1$) depending on if they are within-facet($d_w$) or between-facets($d_b$) as follows:
 \begin{equation}\label{def:raw-wpd}
@@
     \begin{cases}
-\lambda d_{(jk), (j'k')},& \text{if } d = d_w\\
-(1-\lambda)  d_{(jk), (j'k')},              & \text{if } d = d_b\\
+      \lambda d_{(jk), (j'k')},& \text{if } d = d_w;\\
+      (1-\lambda) d_{(jk), (j'k')},       & \text{if } d = d_b.
     \end{cases}
 \end{equation}
-
-\noindent The $wpd_{raw}$ is then computed as $$wpd = max_{j, j', k, k'}(d*_{(jk), (j'k')}) \forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}$$
-
-\noindent The statistic "maximum" is chosen to combine the weighted pairwise distances since the distance measure is aimed at capturing the maximum variation of the measured variable within a panel.
+The $\wpdsub{raw}$ is then computed as
+$$
+  \wpdsub{raw} = \max_{j, j', k, k'}(d*_{(jk), (j'k')}) \qquad\forall j, j' \in \{1, 2, \dots, J\},\quad k, k' \in \{1, 2, \dots, K\}
+$$
+The statistic "maximum" is chosen to combine the weighted pairwise distances since the distance measure is aimed at capturing the maximum variation of the measured variable within a panel.
 The statistic "maximum" is, however, affected by the number of comparisons (resulting pairwise distances).
-For example, for a $(2, 3)$ panel, there are $6$ possible subsets of obervations corresponding to the combinations $(a_1, b_1), (a_1, b_2), (a_1, b_3), (a_2 ,b_1), (a_2 ,b_2), (a_2, b_3)$, whereas for a $(2, 2)$ panel, there are only $4$ possible subsets $(a_1, b_1), (a_1, b_2), (a_2 ,b_1), (a_2 ,b_2)$.
+For example, for a $(2, 3)$ panel, there are $6$ possible subsets of observations corresponding to the combinations $(a_1, b_1), (a_1, b_2), (a_1, b_3), (a_2 ,b_1), (a_2 ,b_2), (a_2, b_3)$, whereas for a $(2, 2)$ panel, there are only $4$ possible subsets $(a_1, b_1), (a_1, b_2), (a_2 ,b_1), (a_2 ,b_2)$.
 Consequently, the measure would have higher values for the panel $(2, 3)$ as compared to $(2, 2)$, since maximum is taken over higher number of pairwise distances.
 
-### Adjusting for the number of comparisons {#sec:norm-wpd}
+### Adjusting for the number of comparisons {-}
 
 Ideally, it is desired that the proposed distance measure takes a higher value only if there is a significant difference between distributions across categories, and not because the number of categories $J$ or $K$ is high.
-That is, under designs like $D_{null}$, their distribution should not differ for a different number of categories.
+That is, under designs like $\Dnull$, their distribution should not differ for a different number of categories.
 Only then the distance measure could be compared across panels with different levels.
 This calls for an adjusted measure, which normalizes for the different number of comparisons.
-We denote it by $wpd$.
+
 Two approaches for adjusting the number of comparisons are discussed, both of which are substantiated using simulations.
-The first one defines an adjusted measure $wpd_{perm}$ based on the permutation method to remove the effect of different comparisons.
-The second approach fits a model to represent the relationship between $wpd_{raw}$ and the number of comparisons and defines the adjusted measure ($wpd_{glm}$) as the residual from the model.
-
-_Permutation approach_
+The first one defines an adjusted measure $\wpdsub{perm}$ based on the permutation method to remove the effect of different comparisons.
+The second approach fits a model to represent the relationship between $\wpdsub{raw}$ and the number of comparisons and defines the adjusted measure ($\wpdsub{glm}$) as the residual from the model.
+
+### _Permutation approach_ {-}
 
@@
 This method accomplishes a different goal of finding the null distribution for different groups (panels in our case) and standardizing the raw values using that distribution.
-The values of $wpd_{raw}$ is computed on many ($nperm$) permuted data sets and stored in $wpd_{perm-data}$.
-Then $wpd_{perm}$ is computed as follows:
-
+The values of $\wpdsub{raw}$ is computed on many ($\nsub{perm}$) permuted data sets and stored in $\wpdsub{perm-data}$.
+Then $\wpdsub{perm}$ is computed as follows:
 \begin{align*}
-wpd_{perm} = \frac{(wpd_{raw} - \bar{wpd_{perm-data}})}{sd(wpd_{perm-data})}
+  \wpdsub{perm} = \frac{(\wpdsub{raw} - \text{mean}(\wpdsub{perm-data}))}{\text{sd}(\wpdsub{perm-data})},
 \end{align*}
-
-\noindent where $\bar{wpd_{perm-data}}$ and $sd(wpd_{perm-data})$ are the mean and standard deviation of $wpd_{perm-data}$ respectively.
-Standardizing  $wpd$ in the permutation approach ensures that the distribution of $wpd_{perm}$ under $D_{null}$ has the same $mean = 0$ and $\sigma^2_{perm} = 1$ across all comparisons.
-While this works successfully to make the location and scale similar across different $nx$ and $nfacet$, it is computationally heavy and time consuming, and hence less user friendly when being actually used in practice.
+where $\text{mean}(\wpdsub{perm-data})$ and $\text{sd}(\wpdsub{perm-data})$ are the mean and standard deviation of $\wpdsub{perm-data}$ respectively.
+Standardizing $\wpd$ in the permutation approach ensures that the distribution of $\wpdsub{perm}$ under $\Dnull$ has zero mean and unit variance across all comparisons.
+While this works successfully to make the location and scale similar across different $\nx$ and $\nf$, it is computationally heavy and time consuming, and hence less user-friendly.
 Hence, another approach to adjustment, with potentially less computational time, is proposed.
@@
 
-_Modeling approach_
-
-In this approach, a Gamma generalized linear model (GLM) for $wpd_{raw}$ is fitted with number of comparisons as the explanatory variable.
-Since, $wpd_{raw}$ is a Jensen-Shannon distance, it follows a Chi-square distribution (@Menendez1997-in), which is a special case of Gamma distribution.
-Furthermore, the mean response is bounded, since any JSD is bounded by $1$ given that base $2$ logarithm is used (@Lin1991-pt).
-Hence, by @Faraway2016-uk, an inverse link is used for the model, which is of the  form $y = a+b*log(z) + e$, where $y = wpd_{raw}$, $z = (nx*nfacet)$ is the number of groups and $e$ are idiosyncratic errors.
-Let $E(y) = \mu$ and $a + b*log(z) = g(\mu)$ where $g$ is the link function.
-Then $g(\mu)=  1/\mu$ and $\hat \mu  = 1/(\hat a + \hat b log(z))$.
-The residuals from this model $(y-\hat y) = (y-1/(\hat a + \hat b log(z)))$ would be expected to have no dependency on $z$.
-Thus, $wpd_{glm}$ is chosen as the residuals from this model and is defined as:
-$$wpd_{glm} = wpd_{raw} - 1/(\hat a + \hat b*log(nx*nfacet))$$
-The distribution of $wpd_{glm}$ under $D_{null}$ will have $mean = 0$, since it is the residuals from the model, and a constant variance $\sigma^2_{glm}$, which might not equal 1.
-
-_Combination approach_
-
-The simulation results (in Section \ref{sec:simulations}) show that the distribution of $wpd_{glm}$ under null is similar for high $nx$ and $nfacet$ (levels higher than $5$) and not so much for lower $nx$ and $nfacet$.
-Hence, a combination approach is proposed which chooses permutation approach for categories with smaller levels and modeling approach for categories with higher levels.
-This ensures that the computational load of the permutation approach is alleviated while maintaining similar null distribution across different categories.
+### _Modeling approach_ {-}
+
+In this approach, a Gamma generalized linear model (GLM) for $\wpdsub{raw}$ is fitted with the number of comparisons as the explanatory variable.
+Since, $\wpdsub{raw}$ is a Jensen-Shannon distance, it follows a Chi-square distribution [@Menendez1997-in], which is a special case of a Gamma distribution.
+Furthermore, the mean response is bounded, since any JSD is bounded by $1$ if a base $2$ logarithm is used [@Lin1991-pt].
+Hence, by @Faraway2016-uk, an inverse link is used for the model, which is of the form $y = a+b*\log(z) + e$, where $y = \wpdsub{raw}$, $z = (\nx*\nf)$ is the number of groups and $e$ are idiosyncratic errors.
+Let $\text{E}(y) = \mu$ and $a + b*\log(z) = g(\mu)$ where $g(\mu)= 1/\mu$ and $\hat \mu = 1/(\hat a + \hat b \log(z))$.
+The residuals from this model $(y-\hat y) = (y-1/(\hat a + \hat b \log(z)))$ would be expected to have no dependency on $z$.
+Thus, $\wpdsub{glm}$ is defined as the residuals from this model given by
+$$\wpdsub{glm} = \wpdsub{raw} - 1/(\hat a + \hat b*\log(\nx*\nf))$$
+The distribution of $\wpdsub{glm}$ under $\Dnull$ will have approximately zero mean and a constant variance (not necessarily 1).
+
+### _Combination approach_ {-}
+
+The simulation results (in Section \ref{sec:simulations}) show that the distribution of $\wpdsub{glm}$ under the null design is similar for high $\nx$ and $\nf$ (levels higher than $5$) but less so for lower values of $\nx$ and $\nf$.
+Hence, a combination approach is proposed where we use a permutation approach for categories with small numbers of levels, and a modeling approach for categories with higher numbers of levels.
+This ensures that the computational load of the permutation approach is alleviated while maintaining a similar null distribution across different categories.
 This approach, however, requires that the adjusted variables from the two approaches are brought to the same scale.
-We define $wpd_{glm-scaled} = wpd_{glm}*\sigma^2_{perm}/\sigma^2_{glm}$ as the transformed $wpd_{glm}$ with a similar scale as $wpd_{perm}$.
-The adjusted measure from the combination approach, denoted by $wpd$ is then defined as follows:
-
+We define $\wpdsub{glm-scaled} = \wpdsub{glm}*\sigma^2_{\text{perm}}/\sigma^2_{\text{glm}}$ as the transformed $\wpdsub{glm}$ with a similar scale as $\wpdsub{perm}$.
+The adjusted measure from the combination approach, denoted by $\wpd$ is then defined as follows:
 \begin{equation}
-wpd =
-\begin{cases}
-wpd_{perm},& \text{if } J, K <=5\\
-wpd_{glm-scaled}             & \text{otherwise}\\
+\wpd = \begin{cases}
+         \wpdsub{perm},       & \text{if $J, K \le 5$};\\
+         \wpdsub{glm-scaled}  & \text{otherwise}.\\
        \end{cases}
@@
 
-<!-- The distance measure $wpd$ between two cyclic granularities $A$ and $B$ is aimed to capture the strength of the structure by estimating the maximum within-group and between-group variations.
+<!-- The distance measure $\wpd$ between two cyclic granularities $A$ and $B$ is aimed to capture the strength of the structure by estimating the maximum within-group and between-group variations.
 Furthermore, -->
 
-<!-- The steps employed for computing $wpd$ is summarized as follows: -->
-
-<!-- The values of $wpd$ indeed depend upon the underlying distribution.
-This is also not desirable as the intended aim of $wpd$ is to capture differences in categories irrespective of the distribution from which the data is generated.
+<!-- The steps employed for computing $\wpd$ is summarized as follows: -->
+
+<!-- The values of $\wpd$ indeed depend upon the underlying distribution.
+This is also not desirable as the intended aim of $\wpd$ is to capture differences in categories irrespective of the distribution from which the data is generated.
 The steps employed for computing the distance measure is summarized as follows: -->
@@
 
-```{r distance-explain, fig.cap = "Within and between-facet distances shown for two cyclic granularities A and B, where A is mapped to x-axis and B is mapped to facets.
-The dotted lines represent the distances between different categories.
-Panel 1) and 2) show the between-facet distances.
-Panel 3) and 4) are used to illustrate within-facet distances when categories are un-ordered or ordered respectively.
-When categories are ordered, distances should only be considered for consecutive x-axis categories.
-Between-facet distances are distances between different facet levels for the same x-axis category, for example, distances between {($a_1$,$b_1$) and ($a_1$, $b_2$)} or {($a_1$,$b_1$) and ($a_1$, $b_3$)}."}
-
-```
-
 <!-- 5. Compute distribution of maximum distance ($M$) by shuffling the data $200$ times and finishing Steps1-4 in each case. Scale $M$ using the mean and sd of the distribution.
@@
 
-<!-- All of these distances are then aggregated by taking the maximum from these distances to obtain $wpd$. -->
+<!-- All of these distances are then aggregated by taking the maximum from these distances to obtain $\wpd$. -->
 
@@
 
-<!-- ## Properties of $wpd$ -->
-
-<!-- Simulations were carried out to explore the behavior of $wpd$ under the following factors that could potentially impact the values of $wpd$: $nx$, $nfacet$, $\lambda$, $\omega$, $dist$ (normal/non-normal distributions with different location and scale), $ntimes$, and $designs$ and results are presented in two parts.
-The dependence of $wpd$ on $nx$ and $nfacet$ under $D_{null}$ is presented here, which lays the foundation for the next section.
-The rest of the results that discuss the relationship of the $wpd$ with other factors is presented in details in the Supplementary section of the paper.
-They show that the designs $D_{var_f}$ and $D_{var_x}$ intersect at $\lambda = 0.5$ and hence for up-weighing designs of the form $D_{var_x}$, $\lambda = 0.67$ has been considered for computation of $wpd$ in the rest of the paper.
--->
-
-<!-- - $nx$ (number of levels of x-axis) -->
-<!-- - $nfacet$ (number of levels of facets) -->
+<!-- ## Properties of $\wpd$ -->
+
+<!-- Simulations were carried out to explore the behavior of $\wpd$ under the following factors that could potentially impact the values of $\wpd$: $\nx$, $\nf$, $\lambda$, $\omega$, $dist$ (normal/non-normal distributions with different location and scale), $ntimes$, and $designs$ and results are presented in two parts.
+The dependence of $\wpd$ on $\nx$ and $\nf$ under $\Dnull$ is presented here, which lays the foundation for the next section.
+The rest of the results that discuss the relationship of the $\wpd$ with other factors is presented in details in the Supplementary section of the paper.
+They show that the designs $\Df$ and $D_x$ intersect at $\lambda = 0.5$ and hence for up-weighing designs of the form $D_x$, $\lambda = 0.67$ has been considered for computation of $\wpd$ in the rest of the paper.
+-->
+
+<!-- - $\nx$ (number of levels of x-axis) -->
+<!-- - $\nf$ (number of levels of facets) -->
 <!-- - $\lambda$ (tuning parameter) -->
@@
 <!-- - $n$ (sample size for each combination of categories) -->
-<!-- - $designs$ ($D_{null}$, $D_{var_f}$, $D_{var_x}$ and $D_{var_{all}}$) -->
-
-<!-- - $nsim$ (number of simulations) -->
-<!-- - $nperm$ (number of permutations of data)   -->
+<!-- - $designs$ ($\Dnull$, $\Df$, $D_x$ and $D_{fx}$) -->
+
+<!-- - $\nsub{sim}$ (number of simulations) -->
+<!-- - $\nsub{perm}$ (number of permutations of data)  -->
 
@@
 
-<!-- Observations are generated from a Gamma(2,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
+<!-- Observations are generated from a Gamma(2,1) distribution for each combination of $\nx$ and $\nf$ from the following sets: $nx = \nf = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
 Each combination is being referred to as a _panel_.
-That is, data is being generated for each of the panels $\{nx = 2, nfacet = 2\}, \{nx = 2, nfacet = 3\}, \{nx = 2, nfacet = 5\},  \dots, \{nx = 50, nfacet = 31\}, \{nx = 50, nfacet = 50\}$.
+That is, data is being generated for each of the panels $\{nx = 2, \nf = 2\}, \{nx = 2, \nf = 3\}, \{nx = 2, \nf = 5\}, \dots, \{nx = 50, \nf = 31\}, \{nx = 50, \nf = 50\}$.
 For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
-That is, if we consider the panel $\{nx = 2, nfacet = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
+That is, if we consider the panel $\{nx = 2, \nf = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
 The values -->
-<!-- of $wpd$ is obtained for each of the panels.
-This design corresponds to $D_{null}$ as each combination of categories in a panel are drawn from the same distribution.
-Furthermore, the data is simulated for each of the panels $nsim=200$ times, so that the distribution oaf $wpd$ under $D_{null}$ could be observed.
-$wpd_{l, s}$ denotes the value of $wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.
+<!-- of $\wpd$ is obtained for each of the panels.
+This design corresponds to $\Dnull$ as each combination of categories in a panel are drawn from the same distribution.
+Furthermore, the data is simulated for each of the panels $\nsub{sim}=200$ times, so that the distribution oaf $\wpd$ under $\Dnull$ could be observed.
+$wpd_{l, s}$ denotes the value of $\wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.
 -->
@@
 
-<!-- Figure \ref{fig:raw} shows the distribution of $wpd$ plotted across different $nx$ and $nfacet$ categories.
-Since under $D_{null}$, there is no difference in distributions across different categories, we expect the distance measure $wpd$ to reflect that as well and have the same distribution across categories.
+<!-- Figure \ref{fig:raw} shows the distribution of $\wpd$ plotted across different $\nx$ and $\nf$ categories.
+Since under $\Dnull$, there is no difference in distributions across different categories, we expect the distance measure $\wpd$ to reflect that as well and have the same distribution across categories.
 But Figure \ref{fig:raw} shows that both the location and scale of the distributions change across panels.
-This is not desirable under $D_{null}$ as it would mean comparisons of $wpd$ values is not appropriate across different $nx$ and $nfacet$.
-Figure \ref{fig:quadratic} shows how the median of $wpd$ varies with the total number of distances $nx*nfacet$ for each panel.
-The median increases abruptly for lower values of $nx*nfacet$ and slowly for higher $nx*nfacet$.
--->
-
-<!-- Furthermore, simulation results also show that the values of $wpd$ indeed depend upon the underlying distribution.
-This is also not desirable as the intended aim of $wpd$ is to capture differences in categories irrespective of the distribution from which the data is generated.
+This is not desirable under $\Dnull$ as it would mean comparisons of $\wpd$ values is not appropriate across different $\nx$ and $\nf$.
+Figure \ref{fig:quadratic} shows how the median of $\wpd$ varies with the total number of distances $nx*\nf$ for each panel.
+The median increases abruptly for lower values of $nx*\nf$ and slowly for higher $nx*\nf$.
+-->
+
+<!-- Furthermore, simulation results also show that the values of $\wpd$ indeed depend upon the underlying distribution.
+This is also not desirable as the intended aim of $\wpd$ is to capture differences in categories irrespective of the distribution from which the data is generated.
 -->
@@
 <!-- last writeup -->
-<!-- In the linear model approach, $wpd\in R$ was assumed, whereas, $wpd$ is a Jensen-Shannon Distance (JSD) and lies between 0 and 1 (@JSD).
+<!-- In the linear model approach, $wpd\in R$ was assumed, whereas, $\wpd$ is a Jensen-Shannon Distance (JSD) and lies between 0 and 1 [@JSD].
 Furthermore, JSD follows a Chi-square distribution, which is a special case of Gamma distribution.
@@
 The residuals from this model $(y-\hat y) = (y-1/(\hat a + \hat b log(z)))$ would be expected to have no dependency on $z$.
-Thus, $wpd_{glm}$ is chosen as the residuals from this model and is defined as: -->
-<!-- $wpd_{glm} = wpd - 1/(\hat a + \hat b*log(nx*nfacet))$. -->
+Thus, $\wpdsub{glm}$ is chosen as the residuals from this model and is defined as: -->
+<!-- $\wpdsub{glm} = wpd - 1/(\hat a + \hat b*log(nx*\nf))$. -->
 
@@
 <!-- use later -->
-<!-- The measure $wpd$ could potentially lead to comparison of the measure across different panels and also help distinguishing the interesting panels from a data set.
+<!-- The measure $\wpd$ could potentially lead to comparison of the measure across different panels and also help distinguishing the interesting panels from a data set.
 We discuss two approaches for normalization, both of which are substantiated using simulations.
@@
 
-<!-- The transformed ${wpd}$ which is normalized for the values of $nx$ and $nfacet$ is denoted by $wpd$.
-Two approaches have been employed - the first one involves a permutation method to make the distribution of the transformed $wpd$ similar for different comparisons and the second one fits a model to represent the relationship between the two variables and defines $wpd$ as the residual of the model.
+<!-- The transformed ${wpd}$ which is normalized for the values of $\nx$ and $\nf$ is denoted by $\wpd$.
+Two approaches have been employed - the first one involves a permutation method to make the distribution of the transformed $\wpd$ similar for different comparisons and the second one fits a model to represent the relationship between the two variables and defines $\wpd$ as the residual of the model.
 -->
@@
 
-<!-- Let $\{nx_{i}, i = 1, 2, \dots, nx\}$, $\{nfacet_{j}, j = 1, 2, \dots, nfacet\}$ be the set of x-axis and facet categories respectively.
-Each combination of $nx_{i}$ and $nfacet_{j}$is being referred to as a _panel_.
-Then the total number of panel is $nx*nfacet$.
-Let the total number of pairwise distances that could result in each panel be $\{z_k, k = 1, 2 , \dots, nx*nfacet\}$.
-Here, $\{z_1 = nx_1*nfacet_1\}$, $\{z_2 = nx_2*nfacet_2\}$ and $\{z_k = nx*nfacet\}$.
-Now, let $\{x_{k,l}, k = 1, 2, \dots, nx*nfacet, l = 1, 2, \dots, nsim\}$ denote the values of $wpd_{raw}$ obtained from the simulation study for $k^{th}$ panel in the $i^{th}$ simulation.
-Hence, for each of those $k$ panel, we have $nsim$ values of $wpd_{raw}$.
+<!-- Let $\{nx_{i}, i = 1, 2, \dots, nx\}$, $\{\nf_{j}, j = 1, 2, \dots, \nf\}$ be the set of x-axis and facet categories respectively.
+Each combination of $nx_{i}$ and $\nf_{j}$is being referred to as a _panel_.
+Then the total number of panel is $nx*\nf$.
+Let the total number of pairwise distances that could result in each panel be $\{z_k, k = 1, 2 , \dots, nx*\nf\}$.
+Here, $\{z_1 = nx_1*\nf_1\}$, $\{z_2 = nx_2*\nf_2\}$ and $\{z_k = nx*\nf\}$.
+Now, let $\{x_{k,l}, k = 1, 2, \dots, nx*\nf, l = 1, 2, \dots, \nsub{sim}\}$ denote the values of $\wpdsub{raw}$ obtained from the simulation study for $k^{th}$ panel in the $i^{th}$ simulation.
+Hence, for each of those $k$ panel, we have $\nsub{sim}$ values of $\wpdsub{raw}$.
 -->
@@
 
-<!-- This section reports the results of a simulation study that was carried out to evaluate the behavior of $wpd$ under different designs and other potential factors.
-The behavior of $wpd$ is explored in designs where there is in fact difference in distribution between facet categories ($D_{var_f}$) or across x-categories ($D_{var_x}$) or both ($D_{var_{all}}$).
-Using $\omega =  \{1, 2, \dots, 10\}$ and $\lambda = seq(from  = 0.1, to = 0.9, by = 0.05)$, observations are drawn from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet =  \{2, 3, 5, 7, 14, 20, 31, 50\}$.
+<!-- This section reports the results of a simulation study that was carried out to evaluate the behavior of $\wpd$ under different designs and other potential factors.
+The behavior of $\wpd$ is explored in designs where there is in fact difference in distribution between facet categories ($\Df$) or across x-categories ($D_x$) or both ($D_{fx}$).
+Using $\omega = \{1, 2, \dots, 10\}$ and $\lambda = seq(from = 0.1, to = 0.9, by = 0.05)$, observations are drawn from a N(0,1) distribution for each combination of $\nx$ and $\nf$ from the following sets: $nx = \nf = \{2, 3, 5, 7, 14, 20, 31, 50\}$.
 $ntimes = 500$ is assumed for this setup as well.
-Furthermore, to generate different distributions across different combination of facet and x levels, the following method is deployed - suppose the distribution of the combination of first levels of $x$ and $facet$ category is $N(\mu,\sigma)$ and $\mu_{jk}$ denotes the mean of the combination $(a_jb_k)$, then $\mu_{j.} = \mu + j\omega$ (for design $D_{var_x}$) and $\mu_{.k} = \mu + k\omega$ (for design $D_{var_f}$).
+Furthermore, to generate different distributions across different combination of facet and x levels, the following method is deployed - suppose the distribution of the combination of first levels of $x$ and $facet$ category is $N(\mu,\sigma)$ and $\mu_{jk}$ denotes the mean of the combination $(a_jb_k)$, then $\mu_{j.} = \mu + j\omega$ (for design $D_x$) and $\mu_{.k} = \mu + k\omega$ (for design $\Df$).
 -->
@@
 <!-- The tabulated values and graphical representations of the simulation results are provided in the Supplementary paper.
-The learning from the simulations are as follows: The values of $wpd$ is least for $D_{null}$, followed by -->
-<!-- $D_{var_f}$, $D_{var_x}$ and $D_{var_{all}}$.
-This is a desirable result since the measure $wpd$ was designed such that this relationship holds.
-Furthermore, the distribution of the measure $wpd$ does not change for different facet and x categories.
-The distribution of $wpd$ looks similar with at least the mean and standard of the distributions being uniform across panels.
-This means $wpd$ could be used to measure differences in distribution across panels.
+The learning from the simulations are as follows: The values of $\wpd$ is least for $\Dnull$, followed by -->
+<!-- $\Df$, $D_x$ and $D_{fx}$.
+This is a desirable result since the measure $\wpd$ was designed such that this relationship holds.
+Furthermore, the distribution of the measure $\wpd$ does not change for different facet and x categories.
+The distribution of $\wpd$ looks similar with at least the mean and standard of the distributions being uniform across panels.
+This means $\wpd$ could be used to measure differences in distribution across panels.
 Also, note that since the data is processed using normal-quantile-transform, this measure is independent of the initial distribution of the underlying data and hence is also comparable across different data sets.
-This is valid for the case when sample size $ntimes$ for each combination of categories is at least 30 and  $nperm$ used for computing $wpd$ is at least 100.
-More detailed results about the properties of $wpd$ could be found in the Supplementary paper.
+This is valid for the case when sample size $ntimes$ for each combination of categories is at least 30 and $\nsub{perm}$ used for computing $\wpd$ is at least 100.
+More detailed results about the properties of $\wpd$ could be found in the Supplementary paper.
 -->
@@
 In this section, a selection criterion to choose significant harmonies is provided, thereby eliminating all harmonies that exhibit complete randomness in the measured variable.
-The distance measure $wpd$ is used as a test statistic to test the null hypothesis that no harmony/cyclic granularity is significant.
+The distance measure $\wpd$ is used as a test statistic to test the null hypothesis that no harmony/cyclic granularity is significant.
 We select only those harmonies/cyclic granularities for which the test fails.
@@
 
-A threshold and consequently a selection criterion is chosen using the notion of Randomization tests (@edgington2007randomization).
-The data is permuted several times and $wpd$ is computed for each of the permuted data sets to obtain the sampling distribution of $wpd$ under the null hypothesis.
-If the null hypothesis is true, then $wpd$ obtained from the original data set would be a likely value in the sampling distribution.
-But in case the null hypothesis is not true, then it is less probable that $wpd$ obtained for the original data will be from the same distribution.
-This idea is utilized to come up with a threshold for selection, denoted by $wpd_{threshold}$, defined as the $99^{th}$ percentile of the sampling distribution.
-A harmony is selected if the value of $wpd$ for that harmony is greater than the chosen threshold.
+A threshold and consequently a selection criterion is chosen using the notion of Randomization tests [@edgington2007randomization].
+The data is permuted several times and $\wpd$ is computed for each of the permuted data sets to obtain the sampling distribution of $\wpd$ under the null hypothesis.
+If the null hypothesis is true, then $\wpd$ obtained from the original data set would be a likely value in the sampling distribution.
+But in case the null hypothesis is not true, then it is less probable that $\wpd$ obtained for the original data will be from the same distribution.
+This idea is utilized to come up with a threshold for selection, denoted by $\wpdsub{threshold}$, defined as the $99^{th}$ percentile of the sampling distribution.
+A harmony is selected if the value of $\wpd$ for that harmony is greater than the chosen threshold.
 The detailed algorithm for choosing a threshold and selection procedure (for two cyclic granularities) is listed as follows:
 
-<!-- The selection criterion is stated as follows: for $(i \in {1, 2, \dots, H_{N_C}})$, select $H_i$ if $wpd_i > wpd_{threshold}$, else reject. -->
+<!-- The selection criterion is stated as follows: for $(i \in {1, 2, \dots, H_{N_C}})$, select $H_i$ if $wpd_i > \wpdsub{threshold}$, else reject. -->
 
@@
 
-- **Output:** Harmony pairs $(A, B)$ for which $wpd$ is significant.
+- **Output:** Harmony pairs $(A, B)$ for which $\wpd$ is significant.
 
@@
 
-2. Given the measured variable; $\{v_t: t=0, 1, 2, \dots, T-1\}$, $wpd$ is computed and is represented by $wpd^{A, B}_{obs}$.
+2. Given the measured variable; $\{v_t: t=0, 1, 2, \dots, T-1\}$, $\wpd$ is computed and is represented by $\wpd^{A, B}_{obs}$.
 
@@
 
-4. $wpd$ is computed for the permuted sequence of the data and is represented by $wpd^{A, B}_{1}$.
+4. $\wpd$ is computed for the permuted sequence of the data and is represented by $\wpd^{A, B}_{1}$.
 
@@
 
-6. For each permutation, one $wpd^{A, B}_{i}$ is obtained. Define $wpd_{sample} = \{wpd^{A, B}_{1} wpd^{A, B}_{2}, \dots, wpd^{A, B}_{M}\}$.
-
-7. Repeat Steps (1-6) for all harmony pairs $(A, B) \in H_{N_C}$ and stored $wpd^{all}_{sample}$.
-
-8. $99^{th}$ percentiles of $wpd^{all}_{sample}$ is computed and stored in $wpd_{threshold99}$
-
-7. If $wpd^{A, B}_{obs} > wpd_{threshold99}$, harmony pair $(A, B)$ is selected, otherwise rejected.
-
-Similarly, a harmony pair $(A, B)$ could be selected if $wpd^{A, B}_{obs} > wpd_{threshold95}$ and $wpd^{A, B}_{obs} > wpd_{threshold90}$, where  $wpd_{threshold95}$ and $wpd_{threshold90}$ denote the $95^{th}$ and $90^{th}$ percentile of $wpd^{all}_{sample}$ respectively.
+6. For each permutation, one $\wpd^{A, B}_{i}$ is obtained. Define $\wpdsub{sample} = \{\wpd^{A, B}_{1} \wpd^{A, B}_{2}, \dots, \wpd^{A, B}_{M}\}$.
+
+7. Repeat Steps (1-6) for all harmony pairs $(A, B) \in H_{N_C}$ and stored $\wpdsub{sample}^{\text{all}}$.
+
+8. $99^{th}$ percentiles of $\wpdsub{sample}^{\text{all}}$ is computed and stored in $\wpdsub{threshold99}$
+
+7. If $\wpd^{A, B}_{obs} > \wpdsub{threshold99}$, harmony pair $(A, B)$ is selected, otherwise rejected.
+
+Similarly, a harmony pair $(A, B)$ could be selected if $\wpd^{A, B}_{obs} > \wpdsub{threshold95}$ and $\wpd^{A, B}_{obs} > \wpdsub{threshold90}$, where $\wpdsub{threshold95}$ and $\wpdsub{threshold90}$ denote the $95^{th}$ and $90^{th}$ percentile of $\wpdsub{sample}^{\text{all}}$ respectively.
 A harmony selected using $99^{th}$, $95^{th}$ and $90^{th}$ threshold are tagged as \*\*\*, \*\*, \* respectively.
 
-## Ranking
-
-The distribution of $wpd$ is expected to be similar for all harmonies under the null hypothesis, since they have been adjusted for different number of categories for the harmonies or underlying distribution of the measured variable.
-Hence, the values of $wpd$ for different harmonies are comparable and can be used to rank the significant harmonies.
-A higher value of $wpd$ for a harmony indicates that higher maximum variation in the measured variable is captured through that harmony.
-Figure \ref{fig:null4by2} presents the results of $wpd$ from the illustrative designs in Section \ref{sec:computation-wpd}.
-The value of $wpd$ under null design (a) is the least, followed by (b), (c) and (d).
-This aligns with the principle of $wpd$, which is expected to have lowest value for null designs and highest for designs of the form $D_{var_{all}}$ (d).
-Moreover, note the relative differences in $wpd$  values between (b) and (c).
+## Ranking {#sec:ranking}
+
+The distribution of $\wpd$ is expected to be similar for all harmonies under the null hypothesis, since they have been adjusted for different number of categories for the harmonies or underlying distribution of the measured variable.
+Hence, the values of $\wpd$ for different harmonies are comparable and can be used to rank the significant harmonies.
+A higher value of $\wpd$ for a harmony indicates that higher maximum variation in the measured variable is captured through that harmony.
+Figure \ref{fig:null4by2} presents the results of $\wpd$ from the illustrative designs in Section \ref{sec:computation-wpd}.
+The value of $\wpd$ under null design (a) is the least, followed by (b), (c) and (d).
+This aligns with the principle of $\wpd$, which is expected to have lowest value for null designs and highest for designs of the form $\Dfx$ (d).
+Moreover, note the relative differences in $\wpd$ values between (b) and (c).
 The value of the tuning parameter $\lambda$ is set to $0.67$, which has resulted in giving more emphasis to differences in x-axis categories.
-Again consider \ref{fig:onegran-new}(a) and \ref{fig:onegran-new}(b) with a $wpd$ value of 20.5 and 145 respectively.
+Again consider \ref{fig:onegran-new}(a) and \ref{fig:onegran-new}(b) with a $\wpd$ value of 20.5 and 145 respectively.
 This is because there is more gradual increase across hours of the day than months of the year.
-If order of the categories is not considered, they result in a $wpd$ value of $97.8$ and $161$ respectively, which follows from the fact that if we consider difference between any hours of the day, the magnitude will be much larger than if we consider difference between consecutive categories.
-Similarly, \ref{fig:onegran-new}(a) and (b) have $wpd$ values of   $110.79$ and $125.82$ respectively.
+If order of the categories is not considered, they result in a $\wpd$ value of $97.8$ and $161$ respectively, which follows from the fact that if we consider difference between any hours of the day, the magnitude will be much larger than if we consider difference between consecutive categories.
+Similarly, \ref{fig:onegran-new}(a) and (b) have $\wpd$ values of  $110.79$ and $125.82$ respectively.
 The ranking implies that the distributional differences are more prominent for the second household, as is also seen from the bigger fluctuations in the $90^{th}$ percentile than the first household.
@@
 <!-- A randomization test involves calculating a test statistic, randomly shuffling the data and calculating the test statistic several times to obtain a distribution of the test statistic.
-But we will use this procedure to obtain a threshold such that harmony pairs with a $wpd$ value higher than this threshold will only be considered significant.
+But we will use this procedure to obtain a threshold such that harmony pairs with a $\wpd$ value higher than this threshold will only be considered significant.
 The process of choosing a threshold is described as follows: -->
 
-<!-- to test if there is any interesting pattern captured by the harmonies, which essentially implies if $wpd$ is significantly different from zero.
-The percentages of times the $wpd$ obtained from the permuted data is greater than or equal to the observed $wpd$ is the p-value.
+<!-- to test if there is any interesting pattern captured by the harmonies, which essentially implies if $\wpd$ is significantly different from zero.
+The percentages of times the $\wpd$ obtained from the permuted data is greater than or equal to the observed $\wpd$ is the p-value.
 The randomization test is described as follows: -->
@@
 This method is based on the generation of randomly chosen reassignments (permutations) of the data across different cyclic granularities and the computation of -->
-<!-- $wpd$ for each of these reassignments. -->
+<!-- $\wpd$ for each of these reassignments. -->
 
@@
 This method is based on the generation of randomly chosen reassignments (permutations) of the data across different cyclic granularities and the computation of -->
-<!-- $wpd$ for each of these reassignments.
-The percentages of times the theoretical distribution greater than or equal to the respective observed $wpd$ values are calculated and are used to obtain the P value.
+<!-- $\wpd$ for each of these reassignments.
+The percentages of times the theoretical distribution greater than or equal to the respective observed $\wpd$ values are calculated and are used to obtain the P value.
 The procedure for the permutation test is: -->
@@
 For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
-The values of $wpd$ is obtained for each of the panels for the designs $D_{null}$, $D_{var_x}$, $D_{var_f}$ and $D_{var_{all}}$.
-$wpd_{threshold}$ is computed from all of these panels together and the number of times a harmony pair $(A, B) \in H_{N_C}$ is selected when in fact it was of the design $D_{null}$ is noted.
+The values of $\wpd$ is obtained for each of the panels for the designs $\Dnull$, $D_x$, $\Df$ and $D_{fx}$.
+$\wpdsub{threshold}$ is computed from all of these panels together and the number of times a harmony pair $(A, B) \in H_{N_C}$ is selected when in fact it was of the design $\Dnull$ is noted.
 This entire process is repeated for several null data sets to see the number of times any harmony pair $(A, B) \in H_{N_C}$ is selected under null.
@@
 
-```{r plot-all-new3, fig.cap = "$wpd$ values for the four illustrative designs are presented here.
-As expected, the value of $wpd$ under null design is the least (a), followed by (b, c and d).
-Moreover, the relative difference is interesting as c is closer to d than b, since the differences between x categories are up-weighed by design.", dependson= "null4by2"}
+(ref:plot-all-new3) $\wpd$ values for the four illustrative designs are presented here.
+As expected, the value of $\wpd$ under null design is the least (a), followed by (b, c and d).
+Moreover, the relative difference is interesting as c is closer to d than b, since the differences between x categories are up-weighed by design.
+
+```{r plot-all-new3, fig.cap = "(ref:plot-all-new3", dependson= "null4by2"}
 
@@
 
-\noindent _Simulation design_
-
-$m=1$
+### _Simulation design_ {-}
+
+\noindent $m=1$
 
@@
 $ntimes = 500$ observations are drawn for each combination of the categories, that is, for a panel with $nx=3$, $500$ observations are simulated for each of the categories.
-This design corresponds to $D_{null}$ as each combination of categories in a panel are drawn from the same distribution.
-Furthermore, the data is simulated for each of the categories $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
-The values of $wpd$ is obtained for each of the panels.
-$wpd_{l, s}$ denotes the value of $wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.
-
-$m=2$  
-\noindent Similarly, observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$.
+This design corresponds to $\Dnull$ as each combination of categories in a panel are drawn from the same distribution.
+Furthermore, the data is simulated for each of the categories $\nsub{sim}=200$ times, so that the distribution of $\wpd$ under $\Dnull$ could be observed.
+The values of $\wpd$ is obtained for each of the panels.
+$wpd_{l, s}$ denotes the value of $\wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.
+
+\noindent $m=2$
+
+\noindent Similarly, observations are generated from a N(0,1) distribution for each combination of $\nx$ and $\nf$ from the following sets: $nx = \nf = \{2, 3, 5, 7, 14, 20, 31, 50\}$.
 That is, data is being generated for each of the panels $(2, 2), (2, 3), (2, 5) \dots, (50, 31), (50, 50)$.
@@
 
-\noindent _Results_
+### _Results_ {-}
 
 Figure \ref{fig:raw} shows that both the location and scale of the distributions change across panels.
-This is not desirable under $D_{null}$ as it would mean comparisons of $wpd$ values is not appropriate across different $nx$ and $nfacet$.
-Table \ref{tab:glm-tab} gives the summary of the generalized linear model to capture the relationship between $wpd_{raw}$ and number of comparisons.
-For example, the model considered for $m = 2$ is $wpd_{l,s} = 23.4 - 0.96*log(nx * nfacet)) + e$.
+This is not desirable under $\Dnull$ as it would mean comparisons of $\wpd$ values is not appropriate across different $\nx$ and $\nf$.
+Table \ref{tab:glm-tab} gives the summary of the generalized linear model to capture the relationship between $\wpdsub{raw}$ and number of comparisons.
+For example, the model considered for $m = 2$ is $wpd_{l,s} = 23.4 - 0.96*log(nx * \nf)) + e$.
 The intercepts and slopes are similar independent of the starting distributions (see supplementary paper for details) and hence the coefficients are shown for the case when observations are drawn from a N(0, 1) distribution.
-Figure \ref{fig:dist-new-same-scale-link} shows the distribution of $wpd_{perm}$ and $wpd_{glm-scaled}$ in the same scale to show that a combination approach could be used for higher values of levels to alleviate the computational time of permutation approach.
-
-```{r raw, fig.cap = "Distribution of $wpd_{raw}$ is plotted across different $nx$ and $nfacet$ categories under $D_{null}$ through density and rug plots.
+Figure \ref{fig:dist-new-same-scale-link} shows the distribution of $\wpdsub{perm}$ and $wpd_{glm-scaled}$ in the same scale to show that a combination approach could be used for higher values of levels to alleviate the computational time of permutation approach.
+
+(ref:raw) Distribution of $\wpdsub{raw}$ is plotted across different $\nx$ and $\nf$ categories under $\Dnull$ through density and rug plots.
 Both location (blue line) and scale (orange marks) of the distribution shifts for different panels.
-This is not desirable since under null design, the distribution  is not expected to capture any differences."}
+This is not desirable since under null design, the distribution is not expected to capture any differences.
+
+```{r raw, fig.cap = "(ref:raw"}
 ```
@@
 
-```{r dist-new-same-scale-link, fig.cap = "The distribution of $wpd_{perm}$ and $wpd_{glm-scaled}$ are overlaid to compare the location and scale across different $nx$ and $nfacet$.
-$wpd_{norm}$ takes the value of $wpd_{perm}$ for lower levels, and $wpd_{glm-scaled}$ for higher levels to to alleviate the problem of computational time in permutation approaches.
-This is possible as the distribution of the adjusted measure looks similar for both appraches for higher levels."}
+(ref:dist-new-same-scale-link) The distribution of $\wpdsub{perm}$ and $\wpdsub{glm-scaled}$ are overlaid to compare the location and scale across different $\nx$ and $\nf$.
+$\wpdnorm$ takes the value of $\wpdsub{perm}$ for lower levels, and $\wpdsub{glm-scaled}$ for higher levels to to alleviate the problem of computational time in permutation approaches.
+This is possible as the distribution of the adjusted measure looks similar for both approaches for higher levels.
+
+```{r dist-new-same-scale-link, fig.cap = "(ref:dist-new-same-scale-link"}
 ```
@@
 
-\noindent _Simulation design_
-
-Observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = \{3, 7, 14\}$ and $nfacet = \{2, 9, 10\}$.
+### _Simulation design_ {-}
+
+Observations are generated from a N(0,1) distribution for each combination of $\nx$ and $\nf$ from the following sets: $nx = \{3, 7, 14\}$ and $\nf = \{2, 9, 10\}$.
 This would result in 9 panels, viz, $(3, 2), (3, 9), (3, 10), \dots, (14,9), (14, 10)$.
 Few experiments were conducted.
-In the first scenario, data for all panels are simulated using the null design  $D_{null}$.
-In other scenarios, data simulated from the panel $(14, 2)$ and $(3, 10)$ are considered under $D_{vary_{all}}$.
+In the first scenario, data for all panels are simulated using the null design $\Dnull$.
+In other scenarios, data simulated from the panel $(14, 2)$ and $(3, 10)$ are considered under $\Dfx$.
 Moreover, $\omega = \{0.5, 2, 5\}$ are considered to examine if the proposed test is able to capture subtle differences and non-subtle differences when we shift from the null design.
 
-<!-- In the last scenario, we consider the panel $(3, 2), (7,9), (14, 10)$ to be under $D_{null}$, the panels $(7, 2), (14, 9)$ to be under $D_{var_f}$.
-$(14, 2), (3, 10)$ under $D_{var_x}$ and the rest under $D_{var_{null}}$.
+<!-- In the last scenario, we consider the panel $(3, 2), (7,9), (14, 10)$ to be under $\Dnull$, the panels $(7, 2), (14, 9)$ to be under $\Df$.
+$(14, 2), (3, 10)$ under $D_x$ and the rest under $\Dvar{{null}}$.
 This is done to check if the consequent ranking procedure leads to designs like $D_{vary_{all}}$ to be chosen first followed by $D_{vary_{all}}$.
@@
 
-\noindent _Results_
-
-For the first scenario, size of the test is obtained as $0.1$ with $wpd_{threshold99}$ as the threshold.
-This implies that the proportion of times a panel is rejected when it is under $D_{null}$ is $0.1$.
+### _Results_ {-}
+
+For the first scenario, size of the test is obtained as $0.1$ with $\wpdsub{threshold99}$ as the threshold.
+This implies that the proportion of times a panel is rejected when it is under $\Dnull$ is $0.1$.
 The level of significance for each test is 1% (as a result of choosing $99^{th}$ percentile as the threshold) and we have $9$ multiple tests.
@@
  geom_histogram(data = all_data, aes(x = wpd)) +
-  geom_vline(data = data_summary, aes(xintercept = p_value),colour = "red") +
+ geom_vline(data = data_summary, aes(xintercept = p_value),color = "red") +
  facet_grid(x_levels~facet_levels)
@@
 
-Simulation studies were carried out to study the behavior of $wpd$, build the normalization method as well as compare and evaluate different normalization approaches.
+Simulation studies were carried out to study the behavior of $\wpd$, build the normalization method as well as compare and evaluate different normalization approaches.
 R version 4.0.1 (2020-06-06) is used with the platform: x86_64-apple-darwin17.0 (64-bit) running under: macOS Mojave 10.14.6 and MonaRCH, which is a next-generation High Power Computing (HPC) Cluster, addressing the needs of the Monash HPC community.
@@
 
-The smart meter data set for eight households in Melbourne has been utilized to see the use of $wpd$ proposed in the paper.
-The data has been cleaned to be a `tsibble` (@wang2020tsibble) containing half-hourly electricity consumption from Jul-2019 to Dec-2019 for each of the households, which is procured by them by downloading their data from the energy supplier/retailer.
+The smart meter data set for eight households in Melbourne has been utilized to see the use of $\wpd$ proposed in the paper.
+The data has been cleaned to be a `tsibble` [@wang2020tsibble] containing half-hourly electricity consumption from Jul-2019 to Dec-2019 for each of the households, which is procured by them by downloading their data from the energy supplier/retailer.
 No behavioral pattern is likely to be discerned from the line graph of energy usage over the entire period, since the plot will have too many measurements squeezed in a linear representation.
@@
 
-_Choosing cyclic granularities of interest and removing clashes_
+### _Choosing cyclic granularities of interest and removing clashes_ {-}
 
@@
 Thus, $7$ cyclic granularities are considered to be of interest.
-The set consisting of pairs of cyclic granularities ($C_{N_C}$) will have $7_{P_2}=42$ elements which could be analyzed for detecting possible periodicities.
+The set consisting of pairs of cyclic granularities ($C_{N_C}$) will have $7\times 6=42$ elements which could be analyzed for detecting possible periodicities.
 The set of possible harmonies $H_{N_C}$ from $C_{N_C}$ are chosen by removing clashes using procedures described in [@Gupta2021-hd].
@@
 
-_Selecting and Ranking harmonies for all households_
-
-$wpd_{i}$ is computed on $v_{i, t}$ for all harmony pairs $\in H_{N_C}$ and for each households $i \in \{1, 2, \dots, 8\}$.
+### _Selecting and Ranking harmonies for all households_ {-}
+
+$\wpd_{i}$ is computed on $v_{i, t}$ for all harmony pairs $\in H_{N_C}$ and for each households $i \in \{1, 2, \dots, 8\}$.
 The harmony pairs are then arranged in descending order and highlighted with `***`, `**` and `*` corresponding to the $99^{th}$, $95^{th}$ and $90^{th}$ percentile threshold.
@@
 
-_Detecting patterns not apparent from linear display_
-
-\noindent Figure \ref{fig:dotplot-8} helps to compare households through the heatmap (a) across harmony pairs with the cyclic granularity mapped to x-axis and facet being plotted on the x-axis and y-axis of the heatmap.
-Here $dom$, $dow$, $wdwnd$ are abbreviations for day-of-month, day-of-week, weekday/weekend and so on.
-The colors represent the value of $wpd$.
+### _Detecting patterns not apparent from linear display_ {-}
+
+Figure \ref{fig:dotplot-8} helps to compare households through the heatmap (a) across harmony pairs with the cyclic granularity mapped to x-axis and facet being plotted on the x-axis and y-axis of the heatmap.
+Here *dom*, *dow*, *wdwnd* are abbreviations for day-of-month, day-of-week, weekday/weekend and so on.
+The colors represent the value of $\wpd$.
 Darker cells correspond to more significant harmony pairs.
-Also, the ones with `*` corresponds to the ones above $wpd_{threshold95}$.
+Also, the ones with `*` corresponds to the ones above $\wpdsub{threshold95}$.
 Few observations that emphasizes patterns not discernible through (b) includes - (1) id 7 and 8 have the same significant harmonies despite having very different total energy usage, (2) id 6 and 7 differ in the sense that for id 6, the difference in patterns only during weekday/weekends, whereas for id 7, all or few other days of the week are also important.
-This might be due to their flexible work routines or different day-off, (3) there are no significant periodic patterns for id 5 when we fix the threshold to $wpd_{threshold95}$.
-Note that the $wpd$ values are computed over the entire range, but the linear display in (b) is zoomed only for September, with the major and minor x-axis corresponding to weeks and days respectively.
+This might be due to their flexible work routines or different day-off, (3) there are no significant periodic patterns for id 5 when we fix the threshold to $\wpdsub{threshold95}$.
+Note that the $\wpd$ values are computed over the entire range, but the linear display in (b) is zoomed only for September, with the major and minor x-axis corresponding to weeks and days respectively.
 
@@
 
-```{r dotplot-8, fig.cap = "An ensemble plot with a heatmap (a), line plot (b), parallel coordinate plot (c) to demonstrate energy behavior of the households in different ways.
+(ref:dotplot-8) An ensemble plot with a heatmap (a), line plot (b), parallel coordinate plot (c) to demonstrate energy behavior of the households in different ways.
 (b) is the zoomed-in raw demand series for September to highlight the repetitive patterns of energy demand.
-(a) shows $wpd$ values across harmonies with the x variable of harmony placed across x-axis and facet variable placed across y-axis.
-The darker the colour in (a), the higher the harmony is ranked.
+(a) shows $\wpd$ values across harmonies with the x variable of harmony placed across x-axis and facet variable placed across y-axis.
+The darker the color in (a), the higher the harmony is ranked.
 Visualizing harmonies through (a) allows to view the significant cyclic granularities along the x-axis, facet or both for each household.
-For eg, ids 7 and 8 have significant patterns across (hod, dow) and (dow, hod), which was not apparent through (a).
-(c) is useful for comparing households across harmonies, for eg, for the harmony (dow-hod), ids 1 and 7 have the least and highest wpd respectively.", fig.height = 7}
+For eg, ids 7 and 8 have significant patterns across (*hod*, *dow*) and (*dow*, *hod*), which was not apparent through (a).
+(c) is useful for comparing households across harmonies, for eg, for the harmony (*dow*-*hod*), ids 1 and 7 have the least and highest $\wpd$ respectively.
+
+```{r dotplot-8, fig.cap = "(ref:dotplot-8)", fig.height = 7}
 ```
@@
 
-_Comparing households and validating rank of harmonies_
-
-According to Figure \ref{fig:dotplot-8}(c), for the harmony pair (dow-hod), household id 7 has the greatest value of $wpd$, while id 1 has the least.
-Also, from table \ref{tab:tab-rank-8} it could be seen that the harmony pair $(dow, hod)$ is important for id 7, however it has been labeled as an inconsequential pair for id 1.
-The distribution of energy demand for both of these households, with $dow$ as the facet and $hod$ on the x-axis, may help explain the choice.
+### _Comparing households and validating rank of harmonies_ {-}
+
+According to Figure \ref{fig:dotplot-8}(c), for the harmony pair (*dow*-*hod*), household id 7 has the greatest value of $\wpd$, while id 1 has the least.
+Also, from table \ref{tab:tab-rank-8} it could be seen that the harmony pair (*dow*, *hod*) is important for id 7, however it has been labeled as an inconsequential pair for id 1.
+The distribution of energy demand for both of these households, with *dow* as the facet and *hod* on the x-axis, may help explain the choice.
 Figure \ref{fig:gravitas-plot-8} demonstrates that for id 7, the median (black) and quartile deviation (orange) of energy consumption fluctuates throughout for most hours of the day and day of the week, while for id 1, daily patterns are consistent within weekdays and weekends.
-As a result, for id 1, it is more appropriate to examine the distributional difference solely across (dow, wdwnd), which has been rated higher in Table \ref{tab:tab-rank-8}.
+As a result, for id 1, it is more appropriate to examine the distributional difference solely across (*dow*, *wdwnd*), which has been rated higher in Table \ref{tab:tab-rank-8}.
 
@@
 However, the difference between morning and evening peaks are higher for weekends.
-Since $wpd$ is designed to put more weightage on within-facet differences for $\lambda>0.5$, it makes sense that the pair (hod, wdwnd) has been ranked higher than (wdwnd, hod).
+Since $\wpd$ is designed to put more weightage on within-facet differences for $\lambda>0.5$, it makes sense that the pair (hod, wdwnd) has been ranked higher than (wdwnd, hod).
 Panel c) shows the distribution of energy demand with weekday/weekend as the x-axis and week-of-month as the facets.
@@
 
-```{r gravitas-plot-8, message = FALSE, warning=FALSE,fig.cap="Comparing distribution of energy demand shown for household id 1 (a) and 7 (b) across hod in x-axis and dow in facets through quantile area plots.
-The value of $wpd$ in Table 3 suggests that the harmony pair (dow, hod) is significant for household id 7, but not for 1.
+(ref:gravitas-plot-8) Comparing distribution of energy demand shown for household id 1 (a) and 7 (b) across *hod* in x-axis and *dow* in facets through quantile area plots.
+The value of $\wpd$ in Table 3 suggests that the harmony pair (*dow*, *hod*) is significant for household id 7, but not for 1.
 This implies that distributional differences are captured more by this harmony for id 7, which is apparent from this display with more fluctuations across median and 75th percentile for different hours of the day and day of week.
 For id 1, patterns look similar within weekdays and weekends.
-Here, the median is represented by the black line, the orange area corresponds to quartile deviation and the green area corresponds to area between $10^{th}$ and $90^{th}$ quantile."}
-
-```
-
-<!-- From Figure \ref{fig:gravitas-plot-8-id5}, it could further be observed that id5 has only one significant harmony $(hod, dow)$.
+Here, the median is represented by the black line, the orange area corresponds to quartile deviation and the green area corresponds to area between $10^{th}$ and $90^{th}$ quantile.
+
+```{r gravitas-plot-8, message = FALSE, warning=FALSE,fig.cap="(ref:gravitas-plot-8)"}
+
+```
+
+<!-- From Figure \ref{fig:gravitas-plot-8-id5}, it could further be observed that id5 has only one significant harmony (*hod*, *dow*).
 Apparently, $(hod, wnd/wday)$ which is an important harmony for most households is not important for this one.
@@
 
-The Australian authors thank the ARC Centre of Excellence for Mathematical and Statistical Frontiers [(ACEMS)](https://acems.org.au/home) for supporting this research.
+The authors thank the ARC Centre of Excellence for Mathematical and Statistical Frontiers [(ACEMS)](https://acems.org.au/home) for supporting this research.
 Sayani Gupta was partially funded by [Data61 CSIRO](https://data61.csiro.au/) during her PhD.
@@
 This article was created with R [@R-language], `knitr` [@knitr2015, @R-knitr] and `rmarkdown` [@rmarkdown2018, @R-rmarkdown].
-Graphics are produced with @Wickham2009pk.
+Graphics are produced with `ggplot2` [@Wickham2009pk].
 
@@
 \noindent
-**R-package:** The open-source R [@R-language] package `hakear` is available on Github (https://github.com/Sayani07/hakear) to implement ideas presented in this paper.
+**R-package:** The open-source R package `hakear` is available on Github (https://github.com/Sayani07/hakear) to implement ideas presented in this paper.
 

### 2021-10-28 paper/main.Rmd
Working on sec 3

@@
 
-Pairwise distances could be within-facets or between-facets for $m \geq 2$.
+Pairwise distances could be within-facets or between-facets for $m = 2$.
 Figure \ref{fig:distance-explain} illustrates how they are defined.
@@
 
-### Adjusting for the number of comparisons {-}
+## Adjusting for the number of comparisons
 
@@
 
-### _Permutation approach_ {-}
+### Permutation approach {-}
 
@@
 
-### _Modeling approach_ {-}
+### Modeling approach {-}
 
@@
 
-### _Combination approach_ {-}
+### Combination approach {-}
 
@@
 A cyclic granularity is referred to as "significant" if there is a significant distributional difference of the measured variable between different categories of the harmony.
-In this section, a selection criterion to choose significant harmonies is provided, thereby eliminating all harmonies that exhibit complete randomness in the measured variable.
+In this section, a selection criterion to choose significant harmonies is provided, thereby eliminating all harmonies that exhibit non-significant differences in the measured variable.
 The distance measure $\wpd$ is used as a test statistic to test the null hypothesis that no harmony/cyclic granularity is significant.
 We select only those harmonies/cyclic granularities for which the test fails.
-They are then ranked basis how well they capture variation in the measured variable.
+They are then ranked based on how well they capture variation in the measured variable.
 
@@
 
-A threshold and consequently a selection criterion is chosen using the notion of Randomization tests [@edgington2007randomization].
+A threshold (and consequently a selection criterion) is chosen using the notion of randomization tests [@edgington2007randomization].
 The data is permuted several times and $\wpd$ is computed for each of the permuted data sets to obtain the sampling distribution of $\wpd$ under the null hypothesis.
@@
 
-- **Input:** All harmonies of the form $\{(A, B), A = \{ a_j: j = 1, 2, \dots, J\}, B = \{ b_k: k = 1, 2, \dots, K\}\}$, $\forall (A, B) \in H_{N_C}$.
+- **Input:** All harmonies of the form $\{(A, B),~ A = \{ a_j: j = 1, 2, \dots, J\},~ B = \{ b_k: k = 1, 2, \dots, K\}\}$, $\forall (A, B) \in H_{N_C}$.
 
@@
 
-1. Fix harmony pair $(A, B)$.
-
-2. Given the measured variable; $\{v_t: t=0, 1, 2, \dots, T-1\}$, $\wpd$ is computed and is represented by $\wpd^{A, B}_{obs}$.
-
-3. From the original sequence a random permutation is obtained: $\{v_t^{1}: t=0, 1, 2, \dots, T-1\}$.
-
-4. $\wpd$ is computed for the permuted sequence of the data and is represented by $\wpd^{A, B}_{1}$.
-
-5. Steps (3) and (4) are repeated a large number of times $M$ (e.g. $M = 200$).
-
-6. For each permutation, one $\wpd^{A, B}_{i}$ is obtained. Define $\wpdsub{sample} = \{\wpd^{A, B}_{1} \wpd^{A, B}_{2}, \dots, \wpd^{A, B}_{M}\}$.
-
-7. Repeat Steps (1-6) for all harmony pairs $(A, B) \in H_{N_C}$ and stored $\wpdsub{sample}^{\text{all}}$.
-
-8. $99^{th}$ percentiles of $\wpdsub{sample}^{\text{all}}$ is computed and stored in $\wpdsub{threshold99}$
-
-7. If $\wpd^{A, B}_{obs} > \wpdsub{threshold99}$, harmony pair $(A, B)$ is selected, otherwise rejected.
-
-Similarly, a harmony pair $(A, B)$ could be selected if $\wpd^{A, B}_{obs} > \wpdsub{threshold95}$ and $\wpd^{A, B}_{obs} > \wpdsub{threshold90}$, where $\wpdsub{threshold95}$ and $\wpdsub{threshold90}$ denote the $95^{th}$ and $90^{th}$ percentile of $\wpdsub{sample}^{\text{all}}$ respectively.
-A harmony selected using $99^{th}$, $95^{th}$ and $90^{th}$ threshold are tagged as \*\*\*, \*\*, \* respectively.
+1. For each harmony pair $(A, B) \in H_{N_C}$, the following steps are taken.
+
+    a. Given the measured variable; $\{v_t: t=0, 1, 2, \dots, T-1\}$, $\wpd$ is computed and is represented by $\wpd^{A, B}_{obs}$.
+    b. For $i=1,\dots,m$, randomly permute the original time series: $\{v_t^{i}: t=0, 1, 2, \dots, T-1\}$ and compute $\wpd^{A, B}_{i}$ from $\{v_t^{i}\}$.
+    c. Define $\wpdsub{sample} = \{\wpd^{A, B}_{1}, \dots, \wpd^{A, B}_{M}\}$.
+
+2. Stack the $\wpdsub{sample}$ vectors as $\wpdsub{sample}^{\text{all}}$ and compute its $p = 100(1-\alpha)$ percentiles as $\wpdsub{threshold\emph{p}}$.
+3. If $\wpd^{A, B}_{obs} > \wpdsub{threshold\emph{p}}$, harmony pair $(A, B)$ is selected at the $1-p/100$ level, otherwise rejected.
+4. Harmonies selected using the $99^{th}$, $95^{th}$ and $90^{th}$ thresholds are tagged as \*\*\*, \*\*, \* respectively.
 
@@
 A higher value of $\wpd$ for a harmony indicates that higher maximum variation in the measured variable is captured through that harmony.
-Figure \ref{fig:null4by2} presents the results of $\wpd$ from the illustrative designs in Section \ref{sec:computation-wpd}.
+
+```{r varall-new}
+
+```
+
+```{r varx-new}
+
+```
+
+```{r varf-new}
+```
+
+```{r null-new}
+
+```
+
+(ref:plot-all-new3) $\wpd$ values for the four illustrative designs are presented here.
+As expected, the value of $\wpd$ under null design is the least (a), followed by (b, c and d).
+Moreover, the relative difference is interesting as c is closer to d than b, since the differences between x categories are up-weighed by design.
+
+```{r plot-all-new3, fig.cap = "(ref:plot-all-new3)", dependson= "null4by2"}
+
+```
+
+\todo[inline]{Plot missing and plot-all-new3 code is not relevant.}
+
+Figure \ref{fig:plot-all-new3} presents the results of $\wpd$ from the illustrative designs in Section \ref{sec:computation-wpd}.
 The value of $\wpd$ under null design (a) is the least, followed by (b), (c) and (d).
@@
 
-```{r varall-new}
-
-```
-
-```{r varx-new}
-
-```
-
-```{r varf-new}
-```
-
-```{r null-new}
-
-```
-
-(ref:plot-all-new3) $\wpd$ values for the four illustrative designs are presented here.
-As expected, the value of $\wpd$ under null design is the least (a), followed by (b, c and d).
-Moreover, the relative difference is interesting as c is closer to d than b, since the differences between x categories are up-weighed by design.
-
-```{r plot-all-new3, fig.cap = "(ref:plot-all-new3", dependson= "null4by2"}
-
-```
-
 # Simulations {#sec:simulations}
@@
 
+(ref:raw) Distribution of $\wpdsub{raw}$ is plotted across different $\nx$ and $\nf$ categories under $\Dnull$ through density and rug plots.
+Both location (blue line) and scale (orange marks) of the distribution shifts for different panels.
+This is not desirable since under null design, the distribution is not expected to capture any differences.
+
+```{r raw, fig.cap = "(ref:raw)", fig.pos="!b"}
+```
+
+```{r glm-tab}
+
+```
+
+```{r wpd-glm-dist}
+
+```
+
+```{r hist-qq-new, eval = FALSE}
+
+```
+
+```{r quadratic, eval=FALSE}
+```
+
+```{r norm, eval}
+```
+
+(ref:dist-new-same-scale-link) The distribution of $\wpdsub{perm}$ and $\wpdsub{glm-scaled}$ are overlaid to compare the location and scale across different $\nx$ and $\nf$.
+$\wpdsub{norm}$ takes the value of $\wpdsub{perm}$ for lower levels, and $\wpdsub{glm-scaled}$ for higher levels to to alleviate the problem of computational time in permutation approaches.
+This is possible as the distribution of the adjusted measure looks similar for both approaches for higher levels.
+
+```{r dist-new-same-scale-link, fig.cap = "(ref:dist-new-same-scale-link)"}
+```
+
 Figure \ref{fig:raw} shows that both the location and scale of the distributions change across panels.
@@
 Figure \ref{fig:dist-new-same-scale-link} shows the distribution of $\wpdsub{perm}$ and $wpd_{glm-scaled}$ in the same scale to show that a combination approach could be used for higher values of levels to alleviate the computational time of permutation approach.
-
-(ref:raw) Distribution of $\wpdsub{raw}$ is plotted across different $\nx$ and $\nf$ categories under $\Dnull$ through density and rug plots.
-Both location (blue line) and scale (orange marks) of the distribution shifts for different panels.
-This is not desirable since under null design, the distribution is not expected to capture any differences.
-
-```{r raw, fig.cap = "(ref:raw"}
-```
-
-```{r glm-tab}
-
-```
-
-```{r wpd-glm-dist}
-
-```
-
-```{r hist-qq-new, eval = FALSE}
-
-```
-
-```{r quadratic, eval=FALSE}
-```
-
-```{r norm, eval}
-```
-
-(ref:dist-new-same-scale-link) The distribution of $\wpdsub{perm}$ and $\wpdsub{glm-scaled}$ are overlaid to compare the location and scale across different $\nx$ and $\nf$.
-$\wpdnorm$ takes the value of $\wpdsub{perm}$ for lower levels, and $\wpdsub{glm-scaled}$ for higher levels to to alleviate the problem of computational time in permutation approaches.
-This is possible as the distribution of the adjusted measure looks similar for both approaches for higher levels.
-
-```{r dist-new-same-scale-link, fig.cap = "(ref:dist-new-same-scale-link"}
-```
 

### 2021-10-28 paper/main.Rmd
updated renv due to in recentincomptability with tlmgr and texLive

@@
 As expected, the value of $\wpd$ under null design is the least (a), followed by (b, c and d).
-Moreover, the relative difference is interesting as c is closer to d than b, since the differences between x categories are up-weighed by design.
-
-```{r plot-all-new3, fig.cap = "(ref:plot-all-new3)", dependson= "null4by2"}
-
-```
-
-\todo[inline]{Plot missing and plot-all-new3 code is not relevant.}
-
-Figure \ref{fig:plot-all-new3} presents the results of $\wpd$ from the illustrative designs in Section \ref{sec:computation-wpd}.
+Moreover, the relative difference is interesting as c is closer to d than b, since the differences between x categories axre up-weighed by design.
+
+Figure \ref{fig:null4by2} also presents the results of $\wpd$ from the illustrative designs in Section \ref{sec:computation-wpd}.
 The value of $\wpd$ under null design (a) is the least, followed by (b), (c) and (d).

### 2021-10-29 paper/main.Rmd
Improved Sec 3 and notational consistency

@@
 Section \ref{sec:rank-wpd} devises a selection criterion by choosing a threshold, which results in detection of only significantly interesting patterns.
-Section \ref{sec:simulations} provides some simulation study on the proposed methodology.
+Section \ref{sec:simulations} provides a simulation study on the proposed methodology.
 Section \ref{sec:application-wpd} presents an application to residential smart meter data in Melbourne to show how the proposed methodology can be used to automatically detect temporal granularities along which distributional differences are significant.
@@
 But it can be easily extended to $m>2$.
-Consider two cyclic granularities $A$ and $B$, such that $A = \{a_j: j = 1, 2, \dots, J\}$ and $B = \{b_k: k = 1, 2, \dots, K\}$ with $A$ placed across the x-axis and $B$ across facets.
+Consider two cyclic granularities $A$ and $B$, such that $A = \{a_j: j = 1, 2, \dots, \nx\}$ and $B = \{b_k: k = 1, 2, \dots, \nf\}$ with $A$ placed across the x-axis and $B$ across facets.
 Let $v = \{v_t: t = 0, 1, 2, \dots, T-1\}$ be a continuous variable observed across $T$ time points.
-This data structure with $J$ x-axis levels and $K$ facet levels is referred to as a $(J, K)$ panel.
+This data structure with $\nx$ x-axis levels and $\nf$ facet levels is referred to as a $(\nx, \nf)$ panel.
 For example, a $(2, 3)$ panel will have cyclic granularities with two x-axis levels and three facet levels.
@@
 Finally, $\Dfx$ denotes those designs for which difference is observed across both $A$ and $B$.
-We can consider a single granularity ($m = 1$) as a special case of two granularities with $J = 1$.
+We can consider a single granularity ($m = 1$) as a special case of two granularities with $\nf = 1$.
 
@@
 The number of observations might vary widely across subsets due to the structure of the calendar, missing observations or uneven locations of events in the time domain.
-In this paper, quantiles of $\{v_{jk}\}$ are chosen as a way to characterize distributions for the category $(a_j, b_k)$, $\forall j\in \{1, 2, \dots, J\}, k\in \{1, 2, \dots, K\}$.
+In this paper, quantiles of $\{v_{jk}\}$ are chosen as a way to characterize distributions for the category $(a_j, b_k)$, $\forall j\in \{1, 2, \dots, \nx\}, k\in \{1, 2, \dots, \nf\}$.
 We use percentiles with $p = {0.01, 0.02, \dots, 0.99}$ to reduce the computational burden in summarising distributions.
@@
 
-<!-- Each $v_{jk}$'s $\forall j\in \{1, 2, \dots, J\}, k\in \{1, 2, \dots, K\}\}$ are assumed to be drawn from a continuous probability distribution and have certain characteristics.
+<!-- Each $v_{jk}$'s $\forall j\in \{1, 2, \dots, \nx\}, k\in \{1, 2, \dots, \nf\}\}$ are assumed to be drawn from a continuous probability distribution and have certain characteristics.
 Shape, central tendency, and variability are the common characteristics used to describe a distribution.
@@
 Pairwise distances are between-facets when they are considered between pairs of the form $(a_{j}b_{k}, a_{j}b_{k'})$.
-There are a total of ${K \choose 2}J$ between-facet distances, and ${J \choose 2}K$ within-facet distances if they are ordered and $K(J-1)$ within-facet distances if they are unordered.
+There are a total of ${\nf \choose 2}\nx$ between-facet distances, and ${\nx \choose 2}\nf$ within-facet distances if they are ordered and $\nf(\nx-1)$ within-facet distances if they are unordered.
 
@@
 Then, for a fixed harmony pair $(A, B)$, percentiles of $v^*_{jk}$ are computed and stored in $q_{jk}$ (_distribution characterization_).
-This is repeated for all pairs of categories of the form $(a_{j} b_{k}, a_{j'}b_{k'}): \{a_j: j = 1, 2, \dots, J\}, B = \{ b_k: k = 1, 2, \dots, K\}$.
+This is repeated for all pairs of categories of the form $(a_{j} b_{k}, a_{j'}b_{k'}): \{a_j: j = 1, 2, \dots, \nx\}, B = \{ b_k: k = 1, 2, \dots, \nf\}$.
 The pairwise distances between pairs $(a_{j} b_{k}, a_{j'}b_{k'})$ denoted by $d_{(jk, j'k')} = JSD(q_{jk}, q_{j'k'})$ are computed (_distance between distributions_).
@@
 $$
-  \wpdsub{raw} = \max_{j, j', k, k'}(d*_{(jk), (j'k')}) \qquad\forall j, j' \in \{1, 2, \dots, J\},\quad k, k' \in \{1, 2, \dots, K\}
+  \wpdsub{raw} = \max_{j, j', k, k'}(d*_{(jk), (j'k')}) \qquad\forall j, j' \in \{1, 2, \dots, \nx\},\quad k, k' \in \{1, 2, \dots, \nf\}
 $$
@@
 
-Ideally, it is desired that the proposed distance measure takes a higher value only if there is a significant difference between distributions across categories, and not because the number of categories $J$ or $K$ is high.
+Ideally, it is desired that the proposed distance measure takes a higher value only if there is a significant difference between distributions across categories, and not because the number of categories $\nx$ or $\nf$ is high.
 That is, under designs like $\Dnull$, their distribution should not differ for a different number of categories.
@@
 \wpd = \begin{cases}
-         \wpdsub{perm},       & \text{if $J, K \le 5$};\\
+         \wpdsub{perm},       & \text{if $\nx, \nf \le 5$};\\
          \wpdsub{glm-scaled}  & \text{otherwise}.\\
@@
 
-<!-- Hence, differences in distributions of the measured variable are computed between all pairs of categories $(a_{j} b_{k}, a_{j'}b_{k'}): j = 1, 2, \dots, J\}, B = \{ b_k: k = 1, 2, \dots, K\}$.
+<!-- Hence, differences in distributions of the measured variable are computed between all pairs of categories $(a_{j} b_{k}, a_{j'}b_{k'}): j = 1, 2, \dots, \nx\}, B = \{ b_k: k = 1, 2, \dots, \nf\}$.
 Percentiles of $v_{jk}$ and $v_{j'k'}$ are computed and stored in $q_{jk}$ and $q_{j'k'}$ respectively.
@@
 Pairwise distances are between-facets ($d_{b}$) when they are considered between pairs of the form $(a_{j}b_{k}, a_{j}b_{k'})$.
-Number of between-facet distances would be $^{K}C_2*J$ and number of within-facet distances are $K*(J-1)$ (ordered) and $^{J}C_2*K$ (un-ordered).
+Number of between-facet distances would be $^{\nf}C_2*\nx$ and number of within-facet distances are $\nf*(\nx-1)$ (ordered) and $^{\nx}C_2*\nf$ (un-ordered).
 The pairwise distances $d_{(jk, j'k')}$ are transformed using a suitable tuning parameter ($0<\lambda<1$) depending on if they are $d_{b}$ or $d_{w}$ as follows: -->
@@
 
-5. Use Steps 1-4 to compute maximum distance for $\forall k \in \{1, 2, \ldots, K\}$.
+5. Use Steps 1-4 to compute maximum distance for $\forall k \in \{1, 2, \ldots, \nf\}$.
 
@@
  <!-- old -->
-<!-- Consider two cyclic granularities $C_i$ and $C_j$, such that $C_i$ maps index set to a set $\{A_k \mid k=1,\dots,K\}$ and $C_j$ maps index set to a set $\{B_\ell \mid \ell =1,\dots,L\}$.
+<!-- Consider two cyclic granularities $C_i$ and $C_j$, such that $C_i$ maps index set to a set $\{A_k \mid k=1,\dots,\nf\}$ and $C_j$ maps index set to a set $\{B_\ell \mid \ell =1,\dots,L\}$.
 Here, $A_k$ and $B_\ell$ are the levels/categories corresponding to $C_i$ and $C_j$ respectively.
@@
 
-<!-- 5. Use Steps 1-4 to compute maximum distance for $\forall k \in \{1, 2, \ldots, K\}$. -->
+<!-- 5. Use Steps 1-4 to compute maximum distance for $\forall k \in \{1, 2, \ldots, \nf\}$. -->
 
@@
 <!-- \begin{algorithm}[!thb] -->
-<!-- 	\caption{Calculation for a raw distance measure between two cyclic granularities $A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.}\label{alg:scoreopt}.
+<!-- 	\caption{Calculation for a raw distance measure between two cyclic granularities $A = \{ a_j: j = 1, 2, \dots, \nx\}$, $B = \{ b_k: k = 1, 2, \dots, \nf\}$ with $A$ placed across x-axis and $B$ across facets.}\label{alg:scoreopt}.
 -->
 <!-- 	\begin{algorithmic}[1] -->
-<!-- 		\Procedure{RawMMPD}{$A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$, $v = \{ v_t: t = 1, 2, \dots, T\}$}. -->
-<!-- 		\For{$k=1:K$, $j=1:J$} -->
+<!-- 		\Procedure{RawMMPD}{$A = \{ a_j: j = 1, 2, \dots, \nx\}$, $B = \{ b_k: k = 1, 2, \dots, \nf\}$, $v = \{ v_t: t = 1, 2, \dots, T\}$}. -->
+<!-- 		\For{$k=1:\nf$, $j=1:\nx$} -->
 <!-- 		\State Find distances between pairs of all possible combinations of categories $(a_jb_k,a_j'b_k')$ by computing JSD between quantiles of the measured variable $q(v)$ across these combinations.
@@
 
-- **Input:** All harmonies of the form $\{(A, B),~ A = \{ a_j: j = 1, 2, \dots, J\},~ B = \{ b_k: k = 1, 2, \dots, K\}\}$, $\forall (A, B) \in H_{N_C}$.
+- **Input:** All harmonies of the form $\{(A, B),~ A = \{ a_j: j = 1, 2, \dots, \nx\},~ B = \{ b_k: k = 1, 2, \dots, \nf\}\}$, $\forall (A, B) \in H_{N_C}$.
 
@@
 ```
-
-(ref:plot-all-new3) $\wpd$ values for the four illustrative designs are presented here.
-As expected, the value of $\wpd$ under null design is the least (a), followed by (b, c and d).
-Moreover, the relative difference is interesting as c is closer to d than b, since the differences between x categories axre up-weighed by design.
 
@@
 Moreover, note the relative differences in $\wpd$ values between (b) and (c).
-The value of the tuning parameter $\lambda$ is set to $0.67$, which has resulted in giving more emphasis to differences in x-axis categories.
+The value of the tuning parameter $\lambda$ is set to 2/3, which gives greater emphasis to differences in x-axis categories than facets.
+
 Again consider \ref{fig:onegran-new}(a) and \ref{fig:onegran-new}(b) with a $\wpd$ value of 20.5 and 145 respectively.
-This is because there is more gradual increase across hours of the day than months of the year.
-If order of the categories is not considered, they result in a $\wpd$ value of $97.8$ and $161$ respectively, which follows from the fact that if we consider difference between any hours of the day, the magnitude will be much larger than if we consider difference between consecutive categories.
+This is because there is a more gradual increase across hours of the day than across months of the year.
+If the order of categories is ignored, the resulting $\wpd$ values are $97.8$ and $161$ respectively, because differences between any hours of the day tend to be larger than differences only between consecutive hours.
 Similarly, \ref{fig:onegran-new}(a) and (b) have $\wpd$ values of $110.79$ and $125.82$ respectively.
-The ranking implies that the distributional differences are more prominent for the second household, as is also seen from the bigger fluctuations in the $90^{th}$ percentile than the first household.
+The ranking implies that the distributional differences are more prominent for the second household, as is also seen from the bigger fluctuations in the $90^{th}$ percentile than for the first household.
 
@@
 
-# Simulations {#sec:simulations}
-
-## Behavior of raw and adjusted distance measures
-
-### _Simulation design_ {-}
+## Simulations {#sec:simulations}
+
+Simulations were carried out to explore the behavior of $\wpd$ as $\nx$ and $\nf$ were varied, in order to compare and evaluate different normalization approaches.
+More detailed simulation results, including an exploration of the size and power of the proposed test, are contained in the supplements.
+
+### Simulation design {-}
 
@@
 
-\noindent Observations are generated from a N(0,1) distribution for a wide range of levels from very low to moderately high.
-$nx = \{2, 3, 5, 7, 9, 14, 17, 20, 24, 31, 42, 50\}$ is considered.
-$ntimes = 500$ observations are drawn for each combination of the categories, that is, for a panel with $nx=3$, $500$ observations are simulated for each of the categories.
-This design corresponds to $\Dnull$ as each combination of categories in a panel are drawn from the same distribution.
-Furthermore, the data is simulated for each of the categories $\nsub{sim}=200$ times, so that the distribution of $\wpd$ under $\Dnull$ could be observed.
-The values of $\wpd$ is obtained for each of the panels.
-$wpd_{l, s}$ denotes the value of $\wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.
+\noindent Observations were generated from a N(0,1) distribution for $\nx \in \{2, 3, 5, 7, 9, 14, 17, 20, 24, 31, 42, 50\}$, with $\nsub{times} = 500$ observations drawn for each combination of categories.
+This design corresponds to $\Dnull$.
+For each of the categories, there were $\nsub{sim}=200$ replications, so that the distribution of $\wpd$ under $\Dnull$ could be observed.
+Let $\wpd_{\ell, s}$ denote the value of $\wpd$ obtained for the $\ell^{th}$ panel and $s^{th}$ simulation.
 
@@
 
-\noindent Similarly, observations are generated from a N(0,1) distribution for each combination of $\nx$ and $\nf$ from the following sets: $nx = \nf = \{2, 3, 5, 7, 14, 20, 31, 50\}$.
-That is, data is being generated for each of the panels $(2, 2), (2, 3), (2, 5) \dots, (50, 31), (50, 50)$.
-For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
-That is, if we consider a $(2, 2)$ panel, $500$ observations are generated for each of the possible subsets, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
-
-### _Results_ {-}
+\noindent Similarly, observations were generated from a N(0,1) distribution for each combination of $\nx$ and $\nf$ from $\{2, 3, 5, 7, 14, 20, 31, 50\}$, with $\nsub{times} = 500$ observations drawn for each of the $64$ combinations.
+
+### Results {-}
+
+Figure \ref{fig:raw} shows that both the location and scale of the distributions change across panels.
+This is not desirable under $\Dnull$ as it would mean comparisons of $\wpd$ values are not appropriate across different $\nx$ and $\nf$ values.
+Table \ref{tab:glm-tab} gives the summary of a Gamma generalized linear model to capture the relationship between $\wpdsub{raw}$ and the number of comparisons.
+The intercepts and slopes are similar, independent of the underlying distributions (see supplementary paper for details) and hence the coefficients are shown for the case when observations are drawn from a N(0,1) distribution.
+Figure \ref{fig:dist-new-same-scale-link} shows the distribution of $\wpdsub{perm}$ and $\wpdsub{glm-scaled}$ on the same scale to show that a combination approach could be used for higher values of $\nx$ and $\nf$ to alleviate the computational time of the permutation approach.
 
@@
 Both location (blue line) and scale (orange marks) of the distribution shifts for different panels.
-This is not desirable since under null design, the distribution is not expected to capture any differences.
+This is not desirable since under the null design, the distribution is not expected to capture any differences.
 
@@
 
-Figure \ref{fig:raw} shows that both the location and scale of the distributions change across panels.
-This is not desirable under $\Dnull$ as it would mean comparisons of $\wpd$ values is not appropriate across different $\nx$ and $\nf$.
-Table \ref{tab:glm-tab} gives the summary of the generalized linear model to capture the relationship between $\wpdsub{raw}$ and number of comparisons.
-For example, the model considered for $m = 2$ is $wpd_{l,s} = 23.4 - 0.96*log(nx * \nf)) + e$.
-The intercepts and slopes are similar independent of the starting distributions (see supplementary paper for details) and hence the coefficients are shown for the case when observations are drawn from a N(0, 1) distribution.
-Figure \ref{fig:dist-new-same-scale-link} shows the distribution of $\wpdsub{perm}$ and $wpd_{glm-scaled}$ in the same scale to show that a combination approach could be used for higher values of levels to alleviate the computational time of permutation approach.
-
-## Choosing threshold
-
-### _Simulation design_ {-}
-
-Observations are generated from a N(0,1) distribution for each combination of $\nx$ and $\nf$ from the following sets: $nx = \{3, 7, 14\}$ and $\nf = \{2, 9, 10\}$.
-This would result in 9 panels, viz, $(3, 2), (3, 9), (3, 10), \dots, (14,9), (14, 10)$.
-Few experiments were conducted.
-In the first scenario, data for all panels are simulated using the null design $\Dnull$.
-In other scenarios, data simulated from the panel $(14, 2)$ and $(3, 10)$ are considered under $\Dfx$.
-Moreover, $\omega = \{0.5, 2, 5\}$ are considered to examine if the proposed test is able to capture subtle differences and non-subtle differences when we shift from the null design.
-
-<!-- In the last scenario, we consider the panel $(3, 2), (7,9), (14, 10)$ to be under $\Dnull$, the panels $(7, 2), (14, 9)$ to be under $\Df$.
+These results justify our use of the permutation approach when $\nx<5$ and $\nf<5$, and the use of the GLM otherwise.
+<!--
+## Choosing the threshold
+
+### Simulation design {-}
+
+Observations were generated from a N(0,1) distribution for each combination of $\nx$ and $\nf$ from the following sets: $nx \in \{3, 7, 14\}$ and $\nf \in \{2, 9, 10\}$, giving nine possible panels/combinations.
+In the first scenario, data for all panels were simulated using the null design $\Dnull$.
+In other scenarios, data simulated from the panel $(14, 2)$ and $(3, 10)$ used $\Dfx$ where the means of the distributions increase by $\omega$ across both x-axis and facets, where $\omega \in \{0.5, 2, 5\}$.
+This allows us to examine if the proposed test is able to capture subtle differences and obvious differences when we shift from the null design.
+
+In the last scenario, we consider the panel $(3, 2), (7,9), (14, 10)$ to be under $\Dnull$, the panels $(7, 2), (14, 9)$ to be under $\Df$.
 $(14, 2), (3, 10)$ under $D_x$ and the rest under $\Dvar{{null}}$.
@@
 We generate $1000$ repetitions of this experiment with different seeds.
--->
-
-### _Results_ {-}
-
-For the first scenario, size of the test is obtained as $0.1$ with $\wpdsub{threshold99}$ as the threshold.
-This implies that the proportion of times a panel is rejected when it is under $\Dnull$ is $0.1$.
-The level of significance for each test is 1% (as a result of choosing $99^{th}$ percentile as the threshold) and we have $9$ multiple tests.
-Hence, it is reasonable
-that the level of significance of the composite tests would be larger than the individual tests.
-We also compute the proportion of times a panel is rejected when it actually belongs to a non-null design.
-These proportions constitute to be the estimated size and power of the test.
-Power can depend on many things like sample size, number of designs that deviate from the null and extent to which from the null.
-It is found that as we increase from low to high changes from the null distribution, the power increased.
-<!---The power also increases with increased sample size, as is expected.---> The results and graphics are included in details in the Supplementary paper.
+
+### Results {-}
+
+For the first scenario, we set $\wpdsub{threshold99}$ so that the probability of rejecting each panel under $\Dnull$ is $0.01$.
+We have 9 tests, so the size of the tests overall is $1-0.99^9 \approx 0.09$.
+We also compute the proportion of times a panel is rejected when it belongs to a non-null design to obtain the power of the test.
+The detailed results and graphics are included in the Supplementary paper.
 
@@
 ```
-
-## Environment
-
-Simulation studies were carried out to study the behavior of $\wpd$, build the normalization method as well as compare and evaluate different normalization approaches.
-R version 4.0.1 (2020-06-06) is used with the platform: x86_64-apple-darwin17.0 (64-bit) running under: macOS Mojave 10.14.6 and MonaRCH, which is a next-generation High Power Computing (HPC) Cluster, addressing the needs of the Monash HPC community.
+ -->
 
@@
 
-### _Choosing cyclic granularities of interest and removing clashes_ {-}
+### Choosing cyclic granularities of interest and removing clashes {-}
 
@@
 
-### _Selecting and Ranking harmonies for all households_ {-}
+### Selecting and Ranking harmonies for all households {-}
 
@@
 
-### _Detecting patterns not apparent from linear display_ {-}
+### Detecting patterns not apparent from linear display {-}
 
@@
 
-### _Comparing households and validating rank of harmonies_ {-}
+### Comparing households and validating rank of harmonies {-}
 

### 2021-10-29 paper/main.Rmd
Finished sections 3, 4 and 5

@@
 In this paper, quantiles of $\{v_{jk}\}$ are chosen as a way to characterize distributions for the category $(a_j, b_k)$, $\forall j\in \{1, 2, \dots, \nx\}, k\in \{1, 2, \dots, \nf\}$.
-We use percentiles with $p = {0.01, 0.02, \dots, 0.99}$ to reduce the computational burden in summarising distributions.
+We use percentiles with $p = {0.01, 0.02, \dots, 0.99}$ to reduce the computational burden in summarizing distributions.
 
@@
 
-The smart meter data set for eight households in Melbourne has been utilized to see the use of $\wpd$ proposed in the paper.
-The data has been cleaned to be a `tsibble` [@wang2020tsibble] containing half-hourly electricity consumption from Jul-2019 to Dec-2019 for each of the households, which is procured by them by downloading their data from the energy supplier/retailer.
-No behavioral pattern is likely to be discerned from the line graph of energy usage over the entire period, since the plot will have too many measurements squeezed in a linear representation.
-When we zoom into the linear representation of this series in Figure \ref{fig:dotplot-8} (b) for September, some patterns are visible in terms of peaks and troughs, but we do not know if they are regular or what is their period.
-Electricity demand, in general, has a daily and weekly periodic pattern.
-However, it is not apparent from this view if all of these households have those patterns and in case they have if they are significant enough.
-Also, it is not clear if any other periodic patterns are present in any household which might have been hidden with this view.
-We start the analysis by choosing few harmonies, ranking them for each of these households, compare households to get more insights into what these rankings imply.
-Furthermore, the ranking and selection of significant harmonies is validated by analyzing the distribution of energy usage across significant harmonies.
+The smart meter data set for eight households in Melbourne were procured by downloading the data from the energy supplier/retailer.
+The data has been cleaned to form a `tsibble` [@wang2020tsibble] containing half-hourly electricity consumption from July to December 2019 for each of the households, No behavioral pattern is likely to be discerned from the time plot of energy usage over the entire period, since the plot will have too many observations squeezed in a linear representation.
+When we zoom into the September 2019 data in Figure \ref{fig:dotplot-8}(b), some patterns are visible in terms of peaks and troughs, but we do not know if they are regular or what is their period.
+
+(ref:dotplot-8) An ensemble plot with a heatmap (a), line plot (b), parallel coordinate plot (c) to demonstrate energy behavior of the households in different ways.
+Panel (b) shows the raw demand series for September to highlight the repetitive patterns of energy demand.
+Panel (a) shows $\wpd$ values across harmonies where a darker color indicates a higher ranking harmony.
+A significant harmony is shown with an asterisk.
+For example, ids 7 and 8 have significant patterns across (*hod*, *dow*) and (*dow*, *hod*).
+Panel (c) is useful for comparing households across harmonies.
+For example, for the harmony (*dow*-*hod*), ids 1 and 7 have the least and highest $\wpd$ respectively.
+
+```{r dotplot-8, fig.cap = "(ref:dotplot-8)", fig.height = 7}
+```
+
+Electricity demand, in general, has daily, weekly and annual seasonal patterns.
+However, it is not apparent from this view if all households have those patterns, or how strong they are in each case.
+It is also not clear from this view if any other periodic patterns are present in any household.
+We start the analysis by choosing a few harmonies, and ranking them for each of these households.
+The ranking and selection of significant harmonies is validated by analyzing the distribution of energy usage across significant harmonies.
 
@@
 
-Let $v_{i, t}$ denote the electricity demand for $i^{th}$ household for time period $t$.
-The series $v_{i, t}$ is the linear granularity corresponding to half-hour since the interval of the tsibble is 30 minutes.
+Let $v_{i, t}$ denote the electricity demand for the $i^{th}$ household in time period $t$.
+The series $\{v_{i, 1},\dots,v_{i,T}\}$ is the linear granularity corresponding to half-hour since the interval of the tsibble is 30 minutes.
 We consider coarser linear granularities like hour, day, week and month from the commonly used Gregorian calendar.
-Considering $4$ linear granularities hour, day, week, month, the number of cyclic granularities is $N_C = (4 * 3/2) = 6$.
-We obtain cyclic granularities namely "hour_day", "hour_week", "hour_month", "day_ week", "day_month" and "week_month", read as "hour of the day", etc.
+From the four linear granularities of hour, day, week, and month, we obtain $N_C = 4\times 3/2 = 6$ cyclic granularities:  "hour_day", "hour_week", "hour_month", "day_ week", "day_month" and "week_month".
 Further, we add cyclic granularity day-type ("wknd wday") to capture weekend and weekday behavior.
-Thus, $7$ cyclic granularities are considered to be of interest.
-The set consisting of pairs of cyclic granularities ($C_{N_C}$) will have $7\times 6=42$ elements which could be analyzed for detecting possible periodicities.
+Thus, seven cyclic granularities are considered to be of interest.
+The pairs of cyclic granularities ($C_{N_C}$) will have $7\times 6=42$ elements.
 The set of possible harmonies $H_{N_C}$ from $C_{N_C}$ are chosen by removing clashes using procedures described in [@Gupta2021-hd].
@@
 
+```{r rank-household-mclapply-8}
+```
+
+```{r elec_select_harmony-8}
+```
+
+```{r tab-rank-8, dependson="dotplot-8"}
+```
+
  <!-- The paper also shows how the number of harmonies could be identified among by removing clashes.
@@
 
-$\wpd_{i}$ is computed on $v_{i, t}$ for all harmony pairs $\in H_{N_C}$ and for each households $i \in \{1, 2, \dots, 8\}$.
+$\wpd_{i}$ is computed on $v_{i, t}$ for all harmony pairs $\in H_{N_C}$ and for each household $i \in \{1, 2, \dots, 8\}$.
 The harmony pairs are then arranged in descending order and highlighted with `***`, `**` and `*` corresponding to the $99^{th}$, $95^{th}$ and $90^{th}$ percentile threshold.
@@
 The rankings are different for different households, which is a reflection of their varied behaviors.
-Most importantly, there are at most $3$ harmonies that are significant for any household.
-This is a huge reduction in the number of potential harmonies to explore closely, starting from $42$.
+Most importantly, there are at most three harmonies that are significant for any household.
+This is a huge reduction in the number of potential harmonies to explore.
 
@@
 
-Figure \ref{fig:dotplot-8} helps to compare households through the heatmap (a) across harmony pairs with the cyclic granularity mapped to x-axis and facet being plotted on the x-axis and y-axis of the heatmap.
+Figure \ref{fig:dotplot-8} helps to compare households through the heatmap (a) across harmony pairs.
 Here *dom*, *dow*, *wdwnd* are abbreviations for day-of-month, day-of-week, weekday/weekend and so on.
 The colors represent the value of $\wpd$.
-Darker cells correspond to more significant harmony pairs.
-Also, the ones with `*` corresponds to the ones above $\wpdsub{threshold95}$.
-Few observations that emphasizes patterns not discernible through (b) includes - (1) id 7 and 8 have the same significant harmonies despite having very different total energy usage, (2) id 6 and 7 differ in the sense that for id 6, the difference in patterns only during weekday/weekends, whereas for id 7, all or few other days of the week are also important.
-This might be due to their flexible work routines or different day-off, (3) there are no significant periodic patterns for id 5 when we fix the threshold to $\wpdsub{threshold95}$.
-Note that the $\wpd$ values are computed over the entire range, but the linear display in (b) is zoomed only for September, with the major and minor x-axis corresponding to weeks and days respectively.
+Darker cells correspond to higher values of $\wpd$.
+Those with `*` correspond to $\wpd$ values above $\wpdsub{threshold95}$.
+
+We can now see some patterns that were not discernible in Panel (b), including:
+
+  1. id 7 and 8 have the same significant harmonies despite having very different total energy usage.
+  2.
+id 6 and 7 differ in the sense that for id 6, the difference in patterns only during weekday/weekends, whereas for id 7, all or few other days of the week are also important.
+This might be due to their flexible work routines or different day-off.
+  3. There are no significant periodic patterns for id 5 when we fix the threshold to $\wpdsub{threshold95}$.
+
+Note that the $\wpd$ values are computed over the entire range, but the linear display in (b) is only for September, with the major and minor x-axis corresponding to weeks and days respectively.
 
@@
 
-```{r rank-household-mclapply-8}
-```
-
-```{r elec_select_harmony-8}
-```
-
-(ref:dotplot-8) An ensemble plot with a heatmap (a), line plot (b), parallel coordinate plot (c) to demonstrate energy behavior of the households in different ways.
-(b) is the zoomed-in raw demand series for September to highlight the repetitive patterns of energy demand.
-(a) shows $\wpd$ values across harmonies with the x variable of harmony placed across x-axis and facet variable placed across y-axis.
-The darker the color in (a), the higher the harmony is ranked.
-Visualizing harmonies through (a) allows to view the significant cyclic granularities along the x-axis, facet or both for each household.
-For eg, ids 7 and 8 have significant patterns across (*hod*, *dow*) and (*dow*, *hod*), which was not apparent through (a).
-(c) is useful for comparing households across harmonies, for eg, for the harmony (*dow*-*hod*), ids 1 and 7 have the least and highest $\wpd$ respectively.
-
-```{r dotplot-8, fig.cap = "(ref:dotplot-8)", fig.height = 7}
-```
-
-```{r tab-rank-8}
-```
-
 ### Comparing households and validating rank of harmonies {-}
@@
 According to Figure \ref{fig:dotplot-8}(c), for the harmony pair (*dow*-*hod*), household id 7 has the greatest value of $\wpd$, while id 1 has the least.
-Also, from table \ref{tab:tab-rank-8} it could be seen that the harmony pair (*dow*, *hod*) is important for id 7, however it has been labeled as an inconsequential pair for id 1.
+From Table \ref{tab:tab-rank-8} it can be seen that the harmony pair (*dow*, *hod*) is important for id 7, however it has been labeled as an inconsequential pair for id 1.
 The distribution of energy demand for both of these households, with *dow* as the facet and *hod* on the x-axis, may help explain the choice.
-Figure \ref{fig:gravitas-plot-8} demonstrates that for id 7, the median (black) and quartile deviation (orange) of energy consumption fluctuates throughout for most hours of the day and day of the week, while for id 1, daily patterns are consistent within weekdays and weekends.
+Figure \ref{fig:gravitas-plot-8} demonstrates that for id 7, the median (black) and quartile deviation (orange) of energy consumption fluctuates for most hours of the day and days of the week, while for id 1, daily patterns are more consistent within weekdays and weekends.
 As a result, for id 1, it is more appropriate to examine the distributional difference solely across (*dow*, *wdwnd*), which has been rated higher in Table \ref{tab:tab-rank-8}.
@@
 (ref:gravitas-plot-8) Comparing distribution of energy demand shown for household id 1 (a) and 7 (b) across *hod* in x-axis and *dow* in facets through quantile area plots.
-The value of $\wpd$ in Table 3 suggests that the harmony pair (*dow*, *hod*) is significant for household id 7, but not for 1.
+The value of $\wpd$ in Table 3 suggests that the harmony pair (*dow*, *hod*) is significant for household id 7, but not for id 1.
 This implies that distributional differences are captured more by this harmony for id 7, which is apparent from this display with more fluctuations across median and 75th percentile for different hours of the day and day of week.
@@
 
-```{r gravitas-plot-8, message = FALSE, warning=FALSE,fig.cap="(ref:gravitas-plot-8)"}
+```{r gravitas-plot-8, message = FALSE, warning=FALSE,fig.cap="(ref:gravitas-plot-8)", fig.pos="!htb"}
 
@@
 With temporal data available at finer scales, exploring time series has become overwhelming with so many possible granularities to explore.
-A common solution is to aggregate and look at the patterns across usual granularities like hour-of-day or day-of-week, but there is no way to know the “interesting” granularities a priori.
+A common solution is to aggregate and look at the patterns across the usual granularities such as hour-of-day or day-of-week, but there is no way to know the “interesting” granularities a priori.
 A huge number of displays need to be analyzed or we might end up missing informative granularities.

### 2021-10-29 paper/scripts/main.R

@@ -1,6 +1,7 @@
 ## ---- load 
 library(knitr)
 library(tidyverse)
+library(broom)
 library(lubridate)
 library(lvplot)
 #library(ggridges)
@@ -17,9 +18,12 @@ library(ggplot2)
 library(patchwork)
 library(scales)
 library(GGally)
-library(viridis)
+#library(viridis)
 #remotes::install_github("Sayani07/hakear", force = TRUE)
 library(hakear)
+
+# OkabeIto color blind friendly scale
+okabeito <- c("#D55E00", "#0072B2","#009E73", "#CC79A7", "#E69F00", "#56B4E9", "#F0E442", "#333333")
 
 #library(tidyquant)
 
@@ -912,12 +916,10 @@ elec_sig_split <- elec_harmony_all %>%
     select_split == "*" ~ "medium",
     select_split == "" ~ "low"
   )) %>% 
-  mutate(rank = case_when(
-    select_split == "***" ~ paste(rank, "***", sep = " "),
-    select_split == "**" ~  paste(rank, "**", sep = " "),
-    select_split == "*" ~  paste(rank, "*", sep = " "),
-    select_split == "" ~  paste(rank, "", sep = " ")
-  ))
+  mutate(
+    rank = if_else(rank < 10, paste0("\\phantom{0}",rank), paste0(rank)),
+    rank = paste0(rank,"\\rlap{$^{",select_split,"}$}")
+  )
 
 
 elec_sig_split$significant <- 
@@ -999,7 +1001,7 @@ elec_zoom <-  elec %>%
         panel.grid.minor.x =  element_line(colour = "#D3D3D3")) +
   theme(
     strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) +
-  scale_color_viridis(discrete=TRUE)
+  scale_color_discrete(type = okabeito)
  
 
 
@@ -1029,7 +1031,7 @@ parcoord <- GGally::ggparcoord(data_pcp,
                    alphaLines = 1 ,
                    scale = "globalminmax"
 ) + ggplot2::theme_bw() +
-  scale_color_viridis(discrete=TRUE) + 
+  scale_color_discrete(type = okabeito) + 
   ggplot2::theme(
     plot.title = ggplot2::element_text(size=10)
   )+
@@ -1061,7 +1063,9 @@ elec_rank <- elec_sig_split %>%
          "x variable" = "x_variable") %>% 
   select(-facet_levels, -x_levels)
 
[…]

### 2021-11-03 paper/hakear_jcgs.Rmd
Split into JCGS and WP versions

--- 2021-10-29 paper/main.Rmd
@@
 bibliography: [bibliography.bib]
-preamble: >
- \setlength {\marginparwidth }{2cm}
- \usepackage{mathtools,amssymb,booktabs,amsthm,todonotes,colortbl}
- \def\mod{~\text{mod}~}
- \usepackage{mathptmx}
- \usepackage{caption,setspace}
- \usepackage{longtable}
- \DeclareCaptionStyle{italic}{labelfont={bf},textfont={it},labelsep=colon}
- \captionsetup[figure]{style=italic,format=hang,singlelinecheck=true,font={stretch=1.2}}
- \captionsetup[table]{style=italic,format=hang,singlelinecheck=true,font={stretch=1.2}}
- \def\novspacing{\setlength{\aboverulesep}{0pt}\setlength{\belowrulesep}{0pt}}
- \def\vspacing{\setlength{\aboverulesep}{0.4ex}\setlength{\belowrulesep}{0.65ex}}
- \newcommand{\DC}[1]{\textcolor{red}{#1}}
- \setcounter{topnumber}{2}
- \setcounter{bottomnumber}{2}
- \setcounter{totalnumber}{4}
- \renewcommand{\topfraction}{0.85}
- \renewcommand{\bottomfraction}{0.85}
- \renewcommand{\textfraction}{0.15}
- \renewcommand{\floatpagefraction}{0.7}
- \def\wpd{\text{\textit{wpd}}}
- \def\wpdsub#1{\text{\textit{wpd}}_{\text{#1}}}
- \def\Dnull{D_{\emptyset}}
- \def\Df{D_{\!f}}
- \def\Dfx{D_{\!fx}}
- \def\Dx{D_{x}}
- \def\nsub#1{n_{\text{#1}}}
- \def\nx{n_x}
- \def\nf{n_{\!f}}
-
 output:
@@
   keep_tex: yes
+  includes:
+    in_header: preamble.tex
 ---
 
-```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
-options("knitr.graphics.auto_pdf" = TRUE,
-    tinytex.verbose = FALSE)
-library(knitr)
-opts_chunk$set(
- echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
- fig.path = "figure/", fig.align = "center", fig.show = "hold",
- cache = TRUE, cache.path = "cache/",
- out.width = ifelse(is_html_output(), "100%", "\\textwidth")
-)
-knitr::opts_knit$set(root.dir = here::here())
-#                           read_chunk('main.R')
-#knitr::read_chunk(here::here("paper/R/", "null_distribution.R"))
-#knitr::read_chunk(here::here("paper/R/", "mean_null.R"))
-#source(here::here("paper/R/sim_panel.R"))
-# Set up plan
-#source("_drake.R")
-# Run all code required
-#drake::r_make()
-# load each object as required
-# loadd()
-```
-
-```{r external, include = FALSE, cache = FALSE}
-read_chunk("paper/scripts/main.R")
-```
-
-```{r load}
-```
-
-```{r}
-set.seed(3215)
-```
-
-# Introduction
-
-<!-- <introducing the problem> -->
-<!-- background of the problem -->
-
-<!--Exploratory data analysis, as coined by John W. Tukey [@Tukey1977-jx] involves many iterations of finding structures and patterns that allow the data to be informative.-->
-
-Cyclic temporal granularities [@Bettini1998-ed, @Gupta2021-hd] are <!--theoretical--> temporal deconstructions that define cyclic repetitions in time, e.g.
-hour-of-day, day-of-month, or regularly scheduled public holidays.
-These granularities form ordered or unordered categorical variables.
-An example of an ordered granularity is day-of-week, where Tuesday is always followed by Wednesday, and so on.
-An unordered granularity example is \DC{week type in an academic semester: orientation, break, exam or regular classes}.
-We can use granularities to explore patterns in univariate time series by examining the distribution of the measured variable across different categories of the cyclic granularities.
-
-```{r calendar-elec, fig.height = 8, fig.cap = "Calendar displays faceted by two households are shown.
-The calendar displays are rich in information and has several components.
-For example, it can be observed easily that the level of energy consumption by household 2 is higher than household 4.
-Also, it gives an overview on when these households are away for holidays and which months consumptions are highest (Jan, Feb).
-However, when it comes to discerning periodic patterns, analyzing all possible periodic patterns through this display is overwhelming due to combination of linear and cyclic representation of time.
-For example, there is more going on in terms of peaks and troughs in id 2 compared to id 4, but it is not clear which all periodic patterns are dominant and if it differs between households."}
+```{r child="main.Rmd"}
 
 ```
-
-```{r onegran-new, fig.cap="A cyclic granularity can be considered to be a categorical variable, and used to break the data into subsets.
-Here, side-by-side boxplots overlaid on jittered dotplots explore the distribution of of energy use by a household for two different cyclic granularities: (a) hour-of-day and (b) and month-of-year.
-Daily peaks occur in morning and evening hours, indicating a working household, where members leave for and return from work.
-More volatility of usage in summer months (Jan, Feb) is probably due air conditioner use on just some days.", fig.pos="!b"}
-```
-
-As a motivating example, consider Figure \ref{fig:onegran-new} which shows electricity smart meter data plotted against two granularities (hour-of-day, month-of-year).
-The data was collected on a single household in Melbourne, Australia, over a six month period, and was previously used in @wang2020calendar.
-The categorical variable (granularity) is mapped to the x-axis, and the distribution of the response variable is displayed using both side-by-side jittered dotplots and boxplots.
-From panel (a) it can be seen that energy consumption is higher during the morning hours (5--8), when members in the household wake up, and again in the evening hours (17--20) possibly when members get back from work.
-In addition, the largest variation in energy use is in the afternoon hours (12--16), as seen in the length of the boxes.
-From panel (b), it is seen that the variability in energy usage is higher in Jan and Feb, probably due to the usage of air conditioners on some days.
-The median usage is highest in January, dips in February--April and rises again in May--June, although not to the height of January usage.
-This suggests that the household does not use as much electricity for heating as it does for air conditioning.
-A lot of households in Victoria use gas heating and hence the heater use might not be reflected in the electricity data.
-
-Many different displays could be constructed using different granularities including day-of-week, day-of-month, weekday/weekend, etc.
-However, only a few might be interesting and reveal important patterns in energy usage.
-Determining which displays have "significant" distributional differences between categories of the cyclic granularity, and plotting only these, would make for efficient exploration.
-
-```{r intro_all}
-
-```
-
-```{r id2-new2, fig.cap = "Distribution of energy consumption displayed through area quantile plots across two cyclic granularities month-of-year and hour-of-day and two households.
-The black line is the median, whereas the orange band covers the 25th to 75th percentile and the green band covers the 10th to 90th percentile.
-Difference between the 90th and 75th quantiles is less for (Jan, Feb) for the first household (a), suggesting that it is a more frequent user of air conditioner than the second household (b).
-Energy consumption for in (a) changes across both granularities, whereas for (b) daily pattern stays same irrespective of the months."}
-```
-
-<!-- comparing one and two grans for one households -->
-Exploring the distribution of the measured variable across two cyclic granularities provides more detailed information on its structure.
-For example, Figure \ref{fig:id2-new2}(a) shows the usage distribution across hour-of-day conditional on month-of-year across two households.
-It shows the hourly usage over a day does not remain the same across months.
-Unlike other months, the 75th and 90th percentile for all hours of the day in January are high, similar, and are not characterized by a morning and evening peak.
-The household in Figure \ref{fig:id2-new2}(b) has 90th percentile consumption higher in summer months relative to autumn or winter, but the 75th and 90th percentile are far apart in all months, implying that the second household resorts to air conditioning much less regularly than the first one.
-The differences seem to be more prominent across month-of-year (facets) than hour-of-day (x-axis) for this household, whereas they are prominent for both cyclic granularities for the first household.
-
-<!-- The problem and its dimension -->
-Are all four displays in Figures \ref{fig:onegran-new} and \ref{fig:id2-new2} useful in understanding the distributional difference in energy usage?
-Which ones are more useful than others?
-If $N_C$ is the total number of cyclic granularities of interest, the number of displays that could be potentially informative is $N_C$ when considering displays of the form in Figure \ref{fig:onegran-new}.
-The dimension of the problem, however, increases when considering more than one cyclic granularity.
-When considering displays of the form in Figure \ref{fig:id2-new2},
-there are $N_C(N_C-1)$ possible pairwise plots exhaustively, with one of the two cyclic granularities acting as the conditioning variable.
-This can be overwhelming for human consumption even for moderately large $N_C$. It is therefore  useful to identify those displays that are informative across at least one cyclic granularity.
-
-<!-- Moreover, the volatility in consumption are almost equal and high for all hours in Jan, whereas variability is most in the evening hours for other months.
-The distribution of consumption across different hours of the day look similar for Apr, May and Jun, characterized by a distinct morning, afternoon and evening peaks and higher variability in evening hours -->
-
-<!-- months Jan and Feb not only have a high median consumption, but also more variability, possibly due to the usage of air conditioning.
-The other months shows more consistent behavior with the energy consumption rising in May and June.
--->
-
-<!-- Scagnostics literature, other literature and why we need more/different -->
-
-This problem is similar to Scagnostics (Scatterplot Diagnostics) by @tukey1988computer, which are used to identify meaningful patterns in large collections of scatterplots.
-Given a set of $v$ variables, there are $v(v-1)/2$ pairs of variables, and thus the same number of possible pairwise scatterplots.
-Therefore, even for small $v$, the number of scatterplots can be large, and scatterplot matrices (SPLOMs) can easily run out of pixels when presenting high-dimensional data.
-@Dang2014-tw and @wilkinson2005graph provide potential solutions to this, where a few characterizations can be used to locate anomalies in density, shape, trend, and other features in the 2D point scatters.
-
-In this paper, we provide a solution to narrowing down the search from $N_C(N_C-1)$ conditional distribution plots by introducing a new distance measure that can be used to detect significant distributional differences across cyclic granularities.<!-- harmonies and why it is not enough --> This work is a natural extension of our previous work [@Gupta2021-hd] which narrows down the search from $N_C(N_C-1)$ plots by identifying pairs of granularities that can be meaningfully examined together (a "harmony"), or when they cannot (a "clash").
-However, even after excluding clashes, the list of harmonies left may be too large for exhaustive exploration.
-Hence, there is a need to reduce the search even further by including only those harmonies that contain useful information.
-
-@inference and @Majumder2013-hb present methods for statistical significance testing of visual findings using human cognition as the statistical tests.
-In this paper, the visual discovery of distributional differences is facilitated by choosing a threshold for the proposed numerical distance measure, eventually selecting only those cyclic granularities for which the distributional differences are sufficient to make it an interesting display.
-
-<!-- \ref{fig:id2-new2} shows the distribution of energy consumption across hour-of-day conditional on month-of-year.
-\ref{fig:id2-new2}(a) shows that energy consumption is higher during the morning hours when members in the household wake up and then again higher in the evening hours possibly when members are back from work with them showing maximum variable behavior in the afternoon hours.
-\ref{fig:id2-new2}(b) shows the months Jan and Feb not only have a high median consumption, but also more variability, possibly due to the usage of air conditioning.
-The other months shows more consistent behavior with the energy consumption rising in May and June.
-\ref{fig:id2-new2} adds to this information, by showing that hours in Jan do not necessarily follow the same pattern across the day (due to Holidays, people visiting).
-Moreover, the volatility in consumption are almost equal and high for all hours in Jan, whereas variability is most in the evening hours for other months.
-The distribution of consumption across different hours of the day look similar for Apr, May and Jun, characterized by a distinct morning, afternoon and evening peaks and higher variability in evening hours.
--->
-
-<!-- # interaction for two households, importance could be across one -->
-
-<!-- Even when it is known which all interactions to look at, all of them would not be interesting and that too will vary across different households. -->
-
-<!-- calendar plots -->
-<!-- The authors show how hour-of-the-day interact with weekdays and weekends and then move on to use calendar display to show daily schedules.
-The calendar display has several components in it, which helps us to look at energy consumption across hour-of-day, day-of-week, week-of-month, and month-of-year at once.
-Some interaction of these cyclic granularities, for example, how day-of-week relates to month-of-year, could also be interpreted from this display.
-This is a great way for having an overview of energy consumption.
-However, if one wants to understand the repetitiveness in energy behavior and how they interact in greater detail, it is not easy to comprehend the interactions of all cyclic granularities from this display, due to the combination of linear and cyclic representation of time.
-For example, this display might not be the best to understand how hour-of-the-day or month-of-year varies across week-of-the-month as well as with each other.
-Furthermore, it is not clear what all interactions of cyclic granularities should be read from this display as there could be many combinations that one can look at.
-Moreover, there could be non-conventional cyclic granularities, which could potentially become useful depending on the context.
--->
-
-<!-- context when it could be useful is monitoring heart rates.
-There are devices that can detect each heartbeat and transfer the data to a receiver such as a watch or phone.
-These data could be available for a temporal scale as fine as a minute and it could be of interest to see regular patterns across any deconstruction of time coarser than a minute.
--->
-
-```{r id4, fig.cap = "something2", eval = FALSE}
-
-```
-
-<!-- Again, look at \ref{fig:} c and d, where energy consumption for these two households are plotted against (weekend/weekday, week-of-month).
-Here, for both households, the pattern of energy consumption vary across different weeks of the month irrespective of the fact it is a weekday or weekend.
-In that respect, the harmony pair (month-of-year, hour-of-day) seems to be more informative than (weekend/weekday, week-of-month) for the first household.
--->
-
-<!-- Take an example of a data set which are observed at fine temporal scales, like that of NYC bike usage available at https://www.citibikenyc.com/system-data.
-We use the `nyc_bikes` data set from the R package `tsibbledata` which takes a sample of 10 bikes for the year 2018.
-The `start_time` and the `stop_time` are recorded to a fineness of seconds.
-We can look at pair of cyclic granularities (hour_day, wknd_wday) or (week_month, day_week) to see how these periodicities interact.
-But there could be other pairs that are important too.
-How to understand which pairs are sufficient to explore given the data set without losing much information about the data.
--->
-
-<!-- When we need to understand the interplay of different periodicities in a high frequency temporal datasets, we have many choices to consider.
-In [@wang2020tsibble] and [@wang2020calendar], periodicities are explored across hour of the day and day of the week or months.
-But calendar effects are not restricted to conventional day-of-week or month-of-year deconstructions.
--->
-
-<!-- If we have $n$ periodic linear granularities in the hierarchy table, then $n(n-1)/2$ circular or quasi-circular cyclic granularities could be constructed. -->
-
-<!-- Our contributions in this paper are: -->
-
- <!-- * We introduce a new distance measure for detecting periodic interactions. This induces data reduction which allows for identification of patterns, if any, in the time series data. -->
-
- <!-- * We show that the distance metric could be used to rank the periodic patterns based on how well they capture the variation in the measured variable as they have been normalized for different number of comparisons.
--->
-
- <!-- * We device a framework for choosing a threshold, which will result in detection of only significantly interesting periodic patterns in the time series data. -->
-
- <!-- * -->
-
- <!-- * ; -->
-
- <!-- * show that the proposed distance metric could be used to rank the interesting patterns across different datasets and temporal granularities since they have been normalized for relevant parameters.
--->
-
-The article is organized as follows.
-Section \ref{sec:computation-wpd} introduces a distance measure for detecting distributional difference in temporal granularities, which enables identification of patterns in the time series data;
-Section \ref{sec:rank-wpd} devises a selection criterion by choosing a threshold, which results in detection of only significantly interesting patterns.
-Section \ref{sec:simulations} provides a simulation study on the proposed methodology.
-Section \ref{sec:application-wpd} presents an application to residential smart meter data in Melbourne to show how the proposed methodology can be used to automatically detect temporal granularities along which distributional differences are significant.
-
-<!-- acts as a way to automatically detect periodic patterns in time series. -->
-
-<!-- Also, ranking the remaining harmony pairs based on how well they capture the variation in the measured variable could be potentially useful.  -->
-
-<!-- Talk about Scagnostics: Tukey -->
-
-# Proposed distance measure {#sec:computation-wpd}
-
-We propose a measure called Weighted Pairwise Distances ($\wpd$) to detect distributional differences in the measured variable across cyclic granularities.
-
-## Principle
-
-(ref:null4by2) An example illustrating the principle of the proposed distance measure, displaying the distribution of a normally distributed variable in four panels each with two x-axis categories and three facet levels, but with different designs.
-Panel (a) is not interesting as the distribution of the variable does not depend on x or facet categories.
-Panels (b) and (c) are more interesting than (a) since there is a change in distribution either across facets (b) or x-axis (c).
-Panel (d) is most interesting in terms of capturing structure in the variable as the distribution of the variable changes across both facet and x-axis variable.
-The value of our proposed distance measure is presented for each panel, the relative differences between which will be explained later in Section \@ref(sec:ranking).
-
-```{r null4by2, fig.cap = "(ref:null4by2)", fig.pos="!b"}
-```
-
-The principle behind the construction of $\wpd$ is explained through a simple example in Figure&nbsp;\ref{fig:null4by2}.
-Each of these figures describes a panel with two x-axis categories and three facet levels, but with different designs.
-Figure \ref{fig:null4by2}a has all categories drawn from a standard normal distribution for each facet.
-It is not a particularly interesting display, as the distributions do not vary across x-axis or facet categories.
-Figure \ref{fig:null4by2}b has x categories drawn from the same distribution, but across facets the distributions are three standard deviations apart.
-Figure \ref{fig:null4by2}c exhibits the opposite situation where distribution between the x-axis categories are three standard deviations apart, but they do not change across facets.
-In Figure \ref{fig:null4by2}d, the distribution varies across both facet and x-axis categories by three standard deviations.
-
-If the panels are to be ranked in order of capturing maximum variation in the measured variable from minimum to maximum, then an obvious choice would be (a) followed by (b), (c) and then (d).
-It might be argued that it is not clear if (b) should precede or succeed (c) in the ranking.
-Gestalt theory suggests items placed at close proximity can be compared more easily, because people assume that they are in the same group and apart from other groups.
-With this principle in mind, Panel (b) is considered less informative compared to Panel (c) in emphasizing the distributional differences.
-
-For displays showing a single cyclic granularity rather than pairs of granularities, we have only two design choices corresponding to no difference and significant differences between categories of that cyclic granularity.
-
-The proposed measure $\wpd$ is constructed in such a way that it can be used to rank panels of different designs as well as test if a design is interesting.
-This measure is aimed to be an estimate of the maximum variation in the measured variable explained by the panel.
-A higher value of $\wpd$ would indicate that the panel is interesting to look at, whereas a lower value would indicate otherwise.
-
-<!-- To compute the maximum variation of the measured variable within each panel, the distributional differences need to be measured for both within-group and between-group categories.
-Moreover, a tuning parameter specifying the weightage given to within-facet or between-facet categories can help to choose between designs like \ref{fig:null4by2}b and c.
-The maximum of all these weighted differences serves as an estimate of the maximum variation in the panel and is taken as the value of $\wpd$.
--->
-
-<!-- Larger differences imply stronger patterns, whereas small difference would imply that the underlying structure is not changing within or between group. -->
-
-<!-- A distance measure aimed to capture the structure of the measured variable in designs like \ref{fig:null4by2}, should ideally estimate these within-group and between-group variations. -->
-
-<!-- \noindent Intuitively, while finding a structure or measuring the strength of patterns in Figure \ref{fig:null4by2}, it makes sense to look for within-group and between-group variations.
-Larger variation would imply stronger patterns, whereas small variation would imply the underlying structure is not changing within or between group.
--->
-<!-- Thus, a distance measure aimed to capture this structure should ideally estimate these within-group and between-group variations.
-One of the potential ways to do this is to measure the distances between distributions of the continuous random variable measured within and between groups, weigh them basis if they are within or between groups and then take the maximum of those distances as an estimate of the maximum variation in the structure.
-This section starts with possible ways of characterizing distributions and computing distances between them and then describe in details how the measure $\wpd$ is defined.
--->
-
-<!-- This is similar to @ieee-irish where the authors compute the Jensen Shannon distance between two density estimates by computing percentiles and stresses the advantages to working with percentiles rather than the raw data directly in case of missing observations.
-Working with quantiles also ensure that unsynchronized time series could be handled.
--->
-
-<!-- Hence, with reference to the graphical design in @Gupta2021-hd, therefore the idea would be to rate a harmony pair higher if the variation between different levels of the x-axis variable is higher on an average across all levels of the facet variables.
--->
-
-<!-- To elaborate further, look at the examples in Figure \ref{}, where Figure \ref{}a represents the panel design with distribution of each x categories drawn from N(5, 10) distribution.
-It could be observed that the graph is not particularly interesting, as there is no significant change in distribution between x-axis levels or facets.
-Figure \ref{}b represents the same panel design with no difference in distribution of x-axis categories within a facet, but different distribution of x-axis categories for different facets.
-For example, if there are 4 facet levels and 2 x-axis levels, data is generated in the way as described in Table \ref{}.
-Figure \ref{}b exhibits an opposite situation where the x-axis within facets are different but not across facets.
--->
-<!-- Figure \ref{}d takes it further by varying the distribution across both facet and x-axis categories. -->
-
-<!-- A "significant" cyclic granularity have at least two categories which are significantly different from each other.
-It does not tell you which categories are statistically significantly different from each other -->
-
-<!-- in the same group would be important to bring out different patterns of the data. -->
-
-## Notation
-
-Let the number of cyclic granularities considered in the display be $m$.
-The notations and methodology are described in detail for $m=2$.
-But it can be easily extended to $m>2$.
-Consider two cyclic granularities $A$ and $B$, such that $A = \{a_j: j = 1, 2, \dots, \nx\}$ and $B = \{b_k: k = 1, 2, \dots, \nf\}$ with $A$ placed across the x-axis and $B$ across facets.
-Let $v = \{v_t: t = 0, 1, 2, \dots, T-1\}$ be a continuous variable observed across $T$ time points.
-This data structure with $\nx$ x-axis levels and $\nf$ facet levels is referred to as a $(\nx, \nf)$ panel.
-For example, a $(2, 3)$ panel will have cyclic granularities with two x-axis levels and three facet levels.
-Let the four elementary designs as described in Figure \ref{fig:null4by2} be $\Dnull$ (referred to as "null distribution") where there is no difference in distribution of $v$ for $A$ or $B$, $\Df$ denotes the set of designs where there is difference in distribution of $v$ for $B$ and not for $A$.
-Similarly, $\Dx$ denotes the set of designs where difference is observed only across A.
-Finally, $\Dfx$ denotes those designs for which difference is observed across both $A$ and $B$.
-We can consider a single granularity ($m = 1$) as a special case of two granularities with $\nf = 1$.
-
-```{r notations}
-
-```
-
- <!-- Thus, by CLT, ${\chi^2}_{m} \tilde{} N(m, 2m)$, which would depend on the number of discretization used to approximate the continuous distribution. -->
- <!-- Then $b_n = 1-1/n$ quantile of the normal distribution and $a_n = 1/[n*\phi(b_n)]$ where $\phi$ is the normal density function. $n$ is the number of pairwise comparisons being made. -->
-
-<!-- The Jensen-Shanon distance between two probability distribution $p_1$ and $p_2$ is given by $$d = [D(p_1, r) + D(p_2, r)]/2 \quad where \quad r = (p_1 + p_2)/2$$ where, -->
-<!-- $$D(p_1,p_2) = \int^{\infty}_{-\infty}p_1(x)log\frac{p_1(x)}{p_2(x)}\,dx$$ is the Kullback-Leibler divergence between $p_1$ and $p_2$.  -->
-
-<!-- We call this measure of variation as Median Maximum Pairwise Distances (MMPD). -->
-
-<!-- #### Distribution of Jensen-Shannon distances -->
-
-<!-- Jensen-Shannon distances (JSD) are distributed as chi-squared with $m$ df where we discretize the continuous distribution with $m$ discrete values.
-Taking sample percentiles to approximate the integral would mean taking $m = 99$.
--->
-<!-- With large $m$, chi-squared is asymptotically normal by the CLT.
-Thus, by CLT, ${\chi^2}_{m} \tilde{} N(m, 2m)$, which would depend on the number of discretization used to approximate the continuous distribution.
-Then $b_n = 1-1/n$ quantile of the normal distribution and $a_n = 1/[n*\phi(b_n)]$ where $\phi$ is the normal density function.
-$n$ is the number of pairwise comparisons being made.
--->
-
-## Computation
-
-The computation of the distance measure $\wpd$ for a panel involves characterizing distributions, computing distances between distributions, choosing a tuning parameter to specify the weight for different groups of distances and summarizing those weighted distances appropriately to estimate maximum variation.
-Furthermore, the data needs to be appropriately transformed to ensure that the value of $\wpd$ emphasizes detection of distributional differences across categories and not across different data generating processes.
-
-<!-- but not when underlying distributions are different -->
-
-<!-- irrespective of the distribution from which the data is generated. -->
-
-<!-- is aimed to capture structure and patterns by estimating the maximum variation of the measured variable within a panel. $\wpd$ -->
-
-<!-- the distributional differences need to be measured for both within-group and between-group categories.
-Moreover, a tuning parameter specifying the weightage given to within-facet or between-facet categories can help to choose between designs like \ref{fig:null4by2}b and c.
-The maximum of all these weighted differences serves as an estimate of the maximum variation in the panel and is taken as the value of $\wpd$.
--->
-
-### Data transformation {-}
-
-The intended aim of $\wpd$ is to capture differences in categories irrespective of the distribution from which the data is generated.
-Hence, as a pre-processing step, the raw data is normal-quantile transformed (NQT) [@Krzysztofowicz1997-bv], so that the transformed data follows a standard normal distribution.
-The empirical NQT involves the following steps:
-
- 1. The observations of measured variable $v$ are sorted from the smallest to the largest observation $v_{(1)},\dots, v_{(n)}$.
- 2. The cumulative probabilities $p_{(1)},\dots, p_{(n)}$ are estimated using $p_{(i)} = i/(n + 1)$  [@Hyndman1996-ty] so that $p_{(i)} = \text{Pr}(v \leq v_{(i)})$.
- 3. Each observation $v_{(i)}$ of $v$ is transformed into $v^*(i) = \Phi^{-1}(p(i))$, with $\Phi$ denoting the standard normal distribution function.
-
-### Characterizing distributions {-}
-
-Multiple observations of $v$ correspond to the subset $v_{jk} = \{s: A(s) = j, B(s) = k\}$.
-The number of observations might vary widely across subsets due to the structure of the calendar, missing observations or uneven locations of events in the time domain.
-In this paper, quantiles of $\{v_{jk}\}$ are chosen as a way to characterize distributions for the category $(a_j, b_k)$, $\forall j\in \{1, 2, \dots, \nx\}, k\in \{1, 2, \dots, \nf\}$.
-We use percentiles with $p = {0.01, 0.02, \dots, 0.99}$ to reduce the computational burden in summarizing distributions.
-
-<!-- The benefit of using a non-parametric estimator is that there are less rigid assumptions made about the nature of the underlying distribution of the data.
-Sample quantiles could be used for estimating population quantiles in a non-parametric setup.
-describes the many ways of defining sample quantiles and recommends the use of median-unbiased estimator because of _desirable properties of a quantile estimator and can be defined independently of the underlying distribution._.
--->
-
-<!-- in this paper. -->
-
-<!-- Each $v_{jk}$'s $\forall j\in \{1, 2, \dots, \nx\}, k\in \{1, 2, \dots, \nf\}\}$ are assumed to be drawn from a continuous probability distribution and have certain characteristics.
-Shape, central tendency, and variability are the common characteristics used to describe a distribution.
--->
-
-<!-- Mean, median or mode are generally used to describe the center of the distribution, while range, standard deviation, quantiles, standard errors and confidence intervals are used to describe variability.
--->
-
-<!-- The quantile of a distribution with probability $p$ is defined as $Q(p)=F^{-1}(p) = inf\{x: F(x) >p\}$, $0<p< 1$ where $F(x)$ is the distribution function.
-There are two broad approaches to quantile estimation, viz, parametric and non-parametric.
-The benefit of using a non-parametric estimator is that there are less rigid assumptions made about the nature of the underlying distribution of the data.
-Sample quantiles could be used for estimating population quantiles in a non-parametric setup.
-@Hyndman1996-ty describes the many ways of defining sample quantiles and recommends the use of median-unbiased estimator because of _desirable properties of a quantile estimator and can be defined independently of the underlying distribution._.
-The `stats::quantile()` function in @R-language could be used for practical implementation where type = 8 refers to the algorithm corresponding to the median-unbiased estimator.
-The default quantile chosen in this paper is percentiles computed for $p = {0.01, 0.02, \dots, 0.99}$, where for example, the $99^{th}$ percentile would be the value corresponding to $p=0.99$ and hence 99% of the observations would lie below that.
--->
-
-### Distance between distributions {-}
-
-<!-- One of the most important class of divergence is the f-divergence and includes measures like Kullback-Leibler divergence, Hellinger distance etc.
-The continuous version of f -divergence is given by -->
-<!-- $$\Df(P||Q) := \int q(x)f(\frac{p(x)}{q(x)})$$, where -->
-<!-- $f : [0,\infty) \rightarrow R \cup \{\infty\}$ is a continuous convex function, and $f(1) = 0$. -->
-
-A common way to measure divergence between distributions is the Kullback-Leibler (KL) divergence [@Kullback1951-jy].
-The KL divergence denoted by $D(q_1||q_2)$ is a non-symmetric measure of the difference between two probability distributions $q_1$ and $q_2$ and is interpreted as the amount of information lost when $q_2$ is used to approximate $q_1$.
-The KL divergence is not symmetric and hence can not be considered as a "distance" measure.
-The Jensen-Shannon divergence [@Menendez1997-in] based on the Kullback-Leibler divergence is symmetric and has a finite value.
-Hence, in this paper, the pairwise distances between the distributions of the measured variable are obtained through the square root of the Jensen-Shannon divergence, called Jensen-Shannon distance (JSD), and defined by,
-$$
-  JSD(q_1||q_2) = \frac{1}{2}D(q_1||M) + \frac{1}{2}D(q_2||M),
-$$
-where $M = \frac{q_1+q_2}{2}$ and $D(q_1||q_2) := \int^\infty_{-\infty} q_1(x)f(\frac{q_1(x)}{q_2(x)})$ is the KL divergence between distributions $q_1$ and $q_2$.
-Other common measures of distance between distributions are Hellinger distance, total variation distance and Fisher information metric.
-
-<!-- Furthermore, these distances are distributed as chi-squared with $m$ degrees of freedom [@Menendez1997-in], if the continuous distribution is being discretized with $m$ discrete values.
-Taking sample percentiles to approximate the integral would mean taking $m = 99$.
-As the degrees of freedom $m$ get larger, the chi-square distribution approaches the normal distribution.
--->
-
-### Within-facet and between-facet distances {-}
-
-```{r distance-explain, fig.cap = "Within and between-facet distances shown for two cyclic granularities A and B, where A is mapped to x-axis and B is mapped to facets.
-The dotted lines represent the distances between different categories.
-Panels 1) and 2) show the between-facet distances.
-Panels 3) and 4) are used to illustrate within-facet distances when categories are un-ordered or ordered respectively.
-When categories are ordered, distances should only be considered for consecutive x-axis categories.
-Between-facet distances are distances between different facet levels for the same x-axis category, for example, distances between {($a_1$,$b_1$) and ($a_1$, $b_2$)} or {($a_1$,$b_1$) and ($a_1$, $b_3$)}.", fig.pos="!b"}
-
-```
-
-Pairwise distances could be within-facets or between-facets for $m = 2$.
-Figure \ref{fig:distance-explain} illustrates how they are defined.
-Pairwise distances are within-facets when $b_{k} = b_{k'}$, that is, between pairs of the form $(a_{j}b_{k}, a_{j'}b_{k})$ as shown in panel (3) of Figure \ref{fig:distance-explain}.
-If categories are ordered (like all temporal cyclic granularities), then only distances between pairs where $a_{j'} = (a_{j+1})$ are considered (panel (4)).
-Pairwise distances are between-facets when they are considered between pairs of the form $(a_{j}b_{k}, a_{j}b_{k'})$.
-There are a total of ${\nf \choose 2}\nx$ between-facet distances, and ${\nx \choose 2}\nf$ within-facet distances if they are ordered and $\nf(\nx-1)$ within-facet distances if they are unordered.
-
-### Tuning parameter {-}
-
-For displays with $m>1$ granularities, we can use a tuning parameter to specify the relative weight given to each granularity.
-In general, the tuning parameters should be chosen such that $\sum_{i=1}^m \lambda_i = 1$.
-
-Following the general principles of Gestalt theory, we wish to weight more heavily granularities that are plotted closer together.
-For $m=2$ we choose  $\lambda_x = \frac{2}{3}$ for the granularity on the x-axis and $\lambda_f = \frac13$ for the granularity mapped to facets, giving a relative weight of $2:1$ for within-facet to between-facet distances.
-No human experiment has been conducted to justify this ratio.
-Specifying $\lambda_x>0.5$ will weight within-facet distances more heavily, while $\lambda_x <0.5$ would weight the between-facet distances more heavily.
-(See the supplements for more details.).
-
-### Raw distance measure {-}
-
-The raw distance measure, denoted by $\wpdsub{raw}$, is computed after combining all the weighted distance measures appropriately.
-First, NQT is performed on the measured variable $v_t$ to obtain $v^*_t$ (_data transformation_).
-Then, for a fixed harmony pair $(A, B)$, percentiles of $v^*_{jk}$ are computed and stored in $q_{jk}$ (_distribution characterization_).
-This is repeated for all pairs of categories of the form $(a_{j} b_{k}, a_{j'}b_{k'}): \{a_j: j = 1, 2, \dots, \nx\}, B = \{ b_k: k = 1, 2, \dots, \nf\}$.
-The pairwise distances between pairs $(a_{j} b_{k}, a_{j'}b_{k'})$ denoted by $d_{(jk, j'k')} = JSD(q_{jk}, q_{j'k'})$ are computed (_distance between distributions_).
-The pairwise distances (_within-facet and between-facet_) are transformed using a suitable _tuning parameter_ ($0<\lambda<1$) depending on if they are within-facet($d_w$) or between-facets($d_b$) as follows:
-\begin{equation}\label{def:raw-wpd}
-  d*_{(j,k), (j'k')} =
-    \begin{cases}
-      \lambda d_{(jk), (j'k')},& \text{if } d = d_w;\\
-      (1-\lambda) d_{(jk), (j'k')},       & \text{if } d = d_b.
-    \end{cases}
-\end{equation}
-The $\wpdsub{raw}$ is then computed as
-$$
-  \wpdsub{raw} = \max_{j, j', k, k'}(d*_{(jk), (j'k')}) \qquad\forall j, j' \in \{1, 2, \dots, \nx\},\quad k, k' \in \{1, 2, \dots, \nf\}
-$$
-The statistic "maximum" is chosen to combine the weighted pairwise distances since the distance measure is aimed at capturing the maximum variation of the measured variable within a panel.
-The statistic "maximum" is, however, affected by the number of comparisons (resulting pairwise distances).
-For example, for a $(2, 3)$ panel, there are $6$ possible subsets of observations corresponding to the combinations $(a_1, b_1), (a_1, b_2), (a_1, b_3), (a_2 ,b_1), (a_2 ,b_2), (a_2, b_3)$, whereas for a $(2, 2)$ panel, there are only $4$ possible subsets $(a_1, b_1), (a_1, b_2), (a_2 ,b_1), (a_2 ,b_2)$.
-Consequently, the measure would have higher values for the panel $(2, 3)$ as compared to $(2, 2)$, since maximum is taken over higher number of pairwise distances.
-
-## Adjusting for the number of comparisons
-
-Ideally, it is desired that the proposed distance measure takes a higher value only if there is a significant difference between distributions across categories, and not because the number of categories $\nx$ or $\nf$ is high.
-That is, under designs like $\Dnull$, their distribution should not differ for a different number of categories.
-Only then the distance measure could be compared across panels with different levels.
-This calls for an adjusted measure, which normalizes for the different number of comparisons.
-
-Two approaches for adjusting the number of comparisons are discussed, both of which are substantiated using simulations.
-The first one defines an adjusted measure $\wpdsub{perm}$ based on the permutation method to remove the effect of different comparisons.
-The second approach fits a model to represent the relationship between $\wpdsub{raw}$ and the number of comparisons and defines the adjusted measure ($\wpdsub{glm}$) as the residual from the model.
-
-### Permutation approach {-}
-
-This method is somewhat similar in spirit to bootstrap or permutation tests, where the goal is to test the hypothesis that the groups under study have identical distributions.
-This method accomplishes a different goal of finding the null distribution for different groups (panels in our case) and standardizing the raw values using that distribution.
-The values of $\wpdsub{raw}$ is computed on many ($\nsub{perm}$) permuted data sets and stored in $\wpdsub{perm-data}$.
-Then $\wpdsub{perm}$ is computed as follows:
-\begin{align*}
-  \wpdsub{perm} = \frac{(\wpdsub{raw} - \text{mean}(\wpdsub{perm-data}))}{\text{sd}(\wpdsub{perm-data})},
-\end{align*}
-where $\text{mean}(\wpdsub{perm-data})$ and $\text{sd}(\wpdsub{perm-data})$ are the mean and standard deviation of $\wpdsub{perm-data}$ respectively.
-Standardizing $\wpd$ in the permutation approach ensures that the distribution of $\wpdsub{perm}$ under $\Dnull$ has zero mean and unit variance across all comparisons.
-While this works successfully to make the location and scale similar across different $\nx$ and $\nf$, it is computationally heavy and time consuming, and hence less user-friendly.
-Hence, another approach to adjustment, with potentially less computational time, is proposed.
-
-<!-- for the $l^{th}$ panel and -->
-
-### Modeling approach {-}
-
-In this approach, a Gamma generalized linear model (GLM) for $\wpdsub{raw}$ is fitted with the number of comparisons as the explanatory variable.
-Since, $\wpdsub{raw}$ is a Jensen-Shannon distance, it follows a Chi-square distribution [@Menendez1997-in], which is a special case of a Gamma distribution.
-Furthermore, the mean response is bounded, since any JSD is bounded by $1$ if a base $2$ logarithm is used [@Lin1991-pt].
-Hence, by @Faraway2016-uk, an inverse link is used for the model, which is of the form $y = a+b*\log(z) + e$, where $y = \wpdsub{raw}$, $z = (\nx*\nf)$ is the number of groups and $e$ are idiosyncratic errors.
-Let $\text{E}(y) = \mu$ and $a + b*\log(z) = g(\mu)$ where $g(\mu)= 1/\mu$ and $\hat \mu = 1/(\hat a + \hat b \log(z))$.
-The residuals from this model $(y-\hat y) = (y-1/(\hat a + \hat b \log(z)))$ would be expected to have no dependency on $z$.
-Thus, $\wpdsub{glm}$ is defined as the residuals from this model given by
-$$\wpdsub{glm} = \wpdsub{raw} - 1/(\hat a + \hat b*\log(\nx*\nf))$$
-The distribution of $\wpdsub{glm}$ under $\Dnull$ will have approximately zero mean and a constant variance (not necessarily 1).
-
-### Combination approach {-}
-
-The simulation results (in Section \ref{sec:simulations}) show that the distribution of $\wpdsub{glm}$ under the null design is similar for high $\nx$ and $\nf$ (levels higher than $5$) but less so for lower values of $\nx$ and $\nf$.
-Hence, a combination approach is proposed where we use a permutation approach for categories with small numbers of levels, and a modeling approach for categories with higher numbers of levels.
-This ensures that the computational load of the permutation approach is alleviated while maintaining a similar null distribution across different categories.
-This approach, however, requires that the adjusted variables from the two approaches are brought to the same scale.
-We define $\wpdsub{glm-scaled} = \wpdsub{glm}*\sigma^2_{\text{perm}}/\sigma^2_{\text{glm}}$ as the transformed $\wpdsub{glm}$ with a similar scale as $\wpdsub{perm}$.
-The adjusted measure from the combination approach, denoted by $\wpd$ is then defined as follows:
-\begin{equation}
-\wpd = \begin{cases}
-         \wpdsub{perm},       & \text{if $\nx, \nf \le 5$};\\
-         \wpdsub{glm-scaled}  & \text{otherwise}.\\
-       \end{cases}
-\end{equation}
-
-<!-- ### Algorithm -->
-
-<!-- The distance measure $\wpd$ between two cyclic granularities $A$ and $B$ is aimed to capture the strength of the structure by estimating the maximum within-group and between-group variations.
-Furthermore, -->
-
-<!-- The steps employed for computing $\wpd$ is summarized as follows: -->
-
-<!-- The values of $\wpd$ indeed depend upon the underlying distribution.
-This is also not desirable as the intended aim of $\wpd$ is to capture differences in categories irrespective of the distribution from which the data is generated.
-The steps employed for computing the distance measure is summarized as follows: -->
-
-<!-- Hence, differences in distributions of the measured variable are computed between all pairs of categories $(a_{j} b_{k}, a_{j'}b_{k'}): j = 1, 2, \dots, \nx\}, B = \{ b_k: k = 1, 2, \dots, \nf\}$.
-Percentiles of $v_{jk}$ and $v_{j'k'}$ are computed and stored in $q_{jk}$ and $q_{j'k'}$ respectively.
-Then the pairwise distances between pairs $(a_{j} b_{k}, a_{j'}b_{k'})$ be denoted as $d_{(jk, j'k')} = JSD(q_{jk}, q_{j'k'})$ is computed.
-Pairwise distances could be within-facets or between-facets.
-Figure \ref{fig:distance-explain} illustrates how the within-facet or between-facet distances are defined.
-Pairwise distances are within-facets ($d_{w}$) when $b_{k} = b_{k'}$, that is, between pairs of the form $(a_{j}b_{k}, a_{j'}b_{k})$ as shown in panel (3) of Figure \ref{fig:distance-explain}.
-If categories are ordered (like all temporal cyclic granularities), then only distances between pairs where $a_{j'} = (a_{j+1})$ are considered (panel (4)).
-Pairwise distances are between-facets ($d_{b}$) when they are considered between pairs of the form $(a_{j}b_{k}, a_{j}b_{k'})$.
-Number of between-facet distances would be $^{\nf}C_2*\nx$ and number of within-facet distances are $\nf*(\nx-1)$ (ordered) and $^{\nx}C_2*\nf$ (un-ordered).
-The pairwise distances $d_{(jk, j'k')}$ are transformed using a suitable tuning parameter ($0<\lambda<1$) depending on if they are $d_{b}$ or $d_{w}$ as follows: -->
-
-<!-- 5. Compute distribution of maximum distance ($M$) by shuffling the data $200$ times and finishing Steps1-4 in each case. Scale $M$ using the mean and sd of the distribution.
-
-5. Use Steps 1-4 to compute maximum distance for $\forall k \in \{1, 2, \ldots, \nf\}$.
-
-6. Compute the distance measure MMPD_raw = median $(M_1, M_2, \dots, M_K)$.
-
-<!-- All of these distances are then aggregated by taking the maximum from these distances to obtain $\wpd$. -->
-
-<!-- _j$ maps index set to a set $\{B_\ell \mid \ell =1,\dots,L\}$.
-Here, $A_k$ and $B_\ell$ are the levels/categories corresponding to $C_i$ and $C_j$ respectively.
-Let $S_{k\ell}$ be a subset of the index set such that for all $s \in S_{k\ell}$, $C_i(s) = A_k$ and $C_j(s) = B_\ell$.
-There are $KL$ such data subsets, one for each combination of levels ($A_k$, $B_\ell$).
-Moreover, consider that in the graphical space, $C_i$ is mapped to facets and $C_j$ is mapped to x-axis.
--->
-
- <!-- old -->
-<!-- Consider two cyclic granularities $C_i$ and $C_j$, such that $C_i$ maps index set to a set $\{A_k \mid k=1,\dots,\nf\}$ and $C_j$ maps index set to a set $\{B_\ell \mid \ell =1,\dots,L\}$.
-Here, $A_k$ and $B_\ell$ are the levels/categories corresponding to $C_i$ and $C_j$ respectively.
-Let $S_{k\ell}$ be a subset of the index set such that for all $s \in S_{k\ell}$, $C_i(s) = A_k$ and $C_j(s) = B_\ell$.
-There are $KL$ such data subsets, one for each combination of levels ($A_k$, $B_\ell$).
-Moreover, consider that in the graphical space, $C_i$ is mapped to facets and $C_j$ is mapped to x-axis.
--->
-
-<!-- The algorithm employed for computing the distance measure is summarized as follows: -->
-
-<!-- 1. Fix harmony pair $(C_i, C_j)$. -->
-
-<!-- 2. Fix $k$. Then there are $L$ groups corresponding to level $A_k$ of $C_i$. -->
-
-<!-- 3. Compute $m = \binom{L}{2}$ pairwise distances between distributions of $L$ unordered levels and $m = L-1$ pairwise distances for $L$ ordered categories. -->
-
-<!-- 4. Identify maximum within the $m$ computed distances. -->
-
-<!-- <!-- 5. Compute distribution of maximum distance ($M$) by shuffling the data $200$ times and finishing Steps1-4 in each case. Scale $M$ using the mean and sd of the distribution. -->
-
-<!-- 5. Use Steps 1-4 to compute maximum distance for $\forall k \in \{1, 2, \ldots, \nf\}$. -->
-
-<!-- 6. Compute the distance measure MMPD_raw = median $(M_1, M_2, \dots, M_K)$. -->
-
-<!-- \begin{algorithm}[!thb] -->
-<!-- 	\caption{Calculation for a raw distance measure between two cyclic granularities $A = \{ a_j: j = 1, 2, \dots, \nx\}$, $B = \{ b_k: k = 1, 2, \dots, \nf\}$ with $A$ placed across x-axis and $B$ across facets.}\label{alg:scoreopt}.
--->
-<!-- 	\begin{algorithmic}[1] -->
-<!-- 		\Procedure{RawMMPD}{$A = \{ a_j: j = 1, 2, \dots, \nx\}$, $B = \{ b_k: k = 1, 2, \dots, \nf\}$, $v = \{ v_t: t = 1, 2, \dots, T\}$}. -->
-<!-- 		\For{$k=1:\nf$, $j=1:\nx$} -->
-<!-- 		\State Find distances between pairs of all possible combinations of categories $(a_jb_k,a_j'b_k')$ by computing JSD between quantiles of the measured variable $q(v)$ across these combinations.
--->
-<!-- 		\State $d \gets JSD(\tilde{q(v)_{a_{j}b_{k}}},\tilde{q(v)_{a_{j}'b_{k}'}})$ -->
-<!-- 		\If {$b_k = b_k'$} -->
-<!-- 		\State $d* \gets \lambda d$ \Comment{upweight within-facet distances} -->
-<!-- 		\Else -->
-<!-- 		\State $d* \gets 1/\lambda d $ \Comment{downweight across-facet distances} -->
-<!-- 		\EndFor -->
-<!-- 		\State Set the raw distance measure as $max(d*)$ where max is taken over all $j, j', k, k'$. -->
-
-<!-- 		\EndProcedure -->
-<!-- 	\end{algorithmic} -->
-<!-- \end{algorithm} -->
-
-<!-- A stronger measure "max" is chosen for aggregating x-axis categories compared to "median" for aggregating facet categories as the measure is intended to put more importance in pointing towards distributional differences between x-axis categories than for facet categories.
--->
-
-<!-- ## Properties of $\wpd$ -->
-
-<!-- Simulations were carried out to explore the behavior of $\wpd$ under the following factors that could potentially impact the values of $\wpd$: $\nx$, $\nf$, $\lambda$, $\omega$, $dist$ (normal/non-normal distributions with different location and scale), $ntimes$, and $designs$ and results are presented in two parts.
-The dependence of $\wpd$ on $\nx$ and $\nf$ under $\Dnull$ is presented here, which lays the foundation for the next section.
-The rest of the results that discuss the relationship of the $\wpd$ with other factors is presented in details in the Supplementary section of the paper.
-They show that the designs $\Df$ and $D_x$ intersect at $\lambda = 0.5$ and hence for up-weighing designs of the form $D_x$, $\lambda = 0.67$ has been considered for computation of $\wpd$ in the rest of the paper.
--->
-
-<!-- - $\nx$ (number of levels of x-axis) -->
-<!-- - $\nf$ (number of levels of facets) -->
-<!-- - $\lambda$ (tuning parameter) -->
-<!-- - $\omega$ (increment in each panel design) -->
-<!-- - $dist$ (normal/non-normal distributions with different location and scale) -->
-<!-- - $n$ (sample size for each combination of categories) -->
-<!-- - $designs$ ($\Dnull$, $\Df$, $D_x$ and $D_{fx}$) -->
-
-<!-- - $\nsub{sim}$ (number of simulations) -->
-<!-- - $\nsub{perm}$ (number of permutations of data)  -->
-
-<!-- ### Simulation design{#sec:sim-study} -->
-
-<!-- Observations are generated from a Gamma(2,1) distribution for each combination of $\nx$ and $\nf$ from the following sets: $nx = \nf = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
-Each combination is being referred to as a _panel_.
-That is, data is being generated for each of the panels $\{nx = 2, \nf = 2\}, \{nx = 2, \nf = 3\}, \{nx = 2, \nf = 5\}, \dots, \{nx = 50, \nf = 31\}, \{nx = 50, \nf = 50\}$.
-For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
-That is, if we consider the panel $\{nx = 2, \nf = 2\}$, $500$ observations are generated for each of the combination of categories from the panel, namely, $\{(1, 1), (1, 2), (2, 1), (2, 2)\}$.
-The values -->
-<!-- of $\wpd$ is obtained for each of the panels.
-This design corresponds to $\Dnull$ as each combination of categories in a panel are drawn from the same distribution.
-Furthermore, the data is simulated for each of the panels $\nsub{sim}=200$ times, so that the distribution oaf $\wpd$ under $\Dnull$ could be observed.
-$wpd_{l, s}$ denotes the value of $\wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.
--->
-
-<!-- ### Results -->
-
-<!-- Figure \ref{fig:raw} shows the distribution of $\wpd$ plotted across different $\nx$ and $\nf$ categories.
-Since under $\Dnull$, there is no difference in distributions across different categories, we expect the distance measure $\wpd$ to reflect that as well and have the same distribution across categories.
-But Figure \ref{fig:raw} shows that both the location and scale of the distributions change across panels.
-This is not desirable under $\Dnull$ as it would mean comparisons of $\wpd$ values is not appropriate across different $\nx$ and $\nf$.
-Figure \ref{fig:quadratic} shows how the median of $\wpd$ varies with the total number of distances $nx*\nf$ for each panel.
-The median increases abruptly for lower values of $nx*\nf$ and slowly for higher $nx*\nf$.
--->
-
-<!-- Furthermore, simulation results also show that the values of $\wpd$ indeed depend upon the underlying distribution.
-This is also not desirable as the intended aim of $\wpd$ is to capture differences in categories irrespective of the distribution from which the data is generated.
--->
-
-<!-- last writeup -->
-<!-- In the linear model approach, $wpd\in R$ was assumed, whereas, $\wpd$ is a Jensen-Shannon Distance (JSD) and lies between 0 and 1 [@JSD].
-Furthermore, JSD follows a Chi-square distribution, which is a special case of Gamma distribution.
-Therefore, a generalized linear model could be fitted instead of a linear model to allow for the response variable to follow a Gamma distribution.
-The inverse link is used when we know that the mean response is bounded, which is applicable in our case since $0 \leq wpd\leq 1$.
--->
-
-<!-- We fit a Gamma generalized linear model with the inverse link which is of the form:  -->
-<!-- $$y_l = a+b*log(z_l) + e_l$$, where $y_l = median_m(wpd_{l, m})$, $z_l$ is the $l^{th}$ panel and $e_l$ are idiosyncratic errors.
-Let $E(y) = \mu$ and $a + b*log(z) = g(\mu)$ where $g$ is the link function.
-Then $g(\mu)= 1/\mu$ and $\hat \mu = 1/(\hat a + \hat b log(z))$.
-The residuals from this model $(y-\hat y) = (y-1/(\hat a + \hat b log(z)))$ would be expected to have no dependency on $z$.
-Thus, $\wpdsub{glm}$ is chosen as the residuals from this model and is defined as: -->
-<!-- $\wpdsub{glm} = wpd - 1/(\hat a + \hat b*log(nx*\nf))$. -->
-
-<!-- which is more approximate than exact but still has the similar accuracy when compared to the permutation approach. -->
-
-<!-- use later -->
-<!-- The measure $\wpd$ could potentially lead to comparison of the measure across different panels and also help distinguishing the interesting panels from a data set.
-We discuss two approaches for normalization, both of which are substantiated using simulations.
--->
-
-<!-- ## Methodology -->
-
-<!-- The transformed ${wpd}$ which is normalized for the values of $\nx$ and $\nf$ is denoted by $\wpd$.
-Two approaches have been employed - the first one involves a permutation method to make the distribution of the transformed $\wpd$ similar for different comparisons and the second one fits a model to represent the relationship between the two variables and defines $\wpd$ as the residual of the model.
--->
-
-<!-- ### Notations -->
-
-<!-- Let $\{nx_{i}, i = 1, 2, \dots, nx\}$, $\{\nf_{j}, j = 1, 2, \dots, \nf\}$ be the set of x-axis and facet categories respectively.
-Each combination of $nx_{i}$ and $\nf_{j}$is being referred to as a _panel_.
-Then the total number of panel is $nx*\nf$.
-Let the total number of pairwise distances that could result in each panel be $\{z_k, k = 1, 2 , \dots, nx*\nf\}$.
-Here, $\{z_1 = nx_1*\nf_1\}$, $\{z_2 = nx_2*\nf_2\}$ and $\{z_k = nx*\nf\}$.
-Now, let $\{x_{k,l}, k = 1, 2, \dots, nx*\nf, l = 1, 2, \dots, \nsub{sim}\}$ denote the values of $\wpdsub{raw}$ obtained from the simulation study for $k^{th}$ panel in the $i^{th}$ simulation.
-Hence, for each of those $k$ panel, we have $\nsub{sim}$ values of $\wpdsub{raw}$.
--->
-
-<!-- use soon -->
-<!-- ## Properties -->
-
-<!-- This section reports the results of a simulation study that was carried out to evaluate the behavior of $\wpd$ under different designs and other potential factors.
-The behavior of $\wpd$ is explored in designs where there is in fact difference in distribution between facet categories ($\Df$) or across x-categories ($D_x$) or both ($D_{fx}$).
-Using $\omega = \{1, 2, \dots, 10\}$ and $\lambda = seq(from = 0.1, to = 0.9, by = 0.05)$, observations are drawn from a N(0,1) distribution for each combination of $\nx$ and $\nf$ from the following sets: $nx = \nf = \{2, 3, 5, 7, 14, 20, 31, 50\}$.
-$ntimes = 500$ is assumed for this setup as well.
-Furthermore, to generate different distributions across different combination of facet and x levels, the following method is deployed - suppose the distribution of the combination of first levels of $x$ and $facet$ category is $N(\mu,\sigma)$ and $\mu_{jk}$ denotes the mean of the combination $(a_jb_k)$, then $\mu_{j.} = \mu + j\omega$ (for design $D_x$) and $\mu_{.k} = \mu + k\omega$ (for design $\Df$).
--->
-
-<!-- The tabulated values and graphical representations of the simulation results are provided in the Supplementary paper.
-The learning from the simulations are as follows: The values of $\wpd$ is least for $\Dnull$, followed by -->
-<!-- $\Df$, $D_x$ and $D_{fx}$.
-This is a desirable result since the measure $\wpd$ was designed such that this relationship holds.
-Furthermore, the distribution of the measure $\wpd$ does not change for different facet and x categories.
-The distribution of $\wpd$ looks similar with at least the mean and standard of the distributions being uniform across panels.
-This means $\wpd$ could be used to measure differences in distribution across panels.
-Also, note that since the data is processed using normal-quantile-transform, this measure is independent of the initial distribution of the underlying data and hence is also comparable across different data sets.
-This is valid for the case when sample size $ntimes$ for each combination of categories is at least 30 and $\nsub{perm}$ used for computing $\wpd$ is at least 100.
-More detailed results about the properties of $\wpd$ could be found in the Supplementary paper.
--->
-
-# Ranking and selection of cyclic granularities {#sec:rank-wpd}
-
-A cyclic granularity is referred to as "significant" if there is a significant distributional difference of the measured variable between different categories of the harmony.
-In this section, a selection criterion to choose significant harmonies is provided, thereby eliminating all harmonies that exhibit non-significant differences in the measured variable.
-The distance measure $\wpd$ is used as a test statistic to test the null hypothesis that no harmony/cyclic granularity is significant.
-We select only those harmonies/cyclic granularities for which the test fails.
-They are then ranked based on how well they capture variation in the measured variable.
-
-<!-- .
-Randomization tests (permutation tests) generates a random distribution by re-ordering the observed data and allows us to test if the observed data is significantly different from any random distribution.
--->
-<!-- the harmonies are not significant under null hypothesis and then test if our hypotheses are true: -->
-
-<!--  $H_0$: harmonies are not significant -->
-<!--  $H_1$: at least one harmony is significant -->
-
-<!-- we provide a method to select important harmonies by eliminating all harmonies for which patterns are not significant by employing randomization test.
-Randomization tests (permutation tests) generates a random distribution by re-ordering our observed data and allow to test if the observed data is significantly different from any random distribution.
-Complete randomness in the measured variable indicates that the process follows a homogeneous underlying distribution over the whole time series, which essentially implies there is no interesting distinction across any different categories of the cyclic granularities.
--->
-
-## Selection
-
-<!-- Under the null hypothesis, the harmonies are not significant. -->
-
-A threshold (and consequently a selection criterion) is chosen using the notion of randomization tests [@edgington2007randomization].
-The data is permuted several times and $\wpd$ is computed for each of the permuted data sets to obtain the sampling distribution of $\wpd$ under the null hypothesis.
-If the null hypothesis is true, then $\wpd$ obtained from the original data set would be a likely value in the sampling distribution.
-But in case the null hypothesis is not true, then it is less probable that $\wpd$ obtained for the original data will be from the same distribution.
-This idea is utilized to come up with a threshold for selection, denoted by $\wpdsub{threshold}$, defined as the $99^{th}$ percentile of the sampling distribution.
-A harmony is selected if the value of $\wpd$ for that harmony is greater than the chosen threshold.
-The detailed algorithm for choosing a threshold and selection procedure (for two cyclic granularities) is listed as follows:
-
-<!-- The selection criterion is stated as follows: for $(i \in {1, 2, \dots, H_{N_C}})$, select $H_i$ if $wpd_i > \wpdsub{threshold}$, else reject. -->
-
-- **Input:** All harmonies of the form $\{(A, B),~ A = \{ a_j: j = 1, 2, \dots, \nx\},~ B = \{ b_k: k = 1, 2, \dots, \nf\}\}$, $\forall (A, B) \in H_{N_C}$.
-
-- **Output:** Harmony pairs $(A, B)$ for which $\wpd$ is significant.
-
-1. For each harmony pair $(A, B) \in H_{N_C}$, the following steps are taken.
-
-    a. Given the measured variable; $\{v_t: t=0, 1, 2, \dots, T-1\}$, $\wpd$ is computed and is represented by $\wpd^{A, B}_{obs}$.
-    b. For $i=1,\dots,m$, randomly permute the original time series: $\{v_t^{i}: t=0, 1, 2, \dots, T-1\}$ and compute $\wpd^{A, B}_{i}$ from $\{v_t^{i}\}$.
-    c. Define $\wpdsub{sample} = \{\wpd^{A, B}_{1}, \dots, \wpd^{A, B}_{M}\}$.
-
-2. Stack the $\wpdsub{sample}$ vectors as $\wpdsub{sample}^{\text{all}}$ and compute its $p = 100(1-\alpha)$ percentiles as $\wpdsub{threshold\emph{p}}$.
-3. If $\wpd^{A, B}_{obs} > \wpdsub{threshold\emph{p}}$, harmony pair $(A, B)$ is selected at the $1-p/100$ level, otherwise rejected.
-4. Harmonies selected using the $99^{th}$, $95^{th}$ and $90^{th}$ thresholds are tagged as \*\*\*, \*\*, \* respectively.
-
-## Ranking {#sec:ranking}
-
-The distribution of $\wpd$ is expected to be similar for all harmonies under the null hypothesis, since they have been adjusted for different number of categories for the harmonies or underlying distribution of the measured variable.
-Hence, the values of $\wpd$ for different harmonies are comparable and can be used to rank the significant harmonies.
-A higher value of $\wpd$ for a harmony indicates that higher maximum variation in the measured variable is captured through that harmony.
-
-```{r varall-new}
-
-```
-
-```{r varx-new}
-
-```
-
-```{r varf-new}
-```
-
-```{r null-new}
-
-```
-
-Figure \ref{fig:null4by2} also presents the results of $\wpd$ from the illustrative designs in Section \ref{sec:computation-wpd}.
-The value of $\wpd$ under null design (a) is the least, followed by (b), (c) and (d).
-This aligns with the principle of $\wpd$, which is expected to have lowest value for null designs and highest for designs of the form $\Dfx$ (d).
-Moreover, note the relative differences in $\wpd$ values between (b) and (c).
-The value of the tuning parameter $\lambda$ is set to 2/3, which gives greater emphasis to differences in x-axis categories than facets.
-
-Again consider \ref{fig:onegran-new}(a) and \ref{fig:onegran-new}(b) with a $\wpd$ value of 20.5 and 145 respectively.
-This is because there is a more gradual increase across hours of the day than across months of the year.
-If the order of categories is ignored, the resulting $\wpd$ values are $97.8$ and $161$ respectively, because differences between any hours of the day tend to be larger than differences only between consecutive hours.
-Similarly, \ref{fig:onegran-new}(a) and (b) have $\wpd$ values of $110.79$ and $125.82$ respectively.
-The ranking implies that the distributional differences are more prominent for the second household, as is also seen from the bigger fluctuations in the $90^{th}$ percentile than for the first household.
-
-<!-- ## Choosing a threshold -->
-
-<!-- A randomization test involves calculating a test statistic, randomly shuffling the data and calculating the test statistic several times to obtain a distribution of the test statistic.
-But we will use this procedure to obtain a threshold such that harmony pairs with a $\wpd$ value higher than this threshold will only be considered significant.
-The process of choosing a threshold is described as follows: -->
-
-<!-- to test if there is any interesting pattern captured by the harmonies, which essentially implies if $\wpd$ is significantly different from zero.
-The percentages of times the $\wpd$ obtained from the permuted data is greater than or equal to the observed $\wpd$ is the p-value.
-The randomization test is described as follows: -->
-
-<!-- <!-- We can remove the harmonies for which no interesting patterns are observed through a randomization permutation method. --> 
-<!-- Essentially, the assumption is that under the null hypothesis, there is no difference in categories between the pair of cyclic granularities in the chosen harmony.
-This method is based on the generation of randomly chosen reassignments (permutations) of the data across different cyclic granularities and the computation of -->
-<!-- $\wpd$ for each of these reassignments. -->
-
-<!-- **Assumption:** random permutation of the data keeping the categories of the cyclic granularities constant. -->
-
-<!-- Complete randomness in the measured variable indicates that the process follows a homogeneous underlying distribution over the whole time series, which essentially implies there is no interesting distinction across any different categories of the cyclic granularities.
-We can remove the harmonies for which no interesting patterns are observed through a randomization permutation method.
-Essentially, the assumption is that under the null hypothesis, there is no difference in categories between the pair of cyclic granularities in the chosen harmony.
-This method is based on the generation of randomly chosen reassignments (permutations) of the data across different cyclic granularities and the computation of -->
-<!-- $\wpd$ for each of these reassignments.
-The percentages of times the theoretical distribution greater than or equal to the respective observed $\wpd$ values are calculated and are used to obtain the P value.
-The procedure for the permutation test is: -->
-
-<!-- **Assumption:** random permutation of the data keeping the categories of the cyclic granularities constant. -->
-
-<!-- 14, 20, 31, 50\}$.
-For each of the $64$ panels, $ntimes = 500$ observations are drawn for each combination of the categories.
-The values of $\wpd$ is obtained for each of the panels for the designs $\Dnull$, $D_x$, $\Df$ and $D_{fx}$.
-$\wpdsub{threshold}$ is computed from all of these panels together and the number of times a harmony pair $(A, B) \in H_{N_C}$ is selected when in fact it was of the design $\Dnull$ is noted.
-This entire process is repeated for several null data sets to see the number of times any harmony pair $(A, B) \in H_{N_C}$ is selected under null.
--->
-
-<!-- ### Results -->
-
-## Simulations {#sec:simulations}
-
-Simulations were carried out to explore the behavior of $\wpd$ as $\nx$ and $\nf$ were varied, in order to compare and evaluate different normalization approaches.
-More detailed simulation results, including an exploration of the size and power of the proposed test, are contained in the supplements.
-
-### Simulation design {-}
-
-\noindent $m=1$
-
-\noindent Observations were generated from a N(0,1) distribution for $\nx \in \{2, 3, 5, 7, 9, 14, 17, 20, 24, 31, 42, 50\}$, with $\nsub{times} = 500$ observations drawn for each combination of categories.
-This design corresponds to $\Dnull$.
-For each of the categories, there were $\nsub{sim}=200$ replications, so that the distribution of $\wpd$ under $\Dnull$ could be observed.
-Let $\wpd_{\ell, s}$ denote the value of $\wpd$ obtained for the $\ell^{th}$ panel and $s^{th}$ simulation.
-
-\noindent $m=2$
-
-\noindent Similarly, observations were generated from a N(0,1) distribution for each combination of $\nx$ and $\nf$ from $\{2, 3, 5, 7, 14, 20, 31, 50\}$, with $\nsub{times} = 500$ observations drawn for each of the $64$ combinations.
-
-### Results {-}
-
-Figure \ref{fig:raw} shows that both the location and scale of the distributions change across panels.
-This is not desirable under $\Dnull$ as it would mean comparisons of $\wpd$ values are not appropriate across different $\nx$ and $\nf$ values.
-Table \ref{tab:glm-tab} gives the summary of a Gamma generalized linear model to capture the relationship between $\wpdsub{raw}$ and the number of comparisons.
-The intercepts and slopes are similar, independent of the underlying distributions (see supplementary paper for details) and hence the coefficients are shown for the case when observations are drawn from a N(0,1) distribution.
-Figure \ref{fig:dist-new-same-scale-link} shows the distribution of $\wpdsub{perm}$ and $\wpdsub{glm-scaled}$ on the same scale to show that a combination approach could be used for higher values of $\nx$ and $\nf$ to alleviate the computational time of the permutation approach.
-
-(ref:raw) Distribution of $\wpdsub{raw}$ is plotted across different $\nx$ and $\nf$ categories under $\Dnull$ through density and rug plots.
-Both location (blue line) and scale (orange marks) of the distribution shifts for different panels.
-This is not desirable since under the null design, the distribution is not expected to capture any differences.
-
-```{r raw, fig.cap = "(ref:raw)", fig.pos="!b"}
-```
-
-```{r glm-tab}
-
-```
-
-```{r wpd-glm-dist}
-
-```
-
-```{r hist-qq-new, eval = FALSE}
-
-```
-
-```{r quadratic, eval=FALSE}
-```
-
-```{r norm, eval}
-```
-
-(ref:dist-new-same-scale-link) The distribution of $\wpdsub{perm}$ and $\wpdsub{glm-scaled}$ are overlaid to compare the location and scale across different $\nx$ and $\nf$.
-$\wpdsub{norm}$ takes the value of $\wpdsub{perm}$ for lower levels, and $\wpdsub{glm-scaled}$ for higher levels to to alleviate the problem of computational time in permutation approaches.
-This is possible as the distribution of the adjusted measure looks similar for both approaches for higher levels.
-
-```{r dist-new-same-scale-link, fig.cap = "(ref:dist-new-same-scale-link)"}
-```
-
-These results justify our use of the permutation approach when $\nx<5$ and $\nf<5$, and the use of the GLM otherwise.
-<!--
-## Choosing the threshold
-
-### Simulation design {-}
-
-Observations were generated from a N(0,1) distribution for each combination of $\nx$ and $\nf$ from the following sets: $nx \in \{3, 7, 14\}$ and $\nf \in \{2, 9, 10\}$, giving nine possible panels/combinations.
-In the first scenario, data for all panels were simulated using the null design $\Dnull$.
-In other scenarios, data simulated from the panel $(14, 2)$ and $(3, 10)$ used $\Dfx$ where the means of the distributions increase by $\omega$ across both x-axis and facets, where $\omega \in \{0.5, 2, 5\}$.
-This allows us to examine if the proposed test is able to capture subtle differences and obvious differences when we shift from the null design.
-
-In the last scenario, we consider the panel $(3, 2), (7,9), (14, 10)$ to be under $\Dnull$, the panels $(7, 2), (14, 9)$ to be under $\Df$.
-$(14, 2), (3, 10)$ under $D_x$ and the rest under $\Dvar{{null}}$.
-This is done to check if the consequent ranking procedure leads to designs like $D_{vary_{all}}$ to be chosen first followed by $D_{vary_{all}}$.
-We generate only one data set each for which these scenarios were simulated and consider this as the original data set.
-We generate $1000$ repetitions of this experiment with different seeds.
-
-### Results {-}
-
-For the first scenario, we set $\wpdsub{threshold99}$ so that the probability of rejecting each panel under $\Dnull$ is $0.01$.
-We have 9 tests, so the size of the tests overall is $1-0.99^9 \approx 0.09$.
-We also compute the proportion of times a panel is rejected when it belongs to a non-null design to obtain the power of the test.
-The detailed results and graphics are included in the Supplementary paper.
-
-```{r, eval = FALSE}
-all_data <- read_rds("simulations/supplementary/test-hpc/data-agg/all_data.rds")
-
-# computes size for 99 percentile threshold
-data_summary <- all_data %>%
- mutate(sig = if_else(significance!=99, 0, 99)) %>%
- group_by(seed_id) %>%
- summarize(sumsig = sum(sig)) %>%
- count(sumsig==0) %>%
- mutate(p_value = n/sum(n)) %>%
- slice(1)
-
-# plots
-ggplot() + 
- geom_histogram(data = all_data, aes(x = wpd)) +
- geom_vline(data = data_summary, aes(xintercept = p_value),color = "red") +
- facet_grid(x_levels~facet_levels)
-
-```
- -->
-
-# Application to residential smart meter dataset {#sec:application-wpd}
-
-The smart meter data set for eight households in Melbourne were procured by downloading the data from the energy supplier/retailer.
-The data has been cleaned to form a `tsibble` [@wang2020tsibble] containing half-hourly electricity consumption from July to December 2019 for each of the households, No behavioral pattern is likely to be discerned from the time plot of energy usage over the entire period, since the plot will have too many observations squeezed in a linear representation.
-When we zoom into the September 2019 data in Figure \ref{fig:dotplot-8}(b), some patterns are visible in terms of peaks and troughs, but we do not know if they are regular or what is their period.
-
-(ref:dotplot-8) An ensemble plot with a heatmap (a), line plot (b), parallel coordinate plot (c) to demonstrate energy behavior of the households in different ways.
-Panel (b) shows the raw demand series for September to highlight the repetitive patterns of energy demand.
-Panel (a) shows $\wpd$ values across harmonies where a darker color indicates a higher ranking harmony.
-A significant harmony is shown with an asterisk.
-For example, ids 7 and 8 have significant patterns across (*hod*, *dow*) and (*dow*, *hod*).
-Panel (c) is useful for comparing households across harmonies.
-For example, for the harmony (*dow*-*hod*), ids 1 and 7 have the least and highest $\wpd$ respectively.
-
-```{r dotplot-8, fig.cap = "(ref:dotplot-8)", fig.height = 7}
-```
-
-Electricity demand, in general, has daily, weekly and annual seasonal patterns.
-However, it is not apparent from this view if all households have those patterns, or how strong they are in each case.
-It is also not clear from this view if any other periodic patterns are present in any household.
-We start the analysis by choosing a few harmonies, and ranking them for each of these households.
-The ranking and selection of significant harmonies is validated by analyzing the distribution of energy usage across significant harmonies.
-
-<!-- if we are benefiting by moving from a linear to cyclic representation of time to . -->
-
-```{r linear-scale-8, fig.cap = "Electricity demand for eight households is shown in different facets from Jul-19 to Dec-19 in Fig a and it has been zoomed in for Sep-19 in Fig b, where a week in Sep-19 has been highlighted.
-From the scales of Fig a, it is apparent that these households vary in consumption levels, but all their periodic patterns have been squeezed with this representation.
-In fig b, we can see some weekly patterns for the entire period and daily patterns for the highlighted week and there could be some other patterns visible in terms of peaks and troughs, but it is not clear if they are regular or significant.", fig.height=8, eval = FALSE}
-
-```
-
-### Choosing cyclic granularities of interest and removing clashes {-}
-
-Let $v_{i, t}$ denote the electricity demand for the $i^{th}$ household in time period $t$.
-The series $\{v_{i, 1},\dots,v_{i,T}\}$ is the linear granularity corresponding to half-hour since the interval of the tsibble is 30 minutes.
-We consider coarser linear granularities like hour, day, week and month from the commonly used Gregorian calendar.
-From the four linear granularities of hour, day, week, and month, we obtain $N_C = 4\times 3/2 = 6$ cyclic granularities:  "hour_day", "hour_week", "hour_month", "day_ week", "day_month" and "week_month".
-Further, we add cyclic granularity day-type ("wknd wday") to capture weekend and weekday behavior.
-Thus, seven cyclic granularities are considered to be of interest.
-The pairs of cyclic granularities ($C_{N_C}$) will have $7\times 6=42$ elements.
-The set of possible harmonies $H_{N_C}$ from $C_{N_C}$ are chosen by removing clashes using procedures described in [@Gupta2021-hd].
-Table \ref{tab:tab-rank-8} shows $14$ harmony pairs that belong to $H_{N_C}$.
-
-```{r rank-household-mclapply-8}
-```
-
-```{r elec_select_harmony-8}
-```
-
-```{r tab-rank-8, dependson="dotplot-8"}
-```
-
- <!-- The paper also shows how the number of harmonies could be identified among by removing clashes.
-This section shows how we could refine the search further by only looking at significant harmonies.
--->
-
-### Selecting and Ranking harmonies for all households {-}
-
-$\wpd_{i}$ is computed on $v_{i, t}$ for all harmony pairs $\in H_{N_C}$ and for each household $i \in \{1, 2, \dots, 8\}$.
-The harmony pairs are then arranged in descending order and highlighted with `***`, `**` and `*` corresponding to the $99^{th}$, $95^{th}$ and $90^{th}$ percentile threshold.
-Table \ref{tab:tab-rank-8} shows the rank of the harmonies for different households.
-The rankings are different for different households, which is a reflection of their varied behaviors.
-Most importantly, there are at most three harmonies that are significant for any household.
-This is a huge reduction in the number of potential harmonies to explore.
-
-### Detecting patterns not apparent from linear display {-}
-
-Figure \ref{fig:dotplot-8} helps to compare households through the heatmap (a) across harmony pairs.
-Here *dom*, *dow*, *wdwnd* are abbreviations for day-of-month, day-of-week, weekday/weekend and so on.
-The colors represent the value of $\wpd$.
-Darker cells correspond to higher values of $\wpd$.
-Those with `*` correspond to $\wpd$ values above $\wpdsub{threshold95}$.
-
-We can now see some patterns that were not discernible in Panel (b), including:
-
-  1. id 7 and 8 have the same significant harmonies despite having very different total energy usage.
-  2.
-id 6 and 7 differ in the sense that for id 6, the difference in patterns only during weekday/weekends, whereas for id 7, all or few other days of the week are also important.
-This might be due to their flexible work routines or different day-off.
-  3. There are no significant periodic patterns for id 5 when we fix the threshold to $\wpdsub{threshold95}$.
-
-Note that the $\wpd$ values are computed over the entire range, but the linear display in (b) is only for September, with the major and minor x-axis corresponding to weeks and days respectively.
-
-<!-- Households id 2 and 3 are similar, in terms of linear display and heatmap, which implies that similar periodic behavior can stem from households with different demographics. -->
-
-### Comparing households and validating rank of harmonies {-}
-
-According to Figure \ref{fig:dotplot-8}(c), for the harmony pair (*dow*-*hod*), household id 7 has the greatest value of $\wpd$, while id 1 has the least.
-From Table \ref{tab:tab-rank-8} it can be seen that the harmony pair (*dow*, *hod*) is important for id 7, however it has been labeled as an inconsequential pair for id 1.
-The distribution of energy demand for both of these households, with *dow* as the facet and *hod* on the x-axis, may help explain the choice.
-Figure \ref{fig:gravitas-plot-8} demonstrates that for id 7, the median (black) and quartile deviation (orange) of energy consumption fluctuates for most hours of the day and days of the week, while for id 1, daily patterns are more consistent within weekdays and weekends.
-As a result, for id 1, it is more appropriate to examine the distributional difference solely across (*dow*, *wdwnd*), which has been rated higher in Table \ref{tab:tab-rank-8}.
-
-<!-- Although the differences might seem significant at first, with closer inspection it could be seen that the scale of the demand is lower in this case and hence the differences are not large enough to cross the threshold for significance.
--->
-
-<!-- Figure \ref{fig:gravitas-plot-8} is used to show -->
-<!-- if this selection and ranking of harmony pairs makes sense for this household.
-Panel a) of Figure \ref{fig:gravitas-plot-8} shows the distribution of energy demand with weekday/weekend as the x-axis and hour-of-day as the facets and helps to compare the weekend/weekday patterns for different hours of the day.
-It could be observed that the difference between weekend and weekday is the highest from 15 to 19 hours of the day.
-Panel b) shows the distribution of energy demand with the variables swapped and helps to compare the daily patterns within weekday and weekend.
-It could be observed that the daily pattern is similar for weekdays and weekends with a morning and evening peak.
-However, the difference between morning and evening peaks are higher for weekends.
-Since $\wpd$ is designed to put more weightage on within-facet differences for $\lambda>0.5$, it makes sense that the pair (hod, wdwnd) has been ranked higher than (wdwnd, hod).
-Panel c) shows the distribution of energy demand with weekday/weekend as the x-axis and week-of-month as the facets.
-Although the differences might seem significant at first, with closer inspection it could be seen that the scale of the demand is lower in this case and hence the differences are not large enough to cross the threshold for significance.
--->
-
-(ref:gravitas-plot-8) Comparing distribution of energy demand shown for household id 1 (a) and 7 (b) across *hod* in x-axis and *dow* in facets through quantile area plots.
-The value of $\wpd$ in Table 3 suggests that the harmony pair (*dow*, *hod*) is significant for household id 7, but not for id 1.
-This implies that distributional differences are captured more by this harmony for id 7, which is apparent from this display with more fluctuations across median and 75th percentile for different hours of the day and day of week.
-For id 1, patterns look similar within weekdays and weekends.
-Here, the median is represented by the black line, the orange area corresponds to quartile deviation and the green area corresponds to area between $10^{th}$ and $90^{th}$ quantile.
-
-```{r gravitas-plot-8, message = FALSE, warning=FALSE,fig.cap="(ref:gravitas-plot-8)", fig.pos="!htb"}
-
-```
-
-<!-- From Figure \ref{fig:gravitas-plot-8-id5}, it could further be observed that id5 has only one significant harmony (*hod*, *dow*).
-Apparently, $(hod, wnd/wday)$ which is an important harmony for most households is not important for this one.
--->
-
-# Discussion
-
-Exploratory data analysis involves many iterations of finding and summarizing patterns.
-With temporal data available at finer scales, exploring time series has become overwhelming with so many possible granularities to explore.
-A common solution is to aggregate and look at the patterns across the usual granularities such as hour-of-day or day-of-week, but there is no way to know the “interesting” granularities a priori.
-A huge number of displays need to be analyzed or we might end up missing informative granularities.
-This work refines the search of informative granularities by identifying those for which the differences between the displayed distributions are greatest and rating them in order of importance of capturing maximum variation.
-
-The significant granularities across different datasets (individuals/subjects) do not imply similar patterns across different datasets.
-They simply mean that maximum distributional differences are being captured across those granularities.
-A future direction of work is to be able to explore and compare many individuals/subjects together for similar patterns across significant granularities.
-
-<!-- patterns are interesting and others are not.
-The subjects for which behaviors across a group of cyclic granularities are similar, could be grouped together as their periodic behavior is similar.
-to group subjects -->
-
-# Acknowledgments {-}
-
-The authors thank the ARC Centre of Excellence for Mathematical and Statistical Frontiers [(ACEMS)](https://acems.org.au/home) for supporting this research.
-Sayani Gupta was partially funded by [Data61 CSIRO](https://data61.csiro.au/) during her PhD.
-The Github repository, [github.com/Sayani07/paper-hakear](https://github.com/Sayani07/paper-gravitas), contains all materials required to reproduce this article and the code is also available online in the supplemental materials.
-This article was created with R [@R-language], `knitr` [@knitr2015, @R-knitr] and `rmarkdown` [@rmarkdown2018, @R-rmarkdown].
-Graphics are produced with `ggplot2` [@Wickham2009pk].
-
-# Supplementary Materials
-
-**Data and scripts:** Data sets and R code to reproduce all figures in this article (main.R).
-
-\noindent
-**Simulation results and scripts:** All simulation table, graphics and and R code to reproduce it (paper-supplementary.pdf, paper-supplementary.Rmd)
-
-\noindent
-**R-package:** The open-source R package `hakear` is available on Github (https://github.com/Sayani07/hakear) to implement ideas presented in this paper.
-
-# Bibliography
-
-```{r write-bib, eval = FALSE}
-write_bib(c("rmarkdown", "bookdown", "rticles", "knitr", "ggplot2", "dplyr", "tsibble", "gravitas", "ggpubr", "kableExtra", "magrittr", "readr", "lubridate", "renv", "archive", "hakear", "patchwork", "ggpubr"), file = "rpkgs.bib")
-```

### 2021-11-03 paper/hakear_wp.Rmd
Split into JCGS and WP versions

--- 2021-11-03 paper/hakear_jcgs.Rmd
@@
 title: Detecting distributional differences between temporal granularities for exploratory time series analysis
+author:
+- familyname: Gupta
+  othernames: Sayani
+  address: Monash University
+  email: Sayani.Gupta@monash.edu
+  correspondingauthor: true
+- familyname: Hyndman
+  othernames: Rob J
+  address: Monash University
+- familyname: Cook
+  othernames: Dianne
+  address: Monash University
 
-# to produce blinded version set to 1
-blinded: 0
-
-authors:
-- name: Sayani Gupta
-  thanks: "Email: Sayani.Gupta@monash.edu"
-  affiliation: Department of Econometrics and Business Statistics, Monash University, Australia
-
-- name: Rob J Hyndman
-  affiliation: Department of Econometrics and Business Statistics, Monash University, Australia
-
-- name: Dianne Cook
-  affiliation: Department of Econometrics and Business Statistics, Monash University, Australia
-keywords:
-- data visualization
-- cyclic granularities
-- periodicities
-- permutation tests
-- distributional difference
-- Jensen-Shannon distances
-- smart meter data
-- R
-
-abstract: |
- Cyclic temporal granularities are temporal deconstructions of a time period into units such as hour-of-the-day and work-day/weekend.
+abstract: "Cyclic temporal granularities are temporal deconstructions of a time period into units such as hour-of-the-day and work-day/weekend.
 They can be useful for measuring repetitive patterns in large univariate time series data, and feed new approaches to exploring time series data.
@@
 The distance measure is computed for a single or pairs of cyclic granularities and can be compared across different cyclic granularities or on a collection of time series.
-The methods are implemented in the open-source R package `hakear`.
-
-bibliography: [bibliography.bib]
+The methods are implemented in the open-source R package `hakear`."
+keywords: "data visualization, cyclic granularities, periodicities, permutation tests, distributional difference, Jensen-Shannon distances, smart meter data, R"
+wpnumber: ??/2021
+jelcodes: C55, C65, C80
+blind: false
+cover: true
+toc: false
+lot: false
+bibliography: bibliography.bib
+biblio-style: authoryear-comp
 output:
- bookdown::pdf_book:
-  base_format: rticles::asa_article
+  MonashEBSTemplates::workingpaper:
+    fig_caption: yes
     fig_height: 5
     fig_width: 8
-  fig_caption: yes
     dev: "pdf"
     keep_tex: yes
+    number_sections: yes
+    citation_package: biblatex
     includes:

### 2021-11-03 paper/main.Rmd
Split into JCGS and WP versions

@@
----
-title: Detecting distributional differences between temporal granularities for exploratory time series analysis
-
-# to produce blinded version set to 1
-blinded: 0
-
-authors:
-- name: Sayani Gupta
-  thanks: "Email: Sayani.Gupta@monash.edu"
-  affiliation: Department of Econometrics and Business Statistics, Monash University, Australia
-
-- name: Rob J Hyndman
-  affiliation: Department of Econometrics and Business Statistics, Monash University, Australia
-
-- name: Dianne Cook
-  affiliation: Department of Econometrics and Business Statistics, Monash University, Australia
-keywords:
-- data visualization
-- cyclic granularities
-- periodicities
-- permutation tests
-- distributional difference
-- Jensen-Shannon distances
-- smart meter data
-- R
-
-abstract: |
- Cyclic temporal granularities are temporal deconstructions of a time period into units such as hour-of-the-day and work-day/weekend.
-They can be useful for measuring repetitive patterns in large univariate time series data, and feed new approaches to exploring time series data.
-One use is to take pairs of granularities, and make plots of response values across the categories induced by the temporal deconstruction.
-However, when there are many granularities that can be constructed for a time period, there will also be too many possible displays to decide which might be the more interesting to display.
-This work proposes a new distance metric to screen and rank the possible granularities, and hence choose the most interesting ones to plot.
-The distance measure is computed for a single or pairs of cyclic granularities and can be compared across different cyclic granularities or on a collection of time series.
-The methods are implemented in the open-source R package `hakear`.
-
-bibliography: [bibliography.bib]
-preamble: >
- \setlength {\marginparwidth }{2cm}
- \usepackage{mathtools,amssymb,booktabs,amsthm,todonotes,colortbl}
- \def\mod{~\text{mod}~}
- \usepackage{mathptmx}
- \usepackage{caption,setspace}
- \usepackage{longtable}
- \DeclareCaptionStyle{italic}{labelfont={bf},textfont={it},labelsep=colon}
- \captionsetup[figure]{style=italic,format=hang,singlelinecheck=true,font={stretch=1.2}}
- \captionsetup[table]{style=italic,format=hang,singlelinecheck=true,font={stretch=1.2}}
- \def\novspacing{\setlength{\aboverulesep}{0pt}\setlength{\belowrulesep}{0pt}}
- \def\vspacing{\setlength{\aboverulesep}{0.4ex}\setlength{\belowrulesep}{0.65ex}}
- \newcommand{\DC}[1]{\textcolor{red}{#1}}
- \setcounter{topnumber}{2}
- \setcounter{bottomnumber}{2}
- \setcounter{totalnumber}{4}
- \renewcommand{\topfraction}{0.85}
- \renewcommand{\bottomfraction}{0.85}
- \renewcommand{\textfraction}{0.15}
- \renewcommand{\floatpagefraction}{0.7}
- \def\wpd{\text{\textit{wpd}}}
- \def\wpdsub#1{\text{\textit{wpd}}_{\text{#1}}}
- \def\Dnull{D_{\emptyset}}
- \def\Df{D_{\!f}}
- \def\Dfx{D_{\!fx}}
- \def\Dx{D_{x}}
- \def\nsub#1{n_{\text{#1}}}
- \def\nx{n_x}
- \def\nf{n_{\!f}}
-
-output:
- bookdown::pdf_book:
-  base_format: rticles::asa_article
-  fig_height: 5
-  fig_width: 8
-  fig_caption: yes
-  dev: "pdf"
-  keep_tex: yes
----
-
-```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
-options("knitr.graphics.auto_pdf" = TRUE,
-    tinytex.verbose = FALSE)
+```{r setup, echo = FALSE, cache = FALSE, include = FALSE}
+options(
+  "knitr.graphics.auto_pdf" = TRUE,
+  tinytex.verbose = FALSE
+)
 library(knitr)
 opts_chunk$set(
- echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
- fig.path = "figure/", fig.align = "center", fig.show = "hold",
- cache = TRUE, cache.path = "cache/",
- out.width = ifelse(is_html_output(), "100%", "\\textwidth")
+  echo = FALSE,
+  warning = FALSE,
+  message = FALSE,
+  comment = "#>",
+  fig.path = "figure/",
+  fig.align = "center",
+  fig.show = "hold",
+  cache = TRUE,
+  cache.path = "cache/",
+  out.width = ifelse(is_html_output(), "100%", "\\textwidth"),
+  root.dir = here::here()
 )
-knitr::opts_knit$set(root.dir = here::here())
-#                           read_chunk('main.R')
-#knitr::read_chunk(here::here("paper/R/", "null_distribution.R"))
-#knitr::read_chunk(here::here("paper/R/", "mean_null.R"))
-#source(here::here("paper/R/sim_panel.R"))
-# Set up plan
-#source("_drake.R")
-# Run all code required
-#drake::r_make()
-# load each object as required
-# loadd()
-```
 
 ```{r external, include = FALSE, cache = FALSE}
-read_chunk("paper/scripts/main.R")
+read_chunk(here::here("paper/scripts/main.R"))
 ```
@@
 
-Cyclic temporal granularities [@Bettini1998-ed, @Gupta2021-hd] are <!--theoretical--> temporal deconstructions that define cyclic repetitions in time, e.g.
+Cyclic temporal granularities [@Bettini1998-ed;@Gupta2021-hd] are <!--theoretical--> temporal deconstructions that define cyclic repetitions in time, e.g.
 hour-of-day, day-of-month, or regularly scheduled public holidays.
@@
 
-```{r raw, fig.cap = "(ref:raw)", fig.pos="!b"}
+```{r raw, fig.cap = "(ref:raw)", fig.pos="!htb"}
 ```
@@
 The Github repository, [github.com/Sayani07/paper-hakear](https://github.com/Sayani07/paper-gravitas), contains all materials required to reproduce this article and the code is also available online in the supplemental materials.
-This article was created with R [@R-language], `knitr` [@knitr2015, @R-knitr] and `rmarkdown` [@rmarkdown2018, @R-rmarkdown].
+This article was created with R [@R-language], `knitr` [@knitr2015;@R-knitr] and `rmarkdown` [@rmarkdown2018;@R-rmarkdown].
 Graphics are produced with `ggplot2` [@Wickham2009pk].
@@
 
-# Bibliography
-
 ```{r write-bib, eval = FALSE}

### 2021-11-03 paper/preamble.tex
Added preamble.tex

\setlength {\marginparwidth }{2cm}
\usepackage{mathtools,amssymb,booktabs,amsthm,todonotes,colortbl}
\def\mod{~\text{mod}~}
\usepackage{mathptmx}
\usepackage{caption,setspace}
\usepackage[section]{placeins}
\usepackage{longtable}
\DeclareCaptionStyle{italic}{labelfont={bf},textfont={it},labelsep=colon}
\captionsetup[figure]{style=italic,format=hang,singlelinecheck=true,font={stretch=1.2}}
\captionsetup[table]{style=italic,format=hang,singlelinecheck=true,font={stretch=1.2}}
\def\novspacing{\setlength{\aboverulesep}{0pt}\setlength{\belowrulesep}{0pt}}
\def\vspacing{\setlength{\aboverulesep}{0.4ex}\setlength{\belowrulesep}{0.65ex}}
\newcommand{\DC}[1]{#1}
\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.85}
\renewcommand{\textfraction}{0.15}
\renewcommand{\floatpagefraction}{0.7}
\def\wpd{\text{\textit{wpd}}}
\def\wpdsub#1{\text{\textit{wpd}}_{\text{#1}}}
\def\Dnull{D_{\emptyset}}
\def\Df{D_{\!f}}
\def\Dfx{D_{\!fx}}
\def\Dx{D_{x}}
\def\nsub#1{n_{\text{#1}}}
\def\nx{n_x}
\def\nf{n_{\!f}}

%% LINE AND PAGE BREAKING
\sloppy
\clubpenalty = 10000
\widowpenalty = 10000
\brokenpenalty = 10000
\RequirePackage{microtype}

### 2021-11-10 paper/main.Rmd
link update from gravitas to hakear

@@
 Sayani Gupta was partially funded by [Data61 CSIRO](https://data61.csiro.au/) during her PhD.
-The Github repository, [github.com/Sayani07/paper-hakear](https://github.com/Sayani07/paper-gravitas), contains all materials required to reproduce this article and the code is also available online in the supplemental materials.
+The Github repository, [github.com/Sayani07/paper-hakear](https://github.com/Sayani07/paper-hakear), contains all materials required to reproduce this article and the code is also available online in the supplemental materials.
 This article was created with R [@R-language], `knitr` [@knitr2015;@R-knitr] and `rmarkdown` [@rmarkdown2018;@R-rmarkdown].

### 2021-11-16 paper/paper-supplementary.Rmd
making notations consistent with paper - continue part 2

@@
     keep_tex: yes
+    number_sections: yes
+    citation_package: biblatex
+    includes:
+      in_header: preamble.tex
 ---
@@
 The number of cyclic granularities considered in the display (at once) is $m$.
-Consider cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$.
+Consider cyclic granularities $A$ and $B$, such that $A = \{a_j: j = 1, 2, \dots, \nx\}$ and $B = \{b_k: k = 1, 2, \dots, \nf\}$.
 For $m=1$, only one of $A$ or $B$ is plotted at once and a _panel_ refers to a display of distributions of $v$ across $J$ or $K$ levels on the x-axis.
-For $m=2$, the distribution display of $v$ with $A$ placed across x-axis and $B$ across facets is referred to as a $(J, K)$ _panel_ ($J$ x-axis levels and $K$ facet levels).
+For $m=2$, the distribution display of $v$ with $A$ placed across x-axis and $B$ across facets is referred to as a $(\nx, \nf)$ _panel_ ($\nx$ x-axis levels and $\nf$ facet levels).
 The pairwise distances between pairs ($a_jb_k,a_j'b_k'$) could be within-facets or between-facets as seen in Figure 4 of the main paper.
 The tuning parameter, used to put relative weight-age to the pairwise distances within and between facets is denoted by $\lambda$.
-Let the four elementary designs be $D_{null}$ where there is no pairwise difference in distribution of $v$ across $A$ or $B$, $D_{var_f}$ denotes the set of designs where there is difference in distribution of $v$ for $B$ and not for $A$.
-Similarly, $D_{var_x}$ denotes the set of designs where difference is observed only across $A$.
-Finally, $D_{var_{all}}$ denotes those designs for which difference is observed across both $A$ and $B$.
-The following method is deployed for generating different distributions across different combinations for non-null designs - suppose the distribution of the combination of first levels of x and facet category is $N(\mu,\sigma)$ and $\mu_{jk}$ denotes the mean of the combination $(a_jb_k)$, then $\mu_{j.} = \mu + j\omega$ (for design $D_{var_x}$) and $\mu_{.k} = \mu + k\omega$ (for design $D_{var_f}$), where $\omega$ denotes the increment in mean.
+Let the four elementary designs be $\\Dnull$ where there is no pairwise difference in distribution of $v$ across $A$ or $B$, $\\Df$ denotes the set of designs where there is difference in distribution of $v$ for $B$ and not for $A$.
+Similarly, $\\Dx$ denotes the set of designs where difference is observed only across $A$.
+Finally, $\\Dfx$ denotes those designs for which difference is observed across both $A$ and $B$.
+The following method is deployed for generating different distributions across different combinations for non-null designs - suppose the distribution of the combination of first levels of x and facet category is $N(\mu,\sigma)$ and $\mu_{jk}$ denotes the mean of the combination $(a_jb_k)$, then $\mu_{j.} = \mu + j\omega$ (for design $\\Dx$) and $\mu_{.k} = \mu + k\omega$ (for design $\\Df$), where $\omega$ denotes the increment in mean.
 Table \ref{tab:explain-design} shows an example of how designs are defined for a $(2, 3)$ panel using $\omega = 3$.
-$nx$ and $nfacet$ denotes the number of categories placed on x-axis and facets respectively.
-$wpd_{raw}$ and $wpd$ denote the raw and normalized weighted pairwise distances.
+$\\nx$ and $\\nf$ denotes the number of categories placed on x-axis and facets respectively.
+$\wpdsub{raw}$ and $\wpd$ denote the raw and normalized weighted pairwise distances.
 
@@
   tibble() 
-names(raw_table) = c("x levels", "facet levels", "$D_{null}$",  "$D_{var_f}$", "$D_{var_x}$", "$D_{var_{all}}$" )
+names(raw_table) = c("x levels", "facet levels", "$\\Dnull$",  "$\\Df$", "$\\Dx$", "$\\Dfx$" )
 raw_table %>% 
@@
 So no tuning parameter is applicable for this case.
-For $m=2$, $\lambda$ might impact $wpd_{raw}$ differently depending on the value of $\omega$ and different values of $nx$, $nfacet$ and designs.
-The following simulation study sees the impact of $\lambda$ for different $\omega$, $nx$, $nfacet$ and designs.
+For $m=2$, $\lambda$ might impact $\wpdsub{raw}$ differently depending on the value of $\omega$ and different values of $\\nx$, $\\nf$ and designs.
+The following simulation study sees the impact of $\lambda$ for different $\omega$, $\\nx$, $\\nf$ and designs.
 
@@
 
-Observations are generated from N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7\}$ and $wpd_{raw}$ is computed for $\lambda = {0.1, 0.2, \dots, 0.9}$ under two designs $D_{var_x}$ and $D_{var_f}$ for $\omega = \{1, 8\}$  to observe how the value of $wpd_{raw}$ changes for different designs.
-Moreover, to observe for which value of $\lambda$ the two designs intersect, we generate observations from N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20\}$ and $\omega = \{1, 2, \dots, 10\}$ under the same two designs.
+Observations are generated from N(0,1) distribution for each combination of $\\nx$ and $\\nf$ from the following sets: $nx = nfacet = \{2, 3, 5, 7\}$ and $\wpdsub{raw}$ is computed for $\lambda = {0.1, 0.2, \dots, 0.9}$ under two designs $\\Dx$ and $\\Df$ for $\omega = \{1, 8\}$  to observe how the value of $\wpdsub{raw}$ changes for different designs.
+Moreover, to observe for which value of $\lambda$ the two designs intersect, we generate observations from N(0,1) distribution for each combination of $\\nx$ and $\\nf$ from the following sets: $\nx\ \in \{2, 3, 5, 7, 14, 20\}$, $\nf\ \in \{2, 3, 5, 7, 14, 20\}$ and $\omega = \{1, 2, \dots, 10\}$ under the same two designs.
 
-<!-- and the values of $wpd$ is computed for all these different values of the variables $nx$, $nfacet$, $\lambda$ and $\omega$ under two different designs $D_{var_x}$ and $D_{var_f}$ .  -->
+<!-- and the values of $\wpd$ is computed for all these different values of the variables $\\nx$, $\\nf$, $\lambda$ and $\omega$ under two different designs $\\Dx$ and $\\Df$ .  -->
 
@@
 
-Figure \ref{fig:tuning-oneomega} shows how the value of $wpd$ changes for $\lambda = {0.1, 0.2, \dots, 0.9}$ for the two different designs $D_{var_x}$ and $D_{var_f}$ for two values of increment in mean $\omega = {1, 8}$.
+Figure \ref{fig:tuning-oneomega} shows how the value of $\\wpd$ changes for $\lambda = {0.1, 0.2, \dots, 0.9}$ for the two different designs $\\Dx$ and $\\Df$ for two values of increment in mean $\omega = {1, 8}$.
 For a lower value of $\omega$, the two designs intersect at $\lambda > 0.7$ and for a higher $\omega$, the two designs intersect at $\lambda =  0.5$.
-The value of $wpd$ increases with $\lambda$ for $D_{var_x}$ and decreases with increasing $\lambda$ for $D_{var_f}$.
+The value of $\wpd$ increases with $\lambda$ for $\\Dx$ and decreases with increasing $\lambda$ for $\\Df$.
 \noindent Figure \ref{fig:tuning-parameter-inter} shows the value of $\lambda$ for which the two designs intersect for different values of $\omega$.
@@
 
-```{r tuning-oneomega, fig.cap = " $wpd_{raw}$ from two designs are plotted for different values of $\\lambda$ $nx$ and $nfacet$.
+```{r tuning-oneomega, fig.cap = " $\\wpdsub{raw}$ from two designs are plotted for different values of $\\lambda$ $\\nx$ and $\\nf$.
 For $\\omega = 1$, the designs intersect for $0.6<\\lambda<=0.75$, whereas for higher omega, design intersects at $\\lambda = 0.5$."}
@@
 
-```{r tuning-parameter-inter, fig.cap ="The point of intersection of $wpd_{raw}$ values under the designs $D_{var_f}$ and $D_{var_x}$ are plotted across different $\\omega$ and $\\lambda$.
+```{r tuning-parameter-inter, fig.cap ="The point of intersection of $\\wpdsub{raw}$ values under the designs $\\Df$ and $\\Dx$ are plotted across different $\\omega$ and $\\lambda$.
 For most panels it is observed that a common value of $\\lambda$ for which the designs interact is $0.5$ for $\\omega >= 4$, which implies any value greater than $0.5$ could be chosen to up-weigh the within-facet distances and down-weigh the between-facet distances.
@@
 
-The following simulation study sees the impact of different underlying distributions on $wpd_{raw}$ for different $nx$ and $nfacet$ before and after performing Normal Quantile Transformation.
+The following simulation study sees the impact of different underlying distributions on $\wpdsub{raw}$ for different $\\nx$ and $\\nf$ before and after performing Normal Quantile Transformation.
 
@@
 
-Observations are generated from N(0,1), N(5, 1), N(0, 5), Gamma(0.5, 1) and Gamma(2, 1) distributions for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ and $wpd_{raw}$ is computed with $\lambda = 0.67$ with (scenario 1) and without (scenario 2) NQT.
+Observations are generated from N(0,1), N(5, 1), N(0, 5), Gamma(0.5, 1) and Gamma(2, 1) distributions for each combination of $\\nx$ and $\\nf$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ and $\wpdsub{raw}$ is computed with $\lambda = 0.67$ with (scenario 1) and without (scenario 2) NQT.
 
@@
 
-Figure \ref{fig:gamma-diff-wotrans} shows ridge plots of $wpd_{raw}$ for a Gamma(0.5,1), Gamma(2,1) before NQT.
+Figure \ref{fig:gamma-diff-wotrans} shows ridge plots of $\wpdsub{raw}$ for a Gamma(0.5,1), Gamma(2,1) before NQT.
 It is observed that for the underlying distribution Gamma(2,1), location and scale of the distribution of wpd changes from top-left panel to bottom-right panel.
-Figure \ref{fig:gamma-diff-quantrans} shows the the distributions of $wpd$ under same underlying distributions after performing NQT.
-It is observed that within each panel, the distributions of the $wpd$ looks same, however, the distributions change from extreme top-left panel to bottom-right panels.
+Figure \ref{fig:gamma-diff-quantrans} shows the the distributions of $\wpd$ under same underlying distributions after performing NQT.
+It is observed that within each panel, the distributions of the $\wpd$ looks same, however, the distributions change from extreme top-left panel to bottom-right panels.
 Similar observations could be made in Figure \ref{fig:normal-diff-quantrans} for different underlying normal distributions  N(0,1), N(5,1) and N(0,5).
-This implies, NQT has atleast been able to make the location and scale of the distribution of $wpd_{raw}$ same for different underlying distributions.
+This implies, NQT has atleast been able to make the location and scale of the distribution of $\wpdsub{raw}$ same for different underlying distributions.
 
-<!-- Since the measure $wpd$ is essentially set up to detect "differences" in distributions irrespective of underlying distribution, it would be ideal if it has minimal dependency on the type, location and scale of the initial distribution.
+<!-- Since the measure $\wpd$ is essentially set up to detect "differences" in distributions irrespective of underlying distribution, it would be ideal if it has minimal dependency on the type, location and scale of the initial distribution.
 To that end, some data pre-processing through the Normal Score Transform (NQT) has been applied in order to make most asymmetrical distributed measured variables more normal-like.
@@
 $ntimes = 500$ observations are drawn for each combination of the categories, that is, for a panel with $nx=3$, $500$ observations are simulated for each of the categories.
-This design corresponds to $D_{null}$ as each combination of categories in a panel are drawn from the same distribution.
-Furthermore, the data is simulated for each of the categories $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
-The values of $wpd$ is obtained for each of the panels.
-$wpd_{l, s}$ denotes the value of $wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.
+This design corresponds to $\\Dnull$ as each combination of categories in a panel are drawn from the same distribution.
+Furthermore, the data is simulated for each of the categories $nsim=200$ times, so that the distribution of $\wpd$ under $\\Dnull$ could be observed.
+The values of $\wpd$ is obtained for each of the panels.
+$wpd_{l, s}$ denotes the value of $\wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.
 
@@
 
-Figure \ref{fig:nxbyfacet-ridge-N01-onegran} shows ridge plots of $wpd_{raw}$ for an underlying N(0,1) distribution.
+Figure \ref{fig:nxbyfacet-ridge-N01-onegran} shows ridge plots of $\wpdsub{raw}$ for an underlying N(0,1) distribution.
 For each panel, it could be seen that the location shifts to the right for increasing x levels.
-Across each panel, the scale of the distribution seems to change for low/moderately from lower values  to higher values of $nx$ and left tails are longer for lower facet levels.
+Across each panel, the scale of the distribution seems to change for low/moderately from lower values  to higher values of $\\nx$ and left tails are longer for lower facet levels.
 
@@
 
-\noindent Similarly, observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$.
+\noindent Similarly, observations are generated from a N(0,1) distribution for each combination of $\\nx$ and $\\nf$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$.
 That is, data is being generated for each of the panels $(2, 2), (2, 3), (2, 5) \dots, (50, 31), (50, 50)$.
@@
 
-<!-- Observations are generated from Gamma(2,1), G(0.5, 1), N(0,1), N(0, 5) and N(5, 1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
+<!-- Observations are generated from Gamma(2,1), G(0.5, 1), N(0,1), N(0, 5) and N(5, 1) distribution for each combination of $\\nx$ and $\\nf$ from the following sets: $nx = nfacet = \{2, 3, 5, 7, 14, 20, 31, 50\}$ to cover a wide range of levels from very low to moderately high.
 Each combination is being referred to as a _panel_.
@@
 The values -->
-<!-- of $wpd$ is obtained for each of the panels.
-The measurement variable for each combination of categories in a panel are drawn from the same distribution and hence the design corresponds to $D_{null}$ .
-Furthermore, this entire method is repeated for each panels $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
+<!-- of $\wpd$ is obtained for each of the panels.
+The measurement variable for each combination of categories in a panel are drawn from the same distribution and hence the design corresponds to $\\Dnull$ .
+Furthermore, this entire method is repeated for each panels $nsim=200$ times, so that the distribution of $\wpd$ under $\\Dnull$ could be observed.
 -->
@@
 
-Figures \ref{fig:nxbyfacet-ridge-N01}, \ref{fig:nfacetbynx} and  \ref{fig:density-raw} shows the ridge plot of $wpd_{raw}$ with $nx$ as facets, $nfacet$ as facets and the density plot of $wpd_{raw}$ with $nx$ on the x-axis and $nfacet$ on the facets.
+Figures \ref{fig:nxbyfacet-ridge-N01}, \ref{fig:nfacetbynx} and  \ref{fig:density-raw} shows the ridge plot of $\wpdsub{raw}$ with $\\nx$ as facets, $\\nf$ as facets and the density plot of $\wpdsub{raw}$ with $\\nx$ on the x-axis and $\\nf$ on the facets.
 The right-ward shift in location can be clearly observed from all figures.
@@
 Simulation design is the same as for raw weighted pairwise distances for $m=1$ and $m=2$.
-In place of $wpd_{raw}$, $wpd_{perm}$, $wpd_{glm}$ and $wpd$ is computed for all panels.
+In place of $\wpdsub{raw}$, $\wpdsub{perm}$, $wpd_{glm}$ and $\wpd$ is computed for all panels.
 
@@
 $ntimes = 500$ observations are drawn for each combination of the categories, that is, for a panel with $nx=3$, $500$ observations are simulated for each of the categories.
-This design corresponds to $D_{null}$ as each combination of categories in a panel are drawn from the same distribution.
-Furthermore, the data is simulated for each of the categories $nsim=200$ times, so that the distribution of $wpd$ under $D_{null}$ could be observed.
-The values of $wpd$ is obtained for each of the panels.
-$wpd_{l, s}$ denotes the value of $wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.
+This design corresponds to $\\Dnull$ as each combination of categories in a panel are drawn from the same distribution.
+Furthermore, the data is simulated for each of the categories $nsim=200$ times, so that the distribution of $\wpd$ under $\\Dnull$ could be observed.
+The values of $\wpd$ is obtained for each of the panels.
+$wpd_{l, s}$ denotes the value of $\wpd$ obtained for the $l^{th}$ panel and $s^{th}$ simulation.
 -->
@@
 Figure \ref{fig:one-gran-nxnyfacet} and \ref{fig:norm} show the normalized ${wpd}$ for $m=1$ and $m=2$ respectively.
-The location and scale of the distribution of ${wpd}$ is similar for increasing values of $nx$ or $nfacet$.
-Due to heavy computational load, $wpd_{perm}$ for few panels with very high value of $nx$ or $nfacet$ are not computed.
+The location and scale of the distribution of ${wpd}$ is similar for increasing values of $\\nx$ or $\\nf$.
+Due to heavy computational load, $\wpdsub{perm}$ for few panels with very high value of $\\nx$ or $\\nf$ are not computed.
 
-```{r one-gran-nxnyfacet, fig.cap="Distribution of $wpd_{perm}$ are shown for different levels for $m=1$ under the null design. The distribution for different panels have similar location and scale."}
+```{r one-gran-nxnyfacet, fig.cap="Distribution of $\\wpdsub{perm}$ are shown for different levels for $m=1$ under the null design.
+The distribution for different panels have similar location and scale."}
 include_graphics(here("simulations/supplementary/one-gran/norm/null_design_quantrans_nperm/figs/nxbyfacet_ridge_wpd_N01.png"))
@@
 
-```{r norm, fig.cap = "Distribution of $wpd_{perm}$ are shown for different levels for $m=2$ under the null design. The distribution for different panels have similar location and scale."}
+```{r norm, fig.cap = "Distribution of $\\wpdsub{perm}$ are shown for different levels for $m=2$ under the null design. The distribution for different panels have similar location and scale."}
 G21_norm <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds"))
@@
 
-For for $m=1$, Figure \ref{fig:glm-horizontal-onegran1} shows the scatterplot of $wpd_{raw}$ against different values of $nx$ and also the display of residuals from the model and Figure \ref{fig:glm-density-onegran} shows the distribution of $wpd_{glm}$ for different $nx$.
-For $m=2$, Figure \ref{fig:glm-horizontal-twogran1} shows the scatter plot of $wpd_{raw}$ against different values of $nx$ and $nfacet$ and also the display of residuals from the model.
-Figure \ref{fig:wpd-glm-dist} shows the distribution of $wpd_{glm}$ for different $nx$ and $nfacet$.
+For for $m=1$, Figure \ref{fig:glm-horizontal-onegran1} shows the scatterplot of $\wpdsub{raw}$ against different values of $\\nx$ and also the display of residuals from the model and Figure \ref{fig:glm-density-onegran} shows the distribution of $wpd_{glm}$ for different $\\nx$.
+For $m=2$, Figure \ref{fig:glm-horizontal-twogran1} shows the scatter plot of $\wpdsub{raw}$ against different values of $\\nx$ and $\\nf$ and also the display of residuals from the model.
+Figure \ref{fig:wpd-glm-dist} shows the distribution of $wpd_{glm}$ for different $\\nx$ and $\\nf$.
 Tables \ref{tab:tab-modelsm1} and \ref{tab:tab-models} show the GLM results for $m=1$ and $m=2$ respectively.
@@
          statistic = round(statistic, 2),
-         p.value = round(p.value, 2)) %>% kable(caption = "Results of generalised linear model to capture the relationship between $wpd_{raw}$ and number of comparisons for $m=1$.")
+         p.value = round(p.value, 2)) %>% kable(caption = "Results of generalised linear model to capture the relationship between $\\wpdsub{raw}$ and number of comparisons for $m=1$.")
 
@@
 
-```{r glm-horizontal-onegran1, fig.cap = "$wpd_{raw}$ (points) and residuals (blue line) from the model is plotted across different number of comparisons for $m=1$.
-Residuals seem to be independent of $nx$ and have been defined as $wpd_{glm}$."}
+```{r glm-horizontal-onegran1, fig.cap = "$\\wpdsub{raw}$ (points) and residuals (blue line) from the model is plotted across different number of comparisons for $m=1$.
+Residuals seem to be independent of $\\nx$ and have been defined as $wpd_{glm}$."}
 knitr::include_graphics(here("paper/figs/G21_horizontal.png"))
@@
 
-```{r glm-density-onegran, fig.cap = "Distribution of $wpd_{glm}$ is plotted across different $nx$ for $m=1$.
-Both shape and location of the distributions are different for lower $nx$ than for higher $nx$."}
+```{r glm-density-onegran, fig.cap = "Distribution of $wpd_{glm}$ is plotted across different $\\nx$ for $m=1$.
+Both shape and location of the distributions are different for lower $\\nx$ than for higher $\\nx$."}
 G21_glm_m1 <- G21 %>% 
@@
 
-tidy_obs %>% kable(caption = "Results of generalised linear model to capture the relationship between $wpd_{raw}$ and number of comparisons for different underlying distribution.")
+tidy_obs %>% kable(caption = "Results of generalised linear model to capture the relationship between $\\wpdsub{raw}$ and number of comparisons for different underlying distribution.")
 ```
@@
 
-```{r glm-horizontal-twogran, fig.cap = "Residuals from the model is plotted across different $nx$ and $nfacet$.
+```{r glm-horizontal-twogran, fig.cap = "Residuals from the model is plotted across different $\\nx$ and $\\nf$.
 Residuals seem to be independent of $log(nx*nfacet)$ and have been defined as $wpd_{glm}$ in the paper."}
@@
 
-# broom::tidy(glm_fit) %>% kable(caption = "Results of generalised linear model to capture the relationship between $wpd_{raw}$ and number of comparisons.")
+# broom::tidy(glm_fit) %>% kable(caption = "Results of generalised linear model to capture the relationship between $\\wpdsub{raw}$ and number of comparisons.")
 
@@
 
-```{r glm-horizontal-twogran1, fig.cap = "$wpd_{raw}$ (points) and residuals (blue line) from the model is plotted across different number of comparisons for $m=2$.
-Residuals seem to be independent of $nx$ and have been defined as $wpd_{glm}$."}
+```{r glm-horizontal-twogran1, fig.cap = "$\\wpdsub{raw}$ (points) and residuals (blue line) from the model is plotted across different number of comparisons for $m=2$.
+Residuals seem to be independent of $\\nx$ and have been defined as $wpd_{glm}$."}
 knitr::include_graphics(here("paper/figs/G21_horizontal_m2.png"))
@@
 
-```{r wpd-glm-dist, fig.cap = "Distribution of $wpd_{glm}$ is plotted across different $nx$ for $m=2$. Both shape and scale of the distributions are different for lower $nx$ than for higher $nx$."}
+```{r wpd-glm-dist, fig.cap = "Distribution of $wpd_{glm}$ is plotted across different $\\nx$ for $m=2$.
+Both shape and scale of the distributions are different for lower $\\nx$ than for higher $\\nx$."}
 G21_glm <- G21 %>% 
@@
 
-Figure \ref{fig:dist-same-scale-onegran} and \ref{fig:dist-new-same-scale-link} show the distribution of $wpd_{perm}$ and $wpd_{glm-scaled}$ overlaid on each other for $m=1$ and $m=2$ respectively.
-$wpd$ takes the value of $wpd_{perm}$ for lower levels
+Figure \ref{fig:dist-same-scale-onegran} and \ref{fig:dist-new-same-scale-link} show the distribution of $\wpdsub{perm}$ and $wpd_{glm-scaled}$ overlaid on each other for $m=1$ and $m=2$ respectively.
+$\wpd$ takes the value of $\wpdsub{perm}$ for lower levels
 $(<=5)$, and $wpd_{glm-scaled}$ for higher levels so that we have similar location and scale across panels with different levels.
 
-```{r dist-same-scale-onegran, fig.cap = "The distribution of $wpd_{perm}$ and $wpd_{glm-scaled}$ are overlaid to compare the location and scale across different $nx$ for $m=1$.
+```{r dist-same-scale-onegran, fig.cap = "The distribution of $\\wpdsub{perm}$ and $wpd_{glm-scaled}$ are overlaid to compare the location and scale across different $\\nx$ for $m=1$.
 The distribution of the adjusted measure looks similar for both approaches for higher levels, but for $nx=2$ both location and scale differs."}
@@
 
-```{r dist-new-same-scale-link, fig.cap = "The distribution of $wpd_{perm}$ and $wpd_{glm-scaled}$ are overlaid to compare the location and scale across different $nx$ and $nfacet$ for $m=2$.
-$wpd$ takes the value of $wpd_{perm}$ for lower levels, and $wpd_{glm-scaled}$ for higher levels.
+```{r dist-new-same-scale-link, fig.cap = "The distribution of $\\wpdsub{perm}$ and $wpd_{glm-scaled}$ are overlaid to compare the location and scale across different $\\nx$ and $\\nf$ for $m=2$.
+$\\wpd$ takes the value of $\\wpdsub{perm}$ for lower levels, and $wpd_{glm-scaled}$ for higher levels.
 "}
@@
 
-Observations are generated from a N(0,1) distribution for each combination of $nx$ and $nfacet$ from the following sets: $nx = \{3, 7, 14\}$ and $nfacet = \{2, 9, 10\}$.
+Observations are generated from a N(0,1) distribution for each combination of $\\nx$ and $\\nf$ from the following sets: $nx = \{3, 7, 14\}$ and $nfacet = \{2, 9, 10\}$.
 This would result in 9 panels, viz, $(3, 2), (3, 9), (3, 10), \dots, (14,9), (14, 10)$.
 Few experiments were conducted.
-In the first scenario, data for all panels are simulated using the null design $D_{null}$.
+In the first scenario, data for all panels are simulated using the null design $\\Dnull$.
 In other scenarios, data simulated from the panel $(14, 2)$ and $(3, 10)$ are under $D_{vary_{all}}$.
 Moreover, $\omega = \{0.5, 2, 5\}$ are considered to examine if the proposed test is able to capture subtle differences and non-subtle differences when we shift from the null design.
-In the last scenario, we consider the panel $(3, 2), (7,9), (14, 10)$ to be under $D_{null}$, the panels $(7, 2), (14, 9)$ to be under $D_{var_f}$.
-$(14, 2), (3, 10)$ under $D_{var_x}$ and the rest under $D_{var_{null}}$.
+In the last scenario, we consider the panel $(3, 2), (7,9), (14, 10)$ to be under $\\Dnull$, the panels $(7, 2), (14, 9)$ to be under $\\Df$.
+$(14, 2), (3, 10)$ under $\\Dx$ and the rest under $D_{var_{null}}$.
 This is done to check if the consequent ranking procedure leads to designs like $D_{vary_{f}}$ rank below $D_{vary_{all}}$.
@@
 
-Figure \ref{fig:foo} shows the distribution of $wpd$ for the simulated $9$ null designs of different levels with each harmony being rejected if the corresponding $wpd$ value is higher than $wpd_{threshold99}$.
+Figure \ref{fig:foo} shows the distribution of $\wpd$ for the simulated $9$ null designs of different levels with each harmony being rejected if the corresponding $\wpd$ value is higher than $\wpdsub{threshold99}$.
 Although the level of significance for each test is 1%, the level of significance for multiple tests together is 10% as displayed through the red line.
@@
 
-<!-- $wpd_{threshold99}$ is obtained as `r round(global_threshold$value, 2)` for this experiment, which leads to a p-value of `r round(data_summary$p_value, 3)`.
-Figure \ref{fig:global-size} shows the distribution of $wpd$ obtained from this experiment with the red line denoting $wpd_{threshold99}$.
-If we split the display of distribution between $nx$ and $nfacet$, then Figure \ref{fig:local-size} shows that the probability of rejecting the null when it is actually true is higher for smaller levels, however, it is still within limits (around `r round(data_summary_lowlev$p_value, 3)`).
+<!-- \wpdsub{threshold99}$, is obtained as `r round(global_threshold$value, 2)` for this experiment, which leads to a p-value of `r round(data_summary$p_value, 3)`.
+Figure \ref{fig:global-size} shows the distribution of $\wpd$ obtained from this experiment with the red line denoting \wpdsub{threshold99}$.
+If we split the display of distribution between $\\nx$ and $\\nf$, then Figure \ref{fig:local-size} shows that the probability of rejecting the null when it is actually true is higher for smaller levels, however, it is still within limits (around `r round(data_summary_lowlev$p_value, 3)`).
 -->
 
-(ref:foo) The distribution of $wpd$ for 9 null designs of different levels with each harmony being rejected if the corresponding $wpd$ value is higher than $wpd_{threshold99}$.
+(ref:foo) The distribution of $\wpd$ for 9 null designs of different levels with each harmony being rejected if the corresponding $\wpd$ value is higher than $\wpdsub{threshold99}$.
 Although the level of significance for each test is 1%, the level of significance for multiple tests together is 10% as displayed through the red line.
@@
 
-```{r quadratic, fig.cap = "$wpd$ is plotted against $nx*nfacet$ (the maximum number of pairwise comparisons) and the blue line represents the median of the multiple values for each $nx*nfacet$.
+```{r quadratic, fig.cap = "$\\wpd$ is plotted against $nx*nfacet$ (the maximum number of pairwise comparisons) and the blue line represents the median of the multiple values for each $nx*nfacet$.
 The median increases abruptly for lower values of $nx*nfacet$ and slowly for higher $nx*nfacet$.
-Thus, the measure will have higher values for higher levels in $nx$ or $nfacet$.", eval = FALSE}
+Thus, the measure will have higher values for higher levels in $\\nx$ or $\\nf$.", eval = FALSE}
 ```
@@
 
-<!-- \noindent where $y_l = median_s(wpd_{l, s})$, $wpd_{l, s}$ denotes the value of $wpd_{raw}$ obtained for the $l^{th}$ panel and $s^{th}$ simulation, $z_l$ is the number of groups $(nx*nfacet)$ in the $l^{th}$ panel and $e_l$ are idiosyncratic errors.
+<!-- \noindent where $y_l = median_s(wpd_{l, s})$, $wpd_{l, s}$ denotes the value of $\wpdsub{raw}$ obtained for the $l^{th}$ panel and $s^{th}$ simulation, $z_l$ is the number of groups $(nx*nfacet)$ in the $l^{th}$ panel and $e_l$ are idiosyncratic errors.
 Let $E(y) = \mu$ and $a + b*log(z) = g(\mu)$ where $g$ is the link function.

### 2022-02-28 paper/paper-supplementary.Rmd
supplementary paper update

@@
          statistic = round(statistic, 2),
-         p.value = round(p.value, 2)) %>% kable(caption = "Results of generalised linear model to capture the relationship between $\\wpdsub{raw}$ and number of comparisons for $m=1$.")
+         #p.value = round(p.value, 2)
+         p.value = "<.001") %>% kable(caption = "Results of generalised linear model to capture the relationship between $\\wpdsub{raw}$ and number of comparisons for $m=1$.")
 
